### 2022-07-01 02_paper/02_study/paper_methods.Rmd
method section

---
title             : "Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions"
shorttitle        : "Professional Vision in Micro-Teaching-Units"

author: 
  - name          : "Mandy Klatt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Dittrichring 5-7, 04109 Leipzig"
    email         : "mandy.klatt@uni-leipzig.de"
  - name          : "Dr. Gregor Kachel"
    affiliation   : "1, 2"
  - name          : "Dr. Christin Lotz"
    affiliation   : "1"
  - name          : "Prof. Dr. Anne Deiglmayr"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Leipzig University"
  - id            : "2"
    institution   : "Max Planck Institute for Evolutionary Anthropology"

authornote: |

  We received funding from QualiFond of University Leipzig. We have no conflicts of interest to disclose. This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).

abstract: |

keywords          : "professional vision, expertise, classroom management, mobile eye-tracking"
wordcount         : "XXX"

bibliography      : ["r-references.bib"]

floatsintext      : no
figsintext        : no
figurelist        : no
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
# bookdown::word_document2
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = FALSE)
library("papaja")
r_refs(file = "r-references.bib")
```

```{r analysis-preferences, include=FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r include=FALSE}
# install.packages("needs")

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

library(needs)

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable)

```

# Introduction

Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson & Weinstein, 2006; Kounin, 2006). Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom. This ability is referred to as classroom professional vision (Goodwin, 1994; Sherin, 2007). The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (“noticing”) and applying knowledge to draw appropriate conclusions in these situations (“knowledge-based reasoning”; Seidel & Stürmer, 2014). Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students’ learning time and minimize classroom interruptions. According to Kounin (2006), these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring (Gold & Holodynski, 2017). Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017). Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, “[…] whereas only a few studies have focused on the basal process of noticing, i.e. the recognition of possible disturbing situations” (Grub et al., 2020, p.75). Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner et al., 2016; Wolff et al., 2016).

# Theoretical background

## Professional competence in teaching profession

Competence is a common term in everyday school life. In most cases, it refers to the acquisition of competencies by students and how to promote them and make them effective. In the same way, the term competence can be applied to teachers. Teachers have to be competent in things such as teaching, educating, evaluating or innovating. Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig & Rauch, 2008). They replace the rigid canon of knowledge that defined professional qualification for generations. In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.). To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf. Klieme et al., 2008, p. 4). In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.

In science, there is some agreement on the two opposing perspectives of competence versus empowerment. The former means a broad, concept, whereas empowerment refers to the different components of competence (cf. of competence (cf. Blömeke, Gustafsson & Shavelson, 2015, p.5). These can be of a cognitive, conative, affective, or motivational nature (ibid.). To determining professional qualification, competence is an irreplaceable tool.

Competence is learnable and can thus be improved through targeted practice (cf. Weinert 2001; cited in Blömeke et al. 2015, p. 5). This is one reason, among others, why this concept is so relevant for empirical school and development research. Another crucial step in clarifying the concept of competence is to understand that the framework of competence recognizes the importance of everyday life situations (Blömeke et al., 2015). Therefore scholars argue, a definition must start from an authentic "analysis of occupational or societal situations and must take into account the tasks and associated associated cognitive, conceptual, affective, and motivational aspects" (Blömeke et al., 2015, p. 5). Through this comprehensive approach, many inconsistencies in the definition of the term can be resolved. The definition of competence is now no longer a question of whether it is a number of cognitive skills or a combination of cognition, conation, affect, or motivation. It combines "complex intellectual characteristics together with affect-motivation, which underlies observable underlying performances" (Blömeke et al. 2015, p. 6). This is best defined as a process or even continuum (see Figure 1), which consists of different levels and should be understood as a multidimensional construct with stronger and weaker Domains (ibid.).

The term competence finds its place in a variety of disciplines as an assessment standard of qualifications. In this context, the term professional competence has become established in research, which defines competence in a specific professional field. Thus, based on the assumption that competence is more than mere knowledge, professional competence offers a way to make teacher success in schools tangible (Kunter et al., 2013).

The term "professional competence" is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation." (cf. Epstein & Hundert, 2002; cited in Kunter et al. 2013, p. 807). Several studies could prove that this idea can be successfully transferred to the teaching profession (cf. Goodmann et al., 2008; Oster, Achtenhagen & Renold, 2006; Tannenbaum & Rosenfeld, 1994; cited in Kunter et al., 2013, p. 807). Accordingly, a quality standard can be applied to assess the quality of a teacher. This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano & Pickering, 2003). Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher. Research has shown that this component can even offset the influence of an ineffective school setting (Marzano et al., 2003). This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.

## Classroom Management

Teachers and students are in the classroom in a place that is always alive, characteristic of its heterogeneity and the interests of different groups. These the circumstances of a classroom are also characterized as multidimensional, simultaneous, immediate, unpredictable, public, and shared (Doyle, 2011, p. 99). All of these circumstances place a number of demands on teachers, which primarily involve planning and monitoring activities (ibid.). "Order in classrooms is not a consequence of reactions to misbehavior but a condition established and sustained by the way a teacher organizes and guides a complex system of classroom activities" (Doyle, 1989, p.12). Thus, "good" teachers create the conditions for effective teaching through pre-planned actions and activities that they are always in control of while teaching. This enables them to maximize work time while keeping disruptions of any kind to a minimum to facilitate learning for all participants (Doyle, 1989).

However, lessons, and specifically classroom disruptions, are unpredictable as well as multifaceted and require a high level of expertise and competence on the part of the teacher to handle. This trained handling, as described above, can be summarized under the aspect of professional competence. It is expressed, among other things, in knowledge about classroom management (Grub, Biermann & Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.

Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, van den Bogert, Jarodzka & Boshuizen, 2015). Marzano et al.'s (2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching. In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015). Therefore, it is often referred to as the central variable of successful teaching (Helmke & Helmke, 2015). Good classroom management is thus the prerequisite for learning to take place (Wolff et al., 2015). While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.

An initial explanatory approach to classroom management was provided by Doyle (1990, p.355) with his definition of teaching, which he described as a "cognitive activity based on knowledge of the probable course of events in the classroom and the ways in which actions affect situations." From this, it is clear that in order to teach successfully, a teacher needs knowledge of how to process as well as represent the full range of classroom events. In addition, it is necessary to be able to respond or interact proactively and effectively to potential events at best.

Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf. Wolff et al., 2015, p. 71). These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.). If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction. This is crucial to maximize students' active learning time (Helmke & Helmke, 2015). It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research. In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise (Wolff et al., 2015).

### Interdependence of classroom management

In research, various models exist for approaching the concept of classroom management. However, they are very similar in their core statements. Therefore, it is merely a matter of preference which concept is consulted to explain connections and terms. In the following, the network of effects of classroom management according to Helmke (2014) is used as a reference model in order to be able to understand the embedding of the concept accordingly.

As was made clear in the definition, classroom management is a complex construct that attempts to accommodate the various modes and challenging characteristics of a classroom. Helmke (2014) therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time. This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (*d* = 0.39; Hattie, 2013, p.219). Due to this diversity of aspects to be investigated, classroom management is a fundamental research topic.

The concepts, strategies and techniques used to implement successful classroom management depend first and foremost on various teacher characteristics and are "interrelated with the quality of teaching and personal relationships" (Helmke & Helmke, 2015, p.5). It should not be forgotten that this space never functions in isolation and independently of other influences. It is embedded in diverse contexts, especially in the school and class context (Helmke & Helmke, 2015). But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led (Helmke, 2014).

Classroom management itself is made up of various components which, according to Helmke (2014), can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior. Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke & Helmke, 2015).

The importance of rules in the classroom has been known and researched for some time. Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules (cf. Emmer, Evertson & Anderson, 1980; Emmer, Sanford, Clements & Martin, 1982; cited in Doyle, 1989, p. 15). Although he also stresses that establishing a system of rules is a difficult task. Classroom rules are situation-dependent, as certain agreements only apply to certain phases of the lesson (for example, speaking quietly during group work; Doyle, 1989). Furthermore, order is always established jointly, in cooperation with the learners (Doyle, 1989).

As a result, students significantly influence these rules by their willingness to follow them. Procedures are another tool to maintain the flow of the lesson, as recurring routines provide learners with security and clarity (Helmke & Helmke, 2015). This inevitably reduces the teacher's workload, eliminates additional explanations are no longer necessary, and it is clear to the learners at all times what needs to be done. needs to be done. In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time (Helmke, 2014). For the reasons just reasons just explained, it is clear why Hattie (2013, p. 122) gives this component of classroom classroom management an effect size of *d* = 0.76.

No other aspect of classroom management is as effective for classroom interruptions as the teacher's omnipresence (Hattie, 2013, p. 122); the effect size is *d* = 1.42. (Helmke & Helmke, 2015, p. 6). The behavioral pattern of presence is not a new concept. It was already recorded by Kounin in 1970 under the term *withitness*. Later research confirmed and validated his assumptions and definition of the term (cf. Helmke, 2014, p.10). In order to be present, the teacher must be able to control the classroom adequately and superficially effectively at all times. This means she must be able to recognize relevant cues or situations that require possible action (Wolff et al., 2015). Presence can consequently be illustrated very vividly by means of the image of "eyes in the back of the head" (Kounin, 2006). In addition to presence, Kounin (2006) uses the term overlap. It is a kind of multitasking ability to be able to cope with parallel processes and situations in the classroom. The two dimensions of overlap and presence can also be summarized together under the term monitoring (Gold & Holodynski, 2017). When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners (Grub et al., 2020.). Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness.
and increases general awareness of relevant events in the classroom (ibid.). From this point of view, it becomes clear why awareness is a core component of teacher competence.

As a third component influencing the quality of classroom management, cites Helmke (2014) time use and management. This seems trivial at first, considering that classroom management serves the goal of maximizing learning time anyway. However, Helmke & Helmke (2015, p. 6) emphasize how elementary it is to identify and minimize possible "time thieves". This includes factors such as unpunctuality or slow transitions, as well as the underemployment of learners (ibid.). If these take up too much space in the classroom, less time is available for teaching important lesson content. This can be prevented by teachers minimizing such "time thieves" in advance through well-planned classroom management.

In order to enforce desired student behavior or to reduce contradictory behavior, teachers can use various discipline-related interventions and also make use of negative sanctions and positive reinforcement (Helmke & Helmke, 2015). The authors emphasize that a healthy balance must be found when using these strategies. Over the years, this constructive approach has fallen into disrepute due to its behaviorist character. However, elements such as reinforcement, extinction or punishment are not negligible laws of learning psychology whose effectiveness has been proven by Hattie (2013), among others. These behavioral psychological measures have an effect size of *d* = 0.76 (cf. Hattie, 2013, p.215) and are therefore an effective means of reducing disruptions (Helmke & Helmke, 2015).

Researchers in pedagogy also point out, however, that it is not only pure knowledge about classroom management that determines its effectiveness and influences it (Helmke & Helmke, 2015). The teacher personality, which includes characteristics such as subjective tolerance margins, i.e. at what point does one perceive a certain behavior as disruptive, also plays a role. This includes further aspects such as emotion control, empathy or the credibility of a teaching person that arises through appearance. These characteristics, which occur in many ways, have a direct impact on the quality of teaching and classroom management, as they influence the planning behavior, perception and reaction of teachers.

## Professional vision

Competence assessment plays a central role in the teaching profession and its training. It follows the approach of concentrating on action-relevant as well as lesson-related content in order to train corresponding competences for teaching practice (KMK, 2004). In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes (Barth, 2017). Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel & Prenzel 2014). The concept of professional vision can originally be traced back to the anthropologist Charles Goodwin and became known under the term Professional Vision (Sherin, 2001). It provided the answer to Goodwin's question regarding the development of a professional vision, in the context of the profession, compared to the vision of everyday situations. Goodwin uses the comparison of an archaeologist and a layperson to figuratively describe the differences. In doing so, he investigated which ability it is that makes the archaeologist see and interpret a landscape differently than the layperson (cf. Sherin, 2001, p. 75). What looks to the former merely like sand, rocks and stones, is to the trained eye of the archaeologist a base of a column or architectural fragments. Goodwin (1994, p.606) defines professional vision as "socially organized ways of seeing and understanding events that are answerable to the distinctive interests of a particular social group" (cited in Sherin, 2001, p. 75). It is assumed that one can see certain phenomena or occurring events in a certain way due to one's professional affiliation (Sherin, 2001). Particularities are more easily recognized because the gaze becomes more trained over time and thus profession-relevant features appear more distinctive. In the previous example of the archaeologist, this would mean that he noticed variations in color, texture and sand and saw a cluster of stones as a possible element of a larger structure (cf. Sherin, 2001, p.75). This distinguishes experts significantly in their visions from non-experts in the field, as they had learned to filter their environment for crucial features.

### Teachers' professional vision

Based on the assumption that the professional vision can develop over time, Sherin (2001) postulates that teachers can also acquire a professional vision. As teachers develop from novices to experts in their field, they accumulate expertise in a variety of areas (cf. Sherin, 2001, p. 76). This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom (Berliner, 1994; Leinhardt & Greeno, 1986). This type of action can be described as a skill that helps teachers make decisions about what is relevant and what is not within the complex classroom setting (van Es & Sherin, 2002). Such decisions are based on professional knowledge that guarantees effective teaching and learning in actual classroom situations (Jahn et al., 2014). Professional awareness is therefore referred to as an indicator of how knowledge is represented in teachers (Stürmer et al., 2017). It can also be seen as a bridge or link between knowledge and action, or professional competence and behavior (Grub et al., 2020). It is important to understand that professional vision is acquired and not inherent. Rather, it is subject to a process of acquisition that is constantly progressing as teachers are exposed to events and learn to interpret them (Wolff et al., 2016). Fundamentally, then, prospective teachers must select what to focus their attention on in the classroom and how to understand these events (Stürmer et al., 2017). Finally, teaching and learning take place in a complex environment. Simultaneous events and situations cannot be given the same attention. "Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects" (Barth, 2017, p.19). Furthermore, teachers benefit from from a trained perception of problems, as this is a significant factor in being able to preventively counteract preventive measures (Wettstein, 2013).

Basically, the complex process of professional vision is divided into three sub-processes (Grub et al., 20202). First of all, the identification, the recognition, of an event takes place. Then connections are made, which are finally evaluated by the teacher using his or her professional knowledge. In research, these processes are often combined and one speaks of noticing to describe recognition (Grub et al., 2020). Knowledge-based reasoning includes the last two processes of applying knowledge to make appropriate decisions (ibid.). During this process, it becomes clear that the recognition of relevant situations, such as disruptions, precedes all others. This process is therefore considered necessary, without which professional vision cannot take place (Grub et al., 2020). As described in the chapter on competence, perceptions is also of particular importance in the competence model according to Blömeke et al. (2015). This is because the process of perception forms an essential basis for situation-specific skills of teachers (Grub et al., 2020). Inferentially, recognition is inevitable for the perception of classroom events and therefore highly relevant for effective classroom management (ibid.).

Even though the recognition of relevant situations in the classroom is the starting point for all further subsequent actions, the processes of knowledge-based reasoning within professional vision are not to be neglected. It is also said that this process is an indicator of the quality of how knowledge is applied to a given situation (Grub et al., 2020), as teachers need to make knowledge-based inferences. Qualitative research on knowledge-based reasoning concluded that it can be subdivided into three further sub-processes. Sherin (2007; cited in Barth, 2017, p. 20) made a first subdivision, which consists of the processes of describing, evaluating and interpreting. When a teacher describes what she notices, she concentrates on observable characteristics, i.e. important aspects of teaching (ibid.). When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event (cf. Barth, 2017, p. 19). Seidel et al. (2010), on the other hand, focus on German-speaking countries in their research on professional vision and modified Sherin's original concept. They also divide knowledge-based-reasoning into three levels, but these differ: describing, explaining and predicting (Barth, 2017). More precisely, these processes encompass the ability to differentially describe instructional components that have an impact on learning; to make theoretically sound explanations about instructional situations; and to predict the effects of these events in relation to the teaching-learning process (cf. Seidel et al., 2010, p. 297). This scientific work examines only the processes of noticing, which is why these two approaches have been presented for the sake of completeness. However, it is not useful to specify which classification of knowledge-based reasoning is referred to in arguments. is referred to in argumentation.

Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect (Sherin, 2007; cited in Barth, 2017, p. 19). What is considered and perceived as relevant in a teacher's selective vision (noticing) functions as the basis of the subsequent processes of describing, evaluating, and interpreting (knowledge-based-reasoning). Conversely, by engaging with these processes, the teacher's perception is sensitized. This leads to the fact that in the future certain characteristics of this situation can be recognized rather.

## Measuring professional vision: eye-tracking technology in research

Professional vision of teachers is a complex undertaking, consisting of various cognitive and visual processes. In the previous chapter, the importance of perception and its associated visuality was emphasized, which places the eye at the center of investigations. In research, process-based methods are used to make these perceptual processes visible. In this context, eye-tracking (ET), a modern method of recording gaze, has proven to be an effective tool in research. It allows us to literally see through the eyes of recipients and provides insight into another perspective. Intrinsic human cognitive processes are often compared to a black box in science, as these activities are not directly measurable (Rakoczi, 2012). Until now, cognitive processes could only be studied by verbalizing the respective subjects. However, this method is highly susceptible to interference due to its incomplete accessibility (Dessus, 2016). The increasingly popular research method of eye-tracking technology therefore represents an innovative means of externalizing, i.e., making visible, internalized processes by means of eye movements (Gegenfurtner et al., 2018). Stimuli in the environment are always perceived by our eyes as the first receiver. They take in the information and pass it on to our brain so that it can finally be processed there. By measuring this complex process, eye movements can be recorded and subsequently analyzed (Rakoczi, 2012). Information is obtained about the visual behavior, attentional focus, selection decisions, and even learning processes of the investigator (ibid). In addition to these qualitative results, which provide information about underlying cognitive processes, quantitative data can also be collected through eye-tracking (Cullipher, 2018). These provide information, for example, about how long and in what order stimuli are looked at, or whether certain parts are looked at more often than others (ibid.). This enables research to make data objectively assessable.

Eye-tracking technology can be roughly divided into two types of devices: Stationary and mobile systems (Blake, 2013). In research so far, mainly eye-tracking devices have been used, which phenotypically resemble a computer (ibid.). They are also referred to as remote devices and, once calibrated, measure eye movements in a non-contact manner using infrared light (Gegenfurtner et al., 2018). However, this technique reaches its limits when it comes to collecting data in everyday situations. For this purpose, the more flexible variant, mobile eye tracking (MET) or head-mounted or wearable eye trackers, can be used. Typically, the technology is found as a head-mounted device on helmets or integrated into an eyeglass frame (Blake, 2013). The difference with stationary tracking is that in addition to an eye camera and infrared light source, additional cameras are built in to capture head movements (ibid.). These are intended to help document the subject's field of view. Therefore, such systems are particularly suitable for applied sciences, as is the case in empirical school and development research (Gegenfurtner et al., 2018).

Eye-tracking research is based on several fundamental assumptions. The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date (cf. Blake, 2018, p.380). In this regard, Hoffmann and Subramaniam (1995) obtained the finding that when the eyes are focused on an object, this is associated with an attentional focus of the person. Based on these findings, ET technology is based on the following two assumptions: The immediacy assumption and the eye-mind assumption (cf. Rakoczi, 2012, p.87). The former defines that cognitive evaluation processes begin immediately upon fixation on an object (Cullipher, 2018). If a new stimulus attracts attention and is fixated, the observer starts processing this new information (ibid.). The eye-mind hypothesis assumes that whatever is fixated by the eye, is subsequently processed by the mind (ibid.). It thereby expansively defines, that objects are visually focused only until they are cognitively evaluated or until there is have been cognitively evaluated or there is still an interest (cf. Rakoczi, 2012, p.87). However, a situational context must exist for the assumptions just explained to be are valid (ibid.). Through these functions, it becomes clear that the intrinsic processes of recognition in professional vision can be measured by eye-tracking technology.

Despite the externalization of internalized processes and the resulting multitude of data potentially to be collected, ET technology cannot provide answers about the exact thoughts during stimulus processing. ET can identify where and when people are looking, but it does not answer why. For this, it is helpful to triangulate the data and apply alternative elicitation (Cullipher, 2018). One proven method is to conduct reflective interviews, which can be conducted in the format of a think aloud protocol (Konrad, 2020). This thinking aloud opens up the possibility of gaining insights into subjects' thinking, feeling, and intentions (edb.). An elaborated form of the Think Aloud Protocol is a Stimulated-Recall Interview (SRI). This is a qualitative scientific method to obtain data on preactional thought processes (cf. Messmer, 2015, p.4). The pre-recorded lesson sequences are played back and subjects have the opportunity to express themselves about their "thoughts, beliefs, norms, and decisions" (Messmer, 2015, p.4) during the interview process. Thus, the visual data of the ET can be matched with cognitive processes and processes of knowledge-based-reasoning can be better understood. Individual-dependent thinking is now no longer pure speculation and can be made objectively observable in a way (Messmer, 2015). Subjects also have the opportunity to explain their actions and become aware of the basis for their decisions (ibid.).

### Parameters and indicators of teachers' professional vision

In university education, there is an increasing focus on developing the professional vision of future teachers (Stürmer et al., 2017). In order to determine the professional vision of teachers by means of mobile eye-tracking (MET), different indicators are worth considering. This scientific work focuses primarily on processes of noticing, i.e., the identification of relevant teaching situations as well as perception time. Therefore, in the following we will focus more on the parameters and indicators necessary for these processes.

In MET, collected data sets are usually output according to different parameters: Fixations and Saccades (Gegenfurtner et al., 2018). The latter describes gaze jumps, i.e., movements of both eyes, which are useful to capture new fixations (Eye-Tracking Kompetenzzentrum Schweiz, 2021). Significant for this scientific work and the analysis of professional vision are the fixations as well as subjects' areas of interests. Fixations describe the period of time in which no movements are emitted by the eye (Holmquist et al. 2011) and are based on the eye-mind hypothesis described in the previous chapter. A fixation of an object can be characterized according to its duration, frequency, and distribution. In the illustration, the radius of a circle defines the duration of a fixation (Gegenfurtner et al., 2018). These data can also be used to describe perception times, such as the time until the first fixation on a particular object. In order to make this time period objectively measurable make it objectively measurable, a concept developed by Tobii Pro Lab Analyzer Software is used. In this software these organized recorded data are called Time of Interests (short TOIs), which describe time intervals of corresponding events or behaviors (Tobii Pro, 2021). Specifically, they are defined by the beginning and end of the corresponding event.

By means of eye movement measurement, attention allocations to areas of interest or objects are made accessible in addition to pure fixations (Gegenfurtner et al., 2018). In research, these regions in the field of view of subjects are referred to as areas of interest (AOI) (edb.). They are significant in that, for the measurement of perceptual velocities of a relevant instructional event, not only TOIs but also the locations of fixations are crucial. Thus, it can be determined how subjects distribute their attentional resources and whether they recognize and perceive relevant events.

### Expertise differences in professional vision

Since it is assumed that professional vision is a preferably knowledge-based process, differences between experienced and inexperienced teachers have already been identified. These differences were in favor of experts, since a connection between teaching experience and the associated increase in knowledge acquisition is assumed (Grub et al., 2020). Student teachers do not have well-structured experiential knowledge due to their almost non-existent practice in everyday school life (Wolff et al., 2016). This causes them selection difficulties in perception and is called pedagogical knowledge gap (cf. Wolff et al., 2016, p.260). Through newly gained experiences, the professional vision of a teacher is continuously restructured and updated, and mental representation is constantly realigned accordingly (ibid.). This has been proven in research as a positive correlation of input to teaching and learning theories in studies and professional classroom perception has been found (Stürmer et al., 2012). Therefore, it can be assumed that there is a relationship between teacher expertise, their visual processing, and mindfulness for classroom management (Wolff et al., 2016). Research has also shown that declarative knowledge acquisition, i.e., acquisition of factual knowledge, supports perceptual processes (Seidel et al., 2012; cited in Treisch, 2018, p.26). Accordingly, this increased knowledge acquisition would explain a positive impact on professional teaching perception. Among the most important prerequisites for this acquisition, Baumert and Kunter (2006) include prior knowledge and interest. The former is elementary for new knowledge acquisition about effective teaching and learning, as it supports processing, integration, and consolidation of it (Stürmer, 2011). Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions (cf. Sabers, 1991; cited in Treisch, 2018). This is explained by increased filtering mechanisms that support perceptual processes, i.e., recognition. Specifically, it has been shown that experienced teachers have more fixations on relevant areas because they have already learned theories on how to detect potential clutter in the classroom (Grub et al., 2020.). Furthermore, experts have an advantage when it comes to coding information. Novices, on average, have a longer viewing times, so-called fixation durations, which is due to their still weakly developed expert knowledge (ibid.).

### Mobile eye tracking in teaching-learning situations

As explained in detail earlier, teachers face a number of challenges during teaching. The teacher as organizer has to permanently scan the classroom for potential interruptions or possible events occurring such as classroom disruptions. In the worst case, they force a standstill in the flow of instruction, which is naturally to be avoided. Lohmann (2015, p.13) describes classroom disruptions as "events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place." However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive (cf. Eckstein, Grob & Reusser, 2016; cited in, Eckstein, 2018, p.11). Thus, instructional disruptions are strongly dependent on perception and involve elements of production as well as reception (ibid.). These discipline conflicts can be divided into four categories of disruptive student behavior: Verbal disruptive behavior (chattering, heckling), lack of eagerness to learn (mental absence in the form of drawing or playing on the cell phone), physical disruptions (snapping, drumming, pen clicking), and aggressive behavior (temper tantrums, attacking people; Lohmann, 2015).

In order to be able to recognize inappropriate behavior in a timely manner, the teacher must have a pronounced omnipresence, as well as pedagogical-psychological knowledge about teaching and learning processes (Cortina et al., 2018). These skills and competencies are reflected in how teaching situations relevant to learning are perceived and interpreted by teachers (ibid.). In this context, a multitude of visual attention processes occur during classroom activities. This simply means the attention or the conscious non-attention to visual stimuli (Rüth et al., 2020). This situational awareness of a teacher and the accompanying control of his or her visual attention forms the foundation of situation-specific skills (cf. Rüth et al. 2020). These data and insights potentially to be collected form an interesting field of research and useful tool for problem-based teaching education (Cortina et al., 2018).

In the last decade, visual input through recorded teaching situations has been preferred (ibid.). Subjects are thus shown an outside perspective from different points of view. This can happen either as self or external video and allows micro-analysis or interaction sequences through the characteristic of repeated playing of a video (ibid.). This characteristic makes it possible to analyze corresponding scenes more intensively and in more detail. This results in a potential for reflection on teaching situations in teacher education that should not be underestimated (cf. Rüth et al., 2020). The problem with these videotaped sequences, however, is the lack of access to the first-person perspective (ibid.). As a result, students usually evaluate and comment on their own videos more negatively than those of others afterwards (Cortina et al., 2018). They find it difficult to analyze the sequences objectively and to leave out unimportant details that concern their person. However, this is not purposeful and conducive to the intended learning process of the participating teachers. This is due to the fact that self-drawn cognition is activated in self-videos and that when negative events occur, subjects tend to defend their actions (ibid.). Kleinknecht and Schneider (2013) analyzed this process in more detail and found that this is particularly problematic for the reflective learning process, as it has a counterproductive effect on analyzing possible alternative actions. They also found that in third-party videos, reflection on potential alternative actions was twice as frequent as in self-recorded videos (ibid.)! In addition, recorded video sequences differ significantly from real classroom settings in which the teacher can independently determine her field of view. The observers cannot decide for themselves what to pay attention to and for how long to pay attention to a situation or event (Sherin, 2001). Based on this finding, it was significant for researchers to use an alternative elicitation technique to factor out the negative effects of self and other videos.

A successful method to reduce this hindering factor of self-drawn cognition and still use self videos for teacher education is to use recordings that show the teacher's perspective and furthermore make it known where the teacher was looking (cf. Cortina et al., 2018). In MET's video material, teachers can never see their teaching through their own eyes. This makes it possible to focus more specifically on essential aspects, such as classroom disruptions and interactions with learners. Although it has not yet been clearly demonstrated that significantly less self-referential cognition was elicited, self-videos counteract over-focusing on the acting person (cf. Cortina et al., 2018). Therefore, MET represents a target-rich method for capturing teachers' attentional processes in the classroom. Previous studies with large data sets on teachers' visual expertise have predominantly used stationary ET (Wolff et al., 2016). In MET studies, the samples turn out to be much smaller; here, the largest study to be mentioned is with 12 experienced and 12 inexperienced teachers by Cortina et al. (2015).

### Perceptions of classroom disruptions and their parameters

The attentional processes of teachers in the classroom that can be captured by MET are complex, as already explained, and are related to various parameters. Individual personality characteristics play a central role when it comes to the perception of relevant classroom events. In general, it should be noted that novices have greater problems in classroom management as well as in dealing with difficult student behavior (Barth, 2017). Often, this is due to their late or even lack of awareness of classroom disruptions. However, their lack of expertise is not the sole reason for this phenomenon. Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher (Baumert & Kunter, 2006). Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors. Individual person characteristics as well as contextual factors not only have an effect on teaching perception, but likewise on the sense of disturbance of a situation (Eckstein, 2019). These specific characteristics include aspects such as self-image, motivation, level of aspiration, attitudes, coping goals, and value orientations (Bakker & Demerouti, 2006; cited in Wickeren, 2019, p. 33). Contextual characteristics include didactic staging or general level of disruption. Undesirable behavior is perceived more strongly by teachers when the class usually displays disciplined and orderly behavior (Eckstein, 2018). This reference group effect is also known as the Big-Fish-Little-Pond effect. Thus, it can be said that teachers' perceptions of situations and people are significantly shaped by their expectations and biases is shaped (cf. Eckstein, 2018). How strongly a disturbance is perceived and felt can also depend on psychological characteristics such as self-efficacy beliefs (ibid. (ibid.). With decreasing self-efficacy, an increasing sense of disturbance was found (ibid.).

The teacher-student relationship aspect, which includes recognizing student needs, must also be considered. In order to be able to adequately counteract classroom disruptions and thus automatically reduce the sense of disruption and the experience of stress, it is important to address the concerns of the learners with empathy (Wickeren, 2019). Regarding gender as a factor, it should be noted that previous research has found higher levels of disruptiveness in discipline problems among female teachers (Kovess-Masféty, Rios-Seidel & Sevilla-Dedieu, 2007; cited in Wickeren, 2019, p. 33). In summary can thus be summarized that the extent and perception of disturbances are based on individual cognitive evaluation processes, the situational context, attentional focus, didactic staging, and, indeed, professional experience (cf. Wickeren, 2019).

# Research Questions and hypothesis

This study examined how the degree of teaching experience of novice and expert teachers influences (1) the number of fixations on relevant areas, (2) the fixation duration on relevant areas and (3) the time to first fixation on relevant events (e.g., the student performing the disruption), using mobile eye-tracking data in a controlled, micro-teaching setting. Furthermore, the study examined the individual evaluation of classroom disruptions among experts and novices by assessing (4) how disruptive an event was and (5) how confident the subjects felt dealing with the events. In addition, subjects' (6) strategic knowledge of classroom management was assessed.

Based on the existing literature, we expected expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation duration and (H3) perceiving classroom disruptions faster (cf. @van2014first), (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions (Barth, 2017), and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).

# Materials and Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

This study had a quasi-experimental study design, as there was no random assignment of the subjects to experimental conditions. Due to the use of mobile eye-tracking technology, the study had a high external validity [@gegenfurtner2018mobiles]. Internal validity could be ensured to the extent that the disruptive events that occurred were exactly the same for all subjects, as the actors received precise behavioral instructions. These disruptions followed a script and coding scheme in which the actions of the class were precisely described. The order of the disruptions as well as the performing actors were fully balanced with Latin Square to exclude row effects.

The scripted behavioral instructions during the micro-teaching unit characterized the study with a high degree of standardization, especially when compared to events taking place in a real classroom. The study was based on an experimental manual, script and coding, which explicitly described the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable.

## Participants

```{r demographicstable, include = TRUE, echo=FALSE}

# read in data and select and rename relevant columns with transmute 
demo.data <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  transmute(Group = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            School_type = LI18,
            Grade = LI16_05,
            Subject = LI10_05,
            Semester = LI11_01,
            Internship = LI13_01,
            `Extracurricular Teaching Experience` = LI14,
            `Secondary Teaching Activities` = LI17
            )

# define expert and novice with ifelse function
demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")

# changing gender to count female gender (male = 2 --> 0)
demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")

# changing character Gender into numeric
demo.data$Gender <- as.numeric(demo.data$Gender)

# creating new column with total participants to calculate percent of gender
demo.data <- demo.data %>%
  group_by(Group) %>%
  mutate(Sum_participants = n())

# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
demo.data$School_type[demo.data$School_type == 2] <- "1"

# creating new column to calculate percent of school type
demo.data <- 
  demo.data %>%
  group_by(School_type, Group) %>%
  mutate(Count_Schooltype = sum(n())) %>% 
  mutate(Percent_schooltype = round((Count_Schooltype/Sum_participants) * 100, 
         digits = 2))

# changing character Percent_schooltype into numeric
demo.data$Percent_schooltype <- as.numeric(demo.data$Percent_schooltype)

XXX

# creating a subset to report school type in text
demo.school <- 
  demo.data %>% 
  dplyr::select(Group,
         Percent_schooltype) %>% 
  group_by(Group) %>% 
  summarise_each(funs(sum))

# changing character Semester into numeric
demo.data$Semester <- as.numeric(demo.data$Semester)

# changing Type of School into character
# LI18:
# 1: Grundschule
# 2: Oberschule
# 3: Gymnasium
# 4: Förderschule/Sondershausen
# 5: Berufsbildende Schule
# -1: andere Schulform
demo.data$School_type <- factor(x = demo.data$School_type,
                   levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
                   labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen

# changing `Extracurricular Teaching Experience` to count experience (no experience = 2 --> 0)
demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 1, "1","0")

# changing character Extra. Exp. into numeric
demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)

# changing `Secondary Teaching Activities` to count experience (no experience = 2 --> 0)
demo.data$`Secondary Teaching Activities` = ifelse(demo.data$`Secondary Teaching Activities` == 1, "1","0")

# changing character Extra. Exp. into numeric
demo.data$`Secondary Teaching Activities` <- as.numeric(demo.data$`Secondary Teaching Activities`)

# create new columns that give proportion of Gender
# percent = female gender divided by all female Gender
# demo.data <- demo.data  %>% 
#   group_by(Group) %>% 
#   mutate(Gender_percent = Gender/Sum_participants) %>% 
#   mutate(Gender_percent = round(sum(Gender_percent)*100, digits=0))

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percent" = round(sum(Gender/Sum_participants) * 100, 
                                               digits = 2),
            "M Age in years" = round(mean(Age), 
                                     digits = 2),
            "SD Age in years" = round(sd(Age), 
                                      digits = 2),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age)
            )

# format and insert table in manuscript
demo.table %>%
papaja::apa_table(
  caption = "Demographic Information",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

# create a basic table (tibble) using tidyverse functions
exp.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
           "M Exp." = round(mean(`Teaching Experience`), 2),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "M Semester" = round(mean(Semester), 2),
            "SD Semester" = round(sd(Semester), 2),
            "Min Semester" = min(Semester),
            "Max Semester" = max(Semester),
            "M Internship" = round(mean(Internship), 2),
            "SD Internship" = round(sd(Internship), 2),
            "Min Internship" = min(Internship),
            "Max Internship" = max(Internship),
            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
           )

# format and insert table in manuscript
exp.table %>%
papaja::apa_table(
  caption = "Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

```

The sample consisted of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.

The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession. According to @palmer2005identifying, we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school. Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`).

`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype")`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype")`% were secondary school teachers.

`r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years. On average, the student teachers were in their `r exp.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`). Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies.

`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype")`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype")`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype")`% to become special education teachers.

`r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at the University Leipzig. All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board. The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University. All participants were informed in detail about the aim and intention of the study prior to testing. Participation in the study was voluntary and only took place after written consent has been given.

##

## Variables

All stimuli are freely available in the following online repository: https://github.com/... .

### Eye-Tracking data

To record eye-tracking data, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker during the micro-teaching-unit. The system consisted of a wearable head unit and a recording unit. As shown in Figure \@ref(fig:tobiiglasses2), the head unit was a measuring device with different sensors. A high-definition scene camera captured a full HD video of the teacher’s field of vision. An integrated microphone recorded the surrounding sounds. Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \@ref(fig:teachersgaze). The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second. The scene camera had a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).

```{r tobiiglasses2, include = T, fig.cap = "Tobii Pro Glasses 2; Source: https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/tobiiglasses2.png", dpi = 108)

```

```{r teachersgaze, include = T, fig.cap = "Teacher's Gaze Point", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/teachersgaze.pdf", dpi = 108)

```

### Video data

The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \@ref(fig:setup). The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.

Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \@ref(fig:setup). The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.

### Questionnaire data

After each micro-teaching-unit, the three actors answered items on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature. In addition, subjects were asked to give a self-assessment on  classroom management by completing the same questionnaire after each micro-teaching-unit. The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).

```{r presence_questionnaire_novices, include=TRUE, echo=FALSE, results='asis'}
# load data files
quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  mutate(Group = ifelse(LI06_05 < 200, "Novice","Expert")) %>%
  dplyr::select(Group, LM01_01:LO01_02)

# create two data frames
quest.data.novice <- quest.data %>% filter(Group == "Novice")
quest.data.expert <- quest.data %>% filter(Group == "Expert")

############## NOVICE TABLE #########################

# creating a matrix
quest.table.novice <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table.novice) <- c("LM", "LB", "LP", "LV")
  colnames(quest.table.novice) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")

# creating a loop
# i <- "LM"

for (i in c("LM", "LB", "LP", "LV")) {

loop.data <- quest.data.novice %>%
  dplyr::select(starts_with(match = i))

quest.table.novice[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  mean() %>%
  round(., digits = 2) ->
quest.table.novice[i, "M"]

# calculating SD
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  sd() %>%
  round(., digits = 2) ->
quest.table.novice[i, "SD"]

# calculating Min
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  min() %>%
  round(., digits = 2) ->
quest.table.novice[i, "Min"]

# calculating Max
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  max() %>%
  round(., digits = 2) ->
quest.table.novice[i, "Max"]

# calculating Skewness
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  skewness() %>%
  round(., digits = 2) ->
quest.table.novice[i, "Skewness"]

# calculating Kurtosis
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  kurtosis() %>%
  round(., digits = 2) ->
quest.table.novice[i, "Kurtosis"]

# calculating alpha
alpha <- loop.data %>%
  cronbach.alpha()

quest.table.novice[i, "alpha"] <- round(alpha$alpha,2)

}

# rename columns
rownames(quest.table.novice) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
papaja::apa_table(
quest.table.novice,
  caption = "Scale analysis for novices' self-assessment",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)
```

```{r presence_questionnaire_experts, include=TRUE, echo=FALSE, results='asis'}

############## EXPERT TABLE #########################

# creating a matrix
quest.table.expert <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table.expert) <- c("LM", "LB", "LP", "LV")
  colnames(quest.table.expert) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")

# creating a loop
# i <- "LM"

for (i in c("LM", "LB", "LP", "LV")) {

loop.data <- quest.data.expert %>%
  dplyr::select(starts_with(match = i))

quest.table.expert[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  mean() %>%
  round(., digits = 2) ->
quest.table.expert[i, "M"]

# calculating SD
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  sd() %>%
  round(., digits = 2) ->
quest.table.expert[i, "SD"]

# calculating Min
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  min() %>%
  round(., digits = 2) ->
quest.table.expert[i, "Min"]

# calculating Max
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  max() %>%
  round(., digits = 2) ->
quest.table.expert[i, "Max"]

# calculating Skewness
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  skewness() %>%
  round(., digits = 2) ->
quest.table.expert[i, "Skewness"]

# calculating Kurtosis
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  kurtosis() %>%
  round(., digits = 2) ->
quest.table.expert[i, "Kurtosis"]

# calculating alpha
alpha <- loop.data %>%
  cronbach.alpha()

quest.table.expert[i, "alpha"] <- round(alpha$alpha,2)

}

# rename columns
rownames(quest.table.expert) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
papaja::apa_table(
quest.table.expert,
  caption = "Scale analysis for experts' self-assessment",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

```

```{r item_analysis_classroom_management, include=TRUE, results='asis'}
# quest.data %>%
#   dplyr::select(contains("LM")) %>%
#   as.data.frame() %>%
#   tab_itemscale(CSS = list(
#     css.firsttablerow.col7 = "'cronbachs alpha';"
#   ))
```

```{r item_analysis_balance, include=TRUE, results='asis'}
# quest.data %>%
#   dplyr::select(contains("LB")) %>%
#   as.data.frame() %>%
#   tab_itemscale()
```

```{r item_analysis_presence, include=TRUE,results='asis'}
# quest.data %>%
#   dplyr::select(contains("LP")) %>%
#   as.data.frame() %>%
#   tab_itemscale()
```

```{r item_analysis_behavior, include=TRUE,results='asis'}
# quest.data %>%
#   dplyr::select(contains("LV")) %>%
#   as.data.frame() %>%
#   tab_itemscale()
```

#### Rating scales

Two self-developed 11-point rating scales were used to record how disruptive the individual disruptions were perceived by the subjects and how confident they felt in dealing with the disruptions. Data for rating scales were collected during the Stimulted Recall Interview, where the experimenter watched the pre-recorded eye-tracking video with the subject.

The questionnaire included nine questions for each scripted disruptive event. The subjects did not have to complete the questionnaire themselves at any time, as this was done by the experimenter.

For the present study, the following two questions from the interview were relevant:
1. "How disturbing did you perceive this event to be?"
2. "How confident did you feel in dealing with this event?"

Both questions were answered using a scale ranging from 0 to 10. On this scale, 0 stood for "not at all disruptive" or "not at all safe" and 10 for "extremely disturbing" or "extremely safe."

With these rating scales, the subjects indicated their personal subjective feeling towards the individual lesson disruption. Rating scales usually consist of a number of clearly arranged categories that can be presented visually in a variety of ways [@albers2009methodik, p. 67f]. In the present questionnaire, the numerical representation with eleven answer options (0-10) was used. There was no specific designated neutral position. In this questionnaire, the middle category 5 was not interpreted as a neutral position. In order to avoid misinterpretations of the scaling, the questionnaire was described verbally by the experimenter and follow-up questions from the test subjects were possible at any time. With regard to the quality criteria, it should be made clear that complete objectivity in answering the two questions is given by the rating scales. The question remained the same for all subjects and no additional comments were made. Validity can also be assumed for the questionnaire, since the subjects couls ask follow-up questions and thus uncertainties were clarified. However, similar to the video data, there was no perfect reliability with this survey instrument, because in a few exceptional cases, for example, the experimenter forgot to ask the subject the relevant questions.

#### Situational Jugdement Test

To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, [@gold2015development]). In the questionnaire, participants were given hypothetical school scenarios with with 5-7 response strategy for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).

In developing the test procedure, the authors divided the concept of classroom management into three main aspects: *Monitoring*, *managing momentum* (structuring) and *rules and routines* [@gold2015development, p. 230f].

*Monitoring* includes proactive strategies such as omnipresence. This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them. The second strategy is overlapping. In this case, the teacher is able to control several teaching processes at the same time. Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf. ibid.; [@kounin2006techniken, p. 89ff).

By *managing momentum* (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention [@kounin2006techniken, p. 101ff]. They also include the group focus specifically identified by Kounin [@kounin2006techniken, p. 117ff], i.e. mobilizing the whole class and demanding accountability [@gold2015development, p. 231].

The third facet of classroom management, establishing *rules, routines and rituals*, supports the other two facets and offers pupils orientation and structure in everyday school life (cf. ibid.).

The construction of the SJT included 14 scenarios that were based on transcribed classroom videos from Germany. For the 14 scenarios, response strategies were derived from evidence-based and theoretical principles by 17 experts on classroom management. With the exception of scenario 5, which was subsequently excluded, the 17 experts agreed on an appropriate level of content validity for all other scenarios (cf. ibid.). For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf. ibid., p. 238). Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf. ibid.).

The construct validity of the SJT with the other 11 scenarios and the sensitivity to differences in strategic knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf. ibid., p. 238ff). Despite limitations in reliability, the test was confirmed to have content and construct validity (cf. ibid., p. 243). On the basis of these results, sufficient reliability and validity of the SJT test procedure was assumed.

The scenarios could each be assigned to one facet of the mentioned classroom management: Scenarios 1-4 cover the facet *monitoring*, scenarios 6-9 the facet *managing momentum* and scenarios 11-14 the facet *rules and routines*.

In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study *ProVisioNET*. The objectivity of analysis was given by processing the obtained questionnaire data in `r cite_r("r-references.bib")` and IBM SPSS 28.

Since the test was a questionnaire designed to assess strategic knowledge of classroom management of *primary school teachers*, but the sample of the study included several types of schools, changes were made in 10 out of 12 scenarios by deleting the indicated class grade. Only in two scenarios was the class grade information not deleted, as the action alternatives would otherwise not be appropriate without the information.

## Procedure

The project was conducted as a laboratory study in a cross-sectional study design to investigate whether and how teachers' experience has an influence on the perception of and reaction to classroom disruptions.

In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and Septemper 2022.

Before the data collection, each subject received a personal digital meeting with the experimenter to go over the study procedure and to arrange a date for the data collection. During the digital meeting, the subjects were asked to prepare a 15-minute lesson in a subject and grade of their choice for the data collection.

On the day of a data collection, the first step was to set up the study room at the University of Leipzig. For this, all the appropriate technical equipment was charged and installed in the room (see set up plan [REFERENZ EINFÜGEN]). Next, all four cameras and the audio recorder were synced via Timecode System.

After the subject arrived, a smart watch was put on to measure the heart rate during the session and to get a pretest time at least 15min before the session started. In addition to the experimenter and the subject, three student assistants from the working group always took part in the data collection, as they represented the class.

After the welcome, the subject was again briefed about the study. It was explicitly pointed out that the student assistants would act as the class and simulate typical class events during the lesson. The subject was asked in advance to behave as naturally as possible during the entire time. Next, the subjects' written informed consent was obtained and contact details were collected in order to inform all persons participating in the study if a covid infection should occur.

After the introduction, the eye-tracking glasses were adjusted for the subject by inserting contact lenses if necessary and changing the nose pad. To start the eye tracking glasses, the Tobii Glasses must be fitted onto the subject's head via an one-point-calibration. In the calibration process the subject was asked to look at a Calibration Card held in-front of the subject for a few seconds. The experimenter started the recording from Tobii Glasses Controller Software running on a computer.

After starting the eye tracking recording, all other technical devices were also switched on: The four cameras and the audio recorder were controlled via iPad using the BLINK Hup app and could be started simultaneously by synchronization. The ZED camera was started manually on another laptop.

Before the 15-minute lesson, there was a short 10-minute warm-up phase. The phase was divided into two parts and served on the one hand to get the subjects used to the eye-tracking glasses and on the other hand to get used to their class. In the first phase of the warm-up, the game "name juggling" was played using two balls. In the game, the subject and the three actors threw two balls at each other and, depending on the color of the ball, called either their own name or that of the target person. After the name juggling, the subjects were supposed to start a conversation. For this, the subject thought of a question for each student and was also asked a question of each student. The content could be anything that interested the participants.

After the warm up phase, the experimenter ensured a manual synchronization of the technique by an acoustic signal in which she clapped her hands loudly twice standing in the middle of the room. After this, another nine-point calibration followed outside the study room in a neighboring room. Before the subject left the room for calibration, the time on the smartwatch was noted, as well as the steps recorded until that point. The subject had to stand at a marked point and look at a board three meters away with nine april tags. The subject was asked to read the nine points aloud in order at a normal speaking speed. This procedure was important to validate the one-point calibration on the one hand and on the other hand to give the subject the feeling of a lesson start, because after this calibration the subject came into the study room to start the 15-minute lesson.

For the micro-teaching lesson, student teachers and experienced teachers were asked to prepare an introduction of 15 minutes which they taught in front of the fictitious class consisting of three student assistants. The actors simulated the nine classroom events during the lesson, derived by research literature. The order of the disruptions as well as the students performing them were fully balanced using Latin Square. The disruptions were only visible for the class on a screen.

```{r disruption_categories, include=TRUE, echo=FALSE, results='asis'}
df_disrup_table <- data.frame(`Verbal Disruption` = c("chatting with neighbor", "whispering with neighbor", "heckling"),
                              Agitation = c("drumming hands", "clicking pen", "snipping with fingers"),
                              `Lack of eagerness to learn` = c("putting head on table", "looking at phone", "drawing on a sheet of paper")
                              )

papaja::apa_table(x = df_disrup_table,
                  caption = "Categories of Disruptions (Lohmann, 2015)",
                  escape = TRUE,
                  placement = "h",
                  font_size = "tiny")

```

During the lesson, a mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson. All other sounds and voices were recorded by an audio recorder. To record facial expressions, gestures and movements, four mobile cameras were installed to record the classroom from all perspectives (!!!see figures).

After the lesson, the time was again noted from the smartwatch as well as the subject's steps. The nine-point calibration was also performed again in the neighboring room. This time, however, the subject was asked to wait outside the room until he or she was called in, because four letters from A to D were placed in the study room. The subject was asked to stand facing the board at a marked point in the room and, when given an acoustic signal, to turn around and search the letters and read them aloud in order. This served as a control condition for the speed of the subjects' perceptual ability as no expertise is required for searching letters.

After the letter search, the experimenter clapped twice with the hands to record an acoustic signal for the synchronization of all technical devices. Afterwards, all devices were switched off and the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature. The completion of the questionnaire took approximately 5 minutes.

In the second part of the study, the experimenter conducted a Stimulated Recall Interview (SRI) with the subject(see in Figure \@ref(fig:sri). The interview was recorded by the ambient recorder and additionally with a software called OBS to record the speech and screen. The recorded eye-tracking video was watched and commented on by the subject while thinking aloud. The interview was structured by a guideline based on a fixed sequence of questions, however the subjects were allowed to answer completely open to these questions. The objective was to collect data that would provide insight into the subjects' thoughts and reactions in relation to the scripted classroom disruptions. The eye-tracking video was not completely re-watched, but stopped at the points where disruptions occurred. After the disruption occurred, the subject was asked to describe what had just happened. If the disruption was noticed, the subject was asked how disruptive the event was at that moment on a scale from 0 to 10 (for a detailed description of the scale question, see Rating Scales). In addition, the subject was asked to reason the given number. In a next step, the experimenter re-played the subject's reaction to the disruption and asked to describe and reason the reaction. The

```{r sri, include = T, fig.cap = "Subject and experimenter during the Stimulated Recall Interview", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/sri.pdf", dpi = 108)

```

Finally, the subjects answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management. The
completion of the entire survey took 15 min on average.

## Data analysis

We investigated whether experts and novice teachers differed

All reported data analyses were conducted with the `r cite_r("r-references.bib")` and IBM SPSS 28.

# Results

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2022-07-01 02_paper/02_study/paper_methods.tex
method section

--- 2022-07-01 02_paper/02_study/paper_methods.Rmd
@@
----
-title             : "Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions"
-shorttitle        : "Professional Vision in Micro-Teaching-Units"
-
-author: 
-  - name          : "Mandy Klatt"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Dittrichring 5-7, 04109 Leipzig"
-    email         : "mandy.klatt@uni-leipzig.de"
-  - name          : "Dr. Gregor Kachel"
-    affiliation   : "1, 2"
-  - name          : "Dr. Christin Lotz"
-    affiliation   : "1"
-  - name          : "Prof. Dr. Anne Deiglmayr"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Leipzig University"
-  - id            : "2"
-    institution   : "Max Planck Institute for Evolutionary Anthropology"
-
-authornote: |
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  man]{apa6}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
+  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
+  pdflang={en-EN},
+  pdfkeywords={professional vision, expertise, classroom management, mobile eye-tracking},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+% Manuscript styling
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+% Table formatting
+\usepackage{longtable}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\keywords{professional vision, expertise, classroom management, mobile eye-tracking\newline\indent Word count: XXX}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
+\usepackage{lineno}
+
+\linenumbers
+\usepackage{csquotes}
+\usepackage[titles]{tocloft}
+\cftpagenumbersoff{table}
+\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
+\renewcommand{\cfttabaftersnum}{.\space}
+\setlength{\cfttabindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cfttabnumwidth}{Table 10.\qquad}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+
+\title{Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions}
+\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
+\date{}
+
+\shorttitle{Professional Vision in Micro-Teaching-Units}
+
+\authornote{
 
@@
 
-abstract: |
-
-keywords          : "professional vision, expertise, classroom management, mobile eye-tracking"
-wordcount         : "XXX"
-
-bibliography      : ["r-references.bib"]
-
-floatsintext      : no
-figsintext        : no
-figurelist        : no
-tablelist         : yes
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-# bookdown::word_document2
----
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(include = FALSE)
-library("papaja")
-r_refs(file = "r-references.bib")
-```
-
-```{r analysis-preferences, include=FALSE}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
-
-```{r include=FALSE}
-# install.packages("needs")
-
-# suppress "summarize" info. 
-# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
-options(dplyr.summarise.inform = FALSE)
-
-library(needs)
-
-needs(tidyverse,
-      lubridate,
-      viridis,
-      grid,
-      gridExtra,
-      cowplot,
-      readxl,
-      ARTofR,
-      moments,
-      ltm,
-      sjPlot,
-      kableExtra,
-      xtable,
-      DescTools,
-      formattable)
-
-```
-
-# Introduction
-
-Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson & Weinstein, 2006; Kounin, 2006).
+Correspondence concerning this article should be addressed to Mandy Klatt, Dittrichring 5-7, 04109 Leipzig. E-mail: \href{mailto:mandy.klatt@uni-leipzig.de}{\nolinkurl{mandy.klatt@uni-leipzig.de}}
+
+}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Leipzig University\\\textsuperscript{2} Max Planck Institute for Evolutionary Anthropology}
+
+\begin{document}
+\maketitle
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson \& Weinstein, 2006; Kounin, 2006).
 Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom.
 This ability is referred to as classroom professional vision (Goodwin, 1994; Sherin, 2007).
-The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (“noticing”) and applying knowledge to draw appropriate conclusions in these situations (“knowledge-based reasoning”; Seidel & Stürmer, 2014).
-Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students’ learning time and minimize classroom interruptions.
-According to Kounin (2006), these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring (Gold & Holodynski, 2017).
+The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (``noticing'') and applying knowledge to draw appropriate conclusions in these situations (``knowledge-based reasoning''; Seidel \& Stürmer, 2014).
+Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students' learning time and minimize classroom interruptions.
+According to Kounin (2006), these important classroom management strategies are called ``withitness'' and ``overlapping'' and can be summarized under the concept of monitoring (Gold \& Holodynski, 2017).
 Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017).
-Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, “[…] whereas only a few studies have focused on the basal process of noticing, i.e.
-the recognition of possible disturbing situations” (Grub et al., 2020, p.75).
+Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, ``{[}\ldots{]} whereas only a few studies have focused on the basal process of noticing, i.e.~the recognition of possible disturbing situations'' (Grub et al., 2020, p.75).
 Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner et al., 2016; Wolff et al., 2016).
 
-# Theoretical background
-
-## Professional competence in teaching profession
+\hypertarget{theoretical-background}{%
+\section{Theoretical background}\label{theoretical-background}}
+
+\hypertarget{professional-competence-in-teaching-profession}{%
+\subsection{Professional competence in teaching profession}\label{professional-competence-in-teaching-profession}}
 
@@
 Teachers have to be competent in things such as teaching, educating, evaluating or innovating.
-Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig & Rauch, 2008).
+Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig \& Rauch, 2008).
 They replace the rigid canon of knowledge that defined professional qualification for generations.
 In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.).
-To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf.
-Klieme et al., 2008, p.
-4).
+To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf.~Klieme et al., 2008, p.~4).
 In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.
@@
 In science, there is some agreement on the two opposing perspectives of competence versus empowerment.
-The former means a broad, concept, whereas empowerment refers to the different components of competence (cf.
-of competence (cf.
-Blömeke, Gustafsson & Shavelson, 2015, p.5).
+The former means a broad, concept, whereas empowerment refers to the different components of competence (cf.~of competence (cf.~Blömeke, Gustafsson \& Shavelson, 2015, p.5).
 These can be of a cognitive, conative, affective, or motivational nature (ibid.).
@@
 
-Competence is learnable and can thus be improved through targeted practice (cf.
-Weinert 2001; cited in Blömeke et al.
-2015, p.
-5).
+Competence is learnable and can thus be improved through targeted practice (cf.~Weinert 2001; cited in Blömeke et al.~2015, p.~5).
 This is one reason, among others, why this concept is so relevant for empirical school and development research.
 Another crucial step in clarifying the concept of competence is to understand that the framework of competence recognizes the importance of everyday life situations (Blömeke et al., 2015).
-Therefore scholars argue, a definition must start from an authentic "analysis of occupational or societal situations and must take into account the tasks and associated associated cognitive, conceptual, affective, and motivational aspects" (Blömeke et al., 2015, p.
-5).
+Therefore scholars argue, a definition must start from an authentic ``analysis of occupational or societal situations and must take into account the tasks and associated associated cognitive, conceptual, affective, and motivational aspects'' (Blömeke et al., 2015, p.~5).
 Through this comprehensive approach, many inconsistencies in the definition of the term can be resolved.
 The definition of competence is now no longer a question of whether it is a number of cognitive skills or a combination of cognition, conation, affect, or motivation.
-It combines "complex intellectual characteristics together with affect-motivation, which underlies observable underlying performances" (Blömeke et al.
-2015, p.
-6).
+It combines ``complex intellectual characteristics together with affect-motivation, which underlies observable underlying performances'' (Blömeke et al.~2015, p.~6).
 This is best defined as a process or even continuum (see Figure 1), which consists of different levels and should be understood as a multidimensional construct with stronger and weaker Domains (ibid.).
@@
 
-The term "professional competence" is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation." (cf.
-Epstein & Hundert, 2002; cited in Kunter et al.
-2013, p.
-807).
-Several studies could prove that this idea can be successfully transferred to the teaching profession (cf.
-Goodmann et al., 2008; Oster, Achtenhagen & Renold, 2006; Tannenbaum & Rosenfeld, 1994; cited in Kunter et al., 2013, p.
-807).
+The term ``professional competence'' is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation.'' (cf.~Epstein \& Hundert, 2002; cited in Kunter et al.~2013, p.~807).
+Several studies could prove that this idea can be successfully transferred to the teaching profession (cf.~Goodmann et al., 2008; Oster, Achtenhagen \& Renold, 2006; Tannenbaum \& Rosenfeld, 1994; cited in Kunter et al., 2013, p.~807).
 Accordingly, a quality standard can be applied to assess the quality of a teacher.
-This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano & Pickering, 2003).
+This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano \& Pickering, 2003).
 Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher.
@@
 
-## Classroom Management
+\hypertarget{classroom-management}{%
+\subsection{Classroom Management}\label{classroom-management}}
 
 Teachers and students are in the classroom in a place that is always alive, characteristic of its heterogeneity and the interests of different groups.
-These the circumstances of a classroom are also characterized as multidimensional, simultaneous, immediate, unpredictable, public, and shared (Doyle, 2011, p.
-99).
+These the circumstances of a classroom are also characterized as multidimensional, simultaneous, immediate, unpredictable, public, and shared (Doyle, 2011, p.~99).
 All of these circumstances place a number of demands on teachers, which primarily involve planning and monitoring activities (ibid.).
-"Order in classrooms is not a consequence of reactions to misbehavior but a condition established and sustained by the way a teacher organizes and guides a complex system of classroom activities" (Doyle, 1989, p.12).
-Thus, "good" teachers create the conditions for effective teaching through pre-planned actions and activities that they are always in control of while teaching.
+``Order in classrooms is not a consequence of reactions to misbehavior but a condition established and sustained by the way a teacher organizes and guides a complex system of classroom activities'' (Doyle, 1989, p.12).
+Thus, ``good'' teachers create the conditions for effective teaching through pre-planned actions and activities that they are always in control of while teaching.
 This enables them to maximize work time while keeping disruptions of any kind to a minimum to facilitate learning for all participants (Doyle, 1989).
@@
 This trained handling, as described above, can be summarized under the aspect of professional competence.
-It is expressed, among other things, in knowledge about classroom management (Grub, Biermann & Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
-
-Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, van den Bogert, Jarodzka & Boshuizen, 2015).
+It is expressed, among other things, in knowledge about classroom management (Grub, Biermann \& Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
+
+Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, van den Bogert, Jarodzka \& Boshuizen, 2015).
 Marzano et al.'s (2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching.
 In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015).
-Therefore, it is often referred to as the central variable of successful teaching (Helmke & Helmke, 2015).
+Therefore, it is often referred to as the central variable of successful teaching (Helmke \& Helmke, 2015).
 Good classroom management is thus the prerequisite for learning to take place (Wolff et al., 2015).
@@
 
-An initial explanatory approach to classroom management was provided by Doyle (1990, p.355) with his definition of teaching, which he described as a "cognitive activity based on knowledge of the probable course of events in the classroom and the ways in which actions affect situations." From this, it is clear that in order to teach successfully, a teacher needs knowledge of how to process as well as represent the full range of classroom events.
+An initial explanatory approach to classroom management was provided by Doyle (1990, p.355) with his definition of teaching, which he described as a ``cognitive activity based on knowledge of the probable course of events in the classroom and the ways in which actions affect situations.'' From this, it is clear that in order to teach successfully, a teacher needs knowledge of how to process as well as represent the full range of classroom events.
 In addition, it is necessary to be able to respond or interact proactively and effectively to potential events at best.
 
-Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf.
-Wolff et al., 2015, p.
-71).
+Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf.~Wolff et al., 2015, p.~71).
 These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.).
 If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction.
-This is crucial to maximize students' active learning time (Helmke & Helmke, 2015).
+This is crucial to maximize students' active learning time (Helmke \& Helmke, 2015).
 It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research.
@@
 
-### Interdependence of classroom management
+\hypertarget{interdependence-of-classroom-management}{%
+\subsubsection{Interdependence of classroom management}\label{interdependence-of-classroom-management}}
 
@@
 Helmke (2014) therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time.
-This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (*d* = 0.39; Hattie, 2013, p.219).
+This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (\emph{d} = 0.39; Hattie, 2013, p.219).
 Due to this diversity of aspects to be investigated, classroom management is a fundamental research topic.
 
-The concepts, strategies and techniques used to implement successful classroom management depend first and foremost on various teacher characteristics and are "interrelated with the quality of teaching and personal relationships" (Helmke & Helmke, 2015, p.5).
+The concepts, strategies and techniques used to implement successful classroom management depend first and foremost on various teacher characteristics and are ``interrelated with the quality of teaching and personal relationships'' (Helmke \& Helmke, 2015, p.5).
 It should not be forgotten that this space never functions in isolation and independently of other influences.
-It is embedded in diverse contexts, especially in the school and class context (Helmke & Helmke, 2015).
+It is embedded in diverse contexts, especially in the school and class context (Helmke \& Helmke, 2015).
 But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led (Helmke, 2014).
@@
 Classroom management itself is made up of various components which, according to Helmke (2014), can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior.
-Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke & Helmke, 2015).
+Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke \& Helmke, 2015).
 
 The importance of rules in the classroom has been known and researched for some time.
-Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules (cf.
-Emmer, Evertson & Anderson, 1980; Emmer, Sanford, Clements & Martin, 1982; cited in Doyle, 1989, p.
-15).
+Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules (cf.~Emmer, Evertson \& Anderson, 1980; Emmer, Sanford, Clements \& Martin, 1982; cited in Doyle, 1989, p.~15).
 Although he also stresses that establishing a system of rules is a difficult task.
@@
 As a result, students significantly influence these rules by their willingness to follow them.
-Procedures are another tool to maintain the flow of the lesson, as recurring routines provide learners with security and clarity (Helmke & Helmke, 2015).
+Procedures are another tool to maintain the flow of the lesson, as recurring routines provide learners with security and clarity (Helmke \& Helmke, 2015).
 This inevitably reduces the teacher's workload, eliminates additional explanations are no longer necessary, and it is clear to the learners at all times what needs to be done.
@@
 In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time (Helmke, 2014).
-For the reasons just reasons just explained, it is clear why Hattie (2013, p.
-122) gives this component of classroom classroom management an effect size of *d* = 0.76.
-
-No other aspect of classroom management is as effective for classroom interruptions as the teacher's omnipresence (Hattie, 2013, p.
-122); the effect size is *d* = 1.42.
-(Helmke & Helmke, 2015, p.
-6).
+For the reasons just reasons just explained, it is clear why Hattie (2013, p.~122) gives this component of classroom classroom management an effect size of \emph{d} = 0.76.
+
+No other aspect of classroom management is as effective for classroom interruptions as the teacher's omnipresence (Hattie, 2013, p.~122); the effect size is \emph{d} = 1.42.
+(Helmke \& Helmke, 2015, p.~6).
 The behavioral pattern of presence is not a new concept.
-It was already recorded by Kounin in 1970 under the term *withitness*.
-Later research confirmed and validated his assumptions and definition of the term (cf.
-Helmke, 2014, p.10).
+It was already recorded by Kounin in 1970 under the term \emph{withitness}.
+Later research confirmed and validated his assumptions and definition of the term (cf.~Helmke, 2014, p.10).
 In order to be present, the teacher must be able to control the classroom adequately and superficially effectively at all times.
 This means she must be able to recognize relevant cues or situations that require possible action (Wolff et al., 2015).
-Presence can consequently be illustrated very vividly by means of the image of "eyes in the back of the head" (Kounin, 2006).
+Presence can consequently be illustrated very vividly by means of the image of ``eyes in the back of the head'' (Kounin, 2006).
 In addition to presence, Kounin (2006) uses the term overlap.
 It is a kind of multitasking ability to be able to cope with parallel processes and situations in the classroom.
-The two dimensions of overlap and presence can also be summarized together under the term monitoring (Gold & Holodynski, 2017).
+The two dimensions of overlap and presence can also be summarized together under the term monitoring (Gold \& Holodynski, 2017).
 When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners (Grub et al., 2020.).
@@
 This seems trivial at first, considering that classroom management serves the goal of maximizing learning time anyway.
-However, Helmke & Helmke (2015, p.
-6) emphasize how elementary it is to identify and minimize possible "time thieves".
+However, Helmke \& Helmke (2015, p.~6) emphasize how elementary it is to identify and minimize possible ``time thieves''.
 This includes factors such as unpunctuality or slow transitions, as well as the underemployment of learners (ibid.).
 If these take up too much space in the classroom, less time is available for teaching important lesson content.
-This can be prevented by teachers minimizing such "time thieves" in advance through well-planned classroom management.
-
-In order to enforce desired student behavior or to reduce contradictory behavior, teachers can use various discipline-related interventions and also make use of negative sanctions and positive reinforcement (Helmke & Helmke, 2015).
+This can be prevented by teachers minimizing such ``time thieves'' in advance through well-planned classroom management.
+
+In order to enforce desired student behavior or to reduce contradictory behavior, teachers can use various discipline-related interventions and also make use of negative sanctions and positive reinforcement (Helmke \& Helmke, 2015).
 The authors emphasize that a healthy balance must be found when using these strategies.
@@
 However, elements such as reinforcement, extinction or punishment are not negligible laws of learning psychology whose effectiveness has been proven by Hattie (2013), among others.
-These behavioral psychological measures have an effect size of *d* = 0.76 (cf.
-Hattie, 2013, p.215) and are therefore an effective means of reducing disruptions (Helmke & Helmke, 2015).
-
-Researchers in pedagogy also point out, however, that it is not only pure knowledge about classroom management that determines its effectiveness and influences it (Helmke & Helmke, 2015).
-The teacher personality, which includes characteristics such as subjective tolerance margins, i.e.
-at what point does one perceive a certain behavior as disruptive, also plays a role.
+These behavioral psychological measures have an effect size of \emph{d} = 0.76 (cf.~Hattie, 2013, p.215) and are therefore an effective means of reducing disruptions (Helmke \& Helmke, 2015).
+
+Researchers in pedagogy also point out, however, that it is not only pure knowledge about classroom management that determines its effectiveness and influences it (Helmke \& Helmke, 2015).
+The teacher personality, which includes characteristics such as subjective tolerance margins, i.e.~at what point does one perceive a certain behavior as disruptive, also plays a role.
 This includes further aspects such as emotion control, empathy or the credibility of a teaching person that arises through appearance.
@@
 
-## Professional vision
+\hypertarget{professional-vision}{%
+\subsection{Professional vision}\label{professional-vision}}
 
@@
 In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes (Barth, 2017).
-Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel & Prenzel 2014).
+Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel \& Prenzel 2014).
 The concept of professional vision can originally be traced back to the anthropologist Charles Goodwin and became known under the term Professional Vision (Sherin, 2001).
@@
 Goodwin uses the comparison of an archaeologist and a layperson to figuratively describe the differences.
-In doing so, he investigated which ability it is that makes the archaeologist see and interpret a landscape differently than the layperson (cf.
-Sherin, 2001, p.
-75).
+In doing so, he investigated which ability it is that makes the archaeologist see and interpret a landscape differently than the layperson (cf.~Sherin, 2001, p.~75).
 What looks to the former merely like sand, rocks and stones, is to the trained eye of the archaeologist a base of a column or architectural fragments.
-Goodwin (1994, p.606) defines professional vision as "socially organized ways of seeing and understanding events that are answerable to the distinctive interests of a particular social group" (cited in Sherin, 2001, p.
-75).
+Goodwin (1994, p.606) defines professional vision as ``socially organized ways of seeing and understanding events that are answerable to the distinctive interests of a particular social group'' (cited in Sherin, 2001, p.~75).
 It is assumed that one can see certain phenomena or occurring events in a certain way due to one's professional affiliation (Sherin, 2001).
 Particularities are more easily recognized because the gaze becomes more trained over time and thus profession-relevant features appear more distinctive.
-In the previous example of the archaeologist, this would mean that he noticed variations in color, texture and sand and saw a cluster of stones as a possible element of a larger structure (cf.
-Sherin, 2001, p.75).
+In the previous example of the archaeologist, this would mean that he noticed variations in color, texture and sand and saw a cluster of stones as a possible element of a larger structure (cf.~Sherin, 2001, p.75).
 This distinguishes experts significantly in their visions from non-experts in the field, as they had learned to filter their environment for crucial features.
 
-### Teachers' professional vision
+\hypertarget{teachers-professional-vision}{%
+\subsubsection{Teachers' professional vision}\label{teachers-professional-vision}}
 
 Based on the assumption that the professional vision can develop over time, Sherin (2001) postulates that teachers can also acquire a professional vision.
-As teachers develop from novices to experts in their field, they accumulate expertise in a variety of areas (cf.
-Sherin, 2001, p.
-76).
-This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom (Berliner, 1994; Leinhardt & Greeno, 1986).
-This type of action can be described as a skill that helps teachers make decisions about what is relevant and what is not within the complex classroom setting (van Es & Sherin, 2002).
+As teachers develop from novices to experts in their field, they accumulate expertise in a variety of areas (cf.~Sherin, 2001, p.~76).
+This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom (Berliner, 1994; Leinhardt \& Greeno, 1986).
+This type of action can be described as a skill that helps teachers make decisions about what is relevant and what is not within the complex classroom setting (van Es \& Sherin, 2002).
 Such decisions are based on professional knowledge that guarantees effective teaching and learning in actual classroom situations (Jahn et al., 2014).
@@
 Simultaneous events and situations cannot be given the same attention.
-"Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects" (Barth, 2017, p.19).
+``Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects'' (Barth, 2017, p.19).
 Furthermore, teachers benefit from from a trained perception of problems, as this is a significant factor in being able to preventively counteract preventive measures (Wettstein, 2013).
@@
 This process is therefore considered necessary, without which professional vision cannot take place (Grub et al., 2020).
-As described in the chapter on competence, perceptions is also of particular importance in the competence model according to Blömeke et al.
-(2015).
+As described in the chapter on competence, perceptions is also of particular importance in the competence model according to Blömeke et al.~(2015).
 This is because the process of perception forms an essential basis for situation-specific skills of teachers (Grub et al., 2020).
@@
 Qualitative research on knowledge-based reasoning concluded that it can be subdivided into three further sub-processes.
-Sherin (2007; cited in Barth, 2017, p.
-20) made a first subdivision, which consists of the processes of describing, evaluating and interpreting.
-When a teacher describes what she notices, she concentrates on observable characteristics, i.e.
-important aspects of teaching (ibid.).
-When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event (cf.
-Barth, 2017, p.
-19).
-Seidel et al.
-(2010), on the other hand, focus on German-speaking countries in their research on professional vision and modified Sherin's original concept.
+Sherin (2007; cited in Barth, 2017, p.~20) made a first subdivision, which consists of the processes of describing, evaluating and interpreting.
+When a teacher describes what she notices, she concentrates on observable characteristics, i.e.~important aspects of teaching (ibid.).
+When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event (cf.~Barth, 2017, p.~19).
+Seidel et al.~(2010), on the other hand, focus on German-speaking countries in their research on professional vision and modified Sherin's original concept.
 They also divide knowledge-based-reasoning into three levels, but these differ: describing, explaining and predicting (Barth, 2017).
-More precisely, these processes encompass the ability to differentially describe instructional components that have an impact on learning; to make theoretically sound explanations about instructional situations; and to predict the effects of these events in relation to the teaching-learning process (cf.
-Seidel et al., 2010, p.
-297).
+More precisely, these processes encompass the ability to differentially describe instructional components that have an impact on learning; to make theoretically sound explanations about instructional situations; and to predict the effects of these events in relation to the teaching-learning process (cf.~Seidel et al., 2010, p.~297).
 This scientific work examines only the processes of noticing, which is why these two approaches have been presented for the sake of completeness.
@@
 
-Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect (Sherin, 2007; cited in Barth, 2017, p.
-19).
+Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect (Sherin, 2007; cited in Barth, 2017, p.~19).
 What is considered and perceived as relevant in a teacher's selective vision (noticing) functions as the basis of the subsequent processes of describing, evaluating, and interpreting (knowledge-based-reasoning).
@@
 
-## Measuring professional vision: eye-tracking technology in research
+\hypertarget{measuring-professional-vision-eye-tracking-technology-in-research}{%
+\subsection{Measuring professional vision: eye-tracking technology in research}\label{measuring-professional-vision-eye-tracking-technology-in-research}}
 
@@
 Eye-tracking research is based on several fundamental assumptions.
-The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date (cf.
-Blake, 2018, p.380).
+The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date (cf.~Blake, 2018, p.380).
 In this regard, Hoffmann and Subramaniam (1995) obtained the finding that when the eyes are focused on an object, this is associated with an attentional focus of the person.
-Based on these findings, ET technology is based on the following two assumptions: The immediacy assumption and the eye-mind assumption (cf.
-Rakoczi, 2012, p.87).
+Based on these findings, ET technology is based on the following two assumptions: The immediacy assumption and the eye-mind assumption (cf.~Rakoczi, 2012, p.87).
 The former defines that cognitive evaluation processes begin immediately upon fixation on an object (Cullipher, 2018).
@@
 The eye-mind hypothesis assumes that whatever is fixated by the eye, is subsequently processed by the mind (ibid.).
-It thereby expansively defines, that objects are visually focused only until they are cognitively evaluated or until there is have been cognitively evaluated or there is still an interest (cf.
-Rakoczi, 2012, p.87).
+It thereby expansively defines, that objects are visually focused only until they are cognitively evaluated or until there is have been cognitively evaluated or there is still an interest (cf.~Rakoczi, 2012, p.87).
 However, a situational context must exist for the assumptions just explained to be are valid (ibid.).
@@
 An elaborated form of the Think Aloud Protocol is a Stimulated-Recall Interview (SRI).
-This is a qualitative scientific method to obtain data on preactional thought processes (cf.
-Messmer, 2015, p.4).
-The pre-recorded lesson sequences are played back and subjects have the opportunity to express themselves about their "thoughts, beliefs, norms, and decisions" (Messmer, 2015, p.4) during the interview process.
+This is a qualitative scientific method to obtain data on preactional thought processes (cf.~Messmer, 2015, p.4).
+The pre-recorded lesson sequences are played back and subjects have the opportunity to express themselves about their ``thoughts, beliefs, norms, and decisions'' (Messmer, 2015, p.4) during the interview process.
 Thus, the visual data of the ET can be matched with cognitive processes and processes of knowledge-based-reasoning can be better understood.
@@
 
-### Parameters and indicators of teachers' professional vision
+\hypertarget{parameters-and-indicators-of-teachers-professional-vision}{%
+\subsubsection{Parameters and indicators of teachers' professional vision}\label{parameters-and-indicators-of-teachers-professional-vision}}
 
@@
 Significant for this scientific work and the analysis of professional vision are the fixations as well as subjects' areas of interests.
-Fixations describe the period of time in which no movements are emitted by the eye (Holmquist et al.
-2011) and are based on the eye-mind hypothesis described in the previous chapter.
+Fixations describe the period of time in which no movements are emitted by the eye (Holmquist et al.~2011) and are based on the eye-mind hypothesis described in the previous chapter.
 A fixation of an object can be characterized according to its duration, frequency, and distribution.
@@
 
-### Expertise differences in professional vision
+\hypertarget{expertise-differences-in-professional-vision}{%
+\subsubsection{Expertise differences in professional vision}\label{expertise-differences-in-professional-vision}}
 
@@
 Student teachers do not have well-structured experiential knowledge due to their almost non-existent practice in everyday school life (Wolff et al., 2016).
-This causes them selection difficulties in perception and is called pedagogical knowledge gap (cf.
-Wolff et al., 2016, p.260).
+This causes them selection difficulties in perception and is called pedagogical knowledge gap (cf.~Wolff et al., 2016, p.260).
 Through newly gained experiences, the professional vision of a teacher is continuously restructured and updated, and mental representation is constantly realigned accordingly (ibid.).
@@
 The former is elementary for new knowledge acquisition about effective teaching and learning, as it supports processing, integration, and consolidation of it (Stürmer, 2011).
-Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions (cf.
-Sabers, 1991; cited in Treisch, 2018).
+Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions (cf.~Sabers, 1991; cited in Treisch, 2018).
 This is explained by increased filtering mechanisms that support perceptual processes, i.e., recognition.
@@
 
-### Mobile eye tracking in teaching-learning situations
+\hypertarget{mobile-eye-tracking-in-teaching-learning-situations}{%
+\subsubsection{Mobile eye tracking in teaching-learning situations}\label{mobile-eye-tracking-in-teaching-learning-situations}}
 
@@
 In the worst case, they force a standstill in the flow of instruction, which is naturally to be avoided.
-Lohmann (2015, p.13) describes classroom disruptions as "events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place." However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive (cf.
-Eckstein, Grob & Reusser, 2016; cited in, Eckstein, 2018, p.11).
+Lohmann (2015, p.13) describes classroom disruptions as ``events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place.'' However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive (cf.~Eckstein, Grob \& Reusser, 2016; cited in, Eckstein, 2018, p.11).
 Thus, instructional disruptions are strongly dependent on perception and involve elements of production as well as reception (ibid.).
@@
 This simply means the attention or the conscious non-attention to visual stimuli (Rüth et al., 2020).
-This situational awareness of a teacher and the accompanying control of his or her visual attention forms the foundation of situation-specific skills (cf.
-Rüth et al.
-2020).
+This situational awareness of a teacher and the accompanying control of his or her visual attention forms the foundation of situation-specific skills (cf.~Rüth et al.~2020).
 These data and insights potentially to be collected form an interesting field of research and useful tool for problem-based teaching education (Cortina et al., 2018).
@@
 This characteristic makes it possible to analyze corresponding scenes more intensively and in more detail.
-This results in a potential for reflection on teaching situations in teacher education that should not be underestimated (cf.
-Rüth et al., 2020).
+This results in a potential for reflection on teaching situations in teacher education that should not be underestimated (cf.~Rüth et al., 2020).
 The problem with these videotaped sequences, however, is the lack of access to the first-person perspective (ibid.).
@@
 
-A successful method to reduce this hindering factor of self-drawn cognition and still use self videos for teacher education is to use recordings that show the teacher's perspective and furthermore make it known where the teacher was looking (cf.
-Cortina et al., 2018).
+A successful method to reduce this hindering factor of self-drawn cognition and still use self videos for teacher education is to use recordings that show the teacher's perspective and furthermore make it known where the teacher was looking (cf.~Cortina et al., 2018).
 In MET's video material, teachers can never see their teaching through their own eyes.
 This makes it possible to focus more specifically on essential aspects, such as classroom disruptions and interactions with learners.
-Although it has not yet been clearly demonstrated that significantly less self-referential cognition was elicited, self-videos counteract over-focusing on the acting person (cf.
-Cortina et al., 2018).
+Although it has not yet been clearly demonstrated that significantly less self-referential cognition was elicited, self-videos counteract over-focusing on the acting person (cf.~Cortina et al., 2018).
 Therefore, MET represents a target-rich method for capturing teachers' attentional processes in the classroom.
 Previous studies with large data sets on teachers' visual expertise have predominantly used stationary ET (Wolff et al., 2016).
-In MET studies, the samples turn out to be much smaller; here, the largest study to be mentioned is with 12 experienced and 12 inexperienced teachers by Cortina et al.
-(2015).
-
-### Perceptions of classroom disruptions and their parameters
+In MET studies, the samples turn out to be much smaller; here, the largest study to be mentioned is with 12 experienced and 12 inexperienced teachers by Cortina et al.~(2015).
+
+\hypertarget{perceptions-of-classroom-disruptions-and-their-parameters}{%
+\subsubsection{Perceptions of classroom disruptions and their parameters}\label{perceptions-of-classroom-disruptions-and-their-parameters}}
 
@@
 However, their lack of expertise is not the sole reason for this phenomenon.
-Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher (Baumert & Kunter, 2006).
+Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher (Baumert \& Kunter, 2006).
 Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors.
 Individual person characteristics as well as contextual factors not only have an effect on teaching perception, but likewise on the sense of disturbance of a situation (Eckstein, 2019).
-These specific characteristics include aspects such as self-image, motivation, level of aspiration, attitudes, coping goals, and value orientations (Bakker & Demerouti, 2006; cited in Wickeren, 2019, p.
-33).
+These specific characteristics include aspects such as self-image, motivation, level of aspiration, attitudes, coping goals, and value orientations (Bakker \& Demerouti, 2006; cited in Wickeren, 2019, p.~33).
 Contextual characteristics include didactic staging or general level of disruption.
@@
 This reference group effect is also known as the Big-Fish-Little-Pond effect.
-Thus, it can be said that teachers' perceptions of situations and people are significantly shaped by their expectations and biases is shaped (cf.
-Eckstein, 2018).
+Thus, it can be said that teachers' perceptions of situations and people are significantly shaped by their expectations and biases is shaped (cf.~Eckstein, 2018).
 How strongly a disturbance is perceived and felt can also depend on psychological characteristics such as self-efficacy beliefs (ibid.
@@
 In order to be able to adequately counteract classroom disruptions and thus automatically reduce the sense of disruption and the experience of stress, it is important to address the concerns of the learners with empathy (Wickeren, 2019).
-Regarding gender as a factor, it should be noted that previous research has found higher levels of disruptiveness in discipline problems among female teachers (Kovess-Masféty, Rios-Seidel & Sevilla-Dedieu, 2007; cited in Wickeren, 2019, p.
-33).
-In summary can thus be summarized that the extent and perception of disturbances are based on individual cognitive evaluation processes, the situational context, attentional focus, didactic staging, and, indeed, professional experience (cf.
-Wickeren, 2019).
-
-# Research Questions and hypothesis
+Regarding gender as a factor, it should be noted that previous research has found higher levels of disruptiveness in discipline problems among female teachers (Kovess-Masféty, Rios-Seidel \& Sevilla-Dedieu, 2007; cited in Wickeren, 2019, p.~33).
+In summary can thus be summarized that the extent and perception of disturbances are based on individual cognitive evaluation processes, the situational context, attentional focus, didactic staging, and, indeed, professional experience (cf.~Wickeren, 2019).
+
+\hypertarget{research-questions-and-hypothesis}{%
+\section{Research Questions and hypothesis}\label{research-questions-and-hypothesis}}
 
@@
 Based on the existing literature, we expected expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation duration and (H3) perceiving classroom disruptions faster (cf.
-@van2014first), (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions (Barth, 2017), and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
-
-# Materials and Methods
+Van den Bogert, Bruggen, Kostons, and Jochems (2014)), (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions (Barth, 2017), and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
+
+\hypertarget{materials-and-methods}{%
+\section{Materials and Methods}\label{materials-and-methods}}
+
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
 
 This study had a quasi-experimental study design, as there was no random assignment of the subjects to experimental conditions.
-Due to the use of mobile eye-tracking technology, the study had a high external validity [@gegenfurtner2018mobiles].
+Due to the use of mobile eye-tracking technology, the study had a high external validity (Gegenfurtner et al., 2018).
 Internal validity could be ensured to the extent that the disruptive events that occurred were exactly the same for all subjects, as the actors received precise behavioral instructions.
@@
 
-## Participants
-
-```{r demographicstable, include = TRUE, echo=FALSE}
-
-# read in data and select and rename relevant columns with transmute 
-demo.data <- 
-  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
-  transmute(Group = LI06_05,
-            Gender = LI02_01_1,
-            Age = LI03_01,
-            `Teaching Experience` = LI04_01,
-            School_type = LI18,
-            Grade = LI16_05,
-            Subject = LI10_05,
-            Semester = LI11_01,
-            Internship = LI13_01,
-            `Extracurricular Teaching Experience` = LI14,
-            `Secondary Teaching Activities` = LI17
-            )
-
-# define expert and novice with ifelse function
-demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")
-
-# changing gender to count female gender (male = 2 --> 0)
-demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")
-
-# changing character Gender into numeric
-demo.data$Gender <- as.numeric(demo.data$Gender)
-
-# creating new column with total participants to calculate percent of gender
-demo.data <- demo.data %>%
-  group_by(Group) %>%
-  mutate(Sum_participants = n())
-
-# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
-demo.data$School_type[demo.data$School_type == 2] <- "1"
-
-# creating new column to calculate percent of school type
-demo.data <- 
-  demo.data %>%
-  group_by(School_type, Group) %>%
-  mutate(Count_Schooltype = sum(n())) %>% 
-  mutate(Percent_schooltype = round((Count_Schooltype/Sum_participants) * 100, 
-         digits = 2))
-
-# changing character Percent_schooltype into numeric
-demo.data$Percent_schooltype <- as.numeric(demo.data$Percent_schooltype)
-
-XXX
-
-# creating a subset to report school type in text
-demo.school <- 
-  demo.data %>% 
-  dplyr::select(Group,
-         Percent_schooltype) %>% 
-  group_by(Group) %>% 
-  summarise_each(funs(sum))
-
-# changing character Semester into numeric
-demo.data$Semester <- as.numeric(demo.data$Semester)
-
-# changing Type of School into character
-# LI18:
-# 1: Grundschule
-# 2: Oberschule
-# 3: Gymnasium
-# 4: Förderschule/Sondershausen
-# 5: Berufsbildende Schule
-# -1: andere Schulform
-demo.data$School_type <- factor(x = demo.data$School_type,
-                   levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
-                   labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen
-
-# changing `Extracurricular Teaching Experience` to count experience (no experience = 2 --> 0)
-demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 1, "1","0")
-
-# changing character Extra. Exp. into numeric
-demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)
-
-# changing `Secondary Teaching Activities` to count experience (no experience = 2 --> 0)
-demo.data$`Secondary Teaching Activities` = ifelse(demo.data$`Secondary Teaching Activities` == 1, "1","0")
-
-# changing character Extra. Exp. into numeric
-demo.data$`Secondary Teaching Activities` <- as.numeric(demo.data$`Secondary Teaching Activities`)
-
-# create new columns that give proportion of Gender
-# percent = female gender divided by all female Gender
-# demo.data <- demo.data  %>% 
-#   group_by(Group) %>% 
-#   mutate(Gender_percent = Gender/Sum_participants) %>% 
-#   mutate(Gender_percent = round(sum(Gender_percent)*100, digits=0))
-
-# create a basic table (tibble) using tidyverse functions
-demo.table <- demo.data %>%
-  group_by(Group) %>%
-  summarise(N=n(),
-            "Gender female in percent" = round(sum(Gender/Sum_participants) * 100, 
-                                               digits = 2),
-            "M Age in years" = round(mean(Age), 
-                                     digits = 2),
-            "SD Age in years" = round(sd(Age), 
-                                      digits = 2),
-            "Min Age in years" = min(Age),
-            "Max Age in years" = max(Age)
-            )
-
-# format and insert table in manuscript
-demo.table %>%
-papaja::apa_table(
-  caption = "Demographic Information",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-# create a basic table (tibble) using tidyverse functions
-exp.table <- demo.data %>%
-  group_by(Group) %>%
-  summarise(N=n(),
-           "M Exp." = round(mean(`Teaching Experience`), 2),
-            "SD Exp." = round(sd(`Teaching Experience`), 2),
-            "Min Exp." = min(`Teaching Experience`),
-            "Max Exp." = max(`Teaching Experience`),
-            "M Semester" = round(mean(Semester), 2),
-            "SD Semester" = round(sd(Semester), 2),
-            "Min Semester" = min(Semester),
-            "Max Semester" = max(Semester),
-            "M Internship" = round(mean(Internship), 2),
-            "SD Internship" = round(sd(Internship), 2),
-            "Min Internship" = min(Internship),
-            "Max Internship" = max(Internship),
-            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
-            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
-           )
-
-# format and insert table in manuscript
-exp.table %>%
-papaja::apa_table(
-  caption = "Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-The sample consisted of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:demographicstable}Demographic Information}
+
+\tiny{
+
+\begin{tabular}{lllllll}
+\toprule
+Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years}\\
+\midrule
+Expert & 19 & 57.89 & 41.68 & 10.41 & 27.00 & 59.00\\
+Novice & 26 & 65.38 & 23.38 & 1.72 & 20.00 & 27.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:demographicstable}Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent}
+
+\tiny{
+
+\begin{tabular}{llllllllllllllll}
+\toprule
+Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
+\midrule
+Expert & 19 & 13.84 & 12.30 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 47.00\\
+Novice & 26 & 0.00 & 0.00 & 0.00 & 0.00 & 7.15 & 2.62 & 3.00 & 11.00 & 10.92 & 8.09 & 0.00 & 36.00 & 88.46 & NA\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+The sample consisted of \emph{N} = 45 participants with \emph{n} = 19 expert teachers and \emph{n} = 26 novice teachers.
 
 The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
-According to @palmer2005identifying, we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
+According to Palmer, Stough, Burdenski, and Gonzales (2005), we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
 Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
 
-The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`).
-
-`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype")`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype")`% were secondary school teachers.
-
-`r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
-
-The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years.
-On average, the student teachers were in their `r exp.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`).
-Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies.
-
-`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype")`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype")`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype")`% to become special education teachers.
-
-`r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+The expert teachers (11 women; 57.89\%) had a mean age of 41.70 years (\emph{SD} = 10.40; range: 27-59) and an average teaching experience of 13.80 years (\emph{SD} = 12.30; range: 3-37).
+
+15.80, 15.80, and 15.80\% of the experts were primary school teachers and 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, and 84.21\% were secondary school teachers.
+
+47\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+
+The novice teachers (17 women; 65.38\%) had a mean age of 23.40 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years.
+On average, the student teachers were in their 7.20 semester (\emph{SD} = 2.60; range: 3-11).
+Furthermore, they had an average teaching experience of 10.90 teaching units à 45min (\emph{SD} = 8.10; range: 0-36) through the internships during their studies.
+
+19.23, 19.23, 19.23, 19.23, and 19.23\% of the novices were studying to become primary school teachers, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, and 65.38\% to become secondary school teachers and 15.38, 15.38, 15.38, and 15.38\% to become special education teachers.
+
+88.46\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
 
 The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at the University Leipzig.
-All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
+All study procedures were carried out in accordance with the ethical standards of the University's Institutional Review Board.
 The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
@@
 
-##
-
-## Variables
-
-All stimuli are freely available in the following online repository: https://github.com/... .
-
-### Eye-Tracking data
+\hypertarget{section}{%
+\subsection{}\label{section}}
+
+\hypertarget{variables}{%
+\subsection{Variables}\label{variables}}
+
+All stimuli are freely available in the following online repository: \url{https://github.com/}\ldots{} .
+
+\hypertarget{eye-tracking-data}{%
+\subsubsection{Eye-Tracking data}\label{eye-tracking-data}}
 
@@
 The system consisted of a wearable head unit and a recording unit.
-As shown in Figure \@ref(fig:tobiiglasses2), the head unit was a measuring device with different sensors.
-A high-definition scene camera captured a full HD video of the teacher’s field of vision.
+As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors.
+A high-definition scene camera captured a full HD video of the teacher's field of vision.
 An integrated microphone recorded the surrounding sounds.
-Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \@ref(fig:teachersgaze).
+Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \ref{fig:teachersgaze}.
 The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second.
@@
 
-```{r tobiiglasses2, include = T, fig.cap = "Tobii Pro Glasses 2; Source: https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/tobiiglasses2.png", dpi = 108)
-
-```
-
-```{r teachersgaze, include = T, fig.cap = "Teacher's Gaze Point", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/teachersgaze.pdf", dpi = 108)
-
-```
-
-### Video data
-
-The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \@ref(fig:setup).
+\begin{figure}
+
+{\centering \includegraphics[width=14.07in]{./pictures/tobiiglasses2}
+
+}
+
+\caption{Tobii Pro Glasses 2; Source: https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}\label{fig:tobiiglasses2}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/teachersgaze}
+
+}
+
+\caption{Teacher's Gaze Point}\label{fig:teachersgaze}
+\end{figure}
+
+\hypertarget{video-data}{%
+\subsubsection{Video data}\label{video-data}}
+
+The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \ref{fig:setup}.
 The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
 
-Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \@ref(fig:setup).
+Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \ref{fig:setup}.
 The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
 
-### Questionnaire data
-
-After each micro-teaching-unit, the three actors answered items on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature.
+\hypertarget{questionnaire-data}{%
+\subsubsection{Questionnaire data}\label{questionnaire-data}}
+
+After each micro-teaching-unit, the three actors answered items on teaching quality using a validated questionnaire (Helmke et al., 2014) and self developed scales on the teacher's presence behavior derived from the research literature.
 In addition, subjects were asked to give a self-assessment on classroom management by completing the same questionnaire after each micro-teaching-unit.
@@
 
-```{r presence_questionnaire_novices, include=TRUE, echo=FALSE, results='asis'}
-# load data files
-quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  mutate(Group = ifelse(LI06_05 < 200, "Novice","Expert")) %>%
-  dplyr::select(Group, LM01_01:LO01_02)
-
-# create two data frames
-quest.data.novice <- quest.data %>% filter(Group == "Novice")
-quest.data.expert <- quest.data %>% filter(Group == "Expert")
-
-############## NOVICE TABLE #########################
-
-# creating a matrix
-quest.table.novice <- matrix(data = NA, nrow = 4, ncol = 8)
-rownames(quest.table.novice) <- c("LM", "LB", "LP", "LV")
-  colnames(quest.table.novice) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
-
-# creating a loop
-# i <- "LM"
-
-for (i in c("LM", "LB", "LP", "LV")) {
-
-loop.data <- quest.data.novice %>%
-  dplyr::select(starts_with(match = i))
-
-quest.table.novice[i, "N Items"] <- length(loop.data)
-
-# calculating mean
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  mean() %>%
-  round(., digits = 2) ->
-quest.table.novice[i, "M"]
-
-# calculating SD
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  sd() %>%
-  round(., digits = 2) ->
-quest.table.novice[i, "SD"]
-
-# calculating Min
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  min() %>%
-  round(., digits = 2) ->
-quest.table.novice[i, "Min"]
-
-# calculating Max
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  max() %>%
-  round(., digits = 2) ->
-quest.table.novice[i, "Max"]
-
-# calculating Skewness
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  skewness() %>%
-  round(., digits = 2) ->
-quest.table.novice[i, "Skewness"]
-
-# calculating Kurtosis
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  kurtosis() %>%
-  round(., digits = 2) ->
-quest.table.novice[i, "Kurtosis"]
-
-# calculating alpha
-alpha <- loop.data %>%
-  cronbach.alpha()
-
-quest.table.novice[i, "alpha"] <- round(alpha$alpha,2)
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:presence_questionnaire_novices}Scale analysis for novices' self-assessment}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
+\midrule
+Classroom Management & 8.00 & 2.93 & 0.26 & 2.50 & 3.38 & 0.24 & 1.77 & 0.37\\
+Balance & 3.00 & 3.17 & 0.56 & 1.67 & 4.00 & -0.36 & 3.23 & 0.63\\
+Presence & 8.00 & 3.10 & 0.34 & 2.50 & 3.88 & 0.05 & 2.64 & 0.65\\
+Natural Behavior & 3.00 & 3.14 & 0.60 & 1.67 & 4.00 & -0.49 & 2.94 & 0.78\\
+\bottomrule
+\end{tabular}
 
@@
 
-# rename columns
-rownames(quest.table.novice) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
-
-# format and insert table in manuscript
-papaja::apa_table(
-quest.table.novice,
-  caption = "Scale analysis for novices' self-assessment",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-```
-
-```{r presence_questionnaire_experts, include=TRUE, echo=FALSE, results='asis'}
-
-############## EXPERT TABLE #########################
-
-# creating a matrix
-quest.table.expert <- matrix(data = NA, nrow = 4, ncol = 8)
-rownames(quest.table.expert) <- c("LM", "LB", "LP", "LV")
-  colnames(quest.table.expert) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
-
-# creating a loop
-# i <- "LM"
-
-for (i in c("LM", "LB", "LP", "LV")) {
-
-loop.data <- quest.data.expert %>%
-  dplyr::select(starts_with(match = i))
-
-quest.table.expert[i, "N Items"] <- length(loop.data)
-
-# calculating mean
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  mean() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "M"]
-
-# calculating SD
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  sd() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "SD"]
-
-# calculating Min
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  min() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "Min"]
-
-# calculating Max
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  max() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "Max"]
-
-# calculating Skewness
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  skewness() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "Skewness"]
-
-# calculating Kurtosis
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  kurtosis() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "Kurtosis"]
-
-# calculating alpha
-alpha <- loop.data %>%
-  cronbach.alpha()
-
-quest.table.expert[i, "alpha"] <- round(alpha$alpha,2)
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:presence_questionnaire_experts}Scale analysis for experts' self-assessment}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
+\midrule
+Classroom Management & 8.00 & 3.18 & 0.37 & 2.38 & 3.88 & 0.00 & 2.74 & 0.65\\
+Balance & 3.00 & 3.30 & 0.57 & 2.00 & 4.00 & -0.74 & 2.79 & 0.76\\
+Presence & 8.00 & 3.36 & 0.37 & 2.50 & 3.88 & -0.61 & 2.76 & 0.76\\
+Natural Behavior & 3.00 & 3.44 & 0.45 & 2.67 & 4.00 & -0.17 & 1.98 & 0.60\\
+\bottomrule
+\end{tabular}
 
@@
 
-# rename columns
-rownames(quest.table.expert) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
-
-# format and insert table in manuscript
-papaja::apa_table(
-quest.table.expert,
-  caption = "Scale analysis for experts' self-assessment",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-```{r item_analysis_classroom_management, include=TRUE, results='asis'}
-# quest.data %>%
-#   dplyr::select(contains("LM")) %>%
-#   as.data.frame() %>%
-#   tab_itemscale(CSS = list(
-#     css.firsttablerow.col7 = "'cronbachs alpha';"
-#   ))
-```
-
-```{r item_analysis_balance, include=TRUE, results='asis'}
-# quest.data %>%
-#   dplyr::select(contains("LB")) %>%
-#   as.data.frame() %>%
-#   tab_itemscale()
-```
-
-```{r item_analysis_presence, include=TRUE,results='asis'}
-# quest.data %>%
-#   dplyr::select(contains("LP")) %>%
-#   as.data.frame() %>%
-#   tab_itemscale()
-```
-
-```{r item_analysis_behavior, include=TRUE,results='asis'}
-# quest.data %>%
-#   dplyr::select(contains("LV")) %>%
-#   as.data.frame() %>%
-#   tab_itemscale()
-```
-
-#### Rating scales
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\hypertarget{rating-scales}{%
+\paragraph{Rating scales}\label{rating-scales}}
 
@@
 For the present study, the following two questions from the interview were relevant:
-1. "How disturbing did you perceive this event to be?"
-2. "How confident did you feel in dealing with this event?"
-
-Both questions were answered using a scale ranging from 0 to 10. On this scale, 0 stood for "not at all disruptive" or "not at all safe" and 10 for "extremely disturbing" or "extremely safe."
+1. ``How disturbing did you perceive this event to be?''
+2. ``How confident did you feel in dealing with this event?''
+
+Both questions were answered using a scale ranging from 0 to 10. On this scale, 0 stood for ``not at all disruptive'' or ``not at all safe'' and 10 for ``extremely disturbing'' or ``extremely safe.''
 
 With these rating scales, the subjects indicated their personal subjective feeling towards the individual lesson disruption.
-Rating scales usually consist of a number of clearly arranged categories that can be presented visually in a variety of ways [@albers2009methodik, p.
-67f].
+Rating scales usually consist of a number of clearly arranged categories that can be presented visually in a variety of ways (Albers, Klapper, Konradt, Walter, \& Wolf, 2009, p.
+67f).
 In the present questionnaire, the numerical representation with eleven answer options (0-10) was used.
@@
 
-#### Situational Jugdement Test
-
-To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, [@gold2015development]).
+\hypertarget{situational-jugdement-test}{%
+\paragraph{Situational Jugdement Test}\label{situational-jugdement-test}}
+
+To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)).
 In the questionnaire, participants were given hypothetical school scenarios with with 5-7 response strategy for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).
 
-In developing the test procedure, the authors divided the concept of classroom management into three main aspects: *Monitoring*, *managing momentum* (structuring) and *rules and routines* [@gold2015development, p.
-230f].
-
-*Monitoring* includes proactive strategies such as omnipresence.
+In developing the test procedure, the authors divided the concept of classroom management into three main aspects: \emph{Monitoring}, \emph{managing momentum} (structuring) and \emph{rules and routines} (Gold \& Holodynski, 2015, p.
+230f).
+
+\emph{Monitoring} includes proactive strategies such as omnipresence.
 This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them.
@@
 In this case, the teacher is able to control several teaching processes at the same time.
-Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf.
-ibid.; [@kounin2006techniken, p.
-89ff).
-
-By *managing momentum* (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention [@kounin2006techniken, p.
-101ff].
-They also include the group focus specifically identified by Kounin [@kounin2006techniken, p.
-117ff], i.e.
-mobilizing the whole class and demanding accountability [@gold2015development, p.
-231].
-
-The third facet of classroom management, establishing *rules, routines and rituals*, supports the other two facets and offers pupils orientation and structure in everyday school life (cf. ibid.).
+Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf.~ibid.; {[}Kounin (2006), p.~89ff).
+
+By \emph{managing momentum} (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention (Kounin, 2006, p.
+101ff).
+They also include the group focus specifically identified by Kounin (Kounin, 2006, p.
+117ff), i.e.~mobilizing the whole class and demanding accountability (Gold \& Holodynski, 2015, p.
+231).
+
+The third facet of classroom management, establishing \emph{rules, routines and rituals}, supports the other two facets and offers pupils orientation and structure in everyday school life (cf.~ibid.).
 
@@
 For the 14 scenarios, response strategies were derived from evidence-based and theoretical principles by 17 experts on classroom management.
-With the exception of scenario 5, which was subsequently excluded, the 17 experts agreed on an appropriate level of content validity for all other scenarios (cf.
-ibid.).
-For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf.
-ibid., p.
-238).
-Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf.
-ibid.).
-
-The construct validity of the SJT with the other 11 scenarios and the sensitivity to differences in strategic knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf.
-ibid., p.
-238ff).
-Despite limitations in reliability, the test was confirmed to have content and construct validity (cf.
-ibid., p.
-243).
+With the exception of scenario 5, which was subsequently excluded, the 17 experts agreed on an appropriate level of content validity for all other scenarios (cf.~ibid.).
+For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf.~ibid., p.~238).
+Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf.~ibid.).
+
+The construct validity of the SJT with the other 11 scenarios and the sensitivity to differences in strategic knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf.~ibid., p.~238ff).
+Despite limitations in reliability, the test was confirmed to have content and construct validity (cf.~ibid., p.~243).
 On the basis of these results, sufficient reliability and validity of the SJT test procedure was assumed.
 
-The scenarios could each be assigned to one facet of the mentioned classroom management: Scenarios 1-4 cover the facet *monitoring*, scenarios 6-9 the facet *managing momentum* and scenarios 11-14 the facet *rules and routines*.
-
-In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study *ProVisioNET*.
-The objectivity of analysis was given by processing the obtained questionnaire data in `r cite_r("r-references.bib")` and IBM SPSS 28.
-
-Since the test was a questionnaire designed to assess strategic knowledge of classroom management of *primary school teachers*, but the sample of the study included several types of schools, changes were made in 10 out of 12 scenarios by deleting the indicated class grade.
+The scenarios could each be assigned to one facet of the mentioned classroom management: Scenarios 1-4 cover the facet \emph{monitoring}, scenarios 6-9 the facet \emph{managing momentum} and scenarios 11-14 the facet \emph{rules and routines}.
+
+In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}.
+The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
+Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
+J.
+Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
+
+Since the test was a questionnaire designed to assess strategic knowledge of classroom management of \emph{primary school teachers}, but the sample of the study included several types of schools, changes were made in 10 out of 12 scenarios by deleting the indicated class grade.
 Only in two scenarios was the class grade information not deleted, as the action alternatives would otherwise not be appropriate without the information.
 
-## Procedure
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
@@
 On the day of a data collection, the first step was to set up the study room at the University of Leipzig.
-For this, all the appropriate technical equipment was charged and installed in the room (see set up plan [REFERENZ EINFÜGEN]).
+For this, all the appropriate technical equipment was charged and installed in the room (see set up plan {[}REFERENZ EINFÜGEN{]}).
 Next, all four cameras and the audio recorder were synced via Timecode System.
@@
 The phase was divided into two parts and served on the one hand to get the subjects used to the eye-tracking glasses and on the other hand to get used to their class.
-In the first phase of the warm-up, the game "name juggling" was played using two balls.
+In the first phase of the warm-up, the game ``name juggling'' was played using two balls.
 In the game, the subject and the three actors threw two balls at each other and, depending on the color of the ball, called either their own name or that of the target person.
@@
 
-```{r disruption_categories, include=TRUE, echo=FALSE, results='asis'}
-df_disrup_table <- data.frame(`Verbal Disruption` = c("chatting with neighbor", "whispering with neighbor", "heckling"),
-                              Agitation = c("drumming hands", "clicking pen", "snipping with fingers"),
-                              `Lack of eagerness to learn` = c("putting head on table", "looking at phone", "drawing on a sheet of paper")
-                              )
-
-papaja::apa_table(x = df_disrup_table,
-                  caption = "Categories of Disruptions (Lohmann, 2015)",
-                  escape = TRUE,
-                  placement = "h",
-                  font_size = "tiny")
-
-```
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:disruption_categories}Categories of Disruptions (Lohmann, 2015)}
+
+\tiny{
+
+\begin{tabular}{lll}
+\toprule
+Verbal.Disruption & \multicolumn{1}{c}{Agitation} & \multicolumn{1}{c}{Lack.of.eagerness.to.learn}\\
+\midrule
+chatting with neighbor & drumming hands & putting head on table\\
+whispering with neighbor & clicking pen & looking at phone\\
+heckling & snipping with fingers & drawing on a sheet of paper\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 After the letter search, the experimenter clapped twice with the hands to record an acoustic signal for the synchronization of all technical devices.
-Afterwards, all devices were switched off and the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature.
+Afterwards, all devices were switched off and the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire (Helmke et al., 2014) and self developed scales on the teacher's presence behavior derived from the research literature.
 The completion of the questionnaire took approximately 5 minutes.
 
-In the second part of the study, the experimenter conducted a Stimulated Recall Interview (SRI) with the subject(see in Figure \@ref(fig:sri).
+In the second part of the study, the experimenter conducted a Stimulated Recall Interview (SRI) with the subject(see in Figure \ref{fig:sri}.
 The interview was recorded by the ambient recorder and additionally with a software called OBS to record the speech and screen.
@@
 
-```{r sri, include = T, fig.cap = "Subject and experimenter during the Stimulated Recall Interview", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/sri.pdf", dpi = 108)
-
-```
-
-Finally, the subjects answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire.
+\begin{figure}
+
+{\centering \includegraphics{./pictures/sri}
+
+}
+
+\caption{Subject and experimenter during the Stimulated Recall Interview}\label{fig:sri}
+\end{figure}
+
+Finally, the subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire.
 Here they had to assess teaching scenarios and evaluate their behavior in response to them.
@@
 
-## Data analysis
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
 
@@
 
-All reported data analyses were conducted with the `r cite_r("r-references.bib")` and IBM SPSS 28.
-
-# Results
-
-# Discussion
+All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.0.8; Wickham et al., 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson et al., 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham et al., 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
+Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
+J.
+Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 
-# References
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
-<div id="refs" custom-style="Bibliography"></div>
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-albers2009methodik}{}}%
+Albers, S., Klapper, D., Konradt, U., Walter, A., \& Wolf, J. (2009). \emph{Methodik der empirischen forschung} (Vol. 3). Springer.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-DescTools}{}}%
+Andri et mult. al., S. (2022). \emph{{DescTools}: Tools for descriptive statistics}. Retrieved from \url{https://cran.r-project.org/package=DescTools}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
+Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-gridExtra}{}}%
+Auguie, B. (2017). \emph{gridExtra: Miscellaneous functions for "grid" graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridExtra}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
+Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
+Bates, D., Mächler, M., Bolker, B., \& Walker, S.
+(2015).
+Fitting linear mixed-effects models using {lme4}.
+\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
+\url{https://doi.org/10.18637/jss.v067.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
+Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rgeos}{}}%
+Bivand, R., \& Rundel, C. (2021). \emph{Rgeos: Interface to geometry engine - open source ('GEOS')}. Retrieved from \url{https://CRAN.R-project.org/package=rgeos}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-xtable}{}}%
+Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-polycor}{}}%
+Fox, J. (2022). \emph{Polycor: Polychoric and polyserial correlations}. Retrieved from \url{https://CRAN.R-project.org/package=polycor}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
+Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
+Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gegenfurtner2018mobiles}{}}%
+Gegenfurtner, A., Eichinger, A., Latzel, R., Dietrich, M. P., Barkowsky, M., Glufke, A., \ldots{} Stern, W. (2018). \emph{Mobiles eye-tracking in den angewandten wissenschaften}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gold2015development}{}}%
+Gold, B., \& Holodynski, M.
+(2015).
+Development and construct validation of a situational judgment test of strategic knowledge of classroom management in elementary schools.
+\emph{Educational Assessment}, \emph{20}(3), 226--248.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lubridate}{}}%
+Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with {lubridate}. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{https://www.jstatsoft.org/v40/i03/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}}%
+Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M.
+(2014).
+Unterrichtsdiagnostik mit EMU.
+\emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rlang}{}}%
+Henry, L., \& Wickham, H. (2022). \emph{Rlang: Functions for base types and core r and 'tidyverse' features}. Retrieved from \url{https://CRAN.R-project.org/package=rlang}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-msm}{}}%
+Jackson, C.
+H.
+(2011).
+Multi-state models for panel data: The {msm} package for {R}.
+\emph{Journal of Statistical Software}, \emph{38}(8), 1--29.
+Retrieved from \url{https://www.jstatsoft.org/v38/i08/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggmosaic}{}}%
+Jeppson, H., Hofmann, H., \& Cook, D. (2021). \emph{Ggmosaic: Mosaic plots in the 'ggplot2' framework}. Retrieved from \url{https://CRAN.R-project.org/package=ggmosaic}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-needs}{}}%
+Katz, J. (2016). \emph{Needs: Attaches and installs packages}. Retrieved from \url{https://CRAN.R-project.org/package=needs}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-moments}{}}%
+Komsta, L., \& Novomestky, F. (2015). \emph{Moments: Moments, cumulants, skewness, kurtosis and related tests}. Retrieved from \url{https://CRAN.R-project.org/package=moments}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kounin2006techniken}{}}%
+Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-sjPlot}{}}%
+Lüdecke, D. (2021). \emph{sjPlot: Data visualization for statistics in social science}. Retrieved from \url{https://CRAN.R-project.org/package=sjPlot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-sjlabelled}{}}%
+Lüdecke, D. (2022). \emph{Sjlabelled: Labelled data utility functions (version 1.2.0)}. \url{https://doi.org/10.5281/zenodo.1249215}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
+Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\vadjust pre{\hypertarget{ref-palmer2005identifying}{}}%
+Palmer, D.
+J., Stough, L.
+M., Burdenski, T.
+K., Jr, \& Gonzales, M.
+(2005).
+Identifying teacher expertise: An examination of researchers' decision making.
+\emph{Educational Psychologist}, \emph{40}(1), 13--25.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-sf}{}}%
+Pebesma, E. (2018). {Simple Features for R: Standardized Support for Spatial Vector Data}. \emph{{The R Journal}}, \emph{10}(1), 439--446. \url{https://doi.org/10.32614/RJ-2018-009}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-sp}{}}%
+Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. Retrieved from \url{https://CRAN.R-project.org/doc/Rnews/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ltm}{}}%
+Rizopoulos, D.
+(2006).
+Ltm: An r package for latent variable modelling and item response theory analyses.
+\emph{Journal of Statistical Software}, \emph{17}(5), 1--25.
+Retrieved from \url{https://doi.org/10.18637/jss.v017.i05}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggrepel}{}}%
+Slowikowski, K. (2021). \emph{Ggrepel: Automatically position non-overlapping text labels with 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggrepel}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rnaturalearth}{}}%
+South, A. (2017a). \emph{Rnaturalearth: World map data from natural earth}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearth}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rnaturalearthdata}{}}%
+South, A. (2017b). \emph{Rnaturalearthdata: World vector map data from natural earth used in 'rnaturalearth'}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearthdata}
+
+\leavevmode\vadjust pre{\hypertarget{ref-van2014first}{}}%
+Van den Bogert, N., Bruggen, J.
+van, Kostons, D., \& Jochems, W.
+(2014).
+First steps into understanding teachers' visual perception of classroom events.
+\emph{Teaching and Teacher Education}, \emph{37}, 208--216.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-MASS}{}}%
+Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
+Wickham, H. (2021). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
+Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2022). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
+Wickham, H., \& Girlich, M. (2022). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
+Wickham, H., Hester, J., \& Bryan, J. (2021). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-haven}{}}%
+Wickham, H., \& Miller, E. (2021). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. Retrieved from \url{https://CRAN.R-project.org/package=haven}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
+Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-knitr}{}}%
+Xie, Y. (2015). \emph{Dynamic documents with {R} and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.org/knitr/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ARTofR}{}}%
+Zhang, H. (2021). \emph{ARTofR: Who ever care about the {[}art of r{]} scripts?} Retrieved from \url{https://CRAN.R-project.org/package=ARTofR}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
+Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
+
+\end{CSLReferences}
+
 \endgroup
+
+\clearpage
+\renewcommand{\listtablename}{Table captions}
+
+\end{document}

### 2022-07-04 02_paper/02_study/paper_methods.Rmd
paper method section participants

@@
 
-XXX
-
-# creating a subset to report school type in text
-demo.school <- 
-  demo.data %>% 
-  dplyr::select(Group,
-         Percent_schooltype) %>% 
-  group_by(Group) %>% 
-  summarise_each(funs(sum))
-
 # changing character Semester into numeric
@@
 The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`).
-
-`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype")`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype")`% were secondary school teachers.
-
+`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers.
 `r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
@@
 Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies.
-
-`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype")`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype")`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype")`% to become special education teachers.
-
+`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype") %>% unique()`% to become special education teachers.
 `r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

### 2022-07-04 02_paper/02_study/paper_methods.tex
paper method section participants

@@
 The expert teachers (11 women; 57.89\%) had a mean age of 41.70 years (\emph{SD} = 10.40; range: 27-59) and an average teaching experience of 13.80 years (\emph{SD} = 12.30; range: 3-37).
-
-15.80, 15.80, and 15.80\% of the experts were primary school teachers and 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, and 84.21\% were secondary school teachers.
-
+15.79\% of the experts were primary school teachers and 84.21\% were secondary school teachers.
 47\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
@@
 Furthermore, they had an average teaching experience of 10.90 teaching units à 45min (\emph{SD} = 8.10; range: 0-36) through the internships during their studies.
-
-19.23, 19.23, 19.23, 19.23, and 19.23\% of the novices were studying to become primary school teachers, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, and 65.38\% to become secondary school teachers and 15.38, 15.38, 15.38, and 15.38\% to become special education teachers.
-
+19.23\% of the novices were studying to become primary school teachers, 65.38\% to become secondary school teachers and 15.38\% to become special education teachers.
 88.46\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
@@
 The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
+al., 2022), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
 Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
@@
 All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.8; Wickham et al., 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson et al., 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham et al., 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
+al., 2022), \emph{dplyr} (Version 1.0.8; Wickham et al., 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson et al., 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham et al., 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
 Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-formattable}{}}%
+Ren, K., \& Russell, K. (2021). \emph{Formattable: Create 'formattable' data structures}. Retrieved from \url{https://CRAN.R-project.org/package=formattable}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-ltm}{}}%

### 2022-07-04 02_paper/02_study/paper_methods.Rmd
update method section

@@
 output            : papaja::apa6_pdf
-# bookdown::word_document2
+# bookdown::word_document2 papaja::apa6_pdf
+
 ---
@@
 
-##
-
-## Variables
-
-All stimuli are freely available in the following online repository: https://github.com/... .
-
-### Eye-Tracking data
+## Design
+
+The underlying research was conducted as a laboratory study in a cross-sectional study design as part of the dissertation project *ProVisioNET*.
+This project investigates whether and how a teacher's classroom experiences have an impact on the perception of and response to classroom disruptions.
+
+The study was based on a quasi-experimental study design, as there was no random assignment of subjects to experimental conditions.
+Due to the use of MET technology, the study had a high external validity (Gegenfurtner et al., 2018).
+To ensure internal validity the occurring instructional events were exactly the same for all subjects, as the learners received precise behavioral instructions.
+These disruptions followed a script and coding guide in which the actions of the class were precisely described.
+The order of the disruptions as well as the performing actors were prompted and fully balanced with Latin Square.
+The scripted behavioral instructions during the classroom sequence distinguish this study with a high degree of standardization, especially when compared to events that take place in a real classroom.
+The study was based on an experimental manual, script, and coding guide which explicitly describes the execution, evaluation and interpretation of the data and thus and interpretation of the data, thus making them objectively ascertainable and measurable.
+
+## Materials
+
+### Eye-Tracking Apparatus
 
@@
 
+#### Apparatus
+
 The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \@ref(fig:setup).
 The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
-
-Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \@ref(fig:setup).
+Movements, facial expressions and gestures of the subjects were recorded with four Go Pro Hero 7 black cameras from different angles (see set up plan \@ref(fig:setup).
 The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
 
-### Questionnaire data
+#### Videography: Coding scheme for expertise indicators
+
+Part of the test procedure was that the subject taught a 15min micro-teaching-unit and was disrupted by the students in the class.
+The participant's behavior and reaction to the disruption were recorded using video cameras and then evaluated with two self developed coding schemes to assess the teacher's reaction on the one hand and the time on task during the unit.
+Both aspects are important indicators of teaching quality and are therefore used as another measure to make differences in expertise visible and measurable.
+
+Video analysis was chosen as the research method for evaluating the teacher's reaction to classroom disruptions because it offers numerous advantages.
+In contrast to transcripts or audio-only recordings, a video also shows nonverbal forms of communication, which is emphasized here, as well as the entire complex lesson excerpt in which many things happen simultaneously (cf.
+Krammer & Reusser, 2012, p.
+47f).
+Video data can also be viewed and analyzed over and over again from different perspectives (Petko et al., 2003, p.
+265).
+The possible problem of selectivity (cf.
+Petko et al., 2003, p.
+271), i.e., the fact that only a section of the events can be shown due to the position and perspective of the camera, was countered by recording the lessons from a total of four cameras.
+In this way, a case of doubt can be analyzed from several angles.
+Another challenge can be the so-called 'camera effect', i.e.
+that the filmed persons feel disturbed and act differently than usual and less naturally.
+However, Petko et al.
+(2003) conclude, despite filming with a camera person at the time, that there is little reason to believe that teachers can easily change their teaching style from one lesson to the next (p.
+270) and that it should not be assumed that the mere presence of a camera has significantly improved or worsened teaching' (p.
+270).
+In the 'ProVisioNET' survey, four very small cameras were placed in the room and their presence was barely noticeable.
+Accordingly, it is assumed that no major nuisance emanates from them.
+
+Schnettler and Knoblauch (2009, p.
+227) distinguish 'natural' and edited video data, depending on whether the situation was created specifically for the recording or whether the situation was influenced as little as possible or not at all.
+In the survey for this paper, although the subjects were to act exactly as they would have done without a camera, the classroom disruptions were scripted events that were performed by the actors.
+
+##### Coding Teachers' Reaction
+
+The evaluation of the teacher's reaction to the disruptions was conducted as a systematic observation using a category system with fixed categories and instructions.
+This corresponds to a highly inferential procedure, which is combined with an event sampling procedure (cf.
+Lotz et al., 2013, p.
+359).
+
+A theory-based coding scheme was developed as an observation tool for classroom observation.
+The coding of the reactions was done in seven levels.
+Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping (cf.
+Kounin 2006; Gold & Holodynski 2015) by not interrupting the flow of instruction.
+Code 2 or Code 3 was assigned for a brief verbal expression with or without a preceding nonverbal response.
+A brief, timely, and purposeful rebuke of the disruptive student is considered by Kounin (2009, p.
+99), among others, to be an important component of the strategy of presence and thus demonstrates good classroom management.
+If the teacher reacts non-verbally and at the same time with a longer verbal statement, code 4 was assigned, because the flow of the lesson was already noticeably delayed.
+There were two possibilities, if there was no reaction: If the teacher deliberately ignored the disruption, code 5 was assigned.
+If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized (cf.
+Gold & Holodynski, 2015).
+If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned.
+According to Gippert et al.
+(2019), there is a relational error in such cases, as the intensity of the student response should be relative to the disruptive behavior (p.
+2).
+
+In developing the coding system, questions initially aroused about how descriptions of responses should be made and in what order (especially codes 3-4).
+Initially, it was planned to assign code 3 for a nonverbal and simultaneously long verbal response and code 4 for a purely verbal response.
+However, during the initial trial coding of the videos, it became apparent that it was difficult to reliably distinguish nonverbal reactions to a classroom disruption from normal facial expressions and gestures of the teacher when talking.
+Moreover, during a prolonged verbal utterance, nonverbal signs could virtually always be detected.
+Furthermore, a category for short, purely verbal reactions was missing.
+
+After developing and reviewing the coding system, the observers coordinated and the consistency of their ratings was verified.
+For the evaluation, the individual videos of the sample were then coded and the data transferred to an Excel file.
+
+###### Test quality criteria
+
+In the construction of the video analysis method, attention was paid to compliance with the quality criteria of objectivity, reliability and validity.
+
+In order to ensure implementation objectivity, uniform implementation conditions were created.
+In the experimental manual of the ProVisioNET study, the survey procedure is described in detail, so that it is the same for each participant.
+On the one hand, the objectivity of the evaluation was given by the processing in the R.
+On the other hand, prior to the analysis of the videos, a precise coding scheme, which precisely describes the individual codes, explains them and contains examples, was created and discursively discussed in the team (see chapter 4.4.1).
+This coding scheme was tested and revised in a piloting process, which increased the internal validity of the method.
+Interrater reliability was determined for the two raters using sample ratings of the same videos.
+Percent agreement yielded 77.8% and a Cohen's Kappa of k = 0.6, which is a satisfactory value according to Landis & Koch (1977).
+Interpretive objectivity was ensured by specifying scientific hypotheses that then had to be neutrally tested.
+
+With the help of scripted behavioral instructions for students in the instructional unit, a high degree of standardization was achieved that is not present in the normal school setting.
+The lessons were recorded with several video cameras from different angles and an audio recorder.
+This means a big advantage compared to the subjective evaluation of observers in real time.
+In addition, video recordings can be viewed multiple times, by different people or from different perspectives.
+Thus, a high measurement accuracy (reliability) is given (cf.
+Mayring, P., Gläser-Zikuda, M., & Ziegelbauer, 2005).
+All measures taken contribute to increase the validity of the method.
+However, it cannot be answered whether the coding scheme is completely valid, because a validation with the help of another measuring instrument was not possible.
+Therefore, it could not be controlled whether the collected construct is related to other similar constructs.
+
+##### Coding Time on Task
+
+### Questionnaie data
+
+#### Presence Questionnaire
 
@@
 
-```{r presence_questionnaire_novices, include=TRUE, echo=FALSE, results='asis'}
+```{r presence_questionnaire, include=TRUE, echo=FALSE, results='asis'}
 # load data files
@@
 # creating a loop
-# i <- "LM"
+i <- "LM"
 
@@
 )
-```
-
-```{r presence_questionnaire_experts, include=TRUE, echo=FALSE, results='asis'}
 
@@
 
-```{r item_analysis_classroom_management, include=TRUE, results='asis'}
-# quest.data %>%
-#   dplyr::select(contains("LM")) %>%
-#   as.data.frame() %>%
-#   tab_itemscale(CSS = list(
-#     css.firsttablerow.col7 = "'cronbachs alpha';"
-#   ))
-```
-
-```{r item_analysis_balance, include=TRUE, results='asis'}
-# quest.data %>%
-#   dplyr::select(contains("LB")) %>%
-#   as.data.frame() %>%
-#   tab_itemscale()
-```
-
-```{r item_analysis_presence, include=TRUE,results='asis'}
-# quest.data %>%
-#   dplyr::select(contains("LP")) %>%
-#   as.data.frame() %>%
-#   tab_itemscale()
-```
-
-```{r item_analysis_behavior, include=TRUE,results='asis'}
-# quest.data %>%
-#   dplyr::select(contains("LV")) %>%
-#   as.data.frame() %>%
-#   tab_itemscale()
+```{r item_analysis_classroom_management_novice, echo=FALSE, include=FALSE, results='asis'}
+quest.data %>%
+  dplyr::filter(Group == "Novice") %>% 
+  dplyr::select(contains("LM")) %>%
+  as.data.frame() %>%
+  tab_itemscale(CSS = list(
+    css.firsttablerow.col7 = "'cronbachs alpha';"
+  ))
+```
+
+```{r item_analysis_classroom_management_expert, echo=FALSE, include=FALSE, results='asis'}
+quest.data %>%
+  dplyr::filter(Group == "Expert") %>% 
+  dplyr::select(contains("LM")) %>%
+  as.data.frame() %>%
+  tab_itemscale(CSS = list(
+    css.firsttablerow.col7 = "'cronbachs alpha';"
+  ))
+```
+
+```{r item_analysis_balance_novice, echo=FALSE, include=FALSE, results='asis'}
+quest.data %>%
+  dplyr::filter(Group == "Novice") %>% 
+  dplyr::select(contains("LB")) %>%
+  as.data.frame() %>%
+  tab_itemscale()
+```
+
+```{r item_analysis_balance_expert, echo=FALSE, include=FALSE, results='asis'}
+quest.data %>%
+  dplyr::filter(Group == "Expert") %>%
+  dplyr::select(contains("LB")) %>%
+  as.data.frame() %>%
+  tab_itemscale()
+```
+
+```{r item_analysis_presence_novice, echo=FALSE, include=FALSE,results='asis'}
+quest.data %>%
+  dplyr::filter(Group == "Novice") %>%
+  dplyr::select(contains("LP")) %>%
+  as.data.frame() %>%
+  tab_itemscale()
+```
+
+```{r item_analysis_presence_expert, echo=FALSE, include=FALSE,results='asis'}
+quest.data %>%
+  dplyr::filter(Group == "Expert") %>%
+  dplyr::select(contains("LP")) %>%
+  as.data.frame() %>%
+  tab_itemscale()
+```
+
+```{r item_analysis_behavior_novice, echo=FALSE, include=FALSE,results='asis'}
+quest.data %>%
+  dplyr::filter(Group == "Novice") %>%
+  dplyr::select(contains("LV")) %>%
+  as.data.frame() %>%
+  tab_itemscale()
+```
+
+```{r item_analysis_behavior_expert, echo=FALSE, include=FALSE,results='asis'}
+quest.data %>%
+  dplyr::filter(Group == "Expert") %>%
+  dplyr::select(contains("LV")) %>%
+  as.data.frame() %>%
+  tab_itemscale()
 ```
@@
 
-#### Situational Jugdement Test
+```{r rating_scales, include=TRUE, echo=FALSE, results='asis'}
+
+# read in data and combine multiple excel sheets into a single table 
+sri <- 
+  excel_sheets("data/Coding_SRI.xlsx") %>% 
+  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% 
+  dplyr::select(Group, Event, `Disruption Factor`, `Confident Factor`) %>% # select relevant columns
+  dplyr::filter(!`Disruption Factor` == -100,
+           !`Confident Factor` == -100,
+           !`Disruption Factor`== -99,
+           !`Confident Factor` == -99)
+
+############## Disruption Factor #########################
+
+sri.disrup.table <- 
+  sri %>%
+  group_by(Group, Event) %>%
+  mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
+  summarise("M" = round(mean(`Disruption Factor`), 
+                        digits = 2),
+            "SD" = round(sd(`Disruption Factor`),
+                         digits = 2),
+            "Min" = min(`Disruption Factor`),
+            "Max" = max(`Disruption Factor`))
+
+# format and insert table in manuscript
+papaja::apa_table(
+sri.disrup.table,
+  caption = "Table Rating Scales Disruption Factor",
+  # note = "Write Note here",
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+)
+
+############## Confident Factor #########################
+
+sri.confi.table <- 
+  sri %>%
+  group_by(Group, Event) %>%
+  mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
+  summarise("M" = round(mean(`Confident Factor`), 
+                        digits = 2),
+            "SD" = round(sd(`Confident Factor`),
+                         digits = 2),
+            "Min" = min(`Confident Factor`),
+            "Max" = max(`Confident Factor`))
+
+# format and insert table in manuscript
+papaja::apa_table(
+sri.confi.table,
+  caption = "Table Rating Scales Confident Factor",
+  # note = "Write Note here",
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+)
+
+```
+
+#### Situational Jugdement Test of Strategic Knowledge of Classroom Management
 
 To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, [@gold2015development]).
-In the questionnaire, participants were given hypothetical school scenarios with with 5-7 response strategy for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).
+In the questionnaire, participants were given hypothetical school scenarios with five to six response strategies for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).
+Depending on the grade given to each strategy, scores were converted in an SPSS syntax resulting in scores ranging from 0 to 1 for each participant.
 
@@
 
+```{r sjt, include=TRUE, echo=FALSE, results='asis'}
+
+# read in data
+df_sjt <- read_csv2(file = "data/SJT.csv") %>% 
+  mutate(Group = ifelse(UI06_05 < 200, "Novice","Expert")) %>%
+  dplyr::select(Group, 
+                PK_S1_AL:PK_S14_R)
+
+# remove NAs
+df_sjt <- na.omit(df_sjt)
+
+# create two data frames
+sjt.novice <- df_sjt %>% filter(Group == "Novice")
+sjt.expert <- df_sjt %>% filter(Group == "Expert")
+
+############## NOVICE TABLE #########################
+
+# creating a matrix
+sjt.table.novice <- 
+  matrix(data = NA, nrow = 3, ncol = 8)
+  rownames(sjt.table.novice) <- c("AL", "ST", "R")
+  colnames(sjt.table.novice) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
+
+# creating a loop
+i <- "AL"
+
+for (i in c("AL", "ST", "R")) {
+
+loop.data <- sjt.novice %>%
+  dplyr::select(ends_with(match = i))
+
+sjt.table.novice[i, "N Items"] <- length(loop.data)
+
+# calculating mean
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  mean() %>%
+  round(., digits = 2) ->
+sjt.table.novice[i, "M"]
+
+# calculating SD
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  sd() %>%
+  round(., digits = 2) ->
+sjt.table.novice[i, "SD"]
+
+# calculating Min
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  min() %>%
+  round(., digits = 2) ->
+sjt.table.novice[i, "Min"]
+
+# calculating Max
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  max() %>%
+  round(., digits = 2) ->
+sjt.table.novice[i, "Max"]
+
+# calculating Skewness
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  skewness() %>%
+  round(., digits = 2) ->
+sjt.table.novice[i, "Skewness"]
+
+# calculating Kurtosis
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  kurtosis() %>%
+  round(., digits = 2) ->
+sjt.table.novice[i, "Kurtosis"]
+
+# calculating alpha
+alpha <- loop.data %>%
+  cronbach.alpha()
+
+sjt.table.novice[i, "alpha"] <- round(alpha$alpha,2)
+
+}
+
+# rename columns
+rownames(sjt.table.novice) <- c("Monitoring", "Managing Momentum", "Rules and routines")
+
+# format and insert table in manuscript
+papaja::apa_table(
+sjt.table.novice,
+  caption = "Scale analysis SJT novices",
+  # note = "Write Note here",
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+)
+
+############## EXPERT TABLE #########################
+
+# creating a matrix
+sjt.table.expert <- 
+  matrix(data = NA, nrow = 3, ncol = 8)
+  rownames(sjt.table.expert) <- c("AL", "ST", "R")
+  colnames(sjt.table.expert) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
+
+# creating a loop
+i <- "AL"
+
+for (i in c("AL", "ST", "R")) {
+
+loop.data <- sjt.expert %>%
+  dplyr::select(ends_with(match = i))
+
+sjt.table.expert[i, "N Items"] <- length(loop.data)
+
+# calculating mean
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  mean() %>%
+  round(., digits = 2) ->
+sjt.table.expert[i, "M"]
+
+# calculating SD
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  sd() %>%
+  round(., digits = 2) ->
+sjt.table.expert[i, "SD"]
+
+# calculating Min
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  min() %>%
+  round(., digits = 2) ->
+sjt.table.expert[i, "Min"]
+
+# calculating Max
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  max() %>%
+  round(., digits = 2) ->
+sjt.table.expert[i, "Max"]
+
+# calculating Skewness
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  skewness() %>%
+  round(., digits = 2) ->
+sjt.table.expert[i, "Skewness"]
+
+# calculating Kurtosis
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  kurtosis() %>%
+  round(., digits = 2) ->
+sjt.table.expert[i, "Kurtosis"]
+
+# calculating alpha
+alpha <- loop.data %>%
+  cronbach.alpha()
+
+sjt.table.expert[i, "alpha"] <- round(alpha$alpha,2)
+
+}
+
+# rename columns
+rownames(sjt.table.expert) <- c("Monitoring", "Managing Momentum", "Rules and routines")
+
+# format and insert table in manuscript
+papaja::apa_table(
+sjt.table.expert,
+  caption = "Scale analysis SJT novices",
+  # note = "Write Note here",
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+)
+
+```
+
 ## Procedure
@@
 After the disruption occurred, the subject was asked to describe what had just happened.
-If the disruption was noticed, the subject was asked how disruptive the event was at that moment on a scale from 0 to 10 (for a detailed description of the scale question, see Rating Scales).
+If the disruption was noticed, the subject was asked how disruptive the event was at that moment on a scale from 0 to 10.
 In addition, the subject was asked to reason the given number.
 In a next step, the experimenter re-played the subject's reaction to the disruption and asked to describe and reason the reaction.
-The
+The experimenter then asked the subject to rate on a scale from 0 to 10 how confident he/she felt in dealing with the disruption and again to reason the number (for a detailed description of the scale question, see Rating Scales).
 
@@
 
-Finally, the subjects answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire.
+Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management (SJT, [@gold2015development]) in the form of a questionnaire.
 Here they had to assess teaching scenarios and evaluate their behavior in response to them.
 The SJT was used to assess strategic knowledge about classroom management.
-The
-completion of the entire survey took 15 min on average.
+The completion of the entire survey took 15 min on average.
 

### 2022-07-04 02_paper/02_study/paper_methods.tex
update method section

@@
 
-\hypertarget{section}{%
-\subsection{}\label{section}}
-
-\hypertarget{variables}{%
-\subsection{Variables}\label{variables}}
-
-All stimuli are freely available in the following online repository: \url{https://github.com/}\ldots{} .
-
-\hypertarget{eye-tracking-data}{%
-\subsubsection{Eye-Tracking data}\label{eye-tracking-data}}
+\hypertarget{design}{%
+\subsection{Design}\label{design}}
+
+The underlying research was conducted as a laboratory study in a cross-sectional study design as part of the dissertation project \emph{ProVisioNET}.
+This project investigates whether and how a teacher's classroom experiences have an impact on the perception of and response to classroom disruptions.
+
+The study was based on a quasi-experimental study design, as there was no random assignment of subjects to experimental conditions.
+Due to the use of MET technology, the study had a high external validity (Gegenfurtner et al., 2018).
+To ensure internal validity the occurring instructional events were exactly the same for all subjects, as the learners received precise behavioral instructions.
+These disruptions followed a script and coding guide in which the actions of the class were precisely described.
+The order of the disruptions as well as the performing actors were prompted and fully balanced with Latin Square.
+The scripted behavioral instructions during the classroom sequence distinguish this study with a high degree of standardization, especially when compared to events that take place in a real classroom.
+The study was based on an experimental manual, script, and coding guide which explicitly describes the execution, evaluation and interpretation of the data and thus and interpretation of the data, thus making them objectively ascertainable and measurable.
+
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+\hypertarget{eye-tracking-apparatus}{%
+\subsubsection{Eye-Tracking Apparatus}\label{eye-tracking-apparatus}}
 
@@
 
+\hypertarget{apparatus}{%
+\paragraph{Apparatus}\label{apparatus}}
+
 The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \ref{fig:setup}.
 The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
-
-Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \ref{fig:setup}.
+Movements, facial expressions and gestures of the subjects were recorded with four Go Pro Hero 7 black cameras from different angles (see set up plan \ref{fig:setup}.
 The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
 
-\hypertarget{questionnaire-data}{%
-\subsubsection{Questionnaire data}\label{questionnaire-data}}
+\hypertarget{videography-coding-scheme-for-expertise-indicators}{%
+\paragraph{Videography: Coding scheme for expertise indicators}\label{videography-coding-scheme-for-expertise-indicators}}
+
+Part of the test procedure was that the subject taught a 15min micro-teaching-unit and was disrupted by the students in the class.
+The participant's behavior and reaction to the disruption were recorded using video cameras and then evaluated with two self developed coding schemes to assess the teacher's reaction on the one hand and the time on task during the unit.
+Both aspects are important indicators of teaching quality and are therefore used as another measure to make differences in expertise visible and measurable.
+
+Video analysis was chosen as the research method for evaluating the teacher's reaction to classroom disruptions because it offers numerous advantages.
+In contrast to transcripts or audio-only recordings, a video also shows nonverbal forms of communication, which is emphasized here, as well as the entire complex lesson excerpt in which many things happen simultaneously (cf.~Krammer \& Reusser, 2012, p.~47f).
+Video data can also be viewed and analyzed over and over again from different perspectives (Petko et al., 2003, p.~265).
+The possible problem of selectivity (cf.~Petko et al., 2003, p.~271), i.e., the fact that only a section of the events can be shown due to the position and perspective of the camera, was countered by recording the lessons from a total of four cameras.
+In this way, a case of doubt can be analyzed from several angles.
+Another challenge can be the so-called `camera effect', i.e.~that the filmed persons feel disturbed and act differently than usual and less naturally.
+However, Petko et al.~(2003) conclude, despite filming with a camera person at the time, that there is little reason to believe that teachers can easily change their teaching style from one lesson to the next (p.~270) and that it should not be assumed that the mere presence of a camera has significantly improved or worsened teaching' (p.~270).
+In the `ProVisioNET' survey, four very small cameras were placed in the room and their presence was barely noticeable.
+Accordingly, it is assumed that no major nuisance emanates from them.
+
+Schnettler and Knoblauch (2009, p.~227) distinguish `natural' and edited video data, depending on whether the situation was created specifically for the recording or whether the situation was influenced as little as possible or not at all.
+In the survey for this paper, although the subjects were to act exactly as they would have done without a camera, the classroom disruptions were scripted events that were performed by the actors.
+
+\hypertarget{coding-teachers-reaction}{%
+\subparagraph{Coding Teachers' Reaction}\label{coding-teachers-reaction}}
+
+The evaluation of the teacher's reaction to the disruptions was conducted as a systematic observation using a category system with fixed categories and instructions.
+This corresponds to a highly inferential procedure, which is combined with an event sampling procedure (cf.~Lotz et al., 2013, p.~359).
+
+A theory-based coding scheme was developed as an observation tool for classroom observation.
+The coding of the reactions was done in seven levels.
+Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping (cf.~Kounin 2006; Gold \& Holodynski 2015) by not interrupting the flow of instruction.
+Code 2 or Code 3 was assigned for a brief verbal expression with or without a preceding nonverbal response.
+A brief, timely, and purposeful rebuke of the disruptive student is considered by Kounin (2009, p.~99), among others, to be an important component of the strategy of presence and thus demonstrates good classroom management.
+If the teacher reacts non-verbally and at the same time with a longer verbal statement, code 4 was assigned, because the flow of the lesson was already noticeably delayed.
+There were two possibilities, if there was no reaction: If the teacher deliberately ignored the disruption, code 5 was assigned.
+If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized (cf.~Gold \& Holodynski, 2015).
+If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned.
+According to Gippert et al.~(2019), there is a relational error in such cases, as the intensity of the student response should be relative to the disruptive behavior (p.~2).
+
+In developing the coding system, questions initially aroused about how descriptions of responses should be made and in what order (especially codes 3-4).
+Initially, it was planned to assign code 3 for a nonverbal and simultaneously long verbal response and code 4 for a purely verbal response.
+However, during the initial trial coding of the videos, it became apparent that it was difficult to reliably distinguish nonverbal reactions to a classroom disruption from normal facial expressions and gestures of the teacher when talking.
+Moreover, during a prolonged verbal utterance, nonverbal signs could virtually always be detected.
+Furthermore, a category for short, purely verbal reactions was missing.
+
+After developing and reviewing the coding system, the observers coordinated and the consistency of their ratings was verified.
+For the evaluation, the individual videos of the sample were then coded and the data transferred to an Excel file.
+
+Test quality criteria
+
+In the construction of the video analysis method, attention was paid to compliance with the quality criteria of objectivity, reliability and validity.
+
+In order to ensure implementation objectivity, uniform implementation conditions were created.
+In the experimental manual of the ProVisioNET study, the survey procedure is described in detail, so that it is the same for each participant.
+On the one hand, the objectivity of the evaluation was given by the processing in the R.
+On the other hand, prior to the analysis of the videos, a precise coding scheme, which precisely describes the individual codes, explains them and contains examples, was created and discursively discussed in the team (see chapter 4.4.1).
+This coding scheme was tested and revised in a piloting process, which increased the internal validity of the method.
+Interrater reliability was determined for the two raters using sample ratings of the same videos.
+Percent agreement yielded 77.8\% and a Cohen's Kappa of k = 0.6, which is a satisfactory value according to Landis \& Koch (1977).
+Interpretive objectivity was ensured by specifying scientific hypotheses that then had to be neutrally tested.
+
+With the help of scripted behavioral instructions for students in the instructional unit, a high degree of standardization was achieved that is not present in the normal school setting.
+The lessons were recorded with several video cameras from different angles and an audio recorder.
+This means a big advantage compared to the subjective evaluation of observers in real time.
+In addition, video recordings can be viewed multiple times, by different people or from different perspectives.
+Thus, a high measurement accuracy (reliability) is given (cf.~Mayring, P., Gläser-Zikuda, M., \& Ziegelbauer, 2005).
+All measures taken contribute to increase the validity of the method.
+However, it cannot be answered whether the coding scheme is completely valid, because a validation with the help of another measuring instrument was not possible.
+Therefore, it could not be controlled whether the collected construct is related to other similar constructs.
+
+\hypertarget{coding-time-on-task}{%
+\subparagraph{Coding Time on Task}\label{coding-time-on-task}}
+
+\hypertarget{questionnaie-data}{%
+\subsubsection{Questionnaie data}\label{questionnaie-data}}
+
+\hypertarget{presence-questionnaire}{%
+\paragraph{Presence Questionnaire}\label{presence-questionnaire}}
 
@@
 
-\caption{\label{tab:presence_questionnaire_novices}Scale analysis for novices' self-assessment}
+\caption{\label{tab:presence_questionnaire}Scale analysis for novices' self-assessment}
 
@@
 
-\caption{\label{tab:presence_questionnaire_experts}Scale analysis for experts' self-assessment}
+\caption{\label{tab:presence_questionnaire}Scale analysis for experts' self-assessment}
 
@@
 
-\hypertarget{situational-jugdement-test}{%
-\paragraph{Situational Jugdement Test}\label{situational-jugdement-test}}
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:rating_scales}Table Rating Scales Disruption Factor}
+
+\tiny{
+
+\begin{tabular}{llllll}
+\toprule
+Group & \multicolumn{1}{c}{Event} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
+\midrule
+Expert & chatting & 6.44 & 3.33 & 1.00 & 10.00\\
+Expert & clicking pen & 5.57 & 2.87 & 0.00 & 10.00\\
+Expert & drawing & 1.85 & 1.46 & 0.00 & 6.00\\
+Expert & drumming & 4.60 & 2.44 & 1.00 & 8.00\\
+Expert & head on table & 3.73 & 2.25 & 0.00 & 8.00\\
+Expert & heckling & 7.19 & 2.37 & 2.00 & 10.00\\
+Expert & looking at phone & 4.71 & 3.10 & 1.00 & 10.00\\
+Expert & snipping & 4.00 & 3.61 & 0.00 & 10.00\\
+Expert & whispering & 4.56 & 2.50 & 0.00 & 9.00\\
+Novice & chatting & 8.62 & 1.35 & 5.00 & 10.00\\
+Novice & clicking pen & 7.00 & 2.11 & 3.00 & 10.00\\
+Novice & drawing & 2.24 & 1.48 & 0.00 & 4.00\\
+Novice & drumming & 6.57 & 2.27 & 0.00 & 10.00\\
+Novice & head on table & 4.09 & 2.09 & 1.00 & 8.00\\
+Novice & heckling & 6.96 & 2.57 & 2.00 & 10.00\\
+Novice & looking at phone & 3.90 & 1.94 & 1.00 & 8.00\\
+Novice & snipping & 4.67 & 3.33 & 0.00 & 9.00\\
+Novice & whispering & 6.08 & 2.36 & 1.00 & 10.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:rating_scales}Table Rating Scales Confident Factor}
+
+\tiny{
+
+\begin{tabular}{llllll}
+\toprule
+Group & \multicolumn{1}{c}{Event} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
+\midrule
+Expert & chatting & 8.44 & 2.03 & 2.00 & 10.00\\
+Expert & clicking pen & 8.93 & 1.00 & 7.00 & 10.00\\
+Expert & drawing & 9.23 & 1.36 & 5.00 & 10.00\\
+Expert & drumming & 9.07 & 0.96 & 7.00 & 10.00\\
+Expert & head on table & 9.00 & 1.41 & 5.00 & 10.00\\
+Expert & heckling & 6.75 & 2.89 & 2.00 & 10.00\\
+Expert & looking at phone & 9.21 & 1.05 & 7.00 & 10.00\\
+Expert & snipping & 9.06 & 1.48 & 4.00 & 10.00\\
+Expert & whispering & 8.06 & 2.11 & 3.00 & 10.00\\
+Novice & chatting & 6.42 & 2.39 & 0.00 & 10.00\\
+Novice & clicking pen & 7.54 & 1.89 & 3.00 & 10.00\\
+Novice & drawing & 8.81 & 1.25 & 5.00 & 10.00\\
+Novice & drumming & 7.57 & 2.11 & 3.00 & 10.00\\
+Novice & head on table & 7.30 & 1.96 & 3.00 & 10.00\\
+Novice & heckling & 5.35 & 2.53 & 1.00 & 10.00\\
+Novice & looking at phone & 7.65 & 1.73 & 3.00 & 10.00\\
+Novice & snipping & 8.04 & 1.73 & 3.00 & 10.00\\
+Novice & whispering & 7.25 & 2.03 & 2.00 & 10.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\hypertarget{situational-jugdement-test-of-strategic-knowledge-of-classroom-management}{%
+\paragraph{Situational Jugdement Test of Strategic Knowledge of Classroom Management}\label{situational-jugdement-test-of-strategic-knowledge-of-classroom-management}}
 
 To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)).
-In the questionnaire, participants were given hypothetical school scenarios with with 5-7 response strategy for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).
+In the questionnaire, participants were given hypothetical school scenarios with five to six response strategies for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).
+Depending on the grade given to each strategy, scores were converted in an SPSS syntax resulting in scores ranging from 0 to 1 for each participant.
 
@@
 Only in two scenarios was the class grade information not deleted, as the action alternatives would otherwise not be appropriate without the information.
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:sjt}Scale analysis SJT novices}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
+\midrule
+Monitoring & 4.00 & 0.71 & 0.11 & 0.44 & 0.96 & -0.11 & 3.76 & 0.37\\
+Managing Momentum & 5.00 & 0.74 & 0.11 & 0.51 & 0.94 & -0.25 & 2.85 & 0.19\\
+Rules and routines & 3.00 & 0.75 & 0.11 & 0.46 & 0.90 & -0.74 & 3.25 & -0.28\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:sjt}Scale analysis SJT novices}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
+\midrule
+Monitoring & 4.00 & 0.71 & 0.15 & 0.52 & 0.92 & 0.17 & 1.76 & 0.38\\
+Managing Momentum & 5.00 & 0.70 & 0.13 & 0.52 & 0.89 & 0.31 & 1.77 & 0.34\\
+Rules and routines & 3.00 & 0.70 & 0.13 & 0.47 & 0.89 & -0.27 & 2.20 & 0.46\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 
-Finally, the subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire.
+Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire.
 Here they had to assess teaching scenarios and evaluate their behavior in response to them.
 The SJT was used to assess strategic knowledge about classroom management.
-The
-completion of the entire survey took 15 min on average.
+The completion of the entire survey took 15 min on average.
 

### 2022-07-06 01_studies/01_Laborstudie ProVisioNET/Amplitude_Extraction/automated_analysis.Rmd
Add Amplitude Extraction Project

---
title: "R Notebook"
output: html_notebook
---

The smoothed amplitude envelope is an acoustic measure that is correlated with for example jaw motion of speech (1. Chandresekaran et al., 2009) and contains gross information about the amplitude of the most dominant frequency of the sound. The smoothed amplitude envelope contains key information about the quasi-rhythmic structure of speech (2. Poeppel & Assaneo, 2020), as well as complex prosodic modulations that occur at multiple time scales (e.g., 2. Tilsen & Arviniti, 2013).

```{r seting_up}
#When running this in Rmarkdown yourself: 
#first make sure to set "Session" -> "Set Working Directory" -> "To Source File Location"

#get current drive
curfolder <- getwd()
#This is the folder where your wav's are saved
data_to_process <- paste0(curfolder, "/Multimedia/Audio/") 
#list of the wav's                                                                    
list_wavs <- list.files(data_to_process, pattern = ".wav")            
#set an output folder to save the amplitude envelope time series to
outputfolder <- paste0(curfolder, "/output/")
```

# Function

So there is more than one way to compute a smoothed amplitude envelope. We however follow the procedure originally coded in PRAAT by He & Dellwo (2017; ref 4.) which we reimplemented in R. The main function below follow their procedure. Firstly, we read in a sound file, and then apply a Hilbert transform to the waveform signal, which yields what is called a complex analytic signal (containing real and imaginary numbers). From this we can extract the amplitude information by applying what is called the complex modulus, and we are left with a 1D signal that will track the \emph{rough or more precise} contours of that audio waveform \emph{depending the amount of smoothing}. Following He & Dellwo, since we are interested in an approximation of the syllable cycles that tend to occur no shorter than 200ms, we will smooth the signal at a max 5Hz (1000ms/5Hz = 200ms) using a Hanning Window filter. We then downsample the smoothed amplitude envelope to something more workable, namely, to 100Hz time series, which we can later align for example with other signals (e.g., motion tracking data). For a more information about the key procedure, the Hilbert transformation, see (5. Cohen, 2019)

Note, that the function below, allows you to set the resampling rate differently (e.g., 200Hz instead of 100Hz), as well as the hanning window settings (e.g., 8Hz instead of 5Hz).

```{r main_function, warning=FALSE, message= FALSE}
library(seewave)
library(signal)
library(rPraat)
library(dplR)
#####################MAIN FUNCTION TO EXTRACT SMOOTHED ENVELOPE###############################
amplitude_envelope.extract <- function(locationsound, smoothingHz, resampledHz)
{
  #read the sound file into R
  snd <- rPraat::snd.read(locationsound)
  #apply the hilbert on the signal
  hilb <- seewave::hilbert(snd$sig, f = snd$fs, fftw =FALSE)
  #apply complex modulus
  env <- as.vector(abs(hilb))
  #smooth with a hanning window
  env_smoothed <- dplR::hanning(x= env, n = snd$fs/smoothingHz)
  #set undeterminable at beginning and end NA's to 0
  env_smoothed[is.na(env_smoothed)] <- 0
  #resample settings at desired sampling rate
  f <- approxfun(1:(snd$duration*snd$fs),env_smoothed)
  #resample apply
  downsampled <- f(seq(from=0,to=snd$duration*snd$fs,by=snd$fs/resampledHz))
  #let function return the downsampled smoothed amplitude envelope
  return(downsampled[!is.na(downsampled)])
}
```

# Apply

```{r applyfunction, warning=FALSE, message= FALSE}
########################APPLY MAIN FUNCTION ON THE SOUNDFILES#################################

#loop through soundfile locations
for(wav in list_wavs)
  {
   #do not run this when these files are already generated
  if(!file.exists(paste0(outputfolder, substr(wav, 1, nchar(wav)-4), "_ENV", ".csv")))
  {
  #location of the current sound file in the loop  
  locsound <- paste0(data_to_process, wav)
  #get the amplitude envelope at location, 5Hz Hanning, 100Hz sampling
  env <- amplitude_envelope.extract(locsound, 5, 100)
  #make a time vector based on sampling rate (1000/Hz)
  time_ms <- seq(1000/100, length(env)*(1000/100), by = 1000/100)
  #bind into data frame
  ENV <- cbind.data.frame(time_ms, env)
  #save it to a folder
  write.csv(ENV, file = paste0(paste0(outputfolder, substr(wav, 1, nchar(wav)-4), "_ENV", ".csv")),row.names=FALSE) 
  }
}
```

# Plots

```{r}
library(needs)
needs(tidyverse,
      pracma,
      gridExtra)

list_csv <- list.files(path = "output", pattern = ".csv")

for (i in list_csv) {

name_list <- str_extract_all(i, pattern = "[:digit:]")[[1]]
name_list <- str_flatten(name_list[1:3])

read_csv(file = paste0("output/", i)) ->
  df_sound

peaks <- pracma::findpeaks(df_sound$env, minpeakdistance = 10, 
                           minpeakheight = mean(df_sound$env)-(1 * sd(df_sound$env)))

df_sound %>% 
  mutate(ID = name_list,
         group = if_else(ID < 200,
                         "Novice",
                         "Expert"
                         )
         ) ->
  df_sound

df_sound$peaks <- NA

df_sound$peaks[peaks[,2]] <- peaks[,1]

assign(x = paste0("provis_", name_list),
       value = df_sound
       )

}

mget(ls(pattern = "provis")) %>%
  bind_rows() ->
  df_sound_all

time <- 
seq(from = 0,
    to = max(df_sound_all$time_ms) - 5000,
    by = 1)

set.seed(567)
start_time <- sample(time, size = 1)

df_sound_all %>% 
  mutate(env_exp = log(env),
         peaks_exp = log(peaks)
         ) %>% 
  ggplot(aes(x = time_ms,
             y = env_exp
             )
         ) +
  geom_path(mapping = aes(color = group),
            alpha = 0.8) + 
  geom_point(aes(y = peaks_exp,
                 color = group),
             size = 2) +
  labs(x = "Time (in ms)",
       y = "log(Amplitude)",
       color = "") +
  scale_color_brewer(palette = "Dark2") +
  xlim(start_time,start_time + 5000) +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")
```

## Syllable Rate

```{r}
df_sound_all %>% 
  group_by(ID) %>% 
  summarise(syllable_p_sec = sum(!is.na(peaks))/(max(time_ms)/diff(range(time_ms))),
            syllable_sd = sd(diff(time_ms[!is.na(peaks)]))
            ) %>% 
  ungroup() %>% 
  mutate(group = if_else(ID < 200,
                         "Novice",
                         "Expert"
                         )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = syllable_p_sec)) +
  geom_bar(mapping = aes(fill = group),
           stat = "identity",
           width = 0.3) +
  labs(y = "Syllables per Second",
       fill = "Group") +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  theme(text = element_text(family = "serif",
                            size = 12))
```

#

```{r someplottingandapplication, warning=FALSE, message= FALSE}
library(pracma) #package that has a peakfinding function
library(ggplot2) #plotting
library(gridExtra) #some plotting extras

#lets read in an amplitude envelope time series
env_ts <- read.csv(paste0(outputfolder, "audio_cartoon_ENV.csv"))
env_ts <- audio_cartoon_ENV
#identify peaks: #this will give you the height of the peak, 
#the index, the index of the left through [,3] and the right through [,4]
peaks <- pracma::findpeaks(env_ts$env, minpeakdistance = 10, 
                           minpeakheight = mean(env_ts$env)-(1 * sd(env_ts$env))) 
#initialize a peak variable
env_ts$peaks <- NA 
#at each location of the timeseries where there is a peak, load in the value of that peak so we can plot it later
env_ts$peaks[peaks[,2]] <- peaks[,1]

#lets plot a sample of 5 seconds
a <- 
  ggplot(env_ts, 
         aes(x = time_ms, 
             y = env
             )
         ) + 
  geom_path() + 
  geom_point(aes(y = peaks), 
             color = "red", size = 3) +
#  xlim(5000, 10000) + 
  theme_bw()

#lets also plot the original sound file to see how this compares
snd <- rPraat::snd.read(paste0(data_to_process, "audio_cartoon.wav"))
waveformdat <- cbind.data.frame(snd$t, snd$sig)
colnames(waveformdat) <- c("time_sec", "signal")
b <- 
  ggplot(waveformdat, 
         aes(x = time_sec, 
             y = signal
             )
         )+ 
  geom_path() +
 # xlim(5, 10) + 
  theme_bw() + 
  ylim(-0.15, 0.15)

grid.arrange(a,b)
```

# Syllable rate

```{r numerical_info, warning=FALSE, message= FALSE}
syllable_p_sec <- sum(!is.na(env_ts$peaks))/(max(env_ts$time_ms)/diff(range(env_ts$time_ms)))
print(paste0("N syllables produced p/s: ", syllable_p_sec))
print(paste0("SD in ms syllable interval: ", sd(diff(env_ts$time_ms[!is.na(env_ts$peaks)]))))
```

### 2022-07-06 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/FitBit_ET_Glasses_Methods.Rmd
update fitbit project

---
title: "Fitbit & ET Glasses - Methods"
output: html_notebook
---
```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Packages
# install.packages("needs")
# Choose "No"
library(needs)
needs(tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS)
```

# Initial Preparations

Run following Code if and only if new data is added to the initial data.

```{r message=FALSE, warning=FALSE,include=FALSE}
source(file = "data.wrangling.R")
```
# ET Glasses

## Acceleration

The Tobii Glases record acceleration data with a frequency of 100Hz. Therefore it should be possible to calculate the walked distance wearing the glasses using the following formulas:

$$\Delta x_{d,i} = 0.5 (t_{i-1}-t_{i})^2, \text{ with }i=2,...,t_n; d = z,x$$

$$x_d=\sum_{i=1}^n |\Delta x_{d,i}|, \text{ with }i=2,...,t_n; d = z,x$$

$$\sum x=\sqrt{x_z^2+x_x^2}$$

Using these formulas, one brave assumption must be made, that is, for every time period the initial velocity is equal to 0.

The real data gives plausible values.

```{r}
df_meter_real <- read_rds(file = "final_data/meter_real.rds")
df_meter_real
summary(df_meter_real$ges)
```

On the contrary, simulated situations revealed multiple problems.

For the first simulation the participant was standing still without moving its head and with stong movements of the head respectively. A reliable measurement would give the same distance for both situations. 
Afterwards, we simulated two two times 5 meter long walks. One time the participant turned around after 5 meters. During the other walk the participant walked 5 meters and walked back backwards. Again, we expect the glasses to give the same walking distance.
To test real world situations we simulated two random walks in a simulated class room. One walk simulated an extensive walk and the other walk simulated a less intense walk.
Additionally, we tested the values for taking the elevator and walking a staircase.
The simulated situations give the following values.

```{r}
df_meter_sim <- read_rds(file = "final_data/meter_test.rds")

df_meter_sim
```
Plotting the acceleration reveals the problems with the acceleration data.

```{r}
df_meter_sim_time <- read_rds(file = "final_data/meter_test_time.rds")

df_meter_sim_time %>%
  pivot_longer(cols = contains("acc"),
               names_to = "acc") %>%
ggplot(mapping = aes(x = time,
                     y = value
                     )
       ) +
  geom_path() +
  labs(y = "") +
  theme(text = element_text(family = "serif")) +
  facet_grid(rows = vars(name),
             cols = vars(acc) 
             ) +
  theme(strip.text.y = element_text(angle = 0))
```

## Pupil Dialation

The ET Glasses report the pupil dilation at a frequency of 100 Hz.

```{r}
# df_dil <- read_rds(file = "final_data/dilation.rds")
# 
# df_dil %>%
#   pivot_longer(cols = right:left,
#                names_to = "dilation") %>%
# ggplot(mapping = aes(x = time,
#                      y = value
#                      )
#        ) +
#   geom_path() +
#   facet_grid(rows = vars(ID),
#              cols = vars(dilation)
#              )
```

# FitBit

All participants were given a FitBit Smart Watch to wear during the experiment.

## Heart Rate

The heart rate of each participant were measured during the experiment.

```{r}
# Plots

df_heart_all <-
  read_rds(file = "final_data/heart_all.rds") |> 
  mutate(status = factor(status,
                         levels = c("Expert","Novice"),
                         labels = c("Expert","Novice")
                         )
         )

df_heart_min <-
  read_rds(file = "final_data/heart_min.rds")

df_heart_aggr <- 
  read_rds(file = "final_data/heart_aggr.rds") |> 
  mutate(status = factor(status,
                         levels = c("Novice","Expert"),
                         labels = c("Novice","Expert")
                         )
         )

plot_flow <-
ggplot(data = df_heart_all,
       mapping = aes(x = as.numeric(Time),
                     y = `Heart Rate`,
                     group = ID)
       ) +
  geom_line(mapping = aes(color = status),
            size = 0.3,
            alpha = 1
            ) +
  xlim(0, min(df_heart_min$min)) +
  scale_color_viridis_d(option = "A",
                       end = 0.8)  +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in Seconds)",
       y = "Heart Rate\n(in Beats per Minute)") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.position = "none",
        strip.text = element_text(size = 16)) +
  facet_grid(cols = vars(Type),
             scales = "free_x")

plot_flow_leg <-
ggplot(data = df_heart_all,
       mapping = aes(x = Time,
                     y = `Heart Rate`
                     )
       ) +
  geom_smooth(mapping = aes(color = status),
              method = "loess") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
 # scale_linetype_manual(values = c(1, 6)) +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank())

legend <- cowplot::get_legend(plot_flow_leg)

plot_loess <-
ggplot(data = filter(df_heart_all),
       mapping = aes(x = as.numeric(Time),
                     y = `Heart Rate`
                     )
       ) +
  stat_smooth(geom = "line",
              mapping = aes(color = status),
              method = "loess",
              se = FALSE) +
  xlim(0,min(df_heart_min$min)) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in Seconds)",
       y = "Heart Rate\n(in Beats per Minute)") +
  theme_minimal() +
  facet_grid(cols = vars(Type),
             scales = "free_x",
             ) +
  theme(text = element_text(family = "serif"),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()
        )

plot_box <- 
ggplot(data = df_heart_aggr,
       mapping = aes(x = Type,
                     y = mean,
                     color = status
                     )
       ) +
  geom_boxplot(color = "darkgrey",
               fill = "grey") +
  geom_line(data = filter(df_heart_aggr,
                          status == "Novice"),
            mapping = aes(x = Type,
                          y = mean,
                          group = as_factor(ID)
                          ),
            linetype = 1,
            alpha = 0.5
            ) +
  geom_line(data = filter(df_heart_aggr,
                          status == "Expert"),
            mapping = aes(x = Type,
                          y = mean,
                          group = as_factor(ID)
                          ),
            linetype = 6,
            alpha = 0.5
            ) +
  geom_point(size = 2,
             alpha = 0.5) +
  labs(x = "",
       y = "Average Heart Rate\n(in Beats per Minute)") +
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        strip.text = element_blank(),
       legend.position = "none",
        axis.text.x = element_blank()
        ) +
  aes(fill = Type)

lo_mat <- rbind(c(1,1,1,1,1,1,NA),
                c(2,2,2,2,2,2,4),
                c(3,3,3,3,3,3,NA))

plot_heart <- 
grid.arrange(grobs = list(plot_flow, plot_loess, plot_box, legend),
             layout_matrix = lo_mat)

plot_heart
```

## Steps

Using the FitBit we could also measure the steps a person walked. Unfortunately, the measurement was not as reliable as hoped. To confirm, we should simulate situations with a fixed number of steps.

```{r}
df_steps <- read_rds(file = "final_data/steps.rds")
set.seed(5678)
ggplot(data = df_steps,
       mapping = aes(x = type,
                     y = Steps
                     )
       ) +
  geom_boxplot(mapping = aes(color = type),
               fill = "grey",
               alpha = 0.6) +
  geom_jitter(mapping = aes(color = type),
              alpha = 0.9,
              width = 0.3) + 
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  labs(x = "",
       y = "Steps During\nMain Phase") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
        ) 
```

# Combined Analysis

## Steps and Heart Rate

```{r}
ggplot(data = df_steps,
       mapping = aes(x = Steps,
                     y = mean)
       ) +
  geom_point(mapping = aes(shape = type,
                           color = type),
             alpha = 0.7,
             size = 2.5) +
    geom_smooth(mapping = aes(color = type),
              method = "lm",
              se = F) +
  scale_color_viridis_d(option = "A",
                       end = 0.8
                       ) +
  labs(x = "Steps",
       y = "Average Heart Rate\n(in Beats per Minute)"
       ) +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank(),
        )
```

## Heart Rate and Pupil Dilation

```{r}
df_dil_aggr <- read_rds(file = "final_data/heart_dilation.rds")

df_dil_aggr %>%
  pivot_longer(cols = contains("dil"),
               names_to = "left_right",
               values_to = "Dilation") %>%
  mutate(type = factor(type,
                       levels = c("Expert","Novice"),
                       labels = c("Expert","Novice")
                       )
         ) |> 
  ggplot(mapping = aes(x = heart_rate_z,
                       y = Dilation)) +
  geom_point(mapping = aes(color = type),
             alpha = 0.7) +
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  geom_smooth(method = "lm",
              linetype = 2,
              color = "darkviolet") +
  labs(x = "Heart Rate\n(z-standardized)") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        text = element_text(family = "serif")) +
  facet_grid(cols = vars(factor(left_right,
                                levels = c("dil_left_z","dil_right_z"),
                                labels = c("Left Eye","Right Eye")
                                )
                         )
             ) 
```

# Measuring

```{r, warning=FALSE, message=FALSE}
df_heart_all %>% 
  clean_names() %>% 
  pivot_wider(names_from = time,
              values_from = heart_rate,
              names_prefix = "x")  %>%
  select(!contains("x")) ->
data_cache

df_heart_all %>% 
  clean_names() %>% 
  pivot_wider(names_from = time,
              values_from = heart_rate,
              names_prefix = "x")  %>%
  filter(id == "101") %>% 
  rowwise() %>%
  na_mean() %>%
  pivot_longer(cols = contains("x"),
               names_to = "time",
               values_to = "heart_rate") %>% 
  mutate(time = str_remove_all(time, "x")) %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_line()

 mutate(id = data_cache$id,
        ) %>% 
 right_join(x = ., 
            y = data_cache,
            by = "id") %>% 
 pivot_longer(cols = contains("x"),
               names_to = "time",
               values_to = "heart_rate") %>%
  mutate(time = str_remove_all(string = time,
                               pattern = "x"),
         time = as.numeric(time),
         heart_rate = as.numeric(heart_rate),
         id = as_factor(id)) %>%
  filter(id == "101") %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate,
                       group = id)
       ) + 
  geom_line(mapping = aes(color = status),
            size = 0.3,
            alpha = 1
            ) +
  xlim(0, min(df_heart_min$min)) +
  facet_grid(cols = vars(type))

  df_heart_all_wide

for (i in colnames(df_heart_all_wide)[-1:-4]) {

  df_heart_all_wide %>% 
    select(i)

}
df_heart_all_wide %>% 
  select(contains("x")) %>%
  as.matrix() %>% 
  rowwise() %>% 
  na_kalman() %>% 
  as_tibble() ->
  imp

imp$id <- data_cache$id

left_join(data_cache, imp,
          by = "id") %>% 
   pivot_longer(cols = contains("x"),
               names_to = "time",
               values_to = "heart_rate") %>%
  filter(id == "101") %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate,
                       group = id)
       ) + 
  geom_line(mapping = aes(color = status),
            size = 0.3,
            alpha = 1
            )

df_heart_all %>% 
  clean_names() %>% 
  pivot_wider(names_from = time,
              values_from = heart_rate,
              names_prefix = "x")  %>%
  filter(id == "101", type == "Post") %>% 
  select(!c("id","type","status")) %>% 
  pivot_longer()
  na_kalman()

imp <- na_kalman(tsAirgap)
ggplot_na_imputations(tsAirgap, imp)

df_heart_all %>% 
  clean_names() %>% 
  pivot_wider(names_from = time,
              values_from = heart_rate,
              names_prefix = "x") %>% 
  pivot_longer(cols = contains("x"),
               names_to = "time",
               values_to = "heart_rate") %>% 
  group_by(id, type) %>% 
  mutate(heart_rate = na_kalman(heart_rate)) %>% 
  ungroup() %>% 
  ggplot(mapping = aes(x = time, 
                       y = heart_rate,
                       group = id
                       )
         ) +
  geom_line()

```

### 2022-07-06 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/acc.Rmd
update fitbit project

---
title: "R Notebook"
output: html_notebook
---
# Packages

```{r}
library(needs)
needs(tidyverse,
      lubridate,
      janitor)
```

# Daten

```{r}
df_acc <- read_tsv(file = "data/ProVisioNET.tsv") %>% 
  clean_names()
```
```{r}
df_acc <- transmute(df_acc,
                    ID = str_replace(str_sub(participant_name,
                                             start = 19,
                                             end = 21
                                             ),
                                     pattern = "_",
                                     replacement = ""
                                     ),
                    gyro_x = as.numeric(str_replace(gyro_x,
                                                    pattern = ",",
                                                    replacement = "."
                                                    )
                                        ),
                    gyro_y = as.numeric(str_replace(gyro_y,
                                                    pattern = ",",
                                                    replacement = "."
                                                    )
                                        ),
                    acc_x = as.numeric(str_replace(accelerometer_x,
                                                    pattern = ",",
                                                    replacement = "."
                                                    )
                                        ),
                    acc_z = as.numeric(str_replace(accelerometer_z,
                                                    pattern = ",",
                                                    replacement = "."
                                                    )
                                        ),
                    time = as.numeric(milliseconds(recording_timestamp
                                                   )
                                      ),
                    sensor = sensor,
                    meter_x = rep(0),
                    meter_z = rep(0)
                    ) %>% 
  filter(as.numeric(ID) > 100) %>%
  select(!contains("gyro")) %>%
  na.omit() %>%
  select(!"sensor")

# df_acc <- df_acc %>% 
#   filter(as.numeric(ID) > 100)
# 
# df_acc_acc <- df_acc %>%
#   filter(sensor == "Accelerometer") %>%
#   select(!contains("gyro")) %>%
#   pivot_longer(cols = c(acc_x, acc_z),
#                names_to = "acc")
# 
# df_acc_gyro <- df_acc %>%
#   filter(sensor == "Gyroscope") %>%
#   select(!contains("acc"))
```

```{r}
plot_acc <- 
ggplot(data = df_acc_acc,
       mapping = aes(x = time,
                     y = value
                     )
       ) +
  geom_path() +
  geom_path() +
  facet_grid(rows = vars(ID),
             cols = vars(acc)
             )

ggsave(plot = plot_acc,
       filename = "Plots/plot_acc.pdf",
       height = 10,
       width = 5)

# df_sum <- 
# df_acc_acc %>% 
#   group_by(acc, ID) %>%
#   summarize(sum = sum(abs(value)),
#             time = max(time)
#             )
```

```{r}
# First step: create tibbles for each individual.
for (i in unique(df_acc$ID)) {

  df <- filter(df_acc,
               ID == i
               )

  assign(value = df,
         x = paste0("df_", i)
         )

}

# For each of the tibbles, create two vectors (x and z) 
  # for meters for each time period.

for (i in unique(df_acc$ID)) {

  df <- get(paste0("df_", i))

# Vectors x and z with length equal to time periods 
  # present in each tibble; initial with 0 meters for each   # time period.

  x <- rep(0, length(get(paste0("df_", i))$time))
  z <- rep(0, length(get(paste0("df_", i))$time))

# For each time period, calculate the meters walked in 
  # two dimensions (x and z), given the initial velocity 
  # for each period is 0 m/s. First value stays 0 for
  # convenience.
  # See formula 1.

  for (j in 2:length(get(paste0("df_", i))$time)) {

    x[[j]] <- 0.5 * get(paste0("df_", i))$acc_x[j] * (get(paste0("df_", i))$time[j] - get(paste0("df_", i))$time[j-1])^2

    z[[j]] <- 0.5 * get(paste0("df_", i))$acc_z[j] * (get(paste0("df_", i))$time[j] - get(paste0("df_", i))$time[j-1])^2

  }

# Save both vectors in new tibble.

  df <- tibble(meter_x = x,
               meter_z = z,
               ID = paste0(i))
  assign(x = paste0("df_meter_", i),
           value = df)

}

# Combine all tibbles containing distance walked per 
  # time period.
  # Calculate sum of absolute distance walked for each 
  # participant and dimension.
  # See formula 2.

df_meter_all <- 
  mget(ls(pattern = "meter")) %>%
  bind_rows() %>% 
  group_by(ID) %>%
  summarise(meter_x = sum(abs(meter_x)),
            meter_z = sum(abs(meter_z)))

# Calculate walked distance in two-dimensional space.
  # See formula 3.

df_meter_all$ges <- sqrt(df_meter_all$meter_x^2 + df_meter_all$meter_z^2)
```

$$\Delta x_{d,i} = 0.5 (t_{i-1}-t_{i})^2, \text{ with }i=2,...,t_n; d = z,x$$
$$x_d=\sum_{i=1}^n |\Delta x_{d,i}|, \text{ with }i=2,...,t_n; d = z,x$$
$$\sum x=\sqrt{x_z^2+x_x^2}$$

- 4 Szenarien (still, still + kopf, viel gehen, wenig gehen, fahrstuhl, treppe) + whatever

```{r}
saveRDS(object = df_meter_all,
        file = "data/df_meter_all.rds")

rm(list = ls())
```

# Plot

```{r}
ggplot(data = df_acc_hr,
       mapping = aes(x = mean,
                      y = ges
                      )
        ) +
   geom_point(mapping = aes(color = status)) +
   geom_smooth(method = "lm",
               se = F) +
   labs(x = "Average Heart Rate\n(in Beats per Minute)",
        y = "Meters Walked\n(in Meters)")
```

### 2022-07-07 01_studies/01_Laborstudie ProVisioNET/Amplitude_Extraction/ampl_extr_ProVisioNet.Rmd

---
title: "Amplitude Extraction"
subtitle: "ProVisioNET Study"
output: html_notebook
---

# Preparations

```{r}
library(needs)

needs(tidyverse)
```

```{r}
# Add file path for synced Audio Files 
# Edit file path according to system
data_to_process <- "/Volumes/EmpForsch/00 Video Archive/022_ProVisioNET/ProVisioNet_study_glasses_synced/"

# Add Vector for all .wav files available
list_wavs <- list.files(path = data_to_process, 
                        pattern = ".wav")

# Add Vector for already existing data 
existing_data <- list.files(path = "data",
                            pattern = ".csv") %>% 
  str_replace(pattern = "_ENV.csv",
              replacement = ".wav")

# Alter the vector so that only data is left that has not already been analyzed.
list_wavs <- str_subset(string = list_wavs,
                        pattern = existing_data,
                        negate = TRUE)
```

# Function

So there is more than one way to compute a smoothed amplitude envelope. We however follow the procedure originally coded in PRAAT by He & Dellwo (2017; ref 4.) which we reimplemented in R. The main function below follow their procedure. Firstly, we read in a sound file, and then apply a Hilbert transform to the waveform signal, which yields what is called a complex analytic signal (containing real and imaginary numbers). From this we can extract the amplitude information by applying what is called the complex modulus, and we are left with a 1D signal that will track the \emph{rough or more precise} contours of that audio waveform \emph{depending the amount of smoothing}. Following He & Dellwo, since we are interested in an approximation of the syllable cycles that tend to occur no shorter than 200ms, we will smooth the signal at a max 5Hz (1000ms/5Hz = 200ms) using a Hanning Window filter. We then downsample the smoothed amplitude envelope to something more workable, namely, to 100Hz time series, which we can later align for example with other signals (e.g., motion tracking data). For a more information about the key procedure, the Hilbert transformation, see (5. Cohen, 2019)

Note, that the function below, allows you to set the resampling rate differently (e.g., 200Hz instead of 100Hz), as well as the hanning window settings (e.g., 8Hz instead of 5Hz).

```{r main_function, warning=FALSE, message= FALSE}
needs(seewave,
      signal,
      rPraat,
      dplR)

#####################MAIN FUNCTION TO EXTRACT SMOOTHED ENVELOPE###############################
amplitude_envelope.extract <- function(locationsound, smoothingHz, resampledHz)
{
  #read the sound file into R
  snd <- rPraat::snd.read(locationsound)
  #apply the hilbert on the signal
  hilb <- seewave::hilbert(snd$sig, f = snd$fs, fftw =FALSE)
  #apply complex modulus
  env <- as.vector(abs(hilb))
  #smooth with a hanning window
  env_smoothed <- dplR::hanning(x= env, n = snd$fs/smoothingHz)
  #set undeterminable at beginning and end NA's to 0
  env_smoothed[is.na(env_smoothed)] <- 0
  #resample settings at desired sampling rate
  f <- approxfun(1:(snd$duration*snd$fs),env_smoothed)
  #resample apply
  downsampled <- f(seq(from=0,to=snd$duration*snd$fs,by=snd$fs/resampledHz))
  #let function return the downsampled smoothed amplitude envelope
  return(downsampled[!is.na(downsampled)])
}
```

# Apply to .wav data

```{r}
#loop through soundfile locations
for(wav in list_wavs){
  #location of the current sound file in the loop  
  locsound <- paste0(data_to_process, wav)
  #get the amplitude envelope at location, 5Hz Hanning, 100Hz sampling
  env <- amplitude_envelope.extract(locsound, 5, 100)
  #make a time vector based on sampling rate (1000/Hz)
  time_ms <- seq(1000/100, length(env)*(1000/100), by = 1000/100)
  #bind into data frame
  ENV <- cbind.data.frame(time_ms, env)
  #save it to a folder
  write.csv(ENV, file = paste0(paste0("data/", substr(wav, 1, nchar(wav)-4), "_ENV", ".csv")),row.names=FALSE) 
  }

```

### 2022-07-07 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/Test Data.Rmd

--- 2022-07-06 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/acc.Rmd
@@
 ---
-title: "R Notebook"
+title: "Test Data"
 output: html_notebook
 ---
+
 # Packages
@@
 needs(tidyverse,
-      lubridate,
-      janitor)
+      janitor,
+      lubridate)
 ```
 
-# Daten
+# Data
+
+```{r message=FALSE}
+df_test <- read_tsv(file = "data/Acc_Test_Data.tsv") %>% 
+  clean_names()
+```
+
+# Let the wrangle begin
 
 ```{r}
-df_acc <- read_tsv(file = "data/ProVisioNET.tsv") %>% 
-  clean_names()
-```
-```{r}
-df_acc <- transmute(df_acc,
-                    ID = str_replace(str_sub(participant_name,
-                                             start = 19,
-                                             end = 21
+df_test <- 
+  df_test %>%
+  transmute(time = as.numeric(milliseconds(recording_timestamp_ms
+                                           )
                               ),
-                                     pattern = "_",
-                                     replacement = ""
-                                     ),
-                    gyro_x = as.numeric(str_replace(gyro_x,
+            name = participant_name,
+            acc_x = as.numeric(str_replace(accelerometer_x_m_s2,
                                            pattern = ",",
@@
                                ),
-                    gyro_y = as.numeric(str_replace(gyro_y,
+            acc_z = as.numeric(str_replace(accelerometer_z_m_s2,
                                            pattern = ",",
@@
                                            )
-                                        ),
-                    acc_x = as.numeric(str_replace(accelerometer_x,
-                                                    pattern = ",",
-                                                    replacement = "."
                                )
-                                        ),
-                    acc_z = as.numeric(str_replace(accelerometer_z,
-                                                    pattern = ",",
-                                                    replacement = "."
             )
-                                        ),
-                    time = as.numeric(milliseconds(recording_timestamp
-                                                   )
-                                      ),
-                    sensor = sensor,
-                    meter_x = rep(0),
-                    meter_z = rep(0)
-                    ) %>% 
-  filter(as.numeric(ID) > 100) %>%
-  select(!contains("gyro")) %>%
-  na.omit() %>%
-  select(!"sensor")
-
-# df_acc <- df_acc %>% 
-#   filter(as.numeric(ID) > 100)
-# 
-# df_acc_acc <- df_acc %>%
-#   filter(sensor == "Accelerometer") %>%
-#   select(!contains("gyro")) %>%
-#   pivot_longer(cols = c(acc_x, acc_z),
-#                names_to = "acc")
-# 
-# df_acc_gyro <- df_acc %>%
-#   filter(sensor == "Gyroscope") %>%
-#   select(!contains("acc"))
 ```
 
-```{r}
-plot_acc <- 
-ggplot(data = df_acc_acc,
-       mapping = aes(x = time,
-                     y = value
-                     )
-       ) +
-  geom_path() +
-  geom_path() +
-  facet_grid(rows = vars(ID),
-             cols = vars(acc)
-             )
-
-ggsave(plot = plot_acc,
-       filename = "Plots/plot_acc.pdf",
-       height = 10,
-       width = 5)
-
-# df_sum <- 
-# df_acc_acc %>% 
-#   group_by(acc, ID) %>%
-#   summarize(sum = sum(abs(value)),
-#             time = max(time)
-#             )
-```
+# Loops
 
@@
 # First step: create tibbles for each individual.
-for (i in unique(df_acc$ID)) {
+for (i in unique(df_test$name)) {
 
-  df <- filter(df_acc,
-               ID == i
+  df <- filter(df_test,
+               name == i
                )
@@
 
-for (i in unique(df_acc$ID)) {
+for (i in unique(df_test$name)) {
 
@@
   summarise(meter_x = sum(abs(meter_x)),
-            meter_z = sum(abs(meter_z)))
+            meter_z = sum(abs(meter_z))
+            )
 
@@
 
-$$\Delta x_{d,i} = 0.5 (t_{i-1}-t_{i})^2, \text{ with }i=2,...,t_n; d = z,x$$
-$$x_d=\sum_{i=1}^n |\Delta x_{d,i}|, \text{ with }i=2,...,t_n; d = z,x$$
-$$\sum x=\sqrt{x_z^2+x_x^2}$$
-
-- 4 Szenarien (still, still + kopf, viel gehen, wenig gehen, fahrstuhl, treppe) + whatever
+# Ergebnisse
 
 ```{r}
-saveRDS(object = df_meter_all,
-        file = "data/df_meter_all.rds")
-
-rm(list = ls())
+df_meter_all
 ```
 
-# Plot
-
 ```{r}
-ggplot(data = df_acc_hr,
-       mapping = aes(x = mean,
-                      y = ges
+df_test %>%
+  pivot_longer(cols = contains("acc"),
+               names_to = "acc") %>%
+ggplot(mapping = aes(x = time,
+                     y = value
                      )
        ) +
-   geom_point(mapping = aes(color = status)) +
-   geom_smooth(method = "lm",
-               se = F) +
-   labs(x = "Average Heart Rate\n(in Beats per Minute)",
-        y = "Meters Walked\n(in Meters)")
+  geom_path() +
+  facet_grid(rows = vars(name),
+             cols = vars(acc) 
+             ) +
+  theme(strip.text.y = element_text(angle = 0))
 ```

### 2022-07-07 02_paper/02_study/paper_methods.Rmd
Update paper_methods.Rmd

@@
 ```
-
+XXX FRANZI
 ```{r item_analysis_classroom_management_novice, echo=FALSE, include=FALSE, results='asis'}
@@
 ```
+XXX FRANZI
 

### 2022-07-09 02_paper/02_study/paper_methods.Rmd
update method section

@@
 
+XXX FRANZI 
+```{r reaction_codingsystem, include=TRUE, echo=FALSE, results='asis'}
+
+audit_table <- structure(
+  list(
+    Description = c(
+      "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
+      "The teacher reacts nonverbally and simultaneously with a short verbal reaction.
+The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixing gaze).
+The verbal response includes name calling, brief verbal prompts / admonitions.",
+      "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
+      "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption.
+The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixating gaze).",
+      "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption.
+This information can only be obtained through the Stimulated Recall Interview.",
+      "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption.
+This information can only be obtained through the Stimulated Recall Interview.",
+      "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
+                  ),
+    `1` = c("Never", "1–2", "Never"),
+    `2` = c("Monthly or less", "3-4", "Less than monthly"),
+    `3` = c("2-4 times per month", "5-6", "monthly"),
+    `4` = c("2-3 times per week","7-9", "Weekly"),
+    `5` = c("4+ times per week", "10+", "Daily or almost daily"),
+    `6` = c("bla"),
+    `7` = c("bla")
+          ),
+  class = "data.frame",
+  row.names = c(NA)
+)
+
+apa_table(
+  audit_table,
+  caption = "AUDIT-C scoring table",
+  align = c("m{8cm}", rep("m{2cm}", 5)),
+  col_spanners = list("Code" = c(2,7)),
+  note = "Item scores are summed. Women who score 3+ and men who score 4+ are at-risk",
+  landscape = TRUE
+  )
+
+# df_react_table <-
+#   structure(list(
+#     Code = c("1", "2", "3", "4", "5", "6", "7"),
+#     Description = c(
+#       "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
+#       "The teacher reacts nonverbally and simultaneously with a short verbal reaction.
+The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixing gaze).
+The verbal response includes name calling, brief verbal prompts / admonitions.",
+#       "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
+#       "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption.
+The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixating gaze).",
+#       "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption.
+This information can only be obtained through the Stimulated Recall Interview.",
+#       "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption.
+This information can only be obtained through the Stimulated Recall Interview.",
+#       "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
+#     ),
+#     `Anchor examples` = c("-",
+#                           "-",
+#                           "drawing on a sheet of paper",
+#                           "-",
+#                           "-",
+#                           "-",
+#                           "-"),
+#     class = "data.frame"
+#   ))
+# 
+# papaja::apa_table(
+#   x = df_react_table,
+#   caption = "Self-developed coding scheme for the teacher's reaction",
+#   align = c("m{8cm}", rep("m{2cm}", 5)),
+#   col_spanners = list("NA"),
+#   # note = "",
+#   landscape = TRUE)
+
+```
+
 After developing and reviewing the coding system, the observers coordinated and the consistency of their ratings was verified.

### 2022-07-18 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/FitBit_ET_Glasses_Methods.Rmd
fitbit data

@@
 
-For the first simulation the participant was standing still without moving its head and with stong movements of the head respectively.
+For the first simulation the participant was standing still without moving its head and with strong movements of the head respectively.
 A reliable measurement would give the same distance for both situations.
@@
         )
+
+### Validation of steps 
+# selecting some rows at random with sample_n()
+sample_n(df_steps, 6)
+
+# Output:
+# Experts: 219, 218, 214
+# Novices: 108, 117, 110
+
 ```

### 2022-07-28 02_paper/02_study/paper_methods.Rmd
update data & plotssss

@@
 
-## Materials
-
-### Eye-Tracking Apparatus
+## Materials and Measures
+
+### Eye-Tracking Data
+
+#### Apparatus
 
@@
 ```
+
+#### Teachers' visual focus of attention
+
+Teachers' areas of interest (AOI) were identified as targets where teachers looked during the micro-teaching-unit using Tobii Pro Lab Analyzer Software Version 1.171.
+In the present study, general AOIs where defined as the student group, the students' nametags, the teacher material, the students' material, the board and non-instructional material in the classroom (wall, window, floor).
+These AOIs were coded during the manual fixation mapping process during the entire micro-teaching-unit.
+Additionally, the disruptive person was coded as an event-based AOI only over the duration of the disruption.
+
+--> Only eye-tracking video recordings with 70 % and above gaze sample percentages were selected for the study to ensure that one or both eyes were detected during 70 % of the recording’s duration (Chaudhuri et al, 2022).
+Screenshots of the video recordings were used to define the AOI in the eye-tracking videos.
+The coder started manual gaze mapping when the teacher entered the classroom and ended coding when the micro-teaching-unit ended.
+The start and end of the micro-teaching-unit was defined by a visual and acoustical signal.
+The two coders who were assigned to code the eye-tracking videos student employees who studied to be teachers and received a detailed introduction to the software.
+The intercoder reliability was checked by double coding 20 % of the videos from the whole dataset.
+Double coding agreement ranged from XXX % to XXX %.
+
+We coded each fixation using the Attention Filter in Pro Lab with the velocity threshold parameter set to 100 degrees/second instead of the default 30 degrees/second.
+This filter is suitable for dynamic situations to study attention without separating any eye movements.
+By choosing the Attention Filter typical fixations, most VOR (Vestibulo-ocular reflex), smooth pursuit eye movements, and slow saccades are classified as fixations.
+
+The relevant fixation metrics such as number of fixations, the total duration of fixations and time to first fixation on the relevant event (disruptive person) were obtained by exporting an interval-based TSV file from the Tobii Pro Lab Analyzer Software.
+The total fixation duration and the time to first fixation metrics were measured in milliseconds (ms) and the number of fixation in counts as an integer.
+To calculate the average fixation of durations for all AOIs, we divided the total duration of fixations by the number of  fixations for each AOI.
 
@@
 
-##### Coding Teachers' Reaction
+##### Teachers' Reaction to disruptions
 
@@
 
+XXX
+
 ### Questionnaie data
@@
 
-#### Rating scales
+#### Teachers' perception of disruption and confidence using Rating scales
 
@@
 For the present study, the following two questions from the interview were relevant:
-1. "How disturbing did you perceive this event to be?"
+1. "How disruptive was this event for you?"
 2. "How confident did you feel in dealing with this event?"

### 2022-07-28 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -20,7 +20,7 @@ sri <-
   excel_sheets("data/Coding_SRI.xlsx") %>% 
   map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% 
   select(Group, Event, `Disruption Factor`, `Confident Factor`) %>% # select relevant columns 
-  filter(Group %in% c(101:122, 202:212))# filter relevant rows
+  filter(Group %in% c(101:125, 202:217))# filter relevant rows
 
  
 # # counting drop outs (-99 not perceived, -100 not answered)
@@ -456,3 +456,4 @@ sd_confi_exp <-
   pull(`Confident Factor`) %>% 
   sd() %>% 
   round(., digits = 0)
+

### 2022-08-01 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
time to first fixation

---
title: "AOI TOI - number of fixations, duration of fixation & time to first fixation"
output: html_notebook
---

# Load packages and read in data
```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot)

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

# return a character vector with names of .tsv data in data folder
file_names <- list.files(path = "data",
                         pattern = "interval_complete.tsv")

# read every object names in file_names and save it as a tibble
for (i in file_names) {

  work_data <- 
    read_tsv(file = paste0("data/", i),
             locale = locale(decimal_mark = ","))

  assign(value = work_data,
         x = str_remove(paste0("tib_", i),
                        pattern = ".tsv"
         )
  )

}

# Bind every tibble that contains "interval_complete" to a new tiblle
df_aoi <- 
  mget(ls(pattern = "interval_complete")) %>%
  bind_rows()

# Remove temporary data for a cleaner workspace
rm(list = ls(pattern = "^tib_ProVisio"))
rm(work_data)
rm(file_names)
rm(i)

```

# Number of fixation on all AOI

```{r}
##################### NUMBER OF FIXATION ON ALL AOIS ########################

# filter group & total duration & number fixation on all AOIs

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          starts_with("Total_duration_of_fixations"),
          starts_with("Number_of_fixations"),
          !"Total_duration_of_fixations.Disruptive_Person",
          !"Number_of_fixations.Disruptive_Person") %>% 
  rowwise() %>% 
  transmute(Group = Group,
            Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
                                                    ),
                                           na.rm = TRUE
                                           ),
            Sum_number_fixation = sum(c_across(starts_with("Number_of")
                                                  ),
                                         na.rm = TRUE
                                         )
            ) %>% 
  mutate(Average_duration = round(Sum_duration_fixation/Sum_number_fixation,
                                         digits = 0),
         Group = as_factor(Group)) -> df_aoi_sum

# mean & SD number fixation 
# novices
mean_number_nov <- 
  df_aoi_sum %>%
  filter(Group == "Novice") %>% 
  pull(Sum_number_fixation) %>% 
  mean() %>% 
  round(., digits = 0)

sd_number_nov <- 
  df_aoi_sum %>%
  filter(Group == "Novice") %>% 
  pull(Sum_number_fixation) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_number_exp <-
  df_aoi_sum %>%
  filter(Group == "Expert") %>% 
  pull(Sum_number_fixation) %>% 
  mean() %>% 
  round(., digits = 0)

sd_number_exp <- 
  df_aoi_sum %>%
  filter(Group == "Expert") %>% 
  pull(Sum_number_fixation) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting number of fixations on ALL AOIS
df_aoi_sum %>% 
  ggplot(mapping = aes(x = Group,
                       y = Sum_number_fixation)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste(
  #   c("Novice\n", "Expert\n"),
  #   glue("$M$ = "),
  #   c(mean_number_nov, mean_number_exp),
  #   glue("; $SD$ = "),
  #   c(sd_number_nov, sd_number_exp)
  # )) +

  # scale_x_discrete(labels = c(
  #   paste(
  #     "Novice\n",
  #     glue("<i>M</i>"),
  #     " = ",
  #     c(mean_number_nov, mean_number_exp)
  #   ),
  #   c(
  #     "Expert\n",
  #     ";",
  #     glue("<i>SD</i>"),
  #     " = ",
  #     c(sd_number_nov, sd_number_exp)
  #   ) 
  # )) +
  labs(x ="",
       y = "Number") +
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Number of Fixations on all AOIs") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
        ) -> plot_number_group
plot_number_group

# saving plot number plot
ggsave(plot = plot_number_group,
       filename = "plots/plot_number_group.svg",
       height = 8,
       width = 14,
       units = "in")

# NUMBER OF FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
       y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"])

# NUMBER OF FIXATIONS on all AOIs
# effect size for expertise differences
d_number_all <- CohenD(x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
                       y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
                       na.rm = TRUE)

```

# Number of fixations on AOI "Disruptive person"

```{r}
##################### NUMBER OF FIXATION ON AOI DISRUPTIVE PERSON ########################

# filter group & total duration & number fixation on AOI Disruptive person

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          "Number_of_fixations.Disruptive_Person") %>%
  mutate(Group = as_factor(Group)) -> df_aoi_disrup

# mean & SD average duration AOI Disruptive person
# novices
mean_number_disrup_nov <- 
  df_aoi_disrup %>%
  filter(Group == "Novice") %>% 
  pull(Number_of_fixations.Disruptive_Person) %>% 
  mean() %>% 
  round(., digits = 0)

sd_number_disrup_nov <- 
  df_aoi_disrup %>%
  filter(Group == "Novice") %>% 
  pull(Number_of_fixations.Disruptive_Person) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_number_disrup_exp <-
  df_aoi_disrup %>%
  filter(Group == "Expert") %>% 
  pull(Number_of_fixations.Disruptive_Person) %>% 
  mean() %>% 
  round(., digits = 0)

sd_number_disrup_exp <- 
  df_aoi_disrup %>%
  filter(Group == "Expert") %>% 
  pull(Number_of_fixations.Disruptive_Person) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on AOI Disruptive person
df_aoi_disrup %>% 
  ggplot(mapping = aes(x = Group,
                       y = Number_of_fixations.Disruptive_Person)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Number") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Number of Fixations\non AOI `Disruptive Person`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_number_disrup

# saving plot average plot
ggsave(plot = plot_number_disrup,
       filename = "plots/plot_number_disrup.svg",
       height = 8,
       width = 8,
       units = "in")

# AVERAGE DURATION OF FIXATIONS on AOI disruptive person 
# t-test for expertise differences
t.test(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
       y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"])

# AVERAGE DURATION OF FIXATIONS 
# effect size for expertise differences
d_number_disrup <- CohenD(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
                        y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"],
                        na.rm = TRUE)

```

# Number of fixations on AOI "Students"

```{r}
##################### NUMBER OF FIXATIONS ON AOI STUDENTS ########################
# filter group & total duration & number fixation on AOI Students
df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          "Total_duration_of_fixations.Anna",
          "Total_duration_of_fixations.Bianca",
          "Total_duration_of_fixations.Carl(a)",
          "Number_of_fixations.Anna",
          "Number_of_fixations.Bianca",
          "Number_of_fixations.Carl(a)") %>% 
  rowwise() %>% 
  transmute(Group = Group,
            Stud_duration_fixation = sum(c_across(starts_with("Total_duration")
                                                 ),
                                         na.rm = TRUE
                                         ),
            Stud_number_fixation = sum(c_across(starts_with("Number_of")
                                                ),
                                       na.rm = TRUE
                                       )
            ) %>% 
  mutate(Average_duration_stud = round(Stud_duration_fixation/Stud_number_fixation, 
                                  digits = 0),
         Group = as_factor(Group)) -> df_aoi_stud

# mean & SD average duration on AOI Students
# novices
mean_number_stud_nov <- 
  df_aoi_stud %>%
  filter(Group == "Novice" ) %>% 
  pull(Stud_number_fixation) %>% 
  mean() %>% 
  round(., digits = 0)

sd_number_stud_nov <- 
  df_aoi_stud %>%
  filter(Group == "Novice") %>% 
  pull(Stud_number_fixation) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_number_stud_exp <-
  df_aoi_stud %>%
  filter(Group == "Expert") %>% 
  pull(Stud_number_fixation) %>% 
  mean() %>% 
  round(., digits = 0)

sd_number_stud_exp <- 
  df_aoi_stud %>%
  filter(Group == "Expert") %>% 
  pull(Stud_number_fixation) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on AOI Students
df_aoi_stud %>% 
  ggplot(mapping = aes(x = Group,
                       y = Stud_number_fixation)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Number") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Number of Fixations\non AOI `Students`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_number_stud

# saving plot average plot
ggsave(plot = plot_number_stud,
       filename = "plots/plot_number_stud.svg",
       height = 8,
       width = 8,
       units = "in")

# AVERAGE DURATION OF FIXATIONS on AOI Students 
# t-test for expertise differences
t.test(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
       y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"])

# AVERAGE DURATION OF FIXATIONS on AOI Students
# effect size for expertise differences
d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
                      y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
                      na.rm = TRUE)

```

# Average duration of fixations on all AOIs

```{r}
##################### AVERAGE DURATION ON ALL AOIS ########################

# filter group & total duration & number fixation on all AOIs

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          starts_with("Total_duration_of_fixations"),
          starts_with("Number_of_fixations"),
          !"Total_duration_of_fixations.Disruptive_Person",
          !"Number_of_fixations.Disruptive_Person") %>% 
  rowwise() %>% 
  transmute(Group = Group,
            Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
                                                    ),
                                           na.rm = TRUE
                                           ),
            Sum_number_fixation = sum(c_across(starts_with("Number_of")
                                                  ),
                                         na.rm = TRUE
                                         )
            ) %>% 
  mutate(Average_duration = round(Sum_duration_fixation/Sum_number_fixation,
                                         digits = 0),
         Group = as_factor(Group)) -> df_aoi_sum

# mean & SD average duration 
# novices
mean_dur_nov <- 
  df_aoi_sum %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_nov <- 
  df_aoi_sum %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_dur_exp <-
  df_aoi_sum %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_exp <- 
  df_aoi_sum %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on ALL AOIS
df_aoi_sum %>% 
  ggplot(mapping = aes(x = Group,
                       y = Average_duration)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Average Duration of Fixations on all AOIs") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
        ) -> plot_average_duration_group

# saving plot average plot
ggsave(plot = plot_average_duration_group,
       filename = "plots/plot_average_duration_group.svg",
       height = 8,
       width = 14,
       units = "in")

# AVERAGE DURATION OF FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
       y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"])

# AVERAGE DURATION OF FIXATIONS on all AOIs
# effect size for expertise differences
d_aver_all <- CohenD(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
                    y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
                    na.rm = TRUE)

```

# Average duration of fixations on AOI "Disruptive Person"

```{r}
##################### AVERAGE DURATION ON AOI DISRUPTIVE PERSON ########################

# filter group & total duration & number fixation on AOI Disruptive person

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          "Total_duration_of_fixations.Disruptive_Person",
          "Number_of_fixations.Disruptive_Person") %>% 
  rowwise() %>% 
  mutate(Average_duration_disrup = round(Total_duration_of_fixations.Disruptive_Person/Number_of_fixations.Disruptive_Person, 
                                  digits = 0),
         Group = as_factor(Group)) -> df_aoi_disrup

# mean & SD average duration AOI Disruptive person
# novices
mean_dur_disrup_nov <- 
  df_aoi_disrup %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration_disrup) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_disrup_nov <- 
  df_aoi_disrup %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration_disrup) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_dur_disrup_exp <-
  df_aoi_disrup %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration_disrup) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_disrup_exp <- 
  df_aoi_disrup %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration_disrup) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on AOI Disruptive person
df_aoi_disrup %>% 
  ggplot(mapping = aes(x = Group,
                       y = Average_duration_disrup)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Average Duration of Fixations\non AOI `Disruptive Person`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_average_duration_disrup

# saving plot average plot
ggsave(plot = plot_average_duration_disrup,
       filename = "plots/plot_average_duration_disrup.svg",
       height = 8,
       width = 8,
       units = "in")

# AVERAGE DURATION OF FIXATIONS on AOI disruptive person 
# t-test for expertise differences
t.test(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
       y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"])

# AVERAGE DURATION OF FIXATIONS 
# effect size for expertise differences
d_aver_disrup <- CohenD(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
                        y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"],
                        na.rm = TRUE)

```

# Average duration of fixations on AOI "Students"

```{r}
##################### AVERAGE DURATION ON AOI STUDENTS ########################

# filter group & total duration & number fixation on AOI Students
df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          "Total_duration_of_fixations.Anna",
          "Total_duration_of_fixations.Bianca",
          "Total_duration_of_fixations.Carl(a)",
          "Number_of_fixations.Anna",
          "Number_of_fixations.Bianca",
          "Number_of_fixations.Carl(a)") %>% 
  rowwise() %>% 
  transmute(Group = Group,
            Stud_duration_fixation = sum(c_across(starts_with("Total_duration")
                                                 ),
                                         na.rm = TRUE
                                         ),
            Stud_number_fixation = sum(c_across(starts_with("Number_of")
                                                ),
                                       na.rm = TRUE
                                       )
            ) %>% 
  mutate(Average_duration_stud = round(Stud_duration_fixation/Stud_number_fixation, 
                                  digits = 0),
         Group = as_factor(Group)) -> df_aoi_stud

# mean & SD average duration on AOI Students
# novices
mean_dur_stud_nov <- 
  df_aoi_stud %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration_stud) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_stud_nov <- 
  df_aoi_stud %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration_stud) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_dur_stud_exp <-
  df_aoi_stud %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration_stud) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_stud_exp <- 
  df_aoi_stud %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration_stud) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on AOI Students
df_aoi_stud %>% 
  ggplot(mapping = aes(x = Group,
                       y = Average_duration_stud)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Average Duration of Fixations\non AOI `Students`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_average_duration_stud

# saving plot average plot
ggsave(plot = plot_average_duration_stud,
       filename = "plots/plot_average_duration_stud.svg",
       height = 8,
       width = 8,
       units = "in")

# AVERAGE DURATION OF FIXATIONS on AOI Students 
# t-test for expertise differences
t.test(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
       y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"])

# AVERAGE DURATION OF FIXATIONS on AOI Students
# effect size for expertise differences
d_aver_stud <- CohenD(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
                      y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
                      na.rm = TRUE)

```

# Time to first fixation on all AOIs

```{r}

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          starts_with("Time_to_first_fixation"),
          !"Time_to_first_fixation.Disruptive_Person") %>%
  rowwise() %>% 
  transmute(Group = Group,
            Sum_time_fixation = sum(c_across(starts_with("Time_to_first_fixation")
                                                    ),
                                           na.rm = TRUE
                                           ) 
            ) %>% 
  mutate(Group = as_factor(Group)) -> df_ttff_sum

# mean & SD time to first fixation 
# novices
mean_time_nov <- 
  df_ttff_sum %>%
  filter(Group == "Novice") %>% 
  pull(Sum_time_fixation) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_nov <- 
  df_ttff_sum %>%
  filter(Group == "Novice") %>% 
  pull(Sum_time_fixation) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_time_exp <-
  df_ttff_sum %>%
  filter(Group == "Expert") %>% 
  pull(Sum_time_fixation) %>% 
  mean() %>% 
  round(., digits = 0)

sd_time_exp <- 
  df_ttff_sum %>%
  filter(Group == "Expert") %>% 
  pull(Sum_time_fixation) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on ALL AOIS
df_ttff_sum %>% 
  ggplot(mapping = aes(x = Group,
                       y = Sum_time_fixation)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Time to first fixation\non all AOIs") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
        ) -> plot_time_group
plot_time_group

# saving plot average plot
ggsave(plot = plot_time_group,
       filename = "plots/plot_time_group.svg",
       height = 8,
       width = 14,
       units = "in")

# TIME TO FIRST FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(x = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Expert"],
       y = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Novice"])

# TIME TO FIRST FIXATIONS on all AOIs 
# effect size for expertise differences
d_time_all <- CohenD(x = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Expert"],
                    y = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Novice"],
                    na.rm = TRUE)

```

# Time to first fixation on AOI "Disruptive Person"

```{r}
############### TIME TO FIRST FIXATION ####################

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          "Time_to_first_fixation.Disruptive_Person") %>% 
  rowwise() %>% 
  mutate(Group = as_factor(Group)) -> df_ttff_disrup

# changing milliseconds into seconds
df_ttff_disrup$`Time to first fixation in seconds` <-
  round(df_ttff_disrup$Time_to_first_fixation.Disruptive_Person / 1000,
        digits = 2)

##################### plotting time to first fixation for groups ##################### 
fix_group_plot <- 
  ggplot(data = df_ttff_disrup,
         mapping = aes(x = Group,
                       y = `Time to first fixation in seconds`)) +
 geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  # ylim(0,250) +
  labs(x ="",
       y = "Seconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Time to First Fixation\non AOI `Disruptive Person`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  )

fix_group_plot

```

# Time to first fixations on AOI "Students"

```{r}
##################### plotting time to first fixation for 3 disruptions sum up ##################### 
df_aoi %>%
  select (Group,
          Participant,
          TOI,
          "Time_to_first_fixation.Disruptive_Person") %>% 
  mutate(Group = as_factor(Group)) -> toi_fix

toi_fix$TOI[toi_fix$TOI == "Chatting_with_neighbour" |
              toi_fix$TOI == "Heckling" |
              toi_fix$TOI == "Whispering"] <- "Verbal disruption"

toi_fix$TOI[toi_fix$TOI == "Head_on_table" |
              toi_fix$TOI == "Looking_at_phone" |
              toi_fix$TOI == "Drawing"] <- "Lack of eagerness"

toi_fix$TOI[toi_fix$TOI == "Clicking_pen" |
              toi_fix$TOI == "Drumming_with_hands" |
              toi_fix$TOI == "Snipping_with_fingers"] <- "Agitation"

toi_fix <-
  toi_fix %>% 
  filter(TOI == "Verbal disruption" |
         TOI == "Lack of eagerness"|
         TOI == "Agitation")

# remoce all NAs
toi_fix <- na.omit(toi_fix)

# changing milliseconds into seconds
toi_fix$`Time to first fixation in seconds`<- round(toi_fix$Time_to_first_fixation.Disruptive_Person/1000,
                                                    digits = 2)

# plotting
fix_plot_sum <-
  ggplot(data = toi_fix,
         mapping = aes(x = Group,
                       y = `Time to first fixation in seconds`)) +
 geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  labs(x ="",
       y = "Seconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Time to First Fixation\non AOI `Disruptive Person`\nfor disruption categories") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")) +
  facet_wrap(facets = vars(TOI),
             nrow = 1,
             strip.position = "bottom")

fix_plot_sum

#################### MEAN, SD, N ############

# mean ttff for groups
toi_group_mean <- df_ttff_disrup %>%
  group_by(Group) %>%
  summarise("N"=n_distinct(Participant),
            "M" = round(mean(`Time to first fixation in seconds`), 2),
            "SD" = round(sd(`Time to first fixation in seconds`), 2))

# mean ttff for disrup. categories
toi_mean <- toi_fix %>%
  group_by(Group,
           TOI) %>%
  summarise("N"=n_distinct(Participant),
            "M" = round(mean(`Time to first fixation in seconds`), 2),
            "SD" = round(sd(`Time to first fixation in seconds`), 2))

################ t-test & effect size
# TIME TO FIRST FIXATIONS 
# t-test for expertise differences
t.test(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
       y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"])

# AVERAGE DURATION OF FIXATIONS on AOI Students
# effect size for expertise differences
d_aver_stud <- CohenD(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
                      y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
                      na.rm = TRUE)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

### 2022-08-03 02_paper/02_study/paper_methods.Rmd
Update paper_methods.Rmd

@@
 
-Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson & Weinstein, 2006; Kounin, 2006).
+Managing classroom disruptions is a crucial aspect of effective classroom management [@evertson2006classroom; @kounin2006techniken].
 Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom.
-This ability is referred to as classroom professional vision (Goodwin, 1994; Sherin, 2007).
-The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (“noticing”) and applying knowledge to draw appropriate conclusions in these situations (“knowledge-based reasoning”; Seidel & Stürmer, 2014).
+This ability is referred to as classroom professional vision [@goodwin2015 professional; @sherin2007development].
+The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (“noticing”) and applying knowledge to draw appropriate conclusions in these situations [“knowledge-based reasoning”; @seidel2014modeling].
 Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students’ learning time and minimize classroom interruptions.
-According to Kounin (2006), these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring (Gold & Holodynski, 2017).
-Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017).
+According to @kounin2006techniken, these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring [@gold2017using].
+Learning to develop such classroom management skills is a demanding and complex task for student teachers [@wolff2016teacher].
 Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, “[…] whereas only a few studies have focused on the basal process of noticing, i.e.
-the recognition of possible disturbing situations” (Grub et al., 2020, p.75).
-Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner et al., 2016; Wolff et al., 2016).
+the recognition of possible disturbing situations” [@grub2020processp, p.75].
+Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions [@lachner2016makes; @wolff2016teacher].
 
@@
 Teachers have to be competent in things such as teaching, educating, evaluating or innovating.
-Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig & Rauch, 2008).
+Therefore, competencies form an important and practical contribution in current educational research and teacher education [@klieme2008concept].
 They replace the rigid canon of knowledge that defined professional qualification for generations.
 In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.).
-To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf.
-Klieme et al., 2008, p.
-4).
+To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education [cf.
+@klieme2008concept, p.
+4].
 In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.
@@
 
-The term "professional competence" is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation." (cf.
-Epstein & Hundert, 2002; cited in Kunter et al.
+The term "professional competence" is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation." [cf.
+@epstein2002defining; cited in Kunter et al.
 2013, p.
-807).
-Several studies could prove that this idea can be successfully transferred to the teaching profession (cf.
-Goodmann et al., 2008; Oster, Achtenhagen & Renold, 2006; Tannenbaum & Rosenfeld, 1994; cited in Kunter et al., 2013, p.
-807).
+807].
+Several studies could prove that this idea can be successfully transferred to the teaching profession [cf.
+Goodmann et al., 2008; @oser2006competence, Achtenhagen & Renold, 2006; Tannenbaum & Rosenfeld, 1994; cited in Kunter et al., 2013, p.
+807].
 Accordingly, a quality standard can be applied to assess the quality of a teacher.
-This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano & Pickering, 2003).
+This quality is elementary in the school context because the teacher factor most influences student learning [@marzano2003classroom].
 Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher.
-Research has shown that this component can even offset the influence of an ineffective school setting (Marzano et al., 2003).
+Research has shown that this component can even offset the influence of an ineffective school setting [@marzano2003classroom].
 This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.
@@
 This trained handling, as described above, can be summarized under the aspect of professional competence.
-It is expressed, among other things, in knowledge about classroom management (Grub, Biermann & Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
-
-Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, van den Bogert, Jarodzka & Boshuizen, 2015).
-Marzano et al.'s (2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching.
-In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015).
+It is expressed, among other things, in knowledge about classroom management [@grub2020process] and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
+
+Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction [@wolff2015keeping].
+@marzano2003classroom research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching.
+In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching [@wolff2015keeping].
 Therefore, it is often referred to as the central variable of successful teaching (Helmke & Helmke, 2015).
-Good classroom management is thus the prerequisite for learning to take place (Wolff et al., 2015).
+Good classroom management is thus the prerequisite for learning to take place [@wolff2015keeping].
 While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.
@@
 
-Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf.
-Wolff et al., 2015, p.
-71).
+Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge [cf.
+@wolff2015keeping, p.
+71].
 These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.).
@@
 It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research.
-In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise (Wolff et al., 2015).
+In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise [@wolff2015keeping].
 

### 2022-08-05 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
update paper fitbit

@@
 
-# Bind every tibble that contains "interval_complete" to a new tiblle
+# Bind every tibble that contains "interval_complete" to a new tible
 df_aoi <- 
@@
             ) %>% 
-  mutate(Group = as_factor(Group)) -> df_ttff_sum
+  mutate(Sum_time_fixation_sec = round(Sum_time_fixation/1000,
+                                         digits = 0),
+         Group = as_factor(Group)
+         ) -> df_ttff_sum
 
@@
   filter(Group == "Novice") %>% 
-  pull(Sum_time_fixation) %>% 
+  pull(Sum_time_fixation_sec) %>% 
   mean() %>% 
@@
   filter(Group == "Novice") %>% 
-  pull(Sum_time_fixation) %>% 
+  pull(Sum_time_fixation_sec) %>% 
   sd() %>% 
@@
   filter(Group == "Expert") %>% 
-  pull(Sum_time_fixation) %>% 
+  pull(Sum_time_fixation_sec) %>% 
   mean() %>% 
@@
   filter(Group == "Expert") %>% 
-  pull(Sum_time_fixation) %>% 
+  pull(Sum_time_fixation_sec) %>% 
   sd() %>% 
@@
   ggplot(mapping = aes(x = Group,
-                       y = Sum_time_fixation)) +
+                       y = Sum_time_fixation_sec)) +
   geom_boxplot(mapping = aes(fill = Group),
@@
   labs(x ="",
-       y = "Milliseconds") + 
+       y = "Seconds") + 
   scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("Time to first fixation\non all AOIs") +
+  ggtitle("Time to first fixation on all AOIs") +
   theme_cowplot() +
@@
 # t-test for expertise differences
-t.test(x = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Expert"],
-       y = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Novice"])
+t.test(x = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Expert"],
+       y = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Novice"])
 
@@
 # effect size for expertise differences
-d_time_all <- CohenD(x = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Expert"],
-                    y = df_ttff_sum$Sum_time_fixation[df_ttff_sum$Group == "Novice"],
+d_time_all <- CohenD(x = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Expert"],
+                    y = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Novice"],
                     na.rm = TRUE)
@@
 # changing milliseconds into seconds
-df_ttff_disrup$`Time to first fixation in seconds` <-
+df_ttff_disrup$Disrup_time_fixation_sec <-
   round(df_ttff_disrup$Time_to_first_fixation.Disruptive_Person / 1000,
@@
 
+# mean & SD time to first fixation "Disruptive Person"
+# novices
+mean_time_disrup_nov <- 
+  df_ttff_disrup %>%
+  filter(Group == "Novice") %>% 
+  pull(Disrup_time_fixation_sec) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_time_disrup_nov <- 
+  df_ttff_disrup %>%
+  filter(Group == "Novice") %>% 
+  pull(Disrup_time_fixation_sec) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# experts
+mean_time_disrup_exp <-
+  df_ttff_disrup %>%
+  filter(Group == "Expert") %>% 
+  pull(Disrup_time_fixation_sec) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_time_disrup_exp <- 
+  df_ttff_disrup %>%
+  filter(Group == "Expert") %>% 
+  pull(Disrup_time_fixation_sec) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
 ##################### plotting time to first fixation for groups ##################### 
-fix_group_plot <- 
+plot_time_disrup <- 
   ggplot(data = df_ttff_disrup,
          mapping = aes(x = Group,
-                       y = `Time to first fixation in seconds`)) +
+                       y = Disrup_time_fixation_sec)) +
  geom_boxplot(mapping = aes(fill = Group),
@@
 
-fix_group_plot
+plot_time_disrup
+
+# saving plot
+ggsave(plot = plot_time_disrup,
+       filename = "plots/plot_time_disrup.svg",
+       height = 8,
+       width = 8,
+       units = "in")
+
+# TIME TO FIRST FIXATIONS on all AOIs 
+# t-test for expertise differences
+t.test(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
+       y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"])
+
+# TIME TO FIRST FIXATIONS on all AOIs 
+# effect size for expertise differences
+d_time_all <- CohenD(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
+                    y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
+                    na.rm = TRUE)
 
@@
 ```{r}
-##################### plotting time to first fixation for 3 disruptions sum up ##################### 
+# filter relevant rows and columns
+
 df_aoi %>% 
+  filter(TOI == "Lesson") %>% 
   select (Group,
-          Participant,
-          TOI,
-          "Time_to_first_fixation.Disruptive_Person") %>% 
-  mutate(Group = as_factor(Group)) -> toi_fix
+          "Time_to_first_fixation.Anna",
+          "Time_to_first_fixation.Bianca",
+          "Time_to_first_fixation.Carl(a)") %>% 
+  rowwise() %>% 
+  transmute(Group = Group,
+            Stud_time_fixation = sum(c_across(starts_with("Time_to_first_fixation")
+                                                 ),
+                                         na.rm = TRUE
+                                         )
+            ) %>% 
+  mutate(Stud_time_fixation_sec = round(Stud_time_fixation/1000, 
+                                  digits = 0),
+         Group = as_factor(Group)) -> df_ttff_stud
 
-toi_fix$TOI[toi_fix$TOI == "Chatting_with_neighbour" |
-              toi_fix$TOI == "Heckling" |
-              toi_fix$TOI == "Whispering"] <- "Verbal disruption"
+# mean & SD time to first fixation "Disruptive Person"
+# novices
+mean_time_stud_nov <- 
+  df_ttff_stud %>%
+  filter(Group == "Novice") %>% 
+  pull(Stud_time_fixation_sec) %>% 
+  mean() %>% 
+  round(., digits = 0)
 
-toi_fix$TOI[toi_fix$TOI == "Head_on_table" |
-              toi_fix$TOI == "Looking_at_phone" |
-              toi_fix$TOI == "Drawing"] <- "Lack of eagerness"
+sd_time_stud_nov <- 
+  df_ttff_stud %>%
+  filter(Group == "Novice") %>% 
+  pull(Stud_time_fixation_sec) %>% 
+  sd() %>% 
+  round(., digits = 0)
 
-toi_fix$TOI[toi_fix$TOI == "Clicking_pen" |
-              toi_fix$TOI == "Drumming_with_hands" |
-              toi_fix$TOI == "Snipping_with_fingers"] <- "Agitation"
+# experts
+mean_time_stud_exp <-
+  df_ttff_stud %>%
+  filter(Group == "Expert") %>% 
+  pull(Stud_time_fixation_sec) %>% 
+  mean() %>% 
+  round(., digits = 0)
 
-toi_fix <-
-  toi_fix %>% 
-  filter(TOI == "Verbal disruption" |
-         TOI == "Lack of eagerness"|
-         TOI == "Agitation")
+sd_time_stud_exp <- 
+  df_ttff_stud %>%
+  filter(Group == "Expert") %>% 
+  pull(Stud_time_fixation_sec) %>% 
+  sd() %>% 
+  round(., digits = 0)
 
-# remoce all NAs
-toi_fix <- na.omit(toi_fix)
-
-# changing milliseconds into seconds
-toi_fix$`Time to first fixation in seconds`<- round(toi_fix$Time_to_first_fixation.Disruptive_Person/1000,
-                                                    digits = 2)
-
-# plotting
-fix_plot_sum <-
-  ggplot(data = toi_fix,
+##################### plotting time to first fixation for AOI students ##################### 
+plot_time_stud <- 
+  ggplot(data = df_ttff_stud,
          mapping = aes(x = Group,
-                       y = `Time to first fixation in seconds`)) +
+                       y = Stud_time_fixation_sec)) +
  geom_boxplot(mapping = aes(fill = Group),
@@
                                         height = 0.1)) +
+  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
+  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
+  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
+  #                                  )
+  #                  ) +
+  # ylim(0,250) +
   labs(x ="",
@@
   scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("Time to First Fixation\non AOI `Disruptive Person`\nfor disruption categories") +
+  ggtitle("Time to First Fixation\non AOI `Students`") +
   theme_cowplot() +
   theme(legend.position="none",
-        axis.text.x = element_text(size = 10),
+        axis.text.x = element_text(size = 34),
         axis.text.y = element_text(size = 18),
@@
         plot.title = element_text(size = 35, 
-                                  face = "bold")) +
-  facet_wrap(facets = vars(TOI),
-             nrow = 1,
-             strip.position = "bottom")
+                                  face = "bold")
+  )
 
-fix_plot_sum
+plot_time_stud
 
-#################### MEAN, SD, N ############
+# saving plot
+ggsave(plot = plot_time_stud,
+       filename = "plots/plot_time_stud.svg",
+       height = 8,
+       width = 8,
+       units = "in")
 
-# mean ttff for groups
-toi_group_mean <- df_ttff_disrup %>%
-  group_by(Group) %>%
-  summarise("N"=n_distinct(Participant),
-            "M" = round(mean(`Time to first fixation in seconds`), 2),
-            "SD" = round(sd(`Time to first fixation in seconds`), 2))
+# TIME TO FIRST FIXATIONS on all AOIs 
+# t-test for expertise differences
+t.test(x = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Expert"],
+       y = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Novice"])
 
-# mean ttff for disrup. categories
-toi_mean <- toi_fix %>%
-  group_by(Group,
-           TOI) %>%
-  summarise("N"=n_distinct(Participant),
-            "M" = round(mean(`Time to first fixation in seconds`), 2),
-            "SD" = round(sd(`Time to first fixation in seconds`), 2))
-
-################ t-test & effect size
-# TIME TO FIRST FIXATIONS 
-# t-test for expertise differences
-t.test(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
-       y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"])
-
-# AVERAGE DURATION OF FIXATIONS on AOI Students
+# TIME TO FIRST FIXATIONS on all AOIs 
 # effect size for expertise differences
-d_aver_stud <- CohenD(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
-                      y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+d_time_all <- CohenD(x = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Expert"],
+                    y = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Novice"],
                     na.rm = TRUE)
-
 ```

### 2022-08-05 02_paper/02_study/01_eye tracking video questionnaire paper/paper_methods.tex
update paper fitbit

--- 2022-07-04 02_paper/02_study/paper_methods.tex
@@
 
+\begin{lltable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} Item scores are summed. Women who score 3+ and men who score 4+ are at-risk}
+\end{TableNotes}
+
+\begin{longtable}{m{8cm}m{2cm}m{2cm}m{2cm}m{2cm}m{2cm}}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:reaction_codingsystem}AUDIT-C scoring table}\\
+\toprule
+ & \multicolumn{5}{c}{Score} \\
+\cmidrule(r){2-6}
+Questions & \multicolumn{1}{c}{0} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:reaction_codingsystem} continued}}\\
+\toprule
+ & \multicolumn{5}{c}{Score} \\
+\cmidrule(r){2-6}
+Questions & \multicolumn{1}{c}{0} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4}\\
+\midrule
+\endhead
+How often do you have a drink containing alcohol? & Never & Monthly or less & 2-4 times per month & 2-3 times per week & 4+ times per week\\
+How many standard drinks of alcohol do you drink on a typical day when you are drinking? & 1–2 & 3-4 & 5-6 & 7-9 & 10+\\
+How often do you have 5 or more drinks on one occasion? & Never & Less than monthly & monthly & Weekly & Daily or almost daily\\
+\bottomrule
+\addlinespace
+\insertTableNotes
+\end{longtable}
+
+\end{lltable}
+
 After developing and reviewing the coding system, the observers coordinated and the consistency of their ratings was verified.
@@
 \end{table}
+
+XXX FRANZI
 
@@
 
+XXX FRANZI
+
 \hypertarget{procedure}{%

### 2022-08-05 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update paper fitbit

---
title             : "A Walk In The Classroom - Using Fitbit Charge 4 to measure expert and novice teachers’ heart rate and step counts in a laboratory study"
shorttitle        : "Measuring novice and expert teachers' heart rate"

author: 
  - name          : "Mandy Klatt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Dittrichring 5-7, 04109 Leipzig"
    email         : "mandy.klatt@uni-leipzig.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Peer Keßler"
    affiliation   : "1"
    role:
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Gregor Kachel"
    affiliation   : "1,2"
    role:
      - "Conceptualization"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Leipzig University"
  - id            : "2"
    institution   : "Max Planck Institute for Evolutionary Anthropology"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "heart rate; photoplethysmography; wearable electronic device; expertise differences "
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2022-08-05 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
update paper fitbit

--- 2022-07-04 02_paper/02_study/paper_methods.tex
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
-  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
-  pdflang={en-EN},
-  pdfkeywords={professional vision, expertise, classroom management, mobile eye-tracking},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 {}{\PatchFailed}
-\keywords{professional vision, expertise, classroom management, mobile eye-tracking\newline\indent Word count: XXX}
+\keywords{heart rate; photoplethysmography; wearable electronic device; expertise differences \newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \usepackage{csquotes}
-\usepackage[titles]{tocloft}
-\cftpagenumbersoff{table}
-\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
-\renewcommand{\cfttabaftersnum}{.\space}
-\setlength{\cfttabindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cfttabnumwidth}{Table 10.\qquad}
 \ifLuaTeX
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={A Walk In The Classroom - Using Fitbit Charge 4 to measure expert and novice teachers' heart rate and step counts in a laboratory study},
+  pdfauthor={Mandy Klatt1, Peer Keßler1, \& Gregor Kachel1,2},
+  pdflang={en-EN},
+  pdfkeywords={heart rate; photoplethysmography; wearable electronic device; expertise differences},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
-\title{Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions}
-\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
+\title{A Walk In The Classroom - Using Fitbit Charge 4 to measure expert and novice teachers' heart rate and step counts in a laboratory study}
+\author{Mandy Klatt\textsuperscript{1}, Peer Keßler\textsuperscript{1}, \& Gregor Kachel\textsuperscript{1,2}}
 \date{}
 
-\shorttitle{Professional Vision in Micro-Teaching-Units}
+\shorttitle{Measuring novice and expert teachers' heart rate}
 
@@
 
-We received funding from QualiFond of University Leipzig.
-We have no conflicts of interest to disclose.
-This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).
+Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+Enter author note here.
+
+The authors made the following contributions.
+Mandy Klatt: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Peer Keßler: Writing - Review \& Editing, Supervision; Gregor Kachel: Supervision.
 
@@
 
+\abstract{%
+One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
+
+Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
+
+One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
+
+One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
+
+Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
+
+One or two sentences to put the results into a more \textbf{general context}.
+
+Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+}
+
 \begin{document}
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson \& Weinstein, 2006; Kounin, 2006).
-Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom.
-This ability is referred to as classroom professional vision (Goodwin, 1994; Sherin, 2007).
-The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (``noticing'') and applying knowledge to draw appropriate conclusions in these situations (``knowledge-based reasoning''; Seidel \& Stürmer, 2014).
-Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students' learning time and minimize classroom interruptions.
-According to Kounin (2006), these important classroom management strategies are called ``withitness'' and ``overlapping'' and can be summarized under the concept of monitoring (Gold \& Holodynski, 2017).
-Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017).
-Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, ``{[}\ldots{]} whereas only a few studies have focused on the basal process of noticing, i.e.~the recognition of possible disturbing situations'' (Grub et al., 2020, p.75).
-Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner et al., 2016; Wolff et al., 2016).
-
-\hypertarget{theoretical-background}{%
-\section{Theoretical background}\label{theoretical-background}}
-
-\hypertarget{professional-competence-in-teaching-profession}{%
-\subsection{Professional competence in teaching profession}\label{professional-competence-in-teaching-profession}}
-
-Competence is a common term in everyday school life.
-In most cases, it refers to the acquisition of competencies by students and how to promote them and make them effective.
-In the same way, the term competence can be applied to teachers.
-Teachers have to be competent in things such as teaching, educating, evaluating or innovating.
-Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig \& Rauch, 2008).
-They replace the rigid canon of knowledge that defined professional qualification for generations.
-In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.).
-To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf.~Klieme et al., 2008, p.~4).
-In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.
-
-In science, there is some agreement on the two opposing perspectives of competence versus empowerment.
-The former means a broad, concept, whereas empowerment refers to the different components of competence (cf.~of competence (cf.~Blömeke, Gustafsson \& Shavelson, 2015, p.5).
-These can be of a cognitive, conative, affective, or motivational nature (ibid.).
-To determining professional qualification, competence is an irreplaceable tool.
-
-Competence is learnable and can thus be improved through targeted practice (cf.~Weinert 2001; cited in Blömeke et al.~2015, p.~5).
-This is one reason, among others, why this concept is so relevant for empirical school and development research.
-Another crucial step in clarifying the concept of competence is to understand that the framework of competence recognizes the importance of everyday life situations (Blömeke et al., 2015).
-Therefore scholars argue, a definition must start from an authentic ``analysis of occupational or societal situations and must take into account the tasks and associated associated cognitive, conceptual, affective, and motivational aspects'' (Blömeke et al., 2015, p.~5).
-Through this comprehensive approach, many inconsistencies in the definition of the term can be resolved.
-The definition of competence is now no longer a question of whether it is a number of cognitive skills or a combination of cognition, conation, affect, or motivation.
-It combines ``complex intellectual characteristics together with affect-motivation, which underlies observable underlying performances'' (Blömeke et al.~2015, p.~6).
-This is best defined as a process or even continuum (see Figure 1), which consists of different levels and should be understood as a multidimensional construct with stronger and weaker Domains (ibid.).
-
-The term competence finds its place in a variety of disciplines as an assessment standard of qualifications.
-In this context, the term professional competence has become established in research, which defines competence in a specific professional field.
-Thus, based on the assumption that competence is more than mere knowledge, professional competence offers a way to make teacher success in schools tangible (Kunter et al., 2013).
-
-The term ``professional competence'' is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation.'' (cf.~Epstein \& Hundert, 2002; cited in Kunter et al.~2013, p.~807).
-Several studies could prove that this idea can be successfully transferred to the teaching profession (cf.~Goodmann et al., 2008; Oster, Achtenhagen \& Renold, 2006; Tannenbaum \& Rosenfeld, 1994; cited in Kunter et al., 2013, p.~807).
-Accordingly, a quality standard can be applied to assess the quality of a teacher.
-This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano \& Pickering, 2003).
-Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher.
-Research has shown that this component can even offset the influence of an ineffective school setting (Marzano et al., 2003).
-This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.
-
-\hypertarget{classroom-management}{%
-\subsection{Classroom Management}\label{classroom-management}}
-
-Teachers and students are in the classroom in a place that is always alive, characteristic of its heterogeneity and the interests of different groups.
-These the circumstances of a classroom are also characterized as multidimensional, simultaneous, immediate, unpredictable, public, and shared (Doyle, 2011, p.~99).
-All of these circumstances place a number of demands on teachers, which primarily involve planning and monitoring activities (ibid.).
-``Order in classrooms is not a consequence of reactions to misbehavior but a condition established and sustained by the way a teacher organizes and guides a complex system of classroom activities'' (Doyle, 1989, p.12).
-Thus, ``good'' teachers create the conditions for effective teaching through pre-planned actions and activities that they are always in control of while teaching.
-This enables them to maximize work time while keeping disruptions of any kind to a minimum to facilitate learning for all participants (Doyle, 1989).
-
-However, lessons, and specifically classroom disruptions, are unpredictable as well as multifaceted and require a high level of expertise and competence on the part of the teacher to handle.
-This trained handling, as described above, can be summarized under the aspect of professional competence.
-It is expressed, among other things, in knowledge about classroom management (Grub, Biermann \& Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
-
-Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, van den Bogert, Jarodzka \& Boshuizen, 2015).
-Marzano et al.'s (2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching.
-In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015).
-Therefore, it is often referred to as the central variable of successful teaching (Helmke \& Helmke, 2015).
-Good classroom management is thus the prerequisite for learning to take place (Wolff et al., 2015).
-While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.
-
-An initial explanatory approach to classroom management was provided by Doyle (1990, p.355) with his definition of teaching, which he described as a ``cognitive activity based on knowledge of the probable course of events in the classroom and the ways in which actions affect situations.'' From this, it is clear that in order to teach successfully, a teacher needs knowledge of how to process as well as represent the full range of classroom events.
-In addition, it is necessary to be able to respond or interact proactively and effectively to potential events at best.
-
-Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf.~Wolff et al., 2015, p.~71).
-These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.).
-If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction.
-This is crucial to maximize students' active learning time (Helmke \& Helmke, 2015).
-It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research.
-In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise (Wolff et al., 2015).
-
-\hypertarget{interdependence-of-classroom-management}{%
-\subsubsection{Interdependence of classroom management}\label{interdependence-of-classroom-management}}
-
-In research, various models exist for approaching the concept of classroom management.
-However, they are very similar in their core statements.
-Therefore, it is merely a matter of preference which concept is consulted to explain connections and terms.
-In the following, the network of effects of classroom management according to Helmke (2014) is used as a reference model in order to be able to understand the embedding of the concept accordingly.
-
-As was made clear in the definition, classroom management is a complex construct that attempts to accommodate the various modes and challenging characteristics of a classroom.
-Helmke (2014) therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time.
-This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (\emph{d} = 0.39; Hattie, 2013, p.219).
-Due to this diversity of aspects to be investigated, classroom management is a fundamental research topic.
-
-The concepts, strategies and techniques used to implement successful classroom management depend first and foremost on various teacher characteristics and are ``interrelated with the quality of teaching and personal relationships'' (Helmke \& Helmke, 2015, p.5).
-It should not be forgotten that this space never functions in isolation and independently of other influences.
-It is embedded in diverse contexts, especially in the school and class context (Helmke \& Helmke, 2015).
-But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led (Helmke, 2014).
-
-Classroom management itself is made up of various components which, according to Helmke (2014), can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior.
-Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke \& Helmke, 2015).
-
-The importance of rules in the classroom has been known and researched for some time.
-Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules (cf.~Emmer, Evertson \& Anderson, 1980; Emmer, Sanford, Clements \& Martin, 1982; cited in Doyle, 1989, p.~15).
-Although he also stresses that establishing a system of rules is a difficult task.
-Classroom rules are situation-dependent, as certain agreements only apply to certain phases of the lesson (for example, speaking quietly during group work; Doyle, 1989).
-Furthermore, order is always established jointly, in cooperation with the learners (Doyle, 1989).
-
-As a result, students significantly influence these rules by their willingness to follow them.
-Procedures are another tool to maintain the flow of the lesson, as recurring routines provide learners with security and clarity (Helmke \& Helmke, 2015).
-This inevitably reduces the teacher's workload, eliminates additional explanations are no longer necessary, and it is clear to the learners at all times what needs to be done.
-needs to be done.
-In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time (Helmke, 2014).
-For the reasons just reasons just explained, it is clear why Hattie (2013, p.~122) gives this component of classroom classroom management an effect size of \emph{d} = 0.76.
-
-No other aspect of classroom management is as effective for classroom interruptions as the teacher's omnipresence (Hattie, 2013, p.~122); the effect size is \emph{d} = 1.42.
-(Helmke \& Helmke, 2015, p.~6).
-The behavioral pattern of presence is not a new concept.
-It was already recorded by Kounin in 1970 under the term \emph{withitness}.
-Later research confirmed and validated his assumptions and definition of the term (cf.~Helmke, 2014, p.10).
-In order to be present, the teacher must be able to control the classroom adequately and superficially effectively at all times.
-This means she must be able to recognize relevant cues or situations that require possible action (Wolff et al., 2015).
-Presence can consequently be illustrated very vividly by means of the image of ``eyes in the back of the head'' (Kounin, 2006).
-In addition to presence, Kounin (2006) uses the term overlap.
-It is a kind of multitasking ability to be able to cope with parallel processes and situations in the classroom.
-The two dimensions of overlap and presence can also be summarized together under the term monitoring (Gold \& Holodynski, 2017).
-When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners (Grub et al., 2020.).
-Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness.
-and increases general awareness of relevant events in the classroom (ibid.). From this point of view, it becomes clear why awareness is a core component of teacher competence.
-
-As a third component influencing the quality of classroom management, cites Helmke (2014) time use and management.
-This seems trivial at first, considering that classroom management serves the goal of maximizing learning time anyway.
-However, Helmke \& Helmke (2015, p.~6) emphasize how elementary it is to identify and minimize possible ``time thieves''.
-This includes factors such as unpunctuality or slow transitions, as well as the underemployment of learners (ibid.).
-If these take up too much space in the classroom, less time is available for teaching important lesson content.
-This can be prevented by teachers minimizing such ``time thieves'' in advance through well-planned classroom management.
-
-In order to enforce desired student behavior or to reduce contradictory behavior, teachers can use various discipline-related interventions and also make use of negative sanctions and positive reinforcement (Helmke \& Helmke, 2015).
-The authors emphasize that a healthy balance must be found when using these strategies.
-Over the years, this constructive approach has fallen into disrepute due to its behaviorist character.
-However, elements such as reinforcement, extinction or punishment are not negligible laws of learning psychology whose effectiveness has been proven by Hattie (2013), among others.
-These behavioral psychological measures have an effect size of \emph{d} = 0.76 (cf.~Hattie, 2013, p.215) and are therefore an effective means of reducing disruptions (Helmke \& Helmke, 2015).
-
-Researchers in pedagogy also point out, however, that it is not only pure knowledge about classroom management that determines its effectiveness and influences it (Helmke \& Helmke, 2015).
-The teacher personality, which includes characteristics such as subjective tolerance margins, i.e.~at what point does one perceive a certain behavior as disruptive, also plays a role.
-This includes further aspects such as emotion control, empathy or the credibility of a teaching person that arises through appearance.
-These characteristics, which occur in many ways, have a direct impact on the quality of teaching and classroom management, as they influence the planning behavior, perception and reaction of teachers.
-
-\hypertarget{professional-vision}{%
-\subsection{Professional vision}\label{professional-vision}}
-
-Competence assessment plays a central role in the teaching profession and its training.
-It follows the approach of concentrating on action-relevant as well as lesson-related content in order to train corresponding competences for teaching practice (KMK, 2004).
-In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes (Barth, 2017).
-Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel \& Prenzel 2014).
-The concept of professional vision can originally be traced back to the anthropologist Charles Goodwin and became known under the term Professional Vision (Sherin, 2001).
-It provided the answer to Goodwin's question regarding the development of a professional vision, in the context of the profession, compared to the vision of everyday situations.
-Goodwin uses the comparison of an archaeologist and a layperson to figuratively describe the differences.
-In doing so, he investigated which ability it is that makes the archaeologist see and interpret a landscape differently than the layperson (cf.~Sherin, 2001, p.~75).
-What looks to the former merely like sand, rocks and stones, is to the trained eye of the archaeologist a base of a column or architectural fragments.
-Goodwin (1994, p.606) defines professional vision as ``socially organized ways of seeing and understanding events that are answerable to the distinctive interests of a particular social group'' (cited in Sherin, 2001, p.~75).
-It is assumed that one can see certain phenomena or occurring events in a certain way due to one's professional affiliation (Sherin, 2001).
-Particularities are more easily recognized because the gaze becomes more trained over time and thus profession-relevant features appear more distinctive.
-In the previous example of the archaeologist, this would mean that he noticed variations in color, texture and sand and saw a cluster of stones as a possible element of a larger structure (cf.~Sherin, 2001, p.75).
-This distinguishes experts significantly in their visions from non-experts in the field, as they had learned to filter their environment for crucial features.
-
-\hypertarget{teachers-professional-vision}{%
-\subsubsection{Teachers' professional vision}\label{teachers-professional-vision}}
-
-Based on the assumption that the professional vision can develop over time, Sherin (2001) postulates that teachers can also acquire a professional vision.
-As teachers develop from novices to experts in their field, they accumulate expertise in a variety of areas (cf.~Sherin, 2001, p.~76).
-This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom (Berliner, 1994; Leinhardt \& Greeno, 1986).
-This type of action can be described as a skill that helps teachers make decisions about what is relevant and what is not within the complex classroom setting (van Es \& Sherin, 2002).
-Such decisions are based on professional knowledge that guarantees effective teaching and learning in actual classroom situations (Jahn et al., 2014).
-Professional awareness is therefore referred to as an indicator of how knowledge is represented in teachers (Stürmer et al., 2017).
-It can also be seen as a bridge or link between knowledge and action, or professional competence and behavior (Grub et al., 2020).
-It is important to understand that professional vision is acquired and not inherent.
-Rather, it is subject to a process of acquisition that is constantly progressing as teachers are exposed to events and learn to interpret them (Wolff et al., 2016).
-Fundamentally, then, prospective teachers must select what to focus their attention on in the classroom and how to understand these events (Stürmer et al., 2017).
-Finally, teaching and learning take place in a complex environment.
-Simultaneous events and situations cannot be given the same attention.
-``Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects'' (Barth, 2017, p.19).
-Furthermore, teachers benefit from from a trained perception of problems, as this is a significant factor in being able to preventively counteract preventive measures (Wettstein, 2013).
-
-Basically, the complex process of professional vision is divided into three sub-processes (Grub et al., 20202).
-First of all, the identification, the recognition, of an event takes place.
-Then connections are made, which are finally evaluated by the teacher using his or her professional knowledge.
-In research, these processes are often combined and one speaks of noticing to describe recognition (Grub et al., 2020).
-Knowledge-based reasoning includes the last two processes of applying knowledge to make appropriate decisions (ibid.).
-During this process, it becomes clear that the recognition of relevant situations, such as disruptions, precedes all others.
-This process is therefore considered necessary, without which professional vision cannot take place (Grub et al., 2020).
-As described in the chapter on competence, perceptions is also of particular importance in the competence model according to Blömeke et al.~(2015).
-This is because the process of perception forms an essential basis for situation-specific skills of teachers (Grub et al., 2020).
-Inferentially, recognition is inevitable for the perception of classroom events and therefore highly relevant for effective classroom management (ibid.).
-
-Even though the recognition of relevant situations in the classroom is the starting point for all further subsequent actions, the processes of knowledge-based reasoning within professional vision are not to be neglected.
-It is also said that this process is an indicator of the quality of how knowledge is applied to a given situation (Grub et al., 2020), as teachers need to make knowledge-based inferences.
-Qualitative research on knowledge-based reasoning concluded that it can be subdivided into three further sub-processes.
-Sherin (2007; cited in Barth, 2017, p.~20) made a first subdivision, which consists of the processes of describing, evaluating and interpreting.
-When a teacher describes what she notices, she concentrates on observable characteristics, i.e.~important aspects of teaching (ibid.).
-When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event (cf.~Barth, 2017, p.~19).
-Seidel et al.~(2010), on the other hand, focus on German-speaking countries in their research on professional vision and modified Sherin's original concept.
-They also divide knowledge-based-reasoning into three levels, but these differ: describing, explaining and predicting (Barth, 2017).
-More precisely, these processes encompass the ability to differentially describe instructional components that have an impact on learning; to make theoretically sound explanations about instructional situations; and to predict the effects of these events in relation to the teaching-learning process (cf.~Seidel et al., 2010, p.~297).
-This scientific work examines only the processes of noticing, which is why these two approaches have been presented for the sake of completeness.
-However, it is not useful to specify which classification of knowledge-based reasoning is referred to in arguments.
-is referred to in argumentation.
-
-Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect (Sherin, 2007; cited in Barth, 2017, p.~19).
-What is considered and perceived as relevant in a teacher's selective vision (noticing) functions as the basis of the subsequent processes of describing, evaluating, and interpreting (knowledge-based-reasoning).
-Conversely, by engaging with these processes, the teacher's perception is sensitized.
-This leads to the fact that in the future certain characteristics of this situation can be recognized rather.
-
-\hypertarget{measuring-professional-vision-eye-tracking-technology-in-research}{%
-\subsection{Measuring professional vision: eye-tracking technology in research}\label{measuring-professional-vision-eye-tracking-technology-in-research}}
-
-Professional vision of teachers is a complex undertaking, consisting of various cognitive and visual processes.
-In the previous chapter, the importance of perception and its associated visuality was emphasized, which places the eye at the center of investigations.
-In research, process-based methods are used to make these perceptual processes visible.
-In this context, eye-tracking (ET), a modern method of recording gaze, has proven to be an effective tool in research.
-It allows us to literally see through the eyes of recipients and provides insight into another perspective.
-Intrinsic human cognitive processes are often compared to a black box in science, as these activities are not directly measurable (Rakoczi, 2012).
-Until now, cognitive processes could only be studied by verbalizing the respective subjects.
-However, this method is highly susceptible to interference due to its incomplete accessibility (Dessus, 2016).
-The increasingly popular research method of eye-tracking technology therefore represents an innovative means of externalizing, i.e., making visible, internalized processes by means of eye movements (Gegenfurtner et al., 2018).
-Stimuli in the environment are always perceived by our eyes as the first receiver.
-They take in the information and pass it on to our brain so that it can finally be processed there.
-By measuring this complex process, eye movements can be recorded and subsequently analyzed (Rakoczi, 2012).
-Information is obtained about the visual behavior, attentional focus, selection decisions, and even learning processes of the investigator (ibid).
-In addition to these qualitative results, which provide information about underlying cognitive processes, quantitative data can also be collected through eye-tracking (Cullipher, 2018).
-These provide information, for example, about how long and in what order stimuli are looked at, or whether certain parts are looked at more often than others (ibid.).
-This enables research to make data objectively assessable.
-
-Eye-tracking technology can be roughly divided into two types of devices: Stationary and mobile systems (Blake, 2013).
-In research so far, mainly eye-tracking devices have been used, which phenotypically resemble a computer (ibid.).
-They are also referred to as remote devices and, once calibrated, measure eye movements in a non-contact manner using infrared light (Gegenfurtner et al., 2018).
-However, this technique reaches its limits when it comes to collecting data in everyday situations.
-For this purpose, the more flexible variant, mobile eye tracking (MET) or head-mounted or wearable eye trackers, can be used.
-Typically, the technology is found as a head-mounted device on helmets or integrated into an eyeglass frame (Blake, 2013).
-The difference with stationary tracking is that in addition to an eye camera and infrared light source, additional cameras are built in to capture head movements (ibid.).
-These are intended to help document the subject's field of view.
-Therefore, such systems are particularly suitable for applied sciences, as is the case in empirical school and development research (Gegenfurtner et al., 2018).
-
-Eye-tracking research is based on several fundamental assumptions.
-The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date (cf.~Blake, 2018, p.380).
-In this regard, Hoffmann and Subramaniam (1995) obtained the finding that when the eyes are focused on an object, this is associated with an attentional focus of the person.
-Based on these findings, ET technology is based on the following two assumptions: The immediacy assumption and the eye-mind assumption (cf.~Rakoczi, 2012, p.87).
-The former defines that cognitive evaluation processes begin immediately upon fixation on an object (Cullipher, 2018).
-If a new stimulus attracts attention and is fixated, the observer starts processing this new information (ibid.).
-The eye-mind hypothesis assumes that whatever is fixated by the eye, is subsequently processed by the mind (ibid.).
-It thereby expansively defines, that objects are visually focused only until they are cognitively evaluated or until there is have been cognitively evaluated or there is still an interest (cf.~Rakoczi, 2012, p.87).
-However, a situational context must exist for the assumptions just explained to be are valid (ibid.).
-Through these functions, it becomes clear that the intrinsic processes of recognition in professional vision can be measured by eye-tracking technology.
-
-Despite the externalization of internalized processes and the resulting multitude of data potentially to be collected, ET technology cannot provide answers about the exact thoughts during stimulus processing.
-ET can identify where and when people are looking, but it does not answer why.
-For this, it is helpful to triangulate the data and apply alternative elicitation (Cullipher, 2018).
-One proven method is to conduct reflective interviews, which can be conducted in the format of a think aloud protocol (Konrad, 2020).
-This thinking aloud opens up the possibility of gaining insights into subjects' thinking, feeling, and intentions (edb.).
-An elaborated form of the Think Aloud Protocol is a Stimulated-Recall Interview (SRI).
-This is a qualitative scientific method to obtain data on preactional thought processes (cf.~Messmer, 2015, p.4).
-The pre-recorded lesson sequences are played back and subjects have the opportunity to express themselves about their ``thoughts, beliefs, norms, and decisions'' (Messmer, 2015, p.4) during the interview process.
-Thus, the visual data of the ET can be matched with cognitive processes and processes of knowledge-based-reasoning can be better understood.
-Individual-dependent thinking is now no longer pure speculation and can be made objectively observable in a way (Messmer, 2015).
-Subjects also have the opportunity to explain their actions and become aware of the basis for their decisions (ibid.).
-
-\hypertarget{parameters-and-indicators-of-teachers-professional-vision}{%
-\subsubsection{Parameters and indicators of teachers' professional vision}\label{parameters-and-indicators-of-teachers-professional-vision}}
-
-In university education, there is an increasing focus on developing the professional vision of future teachers (Stürmer et al., 2017).
-In order to determine the professional vision of teachers by means of mobile eye-tracking (MET), different indicators are worth considering.
-This scientific work focuses primarily on processes of noticing, i.e., the identification of relevant teaching situations as well as perception time.
-Therefore, in the following we will focus more on the parameters and indicators necessary for these processes.
-
-In MET, collected data sets are usually output according to different parameters: Fixations and Saccades (Gegenfurtner et al., 2018).
-The latter describes gaze jumps, i.e., movements of both eyes, which are useful to capture new fixations (Eye-Tracking Kompetenzzentrum Schweiz, 2021).
-Significant for this scientific work and the analysis of professional vision are the fixations as well as subjects' areas of interests.
-Fixations describe the period of time in which no movements are emitted by the eye (Holmquist et al.~2011) and are based on the eye-mind hypothesis described in the previous chapter.
-A fixation of an object can be characterized according to its duration, frequency, and distribution.
-In the illustration, the radius of a circle defines the duration of a fixation (Gegenfurtner et al., 2018).
-These data can also be used to describe perception times, such as the time until the first fixation on a particular object.
-In order to make this time period objectively measurable make it objectively measurable, a concept developed by Tobii Pro Lab Analyzer Software is used.
-In this software these organized recorded data are called Time of Interests (short TOIs), which describe time intervals of corresponding events or behaviors (Tobii Pro, 2021).
-Specifically, they are defined by the beginning and end of the corresponding event.
-
-By means of eye movement measurement, attention allocations to areas of interest or objects are made accessible in addition to pure fixations (Gegenfurtner et al., 2018).
-In research, these regions in the field of view of subjects are referred to as areas of interest (AOI) (edb.).
-They are significant in that, for the measurement of perceptual velocities of a relevant instructional event, not only TOIs but also the locations of fixations are crucial.
-Thus, it can be determined how subjects distribute their attentional resources and whether they recognize and perceive relevant events.
-
-\hypertarget{expertise-differences-in-professional-vision}{%
-\subsubsection{Expertise differences in professional vision}\label{expertise-differences-in-professional-vision}}
-
-Since it is assumed that professional vision is a preferably knowledge-based process, differences between experienced and inexperienced teachers have already been identified.
-These differences were in favor of experts, since a connection between teaching experience and the associated increase in knowledge acquisition is assumed (Grub et al., 2020).
-Student teachers do not have well-structured experiential knowledge due to their almost non-existent practice in everyday school life (Wolff et al., 2016).
-This causes them selection difficulties in perception and is called pedagogical knowledge gap (cf.~Wolff et al., 2016, p.260).
-Through newly gained experiences, the professional vision of a teacher is continuously restructured and updated, and mental representation is constantly realigned accordingly (ibid.).
-This has been proven in research as a positive correlation of input to teaching and learning theories in studies and professional classroom perception has been found (Stürmer et al., 2012).
-Therefore, it can be assumed that there is a relationship between teacher expertise, their visual processing, and mindfulness for classroom management (Wolff et al., 2016).
-Research has also shown that declarative knowledge acquisition, i.e., acquisition of factual knowledge, supports perceptual processes (Seidel et al., 2012; cited in Treisch, 2018, p.26).
-Accordingly, this increased knowledge acquisition would explain a positive impact on professional teaching perception.
-Among the most important prerequisites for this acquisition, Baumert and Kunter (2006) include prior knowledge and interest.
-The former is elementary for new knowledge acquisition about effective teaching and learning, as it supports processing, integration, and consolidation of it (Stürmer, 2011).
-Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions (cf.~Sabers, 1991; cited in Treisch, 2018).
-This is explained by increased filtering mechanisms that support perceptual processes, i.e., recognition.
-Specifically, it has been shown that experienced teachers have more fixations on relevant areas because they have already learned theories on how to detect potential clutter in the classroom (Grub et al., 2020.).
-Furthermore, experts have an advantage when it comes to coding information.
-Novices, on average, have a longer viewing times, so-called fixation durations, which is due to their still weakly developed expert knowledge (ibid.).
-
-\hypertarget{mobile-eye-tracking-in-teaching-learning-situations}{%
-\subsubsection{Mobile eye tracking in teaching-learning situations}\label{mobile-eye-tracking-in-teaching-learning-situations}}
-
-As explained in detail earlier, teachers face a number of challenges during teaching.
-The teacher as organizer has to permanently scan the classroom for potential interruptions or possible events occurring such as classroom disruptions.
-In the worst case, they force a standstill in the flow of instruction, which is naturally to be avoided.
-Lohmann (2015, p.13) describes classroom disruptions as ``events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place.'' However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive (cf.~Eckstein, Grob \& Reusser, 2016; cited in, Eckstein, 2018, p.11).
-Thus, instructional disruptions are strongly dependent on perception and involve elements of production as well as reception (ibid.).
-These discipline conflicts can be divided into four categories of disruptive student behavior: Verbal disruptive behavior (chattering, heckling), lack of eagerness to learn (mental absence in the form of drawing or playing on the cell phone), physical disruptions (snapping, drumming, pen clicking), and aggressive behavior (temper tantrums, attacking people; Lohmann, 2015).
-
-In order to be able to recognize inappropriate behavior in a timely manner, the teacher must have a pronounced omnipresence, as well as pedagogical-psychological knowledge about teaching and learning processes (Cortina et al., 2018).
-These skills and competencies are reflected in how teaching situations relevant to learning are perceived and interpreted by teachers (ibid.).
-In this context, a multitude of visual attention processes occur during classroom activities.
-This simply means the attention or the conscious non-attention to visual stimuli (Rüth et al., 2020).
-This situational awareness of a teacher and the accompanying control of his or her visual attention forms the foundation of situation-specific skills (cf.~Rüth et al.~2020).
-These data and insights potentially to be collected form an interesting field of research and useful tool for problem-based teaching education (Cortina et al., 2018).
-
-In the last decade, visual input through recorded teaching situations has been preferred (ibid.).
-Subjects are thus shown an outside perspective from different points of view.
-This can happen either as self or external video and allows micro-analysis or interaction sequences through the characteristic of repeated playing of a video (ibid.).
-This characteristic makes it possible to analyze corresponding scenes more intensively and in more detail.
-This results in a potential for reflection on teaching situations in teacher education that should not be underestimated (cf.~Rüth et al., 2020).
-The problem with these videotaped sequences, however, is the lack of access to the first-person perspective (ibid.).
-As a result, students usually evaluate and comment on their own videos more negatively than those of others afterwards (Cortina et al., 2018).
-They find it difficult to analyze the sequences objectively and to leave out unimportant details that concern their person.
-However, this is not purposeful and conducive to the intended learning process of the participating teachers.
-This is due to the fact that self-drawn cognition is activated in self-videos and that when negative events occur, subjects tend to defend their actions (ibid.).
-Kleinknecht and Schneider (2013) analyzed this process in more detail and found that this is particularly problematic for the reflective learning process, as it has a counterproductive effect on analyzing possible alternative actions.
-They also found that in third-party videos, reflection on potential alternative actions was twice as frequent as in self-recorded videos (ibid.)!
-In addition, recorded video sequences differ significantly from real classroom settings in which the teacher can independently determine her field of view.
-The observers cannot decide for themselves what to pay attention to and for how long to pay attention to a situation or event (Sherin, 2001).
-Based on this finding, it was significant for researchers to use an alternative elicitation technique to factor out the negative effects of self and other videos.
-
-A successful method to reduce this hindering factor of self-drawn cognition and still use self videos for teacher education is to use recordings that show the teacher's perspective and furthermore make it known where the teacher was looking (cf.~Cortina et al., 2018).
-In MET's video material, teachers can never see their teaching through their own eyes.
-This makes it possible to focus more specifically on essential aspects, such as classroom disruptions and interactions with learners.
-Although it has not yet been clearly demonstrated that significantly less self-referential cognition was elicited, self-videos counteract over-focusing on the acting person (cf.~Cortina et al., 2018).
-Therefore, MET represents a target-rich method for capturing teachers' attentional processes in the classroom.
-Previous studies with large data sets on teachers' visual expertise have predominantly used stationary ET (Wolff et al., 2016).
-In MET studies, the samples turn out to be much smaller; here, the largest study to be mentioned is with 12 experienced and 12 inexperienced teachers by Cortina et al.~(2015).
-
-\hypertarget{perceptions-of-classroom-disruptions-and-their-parameters}{%
-\subsubsection{Perceptions of classroom disruptions and their parameters}\label{perceptions-of-classroom-disruptions-and-their-parameters}}
-
-The attentional processes of teachers in the classroom that can be captured by MET are complex, as already explained, and are related to various parameters.
-Individual personality characteristics play a central role when it comes to the perception of relevant classroom events.
-In general, it should be noted that novices have greater problems in classroom management as well as in dealing with difficult student behavior (Barth, 2017).
-Often, this is due to their late or even lack of awareness of classroom disruptions.
-However, their lack of expertise is not the sole reason for this phenomenon.
-Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher (Baumert \& Kunter, 2006).
-Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors.
-Individual person characteristics as well as contextual factors not only have an effect on teaching perception, but likewise on the sense of disturbance of a situation (Eckstein, 2019).
-These specific characteristics include aspects such as self-image, motivation, level of aspiration, attitudes, coping goals, and value orientations (Bakker \& Demerouti, 2006; cited in Wickeren, 2019, p.~33).
-Contextual characteristics include didactic staging or general level of disruption.
-Undesirable behavior is perceived more strongly by teachers when the class usually displays disciplined and orderly behavior (Eckstein, 2018).
-This reference group effect is also known as the Big-Fish-Little-Pond effect.
-Thus, it can be said that teachers' perceptions of situations and people are significantly shaped by their expectations and biases is shaped (cf.~Eckstein, 2018).
-How strongly a disturbance is perceived and felt can also depend on psychological characteristics such as self-efficacy beliefs (ibid.
-(ibid.).
-With decreasing self-efficacy, an increasing sense of disturbance was found (ibid.).
-
-The teacher-student relationship aspect, which includes recognizing student needs, must also be considered.
-In order to be able to adequately counteract classroom disruptions and thus automatically reduce the sense of disruption and the experience of stress, it is important to address the concerns of the learners with empathy (Wickeren, 2019).
-Regarding gender as a factor, it should be noted that previous research has found higher levels of disruptiveness in discipline problems among female teachers (Kovess-Masféty, Rios-Seidel \& Sevilla-Dedieu, 2007; cited in Wickeren, 2019, p.~33).
-In summary can thus be summarized that the extent and perception of disturbances are based on individual cognitive evaluation processes, the situational context, attentional focus, didactic staging, and, indeed, professional experience (cf.~Wickeren, 2019).
-
-\hypertarget{research-questions-and-hypothesis}{%
-\section{Research Questions and hypothesis}\label{research-questions-and-hypothesis}}
-
-This study examined how the degree of teaching experience of novice and expert teachers influences (1) the number of fixations on relevant areas, (2) the fixation duration on relevant areas and (3) the time to first fixation on relevant events (e.g., the student performing the disruption), using mobile eye-tracking data in a controlled, micro-teaching setting.
-Furthermore, the study examined the individual evaluation of classroom disruptions among experts and novices by assessing (4) how disruptive an event was and (5) how confident the subjects felt dealing with the events.
-In addition, subjects' (6) strategic knowledge of classroom management was assessed.
-
-Based on the existing literature, we expected expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation duration and (H3) perceiving classroom disruptions faster (cf.
-Van den Bogert, Bruggen, Kostons, and Jochems (2014)), (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions (Barth, 2017), and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
-
-\hypertarget{materials-and-methods}{%
-\section{Materials and Methods}\label{materials-and-methods}}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-
-This study had a quasi-experimental study design, as there was no random assignment of the subjects to experimental conditions.
-Due to the use of mobile eye-tracking technology, the study had a high external validity (Gegenfurtner et al., 2018).
-Internal validity could be ensured to the extent that the disruptive events that occurred were exactly the same for all subjects, as the actors received precise behavioral instructions.
-These disruptions followed a script and coding scheme in which the actions of the class were precisely described.
-The order of the disruptions as well as the performing actors were fully balanced with Latin Square to exclude row effects.
-
-The scripted behavioral instructions during the micro-teaching unit characterized the study with a high degree of standardization, especially when compared to events taking place in a real classroom.
-The study was based on an experimental manual, script and coding, which explicitly described the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable.
 
@@
 
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:demographicstable}Demographic Information}
-
-\tiny{
-
-\begin{tabular}{lllllll}
-\toprule
-Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years}\\
-\midrule
-Expert & 19 & 57.89 & 41.68 & 10.41 & 27.00 & 59.00\\
-Novice & 26 & 65.38 & 23.38 & 1.72 & 20.00 & 27.00\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:demographicstable}Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent}
-
-\tiny{
-
-\begin{tabular}{llllllllllllllll}
-\toprule
-Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
-\midrule
-Expert & 19 & 13.84 & 12.30 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 47.00\\
-Novice & 26 & 0.00 & 0.00 & 0.00 & 0.00 & 7.15 & 2.62 & 3.00 & 11.00 & 10.92 & 8.09 & 0.00 & 36.00 & 88.46 & NA\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-The sample consisted of \emph{N} = 45 participants with \emph{n} = 19 expert teachers and \emph{n} = 26 novice teachers.
-
-The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
-According to Palmer, Stough, Burdenski, and Gonzales (2005), we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
-Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
-
-The expert teachers (11 women; 57.89\%) had a mean age of 41.70 years (\emph{SD} = 10.40; range: 27-59) and an average teaching experience of 13.80 years (\emph{SD} = 12.30; range: 3-37).
-15.79\% of the experts were primary school teachers and 84.21\% were secondary school teachers.
-47\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
-
-The novice teachers (17 women; 65.38\%) had a mean age of 23.40 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years.
-On average, the student teachers were in their 7.20 semester (\emph{SD} = 2.60; range: 3-11).
-Furthermore, they had an average teaching experience of 10.90 teaching units à 45min (\emph{SD} = 8.10; range: 0-36) through the internships during their studies.
-19.23\% of the novices were studying to become primary school teachers, 65.38\% to become secondary school teachers and 15.38\% to become special education teachers.
-88.46\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
-
-The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at the University Leipzig.
-All study procedures were carried out in accordance with the ethical standards of the University's Institutional Review Board.
-The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
-All participants were informed in detail about the aim and intention of the study prior to testing.
-Participation in the study was voluntary and only took place after written consent has been given.
-
-\hypertarget{section}{%
-\subsection{}\label{section}}
-
-\hypertarget{variables}{%
-\subsection{Variables}\label{variables}}
-
-All stimuli are freely available in the following online repository: \url{https://github.com/}\ldots{} .
-
-\hypertarget{eye-tracking-data}{%
-\subsubsection{Eye-Tracking data}\label{eye-tracking-data}}
-
-To record eye-tracking data, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker during the micro-teaching-unit.
-The system consisted of a wearable head unit and a recording unit.
-As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors.
-A high-definition scene camera captured a full HD video of the teacher's field of vision.
-An integrated microphone recorded the surrounding sounds.
-Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \ref{fig:teachersgaze}.
-The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera had a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).
-
-\begin{figure}
-
-{\centering \includegraphics[width=14.07in]{./pictures/tobiiglasses2}
-
-}
-
-\caption{Tobii Pro Glasses 2; Source: https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}\label{fig:tobiiglasses2}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics{./pictures/teachersgaze}
-
-}
-
-\caption{Teacher's Gaze Point}\label{fig:teachersgaze}
-\end{figure}
-
-\hypertarget{video-data}{%
-\subsubsection{Video data}\label{video-data}}
-
-The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \ref{fig:setup}.
-The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
-
-Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \ref{fig:setup}.
-The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
-
-\hypertarget{questionnaire-data}{%
-\subsubsection{Questionnaire data}\label{questionnaire-data}}
-
-After each micro-teaching-unit, the three actors answered items on teaching quality using a validated questionnaire (Helmke et al., 2014) and self developed scales on the teacher's presence behavior derived from the research literature.
-In addition, subjects were asked to give a self-assessment on classroom management by completing the same questionnaire after each micro-teaching-unit.
-The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:presence_questionnaire_novices}Scale analysis for novices' self-assessment}
-
-\tiny{
-
-\begin{tabular}{lllllllll}
-\toprule
- & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
-\midrule
-Classroom Management & 8.00 & 2.93 & 0.26 & 2.50 & 3.38 & 0.24 & 1.77 & 0.37\\
-Balance & 3.00 & 3.17 & 0.56 & 1.67 & 4.00 & -0.36 & 3.23 & 0.63\\
-Presence & 8.00 & 3.10 & 0.34 & 2.50 & 3.88 & 0.05 & 2.64 & 0.65\\
-Natural Behavior & 3.00 & 3.14 & 0.60 & 1.67 & 4.00 & -0.49 & 2.94 & 0.78\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:presence_questionnaire_experts}Scale analysis for experts' self-assessment}
-
-\tiny{
-
-\begin{tabular}{lllllllll}
-\toprule
- & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
-\midrule
-Classroom Management & 8.00 & 3.18 & 0.37 & 2.38 & 3.88 & 0.00 & 2.74 & 0.65\\
-Balance & 3.00 & 3.30 & 0.57 & 2.00 & 4.00 & -0.74 & 2.79 & 0.76\\
-Presence & 8.00 & 3.36 & 0.37 & 2.50 & 3.88 & -0.61 & 2.76 & 0.76\\
-Natural Behavior & 3.00 & 3.44 & 0.45 & 2.67 & 4.00 & -0.17 & 1.98 & 0.60\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{rating-scales}{%
-\paragraph{Rating scales}\label{rating-scales}}
-
-Two self-developed 11-point rating scales were used to record how disruptive the individual disruptions were perceived by the subjects and how confident they felt in dealing with the disruptions.
-Data for rating scales were collected during the Stimulted Recall Interview, where the experimenter watched the pre-recorded eye-tracking video with the subject.
-
-The questionnaire included nine questions for each scripted disruptive event. The subjects did not have to complete the questionnaire themselves at any time, as this was done by the experimenter.
-
-For the present study, the following two questions from the interview were relevant:
-1. ``How disturbing did you perceive this event to be?''
-2. ``How confident did you feel in dealing with this event?''
-
-Both questions were answered using a scale ranging from 0 to 10. On this scale, 0 stood for ``not at all disruptive'' or ``not at all safe'' and 10 for ``extremely disturbing'' or ``extremely safe.''
-
-With these rating scales, the subjects indicated their personal subjective feeling towards the individual lesson disruption.
-Rating scales usually consist of a number of clearly arranged categories that can be presented visually in a variety of ways (Albers, Klapper, Konradt, Walter, \& Wolf, 2009, p.
-67f).
-In the present questionnaire, the numerical representation with eleven answer options (0-10) was used.
-There was no specific designated neutral position.
-In this questionnaire, the middle category 5 was not interpreted as a neutral position.
-In order to avoid misinterpretations of the scaling, the questionnaire was described verbally by the experimenter and follow-up questions from the test subjects were possible at any time.
-With regard to the quality criteria, it should be made clear that complete objectivity in answering the two questions is given by the rating scales.
-The question remained the same for all subjects and no additional comments were made.
-Validity can also be assumed for the questionnaire, since the subjects couls ask follow-up questions and thus uncertainties were clarified.
-However, similar to the video data, there was no perfect reliability with this survey instrument, because in a few exceptional cases, for example, the experimenter forgot to ask the subject the relevant questions.
-
-\hypertarget{situational-jugdement-test}{%
-\paragraph{Situational Jugdement Test}\label{situational-jugdement-test}}
-
-To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)).
-In the questionnaire, participants were given hypothetical school scenarios with with 5-7 response strategy for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).
-
-In developing the test procedure, the authors divided the concept of classroom management into three main aspects: \emph{Monitoring}, \emph{managing momentum} (structuring) and \emph{rules and routines} (Gold \& Holodynski, 2015, p.
-230f).
-
-\emph{Monitoring} includes proactive strategies such as omnipresence.
-This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them.
-The second strategy is overlapping.
-In this case, the teacher is able to control several teaching processes at the same time.
-Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf.~ibid.; {[}Kounin (2006), p.~89ff).
-
-By \emph{managing momentum} (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention (Kounin, 2006, p.
-101ff).
-They also include the group focus specifically identified by Kounin (Kounin, 2006, p.
-117ff), i.e.~mobilizing the whole class and demanding accountability (Gold \& Holodynski, 2015, p.
-231).
-
-The third facet of classroom management, establishing \emph{rules, routines and rituals}, supports the other two facets and offers pupils orientation and structure in everyday school life (cf.~ibid.).
-
-The construction of the SJT included 14 scenarios that were based on transcribed classroom videos from Germany.
-For the 14 scenarios, response strategies were derived from evidence-based and theoretical principles by 17 experts on classroom management.
-With the exception of scenario 5, which was subsequently excluded, the 17 experts agreed on an appropriate level of content validity for all other scenarios (cf.~ibid.).
-For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf.~ibid., p.~238).
-Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf.~ibid.).
-
-The construct validity of the SJT with the other 11 scenarios and the sensitivity to differences in strategic knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf.~ibid., p.~238ff).
-Despite limitations in reliability, the test was confirmed to have content and construct validity (cf.~ibid., p.~243).
-On the basis of these results, sufficient reliability and validity of the SJT test procedure was assumed.
-
-The scenarios could each be assigned to one facet of the mentioned classroom management: Scenarios 1-4 cover the facet \emph{monitoring}, scenarios 6-9 the facet \emph{managing momentum} and scenarios 11-14 the facet \emph{rules and routines}.
-
-In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}.
-The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
-Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
-J.
-Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
-
-Since the test was a questionnaire designed to assess strategic knowledge of classroom management of \emph{primary school teachers}, but the sample of the study included several types of schools, changes were made in 10 out of 12 scenarios by deleting the indicated class grade.
-Only in two scenarios was the class grade information not deleted, as the action alternatives would otherwise not be appropriate without the information.
+\hypertarget{material}{%
+\subsection{Material}\label{material}}
 
@@
 
-The project was conducted as a laboratory study in a cross-sectional study design to investigate whether and how teachers' experience has an influence on the perception of and reaction to classroom disruptions.
-
-In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and Septemper 2022.
-
-Before the data collection, each subject received a personal digital meeting with the experimenter to go over the study procedure and to arrange a date for the data collection.
-During the digital meeting, the subjects were asked to prepare a 15-minute lesson in a subject and grade of their choice for the data collection.
-
-On the day of a data collection, the first step was to set up the study room at the University of Leipzig.
-For this, all the appropriate technical equipment was charged and installed in the room (see set up plan {[}REFERENZ EINFÜGEN{]}).
-Next, all four cameras and the audio recorder were synced via Timecode System.
-
-After the subject arrived, a smart watch was put on to measure the heart rate during the session and to get a pretest time at least 15min before the session started.
-In addition to the experimenter and the subject, three student assistants from the working group always took part in the data collection, as they represented the class.
-
-After the welcome, the subject was again briefed about the study.
-It was explicitly pointed out that the student assistants would act as the class and simulate typical class events during the lesson.
-The subject was asked in advance to behave as naturally as possible during the entire time.
-Next, the subjects' written informed consent was obtained and contact details were collected in order to inform all persons participating in the study if a covid infection should occur.
-
-After the introduction, the eye-tracking glasses were adjusted for the subject by inserting contact lenses if necessary and changing the nose pad.
-To start the eye tracking glasses, the Tobii Glasses must be fitted onto the subject's head via an one-point-calibration.
-In the calibration process the subject was asked to look at a Calibration Card held in-front of the subject for a few seconds.
-The experimenter started the recording from Tobii Glasses Controller Software running on a computer.
-
-After starting the eye tracking recording, all other technical devices were also switched on: The four cameras and the audio recorder were controlled via iPad using the BLINK Hup app and could be started simultaneously by synchronization.
-The ZED camera was started manually on another laptop.
-
-Before the 15-minute lesson, there was a short 10-minute warm-up phase.
-The phase was divided into two parts and served on the one hand to get the subjects used to the eye-tracking glasses and on the other hand to get used to their class.
-In the first phase of the warm-up, the game ``name juggling'' was played using two balls.
-In the game, the subject and the three actors threw two balls at each other and, depending on the color of the ball, called either their own name or that of the target person.
-After the name juggling, the subjects were supposed to start a conversation.
-For this, the subject thought of a question for each student and was also asked a question of each student.
-The content could be anything that interested the participants.
-
-After the warm up phase, the experimenter ensured a manual synchronization of the technique by an acoustic signal in which she clapped her hands loudly twice standing in the middle of the room.
-After this, another nine-point calibration followed outside the study room in a neighboring room.
-Before the subject left the room for calibration, the time on the smartwatch was noted, as well as the steps recorded until that point.
-The subject had to stand at a marked point and look at a board three meters away with nine april tags.
-The subject was asked to read the nine points aloud in order at a normal speaking speed.
-This procedure was important to validate the one-point calibration on the one hand and on the other hand to give the subject the feeling of a lesson start, because after this calibration the subject came into the study room to start the 15-minute lesson.
-
-For the micro-teaching lesson, student teachers and experienced teachers were asked to prepare an introduction of 15 minutes which they taught in front of the fictitious class consisting of three student assistants.
-The actors simulated the nine classroom events during the lesson, derived by research literature.
-The order of the disruptions as well as the students performing them were fully balanced using Latin Square.
-The disruptions were only visible for the class on a screen.
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:disruption_categories}Categories of Disruptions (Lohmann, 2015)}
-
-\tiny{
-
-\begin{tabular}{lll}
-\toprule
-Verbal.Disruption & \multicolumn{1}{c}{Agitation} & \multicolumn{1}{c}{Lack.of.eagerness.to.learn}\\
-\midrule
-chatting with neighbor & drumming hands & putting head on table\\
-whispering with neighbor & clicking pen & looking at phone\\
-heckling & snipping with fingers & drawing on a sheet of paper\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-During the lesson, a mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson.
-All other sounds and voices were recorded by an audio recorder.
-To record facial expressions, gestures and movements, four mobile cameras were installed to record the classroom from all perspectives (!!!see figures).
-
-After the lesson, the time was again noted from the smartwatch as well as the subject's steps.
-The nine-point calibration was also performed again in the neighboring room.
-This time, however, the subject was asked to wait outside the room until he or she was called in, because four letters from A to D were placed in the study room.
-The subject was asked to stand facing the board at a marked point in the room and, when given an acoustic signal, to turn around and search the letters and read them aloud in order.
-This served as a control condition for the speed of the subjects' perceptual ability as no expertise is required for searching letters.
-
-After the letter search, the experimenter clapped twice with the hands to record an acoustic signal for the synchronization of all technical devices.
-Afterwards, all devices were switched off and the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire (Helmke et al., 2014) and self developed scales on the teacher's presence behavior derived from the research literature.
-The completion of the questionnaire took approximately 5 minutes.
-
-In the second part of the study, the experimenter conducted a Stimulated Recall Interview (SRI) with the subject(see in Figure \ref{fig:sri}.
-The interview was recorded by the ambient recorder and additionally with a software called OBS to record the speech and screen.
-The recorded eye-tracking video was watched and commented on by the subject while thinking aloud.
-The interview was structured by a guideline based on a fixed sequence of questions, however the subjects were allowed to answer completely open to these questions.
-The objective was to collect data that would provide insight into the subjects' thoughts and reactions in relation to the scripted classroom disruptions.
-The eye-tracking video was not completely re-watched, but stopped at the points where disruptions occurred.
-After the disruption occurred, the subject was asked to describe what had just happened.
-If the disruption was noticed, the subject was asked how disruptive the event was at that moment on a scale from 0 to 10 (for a detailed description of the scale question, see Rating Scales).
-In addition, the subject was asked to reason the given number.
-In a next step, the experimenter re-played the subject's reaction to the disruption and asked to describe and reason the reaction.
-The
-
-\begin{figure}
-
-{\centering \includegraphics{./pictures/sri}
-
-}
-
-\caption{Subject and experimenter during the Stimulated Recall Interview}\label{fig:sri}
-\end{figure}
-
-Finally, the subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire.
-Here they had to assess teaching scenarios and evaluate their behavior in response to them.
-The SJT was used to assess strategic knowledge about classroom management.
-The
-completion of the entire survey took 15 min on average.
-
 \hypertarget{data-analysis}{%
@@
 
-We investigated whether experts and novice teachers differed
-
-All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.8; Wickham et al., 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson et al., 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham et al., 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
-Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
-J.
-Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.
+We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
@@
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
 \hypertarget{refs}{}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-albers2009methodik}{}}%
-Albers, S., Klapper, D., Konradt, U., Walter, A., \& Wolf, J. (2009). \emph{Methodik der empirischen forschung} (Vol. 3). Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-DescTools}{}}%
-Andri et mult. al., S. (2022). \emph{{DescTools}: Tools for descriptive statistics}. Retrieved from \url{https://cran.r-project.org/package=DescTools}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
-Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-gridExtra}{}}%
-Auguie, B. (2017). \emph{gridExtra: Miscellaneous functions for "grid" graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridExtra}
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
-Bates, D., Mächler, M., Bolker, B., \& Walker, S.
-(2015).
-Fitting linear mixed-effects models using {lme4}.
-\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
-\url{https://doi.org/10.18637/jss.v067.i01}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
-Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-rgeos}{}}%
-Bivand, R., \& Rundel, C. (2021). \emph{Rgeos: Interface to geometry engine - open source ('GEOS')}. Retrieved from \url{https://CRAN.R-project.org/package=rgeos}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-xtable}{}}%
-Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-polycor}{}}%
-Fox, J. (2022). \emph{Polycor: Polychoric and polyserial correlations}. Retrieved from \url{https://CRAN.R-project.org/package=polycor}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
-Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
-Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gegenfurtner2018mobiles}{}}%
-Gegenfurtner, A., Eichinger, A., Latzel, R., Dietrich, M. P., Barkowsky, M., Glufke, A., \ldots{} Stern, W. (2018). \emph{Mobiles eye-tracking in den angewandten wissenschaften}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gold2015development}{}}%
-Gold, B., \& Holodynski, M.
-(2015).
-Development and construct validation of a situational judgment test of strategic knowledge of classroom management in elementary schools.
-\emph{Educational Assessment}, \emph{20}(3), 226--248.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-lubridate}{}}%
-Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with {lubridate}. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{https://www.jstatsoft.org/v40/i03/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}}%
-Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M.
-(2014).
-Unterrichtsdiagnostik mit EMU.
-\emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
-Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-rlang}{}}%
-Henry, L., \& Wickham, H. (2022). \emph{Rlang: Functions for base types and core r and 'tidyverse' features}. Retrieved from \url{https://CRAN.R-project.org/package=rlang}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-msm}{}}%
-Jackson, C.
-H.
-(2011).
-Multi-state models for panel data: The {msm} package for {R}.
-\emph{Journal of Statistical Software}, \emph{38}(8), 1--29.
-Retrieved from \url{https://www.jstatsoft.org/v38/i08/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggmosaic}{}}%
-Jeppson, H., Hofmann, H., \& Cook, D. (2021). \emph{Ggmosaic: Mosaic plots in the 'ggplot2' framework}. Retrieved from \url{https://CRAN.R-project.org/package=ggmosaic}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-needs}{}}%
-Katz, J. (2016). \emph{Needs: Attaches and installs packages}. Retrieved from \url{https://CRAN.R-project.org/package=needs}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-moments}{}}%
-Komsta, L., \& Novomestky, F. (2015). \emph{Moments: Moments, cumulants, skewness, kurtosis and related tests}. Retrieved from \url{https://CRAN.R-project.org/package=moments}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kounin2006techniken}{}}%
-Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-sjPlot}{}}%
-Lüdecke, D. (2021). \emph{sjPlot: Data visualization for statistics in social science}. Retrieved from \url{https://CRAN.R-project.org/package=sjPlot}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-sjlabelled}{}}%
-Lüdecke, D. (2022). \emph{Sjlabelled: Labelled data utility functions (version 1.2.0)}. \url{https://doi.org/10.5281/zenodo.1249215}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
-Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
-
-\leavevmode\vadjust pre{\hypertarget{ref-palmer2005identifying}{}}%
-Palmer, D.
-J., Stough, L.
-M., Burdenski, T.
-K., Jr, \& Gonzales, M.
-(2005).
-Identifying teacher expertise: An examination of researchers' decision making.
-\emph{Educational Psychologist}, \emph{40}(1), 13--25.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-sf}{}}%
-Pebesma, E. (2018). {Simple Features for R: Standardized Support for Spatial Vector Data}. \emph{{The R Journal}}, \emph{10}(1), 439--446. \url{https://doi.org/10.32614/RJ-2018-009}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-sp}{}}%
-Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. Retrieved from \url{https://CRAN.R-project.org/doc/Rnews/}
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-formattable}{}}%
-Ren, K., \& Russell, K. (2021). \emph{Formattable: Create 'formattable' data structures}. Retrieved from \url{https://CRAN.R-project.org/package=formattable}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ltm}{}}%
-Rizopoulos, D.
-(2006).
-Ltm: An r package for latent variable modelling and item response theory analyses.
-\emph{Journal of Statistical Software}, \emph{17}(5), 1--25.
-Retrieved from \url{https://doi.org/10.18637/jss.v017.i05}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggrepel}{}}%
-Slowikowski, K. (2021). \emph{Ggrepel: Automatically position non-overlapping text labels with 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggrepel}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-rnaturalearth}{}}%
-South, A. (2017a). \emph{Rnaturalearth: World map data from natural earth}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearth}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-rnaturalearthdata}{}}%
-South, A. (2017b). \emph{Rnaturalearthdata: World vector map data from natural earth used in 'rnaturalearth'}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearthdata}
-
-\leavevmode\vadjust pre{\hypertarget{ref-van2014first}{}}%
-Van den Bogert, N., Bruggen, J.
-van, Kostons, D., \& Jochems, W.
-(2014).
-First steps into understanding teachers' visual perception of classroom events.
-\emph{Teaching and Teacher Education}, \emph{37}, 208--216.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-MASS}{}}%
-Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
-Wickham, H. (2021). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
-Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2022). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
-Wickham, H., \& Girlich, M. (2022). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
-Wickham, H., Hester, J., \& Bryan, J. (2021). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-haven}{}}%
-Wickham, H., \& Miller, E. (2021). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. Retrieved from \url{https://CRAN.R-project.org/package=haven}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
-Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-knitr}{}}%
-Xie, Y. (2015). \emph{Dynamic documents with {R} and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.org/knitr/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ARTofR}{}}%
-Zhang, H. (2021). \emph{ARTofR: Who ever care about the {[}art of r{]} scripts?} Retrieved from \url{https://CRAN.R-project.org/package=ARTofR}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
-Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
+R Core Team. (2022). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
@@
 
-\endgroup
-
-\clearpage
-\renewcommand{\listtablename}{Table captions}
-
 \end{document}

### 2022-08-05 02_paper/02_study/01_eye tracking video questionnaire paper/paper_methods.Rmd

--- 2022-08-03 02_paper/02_study/paper_methods.Rmd
@@
 Therefore, it is merely a matter of preference which concept is consulted to explain connections and terms.
-In the following, the network of effects of classroom management according to Helmke (2014) is used as a reference model in order to be able to understand the embedding of the concept accordingly.
+In the following, the network of effects of classroom management according to @helmke2014unterrichtsdiagnostik is used as a reference model in order to be able to understand the embedding of the concept accordingly.
 
 As was made clear in the definition, classroom management is a complex construct that attempts to accommodate the various modes and challenging characteristics of a classroom.
-Helmke (2014) therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time.
+@helmke2014unterrichtsdiagnostik therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time.
 This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (*d* = 0.39; Hattie, 2013, p.219).
@@
 It is embedded in diverse contexts, especially in the school and class context (Helmke & Helmke, 2015).
-But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led (Helmke, 2014).
-
-Classroom management itself is made up of various components which, according to Helmke (2014), can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior.
+But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led [@helmke2014unterrichtsdiagnostik].
+
+Classroom management itself is made up of various components which, according to @helmke2014unterrichtsdiagnostik, can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior.
 Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke & Helmke, 2015).
@@
 The importance of rules in the classroom has been known and researched for some time.
-Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules (cf.
-Emmer, Evertson & Anderson, 1980; Emmer, Sanford, Clements & Martin, 1982; cited in Doyle, 1989, p.
-15).
+Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules [cf.
+Emmer, Evertson & Anderson, 1980; @emmer1982improving; cited in Doyle, 1989, p.
+15].
 Although he also stresses that establishing a system of rules is a difficult task.
@@
 needs to be done.
-In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time (Helmke, 2014).
+In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time [@helmke2014unterrichtsdiagnostik].
 For the reasons just reasons just explained, it is clear why Hattie (2013, p.
@@
 The behavioral pattern of presence is not a new concept.
-It was already recorded by Kounin in 1970 under the term *withitness*.
-Later research confirmed and validated his assumptions and definition of the term (cf.
-Helmke, 2014, p.10).
+It was already recorded by kounin1970discipline under the term *withitness*.
+Later research confirmed and validated his assumptions and definition of the term [cf.
+@helmke2014unterrichtsdiagnostik, p.10].
 In order to be present, the teacher must be able to control the classroom adequately and superficially effectively at all times.
-This means she must be able to recognize relevant cues or situations that require possible action (Wolff et al., 2015).
-Presence can consequently be illustrated very vividly by means of the image of "eyes in the back of the head" (Kounin, 2006).
-In addition to presence, Kounin (2006) uses the term overlap.
+This means she must be able to recognize relevant cues or situations that require possible action [@wolff2015keeping].
+Presence can consequently be illustrated very vividly by means of the image of "eyes in the back of the head" [@kounin2006techniken].
+In addition to presence, @kounin2006techniken uses the term overlap.
 It is a kind of multitasking ability to be able to cope with parallel processes and situations in the classroom.
-The two dimensions of overlap and presence can also be summarized together under the term monitoring (Gold & Holodynski, 2017).
-When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners (Grub et al., 2020.).
-Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness.
-and increases general awareness of relevant events in the classroom (ibid.). From this point of view, it becomes clear why awareness is a core component of teacher competence.
-
-As a third component influencing the quality of classroom management, cites Helmke (2014) time use and management.
+The two dimensions of overlap and presence can also be summarized together under the term monitoring [@gold2017using].
+When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners [@grub2020process].
+Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness of relevant events in the classroom (ibid.).
+From this point of view, it becomes clear why awareness is a core component of teacher competence.
+
+As a third component influencing the quality of classroom management, cites @helmke2014unterrichtsdiagnostik time use and management.
 This seems trivial at first, considering that classroom management serves the goal of maximizing learning time anyway.
@@
 It follows the approach of concentrating on action-relevant as well as lesson-related content in order to train corresponding competences for teaching practice (KMK, 2004).
-In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes (Barth, 2017).
-Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel & Prenzel 2014).
+In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes [@barth2017professionelle].
+Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic [@jahn2014professionelle].
 The concept of professional vision can originally be traced back to the anthropologist Charles Goodwin and became known under the term Professional Vision (Sherin, 2001).
@@
 76).
-This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom (Berliner, 1994; Leinhardt & Greeno, 1986).
+This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom [@berliner1994expertise, @leinhardt1986cognitive].
 This type of action can be described as a skill that helps teachers make decisions about what is relevant and what is not within the complex classroom setting (van Es & Sherin, 2002).
-Such decisions are based on professional knowledge that guarantees effective teaching and learning in actual classroom situations (Jahn et al., 2014).
+Such decisions are based on professional knowledge that guarantees effective teaching and learning in actual classroom situations [@jahn2014professionelle].
 Professional awareness is therefore referred to as an indicator of how knowledge is represented in teachers (Stürmer et al., 2017).
-It can also be seen as a bridge or link between knowledge and action, or professional competence and behavior (Grub et al., 2020).
+It can also be seen as a bridge or link between knowledge and action, or professional competence and behavior [@grub2020process0].
 It is important to understand that professional vision is acquired and not inherent.
-Rather, it is subject to a process of acquisition that is constantly progressing as teachers are exposed to events and learn to interpret them (Wolff et al., 2016).
+Rather, it is subject to a process of acquisition that is constantly progressing as teachers are exposed to events and learn to interpret them [@wolff2016teacher].
 Fundamentally, then, prospective teachers must select what to focus their attention on in the classroom and how to understand these events (Stürmer et al., 2017).
@@
 Simultaneous events and situations cannot be given the same attention.
-"Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects" (Barth, 2017, p.19).
+"Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects" [@barth2017professionelle, p.19].
 Furthermore, teachers benefit from from a trained perception of problems, as this is a significant factor in being able to preventively counteract preventive measures (Wettstein, 2013).
 
-Basically, the complex process of professional vision is divided into three sub-processes (Grub et al., 20202).
+Basically, the complex process of professional vision is divided into three sub-processes [@grub2020process].
 First of all, the identification, the recognition, of an event takes place.
 Then connections are made, which are finally evaluated by the teacher using his or her professional knowledge.
-In research, these processes are often combined and one speaks of noticing to describe recognition (Grub et al., 2020).
+In research, these processes are often combined and one speaks of noticing to describe recognition [@grub2020process].
 Knowledge-based reasoning includes the last two processes of applying knowledge to make appropriate decisions (ibid.).
 During this process, it becomes clear that the recognition of relevant situations, such as disruptions, precedes all others.
-This process is therefore considered necessary, without which professional vision cannot take place (Grub et al., 2020).
+This process is therefore considered necessary, without which professional vision cannot take place [@grub2020process].
 As described in the chapter on competence, perceptions is also of particular importance in the competence model according to Blömeke et al.
 (2015).
-This is because the process of perception forms an essential basis for situation-specific skills of teachers (Grub et al., 2020).
+This is because the process of perception forms an essential basis for situation-specific skills of teachers [@grub2020process].
 Inferentially, recognition is inevitable for the perception of classroom events and therefore highly relevant for effective classroom management (ibid.).
@@
 Even though the recognition of relevant situations in the classroom is the starting point for all further subsequent actions, the processes of knowledge-based reasoning within professional vision are not to be neglected.
-It is also said that this process is an indicator of the quality of how knowledge is applied to a given situation (Grub et al., 2020), as teachers need to make knowledge-based inferences.
+It is also said that this process is an indicator of the quality of how knowledge is applied to a given situation [@grub2020process], as teachers need to make knowledge-based inferences.
 Qualitative research on knowledge-based reasoning concluded that it can be subdivided into three further sub-processes.
-Sherin (2007; cited in Barth, 2017, p.
-20) made a first subdivision, which consists of the processes of describing, evaluating and interpreting.
+@sherin2007development [cited in @barth2017professionelle, p.
+20] made a first subdivision,  which consists of the processes of describing, evaluating and interpreting.
 When a teacher describes what she notices, she concentrates on observable characteristics, i.e.
 important aspects of teaching (ibid.).
-When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event (cf.
-Barth, 2017, p.
-19).
+When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event [cf.
+@barth2017professionelle, p.
+19].
 Seidel et al.
 (2010), on the other hand, focus on German-speaking countries in their research on professional vision and modified Sherin's original concept.
-They also divide knowledge-based-reasoning into three levels, but these differ: describing, explaining and predicting (Barth, 2017).
+They also divide knowledge-based-reasoning into three levels, but these differ: describing, explaining and predicting [@barth2017professionelle].
 More precisely, these processes encompass the ability to differentially describe instructional components that have an impact on learning; to make theoretically sound explanations about instructional situations; and to predict the effects of these events in relation to the teaching-learning process (cf.
@@
 
-Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect (Sherin, 2007; cited in Barth, 2017, p.
-19).
+Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect [@sherin2007development7; cited in @barth2017professionelle7, p.
+19].
 What is considered and perceived as relevant in a teacher's selective vision (noticing) functions as the basis of the subsequent processes of describing, evaluating, and interpreting (knowledge-based-reasoning).
@@
 However, this method is highly susceptible to interference due to its incomplete accessibility (Dessus, 2016).
-The increasingly popular research method of eye-tracking technology therefore represents an innovative means of externalizing, i.e., making visible, internalized processes by means of eye movements (Gegenfurtner et al., 2018).
-Stimuli in the environment are always perceived by our eyes as the first receiver.
+The increasingly popular research method of eye-tracking technology therefore represents an innovative means of externalizing, i.e., making visible, internalized processes by means of eye movements [@gegenfurtner2018mobiles] Stimuli in the environment are always perceived by our eyes as the first receiver.
 They take in the information and pass it on to our brain so that it can finally be processed there.
@@
 
-Eye-tracking technology can be roughly divided into two types of devices: Stationary and mobile systems (Blake, 2013).
+Eye-tracking technology can be roughly divided into two types of devices: Stationary and mobile systems [@blake2013eye].
 In research so far, mainly eye-tracking devices have been used, which phenotypically resemble a computer (ibid.).
-They are also referred to as remote devices and, once calibrated, measure eye movements in a non-contact manner using infrared light (Gegenfurtner et al., 2018).
+They are also referred to as remote devices and, once calibrated, measure eye movements in a non-contact manner using infrared light [@egenfurtner2018mobiles].
 However, this technique reaches its limits when it comes to collecting data in everyday situations.
 For this purpose, the more flexible variant, mobile eye tracking (MET) or head-mounted or wearable eye trackers, can be used.
-Typically, the technology is found as a head-mounted device on helmets or integrated into an eyeglass frame (Blake, 2013).
+Typically, the technology is found as a head-mounted device on helmets or integrated into an eyeglass frame [@blake2013eye].
 The difference with stationary tracking is that in addition to an eye camera and infrared light source, additional cameras are built in to capture head movements (ibid.).
 These are intended to help document the subject's field of view.
-Therefore, such systems are particularly suitable for applied sciences, as is the case in empirical school and development research (Gegenfurtner et al., 2018).
+Therefore, such systems are particularly suitable for applied sciences, as is the case in empirical school and development research [@gegenfurtner2018mobiles].
 
 Eye-tracking research is based on several fundamental assumptions.
-The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date (cf.
-Blake, 2018, p.380).
-In this regard, Hoffmann and Subramaniam (1995) obtained the finding that when the eyes are focused on an object, this is associated with an attentional focus of the person.
+The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date [cf.
+@blake2013eye, p.
+380].
+In this regard, hoffman1995role obtained the finding that when the eyes are focused on an object, this is associated with an attentional focus of the person.
 Based on these findings, ET technology is based on the following two assumptions: The immediacy assumption and the eye-mind assumption (cf.
@@
 
-In MET, collected data sets are usually output according to different parameters: Fixations and Saccades (Gegenfurtner et al., 2018).
+In MET, collected data sets are usually output according to different parameters: Fixations and Saccades [@gegenfurtner2018mobiles].
 The latter describes gaze jumps, i.e., movements of both eyes, which are useful to capture new fixations (Eye-Tracking Kompetenzzentrum Schweiz, 2021).
@@
 A fixation of an object can be characterized according to its duration, frequency, and distribution.
-In the illustration, the radius of a circle defines the duration of a fixation (Gegenfurtner et al., 2018).
+In the illustration, the radius of a circle defines the duration of a fixation [@gegenfurtner2018mobiles].
 These data can also be used to describe perception times, such as the time until the first fixation on a particular object.
@@
 
-By means of eye movement measurement, attention allocations to areas of interest or objects are made accessible in addition to pure fixations (Gegenfurtner et al., 2018).
+By means of eye movement measurement, attention allocations to areas of interest or objects are made accessible in addition to pure fixations [@gegenfurtner2018mobiles].
 In research, these regions in the field of view of subjects are referred to as areas of interest (AOI) (edb.).
@@
 Since it is assumed that professional vision is a preferably knowledge-based process, differences between experienced and inexperienced teachers have already been identified.
-These differences were in favor of experts, since a connection between teaching experience and the associated increase in knowledge acquisition is assumed (Grub et al., 2020).
-Student teachers do not have well-structured experiential knowledge due to their almost non-existent practice in everyday school life (Wolff et al., 2016).
-This causes them selection difficulties in perception and is called pedagogical knowledge gap (cf.
-Wolff et al., 2016, p.260).
+These differences were in favor of experts, since a connection between teaching experience and the associated increase in knowledge acquisition is assumed [@grub2020process].
+Student teachers do not have well-structured experiential knowledge due to their almost non-existent practice in everyday school life [@wolff2016teacher].
+This causes them selection difficulties in perception and is called pedagogical knowledge gap [cf.
+@wolff2016teacher, 2016, p.260].
 Through newly gained experiences, the professional vision of a teacher is continuously restructured and updated, and mental representation is constantly realigned accordingly (ibid.).
 This has been proven in research as a positive correlation of input to teaching and learning theories in studies and professional classroom perception has been found (Stürmer et al., 2012).
-Therefore, it can be assumed that there is a relationship between teacher expertise, their visual processing, and mindfulness for classroom management (Wolff et al., 2016).
-Research has also shown that declarative knowledge acquisition, i.e., acquisition of factual knowledge, supports perceptual processes (Seidel et al., 2012; cited in Treisch, 2018, p.26).
-Accordingly, this increased knowledge acquisition would explain a positive impact on professional teaching perception.
-Among the most important prerequisites for this acquisition, Baumert and Kunter (2006) include prior knowledge and interest.
+Therefore, it can be assumed that there is a relationship between teacher expertise, their visual processing, and mindfulness for classroom management [@wolff2016teacher].
+Research has also shown that declarative knowledge acquisition, i.e., acquisition of factual knowledge, supports perceptual processes [Seidel et al., 2012; cited in @treisch2018entwicklung, p.26] Accordingly, this increased knowledge acquisition would explain a positive impact on professional teaching perception.
+Among the most important prerequisites for this acquisition, baumert2006key include prior knowledge and interest.
 The former is elementary for new knowledge acquisition about effective teaching and learning, as it supports processing, integration, and consolidation of it (Stürmer, 2011).
-Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions (cf.
-Sabers, 1991; cited in Treisch, 2018).
+Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions [cf.
+@sabers1991differences; cited in @treisch2018entwicklung].
 This is explained by increased filtering mechanisms that support perceptual processes, i.e., recognition.
-Specifically, it has been shown that experienced teachers have more fixations on relevant areas because they have already learned theories on how to detect potential clutter in the classroom (Grub et al., 2020.).
+Specifically, it has been shown that experienced teachers have more fixations on relevant areas because they have already learned theories on how to detect potential clutter in the classroom [@grub2020process].
 Furthermore, experts have an advantage when it comes to coding information.

### 2022-08-05 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
fitbit paper participants

@@
       - "Conceptualization"
+      - "Writing - Review & Editing"
+  - name          : "Anne Deiglmayr"
+    affiliation   : "1"
+    role:
       - "Supervision"
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+  We received funding from QualiFond of University Leipzig.
+We have no conflicts of interest to disclose.
+This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).
 
@@
 
+```{r include=FALSE}
+# install.packages("needs")
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+library(needs)
+
+needs(tidyverse,
+      lubridate,
+      viridis,
+      grid,
+      gridExtra,
+      cowplot,
+      readxl,
+      ARTofR,
+      moments,
+      ltm,
+      sjPlot,
+      kableExtra,
+      xtable,
+      DescTools,
+      formattable)
+
+```
+
 # Methods
@@
 ## Participants
+```{r demographicstable, include = TRUE, echo=FALSE}
+
+# read in data and select and rename relevant columns with transmute 
+demo.data <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
+  transmute(Group = LI06_05,
+            Gender = LI02_01_1,
+            Age = LI03_01,
+            `Teaching Experience` = LI04_01,
+            School_type = LI18,
+            Grade = LI16_05,
+            Subject = LI10_05,
+            Semester = LI11_01,
+            Internship = LI13_01,
+            `Extracurricular Teaching Experience` = LI14,
+            `Secondary Teaching Activities` = LI17
+            )
+
+# define expert and novice with ifelse function
+demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")
+
+# changing gender to count female gender (male = 2 --> 0)
+demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")
+
+# changing character Gender into numeric
+demo.data$Gender <- as.numeric(demo.data$Gender)
+
+# creating new column with total participants to calculate percent of gender
+demo.data <- demo.data %>%
+  group_by(Group) %>%
+  mutate(Sum_participants = n())
+
+# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
+demo.data$School_type[demo.data$School_type == 2] <- "1"
+
+# creating new column to calculate percent of school type
+demo.data <- 
+  demo.data %>%
+  group_by(School_type, Group) %>%
+  mutate(Count_Schooltype = sum(n())) %>% 
+  mutate(Percent_schooltype = round((Count_Schooltype/Sum_participants) * 100, 
+         digits = 2))
+
+# changing character Percent_schooltype into numeric
+demo.data$Percent_schooltype <- as.numeric(demo.data$Percent_schooltype)
+
+# changing character Semester into numeric
+demo.data$Semester <- as.numeric(demo.data$Semester)
+
+# changing Type of School into character
+# LI18:
+# 1: Grundschule
+# 2: Oberschule
+# 3: Gymnasium
+# 4: Förderschule/Sondershausen
+# 5: Berufsbildende Schule
+# -1: andere Schulform
+demo.data$School_type <- factor(x = demo.data$School_type,
+                   levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
+                   labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen
+
+# changing `Extracurricular Teaching Experience` to count experience (no experience = 2 --> 0)
+demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 1, "1","0")
+
+# changing character Extra. Exp. into numeric
+demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)
+
+# changing `Secondary Teaching Activities` to count experience (no experience = 2 --> 0)
+demo.data$`Secondary Teaching Activities` = ifelse(demo.data$`Secondary Teaching Activities` == 1, "1","0")
+
+# changing character Extra. Exp. into numeric
+demo.data$`Secondary Teaching Activities` <- as.numeric(demo.data$`Secondary Teaching Activities`)
+
+# create new columns that give proportion of Gender
+# percent = female gender divided by all female Gender
+# demo.data <- demo.data  %>% 
+#   group_by(Group) %>% 
+#   mutate(Gender_percent = Gender/Sum_participants) %>% 
+#   mutate(Gender_percent = round(sum(Gender_percent)*100, digits=0))
+
+# create a basic table (tibble) using tidyverse functions
+demo.table <- demo.data %>%
+  group_by(Group) %>%
+  summarise(N=n(),
+            "Gender female in percent" = round(sum(Gender/Sum_participants) * 100, 
+                                               digits = 2),
+            "M Age in years" = round(mean(Age), 
+                                     digits = 2),
+            "SD Age in years" = round(sd(Age), 
+                                      digits = 2),
+            "Min Age in years" = min(Age),
+            "Max Age in years" = max(Age)
+            )
+
+# # format and insert table in manuscript
+# demo.table %>%
+# papaja::apa_table(
+#   caption = "Demographic Information",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+#   )
+
+# create a basic table (tibble) using tidyverse functions
+exp.table <- demo.data %>%
+  group_by(Group) %>%
+  summarise(N=n(),
+           "M Exp." = round(mean(`Teaching Experience`), 2),
+            "SD Exp." = round(sd(`Teaching Experience`), 2),
+            "Min Exp." = min(`Teaching Experience`),
+            "Max Exp." = max(`Teaching Experience`),
+            "M Semester" = round(mean(Semester), 2),
+            "SD Semester" = round(sd(Semester), 2),
+            "Min Semester" = min(Semester),
+            "Max Semester" = max(Semester),
+            "M Internship" = round(mean(Internship), 2),
+            "SD Internship" = round(sd(Internship), 2),
+            "Min Internship" = min(Internship),
+            "Max Internship" = max(Internship),
+            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
+            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
+           )
+
+# # format and insert table in manuscript
+# exp.table %>%
+# papaja::apa_table(
+#   caption = "Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+#   )
+
+```
+
+XXX  fitbit data exclusion XXX
+
+The sample consisted of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.
+
+The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
+According to @palmer2005identifying, we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
+Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
+
+The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`).
+`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers.
+`r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+
+The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years.
+On average, the student teachers were in their `r exp.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`).
+Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies.
+`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype") %>% unique()`% to become special education teachers.
+`r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+
+The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at Leipzig University.
+All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
+The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+All participants were informed in detail about the aim and intention of the study prior to testing.
+Participation in the study was voluntary and only took place after written consent has been given.
 

### 2022-08-05 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
fitbit paper participants

@@
   pdftitle={A Walk In The Classroom - Using Fitbit Charge 4 to measure expert and novice teachers' heart rate and step counts in a laboratory study},
-  pdfauthor={Mandy Klatt1, Peer Keßler1, \& Gregor Kachel1,2},
+  pdfauthor={Mandy Klatt1, Peer Keßler1, Gregor Kachel1,2, \& Anne Deiglmayr1},
   pdflang={en-EN},
@@
 \title{A Walk In The Classroom - Using Fitbit Charge 4 to measure expert and novice teachers' heart rate and step counts in a laboratory study}
-\author{Mandy Klatt\textsuperscript{1}, Peer Keßler\textsuperscript{1}, \& Gregor Kachel\textsuperscript{1,2}}
+\author{Mandy Klatt\textsuperscript{1}, Peer Keßler\textsuperscript{1}, Gregor Kachel\textsuperscript{1,2}, \& Anne Deiglmayr\textsuperscript{1}}
 \date{}
@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
+We received funding from QualiFond of University Leipzig.
+We have no conflicts of interest to disclose.
+This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).
 
 The authors made the following contributions.
-Mandy Klatt: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Peer Keßler: Writing - Review \& Editing, Supervision; Gregor Kachel: Supervision.
+Mandy Klatt: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Peer Keßler: Writing - Original Draft Preparation, Writing - Review \& Editing; Gregor Kachel: Conceptualization; Anne Deiglmayr: Supervision.
 
@@
 
+The sample consisted of \emph{N} = 41 participants with \emph{n} = 16 expert teachers and \emph{n} = 25 novice teachers.
+
+The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
+According to Palmer, Stough, Burdenski, and Gonzales (2005), we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
+Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
+
+The expert teachers (9 women; 56.25\%) had a mean age of 41.40 years (\emph{SD} = 10.70; range: 27-59) and an average teaching experience of 13.60 years (\emph{SD} = 12.80; range: 2-37).
+18.75\% of the experts were primary school teachers and 81.25\% were secondary school teachers.
+56\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+
+The novice teachers (16 women; 64\%) had a mean age of 23.40 years (\emph{SD} = 1.80; range: 20-27) with an average teaching experience of 0 years.
+On average, the student teachers were in their 7.30 semester (\emph{SD} = 2.60; range: 3-11).
+Furthermore, they had an average teaching experience of 11.20 teaching units à 45min (\emph{SD} = 8.10; range: 0-36) through the internships during their studies.
+20\% of the novices were studying to become primary school teachers, 68\% to become secondary school teachers and 12\% to become special education teachers.
+88\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+
+The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at Leipzig University.
+All study procedures were carried out in accordance with the ethical standards of the University's Institutional Review Board.
+The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+All participants were informed in detail about the aim and intention of the study prior to testing.
+Participation in the study was voluntary and only took place after written consent has been given.
+
 \hypertarget{material}{%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-palmer2005identifying}{}}%
+Palmer, D.
+J., Stough, L.
+M., Burdenski, T.
+K., Jr, \& Gonzales, M.
+(2005).
+Identifying teacher expertise: An examination of researchers' decision making.
+\emph{Educational Psychologist}, \emph{40}(1), 13--25.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%

### 2022-08-05 02_paper/02_study/01_eye tracking video questionnaire paper/paper_methods.Rmd

@@
 According to @kounin2006techniken, these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring [@gold2017using].
-Learning to develop such classroom management skills is a demanding and complex task for student teachers [@wolff2016teacher].
+Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017).
 Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, “[…] whereas only a few studies have focused on the basal process of noticing, i.e.
@@
 In the worst case, they force a standstill in the flow of instruction, which is naturally to be avoided.
-Lohmann (2015, p.13) describes classroom disruptions as "events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place." However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive (cf.
-Eckstein, Grob & Reusser, 2016; cited in, Eckstein, 2018, p.11).
+Lohmann (2015, p.13) describes classroom disruptions as "events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place." However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive [cf.
+@eckstein2016unterrichtliche; cited in, Eckstein, 2018, p.11].
 Thus, instructional disruptions are strongly dependent on perception and involve elements of production as well as reception (ibid.).
@@
 This is due to the fact that self-drawn cognition is activated in self-videos and that when negative events occur, subjects tend to defend their actions (ibid.).
-Kleinknecht and Schneider (2013) analyzed this process in more detail and found that this is particularly problematic for the reflective learning process, as it has a counterproductive effect on analyzing possible alternative actions.
+@kleinknecht2013teachers analyzed this process in more detail and found that this is particularly problematic for the reflective learning process, as it has a counterproductive effect on analyzing possible alternative actions.
 They also found that in third-party videos, reflection on potential alternative actions was twice as frequent as in self-recorded videos (ibid.)!
@@
 Therefore, MET represents a target-rich method for capturing teachers' attentional processes in the classroom.
-Previous studies with large data sets on teachers' visual expertise have predominantly used stationary ET (Wolff et al., 2016).
+Previous studies with large data sets on teachers' visual expertise have predominantly used stationary ET [@wolff2016teacher].
 In MET studies, the samples turn out to be much smaller; here, the largest study to be mentioned is with 12 experienced and 12 inexperienced teachers by Cortina et al.
@@
 Individual personality characteristics play a central role when it comes to the perception of relevant classroom events.
-In general, it should be noted that novices have greater problems in classroom management as well as in dealing with difficult student behavior (Barth, 2017).
+In general, it should be noted that novices have greater problems in classroom management as well as in dealing with difficult student behavior [@barth2017professionelle].
 Often, this is due to their late or even lack of awareness of classroom disruptions.
 However, their lack of expertise is not the sole reason for this phenomenon.
-Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher (Baumert & Kunter, 2006).
-Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors.
+Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher [@baumert2006key] Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors.
 Individual person characteristics as well as contextual factors not only have an effect on teaching perception, but likewise on the sense of disturbance of a situation (Eckstein, 2019).
@@
 
-Based on the existing literature, we expected expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation duration and (H3) perceiving classroom disruptions faster (cf.
-@van2014first), (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions (Barth, 2017), and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
+Based on the existing literature, we expected expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation duration and (H3) perceiving classroom disruptions faster [cf.
+@van2014first], (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions [@barth2017professionelle], and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
 
@@
 The study was based on a quasi-experimental study design, as there was no random assignment of subjects to experimental conditions.
-Due to the use of MET technology, the study had a high external validity (Gegenfurtner et al., 2018).
-To ensure internal validity the occurring instructional events were exactly the same for all subjects, as the learners received precise behavioral instructions.
+Due to the use of MET technology, the study had a high external validity [@gegenfurtner2018mobiles] To ensure internal validity the occurring instructional events were exactly the same for all subjects, as the learners received precise behavioral instructions.
 These disruptions followed a script and coding guide in which the actions of the class were precisely described.

### 2022-08-05 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
fitbit paper device description

@@
 ## Material
+We used a Fitbit Charge 4 to measure the teachers' heart rate.
+The device was attached 2-finger widths above the ulnar styloid process to the partipant's wrist following the manufacturer’s instructions.
+To determine the heart rate, the Fitbit flashes green LEDs many times per second and uses light-sensitive photodiodes to measure the volume changes in the capillaries and then calculates how many times the heart beats per minute (bpm).
+Data were automatically wireless synced with an iPad via Bluetooth to a Fitbit account, and subsequently, the intraday second-by-second data were exported for each session using the opensource software Pulse Watch (PulseWatch.
+URL: https://iccir919.github.io/pulseWatch/public/index.html [accessed 2022-08-03]).
 

### 2022-08-09 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
upload procedure

@@
 ## Procedure
+In a laboratory setting, three trained actors performed teaching disruptions in a counter balanced fashion while the subject taught a 15-minute micro-teaching unit prepared in advance.
+To record the subject's heart rate, the Fitbit Charge 4 was put on at least 10 minutes before the start of the lesson.
+The lesson was recorded by four cameras and an audio recorder.
+In addition, the subject wore eye-tracking glasses to record gaze behavior.
+
+Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire (EMU, @helmke2014unterrichtsdiagnostik) and self developed scales on the teacher's presence behavior derived from the research literature via the online survey website SoSci Survey (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree).
+The completion of the questionnaire took approximately 5 minutes.
+
+The experimenter then conducted a Stimulated Recall Interview (SRI), where the subject commented and rated the reactions to classroom events while watching the eye tracking video.
+
+Finally, a Situational Judgment Test (SJT, @gold2015development) was used to assess the subject's strategic knowledge of classroom management.
+The subject was asked to judge alternative actions on school scenarios on a 6-point rating scale from 1 (A) to 6 (F) according to school grades.
+Data from the SJT were again collected as an online questionnaire via the website www.soscisurvey.de and lastet approximately 10 minutes.
+
+The Fitbit watch was removed only after the last questionnaire to obtain heart rate at three different measurement time points: before, during, and after the lesson.
 

### 2022-08-09 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
upload procedure

@@
 The authors made the following contributions.
-Mandy Klatt: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Peer Keßler: Writing - Original Draft Preparation, Writing - Review \& Editing; Gregor Kachel: Conceptualization; Anne Deiglmayr: Supervision.
+Mandy Klatt: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Peer Keßler: Writing - Original Draft Preparation, Writing - Review \& Editing; Gregor Kachel: Conceptualization, Writing - Review \& Editing; Anne Deiglmayr: Supervision.
 
@@
 
+XXX fitbit data exclusion XXX
+
 The sample consisted of \emph{N} = 41 participants with \emph{n} = 16 expert teachers and \emph{n} = 25 novice teachers.
@@
 
+We used a Fitbit Charge 4 to measure the teachers' heart rate.
+The device was attached 2-finger widths above the ulnar styloid process to the partipant's wrist following the manufacturer's instructions.
+To determine the heart rate, the Fitbit flashes green LEDs many times per second and uses light-sensitive photodiodes to measure the volume changes in the capillaries and then calculates how many times the heart beats per minute (bpm).
+Data were automatically wireless synced with an iPad via Bluetooth to a Fitbit account, and subsequently, the intraday second-by-second data were exported for each session using the opensource software Pulse Watch (PulseWatch.
+URL: \url{https://iccir919.github.io/pulseWatch/public/index.html} {[}accessed 2022-08-03{]}).
+
 \hypertarget{procedure}{%
 \subsection{Procedure}\label{procedure}}
+
+In a laboratory setting, three trained actors performed teaching disruptions in a counter balanced fashion while the subject taught a 15-minute micro-teaching unit prepared in advance.
+To record the subject's heart rate, the Fitbit Charge 4 was put on at least 10 minutes before the start of the lesson.
+The lesson was recorded by four cameras and an audio recorder.
+In addition, the subject wore eye-tracking glasses to record gaze behavior.
+
+Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire (EMU, Helmke et al.
+(2014)) and self developed scales on the teacher's presence behavior derived from the research literature via the online survey website SoSci Survey (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree).
+The completion of the questionnaire took approximately 5 minutes.
+
+The experimenter then conducted a Stimulated Recall Interview (SRI), where the subject commented and rated the reactions to classroom events while watching the eye tracking video.
+
+Finally, a Situational Judgment Test (SJT, Gold and Holodynski (2015)) was used to assess the subject's strategic knowledge of classroom management.
+The subject was asked to judge alternative actions on school scenarios on a 6-point rating scale from 1 (A) to 6 (F) according to school grades.
+Data from the SJT were again collected as an online questionnaire via the website www.soscisurvey.de and lastet approximately 10 minutes.
+
+The Fitbit watch was removed only after the last questionnaire to obtain heart rate at three different measurement time points: before, during, and after the lesson.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gold2015development}{}}%
+Gold, B., \& Holodynski, M.
+(2015).
+Development and construct validation of a situational judgment test of strategic knowledge of classroom management in elementary schools.
+\emph{Educational Assessment}, \emph{20}(3), 226--248.
+
+\leavevmode\vadjust pre{\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}}%
+Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M.
+(2014).
+Unterrichtsdiagnostik mit EMU.
+\emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
+
 \leavevmode\vadjust pre{\hypertarget{ref-palmer2005identifying}{}}%

### 2022-08-10 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update plots

@@
       lubridate,
+      janitor,
       viridis,
@@
 
+### FitBit
+
+All participants were given a FitBit Smart Watch Charge 4 to wear during the experiment.
+
+## Heart Rate
+
+The heart rate of each subject were measured before, during and after the experiment.
+
+XXX Data and data wrangling need to be imported XXX 
+```{r}
+# Initial Preparations
+## Run following Code if and only if new data is added to the initial data.
+
+source(file = "data.wrangling.R")
+
+# Plots
+
+df_heart_all <-
+  read_rds(file = "final_data/heart_all.rds") |> 
+  mutate(status = factor(status,
+                         levels = c("Expert","Novice"),
+                         labels = c("Expert","Novice")
+                         )
+         )
+
+df_heart_min <-
+  read_rds(file = "final_data/heart_min.rds")
+
+df_heart_aggr <- 
+  read_rds(file = "final_data/heart_aggr.rds") |> 
+  mutate(status = factor(status,
+                         levels = c("Novice","Expert"),
+                         labels = c("Novice","Expert")
+                         )
+         )
+
+plot_flow <-
+ggplot(data = df_heart_all,
+       mapping = aes(x = as.numeric(Time),
+                     y = `Heart Rate`,
+                     group = ID)
+       ) +
+  geom_line(mapping = aes(color = status),
+            size = 0.3,
+            alpha = 1
+            ) +
+  xlim(0, min(df_heart_min$min)) +
+  scale_color_viridis_d(option = "A",
+                       end = 0.8)  +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Time (in Seconds)",
+       y = "Heart Rate\n(in Beats per Minute)") +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        legend.position = "none",
+        strip.text = element_text(size = 16)) +
+  facet_grid(cols = vars(Type),
+             scales = "free_x")
+
+plot_flow_leg <-
+ggplot(data = df_heart_all,
+       mapping = aes(x = Time,
+                     y = `Heart Rate`
+                     )
+       ) +
+  geom_smooth(mapping = aes(color = status),
+              method = "loess") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+ # scale_linetype_manual(values = c(1, 6)) +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        legend.title = element_blank())
+
+legend <- cowplot::get_legend(plot_flow_leg)
+
+plot_loess <-
+ggplot(data = filter(df_heart_all),
+       mapping = aes(x = as.numeric(Time),
+                     y = `Heart Rate`
+                     )
+       ) +
+  stat_smooth(geom = "line",
+              mapping = aes(color = status),
+              method = "loess",
+              se = FALSE) +
+  xlim(0,min(df_heart_min$min)) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Time (in Seconds)",
+       y = "Heart Rate\n(in Beats per Minute)") +
+  theme_minimal() +
+  facet_grid(cols = vars(Type),
+             scales = "free_x",
+             ) +
+  theme(text = element_text(family = "serif"),
+        legend.position = "none",
+        strip.background = element_blank(),
+        strip.text.x = element_blank()
+        )
+
+plot_box <- 
+ggplot(data = df_heart_aggr,
+       mapping = aes(x = Type,
+                     y = mean,
+                     color = status
+                     )
+       ) +
+  geom_boxplot(color = "darkgrey",
+               fill = "grey") +
+  geom_line(data = filter(df_heart_aggr,
+                          status == "Novice"),
+            mapping = aes(x = Type,
+                          y = mean,
+                          group = as_factor(ID)
+                          ),
+            linetype = 1,
+            alpha = 0.5
+            ) +
+  geom_line(data = filter(df_heart_aggr,
+                          status == "Expert"),
+            mapping = aes(x = Type,
+                          y = mean,
+                          group = as_factor(ID)
+                          ),
+            linetype = 6,
+            alpha = 0.5
+            ) +
+  geom_point(size = 2,
+             alpha = 0.5) +
+  labs(x = "",
+       y = "Average Heart Rate\n(in Beats per Minute)") +
+  scale_color_viridis_d(option = "A",
+                       end = 0.8) +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        strip.text = element_blank(),
+       legend.position = "none",
+        axis.text.x = element_blank()
+        ) +
+  aes(fill = Type)
+
+lo_mat <- rbind(c(1,1,1,1,1,1,NA),
+                c(2,2,2,2,2,2,4),
+                c(3,3,3,3,3,3,NA))
+
+plot_heart <- 
+grid.arrange(grobs = list(plot_flow, plot_loess, plot_box, legend),
+             layout_matrix = lo_mat)
+
+plot_heart
+```
+
+### Steps
+
+Using the FitBit we measured the steps a person walked during the experiment as well.
+We validated the steps in six randomly selected videos by manual step counting.
+A step was considered to be the movement of the subject's foot forward, backward, or sideways.
+The measurement was not as reliable as hoped.
+
+```{r}
+df_steps <- read_rds(file = "final_data/steps.rds")
+set.seed(5678)
+ggplot(data = df_steps,
+       mapping = aes(x = type,
+                     y = Steps
+                     )
+       ) +
+  geom_boxplot(mapping = aes(color = type),
+               fill = "grey",
+               alpha = 0.6) +
+  geom_jitter(mapping = aes(color = type),
+              alpha = 0.9,
+              width = 0.3) + 
+  scale_color_viridis_d(option = "A",
+                       end = 0.8) +
+  labs(x = "",
+       y = "Steps During\nMain Phase") +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        legend.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()
+        )
+
+### Validation of steps 
+# selecting some rows at random with sample_n()
+sample_n(df_steps, 6)
+
+# random ID Output:
+# Novices ID: 102, 125, 110
+# Experts ID: 219, 218, 214
+
+# Results from manual step counting:
+# Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
+# Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps
+
+```
+
 # Results
 
-# Discussion
+# Discussion and implication
 

### 2022-08-11 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
upload introduction

@@
 ```
+# Introduction
+Especially the first five years are a crucial time the teaching profession, whether the development from novice to expert is experienced as successful and as an increase in competence or leads to the fact that between 40 and 50 percent of the beginning teachers left the profession [@ingersoll2003wrong; @prilleltensky2016teacher].
+One reason among many why teachers end their careers is the demanding workload and resulting stress in the teaching profession [@struyven2014teachers].
+In her study with 400 secondary teachers, @fisher2011factors showed that burnout scores were significantly different between novice and experienced teachers, whereby novices had higher burnout.
+Furthermore, she found that low years of experience was a statistically significant predictor for stress in the teaching profession, along with job satisfaction and burnout.
+
+XXX ÜBERGANG VON STRESS ZU HEART RATE XXX
+
+The heart rate is considered an indicator of physical or emotional stress.
+Increased workload is accompanied by increased heart rate.
+Therefore, heart rate can be considered the most important psycho physiological parameter [@sachs2014physiologische].
+
+XXX ÜBERGANG VON HEART RATE ZU SMARTWATCHES - VORTEILE XXX low-cost, non-invasive, wrist-worn devices
+
+There is a gap in research on whether heart rate measurements using fitness watches are appropriate to detect differences between experienced and inexperienced teachers in a laboratory setting.
+
+## Aim of the study
+The aim of the study was to uncover differences between 25 experienced and 25 inexperienced teachers on the physical and emotional demands during a 15-minute micro-teaching unit by measuring their heart rate using a fitness watch (Fitbit Charge 4).
+As the fitness watch was put on at the beginning of the survey and was not taken off until the entire data collection was completed, the heart rate could be measured in the resting and arousal states.
+In addition, the watch recorded the subjects' movement activity to determine how many steps were taken during the lesson.
+The practicality of the FitBit for classroom research is discussed.
 
@@
 We used a Fitbit Charge 4 to measure the teachers' heart rate.
-The device was attached 2-finger widths above the ulnar styloid process to the partipant's wrist following the manufacturer’s instructions.
+The device was attached 2-finger widths above the ulnar styloid process to the subject’s wrist following the manufacturer’s instructions.
 To determine the heart rate, the Fitbit flashes green LEDs many times per second and uses light-sensitive photodiodes to measure the volume changes in the capillaries and then calculates how many times the heart beats per minute (bpm).

### 2022-08-12 02_paper/02_study/01_eye tracking video questionnaire paper/paper_methods.Rmd
Update paper_methods.Rmd

@@
 The coding of the reactions was done in seven levels.
-Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping (cf.
-Kounin 2006; Gold & Holodynski 2015) by not interrupting the flow of instruction.
+Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping [cf.
+@kounin2006techniken; @gold2015development] by not interrupting the flow of instruction.
 Code 2 or Code 3 was assigned for a brief verbal expression with or without a preceding nonverbal response.
@@
 There were two possibilities, if there was no reaction: If the teacher deliberately ignored the disruption, code 5 was assigned.
-If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized (cf.
-Gold & Holodynski, 2015).
-If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned.
+If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized [cf.
+@gold2015development].If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned.
 According to Gippert et al.
@@
 In addition, video recordings can be viewed multiple times, by different people or from different perspectives.
-Thus, a high measurement accuracy (reliability) is given (cf.
-Mayring, P., Gläser-Zikuda, M., & Ziegelbauer, 2005).
+Thus, a high measurement accuracy (reliability) is given [cf.@mayring2005auswertung].
 All measures taken contribute to increase the validity of the method.
@@
 In this case, the teacher is able to control several teaching processes at the same time.
-Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf.
-ibid.; [@kounin2006techniken, p.
-89ff).
-
-By *managing momentum* (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention [@kounin2006techniken, p.
+Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions [cf.
+ibid.; @kounin2006techniken, p.
+89ff].
+
+By *managing momentum* (structuring), @gold2015development understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention [@kounin2006techniken, p.
 101ff].
@@
 
-Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management (SJT, [@gold2015development]) in the form of a questionnaire.
+Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management [SJT, @gold2015development] in the form of a questionnaire.
 Here they had to assess teaching scenarios and evaluate their behavior in response to them.

### 2022-09-12 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
fitbit paper

--- 2022-08-09 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
@@
 
+### FitBit
+
+All participants were given a FitBit Smart Watch Charge 4 to wear during the experiment.
+
+## Heart Rate
+
+The heart rate of each subject were measured before, during and after the experiment.
+
+XXX Data and data wrangling need to be imported XXX 
+```{r}
+# # Initial Preparations
+# ## Run following Code if and only if new data is added to the initial data.
+# 
+# source(file = "data.wrangling.R")
+# 
+# 
+# # Plots
+# 
+# df_heart_all <-
+#   read_rds(file = "final_data/heart_all.rds") |> 
+#   mutate(status = factor(status,
+#                          levels = c("Expert","Novice"),
+#                          labels = c("Expert","Novice")
+#                          )
+#          )
+# 
+# df_heart_min <-
+#   read_rds(file = "final_data/heart_min.rds")
+# 
+# df_heart_aggr <- 
+#   read_rds(file = "final_data/heart_aggr.rds") |> 
+#   mutate(status = factor(status,
+#                          levels = c("Novice","Expert"),
+#                          labels = c("Novice","Expert")
+#                          )
+#          )
+# 
+# plot_flow <-
+# ggplot(data = df_heart_all,
+#        mapping = aes(x = as.numeric(Time),
+#                      y = `Heart Rate`,
+#                      group = ID)
+#        ) +
+#   geom_line(mapping = aes(color = status),
+#             size = 0.3,
+#             alpha = 1
+#             ) +
+#   xlim(0, min(df_heart_min$min)) +
+#   scale_color_viridis_d(option = "A",
+#                        end = 0.8)  +
+#   scale_linetype_manual(values = c(1, 6)) +
+#   labs(x = "Time (in Seconds)",
+#        y = "Heart Rate\n(in Beats per Minute)") +
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         legend.position = "none",
+#         strip.text = element_text(size = 16)) +
+#   facet_grid(cols = vars(Type),
+#              scales = "free_x")
+# 
+# plot_flow_leg <-
+# ggplot(data = df_heart_all,
+#        mapping = aes(x = Time,
+#                      y = `Heart Rate`
+#                      )
+#        ) +
+#   geom_smooth(mapping = aes(color = status),
+#               method = "loess") +
+#   scale_color_viridis_d(option = "A",
+#                         end = 0.8) +
+#  # scale_linetype_manual(values = c(1, 6)) +
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         legend.title = element_blank()) 
+# 
+# legend <- cowplot::get_legend(plot_flow_leg)
+# 
+# plot_loess <-
+# ggplot(data = filter(df_heart_all),
+#        mapping = aes(x = as.numeric(Time),
+#                      y = `Heart Rate`
+#                      )
+#        ) +
+#   stat_smooth(geom = "line",
+#               mapping = aes(color = status),
+#               method = "loess",
+#               se = FALSE) +
+#   xlim(0,min(df_heart_min$min)) +
+#   scale_color_viridis_d(option = "A",
+#                         end = 0.8) +
+#   scale_linetype_manual(values = c(1, 6)) +
+#   labs(x = "Time (in Seconds)",
+#        y = "Heart Rate\n(in Beats per Minute)") +
+#   theme_minimal() +
+#   facet_grid(cols = vars(Type),
+#              scales = "free_x",
+#              ) +
+#   theme(text = element_text(family = "serif"),
+#         legend.position = "none",
+#         strip.background = element_blank(),
+#         strip.text.x = element_blank()
+#         )
+# 
+# plot_box <- 
+# ggplot(data = df_heart_aggr,
+#        mapping = aes(x = Type,
+#                      y = mean,
+#                      color = status
+#                      )
+#        ) +
+#   geom_boxplot(color = "darkgrey",
+#                fill = "grey") +
+#   geom_line(data = filter(df_heart_aggr,
+#                           status == "Novice"),
+#             mapping = aes(x = Type,
+#                           y = mean,
+#                           group = as_factor(ID)
+#                           ),
+#             linetype = 1,
+#             alpha = 0.5
+#             ) +
+#   geom_line(data = filter(df_heart_aggr,
+#                           status == "Expert"),
+#             mapping = aes(x = Type,
+#                           y = mean,
+#                           group = as_factor(ID)
+#                           ),
+#             linetype = 6,
+#             alpha = 0.5
+#             ) +
+#   geom_point(size = 2,
+#              alpha = 0.5) +
+#   labs(x = "",
+#        y = "Average Heart Rate\n(in Beats per Minute)") +
+#   scale_color_viridis_d(option = "A",
+#                        end = 0.8) +
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         strip.text = element_blank(),
+#        legend.position = "none",
+#         axis.text.x = element_blank()
+#         ) +
+#   aes(fill = Type)
+# 
+# lo_mat <- rbind(c(1,1,1,1,1,1,NA),
+#                 c(2,2,2,2,2,2,4),
+#                 c(3,3,3,3,3,3,NA))
+# 
+# plot_heart <- 
+# grid.arrange(grobs = list(plot_flow, plot_loess, plot_box, legend),
+#              layout_matrix = lo_mat)
+# 
+# plot_heart
+```
+
+### Steps
+
+Using the FitBit we measured the steps a person walked during the experiment as well.
+We validated the steps in six randomly selected videos by manual step counting.
+A step was considered to be the movement of the subject's foot forward, backward, or sideways.
+The measurement was not as reliable as hoped.
+
+```{r}
+# df_steps <- read_rds(file = "final_data/steps.rds")
+# set.seed(5678)
+# ggplot(data = df_steps,
+#        mapping = aes(x = type,
+#                      y = Steps
+#                      )
+#        ) +
+#   geom_boxplot(mapping = aes(color = type),
+#                fill = "grey",
+#                alpha = 0.6) +
+#   geom_jitter(mapping = aes(color = type),
+#               alpha = 0.9,
+#               width = 0.3) + 
+#   scale_color_viridis_d(option = "A",
+#                        end = 0.8) +
+#   labs(x = "",
+#        y = "Steps During\nMain Phase") +
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         legend.title = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.ticks.x = element_blank()
+#         ) 
+# 
+# ### Validation of steps 
+# # selecting some rows at random with sample_n()
+# sample_n(df_steps, 6)
+# 
+# # random ID Output:
+# # Novices ID: 102, 125, 110
+# # Experts ID: 219, 218, 214
+# 
+# # Results from manual step counting:
+# # Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
+# # Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps
+
+```
+
 # Results
 
-# Discussion
+# Discussion and implication
 

### 2022-09-12 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
fitbit paper

@@
 
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Especially the first five years are a crucial time the teaching profession, whether the development from novice to expert is experienced as successful and as an increase in competence or leads to the fact that between 40 and 50 percent of the beginning teachers left the profession (Ingersoll \& Smith, 2003; Prilleltensky, Neff, \& Bessell, 2016).
+One reason among many why teachers end their careers is the demanding workload and resulting stress in the teaching profession (Struyven \& Vanthournout, 2014).
+In her study with 400 secondary teachers, Fisher (2011) showed that burnout scores were significantly different between novice and experienced teachers, whereby novices had higher burnout.
+Furthermore, she found that low years of experience was a statistically significant predictor for stress in the teaching profession, along with job satisfaction and burnout.
+
+XXX ÜBERGANG VON STRESS ZU HEART RATE XXX
+
+The heart rate is considered an indicator of physical or emotional stress.
+Increased workload is accompanied by increased heart rate.
+Therefore, heart rate can be considered the most important psycho physiological parameter (Sachs, 2014).
+
+XXX ÜBERGANG VON HEART RATE ZU SMARTWATCHES - VORTEILE XXX low-cost, non-invasive, wrist-worn devices
+
+There is a gap in research on whether heart rate measurements using fitness watches are appropriate to detect differences between experienced and inexperienced teachers in a laboratory setting.
+
+\hypertarget{aim-of-the-study}{%
+\subsection{Aim of the study}\label{aim-of-the-study}}
+
+The aim of the study was to uncover differences between 25 experienced and 25 inexperienced teachers on the physical and emotional demands during a 15-minute micro-teaching unit by measuring their heart rate using a fitness watch (Fitbit Charge 4).
+As the fitness watch was put on at the beginning of the survey and was not taken off until the entire data collection was completed, the heart rate could be measured in the resting and arousal states.
+In addition, the watch recorded the subjects' movement activity to determine how many steps were taken during the lesson.
+The practicality of the FitBit for classroom research is discussed.
+
 \hypertarget{methods}{%
@@
 We used a Fitbit Charge 4 to measure the teachers' heart rate.
-The device was attached 2-finger widths above the ulnar styloid process to the partipant's wrist following the manufacturer's instructions.
+The device was attached 2-finger widths above the ulnar styloid process to the subject's wrist following the manufacturer's instructions.
 To determine the heart rate, the Fitbit flashes green LEDs many times per second and uses light-sensitive photodiodes to measure the volume changes in the capillaries and then calculates how many times the heart beats per minute (bpm).
@@
 
+\hypertarget{fitbit}{%
+\subsubsection{FitBit}\label{fitbit}}
+
+All participants were given a FitBit Smart Watch Charge 4 to wear during the experiment.
+
+\hypertarget{heart-rate}{%
+\subsection{Heart Rate}\label{heart-rate}}
+
+The heart rate of each subject were measured before, during and after the experiment.
+
+XXX Data and data wrangling need to be imported XXX
+
+\hypertarget{steps}{%
+\subsubsection{Steps}\label{steps}}
+
+Using the FitBit we measured the steps a person walked during the experiment as well.
+We validated the steps in six randomly selected videos by manual step counting.
+A step was considered to be the movement of the subject's foot forward, backward, or sideways.
+The measurement was not as reliable as hoped.
+
 \hypertarget{results}{%
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\hypertarget{discussion-and-implication}{%
+\section{Discussion and implication}\label{discussion-and-implication}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-fisher2011factors}{}}%
+Fisher, M. H. (2011). Factors influencing stress, burnout, and retention of secondary teachers. \emph{Current Issues in Education}, \emph{14}(1).
+
 \leavevmode\vadjust pre{\hypertarget{ref-gold2015development}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ingersoll2003wrong}{}}%
+Ingersoll, R. M., \& Smith, T. M. (2003). The wrong solution to the teacher shortage. \emph{Educational Leadership}, \emph{60}(8), 30--33.
+
 \leavevmode\vadjust pre{\hypertarget{ref-palmer2005identifying}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-prilleltensky2016teacher}{}}%
+Prilleltensky, I., Neff, M., \& Bessell, A. (2016). Teacher stress: What it is, why it's important, how it can be alleviated. \emph{Theory Into Practice}, \emph{55}(2), 104--111.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. (2022). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sachs2014physiologische}{}}%
+Sachs, S. (2014). \emph{Physiologische parameter zur bewertung der lernwirksamkeit von lernsituationen} (PhD thesis). Universit{ä}t Ulm.
+
+\leavevmode\vadjust pre{\hypertarget{ref-struyven2014teachers}{}}%
+Struyven, K., \& Vanthournout, G.
+(2014).
+Teachers' exit decisions: An investigation into the reasons why newly qualified teachers fail to enter the teaching profession or why those who do enter do not continue teaching.
+\emph{Teaching and Teacher Education}, \emph{43}, 37--45.
 

### 2022-09-15 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update fitbit

@@
 ---
-title             : "A Walk In The Classroom - Using Fitbit Charge 4 to measure expert and novice teachers’ heart rate and step counts in a laboratory study"
+title             : "New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?"
 shorttitle        : "Measuring novice and expert teachers' heart rate"
@@
       - "Conceptualization"
+      - "Writing - Original Draft Preparation"
+      - "Writing - Review & Editing"
+  - name          : "Christin Lotz"
+    affiliation   : "1"
+    role:
+      - "Conceptualization"
+      - "Writing - Original Draft Preparation"
       - "Writing - Review & Editing"
@@
 # Introduction
-Especially the first five years are a crucial time the teaching profession, whether the development from novice to expert is experienced as successful and as an increase in competence or leads to the fact that between 40 and 50 percent of the beginning teachers left the profession [@ingersoll2003wrong; @prilleltensky2016teacher].
-One reason among many why teachers end their careers is the demanding workload and resulting stress in the teaching profession [@struyven2014teachers].
-In her study with 400 secondary teachers, @fisher2011factors showed that burnout scores were significantly different between novice and experienced teachers, whereby novices had higher burnout.
-Furthermore, she found that low years of experience was a statistically significant predictor for stress in the teaching profession, along with job satisfaction and burnout.
 
-XXX ÜBERGANG VON STRESS ZU HEART RATE XXX
+Prospective teachers experience the first five years as a particular professional challenge, as they are associated with a high workload (e.g., class size, poor student behavior) and resulting stress in the teaching profession [@struyven2014teachers].
 
-The heart rate is considered an indicator of physical or emotional stress.
-Increased workload is accompanied by increased heart rate.
-Therefore, heart rate can be considered the most important psycho physiological parameter [@sachs2014physiologische].
+Psychosomatic stress symptoms, such as increasing heart rate, result from an interaction of situational stressors and person-specific available resources ["transactional stress model"; @lazarus1987transactional; @obbarius2021modified].
+If teachers are exposed to a stressful teaching-learning environment for a long time and do not have the sufficient resources and coping strategies, this can lead to burnout.
 
-XXX ÜBERGANG VON HEART RATE ZU SMARTWATCHES - VORTEILE XXX low-cost, non-invasive, wrist-worn devices
+Fisher (2011) showed in her study of 400 secondary school teachers that burnout scores differed significantly between novice and experienced teachers, with novices having higher burnout scores.
+In addition, she found that a low number of years of professional experience was a statistically significant predictor of stress in the teaching profession, along with job satisfaction and burnout.
 
-There is a gap in research on whether heart rate measurements using fitness watches are appropriate to detect differences between experienced and inexperienced teachers in a laboratory setting.
+In addition to self-reported indicators of stress (e.g., emotional exhaustion), psychophysiological indicators (e.g., heart rate) are becoming increasingly important in research.
+Heart rate as the number of heart contractions per minute [@Löllgen2015] is an important indicator of physical or emotional stress.
+Increased workload is associated with increased heart rate [@sachs2014physiologische].
+Arguably, physiological data provide a more objective and non-reactive measure of stress in the classroom (Runge et al., 2020).
+However, in an educational context, this requires the use of low-cost, non-invasive instruments.
+Fitness trackers worn on the wrist could fill this research gap [@ferguson2015validity].
 

### 2022-09-15 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
update fitbit

@@
 \hypersetup{
-  pdftitle={A Walk In The Classroom - Using Fitbit Charge 4 to measure expert and novice teachers' heart rate and step counts in a laboratory study},
-  pdfauthor={Mandy Klatt1, Peer Keßler1, Gregor Kachel1,2, \& Anne Deiglmayr1},
+  pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
+  pdfauthor={Mandy Klatt1, Peer Keßler1, Gregor Kachel1,2, Christin Lotz1, \& Anne Deiglmayr1},
   pdflang={en-EN},
@@
 
-\title{A Walk In The Classroom - Using Fitbit Charge 4 to measure expert and novice teachers' heart rate and step counts in a laboratory study}
-\author{Mandy Klatt\textsuperscript{1}, Peer Keßler\textsuperscript{1}, Gregor Kachel\textsuperscript{1,2}, \& Anne Deiglmayr\textsuperscript{1}}
+\title{New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?}
+\author{Mandy Klatt\textsuperscript{1}, Peer Keßler\textsuperscript{1}, Gregor Kachel\textsuperscript{1,2}, Christin Lotz\textsuperscript{1}, \& Anne Deiglmayr\textsuperscript{1}}
 \date{}
@@
 The authors made the following contributions.
-Mandy Klatt: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Peer Keßler: Writing - Original Draft Preparation, Writing - Review \& Editing; Gregor Kachel: Conceptualization, Writing - Review \& Editing; Anne Deiglmayr: Supervision.
+Mandy Klatt: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Peer Keßler: Writing - Original Draft Preparation, Writing - Review \& Editing; Gregor Kachel: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Christin Lotz: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Anne Deiglmayr: Supervision.
 
@@
 
-Especially the first five years are a crucial time the teaching profession, whether the development from novice to expert is experienced as successful and as an increase in competence or leads to the fact that between 40 and 50 percent of the beginning teachers left the profession (Ingersoll \& Smith, 2003; Prilleltensky, Neff, \& Bessell, 2016).
-One reason among many why teachers end their careers is the demanding workload and resulting stress in the teaching profession (Struyven \& Vanthournout, 2014).
-In her study with 400 secondary teachers, Fisher (2011) showed that burnout scores were significantly different between novice and experienced teachers, whereby novices had higher burnout.
-Furthermore, she found that low years of experience was a statistically significant predictor for stress in the teaching profession, along with job satisfaction and burnout.
+Prospective teachers experience the first five years as a particular professional challenge, as they are associated with a high workload (e.g., class size, poor student behavior) and resulting stress in the teaching profession (Struyven \& Vanthournout, 2014).
 
-XXX ÜBERGANG VON STRESS ZU HEART RATE XXX
+Psychosomatic stress symptoms, such as increasing heart rate, result from an interaction of situational stressors and person-specific available resources {[}``transactional stress model''; Lazarus and Folkman (1987); Obbarius, Fischer, Liegl, Obbarius, and Rose (2021){]}.
+If teachers are exposed to a stressful teaching-learning environment for a long time and do not have the sufficient resources and coping strategies, this can lead to burnout.
 
-The heart rate is considered an indicator of physical or emotional stress.
-Increased workload is accompanied by increased heart rate.
-Therefore, heart rate can be considered the most important psycho physiological parameter (Sachs, 2014).
+Fisher (2011) showed in her study of 400 secondary school teachers that burnout scores differed significantly between novice and experienced teachers, with novices having higher burnout scores.
+In addition, she found that a low number of years of professional experience was a statistically significant predictor of stress in the teaching profession, along with job satisfaction and burnout.
 
-XXX ÜBERGANG VON HEART RATE ZU SMARTWATCHES - VORTEILE XXX low-cost, non-invasive, wrist-worn devices
-
-There is a gap in research on whether heart rate measurements using fitness watches are appropriate to detect differences between experienced and inexperienced teachers in a laboratory setting.
+In addition to self-reported indicators of stress (e.g., emotional exhaustion), psychophysiological indicators (e.g., heart rate) are becoming increasingly important in research.
+Heart rate as the number of heart contractions per minute (Löllgen, 2015) is an important indicator of physical or emotional stress.
+Increased workload is associated with increased heart rate (Sachs, 2014).
+Arguably, physiological data provide a more objective and non-reactive measure of stress in the classroom (Runge et al., 2020).
+However, in an educational context, this requires the use of low-cost, non-invasive instruments.
+Fitness trackers worn on the wrist could fill this research gap (Ferguson, Rowlands, Olds, \& Maher, 2015).
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-fisher2011factors}{}}%
-Fisher, M. H. (2011). Factors influencing stress, burnout, and retention of secondary teachers. \emph{Current Issues in Education}, \emph{14}(1).
+\leavevmode\vadjust pre{\hypertarget{ref-ferguson2015validity}{}}%
+Ferguson, T., Rowlands, A.
+V., Olds, T., \& Maher, C.
+(2015).
+The validity of consumer-level, activity monitors in healthy adults worn in free-living conditions: A cross-sectional study.
+\emph{International Journal of Behavioral Nutrition and Physical Activity}, \emph{12}(1), 1--9.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ingersoll2003wrong}{}}%
-Ingersoll, R. M., \& Smith, T. M. (2003). The wrong solution to the teacher shortage. \emph{Educational Leadership}, \emph{60}(8), 30--33.
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1987transactional}{}}%
+Lazarus, R. S., \& Folkman, S. (1987). Transactional theory and research on emotions and coping. \emph{European Journal of Personality}, \emph{1}(3), 141--169.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Luxf6llgen2015}{}}%
+Löllgen, H.
+(2015).
+Herzfrequenz und blutdruck.
+In J.
+Niebauer (Ed.), \emph{Sportkardiologie} (pp.
+87--105).
+Berlin, Heidelberg: Springer Berlin Heidelberg.
+\url{https://doi.org/10.1007/978-3-662-43711-7_9}
+
+\leavevmode\vadjust pre{\hypertarget{ref-obbarius2021modified}{}}%
+Obbarius, N., Fischer, F., Liegl, G., Obbarius, A., \& Rose, M.
+(2021).
+A modified version of the transactional stress concept according to lazarus and folkman was confirmed in a psychosomatic inpatient sample.
+\emph{Frontiers in Psychology}, \emph{12}, 584333.
 
@@
 \emph{Educational Psychologist}, \emph{40}(1), 13--25.
-
-\leavevmode\vadjust pre{\hypertarget{ref-prilleltensky2016teacher}{}}%
-Prilleltensky, I., Neff, M., \& Bessell, A. (2016). Teacher stress: What it is, why it's important, how it can be alleviated. \emph{Theory Into Practice}, \emph{55}(2), 104--111.
 

### 2022-09-16 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/data.wrangling.R
upload fitbit data

@@ -276,13 +276,12 @@ part <- read_xlsx(path = "Data/Heart Rate.xlsx")
 #...............................................................................
 
 part <- filter(part,
-               `ID participant` != 108,
-               `ID participant` != 103,
-    #           `ID participant` != 117,
-               `ID participant` != 121,
-    `ID participant` != 123
-    
-               #`ID participant` != | etc.
+                `ID participant` != 108,
+#                `ID participant` != 103,
+#                `ID participant` != 117,
+#                `ID participant` != 121,
+               `ID participant` != 123
+#                # `ID participant` != | etc.
                )
 
 part <- part$`ID participant`
@@ -459,7 +458,7 @@ part <- read_xlsx(path = "Data/Heart Rate.xlsx")
 part <- filter(part,
                `ID participant` != 108  |
                  `ID participant` != 123
-               #`ID participant` != | etc.
+#                #`ID participant` != | etc.
                )
 
 part <- part$`ID participant`

### 2022-09-24 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/data.wrangling.R
upload fitbit data

@@ -276,12 +276,9 @@ part <- read_xlsx(path = "Data/Heart Rate.xlsx")
 #...............................................................................
 
 part <- filter(part,
-                `ID participant` != 108,
-#                `ID participant` != 103,
-#                `ID participant` != 117,
-#                `ID participant` != 121,
-               `ID participant` != 123
-#                # `ID participant` != | etc.
+                `ID participant` != 126 |
+                 `ID participant` != 132 |
+                 `ID participant` != 134
                )
 
 part <- part$`ID participant`
@@ -456,9 +453,9 @@ part <- read_xlsx(path = "Data/Heart Rate.xlsx")
 #...............................................................................
 
 part <- filter(part,
-               `ID participant` != 108  |
-                 `ID participant` != 123
-#                #`ID participant` != | etc.
+               `ID participant` != 126  |
+                `ID participant` != 132 |
+               `ID participant` != 134  
                )
 
 part <- part$`ID participant`

### 2022-09-24 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/FitBit_ET_Glasses_Methods.Rmd
update R script fitbit filter

@@
 
+############### FLOW PLOT #############
 plot_flow <-
@@
 
+############### LOESS PLOT #############
+
 plot_loess <-
@@
         )
+
+############### BOX PLOT #############
 

### 2022-09-24 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/data.wrangling.R

@@ -275,12 +275,12 @@ part <- read_xlsx(path = "Data/Heart Rate.xlsx")
 #                                                                              .
 #...............................................................................
 
-part <- filter(part,
-                `ID participant` != 126 |
-                 `ID participant` != 132 |
-                 `ID participant` != 134
-               )
-
+part <- part %>% 
+  filter(!`ID participant`%in% c("126", 
+                                 "132", 
+                                 "134")
+         )
+  
 part <- part$`ID participant`
 
 for (i in part) {
@@ -452,11 +452,11 @@ part <- read_xlsx(path = "Data/Heart Rate.xlsx")
 #                                                                              .
 #...............................................................................
 
-part <- filter(part,
-               `ID participant` != 126  |
-                `ID participant` != 132 |
-               `ID participant` != 134  
-               )
+part <- part %>% 
+  filter(!`ID participant`%in% c("126", 
+                                 "132", 
+                                 "134")
+         )
 
 part <- part$`ID participant`
 

### 2022-09-30 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
upload fitbit data

--- 2022-09-24 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/FitBit_ET_Glasses_Methods.Rmd
@@
       gridExtra,
-      imputeTS)
+      imputeTS,
+      DescTools,
+      cowplot,
+      rstatix,
+      ggpubr)
 ```
@@
 
-Run following Code if and only if new data is added to the initial data.
+Run following Code only if new data is added to the initial data.
 
 ```{r message=FALSE, warning=FALSE,include=FALSE}
+# fitbit data
 source(file = "data.wrangling.R")
-```
-# ET Glasses
 
-## Acceleration
+# demographic data
+# prepare data (selected from questionnaire data)
+demo.data <- readxl::read_xlsx("./Data/data_empschul_labor_lehrperson.xlsx")
 
-The Tobii Glases record acceleration data with a frequency of 100Hz. Therefore it should be possible to calculate the walked distance wearing the glasses using the following formulas:
+# select relevant columns
+demo.data <- demo.data %>% select(LI02_01_1,
+                                  LI03_01,
+                                  LI04_01,
+                                  LI06_05)
 
-$$\Delta x_{d,i} = 0.5 (t_{i-1}-t_{i})^2, \text{ with }i=2,...,t_n; d = z,x$$
+# rename columns
+demo.data <- rename(demo.data, c("ID" = "LI06_05",
+                                  "Gender" = "LI02_01_1",
+                                  "Age" = "LI03_01",
+                                  "Teaching Experience" = "LI04_01"))
 
-$$x_d=\sum_{i=1}^n |\Delta x_{d,i}|, \text{ with }i=2,...,t_n; d = z,x$$
+# exclude cases with no fitbit data
+demo.data <- demo.data %>% filter(!ID %in% c("126",
+                                             "132",
+                                             )
+                                  )
 
-$$\sum x=\sqrt{x_z^2+x_x^2}$$
-
-Using these formulas, one brave assumption must be made, that is, for every time period the initial velocity is equal to 0.
-
-The real data gives plausible values.
-
-```{r}
-df_meter_real <- read_rds(file = "final_data/meter_real.rds")
-df_meter_real
-summary(df_meter_real$ges)
-```
-
-On the contrary, simulated situations revealed multiple problems.
-
-For the first simulation the participant was standing still without moving its head and with strong movements of the head respectively.
-A reliable measurement would give the same distance for both situations.
-Afterwards, we simulated two two times 5 meter long walks.
-One time the participant turned around after 5 meters.
-During the other walk the participant walked 5 meters and walked back backwards.
-Again, we expect the glasses to give the same walking distance.
-To test real world situations we simulated two random walks in a simulated class room. One walk simulated an extensive walk and the other walk simulated a less intense walk.
-Additionally, we tested the values for taking the elevator and walking a staircase.
-The simulated situations give the following values.
-
-```{r}
-df_meter_sim <- read_rds(file = "final_data/meter_test.rds")
-
-df_meter_sim
-```
-Plotting the acceleration reveals the problems with the acceleration data.
-
-```{r}
-df_meter_sim_time <- read_rds(file = "final_data/meter_test_time.rds")
-
-df_meter_sim_time %>%
-  pivot_longer(cols = contains("acc"),
-               names_to = "acc") %>%
-ggplot(mapping = aes(x = time,
-                     y = value
-                     )
-       ) +
-  geom_path() +
-  labs(y = "") +
-  theme(text = element_text(family = "serif")) +
-  facet_grid(rows = vars(name),
-             cols = vars(acc) 
-             ) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-## Pupil Dialation
-
-The ET Glasses report the pupil dilation at a frequency of 100 Hz.
-
-```{r}
-# df_dil <- read_rds(file = "final_data/dilation.rds")
-# 
-# df_dil %>%
-#   pivot_longer(cols = right:left,
-#                names_to = "dilation") %>%
-# ggplot(mapping = aes(x = time,
-#                      y = value
-#                      )
-#        ) +
-#   geom_path() +
-#   facet_grid(rows = vars(ID),
-#              cols = vars(dilation)
-#              )
 ```
@@
 
-The heart rate of each participant were measured during the experiment.
-
 ```{r}
-# Plots
+# aggregate data
 
@@
 
-############### FLOW PLOT #############
+# Mean, SD and Cohen D for experts & novices
+# novices
+mean_nov <- 
+  df_heart_aggr %>%
+  filter(status == "Novice" ) %>% 
+  pull(mean) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_nov <- 
+  df_heart_aggr %>%
+  filter(status == "Novice") %>% 
+  pull(mean) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# experts
+mean_exp <-
+  df_heart_aggr %>%
+  filter(status == "Expert") %>% 
+  pull(mean) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_exp <- 
+  df_heart_aggr %>%
+  filter(status == "Expert") %>% 
+  pull(mean) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# effect size for expertise differences
+d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
+               y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
+               na.rm = TRUE)
+
+```
+
+The heart rate of each participant were measured during the experiment.
+
+```{r}
+# Plots
+
+############## FLOW PLOT #############
 plot_flow <-
@@
             ) +
-  xlim(0, min(df_heart_min$min)) +
+  xlim(0, 600) +
   scale_color_viridis_d(option = "A",
@@
 
+############### FLOW PLOT EXPERT NOVICE #############
+
 plot_flow_leg <-
@@
        ) +
+  xlim(0, 600) +
   geom_smooth(mapping = aes(color = status),
@@
                         end = 0.8) +
- # scale_linetype_manual(values = c(1, 6)) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Time (in Seconds)",
+       y = "Heart Rate\n(in Beats per Minute)") +
+  ggtitle("Experts' and novices' heart rate per phase") +
   theme_minimal() +
   theme(text = element_text(family = "serif"),
-        legend.title = element_blank())
+        legend.text = element_text(size = 15),
+        legend.title = element_blank(),
+        axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 10),
+        strip.text = element_text(size = 16),
+        plot.title = element_text(size = 20, 
+                                  face = "bold")) +
+  facet_grid(cols = vars(Type),
+             scales = "free_x")
 
 legend <- cowplot::get_legend(plot_flow_leg)
+
+# saving plot 
+ggsave(plot = plot_flow_leg,
+       filename = "Plots/plot_flow_leg.svg",
+       height = 5,
+       width = 8,
+       units = "in")
 
@@
               se = FALSE) +
-  xlim(0,min(df_heart_min$min)) +
+  xlim(0,600) +
   scale_color_viridis_d(option = "A",
@@
 
-plot_box <- 
+##### Box 1 Plot ##### 
+plot_box1 <- 
 ggplot(data = df_heart_aggr,
@@
 
-lo_mat <- rbind(c(1,1,1,1,1,1,NA),
-                c(2,2,2,2,2,2,4),
-                c(3,3,3,3,3,3,NA))
+plot_box1
 
-plot_heart <- 
-grid.arrange(grobs = list(plot_flow, plot_loess, plot_box, legend),
-             layout_matrix = lo_mat)
+##### Box 2 Plot ##### 
+plot_box <-
+  ggplot(data = df_heart_aggr,
+         mapping = aes(x = Type,
+                       y = mean)) + 
+  geom_boxplot(mapping = aes(fill = status),
+               outlier.shape = NA) +
+  geom_point(mapping = aes(shape = status),
+             alpha = 0.5,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  labs(x ="",
+       y = "Average Heart Rate\n(in Beats per Minute)") + 
+  ggtitle("Experts' and novices' heart rate per phase") +
+  scale_fill_brewer(palette  = "RdBu") +  
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        legend.text = element_text(size = 15),
+        legend.title = element_blank(),
+        axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 10),
+        strip.text = element_text(size = 16),
+        plot.title = element_text(size = 20, 
+                                  face = "bold"))
 
-plot_heart
+plot_box
+
+# saving plot 
+ggsave(plot = plot_box,
+       filename = "Plots/plot_box.svg",
+       height = 5,
+       width = 8,
+       units = "in")
+
+##############
+
+# lo_mat <- rbind(c(1,1,1,1,1,1,NA),
+#                 c(2,2,2,2,2,2,4),
+#                 c(3,3,3,3,3,3,NA))
+# 
+# plot_heart <- 
+# grid.arrange(grobs = list(plot_flow, plot_loess, plot_box1, legend),
+#              layout_matrix = lo_mat)
+# 
+# plot_heart
+
+```
+
+# Repeated Measures ANOVA
+
+```{r}
+
+# merge demo data and fitbit data
+df_anova <- merge(demo.data,
+                  df_heart_aggr,
+                  by="ID")
+
+# clean variable names
+df_anova <- df_anova %>% clean_names()
+
+# check for outliers
+outliers <-
+  df_anova %>%
+  group_by(type) %>%
+  identify_outliers(mean)
+
+# check for normality assumption --> can be checked by computing Shapiro-Wilk test for each time point. If the data is normally distributed, the p-value should be greater than 0.05
+norm_assump <-
+  df_anova %>%
+  group_by(type) %>%
+  shapiro_test(mean)
+
+ggqqplot(df_anova, "mean", facet.by = "type")
+
+# anova
+res.aov <- rstatix::anova_test(data = df_anova,
+                               dv = mean,
+                               wid = id,
+                               within = type)
+get_anova_table(res.aov)
+
+# anova expert novice
+res.aov2 <- rstatix::anova_test(data = df_anova,
+                               dv = mean,
+                               between = status,
+                               wid = id,
+                               within = type)
+get_anova_table(res.aov2)
+
+# pairwise comparisons
+pwc <- df_anova %>%
+  pairwise_t_test(
+    mean ~ type, paired = TRUE,
+    p.adjust.method = "bonferroni"
+    )
+pwc
+
+# Visualization: box plots with p-values
+pwc <- 
+  pwc %>% 
+  add_xy_position(x = "type")
+
+# boxplot
+bxp_anova <- ggboxplot(data = df_anova, 
+                 x = "type", 
+                 y = "mean", 
+                 add = "point")
+
+bxp_anova + 
+  stat_pvalue_manual(pwc) +
+  labs(
+    subtitle = get_test_label(res.aov, detailed = TRUE),
+    caption = get_pwc_label(pwc)
+    )
+
+# saving plot 
+ggsave(plot = bxp_anova,
+       filename = "Plots/bxp_anova.svg",
+       height = 5,
+       width = 8,
+       units = "in")
+
 ```

### 2022-09-30 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
fitbit anova
upload fitbit data

@@
 
-keywords          : "heart rate; photoplethysmography; wearable electronic device; expertise differences "
+keywords          : "heart rate; photoplethysmography; wearable electronic device; expertise differences"
 wordcount         : "X"
@@
       DescTools,
-      formattable)
+      formattable,
+      ggthemes,
+      imputeTS,
+      rstatix,
+      ggpubr)
 
@@
 
+# DEMOGRAPHIC DATA
 # read in data and select and rename relevant columns with transmute 
-demo.data <- 
+demo.data.raw <- 
   read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
-  transmute(Group = LI06_05,
+  transmute(ID = LI06_05,
             Gender = LI02_01_1,
@@
 
+# exclude cases with no fitbit data
+demo.data.raw <- demo.data %>% filter(!ID %in% c("126",
+                                                 "132"
+                                                 )
+                                      )
+
 # define expert and novice with ifelse function
-demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")
+demo.data$ID = ifelse(demo.data$ID < 200, "Novice","Expert")
 
@@
 demo.data <- demo.data %>%
-  group_by(Group) %>%
+  group_by(ID) %>%
   mutate(Sum_participants = n())
@@
   demo.data %>%
-  group_by(School_type, Group) %>%
+  group_by(School_type, ID) %>%
   mutate(Count_Schooltype = sum(n())) %>% 
@@
 demo.table <- demo.data %>%
-  group_by(Group) %>%
+  group_by(ID) %>%
   summarise(N=n(),
@@
 exp.table <- demo.data %>%
-  group_by(Group) %>%
+  group_by(ID) %>%
   summarise(N=n(),
@@
 
-XXX  fitbit data exclusion XXX
+The sample consisted of *N* = `r length(demo.data$ID)` participants with *n* = `r length(demo.data$ID[demo.data$ID == "Expert"])` expert teachers and *n* = `r length(demo.data$ID[demo.data$ID == "Novice"])` novice teachers.
 
-The sample consisted of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.
+The data of two participants (two novices, XXX experts) were excluded from the analyses due to insufficient data quality.
 
@@
 
-The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`).
-`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers.
-`r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+The expert teachers (`r demo.data %>% filter(Gender == 1 & ID == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(ID == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(ID == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(ID == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(ID == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(ID == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(ID == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(ID == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(ID == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(ID == "Expert") %>% pull("Max Exp.")`).
+`r demo.data %>% filter(ID == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(ID == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers.
+`r exp.table %>% filter(ID == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
 
-The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years.
-On average, the student teachers were in their `r exp.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`).
-Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies.
-`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype") %>% unique()`% to become special education teachers.
-`r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+The novice teachers (`r demo.data %>% filter(Gender == 1 & ID == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(ID == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(ID == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(ID == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(ID == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(ID == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(ID == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years.
+On average, the student teachers were in their `r exp.table %>% filter(ID == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(ID == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(ID == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(ID == "Novice") %>% pull("Max Semester")`).
+Furthermore, they had an average teaching experience of `r exp.table %>% filter(ID == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(ID == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(ID == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(ID == "Novice") %>% pull("Max Internship")`) through the internships during their studies.
+`r demo.data %>% filter(ID == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(ID == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% to become secondary school teachers and `r demo.data %>% filter(ID == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype") %>% unique()`% to become special education teachers.
+`r exp.table %>% filter(ID == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
 
@@
 
-XXX Data and data wrangling need to be imported XXX 
 ```{r}
-# # Initial Preparations
-# ## Run following Code if and only if new data is added to the initial data.
-# 
-# source(file = "data.wrangling.R")
-# 
-# 
-# # Plots
-# 
-# df_heart_all <-
-#   read_rds(file = "final_data/heart_all.rds") |> 
-#   mutate(status = factor(status,
-#                          levels = c("Expert","Novice"),
-#                          labels = c("Expert","Novice")
-#                          )
-#          )
-# 
-# df_heart_min <-
-#   read_rds(file = "final_data/heart_min.rds")
-# 
-# df_heart_aggr <- 
-#   read_rds(file = "final_data/heart_aggr.rds") |> 
-#   mutate(status = factor(status,
-#                          levels = c("Novice","Expert"),
-#                          labels = c("Novice","Expert")
-#                          )
-#          )
-# 
-# plot_flow <-
-# ggplot(data = df_heart_all,
-#        mapping = aes(x = as.numeric(Time),
-#                      y = `Heart Rate`,
-#                      group = ID)
-#        ) +
-#   geom_line(mapping = aes(color = status),
-#             size = 0.3,
-#             alpha = 1
-#             ) +
-#   xlim(0, min(df_heart_min$min)) +
-#   scale_color_viridis_d(option = "A",
-#                        end = 0.8)  +
-#   scale_linetype_manual(values = c(1, 6)) +
-#   labs(x = "Time (in Seconds)",
-#        y = "Heart Rate\n(in Beats per Minute)") +
-#   theme_minimal() +
-#   theme(text = element_text(family = "serif"),
-#         legend.position = "none",
-#         strip.text = element_text(size = 16)) +
-#   facet_grid(cols = vars(Type),
-#              scales = "free_x")
-# 
-# plot_flow_leg <-
-# ggplot(data = df_heart_all,
-#        mapping = aes(x = Time,
-#                      y = `Heart Rate`
-#                      )
-#        ) +
-#   geom_smooth(mapping = aes(color = status),
-#               method = "loess") +
-#   scale_color_viridis_d(option = "A",
-#                         end = 0.8) +
-#  # scale_linetype_manual(values = c(1, 6)) +
-#   theme_minimal() +
-#   theme(text = element_text(family = "serif"),
-#         legend.title = element_blank()) 
-# 
-# legend <- cowplot::get_legend(plot_flow_leg)
-# 
-# plot_loess <-
-# ggplot(data = filter(df_heart_all),
-#        mapping = aes(x = as.numeric(Time),
-#                      y = `Heart Rate`
-#                      )
-#        ) +
-#   stat_smooth(geom = "line",
-#               mapping = aes(color = status),
-#               method = "loess",
-#               se = FALSE) +
-#   xlim(0,min(df_heart_min$min)) +
-#   scale_color_viridis_d(option = "A",
-#                         end = 0.8) +
-#   scale_linetype_manual(values = c(1, 6)) +
-#   labs(x = "Time (in Seconds)",
-#        y = "Heart Rate\n(in Beats per Minute)") +
-#   theme_minimal() +
-#   facet_grid(cols = vars(Type),
-#              scales = "free_x",
-#              ) +
-#   theme(text = element_text(family = "serif"),
-#         legend.position = "none",
-#         strip.background = element_blank(),
-#         strip.text.x = element_blank()
-#         )
-# 
-# plot_box <- 
-# ggplot(data = df_heart_aggr,
-#        mapping = aes(x = Type,
-#                      y = mean,
-#                      color = status
-#                      )
-#        ) +
-#   geom_boxplot(color = "darkgrey",
-#                fill = "grey") +
-#   geom_line(data = filter(df_heart_aggr,
-#                           status == "Novice"),
-#             mapping = aes(x = Type,
-#                           y = mean,
-#                           group = as_factor(ID)
-#                           ),
-#             linetype = 1,
-#             alpha = 0.5
-#             ) +
-#   geom_line(data = filter(df_heart_aggr,
-#                           status == "Expert"),
-#             mapping = aes(x = Type,
-#                           y = mean,
-#                           group = as_factor(ID)
-#                           ),
-#             linetype = 6,
-#             alpha = 0.5
-#             ) +
-#   geom_point(size = 2,
-#              alpha = 0.5) +
-#   labs(x = "",
-#        y = "Average Heart Rate\n(in Beats per Minute)") +
-#   scale_color_viridis_d(option = "A",
-#                        end = 0.8) +
-#   theme_minimal() +
-#   theme(text = element_text(family = "serif"),
-#         strip.text = element_blank(),
-#        legend.position = "none",
-#         axis.text.x = element_blank()
-#         ) +
-#   aes(fill = Type)
-# 
-# lo_mat <- rbind(c(1,1,1,1,1,1,NA),
-#                 c(2,2,2,2,2,2,4),
-#                 c(3,3,3,3,3,3,NA))
-# 
-# plot_heart <- 
-# grid.arrange(grobs = list(plot_flow, plot_loess, plot_box, legend),
-#              layout_matrix = lo_mat)
-# 
-# plot_heart
+# Initial Preparations
+## Run following Code if and only if new data is added to the initial data.
+
+source(file = "data.wrangling.R")
+
+# Mean, SD, t-test & Cohen D for experts & novices
+# novices
+mean_nov <- 
+  df_heart_aggr %>%
+  filter(status == "Novice" ) %>% 
+  pull(mean) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_nov <- 
+  df_heart_aggr %>%
+  filter(status == "Novice") %>% 
+  pull(mean) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# experts
+mean_exp <-
+  df_heart_aggr %>%
+  filter(status == "Expert") %>% 
+  pull(mean) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_exp <- 
+  df_heart_aggr %>%
+  filter(status == "Expert") %>% 
+  pull(mean) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# t-test for expertise differences
+t.test(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
+       y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"])
+
+# effect size for expertise differences
+d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
+               y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
+               na.rm = TRUE)
+
+# Plots
+
+df_heart_all <-
+  read_rds(file = "data/heart_all.rds") |>
+  mutate(status = factor(status,
+                         levels = c("Expert","Novice"),
+                         labels = c("Expert","Novice")
+                         )
+         )
+
+df_heart_min <-
+  read_rds(file = "data/heart_min.rds")
+
+df_heart_aggr <-
+  read_rds(file = "data/heart_aggr.rds") |>
+  mutate(status = factor(status,
+                         levels = c("Novice","Expert"),
+                         labels = c("Novice","Expert")
+                         )
+         )
+
+plot_flow_leg <-
+ggplot(data = df_heart_all,
+       mapping = aes(x = Time,
+                     y = `Heart Rate`
+                     )
+       ) +
+  xlim(0, 600) +
+  geom_smooth(mapping = aes(color = status),
+              method = "loess") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Time (in Seconds)",
+       y = "Heart Rate\n(in Beats per Minute)") +
+  ggtitle("Experts' and novices' heart rate per phase") +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        legend.text = element_text(size = 15),
+        legend.title = element_blank(),
+        axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 10),
+        strip.text = element_text(size = 16),
+        plot.title = element_text(size = 20, 
+                                  face = "bold")) +
+  facet_grid(cols = vars(Type),
+             scales = "free_x")
+
+legend <- cowplot::get_legend(plot_flow_leg)
+
+# saving plot 
+ggsave(plot = plot_flow_leg,
+       filename = "Plots/plot_flow_leg.svg",
+       height = 5,
+       width = 8,
+       units = "in")
+
+############### BOX PLOT #############
+
+##### Box 1 Plot ##### 
+plot_box1 <- 
+ggplot(data = df_heart_aggr,
+       mapping = aes(x = Type,
+                     y = mean,
+                     color = status
+                     )
+       ) +
+  geom_boxplot(color = "darkgrey",
+               fill = "grey") +
+  geom_line(data = filter(df_heart_aggr,
+                          status == "Novice"),
+            mapping = aes(x = Type,
+                          y = mean,
+                          group = as_factor(ID)
+                          ),
+            linetype = 1,
+            alpha = 0.5
+            ) +
+  geom_line(data = filter(df_heart_aggr,
+                          status == "Expert"),
+            mapping = aes(x = Type,
+                          y = mean,
+                          group = as_factor(ID)
+                          ),
+            linetype = 6,
+            alpha = 0.5
+            ) +
+  geom_point(size = 2,
+             alpha = 0.5) +
+  labs(x = "",
+       y = "Average Heart Rate\n(in Beats per Minute)") +
+  scale_color_viridis_d(option = "A",
+                       end = 0.8) +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        strip.text = element_blank(),
+        legend.position = "none",
+        axis.text.x = element_blank()
+        ) +
+  aes(fill = Type)
+
+plot_box1
+
+##### Box 2 Plot ##### 
+plot_box <-
+  ggplot(data = df_heart_aggr,
+         mapping = aes(x = Type,
+                       y = mean)) + 
+  geom_boxplot(mapping = aes(fill = status),
+               outlier.shape = NA) +
+  geom_point(mapping = aes(shape = status),
+             alpha = 0.5,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  labs(x ="",
+       y = "Average Heart Rate\n(in Beats per Minute)") + 
+  ggtitle("Experts' and novices' heart rate per phase") +
+  scale_fill_brewer(palette  = "RdBu") +  
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        legend.text = element_text(size = 15),
+        legend.title = element_blank(),
+        axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 10),
+        strip.text = element_text(size = 16),
+        plot.title = element_text(size = 20, 
+                                  face = "bold"))
+
+plot_box
+
+# saving plot 
+ggsave(plot = plot_box,
+       filename = "Plots/plot_box.svg",
+       height = 5,
+       width = 8,
+       units = "in")
+
 ```
@@
 ```{r}
-# df_steps <- read_rds(file = "final_data/steps.rds")
-# set.seed(5678)
-# ggplot(data = df_steps,
-#        mapping = aes(x = type,
-#                      y = Steps
-#                      )
-#        ) +
-#   geom_boxplot(mapping = aes(color = type),
-#                fill = "grey",
-#                alpha = 0.6) +
-#   geom_jitter(mapping = aes(color = type),
-#               alpha = 0.9,
-#               width = 0.3) + 
-#   scale_color_viridis_d(option = "A",
-#                        end = 0.8) +
-#   labs(x = "",
-#        y = "Steps During\nMain Phase") +
-#   theme_minimal() +
-#   theme(text = element_text(family = "serif"),
-#         legend.title = element_blank(),
-#         axis.text.x = element_blank(),
-#         axis.ticks.x = element_blank()
-#         ) 
-# 
-# ### Validation of steps 
-# # selecting some rows at random with sample_n()
-# sample_n(df_steps, 6)
-# 
-# # random ID Output:
-# # Novices ID: 102, 125, 110
-# # Experts ID: 219, 218, 214
-# 
-# # Results from manual step counting:
-# # Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
-# # Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps
+df_steps <- read_rds(file = "data/steps.rds")
+set.seed(5678)
+ggplot(data = df_steps,
+       mapping = aes(x = type,
+                     y = Steps
+                     )
+       ) +
+  geom_boxplot(mapping = aes(color = type),
+               fill = "grey",
+               alpha = 0.6) +
+  geom_jitter(mapping = aes(color = type),
+              alpha = 0.9,
+              width = 0.3) +
+  scale_color_viridis_d(option = "A",
+                       end = 0.8) +
+  labs(x = "",
+       y = "Steps During\nMain Phase") +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        legend.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()
+        )
+
+### Validation of steps
+# selecting some rows at random with sample_n()
+sample_n(df_steps, 6)
+
+# random ID Output:
+# Novices ID: 102, 125, 110
+# Experts ID: 219, 218, 214
+
+# Results from manual step counting:
+# Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
+# Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps
 

### 2022-09-30 02_paper/02_study/02_fitbit paper/data.wrangling.R

@@ -1,273 +1,7 @@
-rm(list = ls())
 
-##### 1. Test Data #####
+##### I. Heart Rate ####
 
-
-df_test <- read_tsv(file = "data/Acc_Test_Data.tsv") %>% 
-  clean_names() %>%
-  transmute(time = as.numeric(milliseconds(recording_timestamp_ms)
-                              ),
-  name = participant_name,
-  acc_x = as.numeric(str_replace(accelerometer_x_m_s2,
-                                 pattern = ",",
-                                 replacement = "."
-                                 )
-                     ),
-  acc_z = as.numeric(str_replace(accelerometer_z_m_s2,
-                                 pattern = ",",
-                                 replacement = "."
-                                 )
-                     )
-  )
-
-# First step: create tibbles for each individual.
-for (i in unique(df_test$name)) {
-  
-  df <- filter(df_test,
-               name == i
-               )
-  
-  assign(value = df,
-         x = paste0("df_", i)
-         )
-  }
-
-# For each of the tibbles, create two vectors (x and z) 
-# for meters for each time period.
-
-for (i in unique(df_test$name)) {
-  
-  df <- get(paste0("df_", i))
-  
-  # Vectors x and z with length equal to time periods 
-  # present in each tibble; initial with 0 meters for each   # time period. 
-  
-  x <- rep(0, length(get(paste0("df_", i))$time))
-  z <- rep(0, length(get(paste0("df_", i))$time))
-  
-  # For each time period, calculate the meters walked in 
-  # two dimensions (x and z), given the initial velocity 
-  # for each period is 0 m/s. First value stays 0 for
-  # convenience.
-  # See formula 1.
-  
-  for (j in 2:length(get(paste0("df_", i))$time)) {
-    
-    x[[j]] <- 0.5 * get(paste0("df_", i))$acc_x[j] * (get(paste0("df_", i))$time[j] - get(paste0("df_", i))$time[j-1])^2
-    
-    z[[j]] <- 0.5 * get(paste0("df_", i))$acc_z[j] * (get(paste0("df_", i))$time[j] - get(paste0("df_", i))$time[j-1])^2
-    
-  }
-  
-  # Save both vectors in new tibble.
-  
-  df <- tibble(meter_x = x,
-               meter_z = z,
-               ID = paste0(i))
-  assign(x = paste0("df_meter_", i),
-         value = df)
-  }
-
-# Combine all tibbles containing distance walked per 
-# time period.
-# Calculate sum of absolute distance walked for each 
-# participant and dimension.
[…]

### 2022-10-19 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
upload data

@@
 title             : "New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?"
-shorttitle        : "Measuring novice and expert teachers' heart rate"
+shorttitle        : "Using fitbit to measure teachers' heart rate"
 
@@
 ```
+
+```{r, include=FALSE}
+options(tinytex.verbose = TRUE)
+```
+
 # Introduction
+Physiological data such as heart rate are becoming increasingly important in research on stress experience.
+They represent an important indicator of physical or emotional stress, as increased workload is associated with increased heart rate [@sachs2014physiologische].
+Furthermore, they allow a more objective recording of stress than self-reports [@rungeusing].
+However, capturing heart rate in an educational context requires the use of low-cost and non-invasive instruments.
+Fitness trackers worn on the wrist have the potential to be such a useful tool [@ferguson2015validity].
 
-Prospective teachers experience the first five years as a particular professional challenge, as they are associated with a high workload (e.g., class size, poor student behavior) and resulting stress in the teaching profession [@struyven2014teachers].
+To date, there is still little evidence on the usefulness of heart rate measurements using fitness trackers in teaching and learning settings [@ertzberger2016use; @lowe2016educational].
+@rungeusing alone examined teacher stress in a relatively small sample (*N* = 4 teachers) and showed that high heart rate, high step count, and little sleep indicate more stress in teachers.
 
-Psychosomatic stress symptoms, such as increasing heart rate, result from an interaction of situational stressors and person-specific available resources ["transactional stress model"; @lazarus1987transactional; @obbarius2021modified].
-If teachers are exposed to a stressful teaching-learning environment for a long time and do not have the sufficient resources and coping strategies, this can lead to burnout.
-
-Fisher (2011) showed in her study of 400 secondary school teachers that burnout scores differed significantly between novice and experienced teachers, with novices having higher burnout scores.
-In addition, she found that a low number of years of professional experience was a statistically significant predictor of stress in the teaching profession, along with job satisfaction and burnout.
-
-In addition to self-reported indicators of stress (e.g., emotional exhaustion), psychophysiological indicators (e.g., heart rate) are becoming increasingly important in research.
-Heart rate as the number of heart contractions per minute [@Löllgen2015] is an important indicator of physical or emotional stress.
-Increased workload is associated with increased heart rate [@sachs2014physiologische].
-Arguably, physiological data provide a more objective and non-reactive measure of stress in the classroom (Runge et al., 2020).
-However, in an educational context, this requires the use of low-cost, non-invasive instruments.
-Fitness trackers worn on the wrist could fill this research gap [@ferguson2015validity].
+Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of stress.
+Since, among other things, greater professional experience is associated with lower feelings of stress in the teaching profession [@fisher2011factors], this study will also consider the heart rate measurements of experienced and inexperienced teachers.
 
 ## Aim of the study
-The aim of the study was to uncover differences between 25 experienced and 25 inexperienced teachers on the physical and emotional demands during a 15-minute micro-teaching unit by measuring their heart rate using a fitness watch (Fitbit Charge 4).
-As the fitness watch was put on at the beginning of the survey and was not taken off until the entire data collection was completed, the heart rate could be measured in the resting and arousal states.
-In addition, the watch recorded the subjects' movement activity to determine how many steps were taken during the lesson.
-The practicality of the FitBit for classroom research is discussed.
+Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases and (2) between experienced and inexperienced teachers.
+We expected heart rates to be higher in the arousal phase than in the rest phases and exploratively examine whether experienced teachers have lower heart rates and more steps compared to inexperienced teachers.
 
@@
 # exclude cases with no fitbit data
-demo.data.raw <- demo.data %>% filter(!ID %in% c("126",
+demo.data <- demo.data.raw %>% filter(!ID %in% c("126",
                                                  "132"
@@
 # Initial Preparations
-## Run following Code if and only if new data is added to the initial data.
 
-source(file = "data.wrangling.R")
-
-# Mean, SD, t-test & Cohen D for experts & novices
-# novices
-mean_nov <- 
-  df_heart_aggr %>%
-  filter(status == "Novice" ) %>% 
-  pull(mean) %>% 
-  mean() %>% 
-  round(., digits = 0)
-
-sd_nov <- 
-  df_heart_aggr %>%
-  filter(status == "Novice") %>% 
-  pull(mean) %>% 
-  sd() %>% 
-  round(., digits = 0)
-
-# experts
-mean_exp <-
-  df_heart_aggr %>%
-  filter(status == "Expert") %>% 
-  pull(mean) %>% 
-  mean() %>% 
-  round(., digits = 0)
-
-sd_exp <- 
-  df_heart_aggr %>%
-  filter(status == "Expert") %>% 
-  pull(mean) %>% 
-  sd() %>% 
-  round(., digits = 0)
-
-# t-test for expertise differences
-t.test(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
-       y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"])
-
-# effect size for expertise differences
-d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
-               y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
-               na.rm = TRUE)
-
-# Plots
-
-df_heart_all <-
-  read_rds(file = "data/heart_all.rds") |>
-  mutate(status = factor(status,
-                         levels = c("Expert","Novice"),
-                         labels = c("Expert","Novice")
-                         )
-         )
-
-df_heart_min <-
-  read_rds(file = "data/heart_min.rds")
-
-df_heart_aggr <-
-  read_rds(file = "data/heart_aggr.rds") |>
-  mutate(status = factor(status,
-                         levels = c("Novice","Expert"),
-                         labels = c("Novice","Expert")
-                         )
-         )
-
-plot_flow_leg <-
-ggplot(data = df_heart_all,
-       mapping = aes(x = Time,
-                     y = `Heart Rate`
-                     )
-       ) +
-  xlim(0, 600) +
-  geom_smooth(mapping = aes(color = status),
-              method = "loess") +
-  scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  labs(x = "Time (in Seconds)",
-       y = "Heart Rate\n(in Beats per Minute)") +
-  ggtitle("Experts' and novices' heart rate per phase") +
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        legend.text = element_text(size = 15),
-        legend.title = element_blank(),
-        axis.text.x = element_text(size = 12),
-        axis.text.y = element_text(size = 10),
-        strip.text = element_text(size = 16),
-        plot.title = element_text(size = 20, 
-                                  face = "bold")) +
-  facet_grid(cols = vars(Type),
-             scales = "free_x")
-
-legend <- cowplot::get_legend(plot_flow_leg)
-
-# saving plot 
-ggsave(plot = plot_flow_leg,
-       filename = "Plots/plot_flow_leg.svg",
-       height = 5,
-       width = 8,
-       units = "in")
-
-############### BOX PLOT #############
-
-##### Box 1 Plot ##### 
-plot_box1 <- 
-ggplot(data = df_heart_aggr,
-       mapping = aes(x = Type,
-                     y = mean,
-                     color = status
-                     )
-       ) +
-  geom_boxplot(color = "darkgrey",
-               fill = "grey") +
-  geom_line(data = filter(df_heart_aggr,
-                          status == "Novice"),
-            mapping = aes(x = Type,
-                          y = mean,
-                          group = as_factor(ID)
-                          ),
-            linetype = 1,
-            alpha = 0.5
-            ) +
-  geom_line(data = filter(df_heart_aggr,
-                          status == "Expert"),
-            mapping = aes(x = Type,
-                          y = mean,
-                          group = as_factor(ID)
-                          ),
-            linetype = 6,
-            alpha = 0.5
-            ) +
-  geom_point(size = 2,
-             alpha = 0.5) +
-  labs(x = "",
-       y = "Average Heart Rate\n(in Beats per Minute)") +
-  scale_color_viridis_d(option = "A",
-                       end = 0.8) +
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        strip.text = element_blank(),
-        legend.position = "none",
-        axis.text.x = element_blank()
-        ) +
-  aes(fill = Type)
-
-plot_box1
-
-##### Box 2 Plot ##### 
-plot_box <-
-  ggplot(data = df_heart_aggr,
-         mapping = aes(x = Type,
-                       y = mean)) + 
-  geom_boxplot(mapping = aes(fill = status),
-               outlier.shape = NA) +
-  geom_point(mapping = aes(shape = status),
-             alpha = 0.5,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  labs(x ="",
-       y = "Average Heart Rate\n(in Beats per Minute)") + 
-  ggtitle("Experts' and novices' heart rate per phase") +
-  scale_fill_brewer(palette  = "RdBu") +  
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        legend.text = element_text(size = 15),
-        legend.title = element_blank(),
-        axis.text.x = element_text(size = 12),
-        axis.text.y = element_text(size = 10),
-        strip.text = element_text(size = 16),
-        plot.title = element_text(size = 20, 
-                                  face = "bold"))
-
-plot_box
-
-# saving plot 
-ggsave(plot = plot_box,
-       filename = "Plots/plot_box.svg",
-       height = 5,
-       width = 8,
-       units = "in")
+## Run following Code only if new data is added to the initial data.
+# 
+# source(file = "data.wrangling.R")
+# 
+# # aggregate data 
+# df_heart_all <-
+#   read_rds(file = "data/heart_all.rds") |> 
+#   mutate(status = factor(status,
+#                          levels = c("Expert","Novice"),
+#                          labels = c("Expert","Novice")
+#                          )
+#          )
+# 
+# df_heart_min <-
+#   read_rds(file = "data/heart_min.rds")
+# 
+# df_heart_aggr <- 
+#   read_rds(file = "data/heart_aggr.rds") |> 
+#   mutate(status = factor(status,
+#                          levels = c("Novice","Expert"),
+#                          labels = c("Novice","Expert")
+#                          )
+#          )
+# 
+# 
+# # Mean, SD, t-test & Cohen D for experts & novices
+# # novices
+# mean_nov <- 
+#   df_heart_aggr %>%
+#   filter(status == "Novice" ) %>% 
+#   pull(mean) %>% 
+#   mean() %>% 
+#   round(., digits = 0)
+# 
+# sd_nov <- 
+#   df_heart_aggr %>%
+#   filter(status == "Novice") %>% 
+#   pull(mean) %>% 
+#   sd() %>% 
+#   round(., digits = 0)
+# 
+# # experts
+# mean_exp <-
+#   df_heart_aggr %>%
+#   filter(status == "Expert") %>% 
+#   pull(mean) %>% 
+#   mean() %>% 
+#   round(., digits = 0)
+# 
+# sd_exp <- 
+#   df_heart_aggr %>%
+#   filter(status == "Expert") %>% 
+#   pull(mean) %>% 
+#   sd() %>% 
+#   round(., digits = 0)
+# 
+# # t-test for expertise differences
+# t.test(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
+#        y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"])
+# 
+# 
+# # effect size for expertise differences
+# d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
+#                y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
+#                na.rm = TRUE)
+# 
+# 
+# # Plots
+# 
+# plot_flow_leg <-
+# ggplot(data = df_heart_all,
+#        mapping = aes(x = Time,
+#                      y = `Heart Rate`
+#                      )
+#        ) +
+#   xlim(0, 600) +
+#   geom_smooth(mapping = aes(color = status),
+#               method = "loess") +
+#   scale_color_viridis_d(option = "A",
+#                         end = 0.8) +
+#   scale_linetype_manual(values = c(1, 6)) +
+#   labs(x = "Time (in Seconds)",
+#        y = "Heart Rate\n(in Beats per Minute)") +
+#   ggtitle("Experts' and novices' heart rate per phase") +
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_blank(),
+#         axis.text.x = element_text(size = 12),
+#         axis.text.y = element_text(size = 10),
+#         strip.text = element_text(size = 16),
+#         plot.title = element_text(size = 20, 
+#                                   face = "bold")) +
+#   facet_grid(cols = vars(Type),
+#              scales = "free_x")
+# 
+# # saving plot 
+# ggsave(plot = plot_flow_leg,
+#        filename = "plots/plot_flow_leg.svg",
+#        height = 5,
+#        width = 8,
+#        units = "in")
 
@@
 ```{r}
-df_steps <- read_rds(file = "data/steps.rds")
-set.seed(5678)
-ggplot(data = df_steps,
-       mapping = aes(x = type,
-                     y = Steps
-                     )
-       ) +
-  geom_boxplot(mapping = aes(color = type),
-               fill = "grey",
-               alpha = 0.6) +
-  geom_jitter(mapping = aes(color = type),
-              alpha = 0.9,
-              width = 0.3) +
-  scale_color_viridis_d(option = "A",
-                       end = 0.8) +
-  labs(x = "",
-       y = "Steps During\nMain Phase") +
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        legend.title = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()
-        )
-
-### Validation of steps
-# selecting some rows at random with sample_n()
-sample_n(df_steps, 6)
-
-# random ID Output:
-# Novices ID: 102, 125, 110
-# Experts ID: 219, 218, 214
-
-# Results from manual step counting:
-# Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
-# Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps
+# df_steps <- read_rds(file = "data/steps.rds")
+# set.seed(5678)
+# ggplot(data = df_steps,
+#        mapping = aes(x = type,
+#                      y = Steps
+#                      )
+#        ) +
+#   geom_boxplot(mapping = aes(color = type),
+#                fill = "grey",
+#                alpha = 0.6) +
+#   geom_jitter(mapping = aes(color = type),
+#               alpha = 0.9,
+#               width = 0.3) +
+#   scale_color_viridis_d(option = "A",
+#                        end = 0.8) +
+#   labs(x = "",
+#        y = "Steps During\nMain Phase") +
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         legend.title = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.ticks.x = element_blank()
+#         )
+# 
+# ### Validation of steps
+# # selecting some rows at random with sample_n()
+# sample_n(df_steps, 6)
+# 
+# # random ID Output:
+# # Novices ID: 102, 125, 110
+# # Experts ID: 219, 218, 214
+# 
+# # Results from manual step counting:
+# # Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
+# # Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps
 

### 2022-10-19 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
upload data

@@
 {}{\PatchFailed}
-\keywords{heart rate; photoplethysmography; wearable electronic device; expertise differences \newline\indent Word count: X}
+\keywords{heart rate; photoplethysmography; wearable electronic device; expertise differences\newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 
-\shorttitle{Measuring novice and expert teachers' heart rate}
+\shorttitle{Using fitbit to measure teachers' heart rate}
 
@@
 
-Prospective teachers experience the first five years as a particular professional challenge, as they are associated with a high workload (e.g., class size, poor student behavior) and resulting stress in the teaching profession (Struyven \& Vanthournout, 2014).
+Physiological data such as heart rate are becoming increasingly important in research on stress experience.
+They represent an important indicator of physical or emotional stress, as increased workload is associated with increased heart rate (Sachs, 2014).
+Furthermore, they allow a more objective recording of stress than self-reports (Runge, Haarman, \& Fisher, n.d.).
+However, capturing heart rate in an educational context requires the use of low-cost and non-invasive instruments.
+Fitness trackers worn on the wrist have the potential to be such a useful tool (Ferguson, Rowlands, Olds, \& Maher, 2015).
 
-Psychosomatic stress symptoms, such as increasing heart rate, result from an interaction of situational stressors and person-specific available resources {[}``transactional stress model''; Lazarus and Folkman (1987); Obbarius, Fischer, Liegl, Obbarius, and Rose (2021){]}.
-If teachers are exposed to a stressful teaching-learning environment for a long time and do not have the sufficient resources and coping strategies, this can lead to burnout.
+To date, there is still little evidence on the usefulness of heart rate measurements using fitness trackers in teaching and learning settings (Ertzberger \& Martin, 2016; Lowe, 2016).
+Runge et al.
+(n.d.) alone examined teacher stress in a relatively small sample (\emph{N} = 4 teachers) and showed that high heart rate, high step count, and little sleep indicate more stress in teachers.
 
-Fisher (2011) showed in her study of 400 secondary school teachers that burnout scores differed significantly between novice and experienced teachers, with novices having higher burnout scores.
-In addition, she found that a low number of years of professional experience was a statistically significant predictor of stress in the teaching profession, along with job satisfaction and burnout.
-
-In addition to self-reported indicators of stress (e.g., emotional exhaustion), psychophysiological indicators (e.g., heart rate) are becoming increasingly important in research.
-Heart rate as the number of heart contractions per minute (Löllgen, 2015) is an important indicator of physical or emotional stress.
-Increased workload is associated with increased heart rate (Sachs, 2014).
-Arguably, physiological data provide a more objective and non-reactive measure of stress in the classroom (Runge et al., 2020).
-However, in an educational context, this requires the use of low-cost, non-invasive instruments.
-Fitness trackers worn on the wrist could fill this research gap (Ferguson, Rowlands, Olds, \& Maher, 2015).
+Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of stress.
+Since, among other things, greater professional experience is associated with lower feelings of stress in the teaching profession (Fisher, 2011), this study will also consider the heart rate measurements of experienced and inexperienced teachers.
 
@@
 
-The aim of the study was to uncover differences between 25 experienced and 25 inexperienced teachers on the physical and emotional demands during a 15-minute micro-teaching unit by measuring their heart rate using a fitness watch (Fitbit Charge 4).
-As the fitness watch was put on at the beginning of the survey and was not taken off until the entire data collection was completed, the heart rate could be measured in the resting and arousal states.
-In addition, the watch recorded the subjects' movement activity to determine how many steps were taken during the lesson.
-The practicality of the FitBit for classroom research is discussed.
+Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases and (2) between experienced and inexperienced teachers.
+We expected heart rates to be higher in the arousal phase than in the rest phases and exploratively examine whether experienced teachers have lower heart rates and more steps compared to inexperienced teachers.
 
@@
 
-XXX fitbit data exclusion XXX
+The sample consisted of \emph{N} = 51 participants with \emph{n} = 19 expert teachers and \emph{n} = 32 novice teachers.
 
-The sample consisted of \emph{N} = 41 participants with \emph{n} = 16 expert teachers and \emph{n} = 25 novice teachers.
+The data of two participants (two novices, XXX experts) were excluded from the analyses due to insufficient data quality.
 
@@
 
-The expert teachers (9 women; 56.25\%) had a mean age of 41.40 years (\emph{SD} = 10.70; range: 27-59) and an average teaching experience of 13.60 years (\emph{SD} = 12.80; range: 2-37).
-18.75\% of the experts were primary school teachers and 81.25\% were secondary school teachers.
-56\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+The expert teachers (11 women; 57.89\%) had a mean age of 41.70 years (\emph{SD} = 10.40; range: 27-59) and an average teaching experience of 13.70 years (\emph{SD} = 12.40; range: 2-37).
+15.79\% of the experts were primary school teachers and 84.21\% were secondary school teachers.
+47\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
 
-The novice teachers (16 women; 64\%) had a mean age of 23.40 years (\emph{SD} = 1.80; range: 20-27) with an average teaching experience of 0 years.
-On average, the student teachers were in their 7.30 semester (\emph{SD} = 2.60; range: 3-11).
-Furthermore, they had an average teaching experience of 11.20 teaching units à 45min (\emph{SD} = 8.10; range: 0-36) through the internships during their studies.
-20\% of the novices were studying to become primary school teachers, 68\% to become secondary school teachers and 12\% to become special education teachers.
-88\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+The novice teachers (23 women; 71.88\%) had a mean age of 23 years (\emph{SD} = 1.90; range: 19-27) with an average teaching experience of 0 years.
+On average, the student teachers were in their 7 semester (\emph{SD} = 2.60; range: 3-11).
+Furthermore, they had an average teaching experience of 10.30 teaching units à 45min (\emph{SD} = 7.70; range: 0-36) through the internships during their studies.
+21.88\% of the novices were studying to become primary school teachers, 62.50\% to become secondary school teachers and 15.62\% to become special education teachers.
+90.62\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
 
@@
 
-XXX Data and data wrangling need to be imported XXX
-
 \hypertarget{steps}{%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ertzberger2016use}{}}%
+Ertzberger, J., \& Martin, F. (2016). Use of fitness bands by teachers in the classroom. \emph{TechTrends}, \emph{60}(4), 392--397.
+
 \leavevmode\vadjust pre{\hypertarget{ref-ferguson2015validity}{}}%
@@
 \emph{International Journal of Behavioral Nutrition and Physical Activity}, \emph{12}(1), 1--9.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fisher2011factors}{}}%
+Fisher, M. H. (2011). Factors influencing stress, burnout, and retention of secondary teachers. \emph{Current Issues in Education}, \emph{14}(1).
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1987transactional}{}}%
-Lazarus, R. S., \& Folkman, S. (1987). Transactional theory and research on emotions and coping. \emph{European Journal of Personality}, \emph{1}(3), 141--169.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Luxf6llgen2015}{}}%
-Löllgen, H.
-(2015).
-Herzfrequenz und blutdruck.
-In J.
-Niebauer (Ed.), \emph{Sportkardiologie} (pp.
-87--105).
-Berlin, Heidelberg: Springer Berlin Heidelberg.
-\url{https://doi.org/10.1007/978-3-662-43711-7_9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-obbarius2021modified}{}}%
-Obbarius, N., Fischer, F., Liegl, G., Obbarius, A., \& Rose, M.
-(2021).
-A modified version of the transactional stress concept according to lazarus and folkman was confirmed in a psychosomatic inpatient sample.
-\emph{Frontiers in Psychology}, \emph{12}, 584333.
+\leavevmode\vadjust pre{\hypertarget{ref-lowe2016educational}{}}%
+Lowe, H. (2016). Educational behavior apps and wearable devices: Current research and prospects. \emph{Educational Technology}, 30--33.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-rungeusing}{}}%
+Runge, N., Haarman, S., \& Fisher, M. H. (n.d.). \emph{Using fitbit fitness trackers to measure teacher stress and coping}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-sachs2014physiologische}{}}%
 Sachs, S. (2014). \emph{Physiologische parameter zur bewertung der lernwirksamkeit von lernsituationen} (PhD thesis). Universit{ä}t Ulm.
-
-\leavevmode\vadjust pre{\hypertarget{ref-struyven2014teachers}{}}%
-Struyven, K., \& Vanthournout, G.
-(2014).
-Teachers' exit decisions: An investigation into the reasons why newly qualified teachers fail to enter the teaching profession or why those who do enter do not continue teaching.
-\emph{Teaching and Teacher Education}, \emph{43}, 37--45.
 

### 2022-10-19 02_paper/02_study/02_fitbit paper/data.wrangling.R

@@ -1,5 +1,271 @@
+# rm(list = ls())
+# 
+# ##### 1. Test data #####
+# 
+# 
+# df_test <- read_tsv(file = "data/Acc_Test_data.tsv") %>% 
+#   clean_names() %>%
+#   transmute(time = as.numeric(milliseconds(recording_timestamp_ms)
+#   ),
+#   name = participant_name,
+#   acc_x = as.numeric(str_replace(accelerometer_x_m_s2,
+#                                  pattern = ",",
+#                                  replacement = "."
+#   )
+#   ),
+#   acc_z = as.numeric(str_replace(accelerometer_z_m_s2,
+#                                  pattern = ",",
+#                                  replacement = "."
+#   )
+#   )
+#   )
+# 
+# # First step: create tibbles for each individual.
+# for (i in unique(df_test$name)) {
+#   
+#   df <- filter(df_test,
+#                name == i
+#   )
+#   
+#   assign(value = df,
+#          x = paste0("df_", i)
+#   )
+# }
+# 
+# # For each of the tibbles, create two vectors (x and z) 
+# # for meters for each time period.
+# 
+# for (i in unique(df_test$name)) {
+#   
+#   df <- get(paste0("df_", i))
+#   
+#   # Vectors x and z with length equal to time periods 
+#   # present in each tibble; initial with 0 meters for each   # time period. 
+#   
+#   x <- rep(0, length(get(paste0("df_", i))$time))
+#   z <- rep(0, length(get(paste0("df_", i))$time))
+#   
+#   # For each time period, calculate the meters walked in 
+#   # two dimensions (x and z), given the initial velocity 
+#   # for each period is 0 m/s. First value stays 0 for
+#   # convenience.
+#   # See formula 1.
+#   
+#   for (j in 2:length(get(paste0("df_", i))$time)) {
+#     
+#     x[[j]] <- 0.5 * get(paste0("df_", i))$acc_x[j] * (get(paste0("df_", i))$time[j] - get(paste0("df_", i))$time[j-1])^2
+#     
+#     z[[j]] <- 0.5 * get(paste0("df_", i))$acc_z[j] * (get(paste0("df_", i))$time[j] - get(paste0("df_", i))$time[j-1])^2
+#     
+#   }
+#   
+#   # Save both vectors in new tibble.
+#   
+#   df <- tibble(meter_x = x,
+#                meter_z = z,
+#                ID = paste0(i))
[…]

### 2022-11-15 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
fit bit presentation added

---
title: "FitBit Analysis"
author: "Peer Keßler"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, warning = FALSE)
```

```{r data wrangling, include = FALSE}
library(needs)
needs(ltm,
      lm.beta,
      tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis)

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confident_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confident_factor = ifelse(confident_factor < 0,
                                   yes = NA,
                                   no = confident_factor),
         event = as_factor(event)
         )

# demographic data
df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
  transmute(ID = LI06_05, # select and rename relevant columns 
            gender = factor(LI02_01_1,
                            levels = 1:2,
                            labels = c("male","female")
                            ),
            age = LI03_01, # 1 = male; 2 = female
            teaching_experience = LI04_01)

# merge two data frames by ID 
df_merge <- merge(df_demo,
                  df_rating,
                  by = "ID") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132")
         )

# rm(list = c("df_demo","df_rating"))

data_path <- "./data/heart_rate_data"

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), id = "id") %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(
           str_detect(string = id, pattern = "_a") ~ "after",
           str_detect(string = id, pattern = "_m") ~ "main",
           str_detect(string = id, pattern = "_p") ~ "pre"
           ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
      filter(time <= 600) %>%
    select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

main <-
  left_join(main, df_merge,
            by = "ID")
```

# Überblick Daten

```{r}
knitr::kable(main[1:10,], format = "simple")
```

# Verteilungen

# Geschlecht

```{r}
df_demo %>% 
  ggplot(mapping = aes(x = gender)) +
  geom_bar()
```

# Alter

```{r}
df_demo %>% 
  ggplot(mapping = aes(x = age)) +
  geom_histogram(binwidth = 5)
```

- Linkssteile Verteilung
- Möglicher Umgang: Logarithmieren

```{r}
df_demo %>% 
  ggplot(mapping = aes(x = log(age))) +
  geom_histogram(binwidth = 0.1)
```

# Alter x Geschlecht

```{r}
df_demo %>% 
  ggplot(mapping = aes(x = gender,
                       y = age
                       )
         ) +
  geom_boxplot()
```

- Alter und Geschlecht unkorreliert
- $\chi^2=$ `r chisq.test(df_demo$gender, df_demo$age)$statistic[[1]] %>% round(., 2)`

# Lehrerfahrung

```{r}
df_demo %>% 
  ggplot(mapping = aes(x = teaching_experience)) +
  geom_histogram(binwidth = 2)
```

- Starke links-verzerrte Verteilung (zero inflation)
- 0 rausfiltern (keine Option)
- log(x + 1)

```{r}
df_demo %>% 
  ggplot(mapping = aes(x = log(teaching_experience + 1))) +
  geom_histogram(binwidth = 0.3)
```

- In jedem Fall stark korreliert mit Alter $\rightarrow$ Gefahr der Multikollinearität

```{r}
paste0("r = ", round(cor(df_demo$teaching_experience, df_demo$age), 2))
```

- Vorschlag: Lehrerfahrung weglassen und Alter aufnehmen
- Konsistent mit Idee, Expert\*innen und Noviz\*innen nicht zu trennen

## Confident Factor

```{r}
df_merge %>% 
  filter(!is.na(confident_factor)) %>% 
  group_by(event, confident_factor) %>% 
  summarize(value = n()) %>% 
  mutate(prop = value/sum(value)) %>% 
  ggplot(mapping = aes(x = reorder(event, prop),
                       y = prop,
                       fill = confident_factor
                       )
         ) +
  geom_bar(position = "stack",
           stat = "identity") +
  coord_flip() +
  scale_fill_viridis_c() +
  labs(y = "",
       x = "Event",
       fill = "Confident Factor")
```

## Disruption Factor

```{r}
df_merge %>% 
  filter(!is.na(disruption_factor)) %>% 
  group_by(event, disruption_factor) %>% 
  summarize(value = n()) %>% 
  mutate(prop = value/sum(value)) %>% 
  ggplot(mapping = aes(x = reorder(event, prop),
                       y = prop,
                       fill = disruption_factor
                       )
         ) +
  geom_bar(position = "stack",
           stat = "identity") +
  coord_flip() +
  scale_fill_viridis_c() +
  labs(y = "",
       x = "Event",
       fill = "Disruption Factor")
```

- Mittelwerte bilden? (potentielle Aussagekraft: Im Schnitt fühlten sich manche Lehrpersonen sicherer mit der Situation/fühlten sich eher gestört von der Situation)

# Erste Zusammenhänge

## Confidence x Disruption (out of curiosity)

```{r}
df_merge %>% 
  filter(!is.na(disruption_factor) | !is.na(confident_factor)) %>% 
  ggplot(mapping = aes(x = confident_factor,
                       y = disruption_factor
                       )
         ) +
  geom_jitter(mapping = aes(color = event)) +
  geom_smooth(method = "lm",
              se = FALSE) +
  scale_color_viridis_d() +
  labs(x = "Confident Factor",
       y = "Disruption Factor",
       color = "Event")

```

## Alter x Confidence

```{r}
df_merge %>% 
  filter(!is.na(confident_factor) | !is.na(disruption_factor)) %>% 
  ggplot(mapping = aes(x = age,
                       y = confident_factor
                       )
         ) +
  geom_jitter(mapping = aes(color = event)) +
  geom_smooth(method = "lm")
```

- Mittelwerte:

```{r}
df_merge %>% 
  filter(!(is.na(confident_factor) | is.na(disruption_factor))) %>% 
  group_by(ID) %>% 
  summarize(mean_confident = mean(confident_factor),
            age = mean(age)) %>%
  ungroup() %>% 
  ggplot(mapping = aes(x = age,
                       y = mean_confident
                       )
         ) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Alter x Disruption

```{r}
df_merge %>% 
  filter(!is.na(confident_factor) | !is.na(disruption_factor)) %>% 
  ggplot(mapping = aes(x = age,
                       y = disruption_factor
                       )
         ) +
  geom_jitter(mapping = aes(color = event)) +
  geom_smooth(method = "lm")
```

- Mittelwerte:

```{r}
df_merge %>% 
  filter(!(is.na(confident_factor) | is.na(disruption_factor))) %>% 
  group_by(ID) %>% 
  summarize(mean_disruption = mean(disruption_factor),
            age = mean(age)) %>%
  ungroup() %>% 
  ggplot(mapping = aes(x = age,
                       y = mean_disruption
                       )
         ) +
  geom_point() +
  geom_smooth(method = "lm")
```

# Heart Rate

Vorüberlegungen

- Idee: Was erklärt die zunehmende Aufregung am Anfang bzw. abnehmende Aufregung nach der Unterrichtssession?
- AV: geschätzte Lineare Steigung der Herzrate vor der Session
- Beachten: jede Person hat eigenen Ruhepuls! $\rightarrow$ random intercept, fixed slope regression model

## Pre-Phase

```{r}
main %>% 
  filter(time_span == "pre") %>% 
  select("ID","time","heart_rate") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_line(mapping = aes(color = as_factor(ID)),
            stat = "smooth", 
            method = "lm",
            alpha = 0.6) +
  geom_point(mapping = aes(color = as_factor(ID)),
             alpha = 0.1) +
  geom_line(stat = "smooth",
            method = "lm",
            linetype = 2) +
  labs(x = "Time (in seconds)",
       y = "Heart Rate (in beats per minute)") +
  theme(legend.position = "none",
        text = element_text(family = "serif"))
```

```{r}
main %>% 
  filter(time_span == "pre") %>% 
  select("time","ID","heart_rate","age") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  lmer(formula = heart_rate ~ (1|ID) + ID * time) %>% 
  summary() ->
  fit_first

as_tibble(fit_first$coefficients,
          rownames = "Coefficient") %>%
  filter(str_detect(.$Coefficient,
                    pattern = "time")) %>% 
  mutate(coefficient = case_when(Coefficient == "time" ~ "101",
                                 TRUE ~ Coefficient),
         ID = str_extract(string = coefficient,
                                   pattern = "[:digit:]{3}"
                                   ),
         ID = as.numeric(ID)
         ) %>% 
  select("ID","Estimate") ->
  df_estimates

df_merge %>% 
  group_by(ID) %>% 
  summarize(confident_factor_m = mean(confident_factor,
                                      na.rm = TRUE),
            disruption_factor_m = mean(disruption_factor,
                                       na.rm = TRUE),
            ID = ID,
            t_exp = teaching_experience) %>% 
  distinct() %>% 
  left_join(., df_estimates,
            by = "ID") ->
  df_corr_pre
```

```{r}
df_corr_pre %>% 
  select("ID","Estimate") %>% 
  filter(ID < 110) %>% 
  knitr::kable(., format = "simple")
```

### 2022-11-18 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
fit bit presentation

@@
 title: "FitBit Analysis"
-author: "Peer Keßler"
 date: "`r Sys.Date()`"
@@
 needs(ltm,
+      broom,
+      ppcor,
+      jtools,
       lm.beta,
@@
              pattern = ".csv"),
-    ~ read_csv(file.path(data_path, .), id = "id") %>% 
+    ~ read_csv(file.path(data_path, .), 
+               id = "id",
+               col_types = c("t","n")
+               ) %>% 
   mutate(time = .$Time - min(.$Time),
@@
          ID = id,
-         time_span = case_when(
-           str_detect(string = id, pattern = "_a") ~ "after",
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
            str_detect(string = id, pattern = "_m") ~ "main",
-           str_detect(string = id, pattern = "_p") ~ "pre"
+           str_detect(string = id, pattern = "_p") ~ "pre",
+           str_detect(string = id, pattern = "_s") ~ "subsequent",
+           str_detect(string = id, pattern = "_i") ~ "interview",
+           TRUE ~ "overall"
            ),
@@
 df_demo %>% 
+  mutate(gender = fct_recode(gender,
+                             "Männlich" = "male",
+                             "Weiblich" = "female"
+                             )
+         ) %>% 
   ggplot(mapping = aes(x = gender)) +
-  geom_bar()
+  geom_bar(fill = "#440154") +
+  labs(x = "Geschlecht",
+       y = "Anzahl") +
+  theme_apa()
 ```
@@
   ggplot(mapping = aes(x = age)) +
-  geom_histogram(binwidth = 5)
+  geom_histogram(binwidth = 5,
+                 fill = "#440154") +
+  labs(x = "Alter",
+       y = "Anzahl") +
+  theme_apa()
 ```
@@
   ggplot(mapping = aes(x = log(age))) +
-  geom_histogram(binwidth = 0.1)
+  geom_histogram(binwidth = 0.1,
+                 fill = "#440154") +
+  labs(x = "log(Alter)",
+       y = "Anzahl") +
+  theme_apa()
 ```
@@
 df_demo %>% 
+  mutate(gender = fct_recode(gender,
+                             "Männlich" = "male",
+                             "Weiblich" = "female"
+                             )
+         ) %>% 
   ggplot(mapping = aes(x = gender,
@@
          ) +
-  geom_boxplot()
+  geom_boxplot(fill = "#440154",
+               color = "#3b528b") +
+  labs(x = "Geschlecht",
+       y = "Alter") +
+  theme_apa()
 ```
@@
   ggplot(mapping = aes(x = teaching_experience)) +
-  geom_histogram(binwidth = 2)
+  geom_histogram(binwidth = 2,
+                 fill = "#440154") + 
+  labs(x = "Lehrerfahrung",
+       y = "Anzahl") +
+  theme_apa()
 ```
@@
   ggplot(mapping = aes(x = log(teaching_experience + 1))) +
-  geom_histogram(binwidth = 0.3)
+  geom_histogram(binwidth = 0.3,
+                 fill = "#440154") + 
+  labs(x = "log(Lehrerfahrung + 1)",
+       y = "Anzahl") +
+  theme_apa()
 ```
@@
 - In jedem Fall stark korreliert mit Alter $\rightarrow$ Gefahr der Multikollinearität
-
-```{r}
-paste0("r = ", round(cor(df_demo$teaching_experience, df_demo$age), 2))
-```
+- `r paste0("r = ", round(cor(df_demo$teaching_experience, df_demo$age), 2))`
 
@@
   labs(y = "",
-       x = "Event",
-       fill = "Confident Factor")
+       x = "",
+       fill = "Confident Factor") +
+  theme_apa()
 ```
@@
   labs(y = "",
-       x = "Event",
-       fill = "Disruption Factor")
+       x = "",
+       fill = "Disruption Factor") +
+  theme_apa()
 ```
@@
        y = "Disruption Factor",
-       color = "Event")
+       color = "Event") +
+  theme_apa()
 
@@
   geom_jitter(mapping = aes(color = event)) +
-  geom_smooth(method = "lm")
+  geom_smooth(method = "lm",
+              se = F) +
+  labs(x = "Alter",
+       y = "Confident Factor") +
+  scale_color_viridis_d() +
+  theme_apa()
 ```
@@
          ) +
-  geom_point() +
-  geom_smooth(method = "lm")
+  geom_point(color = "#440154") +
+  geom_smooth(method = "lm",
+              se = FALSE) +
+  labs(x = "Alter",
+       y = "Mean(Confident Factor)") +
+  theme_apa()
 ```
@@
   geom_jitter(mapping = aes(color = event)) +
-  geom_smooth(method = "lm")
+  geom_smooth(method = "lm",
+              se = F) +
+  scale_color_viridis_d() +
+  labs(x = "Alter",
+       y = "Disruption Factor") +
+  theme_apa()
 ```
@@
          ) +
-  geom_point() +
-  geom_smooth(method = "lm")
+  geom_point(color = "#440154") +
+  geom_smooth(method = "lm",
+              se = F) +
+  labs(x = "Alter",
+       y = "Mean(Disruption Factor)") +
+  theme_apa()
 ```
@@
 
-## Pre-Phase
+## Beispiel (Pre-Phase)
 
@@
             linetype = 2) +
-  labs(x = "Time (in seconds)",
-       y = "Heart Rate (in beats per minute)") +
-  theme(legend.position = "none",
-        text = element_text(family = "serif"))
+  scale_color_viridis_d() +
+  labs(x = "Zeit (in Sekunden)",
+       y = "Herzrate (in Schlägen pro Minute)") +
+  theme_apa() +
+  theme(legend.position = "none") 
 ```
@@
   filter(time_span == "pre") %>% 
-  select("time","ID","heart_rate","age") %>% 
+  select("time","ID","heart_rate") %>% 
   distinct() %>% 
@@
 ```
+
+Plan für Pre- und Subsequent Phase:
+
+- Partielle Korrelationen
+
+- Multiple Lineare Regression
+  - AV: Estimate
+  - UV: Gender, Alter, Disruption Factor (mean), Confident Factor (mean)
+  - Alle metrischen Variablen sind standardisiert
+
+## Pre Phase
+
+- 10 Minuten nach Anlegen der FitBit
+
+### Korrelationen
+
+```{r}
+main %>% 
+  filter(time_span == "pre") %>% 
+  select("time","ID","heart_rate") %>% 
+  distinct() %>% 
+  mutate(ID = as_factor(ID)) %>% 
+  lmer(formula = heart_rate ~ (1|ID) + ID * time) %>% 
+  summary() ->
+  fit_first
+
+as_tibble(fit_first$coefficients,
+          rownames = "Coefficient") %>%
+  filter(str_detect(.$Coefficient,
+                    pattern = "time")) %>% 
+  mutate(coefficient = case_when(Coefficient == "time" ~ "101",
+                                 TRUE ~ Coefficient),
+         ID = str_extract(string = coefficient,
+                                   pattern = "[:digit:]{3}"
+                                   ),
+         ID = as.numeric(ID)
+         ) %>% 
+  select("ID","Estimate") ->
+  df_estimates
+
+df_merge %>% 
+  group_by(ID) %>% 
+  summarize(confident_factor_m = mean(confident_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            ID = ID,
+            t_exp = teaching_experience) %>% 
+  distinct() %>% 
+  left_join(., df_estimates,
+            by = "ID") %>% 
+  ungroup() ->
+  df_corr_pre
+
+left_join(x = df_corr_pre,
+          y = df_demo,
+          by = "ID") %>% 
+transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
+          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+          gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          age = (age - mean(.$age))/sd(.$age)
+          ) %>% 
+  pcor(., method = "spearman") %>% 
+  .$estimate %>% 
+  round(., 2) %>% 
+  knitr::kable(format = "simple")
+
+left_join(x = df_corr_pre,
+          y = df_demo,
+          by = "ID") %>% 
+transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
+          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+          gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          age = (age - mean(.$age))/sd(.$age)
+          ) %>% 
+  pcor(., method = "pearson") %>% 
+  .$p.value %>% 
+  round(., 3) %>% 
+  knitr::kable(format = "simple")
+```
+
+### Regression
+
+```{r}
+left_join(x = df_corr_pre,
+          y = df_demo,
+          by = "ID") %>% 
+  ungroup() %>% 
+  mutate(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
+         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = gender,
+         age = (age - mean(.$age))/sd(.$age)
+         ) %>%
+  lm(formula = Estimate ~ confident_factor_m + disruption_factor_m  + gender + age) %>% 
+  tidy(x = .,
+       conf.int = TRUE) %>% 
+  mutate(term = case_when(term == "confident_factor_m" ~ "Confident Factor",
+                              term == "disruption_factor_m" ~ "Disruption Factor",
+                              term == "genderfemale" ~ "Weiblich\n(Ref.: Männlich)",
+                              term == "age" ~ "Alter",
+                              TRUE ~ "Intercept"
+                           ),
+         term = fct_relevel(term, 
+                            c("Confident Factor",
+                              "Disruption Factor",
+                              "Weiblich\n(Ref.: Männlich)",
+                              "Alter"
+                              )),
+         term = fct_rev(as_factor(term)),
+         ) %>% 
+  filter(term != "Intercept") %>% 
+  ggplot(mapping = aes(y = term)) +
+    geom_point(aes(x = estimate)) +
+  geom_vline(xintercept = 0) +
+  geom_segment(mapping = aes(x = conf.low,
+                             xend = conf.high,
+                             y = term,
+                             yend = term),
+               color = "#440154") +
+  labs(x = "Effect",
+       y = "",
+       title = "Pre-Phase",
+       subtitle = paste0("Dependend Variable: Standardized Estimate\n(M = ", 
+                         mean(df_corr_pre$Estimate) %>% round(.,2),
+                         ")"
+                         )
+       ) +
+  theme_apa() 
+```
+
+- Keine sign. Ergebnisse
+- Selbstbewusste Personen haben einen *niedrigeren* Anstieg der HR vor der Erhebung
+- Personen, die sich stärker gestört gefühlt haben, haben einen *stärkeren* Anstieg der HR
+- Die HR von Frauen steigt *stärker* als die der Männer
+- Je älter die Personen sind, desto *niedriger* ist der Anstieg der HR
+
+## Subsequent Phase
+
+- 10 Minuten nach der Unterrichtseinheit
+
+### Korrelation
+
+```{r}
+main %>% 
+  filter(time_span == "subsequent") %>% 
+  select("time","ID","heart_rate") %>% 
+  distinct() %>% 
+  mutate(ID = as_factor(ID)) %>% 
+  lmer(formula = heart_rate ~ (1|ID) + ID * time) %>% 
+  summary() ->
+  fit_first
+
+as_tibble(fit_first$coefficients,
+          rownames = "Coefficient") %>%
+  filter(str_detect(.$Coefficient,
+                    pattern = "time")) %>% 
+  mutate(coefficient = case_when(Coefficient == "time" ~ "101",
+                                 TRUE ~ Coefficient),
+         ID = str_extract(string = coefficient,
+                                   pattern = "[:digit:]{3}"
+                                   ),
+         ID = as.numeric(ID)
+         ) %>% 
+  select("ID","Estimate") ->
+  df_estimates
+
+df_merge %>% 
+  group_by(ID) %>% 
+  summarize(confident_factor_m = mean(confident_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            ID = ID,
+            t_exp = teaching_experience) %>% 
+  distinct() %>% 
+  left_join(., df_estimates,
+            by = "ID") %>% 
+  ungroup() ->
+  df_corr_pre
+
+left_join(x = df_corr_pre,
+          y = df_demo,
+          by = "ID") %>% 
+transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
+          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+          gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          age = (age - mean(.$age))/sd(.$age)
+          ) %>% 
+  pcor(., method = "spearman") %>% 
+  .$estimate %>% 
+  round(., 2) %>% 
+  knitr::kable(format = "simple")
+
+left_join(x = df_corr_pre,
+          y = df_demo,
+          by = "ID") %>% 
+transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
+          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+          gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          age = (age - mean(.$age))/sd(.$age)
+          ) %>% 
+  pcor(., method = "pearson") %>% 
+  .$p.value %>% 
+  round(., 3) %>% 
+  knitr::kable(format = "simple")
+```
+
+### Regression
+
+```{r}
+main %>% 
+  filter(time_span == "subsequent") %>% 
+  select("time","ID","heart_rate") %>% 
+  distinct() %>% 
+  mutate(ID = as_factor(ID)) %>% 
+  lmer(formula = heart_rate ~ (1|ID) + ID * time) %>% 
+  summary() ->
+  fit_first
+
+as_tibble(fit_first$coefficients,
+          rownames = "Coefficient") %>%
+  filter(str_detect(.$Coefficient,
+                    pattern = "time")) %>% 
+  mutate(coefficient = case_when(Coefficient == "time" ~ "101",
+                                 TRUE ~ Coefficient),
+         ID = str_extract(string = coefficient,
+                                   pattern = "[:digit:]{3}"
+                                   ),
+         ID = as.numeric(ID)
+         ) %>% 
+  select("ID","Estimate") ->
+  df_estimates
+
+df_merge %>% 
+  group_by(ID) %>% 
+  summarize(confident_factor_m = mean(confident_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            ID = ID,
+            t_exp = teaching_experience) %>% 
+  distinct() %>% 
+  left_join(., df_estimates,
+            by = "ID") ->
+  df_corr_sub
+
+left_join(x = df_corr_sub,
+          y = df_demo,
+          by = "ID") %>% 
+  mutate(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
+         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = gender,
+         age = (age - mean(.$age))/sd(.$age)
+         ) %>%
+  lm(formula = Estimate ~ confident_factor_m + disruption_factor_m + gender + age) %>% 
+  tidy(x = .,
+       conf.int = TRUE) %>% 
+  mutate(term = case_when(term == "confident_factor_m" ~ "Confident Factor",
+                              term == "disruption_factor_m" ~ "Disruption Factor",
+                              term == "genderfemale" ~ "Weiblich\n(Ref.: Männlich)",
+                              term == "age" ~ "Alter",
+                              TRUE ~ "Intercept"
+                           ),
+         term = fct_rev(as_factor(term))
+         ) %>% 
+  filter(term != "Intercept") %>% 
+  ggplot(mapping = aes(y = term)) +
+    geom_point(aes(x = estimate)) +
+  geom_vline(xintercept = 0) +
+  geom_segment(mapping = aes(x = conf.low,
+                             xend = conf.high,
+                             y = term,
+                             yend = term
+                             ),
+               color = "#440154"
+               ) +
+  labs(x = "Effect",
+       y = "",
+       title = "Subsequent Phase",
+       subtitle = paste0("Dependend Variable: Standardized Estimate\n(M = ", 
+                         mean(df_corr_sub$Estimate) %>% round(.,2),
+                         ")"
+                         )
+       ) +
+  theme_apa() 
+```
+
+- Nach der Erhebung fällt die HR der Personen, die sich stärker gestört gefühlt haben, *signifikant stärker* ab
+
+## Main Phase vs. Interview Phase
+
+- Main Phase = 10 Minuten der...
+- Interview Phase =
+
+Plan:
+
+- Partielle Korrelation (mittlere HR x ...)
+- Mittelwertvergleich
+
+### Partielle Korrelationen
+
+#### Main Phase
+
+```{r}
+main %>% 
+  filter(time_span == "main") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate),
+            confident_factor_m = mean(confident_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            age = age,
+            gender = gender
+            ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          age = (age - mean(.$age))/sd(.$age)
+         ) %>% 
+  pcor()  -> pcor_main
+
+knitr::kable(x = list(pcor_main$estimate, pcor_main$p.value), format = "simple")  
+```
+
+#### Interview Phase
+
+```{r}
+main %>% 
+  filter(time_span == "interview") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate),
+            confident_factor_m = mean(confident_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            age = age,
+            gender = gender
+            ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          age = (age - mean(.$age))/sd(.$age)
+         ) %>% 
+  pcor()  -> pcor_interview
+
+knitr::kable(x = list(pcor_interview$estimate, pcor_interview$p.value), format = "simple")  
+```
+
+### t-Test
+
+- Paired t-Test
+- Idee: Vorher standardisieren anhand von allen Herzraten-Daten
+  - Mittlere Herzrate über alle Datenpunkte = beste Schätzung für den realen Mittelwert
+
+$$z_{Phase}=\frac{x_{Phase}-M_{overall}}{SD_{overall}} $$
+
+```{r}
+
+main %>% 
+  filter(time_span == "overall") %>% 
+  group_by(ID) %>% 
+  summarize(heart_rate_m_oa = mean(heart_rate),
+            heart_rate_sd_oa = sd(heart_rate)) %>% 
+  ungroup() %>% 
+  left_join(.,
+            y = main,
+            by = "ID") %>% 
+  filter(time_span == "interview" | time_span == "main") %>% 
+  select("time", "heart_rate", "ID", "time_span", "heart_rate_m_oa", "heart_rate_sd_oa") %>% 
+  distinct() %>% 
+  mutate(heart_rate_m = (heart_rate - heart_rate_m_oa)/heart_rate_sd_oa) %>% 
+  select("heart_rate_m","time_span","ID") %>% 
+  group_by(ID, time_span) %>% 
+  summarise(heart_rate_m = mean(heart_rate_m)) %>% 
+  ungroup() %>% 
+  pivot_wider(id_cols = ID,
+              names_from = time_span,
+              values_from = heart_rate_m) -> tib_test
+
+t.test(x = tib_test$interview,
+       y = tib_test$main,
+       paired = TRUE)
+```
+
+Ohne Standardisierung:
+
+```{r}
+main %>% 
+  filter(time_span == "interview" | time_span == "main") %>% 
+  select("ID","time","time_span","heart_rate") %>% 
+  distinct() %>% 
+  group_by(ID, time_span) %>% 
+  summarize(heart_rate_m = mean(heart_rate)) %>% 
+  ungroup() %>% 
+  pivot_wider(id_cols = ID,
+              names_from = time_span,
+              values_from = heart_rate_m) -> tib_test_einfach
+
+t.test(x = tib_test_einfach$interview,
+       y = tib_test_einfach$main,
+       paired = TRUE)
+```
+
+- Beide Testresultate zeigen einen signifikanten Unterschied

### 2022-11-21 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
präsentation fitbit timeline + plot

@@
 
+# Überblick Datenerhebung
+
+```{r timeline, fig.align = "center", echo = FALSE}
+
+knitr::include_graphics("./images/timeline_fitbit.png", dpi = 130)
+
+```
+
 # Überblick Daten
@@
 knitr::kable(main[1:10,], format = "simple")
+```
+
+# Plot für einzelne Phasen
+
+```{r, fig.height = 8, fig.width = 15}
+
+main %>% 
+  filter(time_span != "overall") %>% 
+  select("ID","time_span", "time","heart_rate") %>% 
+  mutate(status = case_when(ID < 200 ~ "Unerfahren",
+                            ID > 200 ~ "Erfahren"),
+         time_span = fct_recode(time_span,
+                                "Pre-Lehrphase" = "pre",
+                                "Lehrphase" = "main",
+                                "Post-Lehrphase" = "subsequent",
+                                "Intviewphase" = "interview",
+                                "Endphase" = "after"
+                                ),
+         time_span = factor(time_span,
+                            levels = c("Pre-Lehrphase",
+                                       "Lehrphase",
+                                       "Post-Lehrphase",
+                                       "Intviewphase",
+                                       "Endphase"
+                                       )
+                            )
+         ) %>%
+  distinct() %>% 
+ggplot(mapping = aes(x = time,
+                     y = heart_rate
+                     )
+       ) +
+  stat_smooth(geom = "line",
+              mapping = aes(color = status),
+              method = "loess",
+              se = FALSE) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Zeit (in Sekunden)",
+       y = "Herzrate (in Schlägen pro Minute)") +
+  theme_apa() +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x",
+             )
+
 ```

### 2022-11-22 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
fitbit

@@
 
-- Main Phase = 10 Minuten der...
-- Interview Phase =
+- Main Phase = 10 Minuten ab Lektionsbeginn 
+- Interview Phase = 10 Minuten mittig vom Interview (Differenz vom Ende der Unterrichtseinheit und von take off watch - die Länge des Zeitraumes, wo die 10 Minuten mittig reinlegt werden --> diese Länge wurde nochmals halbiert, um zur Mitte des Intervalls zu kommen und 5 Minuten abgezogen, um am Start des 10-Minuten-Intervalls zu landen)
 

### 2022-11-24 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update fitbit paper

@@
 
-keywords          : "heart rate; photoplethysmography; wearable electronic device; expertise differences"
+keywords          : "heart rate; photoplethysmography; wearable electronic device; teaching"
 wordcount         : "X"
@@
 
-```{r include=FALSE}
-# install.packages("needs")
-
-# suppress "summarize" info. 
-# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
-options(dplyr.summarise.inform = FALSE)
+```{r data wrangling, include=FALSE}
 
 library(needs)
+needs(ltm,
+      broom,
+      ppcor,
+      jtools,
+      lm.beta,
+      tidyverse,
+      janitor,
+      lubridate,
+      readxl,
+      ggthemes,
+      gridExtra,
+      imputeTS,
+      DescTools,
+      cowplot,
+      rstatix,
+      ggpubr,
+      lme4,
+      viridis)
 
-needs(tidyverse,
-      lubridate,
-      janitor,
-      viridis,
-      grid,
-      gridExtra,
-      cowplot,
-      readxl,
-      ARTofR,
-      moments,
-      ltm,
-      sjPlot,
-      kableExtra,
-      xtable,
-      DescTools,
-      formattable,
-      ggthemes,
-      imputeTS,
-      rstatix,
-      ggpubr)
+# disruption & confidence rating
+df_rating <- 
+  excel_sheets("data/Coding_SRI.xlsx") %>% 
+  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
+  select(ID, # select relevant columns 
+         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
+         confident_factor,
+         event
+         ) %>% 
+  mutate(disruption_factor = ifelse(disruption_factor < 0,
+                                    yes = NA,
+                                    no = disruption_factor
+                                    ),
+         confident_factor = ifelse(confident_factor < 0,
+                                   yes = NA,
+                                   no = confident_factor),
+         event = as_factor(event)
+         )
 
+# demographic data
+df_demo <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
+  transmute(ID = LI06_05, # select and rename relevant columns 
+            gender = factor(LI02_01_1,
+                            levels = 1:2,
+                            labels = c("male","female")
+                            ),
+            age = LI03_01, # 1 = male; 2 = female
+            teaching_experience = LI04_01,
+            school_type = LI18,
+            term = LI11_01, 
+            extracurricular_teaching_experience = LI14,
+            secondary_teaching_activities = LI17)
+
+# merge two data frames by ID 
+df_merge <- merge(df_demo,
+                  df_rating,
+                  by = "ID") %>% 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132")
+         )
+
+# rm(list = c("df_demo","df_rating"))
+
+data_path <- "./data/heart_rate_data"
+
+main <-
+map(.x = dir(path = data_path,
+             pattern = ".csv"),
+    ~ read_csv(file.path(data_path, .), 
+               id = "id",
+               col_types = c("t","n")
+               ) %>% 
+  mutate(time = .$Time - min(.$Time),
+         time = as.numeric(time),
+         heart_rate = `Heart Rate`,
+         ID = id,
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
+           str_detect(string = id, pattern = "_m") ~ "main",
+           str_detect(string = id, pattern = "_p") ~ "pre",
+           str_detect(string = id, pattern = "_s") ~ "subsequent",
+           str_detect(string = id, pattern = "_i") ~ "interview",
+           TRUE ~ "overall"
+           ),
+         ID = str_extract(string = ID,
+                          pattern = "[:digit:]{3}"),
+         ID = as.numeric(ID)
+      ) %>%
+      filter(time <= 600) %>%
+    select(!c("Time","Heart Rate","id"))
+    ) %>%
+  bind_rows()
+
+main <-
+  left_join(main, df_merge,
+            by = "ID")
 ```
@@
 ## Aim of the study
-Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases and (2) between experienced and inexperienced teachers.
-We expected heart rates to be higher in the arousal phase than in the rest phases and exploratively examine whether experienced teachers have lower heart rates and more steps compared to inexperienced teachers.
+Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases.
+We expected heart rates to be higher in the arousal phase than in the rest phases.
 
@@
 
-# DEMOGRAPHIC DATA
-# read in data and select and rename relevant columns with transmute 
-demo.data.raw <- 
-  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
-  transmute(ID = LI06_05,
-            Gender = LI02_01_1,
-            Age = LI03_01,
-            `Teaching Experience` = LI04_01,
-            School_type = LI18,
-            Grade = LI16_05,
-            Subject = LI10_05,
-            Semester = LI11_01,
-            Internship = LI13_01,
-            `Extracurricular Teaching Experience` = LI14,
-            `Secondary Teaching Activities` = LI17
-            )
-
-# exclude cases with no fitbit data
-demo.data <- demo.data.raw %>% filter(!ID %in% c("126",
-                                                 "132"
-                                                 )
-                                      )
-
 # define expert and novice with ifelse function
-demo.data$ID = ifelse(demo.data$ID < 200, "Novice","Expert")
+df_demo$ID = ifelse(df_demo$ID < 200, "Novice","Expert")
 
 # changing gender to count female gender (male = 2 --> 0)
-demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")
+df_demo$gender = ifelse(df_demo$gender == 2, "1","0")
 
 # changing character Gender into numeric
-demo.data$Gender <- as.numeric(demo.data$Gender)
+df_demo$gender <- as.numeric(df_demo$gender)
 
 # creating new column with total participants to calculate percent of gender
-demo.data <- demo.data %>%
+df_demo <- df_demo %>%
   group_by(ID) %>%
-  mutate(Sum_participants = n())
+  mutate(sum_participants = n())
 
 # replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
-demo.data$School_type[demo.data$School_type == 2] <- "1"
+df_demo$school_type[df_demo$school_type == 2] <- "1"
 
 # creating new column to calculate percent of school type
-demo.data <- 
-  demo.data %>%
-  group_by(School_type, ID) %>%
-  mutate(Count_Schooltype = sum(n())) %>% 
-  mutate(Percent_schooltype = round((Count_Schooltype/Sum_participants) * 100, 
+df_demo <- 
+  df_demo %>%
+  group_by(school_type, ID) %>%
+  mutate(count_schooltype = sum(n())) %>% 
+  mutate(percent_schooltype = round((count_schooltype/sum_participants) * 100, 
          digits = 2))
 
-# changing character Percent_schooltype into numeric
-demo.data$Percent_schooltype <- as.numeric(demo.data$Percent_schooltype)
-
-# changing character Semester into numeric
-demo.data$Semester <- as.numeric(demo.data$Semester)
+# changing character percent_schooltype into numeric
+df_demo$percent_schooltype <- as.numeric(df_demo$percent_schooltype)
 
@@
 # -1: andere Schulform
-demo.data$School_type <- factor(x = demo.data$School_type,
+df_demo$school_type <- factor(x = df_demo$school_type,
                    levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
@@
 
-# changing `Extracurricular Teaching Experience` to count experience (no experience = 2 --> 0)
-demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 1, "1","0")
+# changing character semester into numeric
+df_demo$term <- as.numeric(df_demo$term)
+
+# changing `extracurricular_teaching_experience to count experience (no experience = 2 --> 0)
+df_demo$extracurricular_teaching_experience = ifelse(demo.data$extracurricular_teaching_experience == 1, "1","0")
+
+# changing character extracurricular_teaching_experience into numeric
+df_demo$extracurricular_teaching_experience <- as.numeric(df_demo$extracurricular_teaching_experience)
+
+# changing secondary_teaching_activities to count experience (no experience = 2 --> 0)
+df_demo$secondary_teaching_activities = ifelse(df_demo$secondary_teaching_activities == 1, "1","0")
 
 # changing character Extra. Exp. into numeric
-demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)
-
-# changing `Secondary Teaching Activities` to count experience (no experience = 2 --> 0)
-demo.data$`Secondary Teaching Activities` = ifelse(demo.data$`Secondary Teaching Activities` == 1, "1","0")
-
-# changing character Extra. Exp. into numeric
-demo.data$`Secondary Teaching Activities` <- as.numeric(demo.data$`Secondary Teaching Activities`)
-
-# create new columns that give proportion of Gender
-# percent = female gender divided by all female Gender
-# demo.data <- demo.data  %>% 
-#   group_by(Group) %>% 
-#   mutate(Gender_percent = Gender/Sum_participants) %>% 
-#   mutate(Gender_percent = round(sum(Gender_percent)*100, digits=0))
+df_demo$secondary_teaching_activities <- as.numeric(df_demo$secondary_teaching_activities)
 
 # create a basic table (tibble) using tidyverse functions
-demo.table <- demo.data %>%
+df_demo <- df_demo %>%
   group_by(ID) %>%
@@
 
-The sample consisted of *N* = `r length(demo.data$ID)` participants with *n* = `r length(demo.data$ID[demo.data$ID == "Expert"])` expert teachers and *n* = `r length(demo.data$ID[demo.data$ID == "Novice"])` novice teachers.
+The sample consisted of *N* = `r length(df_demo$ID)` participants with *n* = `r length(df_demo$ID[df_demo$ID == "Expert"])` expert teachers and *n* = `r length(demo.data$ID[demo.data$ID == "Novice"])` novice teachers.
 

### 2022-11-24 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd

--- 2022-11-18 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
@@
 knitr::kable(main[1:10,], format = "simple")
+```
+
+# Plot für einzelne Phasen
+
+```{r, fig.height = 8, fig.width = 15}
+
+main %>% 
+  filter(time_span != "overall") %>% 
+  select("ID","time_span", "time","heart_rate") %>% 
+  mutate(status = case_when(ID < 200 ~ "Unerfahren",
+                            ID > 200 ~ "Erfahren"),
+         time_span = fct_recode(time_span,
+                                "Pre-Lehrphase" = "pre",
+                                "Lehrphase" = "main",
+                                "Post-Lehrphase" = "subsequent",
+                                "Intviewphase" = "interview",
+                                "Endphase" = "after"
+                                ),
+         time_span = factor(time_span,
+                            levels = c("Pre-Lehrphase",
+                                       "Lehrphase",
+                                       "Post-Lehrphase",
+                                       "Intviewphase",
+                                       "Endphase"
+                                       )
+                            )
+         ) %>%
+  distinct() %>% 
+ggplot(mapping = aes(x = time,
+                     y = heart_rate
+                     )
+       ) +
+ # stat_smooth(geom = "line",
+             # mapping = aes(color = status),
+  #            method = "loess",
+   #           se = TRUE) 
+  geom_smooth(method = "glm") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Zeit (in Sekunden)",
+       y = "Herzrate (in Schlägen pro Minute)") +
+  theme_apa() +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x",
+             )
+
 ```

### 2022-11-25 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
upload fitbit paper

@@
       ) %>%
-      filter(time <= 600) %>%
+      # filter(time <= 600) %>% # filter for 10min intervals
+    filter(time <= 9000) %>% # filter for 2 hours 30min (maximal duration of study)
     select(!c("Time","Heart Rate","id"))
@@
 
-# Plot für einzelne Phasen
+## Plot für Gesamtverlauf
+
+```{r, fig.height = 8, fig.width = 15}
+
+  main %>% 
+  filter(time_span == "overall") %>% 
+  select("ID","time_span", "time","heart_rate") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+ # stat_smooth(geom = "line",
+ #             method = "loess",
+ #             se = FALSE) +
+  geom_smooth(method = "loess",
+              se = FALSE) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Zeit (in Sekunden)",
+       y = "Herzrate (in Schlägen pro Minute)") +
+  theme_apa()
+
+```
+
+## Plot für einzelne Phasen
 

### 2022-11-25 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
upload fitbit paper

@@
   transmute(ID = LI06_05, # select and rename relevant columns 
-            gender = factor(LI02_01_1,
-                            levels = 1:2,
-                            labels = c("male","female")
-                            ),
-            age = LI03_01, # 1 = male; 2 = female
-            teaching_experience = LI04_01,
-            school_type = LI18,
-            term = LI11_01, 
-            extracurricular_teaching_experience = LI14,
-            secondary_teaching_activities = LI17)
+            # gender = factor(LI02_01_1,
+            #                 levels = 1:2,
+            #                 labels = c("male","female")
+            #                 ),
+            gender = LI02_01_1, # 1 = male; 2 = female
+            age = LI03_01, 
+            teaching_experience = LI04_01)
+            # school_type = LI18)
+            # term = LI11_01, 
+            # extracurricular_teaching_experience = LI14,
+            # secondary_teaching_activities = LI17)
 
@@
             by = "ID")
+
 ```
@@
 
-# define expert and novice with ifelse function
-df_demo$ID = ifelse(df_demo$ID < 200, "Novice","Expert")
-
 # changing gender to count female gender (male = 2 --> 0)
@@
 df_demo <- df_demo %>%
-  group_by(ID) %>%
-  mutate(sum_participants = n())
-
-# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
-df_demo$school_type[df_demo$school_type == 2] <- "1"
-
-# creating new column to calculate percent of school type
-df_demo <- 
-  df_demo %>%
-  group_by(school_type, ID) %>%
-  mutate(count_schooltype = sum(n())) %>% 
-  mutate(percent_schooltype = round((count_schooltype/sum_participants) * 100, 
-         digits = 2))
-
-# changing character percent_schooltype into numeric
-df_demo$percent_schooltype <- as.numeric(df_demo$percent_schooltype)
-
-# changing Type of School into character
-# LI18:
-# 1: Grundschule
-# 2: Oberschule
-# 3: Gymnasium
-# 4: Förderschule/Sondershausen
-# 5: Berufsbildende Schule
-# -1: andere Schulform
-df_demo$school_type <- factor(x = df_demo$school_type,
-                   levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
-                   labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen
-
-# changing character semester into numeric
-df_demo$term <- as.numeric(df_demo$term)
-
-# changing `extracurricular_teaching_experience to count experience (no experience = 2 --> 0)
-df_demo$extracurricular_teaching_experience = ifelse(demo.data$extracurricular_teaching_experience == 1, "1","0")
-
-# changing character extracurricular_teaching_experience into numeric
-df_demo$extracurricular_teaching_experience <- as.numeric(df_demo$extracurricular_teaching_experience)
-
-# changing secondary_teaching_activities to count experience (no experience = 2 --> 0)
-df_demo$secondary_teaching_activities = ifelse(df_demo$secondary_teaching_activities == 1, "1","0")
-
-# changing character Extra. Exp. into numeric
-df_demo$secondary_teaching_activities <- as.numeric(df_demo$secondary_teaching_activities)
+  mutate(sum_participants = sum(n()))
 
 # create a basic table (tibble) using tidyverse functions
-df_demo <- df_demo %>%
-  group_by(ID) %>%
+df_demo_table <- df_demo %>%
   summarise(N=n(),
-            "Gender female in percent" = round(sum(Gender/Sum_participants) * 100, 
+            "Gender female in percent" = round(sum(gender/sum_participants) * 100,
                                                digits = 2),
-            "M Age in years" = round(mean(Age), 
+            "M Age in years" = round(mean(age),
                                      digits = 2),
-            "SD Age in years" = round(sd(Age), 
+            "SD Age in years" = round(sd(age),
                                       digits = 2),
-            "Min Age in years" = min(Age),
-            "Max Age in years" = max(Age)
+            "Min Age in years" = min(age),
+            "Max Age in years" = max(age),
+            "M Teaching Experience in years" = round(mean(teaching_experience),
+                                            digits = 2),
+            "SD Teaching Experience in years" = round(sd(teaching_experience),
+                                            digits = 2),
+            "Min Teaching Experience in years" = min(teaching_experience),
+            "Max Teaching Experience in years" = max(teaching_experience)
             )
@@
 # # format and insert table in manuscript
-# demo.table %>%
+# df_demo_table %>%
 # papaja::apa_table(
@@
 
-# create a basic table (tibble) using tidyverse functions
-exp.table <- demo.data %>%
-  group_by(ID) %>%
-  summarise(N=n(),
-           "M Exp." = round(mean(`Teaching Experience`), 2),
-            "SD Exp." = round(sd(`Teaching Experience`), 2),
-            "Min Exp." = min(`Teaching Experience`),
-            "Max Exp." = max(`Teaching Experience`),
-            "M Semester" = round(mean(Semester), 2),
-            "SD Semester" = round(sd(Semester), 2),
-            "Min Semester" = min(Semester),
-            "Max Semester" = max(Semester),
-            "M Internship" = round(mean(Internship), 2),
-            "SD Internship" = round(sd(Internship), 2),
-            "Min Internship" = min(Internship),
-            "Max Internship" = max(Internship),
-            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
-            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
-           )
-
-# # format and insert table in manuscript
-# exp.table %>%
-# papaja::apa_table(
-#   caption = "Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent",
-#   # note = "Write Note here",
-#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-#   )
-
 ```
 
-The sample consisted of *N* = `r length(df_demo$ID)` participants with *n* = `r length(df_demo$ID[df_demo$ID == "Expert"])` expert teachers and *n* = `r length(demo.data$ID[demo.data$ID == "Novice"])` novice teachers.
+The sample consisted of *N* = `r length(df_demo$ID)` participants. Data of two participants were excluded from the analyses due to insufficient data quality.
 
-The data of two participants (two novices, XXX experts) were excluded from the analyses due to insufficient data quality.
-
-The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
-According to @palmer2005identifying, we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
-Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
-
-The expert teachers (`r demo.data %>% filter(Gender == 1 & ID == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(ID == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(ID == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(ID == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(ID == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(ID == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(ID == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(ID == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(ID == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(ID == "Expert") %>% pull("Max Exp.")`).
-`r demo.data %>% filter(ID == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(ID == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers.
-`r exp.table %>% filter(ID == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
-
-The novice teachers (`r demo.data %>% filter(Gender == 1 & ID == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(ID == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(ID == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(ID == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(ID == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(ID == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(ID == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years.
-On average, the student teachers were in their `r exp.table %>% filter(ID == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(ID == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(ID == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(ID == "Novice") %>% pull("Max Semester")`).
-Furthermore, they had an average teaching experience of `r exp.table %>% filter(ID == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(ID == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(ID == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(ID == "Novice") %>% pull("Max Internship")`) through the internships during their studies.
-`r demo.data %>% filter(ID == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(ID == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% to become secondary school teachers and `r demo.data %>% filter(ID == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype") %>% unique()`% to become special education teachers.
-`r exp.table %>% filter(ID == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
-
-The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at Leipzig University.
-All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
-The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
-All participants were informed in detail about the aim and intention of the study prior to testing.
-Participation in the study was voluntary and only took place after written consent has been given.
+The subjects (`r df_demo %>% filter(gender == 1) %>% pull(gender) %>% length()` women; `r df_demo_table %>% pull("Gender female in percent")` %) had a mean age of `r df_demo %>% pull(age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r df_demo_table %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r df_demo_table %>%  pull("Min Age in years")`-`r df_demo_table %>% pull("Max Age in years")`) and an average teaching experience of `r df_demo_table %>% pull("M Teaching Experience in years")` years (*SD* = `r df_demo_table %>% pull("SD Teaching Experience in years")`; range: `r df_demo_table %>% pull("Min Teaching Experience in years")`-`r df_demo_table %>% pull("Max Teaching Experience in years")`).
 

### 2022-11-25 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
upload fitbit paper

@@
 {}{\PatchFailed}
-\keywords{heart rate; photoplethysmography; wearable electronic device; expertise differences\newline\indent Word count: X}
+\keywords{heart rate; photoplethysmography; wearable electronic device; teaching\newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
   pdflang={en-EN},
-  pdfkeywords={heart rate; photoplethysmography; wearable electronic device; expertise differences},
+  pdfkeywords={heart rate; photoplethysmography; wearable electronic device; teaching},
   hidelinks,
@@
 
-Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases and (2) between experienced and inexperienced teachers.
-We expected heart rates to be higher in the arousal phase than in the rest phases and exploratively examine whether experienced teachers have lower heart rates and more steps compared to inexperienced teachers.
+Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases.
+We expected heart rates to be higher in the arousal phase than in the rest phases.
 
@@
 
-The sample consisted of \emph{N} = 51 participants with \emph{n} = 19 expert teachers and \emph{n} = 32 novice teachers.
+\begin{table}[h]
 
-The data of two participants (two novices, XXX experts) were excluded from the analyses due to insufficient data quality.
+\begin{center}
+\begin{threeparttable}
 
-The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
-According to Palmer, Stough, Burdenski, and Gonzales (2005), we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
-Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
+\caption{\label{tab:demographicstable}Demographic Information}
 
-The expert teachers (11 women; 57.89\%) had a mean age of 41.70 years (\emph{SD} = 10.40; range: 27-59) and an average teaching experience of 13.70 years (\emph{SD} = 12.40; range: 2-37).
-15.79\% of the experts were primary school teachers and 84.21\% were secondary school teachers.
-47\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+\tiny{
 
-The novice teachers (23 women; 71.88\%) had a mean age of 23 years (\emph{SD} = 1.90; range: 19-27) with an average teaching experience of 0 years.
-On average, the student teachers were in their 7 semester (\emph{SD} = 2.60; range: 3-11).
-Furthermore, they had an average teaching experience of 10.30 teaching units à 45min (\emph{SD} = 7.70; range: 0-36) through the internships during their studies.
-21.88\% of the novices were studying to become primary school teachers, 62.50\% to become secondary school teachers and 15.62\% to become special education teachers.
-90.62\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+\begin{tabular}{llllllllll}
+\toprule
+N & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Teaching Experience in years} & \multicolumn{1}{c}{SD Teaching Experience in years} & \multicolumn{1}{c}{Min Teaching Experience in years} & \multicolumn{1}{c}{Max Teaching Experience in years}\\
+\midrule
+63 & 63.49 & 29.32 & 10.34 & 19.00 & 59.00 & 4.51 & 9.18 & 0.00 & 37.00\\
+\bottomrule
+\end{tabular}
 
-The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at Leipzig University.
-All study procedures were carried out in accordance with the ethical standards of the University's Institutional Review Board.
-The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
-All participants were informed in detail about the aim and intention of the study prior to testing.
-Participation in the study was voluntary and only took place after written consent has been given.
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+The sample consisted of \emph{N} = 63 participants. Data of two participants were excluded from the analyses due to insufficient data quality.
+
+The subjects (40 women; 63.49 \%) had a mean age of 29.30 years (\emph{SD} = 10.30; range: 19-59) and an average teaching experience of 4.51 years (\emph{SD} = 9.18; range: 0-37).
 
@@
 
-We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) for all our analyses.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-R-DescTools}{}}%
+Andri et mult. al., S. (2022). \emph{{DescTools}: Tools for descriptive statistics}. Retrieved from \url{https://cran.r-project.org/package=DescTools}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
+Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-gridExtra}{}}%
+Auguie, B. (2017). \emph{gridExtra: Miscellaneous functions for "grid" graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridExtra}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
@@
 Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
+Bates, D., Mächler, M., Bolker, B., \& Walker, S.
+(2015).
+Fitting linear mixed-effects models using {lme4}.
+\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
+\url{https://doi.org/10.18637/jss.v067.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
+Bates, D., Maechler, M., \& Jagan, M. (2022). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lm.beta}{}}%
+Behrendt, S. (2022). \emph{Lm.beta: Add standardized regression coefficients to lm-objects}. Retrieved from \url{https://CRAN.R-project.org/package=lm.beta}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-janitor}{}}%
+Firke, S. (2021). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
+
 \leavevmode\vadjust pre{\hypertarget{ref-fisher2011factors}{}}%
 Fisher, M. H. (2011). Factors influencing stress, burnout, and retention of secondary teachers. \emph{Current Issues in Education}, \emph{14}(1).
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-polycor}{}}%
+Fox, J. (2022). \emph{Polycor: Polychoric and polyserial correlations}. Retrieved from \url{https://CRAN.R-project.org/package=polycor}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
+Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
+Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-lubridate}{}}%
+Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with {lubridate}. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{https://www.jstatsoft.org/v40/i03/}
+
 \leavevmode\vadjust pre{\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-msm}{}}%
+Jackson, C.
+H.
+(2011).
+Multi-state models for panel data: The {msm} package for {R}.
+\emph{Journal of Statistical Software}, \emph{38}(8), 1--29.
+Retrieved from \url{https://www.jstatsoft.org/v38/i08/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggpubr}{}}%
+Kassambara, A. (2020). \emph{Ggpubr: 'ggplot2' based publication ready plots}. Retrieved from \url{https://CRAN.R-project.org/package=ggpubr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rstatix}{}}%
+Kassambara, A. (2021). \emph{Rstatix: Pipe-friendly framework for basic statistical tests}. Retrieved from \url{https://CRAN.R-project.org/package=rstatix}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-needs}{}}%
+Katz, J. (2016). \emph{Needs: Attaches and installs packages}. Retrieved from \url{https://CRAN.R-project.org/package=needs}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ppcor}{}}%
+Kim, S. (2015). \emph{Ppcor: Partial and semi-partial (part) correlation}. Retrieved from \url{https://CRAN.R-project.org/package=ppcor}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-jtools}{}}%
+Long, J. A. (2022). \emph{Jtools: Analysis and presentation of social scientific data}. Retrieved from \url{https://cran.r-project.org/package=jtools}
+
 \leavevmode\vadjust pre{\hypertarget{ref-lowe2016educational}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-palmer2005identifying}{}}%
-Palmer, D.
-J., Stough, L.
-M., Burdenski, T.
-K., Jr, \& Gonzales, M.
-(2005).
-Identifying teacher expertise: An examination of researchers' decision making.
-\emph{Educational Psychologist}, \emph{40}(1), 13--25.
+\leavevmode\vadjust pre{\hypertarget{ref-R-imputeTS}{}}%
+Moritz, S., \& Bartz-Beielstein, T. (2017). {imputeTS: Time Series Missing Value Imputation in R}. \emph{{The R Journal}}, \emph{9}(1), 207--218. \url{https://doi.org/10.32614/RJ-2017-009}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
+Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
@@
 R Core Team. (2022). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ltm}{}}%
+Rizopoulos, D.
+(2006).
+Ltm: An r package for latent variable modelling and item response theory analyses.
+\emph{Journal of Statistical Software}, \emph{17}(5), 1--25.
+Retrieved from \url{https://doi.org/10.18637/jss.v017.i05}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-broom}{}}%
+Robinson, D., Hayes, A., \& Couch, S. (2022). \emph{Broom: Convert statistical objects into tidy tibbles}. Retrieved from \url{https://CRAN.R-project.org/package=broom}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-MASS}{}}%
+Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
+Wickham, H. (2021). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
+Wickham, H., \& Bryan, J. (2022). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2022). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
+Wickham, H., \& Girlich, M. (2022). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
+Wickham, H., Hester, J., \& Bryan, J. (2022). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
+Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+
 \end{CSLReferences}

### 2022-11-25 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
fitbit paper participants

@@
 # demographic data
-df_demo <- 
+df_demo_all <- 
   read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
@@
             age = LI03_01, 
-            teaching_experience = LI04_01)
-            # school_type = LI18)
-            # term = LI11_01, 
-            # extracurricular_teaching_experience = LI14,
-            # secondary_teaching_activities = LI17)
+            teaching_experience = LI04_01,
+            school_type = LI18,
+            term = LI11_01,
+            extracurricular_teaching_experience = LI14,
+            secondary_teaching_activities = LI17)
 
 # merge two data frames by ID 
-df_merge <- merge(df_demo,
+df_merge <- merge(df_demo_all,
                   df_rating,
@@
 
+# exclude cases with no fitbit data
+df_demo <- df_demo_all %>% 
+  filter(!ID %in% c("126",
+                     "132"
+                     )
+          )
+
 # changing gender to count female gender (male = 2 --> 0)
@@
 
+# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
+df_demo$school_type[df_demo$school_type == 2] <- "1"
+
+# creating new column to calculate percent of school type
+df_demo <- 
+  df_demo %>%
+  group_by(school_type) %>%
+  mutate(count_schooltype = sum(n())) %>% 
+  mutate(percent_schooltype = round((count_schooltype/sum_participants) * 100, 
+         digits = 2))
+
+# changing character Percent_schooltype into numeric
+df_demo$percent_schooltype <- as.numeric(df_demo$percent_schooltype)
+
+#changing type of school into character
+# LI18:
+# 1: Grundschule
+# 2: Oberschule
+# 3: Gymnasium
+# 4: Förderschule/Sondershausen
+# 5: Berufsbildende Schule
+# -1: andere Schulform
+df_demo$school_type <- factor(x = df_demo$school_type,
+                              levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
+                              labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen
+
 # create a basic table (tibble) using tidyverse functions
 df_demo_table <- df_demo %>%
+  ungroup() %>%
   summarise(N=n(),
@@
 
-The sample consisted of *N* = `r length(df_demo$ID)` participants. Data of two participants were excluded from the analyses due to insufficient data quality.
+The sample consisted in total of *N* = `r length(df_demo_all$ID)` pre- and in-service teachers.
+The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
+Data of two participants were excluded from the analyses due to insufficient data quality, yielding demographic data from *N* = `r length(df_demo$ID)` subjects.
 
@@
 
+`r df_demo %>% filter(school_type == "Primary School") %>% pull("percent_schooltype") %>% unique()`% of the subjects were (studying to become) teachers for primary school, `r df_demo %>% filter(school_type == "Secondary School") %>% pull("percent_schooltype") %>% unique()`% were (studying to become) teachers for secondary school and  `r df_demo %>% filter(school_type == "Special Education") %>% pull("percent_schooltype") %>% unique()`% were (studying to become) teachers for special education needs.
+
+All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+All participants were informed in detail about the aim and intention of the study prior to testing.
+Participation in the study was voluntary and only took place after written consent has been given.
+
 ## Material
+
+### Teachers' heart rate
 We used a Fitbit Charge 4 to measure the teachers' heart rate.
@@
 
+### Teachers' self-assessment of arousal during the teaching phase
+
 ## Procedure
+
+The data collection was part of a larger research project with a planned sample of *n* = 40 in-service teachers and *n* = 40 pre-service teachers.
+
+In a controlled laboratory setting, heart rate data in beats per minute (bpm) were recorded using Fitbit Charge 4 over a total period of approximately two hours.
+Within this time frame, teachers taught a 15-minute self-prepared lesson to an audience of three actors.
+For analyzing the heart rate data, we selected five 10-minute intervals of theoretical interest:
+(1) the pre-teaching phase, which started from the moment the subject put on the watch 
+(2) the teaching phase, which began at the moment when the subject started the lesson 
+(3) the post-teaching phase, which was the 10 minutes immediately after the end of the lesson
+(4) the interview phase, which was 10 minutes in the middle of the interview (for this, the difference was calculated from the end of the lesson and from the time when the subject took off the watch.
+This duration was divided in two to get to the middle of the interval and 5 minutes were subtracted to get to the start of the 10-minute interval),
+(5) the end phase, which was the 10 minutes before the subject took off the watch.
+
 In a laboratory setting, three trained actors performed teaching disruptions in a counter balanced fashion while the subject taught a 15-minute micro-teaching unit prepared in advance.
@@
 
-The Fitbit watch was removed only after the last questionnaire to obtain heart rate at three different measurement time points: before, during, and after the lesson.
+The Fitbit watch was removed only after the last questionnaire to obtain heart rate data during the entire study.
 
@@
 ## Heart Rate
-
-The heart rate of each subject were measured before, during and after the experiment.
-
-```{r}
-# Initial Preparations
-
-## Run following Code only if new data is added to the initial data.
-# 
-# source(file = "data.wrangling.R")
-# 
-# # aggregate data 
-# df_heart_all <-
-#   read_rds(file = "data/heart_all.rds") |> 
-#   mutate(status = factor(status,
-#                          levels = c("Expert","Novice"),
-#                          labels = c("Expert","Novice")
-#                          )
-#          )
-# 
-# df_heart_min <-
-#   read_rds(file = "data/heart_min.rds")
-# 
-# df_heart_aggr <- 
-#   read_rds(file = "data/heart_aggr.rds") |> 
-#   mutate(status = factor(status,
-#                          levels = c("Novice","Expert"),
-#                          labels = c("Novice","Expert")
-#                          )
-#          )
-# 
-# 
-# # Mean, SD, t-test & Cohen D for experts & novices
-# # novices
-# mean_nov <- 
-#   df_heart_aggr %>%
-#   filter(status == "Novice" ) %>% 
-#   pull(mean) %>% 
-#   mean() %>% 
-#   round(., digits = 0)
-# 
-# sd_nov <- 
-#   df_heart_aggr %>%
-#   filter(status == "Novice") %>% 
-#   pull(mean) %>% 
-#   sd() %>% 
-#   round(., digits = 0)
-# 
-# # experts
-# mean_exp <-
-#   df_heart_aggr %>%
-#   filter(status == "Expert") %>% 
-#   pull(mean) %>% 
-#   mean() %>% 
-#   round(., digits = 0)
-# 
-# sd_exp <- 
-#   df_heart_aggr %>%
-#   filter(status == "Expert") %>% 
-#   pull(mean) %>% 
-#   sd() %>% 
-#   round(., digits = 0)
-# 
-# # t-test for expertise differences
-# t.test(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
-#        y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"])
-# 
-# 
-# # effect size for expertise differences
-# d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
-#                y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
-#                na.rm = TRUE)
-# 
-# 
-# # Plots
-# 
-# plot_flow_leg <-
-# ggplot(data = df_heart_all,
-#        mapping = aes(x = Time,
-#                      y = `Heart Rate`
-#                      )
-#        ) +
-#   xlim(0, 600) +
-#   geom_smooth(mapping = aes(color = status),
-#               method = "loess") +
-#   scale_color_viridis_d(option = "A",
-#                         end = 0.8) +
-#   scale_linetype_manual(values = c(1, 6)) +
-#   labs(x = "Time (in Seconds)",
-#        y = "Heart Rate\n(in Beats per Minute)") +
-#   ggtitle("Experts' and novices' heart rate per phase") +
-#   theme_minimal() +
-#   theme(text = element_text(family = "serif"),
-#         legend.text = element_text(size = 15),
-#         legend.title = element_blank(),
-#         axis.text.x = element_text(size = 12),
-#         axis.text.y = element_text(size = 10),
-#         strip.text = element_text(size = 16),
-#         plot.title = element_text(size = 20, 
-#                                   face = "bold")) +
-#   facet_grid(cols = vars(Type),
-#              scales = "free_x")
-# 
-# # saving plot 
-# ggsave(plot = plot_flow_leg,
-#        filename = "plots/plot_flow_leg.svg",
-#        height = 5,
-#        width = 8,
-#        units = "in")
-
-```
-
-### Steps
-
-Using the FitBit we measured the steps a person walked during the experiment as well.
-We validated the steps in six randomly selected videos by manual step counting.
-A step was considered to be the movement of the subject's foot forward, backward, or sideways.
-The measurement was not as reliable as hoped.
-
-```{r}
-# df_steps <- read_rds(file = "data/steps.rds")
-# set.seed(5678)
-# ggplot(data = df_steps,
-#        mapping = aes(x = type,
-#                      y = Steps
-#                      )
-#        ) +
-#   geom_boxplot(mapping = aes(color = type),
-#                fill = "grey",
-#                alpha = 0.6) +
-#   geom_jitter(mapping = aes(color = type),
-#               alpha = 0.9,
-#               width = 0.3) +
-#   scale_color_viridis_d(option = "A",
-#                        end = 0.8) +
-#   labs(x = "",
-#        y = "Steps During\nMain Phase") +
-#   theme_minimal() +
-#   theme(text = element_text(family = "serif"),
-#         legend.title = element_blank(),
-#         axis.text.x = element_blank(),
-#         axis.ticks.x = element_blank()
-#         )
-# 
-# ### Validation of steps
-# # selecting some rows at random with sample_n()
-# sample_n(df_steps, 6)
-# 
-# # random ID Output:
-# # Novices ID: 102, 125, 110
-# # Experts ID: 219, 218, 214
-# 
-# # Results from manual step counting:
-# # Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
-# # Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps
-
-```
 

### 2022-11-25 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
fitbit paper participants

@@
 
-\begin{table}[h]
+The sample consisted in total of \emph{N} = 63 pre- and in-service teachers.
+The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
+Data of two participants were excluded from the analyses due to insufficient data quality, yielding demographic data from \emph{N} = 61 subjects.
 
-\begin{center}
-\begin{threeparttable}
+The subjects (39 women; 63.93 \%) had a mean age of 29.60 years (\emph{SD} = 10.40; range: 19-59) and an average teaching experience of 4.66 years (\emph{SD} = 9.30; range: 0-37).
 
-\caption{\label{tab:demographicstable}Demographic Information}
+18.03\% of the subjects were (studying to become) teachers for primary school, 72.13\% were (studying to become) teachers for secondary school and 9.84\% were (studying to become) teachers for special education needs.
 
-\tiny{
-
-\begin{tabular}{llllllllll}
-\toprule
-N & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Teaching Experience in years} & \multicolumn{1}{c}{SD Teaching Experience in years} & \multicolumn{1}{c}{Min Teaching Experience in years} & \multicolumn{1}{c}{Max Teaching Experience in years}\\
-\midrule
-63 & 63.49 & 29.32 & 10.34 & 19.00 & 59.00 & 4.51 & 9.18 & 0.00 & 37.00\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-The sample consisted of \emph{N} = 63 participants. Data of two participants were excluded from the analyses due to insufficient data quality.
-
-The subjects (40 women; 63.49 \%) had a mean age of 29.30 years (\emph{SD} = 10.30; range: 19-59) and an average teaching experience of 4.51 years (\emph{SD} = 9.18; range: 0-37).
+All study procedures were carried out in accordance with the ethical standards of the University's Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+All participants were informed in detail about the aim and intention of the study prior to testing.
+Participation in the study was voluntary and only took place after written consent has been given.
 
@@
 \subsection{Material}\label{material}}
+
+\hypertarget{teachers-heart-rate}{%
+\subsubsection{Teachers' heart rate}\label{teachers-heart-rate}}
 
@@
 URL: \url{https://iccir919.github.io/pulseWatch/public/index.html} {[}accessed 2022-08-03{]}).
+
+\hypertarget{teachers-self-assessment-of-arousal-during-the-teaching-phase}{%
+\subsubsection{Teachers' self-assessment of arousal during the teaching phase}\label{teachers-self-assessment-of-arousal-during-the-teaching-phase}}
 

### 2022-11-25 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
Update fitbit_paper.Rmd

@@
 ### Teachers' self-assessment of arousal during the teaching phase
+Two 11-point rating scales were used to assess the subject's self-assessment of arousal during the Stimulated Recall Interview.
+The rating scales collected data of the teacher's subjective perception of disruptiveness of a lesson event and their subjective perception of confidence in dealing with the event during the lesson.
+
+For this purpose, the recording was stopped shortly before the respective disruption and first a stimulus was given to the following event, as well as the teacher was asked to briefly comment on the disturbance itself.
+The subjective perception of the disruptiveness of an event was asked following the teacher's elaboration on the disturbance in question as follows: "On a scale of 0-10: how disruptive did you find the event?
+0 is not disruptive at all, 10 is extremely disruptive" (see appendix).
+
+The subjective confidence with regard to the respective classroom disruption was collected and measured in the same way as the subjective perception of disruptiveness.
+The collection of the data took place chronologically after the statements about the disruption perception.
+After the description and justification of the reaction, the feeling of safety in dealing with the classroom disturbance was asked as follows: "Please rate your confidence in dealing with the event on a scale of 0-10: How confident did you feel in dealing with this event?
+0 is not confident at all and 10 is extremely confident" (see Appendix).
+
+The response format was deliberately chosen to be closed and multilevel, since numerical values are thus assigned to the subjects' emotional world, and this can thus be made measurable and comparable (cf.
+Eid et al., 2013; Botz & Döring, 2016).
+The levels of the rating scale prepared for this purpose are unambiguous, and the distances between them were equal.
+The feature expression was estimated and verbally communicated by the subjects immediately after seeing the recording of the respective disturbance.
 

### 2022-12-01 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update fitbit paper

--- 2022-11-25 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
@@
 The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
-Data of two participants were excluded from the analyses due to insufficient data quality, yielding demographic data from *N* = `r length(df_demo$ID)` subjects.
+Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from *N* = `r length(df_demo$ID)` subjects.
 
@@
 ### Teachers' self-assessment of arousal during the teaching phase
+The subject's self-assessment of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.
+For this purpose, two numerical 11-point rating scales were used: _(1)_	The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption with the following question: "On a scale of 0-10: how disruptive did you find the event?
+0 is not disruptive at all, 10 is extremely disruptive" _(2)_	The second rating scale assessed the teacher’s subjective perception of confidence in dealing with the disruptions during the lesson asked as follows: "How confident did you feel in dealing with this event on a scale of 0-10?
+0 is not confident at all and 10 is extremely confident"
+The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjetcts' self-assessment and emotional experience, and thus to make them measurable and comparable [@eid2015statistik; @doring2016empirische].
+The gradations of the rating scale were unambiguous and the intervals between them identical.
+The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally to the experimenter.
 

### 2022-12-01 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
update fitbit paper

@@
 
+The subject's self-assessment of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.
+
+For this purpose, two numerical 11-point rating scales were used:
+(1) The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption with the following question: ``On a scale of 0-10: how disruptive did you find the event?
+0 is not disruptive at all, 10 is extremely disruptive''
+(2) The second rating scale assessed the teacher's subjective perception of confidence in dealing with the disruptions during the lesson asked as follows: ``How confident did you feel in dealing with this event on a scale of 0-10?
+0 is not confident at all and 10 is extremely confident''
+
+The response format here was purposely chosen to be closed and with several answer options in order to assign numerical values to the assessment and emotional experience of the subjects, and thus to make them measurable and comparable {[}Eid, Gollwitzer, and Schmitt (2015); doring2016empirische{]}.
+The gradations of the rating scale are unambiguous and the intervals between them are identical.
+The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally.
+
 \hypertarget{procedure}{%
 \subsection{Procedure}\label{procedure}}
+
+The data collection was part of a larger research project with a planned sample of \emph{n} = 40 in-service teachers and \emph{n} = 40 pre-service teachers.
+
+In a controlled laboratory setting, heart rate data in beats per minute (bpm) were recorded using Fitbit Charge 4 over a total period of approximately two hours.
+Within this time frame, teachers taught a 15-minute self-prepared lesson to an audience of three actors.
+For analyzing the heart rate data, we selected five 10-minute intervals of theoretical interest:
+(1) the pre-teaching phase, which started from the moment the subject put on the watch
+(2) the teaching phase, which began at the moment when the subject started the lesson
+(3) the post-teaching phase, which was the 10 minutes immediately after the end of the lesson
+(4) the interview phase, which was 10 minutes in the middle of the interview (for this, the difference was calculated from the end of the lesson and from the time when the subject took off the watch.
+This duration was divided in two to get to the middle of the interval and 5 minutes were subtracted to get to the start of the 10-minute interval),
+(5) the end phase, which was the 10 minutes before the subject took off the watch.
 
@@
 \subsection{Heart Rate}\label{heart-rate}}
-
-The heart rate of each subject were measured before, during and after the experiment.
-
-\hypertarget{steps}{%
-\subsubsection{Steps}\label{steps}}
-
-Using the FitBit we measured the steps a person walked during the experiment as well.
-We validated the steps in six randomly selected videos by manual step counting.
-A step was considered to be the movement of the subject's foot forward, backward, or sideways.
-The measurement was not as reliable as hoped.
 
@@
 Behrendt, S. (2022). \emph{Lm.beta: Add standardized regression coefficients to lm-objects}. Retrieved from \url{https://CRAN.R-project.org/package=lm.beta}
+
+\leavevmode\vadjust pre{\hypertarget{ref-eid2015statistik}{}}%
+Eid, M., Gollwitzer, M., \& Schmitt, M.
+(2015).
+\emph{Statistik und forschungsmethoden: Mit online-materialien (4., {ü}berarb.
+Und erw.
+aufl.)}.
+Weinheim: Beltz.
+Retrieved from https://contentselect.
+com/media/moz\_viewer~\ldots.
 

### 2022-12-04 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
uploading the procedure

@@
 
+The study took place in the rooms of the Faculty of Education at Leipzig University.
 In a controlled laboratory setting, heart rate data in beats per minute (bpm) were recorded using Fitbit Charge 4 over a total period of approximately two hours.
 Within this time frame, teachers taught a 15-minute self-prepared lesson to an audience of three actors.
-For analyzing the heart rate data, we selected five 10-minute intervals of theoretical interest:
-(1) the pre-teaching phase, which started from the moment the subject put on the watch 
-(2) the teaching phase, which began at the moment when the subject started the lesson 
-(3) the post-teaching phase, which was the 10 minutes immediately after the end of the lesson
-(4) the interview phase, which was 10 minutes in the middle of the interview (for this, the difference was calculated from the end of the lesson and from the time when the subject took off the watch.
-This duration was divided in two to get to the middle of the interval and 5 minutes were subtracted to get to the start of the 10-minute interval),
-(5) the end phase, which was the 10 minutes before the subject took off the watch.
 
-In a laboratory setting, three trained actors performed teaching disruptions in a counter balanced fashion while the subject taught a 15-minute micro-teaching unit prepared in advance.
-To record the subject's heart rate, the Fitbit Charge 4 was put on at least 10 minutes before the start of the lesson.
-The lesson was recorded by four cameras and an audio recorder.
-In addition, the subject wore eye-tracking glasses to record gaze behavior.
+For this purpose, a seminar room was converted into a classroom.
+The classroom was equipped with a digital whiteboard and a blackboard.
+The fictitious class consisting of three trained actors sat facing the teacher head-on in a "U"; pen and paper were provided on their seats.
+In addition, the students brought their own mobile phone, which was also visibly positioned on the desk.
 
-Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire (EMU, @helmke2014unterrichtsdiagnostik) and self developed scales on the teacher's presence behavior derived from the research literature via the online survey website SoSci Survey (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree).
+The subject was instructed during the lesson to behave and move as naturally as possible, as they would in a real classroom.
+In advance, all subjects were given information about planning their lesson in a meeting to ensure that an appropriately realistic teaching situation could take place, e.g.
+it was pointed out that longer film clips as well as group work as a social form should be avoided in order to ensure interaction between teacher and students in the short time of the study.
+
+For analyzing the heart rate data, we selected five 10-minute intervals of theoretical interest.
+To ensure that the intervals are comparable for all participants, we decided on 10-minute intervals because this was the minimum duration of all intervals.
+The individual intervals are described in detail below.
+
+_(1)_ The _pre-teaching phase_ was the first 10 minutes belonging to the interval of interest.
+This interval was calculated from the moment the subject arrived and the Fitbit watch was put on, which happened immediately after the subject was welcomed by the experimenter and the three actors.
+After the experimenter briefly explained the project and the procedure of the study to the subject, contact details were subsequently collected as part of the hygiene concept of COVID-19 and the written consent to voluntarily participate in the study was requested.
+Next, the subject was asked to prepare the necessary materials for the lesson (connecting the laptop to the beamer, preparing worksheets, etc.).
+This phase varied in duration according to the prepared lesson (about 1-5min on average).
+
+Once the preparation was completed, the eye-tracking glasses were briefly explained to the subject as well as the adjustment made to the subject by the experimenter (changing the lenses or the nose pad if necessary).
+Subsequently, a 1-point calibration of the eye-tracking glasses took place and together with further devices (GoPro camera, 3D camera, audio recorder) the recordings were started.
+
+Before the lesson began, a warm-up phase took place to familiarize the subject with the laboratory setting and equipment. This warm-up phase consisted of two parts:
+
+-	In the first part, the subject and the three actors playfully learned each other's names.
+Additional fictitious name tags of the actors were attached to the table and did not change across the study.
+In the game, by throwing two balls, either the participant's own name or the name of the target person was called.
+-	The second part of the warm-up phase involved getting into conversation with each other by asking questions.
+For this purpose, the subject was asked to come up with a question for each of the actors (three questions in total) and was also asked a question in return by each actor.
+This could be anything that interested the participants.
+The questions should be as authentic as possible and were not tailored to the role of the actors.
+The purpose of this warming-up phase was, on the one hand, to make the subject forget about the devices and, on the other hand, to create as realistic as possible a classroom situation in which interactions were based on a teacher-student relationship.
+
+The pre-teaching phase lasted 10-15 minutes on average, depending on different issues (preparing the lesson, technical problems, adjusting the eye-tracking glasses). XXX GENAUEN M + SD BERECHNEN XXX
+
+_(2)_ The second 10-minute interval was the _teaching phase_, which began with the experimenter noting the time and step count of the fitness tracker.
+The subject was then asked to carry out a 9-point calibration alone in a room next door.
+After the calibration, the lesson started with the subject opening the door to the laboratory room.
+During the lesson, the actors were instructed to simulate nine typical classroom events, three each in the following categories: (a) verbal disruptive behavior (chatting with the neighbor, whispering, heckling), (b) physical disruptions (clicking with a pen, drumming with hands on the table, snipping) and (c) lack of eagerness to learn (drawing on a sheet of paper, putting the head on the table, looking at the phone).
+
+The order of the events and the performing actors were fully balanced with Latin square. The actors were trained before to perform the disruptions identically in each data collection.
+
+After a short familiarization phase for the teacher of two and a half minutes, the instructions appeared as intervals (every 90 seconds for 30 seconds) on a screen that was only visible for the class.
+The actors were trained to stop the disruptive behavior as soon as the teacher intervened.
+
+Time management was regulated by the experimenter by showing time cards (yellow = 1 minute until the end; red = end of the lesson).
+The lesson lasted about 18 minutes on average but only the first 10 minutes were used as an interval to ensure the identical duration for all participants.
+XXX GENAUEN M + SD BERECHNEN XXX At the end of the lesson, the experimenter again noted the time and the steps on the clock.
+
+_(3)_ The noted time of the lesson end was also the starting point for the _post-teaching_ phase as the third 10 minute interval.
+At the end of the lesson, the experimenter attached letters A through D in the lab while the teacher performed a second 9-point calibration outside.
+The letter search as a control condition was part of another project, which is why it will not be discussed further in the study.
+Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree; EMU, @helmke2014unterrichtsdiagnostik) via the online survey website SoSci Survey.
 The completion of the questionnaire took approximately 5 minutes.
 
-The experimenter then conducted a Stimulated Recall Interview (SRI), where the subject commented and rated the reactions to classroom events while watching the eye tracking video.
+Meanwhile, the experimenter prepared the second part of the data collection: The Stimulated Recall Interview.
+Within post-teaching phase, the majority of subjects completed the questionnaire and positioned themselves next to the experimenter to begin the interview.
+In some cases, the beginning of the interview was part of the post-teaching phase due to individual needs (going to the toilet, spending more time completing the questionnaire, etc.).
 
-Finally, a Situational Judgment Test (SJT, @gold2015development) was used to assess the subject's strategic knowledge of classroom management.
+_(4)_ The fourth 10 minute interval of interest was the _interview phase_ that are 10 minutes in the middle of the interview.
+To ensure that all subjects were in the middle of the interview, we calculated the difference from the end of the lesson and from the time when the subject took off the watch.
+This duration was divided in two to get to the middle of the interval.
+Then, 5 minutes were subtracted to get to the start of the 10-minute interval.
+
+The interview itself took place using the Think Aloud procedure (Konrad, 2020).
+For this purpose, the eye tracking video was watched again and the experimenter stopped the video at the nine disruptions when they appeared to asks several questions.
+The questions were identical for each disruption, they were asked in a fixed order.
+First, the subject was asked to describe the disruption, to evaluate (11-point rating scale) and justify the disruptiveness of each disruption.
+Next, the subject was asked to describe and justify the reaction.
+The experimenter then asked the subject to evaluate (11-point rating scale) and justify the confidence the subject had in dealing with the disruption.
+Statements about the evaluation of the disruptiveness and the confidence were quantified.
+For this purpose, subjects determined their individual value on a rating scale from 0 (not disturbing / not safe) to 10 (disturbing / safe).
+
+The interview lasted on average 45-60 minutes.
+
+_(5)_ The last interesting interval for the analyses is the _end phase_, which was the 10 minutes before the subject took off the watch.
+In this interval, the subject answered a second questionnaire (Situational Judgment Test, @gold2015development) to assess the subject's strategic knowledge of classroom management.
 The subject was asked to judge alternative actions on school scenarios on a 6-point rating scale from 1 (A) to 6 (F) according to school grades.
-Data from the SJT were again collected as an online questionnaire via the website www.soscisurvey.de and lastet approximately 10 minutes.
+Data from the questionnaire were again collected as an online questionnaire via the website www.soscisurvey.de and lasted approximately 10-15 minutes.
 

### 2022-12-04 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
uploading the procedure

--- 2022-11-25 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
@@
 The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
-Data of two participants were excluded from the analyses due to insufficient data quality, yielding demographic data from \emph{N} = 61 subjects.
+Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 61 subjects.
 
@@
 
+The subject's self-assessment of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.
+For this purpose, two numerical 11-point rating scales were used: \emph{(1)} The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption with the following question: ``On a scale of 0-10: how disruptive did you find the event?
+0 is not disruptive at all, 10 is extremely disruptive'' \emph{(2)} The second rating scale assessed the teacher's subjective perception of confidence in dealing with the disruptions during the lesson asked as follows: ``How confident did you feel in dealing with this event on a scale of 0-10?
+0 is not confident at all and 10 is extremely confident''
+The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjetcts' self-assessment and emotional experience, and thus to make them measurable and comparable (Döring \& Bortz, 2016; Eid, Gollwitzer, \& Schmitt, 2015).
+The gradations of the rating scale were unambiguous and the intervals between them identical.
+The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally to the experimenter.
+
 \hypertarget{procedure}{%
@@
 
-In a laboratory setting, three trained actors performed teaching disruptions in a counter balanced fashion while the subject taught a 15-minute micro-teaching unit prepared in advance.
-To record the subject's heart rate, the Fitbit Charge 4 was put on at least 10 minutes before the start of the lesson.
-The lesson was recorded by four cameras and an audio recorder.
-In addition, the subject wore eye-tracking glasses to record gaze behavior.
+The data collection was part of a larger research project with a planned sample of \emph{n} = 40 in-service teachers and \emph{n} = 40 pre-service teachers.
 
-Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire (EMU, Helmke et al.
-(2014)) and self developed scales on the teacher's presence behavior derived from the research literature via the online survey website SoSci Survey (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree).
+The study took place in the rooms of the Faculty of Education at Leipzig University.
+In a controlled laboratory setting, heart rate data in beats per minute (bpm) were recorded using Fitbit Charge 4 over a total period of approximately two hours.
+Within this time frame, teachers taught a 15-minute self-prepared lesson to an audience of three actors.
+
+For this purpose, a seminar room was converted into a classroom.
+The classroom was equipped with a digital whiteboard and a blackboard.
+The fictitious class consisting of three trained actors sat facing the teacher head-on in a ``U''; pen and paper were provided on their seats.
+In addition, the students brought their own mobile phone, which was also visibly positioned on the desk.
+
+The subject was instructed during the lesson to behave and move as naturally as possible, as they would in a real classroom.
+In advance, all subjects were given information about planning their lesson in a meeting to ensure that an appropriately realistic teaching situation could take place, e.g.~it was pointed out that longer film clips as well as group work as a social form should be avoided in order to ensure interaction between teacher and students in the short time of the study.
+
+For analyzing the heart rate data, we selected five 10-minute intervals of theoretical interest.
+To ensure that the intervals are comparable for all participants, we decided on 10-minute intervals because this was the minimum duration of all intervals.
+The individual intervals are described in detail below.
+
+\emph{(1)} The \emph{pre-teaching phase} was the first 10 minutes belonging to the interval of interest.
+This interval was calculated from the moment the subject arrived and the Fitbit watch was put on, which happened immediately after the subject was welcomed by the experimenter and the three actors.
+After the experimenter briefly explained the project and the procedure of the study to the subject, contact details were subsequently collected as part of the hygiene concept of COVID-19 and the written consent to voluntarily participate in the study was requested.
+Next, the subject was asked to prepare the necessary materials for the lesson (connecting the laptop to the beamer, preparing worksheets, etc.).
+This phase varied in duration according to the prepared lesson (about 1-5min on average).
+
+Once the preparation was completed, the eye-tracking glasses were briefly explained to the subject as well as the adjustment made to the subject by the experimenter (changing the lenses or the nose pad if necessary).
+Subsequently, a 1-point calibration of the eye-tracking glasses took place and together with further devices (GoPro camera, 3D camera, audio recorder) the recordings were started.
+
+Before the lesson began, a warm-up phase took place to familiarize the subject with the laboratory setting and equipment. This warm-up phase consisted of two parts:
+
+\begin{itemize}
+\tightlist
+\item
+  In the first part, the subject and the three actors playfully learned each other's names.
+Additional fictitious name tags of the actors were attached to the table and did not change across the study.
+In the game, by throwing two balls, either the participant's own name or the name of the target person was called.
+\item
+  The second part of the warm-up phase involved getting into conversation with each other by asking questions.
+For this purpose, the subject was asked to come up with a question for each of the actors (three questions in total) and was also asked a question in return by each actor.
+This could be anything that interested the participants.
+The questions should be as authentic as possible and were not tailored to the role of the actors.
+  The purpose of this warming-up phase was, on the one hand, to make the subject forget about the devices and, on the other hand, to create as realistic as possible a classroom situation in which interactions were based on a teacher-student relationship.
+\end{itemize}
+
+The pre-teaching phase lasted 10-15 minutes on average, depending on different issues (preparing the lesson, technical problems, adjusting the eye-tracking glasses). XXX GENAUEN M + SD BERECHNEN XXX
+
+\emph{(2)} The second 10-minute interval was the \emph{teaching phase}, which began with the experimenter noting the time and step count of the fitness tracker.
+The subject was then asked to carry out a 9-point calibration alone in a room next door.
+After the calibration, the lesson started with the subject opening the door to the laboratory room.
+During the lesson, the actors were instructed to simulate nine typical classroom events, three each in the following categories: (a) verbal disruptive behavior (chatting with the neighbor, whispering, heckling), (b) physical disruptions (clicking with a pen, drumming with hands on the table, snipping) and (c) lack of eagerness to learn (drawing on a sheet of paper, putting the head on the table, looking at the phone).
+
+The order of the events and the performing actors were fully balanced with Latin square. The actors were trained before to perform the disruptions identically in each data collection.
+
+After a short familiarization phase for the teacher of two and a half minutes, the instructions appeared as intervals (every 90 seconds for 30 seconds) on a screen that was only visible for the class.
+The actors were trained to stop the disruptive behavior as soon as the teacher intervened.
+
+Time management was regulated by the experimenter by showing time cards (yellow = 1 minute until the end; red = end of the lesson).
+The lesson lasted about 18 minutes on average but only the first 10 minutes were used as an interval to ensure the identical duration for all participants.
+XXX GENAUEN M + SD BERECHNEN XXX At the end of the lesson, the experimenter again noted the time and the steps on the clock.
+
+\emph{(3)} The noted time of the lesson end was also the starting point for the \emph{post-teaching} phase as the third 10 minute interval.
+At the end of the lesson, the experimenter attached letters A through D in the lab while the teacher performed a second 9-point calibration outside.
+The letter search as a control condition was part of another project, which is why it will not be discussed further in the study.
+Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree; EMU, Helmke et al.
+(2014)) via the online survey website SoSci Survey.
 The completion of the questionnaire took approximately 5 minutes.
 
-The experimenter then conducted a Stimulated Recall Interview (SRI), where the subject commented and rated the reactions to classroom events while watching the eye tracking video.
+Meanwhile, the experimenter prepared the second part of the data collection: The Stimulated Recall Interview.
+Within post-teaching phase, the majority of subjects completed the questionnaire and positioned themselves next to the experimenter to begin the interview.
+In some cases, the beginning of the interview was part of the post-teaching phase due to individual needs (going to the toilet, spending more time completing the questionnaire, etc.).
 
-Finally, a Situational Judgment Test (SJT, Gold and Holodynski (2015)) was used to assess the subject's strategic knowledge of classroom management.
+\emph{(4)} The fourth 10 minute interval of interest was the \emph{interview phase} that are 10 minutes in the middle of the interview.
+To ensure that all subjects were in the middle of the interview, we calculated the difference from the end of the lesson and from the time when the subject took off the watch.
+This duration was divided in two to get to the middle of the interval.
+Then, 5 minutes were subtracted to get to the start of the 10-minute interval.
+
+The interview itself took place using the Think Aloud procedure (Konrad, 2020).
+For this purpose, the eye tracking video was watched again and the experimenter stopped the video at the nine disruptions when they appeared to asks several questions.
+The questions were identical for each disruption, they were asked in a fixed order.
+First, the subject was asked to describe the disruption, to evaluate (11-point rating scale) and justify the disruptiveness of each disruption.
+Next, the subject was asked to describe and justify the reaction.
+The experimenter then asked the subject to evaluate (11-point rating scale) and justify the confidence the subject had in dealing with the disruption.
+Statements about the evaluation of the disruptiveness and the confidence were quantified.
+For this purpose, subjects determined their individual value on a rating scale from 0 (not disturbing / not safe) to 10 (disturbing / safe).
+
+The interview lasted on average 45-60 minutes.
+
+\emph{(5)} The last interesting interval for the analyses is the \emph{end phase}, which was the 10 minutes before the subject took off the watch.
+In this interval, the subject answered a second questionnaire (Situational Judgment Test, Gold and Holodynski (2015)) to assess the subject's strategic knowledge of classroom management.
 The subject was asked to judge alternative actions on school scenarios on a 6-point rating scale from 1 (A) to 6 (F) according to school grades.
-Data from the SJT were again collected as an online questionnaire via the website www.soscisurvey.de and lastet approximately 10 minutes.
+Data from the questionnaire were again collected as an online questionnaire via the website www.soscisurvey.de and lasted approximately 10-15 minutes.
 
-The Fitbit watch was removed only after the last questionnaire to obtain heart rate at three different measurement time points: before, during, and after the lesson.
+The Fitbit watch was removed only after the last questionnaire to obtain heart rate data during the entire study.
 
@@
 Behrendt, S. (2022). \emph{Lm.beta: Add standardized regression coefficients to lm-objects}. Retrieved from \url{https://CRAN.R-project.org/package=lm.beta}
+
+\leavevmode\vadjust pre{\hypertarget{ref-doring2016empirische}{}}%
+Döring, N., \& Bortz, J. (2016). Empirische sozialforschung im {Ü}berblick. In \emph{Forschungsmethoden und evaluation in den sozial-und humanwissenschaften} (pp. 3--30). Springer.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eid2015statistik}{}}%
+Eid, M., Gollwitzer, M., \& Schmitt, M.
+(2015).
+\emph{Statistik und forschungsmethoden: Mit online-materialien (4., {ü}berarb.
+Und erw.
+aufl.)}.
+Weinheim: Beltz.
+Retrieved from https://contentselect.
+com/media/moz\_viewer~\ldots.
 

### 2022-12-05 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
Update fitbit_paper.Rmd

@@
 
-Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of stress.
-Since, among other things, greater professional experience is associated with lower feelings of stress in the teaching profession [@fisher2011factors], this study will also consider the heart rate measurements of experienced and inexperienced teachers.
+Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of arousal during teaching.
+
+## Theoretical Backround
+
+### Stress in Teaching Profession
+--> Lehrberuf sehr stressig
+--> wie entsteht Stress
+
+### Measuring stress in eductional context
+--> wie wurde Stress bisher gemessen
 
 ## Aim of the study
-Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases.
-We expected heart rates to be higher in the arousal phase than in the rest phases.
+In the present study, we assessed HR measures and self-report data of pre- and in-service teachers in a controlled teaching-learning setting.
+The aim was to investigate whether heart rate measurements using wrist-worn fitness trackers are a suitable and effective method __(1)__ to map differences in states of arousal between five different phases (pre-teaching phase, teaching phase, post-teaching phase, interview phase and end phase) and __(2)__ to evaluate the correlation between self-report arousal states and HR measures.
+
+__(H1)__ We expected heart rates to be higher during the teaching phase than during the pre- and the three post-teaching phases, and the HR measures would decrease over the course of the study.
+__(H2)__ We also predicted that HR response and a high ranking on the negative arousal item on our survey (feeling disturbed by disruptions) would correlate positively and a high ranking on the positive arousal item (feeling confident in dealing with disruptions) would follow the inverse pattern.
 
@@
 
-### FitBit
+### Heart rate Data
 
@@
 
-## Heart Rate
+### Rating Scale Data
 
@@
 # Discussion and implication
+The analyses showed that wrist-worn fitness trackers are a suitable method to measure different phases of arousal in (prospective) teachers in laboratory settings, with clear effects visible even in intervals of just 10 minutes.
 

### 2022-12-07 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update theory

@@
 To date, there is still little evidence on the usefulness of heart rate measurements using fitness trackers in teaching and learning settings [@ertzberger2016use; @lowe2016educational].
-@rungeusing alone examined teacher stress in a relatively small sample (*N* = 4 teachers) and showed that high heart rate, high step count, and little sleep indicate more stress in teachers.
+@rungeusing alone examined teacher stress in a relatively small sample (*N* = 4 teachers) and showed that high heart rate indicate more stress in teachers.
 
@@
 ### Stress in Teaching Profession
---> Lehrberuf sehr stressig
+
+--> teacher profession is one of the most stressful professions.
+
+Teacher stress can be defined as "[...] the experience by a teacher of unpleasant, negative emotions, such as anger, anxiety, tension, frustration or depression, resulting from some aspect of their work as a teacher." [@kyriacou2001teacher].
+
+Teachers' individual perceptions of student misbehavior in the classroom are closely related to their well-being [@ALDRUP2018126].
+
 --> wie entsteht Stress
+--> wie wurde Stress bisher gemessen
 
-### Measuring stress in eductional context
---> wie wurde Stress bisher gemessen
+### Heart rate as an indicator for stress or arousal
+Heart rate is physiologically regulated by the autonomic nervous system.
+An increase in the activity of the sympathetic as part of the autonomic nervous system results in the heart rate being speeded up ("fight or flight").
+On the other hand, an increased activity of the parasympathetic as the counterpart has the effect of slowing down the heart rate ("rest and digest") [@Battipaglia2015].
+In addition to the autonomic nervous system and genetic factors, heart rate is influenced by numerous external factors such as social, personal, psychological, environmental and behavioural factors [@wang2022using].
+
+### Wrist-worn devices as a new approach to assess physiological measures
+"The use of physiological measures enabled us to get some insight into teachers’ affective responses without disrupting the teaching process (Mauss & Robinson, 2009) and to reduce issues with social desirability, retrospective bias, and high cognitive load (Becker et al., 2015; Goetz et al., 2015; Scollon et al.,2009; Wilhelm & Grossman, 2010).
+Moreover, we found that heart rate measures discriminated between both teachers, even when their interpersonal behavior during the lesson start was relatively similar."
+
+(20) (PDF) A Quantitative Exploration of Two Teachers with Contrasting Emotions: Intra-Individual Process Analyses of Physiology and Interpersonal Behavior.
+Available from: https://www.researchgate.net/publication/329787434_A_Quantitative_Exploration_of_Two_Teachers_with_Contrasting_Emotions_Intra-Individual_Process_Analyses_of_Physiology_and_Interpersonal_Behavior [accessed Dec 07 2022].
+
+In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress.
 
@@
 In the present study, we assessed HR measures and self-report data of pre- and in-service teachers in a controlled teaching-learning setting.
-The aim was to investigate whether heart rate measurements using wrist-worn fitness trackers are a suitable and effective method __(1)__ to map differences in states of arousal between five different phases (pre-teaching phase, teaching phase, post-teaching phase, interview phase and end phase) and __(2)__ to evaluate the correlation between self-report arousal states and HR measures.
+The aim was to investigate whether heart rate measurements using wrist-worn fitness trackers are a suitable and effective method __(1)__ to map differences in states of arousal between five different phases (pre-teaching phase, teaching phase, post-teaching phase, interview phase and end phase) and __(2)__ to evaluate the correlation between self-reported evaluations and HR measures.
 
-__(H1)__ We expected heart rates to be higher during the teaching phase than during the pre- and the three post-teaching phases, and the HR measures would decrease over the course of the study.
-__(H2)__ We also predicted that HR response and a high ranking on the negative arousal item on our survey (feeling disturbed by disruptions) would correlate positively and a high ranking on the positive arousal item (feeling confident in dealing with disruptions) would follow the inverse pattern.
+__(H1)__ We expected heart rates to be higher during the teaching phase than during the pre- and the three post-teaching phases, and that the HR measures would decrease over the course of the study.
+__(H2)__ We also predicted that HR and a high ranking on the negative scale on our survey (feeling disturbed by disruptions) would correlate positively and a high ranking on the positive scale (feeling confident in dealing with disruptions) would follow the inverse pattern.
 

### 2022-12-08 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
fitbit theory

@@
   Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  XXX In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress.
+XXX
 
@@
 To date, there is still little evidence on the usefulness of heart rate measurements using fitness trackers in teaching and learning settings [@ertzberger2016use; @lowe2016educational].
-@rungeusing alone examined teacher stress in a relatively small sample (*N* = 4 teachers) and showed that high heart rate indicate more stress in teachers.
+@rungeusing alone examined teacher stress in a relatively small sample (*N* = 4 teachers) and showed that high heart rate indicates more stress in teachers.
 
-Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of arousal during teaching.
+Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, low-cost, and robust measurement method for assessing teachers' experience of arousal during teaching.
 
@@
 --> wie entsteht Stress
+
 --> wie wurde Stress bisher gemessen
@@
 Available from: https://www.researchgate.net/publication/329787434_A_Quantitative_Exploration_of_Two_Teachers_with_Contrasting_Emotions_Intra-Individual_Process_Analyses_of_Physiology_and_Interpersonal_Behavior [accessed Dec 07 2022].
-
-In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress.
 
@@
 
-For analyzing the heart rate data, we selected five 10-minute intervals of theoretical interest.
-To ensure that the intervals are comparable for all participants, we decided on 10-minute intervals because this was the minimum duration of all intervals.
-The individual intervals are described in detail below.
+For analyzing the heart rate data, we focused on five 10-minute intervals of theoretical interest for multiple reason.
+First, 10 minutes was to the minimum duration of all intervals, so we wanted to ensure the comparability of the intervals for all participants.
+Second, @lu2008can confirmed in their study that 10-minute intervals are an useful duration for analyzing photoplethysmography (PPG) data.
+Third, other studies revealed that the first minutes of the lesson start are essential regarding teacher-student interaction [@donker2018quantitative; @claessens2017positive].
 
@@
 
-The pre-teaching phase lasted 10-15 minutes on average, depending on different issues (preparing the lesson, technical problems, adjusting the eye-tracking glasses). XXX GENAUEN M + SD BERECHNEN XXX
+The pre-teaching phase lasted 10-15 minutes on average, depending on different issues (preparing the lesson, technical problems, adjusting the eye-tracking glasses).
 
@@
 The lesson lasted about 18 minutes on average but only the first 10 minutes were used as an interval to ensure the identical duration for all participants.
-XXX GENAUEN M + SD BERECHNEN XXX At the end of the lesson, the experimenter again noted the time and the steps on the clock.
+At the end of the lesson, the experimenter again noted the time and the steps on the clock.
 
-_(3)_ The noted time of the lesson end was also the starting point for the _post-teaching_ phase as the third 10 minute interval.
+_(3)_ The noted time of the lesson end was also the starting point for the _post-teaching_ phase as the third 10-minute interval.
 At the end of the lesson, the experimenter attached letters A through D in the lab while the teacher performed a second 9-point calibration outside.
@@
 
-_(4)_ The fourth 10 minute interval of interest was the _interview phase_ that are 10 minutes in the middle of the interview.
+_(4)_ The fourth 10-minute interval of interest was the _interview phase_ that was 10 minutes in the middle of the interview.
 To ensure that all subjects were in the middle of the interview, we calculated the difference from the end of the lesson and from the time when the subject took off the watch.
@@
 
-_(5)_ The last interesting interval for the analyses is the _end phase_, which was the 10 minutes before the subject took off the watch.
+_(5)_ The last interesting interval for the analyses was the _end phase_, which was the 10 minutes before the subject took off the watch.
 In this interval, the subject answered a second questionnaire (Situational Judgment Test, @gold2015development) to assess the subject's strategic knowledge of classroom management.

### 2022-12-08 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
fitbit theory

@@
 Runge et al.
-(n.d.) alone examined teacher stress in a relatively small sample (\emph{N} = 4 teachers) and showed that high heart rate, high step count, and little sleep indicate more stress in teachers.
+(n.d.) alone examined teacher stress in a relatively small sample (\emph{N} = 4 teachers) and showed that high heart rate indicate more stress in teachers.
 
-Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of stress.
-Since, among other things, greater professional experience is associated with lower feelings of stress in the teaching profession (Fisher, 2011), this study will also consider the heart rate measurements of experienced and inexperienced teachers.
+Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of arousal during teaching.
+
+\hypertarget{theoretical-backround}{%
+\subsection{Theoretical Backround}\label{theoretical-backround}}
+
+\hypertarget{stress-in-teaching-profession}{%
+\subsubsection{Stress in Teaching Profession}\label{stress-in-teaching-profession}}
+
+--\textgreater{} teacher profession is one of the most stressful professions.
+
+Teacher stress can be defined as ``{[}\ldots{]} the experience by a teacher of unpleasant, negative emotions, such as anger, anxiety, tension, frustration or depression, resulting from some aspect of their work as a teacher.'' (Kyriacou, 2001).
+
+Teachers' individual perceptions of student misbehavior in the classroom are closely related to their well-being (Aldrup, Klusmann, Lüdtke, Göllner, \& Trautwein, 2018).
+
+--\textgreater{} wie entsteht Stress
+--\textgreater{} wie wurde Stress bisher gemessen
+
+\hypertarget{heart-rate-as-an-indicator-for-stress-or-arousal}{%
+\subsubsection{Heart rate as an indicator for stress or arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}
+
+Heart rate is physiologically regulated by the autonomic nervous system.
+An increase in the activity of the sympathetic as part of the autonomic nervous system results in the heart rate being speeded up (``fight or flight'').
+On the other hand, an increased activity of the parasympathetic as the counterpart has the effect of slowing down the heart rate (``rest and digest'') (Battipaglia \& Lanza, 2015).
+In addition to the autonomic nervous system and genetic factors, heart rate is influenced by numerous external factors such as social, personal, psychological, environmental and behavioural factors (Wang, Lizardo, \& Hachen, 2022).
+
+\hypertarget{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}{%
+\subsubsection{Wrist-worn devices as a new approach to assess physiological measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}
+
+``The use of physiological measures enabled us to get some insight into teachers' affective responses without disrupting the teaching process (Mauss \& Robinson, 2009) and to reduce issues with social desirability, retrospective bias, and high cognitive load (Becker et al., 2015; Goetz et al., 2015; Scollon et al.,2009; Wilhelm \& Grossman, 2010).
+Moreover, we found that heart rate measures discriminated between both teachers, even when their interpersonal behavior during the lesson start was relatively similar.''
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\setcounter{enumi}{19}
+\tightlist
+\item
+  (PDF) A Quantitative Exploration of Two Teachers with Contrasting Emotions: Intra-Individual Process Analyses of Physiology and Interpersonal Behavior.
+Available from: \url{https://www.researchgate.net/publication/329787434_A_Quantitative_Exploration_of_Two_Teachers_with_Contrasting_Emotions_Intra-Individual_Process_Analyses_of_Physiology_and_Interpersonal_Behavior} {[}accessed Dec 07 2022{]}.
+\end{enumerate}
+
+In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress.
 
@@
 
-Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases.
-We expected heart rates to be higher in the arousal phase than in the rest phases.
+In the present study, we assessed HR measures and self-report data of pre- and in-service teachers in a controlled teaching-learning setting.
+The aim was to investigate whether heart rate measurements using wrist-worn fitness trackers are a suitable and effective method \textbf{(1)} to map differences in states of arousal between five different phases (pre-teaching phase, teaching phase, post-teaching phase, interview phase and end phase) and \textbf{(2)} to evaluate the correlation between self-reported evaluations and HR measures.
+
+\textbf{(H1)} We expected heart rates to be higher during the teaching phase than during the pre- and the three post-teaching phases, and that the HR measures would decrease over the course of the study.
+\textbf{(H2)} We also predicted that HR and a high ranking on the negative scale on our survey (feeling disturbed by disruptions) would correlate positively and a high ranking on the positive scale (feeling confident in dealing with disruptions) would follow the inverse pattern.
 
@@
 
-\hypertarget{fitbit}{%
-\subsubsection{FitBit}\label{fitbit}}
+\hypertarget{heart-rate-data}{%
+\subsubsection{Heart rate Data}\label{heart-rate-data}}
 
@@
 
-\hypertarget{heart-rate}{%
-\subsection{Heart Rate}\label{heart-rate}}
+\hypertarget{rating-scale-data}{%
+\subsubsection{Rating Scale Data}\label{rating-scale-data}}
 
@@
 \section{Discussion and implication}\label{discussion-and-implication}}
+
+The analyses showed that wrist-worn fitness trackers are a suitable method to measure different phases of arousal in (prospective) teachers in laboratory settings, with clear effects visible even in intervals of just 10 minutes.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-ALDRUP2018126}{}}%
+Aldrup, K., Klusmann, U., Lüdtke, O., Göllner, R., \& Trautwein, U.
+(2018).
+Student misbehavior and teacher well-being: Testing the mediating role of the teacher-student relationship.
+\emph{Learning and Instruction}, \emph{58}, 126--136.
+https://doi.org/\url{https://doi.org/10.1016/j.learninstruc.2018.05.006}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-DescTools}{}}%
@@
 Bates, D., Maechler, M., \& Jagan, M. (2022). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Battipaglia2015}{}}%
+Battipaglia, I., \& Lanza, G.
+A.
+(2015).
+The autonomic nervous system of the heart.
+In R.
+H.
+J.
+A.
+Slart, R.
+A.
+Tio, P.
+H.
+Elsinga, \& M.
+Schwaiger (Eds.), \emph{Autonomic innervation of the heart: Role of molecular imaging} (pp.
+1--12).
+Berlin, Heidelberg: Springer Berlin Heidelberg.
+\url{https://doi.org/10.1007/978-3-662-45074-1_1}
 
@@
 Firke, S. (2021). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fisher2011factors}{}}%
-Fisher, M. H. (2011). Factors influencing stress, burnout, and retention of secondary teachers. \emph{Current Issues in Education}, \emph{14}(1).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-kyriacou2001teacher}{}}%
+Kyriacou, C. (2001). Teacher stress: Directions for future research. \emph{Educational Review}, \emph{53}(1), 27--35.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-jtools}{}}%
@@
 Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wang2022using}{}}%
+Wang, C., Lizardo, O., \& Hachen, D. S. (2022). Using fitbit data to monitor the heart rate evolution patterns of college students. \emph{Journal of American College Health}, \emph{70}(3), 875--882.
 

### 2022-12-20 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
Update fitbit_paper.Rmd

@@
 
-All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+XXX Helsinki XXX All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
 All participants were informed in detail about the aim and intention of the study prior to testing.
@@
 
-_(1)_ The _pre-teaching phase_ was the first 10 minutes belonging to the interval of interest.
+The procedure of the study and how we calculated the five phases is described in the following:
+
+_(1)_ The _pre-teaching phase_ was the first 10-minute interval of interest.
 This interval was calculated from the moment the subject arrived and the Fitbit watch was put on, which happened immediately after the subject was welcomed by the experimenter and the three actors.

### 2022-12-20 02_paper/02_study/02_fitbit paper/Presentation_Analysis_update.Rmd
create updated presentation

--- 2022-11-25 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
@@
 
-main <-
-  left_join(main, df_merge,
-            by = "ID")
+# main <-
+#   left_join(main, df_merge,
+#             by = "ID")
 ```
 
-# Überblick Datenerhebung
-
-```{r timeline, fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./images/timeline_fitbit.png", dpi = 130)
-
-```
-
-# Überblick Daten
+# Plot Gesamtverlauf
 
 ```{r}
-knitr::kable(main[1:10,], format = "simple")
-```
-
-## Plot für Gesamtverlauf
-
-```{r, fig.height = 8, fig.width = 15}
-
 main %>% 
   filter(time_span == "overall") %>% 
-  select("ID","time_span", "time","heart_rate") %>% 
-  distinct() %>% 
-  ggplot(mapping = aes(x = time,
-                       y = heart_rate
-                       )
-         ) +
- # stat_smooth(geom = "line",
- #             method = "loess",
- #             se = FALSE) +
-  geom_smooth(method = "loess",
-              se = FALSE) +
-  scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  labs(x = "Zeit (in Sekunden)",
-       y = "Herzrate (in Schlägen pro Minute)") +
-  theme_apa()
-
-```
-
-## Plot für einzelne Phasen
-
-```{r, fig.height = 8, fig.width = 15}
-
-main %>% 
-  filter(time_span != "overall") %>% 
-  select("ID","time_span", "time","heart_rate") %>% 
-  mutate(status = case_when(ID < 200 ~ "Unerfahren",
-                            ID > 200 ~ "Erfahren"),
-         time_span = fct_recode(time_span,
-                                "Pre-Lehrphase" = "pre",
-                                "Lehrphase" = "main",
-                                "Post-Lehrphase" = "subsequent",
-                                "Intviewphase" = "interview",
-                                "Endphase" = "after"
-                                ),
-         time_span = factor(time_span,
-                            levels = c("Pre-Lehrphase",
-                                       "Lehrphase",
-                                       "Post-Lehrphase",
-                                       "Intviewphase",
-                                       "Endphase"
-                                       )
-                            )
-         ) %>%
-  distinct() %>% 
-ggplot(mapping = aes(x = time,
-                     y = heart_rate
-                     )
-       ) +
- # stat_smooth(geom = "line",
-             # mapping = aes(color = status),
-  #            method = "loess",
-   #           se = TRUE) 
-  geom_smooth(method = "glm") +
-  scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  labs(x = "Zeit (in Sekunden)",
-       y = "Herzrate (in Schlägen pro Minute)") +
-  theme_apa() +
-  facet_grid(cols = vars(time_span),
-             scales = "free_x",
+  group_by(ID) %>% 
+  summarise(mean_hr = mean(heart_rate),
+            sd_hr = sd(heart_rate)) %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  transmute(ID = ID,
+            heart_rate_std = (heart_rate - mean_hr) / sd_hr,
             )
@@
 ```
-
-# Verteilungen
-
-# Geschlecht
-
-```{r}
-df_demo %>% 
-  mutate(gender = fct_recode(gender,
-                             "Männlich" = "male",
-                             "Weiblich" = "female"
-                             )
-         ) %>% 
-  ggplot(mapping = aes(x = gender)) +
-  geom_bar(fill = "#440154") +
-  labs(x = "Geschlecht",
-       y = "Anzahl") +
-  theme_apa()
-```
-
-# Alter
-
-```{r}
-df_demo %>% 
-  ggplot(mapping = aes(x = age)) +
-  geom_histogram(binwidth = 5,
-                 fill = "#440154") +
-  labs(x = "Alter",
-       y = "Anzahl") +
-  theme_apa()
-```
-
-- Linkssteile Verteilung
-- Möglicher Umgang: Logarithmieren
-
-```{r}
-df_demo %>% 
-  ggplot(mapping = aes(x = log(age))) +
-  geom_histogram(binwidth = 0.1,
-                 fill = "#440154") +
-  labs(x = "log(Alter)",
-       y = "Anzahl") +
-  theme_apa()
-```
-
-# Alter x Geschlecht
-
-```{r}
-df_demo %>% 
-  mutate(gender = fct_recode(gender,
-                             "Männlich" = "male",
-                             "Weiblich" = "female"
-                             )
-         ) %>% 
-  ggplot(mapping = aes(x = gender,
-                       y = age
-                       )
-         ) +
-  geom_boxplot(fill = "#440154",
-               color = "#3b528b") +
-  labs(x = "Geschlecht",
-       y = "Alter") +
-  theme_apa()
-```
-
-- Alter und Geschlecht unkorreliert
-- $\chi^2=$ `r chisq.test(df_demo$gender, df_demo$age)$statistic[[1]] %>% round(., 2)`
-
-# Lehrerfahrung
-
-```{r}
-df_demo %>% 
-  ggplot(mapping = aes(x = teaching_experience)) +
-  geom_histogram(binwidth = 2,
-                 fill = "#440154") + 
-  labs(x = "Lehrerfahrung",
-       y = "Anzahl") +
-  theme_apa()
-```
-
-- Starke links-verzerrte Verteilung (zero inflation)
-- 0 rausfiltern (keine Option)
-- log(x + 1)
-
-```{r}
-df_demo %>% 
-  ggplot(mapping = aes(x = log(teaching_experience + 1))) +
-  geom_histogram(binwidth = 0.3,
-                 fill = "#440154") + 
-  labs(x = "log(Lehrerfahrung + 1)",
-       y = "Anzahl") +
-  theme_apa()
-```
-
-- In jedem Fall stark korreliert mit Alter $\rightarrow$ Gefahr der Multikollinearität
-- `r paste0("r = ", round(cor(df_demo$teaching_experience, df_demo$age), 2))`
-
-- Vorschlag: Lehrerfahrung weglassen und Alter aufnehmen
-- Konsistent mit Idee, Expert\*innen und Noviz\*innen nicht zu trennen
-
-## Confident Factor
-
-```{r}
-df_merge %>% 
-  filter(!is.na(confident_factor)) %>% 
-  group_by(event, confident_factor) %>% 
-  summarize(value = n()) %>% 
-  mutate(prop = value/sum(value)) %>% 
-  ggplot(mapping = aes(x = reorder(event, prop),
-                       y = prop,
-                       fill = confident_factor
-                       )
-         ) +
-  geom_bar(position = "stack",
-           stat = "identity") +
-  coord_flip() +
-  scale_fill_viridis_c() +
-  labs(y = "",
-       x = "",
-       fill = "Confident Factor") +
-  theme_apa()
-```
-
-## Disruption Factor
-
-```{r}
-df_merge %>% 
-  filter(!is.na(disruption_factor)) %>% 
-  group_by(event, disruption_factor) %>% 
-  summarize(value = n()) %>% 
-  mutate(prop = value/sum(value)) %>% 
-  ggplot(mapping = aes(x = reorder(event, prop),
-                       y = prop,
-                       fill = disruption_factor
-                       )
-         ) +
-  geom_bar(position = "stack",
-           stat = "identity") +
-  coord_flip() +
-  scale_fill_viridis_c() +
-  labs(y = "",
-       x = "",
-       fill = "Disruption Factor") +
-  theme_apa()
-```
-
-- Mittelwerte bilden? (potentielle Aussagekraft: Im Schnitt fühlten sich manche Lehrpersonen sicherer mit der Situation/fühlten sich eher gestört von der Situation)
-
-# Erste Zusammenhänge
-
-## Confidence x Disruption (out of curiosity)
-
-```{r}
-df_merge %>% 
-  filter(!is.na(disruption_factor) | !is.na(confident_factor)) %>% 
-  ggplot(mapping = aes(x = confident_factor,
-                       y = disruption_factor
-                       )
-         ) +
-  geom_jitter(mapping = aes(color = event)) +
-  geom_smooth(method = "lm",
-              se = FALSE) +
-  scale_color_viridis_d() +
-  labs(x = "Confident Factor",
-       y = "Disruption Factor",
-       color = "Event") +
-  theme_apa()
-
-```
-
-## Alter x Confidence
-
-```{r}
-df_merge %>% 
-  filter(!is.na(confident_factor) | !is.na(disruption_factor)) %>% 
-  ggplot(mapping = aes(x = age,
-                       y = confident_factor
-                       )
-         ) +
-  geom_jitter(mapping = aes(color = event)) +
-  geom_smooth(method = "lm",
-              se = F) +
-  labs(x = "Alter",
-       y = "Confident Factor") +
-  scale_color_viridis_d() +
-  theme_apa()
-```
-
-- Mittelwerte:
-
-```{r}
-df_merge %>% 
-  filter(!(is.na(confident_factor) | is.na(disruption_factor))) %>% 
-  group_by(ID) %>% 
-  summarize(mean_confident = mean(confident_factor),
-            age = mean(age)) %>%
-  ungroup() %>% 
-  ggplot(mapping = aes(x = age,
-                       y = mean_confident
-                       )
-         ) +
-  geom_point(color = "#440154") +
-  geom_smooth(method = "lm",
-              se = FALSE) +
-  labs(x = "Alter",
-       y = "Mean(Confident Factor)") +
-  theme_apa()
-```
-
-## Alter x Disruption
-
-```{r}
-df_merge %>% 
-  filter(!is.na(confident_factor) | !is.na(disruption_factor)) %>% 
-  ggplot(mapping = aes(x = age,
-                       y = disruption_factor
-                       )
-         ) +
-  geom_jitter(mapping = aes(color = event)) +
-  geom_smooth(method = "lm",
-              se = F) +
-  scale_color_viridis_d() +
-  labs(x = "Alter",
-       y = "Disruption Factor") +
-  theme_apa()
-```
-
-- Mittelwerte:
-
-```{r}
-df_merge %>% 
-  filter(!(is.na(confident_factor) | is.na(disruption_factor))) %>% 
-  group_by(ID) %>% 
-  summarize(mean_disruption = mean(disruption_factor),
-            age = mean(age)) %>%
-  ungroup() %>% 
-  ggplot(mapping = aes(x = age,
-                       y = mean_disruption
-                       )
-         ) +
-  geom_point(color = "#440154") +
-  geom_smooth(method = "lm",
-              se = F) +
-  labs(x = "Alter",
-       y = "Mean(Disruption Factor)") +
-  theme_apa()
-```
-
-# Heart Rate
-
-Vorüberlegungen
-
-- Idee: Was erklärt die zunehmende Aufregung am Anfang bzw. abnehmende Aufregung nach der Unterrichtssession?
-- AV: geschätzte Lineare Steigung der Herzrate vor der Session
-- Beachten: jede Person hat eigenen Ruhepuls! $\rightarrow$ random intercept, fixed slope regression model
-
-## Beispiel (Pre-Phase)
-
-```{r}
-main %>% 
-  filter(time_span == "pre") %>% 
-  select("ID","time","heart_rate") %>% 
-  distinct() %>% 
-  ggplot(mapping = aes(x = time,
-                       y = heart_rate
-                       )
-         ) +
-  geom_line(mapping = aes(color = as_factor(ID)),
-            stat = "smooth", 
-            method = "lm",
-            alpha = 0.6) +
-  geom_point(mapping = aes(color = as_factor(ID)),
-             alpha = 0.1) +
-  geom_line(stat = "smooth",
-            method = "lm",
-            linetype = 2) +
-  scale_color_viridis_d() +
-  labs(x = "Zeit (in Sekunden)",
-       y = "Herzrate (in Schlägen pro Minute)") +
-  theme_apa() +
-  theme(legend.position = "none") 
-```
-
-```{r}
-main %>% 
-  filter(time_span == "pre") %>% 
-  select("time","ID","heart_rate") %>% 
-  distinct() %>% 
-  mutate(ID = as_factor(ID)) %>% 
-  lmer(formula = heart_rate ~ (1|ID) + ID * time) %>% 
-  summary() ->
-  fit_first
-
-as_tibble(fit_first$coefficients,
-          rownames = "Coefficient") %>%
-  filter(str_detect(.$Coefficient,
-                    pattern = "time")) %>% 
-  mutate(coefficient = case_when(Coefficient == "time" ~ "101",
-                                 TRUE ~ Coefficient),
-         ID = str_extract(string = coefficient,
-                                   pattern = "[:digit:]{3}"
-                                   ),
-         ID = as.numeric(ID)
-         ) %>% 
-  select("ID","Estimate") ->
-  df_estimates
-
-df_merge %>% 
-  group_by(ID) %>% 
-  summarize(confident_factor_m = mean(confident_factor,
-                                      na.rm = TRUE),
-            disruption_factor_m = mean(disruption_factor,
-                                       na.rm = TRUE),
-            ID = ID,
-            t_exp = teaching_experience) %>% 
-  distinct() %>% 
-  left_join(., df_estimates,
-            by = "ID") ->
-  df_corr_pre
-```
-
-```{r}
-df_corr_pre %>% 
-  select("ID","Estimate") %>% 
-  filter(ID < 110) %>% 
-  knitr::kable(., format = "simple")
-```
-
-Plan für Pre- und Subsequent Phase:
-
-- Partielle Korrelationen
-
-- Multiple Lineare Regression
-  - AV: Estimate
-  - UV: Gender, Alter, Disruption Factor (mean), Confident Factor (mean)
-  - Alle metrischen Variablen sind standardisiert
-
-## Pre Phase
-
-- 10 Minuten nach Anlegen der FitBit
-
-### Korrelationen
-
-```{r}
-main %>% 
-  filter(time_span == "pre") %>% 
-  select("time","ID","heart_rate") %>% 
-  distinct() %>% 
-  mutate(ID = as_factor(ID)) %>% 
-  lmer(formula = heart_rate ~ (1|ID) + ID * time) %>% 
-  summary() ->
-  fit_first
-
-as_tibble(fit_first$coefficients,
-          rownames = "Coefficient") %>%
-  filter(str_detect(.$Coefficient,
-                    pattern = "time")) %>% 
-  mutate(coefficient = case_when(Coefficient == "time" ~ "101",
-                                 TRUE ~ Coefficient),
-         ID = str_extract(string = coefficient,
-                                   pattern = "[:digit:]{3}"
-                                   ),
-         ID = as.numeric(ID)
-         ) %>% 
-  select("ID","Estimate") ->
-  df_estimates
-
-df_merge %>% 
-  group_by(ID) %>% 
-  summarize(confident_factor_m = mean(confident_factor,
-                                      na.rm = TRUE),
-            disruption_factor_m = mean(disruption_factor,
-                                       na.rm = TRUE),
-            ID = ID,
-            t_exp = teaching_experience) %>% 
-  distinct() %>% 
-  left_join(., df_estimates,
-            by = "ID") %>% 
-  ungroup() ->
-  df_corr_pre
-
-left_join(x = df_corr_pre,
-          y = df_demo,
-          by = "ID") %>% 
-transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
-          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
-          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-          gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
-          age = (age - mean(.$age))/sd(.$age)
-          ) %>% 
-  pcor(., method = "spearman") %>% 
-  .$estimate %>% 
-  round(., 2) %>% 
-  knitr::kable(format = "simple")
-
-left_join(x = df_corr_pre,
-          y = df_demo,
-          by = "ID") %>% 
-transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
-          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
-          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-          gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
-          age = (age - mean(.$age))/sd(.$age)
-          ) %>% 
-  pcor(., method = "pearson") %>% 
-  .$p.value %>% 
-  round(., 3) %>% 
-  knitr::kable(format = "simple")
-```
-
-### Regression
-
-```{r}
-left_join(x = df_corr_pre,
-          y = df_demo,
-          by = "ID") %>% 
-  ungroup() %>% 
-  mutate(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
-         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
-         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-         gender = gender,
-         age = (age - mean(.$age))/sd(.$age)
-         ) %>%
-  lm(formula = Estimate ~ confident_factor_m + disruption_factor_m  + gender + age) %>% 
-  tidy(x = .,
-       conf.int = TRUE) %>% 
-  mutate(term = case_when(term == "confident_factor_m" ~ "Confident Factor",
-                              term == "disruption_factor_m" ~ "Disruption Factor",
-                              term == "genderfemale" ~ "Weiblich\n(Ref.: Männlich)",
-                              term == "age" ~ "Alter",
-                              TRUE ~ "Intercept"
-                           ),
-         term = fct_relevel(term, 
-                            c("Confident Factor",
-                              "Disruption Factor",
-                              "Weiblich\n(Ref.: Männlich)",
-                              "Alter"
-                              )),
-         term = fct_rev(as_factor(term)),
-         ) %>% 
-  filter(term != "Intercept") %>% 
-  ggplot(mapping = aes(y = term)) +
-    geom_point(aes(x = estimate)) +
-  geom_vline(xintercept = 0) +
-  geom_segment(mapping = aes(x = conf.low,
-                             xend = conf.high,
-                             y = term,
-                             yend = term),
-               color = "#440154") +
-  labs(x = "Effect",
-       y = "",
-       title = "Pre-Phase",
-       subtitle = paste0("Dependend Variable: Standardized Estimate\n(M = ", 
-                         mean(df_corr_pre$Estimate) %>% round(.,2),
-                         ")"
-                         )
-       ) +
-  theme_apa() 
-```
-
-- Keine sign. Ergebnisse
-- Selbstbewusste Personen haben einen *niedrigeren* Anstieg der HR vor der Erhebung
-- Personen, die sich stärker gestört gefühlt haben, haben einen *stärkeren* Anstieg der HR
-- Die HR von Frauen steigt *stärker* als die der Männer
-- Je älter die Personen sind, desto *niedriger* ist der Anstieg der HR
-
-## Subsequent Phase
-
-- 10 Minuten nach der Unterrichtseinheit
-
-### Korrelation
-
-```{r}
-main %>% 
-  filter(time_span == "subsequent") %>% 
-  select("time","ID","heart_rate") %>% 
-  distinct() %>% 
-  mutate(ID = as_factor(ID)) %>% 
-  lmer(formula = heart_rate ~ (1|ID) + ID * time) %>% 
-  summary() ->
-  fit_first
-
-as_tibble(fit_first$coefficients,
-          rownames = "Coefficient") %>%
-  filter(str_detect(.$Coefficient,
-                    pattern = "time")) %>% 
-  mutate(coefficient = case_when(Coefficient == "time" ~ "101",
-                                 TRUE ~ Coefficient),
-         ID = str_extract(string = coefficient,
-                                   pattern = "[:digit:]{3}"
-                                   ),
-         ID = as.numeric(ID)
-         ) %>% 
-  select("ID","Estimate") ->
-  df_estimates
-
-df_merge %>% 
-  group_by(ID) %>% 
-  summarize(confident_factor_m = mean(confident_factor,
-                                      na.rm = TRUE),
-            disruption_factor_m = mean(disruption_factor,
-                                       na.rm = TRUE),
-            ID = ID,
-            t_exp = teaching_experience) %>% 
-  distinct() %>% 
-  left_join(., df_estimates,
-            by = "ID") %>% 
-  ungroup() ->
-  df_corr_pre
-
-left_join(x = df_corr_pre,
-          y = df_demo,
-          by = "ID") %>% 
-transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
-          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
-          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-          gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
-          age = (age - mean(.$age))/sd(.$age)
-          ) %>% 
-  pcor(., method = "spearman") %>% 
-  .$estimate %>% 
-  round(., 2) %>% 
-  knitr::kable(format = "simple")
-
-left_join(x = df_corr_pre,
-          y = df_demo,
-          by = "ID") %>% 
-transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
-          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
-          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-          gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
-          age = (age - mean(.$age))/sd(.$age)
-          ) %>% 
-  pcor(., method = "pearson") %>% 
-  .$p.value %>% 
-  round(., 3) %>% 
-  knitr::kable(format = "simple")
-```
-
-### Regression
-
-```{r}
-main %>% 
-  filter(time_span == "subsequent") %>% 
-  select("time","ID","heart_rate") %>% 
-  distinct() %>% 
-  mutate(ID = as_factor(ID)) %>% 
-  lmer(formula = heart_rate ~ (1|ID) + ID * time) %>% 
-  summary() ->
-  fit_first
-
-as_tibble(fit_first$coefficients,
-          rownames = "Coefficient") %>%
-  filter(str_detect(.$Coefficient,
-                    pattern = "time")) %>% 
-  mutate(coefficient = case_when(Coefficient == "time" ~ "101",
-                                 TRUE ~ Coefficient),
-         ID = str_extract(string = coefficient,
-                                   pattern = "[:digit:]{3}"
-                                   ),
-         ID = as.numeric(ID)
-         ) %>% 
-  select("ID","Estimate") ->
-  df_estimates
-
-df_merge %>% 
-  group_by(ID) %>% 
-  summarize(confident_factor_m = mean(confident_factor,
-                                      na.rm = TRUE),
-            disruption_factor_m = mean(disruption_factor,
-                                       na.rm = TRUE),
-            ID = ID,
-            t_exp = teaching_experience) %>% 
-  distinct() %>% 
-  left_join(., df_estimates,
-            by = "ID") ->
-  df_corr_sub
-
-left_join(x = df_corr_sub,
-          y = df_demo,
-          by = "ID") %>% 
-  mutate(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
-         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
-         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-         gender = gender,
-         age = (age - mean(.$age))/sd(.$age)
-         ) %>%
-  lm(formula = Estimate ~ confident_factor_m + disruption_factor_m + gender + age) %>% 
-  tidy(x = .,
-       conf.int = TRUE) %>% 
-  mutate(term = case_when(term == "confident_factor_m" ~ "Confident Factor",
-                              term == "disruption_factor_m" ~ "Disruption Factor",
-                              term == "genderfemale" ~ "Weiblich\n(Ref.: Männlich)",
-                              term == "age" ~ "Alter",
-                              TRUE ~ "Intercept"
-                           ),
-         term = fct_rev(as_factor(term))
-         ) %>% 
-  filter(term != "Intercept") %>% 
-  ggplot(mapping = aes(y = term)) +
-    geom_point(aes(x = estimate)) +
-  geom_vline(xintercept = 0) +
-  geom_segment(mapping = aes(x = conf.low,
-                             xend = conf.high,
-                             y = term,
-                             yend = term
-                             ),
-               color = "#440154"
-               ) +
-  labs(x = "Effect",
-       y = "",
-       title = "Subsequent Phase",
-       subtitle = paste0("Dependend Variable: Standardized Estimate\n(M = ", 
-                         mean(df_corr_sub$Estimate) %>% round(.,2),
-                         ")"
-                         )
-       ) +
-  theme_apa() 
-```
-
-- Nach der Erhebung fällt die HR der Personen, die sich stärker gestört gefühlt haben, *signifikant stärker* ab
-
-## Main Phase vs. Interview Phase
-
-- Main Phase = 10 Minuten ab Lektionsbeginn 
-- Interview Phase = 10 Minuten mittig vom Interview (Differenz vom Ende der Unterrichtseinheit und von take off watch - die Länge des Zeitraumes, wo die 10 Minuten mittig reinlegt werden --> diese Länge wurde nochmals halbiert, um zur Mitte des Intervalls zu kommen und 5 Minuten abgezogen, um am Start des 10-Minuten-Intervalls zu landen)
-
-Plan:
-
-- Partielle Korrelation (mittlere HR x ...)
-- Mittelwertvergleich
-
-### Partielle Korrelationen
-
-#### Main Phase
-
-```{r}
-main %>% 
-  filter(time_span == "main") %>% 
-  group_by(ID) %>% 
-  transmute(heart_rate_m = mean(heart_rate),
-            confident_factor_m = mean(confident_factor,
-                                      na.rm = TRUE),
-            disruption_factor_m = mean(disruption_factor,
-                                       na.rm = TRUE),
-            age = age,
-            gender = gender
-            ) %>%
-  distinct() %>% 
-  ungroup() %>% 
-  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
-         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
-         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-         gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
-          age = (age - mean(.$age))/sd(.$age)
-         ) %>% 
-  pcor()  -> pcor_main
-
-knitr::kable(x = list(pcor_main$estimate, pcor_main$p.value), format = "simple")  
-```
-
-#### Interview Phase
-
-```{r}
-main %>% 
-  filter(time_span == "interview") %>% 
-  group_by(ID) %>% 
-  transmute(heart_rate_m = mean(heart_rate),
-            confident_factor_m = mean(confident_factor,
-                                      na.rm = TRUE),
-            disruption_factor_m = mean(disruption_factor,
-                                       na.rm = TRUE),
-            age = age,
-            gender = gender
-            ) %>%
-  distinct() %>% 
-  ungroup() %>% 
-  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
-         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
-         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-         gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
-          age = (age - mean(.$age))/sd(.$age)
-         ) %>% 
-  pcor()  -> pcor_interview
-
-knitr::kable(x = list(pcor_interview$estimate, pcor_interview$p.value), format = "simple")  
-```
-
-### t-Test
-
-- Paired t-Test
-- Idee: Vorher standardisieren anhand von allen Herzraten-Daten
-  - Mittlere Herzrate über alle Datenpunkte = beste Schätzung für den realen Mittelwert
-
-$$z_{Phase}=\frac{x_{Phase}-M_{overall}}{SD_{overall}} $$
-
-```{r}
-
-main %>% 
-  filter(time_span == "overall") %>% 
-  group_by(ID) %>% 
-  summarize(heart_rate_m_oa = mean(heart_rate),
-            heart_rate_sd_oa = sd(heart_rate)) %>% 
-  ungroup() %>% 
-  left_join(.,
-            y = main,
-            by = "ID") %>% 
-  filter(time_span == "interview" | time_span == "main") %>% 
-  select("time", "heart_rate", "ID", "time_span", "heart_rate_m_oa", "heart_rate_sd_oa") %>% 
-  distinct() %>% 
-  mutate(heart_rate_m = (heart_rate - heart_rate_m_oa)/heart_rate_sd_oa) %>% 
-  select("heart_rate_m","time_span","ID") %>% 
-  group_by(ID, time_span) %>% 
-  summarise(heart_rate_m = mean(heart_rate_m)) %>% 
-  ungroup() %>% 
-  pivot_wider(id_cols = ID,
-              names_from = time_span,
-              values_from = heart_rate_m) -> tib_test
-
-t.test(x = tib_test$interview,
-       y = tib_test$main,
-       paired = TRUE)
-```
-
-Ohne Standardisierung:
-
-```{r}
-main %>% 
-  filter(time_span == "interview" | time_span == "main") %>% 
-  select("ID","time","time_span","heart_rate") %>% 
-  distinct() %>% 
-  group_by(ID, time_span) %>% 
-  summarize(heart_rate_m = mean(heart_rate)) %>% 
-  ungroup() %>% 
-  pivot_wider(id_cols = ID,
-              names_from = time_span,
-              values_from = heart_rate_m) -> tib_test_einfach
-
-t.test(x = tib_test_einfach$interview,
-       y = tib_test_einfach$main,
-       paired = TRUE)
-```
-
-- Beide Testresultate zeigen einen signifikanten Unterschied

### 2023-01-04 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
Update fitbit_paper.Rmd

@@
 ### Wrist-worn devices as a new approach to assess physiological measures
+
+@fuller2020reliability showed in their review article that wearable devices such as Fitbit watches are accurate and reliable for measuring heart rate in controlled settings.
+
 "The use of physiological measures enabled us to get some insight into teachers’ affective responses without disrupting the teaching process (Mauss & Robinson, 2009) and to reduce issues with social desirability, retrospective bias, and high cognitive load (Becker et al., 2015; Goetz et al., 2015; Scollon et al.,2009; Wilhelm & Grossman, 2010).
@@
 
-### Teachers' self-assessment of arousal during the teaching phase
-The subject's self-assessment of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.
-For this purpose, two numerical 11-point rating scales were used: _(1)_	The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption with the following question: "On a scale of 0-10: how disruptive did you find the event?
-0 is not disruptive at all, 10 is extremely disruptive" _(2)_	The second rating scale assessed the teacher’s subjective perception of confidence in dealing with the disruptions during the lesson asked as follows: "How confident did you feel in dealing with this event on a scale of 0-10?
-0 is not confident at all and 10 is extremely confident"
-The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjetcts' self-assessment and emotional experience, and thus to make them measurable and comparable [@eid2015statistik; @doring2016empirische].
+### Teachers' self-reported data of arousal during the teaching phase
+The subject's self-reported data of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.
+For this purpose, two numerical 11-point rating scales were used: _(1)_	The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption ("On a scale of 0-10: how disruptive did you find the event?
+0 is not disruptive at all, 10 is extremely disruptive") _(2)_	The second rating scale assessed the teacher’s subjective perception of confidence in dealing with the disruptions during the lesson ("How confident did you feel in dealing with this event on a scale of 0-10?
+0 is not confident at all and 10 is extremely confident").
+
+The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjects' self-report and emotional experience, and thus to make them measurable and comparable [@eid2015statistik; @doring2016empirische].
 The gradations of the rating scale were unambiguous and the intervals between them identical.
@@
 
-### Heart rate Data
+### Heart rate data
 
@@
 
-### Rating Scale Data
+### Teachers' self-reported data of arousal during the teaching phase
 
@@
 
-# Discussion and implication
+# Discussion and implications
 The analyses showed that wrist-worn fitness trackers are a suitable method to measure different phases of arousal in (prospective) teachers in laboratory settings, with clear effects visible even in intervals of just 10 minutes.

### 2023-01-05 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data.Rmd
script

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : bookdown::word_document2 #papaja::apa6_pdf
---

```{r setup, include = FALSE}

library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Packages

```{r}
#install.packages("needs")

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

library(needs)

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR)
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

```{r demographicstable, echo = FALSE}

# prepare data (selected from questionnaire data)
demo.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")

# select relevant columns
demo.data <- demo.data %>% select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05)

# rename columns
demo.data <- rename(demo.data, c("Group" = "LI06_05",
                                  "Gender" = "LI02_01_1",
                                  "Age" = "LI03_01",
                                  "Teaching Experience" = "LI04_01")) %>% 
    filter(Group %in% c(101:125, 202:217))# filter relevant rows

# define expert and novice with ifelse function
demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")

# changing gender female 2 = 0 
demo.data$Gender = ifelse(demo.data$Gender == 2, "0","1")

# changing character into numeric
demo.data$Gender <- as.numeric(demo.data$Gender)

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Male" = sum(Gender),
            "M Age" = round(mean(Age), 2),
            "Min Age" = min(Age),
            "Max Age" = max(Age),
            "SD Age" = round(sd(Age), 2),
            "M Exp." = round(mean(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
           )

# format and insert table in manuscript
apa_table(
  demo.table,
  caption = "Demographic Information and Teaching Experience",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

```

### 2023-01-13 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update fitbit paper

@@
 output            : papaja::apa6_pdf
+# bookdown::word_document2 
 ---
@@
 
-main <-
-  left_join(main, df_merge,
-            by = "ID")
+# main <-
+#   left_join(main, df_merge,
+#             by = "ID")
 
@@
 
-## Theoretical Backround
+# Theoretical Background
 
-### Stress in Teaching Profession
+## Stress in Teaching Profession
 
@@
 
-### Heart rate as an indicator for stress or arousal
+## Heart rate as an indicator for stress or arousal
 Heart rate is physiologically regulated by the autonomic nervous system.
@@
 
-### Wrist-worn devices as a new approach to assess physiological measures
+## Wrist-worn devices as a new approach to assess physiological measures
 
@@
 
-XXX Helsinki XXX All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
 All participants were informed in detail about the aim and intention of the study prior to testing.
@@
 ## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+We used `r cite_r("r-references.bib")` for all our analyses (descriptive statistics, correlations, and multilevel regression).
+Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio [palmeri2020].
+An alpha level of 0.05 was used for the statistical tests.
 
-### Heart rate data
+### Descriptive statistics
 
-All participants were given a FitBit Smart Watch Charge 4 to wear during the experiment.
+Means, standard deviations and the range of teachers’ heart rate and the self-reported data are shown in Table 2.
 
-### Teachers' self-reported data of arousal during the teaching phase
+```{r descriptive statistics}
+# Mean, SD and range for overall 
+descrip_hr_overall <- main %>%
+  filter(time_span %in% c("overall")) %>% 
+  summarise("M heart rate in bpm" = round(mean(heart_rate),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate),
+                                      digits = 2),
+            "Min heart rate in bpm" = min(heart_rate),
+            "Max heart rate in bpm" = max(heart_rate)
+  )
+
+# Mean, SD and range for individual phases 
+descrip_hr_phases <- main %>% 
+  filter(!time_span %in% c("overall")) %>% 
+  group_by(time_span) %>% 
+  summarise("M heart rate in bpm" = round(mean(heart_rate),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate),
+                                      digits = 2),
+            "Min heart rate in bpm" = min(heart_rate),
+            "Max heart rate in bpm" = max(heart_rate)
+  )
+
+# # format and insert table in manuscript
+# descrip_hr_phases %>%
+# papaja::apa_table(
+#   caption = "Mean, SD and range for teachers' heart rate in individual phases",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+#   )
+
+# Mean, SD and range for disruption and confident factor
+rating_table <- 
+  df_rating %>% 
+  filter(!is.na(confident_factor),
+         !is.na(disruption_factor)) %>% 
+   summarise("M disruption factor" = round(mean(disruption_factor),
+                                     digits = 2),
+            "SD disruption factor" = round(sd(disruption_factor),
+                                      digits = 2),
+            "Min disruption factor" = min(disruption_factor),
+            "Max disruption factor" = max(disruption_factor),
+            "M confident factor" = round(mean(confident_factor),
+                                     digits = 2),
+            "SD confident factor" = round(sd(confident_factor),
+                                      digits = 2),
+            "Min confident factor" = min(confident_factor),
+            "Max confident factor" = max(confident_factor)
+            )
+
+```
+
+Teachers’ average heart rate during the entire course of the study was approximately `r descrip_hr_overall %>% pull("M heart rate in bpm")` bpm with a standard deviation of `r descrip_hr_overall %>% pull("SD heart rate in bpm")` and a range from `r descrip_hr_overall %>% pull("Min heart rate in bpm")` to `r descrip_hr_overall %>% pull("Max heart rate in bpm")` bpm.
+
+Means, standard deviations and the range of teachers’ heart rate for the different phases and the self-reported data are shown in Table 2.
+
+### Multilevel regressions
 
@@
 # Discussion and implications
-The analyses showed that wrist-worn fitness trackers are a suitable method to measure different phases of arousal in (prospective) teachers in laboratory settings, with clear effects visible even in intervals of just 10 minutes.
 

### 2023-01-13 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
update fitbit paper

@@
 Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+
+XXX In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress.
+XXX
 }
@@
 Runge et al.
-(n.d.) alone examined teacher stress in a relatively small sample (\emph{N} = 4 teachers) and showed that high heart rate indicate more stress in teachers.
+(n.d.) alone examined teacher stress in a relatively small sample (\emph{N} = 4 teachers) and showed that high heart rate indicates more stress in teachers.
 
-Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of arousal during teaching.
+Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, low-cost, and robust measurement method for assessing teachers' experience of arousal during teaching.
 
-\hypertarget{theoretical-backround}{%
-\subsection{Theoretical Backround}\label{theoretical-backround}}
+\hypertarget{theoretical-background}{%
+\section{Theoretical Background}\label{theoretical-background}}
 
 \hypertarget{stress-in-teaching-profession}{%
-\subsubsection{Stress in Teaching Profession}\label{stress-in-teaching-profession}}
+\subsection{Stress in Teaching Profession}\label{stress-in-teaching-profession}}
 
@@
 --\textgreater{} wie entsteht Stress
+
 --\textgreater{} wie wurde Stress bisher gemessen
@@
 \hypertarget{heart-rate-as-an-indicator-for-stress-or-arousal}{%
-\subsubsection{Heart rate as an indicator for stress or arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}
+\subsection{Heart rate as an indicator for stress or arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}
 
@@
 \hypertarget{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}{%
-\subsubsection{Wrist-worn devices as a new approach to assess physiological measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}
+\subsection{Wrist-worn devices as a new approach to assess physiological measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}
+
+Fuller et al. (2020) showed in their review article that wearable devices such as Fitbit watches are accurate and reliable for measuring heart rate in controlled settings.
 
@@
 \end{enumerate}
-
-In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress.
 
@@
 
-\hypertarget{teachers-self-assessment-of-arousal-during-the-teaching-phase}{%
-\subsubsection{Teachers' self-assessment of arousal during the teaching phase}\label{teachers-self-assessment-of-arousal-during-the-teaching-phase}}
+\hypertarget{teachers-self-reported-data-of-arousal-during-the-teaching-phase}{%
+\subsubsection{Teachers' self-reported data of arousal during the teaching phase}\label{teachers-self-reported-data-of-arousal-during-the-teaching-phase}}
 
-The subject's self-assessment of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.
-For this purpose, two numerical 11-point rating scales were used: \emph{(1)} The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption with the following question: ``On a scale of 0-10: how disruptive did you find the event?
-0 is not disruptive at all, 10 is extremely disruptive'' \emph{(2)} The second rating scale assessed the teacher's subjective perception of confidence in dealing with the disruptions during the lesson asked as follows: ``How confident did you feel in dealing with this event on a scale of 0-10?
-0 is not confident at all and 10 is extremely confident''
-The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjetcts' self-assessment and emotional experience, and thus to make them measurable and comparable (Döring \& Bortz, 2016; Eid, Gollwitzer, \& Schmitt, 2015).
+The subject's self-reported data of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.
+For this purpose, two numerical 11-point rating scales were used: \emph{(1)} The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption (``On a scale of 0-10: how disruptive did you find the event?
+0 is not disruptive at all, 10 is extremely disruptive'') \emph{(2)} The second rating scale assessed the teacher's subjective perception of confidence in dealing with the disruptions during the lesson (``How confident did you feel in dealing with this event on a scale of 0-10?
+0 is not confident at all and 10 is extremely confident'').
+
+The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjects' self-report and emotional experience, and thus to make them measurable and comparable (Döring \& Bortz, 2016; Eid, Gollwitzer, \& Schmitt, 2015).
 The gradations of the rating scale were unambiguous and the intervals between them identical.
@@
 
-For analyzing the heart rate data, we selected five 10-minute intervals of theoretical interest.
-To ensure that the intervals are comparable for all participants, we decided on 10-minute intervals because this was the minimum duration of all intervals.
-The individual intervals are described in detail below.
+For analyzing the heart rate data, we focused on five 10-minute intervals of theoretical interest for multiple reason.
+First, 10 minutes was to the minimum duration of all intervals, so we wanted to ensure the comparability of the intervals for all participants.
+Second, Lu et al.
+(2008) confirmed in their study that 10-minute intervals are an useful duration for analyzing photoplethysmography (PPG) data.
+Third, other studies revealed that the first minutes of the lesson start are essential regarding teacher-student interaction (Claessens et al., 2017; Donker, Van Gog, \& Mainhard, 2018).
 
-\emph{(1)} The \emph{pre-teaching phase} was the first 10 minutes belonging to the interval of interest.
+The procedure of the study and how we calculated the five phases is described in the following:
+
+\emph{(1)} The \emph{pre-teaching phase} was the first 10-minute interval of interest.
 This interval was calculated from the moment the subject arrived and the Fitbit watch was put on, which happened immediately after the subject was welcomed by the experimenter and the three actors.
@@
 The lesson lasted about 18 minutes on average but only the first 10 minutes were used as an interval to ensure the identical duration for all participants.
-XXX GENAUEN M + SD BERECHNEN XXX At the end of the lesson, the experimenter again noted the time and the steps on the clock.
+At the end of the lesson, the experimenter again noted the time and the steps on the clock.
 
-\emph{(3)} The noted time of the lesson end was also the starting point for the \emph{post-teaching} phase as the third 10 minute interval.
+\emph{(3)} The noted time of the lesson end was also the starting point for the \emph{post-teaching} phase as the third 10-minute interval.
 At the end of the lesson, the experimenter attached letters A through D in the lab while the teacher performed a second 9-point calibration outside.
@@
 
-\emph{(4)} The fourth 10 minute interval of interest was the \emph{interview phase} that are 10 minutes in the middle of the interview.
+\emph{(4)} The fourth 10-minute interval of interest was the \emph{interview phase} that was 10 minutes in the middle of the interview.
 To ensure that all subjects were in the middle of the interview, we calculated the difference from the end of the lesson and from the time when the subject took off the watch.
@@
 
-\emph{(5)} The last interesting interval for the analyses is the \emph{end phase}, which was the 10 minutes before the subject took off the watch.
+\emph{(5)} The last interesting interval for the analyses was the \emph{end phase}, which was the 10 minutes before the subject took off the watch.
 In this interval, the subject answered a second questionnaire (Situational Judgment Test, Gold and Holodynski (2015)) to assess the subject's strategic knowledge of classroom management.
@@
 We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) for all our analyses.
+al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) for all our analyses (descriptive statistics, correlations, and multilevel regression).
+Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}.
+An alpha level of 0.05 was used for the statistical tests.
 
-\hypertarget{heart-rate-data}{%
-\subsubsection{Heart rate Data}\label{heart-rate-data}}
+\hypertarget{descriptive-statistics}{%
+\subsubsection{Descriptive statistics}\label{descriptive-statistics}}
 
-All participants were given a FitBit Smart Watch Charge 4 to wear during the experiment.
+Means, standard deviations and the range of teachers' heart rate and the self-reported data are shown in Table 2.
 
-\hypertarget{rating-scale-data}{%
-\subsubsection{Rating Scale Data}\label{rating-scale-data}}
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:descriptive statistics}Mean, SD and range for teachers' heart rate in individual phases}
+
+\tiny{
+
+\begin{tabular}{lllll}
+\toprule
+time\_span & \multicolumn{1}{c}{M heart rate in bpm} & \multicolumn{1}{c}{SD heart rate in bpm} & \multicolumn{1}{c}{Min heart rate in bpm} & \multicolumn{1}{c}{Max heart rate in bpm}\\
+\midrule
+after & 77.20 & 11.04 & 50.00 & 120.00\\
+interview & 82.40 & 11.78 & 51.00 & 132.00\\
+main & 100.28 & 16.55 & 56.00 & 164.00\\
+pre & 96.21 & 14.10 & 56.00 & 139.00\\
+subsequent & 94.08 & 14.28 & 63.00 & 150.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Teachers' average heart rate during the entire course of the study was approximately 95.93 bpm with a standard deviation of 14.03 and a range from 56 to 139 bpm.
+
+Means, standard deviations and the range of teachers' heart rate for the different phases and the self-reported data are shown in Table 2.
+
+\hypertarget{multilevel-regressions}{%
+\subsubsection{Multilevel regressions}\label{multilevel-regressions}}
 
@@
 
-\hypertarget{discussion-and-implication}{%
-\section{Discussion and implication}\label{discussion-and-implication}}
-
-The analyses showed that wrist-worn fitness trackers are a suitable method to measure different phases of arousal in (prospective) teachers in laboratory settings, with clear effects visible even in intervals of just 10 minutes.
+\hypertarget{discussion-and-implications}{%
+\section{Discussion and implications}\label{discussion-and-implications}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-claessens2017positive}{}}%
+Claessens, L.
+C., Tartwijk, J.
+van, Want, A.
+C.
+van der, Pennings, H.
+J., Verloop, N., Brok, P.
+J.
+den, \& Wubbels, T.
+(2017).
+Positive teacher--student relationships go beyond the classroom, problematic ones stay inside.
+\emph{The Journal of Educational Research}, \emph{110}(5), 478--493.
+
+\leavevmode\vadjust pre{\hypertarget{ref-donker2018quantitative}{}}%
+Donker, M.
+H., Van Gog, T., \& Mainhard, M.
+T.
+(2018).
+A quantitative exploration of two teachers with contrasting emotions: Intra-individual process analyses of physiology and interpersonal behavior.
+\emph{Frontline Learning Research}, \emph{6}(3), 162--184.
+
 \leavevmode\vadjust pre{\hypertarget{ref-doring2016empirische}{}}%
@@
 Fox, J. (2022). \emph{Polycor: Polychoric and polyserial correlations}. Retrieved from \url{https://CRAN.R-project.org/package=polycor}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fuller2020reliability}{}}%
+Fuller, D., Colwell, E., Low, J., Orychock, K., Tobin, M.
+A., Simango, B., et al.others.
+(2020).
+Reliability and validity of commercially available wearable devices for measuring steps, energy expenditure, and heart rate: Systematic review.
+\emph{JMIR mHealth and uHealth}, \emph{8}(9), e18694.
 
@@
 Lowe, H. (2016). Educational behavior apps and wearable devices: Current research and prospects. \emph{Educational Technology}, 30--33.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lu2008can}{}}%
+Lu, S., Zhao, H., Ju, K., Shin, K., Lee, M., Shelley, K., \& Chon, K.
+H.
+(2008).
+Can photoplethysmography variability serve as an alternative approach to obtain heart rate variability information?
+\emph{Journal of Clinical Monitoring and Computing}, \emph{22}(1), 23--29.
 

### 2023-01-23 01_studies/01_Laborstudie ProVisioNET/R script/reli/ProVisioNET_reli_reactions_JH_FP.R
reli

@@ -12,6 +12,7 @@ needs(tidyverse,
       readxl)
 
 
+
 # suppress "summarize" info. 
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
 options(dplyr.summarise.inform = FALSE)
@@ -39,10 +40,14 @@ r2 <- r2 %>% filter(`VP ID` == "101")
 
 # reshape data frame in long format 
 r1_long <- r1 %>% 
-  pivot_longer(!`VP ID`, names_to = "Event", values_to = "Value")
+  pivot_longer(!`VP ID`, 
+               names_to = "Event", 
+               values_to = "Value")
 
 r2_long <- r2 %>% 
-  pivot_longer(!`VP ID`, names_to = "Event", values_to = "Value")
+  pivot_longer(!`VP ID`, 
+               names_to = "Event", 
+               values_to = "Value")
 
 r1_long$Value <- as.numeric(r1_long$Value)
 

### 2023-01-24 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd

@@
 
-floatsintext      : no
+floatsintext      : yes
 linenumbers       : yes
@@
 
+### Pairwaise t-test and effect size
+
 ### Multilevel regressions
 
+XXX
+
 # Results
+
+# First visual results
+
+The graph \@ref(fig:overall_plot) show the heart rate for the entire course of the study.
+
+```{r overall_plot, fig.height = 8, fig.width = 15}
+
+  main %>% 
+  filter(time_span == "overall") %>% 
+  select("ID","time_span", "time","heart_rate") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+ # stat_smooth(geom = "line",
+ #             method = "loess",
+ #             se = FALSE) +
+  geom_smooth(method = "loess",
+              se = FALSE) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Time (in seconds)",
+       y = "Heart rate (in beats per minute)") +
+  theme_apa() -> overall_plot
+
+overall_plot
+
+```
+
+The second graph \@ref(fig:phase_plot) show the heart rate for the individual five phases.
+
+```{r phase_plot, fig.height = 8, fig.width = 15}
+
+main %>% 
+  filter(time_span != "overall") %>% 
+  select("ID","time_span", "time","heart_rate") %>% 
+  mutate(
+    # status = case_when(ID < 200 ~ "Unerfahren",
+    #                         ID > 200 ~ "Erfahren"),
+         time_span = fct_recode(time_span,
+                                "Pre-teaching phase" = "pre",
+                                "Teaching phase" = "main",
+                                "Post-teaching phase" = "subsequent",
+                                "Intview phase" = "interview",
+                                "End phase" = "after"
+                                ),
+         time_span = factor(time_span,
+                            levels = c("Pre-teaching phase",
+                                       "Teaching phase",
+                                       "Post-teaching phase",
+                                       "Intview phase",
+                                       "End phase"
+                                       )
+                            )
+         ) %>%
+  distinct() %>% 
+ggplot(mapping = aes(x = time,
+                     y = heart_rate
+                     )
+       ) +
+  geom_smooth(method = "glm") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Time (in seconds)",
+       y = "Heart rate (in beats per minute)") +
+  theme_apa() +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x",
+             ) -> phase_plot
+
+phase_plot
+
+```
 

### 2023-01-24 02_paper/02_study/02_fitbit paper/fitbit_paper.tex

@@
 \documentclass[
-  man]{apa6}
+  man,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \keywords{heart rate; photoplethysmography; wearable electronic device; teaching\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
 We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) for all our analyses (descriptive statistics, correlations, and multilevel regression).
+al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.36; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression).
 Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}.
@@
 
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:descriptive statistics}Mean, SD and range for teachers' heart rate in individual phases}
-
-\tiny{
-
-\begin{tabular}{lllll}
-\toprule
-time\_span & \multicolumn{1}{c}{M heart rate in bpm} & \multicolumn{1}{c}{SD heart rate in bpm} & \multicolumn{1}{c}{Min heart rate in bpm} & \multicolumn{1}{c}{Max heart rate in bpm}\\
-\midrule
-after & 77.20 & 11.04 & 50.00 & 120.00\\
-interview & 82.40 & 11.78 & 51.00 & 132.00\\
-main & 100.28 & 16.55 & 56.00 & 164.00\\
-pre & 96.21 & 14.10 & 56.00 & 139.00\\
-subsequent & 94.08 & 14.28 & 63.00 & 150.00\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Teachers' average heart rate during the entire course of the study was approximately 95.93 bpm with a standard deviation of 14.03 and a range from 56 to 139 bpm.
+Teachers' average heart rate during the entire course of the study was approximately 96.26 bpm with a standard deviation of 14.22 and a range from 56 to 139 bpm.
 
 Means, standard deviations and the range of teachers' heart rate for the different phases and the self-reported data are shown in Table 2.
+
+\hypertarget{pairwaise-t-test-and-effect-size}{%
+\subsubsection{Pairwaise t-test and effect size}\label{pairwaise-t-test-and-effect-size}}
 
@@
 
+XXX
+
 \hypertarget{results}{%
 \section{Results}\label{results}}
+
+\hypertarget{first-visual-results}{%
+\section{First visual results}\label{first-visual-results}}
+
+The graph @ref(fig:overall\_plot) show the heart rate for the entire course of the study.
+
+\includegraphics{fitbit_paper_files/figure-latex/overall_plot-1.pdf}
+
+The second graph @ref(fig:phase\_plot) show the heart rate for the individual five phases.
+
+\includegraphics{fitbit_paper_files/figure-latex/phase_plot-1.pdf}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-xfun}{}}%
+Xie, Y. (2022). \emph{Xfun: Supporting functions for packages maintained by 'yihui xie'}. Retrieved from \url{https://CRAN.R-project.org/package=xfun}
+
 \end{CSLReferences}

### 2023-01-27 01_studies/01_Laborstudie ProVisioNET/R script/reli/ProVisioNET_reli_reactions_JH_FP.R
upload reli

@@ -21,31 +21,31 @@ options(dplyr.summarise.inform = FALSE)
 ################## RATER 1 ################
 
 # read in data from rater1 while specifying locale allows to set "," 
-r1 <-read_excel ("./data/coding_expertise_reaction_MN.xlsx", col_names = TRUE)
+r1 <-read_excel ("./data/coding_expertise_reaction_GS.xlsx", col_names = TRUE)
 
 
 ################## RATER 2 ################
 
 # read in data from rater1 while specifying locale allows to set "," 
-r2 <-read_excel ("./data/coding_expertise_reaction_NT.xlsx", col_names = TRUE)
+r2 <-read_excel ("./data/coding_expertise_reactions_JG_JP.xlsx", col_names = TRUE)
 
 
 ################## DATA WRANGLING video 01 ################
 
-# filter relevant rows and select relevant columns 
-r1 <- r1 %>% filter(`VP ID` == "101")
-
-r2 <- r2 %>% filter(`VP ID` == "101")
+# # filter relevant rows and select relevant columns 
+# r1 <- r1 %>% filter(`VP ID` == "101")
+# 
+# r2 <- r2 %>% filter(`VP ID` == "101")
 
 
 # reshape data frame in long format 
 r1_long <- r1 %>% 
-  pivot_longer(!`VP ID`, 
+  pivot_longer(!ID, 
                names_to = "Event", 
                values_to = "Value")
 
 r2_long <- r2 %>% 
-  pivot_longer(!`VP ID`, 
+  pivot_longer(!ID, 
                names_to = "Event", 
                values_to = "Value")
 
@@ -60,13 +60,13 @@ r3 <- bind_cols(r1_long$Value, r2_long$Value) %>%
          rating2 = ...2)
 
 #################### Percentage Agreement ##############################
-agree(r3)
+agree(r3, tolerance = 1)
 
 #################### CohenKappa ##############################
 kappa <- psych::cohen.kappa(x = as.matrix(r3))
 
-
-
+################## ICC ###########################
+ICC(r3)
 
 
 

### 2023-02-13 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
update fitbit

@@
          disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
-         confident_factor,
+         confidence_factor,
          event
@@
                                     ),
-         confident_factor = ifelse(confident_factor < 0,
+         confidence_factor = ifelse(confidence_factor < 0,
                                    yes = NA,
-                                   no = confident_factor),
+                                   no = confidence_factor),
          event = as_factor(event)
@@
 
-## Confident Factor
+## confidence Factor
 
@@
 df_merge %>% 
-  filter(!is.na(confident_factor)) %>% 
-  group_by(event, confident_factor) %>% 
+  filter(!is.na(confidence_factor)) %>% 
+  group_by(event, confidence_factor) %>% 
   summarize(value = n()) %>% 
@@
                        y = prop,
-                       fill = confident_factor
+                       fill = confidence_factor
                        )
@@
        x = "",
-       fill = "Confident Factor") +
+       fill = "confidence Factor") +
   theme_apa()
@@
 df_merge %>% 
-  filter(!is.na(disruption_factor) | !is.na(confident_factor)) %>% 
-  ggplot(mapping = aes(x = confident_factor,
+  filter(!is.na(disruption_factor) | !is.na(confidence_factor)) %>% 
+  ggplot(mapping = aes(x = confidence_factor,
                        y = disruption_factor
@@
   scale_color_viridis_d() +
-  labs(x = "Confident Factor",
+  labs(x = "confidence Factor",
        y = "Disruption Factor",
@@
 df_merge %>% 
-  filter(!is.na(confident_factor) | !is.na(disruption_factor)) %>% 
+  filter(!is.na(confidence_factor) | !is.na(disruption_factor)) %>% 
   ggplot(mapping = aes(x = age,
-                       y = confident_factor
+                       y = confidence_factor
                        )
@@
   labs(x = "Alter",
-       y = "Confident Factor") +
+       y = "confidence Factor") +
   scale_color_viridis_d() +
@@
 df_merge %>% 
-  filter(!(is.na(confident_factor) | is.na(disruption_factor))) %>% 
+  filter(!(is.na(confidence_factor) | is.na(disruption_factor))) %>% 
   group_by(ID) %>% 
-  summarize(mean_confident = mean(confident_factor),
+  summarize(mean_confidence = mean(confidence_factor),
             age = mean(age)) %>%
@@
   ggplot(mapping = aes(x = age,
-                       y = mean_confident
+                       y = mean_confidence
                        )
@@
   labs(x = "Alter",
-       y = "Mean(Confident Factor)") +
+       y = "Mean(confidence Factor)") +
   theme_apa()
@@
 df_merge %>% 
-  filter(!is.na(confident_factor) | !is.na(disruption_factor)) %>% 
+  filter(!is.na(confidence_factor) | !is.na(disruption_factor)) %>% 
   ggplot(mapping = aes(x = age,
@@
 df_merge %>% 
-  filter(!(is.na(confident_factor) | is.na(disruption_factor))) %>% 
+  filter(!(is.na(confidence_factor) | is.na(disruption_factor))) %>% 
   group_by(ID) %>% 
@@
   group_by(ID) %>% 
-  summarize(confident_factor_m = mean(confident_factor,
+  summarize(confidence_factor_m = mean(confidence_factor,
                                       na.rm = TRUE),
@@
   - AV: Estimate
-  - UV: Gender, Alter, Disruption Factor (mean), Confident Factor (mean)
+  - UV: Gender, Alter, Disruption Factor (mean), confidence Factor (mean)
   - Alle metrischen Variablen sind standardisiert
@@
 transmute(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
-          confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+          confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
           disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
@@
   mutate(Estimate = (Estimate - mean(.$Estimate))/sd(.$Estimate),
-         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
@@
          ) %>%
-  lm(formula = Estimate ~ confident_factor_m + disruption_factor_m  + gender + age) %>% 
+  lm(formula = Estimate ~ confidence_factor_m + disruption_factor_m  + gender + age) %>% 
   tidy(x = .,
        conf.int = TRUE) %>% 
-  mutate(term = case_when(term == "confident_factor_m" ~ "Confident Factor",
+  mutate(term = case_when(term == "confidence_factor_m" ~ "confidence Factor",
                               term == "disruption_factor_m" ~ "Disruption Factor",
@@
          term = fct_relevel(term, 
-                            c("Confident Factor",
+                            c("confidence Factor",
                               "Disruption Factor",
@@
          ) %>%
-  lm(formula = Estimate ~ confident_factor_m + disruption_factor_m + gender + age) %>% 
+  lm(formula = Estimate ~ confidence_factor_m + disruption_factor_m + gender + age) %>% 
   tidy(x = .,
        conf.int = TRUE) %>% 
-  mutate(term = case_when(term == "confident_factor_m" ~ "Confident Factor",
+  mutate(term = case_when(term == "confidence_factor_m" ~ "confidence Factor",
                               term == "disruption_factor_m" ~ "Disruption Factor",
@@
   transmute(heart_rate_m = mean(heart_rate),
-            confident_factor_m = mean(confident_factor,
+            confidence_factor_m = mean(confidence_factor,
                                       na.rm = TRUE),
@@
   transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
-         confident_factor_m = (confident_factor_m - mean(.$confident_factor_m))/sd(.$confident_factor_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),

### 2023-02-13 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
schone widder fitbit

@@
          ) +
- # stat_smooth(geom = "line",
- #             method = "loess",
- #             se = FALSE) +
-  geom_smooth(method = "loess",
-              se = FALSE) +
+  geom_smooth() +
   scale_color_viridis_d(option = "A",
@@
                                 "Post-Lehrphase" = "subsequent",
-                                "Intviewphase" = "interview",
+                                "Interviewphase" = "interview",
                                 "Endphase" = "after"
@@
                                        "Post-Lehrphase",
-                                       "Intviewphase",
+                                       "Interviewphase",
                                        "Endphase"

### 2023-02-14 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data.Rmd

@@
                                   "Teaching Experience" = "LI04_01")) %>% 
-    filter(Group %in% c(101:125, 202:217))# filter relevant rows
+    filter(Group %in% c(101:136, 202:217))# filter relevant rows
 

### 2023-02-14 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd

@@
 
-# Mean, SD and range for disruption and confident factor
+# Mean, SD and range for disruption and confidence factor
 rating_table <- 
   df_rating %>% 
-  filter(!is.na(confident_factor),
+  filter(!is.na(confidence_factor),
          !is.na(disruption_factor)) %>% 
@@
             "Max disruption factor" = max(disruption_factor),
-            "M confident factor" = round(mean(confident_factor),
+            "M confidence factor" = round(mean(confidence_factor),
                                      digits = 2),
-            "SD confident factor" = round(sd(confident_factor),
+            "SD confidence factor" = round(sd(confidence_factor),
                                       digits = 2),
-            "Min confident factor" = min(confident_factor),
-            "Max confident factor" = max(confident_factor)
+            "Min confidence factor" = min(confidence_factor),
+            "Max confidence factor" = max(confidence_factor)
             )

### 2023-02-15 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
fitbit

@@
 df_heart_all <-
-  read_rds(file = "final_data/heart_all.rds") |> 
+  read_rds(file = "data/heart_all.rds") |> 
   mutate(status = factor(status,
@@
 df_heart_min <-
-  read_rds(file = "final_data/heart_min.rds")
+  read_rds(file = "data/heart_min.rds")
 
 df_heart_aggr <- 
-  read_rds(file = "final_data/heart_aggr.rds") |> 
+  read_rds(file = "data/heart_aggr.rds") |> 
   mutate(status = factor(status,
@@
 
-# merge demo data and fitbit data
-df_anova <- merge(demo.data,
-                  df_heart_aggr,
-                  by="ID")
+# disruption & confidence rating
+df_rating <- 
+  excel_sheets("data/Coding_SRI.xlsx") %>% 
+  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
+  select(ID, # select relevant columns 
+         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
+         confidence_factor,
+         event
+         ) %>% 
+  mutate(disruption_factor = ifelse(disruption_factor < 0,
+                                    yes = NA,
+                                    no = disruption_factor
+                                    ),
+         confidence_factor = ifelse(confidence_factor < 0,
+                                   yes = NA,
+                                   no = confidence_factor),
+         event = as_factor(event)
+         ) %>% 
+  na.omit() 
+  # group_by(ID) %>% 
+  # summarise("mean_disrup" = round(mean(disruption_factor), 2),
+  #           "mean_confi" = round(mean(confidence_factor), 2))
+
+# demographic data
+df_demo <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
+  transmute(ID = LI06_05, # select and rename relevant columns 
+            gender = factor(LI02_01_1,
+                            levels = 1:2,
+                            labels = c("male","female")
+                            ),
+            age = LI03_01, # 1 = male; 2 = female
+            teaching_experience = LI04_01)
+
+# merge two data frames by ID 
+df_merge <- merge(df_demo,
+                  df_rating,
+                  by = "ID") %>% 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132")
+         )
+
+# rm(list = c("df_demo","df_rating"))
+
+data_path <- "./data/heart_rate_data"
+
+main <-
+map(.x = dir(path = data_path,
+             pattern = ".csv"),
+    ~ read_csv(file.path(data_path, .), 
+               id = "id",
+               col_types = c("t","n")
+               ) %>% 
+  mutate(time = .$Time - min(.$Time),
+         time = as.numeric(time),
+         heart_rate = `Heart Rate`,
+         ID = id,
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
+                               str_detect(string = id, pattern = "_m") ~ "main",
+                               str_detect(string = id, pattern = "_p") ~ "pre",
+                               str_detect(string = id, pattern = "_s") ~ "subsequent",
+                               str_detect(string = id, pattern = "_i") ~ "interview",
+                               TRUE ~ "overall"
+                               ),
+         ID = str_extract(string = ID,
+                          pattern = "[:digit:]{3}"),
+         ID = as.numeric(ID)
+      ) %>%
+      # filter(time <= 600) %>% # filter for 10min intervals
+    filter(time <= 9000) %>% # filter for 2 hours 30min (maximal duration of study)
+    select(!c("Time","Heart Rate","id"))
+    ) %>%
+  bind_rows()
+
+main <-
+  left_join(main, df_merge,
+            by = "ID")
+
+df_anova <-
+  main %>% 
+  filter(time_span != "overall") %>%   
+  select("ID",
+         "time_span",
+         "heart_rate",
+         "teaching_experience",
+         "disruption_factor",
+         "confidence_factor") %>% 
+  mutate(time_span = fct_recode(time_span,
+                                "Pre-Lehrphase" = "pre",
+                                "Lehrphase" = "main",
+                                "Post-Lehrphase" = "subsequent",
+                                "Interviewphase" = "interview",
+                                "Endphase" = "after"
+                                ),
+         time_span = factor(time_span,
+                            levels = c("Pre-Lehrphase",
+                                       "Lehrphase",
+                                       "Post-Lehrphase",
+                                       "Interviewphase",
+                                       "Endphase"
+                                       )
+                            )
+         ) %>%
+  distinct() %>% 
+  group_by(ID, time_span) %>%
+  summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
+            mean_confi = mean(disruption_factor, na.rm = TRUE),
+            mean_disrup = mean(disruption_factor, na.rm = TRUE),
+            mean_te = mean(teaching_experience, na.rm = TRUE)
+         )
+
+# # merge demo data and fitbit data
+# df_anova <- merge(df_anova,
+#                   df_heart_aggr,
+#                   by="ID")
 
 # clean variable names
-df_anova <- df_anova %>% clean_names()
+# df_anova <- df_anova %>% clean_names()
+
+# Visualization
+bxp <- ggboxplot(df_anova, x = "time_span", y = "mean_hr", add = "point")
+bxp
 
@@
   df_anova %>%
-  group_by(type) %>%
-  identify_outliers(mean)
+  group_by(time_span) %>%
+  identify_outliers(mean_hr)
 
@@
   df_anova %>%
-  group_by(type) %>%
-  shapiro_test(mean)
+  group_by(time_span) %>%
+  shapiro_test(mean_hr)
 
-ggqqplot(df_anova, "mean", facet.by = "type")
+# QQ plot draws the correlation between a given data and the normal distribution. 
+plot <- 
+  ggqqplot(df_anova, "mean_hr", facet.by = "time_span")
+
+df_anova_subset <- subset(df_anova, select = c(time_span, mean_hr))
+
+# # anova
+# res.aov <- rstatix::anova_test(data = df_anova_subset,
+#                                dv = mean_hr,
+#                                wid = ,
+#                                within = time_span)
+# get_anova_table(res.aov)
 
 # anova
-res.aov <- rstatix::anova_test(data = df_anova,
-                               dv = mean,
-                               wid = id,
-                               within = type)
-get_anova_table(res.aov)
-
-# anova expert novice
-res.aov2 <- rstatix::anova_test(data = df_anova,
-                               dv = mean,
-                               between = status,
-                               wid = id,
-                               within = type)
-get_anova_table(res.aov2)
+df_anova_phase <- 
+  aov(df_anova_subset$mean_hr~df_anova_subset$time_span)
+summary(df_anova_phase)
 
 # pairwise comparisons
-pwc <- df_anova %>%
-  pairwise_t_test(
-    mean ~ type, paired = TRUE,
-    p.adjust.method = "bonferroni"
-    )
-pwc
+pwc <- 
+  pairwise.t.test(df_anova_subset$mean_hr, 
+                  df_anova_subset$time_span, 
+                  p.adjust="holm")
 
-# Visualization: box plots with p-values
-pwc <- 
-  pwc %>% 
-  add_xy_position(x = "type")
+# effect size of ANOVA
+install.packages("DescTools")
+library(DescTools)
+EtaSq(df_anova_phase)
 
-# boxplot
-bxp_anova <- ggboxplot(data = df_anova, 
-                 x = "type", 
-                 y = "mean", 
-                 add = "point")
+effect_size_anova <-
+  sqrt(0.3399757/(1-0.3399757))
 
-bxp_anova + 
-  stat_pvalue_manual(pwc) +
-  labs(
-    subtitle = get_test_label(res.aov, detailed = TRUE),
-    caption = get_pwc_label(pwc)
-    )
+# effect size of pairwise comparisons
+library(dplyr)
+library(rstatix)
+df_anova_subset %>%
+cohens_d(mean_hr~time_span) %>% 
+as.data.frame()
 
-# saving plot 
-ggsave(plot = bxp_anova,
-       filename = "Plots/bxp_anova.svg",
-       height = 5,
-       width = 8,
-       units = "in")
+# # pairwise comparisons
+# pwc <- df_anova_subset %>%
+#   pairwise_t_test(
+#     mean_hr ~ time_span, paired = TRUE,
+#     p.adjust.method = "bonferroni"
+#     )
+# pwc
+
+# # Visualization: box plots with p-values
+# pwc <- 
+#   pwc %>% 
+#   add_xy_position(x = "time_span")
+# 
+# # boxplot
+# bxp_anova <- ggboxplot(data = df_anova, 
+#                  x = "type", 
+#                  y = "mean", 
+#                  add = "point")
+# 
+# bxp_anova + 
+#   stat_pvalue_manual(pwc) +
+#   labs(
+#     subtitle = get_test_label(res.aov, detailed = TRUE),
+#     caption = get_pwc_label(pwc)
+#     )
+
+# # saving plot 
+# ggsave(plot = bxp_anova,
+#        filename = "Plots/bxp_anova.svg",
+#        height = 5,
+#        width = 8,
+#        units = "in")
 

### 2023-02-15 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
fitbit

@@
     theme_apa()
+
+############## neuer Plot für GEBF #################
+
+  plot_overall <-
+  main %>% 
+  filter(time_span == "overall") %>%
+  select("ID","time_span", "time","heart_rate") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  geom_smooth() +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Zeit (in Sekunden)",
+       y = "Herzrate (in Schlägen pro Minute)") +
+  ggtitle("Gesamtverlauf der Herzrate in unterschiedlichen Phasen") +
+  theme(text = element_text(family = "serif"),
+        legend.text = element_text(size = 15),
+        legend.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20),
+        strip.text = element_text(size = 16),
+        plot.title = element_text(size = 20, 
+                                  face = "bold")) + 
+    theme_apa() 
+    # facet_grid(cols = vars(time_span),
+    #          scales = "free_x")
 

### 2023-02-16 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
fitbit bla

@@
       rstatix,
-      ggpubr)
+      ggpubr,
+      psych)
+
 ```
@@
 
+# read in data
 # disruption & confidence rating
@@
   map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
-  select(ID, # select relevant columns 
+  dplyr::select(ID, # select relevant columns 
          disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
@@
     filter(time <= 9000) %>% # filter for 2 hours 30min (maximal duration of study)
-    select(!c("Time","Heart Rate","id"))
+    dplyr::select(!c("Time","Heart Rate","id"))
     ) %>%
@@
 
+# data wrangling - preparing data for anova
 df_anova <-
@@
   filter(time_span != "overall") %>%   
-  select("ID",
+  dplyr::select("ID",
          "time_span",
@@
   summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
-            mean_confi = mean(disruption_factor, na.rm = TRUE),
+            mean_confi = mean(confidence_factor, na.rm = TRUE),
             mean_disrup = mean(disruption_factor, na.rm = TRUE),
@@
          )
+
+# counting participants in individual phases
+table(df_anova['time_span'])
+
+# descriptive analysis
+describeBy(df_anova$mean_hr,
+           df_anova$time_span)
 
@@
 # effect size of ANOVA
-install.packages("DescTools")
-library(DescTools)
 EtaSq(df_anova_phase)
@@
 effect_size_anova <-
-  sqrt(0.3399757/(1-0.3399757))
+  sqrt(0.3413791   /(1-0.3413791   ))
 
@@
 library(rstatix)
+effect_size_pwc <-
   df_anova_subset %>%
@@
 #        units = "in")
+
+```
+
+### Multiple Regression
+
+```{r}
+
+# AV = mittlere Herzrate in teaching phase; UV1 = Störfaktor, UV2 = Sicherheitsfaktor, UV3= Lehrerfahrung
+
+df_lm_subset <- df_anova %>% 
+  filter(time_span == "Lehrphase") %>% 
+  dplyr::select(mean_hr, 
+               mean_disrup, 
+               mean_confi,
+               mean_te)
+
+modell <-   lm(mean_hr ~ mean_confi + mean_disrup + mean_te, 
+               data = df_lm_subset,
+               family = binomial)
+summary(modell)
+
+cor(df_lm_subset)
 

### 2023-02-16 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
fitbit bla

--- 2023-02-13 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
@@
   filter(time_span == "overall") %>% 
-  select("ID","time_span", "time","heart_rate") %>% 
+  dplyr::select("ID","time_span", "time","heart_rate") %>% 
   distinct() %>% 
@@
     theme_apa()
+
+############## neuer Plot für GEBF #################
+
+  plot_overall <-
+  main %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  geom_smooth() +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  labs(x = "Zeit (in Sekunden)",
+       y = "Herzrate (in Schlägen pro Minute)") +
+  ggtitle("Gesamtverlauf der Herzrate in unterschiedlichen Phasen") +
+  theme(text = element_text(family = "serif"),
+        legend.text = element_text(size = 15),
+        legend.title = element_blank(),
+        axis.text.x = element_text(size = 20),
+        axis.text.y = element_text(size = 20),
+        strip.text = element_text(size = 16),
+        plot.title = element_text(size = 20, 
+                                  face = "bold")) + 
+    theme_apa() 
+    # facet_grid(cols = vars(time_span),
+    #          scales = "free_x")
 

### 2023-02-16 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update fitbit
fitbit bla

@@
       filter(time <= 600) %>%
-    select(!c("Time","Heart Rate","id"))
+     dplyr::select(!c("Time","Heart Rate","id"))
     ) %>%
@@
 
-# main <-
-#   left_join(main, df_merge,
-#             by = "ID")
+main <-
+  left_join(main, df_merge,
+            by = "ID")
 

### 2023-02-17 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
plots fitbit

@@
 
-  plot_overall <-
+  loess_plot_overall <-
   main %>% 
@@
          ) +
-  geom_smooth() +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(se = FALSE,
+              size = 1,
+              colour = "red") +
   scale_color_viridis_d(option = "A",
@@
   scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0, NA),
+                     breaks = seq(0, 9000, 600)) +
+  scale_y_continuous(breaks = seq(0, 160, 5)) + 
   labs(x = "Zeit (in Sekunden)",
        y = "Herzrate (in Schlägen pro Minute)") +
-  ggtitle("Gesamtverlauf der Herzrate in unterschiedlichen Phasen") +
-  theme(text = element_text(family = "serif"),
-        legend.text = element_text(size = 15),
+  ggtitle("Gesamtverlauf Herzrate in unterschiedlichen Phasen") +
+  theme_apa() + 
+  theme(text = element_text(family = "sans"),
+        legend.text = element_text(size = 20),
         legend.title = element_blank(),
-        axis.text.x = element_text(size = 20),
-        axis.text.y = element_text(size = 20),
-        strip.text = element_text(size = 16),
+        axis.title.x = element_text(size = 15),
+        axis.title.y = element_text(size = 15),
+        axis.text.x = element_text(size = 11),
+        axis.text.y = element_text(size = 11),
+        strip.text = element_text(size = 15),
         plot.title = element_text(size = 20, 
-                                  face = "bold")) + 
-    theme_apa() 
-    # facet_grid(cols = vars(time_span),
-    #          scales = "free_x")
+                                  face = "bold"))
+loess_plot_overall
+
+# saving plot 
+ggsave(plot = loess_plot_overall,
+       filename = "plots/loess_plot_overall.svg",
+       height = 5,
+       width = 8,
+       units = "in")
+
+```
+
+## Plot mit Mittelwerten und SDs
+
+```{r, fig.height = 8, fig.width = 15}
+
+# checking for outliers
+# df_outliers <-
+#   main %>% 
+#   filter(time_span != "overall") %>%   
+#   dplyr::select("ID",
+#          "time_span",
+#          "heart_rate",
+#          "teaching_experience",
+#          "disruption_factor",
+#          "confidence_factor") %>% 
+#   mutate(time_span = fct_recode(time_span,
+#                                 "Pre-Lehrphase" = "pre",
+#                                 "Lehrphase" = "main",
+#                                 "Post-Lehrphase" = "subsequent",
+#                                 "Interviewphase" = "interview",
+#                                 "Endphase" = "after"
+#                                 ),
+#          time_span = factor(time_span,
+#                             levels = c("Pre-Lehrphase",
+#                                        "Lehrphase",
+#                                        "Post-Lehrphase",
+#                                        "Interviewphase",
+#                                        "Endphase"
+#                                        )
+#                             )
+#          ) %>%
+#   distinct() %>% 
+#   group_by(ID, time_span) %>%
+#   summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
+#             sd_hr = sd(heart_rate, na.rm = TRUE)
+#             ) %>% 
+#   group_by(time_span) %>%
+#   identify_outliers(mean_hr)
+# 
+# # exclude extreme outliers
+# df_plot_mean <-
+#   df_outliers %>% 
+#   filter(!mean_hr %in% c("131.7869",
+#                          "129.3250",
+#                          "137.8485",
+#                          "136.9259",
+#                          "109.2143",
+#                          "110.6800",
+#                          "107.0800"))
+
+# data wrangling - preparing data for plotting
+df_plot_mean <-
+  main %>% 
+  filter(time_span != "overall") %>%   
+  dplyr::select("time_span",
+                "heart_rate") %>% 
+  mutate(time_span = fct_recode(time_span,
+                                "(1) Pre-Lehrphase" = "pre",
+                                "(2) Lehrphase" = "main",
+                                "(3) Post-Lehrphase" = "subsequent",
+                                "(4) Interviewphase" = "interview",
+                                "(5) Endphase" = "after"
+                                ),
+         time_span = factor(time_span,
+                            levels = c("(1) Pre-Lehrphase",
+                                       "(2) Lehrphase",
+                                       "(3) Post-Lehrphase",
+                                       "(4) Interviewphase",
+                                       "(5) Endphase"
+                                       )
+                            )
+         ) %>%
+  distinct() %>% 
+  group_by(time_span) %>%
+  summarise_at(vars(heart_rate),
+               list(mean_hr = mean,
+                    sd_hr = sd)
+               ) %>% 
+  as.data.frame()
+
+# plotting
+plot_mean_sd <- 
+  ggplot(df_plot_mean, 
+         aes(x = time_span, y = mean_hr)) + 
+  geom_point(size = 5,
+             colour = "red")+
+  geom_errorbar(aes(ymin = mean_hr - sd_hr, 
+                    ymax = mean_hr + sd_hr), 
+                width=.2,
+                position = position_dodge(0.05)) + 
+  scale_y_continuous(breaks = seq(0, 160, 10)) +
+  labs(x = "",
+       y = "Herzrate (in Schlägen pro Minute)") +
+  ggtitle("Herzrate (M, SD) in unterschiedlichen Phasen") +
+  theme_apa() + 
+  theme(text = element_text(family = "sans"),
+        legend.text = element_text(size = 20),
+        legend.title = element_blank(),
+        axis.title.x = element_text(size = 15),
+        axis.title.y = element_text(size = 15),
+        axis.text.x = element_text(size = 11, colour = "black"),
+        axis.text.y = element_text(size = 11),
+        strip.text = element_text(size = 15),
+        plot.title = element_text(size = 20, 
+                                  face = "bold"))
+plot_mean_sd
+
+# saving plot 
+ggsave(plot = plot_mean_sd,
+       filename = "plots/plot_mean_sd.svg",
+       height = 5,
+       width = 8,
+       units = "in")
 

### 2023-02-17 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
plots fitbit

@@
 
-The sample consisted in total of \emph{N} = 63 pre- and in-service teachers.
+The sample consisted in total of \emph{N} = 72 pre- and in-service teachers.
 The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
-Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 61 subjects.
+Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 70 subjects.
 
-The subjects (39 women; 63.93 \%) had a mean age of 29.60 years (\emph{SD} = 10.40; range: 19-59) and an average teaching experience of 4.66 years (\emph{SD} = 9.30; range: 0-37).
+The subjects (42 women; 60 \%) had a mean age of 29.70 years (\emph{SD} = 10.70; range: 19-59) and an average teaching experience of 4.84 years (\emph{SD} = 9.31; range: 0-37).
 
-18.03\% of the subjects were (studying to become) teachers for primary school, 72.13\% were (studying to become) teachers for secondary school and 9.84\% were (studying to become) teachers for special education needs.
+17.14\% of the subjects were (studying to become) teachers for primary school, 70\% were (studying to become) teachers for secondary school and 11.43\% were (studying to become) teachers for special education needs.
 
@@
 We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.36; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression).
+al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Version 2.2.9; Revelle, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.36; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression).
 Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}.
@@
 
-Teachers' average heart rate during the entire course of the study was approximately 96.26 bpm with a standard deviation of 14.22 and a range from 56 to 139 bpm.
+Teachers' average heart rate during the entire course of the study was approximately 96.84 bpm with a standard deviation of 14.44 and a range from 56 to 139 bpm.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-psych}{}}%
+Revelle, W.
+(2022).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-ltm}{}}%

### 2023-02-18 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
fitbit plots

@@
   geom_smooth(se = FALSE,
-              size = 1,
-              colour = "red") +
+              size = 0.5,
+              colour = "black") +
   scale_color_viridis_d(option = "A",
@@
   ggtitle("Gesamtverlauf Herzrate in unterschiedlichen Phasen") +
-  theme_apa() + 
   theme(text = element_text(family = "sans"),
@@
         plot.title = element_text(size = 20, 
-                                  face = "bold"))
+                                  face = "bold")) +
+    theme_apa()
+
 loess_plot_overall
@@
          aes(x = time_span, y = mean_hr)) + 
-  geom_point(size = 5,
-             colour = "red")+
+  geom_point(size = 3,
+             colour = "black")+
   geom_errorbar(aes(ymin = mean_hr - sd_hr, 
@@
        y = "Herzrate (in Schlägen pro Minute)") +
-  ggtitle("Herzrate (M, SD) in unterschiedlichen Phasen") +
-  theme_apa() + 
+  ggtitle("Mittlere Herzrate in unterschiedlichen Phasen") +
   theme(text = element_text(family = "sans"),
@@
         axis.title.y = element_text(size = 15),
-        axis.text.x = element_text(size = 11, colour = "black"),
+        axis.text.x = element_text(size = 11, 
+                                   colour = "black"),
         axis.text.y = element_text(size = 11),
@@
         plot.title = element_text(size = 20, 
-                                  face = "bold"))
+                                  face = "bold")) + 
+  theme_apa()
+
 plot_mean_sd

### 2023-02-20 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
upload fitbit
fitbit plot

@@
 title: "Fitbit & ET Glasses - Methods"
-output: html_notebook
+output:
+  pdf_document: default
+  html_document:
+    df_print: paged
 ---
@@
       ggpubr,
-      psych)
+      psych,
+      stargazer,
+      lmtest)
 
@@
 # fitbit data
-source(file = "data.wrangling.R")
-
-# demographic data
-# prepare data (selected from questionnaire data)
-demo.data <- readxl::read_xlsx("./Data/data_empschul_labor_lehrperson.xlsx")
-
-# select relevant columns
-demo.data <- demo.data %>% select(LI02_01_1,
-                                  LI03_01,
-                                  LI04_01,
-                                  LI06_05)
-
-# rename columns
-demo.data <- rename(demo.data, c("ID" = "LI06_05",
-                                  "Gender" = "LI02_01_1",
-                                  "Age" = "LI03_01",
-                                  "Teaching Experience" = "LI04_01"))
-
-# exclude cases with no fitbit data
-demo.data <- demo.data %>% filter(!ID %in% c("126",
-                                             "132",
-                                             )
-                                  )
+# source(file = "data.wrangling.R")
+# 
+# # demographic data
+# # prepare data (selected from questionnaire data)
+# demo.data <- readxl::read_xlsx("./Data/data_empschul_labor_lehrperson.xlsx") 
+# 
+# # select relevant columns
+# demo.data <- demo.data %>% select(LI02_01_1,
+#                                   LI03_01,
+#                                   LI04_01,
+#                                   LI06_05)
+# 
+# # rename columns
+# demo.data <- rename(demo.data, c("ID" = "LI06_05",
+#                                   "Gender" = "LI02_01_1",
+#                                   "Age" = "LI03_01",
+#                                   "Teaching Experience" = "LI04_01"))
+# 
+# # exclude cases with no fitbit data
+# demo.data <- demo.data %>% filter(!ID %in% c("126",
+#                                              "132",
+#                                              )
+#                                   )
 
@@
 ```{r}
-# aggregate data
-
-df_heart_all <-
-  read_rds(file = "data/heart_all.rds") |> 
-  mutate(status = factor(status,
-                         levels = c("Expert","Novice"),
-                         labels = c("Expert","Novice")
-                         )
-         )
-
-df_heart_min <-
-  read_rds(file = "data/heart_min.rds")
-
-df_heart_aggr <- 
-  read_rds(file = "data/heart_aggr.rds") |> 
-  mutate(status = factor(status,
-                         levels = c("Novice","Expert"),
-                         labels = c("Novice","Expert")
-                         )
-         )
-
-# Mean, SD and Cohen D for experts & novices
-# novices
-mean_nov <- 
-  df_heart_aggr %>%
-  filter(status == "Novice" ) %>% 
-  pull(mean) %>% 
-  mean() %>% 
-  round(., digits = 0)
-
-sd_nov <- 
-  df_heart_aggr %>%
-  filter(status == "Novice") %>% 
-  pull(mean) %>% 
-  sd() %>% 
-  round(., digits = 0)
-
-# experts
-mean_exp <-
-  df_heart_aggr %>%
-  filter(status == "Expert") %>% 
-  pull(mean) %>% 
-  mean() %>% 
-  round(., digits = 0)
-
-sd_exp <- 
-  df_heart_aggr %>%
-  filter(status == "Expert") %>% 
-  pull(mean) %>% 
-  sd() %>% 
-  round(., digits = 0)
-
-# effect size for expertise differences
-d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
-               y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
-               na.rm = TRUE)
+# # aggregate data 
+# 
+# df_heart_all <-
+#   read_rds(file = "data/heart_all.rds") |> 
+#   mutate(status = factor(status,
+#                          levels = c("Expert","Novice"),
+#                          labels = c("Expert","Novice")
+#                          )
+#          )
+# 
+# df_heart_min <-
+#   read_rds(file = "data/heart_min.rds")
+# 
+# df_heart_aggr <- 
+#   read_rds(file = "data/heart_aggr.rds") |> 
+#   mutate(status = factor(status,
+#                          levels = c("Novice","Expert"),
+#                          labels = c("Novice","Expert")
+#                          )
+#          )
+# 
+# 
+# # Mean, SD and Cohen D for experts & novices
+# # novices
+# mean_nov <- 
+#   df_heart_aggr %>%
+#   filter(status == "Novice" ) %>% 
+#   pull(mean) %>% 
+#   mean() %>% 
+#   round(., digits = 0)
+# 
+# sd_nov <- 
+#   df_heart_aggr %>%
+#   filter(status == "Novice") %>% 
+#   pull(mean) %>% 
+#   sd() %>% 
+#   round(., digits = 0)
+# 
+# # experts
+# mean_exp <-
+#   df_heart_aggr %>%
+#   filter(status == "Expert") %>% 
+#   pull(mean) %>% 
+#   mean() %>% 
+#   round(., digits = 0)
+# 
+# sd_exp <- 
+#   df_heart_aggr %>%
+#   filter(status == "Expert") %>% 
+#   pull(mean) %>% 
+#   sd() %>% 
+#   round(., digits = 0)
+# 
+# # effect size for expertise differences
+# d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
+#                y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
+#                na.rm = TRUE)
 
@@
 ```{r}
-# Plots
-
-############## FLOW PLOT #############
-plot_flow <-
-ggplot(data = df_heart_all,
-       mapping = aes(x = as.numeric(Time),
-                     y = `Heart Rate`,
-                     group = ID)
-       ) +
-  geom_line(mapping = aes(color = status),
-            size = 0.3,
-            alpha = 1
-            ) +
-  xlim(0, 600) +
-  scale_color_viridis_d(option = "A",
-                       end = 0.8)  +
-  scale_linetype_manual(values = c(1, 6)) +
-  labs(x = "Time (in Seconds)",
-       y = "Heart Rate\n(in Beats per Minute)") +
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        legend.position = "none",
-        strip.text = element_text(size = 16)) +
-  facet_grid(cols = vars(Type),
-             scales = "free_x")
-
-############### FLOW PLOT EXPERT NOVICE #############
-
-plot_flow_leg <-
-ggplot(data = df_heart_all,
-       mapping = aes(x = Time,
-                     y = `Heart Rate`
-                     )
-       ) +
-  xlim(0, 600) +
-  geom_smooth(mapping = aes(color = status),
-              method = "loess") +
-  scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  labs(x = "Time (in Seconds)",
-       y = "Heart Rate\n(in Beats per Minute)") +
-  ggtitle("Experts' and novices' heart rate per phase") +
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        legend.text = element_text(size = 15),
-        legend.title = element_blank(),
-        axis.text.x = element_text(size = 12),
-        axis.text.y = element_text(size = 10),
-        strip.text = element_text(size = 16),
-        plot.title = element_text(size = 20, 
-                                  face = "bold")) +
-  facet_grid(cols = vars(Type),
-             scales = "free_x")
-
-legend <- cowplot::get_legend(plot_flow_leg)
-
-# saving plot 
-ggsave(plot = plot_flow_leg,
-       filename = "Plots/plot_flow_leg.svg",
-       height = 5,
-       width = 8,
-       units = "in")
-
-############### LOESS PLOT #############
-
-plot_loess <-
-ggplot(data = filter(df_heart_all),
-       mapping = aes(x = as.numeric(Time),
-                     y = `Heart Rate`
-                     )
-       ) +
-  stat_smooth(geom = "line",
-              mapping = aes(color = status),
-              method = "loess",
-              se = FALSE) +
-  xlim(0,600) +
-  scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  labs(x = "Time (in Seconds)",
-       y = "Heart Rate\n(in Beats per Minute)") +
-  theme_minimal() +
-  facet_grid(cols = vars(Type),
-             scales = "free_x",
-             ) +
-  theme(text = element_text(family = "serif"),
-        legend.position = "none",
-        strip.background = element_blank(),
-        strip.text.x = element_blank()
-        )
-
-############### BOX PLOT #############
-
-##### Box 1 Plot ##### 
-plot_box1 <- 
-ggplot(data = df_heart_aggr,
-       mapping = aes(x = Type,
-                     y = mean,
-                     color = status
-                     )
-       ) +
-  geom_boxplot(color = "darkgrey",
-               fill = "grey") +
-  geom_line(data = filter(df_heart_aggr,
-                          status == "Novice"),
-            mapping = aes(x = Type,
-                          y = mean,
-                          group = as_factor(ID)
-                          ),
-            linetype = 1,
-            alpha = 0.5
-            ) +
-  geom_line(data = filter(df_heart_aggr,
-                          status == "Expert"),
-            mapping = aes(x = Type,
-                          y = mean,
-                          group = as_factor(ID)
-                          ),
-            linetype = 6,
-            alpha = 0.5
-            ) +
-  geom_point(size = 2,
-             alpha = 0.5) +
-  labs(x = "",
-       y = "Average Heart Rate\n(in Beats per Minute)") +
-  scale_color_viridis_d(option = "A",
-                       end = 0.8) +
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        strip.text = element_blank(),
-        legend.position = "none",
-        axis.text.x = element_blank()
-        ) +
-  aes(fill = Type)
-
-plot_box1
-
-##### Box 2 Plot ##### 
-plot_box <-
-  ggplot(data = df_heart_aggr,
-         mapping = aes(x = Type,
-                       y = mean)) + 
-  geom_boxplot(mapping = aes(fill = status),
-               outlier.shape = NA) +
-  geom_point(mapping = aes(shape = status),
-             alpha = 0.5,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  labs(x ="",
-       y = "Average Heart Rate\n(in Beats per Minute)") + 
-  ggtitle("Experts' and novices' heart rate per phase") +
-  scale_fill_brewer(palette  = "RdBu") +  
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        legend.text = element_text(size = 15),
-        legend.title = element_blank(),
-        axis.text.x = element_text(size = 12),
-        axis.text.y = element_text(size = 10),
-        strip.text = element_text(size = 16),
-        plot.title = element_text(size = 20, 
-                                  face = "bold"))
-
-plot_box
-
-# saving plot 
-ggsave(plot = plot_box,
-       filename = "Plots/plot_box.svg",
-       height = 5,
-       width = 8,
-       units = "in")
+# # Plots
+# 
+# ############## FLOW PLOT #############
+# plot_flow <-
+# ggplot(data = df_heart_all,
+#        mapping = aes(x = as.numeric(Time),
+#                      y = `Heart Rate`,
+#                      group = ID)
+#        ) +
+#   geom_line(mapping = aes(color = status),
+#             size = 0.3,
+#             alpha = 1
+#             ) +
+#   xlim(0, 600) +
+#   scale_color_viridis_d(option = "A",
+#                        end = 0.8)  +
+#   scale_linetype_manual(values = c(1, 6)) +
+#   labs(x = "Time (in Seconds)",
+#        y = "Heart Rate\n(in Beats per Minute)") +
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         legend.position = "none",
+#         strip.text = element_text(size = 16)) +
+#   facet_grid(cols = vars(Type),
+#              scales = "free_x")
+# 
+# ############### FLOW PLOT EXPERT NOVICE #############
+# 
+# plot_flow_leg <-
+# ggplot(data = df_heart_all,
+#        mapping = aes(x = Time,
+#                      y = `Heart Rate`
+#                      )
+#        ) +
+#   xlim(0, 600) +
+#   geom_smooth(mapping = aes(color = status),
+#               method = "loess") +
+#   scale_color_viridis_d(option = "A",
+#                         end = 0.8) +
+#   scale_linetype_manual(values = c(1, 6)) +
+#   labs(x = "Time (in Seconds)",
+#        y = "Heart Rate\n(in Beats per Minute)") +
+#   ggtitle("Experts' and novices' heart rate per phase") +
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_blank(),
+#         axis.text.x = element_text(size = 12),
+#         axis.text.y = element_text(size = 10),
+#         strip.text = element_text(size = 16),
+#         plot.title = element_text(size = 20, 
+#                                   face = "bold")) +
+#   facet_grid(cols = vars(Type),
+#              scales = "free_x")
+# 
+# legend <- cowplot::get_legend(plot_flow_leg)
+# 
+# # saving plot 
+# ggsave(plot = plot_flow_leg,
+#        filename = "Plots/plot_flow_leg.svg",
+#        height = 5,
+#        width = 8,
+#        units = "in")
+# 
+# ############### LOESS PLOT #############
+# 
+# plot_loess <-
+# ggplot(data = filter(df_heart_all),
+#        mapping = aes(x = as.numeric(Time),
+#                      y = `Heart Rate`
+#                      )
+#        ) +
+#   stat_smooth(geom = "line",
+#               mapping = aes(color = status),
+#               method = "loess",
+#               se = FALSE) +
+#   xlim(0,600) +
+#   scale_color_viridis_d(option = "A",
+#                         end = 0.8) +
+#   scale_linetype_manual(values = c(1, 6)) +
+#   labs(x = "Time (in Seconds)",
+#        y = "Heart Rate\n(in Beats per Minute)") +
+#   theme_minimal() +
+#   facet_grid(cols = vars(Type),
+#              scales = "free_x",
+#              ) +
+#   theme(text = element_text(family = "serif"),
+#         legend.position = "none",
+#         strip.background = element_blank(),
+#         strip.text.x = element_blank()
+#         )
+# 
+# 
+# ############### BOX PLOT #############
+# 
+# ##### Box 1 Plot ##### 
+# plot_box1 <- 
+# ggplot(data = df_heart_aggr,
+#        mapping = aes(x = Type,
+#                      y = mean,
+#                      color = status
+#                      )
+#        ) +
+#   geom_boxplot(color = "darkgrey",
+#                fill = "grey") +
+#   geom_line(data = filter(df_heart_aggr,
+#                           status == "Novice"),
+#             mapping = aes(x = Type,
+#                           y = mean,
+#                           group = as_factor(ID)
+#                           ),
+#             linetype = 1,
+#             alpha = 0.5
+#             ) +
+#   geom_line(data = filter(df_heart_aggr,
+#                           status == "Expert"),
+#             mapping = aes(x = Type,
+#                           y = mean,
+#                           group = as_factor(ID)
+#                           ),
+#             linetype = 6,
+#             alpha = 0.5
+#             ) +
+#   geom_point(size = 2,
+#              alpha = 0.5) +
+#   labs(x = "",
+#        y = "Average Heart Rate\n(in Beats per Minute)") +
+#   scale_color_viridis_d(option = "A",
+#                        end = 0.8) +
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         strip.text = element_blank(),
+#         legend.position = "none",
+#         axis.text.x = element_blank()
+#         ) +
+#   aes(fill = Type)
+# 
+# plot_box1
+# 
+# ##### Box 2 Plot ##### 
+# plot_box <-
+#   ggplot(data = df_heart_aggr,
+#          mapping = aes(x = Type,
+#                        y = mean)) + 
+#   geom_boxplot(mapping = aes(fill = status),
+#                outlier.shape = NA) +
+#   geom_point(mapping = aes(shape = status),
+#              alpha = 0.5,
+#              position = position_jitter(seed = 1,
+#                                         width = 0.1,
+#                                         height = 0.1)) +
+#   labs(x ="",
+#        y = "Average Heart Rate\n(in Beats per Minute)") + 
+#   ggtitle("Experts' and novices' heart rate per phase") +
+#   scale_fill_brewer(palette  = "RdBu") +  
+#   theme_minimal() +
+#   theme(text = element_text(family = "serif"),
+#         legend.text = element_text(size = 15),
+#         legend.title = element_blank(),
+#         axis.text.x = element_text(size = 12),
+#         axis.text.y = element_text(size = 10),
+#         strip.text = element_text(size = 16),
+#         plot.title = element_text(size = 20, 
+#                                   face = "bold"))
+# 
+# plot_box
+# 
+# # saving plot 
+# ggsave(plot = plot_box,
+#        filename = "Plots/plot_box.svg",
+#        height = 5,
+#        width = 8,
+#        units = "in")
 
@@
                   p.adjust="holm")
+pwc
 
@@
 effect_size_anova <-
-  sqrt(0.3413791   /(1-0.3413791   ))
+  round(sqrt(0.3413791   /(1-0.3413791   )), 2)
 
@@
 
+# modell rechnen
 modell <-   lm(mean_hr ~ mean_confi + mean_disrup + mean_te, 
@@
 
-cor(df_lm_subset)
+# robuste Standardfehler 
+coeftest(modell, vcov = vcovHC(modell, type = "HC3"))
+
+# standardisierten Koeffizienten
+zmodell <- lm(scale(mean_hr) ~ scale(mean_confi) + scale (mean_disrup) + scale(mean_te), 
+              data = df_lm_subset)
+summary(zmodell)
+
+# cor(df_lm_subset)
 
 ```
-
-## Steps
-
-Using the FitBit we could also measure the steps a person walked. Unfortunately, the measurement was not as reliable as hoped. To confirm, we should simulate situations with a fixed number of steps.
-
-```{r}
-df_steps <- read_rds(file = "final_data/steps.rds")
-set.seed(5678)
-ggplot(data = df_steps,
-       mapping = aes(x = type,
-                     y = Steps
-                     )
-       ) +
-  geom_boxplot(mapping = aes(color = type),
-               fill = "grey",
-               alpha = 0.6) +
-  geom_jitter(mapping = aes(color = type),
-              alpha = 0.9,
-              width = 0.3) + 
-  scale_color_viridis_d(option = "A",
-                       end = 0.8) +
-  labs(x = "",
-       y = "Steps During\nMain Phase") +
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        legend.title = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()
-        )
-
-### Validation of steps 
-# selecting some rows at random with sample_n()
-sample_n(df_steps, 6)
-
-# Output:
-# Experts: 219, 218, 214
-# Novices: 108, 117, 110
-
-```
-
-# Combined Analysis
-
-## Steps and Heart Rate
-
-```{r}
-ggplot(data = df_steps,
-       mapping = aes(x = Steps,
-                     y = mean)
-       ) +
-  geom_point(mapping = aes(shape = type,
-                           color = type),
-             alpha = 0.7,
-             size = 2.5) +
-    geom_smooth(mapping = aes(color = type),
-              method = "lm",
-              se = F) +
-  scale_color_viridis_d(option = "A",
-                       end = 0.8
-                       ) +
-  labs(x = "Steps",
-       y = "Average Heart Rate\n(in Beats per Minute)"
-       ) +
-  theme_minimal() +
-  theme(text = element_text(family = "serif"),
-        legend.title = element_blank(),
-        )
-```
-
-## Heart Rate and Pupil Dilation
-
-```{r}
-df_dil_aggr <- read_rds(file = "final_data/heart_dilation.rds")
-
-df_dil_aggr %>%
-  pivot_longer(cols = contains("dil"),
-               names_to = "left_right",
-               values_to = "Dilation") %>%
-  mutate(type = factor(type,
-                       levels = c("Expert","Novice"),
-                       labels = c("Expert","Novice")
-                       )
-         ) |> 
-  ggplot(mapping = aes(x = heart_rate_z,
-                       y = Dilation)) +
-  geom_point(mapping = aes(color = type),
-             alpha = 0.7) +
-  scale_color_viridis_d(option = "A",
-                       end = 0.8) +
-  geom_smooth(method = "lm",
-              linetype = 2,
-              color = "darkviolet") +
-  labs(x = "Heart Rate\n(z-standardized)") +
-  theme_minimal() +
-  theme(legend.title = element_blank(),
-        text = element_text(family = "serif")) +
-  facet_grid(cols = vars(factor(left_right,
-                                levels = c("dil_left_z","dil_right_z"),
-                                labels = c("Left Eye","Right Eye")
-                                )
-                         )
-             ) 
-```
-
-# Measuring
-
-```{r, warning=FALSE, message=FALSE}
-df_heart_all %>% 
-  clean_names() %>% 
-  pivot_wider(names_from = time,
-              values_from = heart_rate,
-              names_prefix = "x")  %>%
-  select(!contains("x")) ->
-data_cache
-
-df_heart_all %>% 
-  clean_names() %>% 
-  pivot_wider(names_from = time,
-              values_from = heart_rate,
-              names_prefix = "x")  %>%
-  filter(id == "101") %>% 
-  rowwise() %>%
-  na_mean() %>%
-  pivot_longer(cols = contains("x"),
-               names_to = "time",
-               values_to = "heart_rate") %>% 
-  mutate(time = str_remove_all(time, "x")) %>% 
-  ggplot(mapping = aes(x = time,
-                       y = heart_rate
-                       )
-         ) +
-  geom_line()
-
- mutate(id = data_cache$id,
-        ) %>% 
- right_join(x = ., 
-            y = data_cache,
-            by = "id") %>% 
- pivot_longer(cols = contains("x"),
-               names_to = "time",
-               values_to = "heart_rate") %>%
-  mutate(time = str_remove_all(string = time,
-                               pattern = "x"),
-         time = as.numeric(time),
-         heart_rate = as.numeric(heart_rate),
-         id = as_factor(id)) %>%
-  filter(id == "101") %>% 
-  ggplot(mapping = aes(x = time,
-                       y = heart_rate,
-                       group = id)
-       ) + 
-  geom_line(mapping = aes(color = status),
-            size = 0.3,
-            alpha = 1
-            ) +
-  xlim(0, min(df_heart_min$min)) +
-  facet_grid(cols = vars(type))
-
-  df_heart_all_wide
-
-for (i in colnames(df_heart_all_wide)[-1:-4]) {
-
-  df_heart_all_wide %>% 
-    select(i)
-
-}
-df_heart_all_wide %>% 
-  select(contains("x")) %>%
-  as.matrix() %>% 
-  rowwise() %>% 
-  na_kalman() %>% 
-  as_tibble() ->
-  imp
-
-imp$id <- data_cache$id
-
-left_join(data_cache, imp,
-          by = "id") %>% 
-   pivot_longer(cols = contains("x"),
-               names_to = "time",
-               values_to = "heart_rate") %>%
-  filter(id == "101") %>% 
-  ggplot(mapping = aes(x = time,
-                       y = heart_rate,
-                       group = id)
-       ) + 
-  geom_line(mapping = aes(color = status),
-            size = 0.3,
-            alpha = 1
-            )
-
-df_heart_all %>% 
-  clean_names() %>% 
-  pivot_wider(names_from = time,
-              values_from = heart_rate,
-              names_prefix = "x")  %>%
-  filter(id == "101", type == "Post") %>% 
-  select(!c("id","type","status")) %>% 
-  pivot_longer()
-  na_kalman()
-
-imp <- na_kalman(tsAirgap)
-ggplot_na_imputations(tsAirgap, imp)
-
-df_heart_all %>% 
-  clean_names() %>% 
-  pivot_wider(names_from = time,
-              values_from = heart_rate,
-              names_prefix = "x") %>% 
-  pivot_longer(cols = contains("x"),
-               names_to = "time",
-               values_to = "heart_rate") %>% 
-  group_by(id, type) %>% 
-  mutate(heart_rate = na_kalman(heart_rate)) %>% 
-  ungroup() %>% 
-  ggplot(mapping = aes(x = time, 
-                       y = heart_rate,
-                       group = id
-                       )
-         ) +
-  geom_line()
-
-```

### 2023-02-21 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
fitbit plot
plot update

@@
       lme4,
-      viridis)
+      viridis,
+      gridExtra)
 
@@
 
-```{r, fig.height = 8, fig.width = 15}
+```{r, echo=true, fig.height = 8, fig.width = 15}
 
@@
        y = "Herzrate (in Schlägen pro Minute)") +
-  ggtitle("Gesamtverlauf Herzrate in unterschiedlichen Phasen") +
+  ggtitle("Gesamtverlauf der durchschnittlichen Herzraten") +
   theme(text = element_text(family = "sans"),
@@
 loess_plot_overall
+
+lm_plot_phases <-
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("pre","main","subsequent","interview","after"),
+                            labels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase"))) %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(method = "lm",
+              se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  # scale_x_continuous(expand = c(0, NA),
+  #                    breaks = seq(0, 9000, 600)) +
+  #scale_y_continuous(breaks = seq(0, 160, 5)) + 
+  labs(x = "Zeit (in Sekunden)",
+       y = "Durchschnittliche Herzrate (in Schlägen pro Minute)") +
+  ggtitle("Verlauf der durchschnittlichen Herzraten in unterschiedlichen Phasen\n(Lineare Schätzung)") +
+  theme(text = element_text(family = "sans"),
+        legend.text = element_text(size = 20),
+        legend.title = element_blank(),
+        axis.title.x = element_text(size = 15),
+        axis.title.y = element_text(size = 15),
+        axis.text.x = element_text(size = 11),
+        axis.text.y = element_text(size = 11),
+        strip.text = element_text(size = 15),
+        plot.title = element_text(size = 20, 
+                                  face = "bold")) +
+    theme_apa() +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x")
+
+grid.arrange(loess_plot_overall, lm_plot_phases,
+             ncol = 1)
 
@@
        filename = "plots/plot_mean_sd.svg",
-       height = 5,
-       width = 8,
+       height = 4,
+       width = 9,
        units = "in")

### 2023-02-21 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
update references

@@
       stargazer,
-      lmtest)
+      lmtest,
+      sandwich,
+      car)
 
@@
 
+# Voraussetzungen:
+# metrische AV
+# 0 Linearität --> nicht gegeben
+
+# 1 Normalverteilung Residuen = Unterschied zwischen geschätztem Wert der AV und beobachtetem Wert der AV
+plot(modell, 2)
+
+# 2a Homoskedastizität = gleichmäißge Streuung der Residuen
+plot(modell, 1) # Hetereoskedastizität, da Residuen nicht gleichmäßig streuen --> verzerrte Standardfehler
+bptest(modell) # Breusch-Pagan test --> Homoskedastizität liegt vor, da p-Wert unter 0.05; Nullhypothese wird nicht verworfen
+
+# 2b Autokorrelation = Residuen korrelieren miteinander
+# nicht erfüllt, da Wellenlinien bei Plot
+
+# keine Multikollinearität = starke Korrelation der UVs = UV messen das Gleiche
+vif(modell) # konservativ: unter 10 --> check
+
+# 4 keine einflussreiche Fälle (Ausreißer)
+plot(modell, 4)
+
 # robuste Standardfehler 
@@
 
-# standardisierten Koeffizienten
+# standardisierte Koeffizienten
 zmodell <- lm(scale(mean_hr) ~ scale(mean_confi) + scale (mean_disrup) + scale(mean_te), 

### 2023-02-22 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
add standardisierung

@@
 
+main %>% 
+  select("time", "heart_rate", "ID", "time_span") %>% 
+  distinct() %>% 
+  filter(time_span == "overall") %>% 
+  group_by(ID) %>% 
+  summarize(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart) -> main
+
 # data wrangling - preparing data for anova

### 2023-02-22 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
add standardisierung

@@
             by = "ID")
+
+main %>% 
+  select("time", "heart_rate", "ID", "time_span") %>% 
+  distinct() %>% 
+  filter(time_span == "overall") %>% 
+  group_by(ID) %>% 
+  summarize(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart) -> main
 ```
@@
 
+```
+
+## Plot für Gesamtverlauf (STD)
+
+```{r}
+  loess_plot_overall <-
+  main %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0, NA),
+                     breaks = seq(0, 9000, 600)) +
+  scale_y_continuous(breaks = seq(0, 160, 5)) + 
+  labs(x = "Zeit (in Sekunden)",
+       y = "Herzrate (in Schlägen pro Minute)") +
+  ggtitle("Gesamtverlauf der durchschnittlichen Herzraten") +
+  theme(text = element_text(family = "sans"),
+        legend.text = element_text(size = 20),
+        legend.title = element_blank(),
+        axis.title.x = element_text(size = 15),
+        axis.title.y = element_text(size = 15),
+        axis.text.x = element_text(size = 11),
+        axis.text.y = element_text(size = 11),
+        strip.text = element_text(size = 15),
+        plot.title = element_text(size = 20, 
+                                  face = "bold")) +
+    theme_apa()
+
+loess_plot_overall
+
+lm_plot_phases <-
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("pre","main","subsequent","interview","after"),
+                            labels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase"))) %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(method = "lm",
+              se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  # scale_x_continuous(expand = c(0, NA),
+  #                    breaks = seq(0, 9000, 600)) +
+  #scale_y_continuous(breaks = seq(0, 160, 5)) + 
+  labs(x = "Zeit (in Sekunden)",
+       y = "Durchschnittliche Herzrate (in Schlägen pro Minute)") +
+  ggtitle("Verlauf der durchschnittlichen Herzraten in unterschiedlichen Phasen\n(Lineare Schätzung)") +
+  theme(text = element_text(family = "sans"),
+        legend.text = element_text(size = 20),
+        legend.title = element_blank(),
+        axis.title.x = element_text(size = 15),
+        axis.title.y = element_text(size = 15),
+        axis.text.x = element_text(size = 11),
+        axis.text.y = element_text(size = 11),
+        strip.text = element_text(size = 15),
+        plot.title = element_text(size = 20, 
+                                  face = "bold")) +
+    theme_apa() +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x")
+
+grid.arrange(loess_plot_overall, lm_plot_phases,
+             ncol = 1)
 ```

### 2023-02-22 02_paper/02_study/02_fitbit paper/presentation_analysis_std.Rmd
add standardisierung

---
title: "Presentation_Analysis_std"
output: html_notebook
---

### 2023-02-22 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
fitbit anova + lm mit mean_hr_std

@@
          "time_span",
-         "heart_rate",
+         "heart_rate_std",
          "teaching_experience",
@@
   group_by(ID, time_span) %>%
-  summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
+  summarise(mean_hr_std = mean(heart_rate_std, na.rm = TRUE),
             mean_confi = mean(confidence_factor, na.rm = TRUE),
@@
 # descriptive analysis
-describeBy(df_anova$mean_hr,
+describeBy(df_anova$mean_hr_std,
            df_anova$time_span)
@@
 # Visualization
-bxp <- ggboxplot(df_anova, x = "time_span", y = "mean_hr", add = "point")
+bxp <- ggboxplot(df_anova, x = "time_span", y = "mean_hr_std", add = "point")
 bxp
@@
   group_by(time_span) %>%
-  identify_outliers(mean_hr)
+  identify_outliers(mean_hr_std)
 
@@
 plot <- 
-  ggqqplot(df_anova, "mean_hr", facet.by = "time_span")
+  ggqqplot(df_anova, "mean_hr_std", facet.by = "time_span")
 
-df_anova_subset <- subset(df_anova, select = c(time_span, mean_hr))
+df_anova_subset <- subset(df_anova, select = c(time_span, mean_hr_std))
 
@@
 df_anova_phase <- 
-  aov(df_anova_subset$mean_hr~df_anova_subset$time_span)
+  aov(df_anova_subset$mean_hr_std ~ df_anova_subset$time_span)
 summary(df_anova_phase)
@@
 pwc <- 
-  pairwise.t.test(df_anova_subset$mean_hr, 
+  pairwise.t.test(df_anova_subset$mean_hr_std, 
                   df_anova_subset$time_span, 
@@
 effect_size_anova <-
-  round(sqrt(0.3413791   /(1-0.3413791   )), 2)
+  round(sqrt(0.6533274/(1-0.6533274)), 2)
 
@@
   df_anova_subset %>%
-  cohens_d(mean_hr~time_span) %>% 
+  cohens_d(mean_hr_std ~ time_span) %>% 
   as.data.frame()
@@
   filter(time_span == "Lehrphase") %>% 
-  dplyr::select(mean_hr, 
+  dplyr::select(mean_hr_std, 
                mean_disrup, 
@@
 # modell rechnen
-modell <-   lm(mean_hr ~ mean_confi + mean_disrup + mean_te, 
+modell <-   lm(mean_hr_std ~ mean_confi + mean_disrup + mean_te, 
                data = df_lm_subset,
@@
 # standardisierte Koeffizienten
-zmodell <- lm(scale(mean_hr) ~ scale(mean_confi) + scale (mean_disrup) + scale(mean_te), 
+zmodell <- lm(scale(mean_hr_std) ~ scale(mean_confi) + scale (mean_disrup) + scale(mean_te), 
               data = df_lm_subset)

### 2023-02-22 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
plot bla

@@
 main %>% 
-  select("time", "heart_rate", "ID", "time_span") %>% 
+  dplyr::select("time", 
+                "heart_rate", 
+                "ID",
+                "time_span",
+                "teaching_experience",
+                "disruption_factor",
+                "confidence_factor") %>% 
   distinct() %>% 
-  filter(time_span == "overall") %>% 
+  # filter(time_span == "overall") %>% 
+  group_by(ID) %>% 
+  summarize(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart) -> main
+
+# data wrangling - preparing data for anova
+df_anova <-
+  main %>% 
+  filter(time_span != "overall") %>%   
+  dplyr::select("ID",
+         "time_span",
+         "heart_rate",
+         "teaching_experience",
+         "disruption_factor",
+         "confidence_factor") %>% 
+  mutate(time_span = fct_recode(time_span,
+                                "Pre-Lehrphase" = "pre",
+                                "Lehrphase" = "main",
+                                "Post-Lehrphase" = "subsequent",
+                                "Interviewphase" = "interview",
+                                "Endphase" = "after"
+                                ),
+         time_span = factor(time_span,
+                            levels = c("Pre-Lehrphase",
+                                       "Lehrphase",
+                                       "Post-Lehrphase",
+                                       "Interviewphase",
+                                       "Endphase"
+                                       )
+                            )
+         ) %>%
+  distinct() %>% 
+  group_by(ID, time_span) %>%
+  summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
+            mean_confi = mean(confidence_factor, na.rm = TRUE),
+            mean_disrup = mean(disruption_factor, na.rm = TRUE),
+            mean_te = mean(teaching_experience, na.rm = TRUE)
+         )
+
+# counting participants in individual phases
+table(df_anova['time_span'])
+
+# descriptive analysis
+describeBy(df_anova$mean_hr,
+           df_anova$time_span)
+
+# # merge demo data and fitbit data
+# df_anova <- merge(df_anova,
+#                   df_heart_aggr,
+#                   by="ID")
+
+# clean variable names
+# df_anova <- df_anova %>% clean_names()
+
+# Visualization
+bxp <- ggboxplot(df_anova, x = "time_span", y = "mean_hr", add = "point")
+bxp
+
+# check for outliers
+outliers <-
+  df_anova %>%
+  group_by(time_span) %>%
+  identify_outliers(mean_hr)
+
+# check for normality assumption --> can be checked by computing Shapiro-Wilk test for each time point. If the data is normally distributed, the p-value should be greater than 0.05
+norm_assump <-
+  df_anova %>%
+  group_by(time_span) %>%
+  shapiro_test(mean_hr)
+
+# QQ plot draws the correlation between a given data and the normal distribution. 
+plot <- 
+  ggqqplot(df_anova, "mean_hr", facet.by = "time_span")
+
+df_anova_subset <- subset(df_anova, select = c(time_span, mean_hr))
+
+# # anova
+# res.aov <- rstatix::anova_test(data = df_anova_subset,
+#                                dv = mean_hr,
+#                                wid = ,
+#                                within = time_span)
+# get_anova_table(res.aov)
+
+# anova
+df_anova_phase <- 
+  aov(df_anova_subset$mean_hr ~ df_anova_subset$time_span)
+summary(df_anova_phase)
+
+# pairwise comparisons
+pwc <- 
+  pairwise.t.test(df_anova_subset$mean_hr, 
+                  df_anova_subset$time_span, 
+                  p.adjust="holm")
+pwc
+
+# effect size of ANOVA
+EtaSq(df_anova_phase)
+
+effect_size_anova <-
+  round(sqrt(0.6533274/(1-0.6533274)), 2)
+
+# effect size of pairwise comparisons
+library(dplyr)
+library(rstatix)
+effect_size_pwc <-
+  df_anova_subset %>%
+  cohens_d(mean_hr ~ time_span) %>% 
+  as.data.frame()
+
+# # pairwise comparisons
+# pwc <- df_anova_subset %>%
+#   pairwise_t_test(
+#     mean_hr ~ time_span, paired = TRUE,
+#     p.adjust.method = "bonferroni"
+#     )
+# pwc
+
+# # Visualization: box plots with p-values
+# pwc <- 
+#   pwc %>% 
+#   add_xy_position(x = "time_span")
+# 
+# # boxplot
+# bxp_anova <- ggboxplot(data = df_anova, 
+#                  x = "type", 
+#                  y = "mean", 
+#                  add = "point")
+# 
+# bxp_anova + 
+#   stat_pvalue_manual(pwc) +
+#   labs(
+#     subtitle = get_test_label(res.aov, detailed = TRUE),
+#     caption = get_pwc_label(pwc)
+#     )
+
+# # saving plot 
+# ggsave(plot = bxp_anova,
+#        filename = "Plots/bxp_anova.svg",
+#        height = 5,
+#        width = 8,
+#        units = "in")
+
+```
+
+# Repeated Measures ANOVA (STD)
+
+```{r}
+
+# read in data
+# disruption & confidence rating
+df_rating <- 
+  excel_sheets("data/Coding_SRI.xlsx") %>% 
+  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
+  dplyr::select(ID, # select relevant columns 
+         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
+         confidence_factor,
+         event
+         ) %>% 
+  mutate(disruption_factor = ifelse(disruption_factor < 0,
+                                    yes = NA,
+                                    no = disruption_factor
+                                    ),
+         confidence_factor = ifelse(confidence_factor < 0,
+                                   yes = NA,
+                                   no = confidence_factor),
+         event = as_factor(event)
+         ) %>% 
+  na.omit() 
+  # group_by(ID) %>% 
+  # summarise("mean_disrup" = round(mean(disruption_factor), 2),
+  #           "mean_confi" = round(mean(confidence_factor), 2))
+
+# demographic data
+df_demo <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
+  transmute(ID = LI06_05, # select and rename relevant columns 
+            gender = factor(LI02_01_1,
+                            levels = 1:2,
+                            labels = c("male","female")
+                            ),
+            age = LI03_01, # 1 = male; 2 = female
+            teaching_experience = LI04_01)
+
+# merge two data frames by ID 
+df_merge <- merge(df_demo,
+                  df_rating,
+                  by = "ID") %>% 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132")
+         )
+
+# rm(list = c("df_demo","df_rating"))
+
+data_path <- "./data/heart_rate_data"
+
+main <-
+map(.x = dir(path = data_path,
+             pattern = ".csv"),
+    ~ read_csv(file.path(data_path, .), 
+               id = "id",
+               col_types = c("t","n")
+               ) %>% 
+  mutate(time = .$Time - min(.$Time),
+         time = as.numeric(time),
+         heart_rate = `Heart Rate`,
+         ID = id,
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
+                               str_detect(string = id, pattern = "_m") ~ "main",
+                               str_detect(string = id, pattern = "_p") ~ "pre",
+                               str_detect(string = id, pattern = "_s") ~ "subsequent",
+                               str_detect(string = id, pattern = "_i") ~ "interview",
+                               TRUE ~ "overall"
+                               ),
+         ID = str_extract(string = ID,
+                          pattern = "[:digit:]{3}"),
+         ID = as.numeric(ID)
+      ) %>%
+      # filter(time <= 600) %>% # filter for 10min intervals
+    filter(time <= 9000) %>% # filter for 2 hours 30min (maximal duration of study)
+    dplyr::select(!c("Time","Heart Rate","id"))
+    ) %>%
+  bind_rows()
+
+main <-
+  left_join(main, df_merge,
+            by = "ID")
+
+main %>% 
+  dplyr::select("time", 
+                "heart_rate", 
+                "ID",
+                "time_span",
+                "teaching_experience",
+                "disruption_factor",
+                "confidence_factor") %>% 
+  distinct() %>% 
+  # filter(time_span == "overall") %>% 
   group_by(ID) %>% 
@@
 effect_size_anova <-
-  round(sqrt(0.6533274/(1-0.6533274)), 2)
+  round(sqrt(0.6829502   /(1-0.6829502   )), 2)
 
@@
 ```
+### Multiple Regression
 
-### Multiple Regression
+```{r}
+
+# AV = mittlere Herzrate in teaching phase; UV1 = Störfaktor, UV2 = Sicherheitsfaktor, UV3= Lehrerfahrung
+
+df_lm_subset <- df_anova %>% 
+  filter(time_span == "Lehrphase") %>% 
+  dplyr::select(mean_hr, 
+               mean_disrup, 
+               mean_confi,
+               mean_te)
+
+# modell rechnen
+modell <-   lm(mean_hr ~ mean_confi + mean_disrup + mean_te, 
+               data = df_lm_subset,
+               family = binomial)
+summary(modell)
+
+# Voraussetzungen:
+# metrische AV
+# 0 Linearität --> nicht gegeben
+
+# 1 Normalverteilung Residuen = Unterschied zwischen geschätztem Wert der AV und beobachtetem Wert der AV
+plot(modell, 2)
+
+# 2a Homoskedastizität = gleichmäißge Streuung der Residuen
+plot(modell, 1) # Hetereoskedastizität, da Residuen nicht gleichmäßig streuen --> verzerrte Standardfehler
+bptest(modell) # Breusch-Pagan test --> Homoskedastizität liegt vor, da p-Wert unter 0.05; Nullhypothese wird nicht verworfen
+
+# 2b Autokorrelation = Residuen korrelieren miteinander
+# nicht erfüllt, da Wellenlinien bei Plot
+
+# keine Multikollinearität = starke Korrelation der UVs = UV messen das Gleiche
+vif(modell) # konservativ: unter 10 --> check
+
+# 4 keine einflussreiche Fälle (Ausreißer)
+plot(modell, 4)
+
+# robuste Standardfehler 
+coeftest(modell, vcov = vcovHC(modell, type = "HC3"))
+
+# standardisierte Koeffizienten
+zmodell <- lm(scale(mean_hr) ~ scale(mean_confi) + scale (mean_disrup) + scale(mean_te), 
+              data = df_lm_subset)
+summary(zmodell)
+
+# cor(df_lm_subset)
+
+```
+
+### Multiple Regression (STD)
 

### 2023-02-28 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
b

@@
 # AV = mittlere Herzrate in teaching phase; UV1 = Störfaktor, UV2 = Sicherheitsfaktor, UV3= Lehrerfahrung
-
 df_lm_subset <- df_anova %>% 

### 2023-03-07 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
update fitbit

@@
                ) %>% 
-  mutate(time = .$Time - min(.$Time),
+  dplyr::mutate(time = .$Time - min(.$Time),
          time = as.numeric(time),
@@
              by = "ID") %>% 
-  mutate(heart_rate_std = (heart_rate - mean_heart)/
+  dplyr::mutate(heart_rate_std = (heart_rate - mean_heart)/
            sd_heart) -> main

### 2023-03-07 02_paper/02_study/02_fitbit paper/presentation_analysis_std.Rmd
update paper analysis

@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, warning = FALSE)
+```
+
+# Preps
+
+```{r}
+library(needs)
+needs(ltm,
+      broom,
+      ppcor,
+      jtools,
+      lm.beta,
+      tidyverse,
+      janitor,
+      lubridate,
+      readxl,
+      ggthemes,
+      gridExtra,
+      imputeTS,
+      DescTools,
+      cowplot,
+      rstatix,
+      ggpubr,
+      lme4,
+      viridis,
+      gridExtra,
+      gridtext)
+
+# disruption & confidence rating
+df_rating <- 
+  excel_sheets("data/Coding_SRI.xlsx") %>% 
+  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
+  dplyr::select(ID, # select relevant columns 
+         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
+         confidence_factor,
+         event
+         ) %>% 
+  mutate(disruption_factor = ifelse(disruption_factor < 0,
+                                    yes = NA,
+                                    no = disruption_factor
+                                    ),
+         confidence_factor = ifelse(confidence_factor < 0,
+                                   yes = NA,
+                                   no = confidence_factor),
+         event = as_factor(event)
+         )
+
+# demographic data
+df_demo <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
+  transmute(ID = LI06_05, # select and rename relevant columns 
+            gender = factor(LI02_01_1,
+                            levels = 1:2,
+                            labels = c("male","female")
+                            ),
+            age = LI03_01, # 1 = male; 2 = female
+            teaching_experience = LI04_01)
+
+# merge two data frames by ID 
+df_merge <- merge(df_demo,
+                  df_rating,
+                  by = "ID") %>% 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132")
+         )
+
+# rm(list = c("df_demo","df_rating"))
+
+data_path <- "./data/heart_rate_data"
+
+main <-
+map(.x = dir(path = data_path,
+             pattern = ".csv"),
+    ~ read_csv(file.path(data_path, .), 
+               id = "id",
+               col_types = c("t","n")
+               ) %>% 
+  mutate(time = .$Time - min(.$Time),
+         time = as.numeric(time),
+         heart_rate = `Heart Rate`,
+         ID = id,
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
+                               str_detect(string = id, pattern = "_m") ~ "main",
+                               str_detect(string = id, pattern = "_p") ~ "pre",
+                               str_detect(string = id, pattern = "_s") ~ "subsequent",
+                               str_detect(string = id, pattern = "_i") ~ "interview",
+                               TRUE ~ "overall"
+                               ),
+         ID = str_extract(string = ID,
+                          pattern = "[:digit:]{3}"),
+         ID = as.numeric(ID)
+      ) %>%
+      # filter(time <= 600) %>% # filter for 10min intervals
+    filter(time <= 9000) %>% # filter for 2 hours 30min (maximal duration of study)
+    dplyr::select(!c("Time","Heart Rate","id"))
+    ) %>%
+  bind_rows()
+
+main <-
+  left_join(main, df_merge,
+            by = "ID")
+
+main %>% 
+  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
+  distinct() %>% 
+  # filter(time_span == "overall") %>% 
+  group_by(ID) %>% 
+  summarize(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart) -> main
+```
+
+# Plots
+
+## Phases
+
+```{r}
+loess_plot_overall <-
+  main %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0, NA),
+                     breaks = seq(0, 9000, 600)) +
+  scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
+  labs(x = "Zeit (in Sekunden)",
+       y = "") +
+  ggtitle("Gesamtverlauf der durchschnittlichen Herzraten") +
+  theme_apa() + 
+  theme(axis.title.y = element_blank())
+
+lm_plot_phases <-
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("pre","main","subsequent","interview","after"),
+                            labels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase"))) %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(method = "lm",
+              se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  # scale_x_continuous(expand = c(0, NA),
+  #                    breaks = seq(0, 9000, 600)) +
+  #scale_y_continuous(breaks = seq(0, 160, 5)) + 
+  labs(x = "Zeit (in Sekunden)",
+       y = "") +
+  ggtitle("Verlauf der durchschnittlichen Herzraten in unterschiedlichen Phasen\n(Lineare Schätzung)") +
+  theme_apa() +
+  theme(axis.title.y = element_blank()) +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x")
+
+ki_plot_phases <-
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("pre","main","subsequent","interview","after"),
+                            labels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase"))) %>% 
+  distinct() %>%
+  group_by(time_span) %>% 
+  summarise(z_mean = mean(heart_rate_std),
+            z_sd = sd(heart_rate_std),
+            z_t = qt(p = 0.01 / 2,      # 0.01 KI
+               df = n() - 1,
+               lower.tail = F
+               ),
+            z_error = z_sd / sqrt(n()),
+            lower = z_mean - z_t * z_error,
+            upper = z_mean + z_t * z_error,
+            ) %>% 
+  ungroup() %>% 
+  ggplot(mapping = aes(x = factor(0),
+                       y = z_mean)) + 
+  geom_point() +
+  geom_errorbar(mapping = aes(ymin = lower,
+                              ymax = upper),
+                width = 0.2) +
+  geom_hline(yintercept = 0,
+             linetype = "dashed") +
+  labs(title = "1% Konfidenzintervall für unterschiedliche Phasen",
+       x = "") +
+  facet_grid(cols = vars(time_span)) +
+  theme_apa() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.title.y = element_blank())
+
+text_y <- text_grob("Durchschnittliche Herzrate (Standardisiert)",
+                   rot = 90)
+
+plot_overall <-
+  grid.arrange(loess_plot_overall, lm_plot_phases, ki_plot_phases,
+               ncol = 1,
+               left = text_y
+               )
+
+# saving plot 
+ggsave(plot = plot_overall,
+       filename = "plots/verlauf_plot.svg",
+       height = 10,
+       width = 8,
+       units = "in")
+```
+
+# t-test
+
+```{r}
+heart_rate_split <- 
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("pre","main","subsequent","interview","after"),
+                            labels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase"))) %>% 
+  distinct() %>% 
+  group_by(time_span, ID) %>% 
+  summarise(z.mean = mean(heart_rate_std))
+
+heart_rate_test_t <- 
+  matrix(data = NA,
+         nrow = 5,
+         ncol = 5)
+
+colnames(heart_rate_test_t) <- unique(heart_rate_split$time_span)
+rownames(heart_rate_test_t) <- unique(heart_rate_split$time_span)
+
+for (i in colnames(heart_rate_test_t)) {
+
+  for (j in colnames(heart_rate_test_t)) {
+
+    col <- heart_rate_split %>% 
+      filter(time_span == i)
+
+    row <- heart_rate_split %>% 
+      filter(time_span == j)
+
+    t <- t.test(x = row$z.mean,
+                y = col$z.mean,
+                pairwise = TRUE
+                )
+
+    heart_rate_test_t[i,j] <- round(t$statistic,
+                                    digits = 3)
+
+  }
+
+}
+
+heart_rate_test_p <- 
+  matrix(data = NA,
+         nrow = 5,
+         ncol = 5)
+
+colnames(heart_rate_test_p) <- unique(heart_rate_split$time_span)
+rownames(heart_rate_test_p) <- unique(heart_rate_split$time_span)
+
+for (i in colnames(heart_rate_test_p)) {
+
+  for (j in colnames(heart_rate_test_p)) {
+
+    col <- heart_rate_split %>% 
+      filter(time_span == i)
+
+    row <- heart_rate_split %>% 
+      filter(time_span == j)
+
+    t <- t.test(x = row$z.mean,
+                y = col$z.mean,
+                pairwise = TRUE
+                )
+
+    heart_rate_test_p[i,j] <- round(t$p.value,
+                                    digits = 3)
+
+  }
+
+}
+
+```
+
+# Regression
+
+## Prep
+
+```{r}
+heart_rate_regression_data <-   
+  main %>% 
+  group_by(ID) %>% 
+  mutate(disruption_factor = mean(disruption_factor, na.rm = TRUE),
+         confidence_factor = mean(confidence_factor, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  select("disruption_factor","confidence_factor","ID","teaching_experience") %>% 
+  distinct()
+
+heart_rate_regression <-   
+  main %>% 
+  group_by(ID) %>% 
+  mutate(disruption_factor = mean(disruption_factor, na.rm = TRUE),
+         confidence_factor = mean(confidence_factor, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std","disruption_factor","confidence_factor") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("pre","main","subsequent","interview","after"),
+                            labels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase")),
+         ID = factor(ID)) %>% 
+  distinct() %>% 
+  mutate(time = time / 60) %>% 
+  split(.$time_span) %>% 
+  map(~ lm(formula = heart_rate_std ~ time * ID,
+           data = .)) %>% 
+  map(~ .$coefficients %>% 
+        tibble(ID = names(.),
+               value = .
+               ) %>% 
+        filter(str_detect(string = ID,
+                          pattern = "time"
+                          )
+               ) %>% 
+        mutate(ID = if_else(ID == "time",
+                              true = "101",
+                              false = ID),
+               ID = str_extract_all(string = ID,
+                                      pattern = "[0-9]+"),
+               ID = unlist(ID),
+               ID = as.numeric(ID)
+               )
+      ) %>% 
+  bind_rows(., .id = "time_span") %>% 
+   left_join(x = .,
+             y = heart_rate_regression_data,
+             by = "ID")
+```
+
+## Plots
+
+```{r}
+heart_rate_regression %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase")
+                            )
+         ) %>% 
+  ggplot(mapping = aes(x = disruption_factor,
+                       y = value
+                       )
+         ) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(title = "Lineare Regression",
+       subtitle = "Disruption Faktor",
+       x = "Disruption Faktor",
+       y = "Anstieg") +
+  theme_apa() +
+  facet_grid(cols = vars(time_span))
+
+heart_rate_regression %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase")
+                            )
+         ) %>% 
+  ggplot(mapping = aes(x = confidence_factor,
+                       y = value
+                       )
+         ) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(title = "Lineare Regression",
+       subtitle = "Konfidenz Faktor",
+       x = "Konfidenz Faktor",
+       y = "Anstieg") +
+  theme_apa() +
+  facet_grid(cols = vars(time_span))
+```
+
+## Regression
+
+```{r}
+heart_rate_regression %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase")
+                            )
+         ) %>% 
+  split(.$time_span) %>% 
+  map(~ lm(data = .,
+      formula = value ~ disruption_factor + confidence_factor + teaching_experience)) %>% 
+  stargazer::stargazer(type = "latex",
+                       column.labels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase"),
+                       dep.var.labels = "Slope",
+                       covariate.labels = c("Disruption Faktor","Konfidenz Faktor","Lehrerfahrung"),
+                       intercept.bottom = F,
+                       intercept.top = T,
+                       )
+```

### 2023-03-28 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_heckling_alternatives.Rmd
action alternatives

---
title: "Professional vision - link between eye tracking parameters and the ability
  to generate action alternatives"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# Load packages and read in data
```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot)

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

### EYE TRACKING DATA

# return a character vector with names of .tsv data in data folder
file_names <- list.files(path = "data",
                         pattern = "interval_complete.tsv")

# read every object names in file_names and save it as a tibble
for (i in file_names) {

  work_data <- 
    read_tsv(file = paste0("data/", i),
             locale = locale(decimal_mark = ","))

  assign(value = work_data,
         x = str_remove(paste0("tib_", i),
                        pattern = ".tsv"
         )
  )

}

# Bind every tibble that contains "interval_complete" to a new tible
df_aoi <- 
  mget(ls(pattern = "interval_complete")) %>%
  bind_rows()

# Remove temporary data for a cleaner workspace
rm(list = ls(pattern = "^tib_ProVisio"))
rm(work_data)
rm(file_names)
rm(i)

### TIME TO FIRST FIXATION 
df_aoi %>% 
  filter(TOI == "Chatting_with_neighbour") %>% 
  select (Participant, 
          "Time_to_first_fixation.Disruptive_Person") %>% 
  rowwise() %>% 
  mutate(ID = str_extract(string = Participant,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)

         # Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000,digits = 2)#changing milliseconds into seconds
         ) %>% 
  select(ID,
         Time_to_first_fixation.Disruptive_Person) %>% 
  janitor::clean_names() -> df_ttff_disrup
  # filter(!ID %in% c(204))

# df_ttff_disrup$id = ifelse(df_ttff_disrup$id < 200, "Novice","Expert")

# SELF-REPORT DATA
df_sri <- 
  excel_sheets("data/coding_sri.xlsx") %>% 
  map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
  dplyr::select(ID, Event, `Confidence Factor`) %>% 
  filter(
    # ID %in% c(101:125, 202:217),
         Event %in% c("chatting")) %>%
  janitor::clean_names()

# df_sri$id = ifelse(df_sri$id < 200, "Novice","Expert")

# ACTION ALTERNATIVES
df_alternatives <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  janitor::clean_names()

# df_alternatives$id = ifelse(df_alternatives$id < 200, "Novice","Expert")

# merge data frames
# put all data frames into list
df_list <- list(df_ttff_disrup, df_sri, df_alternatives)

# merge all data frames in list
main <-
  df_list %>% reduce(full_join, by='ID') %>%
  janitor::clean_names() %>%
  select(!event) %>% # select relevant columns
  na.omit()

main$id = ifelse(main$id < 200, "Novice","Expert")

```

# Descriptives: Mean & SDs
```{r}
main %>%
  distinct() %>%
  group_by(id) %>%
  summarize(mean_ttff = round(mean(time_to_first_fixation_disruptive_person), digits = 0),
            sd_ttff = round(sd(time_to_first_fixation_disruptive_person), digits = 0),
            mean_sri = round(mean(confidence_factor), digits = 0),
            sd_sri = round(sd(confidence_factor), digits = 0),
            mean_aa_count = round(mean(count), digits = 0),
            sd_aa_count = round(sd(count), digits = 0),
            mean_aa_code = round(mean(code), digits = 0),
            sd_aa_code = round(sd(code), digits = 0)) %>%
  ungroup() -> df_descriptives
```

# t-test and effect size

```{r}
### time to first fixation on disruptive person
# t-test for expertise differences
ttest_ttff <- t.test(x = df_ttff_disrup$time_to_first_fixation_disruptive_person[df_ttff_disrup$id == "Expert"],
                     y = df_ttff_disrup$time_to_first_fixation_disruptive_person[df_ttff_disrup$id == "Novice"])

# effect size for expertise differences
d_ttff <- CohenD(x = df_ttff_disrup$time_to_first_fixation_disruptive_person[df_ttff_disrup$id == "Expert"],
                 y = df_ttff_disrup$time_to_first_fixation_disruptive_person[df_ttff_disrup$id == "Novice"],
                 na.rm = TRUE)

#### sri - confidence factor
# t-test for expertise differences
ttest_sri <- t.test(x = df_sri$confidence_factor[df_sri$id == "Expert"],
                    y = df_sri$confidence_factor[df_sri$id == "Novice"])

# effect size for expertise differences
d_sri <- CohenD(x = df_sri$confidence_factor[df_sri$id == "Expert"],
                y = df_sri$confidence_factor[df_sri$id == "Novice"],
                na.rm = TRUE)

### action alternatives count
# t-test for expertise differences
ttest_aa_count <- t.test(x = df_alternatives$count[df_alternatives$id == "Expert"],
                         y = df_alternatives$count[df_alternatives$id == "Novice"])

# effect size for expertise differences
d_aa_count <- CohenD(x = df_alternatives$count[df_alternatives$id == "Expert"],
                     y = df_alternatives$count[df_alternatives$id == "Novice"],
                     na.rm = TRUE)

### action alternatives code
# t-test for expertise differences
ttest_aa_code <- t.test(x = df_alternatives$code[df_alternatives$id == "Expert"],
                        y = df_alternatives$code[df_alternatives$id == "Novice"])

# effect size for expertise differences
d_aa_code <- CohenD(x = df_alternatives$code[df_alternatives$id == "Expert"],
                    y = df_alternatives$code[df_alternatives$id == "Novice"],
                    na.rm = TRUE)
```

# confidence factor x count of action alternatives
```{r}
# Novices
main %>% 
  filter(!is.na(confidence_factor) | !is.na(count)) %>% 
  filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = count
                       )
         ) +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Novices - Confidence Factor",
       y = "Count")

# Experts
main %>% 
  filter(!is.na(confidence_factor) | !is.na(count)) %>% 
  filter(id %in% c("Expert")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = count
                       )
         ) +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Experts - Confidence Factor",
       y = "Count")

```
# confidence factor x quality of action alternatives

```{r}
# Novices
main %>% 
  filter(!is.na(confidence_factor) | !is.na(code)) %>% 
  filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = code
                       )
         ) +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Novices - Confidence Factor",
       y = "Quality (Code1-6)")

# Experts
main %>% 
  filter(!is.na(confidence_factor) | !is.na(code)) %>% 
  filter(id %in% c("Expert")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = code
                       )
         ) +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Experts - Confidence Factor",
       y = "Quality (Code1-6)")
```

# time to first fixation x count of action alternatives
```{r}
# Novices
main %>% 
  filter(!is.na(time_to_first_fixation_disruptive_person) | !is.na(count)) %>% 
  filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = time_to_first_fixation_disruptive_person,
                       y = count
                       )
         ) +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Novices - Time to first fixation on disruptive person",
       y = "Count")

# Experts
main %>% 
  filter(!is.na(time_to_first_fixation_disruptive_person) | !is.na(count)) %>% 
  filter(id %in% c("Expert")) %>% 
  ggplot(mapping = aes(x = time_to_first_fixation_disruptive_person,
                       y = count
                       )
         ) +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Experts - Time to first fixation on disruptive person",
       y = "Count")
```

# time to first fixation x quality of action alternatives
```{r}
# Novices
main %>% 
  filter(!is.na(time_to_first_fixation_disruptive_person) | !is.na(code)) %>% 
  filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = time_to_first_fixation_disruptive_person,
                       y = code
                       )
         ) +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Novices - Time to first fixation on disruptive person",
       y = "Quality(Code1-6)")

# Experts
main %>% 
  filter(!is.na(time_to_first_fixation_disruptive_person) | !is.na(code)) %>% 
  filter(id %in% c("Expert")) %>% 
  ggplot(mapping = aes(x = time_to_first_fixation_disruptive_person,
                       y = code
                       )
         ) +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Experts - Time to first fixation on disruptive person",
       y = "Quality(Code1-6)")
```

# pearson & spearman correlation

```{r}
# novices: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Novice")) -> corr.nov

cor.test(corr.nov$confidence_factor, corr.nov$count, method=c("pearson"))

# experts: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Expert")) -> corr.exp

cor.test(corr.exp$confidence_factor, corr.exp$count, method=c("pearson"))

# novices: correlation between confidence factor and quality
cor.test(corr.nov$confidence_factor, corr.nov$code, method=c("spearman"))

# experts: correlation between confidence factor and quality
cor.test(corr.exp$confidence_factor, corr.exp$code, method=c("spearman"))

# novices: correlation between time to first fixation and count
cor.test(corr.nov$time_to_first_fixation_disruptive_person, corr.nov$count, method=c("pearson"))

# experts: correlation between time to first fixation and count
cor.test(corr.exp$time_to_first_fixation_disruptive_person, corr.exp$count, method=c("pearson"))

# novices: correlation between time to first fixation and quality
cor.test(corr.nov$time_to_first_fixation_disruptive_person, corr.nov$code, method=c("spearman"))

# experts: correlation between time to first fixation and quality
cor.test(corr.exp$time_to_first_fixation_disruptive_person, corr.exp$code, method=c("spearman"))

```

### 2023-03-28 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/action_alternatives_confidence_factor.Rmd
action alternatives

---
title: "Action alternatives & confidence factor"
output: html_document
date: "2023-03-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages and read in data
```{r}

library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot)

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

# SELF-REPORT DATA
df_sri <- 
  excel_sheets("data/coding_sri.xlsx") %>% 
  map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
  dplyr::select(ID, Event, `Confidence Factor`) %>% 
  filter(
    ID %in% c(101:126, 201:228),
    !ID %in% c(204, 226),
    Event %in% c("chatting")) %>%
  janitor::clean_names()

# ACTION ALTERNATIVES count
df_alternatives_count <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  janitor::clean_names() %>% 
  group_by(id) %>% 
  # mutate(mean_code = mean(code)) %>% 
  distinct(count)

# ACTION ALTERNATIVES non-disruptive 
df_alternatives_nd <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  janitor::clean_names() %>% 
  select(id, code) %>% 
  filter(code %in% c(1:3)) %>%
  group_by(id) %>%
  count() %>% 
  transmute(nd = n)

# merge data frames
# put all data frames into list
df_list <- list(df_sri, df_alternatives_count, df_alternatives_nd)

# merge all data frames in list
main <-
  df_list %>% reduce(full_join, by='id') %>%
  janitor::clean_names() %>%
  select(!event)

# replace NA with 0
main[is.na(main)] <- 0

main$id = ifelse(main$id < 200, "Novice","Expert")

```

```{r}
# confidence factor
describeBy(main$confidence_factor, main$id)
plot_confi <- boxplot(confidence_factor ~ id, data = main)

# action alternatives - count
describeBy(main$count, main$id)
plot_action_count <- boxplot(count ~ id, data = main)

# action alternatives - non disruptive alternatives  
describeBy(main$nd, main$id)
plot_action_quality <- boxplot(nd ~ id, data = main)

```

# confidence factor x count of action alternatives
```{r}
main %>% 
  filter(!is.na(confidence_factor) | !is.na(count)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = count,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Confidence Factor",
       y = "Count of action alternatives") +
  theme_cowplot()

```

# confidence factor x non-disruptive action alternatives
```{r}
main %>% 
  filter(!is.na(confidence_factor) | !is.na(nd)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = nd,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Confidence Factor",
       y = "Non-disruptive action alternatives") + 
  theme_cowplot()

```

# pearson & spearman correlation

```{r}
# novices: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Novice")) -> corr.nov

nov_confi_count_corr <- cor.test(corr.nov$confidence_factor, corr.nov$count, method=c("pearson"))
print(nov_confi_count_corr, short = F)

# experts: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Expert")) -> corr.exp

exp_confi_count_corr <- cor.test(corr.exp$confidence_factor, corr.exp$count, method=c("pearson"))
print(exp_confi_count_corr, short = F)

# full sample: correlation between confidence factor and count
full_confi_count_corr <- corr.test(main$confidence_factor, main$count, method=c("pearson"), adjust="holm")
print(full_confi_count_corr, short = F)

# novices: correlation between confidence factor and non-disruptive alternatives
nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor, corr.nov$nd, method=c("pearson"))
print(nov_confi_nd_corr, short = F)

# experts: correlation between confidence factor and non-disruptive alternatives
exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor, corr.exp$nd, method=c("pearson"))
print(exp_confi_nd_corr, short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives
full_confi_nd_corr <- corr.test(main$confidence_factor, main$nd, method=c("pearson"), adjust="holm")
print(full_confi_nd_corr, short = F)

```

### 2023-03-29 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/action_alternatives_confidence_factor.Rmd
sjt

@@
 
+# SJT CM
+df_sjt <- read_csv2(file = "data/SJT.csv",
+                    locale = locale(decimal_mark = ",")) %>% 
+  select(UI06_05,
+         SJT_KF_gek) %>%
+  filter(UI06_05 %in% c(101:126, 201:228),
+         !UI06_05 %in% c(204, 226)
+         ) %>% 
+  na.omit() %>% 
+  rename("id" = "UI06_05",
+         "sjt" = "SJT_KF_gek")
+
 # ACTION ALTERNATIVES count
@@
 # put all data frames into list
-df_list <- list(df_sri, df_alternatives_count, df_alternatives_nd)
+df_list <- list(df_sri,
+                df_sjt,
+                df_alternatives_count,
+                df_alternatives_nd)
 
@@
 
+# descriptives & plots
 ```{r}
@@
 plot_confi <- boxplot(confidence_factor ~ id, data = main)
+
+# sjt cm
+describeBy(main$sjt, main$id)
+plot_confi <- boxplot(sjt ~ id, data = main)
 
@@
 
+# sjt x count of action alternatives
+```{r}
+main %>% 
+  filter(!is.na(sjt) | !is.na(count)) %>% 
+  # filter(id %in% c("Novice")) %>% 
+  ggplot(mapping = aes(x = sjt,
+                       y = count,
+                       colour = id
+                       )
+         ) +
+  geom_point() + 
+  geom_smooth(method = "lm",
+              se = TRUE) +
+  scale_color_viridis_d() +
+  labs(x = "SJT Classroom Management",
+       y = "Count of action alternatives") +
+  theme_cowplot()
+
+```
+
+# sjt x non-disruptive action alternatives
+```{r}
+main %>% 
+  filter(!is.na(sjt) | !is.na(nd)) %>% 
+  # filter(id %in% c("Novice")) %>% 
+  ggplot(mapping = aes(x = sjt,
+                       y = nd,
+                       colour = id
+                       )
+         ) +
+  geom_point() + 
+  geom_smooth(method = "lm",
+              se = TRUE) +
+  scale_color_viridis_d() +
+  labs(x = "SJT Classroom Management",
+       y = "Non-disruptive action alternatives") + 
+  theme_cowplot()
+
+```
+
+# t-test and effect size
+```{r}
+
+#### confidence factor
+# t-test for expertise differences
+t.test(x = main$confidence_factor[main$id == "Expert"],
+       y = main$confidence_factor[main$id == "Novice"])
+
+# effect size for expertise differences
+CohenD(x = main$confidence_factor[main$id == "Expert"],
+       y = main$confidence_factor[main$id == "Novice"],
+       na.rm = TRUE)
+
+### action alternatives count
+# t-test for expertise differences
+t.test(x = main$count[main$id == "Expert"],
+       y = main$count[main$id == "Novice"])
+
+# effect size for expertise differences
+CohenD(x = main$count[main$id == "Expert"],
+       y = main$count[main$id == "Novice"],
+       na.rm = TRUE)
+
+### action alternatives non-disruptive
+# t-test for expertise differences
+t.test(x = main$nd[main$id == "Expert"],
+       y = main$nd[main$id == "Novice"])
+
+# effect size for expertise differences
+CohenD(x = main$nd[main$id == "Expert"],
+       y = main$nd[main$id == "Novice"],
+       na.rm = TRUE)
+```
+
 # pearson & spearman correlation
@@
 
-nov_confi_count_corr <- cor.test(corr.nov$confidence_factor, corr.nov$count, method=c("pearson"))
-print(nov_confi_count_corr, short = F)
+nov_confi_count_corr <- cor.test(corr.nov$confidence_factor, 
+                                 corr.nov$count, 
+                                 method=c("pearson"),
+                                 adjust="holm")
+print(nov_confi_count_corr, 
+      short = F)
 
@@
 
-exp_confi_count_corr <- cor.test(corr.exp$confidence_factor, corr.exp$count, method=c("pearson"))
-print(exp_confi_count_corr, short = F)
+exp_confi_count_corr <- cor.test(corr.exp$confidence_factor, 
+                                 corr.exp$count, 
+                                 method=c("pearson"),
+                                 adjust="holm")
+print(exp_confi_count_corr, 
+      short = F)
 
 # full sample: correlation between confidence factor and count
-full_confi_count_corr <- corr.test(main$confidence_factor, main$count, method=c("pearson"), adjust="holm")
-print(full_confi_count_corr, short = F)
+full_confi_count_corr <- corr.test(main$confidence_factor, 
+                                   main$count, 
+                                   method=c("pearson"), 
+                                   adjust="holm")
+print(full_confi_count_corr,
+      short = F)
+
+###################################################
 
 # novices: correlation between confidence factor and non-disruptive alternatives
-nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor, corr.nov$nd, method=c("pearson"))
-print(nov_confi_nd_corr, short = F)
+nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
+                              corr.nov$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(nov_confi_nd_corr, 
+      short = F)
 
 # experts: correlation between confidence factor and non-disruptive alternatives
-exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor, corr.exp$nd, method=c("pearson"))
-print(exp_confi_nd_corr, short = F)
+exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
+                              corr.exp$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(exp_confi_nd_corr,
+      short = F)
 
 # full sample: correlation between confidence factor and non-disruptive alternatives
-full_confi_nd_corr <- corr.test(main$confidence_factor, main$nd, method=c("pearson"), adjust="holm")
-print(full_confi_nd_corr, short = F)
+full_confi_nd_corr <- corr.test(main$confidence_factor, 
+                                main$nd, method=c("pearson"),
+                                adjust="holm")
+print(full_confi_nd_corr,
+      short = F)
+
+###################################################
+
+# novices: correlation between sjt and count
+nov_sjt_count_corr <- cor.test(corr.nov$sjt,
+                              corr.nov$count, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(nov_sjt_count_corr, 
+      short = F)
+
+# experts: correlation between sjt and count
+exp_sjt_count_corr <- cor.test(corr.exp$sjt,
+                              corr.exp$count, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(exp_sjt_count_corr,
+      short = F)
+
+# full sample: correlation between sjt and count
+full_sjt_count_corr <- corr.test(main$sjt, 
+                                 main$count, 
+                                 method=c("pearson"), 
+                                 adjust="holm")
+print(full_sjt_count_corr, 
+      short = F)
+
+###################################################
+
+# novices: correlation between sjt and non-disruptive alternatives
+nov_sjt_nd_corr <- cor.test(corr.nov$sjt,
+                              corr.nov$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(nov_sjt_nd_corr, 
+      short = F)
+
+# experts: correlation between sjt and non-disruptive alternatives
+exp_sjt_nd_corr <- cor.test(corr.exp$sjt,
+                              corr.exp$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(exp_sjt_nd_corr,
+      short = F)
+
+# full sample: correlation between sjt and non-disruptive alternatives
+full_sjt_nd_corr <- corr.test(main$sjt,
+                              main$nd,
+                              method=c("pearson"),
+                              adjust="holm")
+print(full_sjt_nd_corr,
+      short = F)
 

### 2023-04-14 02_paper/02_study/02_fitbit paper/presentation_analysis_std.Rmd
update analysis

@@
       lm.beta,
-      tidyverse,
       janitor,
@@
       gridExtra,
-      gridtext)
+      gridtext,
+      magrittr,
+      tidyverse)
 
@@
   distinct() %>% 
-  mutate(time = time / 60) %>% 
+  mutate(time = time / 60) %>%                  # Zeit in Minuten umrechnen, um Effekte besser sichtbar zu machen
   split(.$time_span) %>% 
@@
 ```
+
+- Nur pre und subsequent (lineare Regression mit slopes als av)
+- 7200 sek kürzen (gesamtverlauf)
+- Unterrichtsphase kürzen auf 600 sek
+- für jede Phase intercept + slope (SD) growth curve model 
+  - frage: individual slope + allover slope (+ intercept)
+  - ist der mitterlwert aus slopes = allover slope?
+- individuellen Intercepts -> Mittelwertunterschied
+
+- t-test über
+
+1. rohwert-kurve neben z-std.-kurve (untereinander)
+2. Slope und Intercept mit je Mean und SD (overall aus individuell?) -> sign?
+3. Unterricht vs. Post (t-test über Intercepts), d und p
+4. Intercept (Teaching, interview, Post) vorhersage (4 Modelle)
+5. Unterscheiden sich slopes in pre und subsequent signifikant (Betrag?)
+6. Slopes (pre-Phase und subsequent) vorhersagen (4 Modelle)
+7. slope und intercept correlation?
+
+1. Pre Phase (pre)
+2. Teaching Phase (main)
+3. Post Phase (subsequent)
+4. Interview Phase (interview)
+5. End Phase (after)
+
+1. Rohwertekurve und z-Str. Kurve untereinander
+
+```{r}
+loess_plot_overall <-
+  main %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+ # scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0, NA),
+                     breaks = seq(0, 9000, 600)) +
+ # scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
+  labs(x = "Time (in seconds)",
+       y = "",
+       title = "Overall trend of heartrate",
+       subtitle = "Unstandardized") +
+  theme_apa() + 
+  theme(axis.title.y = element_blank())
+
+loess_plot_overall_std <-
+  main %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0, NA),
+                     breaks = seq(0, 9000, 600)) +
+  scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
+  labs(x = "Time (in seconds)",
+       y = "",
+       subtitle = "Standardized") +
+  theme_apa() + 
+  theme(axis.title.y = element_blank())
+
+grid.arrange(loess_plot_overall, loess_plot_overall_std,
+             nrow = 2)
+```
+
+2. Slope und Intercept mit SD und M
+
+2 Optionen:
+
+1. Fixed Intercept - Fixed Slope
+
+```{r}
+df_regression <- 
+  main %>% 
+  filter(time_span == "pre") %>%
+  dplyr::select("ID","time","heart_rate_std") %>% 
+  distinct() %>% 
+  mutate(ID = as_factor(ID))
+
+fit_ff <- 
+  lm(heart_rate_std ~ 0 + ID + time:ID,
+  data = df_regression)
+
+summary(fit_ff)
+
+fit_ff$coefficients %>%
+  tibble(id = names(.),
+         values = .) %>% 
+  mutate(kind = if_else(condition = str_detect(string = id,
+                                               pattern = ":"),
+                        true = "Slope",
+                        false = "Intercept"
+                        )
+         ) %>% 
+  group_by(kind) %>% 
+  summarize(mean_value = mean(values),
+            sd_value = sd(values)
+            ) %>% 
+  ungroup()
+```
+
+2. Random Intercept - Random Slope Modell
+
+```{r}
+fit_rr <-
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
+       data = df_regression
+       )
+
+summary(fit_rr)$coefficients[1]
+
+ranef(fit_rr)$ID 
+```
+
+Vergleich:
+
+```{r}
+df_regression %>% 
+ # filter(ID %in% c("101","102","103","104")) %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std,
+                       group = ID)) +
+  geom_line(mapping = aes(y = fitted(fit_ff)),
+            color = "blue",
+            size = 1) +
+  geom_line(mapping = aes(y = fitted(fit_rr)),
+            color = "red",
+            size = 1,
+            alpha = 0.5) +
+  geom_point(alpha = 0.5,
+             size = 0.5 ) +
+  facet_wrap(~ID, nrow = 6) +
+  theme_bw()
+ggsave(filename = "plots/regression.pdf",
+       width = 20,
+       height = 15,
+       units = "cm")
+```
+
+Beide Verfahren führen zu ähnlichen Schätzern, aber zu Unterschieden in den Verteilungen der Parameter.
+
+Bei der Random Effects Regression werden Intercepts und Slopes nicht unabhängig voneinander modeliert. Die Modelierung erfolgt auf Basis einer bivariaten Normalverteilung.
+Bei der Fixed Effects Regression werden die Größen unabhängig voneinander modelliert.
+
+3. t-Test
+
+```{r}
+df_ttest <- 
+  main %>% 
+  dplyr::select("ID","time","heart_rate_std","time_span") %>% 
+  distinct() %>% 
+  mutate(ID = as_factor(ID)) %>% 
+  split(.$time_span) %>% 
+  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
+             data = .)) %>% 
+  map(~ ranef(.)$ID %>% 
+        as_tibble(., 
+                  rownames = "ID"
+                  ) %>% 
+        clean_names()
+      ) %>% 
+  bind_rows(.,
+            .id = "time_span")
+
+main %>% 
+  dplyr::select("ID","time","heart_rate_std","time_span") %>% 
+  distinct() %>% 
+  mutate(ID = as_factor(ID)) %>% 
+  split(.$time_span) %>% 
+  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
+             data = .)) %>% 
+  map(~ summary(.) %>% 
+        .$coefficients %>% 
+        .[c(1,2)]) %>% 
+  bind_rows(.,
+            .id = "time_span") %>% 
+  pivot_longer(
+  cols = everything(),
+  names_to = c("diagnosis", "gender"),
+  names_pattern = "new_?(.*)_(.)",
+  values_to = "count"
+)
+
+t.test(df_ttest$`(Intercept)`[df_ttest$time_span == "main"],
+       df_ttest$`(Intercept)`[df_ttest$time_span == "subsequent"],
+       paired = TRUE)
+
+df_ttest %>% 
+  filter(time_span == "main") %>% 
+  ggplot(mapping = aes(x = intercept)) +
+  geom_histogram()
+```

### 2023-04-15 02_paper/02_study/02_fitbit paper/presentation_analysis_std.Rmd
update fitbit analysis

@@
 ```{r}
-df_ttest <- 
+cache1 <- 
   main %>% 
@@
 
+cache2 <-  
   main %>% 
@@
   cols = everything(),
-  names_to = c("diagnosis", "gender"),
-  names_pattern = "new_?(.*)_(.)",
-  values_to = "count"
+  names_to = "time_span",
+  values_to = "mean_value"
   )
 
-t.test(df_ttest$`(Intercept)`[df_ttest$time_span == "main"],
-       df_ttest$`(Intercept)`[df_ttest$time_span == "subsequent"],
+df_ttest <- 
+  tibble(mean_intercept = cache2$mean_value[1:6],
+         mean_time = cache2$mean_value[7:12],
+         time_span = cache2$time_span[1:6]) %>% 
+  right_join(x = .,
+             y = cache1) %>% 
+  transmute(time_span,
+            intercept = mean_intercept + intercept,
+            time = mean_time + time)
+
+t.test(df_ttest$intercept[df_ttest$time_span == "main"],
+       df_ttest$intercept[df_ttest$time_span == "subsequent"],
        paired = TRUE)
-
-df_ttest %>% 
-  filter(time_span == "main") %>% 
-  ggplot(mapping = aes(x = intercept)) +
-  geom_histogram()
 ```

### 2023-04-17 02_paper/02_study/02_fitbit paper/analysis_180423.Rmd
Finalize Analysis

---
title: "Analysis 19.04.23"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, warning = FALSE)
```

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      tidyverse)

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  dplyr::select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confidence_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         )

# demographic data
df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
  transmute(ID = LI06_05, # select and rename relevant columns 
            gender = factor(LI02_01_1,
                            levels = 1:2,
                            labels = c("male","female")
                            ),
            age = LI03_01, # 1 = male; 2 = female
            teaching_experience = LI04_01)

# merge two data frames by ID 
df_merge <- merge(df_demo,
                  df_rating,
                  by = "ID") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132")
         )

# rm(list = c("df_demo","df_rating"))

data_path <- "./data/heart_rate_data"

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
                               str_detect(string = id, pattern = "_m") ~ "main",
                               str_detect(string = id, pattern = "_p") ~ "pre",
                               str_detect(string = id, pattern = "_s") ~ "subsequent",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
      # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 9000) %>% # filter for 2 hours 30min (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

main <-
  left_join(main, df_merge,
            by = "ID")

main %>% 
  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
  distinct() %>% 
  # filter(time_span == "overall") %>% 
  group_by(ID) %>% 
  summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>% 
  right_join(x = .,
             y = main,
             by = "ID") %>% 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart) -> main

```

# To Do 17.04.

1. rohwert-kurve neben z-std.-kurve (untereinander)
2. Slope und Intercept mit je Mean und SD (overall aus individuell?) -> sign?
3. Unterricht vs. Post (t-test über Intercepts), d und p
4. Intercept (Teaching, interview, Post) vorhersage (4 Modelle)
5. Unterscheiden sich slopes in pre und subsequent signifikant (Betrag?)
6. Slopes (pre-Phase und Post) vorhersagen (4 Modelle)
7. slope und intercept correlation?

1. Pre Phase (pre)
2. Teaching Phase (main)
3. Post Phase (subsequent)
4. Interview Phase (interview)
5. End Phase (after)

# 1. Rohwertekurve und z-Str. Kurve untereinander

```{r}
loess_plot_overall <-
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  # geom_point(alpha = 0.05) + 
  geom_smooth(se = FALSE,
              size = 0.5,
              colour = "black") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
 # scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0, NA),
                     breaks = seq(0, 9000, 600)) +
 # scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
  labs(x = "Time (in seconds)",
       y = "",
       title = "Overall trend of heartrate",
       subtitle = "Unstandardized") +
  theme_apa() + 
  theme(axis.title.y = element_blank())

loess_plot_overall_std <-
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate_std
                       )
         ) +
  # geom_point(alpha = 0.05) + 
  geom_smooth(se = FALSE,
              size = 0.5,
              colour = "black") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0, NA),
                     breaks = seq(0, 9000, 600)) +
  scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
  labs(x = "Time (in seconds)",
       y = "",
       subtitle = "Standardized") +
  theme_apa() + 
  theme(axis.title.y = element_blank())

grid.arrange(loess_plot_overall, loess_plot_overall_std,
             nrow = 2)
```

- Kurve zieht am Ende hoch
- Wenig Fälle, kleine Streuung

# 2. Slope und Intercept mit SD und M

2 Optionen:

1. Fixed Intercept - Fixed Slope

```{r}
# heart_rate_var <- "heart_rate_std"
heart_rate_var <- "heart_rate"

df_regression <- 
  main %>% 
  filter(time_span == "pre") %>%
  dplyr::select("ID","time","heart_rate_std","heart_rate") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID))

fit_ff <- 
  lm(eval(parse(text = heart_rate_var)) ~ 0 + ID + time:ID,
  data = df_regression)

summary(fit_ff)

fit_ff$coefficients %>%
  tibble(id = names(.),
         values = .) %>% 
  mutate(kind = if_else(condition = str_detect(string = id,
                                               pattern = ":"),
                        true = "Slope",
                        false = "Intercept"
                        )
         ) %>% 
  group_by(kind) %>% 
  summarize(mean_value = mean(values),
            sd_value = sd(values)
            ) %>% 
  ungroup()
```

2. Random Intercept - Random Slope Modell

```{r}
fit_rr <-
  lmer(formula = eval(parse(text = heart_rate_var)) ~ 1 + time + (1 + time | ID),
       data = df_regression
       )

summary(fit_rr)$coefficients[1]

ranef(fit_rr)$ID 
```

Vergleich:

```{r}
df_regression %>% 
 # filter(ID %in% c("101","102","103","104")) %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate_std,
                       group = ID)) +
  geom_line(mapping = aes(y = fitted(fit_ff)),
            color = "blue",
            size = 1) +
  geom_line(mapping = aes(y = fitted(fit_rr)),
            color = "red",
            size = 1,
            alpha = 0.5) +
  geom_point(alpha = 0.5,
             size = 0.5 ) +
  facet_wrap(~ID, nrow = 6) +
  theme_bw()
ggsave(filename = "plots/regression.pdf",
       width = 20,
       height = 15,
       units = "cm")
```

Beide Verfahren führen zu ähnlichen Schätzern, aber zu Unterschieden in den Verteilungen der Parameter.

Bei der Random Effects Regression werden Intercepts und Slopes nicht unabhängig voneinander modeliert. Die Modelierung erfolgt auf Basis einer bivariaten Normalverteilung.
Bei der Fixed Effects Regression werden die Größen unabhängig voneinander modelliert.
Aus strategischer Sicht die die Fixed Effects Regression vorzuziehen. Modellierung impliziert eine Normalverteilung der Effekte in der Grundgesamtheit. Das ist nicht zwingend notwendig, aber erzeugt automatisch einen schönen Modell-Fit.

# 3. t-Test zwischen Post-Phase und

```{r}
heart_rate_var <- "heart_rate_std"
# heart_rate_var <- "heart_rate"

cache1 <- 
  main %>% 
  dplyr::select("ID","time","heart_rate_std", "heart_rate", "time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = eval(parse(text = heart_rate_var)) ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ ranef(.)$ID %>% 
        as_tibble(., 
                  rownames = "ID"
                  ) %>% 
        clean_names()
      ) %>% 
  bind_rows(.,
            .id = "time_span")

cache2 <-  
  main %>% 
  dplyr::select("ID","time","heart_rate_std", "heart_rate","time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = eval(parse(text = heart_rate_var)) ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ summary(.) %>% 
        .$coefficients %>% 
        .[c(1,2)]) %>% 
  bind_rows(.,
            .id = "time_span") %>% 
  pivot_longer(
  cols = everything(),
  names_to = "time_span",
  values_to = "mean_value"
  )

df_test <- 
  tibble(mean_intercept = cache2$mean_value[1:6],
         mean_time = cache2$mean_value[7:12],
         time_span = cache2$time_span[1:6]) %>% 
  right_join(x = .,
             y = cache1,
             by = "time_span") %>% 
  transmute(time_span,
            intercept = mean_intercept + intercept,
            time = mean_time + time,
            id = id)

t.test(df_test$intercept[df_test$time_span == "main"],
       df_test$intercept[df_test$time_span == "subsequent"],
       paired = TRUE)

CohenD(x = df_test$intercept[df_test$time_span == "main"],
       y = df_test$intercept[df_test$time_span == "subsequent"],
       pooled = T
       )
```

# 4. Intercept (Teaching, interview, Post) vorhersage (4 Modelle)

```{r}
df_test_reg <- 
  df_merge %>% 
  mutate(id = as_factor(ID)) %>% 
  group_by(id) %>% 
  summarise(mean_confidence = mean(confidence_factor, na.rm = T),
            mean_disruption = mean(disruption_factor, na.rm = T)) %>% 
  right_join(x = .,
             y = df_test,
             by = "id") %>% 
  right_join(x = .,
             y = transmute(df_demo, 
                           id = as_factor(ID),
                           teaching_experience = teaching_experience
                           ),
             by = "id")

df_test_reg %>% 
  pivot_longer(cols = c("mean_confidence", "mean_disruption"),
               names_to = "factor_means",
               values_to = "means") %>% 
  ggplot(mapping = aes(x = means,
                       y = intercept
                       )
         ) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(cols = vars(time_span),
             rows = vars(factor_means))
```

## Teaching

```{r}
fit_teach_1 <-
  df_test_reg %>% 
  filter(time_span == "main") %$% 
  lm(intercept ~ mean_disruption)

fit_teach_2 <-
  df_test_reg %>% 
  filter(time_span == "main") %$% 
  lm(intercept ~ mean_confidence)

fit_teach_3 <-
  df_test_reg %>% 
  filter(time_span == "main") %$% 
  lm(intercept ~ mean_confidence + mean_disruption)

fit_teach_4 <-
  df_test_reg %>% 
  filter(time_span == "main") %$% 
  lm(intercept ~ mean_confidence + mean_disruption + teaching_experience)

stargazer::stargazer(fit_teach_1, fit_teach_2, fit_teach_3, fit_teach_4,
                     type = "latex",
                  #   caption = "Teaching Phase",
                     dep.var.labels = "Intercept",
                     order = c(1, 3, 2),
                     covariate.labels = c("Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```

## Interview

```{r}
fit_interview_1 <-
  df_test_reg %>% 
  filter(time_span == "interview") %$% 
  lm(intercept ~ mean_disruption)

fit_interview_2 <-
  df_test_reg %>% 
  filter(time_span == "interview") %$% 
  lm(intercept ~ mean_confidence)

fit_interview_3 <-
  df_test_reg %>% 
  filter(time_span == "interview") %$% 
  lm(intercept ~ mean_confidence + mean_disruption)

fit_interview_4 <-
  df_test_reg %>% 
  filter(time_span == "interview") %$% 
  lm(intercept ~ mean_confidence + mean_disruption + teaching_experience)

stargazer::stargazer(fit_interview_1, fit_interview_2, fit_interview_3, fit_interview_4,
                     type = "latex",
                   #  caption = "Teaching Phase",
                     dep.var.labels = "Intercept",
                     order = c(1, 3, 2),
                     covariate.labels = c("Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```

## Post

```{r}
fit_post_1 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(intercept ~ mean_disruption)

fit_post_2 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(intercept ~ mean_confidence)

fit_post_3 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(intercept ~ mean_confidence + mean_disruption)

fit_post_4 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(intercept ~ mean_confidence + mean_disruption + teaching_experience)

stargazer::stargazer(fit_post_1, fit_post_2, fit_post_3, fit_post_4,
                     type = "latex",
                   #  caption = "Teaching Phase",
                     dep.var.labels = "Intercept",
                     order = c(1, 3, 2),
                     covariate.labels = c("Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```

# 5. Unterscheiden sich slopes in pre und post signifikant (Betrag?)

```{r}
df_test_reg_slope <-
  df_test_reg %>% 
  filter(time_span == "pre" | time_span == "subsequent") %>% 
  mutate(time = abs(time))

fit_slopeabs_1 <-
  df_test_reg_slope %$%
  lm(time ~ time_span)

fit_slopeabs_2 <-
  df_test_reg_slope %$%
  lm(time ~ time_span + mean_disruption + mean_confidence + teaching_experience)

stargazer::stargazer(fit_slopeabs_1, fit_slopeabs_2,
                     type = "latex",
                     dep.var.labels = "Slope (absolut value)",
                     # order = c(1, 3, 2),
                     covariate.labels = c("Pre Phase vs. Post Phase",
                                          "Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```

# 6. Slopes (pre und post) vorhersagen (4 Modelle)

## Pre

```{r}
fit_pre_1 <-
  df_test_reg %>% 
  filter(time_span == "pre") %$% 
  lm(time ~ mean_disruption)

fit_pre_2 <-
  df_test_reg %>% 
  filter(time_span == "pre") %$% 
  lm(time ~ mean_confidence)

fit_pre_3 <-
  df_test_reg %>% 
  filter(time_span == "pre") %$% 
  lm(time ~ mean_confidence + mean_disruption)

fit_pre_4 <-
  df_test_reg %>% 
  filter(time_span == "pre") %$% 
  lm(time ~ mean_confidence + mean_disruption + teaching_experience)

stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4,
                     type = "latex",
                     caption = "Pre Phase",
                     dep.var.labels = "Slope",
                     order = c(1, 3, 2),
                     covariate.labels = c("Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```

## Post

```{r}
fit_postslope_1 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(time ~ mean_disruption)

fit_postslope_2 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(time ~ mean_confidence)

fit_postslope_3 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(time ~ mean_confidence + mean_disruption)

fit_postslope_4 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(time ~ mean_confidence + mean_disruption + teaching_experience)

stargazer::stargazer(fit_postslope_1, fit_postslope_2,fit_postslope_3, fit_postslope_4,
                     type = "latex",
             #        caption = "Post Phase",
                     dep.var.labels = "Slope",
                     order = c(1, 3, 2),
                     covariate.labels = c("Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```

# 7. Slope-Intercept Korrelation

```{r}
df_corr <- 
  df_test_reg %>% 
  split(.$time_span) %>% 
  map(~ cor.test(x = .$intercept,
                 y = .$time,
                 method = "pearson"
                 )
      ) %>% 
  map(~ tibble(estimate = .$estimate,
               p.value = .$p.value
               )
      ) %>% 
  bind_rows(.id = "time_span")

print(xtable(df_corr))
```

### 2023-04-18 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
gvhj

@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:demographicstable}Demographic Information}
+
+\tiny{
+
+\begin{tabular}{llllllllll}
+\toprule
+N & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Teaching Experience in years} & \multicolumn{1}{c}{SD Teaching Experience in years} & \multicolumn{1}{c}{Min Teaching Experience in years} & \multicolumn{1}{c}{Max Teaching Experience in years}\\
+\midrule
+70 & 60.00 & 29.74 & 10.67 & 19.00 & 59.00 & 4.84 & 9.31 & 0.00 & 37.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 The sample consisted in total of \emph{N} = 72 pre- and in-service teachers.
@@
 
-Teachers' average heart rate during the entire course of the study was approximately 96.84 bpm with a standard deviation of 14.44 and a range from 56 to 139 bpm.
+Teachers' average heart rate during the entire course of the study was approximately 96.83 bpm with a standard deviation of 14.40 and a range from 56 to 139 bpm.
 

### 2023-04-19 02_paper/02_study/02_fitbit paper/analysis_180423.Rmd
forgot to push push

@@
 
-1. Pre Phase (pre)
+1. Preparation Phase (pre)
 2. Teaching Phase (main)
-3. Post Phase (subsequent)
+3. Post Teaching Phase (subsequent)
 4. Interview Phase (interview)
@@
 
+- Bei 7200 kappen
 - Kurve zieht am Ende hoch
@@
 ```{r}
-# heart_rate_var <- "heart_rate_std"
-heart_rate_var <- "heart_rate"
+heart_rate_var <- "heart_rate_std"
+# heart_rate_var <- "heart_rate"
 
@@
 Bei der Fixed Effects Regression werden die Größen unabhängig voneinander modelliert.
-Aus strategischer Sicht die die Fixed Effects Regression vorzuziehen.
+Aus strategischer Sicht die die Random Effects Regression vorzuziehen.
 Modellierung impliziert eine Normalverteilung der Effekte in der Grundgesamtheit.
@@
 
-# 3. t-Test zwischen Post-Phase und
+# 3. t-Test zwischen Teaching und Pre-Phase
 
@@
 t.test(df_test$intercept[df_test$time_span == "main"],
-       df_test$intercept[df_test$time_span == "subsequent"],
+       df_test$intercept[df_test$time_span == "interview"],
        paired = TRUE)
@@
 CohenD(x = df_test$intercept[df_test$time_span == "main"],
-       y = df_test$intercept[df_test$time_span == "subsequent"],
+       y = df_test$intercept[df_test$time_span == "interview"],
        pooled = T
@@
 
-# 4. Intercept (Teaching, interview, Post) vorhersage (4 Modelle)
+# 4. Intercept (Teaching, interview, End) vorhersage (4 Modelle)
 
@@
   df_test_reg %>% 
-  filter(time_span == "subsequent") %$% 
+  filter(time_span == "after") %$% 
   lm(intercept ~ mean_disruption)
@@
   df_test_reg %>% 
-  filter(time_span == "subsequent") %$% 
+  filter(time_span == "after") %$% 
   lm(intercept ~ mean_confidence)
@@
   df_test_reg %>% 
-  filter(time_span == "subsequent") %$% 
+  filter(time_span == "after") %$% 
   lm(intercept ~ mean_confidence + mean_disruption)
@@
 ```
+
+# To Do
+
+- unterschiedliche "Enden" setzen für Robustness-Check (Wie viel Prozent erreichen die zwei Stunden?) -> 80% und 90%
+- p werte, mean, sd für alle slopes und intercepts über alle Phasen

### 2023-04-20 02_paper/02_study/02_fitbit paper/analysis_180423.Rmd

@@
 - p werte, mean, sd für alle slopes und intercepts über alle Phasen
+- im 4. Punkt end statt post (Vertagt!)
+- Übersicht aus 2. für alle Phasen
+- Korrelation über disr conf hr alter te (std und normal)

### 2023-04-20 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/action_alternatives_confidence_factor.Rmd
main datei angepasst

@@
 
-# pearson & spearman correlation
+# pearson correlation
 
@@
 
+# novices: correlation between count and non-disruptive alternatives
+nov_count_nd_corr <- cor.test(corr.nov$count,
+                              corr.nov$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(nov_count_nd_corr, 
+      short = F)
+
+# experts: correlation between count and non-disruptive alternatives
+exp_count_nd_corr <- cor.test(corr.exp$count,
+                              corr.exp$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(exp_count_nd_corr,
+      short = F)
+
+# full sample: correlation between confidence factor and non-disruptive alternatives
+full_count_nd_corr <- corr.test(main$count, 
+                                main$nd, 
+                                method=c("pearson"),
+                                adjust="holm")
+print(full_count_nd_corr,
+      short = F)
+
+###################################################
+
 # novices: correlation between sjt and count

### 2023-04-20 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
main datei angepasst

@@
 
-# # format and insert table in manuscript
-# df_demo_table %>%
-# papaja::apa_table(
-#   caption = "Demographic Information",
-#   # note = "Write Note here",
-#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-#   )
+# format and insert table in manuscript
+df_demo_table %>%
+papaja::apa_table(
+  caption = "Demographic Information",
+  # note = "Write Note here",
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
 

### 2023-04-20 02_paper/02_study/02_fitbit paper/presentation_analysis_std.Rmd
main datei angepasst

--- 2023-03-07 02_paper/02_study/02_fitbit paper/presentation_analysis_std.Rmd
@@
 needs(ltm,
+      xtable,
       broom,
@@
 ```
+
+- Nur pre und subsequent (lineare Regression mit slopes als av)
+- 7200 sek kürzen (gesamtverlauf)
+- Unterrichtsphase kürzen auf 600 sek
+- für jede Phase intercept + slope (SD) growth curve model 
+  - frage: individual slope + allover slope (+ intercept)
+  - ist der mitterlwert aus slopes = allover slope?
+- individuellen Intercepts -> Mittelwertunterschied
+
+- t-test über
+
+## Interview
+
+```{r}
+fit_interview_1 <-
+  df_test_reg %>% 
+  filter(time_span == "interview") %$% 
+  lm(intercept ~ mean_disruption)
+
+fit_interview_2 <-
+  df_test_reg %>% 
+  filter(time_span == "interview") %$% 
+  lm(intercept ~ mean_confidence)
+
+fit_interview_3 <-
+  df_test_reg %>% 
+  filter(time_span == "interview") %$% 
+  lm(intercept ~ mean_confidence + mean_disruption)
+
+fit_interview_4 <-
+  df_test_reg %>% 
+  filter(time_span == "interview") %$% 
+  lm(intercept ~ mean_confidence + mean_disruption + teaching_experience)
+
+stargazer::stargazer(fit_interview_1, fit_interview_2, fit_interview_3, fit_interview_4,
+                     type = "latex",
+                     dep.var.labels = "Intercept",
+                     order = c(1, 3, 2),
+                     covariate.labels = c("Disruption Factor",
+                                          "Confidence Factor",
+                                          "Teaching Experience"),
+                     keep.stat = c("n","rsq","adj.rsq")
+                     )
+```
+
+## Post
+
+```{r}
+fit_post_1 <-
+  df_test_reg %>% 
+  filter(time_span == "subsequent") %$% 
+  lm(intercept ~ mean_disruption)
+
+fit_post_2 <-
+  df_test_reg %>% 
+  filter(time_span == "subsequent") %$% 
+  lm(intercept ~ mean_confidence)
+
+fit_post_3 <-
+  df_test_reg %>% 
+  filter(time_span == "subsequent") %$% 
+  lm(intercept ~ mean_confidence + mean_disruption)
+
+fit_post_4 <-
+  df_test_reg %>% 
+  filter(time_span == "subsequent") %$% 
+  lm(intercept ~ mean_confidence + mean_disruption + teaching_experience)
+
+stargazer::stargazer(fit_post_1, fit_post_2, fit_post_3, fit_post_4,
+                     type = "latex",
+                     dep.var.labels = "Intercept",
+                     order = c(1, 3, 2),
+                     covariate.labels = c("Disruption Factor",
+                                          "Confidence Factor",
+                                          "Teaching Experience"),
+                     keep.stat = c("n","rsq","adj.rsq")
+                     )
+```

### 2023-04-20 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -353,7 +353,7 @@ ggsave(plot = confi_group_plot,
 # 
 
 
-#################### MEAN, SD, N ############
+#################### MEAN, SD ############
 
 # mean disrup_factor
 sri_disrup_mean <- sri_disrup %>%

### 2023-04-21 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/TEST.Rmd
update

--- 2023-02-14 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data.Rmd
@@
     institution   : "Konstanz Business School"
+
+authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+  Enter author note here.
+
+abstract: |
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  <!-- https://tinyurl.com/ybremelq -->
 
@@
                                   "Age" = "LI03_01",
-                                  "Teaching Experience" = "LI04_01")) %>% 
-    filter(Group %in% c(101:136, 202:217))# filter relevant rows
+                                  "Teaching Experience" = "LI04_01"))
 
@@
 ```
+
+## Material
+
+## Procedure
+
+## Data analysis
+We used `r cite_r("r-references.bib")` for all our analyses.
+
+# Results
+
+# Discussion
+
+\newpage
+
+# References
+
+::: {#refs custom-style="Bibliography"}
+:::

### 2023-04-21 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/TEST.tex
update

--- 2023-01-24 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
@@
 \documentclass[
-  man,floatsintext]{apa6}
+  english,
+  man]{apa6}
+\title{The title}
+\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
+\date{}
+
 \usepackage{amsmath,amssymb}
@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={The title},
+  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\ifLuaTeX
-\usepackage[bidi=basic]{babel}
-\else
-\usepackage[bidi=default]{babel}
-\fi
-\babelprovide[main,import]{english}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
@@
 {}{\PatchFailed}
-\keywords{heart rate; photoplethysmography; wearable electronic device; teaching\newline\indent Word count: X}
+\keywords{keywords\newline\indent Word count: X}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{lineno}
@@
 \usepackage{csquotes}
+\ifXeTeX
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
 \ifLuaTeX
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
-  pdfauthor={Mandy Klatt1, Peer Keßler1, Gregor Kachel1,2, Christin Lotz1, \& Anne Deiglmayr1},
-  pdflang={en-EN},
-  pdfkeywords={heart rate; photoplethysmography; wearable electronic device; teaching},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
-\title{New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?}
-\author{Mandy Klatt\textsuperscript{1}, Peer Keßler\textsuperscript{1}, Gregor Kachel\textsuperscript{1,2}, Christin Lotz\textsuperscript{1}, \& Anne Deiglmayr\textsuperscript{1}}
-\date{}
-
-\shorttitle{Using fitbit to measure teachers' heart rate}
+\shorttitle{Title}
 
@@
 
-We received funding from QualiFond of University Leipzig.
-We have no conflicts of interest to disclose.
-This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).
+Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
 
-The authors made the following contributions.
-Mandy Klatt: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Peer Keßler: Writing - Original Draft Preparation, Writing - Review \& Editing; Gregor Kachel: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Christin Lotz: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Anne Deiglmayr: Supervision.
+Enter author note here.
 
-Correspondence concerning this article should be addressed to Mandy Klatt, Dittrichring 5-7, 04109 Leipzig. E-mail: \href{mailto:mandy.klatt@uni-leipzig.de}{\nolinkurl{mandy.klatt@uni-leipzig.de}}
+The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.
+
+Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Leipzig University\\\textsuperscript{2} Max Planck Institute for Evolutionary Anthropology}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
 
@@
 Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
-
-XXX In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress.
-XXX
 }
@@
 \maketitle
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Physiological data such as heart rate are becoming increasingly important in research on stress experience.
-They represent an important indicator of physical or emotional stress, as increased workload is associated with increased heart rate (Sachs, 2014).
-Furthermore, they allow a more objective recording of stress than self-reports (Runge, Haarman, \& Fisher, n.d.).
-However, capturing heart rate in an educational context requires the use of low-cost and non-invasive instruments.
-Fitness trackers worn on the wrist have the potential to be such a useful tool (Ferguson, Rowlands, Olds, \& Maher, 2015).
-
-To date, there is still little evidence on the usefulness of heart rate measurements using fitness trackers in teaching and learning settings (Ertzberger \& Martin, 2016; Lowe, 2016).
-Runge et al.
-(n.d.) alone examined teacher stress in a relatively small sample (\emph{N} = 4 teachers) and showed that high heart rate indicates more stress in teachers.
-
-Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, low-cost, and robust measurement method for assessing teachers' experience of arousal during teaching.
-
-\hypertarget{theoretical-background}{%
-\section{Theoretical Background}\label{theoretical-background}}
-
-\hypertarget{stress-in-teaching-profession}{%
-\subsection{Stress in Teaching Profession}\label{stress-in-teaching-profession}}
-
---\textgreater{} teacher profession is one of the most stressful professions.
-
-Teacher stress can be defined as ``{[}\ldots{]} the experience by a teacher of unpleasant, negative emotions, such as anger, anxiety, tension, frustration or depression, resulting from some aspect of their work as a teacher.'' (Kyriacou, 2001).
-
-Teachers' individual perceptions of student misbehavior in the classroom are closely related to their well-being (Aldrup, Klusmann, Lüdtke, Göllner, \& Trautwein, 2018).
-
---\textgreater{} wie entsteht Stress
-
---\textgreater{} wie wurde Stress bisher gemessen
-
-\hypertarget{heart-rate-as-an-indicator-for-stress-or-arousal}{%
-\subsection{Heart rate as an indicator for stress or arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}
-
-Heart rate is physiologically regulated by the autonomic nervous system.
-An increase in the activity of the sympathetic as part of the autonomic nervous system results in the heart rate being speeded up (``fight or flight'').
-On the other hand, an increased activity of the parasympathetic as the counterpart has the effect of slowing down the heart rate (``rest and digest'') (Battipaglia \& Lanza, 2015).
-In addition to the autonomic nervous system and genetic factors, heart rate is influenced by numerous external factors such as social, personal, psychological, environmental and behavioural factors (Wang, Lizardo, \& Hachen, 2022).
-
-\hypertarget{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}{%
-\subsection{Wrist-worn devices as a new approach to assess physiological measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}
-
-Fuller et al. (2020) showed in their review article that wearable devices such as Fitbit watches are accurate and reliable for measuring heart rate in controlled settings.
-
-``The use of physiological measures enabled us to get some insight into teachers' affective responses without disrupting the teaching process (Mauss \& Robinson, 2009) and to reduce issues with social desirability, retrospective bias, and high cognitive load (Becker et al., 2015; Goetz et al., 2015; Scollon et al.,2009; Wilhelm \& Grossman, 2010).
-Moreover, we found that heart rate measures discriminated between both teachers, even when their interpersonal behavior during the lesson start was relatively similar.''
-
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{19}
-\tightlist
-\item
-  (PDF) A Quantitative Exploration of Two Teachers with Contrasting Emotions: Intra-Individual Process Analyses of Physiology and Interpersonal Behavior.
-Available from: \url{https://www.researchgate.net/publication/329787434_A_Quantitative_Exploration_of_Two_Teachers_with_Contrasting_Emotions_Intra-Individual_Process_Analyses_of_Physiology_and_Interpersonal_Behavior} {[}accessed Dec 07 2022{]}.
-\end{enumerate}
-
-\hypertarget{aim-of-the-study}{%
-\subsection{Aim of the study}\label{aim-of-the-study}}
-
-In the present study, we assessed HR measures and self-report data of pre- and in-service teachers in a controlled teaching-learning setting.
-The aim was to investigate whether heart rate measurements using wrist-worn fitness trackers are a suitable and effective method \textbf{(1)} to map differences in states of arousal between five different phases (pre-teaching phase, teaching phase, post-teaching phase, interview phase and end phase) and \textbf{(2)} to evaluate the correlation between self-reported evaluations and HR measures.
-
-\textbf{(H1)} We expected heart rates to be higher during the teaching phase than during the pre- and the three post-teaching phases, and that the HR measures would decrease over the course of the study.
-\textbf{(H2)} We also predicted that HR and a high ranking on the negative scale on our survey (feeling disturbed by disruptions) would correlate positively and a high ranking on the positive scale (feeling confident in dealing with disruptions) would follow the inverse pattern.
 
@@
 
-The sample consisted in total of \emph{N} = 63 pre- and in-service teachers.
-The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
-Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 61 subjects.
-
-The subjects (39 women; 63.93 \%) had a mean age of 29.60 years (\emph{SD} = 10.40; range: 19-59) and an average teaching experience of 4.66 years (\emph{SD} = 9.30; range: 0-37).
-
-18.03\% of the subjects were (studying to become) teachers for primary school, 72.13\% were (studying to become) teachers for secondary school and 9.84\% were (studying to become) teachers for special education needs.
-
-All study procedures were carried out in accordance with the ethical standards of the University's Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
-All participants were informed in detail about the aim and intention of the study prior to testing.
-Participation in the study was voluntary and only took place after written consent has been given.
-
 \hypertarget{material}{%
 \subsection{Material}\label{material}}
-
-\hypertarget{teachers-heart-rate}{%
-\subsubsection{Teachers' heart rate}\label{teachers-heart-rate}}
-
-We used a Fitbit Charge 4 to measure the teachers' heart rate.
-The device was attached 2-finger widths above the ulnar styloid process to the subject's wrist following the manufacturer's instructions.
-To determine the heart rate, the Fitbit flashes green LEDs many times per second and uses light-sensitive photodiodes to measure the volume changes in the capillaries and then calculates how many times the heart beats per minute (bpm).
-Data were automatically wireless synced with an iPad via Bluetooth to a Fitbit account, and subsequently, the intraday second-by-second data were exported for each session using the opensource software Pulse Watch (PulseWatch.
-URL: \url{https://iccir919.github.io/pulseWatch/public/index.html} {[}accessed 2022-08-03{]}).
-
-\hypertarget{teachers-self-reported-data-of-arousal-during-the-teaching-phase}{%
-\subsubsection{Teachers' self-reported data of arousal during the teaching phase}\label{teachers-self-reported-data-of-arousal-during-the-teaching-phase}}
-
-The subject's self-reported data of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.
-For this purpose, two numerical 11-point rating scales were used: \emph{(1)} The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption (``On a scale of 0-10: how disruptive did you find the event?
-0 is not disruptive at all, 10 is extremely disruptive'') \emph{(2)} The second rating scale assessed the teacher's subjective perception of confidence in dealing with the disruptions during the lesson (``How confident did you feel in dealing with this event on a scale of 0-10?
-0 is not confident at all and 10 is extremely confident'').
-
-The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjects' self-report and emotional experience, and thus to make them measurable and comparable (Döring \& Bortz, 2016; Eid, Gollwitzer, \& Schmitt, 2015).
-The gradations of the rating scale were unambiguous and the intervals between them identical.
-The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally to the experimenter.
 
@@
 
-The data collection was part of a larger research project with a planned sample of \emph{n} = 40 in-service teachers and \emph{n} = 40 pre-service teachers.
-
-The study took place in the rooms of the Faculty of Education at Leipzig University.
-In a controlled laboratory setting, heart rate data in beats per minute (bpm) were recorded using Fitbit Charge 4 over a total period of approximately two hours.
-Within this time frame, teachers taught a 15-minute self-prepared lesson to an audience of three actors.
-
-For this purpose, a seminar room was converted into a classroom.
-The classroom was equipped with a digital whiteboard and a blackboard.
-The fictitious class consisting of three trained actors sat facing the teacher head-on in a ``U''; pen and paper were provided on their seats.
-In addition, the students brought their own mobile phone, which was also visibly positioned on the desk.
-
-The subject was instructed during the lesson to behave and move as naturally as possible, as they would in a real classroom.
-In advance, all subjects were given information about planning their lesson in a meeting to ensure that an appropriately realistic teaching situation could take place, e.g.~it was pointed out that longer film clips as well as group work as a social form should be avoided in order to ensure interaction between teacher and students in the short time of the study.
-
-For analyzing the heart rate data, we focused on five 10-minute intervals of theoretical interest for multiple reason.
-First, 10 minutes was to the minimum duration of all intervals, so we wanted to ensure the comparability of the intervals for all participants.
-Second, Lu et al.
-(2008) confirmed in their study that 10-minute intervals are an useful duration for analyzing photoplethysmography (PPG) data.
-Third, other studies revealed that the first minutes of the lesson start are essential regarding teacher-student interaction (Claessens et al., 2017; Donker, Van Gog, \& Mainhard, 2018).
-
-The procedure of the study and how we calculated the five phases is described in the following:
-
-\emph{(1)} The \emph{pre-teaching phase} was the first 10-minute interval of interest.
-This interval was calculated from the moment the subject arrived and the Fitbit watch was put on, which happened immediately after the subject was welcomed by the experimenter and the three actors.
-After the experimenter briefly explained the project and the procedure of the study to the subject, contact details were subsequently collected as part of the hygiene concept of COVID-19 and the written consent to voluntarily participate in the study was requested.
-Next, the subject was asked to prepare the necessary materials for the lesson (connecting the laptop to the beamer, preparing worksheets, etc.).
-This phase varied in duration according to the prepared lesson (about 1-5min on average).
-
-Once the preparation was completed, the eye-tracking glasses were briefly explained to the subject as well as the adjustment made to the subject by the experimenter (changing the lenses or the nose pad if necessary).
-Subsequently, a 1-point calibration of the eye-tracking glasses took place and together with further devices (GoPro camera, 3D camera, audio recorder) the recordings were started.
-
-Before the lesson began, a warm-up phase took place to familiarize the subject with the laboratory setting and equipment. This warm-up phase consisted of two parts:
-
-\begin{itemize}
-\tightlist
-\item
-  In the first part, the subject and the three actors playfully learned each other's names.
-Additional fictitious name tags of the actors were attached to the table and did not change across the study.
-In the game, by throwing two balls, either the participant's own name or the name of the target person was called.
-\item
-  The second part of the warm-up phase involved getting into conversation with each other by asking questions.
-For this purpose, the subject was asked to come up with a question for each of the actors (three questions in total) and was also asked a question in return by each actor.
-This could be anything that interested the participants.
-The questions should be as authentic as possible and were not tailored to the role of the actors.
-  The purpose of this warming-up phase was, on the one hand, to make the subject forget about the devices and, on the other hand, to create as realistic as possible a classroom situation in which interactions were based on a teacher-student relationship.
-\end{itemize}
-
-The pre-teaching phase lasted 10-15 minutes on average, depending on different issues (preparing the lesson, technical problems, adjusting the eye-tracking glasses).
-
-\emph{(2)} The second 10-minute interval was the \emph{teaching phase}, which began with the experimenter noting the time and step count of the fitness tracker.
-The subject was then asked to carry out a 9-point calibration alone in a room next door.
-After the calibration, the lesson started with the subject opening the door to the laboratory room.
-During the lesson, the actors were instructed to simulate nine typical classroom events, three each in the following categories: (a) verbal disruptive behavior (chatting with the neighbor, whispering, heckling), (b) physical disruptions (clicking with a pen, drumming with hands on the table, snipping) and (c) lack of eagerness to learn (drawing on a sheet of paper, putting the head on the table, looking at the phone).
-
-The order of the events and the performing actors were fully balanced with Latin square. The actors were trained before to perform the disruptions identically in each data collection.
-
-After a short familiarization phase for the teacher of two and a half minutes, the instructions appeared as intervals (every 90 seconds for 30 seconds) on a screen that was only visible for the class.
-The actors were trained to stop the disruptive behavior as soon as the teacher intervened.
-
-Time management was regulated by the experimenter by showing time cards (yellow = 1 minute until the end; red = end of the lesson).
-The lesson lasted about 18 minutes on average but only the first 10 minutes were used as an interval to ensure the identical duration for all participants.
-At the end of the lesson, the experimenter again noted the time and the steps on the clock.
-
-\emph{(3)} The noted time of the lesson end was also the starting point for the \emph{post-teaching} phase as the third 10-minute interval.
-At the end of the lesson, the experimenter attached letters A through D in the lab while the teacher performed a second 9-point calibration outside.
-The letter search as a control condition was part of another project, which is why it will not be discussed further in the study.
-Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree; EMU, Helmke et al.
-(2014)) via the online survey website SoSci Survey.
-The completion of the questionnaire took approximately 5 minutes.
-
-Meanwhile, the experimenter prepared the second part of the data collection: The Stimulated Recall Interview.
-Within post-teaching phase, the majority of subjects completed the questionnaire and positioned themselves next to the experimenter to begin the interview.
-In some cases, the beginning of the interview was part of the post-teaching phase due to individual needs (going to the toilet, spending more time completing the questionnaire, etc.).
-
-\emph{(4)} The fourth 10-minute interval of interest was the \emph{interview phase} that was 10 minutes in the middle of the interview.
-To ensure that all subjects were in the middle of the interview, we calculated the difference from the end of the lesson and from the time when the subject took off the watch.
-This duration was divided in two to get to the middle of the interval.
-Then, 5 minutes were subtracted to get to the start of the 10-minute interval.
-
-The interview itself took place using the Think Aloud procedure (Konrad, 2020).
-For this purpose, the eye tracking video was watched again and the experimenter stopped the video at the nine disruptions when they appeared to asks several questions.
-The questions were identical for each disruption, they were asked in a fixed order.
-First, the subject was asked to describe the disruption, to evaluate (11-point rating scale) and justify the disruptiveness of each disruption.
-Next, the subject was asked to describe and justify the reaction.
-The experimenter then asked the subject to evaluate (11-point rating scale) and justify the confidence the subject had in dealing with the disruption.
-Statements about the evaluation of the disruptiveness and the confidence were quantified.
-For this purpose, subjects determined their individual value on a rating scale from 0 (not disturbing / not safe) to 10 (disturbing / safe).
-
-The interview lasted on average 45-60 minutes.
-
-\emph{(5)} The last interesting interval for the analyses was the \emph{end phase}, which was the 10 minutes before the subject took off the watch.
-In this interval, the subject answered a second questionnaire (Situational Judgment Test, Gold and Holodynski (2015)) to assess the subject's strategic knowledge of classroom management.
-The subject was asked to judge alternative actions on school scenarios on a 6-point rating scale from 1 (A) to 6 (F) according to school grades.
-Data from the questionnaire were again collected as an online questionnaire via the website www.soscisurvey.de and lasted approximately 10-15 minutes.
-
-The Fitbit watch was removed only after the last questionnaire to obtain heart rate data during the entire study.
-
 \hypertarget{data-analysis}{%
@@
 
-We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.36; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression).
-Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}.
-An alpha level of 0.05 was used for the statistical tests.
-
-\hypertarget{descriptive-statistics}{%
-\subsubsection{Descriptive statistics}\label{descriptive-statistics}}
-
-Means, standard deviations and the range of teachers' heart rate and the self-reported data are shown in Table 2.
-
-Teachers' average heart rate during the entire course of the study was approximately 96.26 bpm with a standard deviation of 14.22 and a range from 56 to 139 bpm.
-
-Means, standard deviations and the range of teachers' heart rate for the different phases and the self-reported data are shown in Table 2.
-
-\hypertarget{pairwaise-t-test-and-effect-size}{%
-\subsubsection{Pairwaise t-test and effect size}\label{pairwaise-t-test-and-effect-size}}
-
-\hypertarget{multilevel-regressions}{%
-\subsubsection{Multilevel regressions}\label{multilevel-regressions}}
-
-XXX
+We used R (Version 4.1.2; R Core Team, 2020) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2020), \emph{forcats} (Version 0.5.1; Wickham, 2020a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2020), \emph{tidyr} (Version 1.2.0; Wickham, 2020b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.4.0; Garnier, 2018b) for all our analyses.
 
@@
 
-\hypertarget{first-visual-results}{%
-\section{First visual results}\label{first-visual-results}}
-
-The graph @ref(fig:overall\_plot) show the heart rate for the entire course of the study.
-
-\includegraphics{fitbit_paper_files/figure-latex/overall_plot-1.pdf}
-
-The second graph @ref(fig:phase\_plot) show the heart rate for the individual five phases.
-
-\includegraphics{fitbit_paper_files/figure-latex/phase_plot-1.pdf}
-
-\hypertarget{discussion-and-implications}{%
-\section{Discussion and implications}\label{discussion-and-implications}}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-ALDRUP2018126}{}}%
-Aldrup, K., Klusmann, U., Lüdtke, O., Göllner, R., \& Trautwein, U.
-(2018).
-Student misbehavior and teacher well-being: Testing the mediating role of the teacher-student relationship.
-\emph{Learning and Instruction}, \emph{58}, 126--136.
-https://doi.org/\url{https://doi.org/10.1016/j.learninstruc.2018.05.006}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-DescTools}{}}%
-Andri et mult. al., S. (2022). \emph{{DescTools}: Tools for descriptive statistics}. Retrieved from \url{https://cran.r-project.org/package=DescTools}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
-Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-gridExtra}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
-Bates, D., Mächler, M., Bolker, B., \& Walker, S.
-(2015).
-Fitting linear mixed-effects models using {lme4}.
-\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
-\url{https://doi.org/10.18637/jss.v067.i01}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
-Bates, D., Maechler, M., \& Jagan, M. (2022). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Battipaglia2015}{}}%
-Battipaglia, I., \& Lanza, G.
-A.
-(2015).
-The autonomic nervous system of the heart.
-In R.
-H.
-J.
-A.
-Slart, R.
-A.
-Tio, P.
-H.
-Elsinga, \& M.
-Schwaiger (Eds.), \emph{Autonomic innervation of the heart: Role of molecular imaging} (pp.
-1--12).
-Berlin, Heidelberg: Springer Berlin Heidelberg.
-\url{https://doi.org/10.1007/978-3-662-45074-1_1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-lm.beta}{}}%
-Behrendt, S. (2022). \emph{Lm.beta: Add standardized regression coefficients to lm-objects}. Retrieved from \url{https://CRAN.R-project.org/package=lm.beta}
-
-\leavevmode\vadjust pre{\hypertarget{ref-claessens2017positive}{}}%
-Claessens, L.
-C., Tartwijk, J.
-van, Want, A.
-C.
-van der, Pennings, H.
-J., Verloop, N., Brok, P.
-J.
-den, \& Wubbels, T.
-(2017).
-Positive teacher--student relationships go beyond the classroom, problematic ones stay inside.
-\emph{The Journal of Educational Research}, \emph{110}(5), 478--493.
-
-\leavevmode\vadjust pre{\hypertarget{ref-donker2018quantitative}{}}%
-Donker, M.
-H., Van Gog, T., \& Mainhard, M.
-T.
-(2018).
-A quantitative exploration of two teachers with contrasting emotions: Intra-individual process analyses of physiology and interpersonal behavior.
-\emph{Frontline Learning Research}, \emph{6}(3), 162--184.
-
-\leavevmode\vadjust pre{\hypertarget{ref-doring2016empirische}{}}%
-Döring, N., \& Bortz, J. (2016). Empirische sozialforschung im {Ü}berblick. In \emph{Forschungsmethoden und evaluation in den sozial-und humanwissenschaften} (pp. 3--30). Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-eid2015statistik}{}}%
-Eid, M., Gollwitzer, M., \& Schmitt, M.
-(2015).
-\emph{Statistik und forschungsmethoden: Mit online-materialien (4., {ü}berarb.
-Und erw.
-aufl.)}.
-Weinheim: Beltz.
-Retrieved from https://contentselect.
-com/media/moz\_viewer~\ldots.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ertzberger2016use}{}}%
-Ertzberger, J., \& Martin, F. (2016). Use of fitness bands by teachers in the classroom. \emph{TechTrends}, \emph{60}(4), 392--397.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ferguson2015validity}{}}%
-Ferguson, T., Rowlands, A.
-V., Olds, T., \& Maher, C.
-(2015).
-The validity of consumer-level, activity monitors in healthy adults worn in free-living conditions: A cross-sectional study.
-\emph{International Journal of Behavioral Nutrition and Physical Activity}, \emph{12}(1), 1--9.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-janitor}{}}%
-Firke, S. (2021). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-polycor}{}}%
-Fox, J. (2022). \emph{Polycor: Polychoric and polyserial correlations}. Retrieved from \url{https://CRAN.R-project.org/package=polycor}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fuller2020reliability}{}}%
-Fuller, D., Colwell, E., Low, J., Orychock, K., Tobin, M.
-A., Simango, B., et al.others.
-(2020).
-Reliability and validity of commercially available wearable devices for measuring steps, energy expenditure, and heart rate: Systematic review.
-\emph{JMIR mHealth and uHealth}, \emph{8}(9), e18694.
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
-Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}
 
 \leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
-Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gold2015development}{}}%
-Gold, B., \& Holodynski, M.
-(2015).
-Development and construct validation of a situational judgment test of strategic knowledge of classroom management in elementary schools.
-\emph{Educational Assessment}, \emph{20}(3), 226--248.
+Garnier, S. (2018b). \emph{viridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}}%
-Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M.
-(2014).
-Unterrichtsdiagnostik mit EMU.
-\emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
 Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-msm}{}}%
-Jackson, C.
-H.
-(2011).
-Multi-state models for panel data: The {msm} package for {R}.
-\emph{Journal of Statistical Software}, \emph{38}(8), 1--29.
-Retrieved from \url{https://www.jstatsoft.org/v38/i08/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggpubr}{}}%
-Kassambara, A. (2020). \emph{Ggpubr: 'ggplot2' based publication ready plots}. Retrieved from \url{https://CRAN.R-project.org/package=ggpubr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-rstatix}{}}%
-Kassambara, A. (2021). \emph{Rstatix: Pipe-friendly framework for basic statistical tests}. Retrieved from \url{https://CRAN.R-project.org/package=rstatix}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-ppcor}{}}%
-Kim, S. (2015). \emph{Ppcor: Partial and semi-partial (part) correlation}. Retrieved from \url{https://CRAN.R-project.org/package=ppcor}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kyriacou2001teacher}{}}%
-Kyriacou, C. (2001). Teacher stress: Directions for future research. \emph{Educational Review}, \emph{53}(1), 27--35.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-jtools}{}}%
-Long, J. A. (2022). \emph{Jtools: Analysis and presentation of social scientific data}. Retrieved from \url{https://cran.r-project.org/package=jtools}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lowe2016educational}{}}%
-Lowe, H. (2016). Educational behavior apps and wearable devices: Current research and prospects. \emph{Educational Technology}, 30--33.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lu2008can}{}}%
-Lu, S., Zhao, H., Ju, K., Shin, K., Lee, M., Shelley, K., \& Chon, K.
-H.
-(2008).
-Can photoplethysmography variability serve as an alternative approach to obtain heart rate variability information?
-\emph{Journal of Clinical Monitoring and Computing}, \emph{22}(1), 23--29.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-imputeTS}{}}%
-Moritz, S., \& Bartz-Beielstein, T. (2017). {imputeTS: Time Series Missing Value Imputation in R}. \emph{{The R Journal}}, \emph{9}(1), 207--218. \url{https://doi.org/10.32614/RJ-2017-009}
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
-Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+Müller, K., \& Wickham, H. (2020). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2022). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ltm}{}}%
-Rizopoulos, D.
-(2006).
-Ltm: An r package for latent variable modelling and item response theory analyses.
-\emph{Journal of Statistical Software}, \emph{17}(5), 1--25.
-Retrieved from \url{https://doi.org/10.18637/jss.v017.i05}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-broom}{}}%
-Robinson, D., Hayes, A., \& Couch, S. (2022). \emph{Broom: Convert statistical objects into tidy tibbles}. Retrieved from \url{https://CRAN.R-project.org/package=broom}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rungeusing}{}}%
-Runge, N., Haarman, S., \& Fisher, M. H. (n.d.). \emph{Using fitbit fitness trackers to measure teacher stress and coping}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sachs2014physiologische}{}}%
-Sachs, S. (2014). \emph{Physiologische parameter zur bewertung der lernwirksamkeit von lernsituationen} (PhD thesis). Universit{ä}t Ulm.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-MASS}{}}%
-Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wang2022using}{}}%
-Wang, C., Lizardo, O., \& Hachen, D. S. (2022). Using fitbit data to monitor the heart rate evolution patterns of college students. \emph{Journal of American College Health}, \emph{70}(3), 875--882.
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
-Wickham, H. (2021). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+Wickham, H. (2020a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
+Wickham, H. (2020b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
-Wickham, H., \& Bryan, J. (2022). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
+Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
 
 \leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2022). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
-Wickham, H., \& Girlich, M. (2022). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+Wickham, H., François, R., Henry, L., \& Müller, K. (2020). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
 
 \leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
-Wickham, H., Hester, J., \& Bryan, J. (2022). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-xfun}{}}%
-Xie, Y. (2022). \emph{Xfun: Supporting functions for packages maintained by 'yihui xie'}. Retrieved from \url{https://CRAN.R-project.org/package=xfun}
+\leavevmode\vadjust pre{\hypertarget{ref-R-ARTofR}{}}%
+Zhang, H. (2021). \emph{ARTofR: Who ever care about the {[}art of r{]} scripts?} Retrieved from \url{https://CRAN.R-project.org/package=ARTofR}
 

### 2023-04-21 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
update

--- 2023-02-14 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data.Rmd
@@
 ---
-title             : "The title"
-shorttitle        : "Title"
+title             : "Through the eyes of the teacher"
+shorttitle        : "Visual attention in teaching and learning processes"
 
 author: 
-  - name          : "First Author"
+  - name          : "Mandy Klatt"
     affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
-    role:
-      - Writing - Review & Editing
+    address       : "Dittrichring 5-7, 04109 Leipzig"
+    email         : "mandy.klatt@uni-leipzig.de"
+  - name          : "Dr. Gregor Kachel"
+    affiliation   : "1, 2"
+  - name          : "Dr. Christin Lotz"
+    affiliation   : "1"
+  - name          : "Prof. Dr. Anne Deiglmayr"
+    affiliation   : "1"
 
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "Leipzig University"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "Max-Planck University for Evolutionary Anthropology"
 
-keywords          : "keywords"
-wordcount         : "X"
+authornote: |
+  Ethics Approval
+  All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
+The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+
+  Consent to Participate
+  All participants gave informed consent.
+
+abstract: |
+
+keywords          : "Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking"
+wordcount         : "XXX"
 
@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 classoption       : "man"
-output            : bookdown::word_document2 #papaja::apa6_pdf
+output            : bookdown::word_document2
 ---
@@
 ```{r setup, include = FALSE}
-
+install.packages('papaja')
 library("papaja")
@@
 # prepare data (selected from questionnaire data)
-demo.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")
+demo.data <- readxl::read_xlsx("./data/data_empschul_labor_lehrperson.xlsx")
 
@@
 
-# changing gender female 2 = 0 
-demo.data$Gender = ifelse(demo.data$Gender == 2, "0","1")
+# changing gender female 2 = 1 
+demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")
 
@@
 demo.data$Gender <- as.numeric(demo.data$Gender)
+
+# #filter --> 121 two times
+# demo.data <-  demo.data[-c(28), ]
 
@@
   summarise(N=n(),
-            "Male" = sum(Gender),
+            "Female" = sum(Gender),
             "M Age" = round(mean(Age), 2),
@@
 ```
+
+## Material
+
+## Procedure
+
+## Data analysis
+We used `r cite_r("r-references.bib")` for all our analyses.
+
+# Results
+
+# Discussion
+
+\newpage
+
+# References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2023-04-21 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi.R

@@ -1,0 +1,362 @@
+### ProVisioNET Eyetracking AOI Coding Data 
+
+library(needs)
+needs(tidyverse,
+      psych,
+      moments,
+      sjPlot,
+      DescTools,
+      irr,
+      readxl, 
+      gridExtra,
+      janitor)
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+
+# read in expert data
+expert_aoi1 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_202_203_204_interval_complete.tsv",
+                       locale = locale(decimal_mark = ","))
+
+expert_aoi2 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_205_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+expert_aoi3 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_206_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+expert_aoi4 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_207_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+# combine the expert df
+expert_aoi <- rbind(expert_aoi1, 
+                    expert_aoi2, 
+                    expert_aoi3, 
+                    expert_aoi4)
+                    
+
+
+# read in novice data
+novice_aoi1 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_101_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+                      
+novice_aoi2 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_102_103_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+novice_aoi3 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_104_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+novice_aoi4 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_105_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+novice_aoi5 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_106_107_interval_complete.tsv",
[…]

### 2023-04-21 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/kopie/read_data_auto.R

@@ -25,7 +25,12 @@ for (i in file_names) {
 
     work_data <- 
     read_tsv(file = paste0("data/", i),
+<<<<<<< Updated upstream
                           locale = locale(decimal_mark = ","))
+=======
+                          locale = locale(decimal_mark = ",")) %>% 
+      select(!"Minimum_amplitude_of_saccades")
+>>>>>>> Stashed changes
   
   assign(value = work_data,
          x = str_remove(paste0("tib_", i),

### 2023-04-21 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R

@@ -15,6 +15,7 @@ needs(tidyverse,
 options(dplyr.summarise.inform = FALSE)
 
 
+<<<<<<< Updated upstream
 # Return a character vector with names of .tsv data in data folder
 
 file_names <- list.files(path = "data",
@@ -48,7 +49,78 @@ rm(list = ls(pattern = "^tib_ProVisio"))
 rm(work_data)
 rm(file_names)
 rm(i)
+=======
+# read in expert data
+expert_toi1 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_202_203_204_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
 
+expert_toi2 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_205_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+expert_toi3 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_206_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+expert_toi4 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_207_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+# combine the expert df
+expert_toi <- rbind(expert_toi1, 
+                    expert_toi2, 
+                    expert_toi3, 
+                    expert_toi4)
+
+
+
+# read in novice data
+novice_toi1 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_101_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+novice_toi2 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_102_103_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+novice_toi3 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_104_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+novice_toi4 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_105_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+novice_toi5 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_106_107_interval_complete.tsv",
+                        locale = locale(decimal_mark = ","))
+
+
[…]

### 2023-04-21 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -89,12 +89,19 @@ dist_group_plot <-
   theme_cowplot() + 
   theme(
     legend.position="none",
+<<<<<<< Updated upstream
     axis.text.x = element_text(size = 23),
     axis.text.y = element_text(size = 18),
     axis.title.y = element_text(size = 25),
     plot.title = element_text(size = 25, 
                               face = "bold"),
     )
+=======
+    axis.text.x = element_text(size = 15),
+    plot.title = element_text(size = 19, face = "bold"),
+    axis.text.y = element_text(size = 15),
+    axis.title.y = element_text(size = 15))
+>>>>>>> Stashed changes
 
 dist_group_plot
 
@@ -105,6 +112,7 @@ ggsave(plot = dist_group_plot,
        units = "in")
 
 
+<<<<<<< Updated upstream
 # # plotting Disruption factor for 3 disruptions sum up
 # sri_disrup$Event[sri_disrup$Event == "chatting" |
 #                    sri_disrup$Event == "heckling" |
@@ -154,6 +162,55 @@ ggsave(plot = dist_group_plot,
 # 
 # sri_disrup_sum
 # 
+=======
+# plotting Disruption factor for all disruptions
+dist_plot <- 
+  sri_disrup %>% 
+  mutate(Event = factor(Event,
+                      levels = c("chatting",
+                                 "whispering",
+                                 "heckling",
+                                 "snipping",
+                                 "drumming",
+                                 "clicking",
+                                 "looking at phone",
+                                 "head on table",
+                                 "drawing"
+                      ),
+                      labels = c("Chatting",
+                                 "Whispering",
+                                 "Heckling",
+                                 "Snipping",
+                                 "Drumming",
+                                 "Clicking pen",
+                                 "Looking at phone",
+                                 "Head on table",
+                                 "Drawing"
+                      )
+  )) %>%
+  ggplot(data = sri_disrup,
+         mapping = aes(x = Group,
+                       y = Disruption_Factor)) +
+  geom_boxplot(mapping = aes(fill = Group)) +
+  geom_point(size = 2, 
+             alpha = 0.4,
+             position = position_jitter(seed = 1, 
+                                        width = 0.1,
+                                        height = 0)) +
+  labs(x = "",
+       y = "Disruption Factor") + 
+  ylim(0,10)+
+  scale_fill_brewer(palette = "Set1") +
+  facet_wrap(vars(Event), 
[…]

### 2023-04-21 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest.R

@@ -1,0 +1,91 @@
+# load packages
+library(needs)
+needs(tidyverse,
+      lubridate,
+      viridis,
+      grid,
+      gridExtra,
+      cowplot,
+      readxl,
+      ARTofR)
+
+# read in data
+df_sjt <- read_csv2(file = "C:/Users/mk99feta/OneDrive/Dokumente/GitHub/Mandy-PhD/01_studies/01_Laborstudie ProVisioNET/SJTest/data/SJT.csv")
+
+# select relevant columns --> only mean
+df_sjt <- df_sjt %>% select(UI06_05, SJT_AL_gek, SJT_ST_gek, SJT_R_gek, SJT_KF_gek)
+
+# rename columns
+df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
+                           "Monitoring" = "SJT_AL_gek",
+                           "Managing momentum" = "SJT_ST_gek",
+                           "Rules and routines" = "SJT_R_gek",
+                           "All" = "SJT_KF_gek"))
+
+# remove NAs
+df_sjt <- na.omit(df_sjt)
+
+# changing from wide to long format
+df_sjt_long <- df_sjt %>% 
+  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")
+
+# define expert and novice with ifelse function
+df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")
+
+# plotting mean of all aspects 
+mean_plot <- 
+  ggplot(data = df_sjt_long,
+         mapping = aes(x = Group,
+                       y = Mean)) +
+  geom_boxplot(mapping = aes(fill = Group)) +
+  geom_point(size = 2, 
+             alpha = 0.4,
+             position = position_jitter(seed = 1, 
+                                        width = 0.1)) +
+  labs(x = "") +
+  ylim(0,1) + 
+  scale_fill_brewer(palette = "Set1") +
+  facet_wrap(vars(`Facets Classroom Management`), 
+             nrow = 1, strip.position = "bottom") +
+  theme_classic()+
+  ggtitle("Situational Judgment Test of Strategic Knowledge of Classroom Management") +
+  theme(
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    strip.text.x = element_text(size = 14),
+    axis.title.y = element_text(size = 16))
+
+mean_plot
+
[…]

### 2023-04-21 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
dgnysfgn

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
-# bookdown::word_document2 
+output            : bookdown::word_document2 
+# papaja::apa6_pdf
+
 ---
@@
   filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
-                    "132")
+                    "132",
+                    "236")
          )
@@
   filter(!ID %in% c("126",
-                     "132"
+                     "132",
+                    "236"
                      )

### 2023-04-21 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
dgnysfgn

@@
 \midrule
-70 & 60.00 & 29.74 & 10.67 & 19.00 & 59.00 & 4.84 & 9.31 & 0.00 & 37.00\\
+78 & 62.82 & NA & NA & NA & NA & NA & NA & NA & NA\\
 \bottomrule
@@
 
-The sample consisted in total of \emph{N} = 72 pre- and in-service teachers.
+The sample consisted in total of \emph{N} = 80 pre- and in-service teachers.
 The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
-Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 70 subjects.
+Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 78 subjects.
 
-The subjects (42 women; 60 \%) had a mean age of 29.70 years (\emph{SD} = 10.70; range: 19-59) and an average teaching experience of 4.84 years (\emph{SD} = 9.31; range: 0-37).
+The subjects (49 women; 62.82 \%) had a mean age of NA years (\emph{SD} = NA; range: NA-NA) and an average teaching experience of NA years (\emph{SD} = NA; range: NA-NA).
 
-17.14\% of the subjects were (studying to become) teachers for primary school, 70\% were (studying to become) teachers for secondary school and 11.43\% were (studying to become) teachers for special education needs.
+15.38\% of the subjects were (studying to become) teachers for primary school, 69.23\% were (studying to become) teachers for secondary school and 10.26\% were (studying to become) teachers for special education needs.
 

### 2023-04-23 02_paper/02_study/02_fitbit paper/analysis_190423.Rmd
update analysis

---
title: "Analysis 19.04.2023"
author: "Peer Keßler"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, warning = FALSE)
```

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
    #  lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse)

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  dplyr::select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confidence_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         )

# demographic data
df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
  transmute(ID = LI06_05, # select and rename relevant columns 
            gender = factor(LI02_01_1,
                            levels = 1:2,
                            labels = c("male","female")
                            ),
            age = LI03_01, # 1 = male; 2 = female
            teaching_experience = LI04_01)

# merge two data frames by ID 
df_merge <- merge(df_demo,
                  df_rating,
                  by = "ID") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132")
         )

# rm(list = c("df_demo","df_rating"))

data_path <- "./data/heart_rate_data"

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
                               str_detect(string = id, pattern = "_m") ~ "teaching",
                               str_detect(string = id, pattern = "_p") ~ "preparation",
                               str_detect(string = id, pattern = "_s") ~ "post",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
      # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 7200) %>% # filter for 2 hours 30min (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

main <-
  left_join(main, df_merge,
            by = "ID")

main <- 
  main %>% 
  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>% 
  right_join(x = .,
             y = main,
             by = "ID") %>% 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart) %>% 
  filter(!(time_span == "teaching" & time > 600))

```

# Graph

```{r fig.width = 10,results='hide',fig.keep='all'}
loess_plot_overall <-
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate_std
                       )
         ) +
  # geom_point(alpha = 0.05) + 
  geom_smooth(se = FALSE,
              size = 0.5,
              colour = "black") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0, NA),
                     breaks = seq(0, 9000, 600)) +
  scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
  labs(x = "Time (in Seconds)",
       y = "") +
  ggtitle("Overall Course of Average Heartrate") +
  theme_apa() + 
  theme(axis.title.y = element_blank())

lm_plot_phases <-
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
  mutate(time_span = factor(time_span,
                            levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase"))) %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate_std
                       )
         ) +
  # geom_point(alpha = 0.05) + 
  geom_smooth(method = "lm",
              se = FALSE,
              size = 0.5,
              colour = "black") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  # scale_x_continuous(expand = c(0, NA),
  #                    breaks = seq(0, 9000, 600)) +
  #scale_y_continuous(breaks = seq(0, 160, 5)) + 
  labs(x = "Time (in Seconds)",
       y = "",
       subtitle = "Linear Estimation") +
  theme_apa() +
  theme(axis.title.y = element_blank()) +
  facet_grid(cols = vars(time_span),
             scales = "free_x")

ki_plot_phases <-
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
  mutate(time_span = factor(time_span,
                            levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase"))) %>% 
  distinct() %>%
  group_by(time_span) %>% 
  summarise(z_mean = mean(heart_rate_std),
            z_sd = sd(heart_rate_std),
            z_t = qt(p = 0.01 / 2,      # 0.01 KI
               df = n() - 1,
               lower.tail = F
               ),
            z_error = z_sd / sqrt(n()),
            lower = z_mean - z_t * z_error,
            upper = z_mean + z_t * z_error,
            ) %>% 
  ungroup() %>% 
  ggplot(mapping = aes(x = factor(0),
                       y = z_mean)) + 
  geom_point() +
  geom_errorbar(mapping = aes(ymin = lower,
                              ymax = upper),
                width = 0.2) +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  labs(subtitle = "1% Confidence Intervall",
       x = "") +
  facet_grid(cols = vars(time_span)) +
  theme_apa() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank())

text_y <- text_grob("Average Heart Rate (Standardized)",
                   rot = 90)

plot_overall <-
  grid.arrange(loess_plot_overall, lm_plot_phases, ki_plot_phases,
               ncol = 1,
               left = text_y
               )

plot_overall
```

# Correlation

```{r, warning=FALSE}
cache_corr <- 
  main %>% 
  clean_names() %>% 
  group_by(id) %>% 
  dplyr::summarize(`Mean Heartrate` = mean_heart,
            `Age` = age,
            `Teaching Experience` = teaching_experience,
            `Disruption Factor` = mean(disruption_factor, na.rm = T),
            `Confidence Factor` = mean(confidence_factor, na.rm = T)
            ) %>% 
  ungroup() %>% 
  distinct() %>% 
  select(!"id")

res <- rcorr(as.matrix(cache_corr))

knitr::kable(res[1], caption = "Pearson r")
knitr::kable(res[3], caption = "p Value")
```

```{r warning=FALSE,message=FALSE,error=FALSE}
corrplot(res$r, type="upper", order="hclust", sig.level = 0.05)
```

# Slopes, Intercepts

```{r}
df_regression <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID", "time_span","time","heart_rate_std") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ))

table_data <- 
  df_regression %>% 
  split(.$Phase) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      ) %>%
  map(~ tibble(time_span = names(.),
               intercept = fixef(.)[[1]],
               intercept_sd = VarCorr(.) %>% as_tibble() %>% .[1,5],
               intercept_p = coef(summary(.))[1, 5],
               slope = fixef(.)[[2]],
               slope_sd = VarCorr(.) %>% as_tibble() %>% .[2,5],
               slope_p = coef(summary(.))[2, 5]
               )
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = round(intercept, digits = 3),
            `SD(Intercept)` = round(intercept_sd$sdcor, digits = 3),
            `p-Value (Intercept)` = round(intercept_p, digits = 3),
            `Mean(Slope)` = round(slope, digits = 3),
            `SD(Slope)` = round(slope_sd$sdcor, digits = 3),
            `p-Value (Slope)` = round(slope_p, digits = 3)
            )

table_data$n[table_data$Phase == "Pre Teaching Phase"] <- df_regression %>% filter(Phase == "Pre Teaching Phase") %>% pull(heart_rate_std) %>% length()
table_data$n[table_data$Phase == "Teaching Phase"] <- df_regression %>% filter(Phase == "Teaching Phase") %>% pull(heart_rate_std) %>% length()
table_data$n[table_data$Phase == "Post Teaching Phase"] <- df_regression %>% filter(Phase == "Post Teaching Phase") %>% pull(heart_rate_std) %>% length()
table_data$n[table_data$Phase == "Interview Phase"] <- df_regression %>% filter(Phase == "Interview Phase") %>% pull(heart_rate_std) %>% length()
table_data$n[table_data$Phase == "End Phase"] <- df_regression %>% filter(Phase == "End Phase") %>% pull(heart_rate_std) %>% length()

table_data %>% 
  arrange(Phase) %>% 
knitr::kable(., caption = "Overview")
```

# t-Test (Teaching Phase vs. Interview Phase)

Results:

```{r}
cache1 <- 
  main %>% 
  dplyr::select("ID","time","heart_rate_std", "heart_rate", "time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ ranef(.)$ID %>% 
        as_tibble(., 
                  rownames = "ID"
                  ) %>% 
        clean_names()
      ) %>% 
  bind_rows(.,
            .id = "time_span")

cache2 <-  
  main %>% 
  dplyr::select("ID","time","heart_rate_std", "heart_rate","time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ summary(.) %>% 
        .$coefficients %>% 
        .[c(1,2)]) %>% 
  bind_rows(.,
            .id = "time_span") %>% 
  pivot_longer(
  cols = everything(),
  names_to = "time_span",
  values_to = "mean_value"
  )

df_test <- 
  tibble(mean_intercept = cache2$mean_value[1:6],
         mean_time = cache2$mean_value[7:12],
         time_span = cache2$time_span[1:6]) %>% 
  right_join(x = .,
             y = cache1,
             by = "time_span") %>% 
  transmute(time_span,
            intercept = mean_intercept + intercept,
            time = mean_time + time,
            id = id)

t.test(df_test$intercept[df_test$time_span == "teaching"],
       df_test$intercept[df_test$time_span == "interview"],
       paired = TRUE)
```

Cohen D:

```{r}
CohenD(x = df_test$intercept[df_test$time_span == "teaching"],
       y = df_test$intercept[df_test$time_span == "interview"],
       pooled = T
       )
```

# Graphs for all Phases

```{r}
mods <-   
  df_regression %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      )

graph_data <- 
  df_regression %>% 
  split(.$time_span)

example <- list(mod = mods$preparation, data = graph_data$preparation)

list(`Preparation Phase` = list(name = "Preparation Phase", mod = mods$preparation, data = graph_data$preparation),
     `Teaching Phase` = list(name = "Teaching Phase", mod = mods$teaching, data = graph_data$teaching),
     `Post Teaching Phase` = list(name = "Post Teaching Phase",mod = mods$post, data = graph_data$post),
     `Interview Phase` = list(name = "Interview Phase",mod = mods$interview, data = graph_data$interview),
     `End Phase` = list(name = "End Phase",mod = mods$end, data = graph_data$end)
     ) %>% 
  map(~ ggplot(data = .$data,
               mapping = aes(x = time,
                             y = heart_rate_std,
                             group = ID)) +
        geom_line(mapping = aes(y = fitted(.$mod)),
                  color = "blue",
                  size = 1) +
        geom_point(alpha = 0.5,
                   size = 0.5) +
        labs(title = .$name,
             y = "Heart Rate (Standardized)",
             x = "Time (in Seconds)") +
        facet_wrap( ~ ID, nrow = 6) +
        theme_apa()
      )
```

# Different endings

```{r fig.width = 10,results='hide',fig.keep='all'}
df_survival <- 
  main %>% 
  filter(time_span == "overall") %>% 
  select("time","ID") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(max_time = max(time)) %>% 
  ungroup()

df_survival_analysis <- 
  tibble(time = seq(max(df_survival$max_time),
              min(df_survival$max_time),
              by = -1),
         p = NA)

n <- length(df_survival$ID)

for (i in seq(min(df_survival$max_time),
              max(df_survival$max_time),
              by = 1)) {

  p <- 
    df_survival %>%
    filter(max_time >= i) %>%
    pull(max_time) %>%
    length(.)

  df_survival_analysis$p[df_survival_analysis$time == i] <- p/n

}

p_80 <- 
  df_survival_analysis %>% 
  filter(p > 0.8) %>% 
  pull(time) %>% 
  max(.)

p_90 <- 
  df_survival_analysis %>% 
  filter(p > 0.9) %>% 
  pull(time) %>% 
  max(.)

df_survival_analysis %>% 
  ggplot(mapping = aes(x = time,
                       y = p
                       )
         ) + 
  geom_line() +
  geom_hline(yintercept = 0.8,
             linetype = "dashed"
             ) +
  geom_hline(yintercept = 0.9,
             linetype = "dashed"
             ) +
  geom_vline(xintercept = p_80,
             linetype = "dashed"
             ) +
  geom_vline(xintercept = p_90,
             linetype = "dashed"
             ) +
  labs(x = "Time (in Seconds)",
       y = "Relative Frequency") +
  scale_x_continuous(breaks=c(4500, 5000, p_90, 5500, p_80, 6500, 7000)) +
  scale_y_continuous(breaks=c(0.25, 0.5, 0.75, 0.8, 0.9, 1)) +
  theme_apa()
```

```{r fig.width = 10,results='hide',fig.keep='all'}
loess_plot_data_90 <- 
  main %>% 
  filter(time_span == "overall" &
         time <= p_90) %>%
  dplyr::select("heart_rate", "ID", "time") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>% 
  right_join(x = .,
             y = distinct(select(main,
                          "ID","time_span", "time", "heart_rate"
                        )),
             by = "ID") %>% 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

loess_plot_data_80 <- 
  main %>% 
  filter(time_span == "overall" &
         time <= p_80) %>%
  dplyr::select("heart_rate", "ID", "time") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)
            ) %>%
  ungroup() %>%  
  right_join(x = .,
             y = distinct(select(main,
                          "ID","time_span", "time", "heart_rate"
                        )),
             by = "ID") %>%
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

loess_plot_data_all <- 
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("heart_rate", "ID", "time") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)
            ) %>%
  ungroup() %>%  
  right_join(x = .,
             y = distinct(select(main,
                          "ID","time_span", "time", "heart_rate"
                        )),
             by = "ID") %>%
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

ggplot(mapping = aes(x = time,
                            y = heart_rate_std
                            )) +
  geom_smooth(data = loess_plot_data_80,
              aes(color = "80%"),
              se = F
              ) +
  geom_smooth(data = loess_plot_data_90,
              aes(color = "90%"),
              se = F) +
  geom_smooth(data = loess_plot_data_all,
              aes(color = "Baseline"),
              linetype = "dashed",
              se = F) +
  labs(x = "Time (in Seconds)",
       y = "Average Heart Rate (Standardized)",
       color = "Legend") +
  scale_color_manual(values = c("80%" = "blue", "90%" = "red", "Baseline" = "black")) +
  theme_apa()
```

# Robustness

```{r fig.width = 10,results='hide',fig.keep='all'}
linear_plot_data_80 <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID","time_span", "time", "heart_rate") %>% 
  distinct() %>% 
  left_join(x = .,
            y = distinct(select(.data = loess_plot_data_80,
                       "ID", "mean_heart", "sd_heart")),
            by = "ID"
            ) %>% 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart,
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

linear_plot_data_90 <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID","time_span", "time", "heart_rate") %>% 
  distinct() %>% 
  left_join(x = .,
            y = distinct(select(.data = loess_plot_data_90,
                       "ID", "mean_heart", "sd_heart")),
            by = "ID"
            ) %>% 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart,
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

linear_plot_data_all <-
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
  distinct() %>% 
  mutate(Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ))

ggplot(mapping = aes(x = time,
                     y = heart_rate_std
                     )
       ) +
  # geom_point(alpha = 0.05) +
  geom_smooth(data = linear_plot_data_80,
              method = "lm",
              se = FALSE,
              size = 0.5,
              mapping = aes(color = "80%")
              ) +
  geom_smooth(data = linear_plot_data_90,
              method = "lm",
              se = FALSE,
              size = 0.5,
              mapping = aes(color = "90%")
              ) +
  geom_smooth(data = linear_plot_data_all,
              method = "lm",
              se = FALSE,
              size = 0.5,
              linetype = "dashed",
              mapping = aes(color = "Baseline")
              ) +
  scale_color_manual(values = c("80%" = "blue", "90%" = "red", "Baseline" = "black")) + 
  labs(x = "Time (in Seconds)",
       y = "Average Heart Rate (Standardized)",
       color = "") +
  facet_grid(cols = vars(Phase)) +
  theme_apa()
```

### 2023-04-24 02_paper/02_study/02_fitbit paper/analysis_190423.Rmd
update analysis

@@
   df_regression %>% 
+#  mutate(time = time * 60) %>% 
   split(.$Phase) %>% 
@@
        paired = TRUE)
+
+t.test(df_test$intercept[df_test$time_span == "teaching"],
+       df_test$intercept[df_test$time_span == "end"],
+       paired = TRUE)
 ```
@@
        y = df_test$intercept[df_test$time_span == "interview"],
+       pooled = T
+       )
+
+CohenD(x = df_test$intercept[df_test$time_span == "teaching"],
+       y = df_test$intercept[df_test$time_span == "end"],
        pooled = T
@@
 ```
+
+```{r}
+
+loess_plot_overall <-
+  main %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0, NA),
+                     breaks = seq(0, 9000, 600)) +
+  scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
+  labs(x = "Time (in Seconds)",
+       y = "") +
+  ggtitle("Overall Course of Average Heartrate") +
+  theme_apa() + 
+  theme(axis.title.y = element_blank())
+```
+
+t-Test mit Mittelwerten -> teaching vs. interview & teaching vs. end & interview vs. end

### 2023-04-27 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
update_analysis

--- 2023-04-23 02_paper/02_study/02_fitbit paper/analysis_190423.Rmd
@@
 ---
-title: "Analysis 19.04.2023"
-author: "Peer Keßler"
-date: "`r Sys.Date()`"
-output: html_document
+title: "R Notebook"
+output: html_notebook
 ---
@@
       ggpubr,
-    #  lme4,
+      lme4,
       lmerTest,
@@
 
-# Correlation
-
-```{r, warning=FALSE}
-cache_corr <- 
-  main %>% 
-  clean_names() %>% 
-  group_by(id) %>% 
-  dplyr::summarize(`Mean Heartrate` = mean_heart,
-            `Age` = age,
-            `Teaching Experience` = teaching_experience,
-            `Disruption Factor` = mean(disruption_factor, na.rm = T),
-            `Confidence Factor` = mean(confidence_factor, na.rm = T)
-            ) %>% 
-  ungroup() %>% 
-  distinct() %>% 
-  select(!"id")
-
-res <- rcorr(as.matrix(cache_corr))
-
-knitr::kable(res[1], caption = "Pearson r")
-knitr::kable(res[3], caption = "p Value")
-```
-
-```{r warning=FALSE,message=FALSE,error=FALSE}
-corrplot(res$r, type="upper", order="hclust", sig.level = 0.05)
-```
-
-# Slopes, Intercepts
+# Slopes and Intercepts
 
@@
   filter(time_span != "overall") %>%
-  dplyr::select("ID", "time_span","time","heart_rate_std") %>% 
+  dplyr::select("ID", "time_span","time","heart_rate_std","heart_rate") %>% 
   distinct() %>% 
+  mutate(time = time / 60) %>% 
   mutate(ID = as_factor(ID),
@@
                             labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
-                           ))
+                           )
+         )
+
+fix_models <-
+  df_regression %>%
+  split(.$Phase) %>%
+  map( ~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
+            data = .)) %>%
+  map(
+    ~ coef(.) %>%
+      tibble::as_tibble(.,
+                        rownames = "name") %>%
+      transmute(
+        type = if_else(str_detect(name,
+                                  ":"),
+                       true = "slope",
+                       false = "intercept"),
+        id = str_remove_all(name,
+                            "[^[:digit:]]"),
+        value = value
+      ),
+
+  ) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_wider(names_from = type,
+              values_from = value)
+
+p.values_slope <-
+  fix_models %>%
+  split(.$Phase) %>%
+  map( ~ t.test(x = .$slope,
+                mu = 0)$p.value) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_slope")
+
+p.values_intercept <-
+  fix_models %>%
+  split(.$Phase) %>%
+  map( ~ t.test(x = .$intercept,
+                mu = 0)$p.value) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_intercept")
+
+sd_mean <-
+  fix_models %>%
+  group_by(Phase) %>%
+  summarize(
+    mean_slope = mean(slope),
+    sd_slope = sd(slope),
+    mean_intercept = mean(intercept),
+    sd_intercept = sd(intercept)
+  )
 
 table_data <- 
-  df_regression %>% 
-  split(.$Phase) %>% 
-  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
-       data = .
-       )
-      ) %>%
-  map(~ tibble(time_span = names(.),
-               intercept = fixef(.)[[1]],
-               intercept_sd = VarCorr(.) %>% as_tibble() %>% .[1,5],
-               intercept_p = coef(summary(.))[1, 5],
-               slope = fixef(.)[[2]],
-               slope_sd = VarCorr(.) %>% as_tibble() %>% .[2,5],
-               slope_p = coef(summary(.))[2, 5]
-               )
-      ) %>% 
-  bind_rows(.id = "Phase") %>% 
+  right_join(x = sd_mean,
+             y = p.values_intercept,
+             by = "Phase") %>% 
+  right_join(x = .,
+             y = p.values_slope,
+             by = "Phase") %>% 
   transmute(Phase = factor(Phase,
@@
             n = NA,
-            `Mean(Intercept)` = round(intercept, digits = 3),
-            `SD(Intercept)` = round(intercept_sd$sdcor, digits = 3),
-            `p-Value (Intercept)` = round(intercept_p, digits = 3),
-            `Mean(Slope)` = round(slope, digits = 3),
-            `SD(Slope)` = round(slope_sd$sdcor, digits = 3),
-            `p-Value (Slope)` = round(slope_p, digits = 3)
-            )
+            `Mean(Intercept)` = mean_intercept,
+            `SD(Intercept)` = sd_intercept,
+            `p-Value (Intercept)` = p.value_intercept,
+            `Mean(Slope)` = mean_slope, 
+            `SD(Slope)` = sd_slope,
+            `p-Value (Slope)` = p.value_slope, 
+            ) %>% 
+  arrange(Phase)
 
@@
 table_data %>% 
-  arrange(Phase) %>% 
-knitr::kable(., caption = "Overview")
+  knitr::kable(.)
 ```
 
-# t-Test (Teaching Phase vs. Interview Phase)
-
-Results:
-
-```{r}
-cache1 <- 
-  main %>% 
-  dplyr::select("ID","time","heart_rate_std", "heart_rate", "time_span") %>% 
-  distinct() %>% 
-  mutate(ID = as_factor(ID)) %>% 
-  split(.$time_span) %>% 
-  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
-             data = .)) %>% 
-  map(~ ranef(.)$ID %>% 
-        as_tibble(., 
-                  rownames = "ID"
-                  ) %>% 
-        clean_names()
-      ) %>% 
-  bind_rows(.,
-            .id = "time_span")
-
-cache2 <-  
-  main %>% 
-  dplyr::select("ID","time","heart_rate_std", "heart_rate","time_span") %>% 
-  distinct() %>% 
-  mutate(ID = as_factor(ID)) %>% 
-  split(.$time_span) %>% 
-  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
-             data = .)) %>% 
-  map(~ summary(.) %>% 
-        .$coefficients %>% 
-        .[c(1,2)]) %>% 
-  bind_rows(.,
-            .id = "time_span") %>% 
-  pivot_longer(
-  cols = everything(),
-  names_to = "time_span",
-  values_to = "mean_value"
-  )
-
-df_test <- 
-  tibble(mean_intercept = cache2$mean_value[1:6],
-         mean_time = cache2$mean_value[7:12],
-         time_span = cache2$time_span[1:6]) %>% 
-  right_join(x = .,
-             y = cache1,
-             by = "time_span") %>% 
-  transmute(time_span,
-            intercept = mean_intercept + intercept,
-            time = mean_time + time,
-            id = id)
-
-t.test(df_test$intercept[df_test$time_span == "teaching"],
-       df_test$intercept[df_test$time_span == "interview"],
-       paired = TRUE)
-```
-
-Cohen D:
-
-```{r}
-CohenD(x = df_test$intercept[df_test$time_span == "teaching"],
-       y = df_test$intercept[df_test$time_span == "interview"],
-       pooled = T
-       )
-```
-
-# Graphs for all Phases
+# Plots for all phases
 
@@
   split(.$time_span) %>% 
-  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
+  map(~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
        data = .
@@
 
-# Different endings
+# t-Tests
 
-```{r fig.width = 10,results='hide',fig.keep='all'}
-df_survival <- 
-  main %>% 
-  filter(time_span == "overall") %>% 
-  select("time","ID") %>% 
-  distinct() %>% 
-  group_by(ID) %>% 
-  summarise(max_time = max(time)) %>% 
+using heart rate means
+
+```{r}
+df_ttest <- 
+  df_regression %>% 
+  group_by(ID, time_span) %>% 
+  summarize(mean_heart_rate = mean(heart_rate_std)) %>% 
   ungroup()
-
-df_survival_analysis <- 
-  tibble(time = seq(max(df_survival$max_time),
-              min(df_survival$max_time),
-              by = -1),
-         p = NA)
-
-n <- length(df_survival$ID)
-
-for (i in seq(min(df_survival$max_time),
-              max(df_survival$max_time),
-              by = 1)) {
-
-  p <- 
-    df_survival %>%
-    filter(max_time >= i) %>%
-    pull(max_time) %>%
-    length(.)
-
-  df_survival_analysis$p[df_survival_analysis$time == i] <- p/n
-
-}
-
-p_80 <- 
-  df_survival_analysis %>% 
-  filter(p > 0.8) %>% 
-  pull(time) %>% 
-  max(.)
-
-p_90 <- 
-  df_survival_analysis %>% 
-  filter(p > 0.9) %>% 
-  pull(time) %>% 
-  max(.)
-
-df_survival_analysis %>% 
-  ggplot(mapping = aes(x = time,
-                       y = p
-                       )
-         ) + 
-  geom_line() +
-  geom_hline(yintercept = 0.8,
-             linetype = "dashed"
-             ) +
-  geom_hline(yintercept = 0.9,
-             linetype = "dashed"
-             ) +
-  geom_vline(xintercept = p_80,
-             linetype = "dashed"
-             ) +
-  geom_vline(xintercept = p_90,
-             linetype = "dashed"
-             ) +
-  labs(x = "Time (in Seconds)",
-       y = "Relative Frequency") +
-  scale_x_continuous(breaks=c(4500, 5000, p_90, 5500, p_80, 6500, 7000)) +
-  scale_y_continuous(breaks=c(0.25, 0.5, 0.75, 0.8, 0.9, 1)) +
-  theme_apa()
 ```
 
-```{r fig.width = 10,results='hide',fig.keep='all'}
-loess_plot_data_90 <- 
-  main %>% 
-  filter(time_span == "overall" &
-         time <= p_90) %>%
-  dplyr::select("heart_rate", "ID", "time") %>% 
-  distinct() %>% 
-  group_by(ID) %>% 
-  summarize(mean_heart = mean(heart_rate),
-            sd_heart = sd(heart_rate)) %>%
-  ungroup() %>% 
-  right_join(x = .,
-             y = distinct(select(main,
-                          "ID","time_span", "time", "heart_rate"
-                        )),
-             by = "ID") %>% 
-  mutate(heart_rate_std = (heart_rate - mean_heart)/
-           sd_heart)
+## Teaching vs. Interview
 
-loess_plot_data_80 <- 
-  main %>% 
-  filter(time_span == "overall" &
-         time <= p_80) %>%
-  dplyr::select("heart_rate", "ID", "time") %>% 
-  distinct() %>% 
-  group_by(ID) %>% 
-  summarize(mean_heart = mean(heart_rate),
-            sd_heart = sd(heart_rate)
-            ) %>%
-  ungroup() %>%  
-  right_join(x = .,
-             y = distinct(select(main,
-                          "ID","time_span", "time", "heart_rate"
-                        )),
-             by = "ID") %>%
-  mutate(heart_rate_std = (heart_rate - mean_heart)/
-           sd_heart)
+```{r}
+df_ttest %$% 
+  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
+         y = .$mean_heart_rate[.$time_span == "interview"],
+         paired = T)
 
-loess_plot_data_all <- 
-  main %>% 
-  filter(time_span == "overall") %>%
-  dplyr::select("heart_rate", "ID", "time") %>% 
-  distinct() %>% 
-  group_by(ID) %>% 
-  summarize(mean_heart = mean(heart_rate),
-            sd_heart = sd(heart_rate)
-            ) %>%
-  ungroup() %>%  
-  right_join(x = .,
-             y = distinct(select(main,
-                          "ID","time_span", "time", "heart_rate"
-                        )),
-             by = "ID") %>%
-  mutate(heart_rate_std = (heart_rate - mean_heart)/
-           sd_heart)
-
-ggplot(mapping = aes(x = time,
-                            y = heart_rate_std
-                            )) +
-  geom_smooth(data = loess_plot_data_80,
-              aes(color = "80%"),
-              se = F
-              ) +
-  geom_smooth(data = loess_plot_data_90,
-              aes(color = "90%"),
-              se = F) +
-  geom_smooth(data = loess_plot_data_all,
-              aes(color = "Baseline"),
-              linetype = "dashed",
-              se = F) +
-  labs(x = "Time (in Seconds)",
-       y = "Average Heart Rate (Standardized)",
-       color = "Legend") +
-  scale_color_manual(values = c("80%" = "blue", "90%" = "red", "Baseline" = "black")) +
-  theme_apa()
+df_ttest %$% 
+  CohenD(x = .$mean_heart_rate[.$time_span == "teaching"],
+         y = .$mean_heart_rate[.$time_span == "interview"],
+         pooled = T)
 ```
 
-# Robustness
+## teaching vs. end
 
-```{r fig.width = 10,results='hide',fig.keep='all'}
-linear_plot_data_80 <- 
-  main %>% 
-  filter(time_span != "overall") %>%
-  dplyr::select("ID","time_span", "time", "heart_rate") %>% 
-  distinct() %>% 
-  left_join(x = .,
-            y = distinct(select(.data = loess_plot_data_80,
-                       "ID", "mean_heart", "sd_heart")),
-            by = "ID"
-            ) %>% 
-  mutate(heart_rate_std = (heart_rate - mean_heart)/
-           sd_heart,
-         Phase = factor(time_span,
-                           levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
+```{r}
+df_ttest %$% 
+  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
+         y = .$mean_heart_rate[.$time_span == "end"],
+         paired = T)
+
+df_ttest %$% 
+  CohenD(x = .$mean_heart_rate[.$time_span == "teaching"],
+         y = .$mean_heart_rate[.$time_span == "end"],
+         pooled = T)
+```
+
+## interview vs. end
+
+```{r}
+df_ttest %$% 
+  t.test(x = .$mean_heart_rate[.$time_span == "interview"],
+         y = .$mean_heart_rate[.$time_span == "end"],
+         paired = T)
+
+df_ttest %$% 
+  CohenD(x = .$mean_heart_rate[.$time_span == "interview"],
+         y = .$mean_heart_rate[.$time_span == "end"],
+         pooled = T)
+```
+
+# Multiple Linear Regression
+
+# Pre Teaching Phase
+
+```{r}
+
+fit_pre_1 <-
+   %>% 
+  filter(time_span == "pre") %$% 
+  lm(slope ~ mean_disruption)
+
+fit_pre_2 <-
+  df_test_reg %>% 
+  filter(time_span == "pre") %$% 
+  lm(time ~ mean_confidence)
+
+fit_pre_3 <-
+  df_test_reg %>% 
+  filter(time_span == "pre") %$% 
+  lm(time ~ mean_confidence + mean_disruption)
+
+fit_pre_4 <-
+  df_test_reg %>% 
+  filter(time_span == "pre") %$% 
+  lm(time ~ mean_confidence + mean_disruption + teaching_experience)
+
+stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4,
+                     type = "latex",
+                     caption = "Pre Phase",
+                     dep.var.labels = "Slope",
+                     order = c(1, 3, 2),
+                     covariate.labels = c("Disruption Factor",
+                                          "Confidence Factor",
+                                          "Teaching Experience"),
+                     keep.stat = c("n","rsq","adj.rsq")
                      )
-         )
-
-linear_plot_data_90 <- 
-  main %>% 
-  filter(time_span != "overall") %>%
-  dplyr::select("ID","time_span", "time", "heart_rate") %>% 
-  distinct() %>% 
-  left_join(x = .,
-            y = distinct(select(.data = loess_plot_data_90,
-                       "ID", "mean_heart", "sd_heart")),
-            by = "ID"
-            ) %>% 
-  mutate(heart_rate_std = (heart_rate - mean_heart)/
-           sd_heart,
-         Phase = factor(time_span,
-                           levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
-                           )
-         )
-
-linear_plot_data_all <-
-  main %>% 
-  filter(time_span != "overall") %>%
-  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
-  distinct() %>% 
-  mutate(Phase = factor(time_span,
-                           levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
-                           ))
-
-ggplot(mapping = aes(x = time,
-                     y = heart_rate_std
-                     )
-       ) +
-  # geom_point(alpha = 0.05) +
-  geom_smooth(data = linear_plot_data_80,
-              method = "lm",
-              se = FALSE,
-              size = 0.5,
-              mapping = aes(color = "80%")
-              ) +
-  geom_smooth(data = linear_plot_data_90,
-              method = "lm",
-              se = FALSE,
-              size = 0.5,
-              mapping = aes(color = "90%")
-              ) +
-  geom_smooth(data = linear_plot_data_all,
-              method = "lm",
-              se = FALSE,
-              size = 0.5,
-              linetype = "dashed",
-              mapping = aes(color = "Baseline")
-              ) +
-  scale_color_manual(values = c("80%" = "blue", "90%" = "red", "Baseline" = "black")) + 
-  labs(x = "Time (in Seconds)",
-       y = "Average Heart Rate (Standardized)",
-       color = "") +
-  facet_grid(cols = vars(Phase)) +
-  theme_apa()
 ```
+```

### 2023-04-27 02_paper/02_study/02_fitbit paper/was weiß ich datei.R
test

@@ -1,0 +1,1 @@
+was weiß ich

### 2023-04-27 02_paper/02_study/02_fitbit paper/was weiß ich datei.R
Delete was weiß ich datei.R

@@ -1,1 +1,0 @@
-was weiß ich

### 2023-04-27 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
update analysis

@@
   dplyr::select(ID, # select relevant columns 
-         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
-         confidence_factor,
-         event
+         "Disruption Factor", # -99 = subject did not notice event; -100 = experimenter did not asked for event
+         "Confidence Factor",
+         "Event"
          ) %>% 
-  mutate(disruption_factor = ifelse(disruption_factor < 0,
+  mutate(disruption_factor = ifelse(`Disruption Factor` < 0,
                                     yes = NA,
-                                    no = disruption_factor
+                                    no = `Disruption Factor`
                                     ),
-         confidence_factor = ifelse(confidence_factor < 0,
+         confidence_factor = ifelse(`Confidence Factor` < 0,
                                    yes = NA,
-                                   no = confidence_factor),
-         event = as_factor(event)
+                                   no = `Confidence Factor`),
+         event = as_factor(Event)
          )
@@
 ```{r}
+df_multi <- 
+  main %>% 
+  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  summarize(disruption = mean(disruption_factor, na.rm = T),
+            confidence = mean(confidence_factor, na.rm = T),
+            teaching_experience) %>% 
+  ungroup() %>% 
+  mutate(id = as.character(ID)) %>% 
+  distinct() %>% 
+  right_join(x = .,
+            y = fix_models,
+            by = "id")
 
 fit_pre_1 <-
-   %>% 
-  filter(time_span == "pre") %$% 
-  lm(slope ~ mean_disruption)
+  df_multi %>% 
+  filter(Phase == "Pre Teaching Phase") %$% 
+  lm(slope ~ disruption)
 
 fit_pre_2 <-
-  df_test_reg %>% 
-  filter(time_span == "pre") %$% 
-  lm(time ~ mean_confidence)
+  df_multi %>% 
+  filter(Phase == "Pre Teaching Phase") %$% 
+  lm(slope ~ confidence)
 
 fit_pre_3 <-
-  df_test_reg %>% 
-  filter(time_span == "pre") %$% 
-  lm(time ~ mean_confidence + mean_disruption)
+  df_multi %>% 
+  filter(Phase == "Pre Teaching Phase") %$% 
+  lm(slope ~ teaching_experience)
 
 fit_pre_4 <-
-  df_test_reg %>% 
-  filter(time_span == "pre") %$% 
-  lm(time ~ mean_confidence + mean_disruption + teaching_experience)
+  df_multi %>% 
+  filter(Phase == "Pre Teaching Phase") %$% 
+  lm(slope ~ confidence + disruption)
 
-stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4,
+fit_pre_5 <-
+  df_multi %>% 
+  filter(Phase == "Pre Teaching Phase") %$% 
+  lm(slope ~ confidence + disruption + teaching_experience)
+
+stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
                      type = "latex",
-                     caption = "Pre Phase",
+                     caption = "Pre Teaching Phase",
                      dep.var.labels = "Slope",
-                     order = c(1, 3, 2),
+                     order = c(1, 2, 3),
                      covariate.labels = c("Disruption Factor",
@@
 ```
+
+# Post Teaching Phase
+
+```{r}
+df_multi <- 
+  main %>% 
+  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  summarize(disruption = mean(disruption_factor, na.rm = T),
+            confidence = mean(confidence_factor, na.rm = T),
+            teaching_experience) %>% 
+  ungroup() %>% 
+  mutate(id = as.character(ID)) %>% 
+  distinct() %>% 
+  right_join(x = .,
+            y = fix_models,
+            by = "id")
+
+fit_post_1 <-
+  df_multi %>% 
+  filter(Phase == "Post Teaching Phase") %$% 
+  lm(slope ~ disruption)
+
+fit_post_2 <-
+  df_multi %>% 
+  filter(Phase == "Post Teaching Phase") %$% 
+  lm(slope ~ confidence)
+
+fit_post_3 <-
+  df_multi %>% 
+  filter(Phase == "Post Teaching Phase") %$% 
+  lm(slope ~ teaching_experience)
+
+fit_post_4 <-
+  df_multi %>% 
+  filter(Phase == "Post Teaching Phase") %$% 
+  lm(slope ~ confidence + disruption)
+
+fit_post_5 <-
+  df_multi %>% 
+  filter(Phase == "Post Teaching Phase") %$% 
+  lm(slope ~ confidence + disruption + teaching_experience)
+
+stargazer::stargazer(fit_post_1, fit_post_2,fit_post_3, fit_post_4, fit_post_5,
+                     type = "latex",
+                #     caption = "Post Teaching Phase",
+                     dep.var.labels = "Slope",
+                     order = c(1, 2, 3),
+                     covariate.labels = c("Disruption Factor",
+                                          "Confidence Factor",
+                                          "Teaching Experience"),
+                     keep.stat = c("n","rsq","adj.rsq")
+                     )
 ```

### 2023-04-28 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
fitbit paper data update

@@
          ) %>% 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132",
+                    "236")
+         ) %>% 
   mutate(disruption_factor = ifelse(disruption_factor < 0,
@@
             extracurricular_teaching_experience = LI14,
-            secondary_teaching_activities = LI17)
+            secondary_teaching_activities = LI17) %>% 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132",
+                    "236")
+        )
 
@@
                   df_rating,
-                  by = "ID") %>% 
-  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
-                    "132",
-                    "236")
-         )
+                  by = "ID")
 
@@
          ID = id,
-         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
-           str_detect(string = id, pattern = "_m") ~ "main",
-           str_detect(string = id, pattern = "_p") ~ "pre",
-           str_detect(string = id, pattern = "_s") ~ "subsequent",
-           str_detect(string = id, pattern = "_i") ~ "interview",
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end_phase",
+                               str_detect(string = id, pattern = "_m") ~ "teaching_phase",
+                               str_detect(string = id, pattern = "_p") ~ "pre-teaching_phase",
+                               str_detect(string = id, pattern = "_s") ~ "post-teaching_phase",
+                               str_detect(string = id, pattern = "_i") ~ "interview_phase",
                                TRUE ~ "overall"
@@
       ) %>%
-      filter(time <= 600) %>%
+      # filter(time <= 600) %>% # filter for 10min intervals
+    filter(time <= 7200) %>% # filter for 2 hours 30min (maximal duration of study)
     dplyr::select(!c("Time","Heart Rate","id"))
@@
             by = "ID")
+
+main <- 
+  main %>% 
+  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132",
+                    "236")
+        ) %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  summarize(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart) %>% 
+  filter(!(time_span == "teaching" & time > 600))
 
@@
 ```{r descriptive statistics}
-# Mean, SD and range for overall 
+# Mean, SD and range for overall (unstandardized)
 descrip_hr_overall <- main %>%
   filter(time_span %in% c("overall")) %>% 
-  summarise("M heart rate in bpm" = round(mean(heart_rate),
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate),
                                      digits = 2),
@@
 
-# Mean, SD and range for individual phases 
+# Mean, SD and range for overall (standardized)
+descrip_hr_overall_std <- main %>%
+  filter(time_span %in% c("overall")) %>% 
+  summarise(N = n_distinct(ID),
+            "M std heart rate in bpm" = round(mean(heart_rate_std),
+                                              digits = 2),
+            "SD std heart rate in bpm" = round(sd(heart_rate_std),
+                                               digits = 2),
+            "Min std heart rate in bpm" = round(min(heart_rate_std),
+                                                digits = 2),
+            "Max heart rate in bpm" = round(max(heart_rate_std),
+                                            digits = 2)
+            )
+
+# Mean, SD and range for individual phases (unstandardized)
 descrip_hr_phases <- main %>% 
@@
   group_by(time_span) %>% 
-  summarise("M heart rate in bpm" = round(mean(heart_rate),
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate),
                                      digits = 2),
@@
             "Max heart rate in bpm" = max(heart_rate)
+  )
+
+# Mean, SD and range for individual phases (standardized)
+descrip_hr_phases_std <- main %>% 
+  filter(!time_span %in% c("overall")) %>% 
+  group_by(time_span) %>% 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate_std),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate_std),
+                                      digits = 2),
+            "Min heart rate in bpm" = round(min(heart_rate_std),
+                                            digits = 2),
+            "Max heart rate in bpm" = round(max(heart_rate_std),
+                                            digits = 2)
   )
@@
          !is.na(disruption_factor)) %>% 
-   summarise("M disruption factor" = round(mean(disruption_factor),
+   summarise(N = n_distinct(ID), 
+            "M disruption factor" = round(mean(disruption_factor),
                                      digits = 2),

### 2023-04-29 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
jgsldjf

@@
             y = fix_models,
-            by = "id")
+            by = "id") %>% 
+  mutate(posneg = if_else(condition = slope < 0,
+                          true = "negative",
+                          false = "positive"))
 
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ disruption)
+  lm(slope ~ disruption * posneg)
 
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ confidence)
+  lm(slope ~ confidence:posneg)
 
@@
   df_multi %>% 
+  mutate(teaching_experience = log(teaching_experience + 1)) %>% 
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ teaching_experience)
+  lm(slope ~ teaching_experience:posneg)
 
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ confidence + disruption)
+  lm(slope ~ confidence:posneg + disruption:posneg)
 
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ confidence + disruption + teaching_experience)
+  lm(slope ~ posneg:confidence + posneg:disruption + posneg:teaching_experience)
 
@@
                      dep.var.labels = "Slope",
-                     order = c(1, 2, 3),
-                     covariate.labels = c("Disruption Factor",
-                                          "Confidence Factor",
-                                          "Teaching Experience"),
+                     # order = c(1, 2, 3),
+                     # covariate.labels = c("Disruption Factor",
+                     #                      "Confidence Factor",
+                     #                      "Teaching Experience"),
                      keep.stat = c("n","rsq","adj.rsq")
                      )
+
+fit_pre_3$model %>%
+  mutate(fitted.values = fit_pre_3$fitted.values) %>% 
+  ggplot(mapping = aes(x = teaching_experience,
+                       y = slope
+                       )
+         ) +
+  geom_point(mapping = aes(group = posneg)) +
+          geom_line(mapping = aes(y = fitted.values,
+                                  group = posneg)) +
+  geom_smooth(method = "lm",
+              se = F,
+              linetype = "dashed") +
+        # geom_point(alpha = 0.5,
+        #            size = 0.5) +
+        theme_apa()
+
 ```
@@
   df_multi %>% 
+  filter(Phase == "Post Teaching Phase") %>% 
+  split(.$posneg) %>% 
+  map(~ lm(slope ~ disruption,
+           data = .))
+
+df_multi %>% 
   filter(Phase == "Post Teaching Phase") %$% 
-  lm(slope ~ disruption)
+  lm(slope ~ disruption:posneg)
 

### 2023-05-02 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
ich hab nix am script verändert ;-)

@@
   dplyr::select(ID, # select relevant columns 
-         "Disruption Factor", # -99 = subject did not notice event; -100 = experimenter did not asked for event
-         "Confidence Factor",
-         "Event"
+         "disruption_factor", # -99 = subject did not notice event; -100 = experimenter did not asked for event
+         "confidence_factor",
+         "event"
          ) %>% 
-  mutate(disruption_factor = ifelse(`Disruption Factor` < 0,
+  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                     yes = NA,
-                                    no = `Disruption Factor`
+                                    no = disruption_factor
                                     ),
-         confidence_factor = ifelse(`Confidence Factor` < 0,
+         confidence_factor = ifelse(confidence_factor < 0,
                                    yes = NA,
-                                   no = `Confidence Factor`),
-         event = as_factor(Event)
+                                   no = confidence_factor),
+         event = as_factor(event)
          )
@@
   group_by(ID) %>% 
-  summarize(mean_heart = mean(heart_rate),
+  dplyr::summarize(mean_heart = mean(heart_rate),
             sd_heart = sd(heart_rate)) %>%
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase"))) %>% 
+                            labels = c("(1) Pre-teaching phase","(2) Teaching phase","(3) Post-teaching phase","(4) Interview phase","(5) End phase"))) %>% 
   distinct() %>% 
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase"))) %>% 
+                            labels = c("(1) Pre-teaching phase","(2) Teaching phase","(3) Post-teaching phase","(4) Interview phase","(5) End phase"))) %>% 
   distinct() %>%
@@
   group_by(Phase) %>%
-  summarize(
+  dplyr::summarize(
     mean_slope = mean(slope),

### 2023-05-05 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/action_alternatives_confidence_factor.Rmd
update R script action alternatives

@@
       RColorBrewer,
-      cowplot)
+      cowplot,
+      zoo)
 
@@
 
-# SJT CM
-df_sjt <- read_csv2(file = "data/SJT.csv",
-                    locale = locale(decimal_mark = ",")) %>% 
-  select(UI06_05,
-         SJT_KF_gek) %>%
-  filter(UI06_05 %in% c(101:126, 201:228),
-         !UI06_05 %in% c(204, 226)
-         ) %>% 
-  na.omit() %>% 
-  rename("id" = "UI06_05",
-         "sjt" = "SJT_KF_gek")
+# # SJT CM
+# df_sjt <- read_csv2(file = "data/SJT.csv",
+#                     locale = locale(decimal_mark = ",")) %>% 
+#   select(UI06_05,
+#          SJT_KF_gek) %>%
+#   filter(UI06_05 %in% c(101:126, 201:228),
+#          !UI06_05 %in% c(204, 226)
+#          ) %>% 
+#   na.omit() %>% 
+#   rename("id" = "UI06_05",
+#          "sjt" = "SJT_KF_gek")
 
@@
 df_alternatives_count <- read_excel("data/coding_action_alternatives.xlsx") %>% 
+  na.locf() %>% 
   janitor::clean_names() %>% 
@@
   # mutate(mean_code = mean(code)) %>% 
+  mutate(count = max(count)) %>% 
   distinct(count)
@@
 df_alternatives_nd <- read_excel("data/coding_action_alternatives.xlsx") %>% 
+  na.locf() %>% 
   janitor::clean_names() %>% 
   select(id, code) %>% 
-  filter(code %in% c(1:3)) %>%
+  mutate(nd = 
+           as.numeric(
+             case_when(code > 3 ~ '0',
+                       code <= 3 ~ '1',
+                       TRUE ~ 'F'
+                       )
+             )
+         ) %>%
   group_by(id) %>% 
-  count() %>% 
-  transmute(nd = n)
+  summarise(nd = sum(nd))
 
@@
 df_list <- list(df_sri,
-                df_sjt,
+                # df_sjt,
                 df_alternatives_count,

### 2023-05-05 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_action_alternatives.Rmd
update R script action alternatives

---
title: "Professional vision - link between eye tracking parameters and the ability
  to generate action alternatives"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, warning = FALSE)
```

# load packages and read in data
```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot)

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

### EYE TRACKING DATA

# return a character vector with names of .tsv data in data folder
file_names <- list.files(path = "data",
                         pattern = "interval_complete.tsv")

# read every object names in file_names and save it as a tibble
for (i in file_names) {

  work_data <- 
    read_tsv(file = paste0("data/", i),
             locale = locale(decimal_mark = ","))

  assign(value = work_data,
         x = str_remove(paste0("tib_", i),
                        pattern = ".tsv"
         )
  )

}

# Bind every tibble that contains "interval_complete" to a new tible
df_aoi <- 
  mget(ls(pattern = "interval_complete")) %>%
  bind_rows()

# Remove temporary data for a cleaner workspace
rm(list = ls(pattern = "^tib_ProVisio"))
rm(work_data)
rm(file_names)
rm(i)

### TIME TO FIRST FIXATION 
df_aoi %>% 
  filter(TOI == "Chatting_with_neighbour") %>% 
  select (Participant, 
          "Time_to_first_fixation.Disruptive_Person") %>% 
  rowwise() %>% 
  mutate(ID = str_extract(string = Participant,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)

         # Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000,digits = 2)#changing milliseconds into seconds
         ) %>% 
  select(ID,
         Time_to_first_fixation.Disruptive_Person) %>% 
  janitor::clean_names() -> df_ttff_disrup
  # filter(!ID %in% c(204))

# SELF-REPORT DATA
df_sri <- 
  excel_sheets("data/coding_sri.xlsx") %>% 
  map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
  dplyr::select(ID, Event, `Confidence Factor`) %>% 
  filter(
    # ID %in% c(101:125, 202:217),
         Event %in% c("chatting")) %>%
  janitor::clean_names()

# ACTION ALTERNATIVES
df_alternatives <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  janitor::clean_names() %>% 
  group_by(id) %>% 
  mutate(mean_code = mean(code)) %>% 
  distinct(count, mean_code)

# merge data frames
# put all data frames into list
df_list <- list(df_ttff_disrup, df_sri, df_alternatives)

# merge all data frames in list
main <-
  df_list %>% reduce(full_join, by='id') %>%
  janitor::clean_names() %>%
  select(!event) %>% # select relevant columns
  na.omit()

main$id = ifelse(main$id < 200, "Novice","Expert")

```

# descriptives
```{r}
# main %>%
#   distinct() %>%
#   group_by(id) %>%
#   summarize(mean_ttff = round(mean(time_to_first_fixation_disruptive_person), digits = 0),
#             sd_ttff = round(sd(time_to_first_fixation_disruptive_person), digits = 0),
#             mean_confi = round(mean(confidence_factor), digits = 0),
#             sd_confi = round(sd(confidence_factor), digits = 0),
#             mean_aa_count = round(mean(count), digits = 0),
#             sd_aa_count = round(sd(count), digits = 0),
#             mean_aa_code = round(mean(mean_code), digits = 0),
#             sd_aa_code = round(sd(mean_code), digits = 0)) %>%
#   ungroup() -> df_descriptives

# time_to_first_fixation_disruptive_person
describeBy(main$time_to_first_fixation_disruptive_person, main$id)
plot_ttff <- boxplot(time_to_first_fixation_disruptive_person ~ id, data = main)

# confidence factor
describeBy(main$confidence_factor, main$id)
plot_confi <- boxplot(confidence_factor ~ id, data = main)

# action alternatives - count
describeBy(main$count, main$id)
plot_action_count <- boxplot(count ~ id, data = main)

# action alternatives - quality  
describeBy(main$mean_code, main$id)
plot_action_quality <- boxplot(mean_code ~ id, data = main)

```

# t-test and effect size

```{r}
### time to first fixation on disruptive person

df_ttff_disrup$id = ifelse(df_ttff_disrup$id < 200, "Novice","Expert")

# t-test for expertise differences
t.test(x = df_ttff_disrup$time_to_first_fixation_disruptive_person[df_ttff_disrup$id == "Expert"],
                     y = df_ttff_disrup$time_to_first_fixation_disruptive_person[df_ttff_disrup$id == "Novice"])

# effect size for expertise differences
CohenD(x = df_ttff_disrup$time_to_first_fixation_disruptive_person[df_ttff_disrup$id == "Expert"],
                 y = df_ttff_disrup$time_to_first_fixation_disruptive_person[df_ttff_disrup$id == "Novice"],
                 na.rm = TRUE)

#### sri - confidence factor

df_sri$id = ifelse(df_sri$id < 200, "Novice","Expert")

# t-test for expertise differences
t.test(x = df_sri$confidence_factor[df_sri$id == "Expert"],
                    y = df_sri$confidence_factor[df_sri$id == "Novice"])

# effect size for expertise differences
CohenD(x = df_sri$confidence_factor[df_sri$id == "Expert"],
                y = df_sri$confidence_factor[df_sri$id == "Novice"],
                na.rm = TRUE)

### action alternatives count

df_alternatives$id = ifelse(df_alternatives$id < 200, "Novice","Expert")

# t-test for expertise differences
t.test(x = df_alternatives$count[df_alternatives$id == "Expert"],
                         y = df_alternatives$count[df_alternatives$id == "Novice"])

# effect size for expertise differences
CohenD(x = df_alternatives$count[df_alternatives$id == "Expert"],
                     y = df_alternatives$count[df_alternatives$id == "Novice"],
                     na.rm = TRUE)

### action alternatives code
# Mann-Whitney-U-Test
wilcox.test(main$mean_code ~ main$id)

# t-test for expertise differences
t.test(x = df_alternatives$mean_code[df_alternatives$id == "Expert"],
                        y = df_alternatives$mean_code[df_alternatives$id == "Novice"])

# effect size for expertise differences
CohenD(x = df_alternatives$mean_code[df_alternatives$id == "Expert"],
                    y = df_alternatives$mean_code[df_alternatives$id == "Novice"],
                    na.rm = TRUE)
```

# confidence factor x count of action alternatives
```{r}
main %>% 
  filter(!is.na(confidence_factor) | !is.na(count)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = count,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Confidence Factor",
       y = "Count of action alternatives") +
  theme_cowplot()

```
# confidence factor x quality of action alternatives

```{r}
main %>% 
  filter(!is.na(confidence_factor) | !is.na(mean_code)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = mean_code,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Confidence Factor",
       y = "Quality of action alternatives (Code1-6)") + 
  theme_cowplot()

```

# time to first fixation x count of action alternatives
```{r}
main %>% 
  filter(!is.na(time_to_first_fixation_disruptive_person) | !is.na(count)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = time_to_first_fixation_disruptive_person,
                       y = count,
                       colour = id
                       )
         ) +
  geom_point() +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Time to first fixation on disruptive person",
       y = "Count of action alternatives") + 
  theme_cowplot()

```

# time to first fixation x quality of action alternatives
```{r}
main %>% 
  filter(!is.na(time_to_first_fixation_disruptive_person) | !is.na(mean_code)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = time_to_first_fixation_disruptive_person,
                       y = mean_code,
                       colour = id
                       )
         ) +
  geom_point() +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Time to first fixation on disruptive person",
       y = "Quality of action alternatives (Code1-6)") + 
  theme_cowplot()

```

# count x quality of action alternatives
```{r}
main %>% 
  filter(!is.na(count) | !is.na(mean_code)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = count,
                       y = mean_code,
                       colour = id
                       )
         ) +
  geom_point() +
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Count of action alternatives",
       y = "Quality of action alternatives (Code1-6)") + 
  theme_cowplot()

```

# pearson & spearman correlation

```{r}
# novices: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Novice")) -> corr.nov

cor.test(corr.nov$confidence_factor, corr.nov$count, method=c("pearson"))

# experts: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Expert")) -> corr.exp

cor.test(corr.exp$confidence_factor, corr.exp$count, method=c("pearson"))

# novices: correlation between confidence factor and quality
cor.test(corr.nov$confidence_factor, corr.nov$mean_code, method=c("spearman"))

# experts: correlation between confidence factor and quality
cor.test(corr.exp$confidence_factor, corr.exp$mean_code, method=c("spearman"))

# novices: correlation between time to first fixation and count
cor.test(corr.nov$time_to_first_fixation_disruptive_person, corr.nov$count, method=c("pearson"))

####### experts: correlation between time to first fixation and count
cor.test(corr.exp$time_to_first_fixation_disruptive_person, corr.exp$count, method=c("pearson"))

# novices: correlation between time to first fixation and quality
cor.test(corr.nov$time_to_first_fixation_disruptive_person, corr.nov$mean_code, method=c("spearman"))

# experts: correlation between time to first fixation and quality
cor.test(corr.exp$time_to_first_fixation_disruptive_person, corr.exp$mean_code, method=c("spearman"))

# novices: correlation between count and quality
cor.test(corr.nov$count, corr.nov$mean_code, method=c("spearman"))

# experts: correlation between count and quality
cor.test(corr.exp$count, corr.exp$mean_code, method=c("spearman"))

```

### 2023-05-09 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
Demo_Tabelle

@@
 classoption       : "man"
-output            : bookdown::word_document2 
-# papaja::apa6_pdf
+output            : papaja::apa6_pdf
 
@@
 
-# changing gender to count female gender (male = 2 --> 0)
-df_demo$gender = ifelse(df_demo$gender == 2, "1","0")
+# changing gender to count female gender (female = 2 --> 1, male --> 0)
+df_demo$gender = ifelse(test = df_demo$gender == 2,
+                        yes = 1,
+                        no = 0)
 
 # changing character Gender into numeric
-df_demo$gender <- as.numeric(df_demo$gender)
+# df_demo$gender <- as.numeric(df_demo$gender)
+
+# recoding gender - Freddy
 
@@
 # replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
-df_demo$school_type[df_demo$school_type == 2] <- "1"
+df_demo$school_type[df_demo$school_type == 2] <- 1
 
@@
 # changing character Percent_schooltype into numeric
-df_demo$percent_schooltype <- as.numeric(df_demo$percent_schooltype)
+# df_demo$percent_schooltype <- as.numeric(df_demo$percent_schooltype)
 
@@
   ungroup() %>%
-  summarise(N=n(),
+  summarise('N' = round(mean(sum_participants),
+                             digits = 0),
             "Gender female in percent" = round(sum(gender/sum_participants) * 100,
@@
 
+df_demo_table_long <- pivot_longer(data = df_demo_table,
+                              cols = everything(),
+                              names_to = 'Variable',
+                              values_to = 'values')
+
 # # format and insert table in manuscript
-# df_demo_table %>%
-# papaja::apa_table(
-#   caption = "Demographic Information",
+ df_demo_table_long %>%
+ papaja::apa_table(
+   caption = "Demographic Information",
 #   # note = "Write Note here",
-#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-#   )
+   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+   )
 

### 2023-05-09 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
Demo_Tabelle

--- 2023-02-17 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
@@
 
-The sample consisted in total of \emph{N} = 72 pre- and in-service teachers.
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:demographicstable}Demographic Information}
+
+\tiny{
+
+\begin{tabular}{ll}
+\toprule
+Variable & \multicolumn{1}{c}{values}\\
+\midrule
+N & 76.00\\
+Gender female in percent & 63.16\\
+M Age in years & 30.26\\
+SD Age in years & 10.52\\
+Min Age in years & 19.00\\
+Max Age in years & 59.00\\
+M Teaching Experience in years & 5.17\\
+SD Teaching Experience in years & 9.12\\
+Min Teaching Experience in years & 0.00\\
+Max Teaching Experience in years & 37.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+The sample consisted in total of \emph{N} = 76 pre- and in-service teachers.
 The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
-Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 70 subjects.
+Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 76 subjects.
 
-The subjects (42 women; 60 \%) had a mean age of 29.70 years (\emph{SD} = 10.70; range: 19-59) and an average teaching experience of 4.84 years (\emph{SD} = 9.31; range: 0-37).
+The subjects (48 women; 63.16 \%) had a mean age of 30.30 years (\emph{SD} = 10.50; range: 19-59) and an average teaching experience of 5.17 years (\emph{SD} = 9.12; range: 0-37).
 
-17.14\% of the subjects were (studying to become) teachers for primary school, 70\% were (studying to become) teachers for secondary school and 11.43\% were (studying to become) teachers for special education needs.
+15.79\% of the subjects were (studying to become) teachers for primary school, 71.05\% were (studying to become) teachers for secondary school and 10.53\% were (studying to become) teachers for special education needs.
 
@@
 
-We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Version 2.2.9; Revelle, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.36; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression).
+We used R (Version 4.2.2; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.48; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.2; Wickham, 2021), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{jtools} (Version 2.2.1; Long, 2022), \emph{lm.beta} (Version 1.7.2; Behrendt, 2022), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.58.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.1.9001; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Revelle, 2022), \emph{purrr} (Version 0.3.5; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.1; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.1; Kassambara, 2021), \emph{stringr} (Version 1.4.1; Wickham, 2019), \emph{tibble} (Version 3.1.8; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.2; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.38; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression).
 Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}.
@@
 
-Teachers' average heart rate during the entire course of the study was approximately 96.84 bpm with a standard deviation of 14.44 and a range from 56 to 139 bpm.
+Teachers' average heart rate during the entire course of the study was approximately 90.40 bpm with a standard deviation of 15.82 and a range from 51 to 164 bpm.
 
@@
 The second graph @ref(fig:phase\_plot) show the heart rate for the individual five phases.
+
+\begin{verbatim}
+## Warning: Unknown levels in `f`: pre, main, subsequent, interview, after
+\end{verbatim}
 

### 2023-05-17 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
action alternatives update

---
title: "Reaction & action alternatives"
output: html_document
date: "2023-05-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages and read in data
```{r}

library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot,
      zoo)

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

# REACTION 
df_reaction <- read_excel("data/coding_reactions_MK.xlsx") %>% 
  janitor::clean_names() %>%
  mutate(reaction = as.numeric(case_when(code > 3 ~ '0',
                                         code <= 3 ~ '1',
                                         TRUE ~ 'F')
                               )
         ) %>% 
  select(id, reaction)

# ACTION ALTERNATIVES count
df_alternatives_count <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  na.locf() %>% # replacing NA with most forward non-NA to it
  janitor::clean_names() %>% 
  group_by(id) %>% 
  # mutate(mean_code = mean(code)) %>% 
  mutate(count = max(count)) %>% 
  distinct(count)

# ACTION ALTERNATIVES non-disruptive 
df_alternatives_nd <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  na.locf() %>% 
  janitor::clean_names() %>% 
  select(id, code) %>% 
  mutate(nd = as.numeric(case_when(code > 3 ~ '0',
                                 code <= 3 ~ '1',
                                 TRUE ~ 'F')
                         )
         ) %>% 
  select(id, nd) %>%
  group_by(id) %>% 
  summarise(nd = sum(nd))

# merge data frames
# put all data frames into list
df_list <- list(df_reaction,
                df_alternatives_count,
                df_alternatives_nd)

# merge all data frames in list
main <-
  df_list %>% reduce(full_join, by='id') %>%
  janitor::clean_names()

# drop NA 
main <- 
  na.omit(main)

# replace IDs with expertise factor
main$id = ifelse(main$id < 200, "Novice","Expert")

# creating new column with total reactions
main_novice <- main %>%
  filter(id %in% c("Novice")) %>% 
  mutate(reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum = sum(n()),
         percent_reaction = round((reaction_sum/sum),
                                  digits = 2),
         percent_nd = round((nd/count),
                            digits = 2)
         )

# creating new column with total reactions
main_expert <- main %>%
  filter(id %in% c("Expert")) %>% 
  mutate(reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum = sum(n()),
         percent_reaction = round((reaction_sum/sum),
                                  digits = 2),

         percent_nd = round((nd/count),
                            digits = 2)
         )

# merge novice & expert data frame
main <- rbind(main_expert, main_novice)

```

# descriptives & plots
```{r}
# reaction 
describeBy(main$percent_reaction, main$id)
plot_action_count <- boxplot(percent_reaction ~ id, data = main)

# action alternatives - count
describeBy(main$count, main$id)
plot_action_count <- boxplot(count ~ id, data = main)

# action alternatives - non disruptive alternatives (sum score)
describeBy(main$nd, main$id)
plot_action_quality <- boxplot(nd ~ id, data = main)

# action alternative - non disruptive alternatives (relative score)
describeBy(main$percent_nd, main$id)
plot_reaction <- boxplot(percent_nd ~ id, data = main)

```

# t-test and effect size
```{r}

#### reaction
# t-test for expertise differences
t.test(x = main$reaction[main$id == "Expert"],
       y = main$reaction[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$reaction[main$id == "Expert"],
       y = main$reaction[main$id == "Novice"],
       na.rm = TRUE)

### action alternatives count (sum score)
# t-test for expertise differences
t.test(x = main$count[main$id == "Expert"],
       y = main$count[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$count[main$id == "Expert"],
       y = main$count[main$id == "Novice"],
       na.rm = TRUE)

### action alternatives non-disruptive (sum score)
# t-test for expertise differences
t.test(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"],
       na.rm = TRUE)

### action alternatives non-disruptive (relative score)
# t-test for expertise differences
t.test(x = main$percent_nd[main$id == "Expert"],
       y = main$percent_nd[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"],
       na.rm = TRUE)
```

### 2023-05-17 01_studies/01_Laborstudie ProVisioNET/R script/et toi/ProVisioNet_ET_TOI_AOI-based_data.nb.Rmd
action alternatives update

---
title: "AOI and TOI based analyses ProVisioNet"
output: html_notebook
---

# Install Packages

```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl,
      gridExtra)
```

# Read In Data sets

```{r, include = FALSE}
AOI_AP_01 <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

AOI_MK_01 <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

AOI_AP_04 <- read_tsv(file = "data/04_04_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

AOI_MK_04 <- read_tsv(file = "data/04_04_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

```

# AOI based analyses 
# Data Wrangling - Total Duration and Proportional Duration of looking at AOIs

```{r, include = TRUE, cache = TRUE, echo=TRUE}

# select relevant columns
AOI_AP_01 <- AOI_AP_01 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

AOI_MK_01 <- AOI_MK_01 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

AOI_AP_04 <- AOI_AP_04 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

AOI_MK_04 <- AOI_MK_04 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

# filter only for TOIs
AOI_AP_01 <- AOI_AP_01 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering" |
          TOI == "Entire Recording")

AOI_MK_01 <- AOI_MK_01 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering" |
          TOI == "Entire Recording")

AOI_AP_04 <- AOI_AP_04 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering"|
          TOI == "Entire Recording")

AOI_MK_04 <- AOI_MK_04 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering"|
          TOI == "Entire Recording")

# create new column names that give total duration of looking at all AOIs
AOI_AP_01 <- AOI_AP_01  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Material = Total_duration_of_fixations.Material,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

AOI_MK_01 <- AOI_MK_01  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Teacher_Material = Total_duration_of_fixations.Material_Teacher,
          Students_Material = Total_duration_of_fixations.Material_Students,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

AOI_AP_04 <- AOI_AP_04  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Material = Total_duration_of_fixations.Material,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

AOI_MK_04 <- AOI_MK_04  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Students_Material = Total_duration_of_fixations.Students_material,
          Teacher_Material = Total_duration_of_fixations.Teacher_material,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

# replace NAs with 0
AOI_AP_01 <- AOI_AP_01 %>%
  mutate_all(~replace(., is.na(.), 0))

AOI_AP_04 <- AOI_AP_04 %>%
  mutate_all(~replace(., is.na(.), 0))

AOI_MK_01 <- AOI_MK_01 %>%
  mutate_all(~replace(., is.na(.), 0))

AOI_MK_04 <- AOI_MK_04 %>%
  mutate_all(~replace(., is.na(.), 0))

# create data set of total durations in long format for plotting --> for later
AOI_AP_01_long <- gather(AOI_AP_01, TOI, Duration)

AOI_MK_01_long <- gather(AOI_MK_01, TOI, Duration)

AOI_AP_04_long <- gather(AOI_AP_04, TOI, Duration)

AOI_MK_04_long <- gather(AOI_MK_04, TOI, Duration)

# create a new column with name sum_aois that gives the sum of looking at all AOIs
AOI_AP_01 <- AOI_AP_01  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

AOI_MK_01 <- AOI_MK_01  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Teacher_Material +
                                              Students_Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

AOI_AP_04 <- AOI_AP_04  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

AOI_MK_04 <- AOI_MK_04  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Teacher_Material +
                                              Students_Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

# create new columns that give proportion of the duration of looking at all AOIs
# the proportion is the relative duration divided by total duration 
prop_AP_01 <- AOI_AP_01  %>% 
  mutate(Anna = Anna/Sum_AOI)   %>% 
  mutate(Bianca = Bianca/Sum_AOI)   %>% 
  mutate (Carl_a = Carl_a/Sum_AOI) %>%
  mutate(Disruptive_Person = Disruptive_Person/Sum_AOI)   %>% 
  mutate(Board_Screen = Board_Screen/Sum_AOI) %>%
  mutate(Classroom_Others = Classroom_Others/Sum_AOI) %>%
  mutate (Material = Material/Sum_AOI) %>%
  mutate (Nametag_Anna = Nametag_Anna/Sum_AOI) %>%
  mutate (Nametag_Bianca = Nametag_Bianca/Sum_AOI) %>%
  mutate (Nametage_Carl_a = Nametage_Carl_a/Sum_AOI)

# chose all columns exept the last one (Sum_AOI)
prop_AP_01 <- prop_AP_01 %>% filter(TOI == "Lesson") %>%
                              select(,1:11)

prop_MK_01 <- AOI_MK_01  %>% 
  mutate(Anna = Anna/Sum_AOI)   %>% 
  mutate(Bianca = Bianca/Sum_AOI)   %>% 
  mutate (Carl_a = Carl_a/Sum_AOI) %>%
  mutate(Disruptive_Person = Disruptive_Person/Sum_AOI)   %>% 
  mutate(Board_Screen = Board_Screen/Sum_AOI) %>%
  mutate(Classroom_Others = Classroom_Others/Sum_AOI) %>%
  mutate (Teacher_Material = Teacher_Material/Sum_AOI) %>%
  mutate (Nametag_Anna = Nametag_Anna/Sum_AOI) %>%
  mutate (Nametag_Bianca = Nametag_Bianca/Sum_AOI) %>%
  mutate (Nametage_Carl_a = Nametage_Carl_a/Sum_AOI) %>%
  rename(Material = Teacher_Material)

prop_MK_01 <- prop_MK_01 %>% filter(TOI == "Lesson") %>%
                              select(!"Students_Material")

prop_AP_04 <- AOI_AP_04  %>% 
  mutate(Anna = Anna/Sum_AOI)   %>% 
  mutate(Bianca = Bianca/Sum_AOI)   %>% 
  mutate (Carl_a = Carl_a/Sum_AOI) %>%
  mutate(Disruptive_Person = Disruptive_Person/Sum_AOI)   %>% 
  mutate(Board_Screen = Board_Screen/Sum_AOI) %>%
  mutate(Classroom_Others = Classroom_Others/Sum_AOI) %>%
  mutate (Material = Material/Sum_AOI) %>%
  mutate (Nametag_Anna = Nametag_Anna/Sum_AOI) %>%
  mutate (Nametag_Bianca = Nametag_Bianca/Sum_AOI) %>%
  mutate (Nametage_Carl_a = Nametage_Carl_a/Sum_AOI)

prop_AP_04 <- prop_AP_04 %>% filter(TOI == "Lesson") %>%
                              select(,1:11)

prop_MK_04 <- AOI_MK_04  %>% 
  mutate(Anna = Anna/Sum_AOI)   %>% 
  mutate(Bianca = Bianca/Sum_AOI)   %>% 
  mutate (Carl_a = Carl_a/Sum_AOI) %>%
  mutate(Disruptive_Person = Disruptive_Person/Sum_AOI)   %>% 
  mutate(Board_Screen = Board_Screen/Sum_AOI) %>%
  mutate(Classroom_Others = Classroom_Others/Sum_AOI) %>%
  mutate (Teacher_Material = Teacher_Material/Sum_AOI) %>%
  mutate(Students_Material = Students_Material/Sum_AOI) %>%
  mutate (Nametag_Anna = Nametag_Anna/Sum_AOI) %>%
  mutate (Nametag_Bianca = Nametag_Bianca/Sum_AOI) %>%
  mutate (Nametage_Carl_a = Nametage_Carl_a/Sum_AOI) %>%
  mutate (Material = Students_Material + Teacher_Material)

prop_MK_04 <- prop_MK_04 %>% filter(TOI == "Lesson") %>%
                              select(!"Students_Material") %>%
                              select(!"Teacher_Material") %>%
                              select (!"Sum_AOI")

# create data set of proportions in long format for plotting
prop_AP_01_long  <- prop_AP_01 %>% gather(TOI, Duration)

prop_MK_01_long <- prop_MK_01 %>% gather (TOI, Duration)

prop_AP_04_long <- prop_AP_04 %>% gather (TOI, Duration)

prop_MK_04_long <- prop_MK_04 %>% gather (TOI, Duration)

################################################

```

### Ploting data - Total Duration and Proportional Data of Video 01 and 04, coded by AP and MK

```{r echo = TRUE, include=TRUE}
total_AP_01 <- AOI_AP_01_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
            geom_jitter(color="black", size=0.4, alpha=0.9) +
            geom_point() + ylim (0,1000) + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Total Duration of Looking at AOIs in ms - Video 01 Rater AP") +
             xlab("AOI")

total_AP_01

total_MK_01 <- AOI_MK_01_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
            geom_jitter(color="black", size=0.4, alpha=0.9) +
            geom_point() + ylim (0,1000) + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Total Duration of Looking at AOIs in ms - Video 01 Rater MK") +
             xlab("AOI")

total_MK_01

### Plot data TOTAL DURATION video 04
total_AP_04 <- AOI_AP_04_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
            geom_jitter(color="black", size=0.4, alpha=0.9) +
            geom_point() + ylim (0,1000) + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Total Duration of Looking at AOIs in ms - Video 04 Rater AP") +
             xlab("AOI")

total_AP_04

total_MK_04 <- AOI_MK_04_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
            geom_jitter(color="black", size=0.4, alpha=0.9) +
            geom_point() + ylim (0,1000) + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Total Duration of Looking at AOIs in ms - Video 04 Rater MK") +
             xlab("AOI")

total_MK_04

### Plot data PROPORTIONAL DURATION video 01
prop_AP_01 <- prop_AP_01_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Proportional Duration of Looking at AOIs - Video 01 Rater AP") +
             xlab("AOI")

prop_AP_01

prop_MK_01 <- prop_MK_01_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Proportional Duration of Looking at AOIs in ms") +
             xlab("AOI")

prop_MK_01

### Plot data PROPORTIONAL DURATION video 04
prop_AP_04 <- prop_AP_04_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Proportional Duration of Looking at AOIs - Video 04 Rater AP") +
             xlab("AOI")

prop_AP_04

prop_MK_04 <- prop_MK_04_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Proportional Duration of Looking at AOIs - Video 04 Rater MK") +
             xlab("AOI")

prop_MK_04

```

# Reliabilty for Hits in AOIs
# Read in Data Sets
```{r, include=TRUE}
AOI_hit_AP_01 <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Event-based.tsv"
                   )

AOI_hit_MK_01 <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Event-based.tsv"
                  )

AOI_hit_AP_04 <- read_tsv(file = "data/04_04_AP_ProVisioNET_study_glasses Metrics_event-based.tsv")

AOI_hit_MK_04 <- read_tsv(file = "data/04_04_MK_ProVisioNET_study_glasses Metrics_event-based.tsv")
```

# Data Wrangling
```{r echo=FALSE, include=TRUE}
# filter only rows lesson
AOI_hit_AP_01 <- AOI_hit_AP_01 %>% filter(TOI == "Lesson")

AOI_hit_MK_01 <- AOI_hit_MK_01 %>% filter(TOI == "Lesson")

AOI_hit_AP_04 <- AOI_hit_AP_04 %>% filter(TOI == "Lesson")

AOI_hit_MK_04 <- AOI_hit_MK_04 %>% filter(TOI == "Lesson")

# select variable AOI + Hit_proportion
AOI_hit_AP_01 <- AOI_hit_AP_01 %>% select(AOI, Hit_proportion)

AOI_hit_MK_01 <- AOI_hit_MK_01 %>% select(AOI, Hit_proportion)

AOI_hit_AP_04 <- AOI_hit_AP_04 %>% select(AOI, Hit_proportion)

AOI_hit_MK_04 <- AOI_hit_MK_04 %>% select(AOI, Hit_proportion)

# changing character to numeric
AOI_hit_AP_01$Hit_proportion <- as.numeric(AOI_hit_AP_01$Hit_proportion)

AOI_hit_MK_01$Hit_proportion <- as.numeric(AOI_hit_MK_01$Hit_proportion)

AOI_hit_AP_04$Hit_proportion <- as.numeric(AOI_hit_AP_04$Hit_proportion)

AOI_hit_MK_04$Hit_proportion <- as.numeric(AOI_hit_MK_04$Hit_proportion)

# round Hit_proportion to 1
AOI_hit_AP_01$Hit_proportion <- round(AOI_hit_AP_01$Hit_proportion, digits = 0)

AOI_hit_MK_01$Hit_proportion <- round(AOI_hit_MK_01$Hit_proportion, digits = 0)

AOI_hit_AP_04$Hit_proportion <- round(AOI_hit_AP_04$Hit_proportion, digits = 0)

AOI_hit_MK_04$Hit_proportion <- round(AOI_hit_MK_04$Hit_proportion, digits = 0)

#delete NAs
AOI_hit_AP_01 <- na.omit(AOI_hit_AP_01)

AOI_hit_MK_01 <- na.omit(AOI_hit_MK_01)

AOI_hit_AP_04 <- na.omit(AOI_hit_AP_04)

AOI_hit_MK_04 <- na.omit(AOI_hit_MK_04)

# group data by AOI and summarise Hit_prop
Hit_AP_01_aggr <- group_by(.data = AOI_hit_AP_01,
                    AOI) %>% summarise(Hit_count = length(Hit_proportion))

Hit_MK_01_aggr <- group_by(.data = AOI_hit_MK_01,
                    AOI) %>% summarise(Hit_count = length(Hit_proportion))

Hit_AP_04_aggr <- group_by(.data = AOI_hit_AP_04,
                    AOI) %>% summarise(Hit_count = length(Hit_proportion))

Hit_MK_04_aggr <- group_by(.data = AOI_hit_MK_04,
                    AOI) %>% summarise(Hit_count = length(Hit_proportion))

###### filter only for identical rows for both rater

AP_01_filter <- Hit_AP_01_aggr %>% filter(
                    AOI != "Nametag_Anna",
                    AOI != "Nametag_Bianca",
                    AOI != "Nametag_Carl(a)")

AP_01_filter

MK_01_filter <- Hit_MK_01_aggr %>% filter( 
                    AOI != "Bianca,Classroom_Others")

MK_01_filter$AOI[MK_01_filter$AOI == "Material_Teacher"] <- "Material"

MK_01_filter

# merge two data frames --> adding Columns, don't forget to merge BY AOI !

r3 <- merge(AP_01_filter, MK_01_filter, by = 'AOI')

# create a new df with only the ratings 
r3_agree <- r3 %>% select(Hit_count.x, Hit_count.y)

# function agree() with a tolerance
agree(r3_agree, tolerance=50)

#################### CohenKappa ##############################

# first, create a xtab and specify who is rater1 and rater2
ratertab <- xtabs(~r3$Hit_count.x + r3$Hit_count.y)
ratertab

# now you can calculate CohenKappa
CohenKappa(ratertab)

#################### ICC ##############################

# build a subset that contains the two AOI hit variables  
data_icc <- subset(r3, select = c(Hit_count.x, Hit_count.y))

# calculate the ICC for two raters with new subset
ICC(data_icc)

```

# TOI based analyses 
# Data Wrangling - TOIs classified by disruptions

```{r, echo=TRUE, include=TRUE}

df_AP_01 <- df_AP_01 %>% 
  select(TOI, Duration_of_interval)

df_MK_01 <- df_MK_01 %>% 
  select(TOI, Duration_of_interval)

df_AP_04 <- df_AP_04 %>% 
  select(TOI, Duration_of_interval)

df_MK_04 <- df_MK_04 %>% 
  select(TOI, Duration_of_interval)

# Duration

df_cappa_dur <- matrix(ncol = 3,
                       nrow = 11)

colnames(df_cappa_dur) <- c("TOI","Duration_of_interval_AP_01","Duration_of_interval_MK_01")

df_cappa_dur <- as_tibble(df_cappa_dur)

TOI_names <- c("Calibration_phase",
               "Chatting_with_neighbour",
               "Clicking_pen",
               "Drawing",
               "Drumming_with_hands",
               "Head_on_table",
               "Looking_at_phone",
               "Heckling","Lesson",
               "Snipping_with_fingers",
               "Whispering")

df_cappa_dur$TOI <- TOI_names

# AP_01 Duration TOI
for (i in TOI_names) {

  val <- df_AP_01$Duration_of_interval[df_AP_01 == i]

  df_cappa_dur$Duration_of_interval_AP_01[df_cappa_dur$TOI == i] <- val
}

# MK_01 Duration TOI
for (i in TOI_names) {

  val <- df_MK_01$Duration_of_interval[df_MK_01 == i]

  df_cappa_dur$Duration_of_interval_MK_01[df_cappa_dur$TOI == i] <- val
}

# AP_04 Duration TOI
for (i in TOI_names) {

  val <- df_AP_04$Duration_of_interval[df_AP_04 == i]

  df_cappa_dur$Duration_of_interval_AP_04[df_cappa_dur$TOI == i] <- val
}

# MK_04 Duration TOI
for (i in TOI_names) {

  val <- df_MK_04$Duration_of_interval[df_MK_04 == i]

  df_cappa_dur$Duration_of_interval_MK_04[df_cappa_dur$TOI == i] <- val
}

```

# Creating TOI classes
```{r, include=TRUE}
df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Calibration_phase"] <- "Calibration_phase"

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Chatting_with_neighbour" |
                         df_cappa_dur$TOI == "Heckling" |
                         df_cappa_dur$TOI == "Whispering"] <- "Verbal_disruption"

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Head_on_table" |
                         df_cappa_dur$TOI == "Looking_at_phone" |
                         df_cappa_dur$TOI == "Drawing"] <- "Lack_of_eagerness"

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Lesson"] <- "Lesson"

df_cappa_dur$TOI_class[is.na(df_cappa_dur$TOI_class)] <- "Agitation"

df_cappa_dur$TOI_class <- as_factor(df_cappa_dur$TOI_class)

df_cappa_dur_aggr <- df_cappa_dur %>%
  group_by(TOI_class) %>%
  summarise(Duration_mean_AP_01 = mean(Duration_of_interval_AP_01),
            Duration_mean_MK_01 = mean(Duration_of_interval_MK_01),
            Duration_mean_AP_04 = mean(Duration_of_interval_AP_04),
            Duration_mean_MK_04 = mean(Duration_of_interval_MK_04)
            )

```

#
```{r}
fun_1 <- function(x) {
    y <- x
    return(y)
  }
```

# TOI Reliability
# Start and Duration

# Data Wrangling

```{r, include=TRUE}
df_AP <- df_AP %>% 
  select(TOI, Duration_of_interval, Start_of_interval)

df_MK <- df_MK %>% 
  select(TOI, Duration_of_interval, Start_of_interval)

# Start

df_cappa_start <- matrix(ncol = 3,
                         nrow = 8)

colnames(df_cappa_start) <- c("TOI","Start_of_interval_EH","Start_of_interval_RD")

df_cappa_start <- as_tibble(df_cappa_start)

TOI_names <- c("Calibration_phase","Clicking_pen","Drumming_with_hands",
               "Head_on_table","Heckling","Lesson","Snipping_with_fingers",
               "Whispering")

df_cappa_start$TOI <- TOI_names

# AP Start TOI
for (i in TOI_names) {

  val <- df_AP$Start_of_interval[df_AP == i]

  df_cappa_start$Start_of_interval_AP[df_cappa_start$TOI == i] <- val
}

# MK Start TOI
for (i in TOI_names) {

  val <- df_MK$Start_of_interval[df_MK == i]

  df_cappa_start$Start_of_interval_MK[df_cappa_start$TOI == i] <- val
}

# Duration

df_cappa_dur <- matrix(ncol = 3,
                       nrow = 8)

colnames(df_cappa_dur) <- c("TOI","Duration_of_interval_EH","Duration_of_interval_RD")

df_cappa_dur <- as_tibble(df_cappa_dur)

TOI_names <- c("Calibration_phase","Clicking_pen","Drumming_with_hands",
               "Head_on_table","Heckling","Lesson","Snipping_with_fingers",
               "Whispering")

df_cappa_dur$TOI <- TOI_names

# AP Duration TOI
for (i in TOI_names) {

  val <- df_AP$Duration_of_interval[df_AP == i]

  df_cappa_dur$Duration_of_interval_AP[df_cappa_dur$TOI == i] <- val
}

# MK Duration TOI
for (i in TOI_names) {

  val <- df_MK$Duration_of_interval[df_MK == i]

  df_cappa_dur$Duration_of_interval_MK[df_cappa_dur$TOI == i] <- val
}

# In seconds

df_cappa_dur$Duration_of_interval_AP <- round(df_cappa_dur$Duration_of_interval_AP/1000,
                                              digits = 2
                                              )

df_cappa_dur$Duration_of_interval_MK <- round(df_cappa_dur$Duration_of_interval_MK/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_AP <- round(df_cappa_start$Start_of_interval_AP/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_MK <- round(df_cappa_start$Start_of_interval_MK/1000,
                                              digits = 2
                                             )
```

```{r, include=FALSE}
fun_1 <- function(x) {
    y <- x
    return(y)
  }
```

# Reliabiltät

## Plotting Duration

```{r, echo=TRUE}
cor.test(x = df_cappa_dur$Duration_of_interval_AP,
     y = df_cappa_dur$Duration_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_dur,
               Duration_of_interval_AP,
               Duration_of_interval_MK
               )
    )

# Lesson is significant longer and gives a biased view on the points.

ggplot(data = filter(df_cappa_dur,
                     TOI != "Lesson"),
       mapping = aes(x = Duration_of_interval_AP,
                     y = Duration_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Duration coded by AP",
       y = "Duration coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

### 2023-05-19 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
action alternatives

@@
 
-### action alternatives count (sum score)
+### action alternatives count
 # t-test for expertise differences
@@
        na.rm = TRUE)
+
 ```

### 2023-05-22 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
Neues Morkdowndokument mit Elsevier-Template erstellt

@@
 We used R (Version 4.2.2; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.48; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.2; Wickham, 2021), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{jtools} (Version 2.2.1; Long, 2022), \emph{lm.beta} (Version 1.7.2; Behrendt, 2022), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.58.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.1.9001; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Revelle, 2022), \emph{purrr} (Version 0.3.5; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.1; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.1; Kassambara, 2021), \emph{stringr} (Version 1.4.1; Wickham, 2019), \emph{tibble} (Version 3.1.8; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.2; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.38; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression).
+al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.2; Wickham, 2021), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{jtools} (Version 2.2.1; Long, 2022), \emph{lm.beta} (Version 1.7.2; Behrendt, 2022), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.58.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.1.9001; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Version 2.3.3; Revelle, 2022), \emph{purrr} (Version 0.3.5; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.1; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.1; Kassambara, 2021), \emph{rticles} (Version 0.25; Allaire et al., 2023), \emph{stringr} (Version 1.4.1; Wickham, 2019), \emph{tibble} (Version 3.1.8; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.2; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.38; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression).
 Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}.
@@
 https://doi.org/\url{https://doi.org/10.1016/j.learninstruc.2018.05.006}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rticles}{}}%
+Allaire, J., Xie, Y., Dervieux, C., R Foundation, Wickham, H., Journal of Statistical Software, \ldots{} Hyndman, R.
+(2023).
+\emph{Rticles: Article formats for r markdown}.
+Retrieved from \url{https://CRAN.R-project.org/package=rticles}
 

### 2023-05-22 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier.Rmd
Neues Morkdowndokument mit Elsevier-Template erstellt

--- 2023-04-28 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
@@
 
-bibliography      : "r-references.bib"
+bibliography      : "r-references.bib" # Dateipfad einfügen
 
 floatsintext      : yes
-linenumbers       : yes
+linenumbers       : yes  # Da hatten wir ja mal drüber gesprochen. Kann perspektivisch sicherlich geändert werden
 draft             : no
@@
 
-classoption       : "man"
-output            : bookdown::word_document2 
-# papaja::apa6_pdf
+# classoption       : "man" # unused global option. Was soll das tun?
+output            : 
+  rticles::elsevier_article:
+  bibliography: "r-references.bib"
 
@@
 ```{r setup, include = FALSE}
+library("rticles")
 library("papaja")
-r_refs("r-references.bib")
+r_refs("r-references.bib") # -> ist ein Befehl aus dem Papaja_package. Funktioniert im rticles_Package etwas anders. Muss besprochen werden
 ```
@@
       lme4,
-      viridis)
+      viridis,
+      bibtex)
 
@@
 ## Participants
-```{r demographicstable, include = TRUE, echo=FALSE}
-
-# exclude cases with no fitbit data
-df_demo <- df_demo_all %>% 
-  filter(!ID %in% c("126",
-                     "132",
-                    "236"
-                     )
-          )
-
-# changing gender to count female gender (male = 2 --> 0)
-df_demo$gender = ifelse(df_demo$gender == 2, "1","0")
-
-# changing character Gender into numeric
-df_demo$gender <- as.numeric(df_demo$gender)
-
-# creating new column with total participants to calculate percent of gender
-df_demo <- df_demo %>%
-  mutate(sum_participants = sum(n()))
-
-# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
-df_demo$school_type[df_demo$school_type == 2] <- "1"
-
-# creating new column to calculate percent of school type
-df_demo <- 
-  df_demo %>%
-  group_by(school_type) %>%
-  mutate(count_schooltype = sum(n())) %>% 
-  mutate(percent_schooltype = round((count_schooltype/sum_participants) * 100, 
-         digits = 2))
-
-# changing character Percent_schooltype into numeric
-df_demo$percent_schooltype <- as.numeric(df_demo$percent_schooltype)
-
-#changing type of school into character
-# LI18:
-# 1: Grundschule
-# 2: Oberschule
-# 3: Gymnasium
-# 4: Förderschule/Sondershausen
-# 5: Berufsbildende Schule
-# -1: andere Schulform
-df_demo$school_type <- factor(x = df_demo$school_type,
-                              levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
-                              labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen
-
-# create a basic table (tibble) using tidyverse functions
-df_demo_table <- df_demo %>%
-  ungroup() %>%
-  summarise(N=n(),
-            "Gender female in percent" = round(sum(gender/sum_participants) * 100,
-                                               digits = 2),
-            "M Age in years" = round(mean(age),
-                                     digits = 2),
-            "SD Age in years" = round(sd(age),
-                                      digits = 2),
-            "Min Age in years" = min(age),
-            "Max Age in years" = max(age),
-            "M Teaching Experience in years" = round(mean(teaching_experience),
-                                            digits = 2),
-            "SD Teaching Experience in years" = round(sd(teaching_experience),
-                                            digits = 2),
-            "Min Teaching Experience in years" = min(teaching_experience),
-            "Max Teaching Experience in years" = max(teaching_experience)
-            )
-
-# # format and insert table in manuscript
-# df_demo_table %>%
-# papaja::apa_table(
-#   caption = "Demographic Information",
-#   # note = "Write Note here",
-#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-#   )
-
-```
-
-The sample consisted in total of *N* = `r length(df_demo_all$ID)` pre- and in-service teachers.
-The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
-Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from *N* = `r length(df_demo$ID)` subjects.
-
-The subjects (`r df_demo %>% filter(gender == 1) %>% pull(gender) %>% length()` women; `r df_demo_table %>% pull("Gender female in percent")` %) had a mean age of `r df_demo %>% pull(age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r df_demo_table %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r df_demo_table %>%  pull("Min Age in years")`-`r df_demo_table %>% pull("Max Age in years")`) and an average teaching experience of `r df_demo_table %>% pull("M Teaching Experience in years")` years (*SD* = `r df_demo_table %>% pull("SD Teaching Experience in years")`; range: `r df_demo_table %>% pull("Min Teaching Experience in years")`-`r df_demo_table %>% pull("Max Teaching Experience in years")`).
-
-`r df_demo %>% filter(school_type == "Primary School") %>% pull("percent_schooltype") %>% unique()`% of the subjects were (studying to become) teachers for primary school, `r df_demo %>% filter(school_type == "Secondary School") %>% pull("percent_schooltype") %>% unique()`% were (studying to become) teachers for secondary school and  `r df_demo %>% filter(school_type == "Special Education") %>% pull("percent_schooltype") %>% unique()`% were (studying to become) teachers for special education needs.
-
-All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
-All participants were informed in detail about the aim and intention of the study prior to testing.
-Participation in the study was voluntary and only took place after written consent has been given.
-
-## Material
-
-### Teachers' heart rate
-We used a Fitbit Charge 4 to measure the teachers' heart rate.
-The device was attached 2-finger widths above the ulnar styloid process to the subject’s wrist following the manufacturer’s instructions.
-To determine the heart rate, the Fitbit flashes green LEDs many times per second and uses light-sensitive photodiodes to measure the volume changes in the capillaries and then calculates how many times the heart beats per minute (bpm).
-Data were automatically wireless synced with an iPad via Bluetooth to a Fitbit account, and subsequently, the intraday second-by-second data were exported for each session using the opensource software Pulse Watch (PulseWatch.
-URL: https://iccir919.github.io/pulseWatch/public/index.html [accessed 2022-08-03]).
-
-### Teachers' self-reported data of arousal during the teaching phase
-The subject's self-reported data of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.
-For this purpose, two numerical 11-point rating scales were used: _(1)_	The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption ("On a scale of 0-10: how disruptive did you find the event?
-0 is not disruptive at all, 10 is extremely disruptive") _(2)_	The second rating scale assessed the teacher’s subjective perception of confidence in dealing with the disruptions during the lesson ("How confident did you feel in dealing with this event on a scale of 0-10?
-0 is not confident at all and 10 is extremely confident").
-
-The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjects' self-report and emotional experience, and thus to make them measurable and comparable [@eid2015statistik; @doring2016empirische].
-The gradations of the rating scale were unambiguous and the intervals between them identical.
-The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally to the experimenter.
-
-## Procedure
-
-The data collection was part of a larger research project with a planned sample of *n* = 40 in-service teachers and *n* = 40 pre-service teachers.
-
-The study took place in the rooms of the Faculty of Education at Leipzig University.
-In a controlled laboratory setting, heart rate data in beats per minute (bpm) were recorded using Fitbit Charge 4 over a total period of approximately two hours.
-Within this time frame, teachers taught a 15-minute self-prepared lesson to an audience of three actors.
-
-For this purpose, a seminar room was converted into a classroom.
-The classroom was equipped with a digital whiteboard and a blackboard.
-The fictitious class consisting of three trained actors sat facing the teacher head-on in a "U"; pen and paper were provided on their seats.
-In addition, the students brought their own mobile phone, which was also visibly positioned on the desk.
-
-The subject was instructed during the lesson to behave and move as naturally as possible, as they would in a real classroom.
-In advance, all subjects were given information about planning their lesson in a meeting to ensure that an appropriately realistic teaching situation could take place, e.g.
-it was pointed out that longer film clips as well as group work as a social form should be avoided in order to ensure interaction between teacher and students in the short time of the study.
-
-For analyzing the heart rate data, we focused on five 10-minute intervals of theoretical interest for multiple reason.
-First, 10 minutes was to the minimum duration of all intervals, so we wanted to ensure the comparability of the intervals for all participants.
-Second, @lu2008can confirmed in their study that 10-minute intervals are an useful duration for analyzing photoplethysmography (PPG) data.
-Third, other studies revealed that the first minutes of the lesson start are essential regarding teacher-student interaction [@donker2018quantitative; @claessens2017positive].
-
-The procedure of the study and how we calculated the five phases is described in the following:
-
-_(1)_ The _pre-teaching phase_ was the first 10-minute interval of interest.
-This interval was calculated from the moment the subject arrived and the Fitbit watch was put on, which happened immediately after the subject was welcomed by the experimenter and the three actors.
-After the experimenter briefly explained the project and the procedure of the study to the subject, contact details were subsequently collected as part of the hygiene concept of COVID-19 and the written consent to voluntarily participate in the study was requested.
-Next, the subject was asked to prepare the necessary materials for the lesson (connecting the laptop to the beamer, preparing worksheets, etc.).
-This phase varied in duration according to the prepared lesson (about 1-5min on average).
-
-Once the preparation was completed, the eye-tracking glasses were briefly explained to the subject as well as the adjustment made to the subject by the experimenter (changing the lenses or the nose pad if necessary).
-Subsequently, a 1-point calibration of the eye-tracking glasses took place and together with further devices (GoPro camera, 3D camera, audio recorder) the recordings were started.
-
-Before the lesson began, a warm-up phase took place to familiarize the subject with the laboratory setting and equipment. This warm-up phase consisted of two parts:
-
--	In the first part, the subject and the three actors playfully learned each other's names.
-Additional fictitious name tags of the actors were attached to the table and did not change across the study.
-In the game, by throwing two balls, either the participant's own name or the name of the target person was called.
--	The second part of the warm-up phase involved getting into conversation with each other by asking questions.
-For this purpose, the subject was asked to come up with a question for each of the actors (three questions in total) and was also asked a question in return by each actor.
-This could be anything that interested the participants.
-The questions should be as authentic as possible and were not tailored to the role of the actors.
-The purpose of this warming-up phase was, on the one hand, to make the subject forget about the devices and, on the other hand, to create as realistic as possible a classroom situation in which interactions were based on a teacher-student relationship.
-
-The pre-teaching phase lasted 10-15 minutes on average, depending on different issues (preparing the lesson, technical problems, adjusting the eye-tracking glasses).
-
-_(2)_ The second 10-minute interval was the _teaching phase_, which began with the experimenter noting the time and step count of the fitness tracker.
-The subject was then asked to carry out a 9-point calibration alone in a room next door.
-After the calibration, the lesson started with the subject opening the door to the laboratory room.
-During the lesson, the actors were instructed to simulate nine typical classroom events, three each in the following categories: (a) verbal disruptive behavior (chatting with the neighbor, whispering, heckling), (b) physical disruptions (clicking with a pen, drumming with hands on the table, snipping) and (c) lack of eagerness to learn (drawing on a sheet of paper, putting the head on the table, looking at the phone).
-
-The order of the events and the performing actors were fully balanced with Latin square. The actors were trained before to perform the disruptions identically in each data collection.
-
-After a short familiarization phase for the teacher of two and a half minutes, the instructions appeared as intervals (every 90 seconds for 30 seconds) on a screen that was only visible for the class.
-The actors were trained to stop the disruptive behavior as soon as the teacher intervened.
-
-Time management was regulated by the experimenter by showing time cards (yellow = 1 minute until the end; red = end of the lesson).
-The lesson lasted about 18 minutes on average but only the first 10 minutes were used as an interval to ensure the identical duration for all participants.
-At the end of the lesson, the experimenter again noted the time and the steps on the clock.
-
-_(3)_ The noted time of the lesson end was also the starting point for the _post-teaching_ phase as the third 10-minute interval.
-At the end of the lesson, the experimenter attached letters A through D in the lab while the teacher performed a second 9-point calibration outside.
-The letter search as a control condition was part of another project, which is why it will not be discussed further in the study.
-Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree; EMU, @helmke2014unterrichtsdiagnostik) via the online survey website SoSci Survey.
-The completion of the questionnaire took approximately 5 minutes.
-
-Meanwhile, the experimenter prepared the second part of the data collection: The Stimulated Recall Interview.
-Within post-teaching phase, the majority of subjects completed the questionnaire and positioned themselves next to the experimenter to begin the interview.
-In some cases, the beginning of the interview was part of the post-teaching phase due to individual needs (going to the toilet, spending more time completing the questionnaire, etc.).
-
-_(4)_ The fourth 10-minute interval of interest was the _interview phase_ that was 10 minutes in the middle of the interview.
-To ensure that all subjects were in the middle of the interview, we calculated the difference from the end of the lesson and from the time when the subject took off the watch.
-This duration was divided in two to get to the middle of the interval.
-Then, 5 minutes were subtracted to get to the start of the 10-minute interval.
-
-The interview itself took place using the Think Aloud procedure (Konrad, 2020).
-For this purpose, the eye tracking video was watched again and the experimenter stopped the video at the nine disruptions when they appeared to asks several questions.
-The questions were identical for each disruption, they were asked in a fixed order.
-First, the subject was asked to describe the disruption, to evaluate (11-point rating scale) and justify the disruptiveness of each disruption.
-Next, the subject was asked to describe and justify the reaction.
-The experimenter then asked the subject to evaluate (11-point rating scale) and justify the confidence the subject had in dealing with the disruption.
-Statements about the evaluation of the disruptiveness and the confidence were quantified.
-For this purpose, subjects determined their individual value on a rating scale from 0 (not disturbing / not safe) to 10 (disturbing / safe).
-
-The interview lasted on average 45-60 minutes.
-
-_(5)_ The last interesting interval for the analyses was the _end phase_, which was the 10 minutes before the subject took off the watch.
-In this interval, the subject answered a second questionnaire (Situational Judgment Test, @gold2015development) to assess the subject's strategic knowledge of classroom management.
-The subject was asked to judge alternative actions on school scenarios on a 6-point rating scale from 1 (A) to 6 (F) according to school grades.
-Data from the questionnaire were again collected as an online questionnaire via the website www.soscisurvey.de and lasted approximately 10-15 minutes.
-
-The Fitbit watch was removed only after the last questionnaire to obtain heart rate data during the entire study.
-
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses (descriptive statistics, correlations, and multilevel regression).
-Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio [palmeri2020].
-An alpha level of 0.05 was used for the statistical tests.
-
-### Descriptive statistics
-
-Means, standard deviations and the range of teachers’ heart rate and the self-reported data are shown in Table 2.
-
-```{r descriptive statistics}
-# Mean, SD and range for overall (unstandardized)
-descrip_hr_overall <- main %>%
-  filter(time_span %in% c("overall")) %>% 
-  summarise(N = n_distinct(ID),
-            "M heart rate in bpm" = round(mean(heart_rate),
-                                     digits = 2),
-            "SD heart rate in bpm" = round(sd(heart_rate),
-                                      digits = 2),
-            "Min heart rate in bpm" = min(heart_rate),
-            "Max heart rate in bpm" = max(heart_rate)
-  )
-
-# Mean, SD and range for overall (standardized)
-descrip_hr_overall_std <- main %>%
-  filter(time_span %in% c("overall")) %>% 
-  summarise(N = n_distinct(ID),
-            "M std heart rate in bpm" = round(mean(heart_rate_std),
-                                              digits = 2),
-            "SD std heart rate in bpm" = round(sd(heart_rate_std),
-                                               digits = 2),
-            "Min std heart rate in bpm" = round(min(heart_rate_std),
-                                                digits = 2),
-            "Max heart rate in bpm" = round(max(heart_rate_std),
-                                            digits = 2)
-            )
-
-# Mean, SD and range for individual phases (unstandardized)
-descrip_hr_phases <- main %>% 
-  filter(!time_span %in% c("overall")) %>% 
-  group_by(time_span) %>% 
-  summarise(N = n_distinct(ID),
-            "M heart rate in bpm" = round(mean(heart_rate),
-                                     digits = 2),
-            "SD heart rate in bpm" = round(sd(heart_rate),
-                                      digits = 2),
-            "Min heart rate in bpm" = min(heart_rate),
-            "Max heart rate in bpm" = max(heart_rate)
-  )
-
-# Mean, SD and range for individual phases (standardized)
-descrip_hr_phases_std <- main %>% 
-  filter(!time_span %in% c("overall")) %>% 
-  group_by(time_span) %>% 
-  summarise(N = n_distinct(ID),
-            "M heart rate in bpm" = round(mean(heart_rate_std),
-                                     digits = 2),
-            "SD heart rate in bpm" = round(sd(heart_rate_std),
-                                      digits = 2),
-            "Min heart rate in bpm" = round(min(heart_rate_std),
-                                            digits = 2),
-            "Max heart rate in bpm" = round(max(heart_rate_std),
-                                            digits = 2)
-  )
-
-# # format and insert table in manuscript
-# descrip_hr_phases %>%
-# papaja::apa_table(
-#   caption = "Mean, SD and range for teachers' heart rate in individual phases",
-#   # note = "Write Note here",
-#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-#   )
-
-# Mean, SD and range for disruption and confidence factor
-rating_table <- 
-  df_rating %>% 
-  filter(!is.na(confidence_factor),
-         !is.na(disruption_factor)) %>% 
-   summarise(N = n_distinct(ID), 
-            "M disruption factor" = round(mean(disruption_factor),
-                                     digits = 2),
-            "SD disruption factor" = round(sd(disruption_factor),
-                                      digits = 2),
-            "Min disruption factor" = min(disruption_factor),
-            "Max disruption factor" = max(disruption_factor),
-            "M confidence factor" = round(mean(confidence_factor),
-                                     digits = 2),
-            "SD confidence factor" = round(sd(confidence_factor),
-                                      digits = 2),
-            "Min confidence factor" = min(confidence_factor),
-            "Max confidence factor" = max(confidence_factor)
-            )
-
-```
-
-Teachers’ average heart rate during the entire course of the study was approximately `r descrip_hr_overall %>% pull("M heart rate in bpm")` bpm with a standard deviation of `r descrip_hr_overall %>% pull("SD heart rate in bpm")` and a range from `r descrip_hr_overall %>% pull("Min heart rate in bpm")` to `r descrip_hr_overall %>% pull("Max heart rate in bpm")` bpm.
-
-Means, standard deviations and the range of teachers’ heart rate for the different phases and the self-reported data are shown in Table 2.
-
-### Pairwaise t-test and effect size
-
-### Multilevel regressions
-
-XXX
-
-# Results
-
-# First visual results
-
-The graph \@ref(fig:overall_plot) show the heart rate for the entire course of the study.
-
-```{r overall_plot, fig.height = 8, fig.width = 15}
-
-  main %>% 
-  filter(time_span == "overall") %>% 
-  select("ID","time_span", "time","heart_rate") %>% 
-  distinct() %>% 
-  ggplot(mapping = aes(x = time,
-                       y = heart_rate
-                       )
-         ) +
- # stat_smooth(geom = "line",
- #             method = "loess",
- #             se = FALSE) +
-  geom_smooth(method = "loess",
-              se = FALSE) +
-  scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  labs(x = "Time (in seconds)",
-       y = "Heart rate (in beats per minute)") +
-  theme_apa() -> overall_plot
-
-overall_plot
-
-```
-
-The second graph \@ref(fig:phase_plot) show the heart rate for the individual five phases.
-
-```{r phase_plot, fig.height = 8, fig.width = 15}
-
-main %>% 
-  filter(time_span != "overall") %>% 
-  select("ID","time_span", "time","heart_rate") %>% 
-  mutate(
-    # status = case_when(ID < 200 ~ "Unerfahren",
-    #                         ID > 200 ~ "Erfahren"),
-         time_span = fct_recode(time_span,
-                                "Pre-teaching phase" = "pre",
-                                "Teaching phase" = "main",
-                                "Post-teaching phase" = "subsequent",
-                                "Intview phase" = "interview",
-                                "End phase" = "after"
-                                ),
-         time_span = factor(time_span,
-                            levels = c("Pre-teaching phase",
-                                       "Teaching phase",
-                                       "Post-teaching phase",
-                                       "Intview phase",
-                                       "End phase"
-                                       )
-                            )
-         ) %>%
-  distinct() %>% 
-ggplot(mapping = aes(x = time,
-                     y = heart_rate
-                     )
-       ) +
-  geom_smooth(method = "glm") +
-  scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  labs(x = "Time (in seconds)",
-       y = "Heart rate (in beats per minute)") +
-  theme_apa() +
-  facet_grid(cols = vars(time_span),
-             scales = "free_x",
-             ) -> phase_plot
-
-phase_plot
-
-```
-
-# Discussion and implications
-
-\newpage
-
-# References
-
-::: {#refs custom-style="Bibliography"}
-:::

### 2023-05-22 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier.tex
Neues Morkdowndokument mit Elsevier-Template erstellt

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
  \linenumbers % turns line numbering on
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

% Pandoc syntax highlighting
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\begin{frontmatter}

  \title{New approaches to teachers' experience of stress: Do heart rate
measurements with fitness trackers provide an efficient, inexpensive,
and robust measurement method?}
    \author[1]{Mandy Klatt%
  %
  }
   \ead{mandy.klatt@uni-leipzig.de} 
    \author[1]{Peer Keßler%
  %
  }

    \author[1,2]{Gregor Kachel%
  %
  }

    \author[1]{Christin Lotz%
  %
  }

    \author[1]{Anne Deiglmayr%
  %
  }

      \cortext[cor1]{Corresponding author}

  \begin{abstract}
  One or two sentences providing a \textbf{basic introduction} to the
  field, comprehensible to a scientist in any discipline.

  Two to three sentences of \textbf{more detailed background},
  comprehensible to scientists in related disciplines.

  One sentence clearly stating the \textbf{general problem} being
  addressed by this particular study.

  One sentence summarizing the main result (with the words
  ``\textbf{here we show}'' or their equivalent).

  Two or three sentences explaining what the \textbf{main result}
  reveals in direct comparison to what was thought to be the case
  previously, or how the main result adds to previous knowledge.

  One or two sentences to put the results into a more \textbf{general
  context}.

  Two or three sentences to provide a \textbf{broader perspective},
  readily comprehensible to a scientist in any discipline.

  XXX In this proof-of-concept study, we aimed to advance the field of
  teacher stress by collecting heart rate data with wrist-worn devices
  and testing a methodology that has the potential to provide more
  insights on the non-invasive assessment of teacher stress. XXX
  \end{abstract}
    \begin{keyword}
    heart rate; photoplethysmography; wearable electronic device;
teaching \sep 
    heart rate; photoplethysmography; wearable electronic device;
teaching
  \end{keyword}

 \end{frontmatter}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Seed for random number generation}
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{42}\NormalTok{)}
\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{cache.extra =}\NormalTok{ knitr}\SpecialCharTok{::}\NormalTok{rand\_seed)}
\end{Highlighting}
\end{Shaded}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Physiological data such as heart rate are becoming increasingly
important in research on stress experience. They represent an important
indicator of physical or emotional stress, as increased workload is
associated with increased heart rate \citep{sachs2014physiologische}.
Furthermore, they allow a more objective recording of stress than
self-reports \citep{rungeusing}. However, capturing heart rate in an
educational context requires the use of low-cost and non-invasive
instruments. Fitness trackers worn on the wrist have the potential to be
such a useful tool \citep{ferguson2015validity}.

To date, there is still little evidence on the usefulness of heart rate
measurements using fitness trackers in teaching and learning settings
\citep{ertzberger2016use, lowe2016educational}. \citet{rungeusing} alone
examined teacher stress in a relatively small sample (\emph{N} = 4
teachers) and showed that high heart rate indicates more stress in
teachers.

Thus, there remains a lack of robust studies on whether fitness trackers
are an efficient, low-cost, and robust measurement method for assessing
teachers' experience of arousal during teaching.

\hypertarget{theoretical-background}{%
\section{Theoretical Background}\label{theoretical-background}}

\hypertarget{stress-in-teaching-profession}{%
\subsection{Stress in Teaching
Profession}\label{stress-in-teaching-profession}}

--\textgreater{} teacher profession is one of the most stressful
professions.

Teacher stress can be defined as ``{[}\ldots{]} the experience by a
teacher of unpleasant, negative emotions, such as anger, anxiety,
tension, frustration or depression, resulting from some aspect of their
work as a teacher.'' \citep{kyriacou2001teacher}.

Teachers' individual perceptions of student misbehavior in the classroom
are closely related to their well-being \citep{ALDRUP2018126}.

--\textgreater{} wie entsteht Stress

--\textgreater{} wie wurde Stress bisher gemessen

\hypertarget{heart-rate-as-an-indicator-for-stress-or-arousal}{%
\subsection{Heart rate as an indicator for stress or
arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}

Heart rate is physiologically regulated by the autonomic nervous system.
An increase in the activity of the sympathetic as part of the autonomic
nervous system results in the heart rate being speeded up (``fight or
flight''). On the other hand, an increased activity of the
parasympathetic as the counterpart has the effect of slowing down the
heart rate (``rest and digest'') \citep{Battipaglia2015}. In addition to
the autonomic nervous system and genetic factors, heart rate is
influenced by numerous external factors such as social, personal,
psychological, environmental and behavioural factors
\citep{wang2022using}.

\hypertarget{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}{%
\subsection{Wrist-worn devices as a new approach to assess physiological
measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}

\citet{fuller2020reliability} showed in their review article that
wearable devices such as Fitbit watches are accurate and reliable for
measuring heart rate in controlled settings.

``The use of physiological measures enabled us to get some insight into
teachers' affective responses without disrupting the teaching process
(Mauss \& Robinson, 2009) and to reduce issues with social desirability,
retrospective bias, and high cognitive load (Becker et al., 2015; Goetz
et al., 2015; Scollon et al.,2009; Wilhelm \& Grossman, 2010). Moreover,
we found that heart rate measures discriminated between both teachers,
even when their interpersonal behavior during the lesson start was
relatively similar.''

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{19}
\tightlist
\item
  (PDF) A Quantitative Exploration of Two Teachers with Contrasting
  Emotions: Intra-Individual Process Analyses of Physiology and
  Interpersonal Behavior. Available from:
  https://www.researchgate.net/publication/329787434\_A\_Quantitative\_Exploration\_of\_Two\_Teachers\_with\_Contrasting\_Emotions\_Intra-Individual\_Process\_Analyses\_of\_Physiology\_and\_Interpersonal\_Behavior
  {[}accessed Dec 07 2022{]}.
\end{enumerate}

\hypertarget{aim-of-the-study}{%
\subsection{Aim of the study}\label{aim-of-the-study}}

In the present study, we assessed HR measures and self-report data of
pre- and in-service teachers in a controlled teaching-learning setting.
The aim was to investigate whether heart rate measurements using
wrist-worn fitness trackers are a suitable and effective method
\textbf{(1)} to map differences in states of arousal between five
different phases (pre-teaching phase, teaching phase, post-teaching
phase, interview phase and end phase) and \textbf{(2)} to evaluate the
correlation between self-reported evaluations and HR measures.

\textbf{(H1)} We expected heart rates to be higher during the teaching
phase than during the pre- and the three post-teaching phases, and that
the HR measures would decrease over the course of the study.
\textbf{(H2)} We also predicted that HR and a high ranking on the
negative scale on our survey (feeling disturbed by disruptions) would
correlate positively and a high ranking on the positive scale (feeling
confident in dealing with disruptions) would follow the inverse pattern.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if
any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\bibliography{r-references.bib}

\end{document}

### 2023-05-22 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier/fitbit_paper_elsevier.tex
Neues Morkdowndokument mit Elsevier-Template erstellt

--- 2023-05-22 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier.tex
@@
-\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+\documentclass[man]{elsarticle} %review=doublespace preprint=single 5p=2 column
 %%% Begin My package additions %%%%%%%%%%%%%%%%%%%
@@
 \setcounter{secnumdepth}{0}
-
-% Pandoc syntax highlighting
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Seed for random number generation}
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{42}\NormalTok{)}
-\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{cache.extra =}\NormalTok{ knitr}\SpecialCharTok{::}\NormalTok{rand\_seed)}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Physiological data such as heart rate are becoming increasingly
-important in research on stress experience. They represent an important
-indicator of physical or emotional stress, as increased workload is
-associated with increased heart rate \citep{sachs2014physiologische}.
-Furthermore, they allow a more objective recording of stress than
-self-reports \citep{rungeusing}. However, capturing heart rate in an
-educational context requires the use of low-cost and non-invasive
-instruments. Fitness trackers worn on the wrist have the potential to be
-such a useful tool \citep{ferguson2015validity}.
-
-To date, there is still little evidence on the usefulness of heart rate
-measurements using fitness trackers in teaching and learning settings
-\citep{ertzberger2016use, lowe2016educational}. \citet{rungeusing} alone
-examined teacher stress in a relatively small sample (\emph{N} = 4
-teachers) and showed that high heart rate indicates more stress in
-teachers.
-
-Thus, there remains a lack of robust studies on whether fitness trackers
-are an efficient, low-cost, and robust measurement method for assessing
-teachers' experience of arousal during teaching.
-
-\hypertarget{theoretical-background}{%
-\section{Theoretical Background}\label{theoretical-background}}
-
-\hypertarget{stress-in-teaching-profession}{%
-\subsection{Stress in Teaching
-Profession}\label{stress-in-teaching-profession}}
-
---\textgreater{} teacher profession is one of the most stressful
-professions.
-
-Teacher stress can be defined as ``{[}\ldots{]} the experience by a
-teacher of unpleasant, negative emotions, such as anger, anxiety,
-tension, frustration or depression, resulting from some aspect of their
-work as a teacher.'' \citep{kyriacou2001teacher}.
-
-Teachers' individual perceptions of student misbehavior in the classroom
-are closely related to their well-being \citep{ALDRUP2018126}.
-
---\textgreater{} wie entsteht Stress
-
---\textgreater{} wie wurde Stress bisher gemessen
-
-\hypertarget{heart-rate-as-an-indicator-for-stress-or-arousal}{%
-\subsection{Heart rate as an indicator for stress or
-arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}
-
-Heart rate is physiologically regulated by the autonomic nervous system.
-An increase in the activity of the sympathetic as part of the autonomic
-nervous system results in the heart rate being speeded up (``fight or
-flight''). On the other hand, an increased activity of the
-parasympathetic as the counterpart has the effect of slowing down the
-heart rate (``rest and digest'') \citep{Battipaglia2015}. In addition to
-the autonomic nervous system and genetic factors, heart rate is
-influenced by numerous external factors such as social, personal,
-psychological, environmental and behavioural factors
-\citep{wang2022using}.
-
-\hypertarget{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}{%
-\subsection{Wrist-worn devices as a new approach to assess physiological
-measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}
-
-\citet{fuller2020reliability} showed in their review article that
-wearable devices such as Fitbit watches are accurate and reliable for
-measuring heart rate in controlled settings.
-
-``The use of physiological measures enabled us to get some insight into
-teachers' affective responses without disrupting the teaching process
-(Mauss \& Robinson, 2009) and to reduce issues with social desirability,
-retrospective bias, and high cognitive load (Becker et al., 2015; Goetz
-et al., 2015; Scollon et al.,2009; Wilhelm \& Grossman, 2010). Moreover,
-we found that heart rate measures discriminated between both teachers,
-even when their interpersonal behavior during the lesson start was
-relatively similar.''
-
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{19}
-\tightlist
-\item
-  (PDF) A Quantitative Exploration of Two Teachers with Contrasting
-  Emotions: Intra-Individual Process Analyses of Physiology and
-  Interpersonal Behavior. Available from:
-  https://www.researchgate.net/publication/329787434\_A\_Quantitative\_Exploration\_of\_Two\_Teachers\_with\_Contrasting\_Emotions\_Intra-Individual\_Process\_Analyses\_of\_Physiology\_and\_Interpersonal\_Behavior
-  {[}accessed Dec 07 2022{]}.
-\end{enumerate}
-
-\hypertarget{aim-of-the-study}{%
-\subsection{Aim of the study}\label{aim-of-the-study}}
-
-In the present study, we assessed HR measures and self-report data of
-pre- and in-service teachers in a controlled teaching-learning setting.
-The aim was to investigate whether heart rate measurements using
-wrist-worn fitness trackers are a suitable and effective method
-\textbf{(1)} to map differences in states of arousal between five
-different phases (pre-teaching phase, teaching phase, post-teaching
-phase, interview phase and end phase) and \textbf{(2)} to evaluate the
-correlation between self-reported evaluations and HR measures.
-
-\textbf{(H1)} We expected heart rates to be higher during the teaching
-phase than during the pre- and the three post-teaching phases, and that
-the HR measures would decrease over the course of the study.
-\textbf{(H2)} We also predicted that HR and a high ranking on the
-negative scale on our survey (feeling disturbed by disruptions) would
-correlate positively and a high ranking on the positive scale (feeling
-confident in dealing with disruptions) would follow the inverse pattern.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We report how we determined our sample size, all data exclusions (if
-any), all manipulations, and all measures in the study.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
 \bibliography{r-references.bib}

### 2023-05-30 01_studies/01_Laborstudie ProVisioNET/R script/reli/ProVisioNET_reli_action_alternatives.R
reli altern. actions

@@ -22,23 +22,27 @@ options(dplyr.summarise.inform = FALSE)
 ################## RATER 1 ################
 
 # read in data from rater1 while specifying locale allows to set "," 
-r1 <-read_excel ("./data/coding_handlungsalternativen_JG.xlsx", col_names = TRUE)
+r1 <-read_excel ("./data/coding_reactions_MK.xlsx", col_names = TRUE)
 
 
 ################## RATER 2 ################
 
 # read in data from rater1 while specifying locale allows to set "," 
-r2 <-read_excel ("./data/coding_handlungsalternativen_MK.xlsx", col_names = TRUE)
+r2 <-read_excel ("./data/coding_reactions_GS.xlsx", col_names = TRUE)
 
-r4 <-read_excel ("./data/coding_handlungsalternativen_JG_MK_nur_ratings.xlsx", col_names = TRUE)
+# read in data from two ratings
+r3 <-read_excel ("./data/coding_handlungsalternativen_JG_MK_nur_ratings.xlsx", col_names = TRUE) %>% 
+  select(code1, code2)
+
+# read in data from two rating 
 
 ################## DATA WRANGLING video 01 ################
 
 # filter relevant rows and select relevant columns
-r1 <- r1 %>% select(number) %>% 
+r1 <- r1 %>% select(code) %>% 
   na.omit(r1)
   
-r2 <- r2 %>% select(number) %>% 
+r2 <- r2 %>% select(code) %>% 
   na.omit(r2)
 
 # # reshape data frame in long format 
@@ -52,14 +56,14 @@ r2 <- r2 %>% select(number) %>%
 #                names_to = "Event", 
 #                values_to = "Value")
 
-r1$number <- as.numeric(r1$number)
-r2$number <- as.numeric(r2$number)
+r1$code <- as.numeric(r1$code)
+r2$code <- as.numeric(r2$code)
 
 
-r3 <- bind_cols(r1$number, r2$number)
+r3 <- bind_cols(r1$code, r2$code)
 
 #################### Percentage Agreement ##############################
-agree(r3, tolerance = 0)
+agree(r3, tolerance = 1)
 
 r4 <- subset(r4, select = c(code1, code2))
 agree(r4, tolerance = 0)

### 2023-05-30 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
action alt. r code
Update reaction_action_alternatives.Rmd

@@
          nd_sum = sum(nd),
-         sum = sum(n()),
-         percent_reaction = round((reaction_sum/sum),
+         sum_participants = sum(n()),
+         percent_reaction = round((reaction_sum/sum_participants),
                                   digits = 2),
@@
 # effect size for expertise differences
-CohenD(x = main$nd[main$id == "Expert"],
-       y = main$nd[main$id == "Novice"],
+CohenD(x = main$percent_nd[main$id == "Expert"],
+       y = main$percent_nd[main$id == "Novice"],
        na.rm = TRUE)
@@
 ```
+
+# correlation: count x efficacy

### 2023-05-30 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
Update reaction_action_alternatives.Rmd

@@
 
-# correlation: count x efficacy
+# correlation: count x quality 
+```{r}
+
+# filter for novices
+main %>% 
+  filter(id %in% c("Novice")) -> corr.nov
+
+# filter for novices
+main %>% 
+  filter(id %in% c("Expert")) -> corr.exp
+
+# novices: correlation between count and quality
+cor.test(corr.nov$count, corr.nov$nd, method=c("spearman"))
+
+# experts: correlation between count and quality
+cor.test(corr.exp$count, corr.exp$nd, method=c("spearman"))
+
+```
+
+# correlation: reaction x count 
+```{r}
+
+# novices: correlation between reaction and count
+cor.test(corr.nov$count, corr.nov$reaction, method=c("spearman"))
+
+# experts: correlation between count and quality
+cor.test(corr.exp$count, corr.exp$nd, method=c("spearman"))
+
+```

### 2023-05-31 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
action alternatives

@@
 
-# correlation: count x quality 
+# correlation: count x quality (sum score)
 ```{r}
@@
 # novices: correlation between count and quality
-cor.test(corr.nov$count, corr.nov$nd, method=c("spearman"))
+cor.test(corr.nov$count, corr.nov$nd, method=c("pearson"))
 
 # experts: correlation between count and quality
-cor.test(corr.exp$count, corr.exp$nd, method=c("spearman"))
+cor.test(corr.exp$count, corr.exp$nd, method=c("pearson"))
+
+```
+
+# correlation: count x quality (relative score)
+```{r}
+
+# novices: correlation between count and quality
+cor.test(corr.nov$count, corr.nov$percent_nd, method=c("pearson"))
+
+# experts: correlation between count and quality
+cor.test(corr.exp$count, corr.exp$percent_nd, method=c("pearson"))
 

### 2023-05-31 01_studies/01_Laborstudie ProVisioNET/R script/reli/ProVisioNET_reli_action_alternatives.R
reli act. alternatives

@@ -19,64 +19,38 @@ needs(tidyverse,
 options(dplyr.summarise.inform = FALSE)
 
 
-################## RATER 1 ################
+# read in data for numbers of action alternatives
+df_number <- read_excel ("./data/coding_handlungsalternativen_JG_MK_number.xlsx", col_names = TRUE) %>% 
+  select(rater1, rater2)
 
-# read in data from rater1 while specifying locale allows to set "," 
-r1 <-read_excel ("./data/coding_reactions_MK.xlsx", col_names = TRUE)
-
-
-################## RATER 2 ################
-
-# read in data from rater1 while specifying locale allows to set "," 
-r2 <-read_excel ("./data/coding_reactions_GS.xlsx", col_names = TRUE)
-
-# read in data from two ratings
-r3 <-read_excel ("./data/coding_handlungsalternativen_JG_MK_nur_ratings.xlsx", col_names = TRUE) %>% 
-  select(code1, code2)
-
-# read in data from two rating 
-
-################## DATA WRANGLING video 01 ################
-
-# filter relevant rows and select relevant columns
-r1 <- r1 %>% select(code) %>% 
-  na.omit(r1)
-  
-r2 <- r2 %>% select(code) %>% 
-  na.omit(r2)
-
-# # reshape data frame in long format 
-# r1_long <- r1 %>% 
-#   pivot_longer(!ID, 
-#                names_to = "Event", 
-#                values_to = "Value")
-# 
-# r2_long <- r2 %>% 
-#   pivot_longer(!ID, 
-#                names_to = "Event", 
-#                values_to = "Value")
-
-r1$code <- as.numeric(r1$code)
-r2$code <- as.numeric(r2$code)
-
-
-r3 <- bind_cols(r1$code, r2$code)
+# read in data for rating of action alternatives
+df_rating <- read_excel ("./data/coding_handlungsalternativen_JG_MK_ratings.xlsx", col_names = TRUE) %>% 
+  mutate(rater1 = as.numeric(case_when(rater1 > 3 ~ '0',
+                                       rater1 <= 3 ~ '1',
+                                       TRUE ~ 'F')
+                             ),
+         rater2 = as.numeric(case_when(rater2 > 3 ~ '0',
+                                       rater2 <= 3 ~ '1',
+                                       TRUE ~ 'F')
+                             )
+         ) %>%
+  select(rater1, rater2)
 
[…]

### 2023-07-15 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fitbit data

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, warning = FALSE)
+knitr::opts_chunk$set(
+	echo = TRUE,
+	error = FALSE,
+	message = FALSE,
+	warning = FALSE
+)
 ```
@@
             n = NA,
-            `Mean(Intercept)` = mean_intercept,
-            `SD(Intercept)` = sd_intercept,
+            `Mean(Intercept)` = round(mean_intercept, digits = 3),
+            `SD(Intercept)` = round(sd_intercept, digits = 3),
             `p-Value (Intercept)` = p.value_intercept,
-            `Mean(Slope)` = mean_slope, 
-            `SD(Slope)` = sd_slope,
+            `Mean(Slope)` = round(mean_slope, digits = 3), 
+            `SD(Slope)` = round(sd_slope,digits = 3),
             `p-Value (Slope)` = p.value_slope, 
@@
 
-```{r}
+```{r echo = FALSE, results='asis'}
 df_multi <- 
@@
 stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
-                     type = "latex",
+                     type = "html",
                      caption = "Pre Teaching Phase",
@@
 
-# Post Teaching Phase
+# Teaching Phase
 
-```{r}
+```{r echo = FALSE, results='asis'}
 df_multi <- 
@@
             y = fix_models,
-            by = "id")
+            by = "id") %>% 
+  mutate(posneg = if_else(condition = slope < 0,
+                          true = "negative",
+                          false = "positive"))
+fit_teach_1 <-
+  df_multi %>% 
+  filter(Phase == "Teaching Phase") %>% 
+  split(.$posneg) %>% 
+  map(~ lm(slope ~ disruption,
+           data = .))
+
+df_multi %>% 
+  filter(Phase == "Teaching Phase") %$% 
+  lm(slope ~ disruption:posneg)
+
+fit_teach_2 <-
+  df_multi %>% 
+  filter(Phase == "Teaching Phase") %$% 
+  lm(slope ~ confidence)
+
+fit_teach_3 <-
+  df_multi %>% 
+  filter(Phase == "Post Teaching Phase") %$% 
+  lm(slope ~ teaching_experience)
+
+fit_teach_4 <-
+  df_multi %>% 
+  filter(Phase == "Teaching Phase") %$% 
+  lm(slope ~ confidence + disruption)
+
+fit_teach_5 <-
+  df_multi %>% 
+  filter(Phase == "Teaching Phase") %$% 
+  lm(slope ~ confidence + disruption + teaching_experience)
+
+stargazer::stargazer(fit_teach_1, fit_teach_2,fit_teach_3, fit_teach_4, fit_teach_5,
+                     type = "html",
+                     caption = "Teaching Phase",
+                     dep.var.labels = "Slope",
+                     order = c(1, 2, 3),
+                     covariate.labels = c("Disruption Factor",
+                                          "Confidence Factor",
+                                          "Teaching Experience"),
+                     keep.stat = c("n","rsq","adj.rsq")
+                     )
+```
+
+# Post Teaching Phase
+
+```{r echo = FALSE, results='asis'}
+df_multi <- 
+  main %>% 
+  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  summarize(disruption = mean(disruption_factor, na.rm = T),
+            confidence = mean(confidence_factor, na.rm = T),
+            teaching_experience) %>% 
+  ungroup() %>% 
+  mutate(id = as.character(ID)) %>% 
+  distinct() %>% 
+  right_join(x = .,
+            y = fix_models,
+            by = "id") %>% 
+  mutate(posneg = if_else(condition = slope < 0,
+                          true = "negative",
+                          false = "positive"))
 
@@
 stargazer::stargazer(fit_post_1, fit_post_2,fit_post_3, fit_post_4, fit_post_5,
-                     type = "latex",
-                #     caption = "Post Teaching Phase",
+                     type = "html",
+                     caption = "Post Teaching Phase",
                      dep.var.labels = "Slope",
@@
 ```
+
+# Interview Phase
+
+```{r echo = FALSE, results='asis'}
+df_multi <- 
+  main %>% 
+  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  summarize(disruption = mean(disruption_factor, na.rm = T),
+            confidence = mean(confidence_factor, na.rm = T),
+            teaching_experience) %>% 
+  ungroup() %>% 
+  mutate(id = as.character(ID)) %>% 
+  distinct() %>% 
+  right_join(x = .,
+            y = fix_models,
+            by = "id") %>% 
+  mutate(posneg = if_else(condition = slope < 0,
+                          true = "negative",
+                          false = "positive"))
+
+fit_inter_1 <-
+  df_multi %>% 
+  filter(Phase == "Interview Phase") %>% 
+  split(.$posneg) %>% 
+  map(~ lm(slope ~ disruption,
+           data = .))
+
+df_multi %>% 
+  filter(Phase == "Interview Phase") %$% 
+  lm(slope ~ disruption:posneg)
+
+fit_inter_2 <-
+  df_multi %>% 
+  filter(Phase == "Interview Phase") %$% 
+  lm(slope ~ confidence)
+
+fit_inter_3 <-
+  df_multi %>% 
+  filter(Phase == "Interview Phase") %$% 
+  lm(slope ~ teaching_experience)
+
+fit_inter_4 <-
+  df_multi %>% 
+  filter(Phase == "Interview Phase") %$% 
+  lm(slope ~ confidence + disruption)
+
+fit_inter_5 <-
+  df_multi %>% 
+  filter(Phase == "Interview Phase") %$% 
+  lm(slope ~ confidence + disruption + teaching_experience)
+
+stargazer::stargazer(fit_post_1, fit_post_2,fit_post_3, fit_post_4, fit_post_5,
+                     type = "html",
+                     caption = "Interview Phase",
+                     dep.var.labels = "Slope",
+                     order = c(1, 2, 3),
+                     covariate.labels = c("Disruption Factor",
+                                          "Confidence Factor",
+                                          "Teaching Experience"),
+                     keep.stat = c("n","rsq","adj.rsq")
+                     )
+```
+
+# End Phase
+
+```{r echo = FALSE, results='asis'}
+df_multi <- 
+  main %>% 
+  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  summarize(disruption = mean(disruption_factor, na.rm = T),
+            confidence = mean(confidence_factor, na.rm = T),
+            teaching_experience) %>% 
+  ungroup() %>% 
+  mutate(id = as.character(ID)) %>% 
+  distinct() %>% 
+  right_join(x = .,
+            y = fix_models,
+            by = "id") %>% 
+  mutate(posneg = if_else(condition = slope < 0,
+                          true = "negative",
+                          false = "positive"))
+
+fit_end_1 <-
+  df_multi %>% 
+  filter(Phase == "End Phase") %>% 
+  split(.$posneg) %>% 
+  map(~ lm(slope ~ disruption,
+           data = .))
+
+df_multi %>% 
+  filter(Phase == "End Phase") %$% 
+  lm(slope ~ disruption:posneg)
+
+fit_end_2 <-
+  df_multi %>% 
+  filter(Phase == "End Phase") %$% 
+  lm(slope ~ confidence)
+
+fit_end_3 <-
+  df_multi %>% 
+  filter(Phase == "End Phase") %$% 
+  lm(slope ~ teaching_experience)
+
+fit_end_4 <-
+  df_multi %>% 
+  filter(Phase == "End Phase") %$% 
+  lm(slope ~ confidence + disruption)
+
+fit_end_5 <-
+  df_multi %>% 
+  filter(Phase == "End Phase") %$% 
+  lm(slope ~ confidence + disruption + teaching_experience)
+
+stargazer::stargazer(fit_post_1, fit_post_2,fit_post_3, fit_post_4, fit_post_5,
+                     type = "html",
+                     caption = "End Phase",
+                     dep.var.labels = "Slope",
+                     order = c(1, 2, 3),
+                     covariate.labels = c("Disruption Factor",
+                                          "Confidence Factor",
+                                          "Teaching Experience"),
+                     keep.stat = c("n","rsq","adj.rsq")
+                     )
+```

### 2023-07-15 02_paper/02_study/02_fitbit paper/test.Rmd
fitbit data

---
title: "Getting familiar with Rmarkdown PDF"
author: |
  | Arimitra Maiti
  | Author-2
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    keep_tex: yes
    latex_engine: pdflatex
    fig_caption: yes
    highlight: haddock
    number_sections: yes
    toc: yes
    toc_depth: 2
    citation_package: natbib
abstract: This is the section for abstract with a limit of 150 words.\par \textbf{Keywords:}
  Keyword-1, Keyword-2, Keyword-3, Keyword-4
subtitle: |
  | Examples for Towards Data Science
  | Focussing on Metadata
  | Reviewed by: Towards Data Science Team
geometry: left=2.5cm,right=2.5cm,top=2cm,bottom=2cm
fontfamily: mathpazo
thanks: |
  This is the section for acknoledgement with a limit of 150 words
header-includes:
- \usepackage{graphicx}
- \usepackage{float}
- \usepackage{amsmath}
- \nocite{*}
bibliography: example.bib
biblio-style: apalike
natbiboptions: round
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r echo=FALSE, results='asis'}
library("rmarkdown")
library("tinytex")
library("stargazer")
library("sandwich")

m1 = lm(y~ lag.quarterly.revenue, data = freeny)
m2 = lm(y~ lag.quarterly.revenue + price.index, data = freeny)
m3 = lm(y~ lag.quarterly.revenue + price.index + income.level, data = freeny)
m4 = lm(y~ lag.quarterly.revenue + price.index + income.level + market.potential, data = freeny)

model.lst = list(m1, m2, m3, m4)

stargazer(m1,
          m2,
          m3,
          m4,
          title="How quarterly revenue is affected by revenue, price index, inccome and market potential?",
          type = "latex",
          float = TRUE,
          report = "vcs*",
          se=lapply(model.lst, function(x) sqrt(diag(vcovHC(x, type = "HC1")))),
          no.space = TRUE,
          header=FALSE,
          single.row = TRUE,
          font.size = "small",
          intercept.bottom = F,
          column.labels = c("Iteration-1", "Iteration-2", "Iteration-3", "Iteration-4"),
          column.separate = c(1,1, 1, 1),
          digits = 2,
          t.auto = F,
          p.auto = F,
          notes.align = "l",
          notes = c("datasets::freeny", "lm() function", "vcovHC(type = 'HC1')-Robust SE"),
          notes.append = TRUE
          )

```

### 2023-07-17 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
Update analysis_270423.Rmd

@@
       corrplot,
-      tidyverse)
+      tidyverse,
+      ggplot2)
 

### 2023-07-18 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fitbit model
upload Rmd file

@@
 # t-Tests 
-
-using heart rate means
+## using heart rate means
 
@@
 
-## Teaching vs. Interview
+## Teaching vs. Interview (mean HR)
 
@@
 
-## teaching vs. end
+## Teaching vs. End (mean HR)
 
@@
 
-## interview vs. end
+## Interview vs. End (mean HR)
 
@@
 
-# Multiple Linear Regression
+# t-Tests 
+## using mean Slope
+
+```{r}
+df_ttest_slope <- 
+  fix_models %>% 
+  group_by(id, Phase) %>% 
+  summarize(mean_slope = mean(slope)) %>% 
+  ungroup()
+```
+
+## Teaching vs. Interview
+
+```{r}
+df_ttest_slope %$% 
+  t.test(x = .$mean_slope[.$Phase == "Teaching Phase"],
+         y = .$mean_slope[.$Phase == "Interview Phase"],
+         paired = T)
+
+df_ttest_slope %$% 
+  CohenD(x = .$mean_slope[.$Phase == "Teaching Phase"],
+         y = .$mean_slope[.$Phase == "Interview Phase"],
+         pooled = T)
+```
+
+## Teaching vs. End
+
+```{r}
+df_ttest_slope %$% 
+  t.test(x = .$mean_slope[.$Phase == "Teaching Phase"],
+         y = .$mean_slope[.$Phase == "End Phase"],
+         paired = T)
+
+df_ttest_slope %$% 
+  CohenD(x = .$mean_slope[.$Phase == "Teaching Phase"],
+         y = .$mean_slope[.$Phase == "End Phase"],
+         pooled = T)
+```
+
+## Interview vs. End
+
+```{r}
+df_ttest_slope %$% 
+  t.test(x = .$mean_slope[.$Phase == "Interview Phase"],
+         y = .$mean_slope[.$Phase == "End Phase"],
+         paired = T)
+
+df_ttest_slope %$% 
+  CohenD(x = .$mean_slope[.$Phase == "Interview Phase"],
+         y = .$mean_slope[.$Phase == "End Phase"],
+         pooled = T)
+```
+
+# Multiple Linear Regression (Mean)
+
+```{r}
+main %>% 
+  group_by(ID, time_span) %>% 
+  summarize(disruption_factor = mean(disruption_factor,
+                                     na.rm = T),
+            confidence_factor = mean(confidence_factor,
+                                     na.rm = T),
+            teaching_experience = mean(teaching_experience),
+            heart_rate = mean(heart_rate_std)
+            ) %>% 
+  ungroup() -> data_regression_mean
+
+for (i in unique(data_regression_mean$time_span)) {
+
+  cache <- data_regression_mean %>% 
+    filter(time_span == i)
+
+  regr1 <-
+    lm(heart_rate ~ disruption_factor,
+    data = cache)
+
+  assign(value = regr1,
+         x = paste0("regr_", i, "1"))
+
+  regr2 <-
+    lm(heart_rate ~ confidence_factor,
+    data = cache)
+
+  assign(value = regr2,
+         x = paste0("regr_", i, "2"))
+
+  regr3 <-
+    lm(heart_rate ~ teaching_experience,
+    data = cache)
+
+  assign(value = regr3,
+         x = paste0("regr_", i, "3"))
+
+  regr4 <-
+    lm(heart_rate ~ disruption_factor + confidence_factor,
+    data = cache)
+
+  assign(value = regr4,
+         x = paste0("regr_", i, "4"))
+
+  regr5 <-
+    lm(heart_rate ~ disruption_factor + confidence_factor + teaching_experience,
+    data = cache)
+
+  assign(value = regr5,
+         x = paste0("regr_", i, "5"))
+}
+
+# Hier habe ich immer nur die Modelle getauscht. Also statt regr_end1 regr_teaching1 usw.
+
+summary(regr_end1)
+summary(regr_end2)
+summary(regr_end3)
+summary(regr_end4)
+summary(regr_end5)
+
+```
+
+# Plot
+
+```{r}
+df_heart_rate <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate") %>% 
+  distinct() %>% 
+  mutate(type = "a. Heart Rate (in Beats per Minute)")
+
+df_heart_rate_std <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate_std") %>% 
+  distinct() %>% 
+  transmute(ID,
+            time,
+            type = "b. Heart Rate (Standardized)",
+            heart_rate = heart_rate_std)
+
+# left_join(x = df_heart_rate,
+#           y = df_heart_rate_std,
+#           by = c("ID","time")) %>% 
+bind_rows(df_heart_rate,
+          df_heart_rate_std
+          ) %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.99) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  # scale_x_continuous(expand = c(0, NA),
+  #                    breaks = seq(0, 120, 10)) +
+  scale_x_continuous(expand = c(0.01,0)) + 
+  labs(x = "Time (in Minutes)",
+       #y = "Heart Rate (in Beats per Minute)",
+       y = "",
+       # title = "Figure #",
+       # subtitle = "Overall Course of Average Heartrate",
+       caption = expression(paste(italic("Note: "), 
+                                  "The shadow around the line represents the 99% confidence interval."))
+       ) +
+  #ggtitle("Overall Course of Average Heartrate") +
+  theme_apa() + 
+  # theme(plot.subtitle = element_text(face = "italic"),
+  #       plot.caption = element_text(hjust = 0),
+  #       axis.line = element_line(colour = "black"),
+  #       panel.grid.major = element_blank(),
+  #       panel.grid.minor = element_blank(),
+  #       panel.border = element_blank(),
+  #       panel.background = element_blank()) +
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y")
+
+ggsave(filename = "plots_publication/loess_plot_std_unstd.png",
+       width = 16,
+       height = 12,
+       units = "cm")
+```
+
+```{r}
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("preparation","teaching","post","interview","end"),
+                            labels = c("Pre Teaching\nPhase","Teaching\nPhase","Post Teaching\nPhase","Interview\nPhase","End\nPhase"))) %>% 
+  distinct() %>%
+  group_by(time_span) %>% 
+  summarise(z_mean = mean(heart_rate_std),
+            z_sd = sd(heart_rate_std),
+            z_t = qt(p = 0.01 / 2,      # 0.01 KI
+               df = n() - 1,
+               lower.tail = F
+               ),
+            z_error = z_sd / sqrt(n()),
+            lower = z_mean - z_t * z_error,
+            upper = z_mean + z_t * z_error,
+            ) %>% 
+  ungroup() %>% 
+  ggplot(mapping = aes(x = factor(0),
+                       y = z_mean)) + 
+  geom_point() +
+  geom_errorbar(mapping = aes(ymin = lower,
+                              ymax = upper),
+                width = 0.2) +
+  geom_hline(yintercept = 0,
+             linetype = "dashed") +
+  labs(x = "",
+       y = "Average Standardized Heart Rate",
+       caption = expression(paste(italic("Note: "), 
+                                  "The dotted line represents the null effect; bars represent the 1% confidence interval."
+                                  )
+                            )
+       ) +
+  facet_grid(cols = vars(time_span)) +
+  theme_apa() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        plot.caption = element_text(hjust = 0))
+
+ggsave(filename = "plots_publication/ki_plot.png",
+       width = 16,
+       height = 12,
+       units = "cm")
+```
+
+# Multiple Linear Regression (Slope)
 
@@
 
+summary(fit_pre_1)
+
 fit_pre_2 <-
@@
   lm(slope ~ confidence:posneg)
+
+summary(fit_pre_2)
 
@@
 
+summary(fit_pre_3)
+
 fit_pre_4 <-
@@
 
+summary(fit_pre_4)
+
 fit_pre_5 <-
@@
   lm(slope ~ posneg:confidence + posneg:disruption + posneg:teaching_experience)
+
+summary(fit_pre_5)
 

### 2023-07-19 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
bla

--- 2023-07-17 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("(1) Pre-teaching phase","(2) Teaching phase","(3) Post-teaching phase","(4) Interview phase","(5) End phase"))) %>% 
+                            labels = c("(1) Pre-teaching\nphase","(2) Teaching\nphase","(3) Post-teaching\nphase","(4) Interview\nphase","(5) End\nphase"))) %>% 
   distinct() %>% 
@@
   geom_smooth(method = "lm",
-              se = FALSE,
+              se = TRUE,
               size = 0.5,
@@
        y = "",
-       subtitle = "Linear Estimation") +
+       subtitle = "") +
   theme_apa() +
@@
              scales = "free_x")
+
+ggsave(filename = "plots_publication/lm_plot.png",
+       width = 22,
+       height = 12,
+       units = "cm")
 
@@
 
-# Multiple Linear Regression
+# t-Tests 
+## using mean Slope
+
+```{r}
+df_ttest_slope <- 
+  fix_models %>% 
+  group_by(id, Phase) %>% 
+  summarize(mean_slope = mean(slope)) %>% 
+  ungroup()
+```
+
+## Teaching vs. Interview
+
+```{r}
+df_ttest_slope %$% 
+  t.test(x = .$mean_slope[.$Phase == "Teaching Phase"],
+         y = .$mean_slope[.$Phase == "Interview Phase"],
+         paired = T)
+
+df_ttest_slope %$% 
+  CohenD(x = .$mean_slope[.$Phase == "Teaching Phase"],
+         y = .$mean_slope[.$Phase == "Interview Phase"],
+         pooled = T)
+```
+
+## Teaching vs. End
+
+```{r}
+df_ttest_slope %$% 
+  t.test(x = .$mean_slope[.$Phase == "Teaching Phase"],
+         y = .$mean_slope[.$Phase == "End Phase"],
+         paired = T)
+
+df_ttest_slope %$% 
+  CohenD(x = .$mean_slope[.$Phase == "Teaching Phase"],
+         y = .$mean_slope[.$Phase == "End Phase"],
+         pooled = T)
+```
+
+## Interview vs. End
+
+```{r}
+df_ttest_slope %$% 
+  t.test(x = .$mean_slope[.$Phase == "Interview Phase"],
+         y = .$mean_slope[.$Phase == "End Phase"],
+         paired = T)
+
+df_ttest_slope %$% 
+  CohenD(x = .$mean_slope[.$Phase == "Interview Phase"],
+         y = .$mean_slope[.$Phase == "End Phase"],
+         pooled = T)
+```
+
+# Multiple Linear Regression (Mean)
+
+```{r}
+main %>% 
+  group_by(ID, time_span) %>% 
+  summarize(disruption_factor = mean(disruption_factor,
+                                     na.rm = T),
+            confidence_factor = mean(confidence_factor,
+                                     na.rm = T),
+            teaching_experience = mean(teaching_experience),
+            heart_rate = mean(heart_rate_std)
+            ) %>% 
+  ungroup() -> data_regression_mean
+
+for (i in unique(data_regression_mean$time_span)) {
+
+  cache <- data_regression_mean %>% 
+    filter(time_span == i)
+
+  regr1 <-
+    lm(heart_rate ~ teaching_experience,
+    data = cache)
+
+  assign(value = regr1,
+         x = paste0("regr_", i, "1"))
+
+  regr2 <-
+    lm(heart_rate ~ teaching_experience + disruption_factor,
+    data = cache)
+
+  assign(value = regr2,
+         x = paste0("regr_", i, "2"))
+
+  regr3 <-
+    lm(heart_rate ~ teaching_experience + confidence_factor,
+    data = cache)
+
+  assign(value = regr3,
+         x = paste0("regr_", i, "3"))
+
+  regr4 <-
+    lm(heart_rate ~ teaching_experience + disruption_factor + confidence_factor,
+    data = cache)
+
+  assign(value = regr4,
+         x = paste0("regr_", i, "4"))
+
+}
+
+# Hier habe ich immer nur die Modelle getauscht. Also statt regr_end1 regr_teaching1 usw.
+
+summary(regr_end1)
+summary(regr_end2)
+summary(regr_end3)
+summary(regr_end4)
+
+```
+
+# Plot
+
+```{r}
+df_heart_rate <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate") %>% 
+  distinct() %>% 
+  mutate(type = "a. Heart Rate (in beats per minute)")
+
+df_heart_rate_std <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate_std") %>% 
+  distinct() %>% 
+  transmute(ID,
+            time,
+            type = "b. Heart Rate (standardized)",
+            heart_rate = heart_rate_std)
+
+# left_join(x = df_heart_rate,
+#           y = df_heart_rate_std,
+#           by = c("ID","time")) %>% 
+bind_rows(df_heart_rate,
+          df_heart_rate_std
+          ) %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.99) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  # scale_x_continuous(expand = c(0, NA),
+  #                    breaks = seq(0, 120, 10)) +
+  scale_x_continuous(expand = c(0.01,0)) + 
+  labs(x = "Time (in minutes)",
+       #y = "Heart Rate (in Beats per Minute)",
+       y = "",
+       # title = "Figure #",
+       # subtitle = "Overall Course of Average Heartrate",
+       # caption = expression(paste(italic("Note: "),
+       #                            "The shadow around the line represents the 99% confidence interval. 
+       #                            We used the ggplot2 package (v3.3.3; Wickham, 2016) to calculate the moving average of the course."))
+       ) +
+  #ggtitle("Overall Course of Average Heartrate") +
+  theme_apa() + 
+  # theme(plot.subtitle = element_text(face = "italic"),
+  #       plot.caption = element_text(hjust = 0),
+  #       axis.line = element_line(colour = "black"),
+  #       panel.grid.major = element_blank(),
+  #       panel.grid.minor = element_blank(),
+  #       panel.border = element_blank(),
+  #       panel.background = element_blank()) +
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y")
+
+ggsave(filename = "plots_publication/loess_plot_std_unstd.png",
+       width = 16,
+       height = 12,
+       units = "cm")
+```
+
+```{r}
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("preparation","teaching","post","interview","end"),
+                            labels = c("(1) Pre-teaching\nphase","(2) Teaching\nphase","(3) Post-teaching\nphase","(4) Interview\nphase","(5) End\nphase"))) %>% 
+  distinct() %>%
+  group_by(time_span) %>% 
+  summarise(z_mean = mean(heart_rate_std),
+            z_sd = sd(heart_rate_std),
+            z_t = qt(p = 0.01 / 2,      # 0.01 KI
+               df = n() - 1,
+               lower.tail = F
+               ),
+            z_error = z_sd / sqrt(n()),
+            lower = z_mean - z_t * z_error,
+            upper = z_mean + z_t * z_error,
+            ) %>% 
+  ungroup() %>% 
+  ggplot(mapping = aes(x = factor(0),
+                       y = z_mean)) + 
+  geom_point() +
+  geom_errorbar(mapping = aes(ymin = lower,
+                              ymax = upper),
+                width = 0.2) +
+  geom_hline(yintercept = 0,
+             linetype = "dashed") +
+  labs(x = "",
+       y = "Standardized mean HR",
+       caption = expression(paste(italic("Note: "), 
+                                  "The dotted line represents the null effect; bars represent the 1% confidence interval. "
+                                  )
+                            )
+       ) +
+  facet_grid(cols = vars(time_span)) +
+  theme_apa() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        plot.caption = element_text(hjust = 0))
+
+ggsave(filename = "plots_publication/mean_plot.png",
+       width = 20,
+       height = 12,
+       units = "cm")
+```
+
+# Multiple Linear Regression (Slope)
 

### 2023-07-26 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
blabla
upload plot

@@
 plot_overall
+
+lm_plot <-
+  main %>%
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>%
+  mutate(time_span = factor(time_span,
+                            levels = c("preparation","teaching","post","interview","end"),
+                            labels = c("(1) Pre Teaching\nPhase","(2) Teaching\nPhase","(3) Post Teaching\nPhase","(4) Interview\nPhase","(5) End\nPhase")
+                            ),
+         time = time / 60
+         ) %>%
+  distinct() %>%
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std
+                       )
+         ) +
+  # geom_point(alpha = 0.05) +
+  geom_smooth(method = "lm",
+              se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.99) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  #scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(breaks = seq(0, 10, 2)) +
+  #scale_y_continuous(breaks = seq(0, 160, 5)) +
+  labs(x = "Time (in Minutes)",
+       y = "Average Standardized Heart Rate",
+       caption = expression(paste(italic("Note: "),
+                                  "The shadow around the line represents the 99% confidence interval."
+                                  )
+                            )
+       ) +
+  theme_apa() +
+  theme(plot.subtitle = element_text(face = "italic"),
+        plot.caption = element_text(hjust = 0)) +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x")
+ggsave(filename = "plots_publication/lm_plot.png",
+       plot = lm_plot,
+       width = 20,
+       height = 12,
+       units = "cm")
+
+```
 ```
@@
 
+## Teaching vs. Pre-Teaching (mean HR)
+
+```{r}
+df_ttest %$% 
+  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
+         y = .$mean_heart_rate[.$time_span == "preparation"],
+         paired = T)
+
+df_ttest %$% 
+  CohenD(x = .$mean_heart_rate[.$time_span == "teaching"],
+         y = .$mean_heart_rate[.$time_span == "preparation"],
+         pooled = T)
+```
+
+## Teaching vs. Post-Teaching (mean HR)
+
+```{r}
+df_ttest %$% 
+  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
+         y = .$mean_heart_rate[.$time_span == "post"],
+         paired = T)
+
+df_ttest %$% 
+  CohenD(x = .$mean_heart_rate[.$time_span == "teaching"],
+         y = .$mean_heart_rate[.$time_span == "post"],
+         pooled = T)
+```
+
 ## Teaching vs. Interview (mean HR)
@@
   CohenD(x = .$mean_heart_rate[.$time_span == "teaching"],
-         y = .$mean_heart_rate[.$time_span == "end"],
-         pooled = T)
-```
-
-## Interview vs. End (mean HR)
-
-```{r}
-df_ttest %$% 
-  t.test(x = .$mean_heart_rate[.$time_span == "interview"],
-         y = .$mean_heart_rate[.$time_span == "end"],
-         paired = T)
-
-df_ttest %$% 
-  CohenD(x = .$mean_heart_rate[.$time_span == "interview"],
          y = .$mean_heart_rate[.$time_span == "end"],
@@
 
-summary(regr_end1)
-summary(regr_end2)
-summary(regr_end3)
-summary(regr_end4)
+summary(regr_teaching1)
+summary(regr_teaching2)
+summary(regr_teaching3)
+summary(regr_teaching4)
 

### 2023-07-29 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
upload method section

@@
       tidyverse,
-      ggplot2)
+      ggplot2,
+      apaTables)
 
@@
       # filter(time <= 600) %>% # filter for 10min intervals
-    filter(time <= 7200) %>% # filter for 2 hours 30min (maximal duration of study)
+    filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
     dplyr::select(!c("Time","Heart Rate","id"))
@@
 ```
-```
 
@@
          pooled = T)
+```
+
+### Correlation
+
+## Pr-teaching phase
+
+```{r}
+main %>% 
+  filter(time_span == "preparation") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) %>%
+  pcor()  -> pcor_pre
+
+# knitr::kable(x = list(pcor_main$estimate, pcor_main$p.value), format = "simple")
+
+```
+
+## Teaching phase
+
+```{r}
+main %>% 
+  filter(time_span == "teaching") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) %>%
+  pcor()  -> pcor_teaching
+
+# knitr::kable(x = list(pcor_main$estimate, pcor_main$p.value), format = "simple")
+
+```
+
+## Post-teaching phase
+
+```{r}
+main %>% 
+  filter(time_span == "post") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) %>%
+  pcor()  -> pcor_post
+
+# knitr::kable(x = list(pcor_main$estimate, pcor_main$p.value), format = "simple")
+
+```
+
+## Interview phase
+
+```{r}
+main %>% 
+  filter(time_span == "interview") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) %>%
+  pcor()  -> pcor_interview
+
+# knitr::kable(x = list(pcor_main$estimate, pcor_main$p.value), format = "simple")
+
+```
+
+## End phase
+
+```{r}
+main %>% 
+  filter(time_span == "end") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) %>%
+  pcor()  -> pcor_end
+
+# knitr::kable(x = list(pcor_main$estimate, pcor_main$p.value), format = "simple")
+
 ```

### 2023-08-03 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
bla

@@
 
-# REACTION 
+# REACTION ALTERNATIVE
 df_reaction <- read_excel("data/coding_reactions_MK.xlsx") %>% 

### 2023-08-03 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
update action alternatives

--- 2023-05-05 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/action_alternatives_confidence_factor.Rmd
@@
   map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
-  dplyr::select(ID, Event, `Confidence Factor`) %>% 
-  filter(
-    ID %in% c(101:126, 201:228),
-    !ID %in% c(204, 226),
-    Event %in% c("chatting")) %>%
+  dplyr::select(ID, event, confidence_factor) %>% 
+  filter(!ID %in% c(141,
+                    142,
+                    204,
+                    226), # filter relevant rows
+         event %in% c("chatting")) %>%
   janitor::clean_names()
@@
 
+# creating new column with total reactions
+main_novice <- main %>%
+  filter(id %in% c("Novice")) %>% 
+  mutate(
+    # reaction_sum = sum(reaction),
+         nd_sum = sum(nd),
+         sum_participants = sum(n()),
+    # percent_reaction = round((reaction_sum/sum_participants),digits = 2),
+         percent_nd = round((nd/count),
+                            digits = 2)
+         )
+
+# creating new column with total reactions
+main_expert <- main %>%
+  filter(id %in% c("Expert")) %>% 
+  mutate(
+    # reaction_sum = sum(reaction),
+         nd_sum = sum(nd),
+         sum_participants = sum(n()),
+    # percent_reaction = round((reaction_sum/sum_participants), digits = 2),
+         percent_nd = round((nd/count),
+                            digits = 2)
+         )
+
+# merge novice & expert data frame
+main <- rbind(main_expert, main_novice)
+
 ```
@@
 
-# sjt cm
-describeBy(main$sjt, main$id)
-plot_confi <- boxplot(sjt ~ id, data = main)
+# # sjt cm
+# describeBy(main$sjt, main$id)
+# plot_confi <- boxplot(sjt ~ id, data = main)
 
@@
 # action alternatives - non disruptive alternatives  
-describeBy(main$nd, main$id)
-plot_action_quality <- boxplot(nd ~ id, data = main)
+describeBy(main$percent_nd, main$id)
+plot_action_quality <- boxplot(percent_nd ~ id, data = main)
 
@@
 main %>% 
-  filter(!is.na(confidence_factor) | !is.na(nd)) %>% 
+  filter(!is.na(confidence_factor) | !is.na(percent_nd)) %>% 
   # filter(id %in% c("Novice")) %>% 
   ggplot(mapping = aes(x = confidence_factor,
-                       y = nd,
+                       y = percent_nd,
                        colour = id
@@
 # t-test for expertise differences
-t.test(x = main$nd[main$id == "Expert"],
-       y = main$nd[main$id == "Novice"])
+t.test(x = main$percent_nd[main$id == "Expert"],
+       y = main$percent_nd[main$id == "Novice"])
 
 # effect size for expertise differences
-CohenD(x = main$nd[main$id == "Expert"],
-       y = main$nd[main$id == "Novice"],
+CohenD(x = main$percent_nd[main$id == "Expert"],
+       y = main$percent_nd[main$id == "Novice"],
        na.rm = TRUE)
+
 ```
@@
 nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
-                              corr.nov$nd, 
+                              corr.nov$percent_nd, 
                               method=c("pearson"),
@@
 exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
-                              corr.exp$nd, 
+                              corr.exp$percent_nd, 
                               method=c("pearson"),
@@
 full_confi_nd_corr <- corr.test(main$confidence_factor, 
-                                main$nd, method=c("pearson"),
+                                main$percent_nd, method=c("pearson"),
                                 adjust="holm")
@@
 nov_count_nd_corr <- cor.test(corr.nov$count,
-                              corr.nov$nd, 
+                              corr.nov$percent_nd, 
                               method=c("pearson"),
@@
 exp_count_nd_corr <- cor.test(corr.exp$count,
-                              corr.exp$nd, 
+                              corr.exp$percent_nd, 
                               method=c("pearson"),
@@
 full_count_nd_corr <- corr.test(main$count, 
-                                main$nd, 
+                                main$percent_nd, 
                                 method=c("pearson"),
@@
 
-# novices: correlation between sjt and count
-nov_sjt_count_corr <- cor.test(corr.nov$sjt,
-                              corr.nov$count, 
-                              method=c("pearson"),
-                              adjust="holm")
-print(nov_sjt_count_corr, 
-      short = F)
-
-# experts: correlation between sjt and count
-exp_sjt_count_corr <- cor.test(corr.exp$sjt,
-                              corr.exp$count, 
-                              method=c("pearson"),
-                              adjust="holm")
-print(exp_sjt_count_corr,
-      short = F)
-
-# full sample: correlation between sjt and count
-full_sjt_count_corr <- corr.test(main$sjt, 
-                                 main$count, 
-                                 method=c("pearson"), 
-                                 adjust="holm")
-print(full_sjt_count_corr, 
-      short = F)
-
-###################################################
-
-# novices: correlation between sjt and non-disruptive alternatives
-nov_sjt_nd_corr <- cor.test(corr.nov$sjt,
-                              corr.nov$nd, 
-                              method=c("pearson"),
-                              adjust="holm")
-print(nov_sjt_nd_corr, 
-      short = F)
-
-# experts: correlation between sjt and non-disruptive alternatives
-exp_sjt_nd_corr <- cor.test(corr.exp$sjt,
-                              corr.exp$nd, 
-                              method=c("pearson"),
-                              adjust="holm")
-print(exp_sjt_nd_corr,
-      short = F)
-
-# full sample: correlation between sjt and non-disruptive alternatives
-full_sjt_nd_corr <- corr.test(main$sjt,
-                              main$nd,
-                              method=c("pearson"),
-                              adjust="holm")
-print(full_sjt_nd_corr,
-      short = F)
+# # novices: correlation between sjt and count
+# nov_sjt_count_corr <- cor.test(corr.nov$sjt,
+#                               corr.nov$count, 
+#                               method=c("pearson"),
+#                               adjust="holm")
+# print(nov_sjt_count_corr, 
+#       short = F)
+# 
+# # experts: correlation between sjt and count
+# exp_sjt_count_corr <- cor.test(corr.exp$sjt,
+#                               corr.exp$count, 
+#                               method=c("pearson"),
+#                               adjust="holm")
+# print(exp_sjt_count_corr,
+#       short = F)
+# 
+# # full sample: correlation between sjt and count
+# full_sjt_count_corr <- corr.test(main$sjt, 
+#                                  main$count, 
+#                                  method=c("pearson"), 
+#                                  adjust="holm")
+# print(full_sjt_count_corr, 
+#       short = F)
+# 
+# 
+# ###################################################
+# 
+# # novices: correlation between sjt and non-disruptive alternatives
+# nov_sjt_nd_corr <- cor.test(corr.nov$sjt,
+#                               corr.nov$nd, 
+#                               method=c("pearson"),
+#                               adjust="holm")
+# print(nov_sjt_nd_corr, 
+#       short = F)
+# 
+# # experts: correlation between sjt and non-disruptive alternatives
+# exp_sjt_nd_corr <- cor.test(corr.exp$sjt,
+#                               corr.exp$nd, 
+#                               method=c("pearson"),
+#                               adjust="holm")
+# print(exp_sjt_nd_corr,
+#       short = F)
+# 
+# 
+# # full sample: correlation between sjt and non-disruptive alternatives
+# full_sjt_nd_corr <- corr.test(main$sjt,
+#                               main$nd,
+#                               method=c("pearson"),
+#                               adjust="holm")
+# print(full_sjt_nd_corr,
+#       short = F)
 

### 2023-08-07 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R
update SRI

@@ -19,8 +19,11 @@ needs(tidyverse,
 sri <- 
   excel_sheets("data/Coding_SRI.xlsx") %>% 
   map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% 
-  select(Group, Event, `Disruption Factor`, `Confident Factor`) %>% # select relevant columns 
-  filter(Group %in% c(101:125, 202:217))# filter relevant rows
+  select(ID, event, disruption_factor, confidence_factor) %>% # select relevant columns 
+  filter(!ID %in% c(141,
+                       142,
+                       204, 
+                       226)) # filter relevant rows
 
  
 # # counting drop outs (-99 not perceived, -100 not answered)

### 2023-08-09 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
Update action_alternatives_confidence_factor.Rmd

@@
 describeBy(main$count, main$id)
-plot_action_count <- boxplot(count ~ id, data = main)
+plot_action_count <- boxplot(count ~ id, data = main)^
 
-# action alternatives - non disruptive alternatives  
+# action alternatives - non disruptive alternatives (sum score)
+describeBy(main$nd, main$id)
+plot_action_quality <- boxplot(nd ~ id, data = main)
+
+# action alternatives - non disruptive alternatives (relative score)
 describeBy(main$percent_nd, main$id)
@@
 
-### action alternatives non-disruptive
+### action alternatives non-disruptive absolute score
+# t-test for expertise differences
+t.test(x = main$nd[main$id == "Expert"],
+       y = main$nd[main$id == "Novice"])
+
+# effect size for expertise differences
+CohenD(x = main$nd[main$id == "Expert"],
+       y = main$nd[main$id == "Novice"],
+       na.rm = TRUE)
+
+### action alternatives non-disruptive relative score
 # t-test for expertise differences
@@
 
-# novices: correlation between confidence factor and non-disruptive alternatives
+# novices: correlation between confidence factor and non-disruptive alternatives (absolute score)
+nov_confi_abs.nd_corr <- cor.test(corr.nov$confidence_factor,
+                              corr.nov$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(nov_confi_abs.nd_corr, 
+      short = F)
+
+# experts: correlation between confidence factor and non-disruptive alternatives (absolute score)
+exp_confi_abs.nd_corr <- cor.test(corr.exp$confidence_factor,
+                              corr.exp$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(exp_confi_abs.nd_corr,
+      short = F)
+
+# full sample: correlation between confidence factor and non-disruptive alternatives (absolute score)
+full_confi_abs.nd_corr <- corr.test(main$confidence_factor, 
+                                main$nd, method=c("pearson"),
+                                adjust="holm")
+print(full_confi_abs.nd_corr,
+      short = F)
+
+###################################################
+
+# novices: correlation between confidence factor and non-disruptive alternatives (relative score)
 nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
@@
 
-# experts: correlation between confidence factor and non-disruptive alternatives
+# experts: correlation between confidence factor and non-disruptive alternatives (relative score)
 exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
@@
 
-# full sample: correlation between confidence factor and non-disruptive alternatives
+# full sample: correlation between confidence factor and non-disruptive alternatives (relative score)
 full_confi_nd_corr <- corr.test(main$confidence_factor, 
@@
 
-# novices: correlation between count and non-disruptive alternatives
+# novices: correlation between count and non-disruptive alternatives (absolute score)
+nov_count_abs.nd_corr <- cor.test(corr.nov$count,
+                              corr.nov$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(nov_count_abs.nd_corr, 
+      short = F)
+
+# experts: correlation between count and non-disruptive alternatives (absolute score)
+exp_count_abs.nd_corr <- cor.test(corr.exp$count,
+                              corr.exp$nd, 
+                              method=c("pearson"),
+                              adjust="holm")
+print(exp_count_abs.nd_corr,
+      short = F)
+
+# full sample: correlation between confidence factor and non-disruptive alternatives (absolute score)
+full_count_abs.nd_corr <- corr.test(main$count, 
+                                main$nd, 
+                                method=c("pearson"),
+                                adjust="holm")
+print(full_count_abs.nd_corr,
+      short = F)
+
+###################################################
+
+# novices: correlation between count and non-disruptive alternatives (relative score)
 nov_count_nd_corr <- cor.test(corr.nov$count,
@@
 
-# experts: correlation between count and non-disruptive alternatives
+# experts: correlation between count and non-disruptive alternatives (relative score)
 exp_count_nd_corr <- cor.test(corr.exp$count,
@@
 
-# full sample: correlation between confidence factor and non-disruptive alternatives
+# full sample: correlation between confidence factor and non-disruptive alternatives (relative score)
 full_count_nd_corr <- corr.test(main$count, 

### 2023-08-10 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
Update action_alternatives_confidence_factor.Rmd

@@
       cowplot,
-      zoo)
+      zoo,
+      apaTables)
 
@@
 ```{r}
+
+# Korrelationstabelle nach APA-Standards
+
+head(main)
+
+# Subset anlegen nur mit Variablen
+main %>% 
+  select(confidence_factor, 
+         count, 
+         nd,
+         percent_nd) -> corr_subset
+
+apa.cor.table(corr_subset, filename = "Korrelationen.doc")
+
+###################################################
+
 # novices: correlation between confidence factor and count

### 2023-08-11 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
update disruption

@@
 ---
-title: "Action alternatives & confidence factor"
+title: "Action alternatives & disruption factor"
 output: html_document
@@
   map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
-  dplyr::select(ID, event, confidence_factor) %>% 
+  dplyr::select(ID, event, disruption_factor) %>% 
   filter(!ID %in% c(141,
@@
 ```{r}
-# confidence factor
-describeBy(main$confidence_factor, main$id)
-plot_confi <- boxplot(confidence_factor ~ id, data = main)
+# disruption factor
+describeBy(main$disruption_factor, main$id)
+plot_disrup <- boxplot(disruption_factor ~ id, data = main)
 
@@
 # describeBy(main$sjt, main$id)
-# plot_confi <- boxplot(sjt ~ id, data = main)
+# plot_disrup <- boxplot(sjt ~ id, data = main)
 
@@
 
-# confidence factor x count of action alternatives
+# disruption factor x count of action alternatives
 ```{r}
 main %>% 
-  filter(!is.na(confidence_factor) | !is.na(count)) %>% 
+  filter(!is.na(disruption_factor) | !is.na(count)) %>% 
   # filter(id %in% c("Novice")) %>% 
-  ggplot(mapping = aes(x = confidence_factor,
+  ggplot(mapping = aes(x = disruption_factor,
                        y = count,
@@
   scale_color_viridis_d() +
-  labs(x = "Confidence Factor",
+  labs(x = "disruption Factor",
        y = "Count of action alternatives") +
@@
 
-# confidence factor x non-disruptive action alternatives
+# disruption factor x non-disruptive action alternatives
 ```{r}
 main %>% 
-  filter(!is.na(confidence_factor) | !is.na(percent_nd)) %>% 
+  filter(!is.na(disruption_factor) | !is.na(percent_nd)) %>% 
   # filter(id %in% c("Novice")) %>% 
-  ggplot(mapping = aes(x = confidence_factor,
+  ggplot(mapping = aes(x = disruption_factor,
                        y = percent_nd,
@@
   scale_color_viridis_d() +
-  labs(x = "Confidence Factor",
+  labs(x = "disruption Factor",
        y = "Non-disruptive action alternatives") + 
@@
 
-#### confidence factor
+#### disruption factor
 # t-test for expertise differences
-t.test(x = main$confidence_factor[main$id == "Expert"],
-       y = main$confidence_factor[main$id == "Novice"])
+t.test(x = main$disruption_factor[main$id == "Expert"],
+       y = main$disruption_factor[main$id == "Novice"])
 
 # effect size for expertise differences
-CohenD(x = main$confidence_factor[main$id == "Expert"],
-       y = main$confidence_factor[main$id == "Novice"],
+CohenD(x = main$disruption_factor[main$id == "Expert"],
+       y = main$disruption_factor[main$id == "Novice"],
        na.rm = TRUE)
@@
 main %>% 
-  select(confidence_factor, 
+  select(disruption_factor, 
          count, 
@@
 
-# novices: correlation between confidence factor and count
+# novices: correlation between disruption factor and count
 main %>% 
@@
 
-nov_confi_count_corr <- cor.test(corr.nov$confidence_factor, 
+nov_disrup_count_corr <- cor.test(corr.nov$disruption_factor, 
                                  corr.nov$count, 
@@
                                  adjust="holm")
-print(nov_confi_count_corr, 
+print(nov_disrup_count_corr, 
       short = F)
 
-# experts: correlation between confidence factor and count
+# experts: correlation between disruption factor and count
 main %>% 
@@
 
-exp_confi_count_corr <- cor.test(corr.exp$confidence_factor, 
+exp_disrup_count_corr <- cor.test(corr.exp$disruption_factor, 
                                  corr.exp$count, 
@@
                                  adjust="holm")
-print(exp_confi_count_corr, 
+print(exp_disrup_count_corr, 
       short = F)
 
-# full sample: correlation between confidence factor and count
-full_confi_count_corr <- corr.test(main$confidence_factor, 
+# full sample: correlation between disruption factor and count
+full_disrup_count_corr <- corr.test(main$disruption_factor, 
                                    main$count, 
@@
                                    adjust="holm")
-print(full_confi_count_corr,
+print(full_disrup_count_corr,
       short = F)
@@
 
-# novices: correlation between confidence factor and non-disruptive alternatives (absolute score)
-nov_confi_abs.nd_corr <- cor.test(corr.nov$confidence_factor,
+# novices: correlation between disruption factor and non-disruptive alternatives (absolute score)
+nov_disrup_abs.nd_corr <- cor.test(corr.nov$disruption_factor,
                               corr.nov$nd, 
@@
                               adjust="holm")
-print(nov_confi_abs.nd_corr, 
+print(nov_disrup_abs.nd_corr, 
       short = F)
 
-# experts: correlation between confidence factor and non-disruptive alternatives (absolute score)
-exp_confi_abs.nd_corr <- cor.test(corr.exp$confidence_factor,
+# experts: correlation between disruption factor and non-disruptive alternatives (absolute score)
+exp_disrup_abs.nd_corr <- cor.test(corr.exp$disruption_factor,
                               corr.exp$nd, 
@@
                               adjust="holm")
-print(exp_confi_abs.nd_corr,
+print(exp_disrup_abs.nd_corr,
       short = F)
 
-# full sample: correlation between confidence factor and non-disruptive alternatives (absolute score)
-full_confi_abs.nd_corr <- corr.test(main$confidence_factor, 
+# full sample: correlation between disruption factor and non-disruptive alternatives (absolute score)
+full_disrup_abs.nd_corr <- corr.test(main$disruption_factor, 
                                 main$nd, method=c("pearson"),
                                 adjust="holm")
-print(full_confi_abs.nd_corr,
+print(full_disrup_abs.nd_corr,
       short = F)
@@
 
-# novices: correlation between confidence factor and non-disruptive alternatives (relative score)
-nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
+# novices: correlation between disruption factor and non-disruptive alternatives (relative score)
+nov_disrup_nd_corr <- cor.test(corr.nov$disruption_factor,
                               corr.nov$percent_nd, 
@@
                               adjust="holm")
-print(nov_confi_nd_corr, 
+print(nov_disrup_nd_corr, 
       short = F)
 
-# experts: correlation between confidence factor and non-disruptive alternatives (relative score)
-exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
+# experts: correlation between disruption factor and non-disruptive alternatives (relative score)
+exp_disrup_nd_corr <- cor.test(corr.exp$disruption_factor,
                               corr.exp$percent_nd, 
@@
                               adjust="holm")
-print(exp_confi_nd_corr,
+print(exp_disrup_nd_corr,
       short = F)
 
-# full sample: correlation between confidence factor and non-disruptive alternatives (relative score)
-full_confi_nd_corr <- corr.test(main$confidence_factor, 
+# full sample: correlation between disruption factor and non-disruptive alternatives (relative score)
+full_disrup_nd_corr <- corr.test(main$disruption_factor, 
                                 main$percent_nd, method=c("pearson"),
                                 adjust="holm")
-print(full_confi_nd_corr,
+print(full_disrup_nd_corr,
       short = F)
@@
 
-# full sample: correlation between confidence factor and non-disruptive alternatives (absolute score)
+# full sample: correlation between disruption factor and non-disruptive alternatives (absolute score)
 full_count_abs.nd_corr <- corr.test(main$count, 
@@
 
-# full sample: correlation between confidence factor and non-disruptive alternatives (relative score)
+# full sample: correlation between disruption factor and non-disruptive alternatives (relative score)
 full_count_nd_corr <- corr.test(main$count, 

### 2023-08-22 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier/FitBit_elsevier/FitBit_elsevier.tex
neues Elsevier-Markdown file erstellt

\documentclass[preprint, 3p,
authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

  \journal{Computers \& Education} % Sets Journal name

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

\begin{frontmatter}

  \title{New approaches to teachers' experience of stress: Do heart rate
measurements with fitness trackers provide an efficient, inexpensive,
and robust measurement method?}
    \author[Leipzig University]{Mandy Klatt%
  \corref{cor1}%
  \fnref{1}}
   \ead{mandy.klatt@uni-leipzig.de} 
    \author[Leipzig University]{Peer Keßler%
  %
  \fnref{2}}
   \ead{Peer@example.com} 
    \author[Leipzig University, Max Planck Institute for Evolutionary
Anthropology]{Gregor Kachel%
  %
  \fnref{1}}
   \ead{gregor@example.com} 
    \author[Leipzig University]{Christin Lotz%
  %
  \fnref{1}}
   \ead{christin@example.com} 
    \author[Leipzig University]{Anne Deiglmayr%
  %
  \fnref{3}}
   \ead{anne@example.com} 
      \affiliation[Leipzig University]{
    organization={Empirische Schul- und
Unterrichtsforschung},addressline={Marschnerstr.
29},city={Leipzig},postcode={4109},state={Sachsen},country={Germany},}
    \affiliation[Max Planck Institute for Evolutionary Anthropology]{
    organization={Department},addressline={Deutscher Pl.
6},city={Leipzig},postcode={4103},state={Sachsen},country={Germany},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{ConceptualizationWriting - Original Draft
PreparationWriting - Review \& Editing}
    \fntext[2]{Writing - Original Draft PreparationWriting - Review \&
Editing}
    \fntext[3]{Supervision}

  \begin{abstract}
  One or two sentences providing a \textbf{basic introduction} to the
  field, comprehensible to a scientist in any discipline.

  Two to three sentences of \textbf{more detailed background},
  comprehensible to scientists in related disciplines.

  One sentence clearly stating the \textbf{general problem} being
  addressed by this particular study.

  One sentence summarizing the main result (with the words
  ``\textbf{here we show}'' or their equivalent).

  Two or three sentences explaining what the \textbf{main result}
  reveals in direct comparison to what was thought to be the case
  previously, or how the main result adds to previous knowledge.

  One or two sentences to put the results into a more \textbf{general
  context}.

  Two or three sentences to provide a \textbf{broader perspective},
  readily comprehensible to a scientist in any discipline.

  XXX In this proof-of-concept study, we aimed to advance the field of
  teacher stress by collecting heart rate data with wrist-worn devices
  and testing a methodology that has the potential to provide more
  insights on the non-invasive assessment of teacher stress. XXX
  \end{abstract}
    \begin{keyword}
    heart rate \sep photoplethysmography \sep wearable electronic
device \sep 
    teaching
  \end{keyword}

 \end{frontmatter}

\hypertarget{present-investigation}{%
\section{Present investigation}\label{present-investigation}}

The aim was to investigate whether HR measures assessed by a Fitbit
Charge 4 are a suitable and effective method to \textbf{(1)} map
teachers course of arousal over the course of a five phase lab study,
including a micro teaching unit, and \textbf{(2)} examine whether HR
measures can be predicted by self-reported data on cognitive appraisal.

Within the time frame of approximately two hours, we investigated five
intervals with a duration of 10-minutes each: In the (1) pre-teaching
phase, the subjects were prepared for the following micro teaching unit
teaching lesson and familiarized with the setting. During the (2)
teaching phase, the participants taught a 15-minute self-prepared lesson
to a ``class'' of three actors that simulated nine classroom disruptions
. In the following (3) post-teaching phase, the subjects answered a
questionnaires, followed by and in the (4) interview phase, in which
they subjects watched thea pre-recorded video of their 15-minute lesson
to assess the self-report data of how disrupted subjects felt and how
confident they felt in dealing with disruptions. In the (5) end phase,
the subject answered another second questionnaire.

According to previous findings that fitness trackers can be used as a
low-cost, non-invasive method of measuring HR (\textbf{hajj2022wrist?};
Fuller et al. 2020) and that different HRs of teachers can be measured
in different teaching phases (\textbf{donker2020associations?};
\textbf{junker2021potential?}), we formulate the hypotheses as follows:

\textbf{Hypothesis 1}. In a first step, we wanted to display
exploratively the course of HR during the entire study. Additionally, we
presumed the highest mean HR in the (2) teaching phase and lower mean
values in all other phases (\textbf{Hypothesis 1a}). Moreover, we
expected an increase in HR in the (1) pre-teaching phase as the first
phase and a decrease in the following phases (\textbf{Hypothesis 1b}).
\textbf{Hypothesis 2}. We statistically predicted the subjects'
standardized mean HR for the (2) teaching, the (3) post-teaching, the
(4) interview and the (5) end phase with teaching experience and
self-repoted data on \ldots. With respect to teaching experience, Wwe
expected a lower HR in teachers with more teaching experience for the
four phases (\textbf{Hypothesis 2a}). According to the relationship
between physiological arousal and cognitive appraisal, we controlled for
shared variance with the self-reported data. Concerning the \ldots, Wwe
expected higher HR values for for the four phases that teachers who
reported that they felt more disrupted by disruptions would have higher
standardized mean HR (\textbf{Hypotheses 2b}). In contrast, individuals
with high confidence in dealing with disruptions would have a lower
standardized mean HR in the four phases (\textbf{Hypothesis 2c}). When
considering the three predictors in concert and controlling for their
common variance, we expected teaching experience and self-reported data
to remain substantial predictors (\textbf{Hypothesis 2d}).

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-fuller2020reliability}{}}%
Fuller, Daniel, Emily Colwell, Jonathan Low, Kassia Orychock, Melissa
Ann Tobin, Bo Simango, Richard Buote, et al. 2020. {``Reliability and
Validity of Commercially Available Wearable Devices for Measuring Steps,
Energy Expenditure, and Heart Rate: Systematic Review.''} \emph{JMIR
mHealth and uHealth} 8 (9): e18694.

\end{CSLReferences}

\end{document}

### 2023-08-24 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier/FitBit_elsevier/FitBit_elsevier.Rmd

---
title: "New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?"
shorttitle: "Using fitbit to measure teachers' heart rate"
authornote: |
 We received funding from QualiFond of University Leipzig. We have no conflicts of interest to disclose. This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022). 
author:
  - name: Mandy Klatt
    email: mandy.klatt@uni-leipzig.de
    affiliation: Leipzig University
    correspondingauthor: true
    footnote: 1
  - name: Peer Keßler
    email: Peer@example.com
    affiliation: Leipzig University
    footnote: 2
  - name: Gregor Kachel
    email: gregor@example.com
    affiliation: Leipzig University, Max Planck Institute for Evolutionary Anthropology
    footnote: 1
  - name: Christin Lotz
    email: christin@example.com
    affiliation: Leipzig University
    footnote: 1
  - name: Anne Deiglmayr
    email: anne@example.com
    affiliation: Leipzig University
    footnote: 3
address:
  - code: Leipzig University
    organization: Empirische Schul- und Unterrichtsforschung
    addressline: Marschnerstr. 29
    city: Leipzig
    state: Sachsen
    postcode: 04109
    country: Germany
  - code: Max Planck Institute for Evolutionary Anthropology
    organization: Department
    addressline: Deutscher Pl. 6
    postcode: 04103
    city: Leipzig
    state: Sachsen
    country: Germany
footnote:
  - code: 1
    text: 
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - code: 2
    text: 
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - code: 3
    text: "Supervision"
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  XXX In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress. XXX

  <!-- https://tinyurl.com/ybremelq -->
keywords: 
  - heart rate
  - photoplethysmography
  - wearable electronic device
  - teaching
journal: "Computers & Education"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: r-references.bib
linenumbers: false
numbersections: true
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: default
---

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r installing packages, include=FALSE}

library(needs)
needs(ltm,
      broom,
      ppcor,
      jtools,
      lm.beta,
      tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis)
```

```{r data wrangling, include=FALSE}
# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  dplyr::select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confidence_factor,
         event
         ) %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132",
                    "236")
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         )

# demographic data
df_demo_all <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
  transmute(ID = LI06_05, # select and rename relevant columns 
            # gender = factor(LI02_01_1,
            #                 levels = 1:2,
            #                 labels = c("male","female")
            #                 ),
            gender = LI02_01_1, # 1 = male; 2 = female
            age = LI03_01, 
            teaching_experience = LI04_01,
            school_type = LI18,
            term = LI11_01,
            extracurricular_teaching_experience = LI14,
            secondary_teaching_activities = LI17) %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132",
                    "236")
        )

# merge two data frames by ID 
df_merge <- merge(df_demo_all,
                  df_rating,
                  by = "ID")

# rm(list = c("df_demo","df_rating"))

data_path <- "./data/heart_rate_data"

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end_phase",
                               str_detect(string = id, pattern = "_m") ~ "teaching_phase",
                               str_detect(string = id, pattern = "_p") ~ "pre-teaching_phase",
                               str_detect(string = id, pattern = "_s") ~ "post-teaching_phase",
                               str_detect(string = id, pattern = "_i") ~ "interview_phase",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
      # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 7200) %>% # filter for 2 hours 30min (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

main <-
  left_join(main, df_merge,
            by = "ID")

main <- 
  main %>% 
  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132",
                    "236")
        ) %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>% 
  right_join(x = .,
             y = main,
             by = "ID") %>% 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart) %>% 
  filter(!(time_span == "teaching" & time > 600))

```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Present investigation 
The aim was to investigate whether HR measures assessed by a Fitbit Charge 4 are a suitable and effective method to **(1)** map teachers course of arousal over the course of a five phase lab study, including a micro teaching unit,  and **(2)**  examine whether HR measures can be predicted by self-reported data on cognitive appraisal.

Within the time frame of approximately two hours, we investigated five intervals with a duration of 10-minutes each: In the (1) pre-teaching phase, the subjects were prepared for the following micro teaching unit  teaching lesson and familiarized with the setting. During the (2) teaching phase, the participants taught a 15-minute self-prepared lesson to a "class" of three actors that simulated nine classroom disruptions . In the following (3) post-teaching phase, the subjects answered a questionnaires, followed by  and in the (4) interview phase, in which they subjects watched thea pre-recorded video of their 15-minute lesson to assess the self-report data of how disrupted subjects felt and how confident they felt in dealing with disruptions. In the (5) end phase, the subject answered another  second questionnaire.

According to previous findings that fitness trackers can be used as a low-cost, non-invasive method of measuring HR [@hajj2022wrist; @fuller2020reliability] and that different HRs of teachers can be measured in different teaching phases [@donker2020associations; @junker2021potential], we formulate the hypotheses as follows:

**Hypothesis 1**. In a first step, we wanted to display exploratively  the course of HR during the entire study.  Additionally, we presumed the highest mean HR in the (2) teaching phase and lower mean values in all other phases (**Hypothesis 1a**). Moreover, we expected an increase in HR in the (1) pre-teaching phase as the first phase and a decrease in the following phases (**Hypothesis 1b**).
**Hypothesis 2**. We statistically predicted  the subjects’ standardized mean HR for the (2) teaching, the (3) post-teaching, the (4) interview and the (5) end phase with teaching experience and self-repoted data on ….  With respect to teaching experience, Wwe expected a lower HR in teachers with more teaching experience for the four phases (**Hypothesis 2a**). According to the relationship between physiological arousal and cognitive appraisal, we controlled for shared variance with the self-reported data. Concerning the …, Wwe expected higher HR values for for the four phases that teachers who reported that they felt more disrupted by disruptions would have higher standardized mean HR  (**Hypotheses 2b**). In contrast, individuals with high confidence in dealing with disruptions would have a lower standardized mean HR in the four phases (**Hypothesis 2c**). When considering the three predictors in concert and controlling for their common variance, we expected teaching experience and self-reported data to remain substantial predictors (**Hypothesis 2d**).

# References {-}

### 2023-08-25 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
update aa

@@
   map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
-  dplyr::select(ID, event, disruption_factor) %>% 
+  dplyr::select(ID, event, disruption_factor, confidence_factor) %>% 
   filter(!ID %in% c(141,
@@
   select(id, code) %>% 
-  mutate(nd = 
-           as.numeric(
-             case_when(code > 3 ~ '0',
+  mutate(nd = as.numeric(case_when(code > 3 ~ '0',
                                    code <= 3 ~ '1',
@@
          ) %>% 
+  select(id, nd) %>% 
   group_by(id) %>%
@@
 
-# creating new column with total reactions
+# creating new column with absolute number of nd-alternatives
 main_novice <- main %>%
   filter(id %in% c("Novice")) %>% 
-  mutate(
-    # reaction_sum = sum(reaction),
-         nd_sum = sum(nd),
-         sum_participants = sum(n()),
-    # percent_reaction = round((reaction_sum/sum_participants),digits = 2),
-         percent_nd = round((nd/count),
+  mutate(percent_nd = round((nd/count),
                             digits = 2)
@@
 
-# creating new column with total reactions
+# creating new column with absolute number of nd-alternatives
 main_expert <- main %>%
   filter(id %in% c("Expert")) %>% 
-  mutate(
-    # reaction_sum = sum(reaction),
-         nd_sum = sum(nd),
-         sum_participants = sum(n()),
-    # percent_reaction = round((reaction_sum/sum_participants), digits = 2),
-         percent_nd = round((nd/count),
+  mutate(percent_nd = round((nd/count),
                             digits = 2)
@@
 
+# confidence factor
+describeBy(main$confidence_factor, main$id)
+plot_disrup <- boxplot(confidence_factor ~ id, data = main)
+
 # # sjt cm
@@
 describeBy(main$count, main$id)
-plot_action_count <- boxplot(count ~ id, data = main)^
+plot_action_count <- boxplot(count ~ id, data = main)
 
-# action alternatives - non disruptive alternatives (sum score)
+# action alternatives - non disruptive alternatives (absolute score)
 describeBy(main$nd, main$id)
@@
 plot_action_quality <- boxplot(percent_nd ~ id, data = main)
+
+# 
+main %>% 
+  group_by(id) %>% 
+  summarise(disruption_factor = n(),
+            confidence_factor = n(),
+            count = n(),
+            nd = n(),
+            percent_nd = n())
+
+table(main$disruption_factor)
+table(main$confidence_factor)
+table(main$count)
+table(main$nd)
+table(main$percent_nd)
 
@@
 t.test(x = main$disruption_factor[main$id == "Expert"],
-       y = main$disruption_factor[main$id == "Novice"])
+       y = main$disruption_factor[main$id == "Novice"],
+       var.equal = TRUE)
 
@@
 
+#### confidence factor
+# t-test for expertise differences
+t.test(x = main$confidence_factor[main$id == "Expert"],
+       y = main$confidence_factor[main$id == "Novice"],
+       var.equal = TRUE)
+
+# effect size for expertise differences
+CohenD(x = main$confidence_factor[main$id == "Expert"],
+       y = main$confidence_factor[main$id == "Novice"],
+       na.rm = TRUE)
+
 ### action alternatives count
@@
 t.test(x = main$count[main$id == "Expert"],
-       y = main$count[main$id == "Novice"])
+       y = main$count[main$id == "Novice"],
+       var.equal = TRUE)
 
@@
 t.test(x = main$nd[main$id == "Expert"],
-       y = main$nd[main$id == "Novice"])
+       y = main$nd[main$id == "Novice"],
+       var.equal = TRUE)
 
@@
 t.test(x = main$percent_nd[main$id == "Expert"],
-       y = main$percent_nd[main$id == "Novice"])
+       y = main$percent_nd[main$id == "Novice"],
+       var.equal = TRUE)
 

### 2023-08-27 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
update :)

@@
 
+# # frequencies
+# main %>% 
+#   group_by(id) %>% 
+#   summarise(disruption_factor = n(),
+#             confidence_factor = n(),
+#             count = n(),
+#             nd = n(),
+#             percent_nd = n())
 # 
-main %>% 
-  group_by(id) %>% 
-  summarise(disruption_factor = n(),
-            confidence_factor = n(),
-            count = n(),
-            nd = n(),
-            percent_nd = n())
-
-table(main$disruption_factor)
-table(main$confidence_factor)
-table(main$count)
-table(main$nd)
-table(main$percent_nd)
+# table(main$disruption_factor)
+# table(main$confidence_factor)
+# table(main$count)
+# table(main$nd)
+# table(main$percent_nd)
 
@@
 
-#### disruption factor
-# t-test for expertise differences
-t.test(x = main$disruption_factor[main$id == "Expert"],
-       y = main$disruption_factor[main$id == "Novice"],
-       var.equal = TRUE)
-
-# effect size for expertise differences
-CohenD(x = main$disruption_factor[main$id == "Expert"],
-       y = main$disruption_factor[main$id == "Novice"],
-       na.rm = TRUE)
-
-#### confidence factor
-# t-test for expertise differences
-t.test(x = main$confidence_factor[main$id == "Expert"],
-       y = main$confidence_factor[main$id == "Novice"],
-       var.equal = TRUE)
-
-# effect size for expertise differences
-CohenD(x = main$confidence_factor[main$id == "Expert"],
-       y = main$confidence_factor[main$id == "Novice"],
-       na.rm = TRUE)
-
 ### action alternatives count
@@
 
+#### disruption factor
+# t-test for expertise differences
+t.test(x = main$disruption_factor[main$id == "Expert"],
+       y = main$disruption_factor[main$id == "Novice"],
+       var.equal = TRUE)
+
+# effect size for expertise differences
+CohenD(x = main$disruption_factor[main$id == "Expert"],
+       y = main$disruption_factor[main$id == "Novice"],
+       na.rm = TRUE)
+
+#### confidence factor
+# t-test for expertise differences
+t.test(x = main$confidence_factor[main$id == "Expert"],
+       y = main$confidence_factor[main$id == "Novice"],
+       var.equal = TRUE)
+
+# effect size for expertise differences
+CohenD(x = main$confidence_factor[main$id == "Expert"],
+       y = main$confidence_factor[main$id == "Novice"],
+       na.rm = TRUE)
+
 ```
@@
 # Korrelationstabelle nach APA-Standards
-
 head(main)
 
-# Subset anlegen nur mit Variablen
+# Subset anlegen nur mit Variablen == Experts
 main %>%
-  select(disruption_factor, 
-         count, 
+  filter(id == "Expert") %>% 
+  select(count, 
          nd,
-         percent_nd) -> corr_subset
+         percent_nd,
+         disruption_factor, 
+         confidence_factor) -> corr_subset_expert
 
-apa.cor.table(corr_subset, filename = "Korrelationen.doc")
+apa.cor.table(corr_subset_expert, filename = "correlation_experts.doc")
+
+# Subset anlegen nur mit Variablen == Novices
+main %>%
+  filter(id == "Novice") %>% 
+  select(count, 
+         nd,
+         percent_nd,
+         disruption_factor, 
+         confidence_factor) -> corr_subset_novice
+
+apa.cor.table(corr_subset_novice, filename = "correlation_novices.doc")
+
+# Subset anlegen nur mit Variablen overall
+main %>%
+  select(count, 
+         nd,
+         percent_nd,
+         disruption_factor, 
+         confidence_factor) -> corr_subset_overall
+
+apa.cor.table(corr_subset_overall, filename = "correlation_overall.doc")
 

### 2023-10-09 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
update fitbitpaper

@@
 
-# pairwise comparisons
-pwc <- 
-  pairwise.t.test(df_anova_subset$mean_hr_std, 
-                  df_anova_subset$time_span, 
-                  p.adjust="holm")
-pwc
-
-# effect size of ANOVA
-EtaSq(df_anova_phase)
-
-effect_size_anova <-
-  round(sqrt(0.6829502   /(1-0.6829502   )), 2)
-
-# effect size of pairwise comparisons
-library(dplyr)
-library(rstatix)
-effect_size_pwc <-
-  df_anova_subset %>%
-  cohens_d(mean_hr_std ~ time_span) %>% 
-  as.data.frame()
+# # pairwise comparisons
+# pwc <- 
+#   pairwise.t.test(df_anova_subset$mean_hr_std, 
+#                   df_anova_subset$time_span, 
+#                   p.adjust="holm")
+# pwc
+# 
+# 
+# # effect size of ANOVA
+# EtaSq(df_anova_phase)
+# 
+# effect_size_anova <-
+#   round(sqrt(0.6829502   /(1-0.6829502   )), 2)
+# 
+# # effect size of pairwise comparisons
+# library(dplyr)
+# library(rstatix)
+# effect_size_pwc <-
+#   df_anova_subset %>%
+#   cohens_d(mean_hr_std ~ time_span) %>% 
+#   as.data.frame()
 

### 2023-10-10 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
update blabla

@@
       sandwich,
-      car)
+      car,
+      stats)
 
@@
   group_by(time_span) %>%
-  shapiro_test(mean_hr)
+  shapiro_test(mean_hr_std)
 
@@
 summary(df_anova_phase)
+
+# effektstärke für ANOVA
+DescTools::EtaSq(df_anova_phase)
+f = sqrt (0.7202944/ (1-0.7202944))
+
+# geplante Kontraste
+model <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
+summary (model)
+
+contrast1 <- c(-1, 1, 0, 0, 0)
+contrast2 <- c(0, 1, -1, 0, 0)
+contrast3 <- c(0, 1, 0, -1, 0)
+contrast4 <- c(0, 1, 0, 0, -1)
+
+contrasts(df_anova_subset$time_span) <- cbind(contrast1,
+                                              contrast2,
+                                              contrast3,
+                                              contrast4)
+
+model2 <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
+summary(model2)
+
+summary.aov(model2, 
+            split = list (time_span = list ("Lehrphase vs. Pre-Lehrphase" = 1,
+                                            "Lehrphase vs. Post-Lehrphase" = 2,
+                                            "Lehrphase vs. Interviewphase" = 3,
+                                            "Lehrphase vs. Endphase" = 4
+                                            )
+                          )
+            )
 

### 2023-10-13 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
update data
update eye tracking

@@
 t.test(x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
-       y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"])
+       y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
+       var.equal = TRUE)
 
@@
 t.test(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
-       y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"])
+       y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"],
+       var.equal = TRUE)
 
@@
 t.test(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
-       y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"])
+       y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
+       var.equal = TRUE)
 
@@
 t.test(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
-       y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"])
+       y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
+       var.equal = TRUE)
 
@@
 t.test(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
-       y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"])
+       y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"],
+       var.equal = TRUE)
 
@@
 t.test(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
-       y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"])
+       y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+       var.equal = TRUE)
 
@@
 t.test(x = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Expert"],
-       y = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Novice"])
+       y = df_ttff_sum$Sum_time_fixation_sec[df_ttff_sum$Group == "Novice"],
+       var.equal = TRUE)
 
@@
 
-# TIME TO FIRST FIXATIONS on all AOIs 
+# TIME TO FIRST FIXATIONS on disruptive person 
 # t-test for expertise differences
 t.test(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
-       y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"])
-
-# TIME TO FIRST FIXATIONS on all AOIs 
+       y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
+       var.equal = TRUE)
+
+# TIME TO FIRST FIXATIONS on disruptive person 
 # effect size for expertise differences
-d_time_all <- CohenD(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
+d_time_disrup <- CohenD(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
                     y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],

### 2023-11-13 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
update fitbitpaper
update fitbit
blabla

@@
 
-list(`Preparation Phase` = list(name = "Preparation Phase", mod = mods$preparation, data = graph_data$preparation),
+list(`Preparation Phase` = list(name = "Pre-Teaching ", mod = mods$preparation, data = graph_data$preparation),
      `Teaching Phase` = list(name = "Teaching Phase", mod = mods$teaching, data = graph_data$teaching),
@@
 
-## Teaching vs. Interview
+## Teaching vs. Interview (mean slope)
 
@@
 
-## Teaching vs. End
+## Teaching vs. End (mean slope)
 
@@
 
-## Interview vs. End
+## Interview vs. End (mean slope)
 
@@
 
-summary(regr_teaching1)
-summary(regr_teaching2)
-summary(regr_teaching3)
-summary(regr_teaching4)
+summary(regr_preparation1)
+summary(regr_preparation2)
+summary(regr_preparation3)
+summary(regr_preparation4)
 

### 2023-11-13 02_paper/paper_1_supplement_et_aoi.Rmd
blabla

---
title             : "Through the eyes of the teacher"
shorttitle        : "Visual attention in teaching and learning processes"

author: 
  - name          : "Mandy Klatt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Egelstraße 2a 04103 Leipzig"
    email         : "mandy.klatt@uni-leipzig.de"
  - name          : "Dr. Gregor Kachel"
    affiliation   : "1, 2"
  - name          : "Dr. Christin Lotz"
    affiliation   : "1"
  - name          : "Prof. Dr. Anne Deiglmayr"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Leipzig University"
  - id            : "2"
    institution   : "Max-Planck University for Evolutionary Anthropology"

authornote: |
  The Ethics Advisory Board of Leipzig University has dealt with the research project and has come to the conclusion that there are no objections to the implementation of this research project. The Ethics Advisory Board points out that the scientific and ethical responsibilty for the implementation of the project remains with the project director.

abstract: |
  This document is a supplement to the paper and shows first graphs findings from the pilot study.

keywords          : "Professional Vision, Expert-Novice-Paradigm, Eye-Tracking"
wordcount         : "1949"

bibliography      : ["r-references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf #bookdown::word_document2
---

```{r setup, include = FALSE}

# if a package is not installed on the current machine, it will install it
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages("papaja"); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

r_refs("r-references.bib")

```

```{r analysis-preferences, echo = FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# State of research

Teaching and classroom management are multidimensional settings in which teachers have to respond immediately to events as they develop [@barnes2004significance]. The different interests and abilities of students must be managed in a way that maximizes the active learning time of students and minimizes disruptions whilst teaching. Learning to develop such classroom management skills and to teach effectively is a complicated and complex process [@wolff2017see].

During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events. This ability is called professional vision and is a key component of teacher expertise and successful teaching [@barth2017professionelle]. Eye tracking technology has become a reliable means to study teachers’ visual focus of attention [@pouta2020student; @bogert2016visualperception; @wolff2017see]

Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies [@barth2017professionelle; @bogert2016visualperception; @wolff2017see]. For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students. The frequency and duration of fixations as eye movement are decisive [@stuermer2017eye]. Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks [@jarodzka2010eyes]. Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions [@cortina2015low].

## Research questions

The aim of the pilot study was to investigate whether there are differences in how expert and novice teachers manage scripted classroom disruptions. The disruptions were experimentally varied using a previously written script. Thus, our aim was to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.

In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disruptions but also notice them faster. In the hypothesis, therefore, it is necessary to check what has already been shown in the research literature: In complex teaching situations, experts have a more structured and elaborate professional knowledge than novices in order to perceive and interpret relevant events and to act appropriately [@berliner2001learning; @lachner2016makes].

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

For the sample recruitment of the subjects (N = 8, experts n = 2, novices n = 6), schools in the city of Leipzig in Saxony were contacted. The institutions as well as the subjects were informed in detail about the aim and intention of the study in advance. Participation in the study was voluntary and only took place after written consent has been given.

```{r demographicspilottable, echo = FALSE}

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)

# knock out NAs
quest.raw.data <- quest.raw.data  %>% filter(
  personID != "NA")

# create a basic table (tibble) using tidyverse functions
demo.quest.table <- quest.raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "Male" = sum(gender),
            "M age" = round(mean(age), 2),
            "Min age" = min(age),
            "Max age" = max(age),
            "SD age" = round(sd(age), 2),
            "M exp." = round(mean(experience), 2),
            "Min exp." = min(experience),
            "Max exp." = max(experience),
            "SD exp." = round(sd(experience), 2),
           )

# format and insert table in manuscript
apa_table(
  demo.quest.table,
  caption = "Demographic Information and Teaching Experience",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

```

The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices. Novices were recruited as teachers who have been working in the teaching profession for no more than 3 years, whereas experts were considered to have professional experience of 10 years or more [@messner2000berufliche].

## Procedure/ Data collection

### Set up

For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig. The subjects were divided into groups of four, so the study was conducted on two different sessions. All participants were asked to hold a 10-minute lesson. The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.

One person from the group of 4 acted as a teacher, the other three subjects acted as the class. The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g. putting their heads on the table, chatting, looking at their mobile phones, etc.).

The lesson disruptions were displayed as instructions during the lesson for all "students" but not the teacher. In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase. In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.

(ref:datacollection-caption) Example for set up during a mini-lesson

```{r datacollection, fig.cap = "(ref:datacollection-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/datacollection.png", dpi = 108)

# # How to insert images in papaja
# - pictures must be png
# - I created a pictures folder in the main folder, just dumb pictures there
# - you just need to hand the name and path of the picture to the knitr::: function (see above)
# - the dpi argument is for adjusting the size on the page in pixels

# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behind it
# the code chunk then opens and after "r" it needs to provide a name for the code chunk, must be unique in the document
# the fig.cap = then calls the text from the line just above
# fig.align allows to position the pic on page, center ist probablby best
# echo = false ensures that the code chunk does not occur in the pdf
# Now, go and try putting your own images in the paper 
#
# TIP = check line 46 in this manuscript. THis section ets global properties for how graphs are put in the paper. 
#         if floatsintext      : yes  --> pics, graphs, tables will be put where the code chunk is
#         if floatsintext      : no   --> pics, graphs, tables will be put at the end as is required by some journals
# TIP: check the folder "papaja_example&tutorial" that I put in this folder for paper1
# Tip: make a bookmark of this and skim through it: http://frederikaust.com/papaja_man/

```

### Eyetracking data

A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants. The head unit is a measuring device with different sensitive sensors. A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds. Infrared light illuminators support the eye tracking sensors which record the eye orientation. The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second. The scene camera has a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height). The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

## Coding/ Data preparation/ Reliability

### Eyetracking Data

The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson. The software allows for non-screen based recordings of a participants’ attention while moving in real-world settings. The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video. In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software. Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data. Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form. Tobii Pro does not allow to do AOI based analyses within Pro Lab. So we exported a tsv. file to do further analyses in the software R.

#### DYNAMIC Areas of Interest (AOI)

``` {r dAOIs, echo=FALSE} 
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages('papaja'); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

# prepare data (selected from AOI data)
et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T)

# convert into numeric
et.raw.data <- et.raw.data %>%  mutate(Total.duration.of.fixation.in.AOI..sec. = as.numeric(Total.duration.of.fixation.in.AOI..sec.),
                                       Average.duration.of.fixation.in.AOI..sec. = as.numeric(Average.duration.of.fixation.in.AOI..sec.),
                                       Number.of.fixations.in.AOI = as.numeric (Number.of.fixations.in.AOI),
                                       Total.Time.of.Interest.Duration..sec. = as.numeric(Total.Time.of.Interest.Duration..sec.))

# create a basic table (tibble) using tidyverse functions for all disruptions 
# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
options(digits = 2)

et.table <- et.raw.data %>%
  group_by(Type.of.disruption, Group) %>%
  filter(Type.of.disruption != "staring out the window") %>%
  rename ('Type of Disruption' = Type.of.disruption) %>%
  summarise("Mean Duration of Fixations" = mean(Total.duration.of.fixation.in.AOI..sec.),
            "Number of Fixations" = mean(Number.of.fixations.in.AOI),
            "TOI" = mean(Total.Time.of.Interest.Duration..sec.))

# create a new column with name Total that gives the sum duration in sec of looking at all AOIs
et.raw.data <- et.raw.data %>% mutate(Total = sum(Total.duration.of.fixation.in.AOI..sec.))

# create new columns that give proportion of the duration of looking at AOIs
# relative duration divided by total duration is the proportion
proportion.et.data <- et.raw.data %>% group_by(Group, Type.of.disruption) %>% 
                                      mutate(Proportion = Total.duration.of.fixation.in.AOI..sec./Total)

### Plot data TOTAL
total.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Total.duration.of.fixation.in.AOI..sec., fill = Type.of.disruption)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  geom_jitter(color="black", size=0.4, alpha=0.5) +
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Total Duration of Looking at AOIs in sec", x = "AOI")

total.plot

### Plot data PROPORTIONS
prop.plot <- ggplot(proportion.et.data, aes(x = Type.of.disruption, y = Proportion, fill = Type.of.disruption)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Proportion of Looking at AOIs", x = "AOI")

prop.plot

### Plot Number of Fixations
number.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Number.of.fixations.in.AOI, fill = Type.of.disruption)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  geom_jitter(color="black", size=0.4, alpha=0.5) +
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Number of Fixations in AOI", x = "AOI")

number.plot

# ### Plot Average duration of fixation
# average.plot <- ggplot(et.table, aes(x = "Type of Disruption", y = "Mean Duration of Fixations", fill = "Type of Disruption")) +
#   scale_x_discrete(guide = guide_axis(angle = 70)) +
#   geom_bar(aes(y="Mean Duration of Fixations")) + 
#   facet_wrap(~ Group)+
#   theme_light() +
#   theme(legend.position="none")+
#   labs(y = "Average Duration of Looking at AOIs in sec", x = "AOI")
# 
# average.plot

```

#########################################

#### MANUAL Areas of Interest (AOI)

``` {r mAOIs, echo=FALSE} 
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages('papaja'); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

# prepare data (selected from AOI data)
et.raw.data<-read.table("./data/Aperol_pilot_AOI_glasses_metrics_session01.txt", dec=",", sep="\t", header=T)

# convert into numeric
et.raw.data <- et.raw.data %>%  mutate(Total_duration_of_fixations = as.numeric(Total_duration_of_fixations),
                                       Average_duration_of_fixations = as.numeric(Average_duration_of_fixations),
                                       Number_of_fixations = as.numeric (Number_of_fixations),
                                       Total_duration_of_Visit = as.numeric(Total_duration_of_Visit))

# create a basic table (tibble) using tidyverse functions for all disruptions 
# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
options(digits = 2)

et.table <- et.raw.data %>%
  group_by(Group, AOI) %>%
  summarise("Mean Duration of Fixations" = mean(Total_duration_of_fixations),
            "Number of Fixations" = mean(Number_of_fixations),
            "Mean Duration of Visits" = mean(Total_duration_of_Visit))

view(et.table)

#FIXATIONS
# create a new column with name Total that gives the sum duration in msec of looking at all AOIs
et.fix.data <- et.raw.data %>% mutate(total_fixations = sum(Total_duration_of_fixations))

# create new columns that give proportion of the duration of looking at AOIs
# relative duration divided by total duration is the proportion
proportion.et.data <- et.fix.data %>% group_by(Group, AOI) %>% 
                                      mutate(proportion_fixations = Total_duration_of_fixations/total_fixations)

#VISITS
# create a new column with name Total that gives the sum duration in msec of visits in AOIs
et.visit.data <- et.raw.data %>% mutate(total_visits = sum(Total_duration_of_Visit))

# create new columns that give proportion of the duration of looking at AOIs
# relative duration divided by total duration is the proportion
proportion.et.data <- et.visit.data %>% group_by(Group, AOI) %>% 
                                      mutate(proportion_visits = Total_duration_of_Visit/total_visits)

### Plot data TOTAL FIXATIONS
total.fix.plot <- ggplot(et.fix.data, aes(x = AOI, y = Total_duration_of_fixations, fill = AOI)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  geom_jitter(color="black", size=0.4, alpha=0.5) +
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Total Duration of Looking at AOIs", x = "AOI")

total.fix.plot

# ### Plot data PROPORTIONS FIXATIONS
# prop.fix.plot <- ggplot(proportion.et.data, aes(x = AOI, y = proportion_fixations, fill = AOI)) +
#   scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
#   scale_x_discrete(guide = guide_axis(angle = 70)) +
#   geom_boxplot()+
#   facet_wrap(~ Group, nrow = 1)+
#   theme_light() +
#   theme(legend.position="none")+
#   labs(y = "Proportion of Looking at AOIs", x = "AOI")
# 
# prop.fix.plot

### Plot Number of Fixations
number.fix.plot <- ggplot(et.fix.data, aes(x = AOI, y = Number_of_fixations, fill = AOI)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  geom_jitter(color="black", size=0.4, alpha=0.5) +
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Number of Fixations in AOI", x = "AOI")

number.fix.plot

### Plot data TOTAL VISITS
total.visit.plot <- ggplot(et.visit.data, aes(x = AOI, y = Total_duration_of_Visit, fill = AOI)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  geom_jitter(color="black", size=0.4, alpha=0.5) +
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Total Duration of Visits in AOIs", x = "AOI")

total.visit.plot

### Plot Number of Saccades
saccade.plot <- ggplot(et.fix.data, aes(x = AOI, y = Number_of_saccades_in_AOI, fill = AOI)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  scale_x_discrete(guide = guide_axis(angle = 70)) +
  geom_boxplot()+
  geom_jitter(color="black", size=0.4, alpha=0.5) +
  facet_wrap(~ Group, nrow = 1)+
  theme_light() +
  theme(legend.position="none")+
  labs(y = "Number of Saccades in AOI", x = "AOI")

saccade.plot

# ### Plot data PROPORTIONS VISITS
# prop.visit.plot <- ggplot(proportion.et.data, aes(x = AOI, y = proportion_visits, fill = AOI)) +
#   scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
#   scale_x_discrete(guide = guide_axis(angle = 70)) +
#   geom_boxplot()+
#   facet_wrap(~ Group, nrow = 1)+
#   theme_light() +
#   theme(legend.position="none")+
#   labs(y = "Proportion of Visits in AOIs", x = "AOI")
# 
# prop.visit.plot

```

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

### Eyetracking Data

# Results

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

### Eyetracking Data

# Discussion

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2023-11-15 02_paper/02_study/02_fitbit paper/R_scripts/Presentation_Analysis.Rmd
update ordner aufräumen

--- 2023-02-18 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
@@
             by = "ID")
+
+main %>% 
+  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
+  distinct() %>% 
+  # filter(time_span == "overall") %>% 
+  group_by(ID) %>% 
+  summarize(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart) -> main
 ```
@@
        y = "Herzrate (in Schlägen pro Minute)") +
-  ggtitle("Gesamtverlauf Herzrate in unterschiedlichen Phasen") +
+  ggtitle("Gesamtverlauf der durchschnittlichen Herzraten") +
+    theme_apa()
+
+loess_plot_overall
+
+lm_plot_phases <-
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("pre","main","subsequent","interview","after"),
+                            labels = c("Pre-Phase","Unterrichtsphase","Subsequentphase","Interviewphase","Post-Phase"))) %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(method = "lm",
+              se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  # scale_x_continuous(expand = c(0, NA),
+  #                    breaks = seq(0, 9000, 600)) +
+  #scale_y_continuous(breaks = seq(0, 160, 5)) + 
+  labs(x = "Zeit (in Sekunden)",
+       y = "Durchschnittliche Herzrate (in Schlägen pro Minute)") +
+  ggtitle("Verlauf der durchschnittlichen Herzraten in unterschiedlichen Phasen\n(Lineare Schätzung)") +
+    theme_apa() +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x")
+
+grid.arrange(loess_plot_overall, lm_plot_phases,
+             ncol = 1)
+
+# saving plot 
+ggsave(plot = loess_plot_overall,
+       filename = "plots/loess_plot_overall.svg",
+       height = 5,
+       width = 8,
+       units = "in")
+
+```
+
+## Plot für Gesamtverlauf (STD)
+
+```{r}
+loess_plot_overall_std <-
+  main %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std
+                       ),
+         xlim = c(0, 7200)
+         )+
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0, NA),
+                     breaks = seq(0, 7200, 600)) +
+  # scale_y_continuous(breaks = seq(0, 160, 5)) + 
+  labs(x = "Zeit (in Sekunden)",
+       y = "z-standardisierte Herzrate") +
+  ggtitle("Gesamtverlauf der durchschnittlichen Herzraten (standardisiert)") +
+    theme_apa()
+
+loess_plot_overall_std
+
+# saving plot 
+ggsave(plot = loess_plot_overall_std,
+       filename = "plots/loess_plot_overall_std.svg",
+       height = 5,
+       width = 8,
+       units = "in")
+
+lm_plot_phases_std <-
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("pre","main","subsequent","interview","after"),
+                            labels = c("Pre-Lehrphase","Lehrphase","Post-Lehrphase","Interviewphase","Endphase"))) %>% 
+  distinct() %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate_std
+                       )
+         ) +
+  # geom_point(alpha = 0.05) + 
+  geom_smooth(method = "lm",
+              se = FALSE,
+              size = 0.5,
+              colour = "black") +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  # scale_x_continuous(expand = c(0, NA),
+  #                    breaks = seq(0, 9000, 600)) +
+  #scale_y_continuous(breaks = seq(0, 160, 5)) + 
+  labs(x = "Zeit (in Sekunden)",
+       y = "standardisierte Herzrate") +
+  ggtitle("Verlauf der durchschnittlichen Herzraten in unterschiedlichen Phasen\n(Lineare Schätzung)") +
   theme(text = element_text(family = "sans"),
@@
                                   face = "bold")) +
-    theme_apa()
-
-loess_plot_overall
+    theme_apa() +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x")
+lm_plot_phases_std
 
 # saving plot 
-ggsave(plot = loess_plot_overall,
-       filename = "plots/loess_plot_overall.svg",
+ggsave(plot = lm_plot_phases_std,
+       filename = "plots/lm_plot_phases_std.svg",
        height = 5,
@@
 
-```
-
-## Plot mit Mittelwerten und SDs
+grid.arrange(loess_plot_overall, lm_plot_phases,
+             ncol = 1)
+```
+
+## Plot mit Mittelwerten und SDs (STD)
 
@@
 # data wrangling - preparing data for plotting
-df_plot_mean <-
+df_plot_mean_std <-
   main %>% 
@@
   dplyr::select("time_span",
-                "heart_rate") %>% 
+                "heart_rate_std") %>% 
   mutate(time_span = fct_recode(time_span,
@@
   group_by(time_span) %>%
-  summarise_at(vars(heart_rate),
-               list(mean_hr = mean,
-                    sd_hr = sd)
+  summarise_at(vars(heart_rate_std),
+               list(mean_hr_std = mean,
+                    sd_hr_std = sd)
                ) %>% 
@@
 # plotting
-plot_mean_sd <- 
+plot_mean_sd_std <- 
   ggplot(df_plot_mean, 
-         aes(x = time_span, y = mean_hr)) + 
+         aes(x = time_span, y = mean_hr_std)) + 
   geom_point(size = 3,
              colour = "black")+
-  geom_errorbar(aes(ymin = mean_hr - sd_hr, 
-                    ymax = mean_hr + sd_hr), 
+  geom_errorbar(aes(ymin = mean_hr_std - sd_hr_std, 
+                    ymax = mean_hr_std + sd_hr_std), 
                 width=.2,
@@
   labs(x = "",
-       y = "Herzrate (in Schlägen pro Minute)") +
+       y = "z-standardisierte Herzrate") +
   ggtitle("Mittlere Herzrate in unterschiedlichen Phasen") +
@@
 
-plot_mean_sd
+plot_mean_sd_std
 
 # saving plot 
-ggsave(plot = plot_mean_sd,
-       filename = "plots/plot_mean_sd.svg",
-       height = 5,
-       width = 8,
+ggsave(plot = plot_mean_sd_std,
+       filename = "plots/plot_mean_sd_std.svg",
+       height = 4,
+       width = 9,
        units = "in")

### 2023-11-16 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
update fitbit paper

@@
              by = "ID") %>% 
+  filter(!(time_span == "teaching" & time > 600)) %>%
   mutate(heart_rate_std = (heart_rate - mean_heart)/
-           sd_heart) %>% 
-  filter(!(time_span == "teaching" & time > 600))
+           sd_heart)
+
+```
+
+# Descriptives
+```{r descriptive statistics}
+
+# Mean, SD and range for overall (unstandardized)
+descrip_hr_overall <- main %>%
+  filter(time_span %in% c("overall")) %>% 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate),
+                                      digits = 2),
+            "Min heart rate in bpm" = min(heart_rate),
+            "Max heart rate in bpm" = max(heart_rate)
+  )
+
+# Mean, SD and range for overall (standardized)
+descrip_hr_overall_std <- main %>%
+  filter(time_span %in% c("overall")) %>% 
+  summarise(N = n_distinct(ID),
+            "M std heart rate in bpm" = round(mean(heart_rate_std),
+                                              digits = 2),
+            "SD std heart rate in bpm" = round(sd(heart_rate_std),
+                                               digits = 2),
+            "Min std heart rate in bpm" = round(min(heart_rate_std),
+                                                digits = 2),
+            "Max heart rate in bpm" = round(max(heart_rate_std),
+                                            digits = 2)
+            )
+
+# Mean, SD and range for individual phases (unstandardized)
+descrip_hr_phases <- main %>% 
+  filter(!time_span %in% c("overall")) %>% 
+  group_by(time_span) %>% 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate),
+                                      digits = 2),
+            "Min heart rate in bpm" = min(heart_rate),
+            "Max heart rate in bpm" = max(heart_rate)
+  )
+
+# Mean, SD and range for individual phases (standardized)
+descrip_hr_phases_std <- main %>% 
+  filter(!time_span %in% c("overall")) %>% 
+  group_by(time_span) %>% 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate_std),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate_std),
+                                      digits = 2),
+            "Min heart rate in bpm" = round(min(heart_rate_std),
+                                            digits = 2),
+            "Max heart rate in bpm" = round(max(heart_rate_std),
+                                            digits = 2)
+  )
+
+# # format and insert table in manuscript
+# descrip_hr_phases %>%
+# papaja::apa_table(
+#   caption = "Mean, SD and range for teachers' heart rate in individual phases",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+#   )
+
+# Mean, SD and range for disruption and confidence factor
+rating_table <- 
+  df_rating %>% 
+  filter(!is.na(confidence_factor),
+         !is.na(disruption_factor)) %>% 
+   summarise(N = n_distinct(ID), 
+            "M disruption factor" = round(mean(disruption_factor),
+                                     digits = 2),
+            "SD disruption factor" = round(sd(disruption_factor),
+                                      digits = 2),
+            "Min disruption factor" = min(disruption_factor),
+            "Max disruption factor" = max(disruption_factor),
+            "M confidence factor" = round(mean(confidence_factor),
+                                     digits = 2),
+            "SD confidence factor" = round(sd(confidence_factor),
+                                      digits = 2),
+            "Min confidence factor" = min(confidence_factor),
+            "Max confidence factor" = max(confidence_factor)
+            )
 
@@
        y = "") +
-  ggtitle("Overall Course of Average Heartrate") +
+  ggtitle("Overall Course of Mean Heart Rate") +
   theme_apa() + 
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("(1) Pre-teaching phase","(2) Teaching phase","(3) Post-teaching phase","(4) Interview phase","(5) End phase"))) %>% 
+                            labels = c("(1) Pre-teaching Interval","(2) Teaching Interval","(3) Post-teaching Interval","(4) Interview Interval","(5) End Interval"))) %>% 
   distinct() %>%
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("(1) Pre Teaching\nPhase","(2) Teaching\nPhase","(3) Post Teaching\nPhase","(4) Interview\nPhase","(5) End\nPhase")
+                            labels = c("(1) Pre-Teaching\nInteval","(2) Teaching\nInterval","(3) Post-Teaching\nInterval","(4) Interview\nInterval","(5) End\nInterval")
                             ),
@@
   scale_x_continuous(breaks = seq(0, 10, 2)) +
-  #scale_y_continuous(breaks = seq(0, 160, 5)) +
+  scale_y_continuous(breaks = seq(from = -1, to = 1, by = 0.5)) +
   labs(x = "Time (in Minutes)",
-       y = "Average Standardized Heart Rate",
+       y = "Standardized Mean Heart Rate",
        caption = expression(paste(italic("Note: "),
@@
              scales = "free_x")
+
 ggsave(filename = "plots_publication/lm_plot.png",
@@
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-         gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
+         # gender = if_else(gender == "male",
+         #                   true = 0,
+         #                   false = 1),
           teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) %>%
-  pcor()  -> pcor_pre
+         ) -> cor_pre
+
+cor.test(cor_pre$heart_rate_m, cor_pre$confidence_factor_m)
 
@@
   ungroup() -> data_regression_mean
+
+for (i in unique(data_regression_mean$time_span)) {
+
+  cache <- data_regression_mean %>% 
+    filter(time_span == i)
+
+  regr1 <-
+    lm(heart_rate ~ teaching_experience,
+    data = cache)
+
+  assign(value = regr1,
+         x = paste0("regr_", i, "1"))
+
+  regr2 <-
+    lm(heart_rate ~ teaching_experience + disruption_factor,
+    data = cache)
+
+  assign(value = regr2,
+         x = paste0("regr_", i, "2"))
+
+  regr3 <-
+    lm(heart_rate ~ teaching_experience + confidence_factor,
+    data = cache)
+
+  assign(value = regr3,
+         x = paste0("regr_", i, "3"))
+
+  regr4 <-
+    lm(heart_rate ~ teaching_experience + disruption_factor + confidence_factor,
+    data = cache)
+
+  assign(value = regr4,
+         x = paste0("regr_", i, "4"))
+
+}
+
+# Hier habe ich immer nur die Modelle getauscht. Also statt regr_end1 regr_teaching1 usw.
+
+summary(regr_preparation1)
+summary(regr_preparation2)
+summary(regr_preparation3)
+summary(regr_preparation4)
+
+```
+
+# Multiple Linear Regression (Slope)
+
+```{r}
+df_multi <- 
+  main %>% 
+  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  summarize(disruption = mean(disruption_factor, na.rm = T),
+            confidence = mean(confidence_factor, na.rm = T),
+            teaching_experience) %>% 
+  ungroup() %>% 
+  mutate(id = as.character(ID)) %>% 
+  distinct() %>% 
+  right_join(x = .,
+            y = fix_models,
+            by = "id") %>% 
+  mutate(slope = abs(slope))
+  # mutate(posneg = if_else(condition = slope < 0,
+  #                         true = "negative",
+  #                         false = "positive"))
 
@@
 # "The shadow around the line represents the 99% confidence interval.
-       #                            We used the ggplot2 package (v3.3.3; Wickham, 2016) to calculate the moving average of the course."))
+The confidence interval shown refers to the HR measurement points during the entire study period.
+We used the ggplot2 package (v3.3.3; Wickham, 2016) to calculate the moving average of the course."))
        ) +
@@
 ```{r}
+
 main %>% 
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("(1) Pre-teaching\nphase","(2) Teaching\nphase","(3) Post-teaching\nphase","(4) Interview\nphase","(5) End\nphase"))) %>% 
+                            labels = c("(1) Pre-teaching\nInterval","(2) Teaching\nInterval","(3) Post-teaching\nInterval","(4) Interview\nInterval","(5) End\nInterval"))) %>% 
   distinct() %>%
@@
              linetype = "dashed") +
-  labs(x = "",
-       y = "Standardized mean HR",
-       caption = expression(paste(italic("Note: "), 
-                                  "The dotted line represents the null effect; bars represent the 1% confidence interval. "
-                                  )
-                            )
+  ylim(-1, 1) + 
+  scale_y_continuous(breaks=seq(-1, 1, 0.5), 
+                     limits=c(-1, 1)) + 
+  labs(x = "Time (in Minutes)",
+       y = "Standardized Mean Heart Rate",
+       # caption = expression(paste(italic("Note: "),
+       #                            "The shadow around the line represents the 99% confidence interval."
+       #                            )
+       #                      )
        ) +
-  facet_grid(cols = vars(time_span)) +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x") +
   theme_apa() +
@@
             by = "id") %>%
-  mutate(posneg = if_else(condition = slope < 0,
-                          true = "negative",
-                          false = "positive"))
+  # mutate(posneg = if_else(condition = slope < 0,
+  #                         true = "negative",
+  #                         false = "positive"))
 
@@
             by = "id") %>% 
-  mutate(posneg = if_else(condition = slope < 0,
-                          true = "negative",
-                          false = "positive"))
+  # mutate(posneg = if_else(condition = slope < 0,
+  #                         true = "negative",
+  #                         false = "positive"))
 fit_teach_1 <-
@@
   filter(Phase == "Teaching Phase") %>% 
-  split(.$posneg) %>% 
+  # split(.$posneg) %>% 
   map(~ lm(slope ~ disruption,

### 2023-11-17 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
blabla

--- 2023-11-16 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
@@
       ggplot2,
-      apaTables)
+      apaTables,
+      rockchalk)
 
@@
 # Graph
-
 ```{r fig.width = 10,results='hide',fig.keep='all'}
@@
 # Plots for all phases
-
 ```{r}
@@
 ## Pr-teaching phase
-
 ```{r}
@@
             teaching_experience = teaching_experience,
-            gender = gender
+            # gender = gender
   ) %>%
@@
 
+# heart rate ~
+cor.test(cor_pre$heart_rate_m, cor_pre$teaching_experience)
+cor.test(cor_pre$heart_rate_m, cor_pre$disruption_factor_m)
 cor.test(cor_pre$heart_rate_m, cor_pre$confidence_factor_m)
 
+# teaching experience ~
+cor.test(cor_pre$teaching_experience, cor_pre$disruption_factor_m)
+cor.test(cor_pre$teaching_experience, cor_pre$confidence_factor_m)
+
+# disruption factor ~
+cor.test(cor_pre$disruption_factor_m, cor_pre$confidence_factor_m)
+
 # knitr::kable(x = list(pcor_main$estimate, pcor_main$p.value), format = "simple")
@@
 ## Teaching phase
-
 ```{r}
@@
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-         gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
+         # gender = if_else(gender == "male",
+         #                   true = 0,
+         #                   false = 1),
           teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) %>%
-  pcor()  -> pcor_teaching
+         ) -> cor_teaching
+
+# heart rate ~
+cor.test(cor_teaching$heart_rate_m, cor_teaching$teaching_experience)
+cor.test(cor_teaching$heart_rate_m, cor_teaching$disruption_factor_m)
+cor.test(cor_teaching$heart_rate_m, cor_teaching$confidence_factor_m)
+
+# teaching experience ~
+cor.test(cor_teaching$teaching_experience, cor_teaching$disruption_factor_m)
+cor.test(cor_teaching$teaching_experience, cor_teaching$confidence_factor_m)
+
+# disruption factor ~
+cor.test(cor_teaching$disruption_factor_m, cor_teaching$confidence_factor_m)
 
@@
 ## Post-teaching phase
-
 ```{r}
@@
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-         gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
+         # gender = if_else(gender == "male",
+         #                   true = 0,
+         #                   false = 1),
           teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) %>%
-  pcor()  -> pcor_post
+         ) -> cor_post
+
+# heart rate ~
+cor.test(cor_post$heart_rate_m, cor_post$teaching_experience)
+cor.test(cor_post$heart_rate_m, cor_post$disruption_factor_m)
+cor.test(cor_post$heart_rate_m, cor_post$confidence_factor_m)
+
+# teaching experience ~
+cor.test(cor_post$teaching_experience, cor_post$disruption_factor_m)
+cor.test(cor_post$teaching_experience, cor_post$confidence_factor_m)
+
+# disruption factor ~
+cor.test(cor_post$disruption_factor_m, cor_post$confidence_factor_m)
 
@@
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-         gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
+         # gender = if_else(gender == "male",
+         #                   true = 0,
+         #                   false = 1),
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) %>%
-  pcor()  -> pcor_interview
+         ) -> cor_interview
+
+# heart rate ~
+cor.test(cor_interview$heart_rate_m, cor_interview$teaching_experience)
+cor.test(cor_interview$heart_rate_m, cor_interview$disruption_factor_m)
+cor.test(cor_interview$heart_rate_m, cor_interview$confidence_factor_m)
+
+# teaching experience ~
+cor.test(cor_interview$teaching_experience, cor_interview$disruption_factor_m)
+cor.test(cor_interview$teaching_experience, cor_interview$confidence_factor_m)
+
+# disruption factor ~
+cor.test(cor_interview$disruption_factor_m, cor_interview$confidence_factor_m)
 
@@
 ## End phase
-
 ```{r}
@@
          disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
-         gender = if_else(gender == "male",
-                           true = 0,
-                           false = 1),
+         # gender = if_else(gender == "male",
+         #                   true = 0,
+         #                   false = 1),
           teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) %>%
-  pcor()  -> pcor_end
+         ) -> cor_end
+
+# heart rate ~
+cor.test(cor_end$heart_rate_m, cor_end$teaching_experience)
+cor.test(cor_end$heart_rate_m, cor_end$disruption_factor_m)
+cor.test(cor_end$heart_rate_m, cor_end$confidence_factor_m)
+
+# teaching experience ~
+cor.test(cor_end$teaching_experience, cor_end$disruption_factor_m)
+cor.test(cor_end$teaching_experience, cor_end$confidence_factor_m)
+
+# disruption factor ~
+cor.test(cor_end$disruption_factor_m, cor_end$confidence_factor_m)
 
@@
 # Multiple Linear Regression (Mean)
-
 ```{r}
@@
 # Multiple Linear Regression (Slope)
-
 ```{r}
@@
             y = fix_models,
-            by = "id") %>% 
-  mutate(slope = abs(slope))
+            by = "id") 
+  # %>% 
+  # mutate(slope = abs(slope))
   # mutate(posneg = if_else(condition = slope < 0,
@@
 
-for (i in unique(data_regression_mean$time_span)) {
-
-  cache <- data_regression_mean %>% 
+for (i in unique(df_multi$time_span)) {
+
+  cache <- df-multi %>% 
     filter(time_span == i)
@@
   regr2 <-
-    lm(heart_rate ~ teaching_experience + disruption_factor,
+    lm(slope ~ teaching_experience + disruption_factor,
     data = cache)
@@
   regr3 <-
-    lm(heart_rate ~ teaching_experience + confidence_factor,
+    lm(slope ~ teaching_experience + confidence_factor,
     data = cache)
@@
   regr4 <-
-    lm(heart_rate ~ teaching_experience + disruption_factor + confidence_factor,
+    lm(slope ~ teaching_experience + disruption_factor + confidence_factor,
     data = cache)
@@
                      limits=c(-1, 1)) + 
+  scale_x_continuous(breaks = seq(0, 10, 2)) +
   labs(x = "Time (in Minutes)",
@@
             y = fix_models,
-            by = "id") %>%
+            by = "id") 
   # mutate(posneg = if_else(condition = slope < 0,
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ disruption * posneg)
+  lm(slope ~ teaching_experience + disruption)
 
@@
 
-fit_pre_2 <-
-  df_multi %>% 
-  filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ confidence:posneg)
-
-summary(fit_pre_2)
-
-fit_pre_3 <-
-  df_multi %>% 
-  mutate(teaching_experience = log(teaching_experience + 1)) %>% 
-  filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ teaching_experience:posneg)
-
-summary(fit_pre_3)
-
-fit_pre_4 <-
-  df_multi %>% 
-  filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ confidence:posneg + disruption:posneg)
-
-summary(fit_pre_4)
-
-fit_pre_5 <-
-  df_multi %>% 
-  filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ posneg:confidence + posneg:disruption + posneg:teaching_experience)
-
-summary(fit_pre_5)
-
-stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
-                     type = "html",
-                     caption = "Pre Teaching Phase",
-                     dep.var.labels = "Slope",
-                     # order = c(1, 2, 3),
-                     # covariate.labels = c("Disruption Factor",
-                     #                      "Confidence Factor",
-                     #                      "Teaching Experience"),
-                     keep.stat = c("n","rsq","adj.rsq")
-                     )
-
-fit_pre_3$model %>%
-  mutate(fitted.values = fit_pre_3$fitted.values) %>% 
-  ggplot(mapping = aes(x = teaching_experience,
-                       y = slope
-                       )
-         ) +
-  geom_point(mapping = aes(group = posneg)) +
-          geom_line(mapping = aes(y = fitted.values,
-                                  group = posneg)) +
-  geom_smooth(method = "lm",
-              se = F,
-              linetype = "dashed") +
-        # geom_point(alpha = 0.5,
-        #            size = 0.5) +
-        theme_apa()
+getDeltaRsquare(fit_pre_1)
+
+dat1 <- genCorrelatedData(N=250, means=c(100,100),
+sds=c(30,20), rho=0.0,  stde = 7, beta=c(1.1, 2.4, 4.1, 0))
+m1 <- lm(y ~ x1 + x2, data=dat1)
+getDeltaRsquare(m1)
+
+# fit_pre_2 <-
+#   df_multi %>% 
+#   filter(Phase == "Pre Teaching Phase") %$% 
+#   lm(slope ~ confidence)
+# 
+# summary(fit_pre_2)
+# 
+# 
+# fit_pre_3 <-
+#   df_multi %>% 
+#   mutate(teaching_experience = log(teaching_experience + 1)) %>% 
+#   filter(Phase == "Pre Teaching Phase") %$% 
+#   lm(slope ~ teaching_experience)
+# 
+# summary(fit_pre_3)
+# 
+# 
+# fit_pre_4 <-
+#   df_multi %>% 
+#   filter(Phase == "Pre Teaching Phase") %$% 
+#   lm(slope ~ confidence + disruption)
+# 
+# summary(fit_pre_4)
+# 
+# fit_pre_5 <-
+#   df_multi %>% 
+#   filter(Phase == "Pre Teaching Phase") %$% 
+#   lm(slope ~ confidence + disruption + teaching_experience)
+# 
+# summary(fit_pre_5)
+# 
+# 
+# stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
+#                      type = "html",
+#                      caption = "Pre Teaching Phase",
+#                      dep.var.labels = "Slope",
+#                      # order = c(1, 2, 3),
+#                      # covariate.labels = c("Disruption Factor",
+#                      #                      "Confidence Factor",
+#                      #                      "Teaching Experience"),
+#                      keep.stat = c("n","rsq","adj.rsq")
+#                      )
+
+# fit_pre_3$model %>%
+#   mutate(fitted.values = fit_pre_3$fitted.values) %>% 
+#   ggplot(mapping = aes(x = teaching_experience,
+#                        y = slope
+#                        )
+#          ) +
+#   geom_point(mapping = aes(group = posneg)) +
+#           geom_line(mapping = aes(y = fitted.values,
+#                                   group = posneg)) +
+#   geom_smooth(method = "lm",
+#               se = F,
+#               linetype = "dashed") +
+#         # geom_point(alpha = 0.5,
+#         #            size = 0.5) +
+#         theme_apa()
 
@@
   filter(Phase == "Teaching Phase") %$% 
-  lm(slope ~ disruption:posneg)
+  lm(slope ~ disruption)
 

### 2023-11-17 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
update fitbit

@@
 ## Interview phase
-
 ```{r}
@@
 
+summary(regr_teaching1)
+summary(regr_teaching2)
+summary(regr_teaching3)
+summary(regr_teaching4)
+
+```
+
+# Multiple Linear Regression (Slope)
+```{r}
+
+  main %>% 
+  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  # summarize(disruption_factor = mean(disruption_factor, na.rm = T),
+  #           confidence_factor = mean(confidence_factor, na.rm = T),
+  #           teaching_experience) %>% 
+  transmute(id = as.character(ID),
+            disruption_factor = mean(disruption_factor, na.rm = T),
+            confidence_factor = mean(confidence_factor, na.rm = T),
+            teaching_experience) %>% 
+  ungroup() %>% 
+  distinct() %>% 
+  right_join(x = .,
+            y = fix_models,
+            by = "id") -> data_regression_slope
+
+for (i in unique(data_regression_slope$Phase)) {
+
+  cache <- data_regression_slope %>% 
+    filter(Phase == i)
+
+  regr1 <-
+    lm(slope ~ teaching_experience,
+    data = cache)
+
+  assign(value = regr1,
+         x = paste0("regr_", i, "1"))
+
+  regr2 <-
+    lm(slope ~ teaching_experience + disruption_factor,
+    data = cache)
+
+  assign(value = regr2,
+         x = paste0("regr_", i, "2"))
+
+  regr3 <-
+    lm(slope ~ teaching_experience + confidence_factor,
+    data = cache)
+
+  assign(value = regr3,
+         x = paste0("regr_", i, "3"))
+
+  regr4 <-
+    lm(slope ~ teaching_experience + disruption_factor + confidence_factor,
+    data = cache)
+
+  assign(value = regr4,
+         x = paste0("regr_", i, "4"))
+
+}
+
+# Hier habe ich immer nur die Modelle getauscht. Also statt regr_end1 regr_teaching1 usw.
+
 summary(regr_preparation1)
@@
 
-# Multiple Linear Regression (Slope)
-
-```{r}
-df_multi <- 
-  main %>% 
-  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
-  distinct() %>% 
-  group_by(ID) %>% 
-  summarize(disruption = mean(disruption_factor, na.rm = T),
-            confidence = mean(confidence_factor, na.rm = T),
-            teaching_experience) %>% 
-  ungroup() %>% 
-  mutate(id = as.character(ID)) %>% 
-  distinct() %>% 
-  right_join(x = .,
-            y = fix_models,
-            by = "id") %>% 
-  mutate(slope = abs(slope))
-  # mutate(posneg = if_else(condition = slope < 0,
-  #                         true = "negative",
-  #                         false = "positive"))
-
-for (i in unique(data_regression_mean$time_span)) {
-
-  cache <- data_regression_mean %>% 
-    filter(time_span == i)
-
-  regr1 <-
-    lm(heart_rate ~ teaching_experience,
-    data = cache)
-
-  assign(value = regr1,
-         x = paste0("regr_", i, "1"))
-
-  regr2 <-
-    lm(heart_rate ~ teaching_experience + disruption_factor,
-    data = cache)
-
-  assign(value = regr2,
-         x = paste0("regr_", i, "2"))
-
-  regr3 <-
-    lm(heart_rate ~ teaching_experience + confidence_factor,
-    data = cache)
-
-  assign(value = regr3,
-         x = paste0("regr_", i, "3"))
-
-  regr4 <-
-    lm(heart_rate ~ teaching_experience + disruption_factor + confidence_factor,
-    data = cache)
-
-  assign(value = regr4,
-         x = paste0("regr_", i, "4"))
-
-}
-
-# Hier habe ich immer nur die Modelle getauscht. Also statt regr_end1 regr_teaching1 usw.
-
-summary(regr_preparation1)
-summary(regr_preparation2)
-summary(regr_preparation3)
-summary(regr_preparation4)
-
-```
-
-# Plot
-
+# Overall Plot (unstd./std.)
 ```{r}
@@
 
+# Mean Plot
 ```{r}
@@
 # Pre Teaching Phase
-
 ```{r echo = FALSE, results='asis'}
@@
   group_by(ID) %>% 
-  summarize(disruption = mean(disruption_factor, na.rm = T),
-            confidence = mean(confidence_factor, na.rm = T),
+  summarize(disruption_factor = mean(disruption_factor, na.rm = T),
+            confidence_factor = mean(confidence_factor, na.rm = T),
             teaching_experience) %>% 
@@
             y = fix_models,
-            by = "id") %>%
+            by = "id")
   # mutate(posneg = if_else(condition = slope < 0,
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ disruption * posneg)
+  lm(slope ~ teaching_experience)
 
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ confidence:posneg)
+  lm(slope ~ teaching_experience + disruption_factor)
 
 summary(fit_pre_2)
+
+summary(fit_pre_1)$r.squared - summary(fit_pre_2)$r.squared
 
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ teaching_experience:posneg)
+  lm(slope ~ teaching_experience + confidence_factor)
 
@@
 
+summary(fit_pre_1)$r.squared - summary(fit_pre_2)$r.squared - summary(fit_pre_3)$r.squared
+
 fit_pre_4 <-
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ confidence:posneg + disruption:posneg)
+  lm(slope ~ teaching_experience + confidence + disruption)
 
 summary(fit_pre_4)
-
-fit_pre_5 <-
-  df_multi %>% 
-  filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ posneg:confidence + posneg:disruption + posneg:teaching_experience)
-
-summary(fit_pre_5)
 

### 2023-11-20 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
fitbiiiiit

@@
       ggplot2,
-      apaTables,
-      rockchalk)
+      apaTables)
 
@@
 
-summary(regr_preparation1)
-summary(regr_preparation2)
-summary(regr_preparation3)
-summary(regr_preparation4)
+summary(regr_end1)
+summary(regr_end2)
+summary(regr_end3)
+summary(regr_end4)
+
+# delta R²
+summary(regr_end1)$r.squared - summary(regr_end2)$r.squared - summary(regr_end3)$r.squared - summary(regr_end4)$r.squared
 
@@
   main %>% 
-  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  select("ID",
+         "disruption_factor",
+         "confidence_factor",
+         "teaching_experience") %>% 
   distinct() %>% 
   group_by(ID) %>% 
-  summarize(disruption = mean(disruption_factor, na.rm = T),
-            confidence = mean(confidence_factor, na.rm = T),
+  summarize(disruption_factor = mean(disruption_factor, na.rm = T),
+            confidence_factor = mean(confidence_factor, na.rm = T),
             teaching_experience) %>% 
   ungroup() %>% 
-  mutate(id = as.character(ID)) %>% 
+  mutate(id = as.character(ID),
+         ) %>% 
   distinct() %>% 
@@
             y = fix_models,
-            by = "id") 
+            by = "id") %>%
+  mutate(time_span = factor(Phase,
+                             levels = c("Pre Teaching Phase",
+                                        "Teaching Phase",
+                                        "Post Teaching Phase",
+                                        "Interview Phase",
+                                        "End Phase"),
+                             labels = c("preparation",
+                                        "teaching",
+                                        "post",
+                                        "interview",
+                                        "end")
+                            )
+         ) %>%
+  select("id",
+         "disruption_factor",
+         "confidence_factor",
+         "teaching_experience",
+         "slope",
+         "time_span")
+
   # %>% 
@@
 
-  cache <- df-multi %>% 
+  cache <- df_multi %>% 
     filter(time_span == i)
@@
   regr1 <-
-    lm(heart_rate ~ teaching_experience,
+    lm(slope ~ teaching_experience,
     data = cache)
@@
 
-summary(regr_preparation1)
-summary(regr_preparation2)
-summary(regr_preparation3)
-summary(regr_preparation4)
+summary(regr_post1)
+summary(regr_post2)
+summary(regr_post3)
+summary(regr_post4)
+
+summary(regr_end1)$r.squared - summary(regr_end2)$r.squared - summary(regr_end3)$r.squared - summary(regr_end4)$r.squared
 
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ teaching_experience + disruption)
+  lm(slope ~ teaching_experience)
 
@@
 
-getDeltaRsquare(fit_pre_1)
-
-dat1 <- genCorrelatedData(N=250, means=c(100,100),
-sds=c(30,20), rho=0.0,  stde = 7, beta=c(1.1, 2.4, 4.1, 0))
-m1 <- lm(y ~ x1 + x2, data=dat1)
-getDeltaRsquare(m1)
-
-# fit_pre_2 <-
-#   df_multi %>% 
-#   filter(Phase == "Pre Teaching Phase") %$% 
-#   lm(slope ~ confidence)
-# 
-# summary(fit_pre_2)
-# 
-# 
-# fit_pre_3 <-
-#   df_multi %>% 
-#   mutate(teaching_experience = log(teaching_experience + 1)) %>% 
-#   filter(Phase == "Pre Teaching Phase") %$% 
-#   lm(slope ~ teaching_experience)
-# 
-# summary(fit_pre_3)
-# 
-# 
-# fit_pre_4 <-
-#   df_multi %>% 
-#   filter(Phase == "Pre Teaching Phase") %$% 
-#   lm(slope ~ confidence + disruption)
-# 
-# summary(fit_pre_4)
-# 
-# fit_pre_5 <-
-#   df_multi %>% 
-#   filter(Phase == "Pre Teaching Phase") %$% 
-#   lm(slope ~ confidence + disruption + teaching_experience)
-# 
-# summary(fit_pre_5)
-# 
-# 
-# stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
-#                      type = "html",
-#                      caption = "Pre Teaching Phase",
-#                      dep.var.labels = "Slope",
-#                      # order = c(1, 2, 3),
-#                      # covariate.labels = c("Disruption Factor",
-#                      #                      "Confidence Factor",
-#                      #                      "Teaching Experience"),
-#                      keep.stat = c("n","rsq","adj.rsq")
-#                      )
-
-# fit_pre_3$model %>%
-#   mutate(fitted.values = fit_pre_3$fitted.values) %>% 
-#   ggplot(mapping = aes(x = teaching_experience,
-#                        y = slope
-#                        )
-#          ) +
-#   geom_point(mapping = aes(group = posneg)) +
-#           geom_line(mapping = aes(y = fitted.values,
-#                                   group = posneg)) +
-#   geom_smooth(method = "lm",
-#               se = F,
-#               linetype = "dashed") +
-#         # geom_point(alpha = 0.5,
-#         #            size = 0.5) +
-#         theme_apa()
+fit_pre_2 <-
+  df_multi %>% 
+  filter(Phase == "Pre Teaching Phase") %$% 
+  lm(slope ~ teaching_experience + disruption_factor)
+
+summary(fit_pre_2)
+
+summary(fit_pre_1)$r.squared - summary(fit_pre_2)$r.squared
+
+fit_pre_3 <-
+  df_multi %>% 
+  mutate(teaching_experience = log(teaching_experience + 1)) %>% 
+  filter(Phase == "Pre Teaching Phase") %$% 
+  lm(slope ~ teaching_experience + confidence_factor)
+
+summary(fit_pre_3)
+
+summary(fit_pre_1)$r.squared - summary(fit_pre_2)$r.squared - summary(fit_pre_3)$r.squared
+
+fit_pre_4 <-
+  df_multi %>% 
+  filter(Phase == "Pre Teaching Phase") %$% 
+  lm(slope ~ teaching_experience + confidence + disruption)
+
+summary(fit_pre_4)
+
+stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
+                     type = "html",
+                     caption = "Pre Teaching Phase",
+                     dep.var.labels = "Slope",
+                     # order = c(1, 2, 3),
+                     # covariate.labels = c("Disruption Factor",
+                     #                      "Confidence Factor",
+                     #                      "Teaching Experience"),
+                     keep.stat = c("n","rsq","adj.rsq")
+                     )
+
+fit_pre_3$model %>%
+  mutate(fitted.values = fit_pre_3$fitted.values) %>% 
+  ggplot(mapping = aes(x = teaching_experience,
+                       y = slope
+                       )
+         ) +
+  geom_point(mapping = aes(group = posneg)) +
+          geom_line(mapping = aes(y = fitted.values,
+                                  group = posneg)) +
+  geom_smooth(method = "lm",
+              se = F,
+              linetype = "dashed") +
+        # geom_point(alpha = 0.5,
+        #            size = 0.5) +
+        theme_apa()
 

### 2023-12-01 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
fiiitbiiiiitttttttt

@@
       tidyverse,
-      ggplot2,
-      apaTables)
+      ggplot2)
 
@@
   group_by(ID) %>% 
-  dplyr::summarize(mean_heart = mean(heart_rate),
+  dplyr::summarise(mean_heart = mean(heart_rate),
             sd_heart = sd(heart_rate)) %>%
@@
   group_by(Phase) %>%
-  dplyr::summarize(
+  dplyr::summarise(
     mean_slope = mean(slope),
@@
   group_by(ID, time_span) %>% 
-  summarize(mean_heart_rate = mean(heart_rate_std)) %>% 
+  summarise(mean_heart_rate = mean(heart_rate_std)) %>% 
   ungroup()
@@
   group_by(id, Phase) %>% 
-  summarize(mean_slope = mean(slope)) %>% 
+  summarise(mean_slope = mean(slope)) %>% 
   ungroup()
@@
   group_by(ID, time_span) %>% 
-  summarize(disruption_factor = mean(disruption_factor,
+  summarise(disruption_factor = mean(disruption_factor,
                                      na.rm = T),
@@
   main %>% 
-  select("ID",
+  dplyr::select("ID",
          "disruption_factor",
@@
   group_by(ID) %>% 
-  summarize(disruption_factor = mean(disruption_factor, na.rm = T),
+  summarise(disruption_factor = mean(disruption_factor, na.rm = T),
             confidence_factor = mean(confidence_factor, na.rm = T),
@@
          ) %>%
-  select("id",
+  dplyr::select("id",
          "disruption_factor",
@@
 
-summary(regr_post1)
-summary(regr_post2)
-summary(regr_post3)
-summary(regr_post4)
-
-summary(regr_end1)$r.squared - summary(regr_end2)$r.squared - summary(regr_end3)$r.squared - summary(regr_end4)$r.squared
+summary(regr_interview1)
+summary(regr_interview2)
+summary(regr_interview3)
+summary(regr_interview4)
+
+summary(regr_teaching2)$r.squared - summary(regr_teaching1)$r.squared
+
+- summary(regr_end3)$r.squared - summary(regr_end4)$r.squared
 
@@
   scale_x_continuous(expand = c(0.01,0)) + 
-  labs(x = "Time (in minutes)",
+  labs(x = "Time (in Minutes)",
        #y = "Heart Rate (in Beats per Minute)",
@@
   group_by(ID) %>% 
-  summarize(disruption = mean(disruption_factor, na.rm = T),
+  summarise(disruption = mean(disruption_factor, na.rm = T),
             confidence = mean(confidence_factor, na.rm = T),

### 2023-12-01 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fiiitbiiiiitttttttt

@@
       tidyverse,
-      ggplot2,
-      apaTables,
-      rockchalk)
+      ggplot2)
 
@@
 main %>% 
-  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  dplyr::select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
   distinct() %>% 
   group_by(ID) %>% 
-  # summarize(disruption_factor = mean(disruption_factor, na.rm = T),
+  # summarise(disruption_factor = mean(disruption_factor, na.rm = T),
   #           confidence_factor = mean(confidence_factor, na.rm = T),

### 2023-12-02 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
loess_plot und mean_plot angepasst

@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("(1) Pre-teaching Interval","(2) Teaching Interval","(3) Post-teaching Interval","(4) Interview Interval","(5) End Interval"))) %>% 
+                            labels = c("(1) Pre-teaching\nInterval","(2) Teaching\nInterval","(3) Post-teaching\nInterval","(4) Interview\nInterval","(5) End\nInterval"))) %>% 
   distinct() %>%
@@
              linetype = "dashed") +
-  labs(subtitle = "1% Confidence Intervall",
+  labs(subtitle = "99% Confidence Intervall",
        x = "") +
@@
         axis.title.y = element_blank())
+
+ggsave(filename = "plots_publication/mean_plot_new.png",
+       width = 22,
+       height = 12,
+       units = "cm")
 
@@
 ```
+# Plot alternative
+
+```{r}
+
+df_heart_rate <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate") %>% 
+  distinct() %>% 
+  mutate(type = "a. Heart Rate (in beats per minute)")
+
+df_heart_rate_std <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate_std") %>% 
+  distinct() %>% 
+  transmute(ID,
+            time,
+            type = "b. Heart Rate (standardized)",
+            heart_rate = heart_rate_std)
+
+df_heart_rate %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  geom_smooth(se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.99) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0.01,0)) + 
+ labs(x = "",
+      y = "",
+      ) +
+  theme_apa() + 
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y") -> loess_hr
+
+df_heart_rate_std %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  geom_smooth(se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.99) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0.01,0)) +
+  scale_y_continuous(expand = c(0, 0.25)) +
+  labs(x = "",
+       y = "",
+       ) +
+  theme_apa() + 
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y") -> loess_hr_std
+
+loess_comp <- grid.arrange(loess_hr, loess_hr_std,
+                           ncol = 2)
+
+loess_comp <- annotate_figure(p = loess_comp,
+                              bottom = 'Time (in Minutes)')
+
+ggsave(loess_comp,
+       filename = "plots_publication/loess_plot_std_unstd_new.png",
+       width = 17,
+       height = 12,
+       units = "cm")
+```
 
@@
                      limits=c(-1, 1)) + 
-  scale_x_continuous(breaks = seq(0, 10, 2)) +
+ # scale_x_continuous(breaks = seq(0, 10, 2)) +
   labs(x = "Time (in Minutes)",

### 2023-12-05 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
Nur wg. KI's rumprobiert

@@
             z_sd = sd(heart_rate_std),
-            z_t = qt(p = 0.01 / 2,      # 0.01 KI
+            z_t = qt(p = 0.01 / 2,      # 0.99 KI
                df = n() - 1,

### 2023-12-05 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
fitbiiiiiit

--- 2023-12-01 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
@@
              linetype = "dashed") +
-  labs(subtitle = "1% Confidence Intervall",
+  scale_y_continuous(expand = c(0, 0.3)
+                     ) +
+  labs(subtitle = "99% Confidence Intervall",
        x = "") +
@@
               colour = "black",
-              level = 0.99) +
+              level = 0.95) +
   scale_color_viridis_d(option = "A",
@@
        caption = expression(paste(italic("Note: "),
-                                  "The shadow around the line represents the 99% confidence interval."
+                                  "The shadow around the line represents the 95% confidence interval."
                                   )
@@
 
-# Plot
-
+# Plot (alter Loess-Ploss)
 ```{r}
@@
 
+# Plot neu (doppelter Loess-Plot)
+```{r}
+
+df_heart_rate <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate") %>% 
+  distinct() %>% 
+  mutate(type = "a. Heart Rate (in Beats per Minute)")
+
+df_heart_rate_std <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate_std") %>% 
+  distinct() %>% 
+  transmute(ID,
+            time,
+            type = "b. Heart Rate (Standardized)",
+            heart_rate = heart_rate_std)
+
+df_heart_rate %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  geom_smooth(se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.95) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0.01,0)) + 
+ labs(x = "",
+      y = "",
+      ) +
+  theme_apa() + 
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y") -> loess_hr
+
+df_heart_rate_std %>% 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  geom_smooth(se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.95) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0.01,0)) +
+  scale_y_continuous(expand = c(0, 0.25)) +
+  labs(x = "",
+       y = "",
+       ) +
+  theme_apa() + 
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y") -> loess_hr_std
+
+loess_comp <- grid.arrange(loess_hr, loess_hr_std,
+                           ncol = 2)
+
+loess_comp <- annotate_figure(p = loess_comp,
+                              bottom = 'Time (in Minutes)')
+
+ggsave(loess_comp,
+       filename = "plots_publication/loess_plot_std_unstd_new.png",
+       width = 17,
+       height = 12,
+       units = "cm")
+```
+
 ```{r}
@@
             z_sd = sd(heart_rate_std),
-            z_t = qt(p = 0.01 / 2,      # 0.01 KI
+            z_t = qt(p = 0.05 / 2,      # 0.01 KI
                df = n() - 1,
@@
              linetype = "dashed") +
-  ylim(-1, 1) + 
   scale_y_continuous(breaks=seq(-1, 1, 0.5), 
-                     limits=c(-1, 1)) + 
-  scale_x_continuous(breaks = seq(0, 10, 2)) +
+                     limits=c(-1.1, 1)) + 
   labs(x = "Time (in Minutes)",

### 2024-01-29 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd

@@
   main %>% 
-  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
+  dplyr::select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
   distinct() %>% 
@@
   filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ teaching_experience + confidence + disruption)
+  lm(slope ~ teaching_experience + confidence_factor + disruption_factor)
 

### 2024-03-11 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
et

@@
 # prepare data (selected from questionnaire data)
-demo.data <- readxl::read_xlsx("./data/data_empschul_labor_lehrperson.xlsx")
+demo.data <- readxl::read_xlsx("./data/demografic_data_empschul_labor_lehrperson.xlsx")
 
@@
                                   LI04_01,
-                                  LI06_05)
+                                  LI06_05) %>%
+  filter(!LI06_05 %in% c(201,
+                         242,
+                         141,
+                         142))
 

### 2024-03-11 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
et

@@
       RColorBrewer,
-      cowplot)
+      cowplot,
+      svglite)
 
@@
   select (Group,
+          Participant,
           starts_with("Total_duration_of_fixations"),
@@
   transmute(Group = Group,
+            Participant = Participant,
             Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
@@
                                          digits = 0),
-         Group = as_factor(Group)) -> df_aoi_sum
+         Group = as_factor(Group)) %>% 
+  drop_na() -> df_aoi_sum
 
@@
   labs(x ="",
-       y = "Number") +
+       y = "Anzahl Fixationen") +
   scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("Number of Fixations on all AOIs") +
+  scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
+  ggtitle("Anzahl der Fixationen in allen AOIs") +
   theme_cowplot() +
@@
   labs(x ="",
-       y = "Number") + 
+       y = "Anzahl Fixationen") + 
   scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("Number of Fixations\non AOI `Disruptive Person`") +
+  ggtitle("Anzahl Fixationen AOI\n`Störperson`") +
+    scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
   theme_cowplot() +
@@
   labs(x ="",
-       y = "Number") + 
+       y = "Anzahl Fixationen") + 
   scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("Number of Fixations\non AOI `Students`") +
+  ggtitle("Anzahl Fixationen AOI\n`Schüler:innen`") +
   theme_cowplot() +
+  scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
   theme(legend.position="none",

### 2024-03-12 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
et

@@
   labs(x ="",
-       y = "Milliseconds") + 
+       y = "Millisekunden") + 
   scale_fill_brewer(palette  = "RdBu") + 
-  ggtitle("Average Duration of Fixations on all AOIs") +
+  scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
+  ggtitle("Durchschnittliche Fixationsdauer in allen AOIs") +
   theme_cowplot() +
@@
   labs(x ="",
-       y = "Milliseconds") + 
+       y = "Millisekunden") + 
   scale_fill_brewer(palette  = "RdBu") + 
-  ggtitle("Average Duration of Fixations\non AOI `Disruptive Person`") +
+  scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
+  ggtitle("Ø Fixationsdauer AOI\n`Störperson`") +
   theme_cowplot() +
@@
   labs(x ="",
-       y = "Milliseconds") + 
+       y = "Millisekunden") + 
   scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("Average Duration of Fixations\non AOI `Students`") +
+  scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
+  ggtitle("Ø Fixationsdauer AOI\n `Schüler:innen`") +
   theme_cowplot() +
@@
   labs(x ="",
-       y = "Seconds") + 
+       y = "Sekunden") + 
   scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Time to first fixation on all AOIs") +
+  scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
+  ggtitle("Zeit bis zur ersten Fixation in allen AOIs") +
   theme_cowplot() +
@@
   labs(x ="",
-       y = "Seconds") + 
+       y = "Sekunden") + 
   scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Time to First Fixation\non AOI `Disruptive Person`") +
+  scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
+  ggtitle("Zeit bis zur ersten Fixation\nAOI `Störperson`") +
   theme_cowplot() +
@@
   labs(x ="",
-       y = "Seconds") + 
+       y = "Sekunden") + 
   scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("Time to First Fixation\non AOI `Students`") +
+  scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
+  ggtitle("Zeit bis zur ersten Fixation\nAOI `Schüler:innen`") +
   theme_cowplot() +
@@
 
-# TIME TO FIRST FIXATIONS on all AOIs 
+# TIME TO FIRST FIXATIONS on AOI "Students"
 # t-test for expertise differences
 t.test(x = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Expert"],
-       y = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Novice"])
-
-# TIME TO FIRST FIXATIONS on all AOIs 
+       y = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Novice"],
+       var.equal = TRUE)
+
+# TIME TO FIRST FIXATIONS on AOI "Students" 
 # effect size for expertise differences
-d_time_all <- CohenD(x = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Expert"],
+d_time_stud <- CohenD(x = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Expert"],
                     y = df_ttff_stud$Stud_time_fixation_sec[df_ttff_stud$Group == "Novice"],

### 2024-04-15 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

@@
       tidyverse,
-      ggplot2)
+      ggplot2,
+      lavaan,
+      lm.beta)
 
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("(1) Pre-teaching\nphase","(2) Teaching\nphase","(3) Post-teaching\nphase","(4) Interview\nphase","(5) End\nphase"))) %>% 
+                            labels = c("Pre-teaching\nphase","Teaching\nphase","Post-teaching\nphase","Interview\nphase","End\nphase"))) %>% 
   distinct() %>% 
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("(1) Pre-teaching Interval","(2) Teaching Interval","(3) Post-teaching Interval","(4) Interview Interval","(5) End Interval"))) %>% 
+                            labels = c("Pre-teaching Interval","Teaching Interval","Post-teaching Interval","Interview Interval","End Interval"))) %>% 
   distinct() %>%
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("(1) Pre-Teaching\nInteval","(2) Teaching\nInterval","(3) Post-Teaching\nInterval","(4) Interview\nInterval","(5) End\nInterval")
+                            labels = c("Pre-Teaching\nInterval","Teaching\nInterval","Post-Teaching\nInterval","Interview\nInterval","End\nInterval")
                             ),
@@
 
+# ## using lavaan package to get std. regression coefficients 
+# MLRModel <- 'heart_rate ~ teaching_experience
+#              heart_rate ~ 1'
+# 
+# output <- sem(model = MLRModel, data = data_regression_mean)
+# summary(output, standardized = TRUE)
+
+## loop for regression model
 for (i in unique(data_regression_mean$time_span)) {
@@
     lm(heart_rate ~ teaching_experience,
-    data = cache)
+    data = cache) %>% 
+    lm.beta()
 
@@
     lm(heart_rate ~ teaching_experience + disruption_factor,
-    data = cache)
+    data = cache) %>% 
+    lm.beta()
 
@@
     lm(heart_rate ~ teaching_experience + confidence_factor,
-    data = cache)
+    data = cache) %>% 
+    lm.beta()
 
@@
     lm(heart_rate ~ teaching_experience + disruption_factor + confidence_factor,
-    data = cache)
+    data = cache) %>% 
+    lm.beta()
 
@@
 
-summary(regr_teaching1)
-summary(regr_teaching2)
-summary(regr_teaching3)
-summary(regr_teaching4)
+summary(regr_end1)
+summary(regr_end2)
+summary(regr_end3)
+summary(regr_post4)
 
@@
 main %>% 
-  dplyr::select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
-  distinct() %>% 
-  group_by(ID) %>% 
-  # summarise(disruption_factor = mean(disruption_factor, na.rm = T),
-  #           confidence_factor = mean(confidence_factor, na.rm = T),
-  #           teaching_experience) %>% 
-  transmute(id = as.character(ID),
-            disruption_factor = mean(disruption_factor, na.rm = T),
-            confidence_factor = mean(confidence_factor, na.rm = T),
-            teaching_experience) %>% 
-  ungroup() %>% 
-  distinct() %>% 
-  right_join(x = .,
-            y = fix_models,
-            by = "id") -> data_regression_slope
-
-for (i in unique(data_regression_slope$Phase)) {
+  group_by(ID, time_span) %>% 
+  filter(! time_span %in% "overall") %>% 
+  mutate(time_span = factor(time_span,
+                            levels = c("end","interview","post","preparation","teaching"),
+                            labels = c("preparation","teaching","post","interview","end")
+                           )
+         ) %>%
+  rename(id = ID) %>% 
+  summarise(disruption_factor = mean(disruption_factor,
+                                     na.rm = T),
+            confidence_factor = mean(confidence_factor,
+                                     na.rm = T),
+            teaching_experience = mean(teaching_experience),
+            heart_rate = mean(heart_rate_std)
+            ) -> df_slope
+
+fix_models %>%
+  mutate(id = as_factor(id),
+         time_span = factor(Phase,
+                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase"),
+                           labels = c("preparation","teaching","post","interview","end")
+                           )
+         ) %>%
+    group_by(id, time_span) %>% 
+    summarise(slope = mean(slope)) %>% 
+  ungroup() -> fix_models_slope
+
+merge(df_slope,
+      fix_models_slope,
+      by=c("id", "time_span")) -> data_regression_slope
+
+for (i in unique(data_regression_slope$time_span)) {
 
   cache <- data_regression_slope %>% 
-    filter(Phase == i)
+    filter(time_span == i)
 
@@
     lm(slope ~ teaching_experience,
-    data = cache)
+    data = cache) %>% 
+    lm.beta()
 
@@
     lm(slope ~ teaching_experience + disruption_factor,
-    data = cache)
+    data = cache) %>% 
+    lm.beta()
 
@@
     lm(slope ~ teaching_experience + confidence_factor,
-    data = cache)
+    data = cache) %>% 
+    lm.beta()
 
@@
     lm(slope ~ teaching_experience + disruption_factor + confidence_factor,
-    data = cache)
+    data = cache) %>% 
+    lm.beta()
 
@@
 
-summary(regr_preparation1)
-summary(regr_preparation2)
-summary(regr_preparation3)
-summary(regr_preparation4)
+summary(regr_end1)
+summary(regr_end2)
+summary(regr_end3)
+summary(regr_end4)
 
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("(1) Pre-teaching\nInterval","(2) Teaching\nInterval","(3) Post-teaching\nInterval","(4) Interview\nInterval","(5) End\nInterval"))) %>% 
+                            labels = c("Pre-teaching\nInterval","Teaching\nInterval","Post-teaching\nInterval","Interview\nInterval","End\nInterval"))) %>% 
   distinct() %>%

### 2024-04-17 02_paper/02_study/02_fitbit paper/Submission/FitBit_submission.Rmd
Neuer Ordner 'FitBit_submission' mit Markdown_file und allem was dazu gehört

---
title: Title here
subtitle: Do you have a subtitle? If so, write it here
titlerunning: Short form of title (if too long for head)
authorrunning:
  Short form of author list if too long for running head
thanks: |
  Grants or other notes about the article that should go
  on the front page should be placed here. General
  acknowledgments should be placed at the end of the article.
authors:
  - name: Author 1
    address: Department of YYY, University of XXX
    email: abc@def
  - name: Author 2
    address: Department of ZZZ, University of WWW
    email: djf@wef
keywords:
  - key
  - dictionary
  - word
MSC:
  - MSC code 1
  - MSC code 2    
abstract: |
  The text of your abstract.  150 -- 250 words.
bibliography: r-references.bib
csl: computers-and-education.csl
output: rticles::elsevier_article
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 8, fig.height = 4, cache = TRUE)
```

# Introduction

In education, there’s interest in identifying reliable indicators for teacher stress and burnout [@fisher2011; @ junker2021]. Previous research often relied on self-report questionnaires [@chaplain2008; @liu2020], which may be prone to biases like social desirability [@razavi2001self] or recall errors [@van2016accuracy]. To overcome these limitations, ambulatory assessment methods are recommended [@trull2013ambulatory; @wettstein2020ambulatory], such as measuring physiological parameters like heart rate (HR), offering objective insights into teachers’ stress levels without disrupting their teaching [@donker2018; @runge2020].

Current studies on teachers’ HR in teaching settings often rely on expensive and invasive electrocardiographs [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021; @huang2022class], showing that teacher-centered activities and common stressors lead to increased HR. However, using affordable and non-invasive instruments like wrist-worn fitness trackers [@ferguson2015] could enhance HR recording in educational contexts. Unlike clinical devices, fitness trackers could offer continuous and less intrusive data collection over time [@godfrey2018z], aligning with the increasing popularity and acceptance of wearables among the general population [@peng2022acceptance]. These devices, equipped with biosensors, provide users with physiological and behavioral data, offering an accessible means for monitoring physical activity and health in daily life.

It can be assumed that teachers also wear personal, private fitness trackers, generating recordings of physiological data that could be a very interesting resource for research on teacher stress. While the use of wearable technology in the field has been explored in various domains [@hughes2023wearable; @ adesida2019exploring; helmer2009smart], research is sparse in educational contexts [@de2017towards]. Although some studies investigated how wearables can help teachers monitor student activity [@quintana2016keeping], there is a notable research gap regarding teachers’ use of wrist-worn wearables.
Given the high stress levels in the teaching profession [@johnson2005experience], fitness trackers could be a valuable tool for analyzing HR and the factors contributing to stress. One of the reasons for teachers’ augmented stress is that they are confronted with a multitude of demands in their everyday work, some of which exceed their resources and therefore make it difficult to cope with immediate stressors such as classroom disruptions [@montgomery2005meta]. However, the extent of the strain depends on the subjective appraisal of a stressor, which involves considerations about available resources to deal with it [@kyriacou2001]. It is, therefore, particularly important for teachers to have sufficient personal and professional resources at their disposal [@cramer2018belastung]. Classroom disruptions, for example, are one of the major stressors in teachers’ daily work [@boyle1995structural; @aloe2014multivariate] and professional knowledge about effective classroom management reduces the risk of teacher stress [@klusmann2012berufliche]. Teachers’ characteristics such as professional experience in turn have an impact on the development of classroom management skills and thus on the appraisal processes, as these skills develop during professional experience [@ophardt2017klassenmanagement; @wolff2015keeping].

To better understand how stressors like classroom disruptions affect teachers and their stress responses, data from wrist-worn fitness trackers could be used to monitor physiological parameters before, during, and after teaching sessions [@wettstein2021]. This study explored the use of wrist-based fitness trackers as a tool to monitor teachers’ stress during different phases of a micro-teaching unit during which teachers had to deal with classroom disruptions. Physiological data were triangulated with teachers’ appraisal of classroom disruptions, and their teaching experience. The physiological indicator employed in this study was teachers’ HR, which can be readily recorded by any fitness tracker. Teachers’ use of wrist-worn fitness trackers in educational research holds transformative potential as obtained fine-grained data and underscores the critical need to monitor teachers’ health as they navigate the stressful landscape of the classroom.

## Fitness Trackers as a Method to Assess HR as an Indicator of Stress

Wearables, defined as electronic devices worn directly on the body or integrated into clothing or accessories, serve as versatile solutions [@godfrey2018z], gathering data like location, movements, and vital signs [@cheng2017underlying]. Fitness trackers, a popular wearable type [@park2020user], offer insights into physical activity and cardiovascular health, supporting personalized fitness goals [@nuss2021effects] and stress management [@hao2018chrv]. Their affordability and ease of use make them ideal not only for various domains including healthcare, entertainment, and fitness [sinha2019taxonomy] but also in education as they offer added benefits for formal and informal learning environments for both students and teachers [@de2017towards]. Yet, few studies focus on their significance for teachers.

One important health parameter assessed by nearly all wrist wearables is HR [@scalise2018wearables]. HR indicates the number of heartbeats within one minute and is typically expressed as beats per minute (BPM) [@hottenrott2007]. At rest, the average HR of adults typically ranges from 60 to 80 BPM [@sammito2015guideline]. HR can be detected and measured using sensors based on electrocardiogram (ECG) or phonocardiogram (PCG) [@mukhopadhyay2017wearable]. Another uncomplicated and inexpensive technique to measure HR via fitness trackers is photoplethysmography (PPG) [@castaneda2018review]. This optical method assesses HR by flashing green or red lights to measure changes in blood volume [@allen2007photoplethysmography].  
Physiologically, HR is regulated and influenced on short-time intervals by the sympathetic and the parasympathetic nervous system [@pham2021]. An increase in the activity of the sympathetic system results in HR being speeded up (“fight or flight”) [@taelman2009influence]. In contrast, increased activity of the parasympathetic has the effect of slowing down the HR (“rest and digest”) [@battipaglia2015]. Therefore, an increase in HR can be regarded as an indicator of increasing stress, and a decrease as an indicator of decreasing stress [@kyriacou1978].

## Teacher Stress and Important Resources

The teaching profession is one of the most stressful professions compared to other occupational groups, facing a variety of stressors during everyday work [@smith2000; @herman2020; @schult2014belastet]. According to @kyriacou1978, teacher stress can be defined as a negative affective response, often accompanied by physiological changes such as increased HR, triggered by job-related demands and perceived as threatening to one’s self-esteem or well-being. Coping mechanisms help to reduce the perceived threat.

This definition of teacher stress is based on the transactional stress model by Lazarus and colleagues [@lazarus1981stressbezogene; @lazarus1984stress], which was modified and tailored to the teaching-learning environment by @kyriacou1978.

In general, the transactional stress model [@lazarus1990theory] highlights the interaction between an individual and the environment, whereby stress refers to any event that exceeds a person’s adaptive resources. It has been shown that there are important connections between stressors and resources experienced by teachers on the one hand, and stress-induced health issues on the other hand [@krause2013messung]. As we are interested in how specific classroom events affect teacher stress, we adapted the transactional stress model to that type of situation, based on a representation of the model first proposed by [van2006stress]; this working model is depicted in Fig. 1.

```{=latex}
\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the author)}
  \label{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the author)}
\end{figure}
```

When potential stressors (e.g., classroom disruptions) occur during teaching (1), teachers subjectively appraise how disruptive the event is (2). If potential stressors are judged as threatening, i.e., as actual stressors (3), teachers consider whether they have sufficient resources for coping with the stressor (4). Based on this evaluation of resources and their characteristics such as professional experience, teachers try to manage classroom disruptions, by utilizing classroom management strategies (5). In cases where coping fails, stress ensues, often accompanied by physiological reactions like increased HR (6). Following resource appraisal and coping outcomes, the stressor is re-evaluated (7).

The appraisal processes of resources play a crucial role as teachers’ assessments of resources and coping mechanisms, both internal (e.g., classroom management skills) and external (e.g., supportive colleagues), significantly impact their stress levels. When resources are lacking and coping fails, negative consequences like burnout and high turnover can arise [@jalongo2006; @unterbrink2007; @aloe2014]. This highlights the importance of teachers’ appraisal of their professional competencies, including their ability to manage classroom disruptions effectively [@klieme2008concept; @konig2016teacher].

As shown in Fig. 1, both primary and secondary appraisals are influenced by teachers’ characteristics, e.g., their professional experience, shaping their classroom management skills. As experience grows, teachers develop cognitive scripts for managing classroom events resulting in more complex classroom management skills [@wolff2021classroom]. Especially beginning teachers face considerable stress and often feel overwhelmed by the demands of teaching [@ophardt2017klassenmanagement; @wolff2015keeping; @ klusmann2012berufliche], with many leaving the profession within the first five years [@ingersoll2003]. Research shows less experienced teachers are more susceptible to burnout, underscoring the importance of experience and job satisfaction in predicting teacher stress [@fisher2011].

## HR in Teaching-Learning Contexts

ECG studies have revealed that HR can be used to map changes in HR during teaching onto stressors experienced by teachers. For example, HR increased during teacher-centered activities when teachers had to take a leading position in the student-teacher interaction [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021]. @sperka1995 for example recorded the HR of 16 pre-service teachers during their first lesson. The results showed significantly increased psychophysiological activation in terms of an increased HR during teaching. The activation effect was particularly prominent at the beginning of the lesson and decreased over the course of the lesson. The authors interpret this result as showing how pre-service teachers’ active coping processes, i.e., the active management of the interaction with the students, helped the teachers regulate their HR downwards. Other ECG studies identified typical stressors predicting increased HR values, such as class size [@huang2022class], or low student engagement and motivation [@junker2021]. For example, @junker2021 recorded the HR of 40 teachers using an ambulatory monitoring system during a real classroom lesson. They provided evidence that teacher stress caused by stressors such as low student engagement, i.e., students displaying a lack of motivation or limited interest in their tasks or classroom activities, or teacher-centered activities, i.e., classroom activities primarily focused on the teacher’s actions., leads to an increase in HR.

In addition to ECG studies, there are a few studies that used wrist-worn fitness trackers to investigate HR trends in teaching-learning situations [@Darnell2019; @chalmers2021]. @Darnell2019 for example measured the HR of 15 medical college students using wrist-worn devices during lectures. The analysis revealed a constant decrease in HR from the beginning to the end of a lecture, whereas the HR peak was reached during active learning sessions. @chalmers2021 examined the usability of the average HR, measured with a Fitbit   fitness tracker, to identify physiological changes during stress-inducing tasks in a study with a total of 60 participants. The average HR increased significantly between the resting and stress phases. Even though the participants in these studies were learners, not teachers, the results are relevant to the study of teacher stress using wearable devices, because the studies showed that a) HR can be effectively recorded using fitness trackers during a whole learning unit, and b) HR changes are in line with the occurrence of activating or stress-inducing tasks.

So far, to the best of our knowledge, only one study has directly assessed teachers’ HR using a wrist-worn fitness tracker during teaching : @runge2020 used a Fitbit fitness tracker to assess HR as an indicator of stress in N=4 teachers. They used the fitness trackers’ recordings to create a profile for each teacher (to differentiate between teachers reporting higher or lower levels of stress  .) In particular, it was found that the combination of a high number of steps, a high HR, and short sleep was an indicator of stress. It should be noted that the generalizability of the results is limited due to the small sample size.

In summary, previous studies have revealed that teachers’ (and students’) HR changes, depending on the activity and stressors they experience, whereby teacher-centered phases  , in particular, led to an increase in HR [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021]. Furthermore, it could be shown that HR as an indicator of stress can be assessed using low-cost, non-intrusive fitness trackers and that HR increases in activating phases and even before stress occurs [@Darnell2019; @chalmers2021]. However, studies collecting data from teacher-worn fitness trackers in a large enough sample to explore links with factors such as subjective stressor appraisal, or effects of teaching experience, are still lacking. Our study aims to close this research gap.

## Present Study

The data analyzed for the present study were obtained from teachers and student teachers who participated in a lab study, as part of a larger project targeting the development of classroom management in teachers.

As part of the larger project, participants came to the lab individually, and each taught a 15-minute, self-prepared micro-teaching unit to a “class” of three actors (trained student assistants). These actors performed nine, possibly disruptive, classroom events. The actors received standardized instructions on a screen (only visible to them, not to the participant) to perform a classroom event every one and a half minutes, and they performed the same scripted disruptions for all participants. While teaching, participants wore eye-tracking glasses, and additionally, their lessons were recorded by cameras.

The micro-teaching unit, with its unfamiliar setting and the scripted disruptions of participants’ teaching flow, was potentially stressful. Thus, we were particularly interested in the development of participants’ HR before, during, and after this micro-teaching unit. We recorded HR data in five phases, with a total duration of approximately two hours: In the *pre-teaching phase*, participants were welcomed, prepared for the following micro-teaching unit, and familiarized with the setting. In the *teaching phase*, participants taught the micro-teaching unit and experienced the classroom disruptions. In the *post-teaching phase*, participants answered several questionnaires in a comfortable seated position. Next, in the *interview phase*, they watched the video of their 15-minute unit, rated the disruptive classroom events, and answered open questions. Finally, in the *end phase*, participants answered another questionnaire. These conditions were identical for all participants. During the entire study, participants wore a fitness tracker on their wrist.

The goals of the present study were twofold:

(1)	The first research goal was to investigate whether HR measures assessed by wrist-based fitness trackers are a suitable and effective method for mapping teachers’ HR over the course of a five-phase lab study, including the time before, during, and after a potentially stressful micro-teaching unit.

First, we expected the participants to show an initial increase in their HR, followed by a peak during the teaching phase and a decrease for the remaining phases. In addition, we examined whether z-standardization of the participants’ mean HR could serve as a useful method to account for individual differences in baseline HR. We expected to observe the same trends in both standardized and non-standardized mean HR values.

Second, five representative 10-minute intervals were selected from the five phases (see section ##Measures for a more detailed description of the intervals), which served as the basis for the data analysis for our hypothesis: pre-teaching interval ($I_1$), teaching interval ($I_2$), post-teaching interval ($I_3$), interview interval ($I_4$), end interval ($I_5$).  We examined the levels of and the changes in HR during these intervals. We assumed the highest HR level in the teaching interval ($I_2$) and lower levels in all other intervals (**Hypothesis 1a**). Further, we expected an increase in participants’ HR while they were preparing for teaching during the pre-teaching interval ($I_1$), and we expected a decrease in participants’ HR during all of the following intervals, because of habituating to ($I_2$) and recovering from ($I_3$-$I_5$) the stressful teaching phase (**Hypothesis 1b**).

(2)	The second research goal was to examine whether variance in HR measures could be explained by participants’ teaching experience (because, presumable, more experienced teachers might have better classroom management strategies, and thus better resources for coping), and/or by their self-reported subjective appraisals of classroom events (specifically, how disruptive it was, and how confident they felt in their coping).

We expected lower HR levels for teachers with more teaching experience, particularly during the teaching interval (**Hypothesis 2a**). We expected higher HR levels for teachers who felt more disrupted by the enacted classroom events, regardless of their teaching experience (**Hypotheses 2b**). At the same time, we expected lower HR levels for teachers who felt more confident in dealing with the events, regardless of teaching experience (**Hypothesis 2c**). Lastly, we hypothesized that each of the three predictors (teaching experience, disruption appraisal, confidence appraisal) uniquely contributes to explaining variance in teachers´ HR levels (**Hypothesis 2d**). In addition, we exploratively examined the same as for the HR levels again for the changes in HR.

# Method

## Participants

The sample consisted of $N$ = 84 pre- and in-service teachers from Germany, who were recruited via personal contact, email lists, and flyers. The data of three participants was lost due to failed data transmission, yielding an analysis sample of $n$ = 81 ($n$ = 52 women, $n$ = 29 men). Participants had a mean age of 30.95 years ($SD$ = 10.90; range: 19-60) and an average teaching experience of 5.64 years ($SD$ = 9.46; range: 0-37).

## Setting and Procedure

The study was carried out following the ethical standards and the approval of the University’s Institutional Review Board. All participants were informed in detail about the aims and intention of the study before testing. Participation was voluntary and only took place after written consent had been given. Participants were not rewarded in any way for participating in the study.

```{=latex}
\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{images/Timeline_ProVision_vertical.png}
  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
\end{figure}
```

Each participant came to the lab for a period of approximately two hours in total, and each underwent the same phases: *pre-teaching phase*, *teaching phase*, *post-teaching phase*, *interview phase*, and *end phase* (please refer to Fig. 2 for a timeline). In the *pre-teaching phase*, the experimenter welcomed the participants and helped them put on the fitness tracker. This was followed by a warm-up session to familiarize the participants with the laboratory setting and the class. This phase took about 10-15 minutes and participants spent this time mostly standing or slowly walking around. During the *teaching phase*, the participants held their self-prepared, micro-teaching  unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table ## in the supplementary material for an overview and categorization of all events; also see Fig## for a depiction of the laboratory setting of the micro-teaching unit).  In preparation for the 15-minute lesson, the topic and class level could be freely chosen by the teachers. The type of course was to be an introductory lesson and the desired social form required individual work or frontal teaching, without longer video sequences and movement of the actors.  The teaching unit lasted about 15-20 minutes. Participants spent this time mostly standing or slowly walking around. After having completed the micro-teaching unit, in the *post-teaching phase*, participants were seated at a desk and filled in questionnaires for approximately 10-15 minutes: a brief computer-based questionnaire assessing sociodemographic data (e.g., teaching experience, gender, studied school type, studied school subjects, extracurricular teaching activities), and a short knowledge test that is irrelevant to the present study. In the *interview phase*, the participants watched the video of their own teaching together with the experimenter. While doing so, they were given a Stimulated Recall Interview (SRI), in which the participants watched their recorded eye-tracking video of the lesson from the ego perspective, indicating the participants’ gaze point. The experimenter stopped the video each time one of the nine classroom events happened and asked a total of eight questions, five of which were open and three closed. We assessed – among other questions irrelevant to this study – with two closed questions the teachers’ subjective appraisal of the classroom events that took place during the *teaching phase* in terms of how subjectively disruptive they were (disruption appraisal) and how confident the participants felt dealing with them (confidence appraisal) with one item each. The interview lasted about 45-60 minutes and the participants’ position was seated. The *end phase* lasted about 10-15 minutes and participants answered in a seated position another questionnaire irrelevant to this study.

## Measures

### Heart Rate Data and Heart Rate Intervals

To measure the teachers’ HR, we used a wrist-based fitness tracker. The model was a Fitbit Charge 4. In line with the manufacturer's instructions [@fitbitnd], the device was attached a finger’s width above the participants’ nondominant hand’s wrist bone. The tracker works by flashing green LEDs hundreds of times per second, using light-sensitive photodiodes to catch the reflected light, and from that information calculating volume changes in the capillaries. From this, the tracker calculates how many times the heart beats per minute. HR measurements are generated at least every 15 seconds[^1]. The raw data that can be extracted from the tracker lists the time stamps of all measurements and the estimated HR in BPM for each time stamp.

The anonymous HR data was synced via Bluetooth to a commercial Fitbit account. Subsequently, the intraday second-by-second data was exported as a CSV file for each session using the open-source software PulseWatch (Ricci, n.d.), and linked to the participant. To account for individual differences in the baseline HR, we first z-standardized the BPM values from the unstandardized mean HRs.

Since we aimed to explore teachers’ HR between different strain phases, we aggregated HR over a 10-minute interval within each phase. Previous research has indicated that 10-minute intervals are a useful duration for analyzing PPG data [@lu2008can]. The intervals were selected based on the following rules: The pre-teaching interval ($I_1$) comprised the first 10 minutes after the fitness tracker had been put on. The teaching interval ($I_2$) started two minutes after the teacher had started the teaching unit. This interval was of the highest relevance to our study. We explicitly chose an early 10-minute interval within the teaching phase, as previous studies revealed that the beginning of a lesson is essential and demanding regarding teacher-student interaction [@donker2018quantitative; @claessens2017positive]. The post-teaching interval ($I_3$) started immediately after the end of the teaching unit. The interview interval ($I_4$) was defined as the mid-10 minutes between the end of the teaching unit and the time point when the fitness tracker was taken off so that all participants were being interviewed during this interval. The end interval ($I_5$) comprised the last 10 minutes before the fitness tracker was taken off.

[^1]: The fluctuations in the number of seconds in which the HR was measured are due to the participants' movements, meaning that the device could not measure the HR every second.

### Teaching Experience

The participants’ teaching experience was assessed as a part of sociodemographic data. Participants stated their work experience in years (excluding the traineeship year).

### Subjective appraisal of the classroom events and coping processes

The subjective disruption and confidence appraisals assessed in the SRI on an 11-point rating scale were averaged across the nine classroom events as we were not interested in individual classroom events, but only in the expected mean level of arousal during the *teaching phase*. Regarding the model (see Fig. 1), the disruption appraisal was used to assess the evaluation of the stressor (see Fig. 1, box 2). The confidence appraisal, in contrast, referred to the resources available for coping with the stressors (see Fig. 1, box 4).

## Data analysis

We conducted all analyses with R [@RStudio2020]. Graphics were created using ggplot2 (v3.3.3; Wickham, 2016).

**Research goal 1**. The first research goal included mapping teachers’ HR before, during, and following a micro-teaching unit in the course of a five-phase lab study.

Regarding the teachers’ HR trend, we displayed the HR trend over the course of the entire study. For z-standardization as a method to account for individual differences in the baseline HR, we visually compared unstandardized and standardized mean HR trends for the entire two-hours study. 
For testing Hypothesis 1a, which examined the HR levels in the different intervals, we initially conducted a one-way ANOVA with repeated measures as an omnibus test. The dependent variable comprised the standardized HR mean for each interval. To identify the highest HR level, we subsequently conducted t-tests with planned contrasts as post-hoc tests, accompanied by the effect size d [@cohen1988new]. Specifically, we tested the differences between the teaching interval ($I_2$) and the other four intervals. Note that mean HR was calculated at the subject level of $n$ = 81 participants (see Table 1), whereas the mean slope and mean intercept estimates are based on all values at all measurement time points (see Table 2).
For testing Hypothesis 1b, which examined the HR changes within each interval, we conducted a linear estimation of the increase or decrease in HR over time. To this end, we used fixed intercept fixed slope regression models [@gelman2006data] for each interval to estimate intercepts and linear slopes for all individuals which were then averaged across individuals[^2].

[^2]: Although this procedure does not account for nonmonotonic progressions in individual HR, a graphical evaluation revealed that the linear estimates corresponded well to the majority of the cases (see XX in the supplementary material).

**Research goal 2**. In addressing our second research goal, we examined the effects of teaching experience and subjective appraisal of disruptive classroom events on teachers’ HR levels during the five phases.

To test hypothesis 2a, we examined the effect of teaching experience on participants’ HR levels for each of the five intervals using linear regression models with teaching experience as the sole predictor. To test hypotheses 2b and 2c, we separately augmented the models by either teachers’ disruption appraisal (Hypothesis 2b) or confidence appraisal (Hypothesis 2c), while controlling for shared variance with teaching experience. HR levels were only predicted with the disruption and confidence appraisal after the teaching had taken place, i.e., for all the intervals following the pre-teaching interval (I1). To test hypothesis 2d, we examined the effects of all three predictors in one regression model. We repeated these steps to explore the effect of teaching experience and subjective appraisals on changes in teachers’ HR at each interval.

### 2024-04-17 02_paper/02_study/02_fitbit paper/Submission/FitBit_submission.tex
Neuer Ordner 'FitBit_submission' mit Markdown_file und allem was dazu gehört

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Title here},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\begin{frontmatter}

  \title{Title here}
      \cortext[cor1]{Corresponding author}

  \begin{abstract}
  The text of your abstract. 150 -- 250 words.
  \end{abstract}
    \begin{keyword}
    key \sep dictionary \sep 
    word
  \end{keyword}

 \end{frontmatter}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In education, there's interest in identifying reliable indicators for
teacher stress and burnout {[}\citet{fisher2011}; @ junker2021{]}.
Previous research often relied on self-report questionnaires
\citep{chaplain2008, liu2020}, which may be prone to biases like social
desirability \citep{razavi2001self} or recall errors
\citep{van2016accuracy}. To overcome these limitations, ambulatory
assessment methods are recommended
\citep{trull2013ambulatory, wettstein2020ambulatory}, such as measuring
physiological parameters like heart rate (HR), offering objective
insights into teachers' stress levels without disrupting their teaching
\citep{donker2018, runge2020}.

Current studies on teachers' HR in teaching settings often rely on
expensive and invasive electrocardiographs
\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021, huang2022class},
showing that teacher-centered activities and common stressors lead to
increased HR. However, using affordable and non-invasive instruments
like wrist-worn fitness trackers \citep{ferguson2015} could enhance HR
recording in educational contexts. Unlike clinical devices, fitness
trackers could offer continuous and less intrusive data collection over
time \citep{godfrey2018z}, aligning with the increasing popularity and
acceptance of wearables among the general population
\citep{peng2022acceptance}. These devices, equipped with biosensors,
provide users with physiological and behavioral data, offering an
accessible means for monitoring physical activity and health in daily
life.

It can be assumed that teachers also wear personal, private fitness
trackers, generating recordings of physiological data that could be a
very interesting resource for research on teacher stress. While the use
of wearable technology in the field has been explored in various domains
{[}\citet{hughes2023wearable}; @ adesida2019exploring;
helmer2009smart{]}, research is sparse in educational contexts
\citep{de2017towards}. Although some studies investigated how wearables
can help teachers monitor student activity \citep{quintana2016keeping},
there is a notable research gap regarding teachers' use of wrist-worn
wearables. Given the high stress levels in the teaching profession
\citep{johnson2005experience}, fitness trackers could be a valuable tool
for analyzing HR and the factors contributing to stress. One of the
reasons for teachers' augmented stress is that they are confronted with
a multitude of demands in their everyday work, some of which exceed
their resources and therefore make it difficult to cope with immediate
stressors such as classroom disruptions \citep{montgomery2005meta}.
However, the extent of the strain depends on the subjective appraisal of
a stressor, which involves considerations about available resources to
deal with it \citep{kyriacou2001}. It is, therefore, particularly
important for teachers to have sufficient personal and professional
resources at their disposal \citep{cramer2018belastung}. Classroom
disruptions, for example, are one of the major stressors in teachers'
daily work \citep{boyle1995structural, aloe2014multivariate} and
professional knowledge about effective classroom management reduces the
risk of teacher stress \citep{klusmann2012berufliche}. Teachers'
characteristics such as professional experience in turn have an impact
on the development of classroom management skills and thus on the
appraisal processes, as these skills develop during professional
experience \citep{ophardt2017klassenmanagement, wolff2015keeping}.

To better understand how stressors like classroom disruptions affect
teachers and their stress responses, data from wrist-worn fitness
trackers could be used to monitor physiological parameters before,
during, and after teaching sessions \citep{wettstein2021}. This study
explored the use of wrist-based fitness trackers as a tool to monitor
teachers' stress during different phases of a micro-teaching unit during
which teachers had to deal with classroom disruptions. Physiological
data were triangulated with teachers' appraisal of classroom
disruptions, and their teaching experience. The physiological indicator
employed in this study was teachers' HR, which can be readily recorded
by any fitness tracker. Teachers' use of wrist-worn fitness trackers in
educational research holds transformative potential as obtained
fine-grained data and underscores the critical need to monitor teachers'
health as they navigate the stressful landscape of the classroom.

\hypertarget{fitness-trackers-as-a-method-to-assess-hr-as-an-indicator-of-stress}{%
\subsection{Fitness Trackers as a Method to Assess HR as an Indicator of
Stress}\label{fitness-trackers-as-a-method-to-assess-hr-as-an-indicator-of-stress}}

Wearables, defined as electronic devices worn directly on the body or
integrated into clothing or accessories, serve as versatile solutions
\citep{godfrey2018z}, gathering data like location, movements, and vital
signs \citep{cheng2017underlying}. Fitness trackers, a popular wearable
type \citep{park2020user}, offer insights into physical activity and
cardiovascular health, supporting personalized fitness goals
\citep{nuss2021effects} and stress management \citep{hao2018chrv}. Their
affordability and ease of use make them ideal not only for various
domains including healthcare, entertainment, and fitness
{[}sinha2019taxonomy{]} but also in education as they offer added
benefits for formal and informal learning environments for both students
and teachers \citep{de2017towards}. Yet, few studies focus on their
significance for teachers.

One important health parameter assessed by nearly all wrist wearables is
HR \citep{scalise2018wearables}. HR indicates the number of heartbeats
within one minute and is typically expressed as beats per minute (BPM)
\citep{hottenrott2007}. At rest, the average HR of adults typically
ranges from 60 to 80 BPM \citep{sammito2015guideline}. HR can be
detected and measured using sensors based on electrocardiogram (ECG) or
phonocardiogram (PCG) \citep{mukhopadhyay2017wearable}. Another
uncomplicated and inexpensive technique to measure HR via fitness
trackers is photoplethysmography (PPG) \citep{castaneda2018review}. This
optical method assesses HR by flashing green or red lights to measure
changes in blood volume \citep{allen2007photoplethysmography}.\\
Physiologically, HR is regulated and influenced on short-time intervals
by the sympathetic and the parasympathetic nervous system
\citep{pham2021}. An increase in the activity of the sympathetic system
results in HR being speeded up (``fight or flight'')
\citep{taelman2009influence}. In contrast, increased activity of the
parasympathetic has the effect of slowing down the HR (``rest and
digest'') \citep{battipaglia2015}. Therefore, an increase in HR can be
regarded as an indicator of increasing stress, and a decrease as an
indicator of decreasing stress \citep{kyriacou1978}.

\hypertarget{teacher-stress-and-important-resources}{%
\subsection{Teacher Stress and Important
Resources}\label{teacher-stress-and-important-resources}}

The teaching profession is one of the most stressful professions
compared to other occupational groups, facing a variety of stressors
during everyday work \citep{smith2000, herman2020, schult2014belastet}.
According to \citet{kyriacou1978}, teacher stress can be defined as a
negative affective response, often accompanied by physiological changes
such as increased HR, triggered by job-related demands and perceived as
threatening to one's self-esteem or well-being. Coping mechanisms help
to reduce the perceived threat.

This definition of teacher stress is based on the transactional stress
model by Lazarus and colleagues
\citep{lazarus1981stressbezogene, lazarus1984stress}, which was modified
and tailored to the teaching-learning environment by
\citet{kyriacou1978}.

In general, the transactional stress model \citep{lazarus1990theory}
highlights the interaction between an individual and the environment,
whereby stress refers to any event that exceeds a person's adaptive
resources. It has been shown that there are important connections
between stressors and resources experienced by teachers on the one hand,
and stress-induced health issues on the other hand
\citep{krause2013messung}. As we are interested in how specific
classroom events affect teacher stress, we adapted the transactional
stress model to that type of situation, based on a representation of the
model first proposed by {[}van2006stress{]}; this working model is
depicted in Fig. 1.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the author)}
  \label{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the author)}
\end{figure}

When potential stressors (e.g., classroom disruptions) occur during
teaching (1), teachers subjectively appraise how disruptive the event is
(2). If potential stressors are judged as threatening, i.e., as actual
stressors (3), teachers consider whether they have sufficient resources
for coping with the stressor (4). Based on this evaluation of resources
and their characteristics such as professional experience, teachers try
to manage classroom disruptions, by utilizing classroom management
strategies (5). In cases where coping fails, stress ensues, often
accompanied by physiological reactions like increased HR (6). Following
resource appraisal and coping outcomes, the stressor is re-evaluated
(7).

The appraisal processes of resources play a crucial role as teachers'
assessments of resources and coping mechanisms, both internal (e.g.,
classroom management skills) and external (e.g., supportive colleagues),
significantly impact their stress levels. When resources are lacking and
coping fails, negative consequences like burnout and high turnover can
arise \citep{jalongo2006, unterbrink2007, aloe2014}. This highlights the
importance of teachers' appraisal of their professional competencies,
including their ability to manage classroom disruptions effectively
\citep{klieme2008concept, konig2016teacher}.

As shown in Fig. 1, both primary and secondary appraisals are influenced
by teachers' characteristics, e.g., their professional experience,
shaping their classroom management skills. As experience grows, teachers
develop cognitive scripts for managing classroom events resulting in
more complex classroom management skills \citep{wolff2021classroom}.
Especially beginning teachers face considerable stress and often feel
overwhelmed by the demands of teaching
{[}\citet{ophardt2017klassenmanagement}; \citet{wolff2015keeping}; @
klusmann2012berufliche{]}, with many leaving the profession within the
first five years \citep{ingersoll2003}. Research shows less experienced
teachers are more susceptible to burnout, underscoring the importance of
experience and job satisfaction in predicting teacher stress
\citep{fisher2011}.

\hypertarget{hr-in-teaching-learning-contexts}{%
\subsection{HR in Teaching-Learning
Contexts}\label{hr-in-teaching-learning-contexts}}

ECG studies have revealed that HR can be used to map changes in HR
during teaching onto stressors experienced by teachers. For example, HR
increased during teacher-centered activities when teachers had to take a
leading position in the student-teacher interaction
\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021}.
\citet{sperka1995} for example recorded the HR of 16 pre-service
teachers during their first lesson. The results showed significantly
increased psychophysiological activation in terms of an increased HR
during teaching. The activation effect was particularly prominent at the
beginning of the lesson and decreased over the course of the lesson. The
authors interpret this result as showing how pre-service teachers'
active coping processes, i.e., the active management of the interaction
with the students, helped the teachers regulate their HR downwards.
Other ECG studies identified typical stressors predicting increased HR
values, such as class size \citep{huang2022class}, or low student
engagement and motivation \citep{junker2021}. For example,
\citet{junker2021} recorded the HR of 40 teachers using an ambulatory
monitoring system during a real classroom lesson. They provided evidence
that teacher stress caused by stressors such as low student engagement,
i.e., students displaying a lack of motivation or limited interest in
their tasks or classroom activities, or teacher-centered activities,
i.e., classroom activities primarily focused on the teacher's actions.,
leads to an increase in HR.

In addition to ECG studies, there are a few studies that used wrist-worn
fitness trackers to investigate HR trends in teaching-learning
situations \citep{Darnell2019, chalmers2021}. \citet{Darnell2019} for
example measured the HR of 15 medical college students using wrist-worn
devices during lectures. The analysis revealed a constant decrease in HR
from the beginning to the end of a lecture, whereas the HR peak was
reached during active learning sessions. \citet{chalmers2021} examined
the usability of the average HR, measured with a Fitbit fitness tracker,
to identify physiological changes during stress-inducing tasks in a
study with a total of 60 participants. The average HR increased
significantly between the resting and stress phases. Even though the
participants in these studies were learners, not teachers, the results
are relevant to the study of teacher stress using wearable devices,
because the studies showed that a) HR can be effectively recorded using
fitness trackers during a whole learning unit, and b) HR changes are in
line with the occurrence of activating or stress-inducing tasks.

So far, to the best of our knowledge, only one study has directly
assessed teachers' HR using a wrist-worn fitness tracker during teaching
: \citet{runge2020} used a Fitbit fitness tracker to assess HR as an
indicator of stress in N=4 teachers. They used the fitness trackers'
recordings to create a profile for each teacher (to differentiate
between teachers reporting higher or lower levels of stress .) In
particular, it was found that the combination of a high number of steps,
a high HR, and short sleep was an indicator of stress. It should be
noted that the generalizability of the results is limited due to the
small sample size.

In summary, previous studies have revealed that teachers' (and
students') HR changes, depending on the activity and stressors they
experience, whereby teacher-centered phases , in particular, led to an
increase in HR
\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021}.
Furthermore, it could be shown that HR as an indicator of stress can be
assessed using low-cost, non-intrusive fitness trackers and that HR
increases in activating phases and even before stress occurs
\citep{Darnell2019, chalmers2021}. However, studies collecting data from
teacher-worn fitness trackers in a large enough sample to explore links
with factors such as subjective stressor appraisal, or effects of
teaching experience, are still lacking. Our study aims to close this
research gap.

\hypertarget{present-study}{%
\subsection{Present Study}\label{present-study}}

The data analyzed for the present study were obtained from teachers and
student teachers who participated in a lab study, as part of a larger
project targeting the development of classroom management in teachers.

As part of the larger project, participants came to the lab
individually, and each taught a 15-minute, self-prepared micro-teaching
unit to a ``class'' of three actors (trained student assistants). These
actors performed nine, possibly disruptive, classroom events. The actors
received standardized instructions on a screen (only visible to them,
not to the participant) to perform a classroom event every one and a
half minutes, and they performed the same scripted disruptions for all
participants. While teaching, participants wore eye-tracking glasses,
and additionally, their lessons were recorded by cameras.

The micro-teaching unit, with its unfamiliar setting and the scripted
disruptions of participants' teaching flow, was potentially stressful.
Thus, we were particularly interested in the development of
participants' HR before, during, and after this micro-teaching unit. We
recorded HR data in five phases, with a total duration of approximately
two hours: In the \emph{pre-teaching phase}, participants were welcomed,
prepared for the following micro-teaching unit, and familiarized with
the setting. In the \emph{teaching phase}, participants taught the
micro-teaching unit and experienced the classroom disruptions. In the
\emph{post-teaching phase}, participants answered several questionnaires
in a comfortable seated position. Next, in the \emph{interview phase},
they watched the video of their 15-minute unit, rated the disruptive
classroom events, and answered open questions. Finally, in the \emph{end
phase}, participants answered another questionnaire. These conditions
were identical for all participants. During the entire study,
participants wore a fitness tracker on their wrist.

The goals of the present study were twofold:

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  The first research goal was to investigate whether HR measures
  assessed by wrist-based fitness trackers are a suitable and effective
  method for mapping teachers' HR over the course of a five-phase lab
  study, including the time before, during, and after a potentially
  stressful micro-teaching unit.
\end{enumerate}

First, we expected the participants to show an initial increase in their
HR, followed by a peak during the teaching phase and a decrease for the
remaining phases. In addition, we examined whether z-standardization of
the participants' mean HR could serve as a useful method to account for
individual differences in baseline HR. We expected to observe the same
trends in both standardized and non-standardized mean HR values.

Second, five representative 10-minute intervals were selected from the
five phases (see section \#\#Measures for a more detailed description of
the intervals), which served as the basis for the data analysis for our
hypothesis: pre-teaching interval (\(I_1\)), teaching interval
(\(I_2\)), post-teaching interval (\(I_3\)), interview interval
(\(I_4\)), end interval (\(I_5\)). We examined the levels of and the
changes in HR during these intervals. We assumed the highest HR level in
the teaching interval (\(I_2\)) and lower levels in all other intervals
(\textbf{Hypothesis 1a}). Further, we expected an increase in
participants' HR while they were preparing for teaching during the
pre-teaching interval (\(I_1\)), and we expected a decrease in
participants' HR during all of the following intervals, because of
habituating to (\(I_2\)) and recovering from (\(I_3\)-\(I_5\)) the
stressful teaching phase (\textbf{Hypothesis 1b}).

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  The second research goal was to examine whether variance in HR
  measures could be explained by participants' teaching experience
  (because, presumable, more experienced teachers might have better
  classroom management strategies, and thus better resources for
  coping), and/or by their self-reported subjective appraisals of
  classroom events (specifically, how disruptive it was, and how
  confident they felt in their coping).
\end{enumerate}

We expected lower HR levels for teachers with more teaching experience,
particularly during the teaching interval (\textbf{Hypothesis 2a}). We
expected higher HR levels for teachers who felt more disrupted by the
enacted classroom events, regardless of their teaching experience
(\textbf{Hypotheses 2b}). At the same time, we expected lower HR levels
for teachers who felt more confident in dealing with the events,
regardless of teaching experience (\textbf{Hypothesis 2c}). Lastly, we
hypothesized that each of the three predictors (teaching experience,
disruption appraisal, confidence appraisal) uniquely contributes to
explaining variance in teachers´ HR levels (\textbf{Hypothesis 2d}). In
addition, we exploratively examined the same as for the HR levels again
for the changes in HR.

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

The sample consisted of \(N\) = 84 pre- and in-service teachers from
Germany, who were recruited via personal contact, email lists, and
flyers. The data of three participants was lost due to failed data
transmission, yielding an analysis sample of \(n\) = 81 (\(n\) = 52
women, \(n\) = 29 men). Participants had a mean age of 30.95 years
(\(SD\) = 10.90; range: 19-60) and an average teaching experience of
5.64 years (\(SD\) = 9.46; range: 0-37).

\hypertarget{setting-and-procedure}{%
\subsection{Setting and Procedure}\label{setting-and-procedure}}

The study was carried out following the ethical standards and the
approval of the University's Institutional Review Board. All
participants were informed in detail about the aims and intention of the
study before testing. Participation was voluntary and only took place
after written consent had been given. Participants were not rewarded in
any way for participating in the study.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{images/Timeline_ProVision_vertical.png}
  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
\end{figure}

Each participant came to the lab for a period of approximately two hours
in total, and each underwent the same phases: \emph{pre-teaching phase},
\emph{teaching phase}, \emph{post-teaching phase}, \emph{interview
phase}, and \emph{end phase} (please refer to Fig. 2 for a timeline). In
the \emph{pre-teaching phase}, the experimenter welcomed the
participants and helped them put on the fitness tracker. This was
followed by a warm-up session to familiarize the participants with the
laboratory setting and the class. This phase took about 10-15 minutes
and participants spent this time mostly standing or slowly walking
around. During the \emph{teaching phase}, the participants held their
self-prepared, micro-teaching unit to a class of three trained actors
who performed nine, potentially disruptive, classroom events (e.g.,
chatting with a neighbor, heckling, looking at the phone; see Table \#\#
in the supplementary material for an overview and categorization of all
events; also see Fig\#\# for a depiction of the laboratory setting of
the micro-teaching unit). In preparation for the 15-minute lesson, the
topic and class level could be freely chosen by the teachers. The type
of course was to be an introductory lesson and the desired social form
required individual work or frontal teaching, without longer video
sequences and movement of the actors. The teaching unit lasted about
15-20 minutes. Participants spent this time mostly standing or slowly
walking around. After having completed the micro-teaching unit, in the
\emph{post-teaching phase}, participants were seated at a desk and
filled in questionnaires for approximately 10-15 minutes: a brief
computer-based questionnaire assessing sociodemographic data (e.g.,
teaching experience, gender, studied school type, studied school
subjects, extracurricular teaching activities), and a short knowledge
test that is irrelevant to the present study. In the \emph{interview
phase}, the participants watched the video of their own teaching
together with the experimenter. While doing so, they were given a
Stimulated Recall Interview (SRI), in which the participants watched
their recorded eye-tracking video of the lesson from the ego
perspective, indicating the participants' gaze point. The experimenter
stopped the video each time one of the nine classroom events happened
and asked a total of eight questions, five of which were open and three
closed. We assessed -- among other questions irrelevant to this study --
with two closed questions the teachers' subjective appraisal of the
classroom events that took place during the \emph{teaching phase} in
terms of how subjectively disruptive they were (disruption appraisal)
and how confident the participants felt dealing with them (confidence
appraisal) with one item each. The interview lasted about 45-60 minutes
and the participants' position was seated. The \emph{end phase} lasted
about 10-15 minutes and participants answered in a seated position
another questionnaire irrelevant to this study.

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

\hypertarget{heart-rate-data-and-heart-rate-intervals}{%
\subsubsection{Heart Rate Data and Heart Rate
Intervals}\label{heart-rate-data-and-heart-rate-intervals}}

To measure the teachers' HR, we used a wrist-based fitness tracker. The
model was a Fitbit Charge 4. In line with the manufacturer's
instructions \citep{fitbitnd}, the device was attached a finger's width
above the participants' nondominant hand's wrist bone. The tracker works
by flashing green LEDs hundreds of times per second, using
light-sensitive photodiodes to catch the reflected light, and from that
information calculating volume changes in the capillaries. From this,
the tracker calculates how many times the heart beats per minute. HR
measurements are generated at least every 15 seconds\footnote{The
  fluctuations in the number of seconds in which the HR was measured are
  due to the participants' movements, meaning that the device could not
  measure the HR every second.}. The raw data that can be extracted from
the tracker lists the time stamps of all measurements and the estimated
HR in BPM for each time stamp.

The anonymous HR data was synced via Bluetooth to a commercial Fitbit
account. Subsequently, the intraday second-by-second data was exported
as a CSV file for each session using the open-source software PulseWatch
(Ricci, n.d.), and linked to the participant. To account for individual
differences in the baseline HR, we first z-standardized the BPM values
from the unstandardized mean HRs.

Since we aimed to explore teachers' HR between different strain phases,
we aggregated HR over a 10-minute interval within each phase. Previous
research has indicated that 10-minute intervals are a useful duration
for analyzing PPG data \citep{lu2008can}. The intervals were selected
based on the following rules: The pre-teaching interval (\(I_1\))
comprised the first 10 minutes after the fitness tracker had been put
on. The teaching interval (\(I_2\)) started two minutes after the
teacher had started the teaching unit. This interval was of the highest
relevance to our study. We explicitly chose an early 10-minute interval
within the teaching phase, as previous studies revealed that the
beginning of a lesson is essential and demanding regarding
teacher-student interaction
\citep{donker2018quantitative, claessens2017positive}. The post-teaching
interval (\(I_3\)) started immediately after the end of the teaching
unit. The interview interval (\(I_4\)) was defined as the mid-10 minutes
between the end of the teaching unit and the time point when the fitness
tracker was taken off so that all participants were being interviewed
during this interval. The end interval (\(I_5\)) comprised the last 10
minutes before the fitness tracker was taken off.

\hypertarget{teaching-experience}{%
\subsubsection{Teaching Experience}\label{teaching-experience}}

The participants' teaching experience was assessed as a part of
sociodemographic data. Participants stated their work experience in
years (excluding the traineeship year).

\hypertarget{subjective-appraisal-of-the-classroom-events-and-coping-processes}{%
\subsubsection{Subjective appraisal of the classroom events and coping
processes}\label{subjective-appraisal-of-the-classroom-events-and-coping-processes}}

The subjective disruption and confidence appraisals assessed in the SRI
on an 11-point rating scale were averaged across the nine classroom
events as we were not interested in individual classroom events, but
only in the expected mean level of arousal during the \emph{teaching
phase}. Regarding the model (see Fig. 1), the disruption appraisal was
used to assess the evaluation of the stressor (see Fig. 1, box 2). The
confidence appraisal, in contrast, referred to the resources available
for coping with the stressors (see Fig. 1, box 4).

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We conducted all analyses with R \citep{RStudio2020}. Graphics were
created using ggplot2 (v3.3.3; Wickham, 2016).

\textbf{Research goal 1}. The first research goal included mapping
teachers' HR before, during, and following a micro-teaching unit in the
course of a five-phase lab study.

Regarding the teachers' HR trend, we displayed the HR trend over the
course of the entire study. For z-standardization as a method to account
for individual differences in the baseline HR, we visually compared
unstandardized and standardized mean HR trends for the entire two-hours
study. For testing Hypothesis 1a, which examined the HR levels in the
different intervals, we initially conducted a one-way ANOVA with
repeated measures as an omnibus test. The dependent variable comprised
the standardized HR mean for each interval. To identify the highest HR
level, we subsequently conducted t-tests with planned contrasts as
post-hoc tests, accompanied by the effect size d \citep{cohen1988new}.
Specifically, we tested the differences between the teaching interval
(\(I_2\)) and the other four intervals. Note that mean HR was calculated
at the subject level of \(n\) = 81 participants (see Table 1), whereas
the mean slope and mean intercept estimates are based on all values at
all measurement time points (see Table 2). For testing Hypothesis 1b,
which examined the HR changes within each interval, we conducted a
linear estimation of the increase or decrease in HR over time. To this
end, we used fixed intercept fixed slope regression models
\citep{gelman2006data} for each interval to estimate intercepts and
linear slopes for all individuals which were then averaged across
individuals\footnote{Although this procedure does not account for
  nonmonotonic progressions in individual HR, a graphical evaluation
  revealed that the linear estimates corresponded well to the majority
  of the cases (see XX in the supplementary material).}.

\textbf{Research goal 2}. In addressing our second research goal, we
examined the effects of teaching experience and subjective appraisal of
disruptive classroom events on teachers' HR levels during the five
phases.

To test hypothesis 2a, we examined the effect of teaching experience on
participants' HR levels for each of the five intervals using linear
regression models with teaching experience as the sole predictor. To
test hypotheses 2b and 2c, we separately augmented the models by either
teachers' disruption appraisal (Hypothesis 2b) or confidence appraisal
(Hypothesis 2c), while controlling for shared variance with teaching
experience. HR levels were only predicted with the disruption and
confidence appraisal after the teaching had taken place, i.e., for all
the intervals following the pre-teaching interval (I1). To test
hypothesis 2d, we examined the effects of all three predictors in one
regression model. We repeated these steps to explore the effect of
teaching experience and subjective appraisals on changes in teachers' HR
at each interval.

\bibliography{r-references.bib}

\end{document}

### 2024-04-24 02_paper/02_study/02_fitbit paper/Submission/FitBit_submission.Rmd
submission weiter

@@
 knitr::opts_chunk$set(echo = FALSE, fig.width = 8, fig.height = 4, cache = TRUE)
+
+# load packages
+
+library(needs)
+
+needs(ltm,
+      xtable,
+      broom,
+      ppcor,
+      jtools,
+      lm.beta,
+      janitor,
+      lubridate,
+      readxl,
+      ggthemes,
+      gridExtra,
+      imputeTS,
+      DescTools,
+      cowplot,
+      rstatix,
+      ggpubr,
+      lme4,
+      lmerTest,
+      viridis,
+      gridExtra,
+      gridtext,
+      magrittr,
+      PerformanceAnalytics,
+      Hmisc,
+      corrplot,
+      tidyverse,
+      ggplot2,
+      lavaan,
+      lm.beta,
+      stargazer)
 ```
@@
 
-In education, there’s interest in identifying reliable indicators for teacher stress and burnout [@fisher2011; @ junker2021].
+In education, there’s interest in identifying reliable indicators for teacher stress and burnout [@fisher2011; @junker2021].
 Previous research often relied on self-report questionnaires [@chaplain2008; @liu2020], which may be prone to biases like social desirability [@razavi2001self] or recall errors [@van2016accuracy].
@@
 
+```{r read the data}
+
+# disruption & confidence rating
+
+df_rating <- 
+  excel_sheets("data/Coding_SRI.xlsx") %>% 
+  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
+  dplyr::select(ID, # select relevant columns 
+         "disruption_factor", # -99 = subject did not notice event; -100 = experimenter did not ask for event
+         "confidence_factor",
+         "event"
+         ) %>% 
+  mutate(disruption_factor = ifelse(disruption_factor < 0,
+                                    yes = NA,
+                                    no = disruption_factor
+                                    ),
+         confidence_factor = ifelse(confidence_factor < 0,
+                                   yes = NA,
+                                   no = confidence_factor),
+         event = as_factor(event)
+         )
+
+# demographic data
+
+df_demo <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
+  transmute(ID = LI06_05, # select and rename relevant columns 
+            gender = factor(LI02_01_1,
+                            levels = 1:2,
+                            labels = c("male","female") # 1 = male; 2 = female
+                            ),
+            age = LI03_01, 
+            teaching_experience = LI04_01)
+
+N_prewrangling <- as.numeric(nrow(df_demo))
+
+# merge two data frames by ID 
+df_merge <- merge(df_demo,
+                  df_rating,
+                  by = "ID") %>% 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132")
+         )
+
+# heart rate data
+
+data_path <- "./data/heart_rate_data"
+
+main <-
+map(.x = dir(path = data_path,
+             pattern = ".csv"),
+    ~ read_csv(file.path(data_path, .), 
+               id = "id",
+               col_types = c("t","n")
+               ) %>% 
+  mutate(time = .$Time - min(.$Time),
+         time = as.numeric(time),
+         heart_rate = `Heart Rate`,
+         ID = id,
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
+                               str_detect(string = id, pattern = "_m") ~ "teaching",
+                               str_detect(string = id, pattern = "_p") ~ "preparation",
+                               str_detect(string = id, pattern = "_s") ~ "post",
+                               str_detect(string = id, pattern = "_i") ~ "interview",
+                               TRUE ~ "overall"
+                               ),
+         ID = str_extract(string = ID,
+                          pattern = "[:digit:]{3}"),
+         ID = as.numeric(ID)
+      ) %>%
+    # filter(time <= 600) %>% # filter for 10min intervals
+    filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
+    dplyr::select(!c("Time","Heart Rate","id"))
+    ) %>%
+  bind_rows()
+
+main <-
+  left_join(main, df_merge,
+            by = "ID")
+
+main <- 
+  main %>% 
+  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  dplyr::summarise(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  filter(!(time_span == "teaching" & time > 600)) %>%
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart)
+
+N_postwrangling <- as.numeric(length(unique(main$ID)))
+
+stargazer
+
+```
+
 # Method
@@
 
-The sample consisted of $N$ = 84 pre- and in-service teachers from Germany, who were recruited via personal contact, email lists, and flyers.
-The data of three participants was lost due to failed data transmission, yielding an analysis sample of $n$ = 81 ($n$ = 52 women, $n$ = 29 men).
+The sample consisted of $N$ = `r N_prewrangling` pre- and in-service teachers from Germany, who were recruited via personal contact, email lists, and flyers.
+The data of three participants was lost due to failed data transmission, yielding an analysis sample of $n$ = `N_postwrangling` ($n$ = 52 women, $n$ = 29 men).
 Participants had a mean age of 30.95 years ($SD$ = 10.90; range: 19-60) and an average teaching experience of 5.64 years ($SD$ = 9.46; range: 0-37).
@@
   \centering
-  \includegraphics[width=1\textwidth]{images/Timeline_ProVision_vertical.png}
+  \includegraphics[width=1\textwidth]{images/Timeline.pdf}
   \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}

### 2024-04-24 02_paper/02_study/02_fitbit paper/Submission/FitBit_submission.tex
submission weiter

@@
 In education, there's interest in identifying reliable indicators for
-teacher stress and burnout {[}\citet{fisher2011}; @ junker2021{]}.
-Previous research often relied on self-report questionnaires
+teacher stress and burnout \citep{fisher2011, junker2021}. Previous
+research often relied on self-report questionnaires
 \citep{chaplain2008, liu2020}, which may be prone to biases like social
@@
 
+\begin{verbatim}
+## New names:
+## * `` -> `...6`
+## * `` -> `...7`
+## * `` -> `...8`
+## * `` -> `...9`
+## * `` -> `...10`
+## * `` -> `...11`
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in left_join(main, df_merge, by = "ID"): Detected an unexpected many-to-many relationship between `x` and `y`.
+## i Row 1 of `x` matches multiple rows in `y`.
+## i Row 1 of `y` matches multiple rows in `x`.
+## i If a many-to-many relationship is expected, set `relationship =
+##   "many-to-many"` to silence this warning.
+\end{verbatim}
+
+\begin{verbatim}
+## function (..., type = "latex", title = "", style = "default", 
+##     summary = NULL, out = NULL, out.header = FALSE, column.labels = NULL, 
+##     column.separate = NULL, covariate.labels = NULL, dep.var.caption = NULL, 
+##     dep.var.labels = NULL, dep.var.labels.include = TRUE, align = FALSE, 
+##     coef = NULL, se = NULL, t = NULL, p = NULL, t.auto = TRUE, 
+##     p.auto = TRUE, ci = FALSE, ci.custom = NULL, ci.level = 0.95, 
+##     ci.separator = NULL, add.lines = NULL, apply.coef = NULL, 
+##     apply.se = NULL, apply.t = NULL, apply.p = NULL, apply.ci = NULL, 
+##     colnames = NULL, column.sep.width = "5pt", decimal.mark = NULL, 
+##     df = TRUE, digit.separate = NULL, digit.separator = NULL, 
+##     digits = NULL, digits.extra = NULL, flip = FALSE, float = TRUE, 
+##     float.env = "table", font.size = NULL, header = TRUE, initial.zero = NULL, 
+##     intercept.bottom = TRUE, intercept.top = FALSE, keep = NULL, 
+##     keep.stat = NULL, label = "", model.names = NULL, model.numbers = NULL, 
+##     multicolumn = TRUE, no.space = NULL, notes = NULL, notes.align = NULL, 
+##     notes.append = TRUE, notes.label = NULL, object.names = FALSE, 
+##     omit = NULL, omit.labels = NULL, omit.stat = NULL, omit.summary.stat = NULL, 
+##     omit.table.layout = NULL, omit.yes.no = c("Yes", "No"), order = NULL, 
+##     ord.intercepts = FALSE, perl = FALSE, report = NULL, rownames = NULL, 
+##     rq.se = "nid", selection.equation = FALSE, single.row = FALSE, 
+##     star.char = NULL, star.cutoffs = NULL, suppress.errors = FALSE, 
+##     table.layout = NULL, table.placement = "!htbp", zero.component = FALSE, 
+##     summary.logical = TRUE, summary.stat = NULL, nobs = TRUE, 
+##     mean.sd = TRUE, min.max = TRUE, median = FALSE, iqr = FALSE) 
+## {
+##     save.warn.option <- getOption("warn")
+##     options(warn = -1)
+##     return(.stargazer.wrap(..., type = type, title = title, style = style, 
+##         summary = summary, out = out, out.header = out.header, 
+##         column.labels = column.labels, column.separate = column.separate, 
+##         covariate.labels = covariate.labels, dep.var.caption = dep.var.caption, 
+##         dep.var.labels = dep.var.labels, dep.var.labels.include = dep.var.labels.include, 
+##         align = align, coef = coef, se = se, t = t, p = p, t.auto = t.auto, 
+##         p.auto = p.auto, ci = ci, ci.custom = ci.custom, ci.level = ci.level, 
+##         ci.separator = ci.separator, add.lines = add.lines, apply.coef = apply.coef, 
+##         apply.se = apply.se, apply.t = apply.t, apply.p = apply.p, 
+##         apply.ci = apply.ci, colnames = colnames, column.sep.width = column.sep.width, 
+##         decimal.mark = decimal.mark, df = df, digit.separate = digit.separate, 
+##         digit.separator = digit.separator, digits = digits, digits.extra = digits.extra, 
+##         flip = flip, float = float, float.env = float.env, font.size = font.size, 
+##         header = header, initial.zero = initial.zero, intercept.bottom = intercept.bottom, 
+##         intercept.top = intercept.top, keep = keep, keep.stat = keep.stat, 
+##         label = label, model.names = model.names, model.numbers = model.numbers, 
+##         multicolumn = multicolumn, no.space = no.space, notes = notes, 
+##         notes.align = notes.align, notes.append = notes.append, 
+##         notes.label = notes.label, object.names = object.names, 
+##         omit = omit, omit.labels = omit.labels, omit.stat = omit.stat, 
+##         omit.summary.stat = omit.summary.stat, omit.table.layout = omit.table.layout, 
+##         omit.yes.no = omit.yes.no, order = order, ord.intercepts = ord.intercepts, 
+##         perl = perl, report = report, rownames = rownames, rq.se = rq.se, 
+##         selection.equation = selection.equation, single.row = single.row, 
+##         star.char = star.char, star.cutoffs = star.cutoffs, suppress.errors = suppress.errors, 
+##         table.layout = table.layout, table.placement = table.placement, 
+##         zero.component = zero.component, summary.logical = summary.logical, 
+##         summary.stat = summary.stat, nobs = nobs, mean.sd = mean.sd, 
+##         min.max = min.max, median = median, iqr = iqr, warn = save.warn.option))
+## }
+## <bytecode: 0x000001fa06756810>
+## <environment: namespace:stargazer>
+\end{verbatim}
+
 \hypertarget{method}{%
@@
 flyers. The data of three participants was lost due to failed data
-transmission, yielding an analysis sample of \(n\) = 81 (\(n\) = 52
-women, \(n\) = 29 men). Participants had a mean age of 30.95 years
-(\(SD\) = 10.90; range: 19-60) and an average teaching experience of
-5.64 years (\(SD\) = 9.46; range: 0-37).
+transmission, yielding an analysis sample of \(n\) =
+\texttt{N\_postwrangling} (\(n\) = 52 women, \(n\) = 29 men).
+Participants had a mean age of 30.95 years (\(SD\) = 10.90; range:
+19-60) and an average teaching experience of 5.64 years (\(SD\) = 9.46;
+range: 0-37).
 

### 2024-04-24 02_paper/02_study/02_fitbit paper/Submission/data.wrangling.R

@@ -1,0 +1,523 @@
+# rm(list = ls())
+# 
+# ##### 1. Test data #####
+# 
+# 
+# df_test <- read_tsv(file = "data/Acc_Test_data.tsv") %>% 
+#   clean_names() %>%
+#   transmute(time = as.numeric(milliseconds(recording_timestamp_ms)
+#   ),
+#   name = participant_name,
+#   acc_x = as.numeric(str_replace(accelerometer_x_m_s2,
+#                                  pattern = ",",
+#                                  replacement = "."
+#   )
+#   ),
+#   acc_z = as.numeric(str_replace(accelerometer_z_m_s2,
+#                                  pattern = ",",
+#                                  replacement = "."
+#   )
+#   )
+#   )
+# 
+# # First step: create tibbles for each individual.
+# for (i in unique(df_test$name)) {
+#   
+#   df <- filter(df_test,
+#                name == i
+#   )
+#   
+#   assign(value = df,
+#          x = paste0("df_", i)
+#   )
+# }
+# 
+# # For each of the tibbles, create two vectors (x and z) 
+# # for meters for each time period.
+# 
+# for (i in unique(df_test$name)) {
+#   
+#   df <- get(paste0("df_", i))
+#   
+#   # Vectors x and z with length equal to time periods 
+#   # present in each tibble; initial with 0 meters for each   # time period. 
+#   
+#   x <- rep(0, length(get(paste0("df_", i))$time))
+#   z <- rep(0, length(get(paste0("df_", i))$time))
+#   
+#   # For each time period, calculate the meters walked in 
+#   # two dimensions (x and z), given the initial velocity 
+#   # for each period is 0 m/s. First value stays 0 for
+#   # convenience.
+#   # See formula 1.
+#   
+#   for (j in 2:length(get(paste0("df_", i))$time)) {
+#     
+#     x[[j]] <- 0.5 * get(paste0("df_", i))$acc_x[j] * (get(paste0("df_", i))$time[j] - get(paste0("df_", i))$time[j-1])^2
+#     
+#     z[[j]] <- 0.5 * get(paste0("df_", i))$acc_z[j] * (get(paste0("df_", i))$time[j] - get(paste0("df_", i))$time[j-1])^2
+#     
+#   }
+#   
+#   # Save both vectors in new tibble.
+#   
+#   df <- tibble(meter_x = x,
+#                meter_z = z,
+#                ID = paste0(i))
+#   assign(x = paste0("df_meter_", i),
+#          value = df)
+# }
+# 
[…]

### 2024-05-02 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

@@
 
+# # Count for in-service and pre-service teachers
+# # Remove duplicate cases
+# distinct_df <- distinct(main, ID, gender, .keep_all = TRUE)
+# 
+# # Count individual cases
+# case_summary <- distinct_df %>%
+#   filter(ID > 200) %>% 
+#   count(gender == "male")
+# print(case_summary)
+
 # Mean, SD and range for overall (unstandardized)
@@
 
-summary(regr_end1)
+summary(regr_preparation1)
 summary(regr_end2)

### 2024-05-14 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

@@
     # filter(time <= 600) %>% # filter for 10min intervals
-    filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
+    # filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
     dplyr::select(!c("Time","Heart Rate","id"))
@@
            sd_heart)
+
+## count for individuals 
+main %>% 
+  filter(time >= 7200) %>% 
+  distinct(ID, .keep_all = TRUE) -> filter_overall
 
@@
 ### Correlation
+
+## age x teaching experience
+``` {r}
+main %>% 
+  filter(time_span == "overall") %>% 
+  group_by(ID) %>% 
+  select(ID,
+         teaching_experience,
+         age) -> teach_gender
+
+cor(cor_teach_gender$teaching_experience,
+    cor_teach_gender$age,
+    method = c("pearson")
+  ) -> cor_teach_gender
+
+```
 

### 2024-05-16 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

@@
   distinct() %>%
-  group_by(time_span) %>% 
+  group_by(ID, time_span) %>% 
   summarise(z_mean = mean(heart_rate_std),
             z_sd = sd(heart_rate_std),
-            z_t = qt(p = 0.01 / 2,      # 0.01 KI
+            z_t = qt(p = 0.05 / 2,      # 0.05 KI
                df = n() - 1,
@@
              linetype = "dashed") +
-  ylim(-1, 1) + 
-  scale_y_continuous(breaks=seq(-1, 1, 0.5), 
-                     limits=c(-1, 1)) + 
+  ylim(-1.5, 1.5) + 
+  scale_y_continuous(breaks=seq(-1.5, 1.5, 0.5), 
+                     limits=c(-1.5, 1.5)
+                     ) + 
   labs(x = "Time (in Minutes)",

### 2024-05-30 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

--- 2024-05-02 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
@@
 
+## count for individuals 
+main %>% 
+  filter(time >= 7200) %>% 
+  distinct(ID, .keep_all = TRUE) -> filter_overall
+
 ```
@@
 
-# Graph
+# Plots
 
 ```{r fig.width = 10,results='hide',fig.keep='all'}
-loess_plot_overall <-
-  main %>% 
+
+## Overall Course Plot (std. vs. unstd.)
+df_heart_rate <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
   filter(time_span == "overall") %>%
-  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
-  distinct() %>% 
+  dplyr::select("ID","time","heart_rate") %>% 
+  distinct() %>% 
+  mutate(type = "a. Heart Rate (in beats per minute)")
+
+df_heart_rate_std <- 
+  main %>% 
+  mutate(time = time / 60) %>% 
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate_std") %>% 
+  distinct() %>% 
+  transmute(ID,
+            time,
+            type = "b. Heart Rate (standardized)",
+            heart_rate = heart_rate_std)
+
+bind_rows(df_heart_rate,
+          df_heart_rate_std
+          ) %>% 
   ggplot(mapping = aes(x = time,
-                       y = heart_rate_std
+                       y = heart_rate
                        )
          ) +
-  # geom_point(alpha = 0.05) + 
-  geom_smooth(se = FALSE,
+  geom_smooth(se = T,
               size = 0.5,
-              colour = "black") +
+              colour = "black",
+              level = 0.99) +
   scale_color_viridis_d(option = "A",
@@
   scale_linetype_manual(values = c(1, 6)) +
-  scale_x_continuous(expand = c(0, NA),
-                     breaks = seq(0, 9000, 600)) +
-  scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
-  labs(x = "Time (in Seconds)",
-       y = "") +
-  ggtitle("Overall Course of Mean Heart Rate") +
+  scale_x_continuous(expand = c(0.01,0)) + 
+  labs(x = "Time (in minutes)",
+       y = "",
+       ) +
   theme_apa() + 
-  theme(axis.title.y = element_blank())
-
-lm_plot_phases <-
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y")
+
+ggsave(filename = "plots_publication/loess_plot_std_unstd.png",
+       width = 16,
+       height = 12,
+       units = "cm")
+
+## Mean Plot
 main %>% 
@@
                             levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre-teaching\nphase","Teaching\nphase","Post-teaching\nphase","Interview\nphase","End\nphase"))) %>% 
-  distinct() %>% 
-  ggplot(mapping = aes(x = time,
-                       y = heart_rate_std
-                       )
-         ) +
-  # geom_point(alpha = 0.05) + 
-  geom_smooth(method = "lm",
-              se = TRUE,
-              size = 0.5,
-              colour = "black") +
-  scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  # scale_x_continuous(expand = c(0, NA),
-  #                    breaks = seq(0, 9000, 600)) +
-  #scale_y_continuous(breaks = seq(0, 160, 5)) + 
-  labs(x = "Time (in Seconds)",
-       y = "",
-       subtitle = "") +
-  theme_apa() +
-  theme(axis.title.y = element_blank()) +
-  facet_grid(cols = vars(time_span),
-             scales = "free_x")
-
-ggsave(filename = "plots_publication/lm_plot.png",
-       width = 22,
-       height = 12,
-       units = "cm")
-
-ki_plot_phases <-
-  main %>% 
-  filter(time_span != "overall") %>%
-  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
-  mutate(time_span = factor(time_span,
-                            levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre-teaching Interval","Teaching Interval","Post-teaching Interval","Interview Interval","End Interval"))) %>% 
+                            labels = c("Pre-teaching\nInterval","Teaching\nInterval","Post-teaching\nInterval","Interview\nInterval","End\nInterval"))) %>% 
   distinct() %>%
@@
             z_sd = sd(heart_rate_std),
-            z_t = qt(p = 0.01 / 2,      # 0.01 KI
+            z_t = qt(p = 0.05 / 2,      # 0.05 KI
                df = n() - 1,
@@
              linetype = "dashed") +
-  labs(subtitle = "1% Confidence Intervall",
-       x = "") +
-  facet_grid(cols = vars(time_span)) +
+  ylim(-1.5, 1.5) + 
+  scale_y_continuous(breaks=seq(-1.5, 1.5, 0.5), 
+                     limits=c(-1.5, 1.5)
+                     ) + 
+  labs(x = "Time (in Minutes)",
+       y = "Standardized Mean Heart Rate",
+       # caption = expression(paste(italic("Note: "),
+       #                            "The shadow around the line represents the 95% confidence interval."
+       #                            )
+       #                      )
+       ) +
+  facet_grid(cols = vars(time_span),
+             scales = "free_x") +
   theme_apa() +
@@
         axis.ticks.x = element_blank(),
-        axis.title.y = element_blank())
-
-text_y <- text_grob("Average Heart Rate (Standardized)",
-                   rot = 90)
-
-plot_overall <-
-  grid.arrange(loess_plot_overall, lm_plot_phases, ki_plot_phases,
-               ncol = 1,
-               left = text_y
-               )
-
-plot_overall
-
+        plot.caption = element_text(hjust = 0))
+
+ggsave(filename = "plots_publication/mean_plot.png",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+## LM Plot
 lm_plot <-
@@
          ) +
-  # geom_point(alpha = 0.05) +
   geom_smooth(method = "lm",
@@
               colour = "black",
-              level = 0.99) +
+              level = 0.95) +
   scale_color_viridis_d(option = "A",
                         end = 0.8) +
-  #scale_linetype_manual(values = c(1, 6)) +
   scale_x_continuous(breaks = seq(0, 10, 2)) +
@@
 
+# lm_plot_phases <-
+#   main %>% 
+#   filter(time_span != "overall") %>%
+#   dplyr::select("ID", "time_span", "time", "heart_rate_std") %>% 
+#   mutate(time_span = factor(time_span,
+#                             levels = c("preparation","teaching","post","interview","end"),
+#                             labels = c("Pre-teaching\nphase", "Teaching\nphase", "Post-teaching\nphase", "Interview\nphase", "End\nphase"))) %>% 
+#   ggplot(aes(x = time, 
+#              y = heart_rate_std, 
+#              color = ID)
+#          ) +
+#   geom_smooth(method = "lm", 
+#               se = TRUE, 
+#               aes(group = ID), 
+#               size = 0.5) + # Regression per ID
+#   geom_smooth(data = . %>% 
+#                 group_by(time_span) %>% 
+#                 summarise_all(mean), 
+#               method = "lm", 
+#               se = TRUE, color = "black", 
+#               size = 1) + # Overall regression
+#   scale_color_viridis_d(option = "A", 
+#                         end = 0.8) +
+#   scale_linetype_manual(values = c(1, 6)) +
+#   labs(x = "Time (in Seconds)", 
+#        y = "", 
+#        subtitle = "") +
+#   theme_apa() +
+#   theme(axis.title.y = element_blank()) +
+#   facet_grid(cols = vars(time_span), 
+#              scales = "free_x")
+
 ggsave(filename = "plots_publication/lm_plot.png",
@@
        units = "cm")
-
 ```
@@
 
+## age x teaching experience
+``` {r}
+main %>% 
+  filter(time_span == "overall") %>% 
+  group_by(ID) %>% 
+  select(ID,
+         teaching_experience,
+         age) -> teach_gender
+
+cor(cor_teach_gender$teaching_experience,
+    cor_teach_gender$age,
+    method = c("pearson")
+  ) -> cor_teach_gender
+
+```
+
 ## Pr-teaching phase
@@
 
-```
-
-# Overall Plot (unstd./std.)
-```{r}
-df_heart_rate <- 
-  main %>% 
-  mutate(time = time / 60) %>% 
-  filter(time_span == "overall") %>%
-  dplyr::select("ID","time","heart_rate") %>% 
-  distinct() %>% 
-  mutate(type = "a. Heart Rate (in beats per minute)")
-
-df_heart_rate_std <- 
-  main %>% 
-  mutate(time = time / 60) %>% 
-  filter(time_span == "overall") %>%
-  dplyr::select("ID","time","heart_rate_std") %>% 
-  distinct() %>% 
-  transmute(ID,
-            time,
-            type = "b. Heart Rate (standardized)",
-            heart_rate = heart_rate_std)
-
-# left_join(x = df_heart_rate,
-#           y = df_heart_rate_std,
-#           by = c("ID","time")) %>% 
-bind_rows(df_heart_rate,
-          df_heart_rate_std
-          ) %>% 
-  ggplot(mapping = aes(x = time,
-                       y = heart_rate
-                       )
-         ) +
-  # geom_point(alpha = 0.05) + 
-  geom_smooth(se = T,
-              size = 0.5,
-              colour = "black",
-              level = 0.99) +
-  scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  # scale_x_continuous(expand = c(0, NA),
-  #                    breaks = seq(0, 120, 10)) +
-  scale_x_continuous(expand = c(0.01,0)) + 
-  labs(x = "Time (in minutes)",
-       #y = "Heart Rate (in Beats per Minute)",
-       y = "",
-       # title = "Figure #",
-       # subtitle = "Overall Course of Average Heartrate",
-#        caption = expression(paste(italic("Note: "),
-# "The shadow around the line represents the 99% confidence interval.
-The confidence interval shown refers to the HR measurement points during the entire study period.
-We used the ggplot2 package (v3.3.3; Wickham, 2016) to calculate the moving average of the course."))
-       ) +
-  #ggtitle("Overall Course of Average Heartrate") +
-  theme_apa() + 
-  # theme(plot.subtitle = element_text(face = "italic"),
-  #       plot.caption = element_text(hjust = 0),
-  #       axis.line = element_line(colour = "black"),
-  #       panel.grid.major = element_blank(),
-  #       panel.grid.minor = element_blank(),
-  #       panel.border = element_blank(),
-  #       panel.background = element_blank()) +
-  facet_wrap(~ type,
-             ncol = 2,
-             scales = "free_y")
-
-ggsave(filename = "plots_publication/loess_plot_std_unstd.png",
-       width = 16,
-       height = 12,
-       units = "cm")
-```
-
-# Mean Plot
-```{r}
-
-main %>% 
-  filter(time_span != "overall") %>%
-  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
-  mutate(time_span = factor(time_span,
-                            levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre-teaching\nInterval","Teaching\nInterval","Post-teaching\nInterval","Interview\nInterval","End\nInterval"))) %>% 
-  distinct() %>%
-  group_by(time_span) %>% 
-  summarise(z_mean = mean(heart_rate_std),
-            z_sd = sd(heart_rate_std),
-            z_t = qt(p = 0.01 / 2,      # 0.01 KI
-               df = n() - 1,
-               lower.tail = F
-               ),
-            z_error = z_sd / sqrt(n()),
-            lower = z_mean - z_t * z_error,
-            upper = z_mean + z_t * z_error,
-            ) %>% 
-  ungroup() %>% 
-  ggplot(mapping = aes(x = factor(0),
-                       y = z_mean)) + 
-  geom_point() +
-  geom_errorbar(mapping = aes(ymin = lower,
-                              ymax = upper),
-                width = 0.2) +
-  geom_hline(yintercept = 0,
-             linetype = "dashed") +
-  ylim(-1, 1) + 
-  scale_y_continuous(breaks=seq(-1, 1, 0.5), 
-                     limits=c(-1, 1)) + 
-  labs(x = "Time (in Minutes)",
-       y = "Standardized Mean Heart Rate",
-       # caption = expression(paste(italic("Note: "),
-       #                            "The shadow around the line represents the 99% confidence interval."
-       #                            )
-       #                      )
-       ) +
-  facet_grid(cols = vars(time_span),
-             scales = "free_x") +
-  theme_apa() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        plot.caption = element_text(hjust = 0))
-
-ggsave(filename = "plots_publication/mean_plot.png",
-       width = 20,
-       height = 12,
-       units = "cm")
 ```

### 2024-05-30 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

@@
 ```
-
+# Packages & read in data
 ```{r}
@@
       lavaan,
-      lm.beta)
+      lm.beta,
+      psych,
+      stats)
 
@@
 # Plots
-
 ```{r fig.width = 10,results='hide',fig.keep='all'}
@@
 ggsave(filename = "plots_publication/mean_plot.png",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+## Box Plot (over 81 participants) 
+box_plot <-
+  main %>% 
+  filter(time_span != "overall") %>%   
+  dplyr::select("ID",
+         "time_span",
+         "heart_rate_std") %>% 
+  mutate(time_span = fct_recode(time_span,
+                                "Pre-teaching Interval" = "pre",
+                                "Teaching Interval" = "main",
+                                "Post-teaching Interval" = "subsequent",
+                                "Interview Interval" = "interview",
+                                "End Interval" = "after"
+                                ),
+         time_span = factor(time_span,
+                            levels = c("Pre-teaching Interval",
+                                       "Teaching Interval",
+                                       "Post-teaching Interval",
+                                       "Interview Interval",
+                                       "End Interval"
+                                       ),
+                            labels = c("Pre-Teaching\nInterval",
+                                       "Teaching\nInterval",
+                                       "Post-Teaching\nInterval",
+                                       "Interview\nInterval",
+                                       "End\nInterval")
+                            )
+         ) %>%
+  distinct() %>% 
+  group_by(ID, time_span) %>%
+  summarise(mean_hr_std = 
+              mean(heart_rate_std, 
+                   na.rm = TRUE)
+            ) %>% 
+  ggplot(mapping = aes(x = time_span,
+                       y = mean_hr_std
+                       )
+         ) +
+  geom_boxplot()+
+  scale_y_continuous(breaks=seq(-2, 2, 1), 
+                     limits=c(-2, 2)
+                     ) +   
+  # geom_jitter(width = 0.2) +
+  theme_apa() + 
+  theme(axis.text.x = 
+          element_text(
+            color="black",
+            size = 12),
+        plot.caption = element_text(hjust = 0)
+        ) + 
+  labs(x = "",
+       y = "Standardized Mean Heart Rate",
+       caption = expression(
+         paste(italic("Note: N"), 
+               "= 81 participants per interval. Fig. shows median (bold line), interquartile range (box) and outliers (dots)."
+         )
+       ))
+
+box_plot
+
+ggsave(filename = "plots_publication/box_plot.png",
+       plot = box_plot,
        width = 20,
@@
 # Slopes and Intercepts
-
 ```{r}
@@
 ## using heart rate means
-
 ```{r}
@@
 ```
-
 ## Teaching vs. Pre-Teaching (mean HR)
@@
 ## Teaching vs. End (mean HR)
-
 ```{r}
@@
 
+## ANOVA & planned constrasts
+```{r}
+# Data wrangling - preparing data for ANOVA
+df_anova <-
+  main %>% 
+  filter(time_span != "overall") %>%   
+  dplyr::select("ID",
+         "time_span",
+         "heart_rate_std") %>% 
+  mutate(time_span = fct_recode(time_span,
+                                "Pre-teaching interval" = "pre",
+                                "Teaching interval" = "main",
+                                "Post-teaching interval" = "subsequent",
+                                "Interview interval" = "interview",
+                                "End interval" = "after"
+                                ),
+         time_span = factor(time_span,
+                            levels = c("Pre-teaching interval",
+                                       "Teaching interval",
+                                       "Post-teaching interval",
+                                       "Interview interval",
+                                       "End interval"
+                                       )
+                            )
+         ) %>%
+  distinct() %>% 
+  group_by(ID, time_span) %>%
+  summarise(mean_hr_std = mean(heart_rate_std, na.rm = TRUE))
+
+# Counting participants in individual phases
+table(df_anova['time_span'])
+
+# descriptive analysis
+describeBy(df_anova$mean_hr_std,
+           df_anova$time_span)
+
+# Visualization
+bxp <- ggboxplot(df_anova, x = "time_span", y = "mean_hr_std", add = "point")
+bxp
+
+# Check for outliers
+outliers <-
+  df_anova %>%
+  group_by(time_span) %>%
+  identify_outliers(mean_hr_std)
+
+# check for normality assumption --> can be checked by computing Shapiro-Wilk test for each time point. If the data is normally distributed, the p-value should be greater than 0.05
+norm_assump <-
+  df_anova %>%
+  group_by(time_span) %>%
+  shapiro_test(mean_hr_std)
+
+# QQ plot draws the correlation between a given data and the normal distribution. 
+plot <- 
+  ggqqplot(df_anova, "mean_hr_std", facet.by = "time_span")
+
+df_anova_subset <- subset(df_anova, select = c(time_span, mean_hr_std))
+
+# # anova
+# res.aov <- rstatix::anova_test(data = df_anova_subset,
+#                                dv = mean_hr,
+#                                wid = ,
+#                                within = time_span)
+# get_anova_table(res.aov)
+
+# anova
+df_anova_phase <- 
+  aov(df_anova_subset$mean_hr_std ~ df_anova_subset$time_span)
+summary(df_anova_phase)
+
+# effect size for ANOVA
+DescTools::EtaSq(df_anova_phase)
+f = sqrt (0.7202944/ (1-0.7202944))
+
+# planned constrasts
+model <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
+summary (model)
+
+contrast1 <- c(-1, 1, 0, 0, 0)
+contrast2 <- c(0, 1, -1, 0, 0)
+contrast3 <- c(0, 1, 0, -1, 0)
+contrast4 <- c(0, 1, 0, 0, -1)
+
+contrasts(df_anova_subset$time_span) <- cbind(contrast1,
+                                              contrast2,
+                                              contrast3,
+                                              contrast4)
+
+model2 <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
+summary(model2)
+
+summary.aov(model2, 
+            split = list (time_span = list ("Teaching interval vs. Pre-teaching interval" = 1,
+                                            "Teaching interval vs. Post-teaching interval" = 2,
+                                            "Teaching interval vs. Interview interval" = 3,
+                                            "Teaching interval vs. End interval" = 4
+                                            )
+                          )
+            )
+
+```
+
 # t-Tests 
 ## using mean Slope 
-
 ```{r}
@@
 ## Teaching vs. Interview (mean slope)
-
 ```{r}
@@
 ```
-
 ## Teaching vs. End (mean slope)
@@
 ## Interview vs. End (mean slope)
-
 ```{r}
@@
 ### Correlation 
-
 ## age x teaching experience
@@
 
-# Multiple Linear Regression (Mean)
+# Multiple Linear Regression (Mean) -- LOOP
 ```{r}
@@
 ```
-
-# Multiple Linear Regression (Slope)
+# Multiple Linear Regression (Slope) -- LOOP
 ```{r}
@@
 # Multiple Linear Regression (Slope)
-
 # Pre Teaching Phase
@@
 ```
-
 # Teaching Phase
@@
 # Interview Phase
-
 ```{r echo = FALSE, results='asis'}
@@
 # End Phase
-
 ```{r echo = FALSE, results='asis'}

### 2024-05-31 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

@@
 
+## Overall Plot (unstd. vs. std. over 81 participants)
+df_heart_rate <-
+  main %>%
+  mutate(time = time / 60) %>%
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate") %>%
+  distinct() %>%
+  group_by(ID) %>%
+  mutate(type = "a. Heart Rate (in beats per minute)") %>%
+  summarise(time = time,
+            mean_hr_unstd = mean(heart_rate,
+                                 na.rm = TRUE)
+            )
+
+df_heart_rate_std <-
+  main %>%
+  mutate(time = time / 60) %>%
+  filter(time_span == "overall") %>%
+  dplyr::select("ID","time","heart_rate_std") %>%
+  distinct() %>%
+  group_by(ID) %>%
+  summarise(time = time,
+            mean_hr_std = mean(heart_rate_std,
+                               na.rm = TRUE)
+            ) %>%
+  transmute(ID,
+            time,
+            type = "b. Heart Rate (standardized)",
+            heart_rate = mean_hr_std)
+
+loess_plot_std_unstd <-
+  bind_rows(df_heart_rate,
+            df_heart_rate_std
+          ) %>%
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  geom_smooth(se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.99) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0.01,0)) +
+  labs(x = "Time (in minutes)",
+       y = "",
+       ) +
+  theme_apa() +
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y")
+
+ggsave(filename = "plots_publication/loess_plot_std_unstd.png",
+       width = 16,
+       height = 12,
+       units = "cm")
+
 ## Mean Plot

### 2024-06-03 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

--- 2024-05-30 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
@@
   mutate(time_span = fct_recode(time_span,
-                                "Pre-teaching Interval" = "pre",
-                                "Teaching Interval" = "main",
-                                "Post-teaching Interval" = "subsequent",
+                                "Pre-teaching Interval" = "preparation",
+                                "Teaching Interval" = "teaching",
+                                "Post-teaching Interval" = "post",
                                 "Interview Interval" = "interview",
-                                "End Interval" = "after"
+                                "End Interval" = "end"
                                 ),
@@
   labs(x = "",
-       y = "Standardized Mean Heart Rate",
+       y = "Mean Standardized Heart Rate",
        caption = expression(
@@
   labs(x = "Time (in Minutes)",
-       y = "Standardized Mean Heart Rate",
+       y = "Mean Standardized Heart Rate",
        caption = expression(paste(italic("Note: "),

### 2024-06-05 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

--- 2024-05-30 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
@@
 
-main <-
+# single bpm values 
+main_single_hr <-
 map(.x = dir(path = data_path,
@@
 
-main <-
-  left_join(main, df_merge,
-            by = "ID")
-
-main <- 
-  main %>% 
-  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
-  distinct() %>% 
-  group_by(ID) %>% 
-  dplyr::summarise(mean_heart = mean(heart_rate),
-            sd_heart = sd(heart_rate)) %>%
-  ungroup() %>% 
-  right_join(x = .,
-             y = main,
-             by = "ID") %>% 
-  filter(!(time_span == "teaching" & time > 600)) %>%
-  mutate(heart_rate_std = (heart_rate - mean_heart)/
-           sd_heart)
+# multiple bpm values
+# 
+# main_single_hr <-
+#   left_join(main, 
+#             df_demo,
+#             by = "ID")
+# 
+# main_single_hr <- 
+#   main_single_hr %>% 
+#   dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
+#   distinct() %>% 
+#   group_by(ID) %>% 
+#   dplyr::summarise(mean_heart = mean(heart_rate),
+#             sd_heart = sd(heart_rate)) %>%
+#   ungroup() %>% 
+#   right_join(x = .,
+#              y = main,
+#              by = "ID") %>% 
+#   filter(!(time_span == "teaching" & time > 600)) %>%
+#   mutate(heart_rate_std = (heart_rate - mean_heart)/
+#            sd_heart)
+# 
+# main_single_hr <-
+# map(.x = dir(path = data_path,
+#              pattern = ".csv"),
+#     ~ read_csv(file.path(data_path, .), 
+#                id = "id",
+#                col_types = c("t","n")
+#                ) %>% 
+#   mutate(time = .$Time - min(.$Time),
+#          time = as.numeric(time),
+#          heart_rate = `Heart Rate`,
+#          ID = id,
+#          time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
+#                                str_detect(string = id, pattern = "_m") ~ "teaching",
+#                                str_detect(string = id, pattern = "_p") ~ "preparation",
+#                                str_detect(string = id, pattern = "_s") ~ "post",
+#                                str_detect(string = id, pattern = "_i") ~ "interview",
+#                                TRUE ~ "overall"
+#                                ),
+#          ID = str_extract(string = ID,
+#                           pattern = "[:digit:]{3}"),
+#          ID = as.numeric(ID)
+#       ) %>%
+#     # filter(time <= 600) %>% # filter for 10min intervals
+#     filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
+#     dplyr::select(!c("Time","Heart Rate","id"))
+#     ) %>%
+#   bind_rows()
+# 
+# 
+# main <-
+#   left_join(main, 
+#             df_demo,
+#             by = "ID")
+# 
+# main_single_hr <- 
+#   main_single_hr %>% 
+#   dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
+#   distinct() %>% 
+#   group_by(ID) %>% 
+#   dplyr::summarise(mean_heart = mean(heart_rate),
+#             sd_heart = sd(heart_rate)) %>%
+#   ungroup() %>% 
+#   right_join(x = .,
+#              y = main,
+#              by = "ID") %>% 
+#   filter(!(time_span == "teaching" & time > 600)) %>%
+#   mutate(heart_rate_std = (heart_rate - mean_heart)/
+#            sd_heart)
 
 ## count for individuals 
-main %>% 
+main_single_hr %>% 
   filter(time >= 7200) %>% 
@@
 # Mean, SD and range for overall (unstandardized)
-descrip_hr_overall <- main %>%
+descrip_hr_overall <- main_single_hr %>%
   filter(time_span %in% c("overall")) %>% 
@@
 # Mean, SD and range for overall (standardized)
-descrip_hr_overall_std <- main %>%
+descrip_hr_overall_std <- main_single_hr %>%
   filter(time_span %in% c("overall")) %>% 
@@
 # Mean, SD and range for individual phases (unstandardized)
-descrip_hr_phases <- main %>% 
+descrip_hr_phases <- main_single_hr %>% 
   filter(!time_span %in% c("overall")) %>% 
@@
 # Mean, SD and range for individual phases (standardized)
-descrip_hr_phases_std <- main %>% 
+descrip_hr_phases_std <- main_single_hr %>% 
   filter(!time_span %in% c("overall")) %>% 
@@
   summarise(N = n_distinct(ID),
-            "M heart rate in bpm" = round(mean(heart_rate_std),
+            "M heart rate std" = round(mean(heart_rate_std),
                                      digits = 2),
-            "SD heart rate in bpm" = round(sd(heart_rate_std),
+            "SD heart rate std" = round(sd(heart_rate_std),
                                       digits = 2),
-            "Min heart rate in bpm" = round(min(heart_rate_std),
+            "Min heart rate std" = round(min(heart_rate_std),
                                             digits = 2),
-            "Max heart rate in bpm" = round(max(heart_rate_std),
+            "Max heart rate std" = round(max(heart_rate_std),
                                             digits = 2)
@@
 ## Overall Course Plot (std. vs. unstd.)
+# data frame unstd. HR
 df_heart_rate <- 
-  main %>% 
+  main_single_hr %>% 
   mutate(time = time / 60) %>% 
@@
 
+# data frame std. HR
 df_heart_rate_std <- 
-  main %>% 
+  main_single_hr %>% 
   mutate(time = time / 60) %>% 
@@
             type = "b. Heart Rate (standardized)",
-            heart_rate = heart_rate_std)
-
+            heart_rate = heart_rate_std
+            )
+# bind data frames
 bind_rows(df_heart_rate,
           df_heart_rate_std
-          ) %>% 
+          ) -> df_hr_hr_std
+# plotting
+df_hr_hr_std %>% 
   ggplot(mapping = aes(x = time,
@@
              ncol = 2,
-             scales = "free_y")
+             scales = "free_y") -> loess_plot_std_unstd
+
+loess_plot_std_unstd
 
@@
 ## Mean Plot
-main %>% 
-  filter(time_span != "overall") %>%
-  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
-  mutate(time_span = factor(time_span,
-                            levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre-teaching\nInterval","Teaching\nInterval","Post-teaching\nInterval","Interview\nInterval","End\nInterval"))) %>% 
-  distinct() %>%
-  group_by(time_span) %>% 
-  summarise(z_mean = mean(heart_rate_std),
-            z_sd = sd(heart_rate_std),
-            z_t = qt(p = 0.05 / 2,      # 0.05 KI
-               df = n() - 1,
-               lower.tail = F
-               ),
-            z_error = z_sd / sqrt(n()),
-            lower = z_mean - z_t * z_error,
-            upper = z_mean + z_t * z_error,
-            ) %>% 
-  ungroup() %>% 
-  ggplot(mapping = aes(x = factor(0),
-                       y = z_mean)) + 
-  geom_point() +
-  geom_errorbar(mapping = aes(ymin = lower,
-                              ymax = upper),
-                width = 0.2) +
-  geom_hline(yintercept = 0,
-             linetype = "dashed") +
-  ylim(-1.5, 1.5) + 
-  scale_y_continuous(breaks=seq(-1.5, 1.5, 0.5), 
-                     limits=c(-1.5, 1.5)
-                     ) + 
-  labs(x = "Time (in Minutes)",
-       y = "Standardized Mean Heart Rate",
-       # caption = expression(paste(italic("Note: "),
-       #                            "The shadow around the line represents the 95% confidence interval."
-       #                            )
-       #                      )
-       ) +
-  facet_grid(cols = vars(time_span),
-             scales = "free_x") +
-  theme_apa() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        plot.caption = element_text(hjust = 0))
-
-ggsave(filename = "plots_publication/mean_plot.png",
-       width = 20,
-       height = 12,
-       units = "cm")
+# main_single_hr %>% 
+#   filter(time_span != "overall") %>%
+#   dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
+#   mutate(time_span = factor(time_span,
+#                             levels = c("preparation","teaching","post","interview","end"),
+#                             labels = c("Pre-teaching\nInterval","Teaching\nInterval","Post-teaching\nInterval","Interview\nInterval","End\nInterval"))) %>% 
+#   distinct() %>%
+#   group_by(time_span) %>% 
+#   summarise(z_mean = mean(heart_rate_std),
+#             z_sd = sd(heart_rate_std),
+#             z_t = qt(p = 0.05 / 2,      # 0.05 KI
+#                df = n() - 1,
+#                lower.tail = F
+#                ),
+#             z_error = z_sd / sqrt(n()),
+#             lower = z_mean - z_t * z_error,
+#             upper = z_mean + z_t * z_error,
+#             ) %>% 
+#   ungroup() %>% 
+#   ggplot(mapping = aes(x = factor(0),
+#                        y = z_mean)) + 
+#   geom_point() +
+#   geom_errorbar(mapping = aes(ymin = lower,
+#                               ymax = upper),
+#                 width = 0.2) +
+#   geom_hline(yintercept = 0,
+#              linetype = "dashed") +
+#   ylim(-1.5, 1.5) + 
+#   scale_y_continuous(breaks=seq(-1.5, 1.5, 0.5), 
+#                      limits=c(-1.5, 1.5)
+#                      ) + 
+#   labs(x = "Time (in Minutes)",
+#        y = "Standardized Mean Heart Rate",
+#        # caption = expression(paste(italic("Note: "),
+#        #                            "The shadow around the line represents the 95% confidence interval."
+#        #                            )
+#        #                      )
+#        ) +
+#   facet_grid(cols = vars(time_span),
+#              scales = "free_x") +
+#   theme_apa() +
+#   theme(axis.text.x = element_blank(),
+#         axis.ticks.x = element_blank(),
+#         plot.caption = element_text(hjust = 0))
+# 
+# ggsave(filename = "plots_publication/mean_plot.png",
+#        width = 20,
+#        height = 12,
+#        units = "cm")
 
@@
 box_plot <-
-  main %>% 
+  main_single_hr %>% 
   filter(time_span != "overall") %>%   
@@
 lm_plot <-
-  main %>%
+  main_single_hr %>%
   filter(time_span != "overall") %>%
@@
 df_regression <- 
-  main %>% 
+  main_single_hr %>% 
   filter(time_span != "overall") %>%
@@
 df_anova <-
-  main %>% 
+  main_single_hr %>% 
   filter(time_span != "overall") %>%   
@@
   mutate(time_span = fct_recode(time_span,
-                                "Pre-teaching interval" = "pre",
-                                "Teaching interval" = "main",
-                                "Post-teaching interval" = "subsequent",
+                                "Pre-teaching interval" = "preparation",
+                                "Teaching interval" = "teaching",
+                                "Post-teaching interval" = "post",
                                 "Interview interval" = "interview",
-                                "End interval" = "after"
+                                "End interval" = "end"
                                 ),
@@
 
-# # anova
-# res.aov <- rstatix::anova_test(data = df_anova_subset,
-#                                dv = mean_hr,
-#                                wid = ,
-#                                within = time_span)
-# get_anova_table(res.aov)
-
 # anova
@@
 
-summary.aov(model2, 
+summary.lm(model2, 
             split = list (time_span = list ("Teaching interval vs. Pre-teaching interval" = 1,
@@
             )
+
+# effect size of pairwise comparisons
+library(dplyr)
+library(rstatix)
+effect_size_pwc <-
+  df_anova_subset %>%
+  cohens_d(mean_hr_std ~ time_span) %>% 
+  as.data.frame()
 

### 2024-06-06 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

@@
 
-# single bpm values 
+# single bpm values (data frame with only single measurement point)
 main_single_hr <-
@@
 
-# multiple bpm values
-# 
-# main_single_hr <-
-#   left_join(main, 
-#             df_demo,
-#             by = "ID")
-# 
-# main_single_hr <- 
-#   main_single_hr %>% 
-#   dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
-#   distinct() %>% 
-#   group_by(ID) %>% 
-#   dplyr::summarise(mean_heart = mean(heart_rate),
-#             sd_heart = sd(heart_rate)) %>%
-#   ungroup() %>% 
-#   right_join(x = .,
-#              y = main,
-#              by = "ID") %>% 
-#   filter(!(time_span == "teaching" & time > 600)) %>%
-#   mutate(heart_rate_std = (heart_rate - mean_heart)/
-#            sd_heart)
-# 
-# main_single_hr <-
-# map(.x = dir(path = data_path,
-#              pattern = ".csv"),
-#     ~ read_csv(file.path(data_path, .), 
-#                id = "id",
-#                col_types = c("t","n")
-#                ) %>% 
-#   mutate(time = .$Time - min(.$Time),
-#          time = as.numeric(time),
-#          heart_rate = `Heart Rate`,
-#          ID = id,
-#          time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
-#                                str_detect(string = id, pattern = "_m") ~ "teaching",
-#                                str_detect(string = id, pattern = "_p") ~ "preparation",
-#                                str_detect(string = id, pattern = "_s") ~ "post",
-#                                str_detect(string = id, pattern = "_i") ~ "interview",
-#                                TRUE ~ "overall"
-#                                ),
-#          ID = str_extract(string = ID,
-#                           pattern = "[:digit:]{3}"),
-#          ID = as.numeric(ID)
-#       ) %>%
-#     # filter(time <= 600) %>% # filter for 10min intervals
-#     filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
-#     dplyr::select(!c("Time","Heart Rate","id"))
-#     ) %>%
-#   bind_rows()
-# 
-# 
-# main <-
-#   left_join(main, 
-#             df_demo,
-#             by = "ID")
-# 
-# main_single_hr <- 
-#   main_single_hr %>% 
-#   dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
-#   distinct() %>% 
-#   group_by(ID) %>% 
-#   dplyr::summarise(mean_heart = mean(heart_rate),
-#             sd_heart = sd(heart_rate)) %>%
-#   ungroup() %>% 
-#   right_join(x = .,
-#              y = main,
-#              by = "ID") %>% 
-#   filter(!(time_span == "teaching" & time > 600)) %>%
-#   mutate(heart_rate_std = (heart_rate - mean_heart)/
-#            sd_heart)
+# adding z-standardized HR
+main_single_hr <-
+  main_single_hr %>%
+  dplyr::select("time", "heart_rate", "ID", "time_span") %>%
+  distinct() %>%
+  group_by(ID) %>%
+  dplyr::summarise(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>%
+  right_join(x = .,
+             y = main_single_hr,
+             by = "ID") %>%
+  filter(!(time_span == "teaching" & time > 600)) %>%
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart)
 
@@
 ```{r}
-main %>% 
+
+# multiple bpm values (merged data frame for multiple regression with multiple measurement points)
+main_multiple_hr <-
+  left_join(main_single_hr,
+            df_merge,
+            by = "ID")
+
+main_multiple_hr %>% 
   group_by(ID, time_span) %>% 

### 2024-06-24 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier/FitBit_elsevier/FitBit_elsevier.Rmd
tabellen

@@
     keep_tex: true
-    citation_package: default
+    citation_package: natbib
+header-includes:
+  - \usepackage{tabularx}
 ---
 
-```{r analysis-preferences}
+```{r analysis-preferences, include=FALSE}
 # Seed for random number generation
@@
       lme4,
-      viridis)
+      viridis, 
+      stargazer)
 ```
@@
 # disruption & confidence rating
+
 df_rating <- 
   excel_sheets("data/Coding_SRI.xlsx") %>% 
-  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
+  map_df(~ read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
   dplyr::select(ID, # select relevant columns 
-         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
-         confidence_factor,
-         event
-         ) %>% 
-  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
-                    "132",
-                    "236")
+         "disruption_factor", # -99 = subject did not notice event; -100 = experimenter did not asked for event
+         "confidence_factor",
+         "event"
          ) %>% 
@@
 # demographic data
-df_demo_all <- 
+
+df_demo <- 
   read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
   transmute(ID = LI06_05, # select and rename relevant columns 
-            # gender = factor(LI02_01_1,
-            #                 levels = 1:2,
-            #                 labels = c("male","female")
-            #                 ),
-            gender = LI02_01_1, # 1 = male; 2 = female
-            age = LI03_01, 
-            teaching_experience = LI04_01,
-            school_type = LI18,
-            term = LI11_01,
-            extracurricular_teaching_experience = LI14,
-            secondary_teaching_activities = LI17) %>% 
-  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
-                    "132",
-                    "236")
-        )
+            gender = factor(LI02_01_1,
+                            levels = 1:2,
+                            labels = c("male","female")
+                            ),
+            age = LI03_01, # 1 = male; 2 = female
+            teaching_experience = LI04_01)
 
 # merge two data frames by ID
-df_merge <- merge(df_demo_all,
+
+df_merge <- merge(df_demo,
                   df_rating,
-                  by = "ID")
+                  by = "ID") %>% 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132")
+         )
 
@@
 
-data_path <- "./data/heart_rate_data"
+data_path <- "data/heart_rate_data"
 
@@
          ID = id,
-         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end_phase",
-                               str_detect(string = id, pattern = "_m") ~ "teaching_phase",
-                               str_detect(string = id, pattern = "_p") ~ "pre-teaching_phase",
-                               str_detect(string = id, pattern = "_s") ~ "post-teaching_phase",
-                               str_detect(string = id, pattern = "_i") ~ "interview_phase",
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
+                               str_detect(string = id, pattern = "_m") ~ "teaching",
+                               str_detect(string = id, pattern = "_p") ~ "preparation",
+                               str_detect(string = id, pattern = "_s") ~ "post",
+                               str_detect(string = id, pattern = "_i") ~ "interview",
                                TRUE ~ "overall"
@@
     # filter(time <= 600) %>% # filter for 10min intervals
-    filter(time <= 7200) %>% # filter for 2 hours 30min (maximal duration of study)
+    filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
     dplyr::select(!c("Time","Heart Rate","id"))
@@
   dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
-  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
-                    "132",
-                    "236")
-        ) %>% 
   distinct() %>% 
   group_by(ID) %>% 
-  summarize(mean_heart = mean(heart_rate),
+  dplyr::summarise(mean_heart = mean(heart_rate),
             sd_heart = sd(heart_rate)) %>%
@@
              by = "ID") %>% 
+  filter(!(time_span == "teaching" & time > 600)) %>%
   mutate(heart_rate_std = (heart_rate - mean_heart)/
-           sd_heart) %>% 
-  filter(!(time_span == "teaching" & time > 600))
+           sd_heart)
+```
 
+```{r descriptives, include=FALSE}
+# Mean, SD and range for overall (unstandardized)
+
+descrip_hr_overall <- main %>%
+  filter(time_span %in% c("overall")) %>% 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate),
+                                      digits = 2),
+            "Min heart rate in bpm" = min(heart_rate),
+            "Max heart rate in bpm" = max(heart_rate)
+  )
+
+# Mean, SD and range for overall (standardized)
+
+descrip_hr_overall_std <- main %>%
+  filter(time_span %in% c("overall")) %>% 
+  summarise(N = n_distinct(ID),
+            "M std heart rate in bpm" = round(mean(heart_rate_std),
+                                              digits = 2),
+            "SD std heart rate in bpm" = round(sd(heart_rate_std),
+                                               digits = 2),
+            "Min std heart rate in bpm" = round(min(heart_rate_std),
+                                                digits = 2),
+            "Max heart rate in bpm" = round(max(heart_rate_std),
+                                            digits = 2)
+            )
+
+# Mean, SD and range for individual phases (unstandardized)
+
+descrip_hr_phases <- main %>% 
+  filter(!time_span %in% c("overall")) %>% 
+  group_by(time_span) %>% 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate),
+                                      digits = 2),
+            "Min heart rate in bpm" = min(heart_rate),
+            "Max heart rate in bpm" = max(heart_rate)
+  )
+
+# Mean, SD and range for individual phases (standardized)
+
+descrip_hr_phases_std <- main %>% 
+  filter(!time_span %in% c("overall")) %>% 
+  group_by(time_span) %>% 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate_std),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate_std),
+                                      digits = 2),
+            "Min heart rate in bpm" = round(min(heart_rate_std),
+                                            digits = 2),
+            "Max heart rate in bpm" = round(max(heart_rate_std),
+                                            digits = 2)
+  )
+
+# # format and insert table in manuscript
+# descrip_hr_phases %>%
+# papaja::apa_table(
+#   caption = "Mean, SD and range for teachers' heart rate in individual phases",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+#   )
+
+# Mean, SD and range for disruption and confidence factor
+
+rating_table <- 
+  df_rating %>% 
+  filter(!is.na(confidence_factor),
+         !is.na(disruption_factor)) %>% 
+   summarise(N = n_distinct(ID), 
+            "M disruption factor" = round(mean(disruption_factor),
+                                     digits = 2),
+            "SD disruption factor" = round(sd(disruption_factor),
+                                      digits = 2),
+            "Min disruption factor" = min(disruption_factor),
+            "Max disruption factor" = max(disruption_factor),
+            "M confidence factor" = round(mean(confidence_factor),
+                                     digits = 2),
+            "SD confidence factor" = round(sd(confidence_factor),
+                                      digits = 2),
+            "Min confidence factor" = min(confidence_factor),
+            "Max confidence factor" = max(confidence_factor)
+            )
+```
+
+```{r, include=FALSE}
+
+desc_hr_phases <- bind_rows(x = descrip_hr_overall,
+                            y = descrip_hr_phases) |> 
+  select(-N) |> 
+  rename(`M HR` = `M heart rate in bpm`,
+         `SD HR` = `SD heart rate in bpm`,
+         `Min` = `Min heart rate in bpm`,
+         `Max` = `Max heart rate in bpm`,
+         Interval = time_span) |> 
+  select(c(Interval,
+           `M HR`,
+           `SD HR`,
+           `Min`,
+           `Max`)
+         )
+
+descrip_hr_overall_std <- descrip_hr_overall_std |> 
+  rename(`M HR` = `M std heart rate in bpm`,
+         `SD HR` = `SD std heart rate in bpm`,
+         `Min` = `Min std heart rate in bpm`,
+         `Max` = `Max heart rate in bpm`,
+          ) |> 
+  mutate(Interval = 'overall')
+
+descrip_hr_phases_std <-  descrip_hr_phases_std |> 
+  rename(`M HR` = `M heart rate in bpm`,
+         `SD HR` = `SD heart rate in bpm`,
+         `Min` = `Min heart rate in bpm`,
+         `Max` = `Max heart rate in bpm`,
+         Interval = time_span)
+
+desc_hr_phases_std <- bind_rows(x = descrip_hr_overall_std,
+                                y = descrip_hr_phases_std) |> 
+  select(-N) |> 
+    select(c(Interval,
+           `M HR`,
+           `SD HR`,
+           `Min`,
+           `Max`)
+         )
+
+desc_hr_phases[1, 1] <- 'overall'
+
+df_desc_hr <- desc_hr_phases |> 
+  mutate(across(everything(),
+                ~ paste(.,
+                        desc_hr_phases_std[[cur_column()]],
+                        sep = "/")
+                )
+         ) #|> 
+  # # rename(`\textit{M} HR` = `M HR`,
+  #        # `\textit{SD} HR` = `SD HR`,
+  #        # `\textit{Min}` = `Min`,
+  #        `\textit{Max}` = `Max`,
+  #       `\textit{Interval}` = Interval)
+
+df_desc_hr$Interval <- c('Overall Course of 2h',
+                         'Pre-teaching interval',
+                         'Teaching interval',
+                         'Post-teaching interval',
+                         'Interview interval',
+                         'End Interval')
+
+names(df_desc_hr) <- paste0("\\textit{", names(df_desc_hr),"}")
+
+stargazer(df_desc_hr,
+          type = 'latex',
+          out = 'tab_1.tex',
+          summary = FALSE,
+          rownames = FALSE,
+          table.placement = 'h',
+          align = FALSE
+          ) -> tab_1
+
+pattern <- "textit\\\\\\{([^}]*)\\\\\\}"
+replacement <- "\textit{\\1}"
+
+# Anwenden des Regex
+tab_1_new <- str_replace_all(tab_1, pattern, replacement)
+
+paste(tab_1_new, collapse = '')
+
+writeLines(tab_1_new, 'tab_1.tex')
+
+```
+
+```{=latex}
+\input{tab_1.tex}
 ```

### 2024-06-24 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier/FitBit_elsevier/FitBit_elsevier.tex
tabellen

@@
 \IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\usepackage[]{natbib}
+\bibliographystyle{plainnat}
 
@@
 
-% Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{tabularx}
 
@@
 
-\hypertarget{present-investigation}{%
-\section{Present investigation}\label{present-investigation}}
+% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy Institute. E-mail: marek.hlavac at gmail.com
+% Date and time: Mo, Jun 24, 2024 - 16:22:09
+
+\\begin{table}[h] 
+\\centering 
+\\caption{} 
+\\label{}
+\\begin{tabular}{@{
+\\extracolsep{5pt}} ccccc} \\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex] \\textbackslash \textit{Interval} & \\textbackslash \textit{M HR} & \\textbackslash \textit{SD HR} & \\textbackslash \textit{Min} & \\textbackslash \textit{Max} \\\\ \\hline \\\\[-1.8ex] Overall Course of 2h & 90.09/-0.04 & 15.76/0.99 & 51/-4.03 & 164/4.56 \\\\ Pre-teaching interval & 77.95/-1.07 & 11.14/0.57 & 50/-2.68 & 120/2.96 \\\\ Teaching interval & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\\\ Post-teaching interval & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\\\ Interview interval & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\\\ End Interval & 100.8/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\\\ \\hline \\\\[-1.8ex]
+\\end{tabular}
+\\end{table}
+
+%\input{tab_1.tex}
+
+\section{Present investigation}\label{present-investigation}
 
@@
 According to previous findings that fitness trackers can be used as a
-low-cost, non-invasive method of measuring HR (\textbf{hajj2022wrist?};
-Fuller et al. 2020) and that different HRs of teachers can be measured
-in different teaching phases (\textbf{donker2020associations?};
-\textbf{junker2021potential?}), we formulate the hypotheses as follows:
+low-cost, non-invasive method of measuring HR
+\citep{hajj2022wrist, fuller2020reliability} and that different HRs of
+teachers can be measured in different teaching phases
+\citep{donker2020associations, junker2021potential}, we formulate the
+hypotheses as follows:
 
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-fuller2020reliability}{}}%
-Fuller, Daniel, Emily Colwell, Jonathan Low, Kassia Orychock, Melissa
-Ann Tobin, Bo Simango, Richard Buote, et al. 2020. {``Reliability and
-Validity of Commercially Available Wearable Devices for Measuring Steps,
-Energy Expenditure, and Heart Rate: Systematic Review.''} \emph{JMIR
-mHealth and uHealth} 8 (9): e18694.
-
-\end{CSLReferences}
+\renewcommand\refname{References}
+\bibliography{r-references.bib}
 

### 2024-06-25 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier/FitBit_elsevier/FitBit_elsevier.Rmd
tabellen

@@
   - \usepackage{tabularx}
+  - \usepackage{threeparttable}
+  - \usepackage{booktabs}
 ---
@@
       viridis, 
-      stargazer)
+      stargazer,
+      papaja)
 ```
@@
 
-```{r, include=FALSE}
+```{r table_1, include=FALSE}
 
@@
                 )
-         ) #|> 
-  # # rename(`\textit{M} HR` = `M HR`,
-  #        # `\textit{SD} HR` = `SD HR`,
-  #        # `\textit{Min}` = `Min`,
-  #        `\textit{Max}` = `Max`,
-  #       `\textit{Interval}` = Interval)
+         )
 
@@
 
-names(df_desc_hr) <- paste0("\\textit{", names(df_desc_hr),"}")
+tab_1 <- apa_table(df_desc_hr,
+                   placement = 'h',
+                   )
 
-stargazer(df_desc_hr,
-          type = 'latex',
-          out = 'tab_1.tex',
-          summary = FALSE,
-          rownames = FALSE,
-          table.placement = 'h',
-          align = FALSE
-          ) -> tab_1
-
-pattern <- "textit\\\\\\{([^}]*)\\\\\\}"
-replacement <- "\textit{\\1}"
-
-# Anwenden des Regex
-tab_1_new <- str_replace_all(tab_1, pattern, replacement)
-
-paste(tab_1_new, collapse = '')
-
-writeLines(tab_1_new, 'tab_1.tex')
+writeLines(tab_1, 'tab_1.tex')
 

### 2024-07-03 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier/FitBit_elsevier/FitBit_elsevier.tex

@@
 \usepackage{tabularx}
+\usepackage{threeparttable}
+\usepackage{booktabs}
 
@@
 
-% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy Institute. E-mail: marek.hlavac at gmail.com
-% Date and time: Mo, Jun 24, 2024 - 16:22:09
-
-\\begin{table}[h] 
-\\centering 
-\\caption{} 
-\\label{}
-\\begin{tabular}{@{
-\\extracolsep{5pt}} ccccc} \\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex] \\textbackslash \textit{Interval} & \\textbackslash \textit{M HR} & \\textbackslash \textit{SD HR} & \\textbackslash \textit{Min} & \\textbackslash \textit{Max} \\\\ \\hline \\\\[-1.8ex] Overall Course of 2h & 90.09/-0.04 & 15.76/0.99 & 51/-4.03 & 164/4.56 \\\\ Pre-teaching interval & 77.95/-1.07 & 11.14/0.57 & 50/-2.68 & 120/2.96 \\\\ Teaching interval & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\\\ Post-teaching interval & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\\\ Interview interval & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\\\ End Interval & 100.8/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\\\ \\hline \\\\[-1.8ex]
-\\end{tabular}
-\\end{table}
-
-%\input{tab_1.tex}
+\input{tab_1.tex}
 

### 2024-07-04 02_paper/02_study/01_fitbit paper/R_scripts/presentation_analysis_std.Rmd
expertise paper

--- 2023-04-20 02_paper/02_study/02_fitbit paper/presentation_analysis_std.Rmd
@@
 needs(ltm,
-      xtable,
       broom,
@@
       lm.beta,
+      tidyverse,
       janitor,
@@
       gridExtra,
-      gridtext,
-      magrittr,
-      tidyverse)
+      gridtext)
 
@@
 
-## Interview
+1. rohwert-kurve neben z-std.-kurve (untereinander)
+2. Slope und Intercept mit je Mean und SD (overall aus individuell?) -> sign?
+3. Unterricht vs. Post (t-test über Intercepts), d und p
+4. Intercept (Teaching, interview, Post) vorhersage (4 Modelle)
+5. Unterscheiden sich slopes in pre und subsequent signifikant (Betrag?)
+6. Slopes (pre-Phase und subsequent) vorhersagen (4 Modelle)
+7. slope und intercept correlation?
 
-```{r}
-fit_interview_1 <-
-  df_test_reg %>% 
-  filter(time_span == "interview") %$% 
-  lm(intercept ~ mean_disruption)
-
-fit_interview_2 <-
-  df_test_reg %>% 
-  filter(time_span == "interview") %$% 
-  lm(intercept ~ mean_confidence)
-
-fit_interview_3 <-
-  df_test_reg %>% 
-  filter(time_span == "interview") %$% 
-  lm(intercept ~ mean_confidence + mean_disruption)
-
-fit_interview_4 <-
-  df_test_reg %>% 
-  filter(time_span == "interview") %$% 
-  lm(intercept ~ mean_confidence + mean_disruption + teaching_experience)
-
-stargazer::stargazer(fit_interview_1, fit_interview_2, fit_interview_3, fit_interview_4,
-                     type = "latex",
-                     dep.var.labels = "Intercept",
-                     order = c(1, 3, 2),
-                     covariate.labels = c("Disruption Factor",
-                                          "Confidence Factor",
-                                          "Teaching Experience"),
-                     keep.stat = c("n","rsq","adj.rsq")
-                     )
-```
-
-## Post
-
-```{r}
-fit_post_1 <-
-  df_test_reg %>% 
-  filter(time_span == "subsequent") %$% 
-  lm(intercept ~ mean_disruption)
-
-fit_post_2 <-
-  df_test_reg %>% 
-  filter(time_span == "subsequent") %$% 
-  lm(intercept ~ mean_confidence)
-
-fit_post_3 <-
-  df_test_reg %>% 
-  filter(time_span == "subsequent") %$% 
-  lm(intercept ~ mean_confidence + mean_disruption)
-
-fit_post_4 <-
-  df_test_reg %>% 
-  filter(time_span == "subsequent") %$% 
-  lm(intercept ~ mean_confidence + mean_disruption + teaching_experience)
-
-stargazer::stargazer(fit_post_1, fit_post_2, fit_post_3, fit_post_4,
-                     type = "latex",
-                     dep.var.labels = "Intercept",
-                     order = c(1, 3, 2),
-                     covariate.labels = c("Disruption Factor",
-                                          "Confidence Factor",
-                                          "Teaching Experience"),
-                     keep.stat = c("n","rsq","adj.rsq")
-                     )
-```
+1. Pre Phase
+2. Teaching Phase
+3. Post Phase
+4. Interview Phase
+5. End Phase

### 2024-07-04 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
expertise paper

--- 2024-04-17 02_paper/02_study/02_fitbit paper/Submission/FitBit_submission.Rmd
@@
 ---
-title: Title here
-subtitle: Do you have a subtitle? If so, write it here
-titlerunning: Short form of title (if too long for head)
-authorrunning:
-  Short form of author list if too long for running head
-thanks: |
-  Grants or other notes about the article that should go
-  on the front page should be placed here. General
-  acknowledgments should be placed at the end of the article.
-authors:
-  - name: Author 1
-    address: Department of YYY, University of XXX
-    email: abc@def
-  - name: Author 2
-    address: Department of ZZZ, University of WWW
-    email: djf@wef
+title: "New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?"
+shorttitle: "Using fitbit to measure teachers' heart rate"
+authornote: |
+ We received funding from QualiFond of University Leipzig.
+We have no conflicts of interest to disclose.
+This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).
+author:
+  - name: Mandy Klatt
+    email: mandy.klatt@uni-leipzig.de
+    affiliation: Leipzig University
+    correspondingauthor: true
+    footnote: 1
+  - name: Peer Keßler
+    email: Peer@example.com
+    affiliation: Leipzig University
+    footnote: 2
+  - name: Gregor Kachel
+    email: gregor@example.com
+    affiliation: Leipzig University, Max Planck Institute for Evolutionary Anthropology
+    footnote: 1
+  - name: Christin Lotz
+    email: christin@example.com
+    affiliation: Leipzig University
+    footnote: 1
+  - name: Anne Deiglmayr
+    email: anne@example.com
+    affiliation: Leipzig University
+    footnote: 3
+address:
+  - code: Leipzig University
+    organization: Empirische Schul- und Unterrichtsforschung
+    addressline: Marschnerstr. 29
+    city: Leipzig
+    state: Sachsen
+    postcode: 04109
+    country: Germany
+  - code: Max Planck Institute for Evolutionary Anthropology
+    organization: Department
+    addressline: Deutscher Pl. 6
+    postcode: 04103
+    city: Leipzig
+    state: Sachsen
+    country: Germany
+footnote:
+  - code: 1
+    text: 
+      - "Conceptualization"
+      - "Writing - Original Draft Preparation"
+      - "Writing - Review & Editing"
+  - code: 2
+    text: 
+      - "Writing - Original Draft Preparation"
+      - "Writing - Review & Editing"
+  - code: 3
+    text: "Supervision"
+abstract: |
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  XXX In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress.
+XXX
+
+  <!-- https://tinyurl.com/ybremelq -->
 keywords: 
-  - key
-  - dictionary
-  - word
-MSC:
-  - MSC code 1
-  - MSC code 2    
-abstract: |
-  The text of your abstract.  150 -- 250 words.
+  - heart rate
+  - photoplethysmography
+  - wearable electronic device
+  - teaching
+journal: "Computers & Education"
+date: "`r Sys.Date()`"
+classoption: preprint, 3p, authoryear
 bibliography: r-references.bib
-csl: computers-and-education.csl
-output: rticles::elsevier_article
+linenumbers: false
+numbersections: true
+output: 
+  rticles::elsevier_article:
+    keep_tex: true
+    citation_package: natbib
+header-includes:
+  - \usepackage{tabularx}
+  - \usepackage{threeparttable}
+  - \usepackage{booktabs}
 ---
@@
 
+```{r installing packages, include=FALSE}
+
+library(needs)
+needs(ltm,
+      broom,
+      ppcor,
+      jtools,
+      lm.beta,
+      tidyverse,
+      janitor,
+      lubridate,
+      readxl,
+      ggthemes,
+      gridExtra,
+      imputeTS,
+      DescTools,
+      cowplot,
+      rstatix,
+      ggpubr,
+      lme4,
+      viridis, 
+      stargazer,
+      papaja)
+```
+
 # Introduction
 
-In education, there’s interest in identifying reliable indicators for teacher stress and burnout [@fisher2011; @ junker2021].
+In education, there’s interest in identifying reliable indicators for teacher stress and burnout [@fisher2011; @junker2021].
 Previous research often relied on self-report questionnaires [@chaplain2008; @liu2020], which may be prone to biases like social desirability [@razavi2001self] or recall errors [@van2016accuracy].
@@
 
+```{r data wrangling, include=FALSE}
+
+# disruption & confidence rating
+
+df_rating <- 
+  excel_sheets("data/Coding_SRI.xlsx") |> 
+  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) |> # read in data with two sheets
+  dplyr::select(ID, # select relevant columns 
+         "disruption_factor", # -99 = subject did not notice event; -100 = experimenter did not asked for event
+         "confidence_factor",
+         "event"
+         ) |> 
+  mutate(disruption_factor = ifelse(disruption_factor < 0,
+                                    yes = NA,
+                                    no = disruption_factor
+                                    ),
+         confidence_factor = ifelse(confidence_factor < 0,
+                                   yes = NA,
+                                   no = confidence_factor),
+         event = as_factor(event)
+         )
+
+# demographic data
+
+df_demo <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") |> # read in excel 
+  transmute(ID = LI06_05, # select and rename relevant columns 
+            gender = factor(LI02_01_1,
+                            levels = 1:2,
+                            labels = c("male","female")
+                            ),
+            age = LI03_01, # 1 = male; 2 = female
+            teaching_experience = LI04_01)
+
+# merge two data frames by ID
+
+df_merge <- merge(df_demo,
+                  df_rating,
+                  by = "ID") |> 
+  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
+                    "132")
+         )
+
+# rm(list = c("df_demo","df_rating"))
+
+data_path <- "./data/heart_rate_data"
+
+main <-
+map(.x = dir(path = data_path,
+             pattern = ".csv"),
+    ~ read_csv(file.path(data_path, .), 
+               id = "id",
+               col_types = c("t","n")
+               ) |> 
+  mutate(time = Time - min(Time),
+         time = as.numeric(time),
+         heart_rate = `Heart Rate`,
+         ID = id,
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
+                               str_detect(string = id, pattern = "_m") ~ "teaching",
+                               str_detect(string = id, pattern = "_p") ~ "preparation",
+                               str_detect(string = id, pattern = "_s") ~ "post",
+                               str_detect(string = id, pattern = "_i") ~ "interview",
+                               TRUE ~ "overall"
+                               ),
+         ID = str_extract(string = ID,
+                          pattern = "[:digit:]{3}"),
+         ID = as.numeric(ID)
+      ) |>
+    # filter(time <= 600) |> # filter for 10min intervals
+    filter(time <= 7200) |> # filter for 2 hours (maximal duration of study)
+    dplyr::select(!c("Time","Heart Rate","id"))
+    ) |>
+  bind_rows()
+
+main <-
+  left_join(main, df_merge,
+            by = "ID")
+
+main <- 
+  main %>% 
+  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  dplyr::summarise(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  filter(!(time_span == "teaching" & time > 600)) %>%
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart)
+
+N_prewrangling <- as.numeric(nrow(df_demo))
+
+N_postwrangling <- as.numeric(length(unique(main$ID)))
+
+```
+
 # Method
@@
 Regarding the teachers’ HR trend, we displayed the HR trend over the course of the entire study.
-For z-standardization as a method to account for individual differences in the baseline HR, we visually compared unstandardized and standardized mean HR trends for the entire two-hours study.
+For z-standardization as a method to account for individual differences in the baseline HR, we visually compared unstandardized and standardized mean HR trends for the entire two-hours study[^3].
+For all further analyses, we used standardized rather than unstandardized HR values.
+[^3]:   Note that the study exceeded the planned duration of two hours for a few participants.
+To avoid distortions when mapping the HR over the course of the study (see Fig.
+3), the endpoint was set at two hours for all participants, even though data from later time points was used in the *end interval* for a few participants.
+
 For testing Hypothesis 1a, which examined the HR levels in the different intervals, we initially conducted a one-way ANOVA with repeated measures as an omnibus test.
@@
 We repeated these steps to explore the effect of teaching experience and subjective appraisals on changes in teachers’ HR at each interval.
+
+# Results
+
+## Research goal 1: Mapping teachers’ HR over the course of the study phases
+
+The first part of our first research goal was to map participants’ overall HR trend and explore whether z-standardization of participants’ HR is a useful method to account for individual differences in the baseline HR.
+Means, standard deviations, and range of teachers’ unstandardized and standardized HR are shown in Table 1.
+Fig.
+3 a.
+and b.
+display the unstandardized and standardized HR trends, respectively.
+HR initially increased, peaked, and then decreased, with the unstandardized and standardized HR graphs showing high similarity.
+Thus, for all further analyses, we used participants’ standardized HR values.
+
+```{r HR descriptives, include=FALSE}
+# Mean, SD and range for overall (unstandardized)
+
+descrip_hr_overall <- main |>
+  filter(time_span %in% c("overall")) |> 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate),
+                                      digits = 2),
+            "Min heart rate in bpm" = min(heart_rate),
+            "Max heart rate in bpm" = max(heart_rate)
+  )
+
+# Mean, SD and range for overall (standardized)
+
+descrip_hr_overall_std <- main |>
+  filter(time_span %in% c("overall")) |> 
+  summarise(N = n_distinct(ID),
+            "M std heart rate in bpm" = round(mean(heart_rate_std),
+                                              digits = 2),
+            "SD std heart rate in bpm" = round(sd(heart_rate_std),
+                                               digits = 2),
+            "Min std heart rate in bpm" = round(min(heart_rate_std),
+                                                digits = 2),
+            "Max heart rate in bpm" = round(max(heart_rate_std),
+                                            digits = 2)
+            )
+
+# Mean, SD and range for individual phases (unstandardized)
+
+descrip_hr_phases <- main |> 
+  filter(!time_span %in% c("overall")) |> 
+  group_by(time_span) |> 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate),
+                                      digits = 2),
+            "Min heart rate in bpm" = min(heart_rate),
+            "Max heart rate in bpm" = max(heart_rate)
+  )
+
+# Mean, SD and range for individual phases (standardized)
+
+descrip_hr_phases_std <- main |> 
+  filter(!time_span %in% c("overall")) |> 
+  group_by(time_span) |> 
+  summarise(N = n_distinct(ID),
+            "M heart rate in bpm" = round(mean(heart_rate_std),
+                                     digits = 2),
+            "SD heart rate in bpm" = round(sd(heart_rate_std),
+                                      digits = 2),
+            "Min heart rate in bpm" = round(min(heart_rate_std),
+                                            digits = 2),
+            "Max heart rate in bpm" = round(max(heart_rate_std),
+                                            digits = 2)
+  )
+
+# # format and insert table in manuscript
+# descrip_hr_phases |>
+# papaja::apa_table(
+#   caption = "Mean, SD and range for teachers' heart rate in individual phases",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+#   )
+
+# Mean, SD and range for disruption and confidence factor
+
+rating_table <- 
+  df_rating |> 
+  filter(!is.na(confidence_factor),
+         !is.na(disruption_factor)) |> 
+   summarise(N = n_distinct(ID), 
+            "M disruption factor" = round(mean(disruption_factor),
+                                     digits = 2),
+            "SD disruption factor" = round(sd(disruption_factor),
+                                      digits = 2),
+            "Min disruption factor" = min(disruption_factor),
+            "Max disruption factor" = max(disruption_factor),
+            "M confidence factor" = round(mean(confidence_factor),
+                                     digits = 2),
+            "SD confidence factor" = round(sd(confidence_factor),
+                                      digits = 2),
+            "Min confidence factor" = min(confidence_factor),
+            "Max confidence factor" = max(confidence_factor)
+            )
+```
+
+```{r table_1, include=FALSE}
+
+desc_hr_phases <- bind_rows(x = descrip_hr_overall,
+                            y = descrip_hr_phases) |> 
+  select(-N) |> 
+  rename(`M HR` = `M heart rate in bpm`,
+         `SD HR` = `SD heart rate in bpm`,
+         `Min` = `Min heart rate in bpm`,
+         `Max` = `Max heart rate in bpm`,
+         Interval = time_span) |> 
+  select(c(Interval,
+           `M HR`,
+           `SD HR`,
+           `Min`,
+           `Max`)
+         )
+
+descrip_hr_overall_std <- descrip_hr_overall_std |> 
+  rename(`M HR` = `M std heart rate in bpm`,
+         `SD HR` = `SD std heart rate in bpm`,
+         `Min` = `Min std heart rate in bpm`,
+         `Max` = `Max heart rate in bpm`,
+          ) |> 
+  mutate(Interval = 'overall')
+
+descrip_hr_phases_std <-  descrip_hr_phases_std |> 
+  rename(`M HR` = `M heart rate in bpm`,
+         `SD HR` = `SD heart rate in bpm`,
+         `Min` = `Min heart rate in bpm`,
+         `Max` = `Max heart rate in bpm`,
+         Interval = time_span)
+
+desc_hr_phases_std <- bind_rows(x = descrip_hr_overall_std,
+                                y = descrip_hr_phases_std) |> 
+  select(-N) |> 
+    select(c(Interval,
+           `M HR`,
+           `SD HR`,
+           `Min`,
+           `Max`)
+         )
+
+desc_hr_phases[1, 1] <- 'overall'
+
+df_desc_hr <- desc_hr_phases |> 
+  mutate(across(everything(),
+                ~ paste(.,
+                        desc_hr_phases_std[[cur_column()]],
+                        sep = "/")
+                )
+         )
+
+df_desc_hr$Interval <- c('Overall Course of 2h',
+                         'Pre-teaching interval',
+                         'Teaching interval',
+                         'Post-teaching interval',
+                         'Interview interval',
+                         'End Interval')
+
+tab_1 <- apa_table(df_desc_hr,
+                   placement = 'h',
+                   label = 'tab_1',
+                   caption = 'Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)',
+                   note = 'Please note that M and SD of the overall course vs. the individual intervals were not exactly 0 and 1 due to rounding differences.' 
+                   )
+
+print(tab_1)
+
+writeLines(tab_1, 'tab_1.tex')
+
+```
+
+```{=latex}
+\input{tab_1.tex}
+```
+
+```{r loess-plot, include=FALSE}
+df_heart_rate <- 
+  main |> 
+  mutate(time = time / 60) |> 
+  filter(time_span == "overall") |>
+  dplyr::select("ID","time","heart_rate") |> 
+  distinct() |> 
+  mutate(type = "a. Heart Rate (in Beats per Minute)")
+
+df_heart_rate_std <- 
+  main |> 
+  mutate(time = time / 60) |> 
+  filter(time_span == "overall") |>
+  dplyr::select("ID","time","heart_rate_std") |> 
+  distinct() |> 
+  transmute(ID,
+            time,
+            type = "b. Heart Rate (Standardized)",
+            heart_rate = heart_rate_std)
+
+df_heart_rate |> 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  geom_smooth(se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.95) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0.01,0)) + 
+ labs(x = "",
+      y = "",
+      ) +
+  theme_apa() + 
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y") -> loess_hr
+
+df_heart_rate_std |> 
+  ggplot(mapping = aes(x = time,
+                       y = heart_rate
+                       )
+         ) +
+  geom_smooth(se = T,
+              size = 0.5,
+              colour = "black",
+              level = 0.95) +
+  scale_color_viridis_d(option = "A",
+                        end = 0.8) +
+  scale_linetype_manual(values = c(1, 6)) +
+  scale_x_continuous(expand = c(0.01,0)) +
+  scale_y_continuous(expand = c(0, 0.25)) +
+  labs(x = "",
+       y = "",
+       ) +
+  theme_apa() + 
+  facet_wrap(~ type,
+             ncol = 2,
+             scales = "free_y") -> loess_hr_std
+
+loess_comp <- grid.arrange(loess_hr, loess_hr_std,
+                           ncol = 2)
+
+loess_comp <- annotate_figure(p = loess_comp,
+                              bottom = 'Time (in Minutes)')
+
+ggsave(loess_comp,
+       filename = "plots_publication/loess_plot_std_unstd_new.pdf",
+       width = 16,
+       height = 12,
+       units = "cm")
+```
+
+```{=latex}
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
+  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
+  \label{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
+\end{figure}
+```
+
+```{r, include=FALSE}
+
+# main |> 
+#   filter(time_span != "overall") |>
+#   dplyr::select("ID","time_span", "time","heart_rate_std") |> 
+#   mutate(time_span = factor(time_span,
+#                             levels = c("preparation","teaching","post","interview","end"),
+#                             labels = c("(1) Pre-teaching\nInterval","(2) Teaching\nInterval","(3) Post-teaching\nInterval","(4) Interview\nInterval","(5) End\nInterval"))) |> 
+#   distinct() |>
+#   group_by(time_span) |> 
+#   summarise(z_mean = mean(heart_rate_std),
+#             z_sd = sd(heart_rate_std),
+#             z_t = qt(p = 0.05 / 2,      # 0.01 KI
+#                df = n() - 1,
+#                lower.tail = F
+#                ),
+#             z_error = z_sd / sqrt(n()),
+#             lower = z_mean - z_t * z_error,
+#             upper = z_mean + z_t * z_error,
+#             ) |> 
+#   ungroup() |> 
+#   ggplot(mapping = aes(x = factor(0),
+#                        y = z_mean)) + 
+#   geom_point() +
+#   geom_errorbar(mapping = aes(ymin = lower,
+#                               ymax = upper),
+#                 width = 0.2) +
+#   geom_hline(yintercept = 0,
+#              linetype = "dashed") +
+#   scale_y_continuous(breaks=seq(-1, 1, 0.5), 
+#                      limits=c(-1.1, 1)) + 
+#   labs(x = "Time (in Minutes)",
+#        y = "Standardized Mean Heart Rate",
+#        # caption = expression(paste(italic("Note: "),
+#        #                            "The shadow around the line represents the 99% confidence interval."
+#        #                            )
+#        #                      )
+#        ) +
+#   facet_grid(cols = vars(time_span),
+#              scales = "free_x") +
+#   theme_apa() +
+#   theme(axis.text.x = element_blank(),
+#         axis.ticks.x = element_blank(),
+#         plot.caption = element_text(hjust = 0))
+# 
+# ggsave(filename = "plots_publication/mean_plot.png",
+#        width = 20,
+#        height = 12,
+#        units = "cm")
+```

### 2024-07-04 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
expertise paper

--- 2024-04-17 02_paper/02_study/02_fitbit paper/Submission/FitBit_submission.tex
@@
-\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+\documentclass[preprint, 3p,
+authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
 %%% Begin My package additions %%%%%%%%%%%%%%%%%%%
@@
 \usepackage[hyphens]{url}
+
+  \journal{Computers \& Education} % Sets Journal name
 
@@
             pdfauthor={},
-            pdftitle={Title here},
+            pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
             colorlinks=false,
@@
 
-\setcounter{secnumdepth}{0}
+\setcounter{secnumdepth}{5}
 % Pandoc toggle for numbering sections (defaults to be off)
-\setcounter{secnumdepth}{0}
 
@@
 
+\usepackage{tabularx}
+\usepackage{threeparttable}
+\usepackage{booktabs}
+
 \begin{document}
@@
 
-  \title{Title here}
+  \title{New approaches to teachers' experience of stress: Do heart rate
+measurements with fitness trackers provide an efficient, inexpensive,
+and robust measurement method?}
+    \author[Leipzig University]{Mandy Klatt%
+  \corref{cor1}%
+  \fnref{1}}
+   \ead{mandy.klatt@uni-leipzig.de} 
+    \author[Leipzig University]{Peer Keßler%
+  %
+  \fnref{2}}
+   \ead{Peer@example.com} 
+    \author[Leipzig University, Max Planck Institute for Evolutionary
+Anthropology]{Gregor Kachel%
+  %
+  \fnref{1}}
+   \ead{gregor@example.com} 
+    \author[Leipzig University]{Christin Lotz%
+  %
+  \fnref{1}}
+   \ead{christin@example.com} 
+    \author[Leipzig University]{Anne Deiglmayr%
+  %
+  \fnref{3}}
+   \ead{anne@example.com} 
+      \affiliation[Leipzig University]{
+    organization={Empirische Schul- und
+Unterrichtsforschung},addressline={Marschnerstr.
+29},city={Leipzig},postcode={4109},state={Sachsen},country={Germany},}
+    \affiliation[Max Planck Institute for Evolutionary Anthropology]{
+    organization={Department},addressline={Deutscher Pl.
+6},city={Leipzig},postcode={4103},state={Sachsen},country={Germany},}
     \cortext[cor1]{Corresponding author}
+    \fntext[1]{ConceptualizationWriting - Original Draft
+PreparationWriting - Review \& Editing}
+    \fntext[2]{Writing - Original Draft PreparationWriting - Review \&
+Editing}
+    \fntext[3]{Supervision}
 
   \begin{abstract}
-  The text of your abstract. 150 -- 250 words.
+  One or two sentences providing a \textbf{basic introduction} to the
+  field, comprehensible to a scientist in any discipline.
+
+  Two to three sentences of \textbf{more detailed background},
+  comprehensible to scientists in related disciplines.
+
+  One sentence clearly stating the \textbf{general problem} being
+  addressed by this particular study.
+
+  One sentence summarizing the main result (with the words
+  ``\textbf{here we show}'' or their equivalent).
+
+  Two or three sentences explaining what the \textbf{main result}
+  reveals in direct comparison to what was thought to be the case
+  previously, or how the main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more \textbf{general
+  context}.
+
+  Two or three sentences to provide a \textbf{broader perspective},
+  readily comprehensible to a scientist in any discipline.
+
+  XXX In this proof-of-concept study, we aimed to advance the field of
+  teacher stress by collecting heart rate data with wrist-worn devices
+  and testing a methodology that has the potential to provide more
+  insights on the non-invasive assessment of teacher stress. XXX
   \end{abstract}
     \begin{keyword}
-    key \sep dictionary \sep 
-    word
+    heart rate \sep photoplethysmography \sep wearable electronic
+device \sep 
+    teaching
   \end{keyword}
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
 In education, there's interest in identifying reliable indicators for
-teacher stress and burnout {[}\citet{fisher2011}; @ junker2021{]}.
-Previous research often relied on self-report questionnaires
+teacher stress and burnout \citep{fisher2011, junker2021}. Previous
+research often relied on self-report questionnaires
 \citep{chaplain2008, liu2020}, which may be prone to biases like social
@@
 
-\hypertarget{fitness-trackers-as-a-method-to-assess-hr-as-an-indicator-of-stress}{%
 \subsection{Fitness Trackers as a Method to Assess HR as an Indicator of
-Stress}\label{fitness-trackers-as-a-method-to-assess-hr-as-an-indicator-of-stress}}
+Stress}\label{fitness-trackers-as-a-method-to-assess-hr-as-an-indicator-of-stress}
 
@@
 
-\hypertarget{teacher-stress-and-important-resources}{%
 \subsection{Teacher Stress and Important
-Resources}\label{teacher-stress-and-important-resources}}
+Resources}\label{teacher-stress-and-important-resources}
 
@@
 
-\hypertarget{hr-in-teaching-learning-contexts}{%
 \subsection{HR in Teaching-Learning
-Contexts}\label{hr-in-teaching-learning-contexts}}
+Contexts}\label{hr-in-teaching-learning-contexts}
 
@@
 
-\hypertarget{present-study}{%
-\subsection{Present Study}\label{present-study}}
+\subsection{Present Study}\label{present-study}
 
@@
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
+\section{Method}\label{method}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
@@
 flyers. The data of three participants was lost due to failed data
-transmission, yielding an analysis sample of \(n\) = 81 (\(n\) = 52
-women, \(n\) = 29 men). Participants had a mean age of 30.95 years
-(\(SD\) = 10.90; range: 19-60) and an average teaching experience of
-5.64 years (\(SD\) = 9.46; range: 0-37).
+transmission, yielding an analysis sample of \(n\) =
+\texttt{N\_postwrangling} (\(n\) = 52 women, \(n\) = 29 men).
+Participants had a mean age of 30.95 years (\(SD\) = 10.90; range:
+19-60) and an average teaching experience of 5.64 years (\(SD\) = 9.46;
+range: 0-37).
 
-\hypertarget{setting-and-procedure}{%
-\subsection{Setting and Procedure}\label{setting-and-procedure}}
+\subsection{Setting and Procedure}\label{setting-and-procedure}
 
@@
 
-\hypertarget{measures}{%
-\subsection{Measures}\label{measures}}
+\subsection{Measures}\label{measures}
 
-\hypertarget{heart-rate-data-and-heart-rate-intervals}{%
 \subsubsection{Heart Rate Data and Heart Rate
-Intervals}\label{heart-rate-data-and-heart-rate-intervals}}
+Intervals}\label{heart-rate-data-and-heart-rate-intervals}
 
@@
 
-\hypertarget{teaching-experience}{%
-\subsubsection{Teaching Experience}\label{teaching-experience}}
+\subsubsection{Teaching Experience}\label{teaching-experience}
 
@@
 
-\hypertarget{subjective-appraisal-of-the-classroom-events-and-coping-processes}{%
 \subsubsection{Subjective appraisal of the classroom events and coping
-processes}\label{subjective-appraisal-of-the-classroom-events-and-coping-processes}}
+processes}\label{subjective-appraisal-of-the-classroom-events-and-coping-processes}
 
@@
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+\subsection{Data analysis}\label{data-analysis}
 
@@
 unstandardized and standardized mean HR trends for the entire two-hours
-study. For testing Hypothesis 1a, which examined the HR levels in the
-different intervals, we initially conducted a one-way ANOVA with
-repeated measures as an omnibus test. The dependent variable comprised
-the standardized HR mean for each interval. To identify the highest HR
-level, we subsequently conducted t-tests with planned contrasts as
-post-hoc tests, accompanied by the effect size d \citep{cohen1988new}.
-Specifically, we tested the differences between the teaching interval
-(\(I_2\)) and the other four intervals. Note that mean HR was calculated
-at the subject level of \(n\) = 81 participants (see Table 1), whereas
-the mean slope and mean intercept estimates are based on all values at
-all measurement time points (see Table 2). For testing Hypothesis 1b,
-which examined the HR changes within each interval, we conducted a
-linear estimation of the increase or decrease in HR over time. To this
-end, we used fixed intercept fixed slope regression models
-\citep{gelman2006data} for each interval to estimate intercepts and
-linear slopes for all individuals which were then averaged across
-individuals\footnote{Although this procedure does not account for
-  nonmonotonic progressions in individual HR, a graphical evaluation
-  revealed that the linear estimates corresponded well to the majority
-  of the cases (see XX in the supplementary material).}.
+study{[}\^{}3{]}. For all further analyses, we used standardized rather
+than unstandardized HR values. {[}\^{}3{]}: Note that the study exceeded
+the planned duration of two hours for a few participants. To avoid
+distortions when mapping the HR over the course of the study (see Fig.
+3), the endpoint was set at two hours for all participants, even though
+data from later time points was used in the \emph{end interval} for a
+few participants.
+
+For testing Hypothesis 1a, which examined the HR levels in the different
+intervals, we initially conducted a one-way ANOVA with repeated measures
+as an omnibus test. The dependent variable comprised the standardized HR
+mean for each interval. To identify the highest HR level, we
+subsequently conducted t-tests with planned contrasts as post-hoc tests,
+accompanied by the effect size d \citep{cohen1988new}. Specifically, we
+tested the differences between the teaching interval (\(I_2\)) and the
+other four intervals. Note that mean HR was calculated at the subject
+level of \(n\) = 81 participants (see Table 1), whereas the mean slope
+and mean intercept estimates are based on all values at all measurement
+time points (see Table 2). For testing Hypothesis 1b, which examined the
+HR changes within each interval, we conducted a linear estimation of the
+increase or decrease in HR over time. To this end, we used fixed
+intercept fixed slope regression models \citep{gelman2006data} for each
+interval to estimate intercepts and linear slopes for all individuals
+which were then averaged across individuals\footnote{Although this
+  procedure does not account for nonmonotonic progressions in individual
+  HR, a graphical evaluation revealed that the linear estimates
+  corresponded well to the majority of the cases (see XX in the
+  supplementary material).}.
 
@@
 
+\section{Results}\label{results}
+
+\subsection{Research goal 1: Mapping teachers' HR over the course of the
+study
+phases}\label{research-goal-1-mapping-teachers-hr-over-the-course-of-the-study-phases}
+
+The first part of our first research goal was to map participants'
+overall HR trend and explore whether z-standardization of participants'
+HR is a useful method to account for individual differences in the
+baseline HR. Means, standard deviations, and range of teachers'
+unstandardized and standardized HR are shown in Table 1. Fig. 3 a. and
+b. display the unstandardized and standardized HR trends, respectively.
+HR initially increased, peaked, and then decreased, with the
+unstandardized and standardized HR graphs showing high similarity. Thus,
+for all further analyses, we used participants' standardized HR values.
+
+\input{tab_1.tex}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
+  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
+  \label{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
+\end{figure}
+
 \bibliography{r-references.bib}

### 2024-07-04 02_paper/02_study/01_fitbit paper/Submission/tab_1.tex
expertise paper

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:table_1}Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)}

\begin{tabular}{lllll}
\toprule
Interval & \multicolumn{1}{c}{M HR} & \multicolumn{1}{c}{SD HR} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
\midrule
Overall Course of 2h & 90.09/-0.04 & 15.76/0.99 & 51/-4.03 & 164/4.56\\
Pre-teaching interval & 77.95/-1.07 & 11.14/0.57 & 50/-2.68 & 120/2.96\\
Teaching interval & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39\\
Post-teaching interval & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06\\
Interview interval & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24\\
End Interval & 100.8/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Please note that M and SD of the overall course vs. the individual intervals were not exactly 0 and 1 due to rounding differences.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

### 2024-07-04 02_paper/02_study/02_eye tracking video questionnaire paper/emu_questionnaire.Rmd
expertise paper

---
title: "EMU Questionnaire - Item & Scale Analysis"
output:
  pdf_document: default
  html_notebook: default
---

```{r include=FALSE}
# install.packages("needs")

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych)

```

# Presence Questionnaire

After each micro-teaching-unit, participants answered items on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature. The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 4 = Strongly Agree).

Klassenmanagement:

LM01_01	Klassenmanagement: Die gesamte Unterrichtslektion wurde für den Lernstoff verwendet.

LM01_02	Klassenmanagement: Ich habe alles mitbekommen, was in der Klasse passiert ist.

LM01_03	Klassenmanagement: Den Lernenden war jederzeit klar, was sie tun sollten.

LM01_04	Klassenmanagement: Die Lernenden konnten ungestört arbeiten.

LM01_05	Klassenmanagement: Die Lernenden waren die ganze Unterrichtslektion über aktiv bei der Sache.

LM01_06	Klassenmanagement: Ich habe vieles mit kurzen Blicken und knappen Gesten geregelt.

LM01_07	Klassenmanagement: Auf Störungen habe ich angemessen reagiert.

LM01_08	Klassenmanagement: Bei Störungen gab ich den Lernenden ein klares STOP-Signal.

Präsenz:

LP01_01	Präsenzindikatoren: Ich hatte eine aufrechte, der Klasse zugewandte Körperhaltung.

LP01_02	Präsenzindikatoren: Ich habe den Lernenden direkt in die Augen geschaut.

LP01_03	Präsenzindikatoren: Ich habe meine Position im Raum bewusst eingesetzt und variiert.

LP01_04	Präsenzindikatoren: Ich habe alle oft angesehen.

LP01_05	Präsenzindikatoren: Meine Artikulation, Lautstärke und Tonhöhe waren angemessen.

LP01_06	Präsenzindikatoren: Meine Sprechgeschwindigkeit und Sprechpausen waren angemessen.

LP01_07	Präsenzindikatoren: Mein Sprechanteil an der gesamten Sprechzeit der Unterrichtslektion war angemessen.

LP01_08	Präsenzindikatoren: Meine Gestik und Mimik waren abwechslungsreich und ausdrucksstark.

Natürliches Verhalten:

LV01_01	Natürliches Verhalten: Während der Unterrichtslektion habe ich mich sehr natürlich verhalten.

LV01_02	Natürliches Verhalten: Es war für mich kein Problem, vor einer fiktiven Klasse zu unterrichten.

LV01_03	Natürliches Verhalten: Beim Unterrichten vor einer fiktiven Klasse habe ich mich so verhalten, wie ich 
es auch in der Schule tun würde.

```{r presence_questionnaire, echo=FALSE, results=TRUE}

# load data files
quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LI06_05, 
                LB01_01:LB01_03,
                LM01_01:LM01_08,
                LP01_01:LP01_08,
                LV01_01:LV01_03)

# creating a matrix
quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table) <- c("LM", "LB", "LP", "LV")
colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")

# creating a loop
i <- "LM"

for (i in c("LM", "LB", "LP", "LV")) {

loop.data <- quest.data %>%
  dplyr::select(starts_with(match = i))

quest.table[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  mean() %>%
  round(., digits = 2) ->
quest.table[i, "M"]

# calculating SD
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  sd() %>%
  round(., digits = 2) ->
quest.table[i, "SD"]

# calculating Min
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  min() %>%
  round(., digits = 2) ->
quest.table[i, "Min"]

# calculating Max
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  max() %>%
  round(., digits = 2) ->
quest.table[i, "Max"]

# calculating Skewness
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  skewness() %>%
  round(., digits = 2) ->
quest.table[i, "Skewness"]

# calculating Kurtosis
loop.data %>%
  mutate(mean = rowMeans(.)) %>%
  pull(mean) %>%
  kurtosis() %>%
  round(., digits = 2) ->
quest.table[i, "Kurtosis"]

# calculating Alpha
alpha <- loop.data %>%
  cronbach.alpha()

quest.table[i, "Alpha"] <- round(alpha$alpha,2)

}

# rename columns
rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
papaja::apa_table(
quest.table,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

```

```{r item_analysis_classroom_management, echo=FALSE, results='asis'}
quest.data %>%
  dplyr::select(contains("LM")) %>%
  as.data.frame() %>%
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))
```

```{r item_analysis_balance, echo=FALSE, results='asis'}
quest.data %>%
  dplyr::select(contains("LB")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

```{r item_analysis_presence, echo=FALSE, results='asis'}
quest.data %>%
  dplyr::select(contains("LP")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

```{r item_analysis_behavior, echo=FALSE, results='asis'}
quest.data %>%
  dplyr::select(contains("LV")) %>%
  as.data.frame() %>%
  tab_itemscale()
```

### 2024-07-04 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.Rmd
expertise paper

--- 2022-08-12 02_paper/02_study/01_eye tracking video questionnaire paper/paper_methods.Rmd
@@
 library(needs)
-
 needs(tidyverse,
@@
       DescTools,
-      formattable)
+      formattable,
+      psych)
 
@@
 
-XXX FRANZI 
 ```{r reaction_codingsystem, include=TRUE, echo=FALSE, results='asis'}
-
-audit_table <- structure(
-  list(
-    Description = c(
-      "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
-      "The teacher reacts nonverbally and simultaneously with a short verbal reaction.
+# audit_table <- structure(
+#   list(
+#     Description = c(
+#       "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
+#       "The teacher reacts nonverbally and simultaneously with a short verbal reaction.
 The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixing gaze).
 The verbal response includes name calling, brief verbal prompts / admonitions.",
-      "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
-      "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption.
+#       "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
+#       "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption.
 The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixating gaze).",
-      "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption.
+#       "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption.
 This information can only be obtained through the Stimulated Recall Interview.",
-      "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption.
+#       "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption.
 This information can only be obtained through the Stimulated Recall Interview.",
-      "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
-                  ),
-    `1` = c("Never", "1–2", "Never"),
-    `2` = c("Monthly or less", "3-4", "Less than monthly"),
-    `3` = c("2-4 times per month", "5-6", "monthly"),
-    `4` = c("2-3 times per week","7-9", "Weekly"),
-    `5` = c("4+ times per week", "10+", "Daily or almost daily"),
-    `6` = c("bla"),
-    `7` = c("bla")
-          ),
-  class = "data.frame",
-  row.names = c(NA)
-)
-
-apa_table(
-  audit_table,
-  caption = "AUDIT-C scoring table",
-  align = c("m{8cm}", rep("m{2cm}", 5)),
-  col_spanners = list("Code" = c(2,7)),
-  note = "Item scores are summed. Women who score 3+ and men who score 4+ are at-risk",
-  landscape = TRUE
-  )
+#       "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
+#                   ),
+#     `1` = c("Never", "1–2", "Never"),
+#     `2` = c("Monthly or less", "3-4", "Less than monthly"),
+#     `3` = c("2-4 times per month", "5-6", "monthly"),
+#     `4` = c("2-3 times per week","7-9", "Weekly"),
+#     `5` = c("4+ times per week", "10+", "Daily or almost daily"),
+#     `6` = c("bla"),
+#     `7` = c("bla")
+#           ),
+#   class = "data.frame",
+#   row.names = c(NA)
+# )
+# 
+# apa_table(
+#   audit_table,
+#   caption = "AUDIT-C scoring table",
+#   align = c("m{8cm}", rep("m{2cm}", 5)),
+#   col_spanners = list("Code" = c(2,7)),
+#   note = "Item scores are summed. Women who score 3+ and men who score 4+ are at-risk",
+#   landscape = TRUE
+#   )
 
@@
 
+Bilanz:
+LB01_01	Bilanz: Die Lernenden haben in dieser Unterrichtslektion etwas dazu gelernt.
+LB01_02	Bilanz: Die Lernenden haben sich in dieser Unterrichtslektion wohl gefühlt.
+LB01_03	Bilanz: Mediennutzung und Sozialformen waren dem Inhalt und der Situation der Unterrichtslektion angemessen.
+
+Klassenmanagement:
+LM01_01	Klassenmanagement: Die gesamte Unterrichtslektion wurde für den Lernstoff verwendet.
+LM01_02	Klassenmanagement: Ich habe alles mitbekommen, was in der Klasse passiert ist.
+LM01_03	Klassenmanagement: Den Lernenden war jederzeit klar, was sie tun sollten.
+LM01_04	Klassenmanagement: Die Lernenden konnten ungestört arbeiten.
+LM01_05	Klassenmanagement: Die Lernenden waren die ganze Unterrichtslektion über aktiv bei der Sache.
+LM01_06	Klassenmanagement: Ich habe vieles mit kurzen Blicken und knappen Gesten geregelt.
+LM01_07	Klassenmanagement: Auf Störungen habe ich angemessen reagiert.
+LM01_08	Klassenmanagement: Bei Störungen gab ich den Lernenden ein klares STOP-Signal.
+
+Redeanteil:
+LO01_01	Redeanteil: Wieviel Prozent der gesamten Unterrichtslektion hat nach Ihrer Schätzung Ihr eigener Redeanteil eingenommen? ... %
+LO01_02	Redeanteil: Wenn ich Fragen oder Aufgaben gestellt habe, habe ich den Lernenden folgende Zeit (in Sekunden) zum Nachdenken gegeben ... Sekunden
+
+Präsenz:
+LP01_01	Präsenzindikatoren: Ich hatte eine aufrechte, der Klasse zugewandte Körperhaltung.
+LP01_02	Präsenzindikatoren: Ich habe den Lernenden direkt in die Augen geschaut.
+LP01_03	Präsenzindikatoren: Ich habe meine Position im Raum bewusst eingesetzt und variiert.
+LP01_04	Präsenzindikatoren: Ich habe alle oft angesehen.
+LP01_05	Präsenzindikatoren: Meine Artikulation, Lautstärke und Tonhöhe waren angemessen.
+LP01_06	Präsenzindikatoren: Meine Sprechgeschwindigkeit und Sprechpausen waren angemessen.
+LP01_07	Präsenzindikatoren: Mein Sprechanteil an der gesamten Sprechzeit der Unterrichtslektion war angemessen.
+LP01_08	Präsenzindikatoren: Meine Gestik und Mimik waren abwechslungsreich und ausdrucksstark.
+
+Natürliches Verhalten:
+LV01_01	Natürliches Verhalten: Während der Unterrichtslektion habe ich mich sehr natürlich verhalten.
+LV01_02	Natürliches Verhalten: Es war für mich kein Problem, vor einer fiktiven Klasse zu unterrichten.
+LV01_03	Natürliches Verhalten: Beim Unterrichten vor einer fiktiven Klasse habe ich mich so verhalten, wie ich es auch in der Schule tun würde.
+
 ```{r presence_questionnaire, include=TRUE, echo=FALSE, results='asis'}
+
 # load data files
 quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  mutate(Group = ifelse(LI06_05 < 200, "Novice","Expert")) %>%
-  dplyr::select(Group, LM01_01:LO01_02)
-
-# create two data frames
-quest.data.novice <- quest.data %>% filter(Group == "Novice")
-quest.data.expert <- quest.data %>% filter(Group == "Expert")
-
-############## NOVICE TABLE #########################
+  dplyr::select(LI06_05, 
+                LB01_01:LB01_03,
+                LM01_01:LM01_08,
+                LP01_01:LP01_08,
+                LV01_01:LV01_03)
 
 # creating a matrix
-quest.table.novice <- matrix(data = NA, nrow = 4, ncol = 8)
-rownames(quest.table.novice) <- c("LM", "LB", "LP", "LV")
-  colnames(quest.table.novice) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
+quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
+rownames(quest.table) <- c("LM", "LB", "LP", "LV")
+colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
 
@@
 
-loop.data <- quest.data.novice %>%
+loop.data <- quest.data %>%
   dplyr::select(starts_with(match = i))
 
-quest.table.novice[i, "N Items"] <- length(loop.data)
+quest.table[i, "N Items"] <- length(loop.data)
 
@@
   round(., digits = 2) ->
-quest.table.novice[i, "M"]
+quest.table[i, "M"]
 
@@
   round(., digits = 2) ->
-quest.table.novice[i, "SD"]
+quest.table[i, "SD"]
 
@@
   round(., digits = 2) ->
-quest.table.novice[i, "Min"]
+quest.table[i, "Min"]
 
@@
   round(., digits = 2) ->
-quest.table.novice[i, "Max"]
+quest.table[i, "Max"]
 
@@
   round(., digits = 2) ->
-quest.table.novice[i, "Skewness"]
+quest.table[i, "Skewness"]
 
@@
   round(., digits = 2) ->
-quest.table.novice[i, "Kurtosis"]
-
-# calculating alpha
+quest.table[i, "Kurtosis"]
+
+# calculating Alpha
 alpha <- loop.data %>%
@@
 
-quest.table.novice[i, "alpha"] <- round(alpha$alpha,2)
+quest.table[i, "Alpha"] <- round(alpha$alpha,2)
 
@@
 # rename columns
-rownames(quest.table.novice) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
+rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
 
@@
 papaja::apa_table(
-quest.table.novice,
-  caption = "Scale analysis for novices' self-assessment",
+quest.table,
+  caption = "Scale analysis for teachers' self-assessment",
   # note = "Write Note here",
@@
 
-############## EXPERT TABLE #########################
-
-# creating a matrix
-quest.table.expert <- matrix(data = NA, nrow = 4, ncol = 8)
-rownames(quest.table.expert) <- c("LM", "LB", "LP", "LV")
-  colnames(quest.table.expert) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
-
-# creating a loop
-# i <- "LM"
-
-for (i in c("LM", "LB", "LP", "LV")) {
-
-loop.data <- quest.data.expert %>%
-  dplyr::select(starts_with(match = i))
-
-quest.table.expert[i, "N Items"] <- length(loop.data)
-
-# calculating mean
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  mean() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "M"]
-
-# calculating SD
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  sd() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "SD"]
-
-# calculating Min
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  min() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "Min"]
-
-# calculating Max
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  max() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "Max"]
-
-# calculating Skewness
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  skewness() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "Skewness"]
-
-# calculating Kurtosis
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  kurtosis() %>%
-  round(., digits = 2) ->
-quest.table.expert[i, "Kurtosis"]
-
-# calculating alpha
-alpha <- loop.data %>%
-  cronbach.alpha()
-
-quest.table.expert[i, "alpha"] <- round(alpha$alpha,2)
-
-}
-
-# rename columns
-rownames(quest.table.expert) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
-
-# format and insert table in manuscript
-papaja::apa_table(
-quest.table.expert,
-  caption = "Scale analysis for experts' self-assessment",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
 ```
-XXX FRANZI
-```{r item_analysis_classroom_management_novice, echo=FALSE, include=FALSE, results='asis'}
+
+```{r item_analysis_classroom_management, echo=FALSE, include=FALSE, results='asis'}
 quest.data %>%
-  dplyr::filter(Group == "Novice") %>% 
   dplyr::select(contains("LM")) %>%
@@
 
-```{r item_analysis_classroom_management_expert, echo=FALSE, include=FALSE, results='asis'}
+```{r item_analysis_balance, echo=FALSE, include=FALSE, results='asis'}
 quest.data %>%
-  dplyr::filter(Group == "Expert") %>% 
-  dplyr::select(contains("LM")) %>%
-  as.data.frame() %>%
-  tab_itemscale(CSS = list(
-    css.firsttablerow.col7 = "'cronbachs alpha';"
-  ))
-```
-
-```{r item_analysis_balance_novice, echo=FALSE, include=FALSE, results='asis'}
-quest.data %>%
-  dplyr::filter(Group == "Novice") %>% 
   dplyr::select(contains("LB")) %>%
@@
 
-```{r item_analysis_balance_expert, echo=FALSE, include=FALSE, results='asis'}
+```{r item_analysis_presence, echo=FALSE, include=FALSE,results='asis'}
 quest.data %>%
-  dplyr::filter(Group == "Expert") %>%
-  dplyr::select(contains("LB")) %>%
-  as.data.frame() %>%
-  tab_itemscale()
-```
-
-```{r item_analysis_presence_novice, echo=FALSE, include=FALSE,results='asis'}
-quest.data %>%
-  dplyr::filter(Group == "Novice") %>%
   dplyr::select(contains("LP")) %>%
@@
 
-```{r item_analysis_presence_expert, echo=FALSE, include=FALSE,results='asis'}
+```{r item_analysis_behavior, echo=FALSE, include=FALSE,results='asis'}
 quest.data %>%
-  dplyr::filter(Group == "Expert") %>%
-  dplyr::select(contains("LP")) %>%
-  as.data.frame() %>%
-  tab_itemscale()
-```
-
-```{r item_analysis_behavior_novice, echo=FALSE, include=FALSE,results='asis'}
-quest.data %>%
-  dplyr::filter(Group == "Novice") %>%
-  dplyr::select(contains("LV")) %>%
-  as.data.frame() %>%
-  tab_itemscale()
-```
-
-```{r item_analysis_behavior_expert, echo=FALSE, include=FALSE,results='asis'}
-quest.data %>%
-  dplyr::filter(Group == "Expert") %>%
   dplyr::select(contains("LV")) %>%

### 2024-07-04 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.tex
expertise paper

--- 2022-07-04 02_paper/02_study/paper_methods.tex
@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \fi
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 \fi
+\usepackage{bookmark}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
+  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
+  pdflang={en-EN},
+  pdfkeywords={professional vision, expertise, classroom management, mobile eye-tracking},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson \& Weinstein, 2006; Kounin, 2006).
+\section{Introduction}\label{introduction}
+
+Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson, Weinstein, et al., 2006; Kounin, 2006).
 Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom.
-This ability is referred to as classroom professional vision (Goodwin, 1994; Sherin, 2007).
-The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (``noticing'') and applying knowledge to draw appropriate conclusions in these situations (``knowledge-based reasoning''; Seidel \& Stürmer, 2014).
+This ability is referred to as classroom professional vision (\textbf{goodwin2015?} professional; Sherin, 2007).
+The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (``noticing'') and applying knowledge to draw appropriate conclusions in these situations {[}``knowledge-based reasoning''; Seidel and Stürmer (2014){]}.
 Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students' learning time and minimize classroom interruptions.
@@
 Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017).
-Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, ``{[}\ldots{]} whereas only a few studies have focused on the basal process of noticing, i.e.~the recognition of possible disturbing situations'' (Grub et al., 2020, p.75).
-Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner et al., 2016; Wolff et al., 2016).
-
-\hypertarget{theoretical-background}{%
-\section{Theoretical background}\label{theoretical-background}}
-
-\hypertarget{professional-competence-in-teaching-profession}{%
-\subsection{Professional competence in teaching profession}\label{professional-competence-in-teaching-profession}}
+Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, ``{[}\ldots{]} whereas only a few studies have focused on the basal process of noticing, i.e.~the recognition of possible disturbing situations'' (\textbf{grub2020processp?}).
+Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner, Jarodzka, \& Nückles, 2016; Wolff, Jarodzka, Bogert, \& Boshuizen, 2016).
+
+\section{Theoretical background}\label{theoretical-background}
+
+\subsection{Professional competence in teaching profession}\label{professional-competence-in-teaching-profession}
 
@@
 Teachers have to be competent in things such as teaching, educating, evaluating or innovating.
-Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig \& Rauch, 2008).
+Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig, \& Rauch, 2008).
 They replace the rigid canon of knowledge that defined professional qualification for generations.
 In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.).
-To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf.~Klieme et al., 2008, p.~4).
+To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf.
+Klieme et al., 2008, p.
+4).
 In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.
@@
 
-The term ``professional competence'' is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation.'' (cf.~Epstein \& Hundert, 2002; cited in Kunter et al.~2013, p.~807).
-Several studies could prove that this idea can be successfully transferred to the teaching profession (cf.~Goodmann et al., 2008; Oster, Achtenhagen \& Renold, 2006; Tannenbaum \& Rosenfeld, 1994; cited in Kunter et al., 2013, p.~807).
+The term ``professional competence'' is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation.'' {[}cf.
+Epstein and Hundert (2002); cited in Kunter et al.~2013, p.~807{]}.
+Several studies could prove that this idea can be successfully transferred to the teaching profession {[}cf.~Goodmann et al., 2008; Oser, Achtenhagen, and Renold (2006), Achtenhagen \& Renold, 2006; Tannenbaum \& Rosenfeld, 1994; cited in Kunter et al., 2013, p.~807{]}.
 Accordingly, a quality standard can be applied to assess the quality of a teacher.
-This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano \& Pickering, 2003).
+This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano, \& Pickering, 2003).
 Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher.
@@
 
-\hypertarget{classroom-management}{%
-\subsection{Classroom Management}\label{classroom-management}}
+\subsection{Classroom Management}\label{classroom-management}
 
@@
 This trained handling, as described above, can be summarized under the aspect of professional competence.
-It is expressed, among other things, in knowledge about classroom management (Grub, Biermann \& Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
-
-Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, van den Bogert, Jarodzka \& Boshuizen, 2015).
-Marzano et al.'s (2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching.
+It is expressed, among other things, in knowledge about classroom management (Grub, Biermann, \& Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
+
+Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, Bogert, Jarodzka, \& Boshuizen, 2015).
+Marzano et al.
+(2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching.
 In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015).
@@
 
-Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf.~Wolff et al., 2015, p.~71).
+Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf.
+Wolff et al., 2015, p.
+71).
 These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.).
@@
 
-\hypertarget{interdependence-of-classroom-management}{%
-\subsubsection{Interdependence of classroom management}\label{interdependence-of-classroom-management}}
+\subsubsection{Interdependence of classroom management}\label{interdependence-of-classroom-management}
 
@@
 Therefore, it is merely a matter of preference which concept is consulted to explain connections and terms.
-In the following, the network of effects of classroom management according to Helmke (2014) is used as a reference model in order to be able to understand the embedding of the concept accordingly.
+In the following, the network of effects of classroom management according to Helmke et al.
+(2014) is used as a reference model in order to be able to understand the embedding of the concept accordingly.
 
 As was made clear in the definition, classroom management is a complex construct that attempts to accommodate the various modes and challenging characteristics of a classroom.
-Helmke (2014) therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time.
+Helmke et al.
+(2014) therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time.
 This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (\emph{d} = 0.39; Hattie, 2013, p.219).
@@
 It is embedded in diverse contexts, especially in the school and class context (Helmke \& Helmke, 2015).
-But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led (Helmke, 2014).
-
-Classroom management itself is made up of various components which, according to Helmke (2014), can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior.
+But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led (Helmke et al., 2014).
+
+Classroom management itself is made up of various components which, according to Helmke et al.
+(2014), can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior.
 Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke \& Helmke, 2015).
@@
 The importance of rules in the classroom has been known and researched for some time.
-Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules (cf.~Emmer, Evertson \& Anderson, 1980; Emmer, Sanford, Clements \& Martin, 1982; cited in Doyle, 1989, p.~15).
+Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules {[}cf.~Emmer, Evertson \& Anderson, 1980; Emmer, Sanford, Clements, and Martin (1982); cited in Doyle, 1989, p.~15{]}.
 Although he also stresses that establishing a system of rules is a difficult task.
@@
 needs to be done.
-In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time (Helmke, 2014).
+In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time (Helmke et al., 2014).
 For the reasons just reasons just explained, it is clear why Hattie (2013, p.~122) gives this component of classroom classroom management an effect size of \emph{d} = 0.76.
@@
 The behavioral pattern of presence is not a new concept.
-It was already recorded by Kounin in 1970 under the term \emph{withitness}.
-Later research confirmed and validated his assumptions and definition of the term (cf.~Helmke, 2014, p.10).
+It was already recorded by kounin1970discipline under the term \emph{withitness}.
+Later research confirmed and validated his assumptions and definition of the term (cf.
+Helmke et al., 2014, p.
+10).
 In order to be present, the teacher must be able to control the classroom adequately and superficially effectively at all times.
@@
 The two dimensions of overlap and presence can also be summarized together under the term monitoring (Gold \& Holodynski, 2017).
-When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners (Grub et al., 2020.).
-Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness.
-and increases general awareness of relevant events in the classroom (ibid.). From this point of view, it becomes clear why awareness is a core component of teacher competence.
-
-As a third component influencing the quality of classroom management, cites Helmke (2014) time use and management.
+When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners (Grub et al., 2020).
+Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness of relevant events in the classroom (ibid.).
+From this point of view, it becomes clear why awareness is a core component of teacher competence.
+
+As a third component influencing the quality of classroom management, cites Helmke et al.
+(2014) time use and management.
 This seems trivial at first, considering that classroom management serves the goal of maximizing learning time anyway.
@@
 
-\hypertarget{professional-vision}{%
-\subsection{Professional vision}\label{professional-vision}}
+\subsection{Professional vision}\label{professional-vision}
 
@@
 It follows the approach of concentrating on action-relevant as well as lesson-related content in order to train corresponding competences for teaching practice (KMK, 2004).
-In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes (Barth, 2017).
-Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel \& Prenzel 2014).
+In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes (V.
+L.
+Barth, 2017).
+Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel, \& Prenzel, 2014).
 The concept of professional vision can originally be traced back to the anthropologist Charles Goodwin and became known under the term Professional Vision (Sherin, 2001).
@@
 
-\hypertarget{teachers-professional-vision}{%
-\subsubsection{Teachers' professional vision}\label{teachers-professional-vision}}
+\subsubsection{Teachers' professional vision}\label{teachers-professional-vision}
 
@@
 As teachers develop from novices to experts in their field, they accumulate expertise in a variety of areas (cf.~Sherin, 2001, p.~76).
-This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom (Berliner, 1994; Leinhardt \& Greeno, 1986).
+This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom Leinhardt \& Greeno (1986).
 This type of action can be described as a skill that helps teachers make decisions about what is relevant and what is not within the complex classroom setting (van Es \& Sherin, 2002).
@@
 Professional awareness is therefore referred to as an indicator of how knowledge is represented in teachers (Stürmer et al., 2017).
-It can also be seen as a bridge or link between knowledge and action, or professional competence and behavior (Grub et al., 2020).
+It can also be seen as a bridge or link between knowledge and action, or professional competence and behavior (\textbf{grub2020process0?}).
 It is important to understand that professional vision is acquired and not inherent.
@@
 Simultaneous events and situations cannot be given the same attention.
-``Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects'' (Barth, 2017, p.19).
+``Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects'' (V.
+L.
+Barth, 2017, p.
+19).
 Furthermore, teachers benefit from from a trained perception of problems, as this is a significant factor in being able to preventively counteract preventive measures (Wettstein, 2013).
 
-Basically, the complex process of professional vision is divided into three sub-processes (Grub et al., 20202).
+Basically, the complex process of professional vision is divided into three sub-processes (Grub et al., 2020).
 First of all, the identification, the recognition, of an event takes place.
@@
 Qualitative research on knowledge-based reasoning concluded that it can be subdivided into three further sub-processes.
-Sherin (2007; cited in Barth, 2017, p.~20) made a first subdivision, which consists of the processes of describing, evaluating and interpreting.
+Sherin (2007; cited in V.
+L.
+Barth, 2017, p.
+20) made a first subdivision, which consists of the processes of describing, evaluating and interpreting.
 When a teacher describes what she notices, she concentrates on observable characteristics, i.e.~important aspects of teaching (ibid.).
-When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event (cf.~Barth, 2017, p.~19).
+When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event (cf.
+V.
+L.
+Barth, 2017, p.
+19).
 Seidel et al.~(2010), on the other hand, focus on German-speaking countries in their research on professional vision and modified Sherin's original concept.
-They also divide knowledge-based-reasoning into three levels, but these differ: describing, explaining and predicting (Barth, 2017).
+They also divide knowledge-based-reasoning into three levels, but these differ: describing, explaining and predicting (V.
+L.
+Barth, 2017).
 More precisely, these processes encompass the ability to differentially describe instructional components that have an impact on learning; to make theoretically sound explanations about instructional situations; and to predict the effects of these events in relation to the teaching-learning process (cf.~Seidel et al., 2010, p.~297).
@@
 
-Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect (Sherin, 2007; cited in Barth, 2017, p.~19).
+Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect (\textbf{sherin2007development7?}; cited in \textbf{barth2017professionelle7?}).
 What is considered and perceived as relevant in a teacher's selective vision (noticing) functions as the basis of the subsequent processes of describing, evaluating, and interpreting (knowledge-based-reasoning).
@@
 
-\hypertarget{measuring-professional-vision-eye-tracking-technology-in-research}{%
-\subsection{Measuring professional vision: eye-tracking technology in research}\label{measuring-professional-vision-eye-tracking-technology-in-research}}
+\subsection{Measuring professional vision: eye-tracking technology in research}\label{measuring-professional-vision-eye-tracking-technology-in-research}
 
@@
 However, this method is highly susceptible to interference due to its incomplete accessibility (Dessus, 2016).
-The increasingly popular research method of eye-tracking technology therefore represents an innovative means of externalizing, i.e., making visible, internalized processes by means of eye movements (Gegenfurtner et al., 2018).
-Stimuli in the environment are always perceived by our eyes as the first receiver.
+The increasingly popular research method of eye-tracking technology therefore represents an innovative means of externalizing, i.e., making visible, internalized processes by means of eye movements (Gegenfurtner et al., 2018) Stimuli in the environment are always perceived by our eyes as the first receiver.
 They take in the information and pass it on to our brain so that it can finally be processed there.
@@
 In research so far, mainly eye-tracking devices have been used, which phenotypically resemble a computer (ibid.).
-They are also referred to as remote devices and, once calibrated, measure eye movements in a non-contact manner using infrared light (Gegenfurtner et al., 2018).
+They are also referred to as remote devices and, once calibrated, measure eye movements in a non-contact manner using infrared light (\textbf{egenfurtner2018mobiles?}).
 However, this technique reaches its limits when it comes to collecting data in everyday situations.
@@
 Eye-tracking research is based on several fundamental assumptions.
-The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date (cf.~Blake, 2018, p.380).
-In this regard, Hoffmann and Subramaniam (1995) obtained the finding that when the eyes are focused on an object, this is associated with an attentional focus of the person.
+The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date (cf.
+Blake, 2013, p.
+380).
+In this regard, hoffman1995role obtained the finding that when the eyes are focused on an object, this is associated with an attentional focus of the person.
 Based on these findings, ET technology is based on the following two assumptions: The immediacy assumption and the eye-mind assumption (cf.~Rakoczi, 2012, p.87).
@@
 
-\hypertarget{parameters-and-indicators-of-teachers-professional-vision}{%
-\subsubsection{Parameters and indicators of teachers' professional vision}\label{parameters-and-indicators-of-teachers-professional-vision}}
+\subsubsection{Parameters and indicators of teachers' professional vision}\label{parameters-and-indicators-of-teachers-professional-vision}
 
@@
 
-\hypertarget{expertise-differences-in-professional-vision}{%
-\subsubsection{Expertise differences in professional vision}\label{expertise-differences-in-professional-vision}}
+\subsubsection{Expertise differences in professional vision}\label{expertise-differences-in-professional-vision}
 
@@
 Student teachers do not have well-structured experiential knowledge due to their almost non-existent practice in everyday school life (Wolff et al., 2016).
-This causes them selection difficulties in perception and is called pedagogical knowledge gap (cf.~Wolff et al., 2016, p.260).
+This causes them selection difficulties in perception and is called pedagogical knowledge gap (cf.
+Wolff et al., 2016, pp.
+2016, p.260).
 Through newly gained experiences, the professional vision of a teacher is continuously restructured and updated, and mental representation is constantly realigned accordingly (ibid.).
@@
 Therefore, it can be assumed that there is a relationship between teacher expertise, their visual processing, and mindfulness for classroom management (Wolff et al., 2016).
-Research has also shown that declarative knowledge acquisition, i.e., acquisition of factual knowledge, supports perceptual processes (Seidel et al., 2012; cited in Treisch, 2018, p.26).
-Accordingly, this increased knowledge acquisition would explain a positive impact on professional teaching perception.
-Among the most important prerequisites for this acquisition, Baumert and Kunter (2006) include prior knowledge and interest.
+Research has also shown that declarative knowledge acquisition, i.e., acquisition of factual knowledge, supports perceptual processes {[}Seidel et al., 2012; cited in Treisch (2018), p.26{]} Accordingly, this increased knowledge acquisition would explain a positive impact on professional teaching perception.
+Among the most important prerequisites for this acquisition, baumert2006key include prior knowledge and interest.
 The former is elementary for new knowledge acquisition about effective teaching and learning, as it supports processing, integration, and consolidation of it (Stürmer, 2011).
-Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions (cf.~Sabers, 1991; cited in Treisch, 2018).
+Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions (cf.
+Sabers, Cushing, \& Berliner, 1991; cited in Treisch, 2018).
 This is explained by increased filtering mechanisms that support perceptual processes, i.e., recognition.
-Specifically, it has been shown that experienced teachers have more fixations on relevant areas because they have already learned theories on how to detect potential clutter in the classroom (Grub et al., 2020.).
+Specifically, it has been shown that experienced teachers have more fixations on relevant areas because they have already learned theories on how to detect potential clutter in the classroom (Grub et al., 2020).
 Furthermore, experts have an advantage when it comes to coding information.
@@
 
-\hypertarget{mobile-eye-tracking-in-teaching-learning-situations}{%
-\subsubsection{Mobile eye tracking in teaching-learning situations}\label{mobile-eye-tracking-in-teaching-learning-situations}}
+\subsubsection{Mobile eye tracking in teaching-learning situations}\label{mobile-eye-tracking-in-teaching-learning-situations}
 
@@
 In the worst case, they force a standstill in the flow of instruction, which is naturally to be avoided.
-Lohmann (2015, p.13) describes classroom disruptions as ``events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place.'' However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive (cf.~Eckstein, Grob \& Reusser, 2016; cited in, Eckstein, 2018, p.11).
+Lohmann (2015, p.13) describes classroom disruptions as ``events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place.'' However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive {[}cf.
+Eckstein, Grob, and Reusser (2016); cited in, Eckstein, 2018, p.11{]}.
 Thus, instructional disruptions are strongly dependent on perception and involve elements of production as well as reception (ibid.).
@@
 
-\hypertarget{perceptions-of-classroom-disruptions-and-their-parameters}{%
-\subsubsection{Perceptions of classroom disruptions and their parameters}\label{perceptions-of-classroom-disruptions-and-their-parameters}}
+\subsubsection{Perceptions of classroom disruptions and their parameters}\label{perceptions-of-classroom-disruptions-and-their-parameters}
 
@@
 Individual personality characteristics play a central role when it comes to the perception of relevant classroom events.
-In general, it should be noted that novices have greater problems in classroom management as well as in dealing with difficult student behavior (Barth, 2017).
+In general, it should be noted that novices have greater problems in classroom management as well as in dealing with difficult student behavior (V.
+L.
+Barth, 2017).
 Often, this is due to their late or even lack of awareness of classroom disruptions.
 However, their lack of expertise is not the sole reason for this phenomenon.
-Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher (Baumert \& Kunter, 2006).
-Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors.
+Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher (Baumert \& Kunter, 2006) Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors.
 Individual person characteristics as well as contextual factors not only have an effect on teaching perception, but likewise on the sense of disturbance of a situation (Eckstein, 2019).
@@
 
-\hypertarget{research-questions-and-hypothesis}{%
-\section{Research Questions and hypothesis}\label{research-questions-and-hypothesis}}
+\section{Research Questions and hypothesis}\label{research-questions-and-hypothesis}
 
@@
 Based on the existing literature, we expected expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation duration and (H3) perceiving classroom disruptions faster (cf.
-Van den Bogert, Bruggen, Kostons, and Jochems (2014)), (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions (Barth, 2017), and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
-
-\hypertarget{materials-and-methods}{%
-\section{Materials and Methods}\label{materials-and-methods}}
+\textbf{van2014first?}), (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions (V.
+L.
+Barth, 2017), and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
+
+\section{Materials and Methods}\label{materials-and-methods}
 
@@
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
@@
 \midrule
-Expert & 19 & 57.89 & 41.68 & 10.41 & 27.00 & 59.00\\
-Novice & 26 & 65.38 & 23.38 & 1.72 & 20.00 & 27.00\\
+Expert & 42 & 59.52 & 39.31 & 10.64 & 26.00 & 60.00\\
+Novice & 42 & 69.05 & 22.83 & 1.85 & 19.00 & 27.00\\
 \bottomrule
@@
 \midrule
-Expert & 19 & 13.84 & 12.30 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 47.00\\
-Novice & 26 & 0.00 & 0.00 & 0.00 & 0.00 & 7.15 & 2.62 & 3.00 & 11.00 & 10.92 & 8.09 & 0.00 & 36.00 & 88.46 & NA\\
+Expert & 42 & 11.79 & 11.43 & 1.00 & 38.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & NA\\
+Novice & 42 & 0.00 & 0.00 & 0.00 & 0.00 & 6.74 & 2.65 & 3.00 & 11.00 & 9.62 & 7.19 & 0.00 & 36.00 & 88.10 & NA\\
 \bottomrule
@@
 
-The sample consisted of \emph{N} = 45 participants with \emph{n} = 19 expert teachers and \emph{n} = 26 novice teachers.
+The sample consisted of \emph{N} = 84 participants with \emph{n} = 42 expert teachers and \emph{n} = 42 novice teachers.
 
@@
 
-The expert teachers (11 women; 57.89\%) had a mean age of 41.70 years (\emph{SD} = 10.40; range: 27-59) and an average teaching experience of 13.80 years (\emph{SD} = 12.30; range: 3-37).
-15.79\% of the experts were primary school teachers and 84.21\% were secondary school teachers.
-47\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
-
-The novice teachers (17 women; 65.38\%) had a mean age of 23.40 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years.
-On average, the student teachers were in their 7.20 semester (\emph{SD} = 2.60; range: 3-11).
-Furthermore, they had an average teaching experience of 10.90 teaching units à 45min (\emph{SD} = 8.10; range: 0-36) through the internships during their studies.
-19.23\% of the novices were studying to become primary school teachers, 65.38\% to become secondary school teachers and 15.38\% to become special education teachers.
-88.46\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+The expert teachers (25 women; 59.52\%) had a mean age of 39.30 years (\emph{SD} = 10.60; range: 26-60) and an average teaching experience of 11.80 years (\emph{SD} = 11.40; range: 1-38).
+9.52\% of the experts were primary school teachers and 80.95\% were secondary school teachers.
+NA\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+
+The novice teachers (29 women; 69.05\%) had a mean age of 22.80 years (\emph{SD} = 1.90; range: 19-27) with an average teaching experience of 0 years.
+On average, the student teachers were in their 6.70 semester (\emph{SD} = 2.60; range: 3-11).
+Furthermore, they had an average teaching experience of 9.60 teaching units à 45min (\emph{SD} = 7.20; range: 0-36) through the internships during their studies.
+21.43\% of the novices were studying to become primary school teachers, 57.14\% to become secondary school teachers and 19.05\% to become special education teachers.
+88.10\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
 
@@
 
-\hypertarget{design}{%
-\subsection{Design}\label{design}}
+\subsection{Design}\label{design}
 
@@
 The study was based on a quasi-experimental study design, as there was no random assignment of subjects to experimental conditions.
-Due to the use of MET technology, the study had a high external validity (Gegenfurtner et al., 2018).
-To ensure internal validity the occurring instructional events were exactly the same for all subjects, as the learners received precise behavioral instructions.
+Due to the use of MET technology, the study had a high external validity (Gegenfurtner et al., 2018) To ensure internal validity the occurring instructional events were exactly the same for all subjects, as the learners received precise behavioral instructions.
 These disruptions followed a script and coding guide in which the actions of the class were precisely described.
@@
 
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
-
-\hypertarget{eye-tracking-apparatus}{%
-\subsubsection{Eye-Tracking Apparatus}\label{eye-tracking-apparatus}}
+\subsection{Materials and Measures}\label{materials-and-measures}
+
+\subsubsection{Eye-Tracking Data}\label{eye-tracking-data}
+
+\paragraph{Apparatus}\label{apparatus}
 
@@
 
-\hypertarget{video-data}{%
-\subsubsection{Video data}\label{video-data}}
-
-\hypertarget{apparatus}{%
-\paragraph{Apparatus}\label{apparatus}}
+\paragraph{Teachers' visual focus of attention}\label{teachers-visual-focus-of-attention}
+
+Teachers' areas of interest (AOI) were identified as targets where teachers looked during the micro-teaching-unit using Tobii Pro Lab Analyzer Software Version 1.171.
+In the present study, general AOIs where defined as the student group, the students' nametags, the teacher material, the students' material, the board and non-instructional material in the classroom (wall, window, floor).
+These AOIs were coded during the manual fixation mapping process during the entire micro-teaching-unit.
+Additionally, the disruptive person was coded as an event-based AOI only over the duration of the disruption.
+
+--\textgreater{} Only eye-tracking video recordings with 70 \% and above gaze sample percentages were selected for the study to ensure that one or both eyes were detected during 70 \% of the recording's duration (Chaudhuri et al, 2022).
+Screenshots of the video recordings were used to define the AOI in the eye-tracking videos.
+The coder started manual gaze mapping when the teacher entered the classroom and ended coding when the micro-teaching-unit ended.
+The start and end of the micro-teaching-unit was defined by a visual and acoustical signal.
+The two coders who were assigned to code the eye-tracking videos student employees who studied to be teachers and received a detailed introduction to the software.
+The intercoder reliability was checked by double coding 20 \% of the videos from the whole dataset.
+Double coding agreement ranged from XXX \% to XXX \%.
+
+We coded each fixation using the Attention Filter in Pro Lab with the velocity threshold parameter set to 100 degrees/second instead of the default 30 degrees/second.
+This filter is suitable for dynamic situations to study attention without separating any eye movements.
+By choosing the Attention Filter typical fixations, most VOR (Vestibulo-ocular reflex), smooth pursuit eye movements, and slow saccades are classified as fixations.
+
+The relevant fixation metrics such as number of fixations, the total duration of fixations and time to first fixation on the relevant event (disruptive person) were obtained by exporting an interval-based TSV file from the Tobii Pro Lab Analyzer Software.
+The total fixation duration and the time to first fixation metrics were measured in milliseconds (ms) and the number of fixation in counts as an integer.
+To calculate the average fixation of durations for all AOIs, we divided the total duration of fixations by the number of fixations for each AOI.
+
+\subsubsection{Video data}\label{video-data}
+
+\paragraph{Apparatus}\label{apparatus-1}
 
@@
 
-\hypertarget{videography-coding-scheme-for-expertise-indicators}{%
-\paragraph{Videography: Coding scheme for expertise indicators}\label{videography-coding-scheme-for-expertise-indicators}}
+\paragraph{Videography: Coding scheme for expertise indicators}\label{videography-coding-scheme-for-expertise-indicators}
 
@@
 
-\hypertarget{coding-teachers-reaction}{%
-\subparagraph{Coding Teachers' Reaction}\label{coding-teachers-reaction}}
+\subparagraph{Teachers' Reaction to disruptions}\label{teachers-reaction-to-disruptions}
 
@@
 The coding of the reactions was done in seven levels.
-Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping (cf.~Kounin 2006; Gold \& Holodynski 2015) by not interrupting the flow of instruction.
+Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping (Gold \& Holodynski, 2015; cf.
+Kounin, 2006) by not interrupting the flow of instruction.
 Code 2 or Code 3 was assigned for a brief verbal expression with or without a preceding nonverbal response.
@@
 There were two possibilities, if there was no reaction: If the teacher deliberately ignored the disruption, code 5 was assigned.
-If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized (cf.~Gold \& Holodynski, 2015).
-If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned.
+If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized (cf.
+Gold \& Holodynski, 2015).If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned.
 According to Gippert et al.~(2019), there is a relational error in such cases, as the intensity of the student response should be relative to the disruptive behavior (p.~2).
@@
 In addition, video recordings can be viewed multiple times, by different people or from different perspectives.
-Thus, a high measurement accuracy (reliability) is given (cf.~Mayring, P., Gläser-Zikuda, M., \& Ziegelbauer, 2005).
+Thus, a high measurement accuracy (reliability) is given {[}cf.@mayring2005auswertung{]}.
 All measures taken contribute to increase the validity of the method.
@@
 
-\hypertarget{coding-time-on-task}{%
-\subparagraph{Coding Time on Task}\label{coding-time-on-task}}
-
-\hypertarget{questionnaie-data}{%
-\subsubsection{Questionnaie data}\label{questionnaie-data}}
-
-\hypertarget{presence-questionnaire}{%
-\paragraph{Presence Questionnaire}\label{presence-questionnaire}}
+\subparagraph{Coding Time on Task}\label{coding-time-on-task}
+
+XXX
+
+\subsubsection{Questionnaie data}\label{questionnaie-data}
+
+\paragraph{Presence Questionnaire}\label{presence-questionnaire}
 
@@
 
+Bilanz:
+LB01\_01 Bilanz: Die Lernenden haben in dieser Unterrichtslektion etwas dazu gelernt.
+LB01\_02 Bilanz: Die Lernenden haben sich in dieser Unterrichtslektion wohl gefühlt.
+LB01\_03 Bilanz: Mediennutzung und Sozialformen waren dem Inhalt und der Situation der Unterrichtslektion angemessen.
+
+Klassenmanagement:
+LM01\_01 Klassenmanagement: Die gesamte Unterrichtslektion wurde für den Lernstoff verwendet.
+LM01\_02 Klassenmanagement: Ich habe alles mitbekommen, was in der Klasse passiert ist.
+LM01\_03 Klassenmanagement: Den Lernenden war jederzeit klar, was sie tun sollten.
+LM01\_04 Klassenmanagement: Die Lernenden konnten ungestört arbeiten.
+LM01\_05 Klassenmanagement: Die Lernenden waren die ganze Unterrichtslektion über aktiv bei der Sache.
+LM01\_06 Klassenmanagement: Ich habe vieles mit kurzen Blicken und knappen Gesten geregelt.
+LM01\_07 Klassenmanagement: Auf Störungen habe ich angemessen reagiert.
+LM01\_08 Klassenmanagement: Bei Störungen gab ich den Lernenden ein klares STOP-Signal.
+
+Redeanteil:
+LO01\_01 Redeanteil: Wieviel Prozent der gesamten Unterrichtslektion hat nach Ihrer Schätzung Ihr eigener Redeanteil eingenommen? \ldots{} \%
+LO01\_02 Redeanteil: Wenn ich Fragen oder Aufgaben gestellt habe, habe ich den Lernenden folgende Zeit (in Sekunden) zum Nachdenken gegeben \ldots{} Sekunden
+
+Präsenz:
+LP01\_01 Präsenzindikatoren: Ich hatte eine aufrechte, der Klasse zugewandte Körperhaltung.
+LP01\_02 Präsenzindikatoren: Ich habe den Lernenden direkt in die Augen geschaut.
+LP01\_03 Präsenzindikatoren: Ich habe meine Position im Raum bewusst eingesetzt und variiert.
+LP01\_04 Präsenzindikatoren: Ich habe alle oft angesehen.
+LP01\_05 Präsenzindikatoren: Meine Artikulation, Lautstärke und Tonhöhe waren angemessen.
+LP01\_06 Präsenzindikatoren: Meine Sprechgeschwindigkeit und Sprechpausen waren angemessen.
+LP01\_07 Präsenzindikatoren: Mein Sprechanteil an der gesamten Sprechzeit der Unterrichtslektion war angemessen.
+LP01\_08 Präsenzindikatoren: Meine Gestik und Mimik waren abwechslungsreich und ausdrucksstark.
+
+Natürliches Verhalten:
+LV01\_01 Natürliches Verhalten: Während der Unterrichtslektion habe ich mich sehr natürlich verhalten.
+LV01\_02 Natürliches Verhalten: Es war für mich kein Problem, vor einer fiktiven Klasse zu unterrichten.
+LV01\_03 Natürliches Verhalten: Beim Unterrichten vor einer fiktiven Klasse habe ich mich so verhalten, wie ich es auch in der Schule tun würde.
+
 \begin{table}[h]
@@
 
-\caption{\label{tab:presence_questionnaire}Scale analysis for novices' self-assessment}
+\caption{\label{tab:presence_questionnaire}Scale analysis for teachers' self-assessment}
 
@@
 \toprule
- & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
+ & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Alpha}\\
 \midrule
-Classroom Management & 8.00 & 2.93 & 0.26 & 2.50 & 3.38 & 0.24 & 1.77 & 0.37\\
-Balance & 3.00 & 3.17 & 0.56 & 1.67 & 4.00 & -0.36 & 3.23 & 0.63\\
-Presence & 8.00 & 3.10 & 0.34 & 2.50 & 3.88 & 0.05 & 2.64 & 0.65\\
-Natural Behavior & 3.00 & 3.14 & 0.60 & 1.67 & 4.00 & -0.49 & 2.94 & 0.78\\
+Classroom Management & 8.00 & 3.09 & 0.35 & 2.38 & 3.88 & 0.29 & 2.45 & 0.60\\
+Balance & 3.00 & 3.27 & 0.52 & 1.67 & 4.00 & -0.49 & 3.14 & 0.69\\
+Presence & 8.00 & 3.21 & 0.40 & 2.12 & 3.88 & -0.38 & 2.44 & 0.74\\
+Natural Behavior & 3.00 & 3.25 & 0.63 & 1.33 & 4.00 & -0.72 & 3.14 & 0.78\\
 \bottomrule
@@
 
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:presence_questionnaire}Scale analysis for experts' self-assessment}
-
-\tiny{
-
-\begin{tabular}{lllllllll}
-\toprule
- & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
-\midrule
-Classroom Management & 8.00 & 3.18 & 0.37 & 2.38 & 3.88 & 0.00 & 2.74 & 0.65\\
-Balance & 3.00 & 3.30 & 0.57 & 2.00 & 4.00 & -0.74 & 2.79 & 0.76\\
-Presence & 8.00 & 3.36 & 0.37 & 2.50 & 3.88 & -0.61 & 2.76 & 0.76\\
-Natural Behavior & 3.00 & 3.44 & 0.45 & 2.67 & 4.00 & -0.17 & 1.98 & 0.60\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{rating-scales}{%
-\paragraph{Rating scales}\label{rating-scales}}
+\paragraph{Teachers' perception of disruption and confidence using Rating scales}\label{teachers-perception-of-disruption-and-confidence-using-rating-scales}
 
@@
 For the present study, the following two questions from the interview were relevant:
-1. ``How disturbing did you perceive this event to be?''
+1. ``How disruptive was this event for you?''
 2. ``How confident did you feel in dealing with this event?''
@@
 
-\hypertarget{situational-jugdement-test-of-strategic-knowledge-of-classroom-management}{%
-\paragraph{Situational Jugdement Test of Strategic Knowledge of Classroom Management}\label{situational-jugdement-test-of-strategic-knowledge-of-classroom-management}}
+\paragraph{Situational Jugdement Test of Strategic Knowledge of Classroom Management}\label{situational-jugdement-test-of-strategic-knowledge-of-classroom-management}
 
@@
 In this case, the teacher is able to control several teaching processes at the same time.
-Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf.~ibid.; {[}Kounin (2006), p.~89ff).
+Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions {[}cf.~ibid.; Kounin (2006), p.~89ff{]}.
 
@@
 In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}.
-The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
-Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
+The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.50; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.1.3; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{ggrepel} (Version 0.9.4; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.3; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.45; Xie, 2015), \emph{lme4} (Version 1.1.35.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.4; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
+Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.15; Lüdecke, 2021), \emph{sp} (E.
 J.
-Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
+Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M.
+Barth, 2022), \emph{viridis} (Version 0.6.4; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
 
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+XXX FRANZI
+
+\subsection{Procedure}\label{procedure}
 
@@
 
-Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire.
+Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management (SJT, Gold \& Holodynski, 2015) in the form of a questionnaire.
 Here they had to assess teaching scenarios and evaluate their behavior in response to them.
@@
 
-All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.8; Wickham et al., 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson et al., 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham et al., 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
-Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
+All reported data analyses were conducted with the R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.50; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.1.3; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{ggrepel} (Version 0.9.4; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.3; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.45; Xie, 2015), \emph{lme4} (Version 1.1.35.1; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.4; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
+Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.15; Lüdecke, 2021), \emph{sp} (E.
 J.
-Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M.
+Barth, 2022), \emph{viridis} (Version 0.6.4; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.
+
+\section{Results}\label{results}
+
+\section{Discussion}\label{discussion}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
@@
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-albers2009methodik}{}}%
+\bibitem[\citeproctext]{ref-albers2009methodik}
 Albers, S., Klapper, D., Konradt, U., Walter, A., \& Wolf, J. (2009). \emph{Methodik der empirischen forschung} (Vol. 3). Springer.
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-DescTools}{}}%
+\bibitem[\citeproctext]{ref-R-DescTools}
 Andri et mult. al., S. (2022). \emph{{DescTools}: Tools for descriptive statistics}. Retrieved from \url{https://cran.r-project.org/package=DescTools}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
+\bibitem[\citeproctext]{ref-R-ggthemes}
 Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-gridExtra}{}}%
+\bibitem[\citeproctext]{ref-R-gridExtra}
 Auguie, B. (2017). \emph{gridExtra: Miscellaneous functions for "grid" graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridExtra}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
+\bibitem[\citeproctext]{ref-R-papaja}
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
+\bibitem[\citeproctext]{ref-R-tinylabels}
 Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
+\bibitem[\citeproctext]{ref-barth2017professionelle}
+Barth, V. L. (2017). \emph{Professionelle wahrnehmung von st{ö}rungen im unterricht}. Springer.
+
+\bibitem[\citeproctext]{ref-R-lme4}
 Bates, D., Mächler, M., Bolker, B., \& Walker, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
+\bibitem[\citeproctext]{ref-R-Matrix}
 Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-rgeos}{}}%
+\bibitem[\citeproctext]{ref-baumert2006key}
+Baumert, J., \& Kunter, M. (2006). Key word: Professional competence of teachers. \emph{ZEITSCHRIFT FUR ERZIEHUNGSWISSENSCHAFT}, \emph{9}(4), 469--520.
+
+\bibitem[\citeproctext]{ref-berliner1994expertise}
+Berliner, D. C. (1994). Expertise: The wonders of exemplary performance. \emph{Creating Powerful Thinking in Teachers and Students}, 161--186.
+
+\bibitem[\citeproctext]{ref-R-rgeos}
 Bivand, R., \& Rundel, C. (2021). \emph{Rgeos: Interface to geometry engine - open source ('GEOS')}. Retrieved from \url{https://CRAN.R-project.org/package=rgeos}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-xtable}{}}%
+\bibitem[\citeproctext]{ref-blake2013eye}
+Blake, C. (2013). Eye-tracking: Grundlagen und anwendungsfelder. In \emph{Handbuch standardisierte erhebungsverfahren in der kommunikationswissenschaft} (pp. 367--387). Springer.
+
+\bibitem[\citeproctext]{ref-R-xtable}
 Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-polycor}{}}%
+\bibitem[\citeproctext]{ref-eckstein2016unterrichtliche}
+Eckstein, B., Grob, U., \& Reusser, K.
+(2016).
+Unterrichtliche devianz und subjektives st{ö}rungsempfinden.
+Entwicklung eines instrumentariums zur erfassung von unterrichtsst{ö}rungen.
+\emph{Empirische P{ä}dagogik (EP)}, \emph{30}(1), 113--129.
+
+\bibitem[\citeproctext]{ref-emmer1982improving}
+Emmer, E., Sanford, J., Clements, B., \& Martin, J.
+(1982).
+Improving classroom management and organization in junior high schools.
+\emph{An.
+Experimental, Investigation.
+Washington, DC: National Institute}.
+
+\bibitem[\citeproctext]{ref-epstein2002defining}
+Epstein, R. M., \& Hundert, E. M. (2002). Defining and assessing professional competence. \emph{Jama}, \emph{287}(2), 226--235.
+
+\bibitem[\citeproctext]{ref-evertson2006classroom}
+Evertson, C. M., Weinstein, C. S., et al. (2006). Classroom management as a field of inquiry. \emph{Handbook of Classroom Management: Research, Practice, and Contemporary Issues}, \emph{3}(1), 16.
+
+\bibitem[\citeproctext]{ref-R-janitor}
+Firke, S. (2021). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
+
+\bibitem[\citeproctext]{ref-R-polycor}
 Fox, J. (2022). \emph{Polycor: Polychoric and polyserial correlations}. Retrieved from \url{https://CRAN.R-project.org/package=polycor}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
+\bibitem[\citeproctext]{ref-R-viridis}
 Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
+\bibitem[\citeproctext]{ref-R-viridisLite}
 Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
 
-\leavevmode\vadjust pre{\hypertarget{ref-gegenfurtner2018mobiles}{}}%
+\bibitem[\citeproctext]{ref-gegenfurtner2018mobiles}
 Gegenfurtner, A., Eichinger, A., Latzel, R., Dietrich, M. P., Barkowsky, M., Glufke, A., \ldots{} Stern, W. (2018). \emph{Mobiles eye-tracking in den angewandten wissenschaften}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gold2015development}{}}%
+\bibitem[\citeproctext]{ref-gold2015development}
 Gold, B., \& Holodynski, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-lubridate}{}}%
+\bibitem[\citeproctext]{ref-gold2017using}
+Gold, B., \& Holodynski, M.
+(2017).
+Using digital video to measure the professional vision of elementary classroom management: Test validation and methodological challenges.
+\emph{Computers \& Education}, \emph{107}, 13--30.
+
+\bibitem[\citeproctext]{ref-R-lubridate}
 Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with {lubridate}. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{https://www.jstatsoft.org/v40/i03/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}}%
+\bibitem[\citeproctext]{ref-grub2020process}
+Grub, A.-S., Biermann, A., \& Brünken, R.
+(2020).
+Process-based measurement of professional vision of (prospective) teachers in the field of classroom management.
+A systematic review.
+\emph{Journal for Educational Research Online}, \emph{12}(3), 75--102.
+
+\bibitem[\citeproctext]{ref-helmke2014unterrichtsdiagnostik}
 Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
+\bibitem[\citeproctext]{ref-R-purrr}
 Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-rlang}{}}%
+\bibitem[\citeproctext]{ref-R-rlang}
 Henry, L., \& Wickham, H. (2022). \emph{Rlang: Functions for base types and core r and 'tidyverse' features}. Retrieved from \url{https://CRAN.R-project.org/package=rlang}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-msm}{}}%
+\bibitem[\citeproctext]{ref-R-msm}
 Jackson, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggmosaic}{}}%
+\bibitem[\citeproctext]{ref-jahn2014professionelle}
+Jahn, G., Stürmer, K., Seidel, T., \& Prenzel, M.
+(2014).
+Professionelle unterrichtswahrnehmung von lehramtsstudierenden: Eine scaling-up studie des observe-projekts.
+\emph{Zeitschrift f{ü}r Entwicklungspsychologie Und p{ä}dagogische Psychologie}, \emph{46}(4), 171--180.
+
+\bibitem[\citeproctext]{ref-R-ggmosaic}
 Jeppson, H., Hofmann, H., \& Cook, D. (2021). \emph{Ggmosaic: Mosaic plots in the 'ggplot2' framework}. Retrieved from \url{https://CRAN.R-project.org/package=ggmosaic}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-needs}{}}%
+\bibitem[\citeproctext]{ref-R-needs}
 Katz, J. (2016). \emph{Needs: Attaches and installs packages}. Retrieved from \url{https://CRAN.R-project.org/package=needs}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-moments}{}}%
+\bibitem[\citeproctext]{ref-kleinknecht2013teachers}
+Kleinknecht, M., \& Schneider, J. (2013). What do teachers think and feel when analyzing videos of themselves and other teachers teaching? \emph{Teaching and Teacher Education}, \emph{33}, 13--23.
+
+\bibitem[\citeproctext]{ref-klieme2008concept}
+Klieme, E., Hartig, J., \& Rauch, D. (2008). The concept of competence in educational contexts. \emph{Assessment of Competencies in Educational Contexts}, \emph{3}, 22.
+
+\bibitem[\citeproctext]{ref-R-moments}
 Komsta, L., \& Novomestky, F. (2015). \emph{Moments: Moments, cumulants, skewness, kurtosis and related tests}. Retrieved from \url{https://CRAN.R-project.org/package=moments}
 
-\leavevmode\vadjust pre{\hypertarget{ref-kounin2006techniken}{}}%
+\bibitem[\citeproctext]{ref-kounin2006techniken}
 Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-sjPlot}{}}%
+\bibitem[\citeproctext]{ref-lachner2016makes}
+Lachner, A., Jarodzka, H., \& Nückles, M.
+(2016).
+What makes an expert teacher?
+Investigating teachers' professional vision and discourse abilities.
+\emph{Instructional Science}, \emph{44}(3), 197--203.
+
+\bibitem[\citeproctext]{ref-leinhardt1986cognitive}
+Leinhardt, G., \& Greeno, J. G. (1986). The cognitive skill of teaching. \emph{Journal of Educational Psychology}, \emph{78}(2), 75.
+
+\bibitem[\citeproctext]{ref-R-sjPlot}
 Lüdecke, D. (2021). \emph{sjPlot: Data visualization for statistics in social science}. Retrieved from \url{https://CRAN.R-project.org/package=sjPlot}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-sjlabelled}{}}%
+\bibitem[\citeproctext]{ref-R-sjlabelled}
 Lüdecke, D. (2022). \emph{Sjlabelled: Labelled data utility functions (version 1.2.0)}. \url{https://doi.org/10.5281/zenodo.1249215}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
+\bibitem[\citeproctext]{ref-marzano2003classroom}
+Marzano, R. J., Marzano, J. S., \& Pickering, D. (2003). \emph{Classroom management that works: Research-based strategies for every teacher}. ASCD.
+
+\bibitem[\citeproctext]{ref-R-imputeTS}
+Moritz, S., \& Bartz-Beielstein, T. (2017). {imputeTS: Time Series Missing Value Imputation in R}. \emph{{The R Journal}}, \emph{9}(1), 207--218. \url{https://doi.org/10.32614/RJ-2017-009}
+
+\bibitem[\citeproctext]{ref-R-tibble}
 Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
-\leavevmode\vadjust pre{\hypertarget{ref-palmer2005identifying}{}}%
+\bibitem[\citeproctext]{ref-oser2006competence}
+Oser, F. K., Achtenhagen, F., \& Renold, U. (2006). Competence-oriented teacher training: Old research demands and new pathways. In \emph{Competence oriented teacher training} (pp. 1--7). Brill.
+
+\bibitem[\citeproctext]{ref-palmer2005identifying}
 Palmer, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-sf}{}}%
+\bibitem[\citeproctext]{ref-R-sf}
 Pebesma, E. (2018). {Simple Features for R: Standardized Support for Spatial Vector Data}. \emph{{The R Journal}}, \emph{10}(1), 439--446. \url{https://doi.org/10.32614/RJ-2018-009}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-sp}{}}%
+\bibitem[\citeproctext]{ref-R-sp}
 Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. Retrieved from \url{https://CRAN.R-project.org/doc/Rnews/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+\bibitem[\citeproctext]{ref-R-base}
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-formattable}{}}%
+\bibitem[\citeproctext]{ref-R-formattable}
 Ren, K., \& Russell, K. (2021). \emph{Formattable: Create 'formattable' data structures}. Retrieved from \url{https://CRAN.R-project.org/package=formattable}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-ltm}{}}%
+\bibitem[\citeproctext]{ref-R-ltm}
 Rizopoulos, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggrepel}{}}%
+\bibitem[\citeproctext]{ref-sabers1991differences}
+Sabers, D.
+S., Cushing, K.
+S., \& Berliner, D.
+C.
+(1991).
+Differences among teachers in a task characterized by simultaneity, multidimensional, and immediacy.
+\emph{American Educational Research Journal}, \emph{28}(1), 63--88.
+
+\bibitem[\citeproctext]{ref-seidel2014modeling}
+Seidel, T., \& Stürmer, K. (2014). Modeling and measuring the structure of professional vision in preservice teachers. \emph{American Educational Research Journal}, \emph{51}(4), 739--771.
+
+\bibitem[\citeproctext]{ref-sherin2007development}
+Sherin, M.
+(2007).
+\emph{The development of teachers' professional vision in video clubs.
+Video research in the learning sciences.
+R.
+Goldman, r.
+Pea, b.
+Barron and SJ derry}.
+Mahwah, NJ, Lawrence Erlbaum.
+
+\bibitem[\citeproctext]{ref-R-ggrepel}
 Slowikowski, K. (2021). \emph{Ggrepel: Automatically position non-overlapping text labels with 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggrepel}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-rnaturalearth}{}}%
+\bibitem[\citeproctext]{ref-R-rnaturalearth}
 South, A. (2017a). \emph{Rnaturalearth: World map data from natural earth}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearth}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-rnaturalearthdata}{}}%
+\bibitem[\citeproctext]{ref-R-rnaturalearthdata}
 South, A. (2017b). \emph{Rnaturalearthdata: World vector map data from natural earth used in 'rnaturalearth'}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearthdata}
 
-\leavevmode\vadjust pre{\hypertarget{ref-van2014first}{}}%
-Van den Bogert, N., Bruggen, J.
-van, Kostons, D., \& Jochems, W.
-(2014).
-First steps into understanding teachers' visual perception of classroom events.
-\emph{Teaching and Teacher Education}, \emph{37}, 208--216.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-MASS}{}}%
+\bibitem[\citeproctext]{ref-treisch2018entwicklung}
+Treisch, F. (2018). \emph{Die entwicklung der professionellen unterrichtswahrnehmung im lehr-lern-labor seminar}. Bayerische Julius-Maximilians-Universitaet Wuerzburg (Germany).
+
+\bibitem[\citeproctext]{ref-R-MASS}
 Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+\bibitem[\citeproctext]{ref-R-ggplot2}
 Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
+\bibitem[\citeproctext]{ref-R-stringr}
 Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
+\bibitem[\citeproctext]{ref-R-forcats}
 Wickham, H. (2021). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
+\bibitem[\citeproctext]{ref-R-tidyverse}
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
+\bibitem[\citeproctext]{ref-R-readxl}
 Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
+\bibitem[\citeproctext]{ref-R-dplyr}
 Wickham, H., François, R., Henry, L., \& Müller, K. (2022). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
+\bibitem[\citeproctext]{ref-R-tidyr}
 Wickham, H., \& Girlich, M. (2022). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
+\bibitem[\citeproctext]{ref-R-readr}
 Wickham, H., Hester, J., \& Bryan, J. (2021). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-haven}{}}%
+\bibitem[\citeproctext]{ref-R-haven}
 Wickham, H., \& Miller, E. (2021). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. Retrieved from \url{https://CRAN.R-project.org/package=haven}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
+\bibitem[\citeproctext]{ref-R-cowplot}
 Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-knitr}{}}%
+\bibitem[\citeproctext]{ref-wolff2015keeping}
+Wolff, C.
+E., Bogert, N.
+van den, Jarodzka, H., \& Boshuizen, H.
+P.
+(2015).
+Keeping an eye on learning: Differences between expert and novice teachers' representations of classroom management events.
+\emph{Journal of Teacher Education}, \emph{66}(1), 68--85.
+
+\bibitem[\citeproctext]{ref-wolff2016teacher}
+Wolff, C.
+E., Jarodzka, H., Bogert, N.
+van den, \& Boshuizen, H.
+(2016).
+Teacher vision: Expert and novice teachers' perception of problematic classroom management scenes.
+\emph{Instructional Science}, \emph{44}(3), 243--265.
+
+\bibitem[\citeproctext]{ref-R-knitr}
 Xie, Y. (2015). \emph{Dynamic documents with {R} and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.org/knitr/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-ARTofR}{}}%
+\bibitem[\citeproctext]{ref-R-ARTofR}
 Zhang, H. (2021). \emph{ARTofR: Who ever care about the {[}art of r{]} scripts?} Retrieved from \url{https://CRAN.R-project.org/package=ARTofR}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
+\bibitem[\citeproctext]{ref-R-kableExtra}
 Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}

### 2024-07-04 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.tex
expertise

@@
 In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}.
-The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.50; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.1.3; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{ggrepel} (Version 0.9.4; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.3; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.45; Xie, 2015), \emph{lme4} (Version 1.1.35.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.4; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
-Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.15; Lüdecke, 2021), \emph{sp} (E.
+The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
+Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E.
 J.
-Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M.
-Barth, 2022), \emph{viridis} (Version 0.6.4; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
+Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M.
+Barth, 2022), \emph{viridis} (Version 0.6.5; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
 
@@
 
-All reported data analyses were conducted with the R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.50; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.1.3; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{ggrepel} (Version 0.9.4; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.3; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.45; Xie, 2015), \emph{lme4} (Version 1.1.35.1; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.4; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
-Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.15; Lüdecke, 2021), \emph{sp} (E.
+All reported data analyses were conducted with the R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.1.4; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
+Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E.
 J.
-Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M.
-Barth, 2022), \emph{viridis} (Version 0.6.4; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.
+Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M.
+Barth, 2022), \emph{viridis} (Version 0.6.5; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.
 

### 2024-07-05 02_paper/02_study/02_eye tracking video questionnaire paper/emu_questionnaire.Rmd
expertise
emu

@@
 
-Klassenmanagement:
+```{r presence_questionnaire, echo=FALSE, results=TRUE}
 
-LM01_01	Klassenmanagement: Die gesamte Unterrichtslektion wurde für den Lernstoff verwendet.
-
-LM01_02	Klassenmanagement: Ich habe alles mitbekommen, was in der Klasse passiert ist.
-
-LM01_03	Klassenmanagement: Den Lernenden war jederzeit klar, was sie tun sollten.
-
-LM01_04	Klassenmanagement: Die Lernenden konnten ungestört arbeiten.
-
-LM01_05	Klassenmanagement: Die Lernenden waren die ganze Unterrichtslektion über aktiv bei der Sache.
-
-LM01_06	Klassenmanagement: Ich habe vieles mit kurzen Blicken und knappen Gesten geregelt.
-
-LM01_07	Klassenmanagement: Auf Störungen habe ich angemessen reagiert.
-
-LM01_08	Klassenmanagement: Bei Störungen gab ich den Lernenden ein klares STOP-Signal.
-
-Präsenz:
-
-LP01_01	Präsenzindikatoren: Ich hatte eine aufrechte, der Klasse zugewandte Körperhaltung.
-
-LP01_02	Präsenzindikatoren: Ich habe den Lernenden direkt in die Augen geschaut.
-
-LP01_03	Präsenzindikatoren: Ich habe meine Position im Raum bewusst eingesetzt und variiert.
-
-LP01_04	Präsenzindikatoren: Ich habe alle oft angesehen.
-
-LP01_05	Präsenzindikatoren: Meine Artikulation, Lautstärke und Tonhöhe waren angemessen.
-
-LP01_06	Präsenzindikatoren: Meine Sprechgeschwindigkeit und Sprechpausen waren angemessen.
-
-LP01_07	Präsenzindikatoren: Mein Sprechanteil an der gesamten Sprechzeit der Unterrichtslektion war angemessen.
-
-LP01_08	Präsenzindikatoren: Meine Gestik und Mimik waren abwechslungsreich und ausdrucksstark.
-
-Natürliches Verhalten:
-
-LV01_01	Natürliches Verhalten: Während der Unterrichtslektion habe ich mich sehr natürlich verhalten.
-
-LV01_02	Natürliches Verhalten: Es war für mich kein Problem, vor einer fiktiven Klasse zu unterrichten.
-
-LV01_03	Natürliches Verhalten: Beim Unterrichten vor einer fiktiven Klasse habe ich mich so verhalten, wie ich 
-es auch in der Schule tun würde.
-
-```{r presence_questionnaire, echo=FALSE, results=TRUE}
+# original scale analysis
 
@@
 quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LI06_05, 
-                LB01_01:LB01_03,
-                LM01_01:LM01_08,
+  dplyr::select(LB01_01:LB01_03,
+                LM01_01,
+                LM01_03:LM01_08,
                 LP01_01:LP01_08,
                 LV01_01:LV01_03)
+
+# descriptive data
+describe(quest.data)
+
+# omega
+omega(quest.data)
 
@@
 
+# load data files with modified sclaes
+quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  dplyr::select(LB01_01:LB01_03,
+                LM01_01:LM01_08,
+                LP01_01:LP01_08,
+                LV01_01:LV01_03) %>% 
+  rename(
+    LZ01_06 = LM01_06,
+    LZ01_07 = LM01_07,
+    LZ01_08 = LM01_08
+    )
+
+# descriptive data
+describe(quest.data)
+
+# omega
+omega(quest.data)
+
+# creating a matrix
+quest.table <- matrix(data = NA, nrow = 5, ncol = 8)
+rownames(quest.table) <- c("LM", "LB", "LP", "LV", "LZ")
+colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
+
+# creating a loop
+i <- "LM"
+
+for (i in c("LM", "LB", "LP", "LV", "LZ")) {
+
+loop.data <- quest.data %>%
+  dplyr::select(starts_with(match = i))
+
+quest.table[i, "N Items"] <- length(loop.data)
+
+# calculating mean
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  mean() %>%
+  round(., digits = 2) ->
+quest.table[i, "M"]
+
+# calculating SD
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  sd() %>%
+  round(., digits = 2) ->
+quest.table[i, "SD"]
+
+# calculating Min
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  min() %>%
+  round(., digits = 2) ->
+quest.table[i, "Min"]
+
+# calculating Max
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  max() %>%
+  round(., digits = 2) ->
+quest.table[i, "Max"]
+
+# calculating Skewness
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  skewness() %>%
+  round(., digits = 2) ->
+quest.table[i, "Skewness"]
+
+# calculating Kurtosis
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  kurtosis() %>%
+  round(., digits = 2) ->
+quest.table[i, "Kurtosis"]
+
+# calculating Alpha
+alpha <- loop.data %>%
+  cronbach.alpha()
+
+quest.table[i, "Alpha"] <- round(alpha$alpha,2)
+
+}
+
+# rename columns
+rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior", "Additional")
+
+# format and insert table in manuscript
+papaja::apa_table(
+quest.table,
+  caption = "Scale analysis for teachers' self-assessment",
+  # note = "Write Note here",
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+)
+
 ```
@@
 ```
+
+```{r item_analysis_additional, echo=FALSE, results='asis'}
+quest.data %>%
+  dplyr::select(contains("LZ")) %>%
+  as.data.frame() %>%
+  tab_itemscale()
+```

### 2024-07-05 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.tex
emu

@@
 
+\begin{verbatim}
+    vars  n mean   sd median trimmed  mad min max range  skew kurtosis   se
+\end{verbatim}
+
+LB01\_01 1 84 3.33 0.66 3 3.41 1.48 1 4 3 -0.72 0.43 0.07
+LB01\_02 2 84 3.11 0.68 3 3.16 0.00 1 4 3 -0.59 0.79 0.07
+LB01\_03 3 84 3.37 0.64 3 3.44 1.48 2 4 2 -0.48 -0.72 0.07
+LM01\_01 4 84 3.32 0.73 3 3.43 1.48 1 4 3 -0.93 0.67 0.08
+LM01\_03 5 84 3.36 0.53 3 3.35 0.00 2 4 2 0.10 -1.02 0.06
+LM01\_04 6 84 3.23 0.65 3 3.28 0.00 2 4 2 -0.24 -0.74 0.07
+LM01\_05 7 84 2.71 0.69 3 2.68 0.00 1 4 3 -0.02 -0.34 0.07
+LM01\_06 8 84 2.54 0.84 2 2.53 1.48 1 4 3 0.19 -0.67 0.09
+LM01\_07 9 84 3.27 0.65 3 3.34 0.00 2 4 2 -0.32 -0.76 0.07
+LM01\_08 10 84 3.02 0.76 3 3.07 0.00 1 4 3 -0.53 0.06 0.08
+LP01\_01 11 84 3.33 0.65 3 3.41 1.48 2 4 2 -0.43 -0.76 0.07
+LP01\_02 12 84 3.33 0.63 3 3.40 0.74 2 4 2 -0.38 -0.73 0.07
+LP01\_03 13 84 2.89 0.78 3 2.88 1.48 1 4 3 0.03 -1.03 0.08
+LP01\_04 14 84 3.52 0.59 4 3.59 0.00 2 4 2 -0.78 -0.41 0.06
+LP01\_05 15 84 3.49 0.57 4 3.53 0.00 2 4 2 -0.53 -0.77 0.06
+LP01\_06 16 84 3.19 0.70 3 3.24 1.48 2 4 2 -0.27 -0.99 0.08
+LP01\_07 17 84 3.00 0.68 3 3.01 0.00 1 4 3 -0.23 -0.16 0.07
+LP01\_08 18 84 2.90 0.67 3 2.90 0.00 1 4 3 -0.13 -0.24 0.07
+LV01\_01 19 84 3.23 0.68 3 3.29 0.00 1 4 3 -0.53 0.05 0.07
+LV01\_02 20 84 3.32 0.84 4 3.44 0.00 1 4 3 -1.01 0.14 0.09
+LV01\_03 21 84 3.19 0.75 3 3.25 1.48 1 4 3 -0.49 -0.58 0.08
+\includegraphics{paper_methods_files/figure-latex/presence_questionnaire-1.pdf} Omega
+Call: omegah(m = m, nfactors = nfactors, fm = fm, key = key, flip = flip,
+digits = digits, title = title, sl = sl, labels = labels,
+plot = plot, n.obs = n.obs, rotate = rotate, Phi = Phi, option = option,
+covar = covar)
+Alpha: 0.83
+G.6: 0.88
+Omega Hierarchical: 0.34
+Omega H asymptotic: 0.4
+Omega Total 0.86
+
+Schmid Leiman Factor loadings greater than 0.2
+g F1* F2* F3* h2 h2 u2 p2 com
+LB01\_01 0.41 0.38 0.34 0.34 0.66 0.49 2.35
+LB01\_02 0.43 0.33 0.29 0.38 0.38 0.62 0.49 2.70
+LB01\_03 0.34 0.23 0.27 0.25 0.25 0.75 0.48 2.74
+LM01\_01 0.21 0.25 0.13 0.87 0.32 2.88
+LM01\_03 0.32 0.12 0.88 0.08 1.33
+LM01\_04 0.20 0.29 0.24 0.18 0.82 0.23 2.81
+LM01\_05 0.29 0.24 0.20 0.20 0.80 0.43 3.22
+LM01\_06 0.20 0.77 0.63 0.63 0.37 0.06 1.16
+LM01\_07 0.42 0.20 0.34 0.31 0.42 0.42 0.58 0.41 3.32
+LM01\_08 0.48 0.23 0.32 0.32 0.68 0.06 1.78
+LP01\_01 0.27 0.46 0.29 0.29 0.71 0.25 1.70
+LP01\_02 0.42 -0.30 0.27 0.27 0.73 0.02 1.85
+LP01\_03 0.21 0.43 0.23 0.23 0.77 0.20 1.51
+LP01\_04 0.58 0.38 0.38 0.62 0.05 1.23
+LP01\_05 0.24 0.63 0.46 0.46 0.54 0.12 1.30
+LP01\_06 0.32 0.43 0.34 0.41 0.41 0.59 0.26 2.84
+LP01\_07 0.41 0.19 0.81 0.02 1.17
+LP01\_08 0.28 0.47 0.35 0.35 0.65 0.22 2.15
+LV01\_01 0.53 0.46 0.53 0.53 0.47 0.54 2.19
+LV01\_02 0.49 0.44 0.45 0.45 0.55 0.53 2.10
+LV01\_03 0.48 0.58 0.60 0.60 0.40 0.38 2.19
+
+With Sums of squares of:
+g F1* F2* F3* h2
+2.0 1.2 2.8 1.2 2.8
+
+general/max 0.71 max/min = 2.41
+mean percent general = 0.27 with sd = 0.18 and cv of 0.68
+Explained Common Variance of the general factor = 0.28
+
+The degrees of freedom are 150 and the fit is 2.42
+The number of observations was 84 with Chi Square = 176.97 with prob \textless{} 0.065
+The root mean square of the residuals is 0.07
+The df corrected root mean square of the residuals is 0.08
+RMSEA index = 0.045 and the 10 \% confidence intervals are 0 0.072
+BIC = -487.65
+
+Compare this with the adequacy of just a general factor and no group factors
+The degrees of freedom for just the general factor are 189 and the fit is 4.53
+The number of observations was 84 with Chi Square = 337.7 with prob \textless{} 1.7e-10
+The root mean square of the residuals is 0.16
+The df corrected root mean square of the residuals is 0.17
+
+RMSEA index = 0.096 and the 10 \% confidence intervals are 0.08 0.114
+BIC = -499.73
+
+Measures of factor score adequacy\\
+g F1* F2* F3*
+Correlation of scores with factors 0.69 0.66 0.86 0.83
+Multiple R square of scores with factors 0.47 0.44 0.75 0.69
+Minimum correlation of factor score estimates -0.06 -0.13 0.49 0.38
+
+Total, General and Subset omega for each subset
+g F1* F2* F3*
+Omega total for total scores and subscales 0.86 0.78 0.79 0.52
+Omega general for total scores and subscales 0.34 0.42 0.17 0.10
+Omega group for total scores and subscales 0.40 0.37 0.63 0.42
+
 \begin{table}[h]
@@
 \midrule
-Classroom Management & 8.00 & 3.09 & 0.35 & 2.38 & 3.88 & 0.29 & 2.45 & 0.60\\
+Classroom Management & 7.00 & 3.06 & 0.39 & 2.14 & 4.00 & 0.11 & 2.61 & 0.63\\
 Balance & 3.00 & 3.27 & 0.52 & 1.67 & 4.00 & -0.49 & 3.14 & 0.69\\
@@
 The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
+al., 2022), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{psych} (Version 2.4.6.26; William Revelle, 2024), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
 Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E.
@@
 All reported data analyses were conducted with the R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.1.4; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
+al., 2022), \emph{dplyr} (Version 1.1.4; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{psych} (Version 2.4.6.26; William Revelle, 2024), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
 Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E.
@@
 
+\bibitem[\citeproctext]{ref-R-psych}
+William Revelle.
+(2024).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
 \bibitem[\citeproctext]{ref-wolff2015keeping}

### 2024-07-08 02_paper/02_study/02_eye tracking video questionnaire paper/emu_questionnaire.Rmd
emu questionnaire factor analysis

@@
 
+# Load packages
 ```{r include=FALSE}
@@
       formattable,
-      psych)
+      psych,
+      psy,
+      nFactors)
 
@@
 
+# Read in data
 ```{r presence_questionnaire, echo=FALSE, results=TRUE}
 
-# original scale analysis
-
-# load data files
-quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LB01_01:LB01_03,
-                LM01_01,
-                LM01_03:LM01_08,
-                LP01_01:LP01_08,
-                LV01_01:LV01_03)
-
-# descriptive data
-describe(quest.data)
-
-# omega
-omega(quest.data)
-
-# creating a matrix
-quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
-rownames(quest.table) <- c("LM", "LB", "LP", "LV")
-colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
-
-# creating a loop
-i <- "LM"
-
-for (i in c("LM", "LB", "LP", "LV")) {
-
-loop.data <- quest.data %>%
-  dplyr::select(starts_with(match = i))
-
-quest.table[i, "N Items"] <- length(loop.data)
-
-# calculating mean
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  mean() %>%
-  round(., digits = 2) ->
-quest.table[i, "M"]
-
-# calculating SD
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  sd() %>%
-  round(., digits = 2) ->
-quest.table[i, "SD"]
-
-# calculating Min
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  min() %>%
-  round(., digits = 2) ->
-quest.table[i, "Min"]
-
-# calculating Max
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  max() %>%
-  round(., digits = 2) ->
-quest.table[i, "Max"]
-
-# calculating Skewness
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  skewness() %>%
-  round(., digits = 2) ->
-quest.table[i, "Skewness"]
-
-# calculating Kurtosis
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  kurtosis() %>%
-  round(., digits = 2) ->
-quest.table[i, "Kurtosis"]
-
-# calculating Alpha
-alpha <- loop.data %>%
-  cronbach.alpha()
-
-quest.table[i, "Alpha"] <- round(alpha$alpha,2)
-
-}
-
-# rename columns
-rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
-
-# format and insert table in manuscript
-papaja::apa_table(
-quest.table,
-  caption = "Scale analysis for teachers' self-assessment",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
+# # original scale analysis
+# 
+# # load data files
+# quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+#   dplyr::select(LB01_01:LB01_03,
+#                 LM01_01,
+#                 LM01_03:LM01_08,
+#                 LP01_01:LP01_08,
+#                 LV01_01:LV01_03) 
+# 
+# # descriptive data
+# describe(quest.data)
+# 
+# # omega
+# omega(quest.data)
+# 
+# # creating a matrix
+# quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
+# rownames(quest.table) <- c("LM", "LB", "LP", "LV")
+# colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
+# 
+# # creating a loop
+# i <- "LM"
+# 
+# for (i in c("LM", "LB", "LP", "LV")) {
+# 
+# loop.data <- quest.data %>%
+#   dplyr::select(starts_with(match = i))
+# 
+# quest.table[i, "N Items"] <- length(loop.data)
+# 
+# # calculating mean
+# loop.data %>%
+#   mutate(mean = rowMeans(.)) %>%
+#   pull(mean) %>%
+#   mean() %>%
+#   round(., digits = 2) ->
+# quest.table[i, "M"]
+# 
+# # calculating SD
+# loop.data %>%
+#   mutate(mean = rowMeans(.)) %>%
+#   pull(mean) %>%
+#   sd() %>%
+#   round(., digits = 2) ->
+# quest.table[i, "SD"]
+# 
+# # calculating Min
+# loop.data %>%
+#   mutate(mean = rowMeans(.)) %>%
+#   pull(mean) %>%
+#   min() %>%
+#   round(., digits = 2) ->
+# quest.table[i, "Min"]
+# 
+# # calculating Max
+# loop.data %>%
+#   mutate(mean = rowMeans(.)) %>%
+#   pull(mean) %>%
+#   max() %>%
+#   round(., digits = 2) ->
+# quest.table[i, "Max"]
+# 
+# # calculating Skewness
+# loop.data %>%
+#   mutate(mean = rowMeans(.)) %>%
+#   pull(mean) %>%
+#   skewness() %>%
+#   round(., digits = 2) ->
+# quest.table[i, "Skewness"]
+# 
+# # calculating Kurtosis
+# loop.data %>%
+#   mutate(mean = rowMeans(.)) %>%
+#   pull(mean) %>%
+#   kurtosis() %>%
+#   round(., digits = 2) ->
+# quest.table[i, "Kurtosis"]
+# 
+# # calculating Alpha
+# alpha <- loop.data %>%
+#   cronbach.alpha()
+# 
+# quest.table[i, "Alpha"] <- round(alpha$alpha,2)
+# 
+# }
+# 
+# # rename columns
+# rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
+# 
+# # format and insert table in manuscript
+# papaja::apa_table(
+# quest.table,
+#   caption = "Scale analysis for teachers' self-assessment",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+# )
 
@@
     )
+```
 
+# Scale analysis 
+```{r presence_questionnaire, echo=FALSE, results=TRUE}
 # descriptive data
 describe(quest.data)
-
-# omega
-omega(quest.data)
 
@@
 
+# calculating Alpha
+omega <- loop.data %>% 
+  omega()
+
 }
@@
 # format and insert table in manuscript
-papaja::apa_table(
+knitr::kable(
 quest.table,
@@
 ```
-
+# Item analysis 
 ```{r item_analysis_classroom_management, echo=FALSE, results='asis'}
@@
 ```
+
+# Exploratory factor analysis
+```{r item_analysis_additional, echo=FALSE, results='asis'}
+## Bartlett-Test 
+# --> prüft, ob Items miteinander korrelieren; das sollten sie tun
+cortest.bartlett(quest.data)
+# p < .05 --> p signifikant, d.h. Items korrelieren
+
+## Kaiser-Meyer-Olkin-Kriterium (KMO-Werte) Measure of Adequacy (MSA) prüfen 
+# gibt an, ob ein Datensatz für eine Faktorenanalyse geeignet ist
+# --> KMO & MSA-Werte sollten größer als 0.5 sein
+KMO(quest.data)
+# overall MSA = 0.7
+# einzelne MSA-Werte checken; sollten auch alle größer als 0.5 sein
+# Item "LZ01_06 Ich habe vieles mit kurzen Blicken und knappen Gesten geregelt" hat einen Wert von 0.43 --> Ausschluss 
+quest.data[, !names(quest.data) %in% c("LZ01_06")] -> clean.data.quest
+KMO(clean.data.quest)
+
+## Anzahl Faktoren mit MAP-Test (unter anderem) 
+# # durch verschiedene Methoden wird optimale Anzahl an Faktoren ermittelt
+# MAP-Test wird häufig empfohlen 
+# mit Varimax-Rotation (macht Sinn, da man die Interpretierbarkeit der Faktoren verbessert) und ML-Faktorenanalyse
+nfactors(clean.data.quest, 
+         rotate = "varimax", 
+         fm = "mle")
+# MAP-Wert = 2 Faktoren
+
+## Anzahl Faktoren kann auch mit Parallelanalyse bestimmt werden
+ev <- eigen(cor(clean.data.quest))
+ap <- parallel(subject = nrow(clean.data.quest),
+               var = ncol(clean.data.quest),
+               rep = 100,
+               cent = .05)
+nS <- nScree(x = ev$values,
+             aparallel = ap$eigen$qevpea)
+plotnScree(nS)
+# Parallel Analysis n = 2 factors
+
+## Maximum-Likelihood-Faktorenanalyse
+# passt methodisch am besten, wenn man noch eine konfirmatorische Faktorenanalyse machen will
+# 2 Faktoren
+# Varimax-Rotation
+fit1 <- factanal(x = clean.data.quest,
+                 factors = 4, # inhaltlich macht es keinen Sinn, nur 2 Faktoren anzunehmen
+                 rotation = "varimax")
+
+# Ergebnisse ausgeben lassen mit 2 Dezimalstellen und Faktorenladung < 0.3 unterdrückt
+print(fit1, 
+      digits = 2,
+      cutoff = .3)
+# wir sehen Faktorladungen, um die Faktoren zu interpretieren
+# Faktorladungen wurden nur ausgegeben, wenn sie größer als 0.3 und -0.3 waren (um nur große Faktorladungen zu sehen)
+# weiter unten: erklärte Varianz (Cumulative Var = 0.29) und wie ist Zuwachs der erklärten Varianz durch einzelne Faktoren
+# zurück zu Faktorladungen: ideal wäre eigentlich, wenn jedes Item nur auf einen Faktor lädt
+
+# Mit Uniquenesses kann Kommunalität berechnet werden
+# --> zeigen an, wie viel Varianz von den einzelnen Items durch die Faktoren erklärt wird (wie wichtig sind die einzelnen Items für Lösung)
+1-fit1$uniquenesses
+
+# Screeplot zur Visualisierung
+scree.plot(fit1$correlation)
+
+## Hauptachsenfaktorenanalyse
+# 4 Faktoren
+# Varimax-Rotation
+
+fit2 <- fa(r = clean.data.quest, 
+           nfactors = 4, 
+           rotate = "varimax")
+
+# Ergebnisse ausgeben
+fit2
+
+# Faktorladungen ausgeben
+fit2$loadings
+
+# Kommunalitäten ausgeben
+fit2$communality
+
+# Sceeplot 
+plot(fit2$values, 
+     type = "b")
+
+```

### 2024-07-08 02_paper/02_study/02_eye tracking video questionnaire paper/emu_questionnaire.Rmd
Update emu_questionnaire.Rmd

@@
 ```{r item_analysis_additional, echo=FALSE, results='asis'}
+
 ## Bartlett-Test 
 # --> prüft, ob Items miteinander korrelieren; das sollten sie tun
+
 cortest.bartlett(quest.data)
+
 # p < .05 --> p signifikant, d.h. Items korrelieren
@@
 # --> KMO & MSA-Werte sollten größer als 0.5 sein
+
 KMO(quest.data)
+
 # overall MSA = 0.7
 # einzelne MSA-Werte checken; sollten auch alle größer als 0.5 sein
+
 # Item "LZ01_06 Ich habe vieles mit kurzen Blicken und knappen Gesten geregelt" hat einen Wert von 0.43 --> Ausschluss
+
 quest.data[, !names(quest.data) %in% c("LZ01_06")] -> clean.data.quest
@@
 ## Anzahl Faktoren mit MAP-Test (unter anderem) 
-# # durch verschiedene Methoden wird optimale Anzahl an Faktoren ermittelt
+# durch verschiedene Methoden wird optimale Anzahl an Faktoren ermittelt
 # MAP-Test wird häufig empfohlen 
 # mit Varimax-Rotation (macht Sinn, da man die Interpretierbarkeit der Faktoren verbessert) und ML-Faktorenanalyse
+
 nfactors(clean.data.quest, 
@@
          fm = "mle")
+
 # MAP-Wert = 2 Faktoren
@@
 ## Anzahl Faktoren kann auch mit Parallelanalyse bestimmt werden
+
 ev <- eigen(cor(clean.data.quest))
@@
 plotnScree(nS)
+
 # Parallel Analysis n = 2 factors
+
+###################################################
 
@@
 # passt methodisch am besten, wenn man noch eine konfirmatorische Faktorenanalyse machen will
-# 2 Faktoren
+# n Faktoren
 # Varimax-Rotation
+
 fit1 <- factanal(x = clean.data.quest,
@@
 # Ergebnisse ausgeben lassen mit 2 Dezimalstellen und Faktorenladung < 0.3 unterdrückt
+
 print(fit1, 
@@
       cutoff = .3)
+
 # wir sehen Faktorladungen, um die Faktoren zu interpretieren
@@
 # --> zeigen an, wie viel Varianz von den einzelnen Items durch die Faktoren erklärt wird (wie wichtig sind die einzelnen Items für Lösung)
+
 1-fit1$uniquenesses
@@
 # Screeplot zur Visualisierung
+
 scree.plot(fit1$correlation)
+
+###################################################
 
@@
 # Ergebnisse ausgeben
+
 fit2
@@
 # Faktorladungen ausgeben
+
 fit2$loadings
@@
 # Kommunalitäten ausgeben
+
 fit2$communality
@@
 # Sceeplot
+
 plot(fit2$values, 
@@
 
+###################################################
+
+## Hauptkomponentenanalyse
+# 4 Faktoren
+# Varimax-Rotation
+
+fit3 <- principal(r = clean.data.quest,
+                  nfactors = 3, 
+                  rotate = "varimax")
+
+# Ergebnisse ausgeben
+
+fit3
+
+# Faktorladungen ausgeben
+
+fit3$loadings
+
+# Kommunalitäten ausgeben
+
+fit3$communality
+
+# Sceeplot
+
+plot(fit3$values, 
+     type = "b")
+
 ```

### 2024-07-09 02_paper/02_study/02_eye tracking video questionnaire paper/emu_questionnaire.Rmd
X paper

@@
 
-# Read in data
+# Scale analysis --> Classroom Management with 16 Items 
 ```{r presence_questionnaire, echo=FALSE, results=TRUE}
 
-# # original scale analysis
-# 
-# # load data files
-# quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-#   dplyr::select(LB01_01:LB01_03,
-#                 LM01_01,
-#                 LM01_03:LM01_08,
-#                 LP01_01:LP01_08,
-#                 LV01_01:LV01_03) 
-# 
-# # descriptive data
-# describe(quest.data)
-# 
-# # omega
-# omega(quest.data)
-# 
-# # creating a matrix
-# quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
-# rownames(quest.table) <- c("LM", "LB", "LP", "LV")
-# colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
-# 
-# # creating a loop
-# i <- "LM"
-# 
-# for (i in c("LM", "LB", "LP", "LV")) {
-# 
-# loop.data <- quest.data %>%
-#   dplyr::select(starts_with(match = i))
-# 
-# quest.table[i, "N Items"] <- length(loop.data)
-# 
-# # calculating mean
-# loop.data %>%
-#   mutate(mean = rowMeans(.)) %>%
-#   pull(mean) %>%
-#   mean() %>%
-#   round(., digits = 2) ->
-# quest.table[i, "M"]
-# 
-# # calculating SD
-# loop.data %>%
-#   mutate(mean = rowMeans(.)) %>%
-#   pull(mean) %>%
-#   sd() %>%
-#   round(., digits = 2) ->
-# quest.table[i, "SD"]
-# 
-# # calculating Min
-# loop.data %>%
-#   mutate(mean = rowMeans(.)) %>%
-#   pull(mean) %>%
-#   min() %>%
-#   round(., digits = 2) ->
-# quest.table[i, "Min"]
-# 
-# # calculating Max
-# loop.data %>%
-#   mutate(mean = rowMeans(.)) %>%
-#   pull(mean) %>%
-#   max() %>%
-#   round(., digits = 2) ->
-# quest.table[i, "Max"]
-# 
-# # calculating Skewness
-# loop.data %>%
-#   mutate(mean = rowMeans(.)) %>%
-#   pull(mean) %>%
-#   skewness() %>%
-#   round(., digits = 2) ->
-# quest.table[i, "Skewness"]
-# 
-# # calculating Kurtosis
-# loop.data %>%
-#   mutate(mean = rowMeans(.)) %>%
-#   pull(mean) %>%
-#   kurtosis() %>%
-#   round(., digits = 2) ->
-# quest.table[i, "Kurtosis"]
-# 
-# # calculating Alpha
-# alpha <- loop.data %>%
-#   cronbach.alpha()
-# 
-# quest.table[i, "Alpha"] <- round(alpha$alpha,2)
-# 
-# }
-# 
-# # rename columns
-# rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
-# 
-# # format and insert table in manuscript
-# papaja::apa_table(
-# quest.table,
-#   caption = "Scale analysis for teachers' self-assessment",
-#   # note = "Write Note here",
-#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-# )
-
-# load data files with modified sclaes
-quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LB01_01:LB01_03,
-                LM01_01:LM01_08,
-                LP01_01:LP01_08,
-                LV01_01:LV01_03) %>% 
-  rename(
-    LZ01_06 = LM01_06,
-    LZ01_07 = LM01_07,
-    LZ01_08 = LM01_08
-    )
-```
-
-# Scale analysis 
-```{r presence_questionnaire, echo=FALSE, results=TRUE}
-# descriptive data
-describe(quest.data)
+# load data files with modified scales
+quest.data1 <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  dplyr::select(LM01_01:LM01_08,
+                LP01_01:LP01_08) %>% 
+  rename(LM09 = LP01_01,
+         LM10 = LP01_02,
+         LM11 = LP01_03,
+         LM12 = LP01_04,
+         LM13 = LP01_05,
+         LM14 = LP01_06,
+         LM15 = LP01_07,
+         LM16 = LP01_08)
 
 # creating a matrix
-quest.table <- matrix(data = NA, nrow = 5, ncol = 8)
-rownames(quest.table) <- c("LM", "LB", "LP", "LV", "LZ")
-colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
+quest.table1 <- matrix(data = NA, nrow = 1, ncol = 8)
+rownames(quest.table1) <- c("LM")
+colnames(quest.table1) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
 
@@
 
-for (i in c("LM", "LB", "LP", "LV", "LZ")) {
+for (i in c("LM")) {
 
-loop.data <- quest.data %>%
+loop.data <- quest.data1 %>%
   dplyr::select(starts_with(match = i))
 
-quest.table[i, "N Items"] <- length(loop.data)
+quest.table1[i, "N Items"] <- length(loop.data)
 
@@
   round(., digits = 2) ->
-quest.table[i, "M"]
+quest.table1[i, "M"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "SD"]
+quest.table1[i, "SD"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "Min"]
+quest.table1[i, "Min"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "Max"]
+quest.table1[i, "Max"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "Skewness"]
+quest.table1[i, "Skewness"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "Kurtosis"]
+quest.table1[i, "Kurtosis"]
 
@@
 
-quest.table[i, "Alpha"] <- round(alpha$alpha,2)
+quest.table1[i, "Alpha"] <- round(alpha$alpha,2)
 
-# calculating Alpha
-omega <- loop.data %>% 
-  omega()
+# # calculating Alpha
+# omega <- loop.data %>% 
+#   omega()
 
@@
 # rename columns
-rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior", "Additional")
+rownames(quest.table1) <- c("Classroom Management")
 
@@
 knitr::kable(
-quest.table,
+quest.table1,
   caption = "Scale analysis for teachers' self-assessment",
@@
 
-```
-# Item analysis 
-```{r item_analysis_classroom_management, echo=FALSE, results='asis'}
-quest.data %>%
+quest.data1 %>%
   dplyr::select(contains("LM")) %>%
@@
   ))
+```
+
+# # Scale analysis --> Classroom Management (8 Items) and Presence (8 Items) 
+```{r presence_questionnaire, echo=FALSE, results=TRUE}
+
+# load data files with modified scales
+quest.data2 <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  dplyr::select(LM01_01:LM01_08,
+                LP01_01:LP01_08)
+
+# creating a matrix
+quest.table2 <- matrix(data = NA, nrow = 2, ncol = 8)
+rownames(quest.table2) <- c("LM", "LP")
+colnames(quest.table2) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
+
+# creating a loop
+i <- "LM"
+
+for (i in c("LM")) {
+
+loop.data <- quest.data2 %>%
+  dplyr::select(starts_with(match = i))
+
+quest.table2[i, "N Items"] <- length(loop.data)
+
+# calculating mean
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  mean() %>%
+  round(., digits = 2) ->
+quest.table2[i, "M"]
+
+# calculating SD
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  sd() %>%
+  round(., digits = 2) ->
+quest.table2[i, "SD"]
+
+# calculating Min
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  min() %>%
+  round(., digits = 2) ->
+quest.table2[i, "Min"]
+
+# calculating Max
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  max() %>%
+  round(., digits = 2) ->
+quest.table2[i, "Max"]
+
+# calculating Skewness
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  skewness() %>%
+  round(., digits = 2) ->
+quest.table2[i, "Skewness"]
+
+# calculating Kurtosis
+loop.data %>%
+  mutate(mean = rowMeans(.)) %>%
+  pull(mean) %>%
+  kurtosis() %>%
+  round(., digits = 2) ->
+quest.table2[i, "Kurtosis"]
+
+# calculating Alpha
+alpha <- loop.data %>%
+  cronbach.alpha()
+
+quest.table2[i, "Alpha"] <- round(alpha$alpha,2)
+
+}
+
+# rename columns
+rownames(quest.table2) <- c("Classroom Management", "Presence")
+
+# format and insert table in manuscript
+knitr::kable(
+quest.table2,
+  caption = "Scale analysis for teachers' self-assessment",
+  # note = "Write Note here",
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+)
+
+quest.data2 %>%
+  dplyr::select(contains("LM")) %>%
+  as.data.frame() %>%
+  tab_itemscale(CSS = list(
+    css.firsttablerow.col7 = "'cronbachs alpha';"
+  ))
+
+quest.data2 %>%
+  dplyr::select(contains("LP")) %>%
+  as.data.frame() %>%
+  tab_itemscale()
+
 ```
@@
 
-quest.data[, !names(quest.data) %in% c("LZ01_06")] -> clean.data.quest
-KMO(clean.data.quest)
+# quest.data[, !names(quest.data) %in% c("LZ01_06")] -> clean.data.quest
+# KMO(clean.data.quest)
 
@@
 
-ev <- eigen(cor(clean.data.quest))
-ap <- parallel(subject = nrow(clean.data.quest),
-               var = ncol(clean.data.quest),
+ev <- eigen(cor(quest.data))
+ap <- parallel(subject = nrow(quest.data),
+               var = ncol(quest.data),
                rep = 100,
@@
            nfactors = 4, 
-           rotate = "varimax")
+           rotate = "varimax",
+           cutoff = .3)
 
@@
 ## Hauptkomponentenanalyse
-# 4 Faktoren
+# 2 Faktoren
 # Varimax-Rotation
 
-fit3 <- principal(r = clean.data.quest,
-                  nfactors = 3, 
+fit3 <- principal(r = quest.data,
+                  nfactors = 2, 
                   rotate = "varimax")
@@
 
-fit3
+print(loadings(fit3), cutoff= .3)
 

### 2024-07-19 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
X paper

--- 2024-07-04 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.Rmd
@@
 ---
-title             : "Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions"
-shorttitle        : "Professional Vision in Micro-Teaching-Units"
-
-author: 
-  - name          : "Mandy Klatt"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Dittrichring 5-7, 04109 Leipzig"
-    email         : "mandy.klatt@uni-leipzig.de"
-  - name          : "Dr. Gregor Kachel"
-    affiliation   : "1, 2"
-  - name          : "Dr. Christin Lotz"
-    affiliation   : "1"
-  - name          : "Prof. Dr. Anne Deiglmayr"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Leipzig University"
-  - id            : "2"
-    institution   : "Max Planck Institute for Evolutionary Anthropology"
-
-authornote: |
-
-  We received funding from QualiFond of University Leipzig.
-We have no conflicts of interest to disclose.
-This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).
-
-abstract: |
-
-keywords          : "professional vision, expertise, classroom management, mobile eye-tracking"
-wordcount         : "XXX"
-
-bibliography      : ["r-references.bib"]
-
-floatsintext      : no
-figsintext        : no
-figurelist        : no
-tablelist         : yes
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-# bookdown::word_document2 papaja::apa6_pdf
-
+title: "Through the eyes of the teacher - Multimodal exploration of expertise differences
+  in the perception of classroom disruptions in a laboratory study"
+output:
+  html_document:
+    df_print: paged
+  pdf_document: default
 ---
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(include = FALSE)
-library("papaja")
-r_refs(file = "r-references.bib")
-```
-
-```{r analysis-preferences, include=FALSE}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
 
@@
 ```
-
-# Introduction
-
-Managing classroom disruptions is a crucial aspect of effective classroom management [@evertson2006classroom; @kounin2006techniken].
-Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom.
-This ability is referred to as classroom professional vision [@goodwin2015 professional; @sherin2007development].
-The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (“noticing”) and applying knowledge to draw appropriate conclusions in these situations [“knowledge-based reasoning”; @seidel2014modeling].
-Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students’ learning time and minimize classroom interruptions.
-According to @kounin2006techniken, these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring [@gold2017using].
-Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017).
-Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, “[…] whereas only a few studies have focused on the basal process of noticing, i.e.
-the recognition of possible disturbing situations” [@grub2020processp, p.75].
-Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions [@lachner2016makes; @wolff2016teacher].
-
-# Theoretical background
-
-## Professional competence in teaching profession
-
-Competence is a common term in everyday school life.
-In most cases, it refers to the acquisition of competencies by students and how to promote them and make them effective.
-In the same way, the term competence can be applied to teachers.
-Teachers have to be competent in things such as teaching, educating, evaluating or innovating.
-Therefore, competencies form an important and practical contribution in current educational research and teacher education [@klieme2008concept].
-They replace the rigid canon of knowledge that defined professional qualification for generations.
-In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.).
-To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education [cf.
-@klieme2008concept, p.
-4].
-In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.
-
-In science, there is some agreement on the two opposing perspectives of competence versus empowerment.
-The former means a broad, concept, whereas empowerment refers to the different components of competence (cf.
-of competence (cf.
-Blömeke, Gustafsson & Shavelson, 2015, p.5).
-These can be of a cognitive, conative, affective, or motivational nature (ibid.).
-To determining professional qualification, competence is an irreplaceable tool.
-
-Competence is learnable and can thus be improved through targeted practice (cf.
-Weinert 2001; cited in Blömeke et al.
-2015, p.
-5).
-This is one reason, among others, why this concept is so relevant for empirical school and development research.
-Another crucial step in clarifying the concept of competence is to understand that the framework of competence recognizes the importance of everyday life situations (Blömeke et al., 2015).
-Therefore scholars argue, a definition must start from an authentic "analysis of occupational or societal situations and must take into account the tasks and associated associated cognitive, conceptual, affective, and motivational aspects" (Blömeke et al., 2015, p.
-5).
-Through this comprehensive approach, many inconsistencies in the definition of the term can be resolved.
-The definition of competence is now no longer a question of whether it is a number of cognitive skills or a combination of cognition, conation, affect, or motivation.
-It combines "complex intellectual characteristics together with affect-motivation, which underlies observable underlying performances" (Blömeke et al.
-2015, p.
-6).
-This is best defined as a process or even continuum (see Figure 1), which consists of different levels and should be understood as a multidimensional construct with stronger and weaker Domains (ibid.).
-
-The term competence finds its place in a variety of disciplines as an assessment standard of qualifications.
-In this context, the term professional competence has become established in research, which defines competence in a specific professional field.
-Thus, based on the assumption that competence is more than mere knowledge, professional competence offers a way to make teacher success in schools tangible (Kunter et al., 2013).
-
-The term "professional competence" is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation." [cf.
-@epstein2002defining; cited in Kunter et al.
-2013, p.
-807].
-Several studies could prove that this idea can be successfully transferred to the teaching profession [cf.
-Goodmann et al., 2008; @oser2006competence, Achtenhagen & Renold, 2006; Tannenbaum & Rosenfeld, 1994; cited in Kunter et al., 2013, p.
-807].
-Accordingly, a quality standard can be applied to assess the quality of a teacher.
-This quality is elementary in the school context because the teacher factor most influences student learning [@marzano2003classroom].
-Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher.
-Research has shown that this component can even offset the influence of an ineffective school setting [@marzano2003classroom].
-This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.
-
-## Classroom Management
-
-Teachers and students are in the classroom in a place that is always alive, characteristic of its heterogeneity and the interests of different groups.
-These the circumstances of a classroom are also characterized as multidimensional, simultaneous, immediate, unpredictable, public, and shared (Doyle, 2011, p.
-99).
-All of these circumstances place a number of demands on teachers, which primarily involve planning and monitoring activities (ibid.).
-"Order in classrooms is not a consequence of reactions to misbehavior but a condition established and sustained by the way a teacher organizes and guides a complex system of classroom activities" (Doyle, 1989, p.12).
-Thus, "good" teachers create the conditions for effective teaching through pre-planned actions and activities that they are always in control of while teaching.
-This enables them to maximize work time while keeping disruptions of any kind to a minimum to facilitate learning for all participants (Doyle, 1989).
-
-However, lessons, and specifically classroom disruptions, are unpredictable as well as multifaceted and require a high level of expertise and competence on the part of the teacher to handle.
-This trained handling, as described above, can be summarized under the aspect of professional competence.
-It is expressed, among other things, in knowledge about classroom management [@grub2020process] and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
-
-Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction [@wolff2015keeping].
-@marzano2003classroom research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching.
-In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching [@wolff2015keeping].
-Therefore, it is often referred to as the central variable of successful teaching (Helmke & Helmke, 2015).
-Good classroom management is thus the prerequisite for learning to take place [@wolff2015keeping].
-While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.
-
-An initial explanatory approach to classroom management was provided by Doyle (1990, p.355) with his definition of teaching, which he described as a "cognitive activity based on knowledge of the probable course of events in the classroom and the ways in which actions affect situations." From this, it is clear that in order to teach successfully, a teacher needs knowledge of how to process as well as represent the full range of classroom events.
-In addition, it is necessary to be able to respond or interact proactively and effectively to potential events at best.
-
-Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge [cf.
-@wolff2015keeping, p.
-71].
-These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.).
-If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction.
-This is crucial to maximize students' active learning time (Helmke & Helmke, 2015).
-It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research.
-In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise [@wolff2015keeping].
-
-### Interdependence of classroom management
-
-In research, various models exist for approaching the concept of classroom management.
-However, they are very similar in their core statements.
-Therefore, it is merely a matter of preference which concept is consulted to explain connections and terms.
-In the following, the network of effects of classroom management according to @helmke2014unterrichtsdiagnostik is used as a reference model in order to be able to understand the embedding of the concept accordingly.
-
-As was made clear in the definition, classroom management is a complex construct that attempts to accommodate the various modes and challenging characteristics of a classroom.
-@helmke2014unterrichtsdiagnostik therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time.
-This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (*d* = 0.39; Hattie, 2013, p.219).
-Due to this diversity of aspects to be investigated, classroom management is a fundamental research topic.
-
-The concepts, strategies and techniques used to implement successful classroom management depend first and foremost on various teacher characteristics and are "interrelated with the quality of teaching and personal relationships" (Helmke & Helmke, 2015, p.5).
-It should not be forgotten that this space never functions in isolation and independently of other influences.
-It is embedded in diverse contexts, especially in the school and class context (Helmke & Helmke, 2015).
-But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led [@helmke2014unterrichtsdiagnostik].
-
-Classroom management itself is made up of various components which, according to @helmke2014unterrichtsdiagnostik, can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior.
-Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke & Helmke, 2015).
-
-The importance of rules in the classroom has been known and researched for some time.
-Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules [cf.
-Emmer, Evertson & Anderson, 1980; @emmer1982improving; cited in Doyle, 1989, p.
-15].
-Although he also stresses that establishing a system of rules is a difficult task.
-Classroom rules are situation-dependent, as certain agreements only apply to certain phases of the lesson (for example, speaking quietly during group work; Doyle, 1989).
-Furthermore, order is always established jointly, in cooperation with the learners (Doyle, 1989).
-
-As a result, students significantly influence these rules by their willingness to follow them.
-Procedures are another tool to maintain the flow of the lesson, as recurring routines provide learners with security and clarity (Helmke & Helmke, 2015).
-This inevitably reduces the teacher's workload, eliminates additional explanations are no longer necessary, and it is clear to the learners at all times what needs to be done.
-needs to be done.
-In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time [@helmke2014unterrichtsdiagnostik].
-For the reasons just reasons just explained, it is clear why Hattie (2013, p.
-122) gives this component of classroom classroom management an effect size of *d* = 0.76.
-
-No other aspect of classroom management is as effective for classroom interruptions as the teacher's omnipresence (Hattie, 2013, p.
-122); the effect size is *d* = 1.42.
-(Helmke & Helmke, 2015, p.
-6).
-The behavioral pattern of presence is not a new concept.
-It was already recorded by kounin1970discipline under the term *withitness*.
-Later research confirmed and validated his assumptions and definition of the term [cf.
-@helmke2014unterrichtsdiagnostik, p.10].
-In order to be present, the teacher must be able to control the classroom adequately and superficially effectively at all times.
-This means she must be able to recognize relevant cues or situations that require possible action [@wolff2015keeping].
-Presence can consequently be illustrated very vividly by means of the image of "eyes in the back of the head" [@kounin2006techniken].
-In addition to presence, @kounin2006techniken uses the term overlap.
-It is a kind of multitasking ability to be able to cope with parallel processes and situations in the classroom.
-The two dimensions of overlap and presence can also be summarized together under the term monitoring [@gold2017using].
-When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners [@grub2020process].
-Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness of relevant events in the classroom (ibid.).
-From this point of view, it becomes clear why awareness is a core component of teacher competence.
-
-As a third component influencing the quality of classroom management, cites @helmke2014unterrichtsdiagnostik time use and management.
-This seems trivial at first, considering that classroom management serves the goal of maximizing learning time anyway.
-However, Helmke & Helmke (2015, p.
-6) emphasize how elementary it is to identify and minimize possible "time thieves".
-This includes factors such as unpunctuality or slow transitions, as well as the underemployment of learners (ibid.).
-If these take up too much space in the classroom, less time is available for teaching important lesson content.
-This can be prevented by teachers minimizing such "time thieves" in advance through well-planned classroom management.
-
-In order to enforce desired student behavior or to reduce contradictory behavior, teachers can use various discipline-related interventions and also make use of negative sanctions and positive reinforcement (Helmke & Helmke, 2015).
-The authors emphasize that a healthy balance must be found when using these strategies.
-Over the years, this constructive approach has fallen into disrepute due to its behaviorist character.
-However, elements such as reinforcement, extinction or punishment are not negligible laws of learning psychology whose effectiveness has been proven by Hattie (2013), among others.
-These behavioral psychological measures have an effect size of *d* = 0.76 (cf.
-Hattie, 2013, p.215) and are therefore an effective means of reducing disruptions (Helmke & Helmke, 2015).
-
-Researchers in pedagogy also point out, however, that it is not only pure knowledge about classroom management that determines its effectiveness and influences it (Helmke & Helmke, 2015).
-The teacher personality, which includes characteristics such as subjective tolerance margins, i.e.
-at what point does one perceive a certain behavior as disruptive, also plays a role.
-This includes further aspects such as emotion control, empathy or the credibility of a teaching person that arises through appearance.
-These characteristics, which occur in many ways, have a direct impact on the quality of teaching and classroom management, as they influence the planning behavior, perception and reaction of teachers.
-
-## Professional vision
-
-Competence assessment plays a central role in the teaching profession and its training.
-It follows the approach of concentrating on action-relevant as well as lesson-related content in order to train corresponding competences for teaching practice (KMK, 2004).
-In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes [@barth2017professionelle].
-Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic [@jahn2014professionelle].
-The concept of professional vision can originally be traced back to the anthropologist Charles Goodwin and became known under the term Professional Vision (Sherin, 2001).
-It provided the answer to Goodwin's question regarding the development of a professional vision, in the context of the profession, compared to the vision of everyday situations.
-Goodwin uses the comparison of an archaeologist and a layperson to figuratively describe the differences.
-In doing so, he investigated which ability it is that makes the archaeologist see and interpret a landscape differently than the layperson (cf.
-Sherin, 2001, p.
-75).
-What looks to the former merely like sand, rocks and stones, is to the trained eye of the archaeologist a base of a column or architectural fragments.
-Goodwin (1994, p.606) defines professional vision as "socially organized ways of seeing and understanding events that are answerable to the distinctive interests of a particular social group" (cited in Sherin, 2001, p.
-75).
-It is assumed that one can see certain phenomena or occurring events in a certain way due to one's professional affiliation (Sherin, 2001).
-Particularities are more easily recognized because the gaze becomes more trained over time and thus profession-relevant features appear more distinctive.
-In the previous example of the archaeologist, this would mean that he noticed variations in color, texture and sand and saw a cluster of stones as a possible element of a larger structure (cf.
-Sherin, 2001, p.75).
-This distinguishes experts significantly in their visions from non-experts in the field, as they had learned to filter their environment for crucial features.
-
-### Teachers' professional vision
-
-Based on the assumption that the professional vision can develop over time, Sherin (2001) postulates that teachers can also acquire a professional vision.
-As teachers develop from novices to experts in their field, they accumulate expertise in a variety of areas (cf.
-Sherin, 2001, p.
-76).
-This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom [@berliner1994expertise, @leinhardt1986cognitive].
-This type of action can be described as a skill that helps teachers make decisions about what is relevant and what is not within the complex classroom setting (van Es & Sherin, 2002).
-Such decisions are based on professional knowledge that guarantees effective teaching and learning in actual classroom situations [@jahn2014professionelle].
-Professional awareness is therefore referred to as an indicator of how knowledge is represented in teachers (Stürmer et al., 2017).
-It can also be seen as a bridge or link between knowledge and action, or professional competence and behavior [@grub2020process0].
-It is important to understand that professional vision is acquired and not inherent.
-Rather, it is subject to a process of acquisition that is constantly progressing as teachers are exposed to events and learn to interpret them [@wolff2016teacher].
-Fundamentally, then, prospective teachers must select what to focus their attention on in the classroom and how to understand these events (Stürmer et al., 2017).
-Finally, teaching and learning take place in a complex environment.
-Simultaneous events and situations cannot be given the same attention.
-"Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects" [@barth2017professionelle, p.19].
-Furthermore, teachers benefit from from a trained perception of problems, as this is a significant factor in being able to preventively counteract preventive measures (Wettstein, 2013).
-
-Basically, the complex process of professional vision is divided into three sub-processes [@grub2020process].
-First of all, the identification, the recognition, of an event takes place.
-Then connections are made, which are finally evaluated by the teacher using his or her professional knowledge.
-In research, these processes are often combined and one speaks of noticing to describe recognition [@grub2020process].
-Knowledge-based reasoning includes the last two processes of applying knowledge to make appropriate decisions (ibid.).
-During this process, it becomes clear that the recognition of relevant situations, such as disruptions, precedes all others.
-This process is therefore considered necessary, without which professional vision cannot take place [@grub2020process].
-As described in the chapter on competence, perceptions is also of particular importance in the competence model according to Blömeke et al.
-(2015).
-This is because the process of perception forms an essential basis for situation-specific skills of teachers [@grub2020process].
-Inferentially, recognition is inevitable for the perception of classroom events and therefore highly relevant for effective classroom management (ibid.).
-
-Even though the recognition of relevant situations in the classroom is the starting point for all further subsequent actions, the processes of knowledge-based reasoning within professional vision are not to be neglected.
-It is also said that this process is an indicator of the quality of how knowledge is applied to a given situation [@grub2020process], as teachers need to make knowledge-based inferences.
-Qualitative research on knowledge-based reasoning concluded that it can be subdivided into three further sub-processes.
-@sherin2007development [cited in @barth2017professionelle, p.
-20] made a first subdivision,  which consists of the processes of describing, evaluating and interpreting.
-When a teacher describes what she notices, she concentrates on observable characteristics, i.e.
-important aspects of teaching (ibid.).
-When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event [cf.
-@barth2017professionelle, p.
-19].
-Seidel et al.
-(2010), on the other hand, focus on German-speaking countries in their research on professional vision and modified Sherin's original concept.
-They also divide knowledge-based-reasoning into three levels, but these differ: describing, explaining and predicting [@barth2017professionelle].
-More precisely, these processes encompass the ability to differentially describe instructional components that have an impact on learning; to make theoretically sound explanations about instructional situations; and to predict the effects of these events in relation to the teaching-learning process (cf.
-Seidel et al., 2010, p.
-297).
-This scientific work examines only the processes of noticing, which is why these two approaches have been presented for the sake of completeness.
-However, it is not useful to specify which classification of knowledge-based reasoning is referred to in arguments.
-is referred to in argumentation.
-
-Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect [@sherin2007development7; cited in @barth2017professionelle7, p.
-19].
-What is considered and perceived as relevant in a teacher's selective vision (noticing) functions as the basis of the subsequent processes of describing, evaluating, and interpreting (knowledge-based-reasoning).
-Conversely, by engaging with these processes, the teacher's perception is sensitized.
-This leads to the fact that in the future certain characteristics of this situation can be recognized rather.
-
-## Measuring professional vision: eye-tracking technology in research
-
-Professional vision of teachers is a complex undertaking, consisting of various cognitive and visual processes.
-In the previous chapter, the importance of perception and its associated visuality was emphasized, which places the eye at the center of investigations.
-In research, process-based methods are used to make these perceptual processes visible.
-In this context, eye-tracking (ET), a modern method of recording gaze, has proven to be an effective tool in research.
-It allows us to literally see through the eyes of recipients and provides insight into another perspective.
-Intrinsic human cognitive processes are often compared to a black box in science, as these activities are not directly measurable (Rakoczi, 2012).
-Until now, cognitive processes could only be studied by verbalizing the respective subjects.
-However, this method is highly susceptible to interference due to its incomplete accessibility (Dessus, 2016).
-The increasingly popular research method of eye-tracking technology therefore represents an innovative means of externalizing, i.e., making visible, internalized processes by means of eye movements [@gegenfurtner2018mobiles] Stimuli in the environment are always perceived by our eyes as the first receiver.
-They take in the information and pass it on to our brain so that it can finally be processed there.
-By measuring this complex process, eye movements can be recorded and subsequently analyzed (Rakoczi, 2012).
-Information is obtained about the visual behavior, attentional focus, selection decisions, and even learning processes of the investigator (ibid).
-In addition to these qualitative results, which provide information about underlying cognitive processes, quantitative data can also be collected through eye-tracking (Cullipher, 2018).
-These provide information, for example, about how long and in what order stimuli are looked at, or whether certain parts are looked at more often than others (ibid.).
-This enables research to make data objectively assessable.
-
-Eye-tracking technology can be roughly divided into two types of devices: Stationary and mobile systems [@blake2013eye].
-In research so far, mainly eye-tracking devices have been used, which phenotypically resemble a computer (ibid.).
-They are also referred to as remote devices and, once calibrated, measure eye movements in a non-contact manner using infrared light [@egenfurtner2018mobiles].
-However, this technique reaches its limits when it comes to collecting data in everyday situations.
-For this purpose, the more flexible variant, mobile eye tracking (MET) or head-mounted or wearable eye trackers, can be used.
-Typically, the technology is found as a head-mounted device on helmets or integrated into an eyeglass frame [@blake2013eye].
-The difference with stationary tracking is that in addition to an eye camera and infrared light source, additional cameras are built in to capture head movements (ibid.).
-These are intended to help document the subject's field of view.
-Therefore, such systems are particularly suitable for applied sciences, as is the case in empirical school and development research [@gegenfurtner2018mobiles].
-
-Eye-tracking research is based on several fundamental assumptions.
-The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date [cf.
-@blake2013eye, p.
-380].
-In this regard, hoffman1995role obtained the finding that when the eyes are focused on an object, this is associated with an attentional focus of the person.
-Based on these findings, ET technology is based on the following two assumptions: The immediacy assumption and the eye-mind assumption (cf.
-Rakoczi, 2012, p.87).
-The former defines that cognitive evaluation processes begin immediately upon fixation on an object (Cullipher, 2018).
-If a new stimulus attracts attention and is fixated, the observer starts processing this new information (ibid.).
-The eye-mind hypothesis assumes that whatever is fixated by the eye, is subsequently processed by the mind (ibid.).
-It thereby expansively defines, that objects are visually focused only until they are cognitively evaluated or until there is have been cognitively evaluated or there is still an interest (cf.
-Rakoczi, 2012, p.87).
-However, a situational context must exist for the assumptions just explained to be are valid (ibid.).
-Through these functions, it becomes clear that the intrinsic processes of recognition in professional vision can be measured by eye-tracking technology.
-
-Despite the externalization of internalized processes and the resulting multitude of data potentially to be collected, ET technology cannot provide answers about the exact thoughts during stimulus processing.
-ET can identify where and when people are looking, but it does not answer why.
-For this, it is helpful to triangulate the data and apply alternative elicitation (Cullipher, 2018).
-One proven method is to conduct reflective interviews, which can be conducted in the format of a think aloud protocol (Konrad, 2020).
-This thinking aloud opens up the possibility of gaining insights into subjects' thinking, feeling, and intentions (edb.).
-An elaborated form of the Think Aloud Protocol is a Stimulated-Recall Interview (SRI).
-This is a qualitative scientific method to obtain data on preactional thought processes (cf.
-Messmer, 2015, p.4).
-The pre-recorded lesson sequences are played back and subjects have the opportunity to express themselves about their "thoughts, beliefs, norms, and decisions" (Messmer, 2015, p.4) during the interview process.
-Thus, the visual data of the ET can be matched with cognitive processes and processes of knowledge-based-reasoning can be better understood.
-Individual-dependent thinking is now no longer pure speculation and can be made objectively observable in a way (Messmer, 2015).
-Subjects also have the opportunity to explain their actions and become aware of the basis for their decisions (ibid.).
-
-### Parameters and indicators of teachers' professional vision
-
-In university education, there is an increasing focus on developing the professional vision of future teachers (Stürmer et al., 2017).
-In order to determine the professional vision of teachers by means of mobile eye-tracking (MET), different indicators are worth considering.
-This scientific work focuses primarily on processes of noticing, i.e., the identification of relevant teaching situations as well as perception time.
-Therefore, in the following we will focus more on the parameters and indicators necessary for these processes.
-
-In MET, collected data sets are usually output according to different parameters: Fixations and Saccades [@gegenfurtner2018mobiles].
-The latter describes gaze jumps, i.e., movements of both eyes, which are useful to capture new fixations (Eye-Tracking Kompetenzzentrum Schweiz, 2021).
-Significant for this scientific work and the analysis of professional vision are the fixations as well as subjects' areas of interests.
-Fixations describe the period of time in which no movements are emitted by the eye (Holmquist et al.
-2011) and are based on the eye-mind hypothesis described in the previous chapter.
-A fixation of an object can be characterized according to its duration, frequency, and distribution.
-In the illustration, the radius of a circle defines the duration of a fixation [@gegenfurtner2018mobiles].
-These data can also be used to describe perception times, such as the time until the first fixation on a particular object.
-In order to make this time period objectively measurable make it objectively measurable, a concept developed by Tobii Pro Lab Analyzer Software is used.
-In this software these organized recorded data are called Time of Interests (short TOIs), which describe time intervals of corresponding events or behaviors (Tobii Pro, 2021).
-Specifically, they are defined by the beginning and end of the corresponding event.
-
-By means of eye movement measurement, attention allocations to areas of interest or objects are made accessible in addition to pure fixations [@gegenfurtner2018mobiles].
-In research, these regions in the field of view of subjects are referred to as areas of interest (AOI) (edb.).
-They are significant in that, for the measurement of perceptual velocities of a relevant instructional event, not only TOIs but also the locations of fixations are crucial.
-Thus, it can be determined how subjects distribute their attentional resources and whether they recognize and perceive relevant events.
-
-### Expertise differences in professional vision
-
-Since it is assumed that professional vision is a preferably knowledge-based process, differences between experienced and inexperienced teachers have already been identified.
-These differences were in favor of experts, since a connection between teaching experience and the associated increase in knowledge acquisition is assumed [@grub2020process].
-Student teachers do not have well-structured experiential knowledge due to their almost non-existent practice in everyday school life [@wolff2016teacher].
-This causes them selection difficulties in perception and is called pedagogical knowledge gap [cf.
-@wolff2016teacher, 2016, p.260].
-Through newly gained experiences, the professional vision of a teacher is continuously restructured and updated, and mental representation is constantly realigned accordingly (ibid.).
-This has been proven in research as a positive correlation of input to teaching and learning theories in studies and professional classroom perception has been found (Stürmer et al., 2012).
-Therefore, it can be assumed that there is a relationship between teacher expertise, their visual processing, and mindfulness for classroom management [@wolff2016teacher].
-Research has also shown that declarative knowledge acquisition, i.e., acquisition of factual knowledge, supports perceptual processes [Seidel et al., 2012; cited in @treisch2018entwicklung, p.26] Accordingly, this increased knowledge acquisition would explain a positive impact on professional teaching perception.
-Among the most important prerequisites for this acquisition, baumert2006key include prior knowledge and interest.
-The former is elementary for new knowledge acquisition about effective teaching and learning, as it supports processing, integration, and consolidation of it (Stürmer, 2011).
-Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions [cf.
-@sabers1991differences; cited in @treisch2018entwicklung].
-This is explained by increased filtering mechanisms that support perceptual processes, i.e., recognition.
-Specifically, it has been shown that experienced teachers have more fixations on relevant areas because they have already learned theories on how to detect potential clutter in the classroom [@grub2020process].
-Furthermore, experts have an advantage when it comes to coding information.
-Novices, on average, have a longer viewing times, so-called fixation durations, which is due to their still weakly developed expert knowledge (ibid.).
-
-### Mobile eye tracking in teaching-learning situations
-
-As explained in detail earlier, teachers face a number of challenges during teaching.
-The teacher as organizer has to permanently scan the classroom for potential interruptions or possible events occurring such as classroom disruptions.
-In the worst case, they force a standstill in the flow of instruction, which is naturally to be avoided.
-Lohmann (2015, p.13) describes classroom disruptions as "events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place." However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive [cf.
-@eckstein2016unterrichtliche; cited in, Eckstein, 2018, p.11].
-Thus, instructional disruptions are strongly dependent on perception and involve elements of production as well as reception (ibid.).
-These discipline conflicts can be divided into four categories of disruptive student behavior: Verbal disruptive behavior (chattering, heckling), lack of eagerness to learn (mental absence in the form of drawing or playing on the cell phone), physical disruptions (snapping, drumming, pen clicking), and aggressive behavior (temper tantrums, attacking people; Lohmann, 2015).
-
-In order to be able to recognize inappropriate behavior in a timely manner, the teacher must have a pronounced omnipresence, as well as pedagogical-psychological knowledge about teaching and learning processes (Cortina et al., 2018).
-These skills and competencies are reflected in how teaching situations relevant to learning are perceived and interpreted by teachers (ibid.).
-In this context, a multitude of visual attention processes occur during classroom activities.
-This simply means the attention or the conscious non-attention to visual stimuli (Rüth et al., 2020).
-This situational awareness of a teacher and the accompanying control of his or her visual attention forms the foundation of situation-specific skills (cf.
-Rüth et al.
-2020).
-These data and insights potentially to be collected form an interesting field of research and useful tool for problem-based teaching education (Cortina et al., 2018).
-
-In the last decade, visual input through recorded teaching situations has been preferred (ibid.).
-Subjects are thus shown an outside perspective from different points of view.
-This can happen either as self or external video and allows micro-analysis or interaction sequences through the characteristic of repeated playing of a video (ibid.).
-This characteristic makes it possible to analyze corresponding scenes more intensively and in more detail.
-This results in a potential for reflection on teaching situations in teacher education that should not be underestimated (cf.
-Rüth et al., 2020).
-The problem with these videotaped sequences, however, is the lack of access to the first-person perspective (ibid.).
-As a result, students usually evaluate and comment on their own videos more negatively than those of others afterwards (Cortina et al., 2018).
-They find it difficult to analyze the sequences objectively and to leave out unimportant details that concern their person.
-However, this is not purposeful and conducive to the intended learning process of the participating teachers.
-This is due to the fact that self-drawn cognition is activated in self-videos and that when negative events occur, subjects tend to defend their actions (ibid.).
-@kleinknecht2013teachers analyzed this process in more detail and found that this is particularly problematic for the reflective learning process, as it has a counterproductive effect on analyzing possible alternative actions.
-They also found that in third-party videos, reflection on potential alternative actions was twice as frequent as in self-recorded videos (ibid.)!
-In addition, recorded video sequences differ significantly from real classroom settings in which the teacher can independently determine her field of view.
-The observers cannot decide for themselves what to pay attention to and for how long to pay attention to a situation or event (Sherin, 2001).
-Based on this finding, it was significant for researchers to use an alternative elicitation technique to factor out the negative effects of self and other videos.
-
-A successful method to reduce this hindering factor of self-drawn cognition and still use self videos for teacher education is to use recordings that show the teacher's perspective and furthermore make it known where the teacher was looking (cf.
-Cortina et al., 2018).
-In MET's video material, teachers can never see their teaching through their own eyes.
-This makes it possible to focus more specifically on essential aspects, such as classroom disruptions and interactions with learners.
-Although it has not yet been clearly demonstrated that significantly less self-referential cognition was elicited, self-videos counteract over-focusing on the acting person (cf.
-Cortina et al., 2018).
-Therefore, MET represents a target-rich method for capturing teachers' attentional processes in the classroom.
-Previous studies with large data sets on teachers' visual expertise have predominantly used stationary ET [@wolff2016teacher].
-In MET studies, the samples turn out to be much smaller; here, the largest study to be mentioned is with 12 experienced and 12 inexperienced teachers by Cortina et al.
-(2015).
-
-### Perceptions of classroom disruptions and their parameters
-
-The attentional processes of teachers in the classroom that can be captured by MET are complex, as already explained, and are related to various parameters.
-Individual personality characteristics play a central role when it comes to the perception of relevant classroom events.
-In general, it should be noted that novices have greater problems in classroom management as well as in dealing with difficult student behavior [@barth2017professionelle].
-Often, this is due to their late or even lack of awareness of classroom disruptions.
-However, their lack of expertise is not the sole reason for this phenomenon.
-Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher [@baumert2006key] Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors.
-Individual person characteristics as well as contextual factors not only have an effect on teaching perception, but likewise on the sense of disturbance of a situation (Eckstein, 2019).
-These specific characteristics include aspects such as self-image, motivation, level of aspiration, attitudes, coping goals, and value orientations (Bakker & Demerouti, 2006; cited in Wickeren, 2019, p.
-33).
-Contextual characteristics include didactic staging or general level of disruption.
-Undesirable behavior is perceived more strongly by teachers when the class usually displays disciplined and orderly behavior (Eckstein, 2018).
-This reference group effect is also known as the Big-Fish-Little-Pond effect.
-Thus, it can be said that teachers' perceptions of situations and people are significantly shaped by their expectations and biases is shaped (cf.
-Eckstein, 2018).
-How strongly a disturbance is perceived and felt can also depend on psychological characteristics such as self-efficacy beliefs (ibid.
-(ibid.).
-With decreasing self-efficacy, an increasing sense of disturbance was found (ibid.).
-
-The teacher-student relationship aspect, which includes recognizing student needs, must also be considered.
-In order to be able to adequately counteract classroom disruptions and thus automatically reduce the sense of disruption and the experience of stress, it is important to address the concerns of the learners with empathy (Wickeren, 2019).
-Regarding gender as a factor, it should be noted that previous research has found higher levels of disruptiveness in discipline problems among female teachers (Kovess-Masféty, Rios-Seidel & Sevilla-Dedieu, 2007; cited in Wickeren, 2019, p.
-33).
-In summary can thus be summarized that the extent and perception of disturbances are based on individual cognitive evaluation processes, the situational context, attentional focus, didactic staging, and, indeed, professional experience (cf.
-Wickeren, 2019).
-
-# Research Questions and hypothesis
-
-This study examined how the degree of teaching experience of novice and expert teachers influences (1) the number of fixations on relevant areas, (2) the fixation duration on relevant areas and (3) the time to first fixation on relevant events (e.g., the student performing the disruption), using mobile eye-tracking data in a controlled, micro-teaching setting.
-Furthermore, the study examined the individual evaluation of classroom disruptions among experts and novices by assessing (4) how disruptive an event was and (5) how confident the subjects felt dealing with the events.
-In addition, subjects' (6) strategic knowledge of classroom management was assessed.
-
-Based on the existing literature, we expected expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation duration and (H3) perceiving classroom disruptions faster [cf.
-@van2014first], (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions [@barth2017professionelle], and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
-
-# Materials and Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
-
-This study had a quasi-experimental study design, as there was no random assignment of the subjects to experimental conditions.
-Due to the use of mobile eye-tracking technology, the study had a high external validity [@gegenfurtner2018mobiles].
-Internal validity could be ensured to the extent that the disruptive events that occurred were exactly the same for all subjects, as the actors received precise behavioral instructions.
-These disruptions followed a script and coding scheme in which the actions of the class were precisely described.
-The order of the disruptions as well as the performing actors were fully balanced with Latin Square to exclude row effects.
-
-The scripted behavioral instructions during the micro-teaching unit characterized the study with a high degree of standardization, especially when compared to events taking place in a real classroom.
-The study was based on an experimental manual, script and coding, which explicitly described the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable.
 
@@
   summarise(N=n(),
-            "Gender female in percent" = round(sum(Gender/Sum_participants) * 100, 
+            "Women in percent" = round(sum(Gender/Sum_participants) * 100, 
                                                digits = 2),
@@
             "Min Age in years" = min(Age),
-            "Max Age in years" = max(Age)
+            "Max Age in years" = max(Age),
+                       "M Exp." = round(mean(`Teaching Experience`), 2),
+            "SD Exp." = round(sd(`Teaching Experience`), 2),
+            "Min Exp." = min(`Teaching Experience`),
+            "Max Exp." = max(`Teaching Experience`)
             )
 
-# format and insert table in manuscript
-demo.table %>%
-papaja::apa_table(
-  caption = "Demographic Information",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
+knitr::kable(demo.table,
+             caption = "Demographic information & teaching experience")
+
+# # format and insert table in manuscript
+# demo.table %>%
+# papaja::apa_table(
+#   caption = "Demographic Information",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+#   )
 
@@
 
-# format and insert table in manuscript
-exp.table %>%
-papaja::apa_table(
-  caption = "Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
+# # format and insert table in manuscript
+# exp.table %>%
+# papaja::apa_table(
+#   caption = "Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+#   )
 
@@
 
-The sample consisted of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.
-
-The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
-According to @palmer2005identifying, we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
-Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
-
-The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`).
-`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers.
-`r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
-
-The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years.
-On average, the student teachers were in their `r exp.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`).
-Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies.
-`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype") %>% unique()`% to become special education teachers.
-`r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
-
-The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at the University Leipzig.
-All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
-The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
-All participants were informed in detail about the aim and intention of the study prior to testing.
-Participation in the study was voluntary and only took place after written consent has been given.
-
-## Design
-
-The underlying research was conducted as a laboratory study in a cross-sectional study design as part of the dissertation project *ProVisioNET*.
-This project investigates whether and how a teacher's classroom experiences have an impact on the perception of and response to classroom disruptions.
-
-The study was based on a quasi-experimental study design, as there was no random assignment of subjects to experimental conditions.
-Due to the use of MET technology, the study had a high external validity [@gegenfurtner2018mobiles] To ensure internal validity the occurring instructional events were exactly the same for all subjects, as the learners received precise behavioral instructions.
-These disruptions followed a script and coding guide in which the actions of the class were precisely described.
-The order of the disruptions as well as the performing actors were prompted and fully balanced with Latin Square.
-The scripted behavioral instructions during the classroom sequence distinguish this study with a high degree of standardization, especially when compared to events that take place in a real classroom.
-The study was based on an experimental manual, script, and coding guide which explicitly describes the execution, evaluation and interpretation of the data and thus and interpretation of the data, thus making them objectively ascertainable and measurable.
-
-## Materials and Measures
-
-### Eye-Tracking Data
-
-#### Apparatus
-
-To record eye-tracking data, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker during the micro-teaching-unit.
-The system consisted of a wearable head unit and a recording unit.
-As shown in Figure \@ref(fig:tobiiglasses2), the head unit was a measuring device with different sensors.
-A high-definition scene camera captured a full HD video of the teacher’s field of vision.
-An integrated microphone recorded the surrounding sounds.
-Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \@ref(fig:teachersgaze).
-The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera had a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).
-
-```{r tobiiglasses2, include = T, fig.cap = "Tobii Pro Glasses 2; Source: https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/tobiiglasses2.png", dpi = 108)
-
+```{r}
+plot(cars)
 ```
 
-```{r teachersgaze, include = T, fig.cap = "Teacher's Gaze Point", fig.align = "center", echo = FALSE}
+Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
 
-knitr::include_graphics("./pictures/teachersgaze.pdf", dpi = 108)
+When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
 
-```
-
-#### Teachers' visual focus of attention
-
-Teachers' areas of interest (AOI) were identified as targets where teachers looked during the micro-teaching-unit using Tobii Pro Lab Analyzer Software Version 1.171.
-In the present study, general AOIs where defined as the student group, the students' nametags, the teacher material, the students' material, the board and non-instructional material in the classroom (wall, window, floor).
-These AOIs were coded during the manual fixation mapping process during the entire micro-teaching-unit.
-Additionally, the disruptive person was coded as an event-based AOI only over the duration of the disruption.
-
---> Only eye-tracking video recordings with 70 % and above gaze sample percentages were selected for the study to ensure that one or both eyes were detected during 70 % of the recording’s duration (Chaudhuri et al, 2022).
-Screenshots of the video recordings were used to define the AOI in the eye-tracking videos.
-The coder started manual gaze mapping when the teacher entered the classroom and ended coding when the micro-teaching-unit ended.
-The start and end of the micro-teaching-unit was defined by a visual and acoustical signal.
-The two coders who were assigned to code the eye-tracking videos student employees who studied to be teachers and received a detailed introduction to the software.
-The intercoder reliability was checked by double coding 20 % of the videos from the whole dataset.
-Double coding agreement ranged from XXX % to XXX %.
-
-We coded each fixation using the Attention Filter in Pro Lab with the velocity threshold parameter set to 100 degrees/second instead of the default 30 degrees/second.
-This filter is suitable for dynamic situations to study attention without separating any eye movements.
-By choosing the Attention Filter typical fixations, most VOR (Vestibulo-ocular reflex), smooth pursuit eye movements, and slow saccades are classified as fixations.
-
-The relevant fixation metrics such as number of fixations, the total duration of fixations and time to first fixation on the relevant event (disruptive person) were obtained by exporting an interval-based TSV file from the Tobii Pro Lab Analyzer Software.
-The total fixation duration and the time to first fixation metrics were measured in milliseconds (ms) and the number of fixation in counts as an integer.
-To calculate the average fixation of durations for all AOIs, we divided the total duration of fixations by the number of  fixations for each AOI.
-
-### Video data
-
-#### Apparatus
-
-The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \@ref(fig:setup).
-The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
-Movements, facial expressions and gestures of the subjects were recorded with four Go Pro Hero 7 black cameras from different angles (see set up plan \@ref(fig:setup).
-The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
-
-#### Videography: Coding scheme for expertise indicators
-
-Part of the test procedure was that the subject taught a 15min micro-teaching-unit and was disrupted by the students in the class.
-The participant's behavior and reaction to the disruption were recorded using video cameras and then evaluated with two self developed coding schemes to assess the teacher's reaction on the one hand and the time on task during the unit.
-Both aspects are important indicators of teaching quality and are therefore used as another measure to make differences in expertise visible and measurable.
-
-Video analysis was chosen as the research method for evaluating the teacher's reaction to classroom disruptions because it offers numerous advantages.
-In contrast to transcripts or audio-only recordings, a video also shows nonverbal forms of communication, which is emphasized here, as well as the entire complex lesson excerpt in which many things happen simultaneously (cf.
-Krammer & Reusser, 2012, p.
-47f).
-Video data can also be viewed and analyzed over and over again from different perspectives (Petko et al., 2003, p.
-265).
-The possible problem of selectivity (cf.
-Petko et al., 2003, p.
-271), i.e., the fact that only a section of the events can be shown due to the position and perspective of the camera, was countered by recording the lessons from a total of four cameras.
-In this way, a case of doubt can be analyzed from several angles.
-Another challenge can be the so-called 'camera effect', i.e.
-that the filmed persons feel disturbed and act differently than usual and less naturally.
-However, Petko et al.
-(2003) conclude, despite filming with a camera person at the time, that there is little reason to believe that teachers can easily change their teaching style from one lesson to the next (p.
-270) and that it should not be assumed that the mere presence of a camera has significantly improved or worsened teaching' (p.
-270).
-In the 'ProVisioNET' survey, four very small cameras were placed in the room and their presence was barely noticeable.
-Accordingly, it is assumed that no major nuisance emanates from them.
-
-Schnettler and Knoblauch (2009, p.
-227) distinguish 'natural' and edited video data, depending on whether the situation was created specifically for the recording or whether the situation was influenced as little as possible or not at all.
-In the survey for this paper, although the subjects were to act exactly as they would have done without a camera, the classroom disruptions were scripted events that were performed by the actors.
-
-##### Teachers' Reaction to disruptions
-
-The evaluation of the teacher's reaction to the disruptions was conducted as a systematic observation using a category system with fixed categories and instructions.
-This corresponds to a highly inferential procedure, which is combined with an event sampling procedure (cf.
-Lotz et al., 2013, p.
-359).
-
-A theory-based coding scheme was developed as an observation tool for classroom observation.
-The coding of the reactions was done in seven levels.
-Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping [cf.
-@kounin2006techniken; @gold2015development] by not interrupting the flow of instruction.
-Code 2 or Code 3 was assigned for a brief verbal expression with or without a preceding nonverbal response.
-A brief, timely, and purposeful rebuke of the disruptive student is considered by Kounin (2009, p.
-99), among others, to be an important component of the strategy of presence and thus demonstrates good classroom management.
-If the teacher reacts non-verbally and at the same time with a longer verbal statement, code 4 was assigned, because the flow of the lesson was already noticeably delayed.
-There were two possibilities, if there was no reaction: If the teacher deliberately ignored the disruption, code 5 was assigned.
-If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized [cf.
-@gold2015development].If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned.
-According to Gippert et al.
-(2019), there is a relational error in such cases, as the intensity of the student response should be relative to the disruptive behavior (p.
-2).
-
-In developing the coding system, questions initially aroused about how descriptions of responses should be made and in what order (especially codes 3-4).
-Initially, it was planned to assign code 3 for a nonverbal and simultaneously long verbal response and code 4 for a purely verbal response.
-However, during the initial trial coding of the videos, it became apparent that it was difficult to reliably distinguish nonverbal reactions to a classroom disruption from normal facial expressions and gestures of the teacher when talking.
-Moreover, during a prolonged verbal utterance, nonverbal signs could virtually always be detected.
-Furthermore, a category for short, purely verbal reactions was missing.
-
-```{r reaction_codingsystem, include=TRUE, echo=FALSE, results='asis'}
-# audit_table <- structure(
-#   list(
-#     Description = c(
-#       "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
-#       "The teacher reacts nonverbally and simultaneously with a short verbal reaction.
-The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixing gaze).
-The verbal response includes name calling, brief verbal prompts / admonitions.",
-#       "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
-#       "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption.
-The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixating gaze).",
-#       "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption.
-This information can only be obtained through the Stimulated Recall Interview.",
-#       "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption.
-This information can only be obtained through the Stimulated Recall Interview.",
-#       "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
-#                   ),
-#     `1` = c("Never", "1–2", "Never"),
-#     `2` = c("Monthly or less", "3-4", "Less than monthly"),
-#     `3` = c("2-4 times per month", "5-6", "monthly"),
-#     `4` = c("2-3 times per week","7-9", "Weekly"),
-#     `5` = c("4+ times per week", "10+", "Daily or almost daily"),
-#     `6` = c("bla"),
-#     `7` = c("bla")
-#           ),
-#   class = "data.frame",
-#   row.names = c(NA)
-# )
-# 
-# apa_table(
-#   audit_table,
-#   caption = "AUDIT-C scoring table",
-#   align = c("m{8cm}", rep("m{2cm}", 5)),
-#   col_spanners = list("Code" = c(2,7)),
-#   note = "Item scores are summed. Women who score 3+ and men who score 4+ are at-risk",
-#   landscape = TRUE
-#   )
-
-# df_react_table <-
-#   structure(list(
-#     Code = c("1", "2", "3", "4", "5", "6", "7"),
-#     Description = c(
-#       "The teacher reacts exclusively non-verbally to a disturbance. The flow of the lesson is not interrupted.",
-#       "The teacher reacts nonverbally and simultaneously with a short verbal reaction.
-The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixing gaze).
-The verbal response includes name calling, brief verbal prompts / admonitions.",
-#       "The teacher responds briefly and verbally to a disruption without a preceding nonverbal response.",
-#       "The teacher responds nonverbally and simultaneously overlapping with a verbal long response to a disruption.
-The nonverbal response includes gestures (stop signals, decreasing proximity) and facial expressions (fixating gaze).",
-#       "There is no reaction from the teacher to a disruption because the teacher does not consider it relevant to address the disruption.
-This information can only be obtained through the Stimulated Recall Interview.",
-#       "There is no reaction to a disruption on the part of the teacher because the teacher has not registered the disruption.
-This information can only be obtained through the Stimulated Recall Interview.",
-#       "Dysfunctional Response: the teacher responds inappropriately to a disruption through a lengthy verbal discussion of class rules, yelling around, etc."
-#     ),
-#     `Anchor examples` = c("-",
-#                           "-",
-#                           "drawing on a sheet of paper",
-#                           "-",
-#                           "-",
-#                           "-",
-#                           "-"),
-#     class = "data.frame"
-#   ))
-# 
-# papaja::apa_table(
-#   x = df_react_table,
-#   caption = "Self-developed coding scheme for the teacher's reaction",
-#   align = c("m{8cm}", rep("m{2cm}", 5)),
-#   col_spanners = list("NA"),
-#   # note = "",
-#   landscape = TRUE)
-
-```
-
-After developing and reviewing the coding system, the observers coordinated and the consistency of their ratings was verified.
-For the evaluation, the individual videos of the sample were then coded and the data transferred to an Excel file.
-
-###### Test quality criteria
-
-In the construction of the video analysis method, attention was paid to compliance with the quality criteria of objectivity, reliability and validity.
-
-In order to ensure implementation objectivity, uniform implementation conditions were created.
-In the experimental manual of the ProVisioNET study, the survey procedure is described in detail, so that it is the same for each participant.
-On the one hand, the objectivity of the evaluation was given by the processing in the R.
-On the other hand, prior to the analysis of the videos, a precise coding scheme, which precisely describes the individual codes, explains them and contains examples, was created and discursively discussed in the team (see chapter 4.4.1).
-This coding scheme was tested and revised in a piloting process, which increased the internal validity of the method.
-Interrater reliability was determined for the two raters using sample ratings of the same videos.
-Percent agreement yielded 77.8% and a Cohen's Kappa of k = 0.6, which is a satisfactory value according to Landis & Koch (1977).
-Interpretive objectivity was ensured by specifying scientific hypotheses that then had to be neutrally tested.
-
-With the help of scripted behavioral instructions for students in the instructional unit, a high degree of standardization was achieved that is not present in the normal school setting.
-The lessons were recorded with several video cameras from different angles and an audio recorder.
-This means a big advantage compared to the subjective evaluation of observers in real time.
-In addition, video recordings can be viewed multiple times, by different people or from different perspectives.
-Thus, a high measurement accuracy (reliability) is given [cf.@mayring2005auswertung].
-All measures taken contribute to increase the validity of the method.
-However, it cannot be answered whether the coding scheme is completely valid, because a validation with the help of another measuring instrument was not possible.
-Therefore, it could not be controlled whether the collected construct is related to other similar constructs.
-
-##### Coding Time on Task
-
-XXX
-
-### Questionnaie data
-
-#### Presence Questionnaire
-
-After each micro-teaching-unit, the three actors answered items on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature.
-In addition, subjects were asked to give a self-assessment on  classroom management by completing the same questionnaire after each micro-teaching-unit.
-The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
-
-Bilanz:
-LB01_01	Bilanz: Die Lernenden haben in dieser Unterrichtslektion etwas dazu gelernt.
-LB01_02	Bilanz: Die Lernenden haben sich in dieser Unterrichtslektion wohl gefühlt.
-LB01_03	Bilanz: Mediennutzung und Sozialformen waren dem Inhalt und der Situation der Unterrichtslektion angemessen.
-
-Klassenmanagement:
-LM01_01	Klassenmanagement: Die gesamte Unterrichtslektion wurde für den Lernstoff verwendet.
-LM01_02	Klassenmanagement: Ich habe alles mitbekommen, was in der Klasse passiert ist.
-LM01_03	Klassenmanagement: Den Lernenden war jederzeit klar, was sie tun sollten.
-LM01_04	Klassenmanagement: Die Lernenden konnten ungestört arbeiten.
-LM01_05	Klassenmanagement: Die Lernenden waren die ganze Unterrichtslektion über aktiv bei der Sache.
-LM01_06	Klassenmanagement: Ich habe vieles mit kurzen Blicken und knappen Gesten geregelt.
-LM01_07	Klassenmanagement: Auf Störungen habe ich angemessen reagiert.
-LM01_08	Klassenmanagement: Bei Störungen gab ich den Lernenden ein klares STOP-Signal.
-
-Redeanteil:
-LO01_01	Redeanteil: Wieviel Prozent der gesamten Unterrichtslektion hat nach Ihrer Schätzung Ihr eigener Redeanteil eingenommen? ... %
-LO01_02	Redeanteil: Wenn ich Fragen oder Aufgaben gestellt habe, habe ich den Lernenden folgende Zeit (in Sekunden) zum Nachdenken gegeben ... Sekunden
-
-Präsenz:
-LP01_01	Präsenzindikatoren: Ich hatte eine aufrechte, der Klasse zugewandte Körperhaltung.
-LP01_02	Präsenzindikatoren: Ich habe den Lernenden direkt in die Augen geschaut.
-LP01_03	Präsenzindikatoren: Ich habe meine Position im Raum bewusst eingesetzt und variiert.
-LP01_04	Präsenzindikatoren: Ich habe alle oft angesehen.
-LP01_05	Präsenzindikatoren: Meine Artikulation, Lautstärke und Tonhöhe waren angemessen.
-LP01_06	Präsenzindikatoren: Meine Sprechgeschwindigkeit und Sprechpausen waren angemessen.
-LP01_07	Präsenzindikatoren: Mein Sprechanteil an der gesamten Sprechzeit der Unterrichtslektion war angemessen.
-LP01_08	Präsenzindikatoren: Meine Gestik und Mimik waren abwechslungsreich und ausdrucksstark.
-
-Natürliches Verhalten:
-LV01_01	Natürliches Verhalten: Während der Unterrichtslektion habe ich mich sehr natürlich verhalten.
-LV01_02	Natürliches Verhalten: Es war für mich kein Problem, vor einer fiktiven Klasse zu unterrichten.
-LV01_03	Natürliches Verhalten: Beim Unterrichten vor einer fiktiven Klasse habe ich mich so verhalten, wie ich es auch in der Schule tun würde.
-
-```{r presence_questionnaire, include=TRUE, echo=FALSE, results='asis'}
-
-# load data files
-quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LI06_05, 
-                LB01_01:LB01_03,
-                LM01_01:LM01_08,
-                LP01_01:LP01_08,
-                LV01_01:LV01_03)
-
-# creating a matrix
-quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
-rownames(quest.table) <- c("LM", "LB", "LP", "LV")
-colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","Alpha")
-
-# creating a loop
-i <- "LM"
-
-for (i in c("LM", "LB", "LP", "LV")) {
-
-loop.data <- quest.data %>%
-  dplyr::select(starts_with(match = i))
-
-quest.table[i, "N Items"] <- length(loop.data)
-
-# calculating mean
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  mean() %>%
-  round(., digits = 2) ->
-quest.table[i, "M"]
-
-# calculating SD
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  sd() %>%
-  round(., digits = 2) ->
-quest.table[i, "SD"]
-
-# calculating Min
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  min() %>%
-  round(., digits = 2) ->
-quest.table[i, "Min"]
-
-# calculating Max
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  max() %>%
-  round(., digits = 2) ->
-quest.table[i, "Max"]
-
-# calculating Skewness
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  skewness() %>%
-  round(., digits = 2) ->
-quest.table[i, "Skewness"]
-
-# calculating Kurtosis
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  kurtosis() %>%
-  round(., digits = 2) ->
-quest.table[i, "Kurtosis"]
-
-# calculating Alpha
-alpha <- loop.data %>%
-  cronbach.alpha()
-
-quest.table[i, "Alpha"] <- round(alpha$alpha,2)
-
-}
-
-# rename columns
-rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
-
-# format and insert table in manuscript
-papaja::apa_table(
-quest.table,
-  caption = "Scale analysis for teachers' self-assessment",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-```{r item_analysis_classroom_management, echo=FALSE, include=FALSE, results='asis'}
-quest.data %>%
-  dplyr::select(contains("LM")) %>%
-  as.data.frame() %>%
-  tab_itemscale(CSS = list(
-    css.firsttablerow.col7 = "'cronbachs alpha';"
-  ))
-```
-
-```{r item_analysis_balance, echo=FALSE, include=FALSE, results='asis'}
-quest.data %>%
-  dplyr::select(contains("LB")) %>%
-  as.data.frame() %>%
-  tab_itemscale()
-```
-
-```{r item_analysis_presence, echo=FALSE, include=FALSE,results='asis'}
-quest.data %>%
-  dplyr::select(contains("LP")) %>%
-  as.data.frame() %>%
-  tab_itemscale()
-```
-
-```{r item_analysis_behavior, echo=FALSE, include=FALSE,results='asis'}
-quest.data %>%
-  dplyr::select(contains("LV")) %>%
-  as.data.frame() %>%
-  tab_itemscale()
-```
-
-#### Teachers' perception of disruption and confidence using Rating scales
-
-Two self-developed 11-point rating scales were used to record how disruptive the individual disruptions were perceived by the subjects and how confident they felt in dealing with the disruptions.
-Data for rating scales were collected during the Stimulted Recall Interview, where the experimenter watched the pre-recorded eye-tracking video with the subject.
-
-The questionnaire included nine questions for each scripted disruptive event. The subjects did not have to complete the questionnaire themselves at any time, as this was done by the experimenter.
-
-For the present study, the following two questions from the interview were relevant:
-1. "How disruptive was this event for you?"
-2. "How confident did you feel in dealing with this event?"
-
-Both questions were answered using a scale ranging from 0 to 10. On this scale, 0 stood for "not at all disruptive" or "not at all safe" and 10 for "extremely disturbing" or "extremely safe."
-
-With these rating scales, the subjects indicated their personal subjective feeling towards the individual lesson disruption.
-Rating scales usually consist of a number of clearly arranged categories that can be presented visually in a variety of ways [@albers2009methodik, p.
-67f].
-In the present questionnaire, the numerical representation with eleven answer options (0-10) was used.
-There was no specific designated neutral position.
-In this questionnaire, the middle category 5 was not interpreted as a neutral position.
-In order to avoid misinterpretations of the scaling, the questionnaire was described verbally by the experimenter and follow-up questions from the test subjects were possible at any time.
-With regard to the quality criteria, it should be made clear that complete objectivity in answering the two questions is given by the rating scales.
-The question remained the same for all subjects and no additional comments were made.
-Validity can also be assumed for the questionnaire, since the subjects couls ask follow-up questions and thus uncertainties were clarified.
-However, similar to the video data, there was no perfect reliability with this survey instrument, because in a few exceptional cases, for example, the experimenter forgot to ask the subject the relevant questions.
-
-```{r rating_scales, include=TRUE, echo=FALSE, results='asis'}
-
-# read in data and combine multiple excel sheets into a single table 
-sri <- 
-  excel_sheets("data/Coding_SRI.xlsx") %>% 
-  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% 
-  dplyr::select(Group, Event, `Disruption Factor`, `Confident Factor`) %>% # select relevant columns
-  dplyr::filter(!`Disruption Factor` == -100,
-           !`Confident Factor` == -100,
-           !`Disruption Factor`== -99,
-           !`Confident Factor` == -99)
-
-############## Disruption Factor #########################
-
-sri.disrup.table <- 
-  sri %>%
-  group_by(Group, Event) %>%
-  mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
-  summarise("M" = round(mean(`Disruption Factor`), 
-                        digits = 2),
-            "SD" = round(sd(`Disruption Factor`),
-                         digits = 2),
-            "Min" = min(`Disruption Factor`),
-            "Max" = max(`Disruption Factor`))
-
-# format and insert table in manuscript
-papaja::apa_table(
-sri.disrup.table,
-  caption = "Table Rating Scales Disruption Factor",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-############## Confident Factor #########################
-
-sri.confi.table <- 
-  sri %>%
-  group_by(Group, Event) %>%
-  mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
-  summarise("M" = round(mean(`Confident Factor`), 
-                        digits = 2),
-            "SD" = round(sd(`Confident Factor`),
-                         digits = 2),
-            "Min" = min(`Confident Factor`),
-            "Max" = max(`Confident Factor`))
-
-# format and insert table in manuscript
-papaja::apa_table(
-sri.confi.table,
-  caption = "Table Rating Scales Confident Factor",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-#### Situational Jugdement Test of Strategic Knowledge of Classroom Management
-
-To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, [@gold2015development]).
-In the questionnaire, participants were given hypothetical school scenarios with five to six response strategies for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).
-Depending on the grade given to each strategy, scores were converted in an SPSS syntax resulting in scores ranging from 0 to 1 for each participant.
-
-In developing the test procedure, the authors divided the concept of classroom management into three main aspects: *Monitoring*, *managing momentum* (structuring) and *rules and routines* [@gold2015development, p.
-230f].
-
-*Monitoring* includes proactive strategies such as omnipresence.
-This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them.
-The second strategy is overlapping.
-In this case, the teacher is able to control several teaching processes at the same time.
-Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions [cf.
-ibid.; @kounin2006techniken, p.
-89ff].
-
-By *managing momentum* (structuring), @gold2015development understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention [@kounin2006techniken, p.
-101ff].
-They also include the group focus specifically identified by Kounin [@kounin2006techniken, p.
-117ff], i.e.
-mobilizing the whole class and demanding accountability [@gold2015development, p.
-231].
-
-The third facet of classroom management, establishing *rules, routines and rituals*, supports the other two facets and offers pupils orientation and structure in everyday school life (cf. ibid.).
-
-The construction of the SJT included 14 scenarios that were based on transcribed classroom videos from Germany.
-For the 14 scenarios, response strategies were derived from evidence-based and theoretical principles by 17 experts on classroom management.
-With the exception of scenario 5, which was subsequently excluded, the 17 experts agreed on an appropriate level of content validity for all other scenarios (cf.
-ibid.).
-For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf.
-ibid., p.
-238).
-Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf.
-ibid.).
-
-The construct validity of the SJT with the other 11 scenarios and the sensitivity to differences in strategic knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf.
-ibid., p.
-238ff).
-Despite limitations in reliability, the test was confirmed to have content and construct validity (cf.
-ibid., p.
-243).
-On the basis of these results, sufficient reliability and validity of the SJT test procedure was assumed.
-
-The scenarios could each be assigned to one facet of the mentioned classroom management: Scenarios 1-4 cover the facet *monitoring*, scenarios 6-9 the facet *managing momentum* and scenarios 11-14 the facet *rules and routines*.
-
-In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study *ProVisioNET*.
-The objectivity of analysis was given by processing the obtained questionnaire data in `r cite_r("r-references.bib")` and IBM SPSS 28.
-
-Since the test was a questionnaire designed to assess strategic knowledge of classroom management of *primary school teachers*, but the sample of the study included several types of schools, changes were made in 10 out of 12 scenarios by deleting the indicated class grade.
-Only in two scenarios was the class grade information not deleted, as the action alternatives would otherwise not be appropriate without the information.
-
-```{r sjt, include=TRUE, echo=FALSE, results='asis'}
-
-# read in data
-df_sjt <- read_csv2(file = "data/SJT.csv") %>% 
-  mutate(Group = ifelse(UI06_05 < 200, "Novice","Expert")) %>%
-  dplyr::select(Group, 
-                PK_S1_AL:PK_S14_R)
-
-# remove NAs
-df_sjt <- na.omit(df_sjt)
-
-# create two data frames
-sjt.novice <- df_sjt %>% filter(Group == "Novice")
-sjt.expert <- df_sjt %>% filter(Group == "Expert")
-
-############## NOVICE TABLE #########################
-
-# creating a matrix
-sjt.table.novice <- 
-  matrix(data = NA, nrow = 3, ncol = 8)
-  rownames(sjt.table.novice) <- c("AL", "ST", "R")
-  colnames(sjt.table.novice) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
-
-# creating a loop
-i <- "AL"
-
-for (i in c("AL", "ST", "R")) {
-
-loop.data <- sjt.novice %>%
-  dplyr::select(ends_with(match = i))
-
-sjt.table.novice[i, "N Items"] <- length(loop.data)
-
-# calculating mean
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  mean() %>%
-  round(., digits = 2) ->
-sjt.table.novice[i, "M"]
-
-# calculating SD
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  sd() %>%
-  round(., digits = 2) ->
-sjt.table.novice[i, "SD"]
-
-# calculating Min
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  min() %>%
-  round(., digits = 2) ->
-sjt.table.novice[i, "Min"]
-
-# calculating Max
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  max() %>%
-  round(., digits = 2) ->
-sjt.table.novice[i, "Max"]
-
-# calculating Skewness
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  skewness() %>%
-  round(., digits = 2) ->
-sjt.table.novice[i, "Skewness"]
-
-# calculating Kurtosis
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  kurtosis() %>%
-  round(., digits = 2) ->
-sjt.table.novice[i, "Kurtosis"]
-
-# calculating alpha
-alpha <- loop.data %>%
-  cronbach.alpha()
-
-sjt.table.novice[i, "alpha"] <- round(alpha$alpha,2)
-
-}
-
-# rename columns
-rownames(sjt.table.novice) <- c("Monitoring", "Managing Momentum", "Rules and routines")
-
-# format and insert table in manuscript
-papaja::apa_table(
-sjt.table.novice,
-  caption = "Scale analysis SJT novices",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-############## EXPERT TABLE #########################
-
-# creating a matrix
-sjt.table.expert <- 
-  matrix(data = NA, nrow = 3, ncol = 8)
-  rownames(sjt.table.expert) <- c("AL", "ST", "R")
-  colnames(sjt.table.expert) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
-
-# creating a loop
-i <- "AL"
-
-for (i in c("AL", "ST", "R")) {
-
-loop.data <- sjt.expert %>%
-  dplyr::select(ends_with(match = i))
-
-sjt.table.expert[i, "N Items"] <- length(loop.data)
-
-# calculating mean
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  mean() %>%
-  round(., digits = 2) ->
-sjt.table.expert[i, "M"]
-
-# calculating SD
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  sd() %>%
-  round(., digits = 2) ->
-sjt.table.expert[i, "SD"]
-
-# calculating Min
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  min() %>%
-  round(., digits = 2) ->
-sjt.table.expert[i, "Min"]
-
-# calculating Max
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  max() %>%
-  round(., digits = 2) ->
-sjt.table.expert[i, "Max"]
-
-# calculating Skewness
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  skewness() %>%
-  round(., digits = 2) ->
-sjt.table.expert[i, "Skewness"]
-
-# calculating Kurtosis
-loop.data %>%
-  mutate(mean = rowMeans(.)) %>%
-  pull(mean) %>%
-  kurtosis() %>%
-  round(., digits = 2) ->
-sjt.table.expert[i, "Kurtosis"]
-
-# calculating alpha
-alpha <- loop.data %>%
-  cronbach.alpha()
-
-sjt.table.expert[i, "alpha"] <- round(alpha$alpha,2)
-
-}
-
-# rename columns
-rownames(sjt.table.expert) <- c("Monitoring", "Managing Momentum", "Rules and routines")
-
-# format and insert table in manuscript
-papaja::apa_table(
-sjt.table.expert,
-  caption = "Scale analysis SJT novices",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-XXX FRANZI
-
-## Procedure
-
-The project was conducted as a laboratory study in a cross-sectional study design to investigate whether and how teachers' experience has an influence on the perception of and reaction to classroom disruptions.
-
-In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and Septemper 2022.
-
-Before the data collection, each subject received a personal digital meeting with the experimenter to go over the study procedure and to arrange a date for the data collection.
-During the digital meeting, the subjects were asked to prepare a 15-minute lesson in a subject and grade of their choice for the data collection.
-
-On the day of a data collection, the first step was to set up the study room at the University of Leipzig.
-For this, all the appropriate technical equipment was charged and installed in the room (see set up plan [REFERENZ EINFÜGEN]).
-Next, all four cameras and the audio recorder were synced via Timecode System.
-
-After the subject arrived, a smart watch was put on to measure the heart rate during the session and to get a pretest time at least 15min before the session started.
-In addition to the experimenter and the subject, three student assistants from the working group always took part in the data collection, as they represented the class.
-
-After the welcome, the subject was again briefed about the study.
-It was explicitly pointed out that the student assistants would act as the class and simulate typical class events during the lesson.
-The subject was asked in advance to behave as naturally as possible during the entire time.
-Next, the subjects' written informed consent was obtained and contact details were collected in order to inform all persons participating in the study if a covid infection should occur.
-
-After the introduction, the eye-tracking glasses were adjusted for the subject by inserting contact lenses if necessary and changing the nose pad.
-To start the eye tracking glasses, the Tobii Glasses must be fitted onto the subject's head via an one-point-calibration.
-In the calibration process the subject was asked to look at a Calibration Card held in-front of the subject for a few seconds.
-The experimenter started the recording from Tobii Glasses Controller Software running on a computer.
-
-After starting the eye tracking recording, all other technical devices were also switched on: The four cameras and the audio recorder were controlled via iPad using the BLINK Hup app and could be started simultaneously by synchronization.
-The ZED camera was started manually on another laptop.
-
-Before the 15-minute lesson, there was a short 10-minute warm-up phase.
-The phase was divided into two parts and served on the one hand to get the subjects used to the eye-tracking glasses and on the other hand to get used to their class.
-In the first phase of the warm-up, the game "name juggling" was played using two balls.
-In the game, the subject and the three actors threw two balls at each other and, depending on the color of the ball, called either their own name or that of the target person.
-After the name juggling, the subjects were supposed to start a conversation.
-For this, the subject thought of a question for each student and was also asked a question of each student.
-The content could be anything that interested the participants.
-
-After the warm up phase, the experimenter ensured a manual synchronization of the technique by an acoustic signal in which she clapped her hands loudly twice standing in the middle of the room.
-After this, another nine-point calibration followed outside the study room in a neighboring room.
-Before the subject left the room for calibration, the time on the smartwatch was noted, as well as the steps recorded until that point.
-The subject had to stand at a marked point and look at a board three meters away with nine april tags.
-The subject was asked to read the nine points aloud in order at a normal speaking speed.
-This procedure was important to validate the one-point calibration on the one hand and on the other hand to give the subject the feeling of a lesson start, because after this calibration the subject came into the study room to start the 15-minute lesson.
-
-For the micro-teaching lesson, student teachers and experienced teachers were asked to prepare an introduction of 15 minutes which they taught in front of the fictitious class consisting of three student assistants.
-The actors simulated the nine classroom events during the lesson, derived by research literature.
-The order of the disruptions as well as the students performing them were fully balanced using Latin Square.
-The disruptions were only visible for the class on a screen.
-
-```{r disruption_categories, include=TRUE, echo=FALSE, results='asis'}
-df_disrup_table <- data.frame(`Verbal Disruption` = c("chatting with neighbor", "whispering with neighbor", "heckling"),
-                              Agitation = c("drumming hands", "clicking pen", "snipping with fingers"),
-                              `Lack of eagerness to learn` = c("putting head on table", "looking at phone", "drawing on a sheet of paper")
-                              )
-
-papaja::apa_table(x = df_disrup_table,
-                  caption = "Categories of Disruptions (Lohmann, 2015)",
-                  escape = TRUE,
-                  placement = "h",
-                  font_size = "tiny")
-
-```
-
-During the lesson, a mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson.
-All other sounds and voices were recorded by an audio recorder.
-To record facial expressions, gestures and movements, four mobile cameras were installed to record the classroom from all perspectives (!!!see figures).
-
-After the lesson, the time was again noted from the smartwatch as well as the subject's steps.
-The nine-point calibration was also performed again in the neighboring room.
-This time, however, the subject was asked to wait outside the room until he or she was called in, because four letters from A to D were placed in the study room.
-The subject was asked to stand facing the board at a marked point in the room and, when given an acoustic signal, to turn around and search the letters and read them aloud in order.
-This served as a control condition for the speed of the subjects' perceptual ability as no expertise is required for searching letters.
-
-After the letter search, the experimenter clapped twice with the hands to record an acoustic signal for the synchronization of all technical devices.
-Afterwards, all devices were switched off and the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature.
-The completion of the questionnaire took approximately 5 minutes.
-
-In the second part of the study, the experimenter conducted a Stimulated Recall Interview (SRI) with the subject(see in Figure \@ref(fig:sri).
-The interview was recorded by the ambient recorder and additionally with a software called OBS to record the speech and screen.
-The recorded eye-tracking video was watched and commented on by the subject while thinking aloud.
-The interview was structured by a guideline based on a fixed sequence of questions, however the subjects were allowed to answer completely open to these questions.
-The objective was to collect data that would provide insight into the subjects' thoughts and reactions in relation to the scripted classroom disruptions.
-The eye-tracking video was not completely re-watched, but stopped at the points where disruptions occurred.
-After the disruption occurred, the subject was asked to describe what had just happened.
-If the disruption was noticed, the subject was asked how disruptive the event was at that moment on a scale from 0 to 10.
-In addition, the subject was asked to reason the given number.
-In a next step, the experimenter re-played the subject's reaction to the disruption and asked to describe and reason the reaction.
-The experimenter then asked the subject to rate on a scale from 0 to 10 how confident he/she felt in dealing with the disruption and again to reason the number (for a detailed description of the scale question, see Rating Scales).
-
-```{r sri, include = T, fig.cap = "Subject and experimenter during the Stimulated Recall Interview", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/sri.pdf", dpi = 108)
-
-```
-
-Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management [SJT, @gold2015development] in the form of a questionnaire.
-Here they had to assess teaching scenarios and evaluate their behavior in response to them.
-The SJT was used to assess strategic knowledge about classroom management.
-The completion of the entire survey took 15 min on average.
-
-## Data analysis
-
-We investigated whether experts and novice teachers differed
-
-All reported data analyses were conducted with the `r cite_r("r-references.bib")` and IBM SPSS 28.
-
-# Results
-
-# Discussion
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
+The preview shows you a rendered HTML copy of the contents of the editor.
+Consequently, unlike *Knit*, *Preview* does not run any R code chunks.
+Instead, the output of the chunk when it was last run in the editor is displayed.

### 2024-07-30 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
submission weiter

@@
       stargazer,
-      papaja)
+      papaja,
+      grid)
 ```
@@
 # disruption & confidence rating
-
 df_rating <- 
@@
 # demographic data
-
 df_demo <- 
@@
 # merge two data frames by ID 
-
 df_merge <- merge(df_demo,
@@
 
-main <-
+# single bpm values (data frame with only single measurement point)
+
+main_single_hr <-
 map(.x = dir(path = data_path,
@@
                col_types = c("t","n")
-               ) |> 
+               ) %>% 
   mutate(time = Time - min(Time),
@@
 
-main <-
-  left_join(main, df_merge,
-            by = "ID")
+# adding z-standardized HR
 
-main <- 
-  main %>% 
-  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
-  distinct() %>% 
-  group_by(ID) %>% 
+main_single_hr <-
+  main_single_hr |> 
+  dplyr::select("time", "heart_rate", "ID", "time_span") |> 
+  distinct() |> 
+  group_by(ID) |> 
   dplyr::summarise(mean_heart = mean(heart_rate),
-            sd_heart = sd(heart_rate)) %>%
-  ungroup() %>% 
-  right_join(x = .,
-             y = main,
-             by = "ID") %>% 
-  filter(!(time_span == "teaching" & time > 600)) %>%
+            sd_heart = sd(heart_rate)) |> 
+  ungroup() |> 
+  right_join(y = main_single_hr,
+             by = "ID") |> 
+  filter(!(time_span == "teaching" & time > 600)) |> 
   mutate(heart_rate_std = (heart_rate - mean_heart)/
@@
 
+## count for individuals
+
+main_single_hr |> 
+  filter(time >= 7200) |> 
+  distinct(ID, .keep_all = TRUE) -> filter_overall
+
 N_prewrangling <- as.numeric(nrow(df_demo))
 
-N_postwrangling <- as.numeric(length(unique(main$ID)))
+N_postwrangling <- as.numeric(length(unique(main_single_hr$ID)))
 
@@
 
-descrip_hr_overall <- main |>
+descrip_hr_overall <- main_single_hr |> 
   filter(time_span %in% c("overall")) |> 
@@
 
-descrip_hr_overall_std <- main |>
+descrip_hr_overall_std <- main_single_hr |> 
   filter(time_span %in% c("overall")) |> 
@@
 
-descrip_hr_phases <- main |> 
+descrip_hr_phases <- main_single_hr |> 
   filter(!time_span %in% c("overall")) |> 
-  group_by(time_span) |> 
+  group_by(time_span) %>% 
   summarise(N = n_distinct(ID),
@@
 
-descrip_hr_phases_std <- main |> 
+descrip_hr_phases_std <- main_single_hr |> 
   filter(!time_span %in% c("overall")) |> 
@@
   summarise(N = n_distinct(ID),
-            "M heart rate in bpm" = round(mean(heart_rate_std),
+            "M heart rate std" = round(mean(heart_rate_std),
                                      digits = 2),
-            "SD heart rate in bpm" = round(sd(heart_rate_std),
+            "SD heart rate std" = round(sd(heart_rate_std),
                                       digits = 2),
-            "Min heart rate in bpm" = round(min(heart_rate_std),
+            "Min heart rate std" = round(min(heart_rate_std),
                                             digits = 2),
-            "Max heart rate in bpm" = round(max(heart_rate_std),
+            "Max heart rate std" = round(max(heart_rate_std),
                                             digits = 2)
   )
-
-# # format and insert table in manuscript
-# descrip_hr_phases |>
-# papaja::apa_table(
-#   caption = "Mean, SD and range for teachers' heart rate in individual phases",
-#   # note = "Write Note here",
-#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-#   )
 
@@
             )
+
 ```
@@
 descrip_hr_phases_std <-  descrip_hr_phases_std |> 
-  rename(`M HR` = `M heart rate in bpm`,
-         `SD HR` = `SD heart rate in bpm`,
-         `Min` = `Min heart rate in bpm`,
-         `Max` = `Max heart rate in bpm`,
+  rename(`M HR` = `M heart rate std`,
+         `SD HR` = `SD heart rate std`,
+         `Min` = `Min heart rate std`,
+         `Max` = `Max heart rate std`,
          Interval = time_span)
@@
 
-print(tab_1)
-
 writeLines(tab_1, 'tab_1.tex')
@@
 df_heart_rate <- 
-  main |> 
+  main_single_hr |> 
   mutate(time = time / 60) |> 
@@
 df_heart_rate_std <- 
-  main |> 
+  main_single_hr |> 
   mutate(time = time / 60) |> 
@@
               colour = "black",
-              level = 0.95) +
+              level = 0.95
+              ) +
   scale_color_viridis_d(option = "A",
-                        end = 0.8) +
-  scale_linetype_manual(values = c(1, 6)) +
-  scale_x_continuous(expand = c(0.01,0)) + 
+                        end = 0.8
+                        ) +
+  scale_linetype_manual(values = c(1, 6)
+                        ) +
+  scale_x_continuous(expand = c(0.01,0)
+                     ) + 
  labs(x = "",
@@
              ncol = 2,
-             scales = "free_y") -> loess_hr
+             scales = "free_y"
+             ) + 
+  theme(plot.margin = margin(r = 15,
+                             t = 20,
+                             b = 20)
+        ) -> loess_hr
 
@@
              ncol = 2,
-             scales = "free_y") -> loess_hr_std
+             scales = "free_y"
+             ) +
+  theme(plot.margin = margin(r = 30,
+                             t = 20,
+                             b = 20)
+        ) -> loess_hr_std
 
-loess_comp <- grid.arrange(loess_hr, loess_hr_std,
+loess_comp <- grid.arrange(loess_hr,
+                           loess_hr_std,
                            ncol = 2)
@@
        filename = "plots_publication/loess_plot_std_unstd_new.pdf",
-       width = 16,
-       height = 12,
+       width = 20,
+       height = 15,
        units = "cm")
@@
 
-```{r, include=FALSE}
+We first tested the hypothesis that teachers showed the highest mean standardized HR during the micro-teaching unit, compared to all other intervals (Hypothesis 1a).
+Repeated measures ANOVA revealed that the mean standardized HR differed statistically significantly between intervals, F(4, 400) = 260.62, p < .05, f = 1.60 (large effect).
+Post-hoc contrasts indicated that, as hypothesized, the mean was significantly higher in the teaching interval (I2) than in all other intervals (see also Fig.
+4).
+Specifically, it was higher than in the pre-teaching interval (I1; t(400)  = -10.08, p < .05, d = 1.03; large effect), the post-teaching interval (I3; t(400) = -6.94, p < .05, d = 1.37; large effect), the interview interval (I4; t(400) = 15.00, p < .05, d = 3.29; large effect), and the end interval (I5); t(400) = 22.54, p < .05, d = 4.64; large effect).
 
-# main |> 
-#   filter(time_span != "overall") |>
-#   dplyr::select("ID","time_span", "time","heart_rate_std") |> 
-#   mutate(time_span = factor(time_span,
-#                             levels = c("preparation","teaching","post","interview","end"),
-#                             labels = c("(1) Pre-teaching\nInterval","(2) Teaching\nInterval","(3) Post-teaching\nInterval","(4) Interview\nInterval","(5) End\nInterval"))) |> 
-#   distinct() |>
-#   group_by(time_span) |> 
-#   summarise(z_mean = mean(heart_rate_std),
-#             z_sd = sd(heart_rate_std),
-#             z_t = qt(p = 0.05 / 2,      # 0.01 KI
-#                df = n() - 1,
-#                lower.tail = F
-#                ),
-#             z_error = z_sd / sqrt(n()),
-#             lower = z_mean - z_t * z_error,
-#             upper = z_mean + z_t * z_error,
-#             ) |> 
-#   ungroup() |> 
-#   ggplot(mapping = aes(x = factor(0),
-#                        y = z_mean)) + 
-#   geom_point() +
-#   geom_errorbar(mapping = aes(ymin = lower,
-#                               ymax = upper),
-#                 width = 0.2) +
-#   geom_hline(yintercept = 0,
-#              linetype = "dashed") +
-#   scale_y_continuous(breaks=seq(-1, 1, 0.5), 
-#                      limits=c(-1.1, 1)) + 
-#   labs(x = "Time (in Minutes)",
-#        y = "Standardized Mean Heart Rate",
-#        # caption = expression(paste(italic("Note: "),
-#        #                            "The shadow around the line represents the 99% confidence interval."
-#        #                            )
-#        #                      )
-#        ) +
-#   facet_grid(cols = vars(time_span),
-#              scales = "free_x") +
-#   theme_apa() +
-#   theme(axis.text.x = element_blank(),
-#         axis.ticks.x = element_blank(),
-#         plot.caption = element_text(hjust = 0))
-# 
-# ggsave(filename = "plots_publication/mean_plot.png",
-#        width = 20,
-#        height = 12,
-#        units = "cm")
+```{r}
+box_plot <-
+  main_single_hr |> 
+  filter(time_span != "overall") |>  
+  dplyr::select("ID",
+         "time_span",
+         "heart_rate_std") |> 
+  mutate(time_span = fct_recode(time_span,
+                                "Pre-teaching Interval" = "preparation",
+                                "Teaching Interval" = "teaching",
+                                "Post-teaching Interval" = "post",
+                                "Interview Interval" = "interview",
+                                "End Interval" = "end"
+                                ),
+         time_span = factor(time_span,
+                            levels = c("Pre-teaching Interval",
+                                       "Teaching Interval",
+                                       "Post-teaching Interval",
+                                       "Interview Interval",
+                                       "End Interval"
+                                       ),
+                            labels = c("Pre-Teaching\nInterval",
+                                       "Teaching\nInterval",
+                                       "Post-Teaching\nInterval",
+                                       "Interview\nInterval",
+                                       "End\nInterval")
+                            )
+         ) |> 
+  distinct() |> 
+  group_by(ID, time_span) |> 
+  summarise(mean_hr_std = 
+              mean(heart_rate_std, 
+                   na.rm = TRUE)
+            ) |> 
+  ggplot(mapping = aes(x = time_span,
+                       y = mean_hr_std
+                       )
+         ) +
+  geom_boxplot()+
+  scale_y_continuous(breaks=seq(-2, 2, 1), 
+                     limits=c(-2, 2)
+                     ) +   
+  # geom_jitter(width = 0.2) +
+  theme_apa() + 
+  theme(axis.text.x = 
+          element_text(
+            color="black",
+            size = 12),
+        plot.caption = element_text(hjust = 0)
+        ) + 
+  labs(x = "",
+       y = "Mean Standardized Heart Rate",
+       caption = expression(
+         paste(italic("Note: N"), 
+               "= 81 participants per interval. Fig. shows median (bold line), interquartile range (box) and outliers (dots)."
+         )
+       ))
+
+ggsave(filename = "plots_publication/box_plot.pdf",
+       plot = box_plot,
+       width = 20,
+       height = 15,
+       units = "cm")
 ```
+
+```{=latex}
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
+  \caption{Distribution of the standardized heart rate means in the five intervals}
+  \label{Distribution of the standardized heart rate means in the five intervals}
+\end{figure}
+```
+
+Next, we examined HR changes (i.e., mean slopes) within each interval to test for the hypothesis that HR increased during the pre-teaching interval and decreased during all other intervals (Hypothesis 1b).
+The mean intercepts and mean slopes, complemented by their standard deviations for each interval, are shown in Table 2; the graphical representation of the slopes is displayed in Figure 5.
+The mean slope of the pre-teaching interval (I1) was significantly positive, indicating an increase in HR, as hypothesized.
+Further, the mean slopes of the teaching interval (I2) and post-teaching interval (I3) were significantly negative, indicating a decrease in HR.
+For the last two intervals, the interview interval (I4)  and end interval (I5), the mean slope was negative but did not differ significantly from zero.
+
+```{r}
+df_regression <- 
+  main_single_hr %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID", "time_span","time","heart_rate_std","heart_rate") %>% 
+  distinct() %>% 
+  mutate(time = time / 60) %>% 
+  mutate(ID = as_factor(ID),
+         Phase = factor(time_span,
+                           levels = c("preparation","teaching","post","interview","end"),
+                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
+                           )
+         )
+
+fix_models <-
+  df_regression %>%
+  split(.$Phase) %>%
+  map( ~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
+            data = .)) %>%
+  map(
+    ~ coef(.) %>%
+      tibble::as_tibble(.,
+                        rownames = "name") %>%
+      transmute(
+        type = if_else(str_detect(name,
+                                  ":"),
+                       true = "slope",
+                       false = "intercept"),
+        id = str_remove_all(name,
+                            "[^[:digit:]]"),
+        value = value
+      ),
+
+  ) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_wider(names_from = type,
+              values_from = value)
+
+p.values_slope <-
+  fix_models %>%
+  split(.$Phase) %>%
+  map( ~ t.test(x = .$slope,
+                mu = 0)$p.value) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_slope")
+
+p.values_intercept <-
+  fix_models %>%
+  split(.$Phase) %>%
+  map( ~ t.test(x = .$intercept,
+                mu = 0)$p.value) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_intercept")
+
+sd_mean <-
+  fix_models %>%
+  group_by(Phase) %>%
+  dplyr::summarise(
+    mean_slope = mean(slope),
+    sd_slope = sd(slope),
+    mean_intercept = mean(intercept),
+    sd_intercept = sd(intercept)
+  )
+
+table_data <- 
+  right_join(x = sd_mean,
+             y = p.values_intercept,
+             by = "Phase") %>% 
+  right_join(x = .,
+             y = p.values_slope,
+             by = "Phase") %>% 
+  transmute(Phase = factor(Phase,
+                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
+                           ),
+            n = NA,
+            `Mean(Intercept)` = round(mean_intercept, digits = 3),
+            `SD(Intercept)` = round(sd_intercept, digits = 3),
+            `p-Value (Intercept)` = p.value_intercept,
+            `Mean(Slope)` = round(mean_slope, digits = 3), 
+            `SD(Slope)` = round(sd_slope,digits = 3),
+            `p-Value (Slope)` = p.value_slope, 
+            ) %>% 
+  arrange(Phase)

### 2024-07-30 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
submission weiter

@@
 
+We first tested the hypothesis that teachers showed the highest mean
+standardized HR during the micro-teaching unit, compared to all other
+intervals (Hypothesis 1a). Repeated measures ANOVA revealed that the
+mean standardized HR differed statistically significantly between
+intervals, F(4, 400) = 260.62, p \textless{} .05, f = 1.60 (large
+effect). Post-hoc contrasts indicated that, as hypothesized, the mean
+was significantly higher in the teaching interval (I2) than in all other
+intervals (see also Fig. 4). Specifically, it was higher than in the
+pre-teaching interval (I1; t(400) = -10.08, p \textless{} .05, d = 1.03;
+large effect), the post-teaching interval (I3; t(400) = -6.94, p
+\textless{} .05, d = 1.37; large effect), the interview interval (I4;
+t(400) = 15.00, p \textless{} .05, d = 3.29; large effect), and the end
+interval (I5); t(400) = 22.54, p \textless{} .05, d = 4.64; large
+effect).
+
+\begin{verbatim}
+## `summarise()` has grouped output by 'ID'. You can override using the `.groups`
+## argument.
+\end{verbatim}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
+  \caption{Distribution of the standardized heart rate means in the five intervals}
+  \label{Distribution of the standardized heart rate means in the five intervals}
+\end{figure}
+
 \bibliography{r-references.bib}

### 2024-07-31 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
Sachen

@@
 
+Next, we examined HR changes (i.e., mean slopes) within each interval to
+test for the hypothesis that HR increased during the pre-teaching
+interval and decreased during all other intervals (Hypothesis 1b). The
+mean intercepts and mean slopes, complemented by their standard
+deviations for each interval, are shown in Table 2; the graphical
+representation of the slopes is displayed in Figure 5. The mean slope of
+the pre-teaching interval (I1) was significantly positive, indicating an
+increase in HR, as hypothesized. Further, the mean slopes of the
+teaching interval (I2) and post-teaching interval (I3) were
+significantly negative, indicating a decrease in HR. For the last two
+intervals, the interview interval (I4) and end interval (I5), the mean
+slope was negative but did not differ significantly from zero.
+
+\input{tab_2.tex}
+
+```
+
 \bibliography{r-references.bib}

### 2024-08-02 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
?!

@@
 ## Participants
-
 ```{r demographicstable, include = TRUE, echo=FALSE}
@@
   read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
+  filter(!LI06_05 == 201) %>% # exclude participant due to missing eye tracking data
   transmute(Group = LI06_05,
@@
 
-# # format and insert table in manuscript
-# demo.table %>%
-# papaja::apa_table(
-#   caption = "Demographic Information",
-#   # note = "Write Note here",
-#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-#   )
-
-# create a basic table (tibble) using tidyverse functions
-exp.table <- demo.data %>%
-  group_by(Group) %>%
-  summarise(N=n(),
-           "M Exp." = round(mean(`Teaching Experience`), 2),
-            "SD Exp." = round(sd(`Teaching Experience`), 2),
-            "Min Exp." = min(`Teaching Experience`),
-            "Max Exp." = max(`Teaching Experience`),
-            "M Semester" = round(mean(Semester), 2),
-            "SD Semester" = round(sd(Semester), 2),
-            "Min Semester" = min(Semester),
-            "Max Semester" = max(Semester),
-            "M Internship" = round(mean(Internship), 2),
-            "SD Internship" = round(sd(Internship), 2),
-            "Min Internship" = min(Internship),
-            "Max Internship" = max(Internship),
-            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
-            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
-           )
-
-# # format and insert table in manuscript
-# exp.table %>%
-# papaja::apa_table(
-#   caption = "Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent",
-#   # note = "Write Note here",
-#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+# # create a basic table (tibble) using tidyverse functions
+# exp.table <- demo.data %>%
+#   group_by(Group) %>%
+#   summarise(N=n(),
+#            "M Exp." = round(mean(`Teaching Experience`), 2),
+#             "SD Exp." = round(sd(`Teaching Experience`), 2),
+#             "Min Exp." = min(`Teaching Experience`),
+#             "Max Exp." = max(`Teaching Experience`),
+#             "M Semester" = round(mean(Semester), 2),
+#             "SD Semester" = round(sd(Semester), 2),
+#             "Min Semester" = min(Semester),
+#             "Max Semester" = max(Semester),
+#             "M Internship" = round(mean(Internship), 2),
+#             "SD Internship" = round(sd(Internship), 2),
+#             "Min Internship" = min(Internship),
+#             "Max Internship" = max(Internship),
+#             "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
+#             "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
 #            )
@@
 
-```{r}
-plot(cars)
+## Measures
+
+### Eye-Tracking Data
+```{r eyetracking, include = TRUE, echo=FALSE}
+
+# return a character vector with names of .tsv data in data folder
+ file_names <- list.files(path = "data",
+                          pattern = "interval_complete.tsv")
+
+# read every object names in file_names and save it as a tibble
+ for (i in file_names) {
+
+   work_data <-
+     read_tsv(file = paste0("data/", i),
+              locale = locale(decimal_mark = ",")) %>%
+     dplyr::select(Group,
+                   Participant,
+                   starts_with("Total_duration_of_fixations"),
+                   starts_with("Number_of_fixations")
+     )
+
+   assign(value = work_data, 
+          x = str_remove(paste0("tib_", i), 
+                         pattern = ".tsv"))
+
+ }
+
+# Bind every tibble that contains "interval_complete" to a new tible
+ df_aoi <-
+   mget(ls(pattern = "interval_complete")) %>%
+   bind_rows()
+
+ df_aoi$Participant <- as.numeric(
+   str_extract(df_aoi$Participant,
+                                   "\\d{3}")
+   )
+
+# Remove temporary data for a cleaner workspace
+ rm(list = ls(pattern = "^tib_ProVisio"))
+ rm(work_data)
+ rm(file_names)
+ rm(i)
+
 ```
 
-Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
+#### Fixation count & fixation duration (M, SD, Effektstärke)
+•	Alles (gesamte Lektion), students (gesamte Lektion)
+•	disruptive person (tatsächliche Dauer der Störung)
 
-When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
+#### Time to first fixation 
+•	disruptive person (tatsächliche Dauer der Störung)
 
-The preview shows you a rendered HTML copy of the contents of the editor.
-Consequently, unlike *Knit*, *Preview* does not run any R code chunks.
-Instead, the output of the chunk when it was last run in the editor is displayed.
+### Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
+```{r rating_scales, echo=FALSE, results='asis'}
+
+# read in data and combine multiple excel sheets into a single table 
+sri <-
+  excel_sheets("data/Coding_SRI.xlsx") %>%
+  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+  filter(
+    !ID %in% c(201),
+    !disruption_appraisal == -100,
+    !confidence_appraisal == -100,
+    !disruption_appraisal == -99,
+    !confidence_appraisal == -99,
+    !disruption_appraisal == -88,
+    !confidence_appraisal == -88,
+    !prevalence_rating == -100,
+    !prevalence_rating == -99,
+    !prevalence_rating == -88
+    ) %>%
+  mutate(ID = ifelse(ID < 200, "Novice", "Expert"))
+
+############## Disruption appraisal #########################
+
+sri.disrup.table <-
+  sri %>%
+  group_by(ID) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(disruption_appraisal), digits = 2),
+    "SD" = round(sd(disruption_appraisal), digits = 2),
+    "Min" = min(disruption_appraisal),
+    "Max" = max(disruption_appraisal)
+    )
+
+knitr::kable(sri.disrup.table,
+             caption = "Disruption Appraisal")
+
+### with event
+sri.disrup.event.table <-
+  sri %>%
+  group_by(ID, event) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(disruption_appraisal), digits = 2),
+    "SD" = round(sd(disruption_appraisal), digits = 2),
+    "Min" = min(disruption_appraisal),
+    "Max" = max(disruption_appraisal)
+  )
+
+# insert a table into HTML
+knitr::kable(sri.disrup.event.table,
+             caption = "Disruption appraisal with event")
+
+# create a new data frame with appraisal
+sri_disrup <- subset.data.frame(sri, select = c(ID, event, disruption_appraisal))
+
+# plotting disruption appraisal for groups
+dist_group_plot <- 
+  sri_disrup %>% 
+  mutate(ID = factor(ID,
+                     levels = c("Novice",
+                                "Expert"
+                                )
+                     )
+         ) %>% 
+  ggplot(mapping = aes(x = ID,
+                       y = disruption_appraisal)) +
+  geom_boxplot(mapping = aes(fill = ID),
+               outlier.shape = NA) +
+  geom_point(size = 1,
+             alpha = 0.4,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  scale_x_discrete(limits = c("Novice", "Expert")) +
+  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
+  labs(x = "",
+       y = "Disruption Appraisal") + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  ggtitle("How disruptive was the event for you?") +
+  theme_cowplot()
+
+dist_group_plot
+
+#################### T-TEST & EFFECT SIZE ############
+
+# Disruption appraisal 
+# t-test for expertise differences
+t_test_disrup <- t.test(x = sri$disruption_appraisal[sri$ID == "Expert"],
+                        y = sri$disruption_appraisal[sri$ID == "Novice"])
+
+# Disruption appraisal 
+# effect size for expertise differences
+d_sri_disrup <- CohenD(x = sri$disruption_appraisal[sri$ID == "Expert"],
+                       y = sri$disruption_appraisal[sri$ID == "Novice"],
+                       na.rm = TRUE)
+
+round(d_sri_disrup, 2)
+
+############## Confidence appraisal #########################
+
+sri.confi.table <-
+  sri %>%
+  group_by(ID) %>%
+  summarise(
+    "M" = round(mean(confidence_appraisal), digits = 2),
+    "SD" = round(sd(confidence_appraisal), digits = 2),
+    "Min" = min(confidence_appraisal),
+    "Max" = max(confidence_appraisal)
+  )
+
+# insert a table into HTML
+knitr::kable(sri.confi.table,
+             caption = "Confidence appraisal")
+
+### with event
+sri.confi.event.table <- 
+  sri %>%
+  group_by(ID, event) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(confidence_appraisal), digits = 2),
+    "SD" = round(sd(confidence_appraisal), digits = 2),
+    "Min" = min(confidence_appraisal),
+    "Max" = max(confidence_appraisal)
+  )
+
+knitr::kable(sri.confi.event.table,
+             caption = "Confidence appraisal with event")
+
+# create a new data frame with appraisal
+sri_confi <- subset.data.frame(sri, 
+                               select = c(ID, 
+                                          event, 
+                                          confidence_appraisal)
+                               )
+
+# plotting confidence appraisal for groups
+confi_group_plot <- 
+  sri_confi %>% 
+  mutate(ID = factor(ID,
+                     levels = c("Novice",
+                                "Expert"
+                                )
+                     )
+         ) %>% 
+  ggplot(mapping = aes(x = ID,
+                       y = confidence_appraisal)) +
+  geom_boxplot(mapping = aes(fill = ID),
+               outlier.shape = NA) +
+  geom_point(size = 1,
+             alpha = 0.4,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  scale_x_discrete(limits = c("Novice", "Expert")) +
+  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
+  labs(x = "",
+       y = "Confidence Appraisal") + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  ggtitle("How confident did you feel dealing with this event?") +
+  theme_cowplot()
+
+confi_group_plot
+
+#################### T-TEST & EFFECT SIZE ############
+
+# Confidence Appraisal 
+# t-test for expertise differences
+t_test_confi <- t.test(x = sri$confidence_appraisal[sri$ID == "Expert"],
+                       y = sri$confidence_appraisal[sri$ID == "Novice"])
+
+# Disruption Factor 
+# effect size for expertise differences
+d_sri_confi <- CohenD(x = sri$confidence_appraisal[sri$ID == "Expert"],
+                      y = sri$confidence_appraisal[sri$ID == "Novice"],
+                      na.rm = TRUE)
+
+round(d_sri_confi, 2)
+
+############## Prevalence Rating #########################
+
+sri.preva.table <-
+  sri %>%
+  group_by(ID) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(prevalence_rating), digits = 2),
+    "SD" = round(sd(prevalence_rating), digits = 2),
+    "Min" = min(prevalence_rating),
+    "Max" = max(prevalence_rating)
+  )
+
+# insert a table into HTML
+knitr::kable(sri.preva.table,
+             caption = "Prevalence rating")
+
+#### with event 
+sri.preva.event.table <-
+  sri %>%
+  group_by(ID, event) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(prevalence_rating), digits = 2),
+    "SD" = round(sd(prevalence_rating), digits = 2),
+    "Min" = min(prevalence_rating),
+    "Max" = max(prevalence_rating)
+  )
+
+# insert a table into HTML
+knitr::kable(sri.preva.event.table,
+             caption = "Prevalence rating with events")
+
+# create a new data frame with rating
+sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
+
+# plotting prevalence rating for groups
+preva_group_plot <- 
+  sri_preva %>% 
+  mutate(ID = factor(ID,
+                     levels = c("Novice",
+                                "Expert"
+                                )
+                     )
+         ) %>% 
+  ggplot(mapping = aes(x = ID,
+                       y = prevalence_rating)) +
+  geom_boxplot(mapping = aes(fill = ID),
+               outlier.shape = NA) +
+  geom_point(size = 1,
+             alpha = 0.4,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  scale_x_discrete(limits = c("Novice", "Expert")) +
+  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
+  labs(x = "",
+       y = "Prevalence Rating") + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  ggtitle("How widespread is this event in the classroom?") +
+  theme_cowplot()
+
+preva_group_plot
+
+#################### T-TEST & EFFECT SIZE ############
+
+# Prevalence Rating 
+# t-test for expertise differences
+t_test_preva <- t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
+                       y = sri$prevalence_rating[sri$ID == "Novice"])
+
+# Prevalence Rating 
+# effect size for expertise differences
+d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
+                      y = sri$prevalence_rating[sri$ID == "Novice"],
+                      na.rm = TRUE)
+
+round(d_sri_preva, 2)
+
+```
+
+### Situational Jugdement Test
+```{r sjt, echo=FALSE, results='asis'}
+
+# read in data
+df_sjt <- 
+  read_excel("./data/SJT.xlsx")
+
+# select relevant columns --> only subject ID and mean 
+df_sjt <- df_sjt %>%
+  dplyr::select(UI06_05, # ID
+         SJT_AL_gek, # Monitoring
+         SJT_ST_gek, # Managing momentum
+         SJT_R_gek, # Rules and routines
+         SJT_KF_gek) %>% # All
+  filter(!UI06_05 == 201) # exclude ID with no eye tracking data
+
+# remove NAs
+df_sjt <- na.omit(df_sjt)
+
+# rename columns
+df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
+                           "Monitoring" = "SJT_AL_gek",
+                           "Managing momentum" = "SJT_ST_gek",
+                           "Rules and routines" = "SJT_R_gek",
+                           "All" = "SJT_KF_gek"))
+
+# changing from wide to long format
+df_sjt_long <- df_sjt %>% 
+  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")
+
+# define expert and novice with ifelse function
+df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")
+
+#################### N, MEAN & SD ############
+
+# mean & SD SJT ALL
+sjt_mean <- df_sjt_long %>%
+  filter(`Facets Classroom Management` == "All") %>%
+  group_by(Group) %>%
+  summarise(N = n(),
+            "M" = round(mean(Mean), 2),
+            "SD" = round(sd(Mean), 2), 
+            "Min" = round(min(Mean), 2),
+            "Max" = round(max(Mean), 2), 
+            )
+
+# insert a table into HTML
+knitr::kable(sjt_mean,
+             caption = "N, M and SD for overall value")
+
+# mean SJT Managing Momentum
+sjt_mm <- df_sjt_long %>%
+  filter(`Facets Classroom Management` == "Managing momentum") %>%
+  group_by(Group) %>%
+  summarise(N = n(),
+            "M" = round(mean(Mean), 2),
+            "SD" = round(sd(Mean), 2), 
+            "Min" = round(min(Mean), 2),
+            "Max" = round(max(Mean), 2), 
+            )
+
+# insert a table into HTML
+knitr::kable(sjt_mm,
+             caption = "N, M and SD for managing momentum")
+
+# mean SJT Monitoring
+sjt_m <- df_sjt_long %>%
+  filter(`Facets Classroom Management` == "Monitoring") %>%
+  group_by(Group) %>%
+  summarise(N = n(),
+            "M" = round(mean(Mean), 2),
+            "SD" = round(sd(Mean), 2), 
+            "Min" = round(min(Mean), 2),
+            "Max" = round(max(Mean), 2), 
+            )
+
+# insert a table into HTML
+knitr::kable(sjt_mean,
+             caption = "N, M and SD for monitoring")
+
+# mean SJT Rules and routins
+sjt_r <- df_sjt_long %>%
+  filter(`Facets Classroom Management` == "Rules and routines") %>%
+  group_by(Group) %>%
+  summarise(N = n(),
+            "M" = round(mean(Mean), 2),
+            "SD" = round(sd(Mean), 2), 
+            "Min" = round(min(Mean), 2),
+            "Max" = round(max(Mean), 2), 
+            )
+
+# insert a table into HTML
+knitr::kable(sjt_mean,
+             caption = "N, M and SD for rules and routines")
+
+#################### Plots ############
+
+# plotting mean of all aspects 
+mean_plot <- 
+df_sjt_long %>% 
+  mutate(Group = factor(Group,
+                        levels = c("Novice", 
+                                   "Expert")
+                        )
+         ) %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Mean)) +
+  geom_boxplot(mapping = aes(fill = Group), 
+               outlier.shape = NA) +
+  geom_point(size = 1, 
+             alpha = 0.4,
+             position = position_jitter(seed = 1, 
+                                        width = 0.1,
+                                        height = 0.1)) +
+  labs(x = "") +
+  ylim(0,1) + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  facet_wrap(vars(`Facets Classroom Management`), 
+             nrow = 1, strip.position = "bottom") +
+  theme_cowplot() +
+  ggtitle("SJT") +
+    theme(
+    plot.title = element_text(size = 25, 
+                              face = "bold"),
+    legend.title = element_text(size = 20),
+    legend.text = element_text(size = 15),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    strip.text.x = element_text(size = 8),
+    axis.title.y = element_text(size = 20),
+    axis.title.x = element_text(size = 22)
+        )
+
+mean_plot
+
+#################### T-TEST & EFFECT SIZE ##################
+
+# define expert and novice with ifelse function in wide format
+df_sjt$Group = ifelse(df_sjt$Group < 200, "Novice","Expert")
+
+#### ALL #### 
+# t-test for expertise differences 
+t.test(x = df_sjt$All[df_sjt$Group == "Expert"],
+       y = df_sjt$All[df_sjt$Group == "Novice"])
+
+# effect size for expertise differences
+d_sjt_all <- CohenD(x = df_sjt$All[df_sjt$Group == "Expert"],
+                    y = df_sjt$All[df_sjt$Group == "Novice"],
+                    na.rm = TRUE
+                    )
+
+round(d_sjt_all, 2)
+
+#### MANAGING MOMENTUM #### 
+# t-test for expertise differences 
+t.test(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
+       y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"]
+       )
+
+# effect size for expertise differences
+d_sjt_mm <- CohenD(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
+                   y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
+                   na.rm = TRUE
+                  )
+
+round(d_sjt_mm, 2)
+
+#### MONITORING ####
+# t-test for expertise differences 
+t.test(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
+       y = df_sjt$Monitoring[df_sjt$Group == "Novice"]
+       )
+
+# effect size for expertise differences
+d_sjt_moni <- CohenD(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
+                     y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
+                     na.rm = TRUE
+                    )
+
+round(d_sjt_moni, 2)
+
+#### RULES & ROUTINES #### 
+# t-test for expertise differences 
+t.test(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
+       y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"]
+      )
+
+# effect size for expertise differences
+d_sjt_rr <- CohenD(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
+                   y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"],
+                   na.rm = TRUE
+                  )
+
+round(d_sjt_rr, 2)
+
+```
+
+### Classroom Questionnaire
+```{r classroom questionnaire, echo=FALSE, results='asis'}
+
+# load data files with modified scales
+df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  dplyr::select(LI06_05,
+                LM01_01:LM01_08, # classroom management 
+                LP01_01:LP01_08) %>% # non- & paraverbal communication 
+  filter(!LI06_05 == 201) %>% # exclude ID with no eye tracking data
+  mutate(LI06_05 = ifelse(LI06_05 < 200, "Novice", "Expert")) %>% 
+  rename(Group = LI06_05)
+
+# remove NAs
+df_quest <- na.omit(df_quest)
+
+# create table with means
+df_quest_table <-
+  df_quest %>%
+  group_by(Group) %>%
+  transmute(
+    Group = Group,
+    # "N cm" = length(c_across(starts_with("LM")), na.rm = TRUE),
+    "M cm" = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
+    "SD cm" = round(sd(c_across(starts_with("LM")), na.rm = TRUE), 2),
+    "Min cm" = round(min(c_across(starts_with("LM")), na.rm = TRUE), 2),
+    "Max cm" = round(max(c_across(starts_with("LM")), na.rm = TRUE), 2),
+    # "N cm" = length(c_across(starts_with("LP")), na.rm = TRUE),
+    "M n&pv com" = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2),
+    "SD n&pv com" = round(sd(c_across(starts_with("LP")), na.rm = TRUE), 2),
+    "Min n&pv com" = round(min(c_across(starts_with("LP")), na.rm = TRUE), 2),
+    "Max n&pv com" = round(max(c_across(starts_with("LP")), na.rm = TRUE), 2)
+  )
+
+knitr::kable(df_quest_table,
+             caption = "Mean, SD, Min, Max for classroom managament and ")
+
+```
+
+o	2 Skalen: 
+	Classroom Management (5 Items + 3 selbstkonstruiert)
+	Non- & paraverbal Communication (8 Items  abgeleitet aus Theorie (Kiel, Frey & Weiß)

### 2024-08-02 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd

@@
       papaja,
-      grid)
+      grid,
+      purrr)
 ```
@@
 df_regression <- 
-  main_single_hr %>% 
-  filter(time_span != "overall") %>%
-  dplyr::select("ID", "time_span","time","heart_rate_std","heart_rate") %>% 
-  distinct() %>% 
-  mutate(time = time / 60) %>% 
+  main_single_hr |> 
+  filter(time_span != "overall") |> 
+  dplyr::select("ID",
+                "time_span",
+                "time",
+                "heart_rate_std",
+                "heart_rate") |> 
+  distinct() |> 
+  mutate(time = time / 60) |> 
   mutate(ID = as_factor(ID),
          Phase = factor(time_span,
-                           levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
+                        levels = c("preparation",
+                                   "teaching",
+                                   "post",
+                                   "interview",
+                                   "end"),
+                        labels = c("Pre Teaching Phase",
+                                   "Teaching Phase",
+                                   "Post Teaching Phase",
+                                   "Interview Phase",
+                                   "End Phase")
                            )
@@
   arrange(Phase)
+
+table_data$n[table_data$Phase == "Pre Teaching Phase"] <- df_regression %>% filter(Phase == "Pre Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Teaching Phase"] <- df_regression %>% filter(Phase == "Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Post Teaching Phase"] <- df_regression %>% filter(Phase == "Post Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Interview Phase"] <- df_regression %>% filter(Phase == "Interview Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "End Phase"] <- df_regression %>% filter(Phase == "End Phase") %>% pull(heart_rate_std) %>% length()
+
+tab_2 <- apa_table(table_data,
+                   placement = 'h',
+                   label = 'tab_2',
+                   caption = 'Descriptive statistics (n, M, SD) for the mean intercepts and the mean slopes for the five intervals',
+                   note = 'Please note that M and SD of the overall course vs. the individual intervals were not exactly 0 and 1 due to rounding differences.' 
+                   )
+
+writeLines(tab_2, 'tab_2.tex')
+
+```
+
+```{=latex}
+\input{tab_2.tex}
+```

### 2024-08-02 02_paper/02_study/01_fitbit paper/Submission/tab_1.tex

@@
 
-\caption{\label{tab:table_1}Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)}
+\caption{Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)}
 
@@
 Teaching interval & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39\\
-Post-teaching interval & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06\\
+Post-teaching interval & 93.61/0.27 & 14.02/0.76 & 60/-2.17 & 150/3.06\\
 Interview interval & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24\\
-End Interval & 100.8/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37\\
+End Interval & 100.8/0.85 & 16.24/0.77 & 63/-2.18 & 164/4.37\\
 \bottomrule

### 2024-08-02 02_paper/02_study/01_fitbit paper/analysis_270423.Rmd
fb

--- 2024-06-06 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
@@
   filter(!is.na(confidence_factor),
-         !is.na(disruption_factor)) %>% 
+         !is.na(disruption_factor),
+         !ID %in% c("126",
+                    "132",
+                    "236")
+         ) %>% 
    summarise(N = n_distinct(ID), 
@@
 
+# Mean, SD and range for teaching experience
+demo_table <-
+  df_demo %>% 
+  filter(!ID %in% c("126",
+                    "132",
+                    "236"
+                    )
+         ) %>% 
+  summarise(N = n(),
+            "M teaching experience" = round(mean(teaching_experience),
+                                            digits = 2),
+            "SD teaching experience" = round(sd(teaching_experience),
+                                             digits = 2),
+            "Min teaching experience" = min(teaching_experience),
+            "Max teaching experience" = max(teaching_experience),
+            )
 ```
@@
 ```
+
 ## Teaching vs. Pre-Teaching (mean HR)
-
 ```{r}
@@
 ## Teaching vs. Post-Teaching (mean HR)
-
 ```{r}
@@
 ## Teaching vs. Interview (mean HR)
-
 ```{r}
@@
 model2 <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
-summary(model2)
+(model2)
 

### 2024-08-02 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
fb

@@
   group_by(Group) %>%
-  transmute(
-    Group = Group,
-    # "N cm" = length(c_across(starts_with("LM")), na.rm = TRUE),
-    "M cm" = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
-    "SD cm" = round(sd(c_across(starts_with("LM")), na.rm = TRUE), 2),
-    "Min cm" = round(min(c_across(starts_with("LM")), na.rm = TRUE), 2),
-    "Max cm" = round(max(c_across(starts_with("LM")), na.rm = TRUE), 2),
+  summarise(
+    N = n(),
+    "M cm" = round(mean(c_across(starts_with(
+      "LM"
+    )), na.rm = TRUE), 2),
+    "SD cm" = round(sd(c_across(starts_with(
+      "LM"
+    )), na.rm = TRUE), 2),
+    "Min cm" = round(min(c_across(starts_with(
+      "LM"
+    )), na.rm = TRUE), 2),
+    "Max cm" = round(max(c_across(starts_with(
+      "LM"
+    )), na.rm = TRUE), 2),
     # "N cm" = length(c_across(starts_with("LP")), na.rm = TRUE),
-    "M n&pv com" = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2),
-    "SD n&pv com" = round(sd(c_across(starts_with("LP")), na.rm = TRUE), 2),
-    "Min n&pv com" = round(min(c_across(starts_with("LP")), na.rm = TRUE), 2),
-    "Max n&pv com" = round(max(c_across(starts_with("LP")), na.rm = TRUE), 2)
+    "M n&pv com" = round(mean(c_across(starts_with(
+      "LP"
+    )), na.rm = TRUE), 2),
+    "SD n&pv com" = round(sd(c_across(starts_with(
+      "LP"
+    )), na.rm = TRUE), 2),
+    "Min n&pv com" = round(min(c_across(starts_with(
+      "LP"
+    )), na.rm = TRUE), 2),
+    "Max n&pv com" = round(max(c_across(starts_with(
+      "LP"
+    )), na.rm = TRUE), 2)
   )

### 2024-08-05 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
Tabellen und so Sachen

--- 2024-07-30 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
@@
   - \usepackage{booktabs}
+  - \usepackage{array}
+  - \usepackage{caption}
+  - \usepackage{tablefootnote}
 ---
@@
 ```{=latex}
-\input{tab_1.tex}
+
+\renewcommand{\arraystretch}{1.5}
+
+\begin{table}[ht]
+    \centering
+    \begin{tabularx}{\textwidth}{lXXXXX}
+        \toprule
+        Interval & \textit{M HR} & \textit{SD HR} & Min & Max \\
+        \midrule
+        Overall Course of 2h & 90.09/0.04\tablefootnote{Please note that standardized M and SD of the overall course were not exactly 0 and 1 due to rounding differences} & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
+        Pre-teaching interval ($I_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
+        Teaching interval ($I_2$) & 100.80/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\
+        Post-teaching interval ($I_3$) & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\
+        Interview interval ($I_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
+        End interval $I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\tablefootnote{Deviations of the minimum values in the overall course vs. the end interval ($I_5$) are due to data of a few participants who
+        needed more than two hours to finish the study.}/-2.68 & 120/2.96 \\
+        \bottomrule
+    \end{tabularx}
+    \caption{Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
+    \label{tab_1}
+\end{table}
 ```
@@
 
-```{r}
+```{r box plot, include=FALSE}
 box_plot <-
@@
 
-```{r}
+```{r table_2, include=FALSE}
 df_regression <- 
-  main_single_hr %>% 
-  filter(time_span != "overall") %>%
-  dplyr::select("ID", "time_span","time","heart_rate_std","heart_rate") %>% 
-  distinct() %>% 
-  mutate(time = time / 60) %>% 
+  main_single_hr |> 
+  filter(time_span != "overall") |> 
+  dplyr::select("ID",
+                "time_span",
+                "time",
+                "heart_rate_std",
+                "heart_rate") |> 
+  distinct() |> 
+  mutate(time = time / 60) |> 
   mutate(ID = as_factor(ID),
          Phase = factor(time_span,
-                           levels = c("preparation","teaching","post","interview","end"),
-                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
+                        levels = c("preparation",
+                                   "teaching",
+                                   "post",
+                                   "interview",
+                                   "end"),
+                        labels = c("Pre Teaching Phase",
+                                   "Teaching Phase",
+                                   "Post Teaching Phase",
+                                   "Interview Phase",
+                                   "End Phase")
                            )
@@
   arrange(Phase)
+
+table_data$n[table_data$Phase == "Pre Teaching Phase"] <- df_regression %>% filter(Phase == "Pre Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Teaching Phase"] <- df_regression %>% filter(Phase == "Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Post Teaching Phase"] <- df_regression %>% filter(Phase == "Post Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Interview Phase"] <- df_regression %>% filter(Phase == "Interview Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "End Phase"] <- df_regression %>% filter(Phase == "End Phase") %>% pull(heart_rate_std) %>% length()
+```
+
+```{=latex}
+
+\renewcommand{\arraystretch}{1.5}
+
+\begin{table}[ht]
+    \centering
+    \begin{tabularx}{\textwidth}{lXXXXX}
+        \toprule
+        Interval & n\tablefootnote{All measurement points per interval for all participants.
+Note that the variation in $n$ stems from the variation in the number of collected data points by the fitness tracker.} & \multicolumn{2}{c}{\textit{M (SD)}} & \multicolumn{2}{c}{$p$} \\
+        & & Intercept & Slope & Intercept & Slope \\
+        \midrule
+        (1) Pre-teaching interval & 6896 & 0.052  & 0.085*  & .57 & $<$ .05 \\
+        & & (0.820) & (0.133) & & \\
+        (2) Teaching interval & 7150 & 1.025* & -0.039* & $<$ .05 & $<$ .05 \\
+        & & (0.690) & (0.108) & & \\
+        (3) Post-teaching interval & 6664 & 0.549* & -0.060* & $<$ .05 & $<$ .05 \\
+        & & (0.547) & (0.101) & & \\
+        (4) Interview interval & 6287 & -0.617* & -0.022 & $<$ .05 & .006 \\
+        & & (0.614) & (0.070) & & \\
+        (5) End interval & 5990 & -1.004* & -0.012 & $<$ .05 & .14 \\
+        & & (0.500) & (0.074) & & \\
+        \bottomrule \\
+        Note. * $p < .05$
+    \end{tabularx}
+    \caption{Descriptive statistics (n, M, SD) for the mean intercepts and the mean slopes for the five intervals.}
+    \label{tab_2}
+\end{table}
+
+```

### 2024-08-05 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
blaaaa

@@
 
-## Participants
+## 1. Participants
 ```{r demographicstable, include = TRUE, echo=FALSE}
@@
 
-## Measures
+## 2. Measures
 
-### Eye-Tracking Data
-```{r eyetracking, include = TRUE, echo=FALSE}
+### 2.1 Eye-Tracking Data
+
+1. Number of fixation, Fixation duration, GRI 
+- Alles (gesamte Lektion), students (gesamte Lektion)
+- disruptive person (tatsächliche Dauer der Störung)
+
+2. Time to first fixation
+- disruptive person (tatsächliche Dauer der Störung)
+
+```{r eyetracking_read_in_data, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
 
@@
                    Participant,
+                   TOI,
                    starts_with("Total_duration_of_fixations"),
-                   starts_with("Number_of_fixations")
+                   starts_with("Number_of_fixations"),
+                   starts_with("Time_to_first_fixation")
      )
@@
 
-#### Fixation count & fixation duration (M, SD, Effektstärke)
-•	Alles (gesamte Lektion), students (gesamte Lektion)
-•	disruptive person (tatsächliche Dauer der Störung)
+XXX 223 & 232 sind fehlerhaft --> Daten nochmal komplett neu ziehen!! XXX
 
-#### Time to first fixation 
-•	disruptive person (tatsächliche Dauer der Störung)
+#### 2.2.1 Number of fixation in entire micro-teaching unit
+```{r nof_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-### Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
-```{r rating_scales, echo=FALSE, results='asis'}
+##################### NUMBER OF FIXATION ON ALL AOIS ########################
+
+# filter group & total duration & number fixation on all AOIs
+df_aoi %>% 
+  filter(TOI == "Lesson") %>% 
+  dplyr::select (Group,
+          Participant,
+          starts_with("Total_duration_of_fixations"),
+          starts_with("Number_of_fixations"),
+          !"Total_duration_of_fixations.Disruptive_Person",
+          !"Number_of_fixations.Disruptive_Person") %>% 
+  rowwise() %>% 
+  transmute(Group = Group,
+            Participant = Participant,
+            Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
+                                                    ),
+                                           na.rm = TRUE
+                                           ),
+            Sum_number_fixation = sum(c_across(starts_with("Number_of")
+                                                  ),
+                                         na.rm = TRUE
+                                         )
+            ) %>% 
+  mutate(Average_duration = round(Sum_duration_fixation/Sum_number_fixation,
+                                         digits = 0),
+         Group = as_factor(Group)) %>% 
+  drop_na() -> df_aoi_sum
+
+# N, M, SD, min & max number of fixation (ent)
+nof.table <-
+  df_aoi_sum %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Sum_number_fixation), digits = 2),
+    "SD" = round(sd(Sum_number_fixation), digits = 2),
+    "Min" = round(min(Sum_number_fixation), digits = 2),
+    "Max" = round(max(Sum_number_fixation), digits = 2)
+    )
+
+knitr::kable(nof.table,
+             caption = "N, M, SD, min & max number of fixation in entire micro-teaching unit")
+
+# plotting number of fixations on ALL AOIS
+df_aoi_sum %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Sum_number_fixation)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  labs(x ="",
+       y = "Number of fixation") +
+  scale_fill_brewer(palette  = "RdBu") +  
+  ggtitle("Number of fixation\n(micro-teaching unit)") +
+  theme_cowplot() +
+  theme(legend.position="none") -> plot_number_group
+
+plot_number_group
+
+```
+
+#### t-test & effect size "Number of fixation in entire micro-teaching unit"
+```{r nof_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# NUMBER OF FIXATIONS on all AOIs 
+# t-test for expertise differences
+t.test(x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
+       y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
+       var.equal = TRUE)
+
+# NUMBER OF FIXATIONS on all AOIs
+# effect size for expertise differences
+d_number_all <- CohenD(x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
+                       y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
+                       na.rm = TRUE)
+round(d_number_all, 2)
+
+```
+
+#### 2.2.2 Number of fixations on AOI "Students" during entire micro-teaching unit
+```{r nof_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### NUMBER OF FIXATIONS ON AOI STUDENTS ########################
+
+# filter group & total duration & number fixation on AOI Students
+df_aoi %>% 
+  filter(TOI == "Lesson") %>% 
+  dplyr::select (Group,
+                 Participant,
+                 "Total_duration_of_fixations.Anna",
+                 "Total_duration_of_fixations.Bianca",
+                 "Total_duration_of_fixations.Carl(a)",
+                 "Number_of_fixations.Anna",
+                 "Number_of_fixations.Bianca",
+                 "Number_of_fixations.Carl(a)") %>% 
+  rowwise() %>% 
+  transmute(Group = Group,
+            Participant = Participant, 
+            Stud_duration_fixation = sum(c_across(starts_with("Total_duration")
+                                                 ),
+                                         na.rm = TRUE
+                                         ),
+            Stud_number_fixation = sum(c_across(starts_with("Number_of")
+                                                ),
+                                       na.rm = TRUE
+                                       )
+            ) %>% 
+  mutate(Average_duration_stud = round(Stud_duration_fixation/Stud_number_fixation, 
+                                  digits = 0),
+         Group = as_factor(Group)
+         ) -> df_aoi_stud
+
+# N, M, SD, min & max number of fixation on AOI students
+nof.stud.table <-
+  df_aoi_stud %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Stud_number_fixation), digits = 2),
+    "SD" = round(sd(Stud_number_fixation), digits = 2),
+    "Min" = round(min(Stud_number_fixation), digits = 2),
+    "Max" = round(max(Stud_number_fixation), digits = 2)
+    )
+
+knitr::kable(nof.stud.table,
+             caption = "N, M, SD, min & max number of fixation on AOI students (entire micro-teaching unit)")
+
+# plotting average duration on AOI Students
+df_aoi_stud %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Stud_number_fixation)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  labs(x ="",
+       y = "Number of fixation") + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  ggtitle("Number of fixation on AOI\n`Students` (micro-teaching unit)") +
+  theme_cowplot() +
+  theme(legend.position="none") -> plot_number_stud
+
+plot_number_stud
+
+```
+
+#### t-test & effect size "Number of fixation on AOI students"
+```{r nof_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# NUMBER OF FIXATIONS on AOI students 
+# t-test for expertise differences
+t.test(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
+       y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
+       var.equal = TRUE)
+
+# NUMBER OF FIXATIONS on AOI students
+# effect size for expertise differences
+d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
+                      y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
+                      na.rm = TRUE)
+
+round(d_number_stud, 2)
+
+```
+
+#### 2.2.3 Average duration in entire micro-teaching unit
+```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### AVERAGE DURATION ########################
+
+# N, M, SD, min & max average duration (entire micro-teaching unit)
+dur.table <-
+  df_aoi_sum %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Average_duration), digits = 2),
+    "SD" = round(sd(Average_duration), digits = 2),
+    "Min" = round(min(Average_duration), digits = 2),
+    "Max" = round(max(Average_duration), digits = 2)
+    )
+
+knitr::kable(dur.table,
+             caption = "N, M, SD, min & max average duration in entire micro-teaching unit")
+
+# plotting average duration on ALL AOIS
+df_aoi_sum %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Average_duration)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  labs(x ="",
+       y = "Milliseconds") + 
+  scale_fill_brewer(palette  = "RdBu") + 
+  ggtitle("Average duration \n(micro-teaching unit)") +
+  theme_cowplot() +
+  theme(legend.position="none") -> plot_average_duration_group
+
+plot_average_duration_group
+
+```
+
+#### t-test & effect size "Average duration in entire micro-teaching unit"
+```{r dur_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# AVERAGE DURATION OF FIXATIONS on all AOIs 
+# t-test for expertise differences
+t.test(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
+       y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
+       var.equal = TRUE)
+
+# AVERAGE DURATION OF FIXATIONS on all AOIs
+# effect size for expertise differences
+d_aver_all <- CohenD(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
+                     y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
+                    na.rm = TRUE)
+round(d_aver_all, 2)
+
+```
+
+#### 2.2.4 Average duration on AOI students
+```{r dur_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### AVERAGE DURATION ON AOI STUDENTS ########################
+
+# filter group & total duration & number fixation on AOI Students
+df_aoi %>% 
+  filter(TOI == "Lesson") %>% 
+  dplyr::select (Group,
+          "Total_duration_of_fixations.Anna",
+          "Total_duration_of_fixations.Bianca",
+          "Total_duration_of_fixations.Carl(a)",
+          "Number_of_fixations.Anna",
+          "Number_of_fixations.Bianca",
+          "Number_of_fixations.Carl(a)") %>% 
+  rowwise() %>% 
+  transmute(Group = Group,
+            Stud_duration_fixation = sum(c_across(starts_with("Total_duration")
+                                                 ),
+                                         na.rm = TRUE
+                                         ),
+            Stud_number_fixation = sum(c_across(starts_with("Number_of")
+                                                ),
+                                       na.rm = TRUE
+                                       )
+            ) %>% 
+  mutate(Average_duration_stud = round(Stud_duration_fixation/Stud_number_fixation, 
+                                  digits = 0),
+         Group = as_factor(Group)) -> df_aoi_stud
+
+# N, M, SD, min & max average duration on AOI students
+dur.stud.table <-
+  df_aoi_stud %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Average_duration_stud), digits = 2),
+    "SD" = round(sd(Average_duration_stud), digits = 2),
+    "Min" = round(min(Average_duration_stud), digits = 2),
+    "Max" = round(max(Average_duration_stud), digits = 2)
+    )
+
+knitr::kable(dur.stud.table,
+             caption = "N, M, SD, min & max average duration on AOI students")
+
+# plotting average duration on AOI Students
+df_aoi_stud %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Average_duration_stud)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
+  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
+  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
+  #                                  )
+  #                  ) +
+  labs(x ="",
+       y = "Millisekunden") + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  scale_x_discrete(labels=c("Novice" = "Unerfahren",
+                            "Expert" = "Erfahren")) +
+  ggtitle("Ø Fixationsdauer AOI\n `Schüler:innen`") +
+  theme_cowplot() +
+  theme(legend.position="none",
+        axis.text.x = element_text(size = 34),
+        axis.text.y = element_text(size = 18),
+        axis.title = element_text(size = 34),
+        plot.title = element_text(size = 35, 
+                                  face = "bold")
+  ) -> plot_average_duration_stud
+
+plot_average_duration_stud
+```
+
+#### t-test & effect size "Average duration on AOI students"
+```{r dur_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# AVERAGE DURATION OF FIXATIONS on AOI Students 
+# t-test for expertise differences
+t.test(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
+       y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+       var.equal = TRUE)
+
+# AVERAGE DURATION OF FIXATIONS on AOI Students
+# effect size for expertise differences
+d_aver_stud <- CohenD(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
+                      y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+                      na.rm = TRUE)
+
+```
+
+#### t-test & effect size "Average duration on AOI students"
+```{r dur_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# AVERAGE DURATION OF FIXATIONS on all AOIs 
+# t-test for expertise differences
+t.test(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
+       y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
+       var.equal = TRUE)
+
+# AVERAGE DURATION OF FIXATIONS on all AOIs
+# effect size for expertise differences
+d_aver_all <- CohenD(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
+                     y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
+                    na.rm = TRUE)
+round(d_aver_all, 2)
+
+```
+
+### 2.2 Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
+```{r rating_scales, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 dist_group_plot
+```
+
+#### t-Test & effect size "Disruption appraisal"
+```{r sri_da_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 # t-test for expertise differences
-t_test_disrup <- t.test(x = sri$disruption_appraisal[sri$ID == "Expert"],
-                        y = sri$disruption_appraisal[sri$ID == "Novice"])
+t.test(x = sri$disruption_appraisal[sri$ID == "Expert"],
+       y = sri$disruption_appraisal[sri$ID == "Novice"],
+       var.equal = TRUE)
 
@@
 round(d_sri_disrup, 2)
+```
+
+```{r sri_ca, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 confi_group_plot
+```
+
+#### t-Test & effect size "Confidence appraisal"
+```{r sri_ca_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 # t-test for expertise differences
-t_test_confi <- t.test(x = sri$confidence_appraisal[sri$ID == "Expert"],
-                       y = sri$confidence_appraisal[sri$ID == "Novice"])
+t.test(x = sri$confidence_appraisal[sri$ID == "Expert"],
+       y = sri$confidence_appraisal[sri$ID == "Novice"],
+       var.equal = TRUE)
 
@@
 round(d_sri_confi, 2)
+```
+
+```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 
+```
+
+#### t-Test & effect size "Prevalence rating"
+```{r sri_pr_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
 #################### T-TEST & EFFECT SIZE ############
@@
 # t-test for expertise differences
-t_test_preva <- t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
-                       y = sri$prevalence_rating[sri$ID == "Novice"])
+t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
+       y = sri$prevalence_rating[sri$ID == "Novice"],
+       var.equal = TRUE)
 
@@
 
-### Situational Jugdement Test
-```{r sjt, echo=FALSE, results='asis'}
+### 2.3 Situational Jugdement Test
+```{r sjt, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 mean_plot
+```
 
+#### t-test & effect size "STJ - All"
+```{r sjt_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 #################### T-TEST & EFFECT SIZE ##################
@@
 t.test(x = df_sjt$All[df_sjt$Group == "Expert"],
-       y = df_sjt$All[df_sjt$Group == "Novice"])
+       y = df_sjt$All[df_sjt$Group == "Novice"],
+       var.equal = TRUE)
 
@@
 
+```
+
+#### t-test & effect size "SJT - Managing momentum"
+```{r sjt_mm, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
 #### MANAGING MOMENTUM #### 
@@
 t.test(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
-       y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"]
+       y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
+       var.equal = TRUE
        )
@@
 round(d_sjt_mm, 2)
+```
+
+#### t-test & effect size "SJT - Monitoring"
+```{r sjt_m, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 t.test(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
-       y = df_sjt$Monitoring[df_sjt$Group == "Novice"]
+       y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
+       var.equal = TRUE
        )
@@
 round(d_sjt_moni, 2)
+```
+
+#### t-test & effect size "SJT - Rules & routines"
+```{r sjt_rr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 t.test(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
-       y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"]
+       y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"],
+       var.equal = TRUE
       )
@@
 
-### Classroom Questionnaire
+### 2.4 Classroom Questionnaire
 ```{r classroom questionnaire, echo=FALSE, results='asis'}
@@
 knitr::kable(df_quest_table,
-             caption = "Mean, SD, Min, Max for classroom managament and ")
+             caption = "Mean, SD, min, max for classroom managament (cm) and non-/paraverbal communication (n&pv com)")
+
+#################### Plots ############
+
+# create table with means
+df_quest_plot <-
+  df_quest %>%
+  rowwise() %>% 
+  transmute(Group = Group,
+            "All" = round(mean(c_across(starts_with("L")), na.rm = TRUE), 2),
+            "Classroom management" = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
+            "Non-/paraverbal communication" = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2)
+            )
+
+# changing from wide to long format
+df_quest_long <- df_quest_plot %>% 
+  pivot_longer(!Group, names_to = "Scales Classroom Questionnaire", values_to = "Mean")
+
+# plotting mean of all aspects 
+quest_plot <- 
+df_quest_long %>% 
+  mutate(Group = factor(Group,
+                        levels = c("Novice", 
+                                   "Expert")
+                        )
+         ) %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Mean)) +
+  geom_boxplot(mapping = aes(fill = Group), 
+               outlier.shape = NA) +
+  geom_point(size = 1, 
+             alpha = 0.4,
+             position = position_jitter(seed = 1, 
+                                        width = 0.1,
+                                        height = 0.1)) +
+  labs(x = "") +
+  ylim(0,4) + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  facet_wrap(vars(`Scales Classroom Questionnaire`), 
+             nrow = 1, strip.position = "bottom") +
+  theme_cowplot() +
+  ggtitle("Classroom Questionnaire") +
+    theme(
+    plot.title = element_text(size = 25, 
+                              face = "bold"),
+    legend.title = element_text(size = 20),
+    legend.text = element_text(size = 15),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    strip.text.x = element_text(size = 8),
+    axis.title.y = element_text(size = 20),
+    axis.title.x = element_text(size = 22)
+        )
+
+quest_plot
+```
+
+#### t-test & effect size "Classroom Questionnaire - All"
+```{r classroom questionnaire_all, echo=FALSE, results='asis'}
+
+#################### T-TEST & EFFECT SIZE ##################
+
+#### All #### 
+# t-test for expertise differences 
+t.test(x = df_quest_plot$All[df_quest_plot$Group == "Expert"],
+       y = df_quest_plot$All[df_quest_plot$Group == "Novice"],
+       var.equal = TRUE
+       )
+
+# effect size for expertise differences
+d_quest_all <- CohenD(x = df_quest_plot$All[df_quest_plot$Group == "Expert"],
+                      y = df_quest_plot$All[df_quest_plot$Group == "Novice"],
+                      na.rm = TRUE
+                      )
+
+round(d_quest_all, 2)
 
@@
 
-o	2 Skalen: 
-	Classroom Management (5 Items + 3 selbstkonstruiert)
-	Non- & paraverbal Communication (8 Items  abgeleitet aus Theorie (Kiel, Frey & Weiß)
+#### t-test & effect size "Classroom Questionnaire - Classroom Management"
+```{r classroom questionnaire_cm, echo=FALSE, results='asis'}
+
+#### Classroom Management #### 
+# t-test for expertise differences 
+t.test(x = df_quest_plot$`Classroom management`[df_quest_plot$Group == "Expert"],
+       y = df_quest_plot$`Classroom management`[df_quest_plot$Group == "Novice"],
+       var.equal = TRUE)
+
+# effect size for expertise differences
+d_quest_cm <- CohenD(x = df_quest_plot$`Classroom management`[df_quest_plot$Group == "Expert"],
+                      y = df_quest_plot$`Classroom management`[df_quest_plot$Group == "Novice"],
+                      na.rm = TRUE
+                      )
+
+round(d_quest_cm, 2)
+```
+
+#### t-test & effect size "Classroom Questionnaire - Non-/paraverbal communication"
+```{r classroom questionnaire_npvc, echo=FALSE, results='asis'}
+
+#### Non-/paraverbal communication #### 
+# t-test for expertise differences 
+t.test(x = df_quest_plot$`Non-/paraverbal communication`[df_quest_plot$Group == "Expert"],
+       y = df_quest_plot$`Non-/paraverbal communication`[df_quest_plot$Group == "Novice"],
+       var.equal = TRUE)
+
+# effect size for expertise differences
+d_quest_npvc <- CohenD(x = df_quest_plot$`Non-/paraverbal communication`[df_quest_plot$Group == "Expert"],
+                      y = df_quest_plot$`Non-/paraverbal communication`[df_quest_plot$Group == "Novice"],
+                      na.rm = TRUE
+                      )
+
+round(d_quest_npvc, 2)
+
+```

### 2024-08-05 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex

@@
 \usepackage{booktabs}
+\usepackage{array}
+\usepackage{caption}
+\usepackage{tablefootnote}
 
@@
 
-\input{tab_1.tex}
+\renewcommand{\arraystretch}{1.5}
+
+\begin{table}[ht]
+    \centering
+    \begin{tabularx}{\textwidth}{lXXXXX}
+        \toprule
+        Interval & \textit{M HR} & \textit{SD HR} & Min & Max \\
+        \midrule
+        Overall Course of 2h & 90.09/0.04\tablefootnote{Please note that standardized M and SD of the overall course were not exactly 0 and 1 due to rounding differences} & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
+        Pre-teaching interval ($I_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
+        Teaching interval ($I_2$) & 100.80/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\
+        Post-teaching interval ($I_3$) & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\
+        Interview interval ($I_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
+        End interval $I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\tablefootnote{Deviations of the minimum values in the overall course vs. the end interval ($I_5$) are due to data of a few participants who
+        needed more than two hours to finish the study.}/-2.68 & 120/2.96 \\
+        \bottomrule
+    \end{tabularx}
+    \caption{Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
+    \label{tab_1}
+\end{table}
 
@@
 
-\begin{verbatim}
-## `summarise()` has grouped output by 'ID'. You can override using the `.groups`
-## argument.
-\end{verbatim}
-
 \begin{figure}[htbp]
@@
 
-\input{tab_2.tex}
+\renewcommand{\arraystretch}{1.5}
 
-```
+\begin{table}[ht]
+    \centering
+    \begin{tabularx}{\textwidth}{lXXXXX}
+        \toprule
+        Interval & n\tablefootnote{All measurement points per interval for all participants.
+Note that the variation in $n$ stems from the variation in the number of collected data points by the fitness tracker.} & \multicolumn{2}{c}{\textit{M (SD)}} & \multicolumn{2}{c}{$p$} \\
+        & & Intercept & Slope & Intercept & Slope \\
+        \midrule
+        (1) Pre-teaching interval & 6896 & 0.052  & 0.085*  & .57 & $<$ .05 \\
+        & & (0.820) & (0.133) & & \\
+        (2) Teaching interval & 7150 & 1.025* & -0.039* & $<$ .05 & $<$ .05 \\
+        & & (0.690) & (0.108) & & \\
+        (3) Post-teaching interval & 6664 & 0.549* & -0.060* & $<$ .05 & $<$ .05 \\
+        & & (0.547) & (0.101) & & \\
+        (4) Interview interval & 6287 & -0.617* & -0.022 & $<$ .05 & .006 \\
+        & & (0.614) & (0.070) & & \\
+        (5) End interval & 5990 & -1.004* & -0.012 & $<$ .05 & .14 \\
+        & & (0.500) & (0.074) & & \\
+        \bottomrule \\
+        Note. * $p < .05$
+    \end{tabularx}
+    \caption{Descriptive statistics (n, M, SD) for the mean intercepts and the mean slopes for the five intervals.}
+    \label{tab_2}
+\end{table}
 

### 2024-08-06 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
tabeleln und so

@@
 ```
+
+## Research goal 2: Prediction of mean standardized HR and mean slopes with teaching experience and subjective appraisals
+
+Correlations among mean standardized HR/mean slopes (see Table 2), teaching experience (M = 5.64, SD = 9.46), disruption appraisal (M = 5.19, SD = 2.87), and confidence appraisal (M = 7.81, SD = 1.97) are presented in Table 3.
+Correlations between mean standardized HR/mean slopes and the other variables were mostly very small and statistically non-significant, except for the pre-teaching interval (I1), in which mean slope and teaching experience correlated negatively (r=-.27), and the interview interval (I4) in which mean HR and teaching experience correlated positively (r=.24).
+Correlations between teaching experience and appraisals were substantial: more experienced teachers had lower disruption appraisals (r=-.36), and higher confidence appraisals (r=.44).
+Moreover, the two appraisal variables were negatively correlated (r=-.37).
+
+Concerning the effect of teaching experience on participants’ HR levels (i.e., mean standardized HR) for each of the five intervals, teaching experience significantly predicted mean standardized HR only in the interview interval (Table 4, Interview interval, Model 1), indicating a higher mean standardized HR for teachers with more teaching experience.
+This relationship is, in fact, in the opposite direction as predicted by Hypothesis 2a.
+
+Neither adding disruption appraisal (**Hypothesis 2b**) nor adding confidence appraisal (**Hypothesis 2c**) while controlling for the shared variance with teaching experience revealed significant effects on teachers’ mean standardized HR.
+
+When considering the effects of the three predictors in concert (**Hypothesis 2d**), mean standardized HR was significantly predicted only by disruption appraisal, and only in the post-teaching interval (Table 4, Post-teaching interval, Model 4), indicating a higher mean standardized HR for teachers who felt more disrupted by the classroom events, when controlling for the other variables.
+
+Concerning the explorative investigation of the effects of teaching experience and subjective appraisals on changes (i.e., mean slopes) in teachers’ HR, teaching experience significantly predicted the mean slope in the pre-teaching interval (Table 4, Pre-teaching interval, Model 1), indicating a less steep HR increase in teachers with more teaching experience.
+For all other intervals, no variable revealed a significant prediction.
+
+```{=latex}
+
+\renewcommand{\arraystretch}{1.5}
+
+\begin{table}[ht]
+    \centering
+    \begin{tabularx}{\textwidth}{lccccc}
+        \toprule
+        Variable & Pre-teaching & Teaching & Post-teaching & Interview & End \\
+        & interval & interval & interval & interval & interval \\
+        \midrule
+        Teaching Experience & $- .17/ - .27^*$ & .11/-.02 & $- .04/-.03$ & $.24^*/-.20$ & .04/.11 \\
+        Disruption Appraisal & $- .01/.16$ & $- .20/.08$ & .20/$- .14$ & $- .13/.01$ & .04/.12 \\
+        Confidence Appraisal & $- .10/ - .18$ & .06/.09 & .04/$- .03$ & .09/$- .19$ & $- .07/.13$ \\
+        \bottomrule \\
+          Note. * $p < .05$.
+    \end{tabularx}
+    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
+    \label{tab_3}
+\end{table}
+
+```

### 2024-08-06 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
tabeleln und so

@@
 
+\subsection{Research goal 2: Prediction of mean standardized HR and mean
+slopes with teaching experience and subjective
+appraisals}\label{research-goal-2-prediction-of-mean-standardized-hr-and-mean-slopes-with-teaching-experience-and-subjective-appraisals}
+
+Correlations among mean standardized HR/mean slopes (see Table 2),
+teaching experience (M = 5.64, SD = 9.46), disruption appraisal (M =
+5.19, SD = 2.87), and confidence appraisal (M = 7.81, SD = 1.97) are
+presented in Table 3. Correlations between mean standardized HR/mean
+slopes and the other variables were mostly very small and statistically
+non-significant, except for the pre-teaching interval (I1), in which
+mean slope and teaching experience correlated negatively (r=-.27), and
+the interview interval (I4) in which mean HR and teaching experience
+correlated positively (r=.24). Correlations between teaching experience
+and appraisals were substantial: more experienced teachers had lower
+disruption appraisals (r=-.36), and higher confidence appraisals
+(r=.44). Moreover, the two appraisal variables were negatively
+correlated (r=-.37).
+
+Concerning the effect of teaching experience on participants' HR levels
+(i.e., mean standardized HR) for each of the five intervals, teaching
+experience significantly predicted mean standardized HR only in the
+interview interval (Table 4, Interview interval, Model 1), indicating a
+higher mean standardized HR for teachers with more teaching experience.
+This relationship is, in fact, in the opposite direction as predicted by
+Hypothesis 2a.
+
+Neither adding disruption appraisal (\textbf{Hypothesis 2b}) nor adding
+confidence appraisal (\textbf{Hypothesis 2c}) while controlling for the
+shared variance with teaching experience revealed significant effects on
+teachers' mean standardized HR.
+
+When considering the effects of the three predictors in concert
+(\textbf{Hypothesis 2d}), mean standardized HR was significantly
+predicted only by disruption appraisal, and only in the post-teaching
+interval (Table 4, Post-teaching interval, Model 4), indicating a higher
+mean standardized HR for teachers who felt more disrupted by the
+classroom events, when controlling for the other variables.
+
+Concerning the explorative investigation of the effects of teaching
+experience and subjective appraisals on changes (i.e., mean slopes) in
+teachers' HR, teaching experience significantly predicted the mean slope
+in the pre-teaching interval (Table 4, Pre-teaching interval, Model 1),
+indicating a less steep HR increase in teachers with more teaching
+experience. For all other intervals, no variable revealed a significant
+prediction.
+
+\renewcommand{\arraystretch}{1.5}
+
+\begin{table}[ht]
+    \centering
+    \begin{tabularx}{\textwidth}{lccccc}
+        \toprule
+        Variable & Pre-teaching & Teaching & Post-teaching & Interview & End \\
+        & interval & interval & interval & interval & interval \\
+        \midrule
+        Teaching Experience & $- .17/ - .27^*$ & .11/-.02 & $- .04/-.03$ & $.24^*/-.20$ & .04/.11 \\
+        Disruption Appraisal & $- .01/.16$ & $- .20/.08$ & .20/$- .14$ & $- .13/.01$ & .04/.12 \\
+        Confidence Appraisal & $- .10/ - .18$ & .06/.09 & .04/$- .03$ & .09/$- .19$ & $- .07/.13$ \\
+        \bottomrule \\
+          Note. * $p < .05$.
+    \end{tabularx}
+    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
+    \label{tab_3}
+\end{table}
+
 \bibliography{r-references.bib}

### 2024-08-06 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
Noch mehr Tabellen

@@
   - \usepackage{tablefootnote}
+  - \usepackage{float}
+  - \usepackage{wrapfig}
+  - \usepackage{pdflscape}
+  - \usepackage{longtable}
 ---
@@
 ```{=latex}
-\begin{figure}[htbp]
+\begin{wrapfigure}{r}{0.5\textwidth}
   \centering
-  \includegraphics[width=1\textwidth]{images/Timeline.pdf}
+  \includegraphics[width=0.5\textwidth]{images/Timeline_small.pdf}
   \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
   \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
-\end{figure}
+\end{wrapfigure}
 ```
@@
 ```{=latex}
-\begin{figure}[htbp]
+\begin{figure}[H]
   \centering
@@
 
+```{r correlations, include=FALSE}
+
+main <-
+map(.x = dir(path = data_path,
+             pattern = ".csv"),
+    ~ read_csv(file.path(data_path, .), 
+               id = "id",
+               col_types = c("t","n")
+               ) %>% 
+  mutate(time = .$Time - min(.$Time),
+         time = as.numeric(time),
+         heart_rate = `Heart Rate`,
+         ID = id,
+         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
+                               str_detect(string = id, pattern = "_m") ~ "teaching",
+                               str_detect(string = id, pattern = "_p") ~ "preparation",
+                               str_detect(string = id, pattern = "_s") ~ "post",
+                               str_detect(string = id, pattern = "_i") ~ "interview",
+                               TRUE ~ "overall"
+                               ),
+         ID = str_extract(string = ID,
+                          pattern = "[:digit:]{3}"),
+         ID = as.numeric(ID)
+      ) %>%
+    # filter(time <= 600) %>% # filter for 10min intervals
+    filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
+    dplyr::select(!c("Time","Heart Rate","id"))
+    ) %>%
+  bind_rows()
+
+main <-
+  left_join(main, df_merge,
+            by = "ID")
+
+main <- 
+  main %>% 
+  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
+  distinct() %>% 
+  group_by(ID) %>% 
+  dplyr::summarise(mean_heart = mean(heart_rate),
+            sd_heart = sd(heart_rate)) %>%
+  ungroup() %>% 
+  right_join(x = .,
+             y = main,
+             by = "ID") %>% 
+  filter(!(time_span == "teaching" & time > 600)) %>%
+  mutate(heart_rate_std = (heart_rate - mean_heart)/
+           sd_heart)
+
+# pre teaching interval
+
+main %>% 
+  filter(time_span == "preparation") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) -> cor_pre
+
+# teaching interval
+
+main %>% 
+  filter(time_span == "teaching") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) %>%
+  pcor()  -> pcor_teaching
+
+# post-teaching interval
+
+main %>% 
+  filter(time_span == "post") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) %>%
+  pcor()  -> pcor_post
+
+# interview interval
+
+main %>% 
+  filter(time_span == "interview") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) %>%
+  pcor()  -> pcor_interview
+
+# end interval
+
+main %>% 
+  filter(time_span == "end") %>% 
+  group_by(ID) %>% 
+  transmute(heart_rate_m = mean(heart_rate_std),
+            confidence_factor_m = mean(confidence_factor,
+                                      na.rm = TRUE),
+            disruption_factor_m = mean(disruption_factor,
+                                       na.rm = TRUE),
+            teaching_experience = teaching_experience,
+            gender = gender
+  ) %>%
+  distinct() %>% 
+  ungroup() %>% 
+  transmute(heart_rate_m = (heart_rate_m - mean(.$heart_rate_m))/sd(.$heart_rate_m),
+         confidence_factor_m = (confidence_factor_m - mean(.$confidence_factor_m))/sd(.$confidence_factor_m),
+         disruption_factor_m = (disruption_factor_m - mean(.$disruption_factor_m))/sd(.$disruption_factor_m),
+         gender = if_else(gender == "male",
+                           true = 0,
+                           false = 1),
+          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
+         ) %>%
+  pcor()  -> pcor_end
+
+```
+
 ```{=latex}
@@
 ```
+
+```{=latex}
+
+\begin{landscape}
+
+% Set longtable to stretch the entire width of the page
+\setlength{\LTleft}{0pt}
+\setlength{\LTright}{0pt}
+
+\begin{longtable}{@{\extracolsep{\fill}} p{1.8cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} @{}}
+
+    \toprule
+    & \multicolumn{4}{c}{Model 1} & \multicolumn{4}{c}{Model 2} & \multicolumn{4}{c}{Model 3} & \multicolumn{4}{c}{Model 4} \\
+    \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13} \cmidrule(lr){14-17}
+    Dependent \newline variable: & \multicolumn{16}{c}{Mean standardized HR and mean slopes} \\
+    \cmidrule(lr){2-17}
+    & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} \\
+    & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ \\
+    \midrule
+    \endfirsthead
+
+    \multicolumn{17}{c}{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
+    \toprule
+    & \multicolumn{4}{c}{Model 1} & \multicolumn{4}{c}{Model 2} & \multicolumn{4}{c}{Model 3} & \multicolumn{4}{c}{Model 4} \\
+    \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13} \cmidrule(lr){14-17}
+    Dependent variable: & \multicolumn{16}{c}{Mean standardized HR and mean slopes} \\
+    \cmidrule(lr){2-17}
+    & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ \\
+    \midrule
+    \endhead
+
+    \bottomrule
+    \multicolumn{17}{c}{{Continued on next page}} \\
+    \endfoot
+
+    \bottomrule
+    \endlastfoot
+
+    Pre-teaching \newline interval (I1) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.17$\\$(.005)$\end{tabular} & $.12$ & \begin{tabular}{@{}c@{}}$-.27^*$\\$(.002)$\end{tabular} & $<.05$ & & & & & & & & & & & & \\
+    R\textsuperscript{2} & $.030$ & & $.071$ & & & & & & & & & & & & & \\
+    \midrule
+    Teaching \newline interval (I2) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.11$\\$(.002)$\end{tabular} & $.34$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.83$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.73$ & \begin{tabular}{@{}c@{}}$.01$\\$(.001)$\end{tabular} & $.96$ & \begin{tabular}{@{}c@{}}$.10$\\$(.006)$\end{tabular} & $.42$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.001)$\end{tabular} & $.54$ & \begin{tabular}{@{}c@{}}$.05$\\$(.006)$\end{tabular} & $.67$ & \begin{tabular}{@{}c@{}}$-.05$\\$(.001)$\end{tabular} & $.72$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$-.18$\\$(.041)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.08$\\$(.010)$\end{tabular} & $.50$ & \begin{tabular}{@{}c@{}}$-.19$\\$(.042)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.12$\\$(.010)$\end{tabular} & $.34$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$.01$\\$(.046)$\end{tabular} & $.92$ & \begin{tabular}{@{}c@{}}$.12$\\$(.011)$\end{tabular} & $.34$ & \begin{tabular}{@{}c@{}}$-.04$\\$(.047)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$.15$\\$(.012)$\end{tabular} & $.24$ \\
+    R\textsuperscript{2} & $.012$ & & $.000$ & & $.040$ & & $.015$ & & $.012$ & & $.010$ & & $.042$ & & $.031$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.028$ & & $.015$ & & $.000$ & & $.010$ & & $.030$ & & $.031$ \\
+    \midrule
+    Post-teaching \newline interval (I3) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.04$\\$(.005)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$-.03$\\$(.001)$\end{tabular} & $.80$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$-.09$\\$(.001)$\end{tabular} & $.44$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.006)$\end{tabular} & $.55$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.89$ & \begin{tabular}{@{}c@{}}$-.01$\\$(.006)$\end{tabular} & $.91$ & \begin{tabular}{@{}c@{}}$-.07$\\$(.001)$\end{tabular} & $.61$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$.22$\\$(.040)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$-.18$\\$(.009)$\end{tabular} & $.14$ & \begin{tabular}{@{}c@{}}$.25^*$\\$(.041)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.20$\\$(.010)$\end{tabular} & $.12$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$.08$\\$(.045)$\end{tabular} & $.55$ & \begin{tabular}{@{}c@{}}$-.03$\\$(.011)$\end{tabular} & $.83$ & \begin{tabular}{@{}c@{}}$.14$\\$(.046)$\end{tabular} & $.27$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.011)$\end{tabular} & $.54$ \\
+    R\textsuperscript{2} & $.002$ & & $.001$ & & $.043$ & & $.020$ & & $.006$ & & $.002$ & & $.058$ & & $.023$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.041$ & & $.019$ & & $.004$ & & $.001$ & & $.056$ & & $.022$ \\
+    \midrule
+    Interview \newline interval (I4) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.24^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.20$\\$(.001)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$.22$\\$(.006)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$-.23$\\$(.001)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$.25^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.14$\\$(.001)$\end{tabular} & $.25$ & \begin{tabular}{@{}c@{}}$.23$\\$(.007)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$-.17$\\$(.001)$\end{tabular} & $.18$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$-.05$\\$(.045)$\end{tabular} & $.66$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.006)$\end{tabular} & $.52$ & \begin{tabular}{@{}c@{}}$-.06$\\$(.047)$\end{tabular} & $.61$ & \begin{tabular}{@{}c@{}}$-.12$\\$(.007)$\end{tabular} & $.34$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$-.02$\\$(.050)$\end{tabular} & $.85$ & \begin{tabular}{@{}c@{}}$-.13$\\$(.007)$\end{tabular} & $.29$ & \begin{tabular}{@{}c@{}}$-.04$\\$(.052)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$-.16$\\$(.007)$\end{tabular} & $.20$ \\
+    R\textsuperscript{2} & $.058$ & & $.040$ & & $.060$ & & $.050$ & & $.058$ & & $.054$ & & $.061$ & & $.069$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.002$ & & $.010$ & & $.000$ & & $.014$ & & $.003$ & & $.029$ \\
+    \midrule
+    End \newline interval (I5) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.04$\\$(.004)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$.11$\\$(.001)$\end{tabular} & $.32$ & \begin{tabular}{@{}c@{}}$.07$\\$(.005)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.18$\\$(.001)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.09$\\$(.005)$\end{tabular} & $.46$ & \begin{tabular}{@{}c@{}}$.07$\\$(.001)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.10$\\$(.005)$\end{tabular} & $.43$ & \begin{tabular}{@{}c@{}}$.12$\\$(.001)$\end{tabular} & $.33$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$.06$\\$(.035)$\end{tabular} & $.60$ & \begin{tabular}{@{}c@{}}$.19$\\$(.007)$\end{tabular} & $.12$ & \begin{tabular}{@{}c@{}}$.04$\\$(.037)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$.23$\\$(.007)$\end{tabular} & $.07$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$-.11$\\$(.039)$\end{tabular} & $.38$ & \begin{tabular}{@{}c@{}}$.10$\\$(.008)$\end{tabular} & $.43$ & \begin{tabular}{@{}c@{}}$-.10$\\$(.041)$\end{tabular} & $.44$ & \begin{tabular}{@{}c@{}}$.16$\\$(.008)$\end{tabular} & $.22$ \\
+    R\textsuperscript{2} & $.002$ & & $.013$ & & $.005$ & & $.053$ & & $.012$ & & $.025$ & & $.013$ & & $.078$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.003$ & & $.040$ & & $.010$ & & $.012$ & & $.011$ & & $.065$ \\
+\end{longtable}
+\begin{tablenotes}
+\footnotesize
+\item Note.
+In Model 1, mean standardized HR and mean slopes were predicted only by teaching experience.
+In Model 2, solely disruption appraisal was added to teaching experience as a predictor.
+In Model 3, solely confidence appraisal was added to teaching experience as a predictor.
+In Model 4, all three predictors were considered in concert.
+\item * $p < .05$.
+\end{tablenotes}
+\end{landscape}
+
+```

### 2024-08-07 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

@@
                    starts_with("Total_duration_of_fixations"),
+                   starts_with("Average_duration_of_fixations"),
                    starts_with("Number_of_fixations"),
@@
 
-# Bind every tibble that contains "interval_complete" to a new tible
+# bind every tibble that contains "interval_complete" to a new tible
  df_aoi <-
@@
 
+# extract only participants ID number
  df_aoi$Participant <- as.numeric(
@@
 
-# Remove temporary data for a cleaner workspace
+# exclude invalid participants
+df_aoi <- df_aoi %>%
+  filter(!Participant == 223,
+         !Participant == 232)
+
+# remove temporary data for a cleaner workspace
  rm(list = ls(pattern = "^tib_ProVisio"))
@@
 
-#### 2.2.1 Number of fixation in entire micro-teaching unit
+#### 2.2.1 Number of fixation (micro-teaching unit)
 ```{r nof_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-##################### NUMBER OF FIXATION ON ALL AOIS ########################
-
-# filter group & total duration & number fixation on all AOIs
+##################### NUMBER OF FIXATION IN MICRO-TEACHING UNIT ########################
+
+# filter group, participants, total duration & number fixation (micro-teaching unit)
 df_aoi %>%
   filter(TOI == "Lesson") %>% 
-  dplyr::select (Group,
+  dplyr::select (
+    Group,
     Participant,
@@
     starts_with("Number_of_fixations"),
+    starts_with("Average_duration"),
     !"Total_duration_of_fixations.Disruptive_Person",
-          !"Number_of_fixations.Disruptive_Person") %>% 
+    !"Number_of_fixations.Disruptive_Person",
+    !"Average_duration_of_fixations.Disruptive_Person"
+  ) %>%
   rowwise() %>%
-  transmute(Group = Group,
+  transmute(
+    Group = Group,
     Participant = Participant,
-            Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
-                                                    ),
-                                           na.rm = TRUE
-                                           ),
-            Sum_number_fixation = sum(c_across(starts_with("Number_of")
-                                                  ),
-                                         na.rm = TRUE
-                                         )
-            ) %>% 
-  mutate(Average_duration = round(Sum_duration_fixation/Sum_number_fixation,
-                                         digits = 0),
-         Group = as_factor(Group)) %>% 
+    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
+    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
+  ) %>%
+  mutate(
+    Average_duration_calc = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
+    Group = as_factor(Group)
+  ) %>%
   drop_na() -> df_aoi_sum
 
-# N, M, SD, min & max number of fixation (ent)
+# N, M, SD, min & max number of fixation (micro-teaching unit)
 nof.table <-
@@
 knitr::kable(nof.table,
-             caption = "N, M, SD, min & max number of fixation in entire micro-teaching unit")
+             caption = "N, M, SD, min & max number of fixation (micro-teaching unit)")
 
@@
 df_aoi_sum %>%
-  ggplot(mapping = aes(x = Group,
-                       y = Sum_number_fixation)) +
-  geom_boxplot(mapping = aes(fill = Group),
-               outlier.shape = NA) +
-  geom_point(size = 2,
+  ggplot(mapping = aes(x = Group, y = Sum_number_fixation)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
     alpha = 0.7,
-             position = position_jitter(seed = 1,
+    position = position_jitter(
+      seed = 1,
       width = 0.1,
-                                        height = 0.1)) +
-  labs(x ="",
-       y = "Number of fixation") +
+      height = 0.1
+    )
+  ) +
+  ylim(0, 2500) +
+  labs(x = "", y = "Number of fixation") +
   scale_fill_brewer(palette  = "RdBu") +
@@
   theme_cowplot() +
-  theme(legend.position="none") -> plot_number_group
+  theme(legend.position = "none") -> plot_number_group
 
@@
 # t-test for expertise differences
-t.test(x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
+t.test(
+  x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
   y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
-       var.equal = TRUE)
+  var.equal = TRUE
+)
 
@@
 # effect size for expertise differences
-d_number_all <- CohenD(x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
+d_number_all <- CohenD(
+  x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
   y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
-                       na.rm = TRUE)
+  na.rm = TRUE
+)
+
 round(d_number_all, 2)
@@
 
-#### 2.2.2 Number of fixations on AOI "Students" during entire micro-teaching unit
+#### 2.2.2 Number of fixations on AOI "students" (micro-teaching unit)
 ```{r nof_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
   filter(TOI == "Lesson") %>%
-  dplyr::select (Group,
+  dplyr::select (
+    Group,
     Participant,
@@
     "Number_of_fixations.Bianca",
-                 "Number_of_fixations.Carl(a)") %>% 
+    "Number_of_fixations.Carl(a)"
+  ) %>%
   rowwise() %>%
-  transmute(Group = Group,
+  transmute(
+    Group = Group,
     Participant = Participant,
-            Stud_duration_fixation = sum(c_across(starts_with("Total_duration")
-                                                 ),
-                                         na.rm = TRUE
-                                         ),
-            Stud_number_fixation = sum(c_across(starts_with("Number_of")
-                                                ),
-                                       na.rm = TRUE
-                                       )
-            ) %>% 
-  mutate(Average_duration_stud = round(Stud_duration_fixation/Stud_number_fixation, 
-                                  digits = 0),
+    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
+  ) %>%
+  mutate(
+    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
     Group = as_factor(Group)
@@
 knitr::kable(nof.stud.table,
-             caption = "N, M, SD, min & max number of fixation on AOI students (entire micro-teaching unit)")
+             caption = "N, M, SD, min & max number of fixation on AOI students (micro-teaching unit)")
 
@@
 df_aoi_stud %>%
+  ggplot(mapping = aes(x = Group, y = Stud_number_fixation)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  labs(x = "", y = "Number of fixation") +
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("Number of fixation on AOI `Students`\n(micro-teaching unit)") +
+  theme_cowplot() +
+  theme(legend.position = "none") -> plot_number_stud
+
+plot_number_stud
+
+```
+
+#### t-test & effect size "Number of fixation on AOI students"
+```{r nof_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# NUMBER OF FIXATIONS on AOI students 
+# t-test for expertise differences
+t.test(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
+       y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
+       var.equal = TRUE)
+
+# NUMBER OF FIXATIONS on AOI students
+# effect size for expertise differences
+d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
+                      y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
+                      na.rm = TRUE)
+
+round(d_number_stud, 2)
+
+```
+
+#### 2.2.3 Number of fixations on AOI "disruptive person" (during disruption)
+```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### NUMBER OF FIXATION ON AOI DISRUPTIVE PERSON ########################
+
+# filter group & total duration & number fixation on AOI "disruptive person"
+df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select(Group, 
+                Participant, 
+                "Number_of_fixations.Disruptive_Person") %>%
+  mutate(Group = as_factor(Group)) -> df_aoi_disrup
+
+# N, M, SD, min & max number of fixation on AOI "disruptive person"
+nof.disrup.table <-
+  df_aoi_disrup %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Number_of_fixations.Disruptive_Person), digits = 2),
+    "SD" = round(sd(Number_of_fixations.Disruptive_Person), digits = 2),
+    "Min" = round(min(Number_of_fixations.Disruptive_Person), digits = 2),
+    "Max" = round(max(Number_of_fixations.Disruptive_Person), digits = 2)
+  )
+
+knitr::kable(nof.disrup.table,
+             caption = "N, M, SD, min & max number of fixation on AOI disruptive person (during disruption)")
+
+# plotting average duration on AOI Disruptive person
+df_aoi_disrup %>%
+  ggplot(mapping = aes(x = Group, y = Number_of_fixations.Disruptive_Person)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  ylim(0, 150) +
+  labs(x = "", y = "Number of fixation") +
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("Number of fixation AOI\n`disruptive person`") +
+  theme_cowplot() +
+  theme(legend.position = "none") -> plot_number_disrup
+
+plot_number_disrup
+```
+
+#### t-test & effect size "Number of fixation on AOI disruptive person"
+```{r nof_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# NUMBER OF FIXATIONS on AOI disruptive person 
+# t-test for expertise differences
+t.test(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
+       y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"],
+       var.equal = TRUE)
+
+# NUMBER OF FIXATIONS 
+# effect size for expertise differences
+d_number_disrup <- CohenD(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
+                        y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"],
+                        na.rm = TRUE)
+
+round(d_number_disrup, 2)
+
+```
+
+#### 2.2.4 Average duration of fixation (micro-teaching unit)
+```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### AVERAGE DURATION OF FIXATION IN ENTIRE MICRO-TEACHING UNIT ########################
+
+# N, M, SD, min & max average duration of fixation (entire micro-teaching unit)
+dur.table <-
+  df_aoi_sum %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M in ms" = round(mean(Sum_duration_fixation), digits = 2),
+    "SD in ms" = round(sd(Sum_duration_fixation), digits = 2),
+    "Min in ms" = round(min(Sum_duration_fixation), digits = 2),
+    "Max in ms" = round(max(Sum_duration_fixation), digits = 2)
+    )
+
+knitr::kable(dur.table,
+             caption = "N, M, SD, min & max duration of fixation in milliseconds (micro-teaching unit)")
+
+# plotting average duration (micro-teaching unit)
+df_aoi_sum %>% 
   ggplot(mapping = aes(x = Group,
-                       y = Stud_number_fixation)) +
+                       y = Sum_duration_fixation)) +
   geom_boxplot(mapping = aes(fill = Group),
@@
                                         height = 0.1)) +
-  labs(x ="",
-       y = "Number of fixation") + 
-  scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("Number of fixation on AOI\n`Students` (micro-teaching unit)") +
-  theme_cowplot() +
-  theme(legend.position="none") -> plot_number_stud
-
-plot_number_stud
-
-```
-
-#### t-test & effect size "Number of fixation on AOI students"
-```{r nof_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# NUMBER OF FIXATIONS on AOI students 
-# t-test for expertise differences
-t.test(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
-       y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
-       var.equal = TRUE)
-
-# NUMBER OF FIXATIONS on AOI students
-# effect size for expertise differences
-d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
-                      y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
-                      na.rm = TRUE)
-
-round(d_number_stud, 2)
-
-```
-
-#### 2.2.3 Average duration in entire micro-teaching unit
-```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### AVERAGE DURATION ########################
-
-# N, M, SD, min & max average duration (entire micro-teaching unit)
-dur.table <-
-  df_aoi_sum %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(Average_duration), digits = 2),
-    "SD" = round(sd(Average_duration), digits = 2),
-    "Min" = round(min(Average_duration), digits = 2),
-    "Max" = round(max(Average_duration), digits = 2)
-    )
-
-knitr::kable(dur.table,
-             caption = "N, M, SD, min & max average duration in entire micro-teaching unit")
-
-# plotting average duration on ALL AOIS
-df_aoi_sum %>% 
-  ggplot(mapping = aes(x = Group,
-                       y = Average_duration)) +
-  geom_boxplot(mapping = aes(fill = Group),
-               outlier.shape = NA) +
-  geom_point(size = 2,
-             alpha = 0.7,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
+  ylim(0, 1000000) +
+
   labs(x ="",
@@
   scale_fill_brewer(palette  = "RdBu") + 
-  ggtitle("Average duration \n(micro-teaching unit)") +
+  ggtitle("Duration of fixation\n(micro-teaching unit)") +
   theme_cowplot() +
@@
 #### t-test & effect size "Average duration in entire micro-teaching unit"
-```{r dur_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r dur_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 
-#### 2.2.4 Average duration on AOI students
+#### 2.2.5 Average duration on AOI students
 ```{r dur_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
   filter(TOI == "Lesson") %>%
-  dplyr::select (Group,
+  dplyr::select (
+    Group,
     "Total_duration_of_fixations.Anna",
@@
     "Number_of_fixations.Bianca",
-          "Number_of_fixations.Carl(a)") %>% 
+    "Number_of_fixations.Carl(a)"
+  ) %>%
   rowwise() %>%
-  transmute(Group = Group,
-            Stud_duration_fixation = sum(c_across(starts_with("Total_duration")
-                                                 ),
-                                         na.rm = TRUE
-                                         ),
-            Stud_number_fixation = sum(c_across(starts_with("Number_of")
-                                                ),
-                                       na.rm = TRUE
-                                       )
-            ) %>% 
-  mutate(Average_duration_stud = round(Stud_duration_fixation/Stud_number_fixation, 
-                                  digits = 0),
-         Group = as_factor(Group)) -> df_aoi_stud
+  transmute(
+    Group = Group,
+    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
+  ) %>%
+  mutate(
+    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
+    Group = as_factor(Group)
+  ) -> df_aoi_stud
 
@@
 df_aoi_stud %>%
+  ggplot(mapping = aes(x = Group, y = Average_duration_stud)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  ylim(0, 1200) + 
+  labs(x ="",
+       y = "Milliseconds") + 
+  scale_fill_brewer(palette  = "RdBu") + 
+  ggtitle("Average duration of fixation on AOI `Students`\n(micro-teaching unit)") +
+  theme_cowplot() +
+  theme(legend.position="none") -> plot_average_duration_stud
+
+plot_average_duration_stud
+
+```
+
+#### t-test & effect size "Average duration on AOI students"
+```{r dur_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# AVERAGE DURATION OF FIXATIONS on AOI Students 
+# t-test for expertise differences
+t.test(
+  x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
+  y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+  var.equal = TRUE
+)
+
+# AVERAGE DURATION OF FIXATIONS on AOI Students
+# effect size for expertise differences
+d_aver_stud <- CohenD(
+  x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
+  y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+  na.rm = TRUE
+)
+
+```
+
+#### 2.2.6 Average duration of fixations on AOI "disruptive person" (during disruption)
+```{r dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### AVERAGE DURATION ON AOI DISRUPTIVE PERSON ########################
+
+# filter group & total duration & number fixation on AOI Disruptive person
+df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select (
+    Group,
+    "Total_duration_of_fixations.Disruptive_Person",
+    "Number_of_fixations.Disruptive_Person"
+  ) %>%
+  rowwise() %>%
+  mutate(
+    Average_duration_disrup = round(
+      Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person,
+      digits = 0
+    ),
+    Group = as_factor(Group)
+  ) -> df_aoi_disrup
+
+# N, M, SD, min & max number of fixation on AOI "disruptive person"
+dur.disrup.table <-
+  df_aoi_disrup %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Average_duration_disrup), digits = 2),
+    "SD" = round(sd(Average_duration_disrup), digits = 2),
+    "Min" = round(min(Average_duration_disrup), digits = 2),
+    "Max" = round(max(Average_duration_disrup), digits = 2)
+  )
+
+knitr::kable(dur.disrup.table,
+             caption = "N, M, SD, min & max average duration of fixation on AOI disruptive person (during disruption)")
+
+# plotting average duration on AOI Disruptive person
+df_aoi_disrup %>% 
   ggplot(mapping = aes(x = Group,
-                       y = Average_duration_stud)) +
+                       y = Average_duration_disrup)) +
   geom_boxplot(mapping = aes(fill = Group),
@@
                                         height = 0.1)) +
-  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
-  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
-  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
-  #                                  )
-  #                  ) +
+  ylim(0, 1500) +
   labs(x ="",
-       y = "Millisekunden") + 
+       y = "Milliseconds") + 
   scale_fill_brewer(palette  = "RdBu") + 
-  scale_x_discrete(labels=c("Novice" = "Unerfahren",
-                            "Expert" = "Erfahren")) +
-  ggtitle("Ø Fixationsdauer AOI\n `Schüler:innen`") +
+  ggtitle("Average duration of fixation AOI\n`disruptive person`") +
   theme_cowplot() +
-  theme(legend.position="none",
-        axis.text.x = element_text(size = 34),
-        axis.text.y = element_text(size = 18),
-        axis.title = element_text(size = 34),
-        plot.title = element_text(size = 35, 
-                                  face = "bold")
-  ) -> plot_average_duration_stud
-
-plot_average_duration_stud
-```
-
-#### t-test & effect size "Average duration on AOI students"
-```{r dur_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# AVERAGE DURATION OF FIXATIONS on AOI Students 
-# t-test for expertise differences
-t.test(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
-       y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+  theme(legend.position="none") -> plot_average_duration_disrup
+
+plot_average_duration_disrup
+
+```
+
+#### t-test & effect size "Average duration of fixation on AOI disruptive person"
+```{r _disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# AVERAGDE DURATION OF FIXATIONS on AOI disruptive person 
+# t-test for expertise differences
+t.test(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
+       y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"],
        var.equal = TRUE)
 
-# AVERAGE DURATION OF FIXATIONS on AOI Students
-# effect size for expertise differences
-d_aver_stud <- CohenD(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
-                      y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+# NUMBER OF FIXATIONS 
+# effect size for expertise differences
+d_dur_disrup <- CohenD(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
+                        y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"],
                         na.rm = TRUE)
 
-```
-
-#### t-test & effect size "Average duration on AOI students"
-```{r dur_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# AVERAGE DURATION OF FIXATIONS on all AOIs 
-# t-test for expertise differences
-t.test(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
-       y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
-       var.equal = TRUE)
-
-# AVERAGE DURATION OF FIXATIONS on all AOIs
-# effect size for expertise differences
-d_aver_all <- CohenD(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
-                     y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
-                    na.rm = TRUE)
-round(d_aver_all, 2)
+round(d_dur_disrup, 2)
+
+```
+
+#### 2.2.1 GRI (micro-teaching unit)
+```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### GRI IN MICRO-TEACHING UNIT ########################
+
+# filter group, participants, total duration & number fixation in entire micro-teaching unit
+df_aoi_sum %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select (
+    Group,
+    Participant,
+    starts_with("Total_duration_of_fixations"),
+    starts_with("Number_of_fixations"),
+    !"Total_duration_of_fixations.Disruptive_Person",
+    !"Number_of_fixations.Disruptive_Person"
+  ) %>%
+  rowwise() %>%
+  transmute(
+    Group = Group,
+    Participant = Participant,
+    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
+  ) %>%
+  mutate(
+    GRI = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
+    Group = as_factor(Group)
+  ) %>%
+  drop_na() -> df_gri
+
+# N, M, SD, min & max number of fixation (micro-teaching unit)
+nof.table <-
+  df_aoi_sum %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Sum_number_fixation), digits = 2),
+    "SD" = round(sd(Sum_number_fixation), digits = 2),
+    "Min" = round(min(Sum_number_fixation), digits = 2),
+    "Max" = round(max(Sum_number_fixation), digits = 2)
+  )
+
+knitr::kable(nof.table,
+             caption = "N, M, SD, min & max number of fixation (micro-teaching unit)")
+
+# plotting number of fixations on ALL AOIS
+df_aoi_sum %>%
+  ggplot(mapping = aes(x = Group, y = Sum_number_fixation)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  ylim(0, 2500) +
+  labs(x = "", y = "Number of fixation") +
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("Number of fixation\n(micro-teaching unit)") +
+  theme_cowplot() +
+  theme(legend.position = "none") -> plot_number_group
+
+plot_number_group
 

### 2024-08-07 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex

@@
 \usepackage{tablefootnote}
+\usepackage{float}
+\usepackage{wrapfig}
+\usepackage{pdflscape}
+\usepackage{longtable}
 
@@
 
-\begin{figure}[htbp]
+\begin{wrapfigure}{r}{0.5\textwidth}
   \centering
-  \includegraphics[width=1\textwidth]{images/Timeline.pdf}
+  \includegraphics[width=0.5\textwidth]{images/Timeline_small.pdf}
   \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
   \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
-\end{figure}
+\end{wrapfigure}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[H]
   \centering
@@
 
+\begin{landscape}
+
+% Set longtable to stretch the entire width of the page
+\setlength{\LTleft}{0pt}
+\setlength{\LTright}{0pt}
+
+\begin{longtable}{@{\extracolsep{\fill}} p{1.8cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} @{}}
+
+    \toprule
+    & \multicolumn{4}{c}{Model 1} & \multicolumn{4}{c}{Model 2} & \multicolumn{4}{c}{Model 3} & \multicolumn{4}{c}{Model 4} \\
+    \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13} \cmidrule(lr){14-17}
+    Dependent \newline variable: & \multicolumn{16}{c}{Mean standardized HR and mean slopes} \\
+    \cmidrule(lr){2-17}
+    & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} \\
+    & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ \\
+    \midrule
+    \endfirsthead
+
+    \multicolumn{17}{c}{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
+    \toprule
+    & \multicolumn{4}{c}{Model 1} & \multicolumn{4}{c}{Model 2} & \multicolumn{4}{c}{Model 3} & \multicolumn{4}{c}{Model 4} \\
+    \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13} \cmidrule(lr){14-17}
+    Dependent variable: & \multicolumn{16}{c}{Mean standardized HR and mean slopes} \\
+    \cmidrule(lr){2-17}
+    & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ \\
+    \midrule
+    \endhead
+
+    \bottomrule
+    \multicolumn{17}{c}{{Continued on next page}} \\
+    \endfoot
+
+    \bottomrule
+    \endlastfoot
+
+    Pre-teaching \newline interval (I1) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.17$\\$(.005)$\end{tabular} & $.12$ & \begin{tabular}{@{}c@{}}$-.27^*$\\$(.002)$\end{tabular} & $<.05$ & & & & & & & & & & & & \\
+    R\textsuperscript{2} & $.030$ & & $.071$ & & & & & & & & & & & & & \\
+    \midrule
+    Teaching \newline interval (I2) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.11$\\$(.002)$\end{tabular} & $.34$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.83$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.73$ & \begin{tabular}{@{}c@{}}$.01$\\$(.001)$\end{tabular} & $.96$ & \begin{tabular}{@{}c@{}}$.10$\\$(.006)$\end{tabular} & $.42$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.001)$\end{tabular} & $.54$ & \begin{tabular}{@{}c@{}}$.05$\\$(.006)$\end{tabular} & $.67$ & \begin{tabular}{@{}c@{}}$-.05$\\$(.001)$\end{tabular} & $.72$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$-.18$\\$(.041)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.08$\\$(.010)$\end{tabular} & $.50$ & \begin{tabular}{@{}c@{}}$-.19$\\$(.042)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.12$\\$(.010)$\end{tabular} & $.34$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$.01$\\$(.046)$\end{tabular} & $.92$ & \begin{tabular}{@{}c@{}}$.12$\\$(.011)$\end{tabular} & $.34$ & \begin{tabular}{@{}c@{}}$-.04$\\$(.047)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$.15$\\$(.012)$\end{tabular} & $.24$ \\
+    R\textsuperscript{2} & $.012$ & & $.000$ & & $.040$ & & $.015$ & & $.012$ & & $.010$ & & $.042$ & & $.031$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.028$ & & $.015$ & & $.000$ & & $.010$ & & $.030$ & & $.031$ \\
+    \midrule
+    Post-teaching \newline interval (I3) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.04$\\$(.005)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$-.03$\\$(.001)$\end{tabular} & $.80$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$-.09$\\$(.001)$\end{tabular} & $.44$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.006)$\end{tabular} & $.55$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.89$ & \begin{tabular}{@{}c@{}}$-.01$\\$(.006)$\end{tabular} & $.91$ & \begin{tabular}{@{}c@{}}$-.07$\\$(.001)$\end{tabular} & $.61$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$.22$\\$(.040)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$-.18$\\$(.009)$\end{tabular} & $.14$ & \begin{tabular}{@{}c@{}}$.25^*$\\$(.041)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.20$\\$(.010)$\end{tabular} & $.12$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$.08$\\$(.045)$\end{tabular} & $.55$ & \begin{tabular}{@{}c@{}}$-.03$\\$(.011)$\end{tabular} & $.83$ & \begin{tabular}{@{}c@{}}$.14$\\$(.046)$\end{tabular} & $.27$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.011)$\end{tabular} & $.54$ \\
+    R\textsuperscript{2} & $.002$ & & $.001$ & & $.043$ & & $.020$ & & $.006$ & & $.002$ & & $.058$ & & $.023$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.041$ & & $.019$ & & $.004$ & & $.001$ & & $.056$ & & $.022$ \\
+    \midrule
+    Interview \newline interval (I4) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.24^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.20$\\$(.001)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$.22$\\$(.006)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$-.23$\\$(.001)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$.25^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.14$\\$(.001)$\end{tabular} & $.25$ & \begin{tabular}{@{}c@{}}$.23$\\$(.007)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$-.17$\\$(.001)$\end{tabular} & $.18$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$-.05$\\$(.045)$\end{tabular} & $.66$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.006)$\end{tabular} & $.52$ & \begin{tabular}{@{}c@{}}$-.06$\\$(.047)$\end{tabular} & $.61$ & \begin{tabular}{@{}c@{}}$-.12$\\$(.007)$\end{tabular} & $.34$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$-.02$\\$(.050)$\end{tabular} & $.85$ & \begin{tabular}{@{}c@{}}$-.13$\\$(.007)$\end{tabular} & $.29$ & \begin{tabular}{@{}c@{}}$-.04$\\$(.052)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$-.16$\\$(.007)$\end{tabular} & $.20$ \\
+    R\textsuperscript{2} & $.058$ & & $.040$ & & $.060$ & & $.050$ & & $.058$ & & $.054$ & & $.061$ & & $.069$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.002$ & & $.010$ & & $.000$ & & $.014$ & & $.003$ & & $.029$ \\
+    \midrule
+    End \newline interval (I5) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.04$\\$(.004)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$.11$\\$(.001)$\end{tabular} & $.32$ & \begin{tabular}{@{}c@{}}$.07$\\$(.005)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.18$\\$(.001)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.09$\\$(.005)$\end{tabular} & $.46$ & \begin{tabular}{@{}c@{}}$.07$\\$(.001)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.10$\\$(.005)$\end{tabular} & $.43$ & \begin{tabular}{@{}c@{}}$.12$\\$(.001)$\end{tabular} & $.33$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$.06$\\$(.035)$\end{tabular} & $.60$ & \begin{tabular}{@{}c@{}}$.19$\\$(.007)$\end{tabular} & $.12$ & \begin{tabular}{@{}c@{}}$.04$\\$(.037)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$.23$\\$(.007)$\end{tabular} & $.07$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$-.11$\\$(.039)$\end{tabular} & $.38$ & \begin{tabular}{@{}c@{}}$.10$\\$(.008)$\end{tabular} & $.43$ & \begin{tabular}{@{}c@{}}$-.10$\\$(.041)$\end{tabular} & $.44$ & \begin{tabular}{@{}c@{}}$.16$\\$(.008)$\end{tabular} & $.22$ \\
+    R\textsuperscript{2} & $.002$ & & $.013$ & & $.005$ & & $.053$ & & $.012$ & & $.025$ & & $.013$ & & $.078$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.003$ & & $.040$ & & $.010$ & & $.012$ & & $.011$ & & $.065$ \\
+\end{longtable}
+\begin{tablenotes}
+\footnotesize
+\item Note.
+In Model 1, mean standardized HR and mean slopes were predicted only by teaching experience.
+In Model 2, solely disruption appraisal was added to teaching experience as a predictor.
+In Model 3, solely confidence appraisal was added to teaching experience as a predictor.
+In Model 4, all three predictors were considered in concert.
+\item * $p < .05$.
+\end{tablenotes}
+\end{landscape}
+
 \bibliography{r-references.bib}

### 2024-08-07 02_paper/02_study/01_fitbit paper/Submission/analysis_270423.Rmd
tabeleln und so

--- 2024-06-06 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
@@
 
-stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
-                     type = "html",
+stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4,
+                     type = "latex",
                      caption = "Pre Teaching Phase",

### 2024-08-08 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

@@
 ### 2.1 Eye-Tracking Data
-
-1. Number of fixation, Fixation duration, GRI 
-- Alles (gesamte Lektion), students (gesamte Lektion)
-- disruptive person (tatsächliche Dauer der Störung)
-
-2. Time to first fixation
-- disruptive person (tatsächliche Dauer der Störung)
-
 ```{r eyetracking_read_in_data, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
@@
 
-XXX 223 & 232 sind fehlerhaft --> Daten nochmal komplett neu ziehen!! XXX
+XXX 223 (ist eine Doppelung der 214) & 232 (enthält NAs) sind fehlerhaft --> Daten nochmal komplett neu ziehen!! XXX
 
@@
 knitr::kable(nof.table,
-             caption = "N, M, SD, min & max number of fixation (micro-teaching unit)")
-
-# plotting number of fixations on ALL AOIS
+             caption = "N, M, SD, min & max number of fixations (micro-teaching unit)")
+
+# plotting number of fixations (micro-teaching unit)
 df_aoi_sum %>%
@@
   ylim(0, 2500) +
-  labs(x = "", y = "Number of fixation") +
+  labs(x = "", y = "Number of fixations") +
   scale_fill_brewer(palette  = "RdBu") +
@@
 
-#### t-test & effect size "Number of fixation in entire micro-teaching unit"
+#### t-test & effect size "Number of fixation (micro-teaching unit)"
 ```{r nof_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.2 Number of fixations on AOI "students" (micro-teaching unit)
+#### 2.2.2 Number of fixations (AOI students)
 ```{r nof_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-##################### NUMBER OF FIXATIONS ON AOI STUDENTS ########################
-
-# filter group & total duration & number fixation on AOI Students
+##################### NUMBER OF FIXATIONS (AOI STUDENTS) ########################
+
+# filter group & total duration & number fixation (AOI students)
 df_aoi %>%
@@
 
-# N, M, SD, min & max number of fixation on AOI students
+# N, M, SD, min & max number of fixations (AOI students)
 nof.stud.table <-
@@
 knitr::kable(nof.stud.table,
-             caption = "N, M, SD, min & max number of fixation on AOI students (micro-teaching unit)")
+             caption = "N, M, SD, min & max number of fixations (AOI students)")
 
@@
   ) +
-  labs(x = "", y = "Number of fixation") +
+  labs(x = "", y = "Number of fixations") +
   scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Number of fixation on AOI `Students`\n(micro-teaching unit)") +
+  ggtitle("Number of fixations\n(AOI students)") +
   theme_cowplot() +
@@
 
-#### t-test & effect size "Number of fixation on AOI students"
+#### t-test & effect size "Number of fixation" (AOI students)
 ```{r nof_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.3 Number of fixations on AOI "disruptive person" (during disruption)
+#### 2.2.3 Number of fixations (AOI disruptive person)
 ```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 knitr::kable(nof.disrup.table,
-             caption = "N, M, SD, min & max number of fixation on AOI disruptive person (during disruption)")
+             caption = "N, M, SD, min & max number of fixation (AOI disruptive person)")
 
@@
   ylim(0, 150) +
-  labs(x = "", y = "Number of fixation") +
+  labs(x = "", y = "Number of fixations") +
   scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Number of fixation AOI\n`disruptive person`") +
+  ggtitle("Number of fixations\n(AOI disruptive person)") +
   theme_cowplot() +
@@
 
-#### t-test & effect size "Number of fixation on AOI disruptive person"
+#### t-test & effect size "Number of fixations" (AOI disruptive person)
 ```{r nof_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.4 Average duration of fixation (micro-teaching unit)
+#### 2.2.4 Average duration of fixations in milliseconds (micro-teaching unit)
 ```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-##################### AVERAGE DURATION OF FIXATION IN ENTIRE MICRO-TEACHING UNIT ########################
-
-# N, M, SD, min & max average duration of fixation (entire micro-teaching unit)
+##################### AVERAGE DURATION OF FIXATIONS (MICRO-TEACHING UNIT) ########################
+
+# N, M, SD, min & max average duration of fixations (micro-teaching unit)
 dur.table <- 
@@
     N = n(),
-    "M in ms" = round(mean(Sum_duration_fixation), digits = 2),
-    "SD in ms" = round(sd(Sum_duration_fixation), digits = 2),
-    "Min in ms" = round(min(Sum_duration_fixation), digits = 2),
-    "Max in ms" = round(max(Sum_duration_fixation), digits = 2)
+    "M in ms" = round(mean(Average_duration_calc), digits = 2),
+    "SD in ms" = round(sd(Average_duration_calc), digits = 2),
+    "Min in ms" = round(min(Average_duration_calc), digits = 2),
+    "Max in ms" = round(max(Average_duration_calc), digits = 2)
     )
@@
 knitr::kable(dur.table,
-             caption = "N, M, SD, min & max duration of fixation in milliseconds (micro-teaching unit)")
+             caption = "N, M, SD, min & max duration of fixations in milliseconds (micro-teaching unit)")
 
@@
   ggplot(mapping = aes(x = Group,
-                       y = Sum_duration_fixation)) +
+                       y = Average_duration_calc)) +
   geom_boxplot(mapping = aes(fill = Group),
@@
                                         height = 0.1)) +
-  ylim(0, 1000000) +
+  ylim(0, 1000) +
 
@@
   scale_fill_brewer(palette  = "RdBu") + 
-  ggtitle("Duration of fixation\n(micro-teaching unit)") +
+  ggtitle("Average duration of fixations\n(micro-teaching unit)") +
   theme_cowplot() +
@@
 
-#### t-test & effect size "Average duration in entire micro-teaching unit"
+#### t-test & effect size "Average duration of fixations" (micro-teaching unit)
 ```{r dur_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 # t-test for expertise differences
-t.test(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
-       y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
+t.test(x = df_aoi_sum$Average_duration_calc[df_aoi_sum$Group == "Expert"],
+       y = df_aoi_sum$Average_duration_calc[df_aoi_sum$Group == "Novice"],
        var.equal = TRUE)
@@
 # effect size for expertise differences
-d_aver_all <- CohenD(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
-                     y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
+d_aver_all <- CohenD(x = df_aoi_sum$Average_duration_calc[df_aoi_sum$Group == "Expert"],
+                     y = df_aoi_sum$Average_duration_calc[df_aoi_sum$Group == "Novice"],
                     na.rm = TRUE)
@@
 
-#### 2.2.5 Average duration on AOI students
+#### 2.2.5 Average duration of fixations (AOI students)
 ```{r dur_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-# N, M, SD, min & max average duration on AOI students
+# N, M, SD, min & max average duration of fixations on AOI students
 dur.stud.table <-
@@
     N = n(),
-    "M" = round(mean(Average_duration_stud), digits = 2),
-    "SD" = round(sd(Average_duration_stud), digits = 2),
-    "Min" = round(min(Average_duration_stud), digits = 2),
-    "Max" = round(max(Average_duration_stud), digits = 2)
+    "M in ms" = round(mean(Average_duration_stud), digits = 2),
+    "SD in ms" = round(sd(Average_duration_stud), digits = 2),
+    "Min in ms" = round(min(Average_duration_stud), digits = 2),
+    "Max in ms" = round(max(Average_duration_stud), digits = 2)
   )
@@
 knitr::kable(dur.stud.table,
-             caption = "N, M, SD, min & max average duration on AOI students")
+             caption = "N, M, SD, min & max average duration of fixations in milliseconds (AOI students)")
 
@@
   scale_fill_brewer(palette  = "RdBu") + 
-  ggtitle("Average duration of fixation on AOI `Students`\n(micro-teaching unit)") +
+  ggtitle("Average duration of fixations\n(AOI students)") +
   theme_cowplot() +
@@
 
-#### t-test & effect size "Average duration on AOI students"
+#### t-test & effect size "Average duration of fixations" (AOI students)
 ```{r dur_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.6 Average duration of fixations on AOI "disruptive person" (during disruption)
+#### 2.2.6 Average duration of fixations (AOI disruptive person)
 ```{r dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-##################### AVERAGE DURATION ON AOI DISRUPTIVE PERSON ########################
+##################### AVERAGE DURATIONS ON AOI DISRUPTIVE PERSON ########################
 
@@
 
-# N, M, SD, min & max number of fixation on AOI "disruptive person"
+# N, M, SD, min & max average duration of fixations in milliseconds (AOI disruptive person)"
 dur.disrup.table <-
@@
     N = n(),
-    "M" = round(mean(Average_duration_disrup), digits = 2),
-    "SD" = round(sd(Average_duration_disrup), digits = 2),
-    "Min" = round(min(Average_duration_disrup), digits = 2),
-    "Max" = round(max(Average_duration_disrup), digits = 2)
+    "M in ms" = round(mean(Average_duration_disrup), digits = 2),
+    "SD in ms" = round(sd(Average_duration_disrup), digits = 2),
+    "Min in ms" = round(min(Average_duration_disrup), digits = 2),
+    "Max in ms" = round(max(Average_duration_disrup), digits = 2)
   )
@@
 knitr::kable(dur.disrup.table,
-             caption = "N, M, SD, min & max average duration of fixation on AOI disruptive person (during disruption)")
+             caption = "N, M, SD, min & max average duration of fixations in milliseconds (AOI disruptive person)")
 
@@
   scale_fill_brewer(palette  = "RdBu") + 
-  ggtitle("Average duration of fixation AOI\n`disruptive person`") +
+  ggtitle("Average duration of fixations\n(AOI disruptive person)") +
   theme_cowplot() +
@@
 
-#### t-test & effect size "Average duration of fixation on AOI disruptive person"
+#### t-test & effect size "Average duration of fixations" (AOI disruptive person)
 ```{r _disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.1 GRI (micro-teaching unit)
+#### 2.2.7 Gaze Relational Index (GRI; micro-teaching unit)
 ```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 df_aoi_sum %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select (
-    Group,
-    Participant,
-    starts_with("Total_duration_of_fixations"),
-    starts_with("Number_of_fixations"),
-    !"Total_duration_of_fixations.Disruptive_Person",
-    !"Number_of_fixations.Disruptive_Person"
-  ) %>%
-  rowwise() %>%
-  transmute(
-    Group = Group,
-    Participant = Participant,
-    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
-  ) %>%
+  group_by(Group) %>% 
   mutate(
-    GRI = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
-    Group = as_factor(Group)
-  ) %>%
-  drop_na() -> df_gri
+    GRI = round(Average_duration_calc / Sum_number_fixation, digits = 2),
+    )-> df_gri
 
 # N, M, SD, min & max number of fixation (micro-teaching unit)
-nof.table <-
-  df_aoi_sum %>%
+gri.table <-
+  df_gri %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M" = round(mean(Sum_number_fixation), digits = 2),
-    "SD" = round(sd(Sum_number_fixation), digits = 2),
-    "Min" = round(min(Sum_number_fixation), digits = 2),
-    "Max" = round(max(Sum_number_fixation), digits = 2)
-  )
-
-knitr::kable(nof.table,
-             caption = "N, M, SD, min & max number of fixation (micro-teaching unit)")
+    "M" = round(mean(GRI), digits = 2),
+    "SD" = round(sd(GRI), digits = 2),
+    "Min" = round(min(GRI), digits = 2),
+    "Max" = round(max(GRI), digits = 2)
+  )
+
+knitr::kable(gri.table,
+             caption = "N, M, SD, min & max GRI (micro-teaching unit)")
 
 # plotting number of fixations on ALL AOIS
-df_aoi_sum %>%
-  ggplot(mapping = aes(x = Group, y = Sum_number_fixation)) +
+df_gri %>%
+  ggplot(mapping = aes(x = Group, y = GRI)) +
   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
@@
   ) +
-  ylim(0, 2500) +
-  labs(x = "", y = "Number of fixation") +
+  ylim(0, 1) +
+  labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
   scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Number of fixation\n(micro-teaching unit)") +
+  ggtitle("GRI\n(micro-teaching unit)") +
   theme_cowplot() +
-  theme(legend.position = "none") -> plot_number_group
-
-plot_number_group
+  theme(legend.position = "none") -> plot_gri_group
+
+plot_gri_group
+
+```
+
+#### t-test & effect size "GRI" (micro-teaching unit)
+```{r gri_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# GRI (mirco-teaching unit)
+# t-test for expertise differences
+t.test(x = df_gri$GRI[df_gri$Group == "Expert"],
+       y = df_gri$GRI[df_gri$Group == "Novice"],
+       var.equal = TRUE)
+
+# GRI (mirco-teaching unit) 
+# effect size for expertise differences
+d_gri_all <- CohenD(x = df_gri$GRI[df_gri$Group == "Expert"],
+                        y = df_gri$GRI[df_gri$Group == "Novice"],
+                        na.rm = TRUE)
+
+round(d_gri_all, 2)
+
+```
+
+#### 2.2.8 Gaze Relational Index (GRI; AOI students)
+```{r gri_stud, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### GRI on AOI students ########################
+
+# filter group, participants, total duration & number fixation on AOI students
+df_aoi_stud %>%
+  group_by(Group) %>% 
+  mutate(
+    GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2),
+    )-> df_gri_stud
+
+# N, M, SD, min & max GRI (AOI students)
+gri.stud.table <-
+  df_gri_stud %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(GRI_stud), digits = 2),
+    "SD" = round(sd(GRI_stud), digits = 2),
+    "Min" = round(min(GRI_stud), digits = 2),
+    "Max" = round(max(GRI_stud), digits = 2)
+  )
+
+knitr::kable(gri.stud.table,
+             caption = "N, M, SD, min & max GRI (AOI students)")
+
+# plotting GRI on AOI students
+df_gri_stud %>%
+  ggplot(mapping = aes(x = Group, y = GRI_stud)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  ylim(0, 2.5) +
+  labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("GRI\n(AOI students)") +
+  theme_cowplot() +
+  theme(legend.position = "none") -> plot_gri_stud
+
+plot_gri_stud
+
+```
+
+#### t-test & effect size "GRI" (AOI students)
+```{r gri_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# GRI (AOI students)
+# t-test for expertise differences
+t.test(x = df_gri_stud$GRI_stud[df_gri_stud$Group == "Expert"],
+       y = df_gri_stud$GRI_stud[df_gri_stud$Group == "Novice"],
+       var.equal = TRUE)
+
+# GRI (AOI students) 
+# effect size for expertise differences
+d_gri_stud <- CohenD(x = df_gri_stud$GRI_stud[df_gri_stud$Group == "Expert"],
+                     y = df_gri_stud$GRI_stud[df_gri_stud$Group == "Novice"],
+                     na.rm = TRUE)
+
+round(d_gri_stud, 2)
+
+```
+
+#### 2.2.9 Gaze Relational Index (GRI; AOI disruptive person)
+```{r gri_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### GRI on AOI students ########################
+
+# filter
+df_aoi_disrup %>%
+  group_by(Group) %>% 
+  mutate(
+    GRI_disrup = round(Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2),
+    )-> df_gri_disrup
+
+# N, M, SD, min & max GRI (AOI disruptive person)
+gri.disrup.table <-
+  df_gri_disrup %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(GRI_disrup), digits = 2),
+    "SD" = round(sd(GRI_disrup), digits = 2),
+    "Min" = round(min(GRI_disrup), digits = 2),
+    "Max" = round(max(GRI_disrup), digits = 2)
+  )
+
+knitr::kable(gri.disrup.table,
+             caption = "N, M, SD, min & max GRI (AOI disruptive person)")
+
+# plotting GRI on AOI disruptive person
+df_gri_disrup %>%
+  ggplot(mapping = aes(x = Group, y = GRI_disrup)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  ylim(0, 25) +
+  labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("GRI\n(AOI disruptive person)") +
+  theme_cowplot() +
+  theme(legend.position = "none") -> plot_gri_disrup
+
+plot_gri_disrup
+
+```
+
+#### t-test & effect size "GRI" (AOI disruptive person)
+```{r gri_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# GRI (AOI disruptive person)
+# t-test for expertise differences
+t.test(x = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Expert"],
+       y = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Novice"],
+       var.equal = TRUE)
+
+# GRI (AOI disruptive person)
+# effect size for expertise differences
+d_gri_disrup <- CohenD(x = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Expert"],
+                       y = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Novice"],
+                       na.rm = TRUE)
+
+round(d_gri_disrup, 2)
+
+```
+
+#### 2.2.10 Time to first fixation in seconds (AOI disruptive person)
+```{r ttff_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+############### TIME TO FIRST FIXATION ####################
+
+df_aoi %>% 
+  filter(TOI == "Lesson") %>% 
+  dplyr::select (Group,
+          "Time_to_first_fixation.Disruptive_Person") %>% 
+  rowwise() %>% 
+  mutate(Group = as_factor(Group)) -> df_ttff_disrup
+
+# changing milliseconds into seconds
+df_ttff_disrup$Disrup_time_fixation_sec <-
+  round(df_ttff_disrup$Time_to_first_fixation.Disruptive_Person / 1000,
+        digits = 2)
+
+# M, SD, min, max time to first fixation "Disruptive Person"
+ttff.disrup.table <-
+  df_ttff_disrup %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M in sec" = round(mean(Disrup_time_fixation_sec), digits = 2),
+    "SD in sec" = round(sd(Disrup_time_fixation_sec), digits = 2),
+    "Min in sec" = round(min(Disrup_time_fixation_sec), digits = 2),
+    "Max in sec" = round(max(Disrup_time_fixation_sec), digits = 2)
+  )
+
+knitr::kable(ttff.disrup.table,
+             caption = "N, M, SD, min & max time to first fixation in seconds (AOI disruptive person)")
+
+##################### plotting time to first fixation for groups ##################### 
+plot_time_disrup <- 
+  ggplot(data = df_ttff_disrup,
+         mapping = aes(x = Group,
+                       y = Disrup_time_fixation_sec)) +
+ geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  ylim(0,350) +
+  labs(x ="",
+       y = "Seconds") + 
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("Time to first fixation\n(AOI disruptive person)") +
+  theme_cowplot() +
+  theme(legend.position="none")
+
+plot_time_disrup
+```
+
+#### t-test & effect size "Time to first fixation" (AOI disruptive person)
+```{r ttff_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# TIME TO FIRST FIXATIONS on disruptive person 
+# t-test for expertise differences
+t.test(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
+       y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
+       var.equal = TRUE)
+
+# TIME TO FIRST FIXATIONS on disruptive person 
+# effect size for expertise differences
+d_time_disrup <- CohenD(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
+                    y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
+                    na.rm = TRUE)
+
+round(d_time_disrup, 2)
 

### 2024-08-09 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

@@
 ```
+
+## 3. Correlations
+
+```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}
+
+# demo data 
+df_demo <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
+  filter(!LI06_05 == 201,
+         !LI06_05 == 223,
+         !LI06_05 == 232) %>% # exclude participant due to missing eye tracking data
+  transmute(ID = LI06_05,
+            Gender = LI02_01_1,
+            Age = LI03_01,
+            `Teaching Experience` = LI04_01,
+            )
+
+# average duration & number fixation (micro-teaching unit)
+df_aoi %>%
+  filter(TOI == "Lesson") %>% 
+  dplyr::select (
+    Group,
+    Participant,
+    starts_with("Total_duration_of_fixations"),
+    starts_with("Number_of_fixations"),
+    starts_with("Average_duration"),
+    !"Total_duration_of_fixations.Disruptive_Person",
+    !"Number_of_fixations.Disruptive_Person",
+    !"Average_duration_of_fixations.Disruptive_Person"
+  ) %>%
+  rowwise() %>%
+  transmute(
+    Group = Group,
+    Participant = Participant,
+    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
+    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
+  ) %>%
+  mutate(
+    Average_duration_calc = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
+    Group = as_factor(Group)
+  ) %>%
+  drop_na() -> df_aoi_sum
+
+# create a big data frame with all measures
+
+```

### 2024-08-12 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

--- 2024-08-08 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
@@
   mutate(
-    Average_duration_calc = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
+    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
     Group = as_factor(Group)
@@
     N = n(),
-    "M in ms" = round(mean(Average_duration_calc), digits = 2),
-    "SD in ms" = round(sd(Average_duration_calc), digits = 2),
-    "Min in ms" = round(min(Average_duration_calc), digits = 2),
-    "Max in ms" = round(max(Average_duration_calc), digits = 2)
+    "M in ms" = round(mean(Average_duration_mtu), digits = 2),
+    "SD in ms" = round(sd(Average_duration_mtu), digits = 2),
+    "Min in ms" = round(min(Average_duration_mtu), digits = 2),
+    "Max in ms" = round(max(Average_duration_mtu), digits = 2)
     )
@@
   ggplot(mapping = aes(x = Group,
-                       y = Average_duration_calc)) +
+                       y = Average_duration_mtu)) +
   geom_boxplot(mapping = aes(fill = Group),
@@
 # t-test for expertise differences
-t.test(x = df_aoi_sum$Average_duration_calc[df_aoi_sum$Group == "Expert"],
-       y = df_aoi_sum$Average_duration_calc[df_aoi_sum$Group == "Novice"],
+t.test(x = df_aoi_sum$Average_duration_mtu[df_aoi_sum$Group == "Expert"],
+       y = df_aoi_sum$Average_duration_mtu[df_aoi_sum$Group == "Novice"],
        var.equal = TRUE)
@@
 # effect size for expertise differences
-d_aver_all <- CohenD(x = df_aoi_sum$Average_duration_calc[df_aoi_sum$Group == "Expert"],
-                     y = df_aoi_sum$Average_duration_calc[df_aoi_sum$Group == "Novice"],
+d_aver_all <- CohenD(x = df_aoi_sum$Average_duration_mtu[df_aoi_sum$Group == "Expert"],
+                     y = df_aoi_sum$Average_duration_mtu[df_aoi_sum$Group == "Novice"],
                     na.rm = TRUE)
@@
   mutate(
-    GRI = round(Average_duration_calc / Sum_number_fixation, digits = 2),
+    GRI = round(Average_duration_mtu / Sum_number_fixation, digits = 2),
     )-> df_gri
@@
 ```
+
+## 3. Correlations
+
+```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}
+
+# demo data 
+df_demo <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
+  filter(!LI06_05 == 201,
+         !LI06_05 == 223,
+         !LI06_05 == 232) %>% # exclude participant due to missing eye tracking data
+  transmute(Participant = LI06_05,
+            Gender = LI02_01_1,
+            Age = LI03_01,
+            `Teaching Experience` = LI04_01,
+            )
+
+# average duration, number fixation, GRI (micro-teaching unit)
+df_aoi %>%
+  filter(TOI == "Lesson") %>% 
+  dplyr::select (
+    Participant,
+    starts_with("Total_duration_of_fixations"),
+    starts_with("Number_of_fixations"),
+    starts_with("Average_duration"),
+    !"Total_duration_of_fixations.Disruptive_Person",
+    !"Number_of_fixations.Disruptive_Person",
+    !"Average_duration_of_fixations.Disruptive_Person"
+  ) %>%
+  rowwise() %>%
+  transmute(
+    Participant = Participant,
+    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
+    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
+  ) %>%
+  mutate(
+    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
+    GRI_mtu = round(Average_duration_mtu / Sum_number_fixation, digits = 2)) %>%
+  drop_na() %>% 
+  dplyr::select(Participant,
+         Sum_number_fixation, 
+         Average_duration_mtu,
+         GRI_mtu) -> df_aoi_numb_dur
+
+# average duration, number fixation, GRI (AOI student)
+df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select (
+    Participant,
+    "Total_duration_of_fixations.Anna",
+    "Total_duration_of_fixations.Bianca",
+    "Total_duration_of_fixations.Carl(a)",
+    "Number_of_fixations.Anna",
+    "Number_of_fixations.Bianca",
+    "Number_of_fixations.Carl(a)"
+  ) %>%
+  rowwise() %>%
+  transmute(
+    Participant = Participant,
+    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
+  ) %>%
+  mutate(
+    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
+    GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2)
+    ) %>% 
+  dplyr::select(Participant,
+         Stud_number_fixation,
+         Average_duration_stud,
+         GRI_stud
+         )-> df_aoi_stud
+
+# average duration, number fixation, GRI (AOI disruptive person)
+df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select(Participant,
+                "Total_duration_of_fixations.Disruptive_Person",
+                "Number_of_fixations.Disruptive_Person"
+                ) %>%
+  rowwise() %>%
+  mutate(
+    Average_duration_disrup = round(
+      Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person,
+      digits = 0),
+    GRI_disrup = round(
+      Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2)) %>% 
+  dplyr::select(Participant,
+                Number_of_fixations.Disruptive_Person,
+                Average_duration_disrup,
+                GRI_disrup
+                ) -> df_aoi_disrup
+
+# time to first fixatoin (AOI disruptive person)
+df_aoi %>% 
+  filter(TOI == "Lesson") %>% 
+  dplyr::select (Participant,
+                 "Time_to_first_fixation.Disruptive_Person") %>% 
+  rowwise() -> df_ttff_disrup
+
+# rating scales
+df_sri <-
+  excel_sheets("data/Coding_SRI.xlsx") %>%
+  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+  filter(
+    !ID %in% c(201,
+               223,
+               232),
+    !disruption_appraisal == -100,
+    !confidence_appraisal == -100,
+    !disruption_appraisal == -99,
+    !confidence_appraisal == -99,
+    !disruption_appraisal == -88,
+    !confidence_appraisal == -88,
+    !prevalence_rating == -100,
+    !prevalence_rating == -99,
+    !prevalence_rating == -88
+    ) %>% 
+  rename(Participant = ID) %>%
+  group_by(Participant) %>% 
+  summarise(
+    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
+    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
+    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
+    )%>% 
+  dplyr::select(Participant,
+                Mean_disrupption_appraisal,
+                Mean_confidence_appraisal,
+                Mean_prevalence_rating)
+
+# sjt
+df_sjt <-
+  read_excel("./data/SJT.xlsx") %>%
+  dplyr::select(UI06_05, # Participant
+                SJT_AL_gek, # Monitoring
+                SJT_ST_gek, # Managing momentum
+                SJT_R_gek, # Rules and routines
+                SJT_KF_gek) %>% # All
+  filter(!UI06_05 %in% c(201, 223, 232)) %>%  # exclude ID with no eye tracking data
+  transmute(
+    Participant = UI06_05,
+    SJT_Monitoring = round(SJT_AL_gek, 2),
+    SJT_Managing_momentum = round(SJT_ST_gek, 2),
+    SJT_Rules_routines = round(SJT_R_gek, 2),
+    SJT_All = round(SJT_KF_gek, 2)
+  )
+
+# classroom questionnaire
+df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  dplyr::select(LI06_05, 
+                LM01_01:LM01_08, # classroom management
+                LP01_01:LP01_08) %>% # non- & paraverbal communication
+  filter(!LI06_05 %in% c(201, 223, 232)) %>% # exclude ID with no eye tracking data
+  rename(Participant = LI06_05) %>% 
+  group_by(Participant) %>% 
+  transmute(Participant = Participant,
+            "Quest_All" = round(mean(c_across(starts_with("L")), na.rm = TRUE), 2),
+            "Quest_classroom_management" = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
+            "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2)
+            )
+
+# create a big data frame with all measures 
+#put all data frames into list
+df_list <- list(df_demo,
+                  df_aoi_numb_dur,
+                  df_aoi_stud,
+                  df_aoi_disrup,
+                  df_sri,
+                  df_sjt,
+                  df_quest)
+
+#merge all data frames in list
+df_merge <-
+  df_list %>% reduce(full_join, by='Participant')
+
+```

### 2024-08-13 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

@@
       formattable,
-      psych)
+      psych,
+      apaTables)
 
@@
 ## 3. Correlations
-
 ```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}
@@
 df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LI06_05, 
-                LM01_01:LM01_08, # classroom management
+  dplyr::select(LI06_05, LM01_01:LM01_08, # classroom management
                 LP01_01:LP01_08) %>% # non- & paraverbal communication
@@
   group_by(Participant) %>%
-  transmute(Participant = Participant,
-            "Quest_All" = round(mean(c_across(starts_with("L")), na.rm = TRUE), 2),
-            "Quest_classroom_management" = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
-            "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2)
+  transmute(
+    Participant = Participant,
+    "Quest_All" = round(mean(c_across(starts_with(
+      "L"
+    )), na.rm = TRUE), 2),
+    "Quest_classroom_management" = round(mean(c_across(starts_with(
+      "LM"
+    )), na.rm = TRUE), 2),
+    "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with(
+      "LP"
+    )), na.rm = TRUE), 2)
   )
@@
 # create a big data frame with all measures 
-#put all data frames into list
+# put all data frames into list
 df_list <- list(df_demo,
@@
 
-#merge all data frames in list
+# merge all data frames in list
 df_merge <-
-  df_list %>% reduce(full_join, by='Participant')
-
-```
+  df_list %>% reduce(full_join, by='Participant') %>% 
+  dplyr::select(.,
+                -"Participant")
+
+# create a correlation matrix
+cor_tab <- 
+  df_merge %>% 
+  cor(method = "spearman") %>% 
+  round(., digits = 2)
+
+# create a scatter plot 
+# pairs(~ Gender + 
+#         Age + 
+#         `Teaching Experience` + 
+#         Sum_number_fixation + 
+#         Stud_number_fixation + 
+#         Number_of_fixations.Disruptive_Person + 
+#         Average_duration_mtu + 
+#         Average_duration_stud + 
+#         Average_duration_disrup + 
+#         GRI_mtu + 
+#         GRI_stud + 
+#         GRI_disrup + 
+#         Mean_disrupption_appraisal + 
+#         Mean_confidence_appraisal + 
+#         Mean_prevalence_rating + 
+#         SJT_Monitoring + 
+#         SJT_Managing_momentum + 
+#         SJT_Rules_routines + 
+#         SJT_All + 
+#         Quest_classroom_management + 
+#         Quest_non_paraverbal_communication + 
+#         Quest_All,
+#       upper.panel = NULL,
+#       pch = 20,
+#       cex = 3, 
+#       main = "Correlation Table Expertise Measures",
+#       col = Gender)
+
+# apa.cor.table(cor_tab)
+
+```

### 2024-08-14 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
Code für submission

@@
 
+```{r regressions, include=FALSE}
+
+# multiple bpm values (merged data frame for multiple regression with multiple measurement points)
+main_multiple_hr <-
+  left_join(main_single_hr,
+            df_merge,
+            by = "ID")
+
+main_multiple_hr %>% 
+  group_by(ID, time_span) %>% 
+  summarise(disruption_factor = mean(disruption_factor,
+                                     na.rm = T),
+            confidence_factor = mean(confidence_factor,
+                                     na.rm = T),
+            teaching_experience = mean(teaching_experience),
+            heart_rate = mean(heart_rate_std)
+            ) %>% 
+  ungroup() -> data_regression_mean
+
+# ## using lavaan package to get std. regression coefficients 
+# MLRModel <- 'heart_rate ~ teaching_experience
+#              heart_rate ~ 1'
+# 
+# output <- sem(model = MLRModel, data = data_regression_mean)
+# summary(output, standardized = TRUE)
+
+## loop for regression model
+for (i in unique(data_regression_mean$time_span)) {
+
+  cache <- data_regression_mean %>% 
+    filter(time_span == i)
+
+  regr1 <-
+    lm(heart_rate ~ teaching_experience,
+    data = cache) %>% 
+    lm.beta()
+
+  assign(value = regr1,
+         x = paste0("regr_", i, "1"))
+
+  regr2 <-
+    lm(heart_rate ~ teaching_experience + disruption_factor,
+    data = cache) %>% 
+    lm.beta()
+
+  assign(value = regr2,
+         x = paste0("regr_", i, "2"))
+
+  regr3 <-
+    lm(heart_rate ~ teaching_experience + confidence_factor,
+    data = cache) %>% 
+    lm.beta()
+
+  assign(value = regr3,
+         x = paste0("regr_", i, "3"))
+
+  regr4 <-
+    lm(heart_rate ~ teaching_experience + disruption_factor + confidence_factor,
+    data = cache) %>% 
+    lm.beta()
+
+  assign(value = regr4,
+         x = paste0("regr_", i, "4"))
+
+}
+
+summary(regr_preparation1)
+summary(regr_preparation2)
+summary(regr_preparation3)
+summary(regr_preparation4)
+summary(regr_teaching1)
+summary(regr_teaching2)
+summary(regr_teaching3)
+summary(regr_teaching4)
+summary(regr_post1)
+summary(regr_post2)
+summary(regr_post3)
+summary(regr_post4)
+summary(regr_interview1)
+summary(regr_interview2)
+summary(regr_interview3)
+summary(regr_interview4)
+summary(regr_end1)
+summary(regr_end2)
+summary(regr_end3)
+summary(regr_end4)
+
+```
+
 ```{=latex}

### 2024-08-21 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

@@
   read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
-  filter(!LI06_05 == 201) %>% # exclude participant due to missing eye tracking data
+  filter(!LI06_05 == 201,
+         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
   transmute(Group = LI06_05,
@@
 df_aoi <- df_aoi %>%
-  filter(!Participant == 223,
-         !Participant == 232)
+  filter(!Participant == 223)
 
@@
 
-XXX 223 (ist eine Doppelung der 214) & 232 (enthält NAs) sind fehlerhaft --> Daten nochmal komplett neu ziehen!! XXX
+XXX 223 (ist eine Doppelung der 214) --> Daten nochmal komplett neu ziehen!! XXX
 
@@
 )
+
+round(d_aver_stud, 2)
 

### 2024-08-27 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper
Update expertise_2024_07_19_MK.Rmd

@@
                    TOI,
+                   Duration_of_interval,
                    starts_with("Total_duration_of_fixations"),
@@
 ```
-
-XXX 223 (ist eine Doppelung der 214) --> Daten nochmal komplett neu ziehen!! XXX
 
@@
     Participant,
+    Duration_of_interval,
     starts_with("Total_duration_of_fixations"),
@@
     Participant = Participant,
+    Duration_of_interval = Duration_of_interval, 
+    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
     Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
-    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
-  ) %>%
-  mutate(
+    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
     Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
+    Number_fixation_msec_mtu = round(Sum_number_fixation / Duration_of_interval, digits = 6),
+    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
     Group = as_factor(Group)
@@
 
-# N, M, SD, min & max number of fixation (micro-teaching unit)
+# N, M, SD, min & max number of fixation per minute (micro-teaching unit)
 nof.table <-
@@
     N = n(),
-    "M" = round(mean(Sum_number_fixation), digits = 2),
-    "SD" = round(sd(Sum_number_fixation), digits = 2),
-    "Min" = round(min(Sum_number_fixation), digits = 2),
-    "Max" = round(max(Sum_number_fixation), digits = 2)
+    "M" = round(mean(Number_fixation_min_mtu), digits = 2),
+    "SD" = round(sd(Number_fixation_min_mtu), digits = 2),
+    "Min" = round(min(Number_fixation_min_mtu), digits = 2),
+    "Max" = round(max(Number_fixation_min_mtu), digits = 2)
   )
@@
 knitr::kable(nof.table,
-             caption = "N, M, SD, min & max number of fixations (micro-teaching unit)")
+             caption = "N, M, SD, min & max number of fixation per minute (micro-teaching unit)")
 
@@
 df_aoi_sum %>%
-  ggplot(mapping = aes(x = Group, y = Sum_number_fixation)) +
+  ggplot(mapping = aes(x = Group, y = Number_fixation_min_mtu)) +
   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
@@
   ) +
-  ylim(0, 2500) +
-  labs(x = "", y = "Number of fixations") +
+  ylim(0, 150) +
+  labs(x = "", y = "Number of fixations per minute") +
   scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Number of fixation\n(micro-teaching unit)") +
+  ggtitle("Number of fixations per minute\n(micro-teaching unit)") +
   theme_cowplot() +
@@
 t.test(
-  x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
-  y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
+  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
+  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
   var.equal = TRUE
@@
 d_number_all <- CohenD(
-  x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
-  y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
+  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
+  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
   na.rm = TRUE
@@
     Group,
+    Duration_of_interval,
     Participant,
@@
   transmute(
-    Group = Group,
+    Group = as_factor(Group),
+    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
     Participant = Participant,
     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
-  ) %>%
-  mutate(
-    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
-    Group = as_factor(Group)
+    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Stud_number_fixation_sec = round(Duration_of_interval_sec / Stud_number_fixation, digits = 2),
+    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0)
     ) -> df_aoi_stud
@@
     N = n(),
-    "M" = round(mean(Stud_number_fixation), digits = 2),
-    "SD" = round(sd(Stud_number_fixation), digits = 2),
-    "Min" = round(min(Stud_number_fixation), digits = 2),
-    "Max" = round(max(Stud_number_fixation), digits = 2)
+    "M" = round(mean(Stud_number_fixation_sec), digits = 2),
+    "SD" = round(sd(Stud_number_fixation_sec), digits = 2),
+    "Min" = round(min(Stud_number_fixation_sec), digits = 2),
+    "Max" = round(max(Stud_number_fixation_sec), digits = 2)
   )
@@
 knitr::kable(nof.stud.table,
-             caption = "N, M, SD, min & max number of fixations (AOI students)")
+             caption = "N, M, SD, min & max number of fixations per second (AOI students)")
 
@@
 df_aoi_stud %>%
-  ggplot(mapping = aes(x = Group, y = Stud_number_fixation)) +
+  ggplot(mapping = aes(x = Group, y = Stud_number_fixation_sec)) +
   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
@@
   ) +
-  labs(x = "", y = "Number of fixations") +
+  ylim(0, 4) + 
+  labs(x = "", y = "Number of fixations per seconds") +
   scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Number of fixations\n(AOI students)") +
+  ggtitle("Number of fixations per second\n(AOI students)") +
   theme_cowplot() +
@@
 # t-test for expertise differences
-t.test(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
-       y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
+t.test(x = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Expert"],
+       y = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Novice"],
        var.equal = TRUE)
@@
 # effect size for expertise differences
-d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
-                      y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
+d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Expert"],
+                      y = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Novice"],
                       na.rm = TRUE)
@@
   mutate(
-    GRI = round(Average_duration_mtu / Sum_number_fixation, digits = 2),
+    GRI = round(Average_duration_mtu / Number_fixation_msec_mtu, digits = 2),
     )-> df_gri
@@
   filter(!LI06_05 == 201,
-         !LI06_05 == 223,
-         !LI06_05 == 232) %>% # exclude participant due to missing eye tracking data
+         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
   transmute(Participant = LI06_05,
@@
     !ID %in% c(201,
-               223,
-               232),
+               223),
     !disruption_appraisal == -100,
@@
                 SJT_KF_gek) %>% # All
-  filter(!UI06_05 %in% c(201, 223, 232)) %>%  # exclude ID with no eye tracking data
+  filter(!UI06_05 %in% c(201, 223)) %>%  # exclude ID with no eye tracking data
   transmute(
@@
                 LP01_01:LP01_08) %>% # non- & paraverbal communication
-  filter(!LI06_05 %in% c(201, 223, 232)) %>% # exclude ID with no eye tracking data
+  filter(!LI06_05 %in% c(201, 223)) %>% # exclude ID with no eye tracking data
   rename(Participant = LI06_05) %>%
@@
   df_merge %>% 
-  cor(method = "spearman") %>% 
+  cor(method = "pearson") %>% 
   round(., digits = 2)

### 2024-08-28 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

@@
 
-#### 2.2.1 Number of fixation (micro-teaching unit)
+#### 2.2.1 Number of fixations per minute (micro-teaching unit)
 ```{r nof_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-# NUMBER OF FIXATIONS on all AOIs 
+# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit) 
 # t-test for expertise differences
@@
 
-# NUMBER OF FIXATIONS on all AOIs
+# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit)
 # effect size for expertise differences
@@
 
-#### 2.2.2 Number of fixations (AOI students)
+#### 2.2.2 Number of fixations per second (AOI students)
 ```{r nof_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
   ylim(0, 4) + 
-  labs(x = "", y = "Number of fixations per seconds") +
+  labs(x = "", y = "Number of fixations per second") +
   scale_fill_brewer(palette  = "RdBu") +

### 2024-08-29 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

@@
     Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
+    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
@@
     Number_fixation_msec_mtu = round(Sum_number_fixation / Duration_of_interval, digits = 6),
+    Number_fixation_sec_mtu = round(Sum_number_fixation / Duration_of_interval_sec, digits = 2),
     Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
@@
     N = n(),
-    "M" = round(mean(Number_fixation_min_mtu), digits = 2),
-    "SD" = round(sd(Number_fixation_min_mtu), digits = 2),
-    "Min" = round(min(Number_fixation_min_mtu), digits = 2),
-    "Max" = round(max(Number_fixation_min_mtu), digits = 2)
+    "M" = round(mean(Number_fixation_sec_mtu), digits = 2),
+    "SD" = round(sd(Number_fixation_sec_mtu), digits = 2),
+    "Min" = round(min(Number_fixation_sec_mtu), digits = 2),
+    "Max" = round(max(Number_fixation_sec_mtu), digits = 2)
   )
@@
     Group = as_factor(Group),
+    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
     Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
@@
     Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Stud_number_fixation_min = round(Duration_of_interval_min / Stud_number_fixation, digits = 2),
     Stud_number_fixation_sec = round(Duration_of_interval_sec / Stud_number_fixation, digits = 2),
@@
 
-# N, M, SD, min & max number of fixations (AOI students)
-nof.stud.table <-
+# N, M, SD, min & max number of fixations per minute (AOI students)
+nof.min.stud.table <-
+  df_aoi_stud %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Stud_number_fixation_min), digits = 2),
+    "SD" = round(sd(Stud_number_fixation_min), digits = 2),
+    "Min" = round(min(Stud_number_fixation_min), digits = 2),
+    "Max" = round(max(Stud_number_fixation_min), digits = 2)
+  )
+
+knitr::kable(nof.min.stud.table,
+             caption = "N, M, SD, min & max number of fixations per minute (AOI students)")
+
+# plotting number of fixations per minute on AOI Students
+df_aoi_stud %>%
+  ggplot(mapping = aes(x = Group, y = Stud_number_fixation_min)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  ylim(0, 0.10) + 
+  labs(x = "", y = "Number of fixations per minute") +
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("Number of fixations per minute\n(AOI students)") +
+  theme_cowplot() +
+  theme(legend.position = "none") -> plot_number_min_stud
+
+plot_number_min_stud
+
+####################### SECONDS #######################
+
+# N, M, SD, min & max number of fixations per seconds (AOI students)
+nof.sec.stud.table <-
   df_aoi_stud %>%
@@
 
-knitr::kable(nof.stud.table,
-             caption = "N, M, SD, min & max number of fixations per second (AOI students)")
-
-# plotting average duration on AOI Students
+knitr::kable(nof.sec.stud.table,
+             caption = "N, M, SD, min & max number of fixations per seconds (AOI students)")
+
+# plotting number of fixations per seconds on AOI Students
 df_aoi_stud %>%
@@
   theme_cowplot() +
-  theme(legend.position = "none") -> plot_number_stud
-
-plot_number_stud
+  theme(legend.position = "none") -> plot_number_sec_stud
+
+plot_number_sec_stud
 

### 2024-09-02 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
plot gefixed

@@
       width = 0.1,
-      height = 0.1
+      height = 0.001
     )
   ) +
-  ylim(0, 0.10) + 
+ # ylim(0, 0.10) + 
   labs(x = "", y = "Number of fixations per minute") +

### 2024-09-02 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

--- 2024-08-29 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
@@
                    Duration_of_interval,
+                   Start_of_interval,
                    starts_with("Total_duration_of_fixations"),
@@
     N = n(),
-    "M" = round(mean(Number_fixation_sec_mtu), digits = 2),
-    "SD" = round(sd(Number_fixation_sec_mtu), digits = 2),
-    "Min" = round(min(Number_fixation_sec_mtu), digits = 2),
-    "Max" = round(max(Number_fixation_sec_mtu), digits = 2)
+    "M" = round(mean(Number_fixation_min_mtu), digits = 2),
+    "SD" = round(sd(Number_fixation_min_mtu), digits = 2),
+    "Min" = round(min(Number_fixation_min_mtu), digits = 2),
+    "Max" = round(max(Number_fixation_min_mtu), digits = 2)
   )
@@
 
-#### 2.2.2 Number of fixations per second (AOI students)
+#### 2.2.2 Number of fixations per minute (AOI students)
 ```{r nof_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
     Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Stud_number_fixation_min = round(Duration_of_interval_min / Stud_number_fixation, digits = 2),
-    Stud_number_fixation_sec = round(Duration_of_interval_sec / Stud_number_fixation, digits = 2),
+    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, digits = 2),
+    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, digits = 2),
     Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0)
@@
       width = 0.1,
-      height = 0.1
+      height = 0.005
     )
   ) +
-  ylim(0, 0.10) + 
+  ylim(0, 50) +
   labs(x = "", y = "Number of fixations per minute") +
@@
 
-####################### SECONDS #######################
-
-# N, M, SD, min & max number of fixations per seconds (AOI students)
-nof.sec.stud.table <-
-  df_aoi_stud %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(Stud_number_fixation_sec), digits = 2),
-    "SD" = round(sd(Stud_number_fixation_sec), digits = 2),
-    "Min" = round(min(Stud_number_fixation_sec), digits = 2),
-    "Max" = round(max(Stud_number_fixation_sec), digits = 2)
-  )
-
-knitr::kable(nof.sec.stud.table,
-             caption = "N, M, SD, min & max number of fixations per seconds (AOI students)")
-
-# plotting number of fixations per seconds on AOI Students
-df_aoi_stud %>%
-  ggplot(mapping = aes(x = Group, y = Stud_number_fixation_sec)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
-  ) +
-  ylim(0, 4) + 
-  labs(x = "", y = "Number of fixations per second") +
-  scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Number of fixations per second\n(AOI students)") +
-  theme_cowplot() +
-  theme(legend.position = "none") -> plot_number_sec_stud
-
-plot_number_sec_stud
-
 ```
@@
 # t-test for expertise differences
-t.test(x = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Expert"],
-       y = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Novice"],
-       var.equal = TRUE)
+t.test(
+  x = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Expert"],
+  y = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Novice"],
+  var.equal = TRUE
+)
 
@@
 # effect size for expertise differences
-d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Expert"],
-                      y = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Novice"],
-                      na.rm = TRUE)
+d_number_stud <- CohenD(
+  x = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Expert"],
+  y = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Novice"],
+  na.rm = TRUE
+)
 
@@
   mutate(
-    GRI = round(Average_duration_mtu / Number_fixation_msec_mtu, digits = 2),
+    GRI = round(Average_duration_mtu / Sum_number_fixation, digits = 2),
     )-> df_gri
@@
 
-#### 2.2.8 Gaze Relational Index (GRI; AOI students)
 ```{r gri_stud, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-##################### GRI on AOI students ########################
-
-# filter group, participants, total duration & number fixation on AOI students
-df_aoi_stud %>%
-  group_by(Group) %>% 
-  mutate(
-    GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2),
-    )-> df_gri_stud
-
-# N, M, SD, min & max GRI (AOI students)
-gri.stud.table <-
-  df_gri_stud %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(GRI_stud), digits = 2),
-    "SD" = round(sd(GRI_stud), digits = 2),
-    "Min" = round(min(GRI_stud), digits = 2),
-    "Max" = round(max(GRI_stud), digits = 2)
-  )
-
-knitr::kable(gri.stud.table,
-             caption = "N, M, SD, min & max GRI (AOI students)")
-
-# plotting GRI on AOI students
-df_gri_stud %>%
-  ggplot(mapping = aes(x = Group, y = GRI_stud)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
-  ) +
-  ylim(0, 2.5) +
-  labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
-  scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("GRI\n(AOI students)") +
-  theme_cowplot() +
-  theme(legend.position = "none") -> plot_gri_stud
-
-plot_gri_stud
-
-```
-
-#### t-test & effect size "GRI" (AOI students)
+# ##################### GRI on AOI students ########################
+# 
+# # filter group, participants, total duration & number fixation on AOI students
+# df_aoi_stud %>%
+#   group_by(Group) %>% 
+#   mutate(
+#     GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2),
+#     )-> df_gri_stud
+# 
+# 
+# # N, M, SD, min & max GRI (AOI students)
+# gri.stud.table <-
+#   df_gri_stud %>%
+#   group_by(Group) %>%
+#   summarise(
+#     N = n(),
+#     "M" = round(mean(GRI_stud), digits = 2),
+#     "SD" = round(sd(GRI_stud), digits = 2),
+#     "Min" = round(min(GRI_stud), digits = 2),
+#     "Max" = round(max(GRI_stud), digits = 2)
+#   )
+# 
+# knitr::kable(gri.stud.table,
+#              caption = "N, M, SD, min & max GRI (AOI students)")
+# 
+# 
+# # plotting GRI on AOI students
+# df_gri_stud %>%
+#   ggplot(mapping = aes(x = Group, y = GRI_stud)) +
+#   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+#   geom_point(
+#     size = 2,
+#     alpha = 0.7,
+#     position = position_jitter(
+#       seed = 1,
+#       width = 0.1,
+#       height = 0.1
+#     )
+#   ) +
+#   ylim(0, 2.5) +
+#   labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
+#   scale_fill_brewer(palette  = "RdBu") +
+#   ggtitle("GRI\n(AOI students)") +
+#   theme_cowplot() +
+#   theme(legend.position = "none") -> plot_gri_stud
+# 
+# plot_gri_stud
+
+```
+
 ```{r gri_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-# GRI (AOI students)
-# t-test for expertise differences
-t.test(x = df_gri_stud$GRI_stud[df_gri_stud$Group == "Expert"],
-       y = df_gri_stud$GRI_stud[df_gri_stud$Group == "Novice"],
-       var.equal = TRUE)
-
-# GRI (AOI students) 
-# effect size for expertise differences
-d_gri_stud <- CohenD(x = df_gri_stud$GRI_stud[df_gri_stud$Group == "Expert"],
-                     y = df_gri_stud$GRI_stud[df_gri_stud$Group == "Novice"],
-                     na.rm = TRUE)
-
-round(d_gri_stud, 2)
-
-```
-
-#### 2.2.9 Gaze Relational Index (GRI; AOI disruptive person)
+# # GRI (AOI students)
+# # t-test for expertise differences
+# t.test(x = df_gri_stud$GRI_stud[df_gri_stud$Group == "Expert"],
+#        y = df_gri_stud$GRI_stud[df_gri_stud$Group == "Novice"],
+#        var.equal = TRUE)
+# 
+# # GRI (AOI students) 
+# # effect size for expertise differences
+# d_gri_stud <- CohenD(x = df_gri_stud$GRI_stud[df_gri_stud$Group == "Expert"],
+#                      y = df_gri_stud$GRI_stud[df_gri_stud$Group == "Novice"],
+#                      na.rm = TRUE)
+# 
+# round(d_gri_stud, 2)
+
+```
+
 ```{r gri_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-##################### GRI on AOI students ########################
-
-# filter
-df_aoi_disrup %>%
-  group_by(Group) %>% 
-  mutate(
-    GRI_disrup = round(Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2),
-    )-> df_gri_disrup
-
-# N, M, SD, min & max GRI (AOI disruptive person)
-gri.disrup.table <-
-  df_gri_disrup %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(GRI_disrup), digits = 2),
-    "SD" = round(sd(GRI_disrup), digits = 2),
-    "Min" = round(min(GRI_disrup), digits = 2),
-    "Max" = round(max(GRI_disrup), digits = 2)
-  )
-
-knitr::kable(gri.disrup.table,
-             caption = "N, M, SD, min & max GRI (AOI disruptive person)")
-
-# plotting GRI on AOI disruptive person
-df_gri_disrup %>%
-  ggplot(mapping = aes(x = Group, y = GRI_disrup)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
-  ) +
-  ylim(0, 25) +
-  labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
-  scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("GRI\n(AOI disruptive person)") +
-  theme_cowplot() +
-  theme(legend.position = "none") -> plot_gri_disrup
-
-plot_gri_disrup
-
-```
-
-#### t-test & effect size "GRI" (AOI disruptive person)
+# ##################### GRI on AOI students ########################
+# 
+# # filter
+# df_aoi_disrup %>%
+#   group_by(Group) %>% 
+#   mutate(
+#     GRI_disrup = round(Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2),
+#     )-> df_gri_disrup
+# 
+# 
+# # N, M, SD, min & max GRI (AOI disruptive person)
+# gri.disrup.table <-
+#   df_gri_disrup %>%
+#   group_by(Group) %>%
+#   summarise(
+#     N = n(),
+#     "M" = round(mean(GRI_disrup), digits = 2),
+#     "SD" = round(sd(GRI_disrup), digits = 2),
+#     "Min" = round(min(GRI_disrup), digits = 2),
+#     "Max" = round(max(GRI_disrup), digits = 2)
+#   )
+# 
+# knitr::kable(gri.disrup.table,
+#              caption = "N, M, SD, min & max GRI (AOI disruptive person)")
+# 
+# 
+# # plotting GRI on AOI disruptive person
+# df_gri_disrup %>%
+#   ggplot(mapping = aes(x = Group, y = GRI_disrup)) +
+#   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+#   geom_point(
+#     size = 2,
+#     alpha = 0.7,
+#     position = position_jitter(
+#       seed = 1,
+#       width = 0.1,
+#       height = 0.1
+#     )
+#   ) +
+#   ylim(0, 25) +
+#   labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
+#   scale_fill_brewer(palette  = "RdBu") +
+#   ggtitle("GRI\n(AOI disruptive person)") +
+#   theme_cowplot() +
+#   theme(legend.position = "none") -> plot_gri_disrup
+# 
+# plot_gri_disrup
+
+```
+
 ```{r gri_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-# GRI (AOI disruptive person)
-# t-test for expertise differences
-t.test(x = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Expert"],
-       y = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Novice"],
-       var.equal = TRUE)
-
-# GRI (AOI disruptive person)
-# effect size for expertise differences
-d_gri_disrup <- CohenD(x = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Expert"],
-                       y = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Novice"],
-                       na.rm = TRUE)
-
-round(d_gri_disrup, 2)
+# # GRI (AOI disruptive person)
+# # t-test for expertise differences
+# t.test(x = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Expert"],
+#        y = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Novice"],
+#        var.equal = TRUE)
+# 
+# # GRI (AOI disruptive person)
+# # effect size for expertise differences
+# d_gri_disrup <- CohenD(x = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Expert"],
+#                        y = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Novice"],
+#                        na.rm = TRUE)
+# 
+# round(d_gri_disrup, 2)
 
@@
 df_aoi %>% 
-  filter(TOI == "Lesson") %>% 
-  dplyr::select (Group,
-          "Time_to_first_fixation.Disruptive_Person") %>% 
+  filter(TOI %in% c("Chatting_with_neighbour",
+                    "Clicking_pen",
+                    "Drawing",
+                    "Drumming_with_hands",
+                    "Head_on_table",
+                    "Heckling",
+                    "Looking_at_phone",
+                    "Snipping_with_fingers",
+                    "Whispering"
+                    )
+         ) %>% 
+  dplyr::select(Participant,
+                TOI,
+                Time_to_first_fixation.Disruptive_Person,
+                ) %>% 
   rowwise() %>% 
-  mutate(Group = as_factor(Group)) -> df_ttff_disrup
-
-# changing milliseconds into seconds
-df_ttff_disrup$Disrup_time_fixation_sec <-
-  round(df_ttff_disrup$Time_to_first_fixation.Disruptive_Person / 1000,
-        digits = 2)
+  drop_na() %>% 
+  group_by(Participant) %>% 
+  filter(!Time_to_first_fixation.Disruptive_Person == 0,
+         !Time_to_first_fixation.Disruptive_Person > 30000) %>% # cut-off 30sec
+  summarise(N = n(),
+            Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person/N)
+            ) %>% 
+  mutate(Group = ifelse(Participant < 200, "Novice", "Expert"),
+         Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000, 
+                                          digits = 2)) -> df_ttff_disrup # changing milliseconds into seconds
 
@@
                                         height = 0.1)) +
-  ylim(0,350) +
+  ylim(0,14) +
   labs(x ="",
@@
 # insert a table into HTML
-knitr::kable(sjt_mean,
+knitr::kable(sjt_m,
              caption = "N, M and SD for monitoring")
@@
 # insert a table into HTML
-knitr::kable(sjt_mean,
+knitr::kable(sjt_r,
              caption = "N, M and SD for rules and routines")
@@
   transmute(Participant = LI06_05,
-            Gender = LI02_01_1,
-            Age = LI03_01,
             `Teaching Experience` = LI04_01,
@@
   filter(TOI == "Lesson") %>% 
-  dplyr::select (
+  dplyr::select(
+    Duration_of_interval,
     Participant,
@@
     Participant = Participant,
+    Duration_of_interval = Duration_of_interval, 
+    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
     Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
-    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
-  ) %>%
-  mutate(
+    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
     Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
-    GRI_mtu = round(Average_duration_mtu / Sum_number_fixation, digits = 2)) %>%
+    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
+    GRI_mtu = round(Average_duration_mtu / Sum_number_fixation, digits = 2)
+    ) %>%
   drop_na() %>% 
   dplyr::select(Participant,
-         Sum_number_fixation, 
+         Number_fixation_min_mtu, 
          Average_duration_mtu,
@@
     Participant,
+    Duration_of_interval,
     "Total_duration_of_fixations.Anna",
@@
     Participant = Participant,
+    Duration_of_interval = Duration_of_interval,
+    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
-  ) %>%
-  mutate(
+    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Stud_number_fixation_min = round(Duration_of_interval_min / Stud_number_fixation, digits = 2),
     Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
@@
   dplyr::select(Participant,
-         Stud_number_fixation,
+                Stud_number_fixation_min,
                 Average_duration_stud,
-         GRI_stud
-         )-> df_aoi_stud
+                GRI_stud) -> df_aoi_stud
 
@@
 df_aoi %>%
-  filter(TOI == "Lesson") %>% 
-  dplyr::select (Participant,
-                 "Time_to_first_fixation.Disruptive_Person") %>% 
-  rowwise() -> df_ttff_disrup
+  filter(
+    TOI %in% c(
+      "Chatting_with_neighbour",
+      "Clicking_pen",
+      "Drawing",
+      "Drumming_with_hands",
+      "Head_on_table",
+      "Heckling",
+      "Looking_at_phone",
+      "Snipping_with_fingers",
+      "Whispering"
+    )
+  ) %>%
+  dplyr::select(Participant, TOI, Time_to_first_fixation.Disruptive_Person, ) %>%
+  rowwise() %>%
+  drop_na() %>%
+  group_by(Participant) %>%
+  summarise(
+    Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person)
+  ) %>%
+  mutate(
+    Group = ifelse(Participant < 200, "Novice", "Expert"),
+    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000,
+      digits = 2
+    )
+  ) -> df_ttff_disrup
 
@@
   df_list %>% reduce(full_join, by='Participant') %>%
+  # filter(Participant > 200) %>% 
   dplyr::select(.,

### 2024-09-04 02_paper/02_study/01_fitbit paper/analysis_270423.Rmd
fb

@@
          ) +
-  geom_smooth(se = T,
+  geom_smooth(se = F,
               size = 0.5,

### 2024-09-09 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
Tabellen
Format Sachen

@@
 ---
-title: "New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?"
-shorttitle: "Using fitbit to measure teachers' heart rate"
+title: "From heartbeat to data – Using wearable fitness trackers as an affordable approach to assess teacher stress"
+shorttitle: "From heartbeat to data"
 authornote: |
@@
     text: "Supervision"
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  XXX In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress.
-XXX
-
-  <!-- https://tinyurl.com/ybremelq -->
+abstract: "
+Past research on physiological indicators of teacher stress often had to rely on expensive and obtrusive assessment methods.
+Modern fitness trackers represent a non-invasive and convenient alternative.
+This study investigated the use of wrist-worn fitness trackers to assess teacher heart rate (HR) as an indicator of stress during teaching.
+In a laboratory study, we used a Fitbit® fitness tracker to assess teachers´ HR before, during, and after a potentially stressful micro-teaching session.
+Our results demonstrate that the fitness tracker was indeed useful for mapping teachers’ stress, with the data showing how teachers’ HR increased before, peaked during, and progressively decreased after the micro-teaching session.
+Moreover, we related the fitness tracker data to retrospective teacher self-reports.
+We found that teachers’ subjective stress appraisals, together with their teaching experience, explained only small amounts of variance in HR data.
+We discuss the potential of fitness trackers as an affordable and ubiquitous assessment tool for research on teacher stress in the classroom and provide advice for practical implementation."
 keywords: 
+  - teacher stress
+  - fitness tracker
   - heart rate
-  - photoplethysmography
-  - wearable electronic device
-  - teaching
+  - classroom disruptions
+  - wearable technology
+  - physiological stress measurement
 journal: "Computers & Education"
@@
 bibliography: r-references.bib
+csl: computers-and-education.csl
 linenumbers: false
@@
     keep_tex: true
-    citation_package: natbib
 header-includes:
@@
 
-In education, there’s interest in identifying reliable indicators for teacher stress and burnout [@fisher2011; @junker2021].
-Previous research often relied on self-report questionnaires [@chaplain2008; @liu2020], which may be prone to biases like social desirability [@razavi2001self] or recall errors [@van2016accuracy].
-To overcome these limitations, ambulatory assessment methods are recommended [@trull2013ambulatory; @wettstein2020ambulatory], such as measuring physiological parameters like heart rate (HR), offering objective insights into teachers’ stress levels without disrupting their teaching [@donker2018; @runge2020].
-
-Current studies on teachers’ HR in teaching settings often rely on expensive and invasive electrocardiographs [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021; @huang2022class], showing that teacher-centered activities and common stressors lead to increased HR.
-However, using affordable and non-invasive instruments like wrist-worn fitness trackers [@ferguson2015] could enhance HR recording in educational contexts.
-Unlike clinical devices, fitness trackers could offer continuous and less intrusive data collection over time [@godfrey2018z], aligning with the increasing popularity and acceptance of wearables among the general population [@peng2022acceptance].
-These devices, equipped with biosensors, provide users with physiological and behavioral data, offering an accessible means for monitoring physical activity and health in daily life.
-
-It can be assumed that teachers also wear personal, private fitness trackers, generating recordings of physiological data that could be a very interesting resource for research on teacher stress.
-While the use of wearable technology in the field has been explored in various domains [@hughes2023wearable; @ adesida2019exploring; helmer2009smart], research is sparse in educational contexts [@de2017towards].
-Although some studies investigated how wearables can help teachers monitor student activity [@quintana2016keeping], there is a notable research gap regarding teachers’ use of wrist-worn wearables.
-Given the high stress levels in the teaching profession [@johnson2005experience], fitness trackers could be a valuable tool for analyzing HR and the factors contributing to stress.
-One of the reasons for teachers’ augmented stress is that they are confronted with a multitude of demands in their everyday work, some of which exceed their resources and therefore make it difficult to cope with immediate stressors such as classroom disruptions [@montgomery2005meta].
-However, the extent of the strain depends on the subjective appraisal of a stressor, which involves considerations about available resources to deal with it [@kyriacou2001].
-It is, therefore, particularly important for teachers to have sufficient personal and professional resources at their disposal [@cramer2018belastung].
-Classroom disruptions, for example, are one of the major stressors in teachers’ daily work [@boyle1995structural; @aloe2014multivariate] and professional knowledge about effective classroom management reduces the risk of teacher stress [@klusmann2012berufliche].
-Teachers’ characteristics such as professional experience in turn have an impact on the development of classroom management skills and thus on the appraisal processes, as these skills develop during professional experience [@ophardt2017klassenmanagement; @wolff2015keeping].
-
-To better understand how stressors like classroom disruptions affect teachers and their stress responses, data from wrist-worn fitness trackers could be used to monitor physiological parameters before, during, and after teaching sessions [@wettstein2021].
-This study explored the use of wrist-based fitness trackers as a tool to monitor teachers’ stress during different phases of a micro-teaching unit during which teachers had to deal with classroom disruptions.
-Physiological data were triangulated with teachers’ appraisal of classroom disruptions, and their teaching experience.
-The physiological indicator employed in this study was teachers’ HR, which can be readily recorded by any fitness tracker.
-Teachers’ use of wrist-worn fitness trackers in educational research holds transformative potential as obtained fine-grained data and underscores the critical need to monitor teachers’ health as they navigate the stressful landscape of the classroom.
-
-## Fitness Trackers as a Method to Assess HR as an Indicator of Stress
-
-Wearables, defined as electronic devices worn directly on the body or integrated into clothing or accessories, serve as versatile solutions [@godfrey2018z], gathering data like location, movements, and vital signs [@cheng2017underlying].
-Fitness trackers, a popular wearable type [@park2020user], offer insights into physical activity and cardiovascular health, supporting personalized fitness goals [@nuss2021effects] and stress management [@hao2018chrv].
-Their affordability and ease of use make them ideal not only for various domains including healthcare, entertainment, and fitness [sinha2019taxonomy] but also in education as they offer added benefits for formal and informal learning environments for both students and teachers [@de2017towards].
-Yet, few studies focus on their significance for teachers.
-
-One important health parameter assessed by nearly all wrist wearables is HR [@scalise2018wearables].
-HR indicates the number of heartbeats within one minute and is typically expressed as beats per minute (BPM) [@hottenrott2007].
-At rest, the average HR of adults typically ranges from 60 to 80 BPM [@sammito2015guideline].
-HR can be detected and measured using sensors based on electrocardiogram (ECG) or phonocardiogram (PCG) [@mukhopadhyay2017wearable].
-Another uncomplicated and inexpensive technique to measure HR via fitness trackers is photoplethysmography (PPG) [@castaneda2018review].
-This optical method assesses HR by flashing green or red lights to measure changes in blood volume [@allen2007photoplethysmography].
-Physiologically, HR is regulated and influenced on short-time intervals by the sympathetic and the parasympathetic nervous system [@pham2021].
-An increase in the activity of the sympathetic system results in HR being speeded up (“fight or flight”) [@taelman2009influence].
-In contrast, increased activity of the parasympathetic has the effect of slowing down the HR (“rest and digest”) [@battipaglia2015].
-Therefore, an increase in HR can be regarded as an indicator of increasing stress, and a decrease as an indicator of decreasing stress [@kyriacou1978].
-
-## Teacher Stress and Important Resources
-
-The teaching profession is one of the most stressful professions compared to other occupational groups, facing a variety of stressors during everyday work [@smith2000; @herman2020; @schult2014belastet].
-According to @kyriacou1978, teacher stress can be defined as a negative affective response, often accompanied by physiological changes such as increased HR, triggered by job-related demands and perceived as threatening to one’s self-esteem or well-being.
+The teaching profession is one of the most stressful professions, with teachers facing a host of stressors during their everyday work [@smith2000; @herman2020; @schult2014belastet].
+To better understand mechanisms in teacher stress, there is a growing research interest in physiological measures such as heart rate (HR) as online measures of teachers’ stress during teaching [@karner2021teachers; @wettstein2020ambulatory].
+For example, it has been shown that teacher-centered activities and typical classroom-related stressors increase teacher HR during teaching activities [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021; @huang2022class].
+However, previous studies have often relied on expensive and obtrusive electrocardiographs (ECG).
+Modern fitness trackers represent a non-invasive and convenient alternative.
+[@ferguson2015]
+
+Classroom disruptions are a major stressor in teachers’ daily work [@boyle1995structural; @aloe2014multivariate], and learning how to deal with them is an important aspect of professional expertise [@wolff2015keeping].
+According to @lazarus1990theory transactional model of stress and coping, the experience of stress in response to stressors such as classroom disruptions depends on the teacher´s subjective appraisal, which, in turn, depends on their coping resources, such as their professional knowledge.
+The resulting stress response has a psychological, physiological, or behavioral dimension [@kyriacou1978].
+Therefore, in order to better understand how classroom stressors affect teachers’ stress response, subjective self-reports should be accompanied by objective, physiological measures [@wettstein2021].
+Teachers’ use of wrist-worn fitness trackers in educational research provides fine-grained, in vivo data, allowing researchers as well as teachers themselves to monitor their physiological stress response continuously during teaching, across settings, and at low costs.
+Being able to monitor, and eventually counteract, teacher stress levels appears particularly relevant given the profession’s generally high stress levels and associated negative health effects [@johnson2005experience; @montgomery2005meta].
+To harness this potential, the present study explored the use of wrist-based fitness trackers as a tool to assess teachers’ HR, as an indicator of stress, before, during, and after a teaching session during which typical, potentially stressful, classroom disruptions occurred.
+Further, we explored to what extent teachers’ subjective appraisals of classroom disruptions and their teaching experience predicted teacher stress as assessed by the fitness tracker.
+
+## Fitness trackers as a ubiquitous, low-cost tool for assessing physiological stress responses
+
+Fitness trackers provide data on physical activity and cardiovascular parameters such as HR, supporting personalized fitness goals [@nuss2021effects] and stress management [@hao2018chrv].
+They can be used as ubiquitous, low-cost, and unintrusive data collection instruments [@godfrey2018z], and their wide-spread use and everyday availability align with the increasing popularity and acceptance of wearables among the general population [@peng2022acceptance].
+In contrast to self-reported questionnaires on stress [@chaplain2008; @liu2020] that are prone to biases like social desirability [@razavi2001self] or recall errors [@van2016accuracy], fitness trackers, as ambulatory assessment methods [@trull2013ambulatory; @wettstein2020ambulatory], offer more objective insights into teachers’ stress levels by monitoring teachers’ physiological stress responses without disrupting teaching [@donker2018; @runge2020].
+
+One important health parameter assessed by nearly all wrist-worn fitness trackers is heart rate [@scalise2018wearables].
+HR indicates the number of heartbeats within one minute and is typically expressed as beats per minute (BPM) [@berntson2007cardiovascular; @hottenrott2007].
+At rest, the average HR of adults typically ranges between 60 and 80 BPM [@sammito2015guideline].
+HR can be detected and measured in different ways using sensors, such as electrocardiography (ECG) or photoplethysmography (PPG) [@mukhopadhyay2017wearable].
+While ECG sensors offer precise measurements by detecting the heart’s electrical activity, their intrusive nature and requirement of direct skin contact may limit their suitability [@kranjec2014non], particularly in educational settings.
+In contrast, photoplethysmography (PPG) is a rather uncomplicated and inexpensive technique to measure HR, commonly found in commercially available fitness trackers [@castaneda2018review].
+This optical method assesses HR by flashing green or red lights to measure changes in blood volume in the capillaries of the skin [@allen2007photoplethysmography].
+
+Physiologically, HR is regulated by the sympathetic and parasympathetic nervous systems [@pham2021].
+An increase in sympathetic activity results in HR being sped up (“fight or flight” response) [@taelman2009influence]; whereas an increase in parasympathetic activity results in HR being slowed down (“rest and digest” response) [@battipaglia2015].
+Stress or mental and physical strain directly increases HR [@custodis2014heart; @sachs2014].
+Therefore, an increase in HR can be regarded as an indicator of increasing stress, and a decrease as an indicator of relaxation and ease [@kyriacou1978].
+Thus, fitness trackers offer low-cost and unobtrusive access to psychological stress data.
+
+## HR in teaching-learning contexts
+
+Prior research, typically using ECG methods, has shown that changes in teachers’ HR can be mapped onto stressors they experience during teaching.
+For example, teachers’ HR tends to increase when teachers take an exposed position in student-teacher interaction [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021].
+@sperka1995 for example recorded the HR of 16 pre-service teachers during their first lesson and showed that teachers’ HR increased significantly during teaching.
+The activation was particularly prominent at the beginning of the lesson and decreased over the course of the lesson.
+The authors suggested that pre-service teachers’ proactive coping strategies, such as actively managing student interactions, helped lower their HR levels.
+Other ECG studies identified typical stressors predicting increases in HR, such as class size [@huang2022class], or low student engagement and motivation [@junker2021].
+@junker2021 recorded the HR of 40 teachers during a real classroom lesson.
+Again, teacher stress, induced by factors such as low student engagement (e.g., lack of motivation or interest in tasks) or teacher-centered activities (e.g., teacher-focused classroom activities), resulted in elevated HR.
+
+More recent studies have begun using wrist-worn fitness trackers to investigate HR trends in instructional settings [@Darnell2019; @chalmers2021].
+@Darnell2019 measured the HR of 15 medical college students listening to lectures, using wrist-worn devices.
+The analysis revealed a constant decrease in HR throughout the lecture, with HR peaks during more interactive learning phases.
+@chalmers2021 used HR data from a fitness tracker to identify physiological changes during stress-inducing tasks (i.e., the Trier Social Stress Test; @kirschbaum1993trier].
+Average HR increased significantly from the resting to the stress inducing phases.
+Even though the participants of these previous studies [@Darnell2019; @chalmers2021] were not teachers but learners, the results are relevant for studying teacher stress as they demonstrated that HR can be effectively recorded using fitness trackers over the course of a whole learning unit, and HR changes are in line with the occurrence of activating or stress-inducing tasks.
+
+To the best of our knowledge, only one study has directly assessed teachers’ HR during teaching using a wrist-worn fitness tracker: @runge2020 assessed HR as an indicator of stress in four in-service teachers during authentic lessons.
+They used fitness trackers’ recordings to create a profile for each teacher, with the aim of differentiating between teachers reporting higher vs.
+lower levels of stress.
+It was found that the combination of a high HR, a high number of steps, and short sleep duration was characteristic for teachers reporting high stress levels.
+However, it should be noted that the generalizability of these results is limited due to the small sample size.
+
+In summary, previous studies have revealed that teachers’ (and students’) HR changes depend on their activities and the stressors they experience, with an increase in HR already before the expected stressors occur, and with peaks in activating phases [@Darnell2019; @chalmers2021].
+For teachers, teacher-centered phases led to an increase in HR [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021].
+However, there is a lack of studies using teacher-worn fitness trackers in larger samples, exploring the feasibility of this convenient tool for researching links between teachers’ HR and stress inducing events and mechanisms.
+
+## A model of teacher stress
+
+According to @kyriacou1978, teacher stress can be defined as a negative affective response, typically accompanied by physiological changes such as increased HR, triggered by job-related demands, and perceived as threatening to one’s self-esteem or well-being.
 Coping mechanisms help to reduce the perceived threat.
-
-This definition of teacher stress is based on the transactional stress model by Lazarus and colleagues [@lazarus1981stressbezogene; @lazarus1984stress], which was modified and tailored to the teaching-learning environment by @kyriacou1978.
-
-In general, the transactional stress model [@lazarus1990theory] highlights the interaction between an individual and the environment, whereby stress refers to any event that exceeds a person’s adaptive resources.
-It has been shown that there are important connections between stressors and resources experienced by teachers on the one hand, and stress-induced health issues on the other hand [@krause2013messung].
-As we are interested in how specific classroom events affect teacher stress, we adapted the transactional stress model to that type of situation, based on a representation of the model first proposed by [van2006stress]; this working model is depicted in Fig.
-1.
+Kyriacou’s definition of teacher stress (see @kyriacou1978 and, for a more recent adaptation, @van2006stress) is based on the transactional stress model by Lazarus and colleagues [lazarus1966psychological; @lazarus1990theory], which highlights the interaction between an individual and the environment, whereby stress refers to a person’s subjective reaction to an event (a stressor) that exceeds the person’s adaptive resources.
 
@@
   \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
-  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the author)}
-  \label{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the author)}
+  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
+  \label{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
 \end{figure}
@@
 
-When potential stressors (e.g., classroom disruptions) occur during teaching (1), teachers subjectively appraise how disruptive the event is (2).
-If potential stressors are judged as threatening, i.e., as actual stressors (3), teachers consider whether they have sufficient resources for coping with the stressor (4).
-Based on this evaluation of resources and their characteristics such as professional experience, teachers try to manage classroom disruptions, by utilizing classroom management strategies (5).
-In cases where coping fails, stress ensues, often accompanied by physiological reactions like increased HR (6).
-Following resource appraisal and coping outcomes, the stressor is re-evaluated (7).
-
-The appraisal processes of resources play a crucial role as teachers’ assessments of resources and coping mechanisms, both internal (e.g., classroom management skills) and external (e.g., supportive colleagues), significantly impact their stress levels.
-When resources are lacking and coping fails, negative consequences like burnout and high turnover can arise [@jalongo2006; @unterbrink2007; @aloe2014].
-This highlights the importance of teachers’ appraisal of their professional competencies, including their ability to manage classroom disruptions effectively [@klieme2008concept; @konig2016teacher].
+Fig.
+1 shows, in a simplified way, how classroom events affect teachers’ stress level, according to the adaptation of the Lazarus model to teacher stress proposed by @van2006stress: When potential stressors (e.g., classroom disruptions) occur during teaching (1), teachers intuitively judge how disruptive the event is in a primary appraisal (2).
+If potential stressors are judged as threatening, i.e., as actual stressors (3), teachers consider whether they have sufficient resources for coping with the stressors (4).
+Teachers utilize these resources in trying to cope with the stressors, e.g., by employing classroom management strategies (5).
+In cases when coping fails, stress ensues, often accompanied by physiological reactions like increased HR (6).
+As part of the coping process, and dependent on its outcomes, teachers re-evaluate the stressor (7).
 
 As shown in Fig.
-1, both primary and secondary appraisals are influenced by teachers’ characteristics, e.g., their professional experience, shaping their classroom management skills.
-As experience grows, teachers develop cognitive scripts for managing classroom events resulting in more complex classroom management skills [@wolff2021classroom].
-Especially beginning teachers face considerable stress and often feel overwhelmed by the demands of teaching [@ophardt2017klassenmanagement; @wolff2015keeping; @ klusmann2012berufliche], with many leaving the profession within the first five years [@ingersoll2003].
-Research shows less experienced teachers are more susceptible to burnout, underscoring the importance of experience and job satisfaction in predicting teacher stress [@fisher2011].
-
-## HR in Teaching-Learning Contexts
-
-ECG studies have revealed that HR can be used to map changes in HR during teaching onto stressors experienced by teachers.
-For example, HR increased during teacher-centered activities when teachers had to take a leading position in the student-teacher interaction [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021].
-@sperka1995 for example recorded the HR of 16 pre-service teachers during their first lesson.
-The results showed significantly increased psychophysiological activation in terms of an increased HR during teaching.
-The activation effect was particularly prominent at the beginning of the lesson and decreased over the course of the lesson.
-The authors interpret this result as showing how pre-service teachers’ active coping processes, i.e., the active management of the interaction with the students, helped the teachers regulate their HR downwards.
-Other ECG studies identified typical stressors predicting increased HR values, such as class size [@huang2022class], or low student engagement and motivation [@junker2021].
-For example, @junker2021 recorded the HR of 40 teachers using an ambulatory monitoring system during a real classroom lesson.
-They provided evidence that teacher stress caused by stressors such as low student engagement, i.e., students displaying a lack of motivation or limited interest in their tasks or classroom activities, or teacher-centered activities, i.e., classroom activities primarily focused on the teacher’s actions., leads to an increase in HR.
-
-In addition to ECG studies, there are a few studies that used wrist-worn fitness trackers to investigate HR trends in teaching-learning situations [@Darnell2019; @chalmers2021].
-@Darnell2019 for example measured the HR of 15 medical college students using wrist-worn devices during lectures.
-The analysis revealed a constant decrease in HR from the beginning to the end of a lecture, whereas the HR peak was reached during active learning sessions.
-@chalmers2021 examined the usability of the average HR, measured with a Fitbit   fitness tracker, to identify physiological changes during stress-inducing tasks in a study with a total of 60 participants.
-The average HR increased significantly between the resting and stress phases.
-Even though the participants in these studies were learners, not teachers, the results are relevant to the study of teacher stress using wearable devices, because the studies showed that a) HR can be effectively recorded using fitness trackers during a whole learning unit, and b) HR changes are in line with the occurrence of activating or stress-inducing tasks.
-
-So far, to the best of our knowledge, only one study has directly assessed teachers’ HR using a wrist-worn fitness tracker during teaching : @runge2020 used a Fitbit fitness tracker to assess HR as an indicator of stress in N=4 teachers.
-They used the fitness trackers’ recordings to create a profile for each teacher (to differentiate between teachers reporting higher or lower levels of stress  .) In particular, it was found that the combination of a high number of steps, a high HR, and short sleep was an indicator of stress.
-It should be noted that the generalizability of the results is limited due to the small sample size.
-
-In summary, previous studies have revealed that teachers’ (and students’) HR changes, depending on the activity and stressors they experience, whereby teacher-centered phases  , in particular, led to an increase in HR [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021].
-Furthermore, it could be shown that HR as an indicator of stress can be assessed using low-cost, non-intrusive fitness trackers and that HR increases in activating phases and even before stress occurs [@Darnell2019; @chalmers2021].
-However, studies collecting data from teacher-worn fitness trackers in a large enough sample to explore links with factors such as subjective stressor appraisal, or effects of teaching experience, are still lacking.
-Our study aims to close this research gap.
+1, teachers’ primary and secondary appraisal as well as coping attempts are influenced by professional experience.
+As professional experience grows, teachers develop cognitive scripts for managing classroom events, resulting in more complex and problem-focused classroom management skills [@wolff2021classroom], and thus more effective coping and less stress.
+Empirically, classroom management skills and problem-focused coping styles are linked to fewer instances of emotional exhaustion [@maslach2001job; @clunies2008self].
+Novices in the teaching profession, on the other hand, face considerable stress and often feel overwhelmed by the demands of teaching [@ophardt2017klassenmanagement; @wolff2015keeping; @klusmann2012berufliche] with many leaving the profession within the first five years [@ingersoll2003].
+Accordingly, when resources are lacking and coping fails, negative consequences for health (e.g., burnout) and for work (e.g., high turnover rates) can arise [@jalongo2006; @unterbrink2007; @aloe2014multivariate], highlighting the importance of professional expertise for managing teacher stress [@fisher2011].
 
@@
 
-The data analyzed for the present study were obtained from teachers and student teachers who participated in a lab study, as part of a larger project targeting the development of classroom management in teachers.
-
-As part of the larger project, participants came to the lab individually, and each taught a 15-minute, self-prepared micro-teaching unit to a “class” of three actors (trained student assistants).
-These actors performed nine, possibly disruptive, classroom events.
-The actors received standardized instructions on a screen (only visible to them, not to the participant) to perform a classroom event every one and a half minutes, and they performed the same scripted disruptions for all participants.
-While teaching, participants wore eye-tracking glasses, and additionally, their lessons were recorded by cameras.
-
-The micro-teaching unit, with its unfamiliar setting and the scripted disruptions of participants’ teaching flow, was potentially stressful.
-Thus, we were particularly interested in the development of participants’ HR before, during, and after this micro-teaching unit.
-We recorded HR data in five phases, with a total duration of approximately two hours: In the *pre-teaching phase*, participants were welcomed, prepared for the following micro-teaching unit, and familiarized with the setting.
-In the *teaching phase*, participants taught the micro-teaching unit and experienced the classroom disruptions.
-In the *post-teaching phase*, participants answered several questionnaires in a comfortable seated position.
-Next, in the *interview phase*, they watched the video of their 15-minute unit, rated the disruptive classroom events, and answered open questions.
-Finally, in the *end phase*, participants answered another questionnaire.
-These conditions were identical for all participants.
-During the entire study, participants wore a fitness tracker on their wrist.
-
-The goals of the present study were twofold:
-
-(1)	The first research goal was to investigate whether HR measures assessed by wrist-based fitness trackers are a suitable and effective method for mapping teachers’ HR over the course of a five-phase lab study, including the time before, during, and after a potentially stressful micro-teaching unit.
-
-First, we expected the participants to show an initial increase in their HR, followed by a peak during the teaching phase and a decrease for the remaining phases.
-In addition, we examined whether z-standardization of the participants’ mean HR could serve as a useful method to account for individual differences in baseline HR.
-We expected to observe the same trends in both standardized and non-standardized mean HR values.
-
-Second, five representative 10-minute intervals were selected from the five phases (see section ##Measures for a more detailed description of the intervals), which served as the basis for the data analysis for our hypothesis: pre-teaching interval ($I_1$), teaching interval ($I_2$), post-teaching interval ($I_3$), interview interval ($I_4$), end interval ($I_5$).
-We examined the levels of and the changes in HR during these intervals.
-We assumed the highest HR level in the teaching interval ($I_2$) and lower levels in all other intervals (**Hypothesis 1a**).
-Further, we expected an increase in participants’ HR while they were preparing for teaching during the pre-teaching interval ($I_1$), and we expected a decrease in participants’ HR during all of the following intervals, because of habituating to ($I_2$) and recovering from ($I_3$-$I_5$) the stressful teaching phase (**Hypothesis 1b**).
-
-(2)	The second research goal was to examine whether variance in HR measures could be explained by participants’ teaching experience (because, presumable, more experienced teachers might have better classroom management strategies, and thus better resources for coping), and/or by their self-reported subjective appraisals of classroom events (specifically, how disruptive it was, and how confident they felt in their coping).
-
-We expected lower HR levels for teachers with more teaching experience, particularly during the teaching interval (**Hypothesis 2a**).
-We expected higher HR levels for teachers who felt more disrupted by the enacted classroom events, regardless of their teaching experience (**Hypotheses 2b**).
-At the same time, we expected lower HR levels for teachers who felt more confident in dealing with the events, regardless of teaching experience (**Hypothesis 2c**).
-Lastly, we hypothesized that each of the three predictors (teaching experience, disruption appraisal, confidence appraisal) uniquely contributes to explaining variance in teachers´ HR levels (**Hypothesis 2d**).
-In addition, we exploratively examined the same as for the HR levels again for the changes in HR.
+The present study aimed to explore the relations between teachers’ HR response, and their subjective appraisals of stress during a micro-teaching unit, and to relate their self-reported appraisals and physiological stress responses to their teaching experience.
+We analyzed data from in-service and pre-service teachers who participated in a laboratory study as part of a larger project targeting the development of classroom management skills.
+Participants came to the lab individually and taught a short lesson to a class of three actors (i.e., trained student assistants) who performed several typical and possibly disruptive classroom events.
+The micro-teaching unit was thus potentially stressful for the participants.
+The aims of the present study were twofold:
+
+(1)	The first research goal was to investigate whether HR measures assessed by a wrist-based fitness tracker were a suitable and effective method for mapping teachers’ HR over the course of the lab study, with a total duration of approximately 2 hours, including phases before, during, and after the stressful micro-teaching unit.
+
+Looking at HR measures globally, we expected the participants to show an initial increase in their HR, followed by a peak during the micro-teaching unit and a decrease for the remaining phases.
+In addition, we examined whether z-standardization of the participants’ HR could serve as a useful method to account for individual differences in baseline HR: We expected to observe the same trends in both standardized and non-standardized HR values.
+
+In addition, we selected five representative 10-minute intervals from the five phases of the lab study (see Figure 2) in order to test the hypotheses that, regarding HR levels, teachers’ HR would be the highest during the micro-teaching unit, compared to all other phases (**Hypothesis 1a**), and, regarding HR slopes, that teachers’ HR would increase while they were preparing for teaching (pre-teaching interval), but decrease in all of the following intervals, i.e.
+when they were habituating to and recovering from the stressful micro-teaching unit (**Hypothesis 1b**).
+
+(2)	We further explored whether teaching experience made a difference in how teachers’ HR reacted to the classroom disruptions.
+We expected more experienced teachers to be less stressed by the classroom events (**Hypothesis 2a**).
+In addition, we examined the relations between teachers’ subjective appraisals of the classroom events (specifically, the disruptiveness of the events, and their confidence in dealing with them) and teachers’ HR level, beyond the explanatory power of teaching experience.
+We expected higher HR levels for teachers who felt more disrupted, regardless of their teaching experience (**Hypotheses 2b**), and lower HR levels for teachers who felt more confident, regardless of teaching experience (**Hypothesis 2c**).
+We hypothesized that each of the three predictors (*teaching experience, disruption appraisal, confidence appraisal*) uniquely contributed to explaining variance in teachers’ HR levels (**Hypothesis 2d**).
+In addition, we exploratively ran analogous analyses for the *changes* in HR (i.e., slopes).
 
@@
 
-The sample consisted of $N$ = `r N_prewrangling` pre- and in-service teachers from Germany, who were recruited via personal contact, email lists, and flyers.
-The data of three participants was lost due to failed data transmission, yielding an analysis sample of $n$ = `N_postwrangling` ($n$ = 52 women, $n$ = 29 men).
+The sample consisted of $N$ = 84 pre- and in-service teachers from Germany, who were recruited via personal contacts, email lists, and flyers.
+The data of three participants was lost due to failed data transmission, yielding an analysis sample of $n_{total}$ = 81 ($n_{total}$ = 52 women, $n_{total}$ = 29 men), including 40 pre-service and 41 in-service teachers.
 Participants had a mean age of 30.95 years ($SD$ = 10.90; range: 19-60) and an average teaching experience of 5.64 years ($SD$ = 9.46; range: 0-37).
@@
 The study was carried out following the ethical standards and the approval of the University’s Institutional Review Board.
-All participants were informed in detail about the aims and intention of the study before testing.
-Participation was voluntary and only took place after written consent had been given.
-Participants were not rewarded in any way for participating in the study.
-
+All participants were informed in detail about the aims of the study prior to testing.
+Participation was voluntary, not incentivized, and only took place after written consent had been given.
+
+Each participant came to the lab for a period of approximately two hours in total, and each participant underwent the same phases (see Fig.
+2): In the *pre-teaching phase*, the experimenter welcomed the participants and helped them put on the fitness tracker.
+This was followed by a warm-up session to familiarize the participants with the laboratory setting and the class.
+This phase took about 10-15 minutes and participants spent this time mostly standing or slowly walking around.
+During the *teaching phase*, the participants held their self-prepared micro-teaching unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table ## in the supplementary material for an overview and categorization of all events; and Fig## in the supplementary material for a depiction of the laboratory setting of the micro-teaching unit).
+The topic and class level of the teaching unit could be freely chosen by the teachers with the only requirement that the unit had to be an introductory lesson, and had to consist of supervised individual work and / or frontal teaching.
+The micro-teaching unit lasted about 15-20 minutes.
+Participants spent this time mostly standing or slowly walking around.
+While teaching, participants wore eye-tracking glasses, and their lesson was video-recorded.
+After having completed the micro-teaching unit, in the *post-teaching phase*, participants filled in questionnaires for approximately 10-15 minutes: a brief computer-based survey of sociodemographic data (e.g., teaching experience, gender, studied school type, studied school subjects, extracurricular teaching activities), and a short knowledge test that was irrelevant to the
+present study. In the *interview phase*,
 ```{=latex}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{images/Timeline_small.pdf}
+  \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
   \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
@@
 ```
-
-Each participant came to the lab for a period of approximately two hours in total, and each underwent the same phases: *pre-teaching phase*, *teaching phase*, *post-teaching phase*, *interview phase*, and *end phase* (please refer to Fig.
-2 for a timeline).
-In the *pre-teaching phase*, the experimenter welcomed the participants and helped them put on the fitness tracker.
-This was followed by a warm-up session to familiarize the participants with the laboratory setting and the class.
-This phase took about 10-15 minutes and participants spent this time mostly standing or slowly walking around.
-During the *teaching phase*, the participants held their self-prepared, micro-teaching  unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table ## in the supplementary material for an overview and categorization of all events; also see Fig## for a depiction of the laboratory setting of the micro-teaching unit).
-In preparation for the 15-minute lesson, the topic and class level could be freely chosen by the teachers.
-The type of course was to be an introductory lesson and the desired social form required individual work or frontal teaching, without longer video sequences and movement of the actors.
-The teaching unit lasted about 15-20 minutes.
-Participants spent this time mostly standing or slowly walking around.
-After having completed the micro-teaching unit, in the *post-teaching phase*, participants were seated at a desk and filled in questionnaires for approximately 10-15 minutes: a brief computer-based questionnaire assessing sociodemographic data (e.g., teaching experience, gender, studied school type, studied school subjects, extracurricular teaching activities), and a short knowledge test that is irrelevant to the present study.
-In the *interview phase*, the participants watched the video of their own teaching together with the experimenter.
-While doing so, they were given a Stimulated Recall Interview (SRI), in which the participants watched their recorded eye-tracking video of the lesson from the ego perspective, indicating the participants’ gaze point.
-The experimenter stopped the video each time one of the nine classroom events happened and asked a total of eight questions, five of which were open and three closed.
-We assessed – among other questions irrelevant to this study – with two closed questions the teachers’ subjective appraisal of the classroom events that took place during the *teaching phase* in terms of how subjectively disruptive they were (disruption appraisal) and how confident the participants felt dealing with them (confidence appraisal) with one item each.
-The interview lasted about 45-60 minutes and the participants’ position was seated.
-The *end phase* lasted about 10-15 minutes and participants answered in a seated position another questionnaire irrelevant to this study.
+\noindent
+participants engaged in a Stimulated Recall Interview (SRI).
+During the SRI, participants sat in front of a computer monitor and watched the video of their own lesson from the ego perspective, as recorded through the eye-tracking glasses.
+The experimenter stopped the video each time one of the nine classroom events happened, and asked five open-ended, and three rating questions per event.
+Two of the rating questions are relevant to the present study: the disruption and the confidence appraisal ratings (see Measures).
+The interview lasted about 45-60 minutes.
+Finally, in the *end phase*, participants filled in another questionnaire irrelevant to the present study, which lasted about 10-15 minutes.
 
@@
 
-To measure the teachers’ HR, we used a wrist-based fitness tracker.
-The model was a Fitbit Charge 4.
-In line with the manufacturer's instructions [@fitbitnd], the device was attached a finger’s width above the participants’ nondominant hand’s wrist bone.
-The tracker works by flashing green LEDs hundreds of times per second, using light-sensitive photodiodes to catch the reflected light, and from that information calculating volume changes in the capillaries.
-From this, the tracker calculates how many times the heart beats per minute.
-HR measurements are generated at least every 15 seconds[^1].
-The raw data that can be extracted from the tracker lists the time stamps of all measurements and the estimated HR in BPM for each time stamp.
-
-The anonymous HR data was synced via Bluetooth to a commercial Fitbit account.
-Subsequently, the intraday second-by-second data was exported as a CSV file for each session using the open-source software PulseWatch (Ricci, n.d.), and linked to the participant.
-To account for individual differences in the baseline HR, we first z-standardized the BPM values from the unstandardized mean HRs.
-
-Since we aimed to explore teachers’ HR between different strain phases, we aggregated HR over a 10-minute interval within each phase.
+To measure teachers’ HR, we used the wrist-based fitness tracker Fitbit® Charge 4.
+In line with the manufacturer's instructions [@fitbitnd], the device was attached to the participants’ nondominant hand, a finger’s width above the wrist bone.
+The tracker works by flashing green LEDs hundreds of times per second, using light-sensitive photodiodes to catch the reflected light, to calculate the volume changes in the capillaries.
+From this, the tracker calculated the heart beats per minute.
+HR measurements were generated at least every 15 seconds .
+The raw data contained the estimated HR in BPM for each time stamp.
+To account for individual differences in the baseline HR, we also calculated z-standardized HR values based on individual means, i.e., at the subject level of $n$ = 81 participants (standardized HR).
+
+Since we aimed to keep measurement intervals comparable between study phases, we aggregated HR over a representative 10-minute interval within each phase (cf.
+Fig.
+2).
 Previous research has indicated that 10-minute intervals are a useful duration for analyzing PPG data [@lu2008can].
-The intervals were selected based on the following rules: The pre-teaching interval ($I_1$) comprised the first 10 minutes after the fitness tracker had been put on.
-The teaching interval ($I_2$) started two minutes after the teacher had started the teaching unit.
+The intervals were selected based on the following rules: The *pre-teaching interval* ($I_1$) comprised the first 10 minutes after the fitness tracker had been put on.
+The *teaching interval* ($I_2$) started two minutes after the lesson had started.
 This interval was of the highest relevance to our study.
-We explicitly chose an early 10-minute interval within the teaching phase, as previous studies revealed that the beginning of a lesson is essential and demanding regarding teacher-student interaction [@donker2018quantitative; @claessens2017positive].
-The post-teaching interval ($I_3$) started immediately after the end of the teaching unit.
-The interview interval ($I_4$) was defined as the mid-10 minutes between the end of the teaching unit and the time point when the fitness tracker was taken off so that all participants were being interviewed during this interval.
-The end interval ($I_5$) comprised the last 10 minutes before the fitness tracker was taken off.
-
-[^1]: The fluctuations in the number of seconds in which the HR was measured are due to the participants' movements, meaning that the device could not measure the HR every second.
+We explicitly chose an early 10-minute interval within the teaching phase, as previous studies revealed that the beginning of a lesson is most demanding and potentially stressful with regards to teacher-student interaction [@donker2018; @claessens2017positive].
+The *post-teaching interval* ($I_3$) started immediately after the end of the teaching unit.
+The *interview interval* ($I_4$) was defined as the mid-10 minutes between the end of the teaching unit and the time point when the fitness tracker was taken off.
+All participants were being interviewed during this interval.
+The end interval (I5) comprised the last 10 minutes before the fitness tracker was taken off.
 
@@
 
-The participants’ teaching experience was assessed as a part of sociodemographic data. Participants stated their work experience in years (excluding the traineeship year).
+Participants’ teaching experience was assessed as a part of their sociodemographic data. Participants stated their work experience in years.
 
@@
 
-The subjective disruption and confidence appraisals assessed in the SRI on an 11-point rating scale were averaged across the nine classroom events as we were not interested in individual classroom events, but only in the expected mean level of arousal during the *teaching phase*.
-Regarding the model (see Fig.
-1), the disruption appraisal was used to assess the evaluation of the stressor (see Fig.
-1, box 2).
-The confidence appraisal, in contrast, referred to the resources available for coping with the stressors (see Fig.
-1, box 4).
+The subjective disruption and confidence appraisals were assessed during the SRI on an 11-point rating scale, ranging from 0 (not at all disrupting/confident) to 10 (extremely disrupting/confident).
+Ratings were averaged across the nine classroom events for each participant, as we were interested in the general stressfulness of the *teaching phase* for each participant.
 
@@
 
-We conducted all analyses with R [@RStudio2020]. Graphics were created using ggplot2 (v3.3.3; Wickham, 2016).
-
-**Research goal 1**. The first research goal included mapping teachers’ HR before, during, and following a micro-teaching unit in the course of a five-phase lab study.
-
-Regarding the teachers’ HR trend, we displayed the HR trend over the course of the entire study.
-For z-standardization as a method to account for individual differences in the baseline HR, we visually compared unstandardized and standardized mean HR trends for the entire two-hours study[^3].
+We conducted all analyses with R [@RStudio2020]. Graphics were created using ggplot2 [@ggplot2].
+To enable visual inspection of HR trends, we displayed smoothed teacher HR over the course of the recording.
+We visually compared unstandardized and standardized HR trends over the two-hour recording period.
 For all further analyses, we used standardized rather than unstandardized HR values.
-[^3]:   Note that the study exceeded the planned duration of two hours for a few participants.
-To avoid distortions when mapping the HR over the course of the study (see Fig.
-3), the endpoint was set at two hours for all participants, even though data from later time points was used in the *end interval* for a few participants.
-
-For testing Hypothesis 1a, which examined the HR levels in the different intervals, we initially conducted a one-way ANOVA with repeated measures as an omnibus test.
-The dependent variable comprised the standardized HR mean for each interval.
-To identify the highest HR level, we subsequently conducted t-tests with planned contrasts as post-hoc tests, accompanied by the effect size d [@cohen1988new].
-Specifically, we tested the differences between the teaching interval ($I_2$) and the other four intervals.
-Note that mean HR was calculated at the subject level of $n$ = 81 participants (see Table 1), whereas the mean slope and mean intercept estimates are based on all values at all measurement time points (see Table 2).
-For testing Hypothesis 1b, which examined the HR changes within each interval, we conducted a linear estimation of the increase or decrease in HR over time.
-To this end, we used fixed intercept fixed slope regression models [@gelman2006data] for each interval to estimate intercepts and linear slopes for all individuals which were then averaged across individuals[^2].
-
-[^2]: Although this procedure does not account for nonmonotonic progressions in individual HR, a graphical evaluation revealed that the linear estimates corresponded well to the majority of the cases (see XX in the supplementary material).
-
-**Research goal 2**.
-In addressing our second research goal, we examined the effects of teaching experience and subjective appraisal of disruptive classroom events on teachers’ HR levels during the five phases.
-
-To test hypothesis 2a, we examined the effect of teaching experience on participants’ HR levels for each of the five intervals using linear regression models with teaching experience as the sole predictor.
-To test hypotheses 2b and 2c, we separately augmented the models by either teachers’ disruption appraisal (Hypothesis 2b) or confidence appraisal (Hypothesis 2c), while controlling for shared variance with teaching experience.
-HR levels were only predicted with the disruption and confidence appraisal after the teaching had taken place, i.e., for all the intervals following the pre-teaching interval (I1).
-To test hypothesis 2d, we examined the effects of all three predictors in one regression model.
-We repeated these steps to explore the effect of teaching experience and subjective appraisals on changes in teachers’ HR at each interval.
-
-# Results
-
-## Research goal 1: Mapping teachers’ HR over the course of the study phases
-
-The first part of our first research goal was to map participants’ overall HR trend and explore whether z-standardization of participants’ HR is a useful method to account for individual differences in the baseline HR.
-Means, standard deviations, and range of teachers’ unstandardized and standardized HR are shown in Table 1.
-Fig.
-3 a.
-and b.
-display the unstandardized and standardized HR trends, respectively.
-HR initially increased, peaked, and then decreased, with the unstandardized and standardized HR graphs showing high similarity.
-Thus, for all further analyses, we used participants’ standardized HR values.
+
+We averaged each person’s standardized HR over each of the five selected intervals , resulting in one measure per person per interval.
+To test Hypothesis 1a, we initially conducted a one-way ANOVA with repeated measures as an omnibus test and then tested the mean differences between the teaching interval (I2) and the other four intervals by planned contrasts and inspection of effect size d [@cohen1988new].
+For testing Hypothesis 1b, concerning HR changes within each interval, we first conducted a linear estimation of the increase or decrease in standardized HR values over time for each participant.
+To this end, we used fixed intercept fixed slope regression models [@gelman2006data] for each interval to estimate intercepts and linear slopes for each individual, which were then averaged across individuals.
+We tested Hypothesis 1b based on the unstandardized estimates of mean slopes (one estimate per participant per interval).
+Addressing our second research goal, we ran linear regression analysis with teaching experience and subjective appraisals as predictors.
+To test Hypothesis 2a, we examined the effect of teaching experience on participants’ HR levels (i.e., mean standardized HR) for each of the five intervals, using linear regression models with teaching experience as the sole predictor.
+To test Hypotheses 2b and 2c, we separately augmented the model by either teachers’ disruption appraisal (Hypothesis 2b) or confidence appraisal (Hypothesis 2c) as predictors, while controlling for teaching experience.
+To test Hypothesis 2d, we examined the effects of all three predictors in one regression model.
+Furthermore, we repeated these steps to explore the effects of teaching experience and subjective appraisals on changes in teachers’ HR (i.e., mean slopes).
+Please note: HR levels and changes were not regressed on the disruption and confidence appraisals in the pre-teaching interval (I1), because the appraised classroom events had not yet taken place in that phase.
 
@@
 \end{table}
+
 ```
@@
 ```
-
-We first tested the hypothesis that teachers showed the highest mean standardized HR during the micro-teaching unit, compared to all other intervals (Hypothesis 1a).
-Repeated measures ANOVA revealed that the mean standardized HR differed statistically significantly between intervals, F(4, 400) = 260.62, p < .05, f = 1.60 (large effect).
-Post-hoc contrasts indicated that, as hypothesized, the mean was significantly higher in the teaching interval (I2) than in all other intervals (see also Fig.
-4).
-Specifically, it was higher than in the pre-teaching interval (I1; t(400)  = -10.08, p < .05, d = 1.03; large effect), the post-teaching interval (I3; t(400) = -6.94, p < .05, d = 1.37; large effect), the interview interval (I4; t(400) = 15.00, p < .05, d = 3.29; large effect), and the end interval (I5); t(400) = 22.54, p < .05, d = 4.64; large effect).
 
@@
 
-Next, we examined HR changes (i.e., mean slopes) within each interval to test for the hypothesis that HR increased during the pre-teaching interval and decreased during all other intervals (Hypothesis 1b).
-The mean intercepts and mean slopes, complemented by their standard deviations for each interval, are shown in Table 2; the graphical representation of the slopes is displayed in Figure 5.
-The mean slope of the pre-teaching interval (I1) was significantly positive, indicating an increase in HR, as hypothesized.
-Further, the mean slopes of the teaching interval (I2) and post-teaching interval (I3) were significantly negative, indicating a decrease in HR.
-For the last two intervals, the interview interval (I4)  and end interval (I5), the mean slope was negative but did not differ significantly from zero.
-
 ```{r table_2, include=FALSE}
@@
 ```
-
-## Research goal 2: Prediction of mean standardized HR and mean slopes with teaching experience and subjective appraisals
-
-Correlations among mean standardized HR/mean slopes (see Table 2), teaching experience (M = 5.64, SD = 9.46), disruption appraisal (M = 5.19, SD = 2.87), and confidence appraisal (M = 7.81, SD = 1.97) are presented in Table 3.
-Correlations between mean standardized HR/mean slopes and the other variables were mostly very small and statistically non-significant, except for the pre-teaching interval (I1), in which mean slope and teaching experience correlated negatively (r=-.27), and the interview interval (I4) in which mean HR and teaching experience correlated positively (r=.24).
-Correlations between teaching experience and appraisals were substantial: more experienced teachers had lower disruption appraisals (r=-.36), and higher confidence appraisals (r=.44).
-Moreover, the two appraisal variables were negatively correlated (r=-.37).
-
-Concerning the effect of teaching experience on participants’ HR levels (i.e., mean standardized HR) for each of the five intervals, teaching experience significantly predicted mean standardized HR only in the interview interval (Table 4, Interview interval, Model 1), indicating a higher mean standardized HR for teachers with more teaching experience.
-This relationship is, in fact, in the opposite direction as predicted by Hypothesis 2a.
-
-Neither adding disruption appraisal (**Hypothesis 2b**) nor adding confidence appraisal (**Hypothesis 2c**) while controlling for the shared variance with teaching experience revealed significant effects on teachers’ mean standardized HR.
-
-When considering the effects of the three predictors in concert (**Hypothesis 2d**), mean standardized HR was significantly predicted only by disruption appraisal, and only in the post-teaching interval (Table 4, Post-teaching interval, Model 4), indicating a higher mean standardized HR for teachers who felt more disrupted by the classroom events, when controlling for the other variables.
-
-Concerning the explorative investigation of the effects of teaching experience and subjective appraisals on changes (i.e., mean slopes) in teachers’ HR, teaching experience significantly predicted the mean slope in the pre-teaching interval (Table 4, Pre-teaching interval, Model 1), indicating a less steep HR increase in teachers with more teaching experience.
-For all other intervals, no variable revealed a significant prediction.
 

### 2024-09-09 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
Tabellen
Format Sachen

@@
             pdfauthor={},
-            pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
+            pdftitle={From heartbeat to data -- Using wearable fitness trackers as an affordable approach to assess teacher stress},
             colorlinks=false,
@@
 
-  \title{New approaches to teachers' experience of stress: Do heart rate
-measurements with fitness trackers provide an efficient, inexpensive,
-and robust measurement method?}
+  \title{From heartbeat to data -- Using wearable fitness trackers as an
+affordable approach to assess teacher stress}
     \author[Leipzig University]{Mandy Klatt%
@@
   \begin{abstract}
-  One or two sentences providing a \textbf{basic introduction} to the
-  field, comprehensible to a scientist in any discipline.
-
-  Two to three sentences of \textbf{more detailed background},
-  comprehensible to scientists in related disciplines.
-
-  One sentence clearly stating the \textbf{general problem} being
-  addressed by this particular study.
-
-  One sentence summarizing the main result (with the words
-  ``\textbf{here we show}'' or their equivalent).
-
-  Two or three sentences explaining what the \textbf{main result}
-  reveals in direct comparison to what was thought to be the case
-  previously, or how the main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more \textbf{general
-  context}.
-
-  Two or three sentences to provide a \textbf{broader perspective},
-  readily comprehensible to a scientist in any discipline.
-
-  XXX In this proof-of-concept study, we aimed to advance the field of
-  teacher stress by collecting heart rate data with wrist-worn devices
-  and testing a methodology that has the potential to provide more
-  insights on the non-invasive assessment of teacher stress. XXX
+  Past research on physiological indicators of teacher stress often had
+  to rely on expensive and obtrusive assessment methods. Modern fitness
+  trackers represent a non-invasive and convenient alternative. This
+  study investigated the use of wrist-worn fitness trackers to assess
+  teacher heart rate (HR) as an indicator of stress during teaching. In
+  a laboratory study, we used a Fitbit® fitness tracker to assess
+  teachers´ HR before, during, and after a potentially stressful
+  micro-teaching session. Our results demonstrate that the fitness
+  tracker was indeed useful for mapping teachers' stress, with the data
+  showing how teachers' HR increased before, peaked during, and
+  progressively decreased after the micro-teaching session. Moreover, we
+  related the fitness tracker data to retrospective teacher
+  self-reports. We found that teachers' subjective stress appraisals,
+  together with their teaching experience, explained only small amounts
+  of variance in HR data. We discuss the potential of fitness trackers
+  as an affordable and ubiquitous assessment tool for research on
+  teacher stress in the classroom and provide advice for practical
+  implementation.
   \end{abstract}
     \begin{keyword}
-    heart rate \sep photoplethysmography \sep wearable electronic
-device \sep 
-    teaching
+    teacher stress \sep fitness tracker \sep heart rate \sep classroom
+disruptions \sep wearable technology \sep 
+    physiological stress measurement
   \end{keyword}
@@
 
-In education, there's interest in identifying reliable indicators for
-teacher stress and burnout \citep{fisher2011, junker2021}. Previous
-research often relied on self-report questionnaires
-\citep{chaplain2008, liu2020}, which may be prone to biases like social
+The teaching profession is one of the most stressful professions, with
+teachers facing a host of stressors during their everyday work
+\citep{smith2000, herman2020, schult2014belastet}. To better understand
+mechanisms in teacher stress, there is a growing research interest in
+physiological measures such as heart rate (HR) as online measures of
+teachers' stress during teaching
+\citep{karner2021teachers, wettstein2020ambulatory}. For example, it has
+been shown that teacher-centered activities and typical
+classroom-related stressors increase teacher HR during teaching
+activities
+\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021, huang2022class}.
+However, previous studies have often relied on expensive and obtrusive
+electrocardiographs (ECG). Modern fitness trackers represent a
+non-invasive and convenient alternative. \citep{ferguson2015}
+
+Classroom disruptions are a major stressor in teachers' daily work
+\citep{boyle1995structural, aloe2014multivariate}, and learning how to
+deal with them is an important aspect of professional expertise
+\citep{wolff2015keeping}. According to \citet{lazarus1990theory}
+transactional model of stress and coping, the experience of stress in
+response to stressors such as classroom disruptions depends on the
+teacher´s subjective appraisal, which, in turn, depends on their coping
+resources, such as their professional knowledge. The resulting stress
+response has a psychological, physiological, or behavioral dimension
+\citep{kyriacou1978}. Therefore, in order to better understand how
+classroom stressors affect teachers' stress response, subjective
+self-reports should be accompanied by objective, physiological measures
+\citep{wettstein2021}. Teachers' use of wrist-worn fitness trackers in
+educational research provides fine-grained, in vivo data, allowing
+researchers as well as teachers themselves to monitor their
+physiological stress response continuously during teaching, across
+settings, and at low costs. Being able to monitor, and eventually
+counteract, teacher stress levels appears particularly relevant given
+the profession's generally high stress levels and associated negative
+health effects \citep{johnson2005experience, montgomery2005meta}. To
+harness this potential, the present study explored the use of
+wrist-based fitness trackers as a tool to assess teachers' HR, as an
+indicator of stress, before, during, and after a teaching session during
+which typical, potentially stressful, classroom disruptions occurred.
+Further, we explored to what extent teachers' subjective appraisals of
+classroom disruptions and their teaching experience predicted teacher
+stress as assessed by the fitness tracker.
+
+\subsection{Fitness trackers as a ubiquitous, low-cost tool for
+assessing physiological stress
+responses}\label{fitness-trackers-as-a-ubiquitous-low-cost-tool-for-assessing-physiological-stress-responses}
+
+Fitness trackers provide data on physical activity and cardiovascular
+parameters such as HR, supporting personalized fitness goals
+\citep{nuss2021effects} and stress management \citep{hao2018chrv}. They
+can be used as ubiquitous, low-cost, and unintrusive data collection
+instruments \citep{godfrey2018z}, and their wide-spread use and everyday
+availability align with the increasing popularity and acceptance of
+wearables among the general population \citep{peng2022acceptance}. In
+contrast to self-reported questionnaires on stress
+\citep{chaplain2008, liu2020} that are prone to biases like social
 desirability \citep{razavi2001self} or recall errors
-\citep{van2016accuracy}. To overcome these limitations, ambulatory
-assessment methods are recommended
-\citep{trull2013ambulatory, wettstein2020ambulatory}, such as measuring
-physiological parameters like heart rate (HR), offering objective
-insights into teachers' stress levels without disrupting their teaching
+\citep{van2016accuracy}, fitness trackers, as ambulatory assessment
+methods \citep{trull2013ambulatory, wettstein2020ambulatory}, offer more
+objective insights into teachers' stress levels by monitoring teachers'
+physiological stress responses without disrupting teaching
 \citep{donker2018, runge2020}.
 
-Current studies on teachers' HR in teaching settings often rely on
-expensive and invasive electrocardiographs
-\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021, huang2022class},
-showing that teacher-centered activities and common stressors lead to
-increased HR. However, using affordable and non-invasive instruments
-like wrist-worn fitness trackers \citep{ferguson2015} could enhance HR
-recording in educational contexts. Unlike clinical devices, fitness
-trackers could offer continuous and less intrusive data collection over
-time \citep{godfrey2018z}, aligning with the increasing popularity and
-acceptance of wearables among the general population
-\citep{peng2022acceptance}. These devices, equipped with biosensors,
-provide users with physiological and behavioral data, offering an
-accessible means for monitoring physical activity and health in daily
-life.
+One important health parameter assessed by nearly all wrist-worn fitness
+trackers is heart rate \citep{scalise2018wearables}. HR indicates the
+number of heartbeats within one minute and is typically expressed as
+beats per minute (BPM)
+\citep{berntson2007cardiovascular, hottenrott2007}. At rest, the average
+HR of adults typically ranges between 60 and 80 BPM
+\citep{sammito2015guideline}. HR can be detected and measured in
+different ways using sensors, such as electrocardiography (ECG) or
+photoplethysmography (PPG) \citep{mukhopadhyay2017wearable}. While ECG
+sensors offer precise measurements by detecting the heart's electrical
+activity, their intrusive nature and requirement of direct skin contact
+may limit their suitability \citep{kranjec2014non}, particularly in
+educational settings. In contrast, photoplethysmography (PPG) is a
+rather uncomplicated and inexpensive technique to measure HR, commonly
+found in commercially available fitness trackers
+\citep{castaneda2018review}. This optical method assesses HR by flashing
+green or red lights to measure changes in blood volume in the
+capillaries of the skin \citep{allen2007photoplethysmography}.
 
-It can be assumed that teachers also wear personal, private fitness
-trackers, generating recordings of physiological data that could be a
-very interesting resource for research on teacher stress. While the use
-of wearable technology in the field has been explored in various domains
-{[}\citet{hughes2023wearable}; @ adesida2019exploring;
-helmer2009smart{]}, research is sparse in educational contexts
-\citep{de2017towards}. Although some studies investigated how wearables
-can help teachers monitor student activity \citep{quintana2016keeping},
-there is a notable research gap regarding teachers' use of wrist-worn
-wearables. Given the high stress levels in the teaching profession
-\citep{johnson2005experience}, fitness trackers could be a valuable tool
-for analyzing HR and the factors contributing to stress. One of the
-reasons for teachers' augmented stress is that they are confronted with
-a multitude of demands in their everyday work, some of which exceed
-their resources and therefore make it difficult to cope with immediate
-stressors such as classroom disruptions \citep{montgomery2005meta}.
-However, the extent of the strain depends on the subjective appraisal of
-a stressor, which involves considerations about available resources to
-deal with it \citep{kyriacou2001}. It is, therefore, particularly
-important for teachers to have sufficient personal and professional
-resources at their disposal \citep{cramer2018belastung}. Classroom
-disruptions, for example, are one of the major stressors in teachers'
-daily work \citep{boyle1995structural, aloe2014multivariate} and
-professional knowledge about effective classroom management reduces the
-risk of teacher stress \citep{klusmann2012berufliche}. Teachers'
-characteristics such as professional experience in turn have an impact
-on the development of classroom management skills and thus on the
-appraisal processes, as these skills develop during professional
-experience \citep{ophardt2017klassenmanagement, wolff2015keeping}.
+Physiologically, HR is regulated by the sympathetic and parasympathetic
+nervous systems \citep{pham2021}. An increase in sympathetic activity
+results in HR being sped up (``fight or flight'' response)
+\citep{taelman2009influence}; whereas an increase in parasympathetic
+activity results in HR being slowed down (``rest and digest'' response)
+\citep{battipaglia2015}. Stress or mental and physical strain directly
+increases HR \citep{custodis2014heart, sachs2014}. Therefore, an
+increase in HR can be regarded as an indicator of increasing stress, and
+a decrease as an indicator of relaxation and ease \citep{kyriacou1978}.
+Thus, fitness trackers offer low-cost and unobtrusive access to
+psychological stress data.
 
-To better understand how stressors like classroom disruptions affect
-teachers and their stress responses, data from wrist-worn fitness
-trackers could be used to monitor physiological parameters before,
-during, and after teaching sessions \citep{wettstein2021}. This study
-explored the use of wrist-based fitness trackers as a tool to monitor
-teachers' stress during different phases of a micro-teaching unit during
-which teachers had to deal with classroom disruptions. Physiological
-data were triangulated with teachers' appraisal of classroom
-disruptions, and their teaching experience. The physiological indicator
-employed in this study was teachers' HR, which can be readily recorded
-by any fitness tracker. Teachers' use of wrist-worn fitness trackers in
-educational research holds transformative potential as obtained
-fine-grained data and underscores the critical need to monitor teachers'
-health as they navigate the stressful landscape of the classroom.
+\subsection{HR in teaching-learning
+contexts}\label{hr-in-teaching-learning-contexts}
 
-\subsection{Fitness Trackers as a Method to Assess HR as an Indicator of
-Stress}\label{fitness-trackers-as-a-method-to-assess-hr-as-an-indicator-of-stress}
+Prior research, typically using ECG methods, has shown that changes in
+teachers' HR can be mapped onto stressors they experience during
+teaching. For example, teachers' HR tends to increase when teachers take
+an exposed position in student-teacher interaction
+\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021}.
+\citet{sperka1995} for example recorded the HR of 16 pre-service
+teachers during their first lesson and showed that teachers' HR
+increased significantly during teaching. The activation was particularly
+prominent at the beginning of the lesson and decreased over the course
+of the lesson. The authors suggested that pre-service teachers'
+proactive coping strategies, such as actively managing student
+interactions, helped lower their HR levels. Other ECG studies identified
+typical stressors predicting increases in HR, such as class size
+\citep{huang2022class}, or low student engagement and motivation
+\citep{junker2021}. \citet{junker2021} recorded the HR of 40 teachers
+during a real classroom lesson. Again, teacher stress, induced by
+factors such as low student engagement (e.g., lack of motivation or
+interest in tasks) or teacher-centered activities (e.g., teacher-focused
+classroom activities), resulted in elevated HR.
 
-Wearables, defined as electronic devices worn directly on the body or
-integrated into clothing or accessories, serve as versatile solutions
-\citep{godfrey2018z}, gathering data like location, movements, and vital
-signs \citep{cheng2017underlying}. Fitness trackers, a popular wearable
-type \citep{park2020user}, offer insights into physical activity and
-cardiovascular health, supporting personalized fitness goals
-\citep{nuss2021effects} and stress management \citep{hao2018chrv}. Their
-affordability and ease of use make them ideal not only for various
-domains including healthcare, entertainment, and fitness
-{[}sinha2019taxonomy{]} but also in education as they offer added
-benefits for formal and informal learning environments for both students
-and teachers \citep{de2017towards}. Yet, few studies focus on their
-significance for teachers.
+More recent studies have begun using wrist-worn fitness trackers to
+investigate HR trends in instructional settings
+\citep{Darnell2019, chalmers2021}. \citet{Darnell2019} measured the HR
+of 15 medical college students listening to lectures, using wrist-worn
+devices. The analysis revealed a constant decrease in HR throughout the
+lecture, with HR peaks during more interactive learning phases.
+\citet{chalmers2021} used HR data from a fitness tracker to identify
+physiological changes during stress-inducing tasks (i.e., the Trier
+Social Stress Test; \citet{kirschbaum1993trier}{]}. Average HR increased
+significantly from the resting to the stress inducing phases. Even
+though the participants of these previous studies
+\citep{Darnell2019, chalmers2021} were not teachers but learners, the
+results are relevant for studying teacher stress as they demonstrated
+that HR can be effectively recorded using fitness trackers over the
+course of a whole learning unit, and HR changes are in line with the
+occurrence of activating or stress-inducing tasks.
 
-One important health parameter assessed by nearly all wrist wearables is
-HR \citep{scalise2018wearables}. HR indicates the number of heartbeats
-within one minute and is typically expressed as beats per minute (BPM)
-\citep{hottenrott2007}. At rest, the average HR of adults typically
-ranges from 60 to 80 BPM \citep{sammito2015guideline}. HR can be
-detected and measured using sensors based on electrocardiogram (ECG) or
-phonocardiogram (PCG) \citep{mukhopadhyay2017wearable}. Another
-uncomplicated and inexpensive technique to measure HR via fitness
-trackers is photoplethysmography (PPG) \citep{castaneda2018review}. This
-optical method assesses HR by flashing green or red lights to measure
-changes in blood volume \citep{allen2007photoplethysmography}.\\
-Physiologically, HR is regulated and influenced on short-time intervals
-by the sympathetic and the parasympathetic nervous system
-\citep{pham2021}. An increase in the activity of the sympathetic system
-results in HR being speeded up (``fight or flight'')
-\citep{taelman2009influence}. In contrast, increased activity of the
-parasympathetic has the effect of slowing down the HR (``rest and
-digest'') \citep{battipaglia2015}. Therefore, an increase in HR can be
-regarded as an indicator of increasing stress, and a decrease as an
-indicator of decreasing stress \citep{kyriacou1978}.
+To the best of our knowledge, only one study has directly assessed
+teachers' HR during teaching using a wrist-worn fitness tracker:
+\citet{runge2020} assessed HR as an indicator of stress in four
+in-service teachers during authentic lessons. They used fitness
+trackers' recordings to create a profile for each teacher, with the aim
+of differentiating between teachers reporting higher vs.~lower levels of
+stress. It was found that the combination of a high HR, a high number of
+steps, and short sleep duration was characteristic for teachers
+reporting high stress levels. However, it should be noted that the
+generalizability of these results is limited due to the small sample
+size.
 
-\subsection{Teacher Stress and Important
-Resources}\label{teacher-stress-and-important-resources}
+In summary, previous studies have revealed that teachers' (and
+students') HR changes depend on their activities and the stressors they
+experience, with an increase in HR already before the expected stressors
+occur, and with peaks in activating phases
+\citep{Darnell2019, chalmers2021}. For teachers, teacher-centered phases
+led to an increase in HR
+\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021}.
+However, there is a lack of studies using teacher-worn fitness trackers
+in larger samples, exploring the feasibility of this convenient tool for
+researching links between teachers' HR and stress inducing events and
+mechanisms.
 
-The teaching profession is one of the most stressful professions
-compared to other occupational groups, facing a variety of stressors
-during everyday work \citep{smith2000, herman2020, schult2014belastet}.
+\subsection{A model of teacher stress}\label{a-model-of-teacher-stress}
+
 According to \citet{kyriacou1978}, teacher stress can be defined as a
-negative affective response, often accompanied by physiological changes
-such as increased HR, triggered by job-related demands and perceived as
-threatening to one's self-esteem or well-being. Coping mechanisms help
-to reduce the perceived threat.
-
-This definition of teacher stress is based on the transactional stress
-model by Lazarus and colleagues
-\citep{lazarus1981stressbezogene, lazarus1984stress}, which was modified
-and tailored to the teaching-learning environment by
-\citet{kyriacou1978}.
-
-In general, the transactional stress model \citep{lazarus1990theory}
-highlights the interaction between an individual and the environment,
-whereby stress refers to any event that exceeds a person's adaptive
-resources. It has been shown that there are important connections
-between stressors and resources experienced by teachers on the one hand,
-and stress-induced health issues on the other hand
-\citep{krause2013messung}. As we are interested in how specific
-classroom events affect teacher stress, we adapted the transactional
-stress model to that type of situation, based on a representation of the
-model first proposed by {[}van2006stress{]}; this working model is
-depicted in Fig. 1.
+negative affective response, typically accompanied by physiological
+changes such as increased HR, triggered by job-related demands, and
+perceived as threatening to one's self-esteem or well-being. Coping
+mechanisms help to reduce the perceived threat. Kyriacou's definition of
+teacher stress (see \citet{kyriacou1978} and, for a more recent
+adaptation, \citet{van2006stress}) is based on the transactional stress
+model by Lazarus and colleagues {[}lazarus1966psychological;
+\citet{lazarus1990theory}{]}, which highlights the interaction between
+an individual and the environment, whereby stress refers to a person's
+subjective reaction to an event (a stressor) that exceeds the person's
+adaptive resources.
 
@@
   \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
-  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the author)}
-  \label{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the author)}
+  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
+  \label{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
 \end{figure}
 
-When potential stressors (e.g., classroom disruptions) occur during
-teaching (1), teachers subjectively appraise how disruptive the event is
-(2). If potential stressors are judged as threatening, i.e., as actual
-stressors (3), teachers consider whether they have sufficient resources
-for coping with the stressor (4). Based on this evaluation of resources
-and their characteristics such as professional experience, teachers try
-to manage classroom disruptions, by utilizing classroom management
-strategies (5). In cases where coping fails, stress ensues, often
-accompanied by physiological reactions like increased HR (6). Following
-resource appraisal and coping outcomes, the stressor is re-evaluated
-(7).
+Fig. 1 shows, in a simplified way, how classroom events affect teachers'
+stress level, according to the adaptation of the Lazarus model to
+teacher stress proposed by \citet{van2006stress}: When potential
+stressors (e.g., classroom disruptions) occur during teaching (1),
+teachers intuitively judge how disruptive the event is in a primary
+appraisal (2). If potential stressors are judged as threatening, i.e.,
+as actual stressors (3), teachers consider whether they have sufficient
+resources for coping with the stressors (4). Teachers utilize these
+resources in trying to cope with the stressors, e.g., by employing
+classroom management strategies (5). In cases when coping fails, stress
+ensues, often accompanied by physiological reactions like increased HR
+(6). As part of the coping process, and dependent on its outcomes,
+teachers re-evaluate the stressor (7).
 
-The appraisal processes of resources play a crucial role as teachers'
-assessments of resources and coping mechanisms, both internal (e.g.,
-classroom management skills) and external (e.g., supportive colleagues),
-significantly impact their stress levels. When resources are lacking and
-coping fails, negative consequences like burnout and high turnover can
-arise \citep{jalongo2006, unterbrink2007, aloe2014}. This highlights the
-importance of teachers' appraisal of their professional competencies,
-including their ability to manage classroom disruptions effectively
-\citep{klieme2008concept, konig2016teacher}.
-
-As shown in Fig. 1, both primary and secondary appraisals are influenced
-by teachers' characteristics, e.g., their professional experience,
-shaping their classroom management skills. As experience grows, teachers
-develop cognitive scripts for managing classroom events resulting in
-more complex classroom management skills \citep{wolff2021classroom}.
-Especially beginning teachers face considerable stress and often feel
-overwhelmed by the demands of teaching
-{[}\citet{ophardt2017klassenmanagement}; \citet{wolff2015keeping}; @
-klusmann2012berufliche{]}, with many leaving the profession within the
-first five years \citep{ingersoll2003}. Research shows less experienced
-teachers are more susceptible to burnout, underscoring the importance of
-experience and job satisfaction in predicting teacher stress
+As shown in Fig. 1, teachers' primary and secondary appraisal as well as
+coping attempts are influenced by professional experience. As
+professional experience grows, teachers develop cognitive scripts for
+managing classroom events, resulting in more complex and problem-focused
+classroom management skills \citep{wolff2021classroom}, and thus more
+effective coping and less stress. Empirically, classroom management
+skills and problem-focused coping styles are linked to fewer instances
+of emotional exhaustion \citep{maslach2001job, clunies2008self}. Novices
+in the teaching profession, on the other hand, face considerable stress
+and often feel overwhelmed by the demands of teaching
+\citep{ophardt2017klassenmanagement, wolff2015keeping, klusmann2012berufliche}
+with many leaving the profession within the first five years
+\citep{ingersoll2003}. Accordingly, when resources are lacking and
+coping fails, negative consequences for health (e.g., burnout) and for
+work (e.g., high turnover rates) can arise
+\citep{jalongo2006, unterbrink2007, aloe2014multivariate}, highlighting
+the importance of professional expertise for managing teacher stress
 \citep{fisher2011}.
-
-\subsection{HR in Teaching-Learning
-Contexts}\label{hr-in-teaching-learning-contexts}
-
-ECG studies have revealed that HR can be used to map changes in HR
-during teaching onto stressors experienced by teachers. For example, HR
-increased during teacher-centered activities when teachers had to take a
-leading position in the student-teacher interaction
-\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021}.
-\citet{sperka1995} for example recorded the HR of 16 pre-service
-teachers during their first lesson. The results showed significantly
-increased psychophysiological activation in terms of an increased HR
-during teaching. The activation effect was particularly prominent at the
-beginning of the lesson and decreased over the course of the lesson. The
-authors interpret this result as showing how pre-service teachers'
-active coping processes, i.e., the active management of the interaction
-with the students, helped the teachers regulate their HR downwards.
-Other ECG studies identified typical stressors predicting increased HR
-values, such as class size \citep{huang2022class}, or low student
-engagement and motivation \citep{junker2021}. For example,
-\citet{junker2021} recorded the HR of 40 teachers using an ambulatory
-monitoring system during a real classroom lesson. They provided evidence
-that teacher stress caused by stressors such as low student engagement,
-i.e., students displaying a lack of motivation or limited interest in
-their tasks or classroom activities, or teacher-centered activities,
-i.e., classroom activities primarily focused on the teacher's actions.,
-leads to an increase in HR.
-
-In addition to ECG studies, there are a few studies that used wrist-worn
-fitness trackers to investigate HR trends in teaching-learning
-situations \citep{Darnell2019, chalmers2021}. \citet{Darnell2019} for
-example measured the HR of 15 medical college students using wrist-worn
-devices during lectures. The analysis revealed a constant decrease in HR
-from the beginning to the end of a lecture, whereas the HR peak was
-reached during active learning sessions. \citet{chalmers2021} examined
-the usability of the average HR, measured with a Fitbit fitness tracker,
-to identify physiological changes during stress-inducing tasks in a
-study with a total of 60 participants. The average HR increased
-significantly between the resting and stress phases. Even though the
-participants in these studies were learners, not teachers, the results
-are relevant to the study of teacher stress using wearable devices,
-because the studies showed that a) HR can be effectively recorded using
-fitness trackers during a whole learning unit, and b) HR changes are in
-line with the occurrence of activating or stress-inducing tasks.
-
-So far, to the best of our knowledge, only one study has directly
-assessed teachers' HR using a wrist-worn fitness tracker during teaching
-: \citet{runge2020} used a Fitbit fitness tracker to assess HR as an
-indicator of stress in N=4 teachers. They used the fitness trackers'
-recordings to create a profile for each teacher (to differentiate
-between teachers reporting higher or lower levels of stress .) In
-particular, it was found that the combination of a high number of steps,
-a high HR, and short sleep was an indicator of stress. It should be
-noted that the generalizability of the results is limited due to the
-small sample size.
-
-In summary, previous studies have revealed that teachers' (and
-students') HR changes, depending on the activity and stressors they
-experience, whereby teacher-centered phases , in particular, led to an
-increase in HR
-\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021}.
-Furthermore, it could be shown that HR as an indicator of stress can be
-assessed using low-cost, non-intrusive fitness trackers and that HR
-increases in activating phases and even before stress occurs
-\citep{Darnell2019, chalmers2021}. However, studies collecting data from
-teacher-worn fitness trackers in a large enough sample to explore links
-with factors such as subjective stressor appraisal, or effects of
-teaching experience, are still lacking. Our study aims to close this
-research gap.
 
@@
 
-The data analyzed for the present study were obtained from teachers and
-student teachers who participated in a lab study, as part of a larger
-project targeting the development of classroom management in teachers.
-
-As part of the larger project, participants came to the lab
-individually, and each taught a 15-minute, self-prepared micro-teaching
-unit to a ``class'' of three actors (trained student assistants). These
-actors performed nine, possibly disruptive, classroom events. The actors
-received standardized instructions on a screen (only visible to them,
-not to the participant) to perform a classroom event every one and a
-half minutes, and they performed the same scripted disruptions for all
-participants. While teaching, participants wore eye-tracking glasses,
-and additionally, their lessons were recorded by cameras.
-
-The micro-teaching unit, with its unfamiliar setting and the scripted
-disruptions of participants' teaching flow, was potentially stressful.
-Thus, we were particularly interested in the development of
-participants' HR before, during, and after this micro-teaching unit. We
-recorded HR data in five phases, with a total duration of approximately
-two hours: In the \emph{pre-teaching phase}, participants were welcomed,
-prepared for the following micro-teaching unit, and familiarized with
-the setting. In the \emph{teaching phase}, participants taught the
-micro-teaching unit and experienced the classroom disruptions. In the
-\emph{post-teaching phase}, participants answered several questionnaires
-in a comfortable seated position. Next, in the \emph{interview phase},
-they watched the video of their 15-minute unit, rated the disruptive
-classroom events, and answered open questions. Finally, in the \emph{end
-phase}, participants answered another questionnaire. These conditions
-were identical for all participants. During the entire study,
-participants wore a fitness tracker on their wrist.
-
-The goals of the present study were twofold:
+The present study aimed to explore the relations between teachers' HR
+response, and their subjective appraisals of stress during a
+micro-teaching unit, and to relate their self-reported appraisals and
+physiological stress responses to their teaching experience. We analyzed
+data from in-service and pre-service teachers who participated in a
+laboratory study as part of a larger project targeting the development
+of classroom management skills. Participants came to the lab
+individually and taught a short lesson to a class of three actors (i.e.,
+trained student assistants) who performed several typical and possibly
+disruptive classroom events. The micro-teaching unit was thus
+potentially stressful for the participants. The aims of the present
+study were twofold:
 
@@
   The first research goal was to investigate whether HR measures
-  assessed by wrist-based fitness trackers are a suitable and effective
-  method for mapping teachers' HR over the course of a five-phase lab
-  study, including the time before, during, and after a potentially
-  stressful micro-teaching unit.
+  assessed by a wrist-based fitness tracker were a suitable and
+  effective method for mapping teachers' HR over the course of the lab
+  study, with a total duration of approximately 2 hours, including
+  phases before, during, and after the stressful micro-teaching unit.
 \end{enumerate}
 
-First, we expected the participants to show an initial increase in their
-HR, followed by a peak during the teaching phase and a decrease for the
-remaining phases. In addition, we examined whether z-standardization of
-the participants' mean HR could serve as a useful method to account for
-individual differences in baseline HR. We expected to observe the same
-trends in both standardized and non-standardized mean HR values.
+Looking at HR measures globally, we expected the participants to show an
+initial increase in their HR, followed by a peak during the
+micro-teaching unit and a decrease for the remaining phases. In
+addition, we examined whether z-standardization of the participants' HR
+could serve as a useful method to account for individual differences in
+baseline HR: We expected to observe the same trends in both standardized
+and non-standardized HR values.
 
-Second, five representative 10-minute intervals were selected from the
-five phases (see section \#\#Measures for a more detailed description of
-the intervals), which served as the basis for the data analysis for our
-hypothesis: pre-teaching interval (\(I_1\)), teaching interval
-(\(I_2\)), post-teaching interval (\(I_3\)), interview interval
-(\(I_4\)), end interval (\(I_5\)). We examined the levels of and the
-changes in HR during these intervals. We assumed the highest HR level in
-the teaching interval (\(I_2\)) and lower levels in all other intervals
-(\textbf{Hypothesis 1a}). Further, we expected an increase in
-participants' HR while they were preparing for teaching during the
-pre-teaching interval (\(I_1\)), and we expected a decrease in
-participants' HR during all of the following intervals, because of
-habituating to (\(I_2\)) and recovering from (\(I_3\)-\(I_5\)) the
-stressful teaching phase (\textbf{Hypothesis 1b}).
+In addition, we selected five representative 10-minute intervals from
+the five phases of the lab study (see Figure 2) in order to test the
+hypotheses that, regarding HR levels, teachers' HR would be the highest
+during the micro-teaching unit, compared to all other phases
+(\textbf{Hypothesis 1a}), and, regarding HR slopes, that teachers' HR
+would increase while they were preparing for teaching (pre-teaching
+interval), but decrease in all of the following intervals, i.e.~when
+they were habituating to and recovering from the stressful
+micro-teaching unit (\textbf{Hypothesis 1b}).
 
@@
 \item
-  The second research goal was to examine whether variance in HR
-  measures could be explained by participants' teaching experience
-  (because, presumable, more experienced teachers might have better
-  classroom management strategies, and thus better resources for
-  coping), and/or by their self-reported subjective appraisals of
-  classroom events (specifically, how disruptive it was, and how
-  confident they felt in their coping).
+  We further explored whether teaching experience made a difference in
+  how teachers' HR reacted to the classroom disruptions. We expected
+  more experienced teachers to be less stressed by the classroom events
+  (\textbf{Hypothesis 2a}). In addition, we examined the relations
+  between teachers' subjective appraisals of the classroom events
+  (specifically, the disruptiveness of the events, and their confidence
+  in dealing with them) and teachers' HR level, beyond the explanatory
+  power of teaching experience. We expected higher HR levels for
+  teachers who felt more disrupted, regardless of their teaching
+  experience (\textbf{Hypotheses 2b}), and lower HR levels for teachers
+  who felt more confident, regardless of teaching experience
+  (\textbf{Hypothesis 2c}). We hypothesized that each of the three
+  predictors (\emph{teaching experience, disruption appraisal,
+  confidence appraisal}) uniquely contributed to explaining variance in
+  teachers' HR levels (\textbf{Hypothesis 2d}). In addition, we
+  exploratively ran analogous analyses for the \emph{changes} in HR
+  (i.e., slopes).
 \end{enumerate}
-
-We expected lower HR levels for teachers with more teaching experience,
-particularly during the teaching interval (\textbf{Hypothesis 2a}). We
-expected higher HR levels for teachers who felt more disrupted by the
-enacted classroom events, regardless of their teaching experience
-(\textbf{Hypotheses 2b}). At the same time, we expected lower HR levels
-for teachers who felt more confident in dealing with the events,
-regardless of teaching experience (\textbf{Hypothesis 2c}). Lastly, we
-hypothesized that each of the three predictors (teaching experience,
-disruption appraisal, confidence appraisal) uniquely contributes to
-explaining variance in teachers´ HR levels (\textbf{Hypothesis 2d}). In
-addition, we exploratively examined the same as for the HR levels again
-for the changes in HR.
 
@@
 The sample consisted of \(N\) = 84 pre- and in-service teachers from
-Germany, who were recruited via personal contact, email lists, and
+Germany, who were recruited via personal contacts, email lists, and
 flyers. The data of three participants was lost due to failed data
-transmission, yielding an analysis sample of \(n\) =
-\texttt{N\_postwrangling} (\(n\) = 52 women, \(n\) = 29 men).
-Participants had a mean age of 30.95 years (\(SD\) = 10.90; range:
-19-60) and an average teaching experience of 5.64 years (\(SD\) = 9.46;
-range: 0-37).
+transmission, yielding an analysis sample of \(n_{total}\) = 81
+(\(n_{total}\) = 52 women, \(n_{total}\) = 29 men), including 40
+pre-service and 41 in-service teachers. Participants had a mean age of
+30.95 years (\(SD\) = 10.90; range: 19-60) and an average teaching
+experience of 5.64 years (\(SD\) = 9.46; range: 0-37).
 
@@
 approval of the University's Institutional Review Board. All
-participants were informed in detail about the aims and intention of the
-study before testing. Participation was voluntary and only took place
-after written consent had been given. Participants were not rewarded in
-any way for participating in the study.
-
-\begin{wrapfigure}{r}{0.5\textwidth}
-  \centering
-  \includegraphics[width=0.5\textwidth]{images/Timeline_small.pdf}
-  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
-  \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
-\end{wrapfigure}
+participants were informed in detail about the aims of the study prior
+to testing. Participation was voluntary, not incentivized, and only took
+place after written consent had been given.
 
 Each participant came to the lab for a period of approximately two hours
-in total, and each underwent the same phases: \emph{pre-teaching phase},
-\emph{teaching phase}, \emph{post-teaching phase}, \emph{interview
-phase}, and \emph{end phase} (please refer to Fig. 2 for a timeline). In
-the \emph{pre-teaching phase}, the experimenter welcomed the
+in total, and each participant underwent the same phases (see Fig. 2):
+In the \emph{pre-teaching phase}, the experimenter welcomed the
 participants and helped them put on the fitness tracker. This was
@@
 around. During the \emph{teaching phase}, the participants held their
-self-prepared, micro-teaching unit to a class of three trained actors
-who performed nine, potentially disruptive, classroom events (e.g.,
-chatting with a neighbor, heckling, looking at the phone; see Table \#\#
-in the supplementary material for an overview and categorization of all
-events; also see Fig\#\# for a depiction of the laboratory setting of
-the micro-teaching unit). In preparation for the 15-minute lesson, the
-topic and class level could be freely chosen by the teachers. The type
-of course was to be an introductory lesson and the desired social form
-required individual work or frontal teaching, without longer video
-sequences and movement of the actors. The teaching unit lasted about
-15-20 minutes. Participants spent this time mostly standing or slowly
-walking around. After having completed the micro-teaching unit, in the
-\emph{post-teaching phase}, participants were seated at a desk and
-filled in questionnaires for approximately 10-15 minutes: a brief
-computer-based questionnaire assessing sociodemographic data (e.g.,
-teaching experience, gender, studied school type, studied school
-subjects, extracurricular teaching activities), and a short knowledge
-test that is irrelevant to the present study. In the \emph{interview
-phase}, the participants watched the video of their own teaching
-together with the experimenter. While doing so, they were given a
-Stimulated Recall Interview (SRI), in which the participants watched
-their recorded eye-tracking video of the lesson from the ego
-perspective, indicating the participants' gaze point. The experimenter
-stopped the video each time one of the nine classroom events happened
-and asked a total of eight questions, five of which were open and three
-closed. We assessed -- among other questions irrelevant to this study --
-with two closed questions the teachers' subjective appraisal of the
-classroom events that took place during the \emph{teaching phase} in
-terms of how subjectively disruptive they were (disruption appraisal)
-and how confident the participants felt dealing with them (confidence
-appraisal) with one item each. The interview lasted about 45-60 minutes
-and the participants' position was seated. The \emph{end phase} lasted
-about 10-15 minutes and participants answered in a seated position
-another questionnaire irrelevant to this study.
+self-prepared micro-teaching unit to a class of three trained actors who
+performed nine, potentially disruptive, classroom events (e.g., chatting
+with a neighbor, heckling, looking at the phone; see Table \#\# in the
+supplementary material for an overview and categorization of all events;
+and Fig\#\# in the supplementary material for a depiction of the
+laboratory setting of the micro-teaching unit). The topic and class
+level of the teaching unit could be freely chosen by the teachers with
+the only requirement that the unit had to be an introductory lesson, and
+had to consist of supervised individual work and / or frontal teaching.
+The micro-teaching unit lasted about 15-20 minutes. Participants spent
+this time mostly standing or slowly walking around. While teaching,
+participants wore eye-tracking glasses, and their lesson was
+video-recorded. After having completed the micro-teaching unit, in the
+\emph{post-teaching phase}, participants filled in questionnaires for
+approximately 10-15 minutes: a brief computer-based survey of
+sociodemographic data (e.g., teaching experience, gender, studied school
+type, studied school subjects, extracurricular teaching activities), and
+a short knowledge test that was irrelevant to the present study. In the
+\emph{interview phase},
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+  \centering
+  \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
+  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
+  \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
+\end{wrapfigure}
+
+\noindent participants engaged in a Stimulated Recall Interview (SRI).
+During the SRI, participants sat in front of a computer monitor and
+watched the video of their own lesson from the ego perspective, as
+recorded through the eye-tracking glasses. The experimenter stopped the
+video each time one of the nine classroom events happened, and asked
+five open-ended, and three rating questions per event. Two of the rating
+questions are relevant to the present study: the disruption and the
+confidence appraisal ratings (see Measures). The interview lasted about
+45-60 minutes. Finally, in the \emph{end phase}, participants filled in
+another questionnaire irrelevant to the present study, which lasted
+about 10-15 minutes.
 
@@
 
-To measure the teachers' HR, we used a wrist-based fitness tracker. The
-model was a Fitbit Charge 4. In line with the manufacturer's
-instructions \citep{fitbitnd}, the device was attached a finger's width
-above the participants' nondominant hand's wrist bone. The tracker works
-by flashing green LEDs hundreds of times per second, using
-light-sensitive photodiodes to catch the reflected light, and from that
-information calculating volume changes in the capillaries. From this,
-the tracker calculates how many times the heart beats per minute. HR
-measurements are generated at least every 15 seconds\footnote{The
-  fluctuations in the number of seconds in which the HR was measured are
-  due to the participants' movements, meaning that the device could not
-  measure the HR every second.}. The raw data that can be extracted from
-the tracker lists the time stamps of all measurements and the estimated
-HR in BPM for each time stamp.
+To measure teachers' HR, we used the wrist-based fitness tracker Fitbit®
+Charge 4. In line with the manufacturer's instructions \citep{fitbitnd},
+the device was attached to the participants' nondominant hand, a
+finger's width above the wrist bone. The tracker works by flashing green
+LEDs hundreds of times per second, using light-sensitive photodiodes to
+catch the reflected light, to calculate the volume changes in the
+capillaries. From this, the tracker calculated the heart beats per
+minute. HR measurements were generated at least every 15 seconds . The
+raw data contained the estimated HR in BPM for each time stamp. To
+account for individual differences in the baseline HR, we also
+calculated z-standardized HR values based on individual means, i.e., at
+the subject level of \(n\) = 81 participants (standardized HR).
 
-The anonymous HR data was synced via Bluetooth to a commercial Fitbit
-account. Subsequently, the intraday second-by-second data was exported
-as a CSV file for each session using the open-source software PulseWatch
-(Ricci, n.d.), and linked to the participant. To account for individual
-differences in the baseline HR, we first z-standardized the BPM values
-from the unstandardized mean HRs.
-
-Since we aimed to explore teachers' HR between different strain phases,
-we aggregated HR over a 10-minute interval within each phase. Previous
-research has indicated that 10-minute intervals are a useful duration
-for analyzing PPG data \citep{lu2008can}. The intervals were selected
-based on the following rules: The pre-teaching interval (\(I_1\))
-comprised the first 10 minutes after the fitness tracker had been put
-on. The teaching interval (\(I_2\)) started two minutes after the
-teacher had started the teaching unit. This interval was of the highest
-relevance to our study. We explicitly chose an early 10-minute interval
-within the teaching phase, as previous studies revealed that the
-beginning of a lesson is essential and demanding regarding
-teacher-student interaction
-\citep{donker2018quantitative, claessens2017positive}. The post-teaching
-interval (\(I_3\)) started immediately after the end of the teaching
-unit. The interview interval (\(I_4\)) was defined as the mid-10 minutes
-between the end of the teaching unit and the time point when the fitness
-tracker was taken off so that all participants were being interviewed
-during this interval. The end interval (\(I_5\)) comprised the last 10
+Since we aimed to keep measurement intervals comparable between study
+phases, we aggregated HR over a representative 10-minute interval within
+each phase (cf.~Fig. 2). Previous research has indicated that 10-minute
+intervals are a useful duration for analyzing PPG data
+\citep{lu2008can}. The intervals were selected based on the following
+rules: The \emph{pre-teaching interval} (\(I_1\)) comprised the first 10
+minutes after the fitness tracker had been put on. The \emph{teaching
+interval} (\(I_2\)) started two minutes after the lesson had started.
+This interval was of the highest relevance to our study. We explicitly
+chose an early 10-minute interval within the teaching phase, as previous
+studies revealed that the beginning of a lesson is most demanding and
+potentially stressful with regards to teacher-student interaction
+\citep{donker2018, claessens2017positive}. The \emph{post-teaching
+interval} (\(I_3\)) started immediately after the end of the teaching
+unit. The \emph{interview interval} (\(I_4\)) was defined as the mid-10
+minutes between the end of the teaching unit and the time point when the
+fitness tracker was taken off. All participants were being interviewed
+during this interval. The end interval (I5) comprised the last 10
 minutes before the fitness tracker was taken off.
-
-\subsubsection{Teaching Experience}\label{teaching-experience}
-
-The participants' teaching experience was assessed as a part of
-sociodemographic data. Participants stated their work experience in
-years (excluding the traineeship year).
-
-\subsubsection{Subjective appraisal of the classroom events and coping
-processes}\label{subjective-appraisal-of-the-classroom-events-and-coping-processes}
-
-The subjective disruption and confidence appraisals assessed in the SRI
-on an 11-point rating scale were averaged across the nine classroom
-events as we were not interested in individual classroom events, but
-only in the expected mean level of arousal during the \emph{teaching
-phase}. Regarding the model (see Fig. 1), the disruption appraisal was
-used to assess the evaluation of the stressor (see Fig. 1, box 2). The
-confidence appraisal, in contrast, referred to the resources available
-for coping with the stressors (see Fig. 1, box 4).
-
-\subsection{Data analysis}\label{data-analysis}
-
-We conducted all analyses with R \citep{RStudio2020}. Graphics were
-created using ggplot2 (v3.3.3; Wickham, 2016).
-
-\textbf{Research goal 1}. The first research goal included mapping
-teachers' HR before, during, and following a micro-teaching unit in the
-course of a five-phase lab study.
-
-Regarding the teachers' HR trend, we displayed the HR trend over the
-course of the entire study. For z-standardization as a method to account
-for individual differences in the baseline HR, we visually compared
-unstandardized and standardized mean HR trends for the entire two-hours
-study{[}\^{}3{]}. For all further analyses, we used standardized rather
-than unstandardized HR values. {[}\^{}3{]}: Note that the study exceeded
-the planned duration of two hours for a few participants. To avoid
-distortions when mapping the HR over the course of the study (see Fig.
-3), the endpoint was set at two hours for all participants, even though
-data from later time points was used in the \emph{end interval} for a
-few participants.
-
-For testing Hypothesis 1a, which examined the HR levels in the different
-intervals, we initially conducted a one-way ANOVA with repeated measures
-as an omnibus test. The dependent variable comprised the standardized HR
-mean for each interval. To identify the highest HR level, we
-subsequently conducted t-tests with planned contrasts as post-hoc tests,
-accompanied by the effect size d \citep{cohen1988new}. Specifically, we
-tested the differences between the teaching interval (\(I_2\)) and the
-other four intervals. Note that mean HR was calculated at the subject
-level of \(n\) = 81 participants (see Table 1), whereas the mean slope
-and mean intercept estimates are based on all values at all measurement
-time points (see Table 2). For testing Hypothesis 1b, which examined the
-HR changes within each interval, we conducted a linear estimation of the
-increase or decrease in HR over time. To this end, we used fixed
-intercept fixed slope regression models \citep{gelman2006data} for each
-interval to estimate intercepts and linear slopes for all individuals
-which were then averaged across individuals\footnote{Although this
-  procedure does not account for nonmonotonic progressions in individual
-  HR, a graphical evaluation revealed that the linear estimates
-  corresponded well to the majority of the cases (see XX in the
-  supplementary material).}.
-
-\textbf{Research goal 2}. In addressing our second research goal, we
-examined the effects of teaching experience and subjective appraisal of
-disruptive classroom events on teachers' HR levels during the five
-phases.
-
-To test hypothesis 2a, we examined the effect of teaching experience on
-participants' HR levels for each of the five intervals using linear
-regression models with teaching experience as the sole predictor. To
-test hypotheses 2b and 2c, we separately augmented the models by either
-teachers' disruption appraisal (Hypothesis 2b) or confidence appraisal
-(Hypothesis 2c), while controlling for shared variance with teaching
-experience. HR levels were only predicted with the disruption and
-confidence appraisal after the teaching had taken place, i.e., for all
-the intervals following the pre-teaching interval (I1). To test
-hypothesis 2d, we examined the effects of all three predictors in one
-regression model. We repeated these steps to explore the effect of
-teaching experience and subjective appraisals on changes in teachers' HR
-at each interval.
-
-\section{Results}\label{results}
-
-\subsection{Research goal 1: Mapping teachers' HR over the course of the
-study
-phases}\label{research-goal-1-mapping-teachers-hr-over-the-course-of-the-study-phases}
-
-The first part of our first research goal was to map participants'
-overall HR trend and explore whether z-standardization of participants'
-HR is a useful method to account for individual differences in the
-baseline HR. Means, standard deviations, and range of teachers'
-unstandardized and standardized HR are shown in Table 1. Fig. 3 a. and
-b. display the unstandardized and standardized HR trends, respectively.
-HR initially increased, peaked, and then decreased, with the
-unstandardized and standardized HR graphs showing high similarity. Thus,
-for all further analyses, we used participants' standardized HR values.
 
@@
 
-We first tested the hypothesis that teachers showed the highest mean
-standardized HR during the micro-teaching unit, compared to all other
-intervals (Hypothesis 1a). Repeated measures ANOVA revealed that the
-mean standardized HR differed statistically significantly between
-intervals, F(4, 400) = 260.62, p \textless{} .05, f = 1.60 (large
-effect). Post-hoc contrasts indicated that, as hypothesized, the mean
-was significantly higher in the teaching interval (I2) than in all other
-intervals (see also Fig. 4). Specifically, it was higher than in the
-pre-teaching interval (I1; t(400) = -10.08, p \textless{} .05, d = 1.03;
-large effect), the post-teaching interval (I3; t(400) = -6.94, p
-\textless{} .05, d = 1.37; large effect), the interview interval (I4;
-t(400) = 15.00, p \textless{} .05, d = 3.29; large effect), and the end
-interval (I5); t(400) = 22.54, p \textless{} .05, d = 4.64; large
-effect).
-
 \begin{figure}[H]
@@
 \end{figure}
-
-Next, we examined HR changes (i.e., mean slopes) within each interval to
-test for the hypothesis that HR increased during the pre-teaching
-interval and decreased during all other intervals (Hypothesis 1b). The
-mean intercepts and mean slopes, complemented by their standard
-deviations for each interval, are shown in Table 2; the graphical
-representation of the slopes is displayed in Figure 5. The mean slope of
-the pre-teaching interval (I1) was significantly positive, indicating an
-increase in HR, as hypothesized. Further, the mean slopes of the
-teaching interval (I2) and post-teaching interval (I3) were
-significantly negative, indicating a decrease in HR. For the last two
-intervals, the interview interval (I4) and end interval (I5), the mean
-slope was negative but did not differ significantly from zero.
 
@@
 \end{table}
-
-\subsection{Research goal 2: Prediction of mean standardized HR and mean
-slopes with teaching experience and subjective
-appraisals}\label{research-goal-2-prediction-of-mean-standardized-hr-and-mean-slopes-with-teaching-experience-and-subjective-appraisals}
-
-Correlations among mean standardized HR/mean slopes (see Table 2),
-teaching experience (M = 5.64, SD = 9.46), disruption appraisal (M =
-5.19, SD = 2.87), and confidence appraisal (M = 7.81, SD = 1.97) are
-presented in Table 3. Correlations between mean standardized HR/mean
-slopes and the other variables were mostly very small and statistically
-non-significant, except for the pre-teaching interval (I1), in which
-mean slope and teaching experience correlated negatively (r=-.27), and
-the interview interval (I4) in which mean HR and teaching experience
-correlated positively (r=.24). Correlations between teaching experience
-and appraisals were substantial: more experienced teachers had lower
-disruption appraisals (r=-.36), and higher confidence appraisals
-(r=.44). Moreover, the two appraisal variables were negatively
-correlated (r=-.37).
-
-Concerning the effect of teaching experience on participants' HR levels
-(i.e., mean standardized HR) for each of the five intervals, teaching
-experience significantly predicted mean standardized HR only in the
-interview interval (Table 4, Interview interval, Model 1), indicating a
-higher mean standardized HR for teachers with more teaching experience.
-This relationship is, in fact, in the opposite direction as predicted by
-Hypothesis 2a.
-
-Neither adding disruption appraisal (\textbf{Hypothesis 2b}) nor adding
-confidence appraisal (\textbf{Hypothesis 2c}) while controlling for the
-shared variance with teaching experience revealed significant effects on
-teachers' mean standardized HR.
-
-When considering the effects of the three predictors in concert
-(\textbf{Hypothesis 2d}), mean standardized HR was significantly
-predicted only by disruption appraisal, and only in the post-teaching
-interval (Table 4, Post-teaching interval, Model 4), indicating a higher
-mean standardized HR for teachers who felt more disrupted by the
-classroom events, when controlling for the other variables.
-
-Concerning the explorative investigation of the effects of teaching
-experience and subjective appraisals on changes (i.e., mean slopes) in
-teachers' HR, teaching experience significantly predicted the mean slope
-in the pre-teaching interval (Table 4, Pre-teaching interval, Model 1),
-indicating a less steep HR increase in teachers with more teaching
-experience. For all other intervals, no variable revealed a significant
-prediction.
 

### 2024-09-10 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
Format_main

@@
 The analysis revealed a constant decrease in HR throughout the lecture, with HR peaks during more interactive learning phases.
-@chalmers2021 used HR data from a fitness tracker to identify physiological changes during stress-inducing tasks (i.e., the Trier Social Stress Test; @kirschbaum1993trier].
+@chalmers2021 used HR data from a fitness tracker to identify physiological changes during stress-inducing tasks (i.e., the Trier Social Stress Test; @kirschbaum1993trier).
 Average HR increased significantly from the resting to the stress inducing phases.
@@
 Coping mechanisms help to reduce the perceived threat.
-Kyriacou’s definition of teacher stress (see @kyriacou1978 and, for a more recent adaptation, @van2006stress) is based on the transactional stress model by Lazarus and colleagues [lazarus1966psychological; @lazarus1990theory], which highlights the interaction between an individual and the environment, whereby stress refers to a person’s subjective reaction to an event (a stressor) that exceeds the person’s adaptive resources.
+Kyriacou’s definition of teacher stress (see @kyriacou1978 and, for a more recent adaptation, @van2006stress) is based on the transactional stress model by Lazarus and colleagues [@lazarus1966psychological; @lazarus1990theory], which highlights the interaction between an individual and the environment, whereby stress refers to a person’s subjective reaction to an event (a stressor) that exceeds the person’s adaptive resources.
 
@@
 From this, the tracker calculated the heart beats per minute.
-HR measurements were generated at least every 15 seconds .
+HR measurements were generated at least every 15 seconds[^1].
 The raw data contained the estimated HR in BPM for each time stamp.
 To account for individual differences in the baseline HR, we also calculated z-standardized HR values based on individual means, i.e., at the subject level of $n$ = 81 participants (standardized HR).
+
+[^1]: The fluctuations in the number of seconds in which the HR was measured are due to the participants' movements, meaning that the device could not measure the HR every second.
 
@@
 We conducted all analyses with R [@RStudio2020]. Graphics were created using ggplot2 [@ggplot2].
-To enable visual inspection of HR trends, we displayed smoothed teacher HR over the course of the recording.
-We visually compared unstandardized and standardized HR trends over the two-hour recording period.
+
+To enable visual inspection of HR trends, we displayed smoothed teacher HR over the course of the recording[^2].
+We visually compared unstandardized and standardized HR trends over the two-hour recording period[^3].
 For all further analyses, we used standardized rather than unstandardized HR values.
 
-We averaged each person’s standardized HR over each of the five selected intervals , resulting in one measure per person per interval.
-To test Hypothesis 1a, we initially conducted a one-way ANOVA with repeated measures as an omnibus test and then tested the mean differences between the teaching interval (I2) and the other four intervals by planned contrasts and inspection of effect size d [@cohen1988new].
+[^2]: The curve was smoothed using the geom_smooth() function from the ggplot2 package in R [@ggplot2] based on the smoothing method LOESS (Locally Estimated Scatterplot Smoothing).
+This method fits a polynomial surface determined by one or more numerical predictors, using local fitting.
+
+[^3]: Note that the study exceeded the planned duration of two hours for a few participants.
+To avoid distortions when mapping the HR over the course of the study (see Fig.
+3), the endpoint was set at two hours for all participants, even though data from later time points was used in the *end interval* for a few participants.
+
+We averaged each person’s standardized HR over each of the five selected intervals[^4], resulting in one measure per person per interval.
+To test Hypothesis 1a, we initially conducted a one-way ANOVA with repeated measures as an omnibus test and then tested the mean differences between the *teaching interval* ($I_2$) and the other four intervals by planned contrasts and inspection of effect size $d$ [@cohen1988statistical].
+
+[^4]: We used the mean standardized HR instead of the mean intercept as we wanted to explain the mean HR of the entire intervals and not the HR at the very beginning of the interval ($x$ = 0).
+
 For testing Hypothesis 1b, concerning HR changes within each interval, we first conducted a linear estimation of the increase or decrease in standardized HR values over time for each participant.
-To this end, we used fixed intercept fixed slope regression models [@gelman2006data] for each interval to estimate intercepts and linear slopes for each individual, which were then averaged across individuals.
-We tested Hypothesis 1b based on the unstandardized estimates of mean slopes (one estimate per participant per interval).
+To this end, we used fixed intercept fixed slope regression models [@gelman2006data] for each interval to estimate intercepts and linear slopes for each individual, which were then averaged across individuals.[^5] We tested Hypothesis 1b based on the unstandardized estimates of mean slopes (one estimate per participant per interval).
+
+[^5]: Although this procedure does not account for nonmonotonic progressions in individual HR, a graphical evaluation revealed that the linear estimates corresponded well to the majority of the cases (see XX in the supplementary material).
+
 Addressing our second research goal, we ran linear regression analysis with teaching experience and subjective appraisals as predictors.
@@
 To test Hypothesis 2d, we examined the effects of all three predictors in one regression model.
-Furthermore, we repeated these steps to explore the effects of teaching experience and subjective appraisals on changes in teachers’ HR (i.e., mean slopes).
-Please note: HR levels and changes were not regressed on the disruption and confidence appraisals in the pre-teaching interval (I1), because the appraised classroom events had not yet taken place in that phase.
+Furthermore, we repeated these steps to explore the effects of teaching experience and subjective appraisals on *changes* in teachers’ HR (i.e., mean slopes).
+Please note: HR levels and changes were not regressed on the disruption and confidence appraisals in the *pre-teaching interval* ($I_1$), because the appraised classroom events had not yet taken place in that phase.
 
@@
 ```
+# Results
+
+## Mapping teachers’ HR over the course of the study phases
+
+Means, standard deviations, and range of teachers’ unstandardized and standardized HR for the entire study period, and for the five intervals, are shown in Table 1.
+Fig.
+3 a.
+and b.
+display the unstandardized and standardized HR trends, respectively, over the course of the entire study period.
+HR initially increased, peaked, and then decreased, with the unstandardized and standardized HR graphs showing high similarity.
+Thus, for all further analyses, we used participants’ standardized HR values.
 
 ```{=latex}
-
 \renewcommand{\arraystretch}{1.5}
@@
         \midrule
-        Overall Course of 2h & 90.09/0.04\tablefootnote{Please note that standardized M and SD of the overall course were not exactly 0 and 1 due to rounding differences} & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
+        Overall Course of 2h & 90.09/0.04\footnotemark[9] & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
         Pre-teaching interval ($I_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
@@
         Interview interval ($I_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
-        End interval $I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\tablefootnote{Deviations of the minimum values in the overall course vs. the end interval ($I_5$) are due to data of a few participants who
-        needed more than two hours to finish the study.}/-2.68 & 120/2.96 \\
+        End interval ($I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\footnotemark[10]/-2.68 & 120/2.96 \\
         \bottomrule
@@
     \label{tab_1}
+
 \end{table}
+ \footnotetext[9]{Please note that standardized M and SD of the overall course were not exactly 0 and 1 due to rounding differences.}
+ \footnotetext[10]{Deviations of the minimum values in the overall course vs. the end interval ($I_5$) are due to data of a few participants who needed more than two hours to finish the study.}
 
@@
                              t = 20,
-                             b = 20)
+                             b = 10)
         ) -> loess_hr
@@
                              t = 20,
-                             b = 20)
+                             b = 10)
         ) -> loess_hr_std
@@
        width = 20,
-       height = 15,
+       height = 12,
        units = "cm")
@@
 ```
+
+\newpage
+
+Figure 4 shows the distribution of teachers’ mean standardized HR for the five intervals.
+Repeated measures ANOVA revealed significant differences in mean standardized HR between intervals, $F(4, 400) = 260.62$, $p < .05$, $d = 1.60$ (large effect).
+Planned contrasts indicated that, as hypothesized (Hypothesis 1a), mean standardized HR was significantly higher in the *teaching interval* ($I_2$) than in all other intervals, specifically, the *pre-teaching interval* ($I_1$; $t(400) = -10.08$, $p < .05$, $d = 1.034$; large effect), the post-teaching interval ($I_3$; $t(400) = -6.94$, $p < .05$, $d = 1.37$; large effect), the interview interval ($I_4$; $t(400) = 15.00$, $p < .05$, $d = 3.29$; large effect), and the end interval ($I_5$); $t(400) = 22.54$, $p < .05$, $d = 4.64$; large effect).
 
@@
 
+Next, we examined HR changes (i.e., mean slopes) within each interval to test the hypothesis that HR increased during the *pre-teaching phase* and decreased during all other phases (Hypothesis 1b).
+The mean intercepts and mean slopes, complemented by their standard deviations for each interval, are shown in Table 2.
+The mean slope of the *pre-teaching interval* ($I_1$) was significantly positive, indicating an increase in HR, as hypothesized.
+Further, the mean slopes of the *teaching interval* ($I_2$), *post-teaching interval* ($I_3$), and *interview interval* ($I_4$) were significantly negative, indicating a decrease in HR.
+For the last interval, the *end interval* ($I_5$), the mean slope was negative, but did not differ significantly from zero.
+
 ```{=latex}
@@
     \centering
-    \begin{tabularx}{\textwidth}{lXXXXX}
+    \begin{tabularx}{\textwidth}{lXXXXXX}
         \toprule
-        Interval & n\tablefootnote{All measurement points per interval for all participants.
-Note that the variation in $n$ stems from the variation in the number of collected data points by the fitness tracker.} & \multicolumn{2}{c}{\textit{M (SD)}} & \multicolumn{2}{c}{$p$} \\
-        & & Intercept & Slope & Intercept & Slope \\
+        Interval  & \multicolumn{2}{c}{M (SD)} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
         \midrule
-        (1) Pre-teaching interval & 6896 & 0.052  & 0.085*  & .57 & $<$ .05 \\
-        & & (0.820) & (0.133) & & \\
-        (2) Teaching interval & 7150 & 1.025* & -0.039* & $<$ .05 & $<$ .05 \\
-        & & (0.690) & (0.108) & & \\
-        (3) Post-teaching interval & 6664 & 0.549* & -0.060* & $<$ .05 & $<$ .05 \\
-        & & (0.547) & (0.101) & & \\
-        (4) Interview interval & 6287 & -0.617* & -0.022 & $<$ .05 & .006 \\
-        & & (0.614) & (0.070) & & \\
-        (5) End interval & 5990 & -1.004* & -0.012 & $<$ .05 & .14 \\
-        & & (0.500) & (0.074) & & \\
-        \bottomrule \\
-        Note. * $p < .05$
+        (1) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
+        (2) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
+        (3) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
+        (4) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
+        (5) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
+        \bottomrule
     \end{tabularx}
-    \caption{Descriptive statistics (n, M, SD) for the mean intercepts and the mean slopes for the five intervals.}
+    \caption{Analysis (\textit{M, SD, p-values}) for the mean intercepts and the mean slopes for the five intervals }
     \label{tab_2}
@@
 ```
+
+## Predicting mean standardized HR and mean slopes
+
+Table 3 shows the raw correlations among mean standardized HR/mean slopes (see Table 2 for means and standard deviations), teaching experience ($M = 5.64$, $SD = 9.46$), disruption appraisal ($M = 5.19$, $SD = 2.87$), and confidence appraisal ($M = 7.81$, $SD = 1.97$).
+With a few notable exceptions, correlations with HR measures were mostly very small and statistically non-significant (Table 3).
+Correlations between teaching experience and appraisals (not shown in Table 3) were substantial: more experienced teachers gave lower disruption appraisals ($r = -.36$), and higher confidence appraisals ($r = .44$).
+Moreover, the two appraisal variables were negatively correlated ($r = -.37$).
 
@@
 ```
+
+Table 4 shows the results of the regression analyses.
+Teaching experience significantly predicted mean standardized HR only in the *interview interval* (Table 4, Interview interval, Model 1), indicating a higher mean standardized HR for teachers with more teaching experience.
+This relationship is, in fact, in the opposite direction as predicted by Hypothesis 2a.
+Neither adding disruption appraisal (**Hypothesis 2b**) nor adding confidence appraisal (**Hypothesis 2c**) increased the amount of explained variance to a statistically significant extent.
+
+When considering the effects of the three predictors in concert (**Hypothesis 2d**), mean standardized HR was significantly predicted only by disruption appraisal, and only in the *post-teaching interval* (Table 4, Post-teaching interval, Model 4), indicating a higher mean standardized HR for teachers who felt more disrupted by the classroom events, when controlling for the other variables.
+
+Concerning the explorative investigation of the effects of teaching experience and subjective appraisals on *changes* (i.e., mean slopes) in teachers’ HR, teaching experience significantly predicted the mean slope in the *pre-teaching interval* (Table 4, Pre-teaching interval, Model 1), indicating a less steep HR increase in teachers with more teaching experience.
+For all other intervals, no variable had significant predictive value.
 
@@
 ```
+
+# Discussion
+
+## Key findings
+
+Overall, our findings indicate that wrist-worn fitness trackers are a useful tool for tracking teachers’ HR and identifying stressful periods during teaching.
+Using HR data from a commercially available and relatively low-cost Fitbit® fitness tracker, we were able to map teachers’ HR before, during, and after a stressful micro-teaching unit, with HR increasing in preparation for teaching, peaking during the teaching phase, and decreasing afterward.
+
+These findings are in line with prior studies showing that teachers’ HR varies depending on their activities and encountered stressors with increases during phases where teachers are in an exposed position [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021], as well as with findings showing how HR changes align with activating events and stress-inducing tasks [@Darnell2019; @chalmers2021].
+
+Building on the model of teacher stress [@kyriacou1978, see Fig.
+2], we had hypothesized that more experienced teachers, with better classroom management skills at their disposal, experience less physiological stress when dealing with classroom disruptions.
+Contrary to our expectations, we found no buffering effect of teaching experience on teachers’ HR, i.e., more experienced teachers did not show lower mean standardized HR during the stressful teaching phase than less experienced teachers.
+Rather, at least descriptively, we observed the opposite trend.
+There are several possible explanations for this finding.
+First, teaching experience is inherently confounded with age (the two variables correlated at $r = .94$ in our sample), and age has been shown to affect indicators of cardiovascular reactivity in various ways [@uchino2010older].
+However, to avoid this kind of confounding influence, we had used not raw BPM but rather standardized mean HR for all our analyses, thus controlling at least for inter-individual differences in mean HR.
+Second, as research on teacher professionalization has repeatedly shown, professional experience is not a guarantee for higher professional knowledge and skills [@kirschner2016professionswissen].
+Rather, honing skills from professional experience necessitates a deliberate practice of choosing to improve, learning through experience, and integrating new knowledge into future performances [@dunn1999deliberate].
+Thus, rather than professional experience alone, more direct assessments of classroom management skills, such as objective behavior-based tests, would be a better indicator of expertise that future studies could explore.
+Finally, and most importantly, the highly controlled teaching situation that we created in the lab might not have provided sufficient resemblance to the expert teachers’ working conditions to let them effectively use their coping resources.
+In other words, since the situation was unfamiliar to both experienced and unexperienced teachers, their stress levels might have been more similar than they would have been in a more authentic classroom setting.
+
+While we did not find a buffering effect of teaching experience on mean HR during teaching, we did, however, find a less steep HR increase in more experienced, compared to less experienced teachers during the pre-teaching phase ($\beta = -.27$), i.e., in preparation for the micro-teaching unit.
+This finding supports the idea that, even though teaching experience guarantees neither superior expertise nor stress resistance, the habits and routines formed by experienced teachers may at least lead to lower arousal levels (e.g., experienced as feeling less nervous and tense) when they anticipate potentially stressful teaching situations.
+
+An interesting observation beyond our hypotheses was that teaching experience was predictive of HR differences, not during teaching, but in the interview phase: compared to less experienced teachers, more experienced teachers showed a higher mean standardized HR ($\beta = .24$) and, thus, probably experienced higher levels of physiological stress during the SRI.
+One possible explanation for this finding could again be the higher age of the more experienced teachers, along with slower recovery from stress in older teachers.
+For instance, @ritvanen2006responses observed that, compared to their younger colleagues, older teachers did not experience a decrease in their HR during periods of low stress levels, from which they concluded that recovery from stress was insufficient in the older teachers [@ritvanen2006responses].
+Alternatively, the finding could also be attributed to the fact that less experienced teachers, due to their ongoing or only recently concluded training, may have been more accustomed to reflecting on their work and receiving feedback as was the case during the SRI, whereas, these activities were less routine and possibly more face-threatening for experienced teachers.
+Therefore, it is possible that more experienced teachers found the interview itself to be more stressful and therefore showed a higher mean standardized HR during this phase.
+
+With regards to the predictive power of teachers’ subjective appraisals of the classroom disruption during teaching, we, first of all, have to conclude that our hypotheses were not supported, as neither confidence appraisal nor disruptiveness appraisal showed any notable correlations with teachers’ means standardized HR or any explanatory power over and beyond teaching experience.
+Possibly, teachers’ self-reported appraisals, and their actual physiological stress responses, tap into quite different phenomena, or at least, quite different aspects of the multifaceted stress response [@kyriacou1978].
+In addition, while HR was assessed online during teaching, self-reported appraisals were given in retrospect during the SRI, and may be subject to biased (e.g., self-serving) reporting or simply an inability to recall one´s immediate stress reactions.
+
+On the other hand, when controlling for all other factors, teachers who reported to have perceived the events as more disruptive showed a higher HR ($\beta = .25$) in the phase immediately following the micro-teaching unit.
+This finding would be consistent with the idea that differences in mean HR, as an indicator of the physiological stress response, can be linked to the cognitive appraisal of stressors.
+
+## Limitations and future directions
+
+While the laboratory setting of the study allowed for a controlled implementation of stressors and high internal validity, it was not an authentic classroom environment, raising questions about its external validity.
+Most importantly, the teacher and their students did not have a shared history, and only a very thin basis for establishing a positive teacher-student relationship, which is a core characteristic of effective classroom management [@ruedi2014; @beaty2010].
+In addition, the micro-teaching unit was only about 15 minutes long, and thus much shorter than a regular school lesson, providing less opportunities for experienced teachers to build up an engaging lesson.
+Finally, student behavior was scripted, with classroom disruptions following the experimental schedule, irrelevant of the behavior of the teacher.
+Thus, the setting may have masked effects of teaching experience by providing too little opportunities of experienced teachers to demonstrate their true classroom management skills, in particular regarding the prevention of disruptions.
+In subsequent studies, it would therefore be insightful to assess teachers’ HR in more authentic classroom settings over a longer period of time (e.g., days, weeks, or even months).
+Extended observation of teachers’ HR in authentic classroom settings could reveal how factors such as student behavior, teaching methods, or organizational and administrative demands contribute to fluctuations in physiological arousal, uncovering insights into the sustained physiological demands of teaching that short-term studies may overlook.
+Finally, linking actual teacher behavior to potential stressors (e.g., classroom disruptions, noise level, etc.) would offer insights into teacher coping strategies and their links with physiological indicators of stress.
+
+Another limitation concerns the assessment of teachers’ HR.
+While our results demonstrate the usefulness of drawing upon easily available HR data from ubiquitous, low-cost, un-intrusive fitness trackers to estimate teacher stress, there also are shortcomings of this type of assessment.
+First, while fitness trackers typically yield HR data, heart rate variability (HRV) has been demonstrated to be an even more accurate indicator of stress [@wettstein2020ambulatory].
+While standard fitness trackers did not provide this measure at the time of our data collection, more recent products do offer this function.
+Thus, future studies might consider assessing HRV instead of HR.
+Second, we did not record participants’ resting HR, which is generally considered an important baseline for determining inter- and intrapersonal differences in cardiovascular health and reactivity [@nanchen2018; @heneghan2019].
+A clean baseline HR requires a resting phase without physical movement or emotional stress, ideally fifteen minutes before the beginning of the activity, which is very difficult to achieve in practice [@sammito2015guideline], e.g., when assessing teacher HR before and during teaching.
+Thus, our study explored the possibility of substituting baseline HR measurement via z-standardization within participants.
+As a result, the absolute standardized values of each participant must always be interpreted in the context of the standardization sample, and thus are less interpretable than individual BPM values together with a baseline HR.
+However, for statistical analyses based on the whole sample, the standardization fulfills the aim of controlling for differences in individual HR due to, for example, age-related differences.
+Finally, depending on the brand and model of fitness trackers used, the precision of the HR measurement varies.
+Research on the reliability of our deployed Fitbit® device has proven that this brand is generally accurate in controlled settings and for moderate activity levels [@wallen2016accuracy; @hajj2023; @fuller2020; @jo2016], as in our study.
+For example, the Fitbit® fitness tracker has previously shown good HR measurement accuracy during resting phases [@jo2016; @muggeridge2021measurement] and for activities such as walking, jogging, and running [@hajj2023].
+At higher exercise intensities such as cycling, the Fitbit® tracker may underestimate HR [@thomson2019heart; @montoye2017comparative; @jo2016; @jachymek2021] but is still within an acceptable range according to systematic reviews [@chevance2022accuracy].
+Nevertheless, @gagnon2022 stressed that Fitbit® trackers cannot replace ECG when precision is paramount.
+Despite these considerations, the Fitbit® model appears suitable for our study purposes, as physical strain was moderate.
+
+Furthermore, while we assessed teachers’ appraisals of the stressful classroom disruptions using a SRI in which they could review the exact situation, these appraisal ratings were still post-hoc self-reports, which limits the interpretation of our results.
+One of the main issues with post-hoc self-reports is that they rely on the teachers’ memories and subjective interpretations of past events, which may be prone to various biases such as social desirability [@razavi2001self] or recall errors [@van2016accuracy].
+Moreover, stress is not a fixed or stable construct; it is a dynamic, constantly evolving affective response that can vary depending on context, individual disposition, and prior experiences, making it particularly challenging to pinpoint valid and reliable process markers for how individuals appraise stress in real-time [@lazarus1990theory].
+While SRIs provide a more detailed and reflective understanding of the stressor in question, the delayed nature of the response makes it difficult to capture the immediate, in-the-moment appraisal that occurs when the stressful event actually takes place.
+
+## Hands-on advice for using wrist-worn fitness trackers for research
+
+For researchers aiming to use fitness trackers to collect data, there are practical aspects to consider concerning the design, data collection, and data analysis phases of research projects [for an additional overview, see @nelson2020guidelines]:
+
+1)	Choosing a suitable model:
+
+Before data collection, researchers need to decide which model of fitness tracker best suits their research question.
+One important point to consider is whether the study will be conducted in the laboratory, in a clinical environment, or under real-world conditions.
+Conventional fitness trackers should not be used if the focus is on measurement accuracy, such as in medical contexts, as they cannot replace the accuracy of ECG measurements [@gagnon2022].
+Moreover, researchers should consider that measurement accuracy also depends on the intensity of the movements performed by the participants during data collection.
+Fitbit® fitness trackers, for example, underestimate HR at higher exercise intensities such as cycling [@thomson2019heart; @montoye2017comparative; @jo2016; @jachymek2021].
+For reference, the systematic review by @fuller2020 provides a detailed overview of studies that used wrist-worn fitness trackers between 2000 and 2019 and discusses their validity and reliability.
+Another point to consider is the price, which at the time of writing ranged between €30 for the cheapest models and up to €1.700 for medical wristbands.
+Currently, models assessing HRV in addition to HR are becoming more and more affordable and widespread.
+Still, Fitbit® fitness trackers might be a good choice for teams operating with moderate budgets or if larger groups of participants need to be tracked at the same time.
+Further, before conducting any study, it should be considered that the data collected with fitness trackers is health data, and therefore very sensitive.
+Researchers have to ensure that their chosen model of fitness tracker allows them to collect and store data in line with relevant ethical and legal requirements, for example, guaranteeing participants’ anonymity and secure data storage.
+
+2)	Operating the fitness tracker:
+
+In planning the operation of their chosen model of fitness tracker, researchers need to specify the circumference and attachment of the wrist band and the placement of the fitness tracker on participants.
+In particular, researchers conducting studies with children should take into account their smaller wrist size.
+When putting on a fitness tracker, attention must also be paid to whether it is attached to the dominant or non-dominant wrist, as this can influence HR measurements.
+Different models of fitness trackers need to be placed differently and in line with the manufacturer’s instructions.
+It is also important to check that the battery is fully charged each time, that the latest software version is loaded, and that the fitness tracker has been synchronized before recording data to avoid unnecessary loss of data.
+Finally, if researchers want to accurately investigate parameters during specific time intervals, such as HR during lessons versus breaks, it is crucial to synchronize the fitness tracker with other time-keeping devices, such as watches.
+This synchronization allows researchers to precisely determine the onset and offset of particular activities or intervals of interest.
+By aligning the recorded data with specific time frames, researchers can ensure that the physiological measurements, such as HR, are accurately associated with the corresponding periods of interest.
+This process enhances the validity and reliability of the data analysis, enabling a more precise examination of variations in physiological responses across different time intervals.
+
+3)	Extracting and analyzing fitness tracker data:
+
+As far as the procedure for processing the data is concerned, researchers should ensure that the raw data of the physiological measurements are available for further analysis.
+For the Fitbit® HR measurements, for example, the raw data can be downloaded from a website in the form of .csv files.
+However, these must be downloaded as soon as possible after data collection, as some platforms automatically delete or archive older data files after a certain period due to policies regarding data storage and retention.
+This can result in loss of access to critical data.
+Additionally, ensuring that data is collected at the intended sampling rate is crucial for accurate analysis.
+For instance, while our fitness tracker was designed to record HR every 1-5 seconds, we occasionally observed recordings only every 15 seconds, possibly due to participant movement and tracker placement.
+
+## Conclusion
+
+This study investigated whether HR data collected from teacher-worn fitness trackers are suitable for exploring links between HR, subjective stressor appraisal, and individual teaching experience, to achieve a more profound comprehension of teacher stress.
+Results suggest that the widespread availability of HR data from wearable fitness trackers, moving “from heartbeat to data”, presents opportunities both to teachers for self-monitoring stress levels, and to researchers for assessing physiological indicators of stress.
+For example, using fitness trackers could enable teachers to strengthen their self-awareness in stressful situations and allow for early self-intervention such as mindfulness techniques (e.g., deep breathing or body scans) [agyapong2023interventions].
+Integrating fitness trackers into teacher training and everyday practice could offer an affordable and practical method for assessing and managing teacher stress.
+In teacher training as well as in research, triangulating data from fitness trackers, lesson videos, and interviews could provide teachers with insights into their own stress management, and foster the implementation of effective stress and classroom management strategies.
+Taken together, our findings cater to @wettstein2021 call for the use of ambulatory assessment methods, particularly in the context of classroom disruptions, for gaining a deeper understanding of teacher stress and its impact on both psychological and physiological variables.
+
+In summary, our study contributes to the understanding of stress in educational settings and underscores the potential of wearable fitness trackers in advancing research on teacher well-being.
+By harnessing the power of wearable technology, we can provide teachers with the tools needed to better understand and manage their stress, ultimately enhancing their overall well-being.

### 2024-09-10 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
Format_main

@@
 physiological changes during stress-inducing tasks (i.e., the Trier
-Social Stress Test; \citet{kirschbaum1993trier}{]}. Average HR increased
+Social Stress Test; \citet{kirschbaum1993trier}). Average HR increased
 significantly from the resting to the stress inducing phases. Even
@@
 adaptation, \citet{van2006stress}) is based on the transactional stress
-model by Lazarus and colleagues {[}lazarus1966psychological;
-\citet{lazarus1990theory}{]}, which highlights the interaction between
-an individual and the environment, whereby stress refers to a person's
-subjective reaction to an event (a stressor) that exceeds the person's
-adaptive resources.
+model by Lazarus and colleagues
+\citep{lazarus1966psychological, lazarus1990theory}, which highlights
+the interaction between an individual and the environment, whereby
+stress refers to a person's subjective reaction to an event (a stressor)
+that exceeds the person's adaptive resources.
 
@@
 capillaries. From this, the tracker calculated the heart beats per
-minute. HR measurements were generated at least every 15 seconds . The
-raw data contained the estimated HR in BPM for each time stamp. To
-account for individual differences in the baseline HR, we also
-calculated z-standardized HR values based on individual means, i.e., at
-the subject level of \(n\) = 81 participants (standardized HR).
+minute. HR measurements were generated at least every 15
+seconds\footnote{The fluctuations in the number of seconds in which the
+  HR was measured are due to the participants' movements, meaning that
+  the device could not measure the HR every second.}. The raw data
+contained the estimated HR in BPM for each time stamp. To account for
+individual differences in the baseline HR, we also calculated
+z-standardized HR values based on individual means, i.e., at the subject
+level of \(n\) = 81 participants (standardized HR).
 
@@
 
+\subsubsection{Teaching Experience}\label{teaching-experience}
+
+Participants' teaching experience was assessed as a part of their
+sociodemographic data. Participants stated their work experience in
+years.
+
+\subsubsection{Subjective appraisal of the classroom events and coping
+processes}\label{subjective-appraisal-of-the-classroom-events-and-coping-processes}
+
+The subjective disruption and confidence appraisals were assessed during
+the SRI on an 11-point rating scale, ranging from 0 (not at all
+disrupting/confident) to 10 (extremely disrupting/confident). Ratings
+were averaged across the nine classroom events for each participant, as
+we were interested in the general stressfulness of the \emph{teaching
+phase} for each participant.
+
+\subsection{Data analysis}\label{data-analysis}
+
+We conducted all analyses with R \citep{RStudio2020}. Graphics were
+created using ggplot2 \citep{ggplot2}.
+
+To enable visual inspection of HR trends, we displayed smoothed teacher
+HR over the course of the recording\footnote{The curve was smoothed
+  using the geom\_smooth() function from the ggplot2 package in R
+  \citep{ggplot2} based on the smoothing method LOESS (Locally Estimated
+  Scatterplot Smoothing). This method fits a polynomial surface
+  determined by one or more numerical predictors, using local fitting.}.
+We visually compared unstandardized and standardized HR trends over the
+two-hour recording period\footnote{Note that the study exceeded the
+  planned duration of two hours for a few participants. To avoid
+  distortions when mapping the HR over the course of the study (see Fig.
+  3), the endpoint was set at two hours for all participants, even
+  though data from later time points was used in the \emph{end interval}
+  for a few participants.}. For all further analyses, we used
+standardized rather than unstandardized HR values.
+
+We averaged each person's standardized HR over each of the five selected
+intervals\footnote{We used the mean standardized HR instead of the mean
+  intercept as we wanted to explain the mean HR of the entire intervals
+  and not the HR at the very beginning of the interval (\(x\) = 0).},
+resulting in one measure per person per interval. To test Hypothesis 1a,
+we initially conducted a one-way ANOVA with repeated measures as an
+omnibus test and then tested the mean differences between the
+\emph{teaching interval} (\(I_2\)) and the other four intervals by
+planned contrasts and inspection of effect size \(d\)
+\citep{cohen1988statistical}.
+
+For testing Hypothesis 1b, concerning HR changes within each interval,
+we first conducted a linear estimation of the increase or decrease in
+standardized HR values over time for each participant. To this end, we
+used fixed intercept fixed slope regression models
+\citep{gelman2006data} for each interval to estimate intercepts and
+linear slopes for each individual, which were then averaged across
+individuals.\footnote{Although this procedure does not account for
+  nonmonotonic progressions in individual HR, a graphical evaluation
+  revealed that the linear estimates corresponded well to the majority
+  of the cases (see XX in the supplementary material).} We tested
+Hypothesis 1b based on the unstandardized estimates of mean slopes (one
+estimate per participant per interval).
+
+Addressing our second research goal, we ran linear regression analysis
+with teaching experience and subjective appraisals as predictors. To
+test Hypothesis 2a, we examined the effect of teaching experience on
+participants' HR levels (i.e., mean standardized HR) for each of the
+five intervals, using linear regression models with teaching experience
+as the sole predictor. To test Hypotheses 2b and 2c, we separately
+augmented the model by either teachers' disruption appraisal (Hypothesis
+2b) or confidence appraisal (Hypothesis 2c) as predictors, while
+controlling for teaching experience. To test Hypothesis 2d, we examined
+the effects of all three predictors in one regression model.
+Furthermore, we repeated these steps to explore the effects of teaching
+experience and subjective appraisals on \emph{changes} in teachers' HR
+(i.e., mean slopes). Please note: HR levels and changes were not
+regressed on the disruption and confidence appraisals in the
+\emph{pre-teaching interval} (\(I_1\)), because the appraised classroom
+events had not yet taken place in that phase.
+
+\section{Results}\label{results}
+
+\subsection{Mapping teachers' HR over the course of the study
+phases}\label{mapping-teachers-hr-over-the-course-of-the-study-phases}
+
+Means, standard deviations, and range of teachers' unstandardized and
+standardized HR for the entire study period, and for the five intervals,
+are shown in Table 1. Fig. 3 a. and b. display the unstandardized and
+standardized HR trends, respectively, over the course of the entire
+study period. HR initially increased, peaked, and then decreased, with
+the unstandardized and standardized HR graphs showing high similarity.
+Thus, for all further analyses, we used participants' standardized HR
+values.
+
 \renewcommand{\arraystretch}{1.5}
@@
 
+\newpage
+
+Figure 4 shows the distribution of teachers' mean standardized HR for
+the five intervals. Repeated measures ANOVA revealed significant
+differences in mean standardized HR between intervals,
+\(F(4, 400) = 260.62\), \(p < .05\), \(d = 1.60\) (large effect).
+Planned contrasts indicated that, as hypothesized (Hypothesis 1a), mean
+standardized HR was significantly higher in the \emph{teaching interval}
+(\(I_2\)) than in all other intervals, specifically, the
+\emph{pre-teaching interval} (\(I_1\); \(t(400) = -10.08\), \(p < .05\),
+\(d = 1.034\); large effect), the post-teaching interval (\(I_3\);
+\(t(400) = -6.94\), \(p < .05\), \(d = 1.37\); large effect), the
+interview interval (\(I_4\); \(t(400) = 15.00\), \(p < .05\),
+\(d = 3.29\); large effect), and the end interval (\(I_5\));
+\(t(400) = 22.54\), \(p < .05\), \(d = 4.64\); large effect).
+
 \begin{figure}[H]
@@
 
+Next, we examined HR changes (i.e., mean slopes) within each interval to
+test the hypothesis that HR increased during the \emph{pre-teaching
+phase} and decreased during all other phases (Hypothesis 1b). The mean
+intercepts and mean slopes, complemented by their standard deviations
+for each interval, are shown in Table 2. The mean slope of the
+\emph{pre-teaching interval} (\(I_1\)) was significantly positive,
+indicating an increase in HR, as hypothesized. Further, the mean slopes
+of the \emph{teaching interval} (\(I_2\)), \emph{post-teaching interval}
+(\(I_3\)), and \emph{interview interval} (\(I_4\)) were significantly
+negative, indicating a decrease in HR. For the last interval, the
+\emph{end interval} (\(I_5\)), the mean slope was negative, but did not
+differ significantly from zero.
+
 \renewcommand{\arraystretch}{1.5}
@@
     \centering
-    \begin{tabularx}{\textwidth}{lXXXXX}
+    \begin{tabularx}{\textwidth}{lXXXXXX}
         \toprule
-        Interval & n\tablefootnote{All measurement points per interval for all participants.
-Note that the variation in $n$ stems from the variation in the number of collected data points by the fitness tracker.} & \multicolumn{2}{c}{\textit{M (SD)}} & \multicolumn{2}{c}{$p$} \\
-        & & Intercept & Slope & Intercept & Slope \\
+        Interval  & \multicolumn{2}{c}{M (SD)} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
         \midrule
-        (1) Pre-teaching interval & 6896 & 0.052  & 0.085*  & .57 & $<$ .05 \\
-        & & (0.820) & (0.133) & & \\
-        (2) Teaching interval & 7150 & 1.025* & -0.039* & $<$ .05 & $<$ .05 \\
-        & & (0.690) & (0.108) & & \\
-        (3) Post-teaching interval & 6664 & 0.549* & -0.060* & $<$ .05 & $<$ .05 \\
-        & & (0.547) & (0.101) & & \\
-        (4) Interview interval & 6287 & -0.617* & -0.022 & $<$ .05 & .006 \\
-        & & (0.614) & (0.070) & & \\
-        (5) End interval & 5990 & -1.004* & -0.012 & $<$ .05 & .14 \\
-        & & (0.500) & (0.074) & & \\
-        \bottomrule \\
-        Note. * $p < .05$
+        (1) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
+        (2) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
+        (3) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
+        (4) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
+        (5) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
+        \bottomrule
     \end{tabularx}
-    \caption{Descriptive statistics (n, M, SD) for the mean intercepts and the mean slopes for the five intervals.}
+    \caption{Analysis (\textit{M, SD, p-values}) for the mean intercepts and the mean slopes for the five intervals }
     \label{tab_2}
 \end{table}
+
+\subsection{Predicting mean standardized HR and mean
+slopes}\label{predicting-mean-standardized-hr-and-mean-slopes}
+
+Table 3 shows the raw correlations among mean standardized HR/mean
+slopes (see Table 2 for means and standard deviations), teaching
+experience (\(M = 5.64\), \(SD = 9.46\)), disruption appraisal
+(\(M = 5.19\), \(SD = 2.87\)), and confidence appraisal (\(M = 7.81\),
+\(SD = 1.97\)). With a few notable exceptions, correlations with HR
+measures were mostly very small and statistically non-significant (Table
+3). Correlations between teaching experience and appraisals (not shown
+in Table 3) were substantial: more experienced teachers gave lower
+disruption appraisals (\(r = -.36\)), and higher confidence appraisals
+(\(r = .44\)). Moreover, the two appraisal variables were negatively
+correlated (\(r = -.37\)).
+
+Table 4 shows the results of the regression analyses. Teaching
+experience significantly predicted mean standardized HR only in the
+\emph{interview interval} (Table 4, Interview interval, Model 1),
+indicating a higher mean standardized HR for teachers with more teaching
+experience. This relationship is, in fact, in the opposite direction as
+predicted by Hypothesis 2a. Neither adding disruption appraisal
+(\textbf{Hypothesis 2b}) nor adding confidence appraisal
+(\textbf{Hypothesis 2c}) increased the amount of explained variance to a
+statistically significant extent.
+
+When considering the effects of the three predictors in concert
+(\textbf{Hypothesis 2d}), mean standardized HR was significantly
+predicted only by disruption appraisal, and only in the
+\emph{post-teaching interval} (Table 4, Post-teaching interval, Model
+4), indicating a higher mean standardized HR for teachers who felt more
+disrupted by the classroom events, when controlling for the other
+variables.
+
+Concerning the explorative investigation of the effects of teaching
+experience and subjective appraisals on \emph{changes} (i.e., mean
+slopes) in teachers' HR, teaching experience significantly predicted the
+mean slope in the \emph{pre-teaching interval} (Table 4, Pre-teaching
+interval, Model 1), indicating a less steep HR increase in teachers with
+more teaching experience. For all other intervals, no variable had
+significant predictive value.
 
@@
 
+\section{Discussion}\label{discussion}
+
+\subsection{Key findings}\label{key-findings}
+
+Overall, our findings indicate that wrist-worn fitness trackers are a
+useful tool for tracking teachers' HR and identifying stressful periods
+during teaching. Using HR data from a commercially available and
+relatively low-cost Fitbit® fitness tracker, we were able to map
+teachers' HR before, during, and after a stressful micro-teaching unit,
+with HR increasing in preparation for teaching, peaking during the
+teaching phase, and decreasing afterward.
+
+These findings are in line with prior studies showing that teachers' HR
+varies depending on their activities and encountered stressors with
+increases during phases where teachers are in an exposed position
+\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021},
+as well as with findings showing how HR changes align with activating
+events and stress-inducing tasks \citep{Darnell2019, chalmers2021}.
+
+Building on the model of teacher stress \citep[see Fig.
+2]{kyriacou1978}, we had hypothesized that more experienced teachers,
+with better classroom management skills at their disposal, experience
+less physiological stress when dealing with classroom disruptions.
+Contrary to our expectations, we found no buffering effect of teaching
+experience on teachers' HR, i.e., more experienced teachers did not show
+lower mean standardized HR during the stressful teaching phase than less
+experienced teachers. Rather, at least descriptively, we observed the
+opposite trend. There are several possible explanations for this
+finding. First, teaching experience is inherently confounded with age
+(the two variables correlated at \(r = .94\) in our sample), and age has
+been shown to affect indicators of cardiovascular reactivity in various
+ways \citep{uchino2010older}. However, to avoid this kind of confounding
+influence, we had used not raw BPM but rather standardized mean HR for
+all our analyses, thus controlling at least for inter-individual
+differences in mean HR. Second, as research on teacher
+professionalization has repeatedly shown, professional experience is not
+a guarantee for higher professional knowledge and skills
+\citep{kirschner2016professionswissen}. Rather, honing skills from
+professional experience necessitates a deliberate practice of choosing
+to improve, learning through experience, and integrating new knowledge
+into future performances \citep{dunn1999deliberate}. Thus, rather than
+professional experience alone, more direct assessments of classroom
+management skills, such as objective behavior-based tests, would be a
+better indicator of expertise that future studies could explore.
+Finally, and most importantly, the highly controlled teaching situation
+that we created in the lab might not have provided sufficient
+resemblance to the expert teachers' working conditions to let them
+effectively use their coping resources. In other words, since the
+situation was unfamiliar to both experienced and unexperienced teachers,
+their stress levels might have been more similar than they would have
+been in a more authentic classroom setting.
+
+While we did not find a buffering effect of teaching experience on mean
+HR during teaching, we did, however, find a less steep HR increase in
+more experienced, compared to less experienced teachers during the
+pre-teaching phase (\(\beta = -.27\)), i.e., in preparation for the
+micro-teaching unit. This finding supports the idea that, even though
+teaching experience guarantees neither superior expertise nor stress
+resistance, the habits and routines formed by experienced teachers may
+at least lead to lower arousal levels (e.g., experienced as feeling less
+nervous and tense) when they anticipate potentially stressful teaching
+situations.
+
+An interesting observation beyond our hypotheses was that teaching
+experience was predictive of HR differences, not during teaching, but in
+the interview phase: compared to less experienced teachers, more
+experienced teachers showed a higher mean standardized HR
+(\(\beta = .24\)) and, thus, probably experienced higher levels of
+physiological stress during the SRI. One possible explanation for this
+finding could again be the higher age of the more experienced teachers,
+along with slower recovery from stress in older teachers. For instance,
+\citet{ritvanen2006responses} observed that, compared to their younger
+colleagues, older teachers did not experience a decrease in their HR
+during periods of low stress levels, from which they concluded that
+recovery from stress was insufficient in the older teachers
+\citep{ritvanen2006responses}. Alternatively, the finding could also be
+attributed to the fact that less experienced teachers, due to their
+ongoing or only recently concluded training, may have been more
+accustomed to reflecting on their work and receiving feedback as was the
+case during the SRI, whereas, these activities were less routine and
+possibly more face-threatening for experienced teachers. Therefore, it
+is possible that more experienced teachers found the interview itself to
+be more stressful and therefore showed a higher mean standardized HR
+during this phase.
+
+With regards to the predictive power of teachers' subjective appraisals
+of the classroom disruption during teaching, we, first of all, have to
+conclude that our hypotheses were not supported, as neither confidence
+appraisal nor disruptiveness appraisal showed any notable correlations
+with teachers' means standardized HR or any explanatory power over and
+beyond teaching experience. Possibly, teachers' self-reported
+appraisals, and their actual physiological stress responses, tap into
+quite different phenomena, or at least, quite different aspects of the
+multifaceted stress response \citep{kyriacou1978}. In addition, while HR
+was assessed online during teaching, self-reported appraisals were given
+in retrospect during the SRI, and may be subject to biased (e.g.,
+self-serving) reporting or simply an inability to recall one´s immediate
+stress reactions.
+
+On the other hand, when controlling for all other factors, teachers who
+reported to have perceived the events as more disruptive showed a higher
+HR (\(\beta = .25\)) in the phase immediately following the
+micro-teaching unit. This finding would be consistent with the idea that
+differences in mean HR, as an indicator of the physiological stress
+response, can be linked to the cognitive appraisal of stressors.
+
+\subsection{Limitations and future
+directions}\label{limitations-and-future-directions}
+
+While the laboratory setting of the study allowed for a controlled
+implementation of stressors and high internal validity, it was not an
+authentic classroom environment, raising questions about its external
+validity. Most importantly, the teacher and their students did not have
+a shared history, and only a very thin basis for establishing a positive
+teacher-student relationship, which is a core characteristic of
+effective classroom management \citep{ruedi2014, beaty2010}. In
+addition, the micro-teaching unit was only about 15 minutes long, and
+thus much shorter than a regular school lesson, providing less
+opportunities for experienced teachers to build up an engaging lesson.
+Finally, student behavior was scripted, with classroom disruptions
+following the experimental schedule, irrelevant of the behavior of the
+teacher. Thus, the setting may have masked effects of teaching
+experience by providing too little opportunities of experienced teachers
+to demonstrate their true classroom management skills, in particular
+regarding the prevention of disruptions. In subsequent studies, it would
+therefore be insightful to assess teachers' HR in more authentic
+classroom settings over a longer period of time (e.g., days, weeks, or
+even months). Extended observation of teachers' HR in authentic
+classroom settings could reveal how factors such as student behavior,
+teaching methods, or organizational and administrative demands
+contribute to fluctuations in physiological arousal, uncovering insights
+into the sustained physiological demands of teaching that short-term
+studies may overlook. Finally, linking actual teacher behavior to
+potential stressors (e.g., classroom disruptions, noise level, etc.)
+would offer insights into teacher coping strategies and their links with
+physiological indicators of stress.
+
+Another limitation concerns the assessment of teachers' HR. While our
+results demonstrate the usefulness of drawing upon easily available HR
+data from ubiquitous, low-cost, un-intrusive fitness trackers to
+estimate teacher stress, there also are shortcomings of this type of
+assessment. First, while fitness trackers typically yield HR data, heart
+rate variability (HRV) has been demonstrated to be an even more accurate
+indicator of stress \citep{wettstein2020ambulatory}. While standard
+fitness trackers did not provide this measure at the time of our data
+collection, more recent products do offer this function. Thus, future
+studies might consider assessing HRV instead of HR. Second, we did not
+record participants' resting HR, which is generally considered an
+important baseline for determining inter- and intrapersonal differences
+in cardiovascular health and reactivity
+\citep{nanchen2018, heneghan2019}. A clean baseline HR requires a
+resting phase without physical movement or emotional stress, ideally
+fifteen minutes before the beginning of the activity, which is very
+difficult to achieve in practice \citep{sammito2015guideline}, e.g.,
+when assessing teacher HR before and during teaching. Thus, our study
+explored the possibility of substituting baseline HR measurement via
+z-standardization within participants. As a result, the absolute
+standardized values of each participant must always be interpreted in
+the context of the standardization sample, and thus are less
+interpretable than individual BPM values together with a baseline HR.
+However, for statistical analyses based on the whole sample, the
+standardization fulfills the aim of controlling for differences in
+individual HR due to, for example, age-related differences. Finally,
+depending on the brand and model of fitness trackers used, the precision
+of the HR measurement varies. Research on the reliability of our
+deployed Fitbit® device has proven that this brand is generally accurate
+in controlled settings and for moderate activity levels
+\citep{wallen2016accuracy, hajj2023, fuller2020, jo2016}, as in our
+study. For example, the Fitbit® fitness tracker has previously shown
+good HR measurement accuracy during resting phases
+\citep{jo2016, muggeridge2021measurement} and for activities such as
+walking, jogging, and running \citep{hajj2023}. At higher exercise
+intensities such as cycling, the Fitbit® tracker may underestimate HR
+\citep{thomson2019heart, montoye2017comparative, jo2016, jachymek2021}
+but is still within an acceptable range according to systematic reviews
+\citep{chevance2022accuracy}. Nevertheless, \citet{gagnon2022} stressed
+that Fitbit® trackers cannot replace ECG when precision is paramount.
+Despite these considerations, the Fitbit® model appears suitable for our
+study purposes, as physical strain was moderate.
+
+Furthermore, while we assessed teachers' appraisals of the stressful
+classroom disruptions using a SRI in which they could review the exact
+situation, these appraisal ratings were still post-hoc self-reports,
+which limits the interpretation of our results. One of the main issues
+with post-hoc self-reports is that they rely on the teachers' memories
+and subjective interpretations of past events, which may be prone to
+various biases such as social desirability \citep{razavi2001self} or
+recall errors \citep{van2016accuracy}. Moreover, stress is not a fixed
+or stable construct; it is a dynamic, constantly evolving affective
+response that can vary depending on context, individual disposition, and
+prior experiences, making it particularly challenging to pinpoint valid
+and reliable process markers for how individuals appraise stress in
+real-time \citep{lazarus1990theory}. While SRIs provide a more detailed
+and reflective understanding of the stressor in question, the delayed
+nature of the response makes it difficult to capture the immediate,
+in-the-moment appraisal that occurs when the stressful event actually
+takes place.
+
+\subsection{Hands-on advice for using wrist-worn fitness trackers for
+research}\label{hands-on-advice-for-using-wrist-worn-fitness-trackers-for-research}
+
+For researchers aiming to use fitness trackers to collect data, there
+are practical aspects to consider concerning the design, data
+collection, and data analysis phases of research projects \citep[for an
+additional overview, see][]{nelson2020guidelines}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  Choosing a suitable model:
+\end{enumerate}
+
+Before data collection, researchers need to decide which model of
+fitness tracker best suits their research question. One important point
+to consider is whether the study will be conducted in the laboratory, in
+a clinical environment, or under real-world conditions. Conventional
+fitness trackers should not be used if the focus is on measurement
+accuracy, such as in medical contexts, as they cannot replace the
+accuracy of ECG measurements \citep{gagnon2022}. Moreover, researchers
+should consider that measurement accuracy also depends on the intensity
+of the movements performed by the participants during data collection.
+Fitbit® fitness trackers, for example, underestimate HR at higher
+exercise intensities such as cycling
+\citep{thomson2019heart, montoye2017comparative, jo2016, jachymek2021}.
+For reference, the systematic review by \citet{fuller2020} provides a
+detailed overview of studies that used wrist-worn fitness trackers
+between 2000 and 2019 and discusses their validity and reliability.
+Another point to consider is the price, which at the time of writing
+ranged between €30 for the cheapest models and up to €1.700 for medical
+wristbands. Currently, models assessing HRV in addition to HR are
+becoming more and more affordable and widespread. Still, Fitbit® fitness
+trackers might be a good choice for teams operating with moderate
+budgets or if larger groups of participants need to be tracked at the
+same time. Further, before conducting any study, it should be considered
+that the data collected with fitness trackers is health data, and
+therefore very sensitive. Researchers have to ensure that their chosen
+model of fitness tracker allows them to collect and store data in line
+with relevant ethical and legal requirements, for example, guaranteeing
+participants' anonymity and secure data storage.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Operating the fitness tracker:
+\end{enumerate}
+
+In planning the operation of their chosen model of fitness tracker,
+researchers need to specify the circumference and attachment of the
+wrist band and the placement of the fitness tracker on participants. In
+particular, researchers conducting studies with children should take
+into account their smaller wrist size. When putting on a fitness
+tracker, attention must also be paid to whether it is attached to the
+dominant or non-dominant wrist, as this can influence HR measurements.
+Different models of fitness trackers need to be placed differently and
+in line with the manufacturer's instructions. It is also important to
+check that the battery is fully charged each time, that the latest
+software version is loaded, and that the fitness tracker has been
+synchronized before recording data to avoid unnecessary loss of data.
+Finally, if researchers want to accurately investigate parameters during
+specific time intervals, such as HR during lessons versus breaks, it is
+crucial to synchronize the fitness tracker with other time-keeping
+devices, such as watches. This synchronization allows researchers to
+precisely determine the onset and offset of particular activities or
+intervals of interest. By aligning the recorded data with specific time
+frames, researchers can ensure that the physiological measurements, such
+as HR, are accurately associated with the corresponding periods of
+interest. This process enhances the validity and reliability of the data
+analysis, enabling a more precise examination of variations in
+physiological responses across different time intervals.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Extracting and analyzing fitness tracker data:
+\end{enumerate}
+
+As far as the procedure for processing the data is concerned,
+researchers should ensure that the raw data of the physiological
+measurements are available for further analysis. For the Fitbit® HR
+measurements, for example, the raw data can be downloaded from a website
+in the form of .csv files. However, these must be downloaded as soon as
+possible after data collection, as some platforms automatically delete
+or archive older data files after a certain period due to policies
+regarding data storage and retention. This can result in loss of access
+to critical data. Additionally, ensuring that data is collected at the
+intended sampling rate is crucial for accurate analysis. For instance,
+while our fitness tracker was designed to record HR every 1-5 seconds,
+we occasionally observed recordings only every 15 seconds, possibly due
+to participant movement and tracker placement.
+
+\subsection{Conclusion}\label{conclusion}
+
+This study investigated whether HR data collected from teacher-worn
+fitness trackers are suitable for exploring links between HR, subjective
+stressor appraisal, and individual teaching experience, to achieve a
+more profound comprehension of teacher stress. Results suggest that the
+widespread availability of HR data from wearable fitness trackers,
+moving ``from heartbeat to data'', presents opportunities both to
+teachers for self-monitoring stress levels, and to researchers for
+assessing physiological indicators of stress. For example, using fitness
+trackers could enable teachers to strengthen their self-awareness in
+stressful situations and allow for early self-intervention such as
+mindfulness techniques (e.g., deep breathing or body scans)
+{[}agyapong2023interventions{]}. Integrating fitness trackers into
+teacher training and everyday practice could offer an affordable and
+practical method for assessing and managing teacher stress. In teacher
+training as well as in research, triangulating data from fitness
+trackers, lesson videos, and interviews could provide teachers with
+insights into their own stress management, and foster the implementation
+of effective stress and classroom management strategies. Taken together,
+our findings cater to \citet{wettstein2021} call for the use of
+ambulatory assessment methods, particularly in the context of classroom
+disruptions, for gaining a deeper understanding of teacher stress and
+its impact on both psychological and physiological variables.
+
+In summary, our study contributes to the understanding of stress in
+educational settings and underscores the potential of wearable fitness
+trackers in advancing research on teacher well-being. By harnessing the
+power of wearable technology, we can provide teachers with the tools
+needed to better understand and manage their stress, ultimately
+enhancing their overall well-being.
+
 \bibliography{r-references.bib}

### 2024-09-10 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
format_fertig

@@
 date: "`r Sys.Date()`"
-classoption: preprint, 3p, authoryear
+classoption: preprint, 3p, sort,
 bibliography: r-references.bib
-csl: computers-and-education.csl
 linenumbers: false
@@
     keep_tex: true
+    citation_package: natbib
 header-includes:
@@
   - \usepackage{longtable}
+  - \usepackage{geometry}
 ---
@@
 Results suggest that the widespread availability of HR data from wearable fitness trackers, moving “from heartbeat to data”, presents opportunities both to teachers for self-monitoring stress levels, and to researchers for assessing physiological indicators of stress.
-For example, using fitness trackers could enable teachers to strengthen their self-awareness in stressful situations and allow for early self-intervention such as mindfulness techniques (e.g., deep breathing or body scans) [agyapong2023interventions].
+For example, using fitness trackers could enable teachers to strengthen their self-awareness in stressful situations and allow for early self-intervention such as mindfulness techniques (e.g., deep breathing or body scans) [@agyapong2023interventions].
 Integrating fitness trackers into teacher training and everyday practice could offer an affordable and practical method for assessing and managing teacher stress.

### 2024-09-10 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x paper

--- 2024-09-02 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
@@
       psych,
-      apaTables)
+      apaTables,
+      rstatix )
 
@@
     Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
-    Number_fixation_msec_mtu = round(Sum_number_fixation / Duration_of_interval, digits = 6),
     Number_fixation_sec_mtu = round(Sum_number_fixation / Duration_of_interval_sec, digits = 2),
@@
 
-# N, M, SD, min & max number of fixation per minute (micro-teaching unit)
+######## Statistical Methods for Outlier Detection
+
+# Boxplot showing outliers
+ggplot(df_aoi_sum, aes(x = "", y = Number_fixation_min_mtu)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of mumber of fixations per minute (micro-teaching unit)",
+       y = "Number of fixations per minute") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_sum$Number_fixation_min_mtu, 0.25)
+Q3 <- quantile(df_aoi_sum$Number_fixation_min_mtu, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_mtu <- df_aoi_sum %>%
+  filter(Number_fixation_min_mtu >= LowerBound & Number_fixation_min_mtu <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_sum)  # Original data
+nrow(df_no_outliers_mtu)  # After removing outliers
+
+######## N, M, SD, min & max number of fixation per minute (micro-teaching unit)
 nof.table <-
@@
              caption = "N, M, SD, min & max number of fixation per minute (micro-teaching unit)")
+
+######## Plotting
 
@@
 
-# N, M, SD, min & max number of fixations per minute (AOI students)
+######## Statistical Methods for Outlier Detection
+
+# Boxplot showing outliers
+ggplot(df_aoi_stud, aes(x = "", y = Stud_number_fixation_min)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of number of fixations per minute (AOI students)",
+       y = "Number of fixations per minute") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_stud$Stud_number_fixation_min, 0.25)
+Q3 <- quantile(df_aoi_stud$Stud_number_fixation_min, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_stud <- df_aoi_stud %>%
+  filter(Stud_number_fixation_min >= LowerBound & Stud_number_fixation_min <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_stud)  # Original data
+nrow(df_no_outliers_stud)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_stud <- df_aoi_stud %>%
+  filter(Stud_number_fixation_min < LowerBound | Stud_number_fixation_min > UpperBound)
+
+# View the removed outliers
+df_outliers_stud
+
+##### N, M, SD, min & max number of fixations per minute (AOI students)
 nof.min.stud.table <-
-  df_aoi_stud %>%
+  df_no_outliers_stud %>%
   group_by(Group) %>%
@@
              caption = "N, M, SD, min & max number of fixations per minute (AOI students)")
+
+##### PLOTTING
 
@@
   ) +
-  ylim(0, 50) +
+  ylim(0, 80) +
   labs(x = "", y = "Number of fixations per minute") +
@@
 t.test(
-  x = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Expert"],
-  y = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Novice"],
+  x = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Expert"],
+  y = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Novice"],
   var.equal = TRUE
@@
 d_number_stud <- CohenD(
-  x = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Expert"],
-  y = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Novice"],
+  x = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Expert"],
+  y = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Novice"],
   na.rm = TRUE
@@
 
-# N, M, SD, min & max number of fixation on AOI "disruptive person"
+######## Statistical Methods for Outlier Detection
+
+# Boxplot showing outliers
+ggplot(df_aoi_disrup, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of number of fixations per minute (AOI disruptive person)",
+       y = "Number of fixations per minute") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_disrup$Number_of_fixations.Disruptive_Person, 0.25)
+Q3 <- quantile(df_aoi_disrup$Number_of_fixations.Disruptive_Person, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_disrup <- df_aoi_disrup %>%
+  filter(Number_of_fixations.Disruptive_Person >= LowerBound & Number_of_fixations.Disruptive_Person <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_disrup)  # Original data
+nrow(df_no_outliers_disrup)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_disrup <- df_aoi_disrup %>%
+  filter(Number_of_fixations.Disruptive_Person < LowerBound | Number_of_fixations.Disruptive_Person > UpperBound)
+
+# View the removed outliers
+df_outliers_disrup
+
+######## N, M, SD, min & max number of fixation on AOI "disruptive person"
 nof.disrup.table <-
-  df_aoi_disrup %>%
+  df_no_outliers_disrup %>%
   group_by(Group) %>%
@@
 
+######## PLOTTING
+
 # plotting average duration on AOI Disruptive person
-df_aoi_disrup %>%
+df_no_outliers_disrup %>%
   ggplot(mapping = aes(x = Group, y = Number_of_fixations.Disruptive_Person)) +
@@
   ) +
-  ylim(0, 150) +
+  ylim(0, 100) +
   labs(x = "", y = "Number of fixations") +
@@
 # t-test for expertise differences
-t.test(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
-       y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"],
+t.test(x = df_no_outliers_disrup$Number_of_fixations.Disruptive_Person[df_no_outliers_disrup$Group == "Expert"],
+       y = df_no_outliers_disrup$Number_of_fixations.Disruptive_Person[df_no_outliers_disrup$Group == "Novice"],
        var.equal = TRUE)
@@
 # effect size for expertise differences
-d_number_disrup <- CohenD(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
-                        y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"],
+d_number_disrup <- CohenD(x = df_no_outliers_disrup$Number_of_fixations.Disruptive_Person[df_no_outliers_disrup$Group == "Expert"],
+                        y = df_no_outliers_disrup$Number_of_fixations.Disruptive_Person[df_no_outliers_disrup$Group == "Novice"],
                         na.rm = TRUE)
@@
 
-# N, M, SD, min & max average duration of fixations (micro-teaching unit)
+######## Statistical Methods for Outlier Detection
+
+# Boxplot showing outliers
+ggplot(df_aoi_sum, aes(x = "", y = Average_duration_mtu)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of Average duration of fixations per minute",
+       y = "Average duration of fixations per minute") +
+  theme_minimal()
+
+######## N, M, SD, min & max average duration of fixations (micro-teaching unit)
 dur.table <- 
@@
              caption = "N, M, SD, min & max duration of fixations in milliseconds (micro-teaching unit)")
+
+######## PLOTTING
 
@@
 
-# N, M, SD, min & max average duration of fixations on AOI students
+######## Statistical Methods for Outlier Detection
+
+# Boxplot showing outliers
+ggplot(df_aoi_stud, aes(x = "", y = Average_duration_stud)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of average duration of fixations (AOI students)",
+       y = "Average duration of fixations") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_stud$Average_duration_stud, 0.25)
+Q3 <- quantile(df_aoi_stud$Average_duration_stud, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_stud_dur <- df_aoi_stud %>%
+  filter(Average_duration_stud >= LowerBound & Average_duration_stud <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_stud)  # Original data
+nrow(df_no_outliers_stud_dur)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_stud_dur <- df_aoi_stud %>%
+  filter(Average_duration_stud < LowerBound | Average_duration_stud > UpperBound)
+
+# View the removed outliers
+df_outliers_stud_dur
+
+######## N, M, SD, min & max average duration of fixations on AOI students
 dur.stud.table <-
-  df_aoi_stud %>%
+  df_no_outliers_stud_dur %>%
   group_by(Group) %>%
@@
 
+######## PLOTTING
+
 # plotting average duration on AOI Students
-df_aoi_stud %>%
+df_no_outliers_stud_dur %>%
   ggplot(mapping = aes(x = Group, y = Average_duration_stud)) +
@@
   ) +
-  ylim(0, 1200) + 
+  ylim(0, 1000) + 
   labs(x ="",
@@
 t.test(
-  x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
-  y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+  x = df_no_outliers_stud_dur$Average_duration_stud[df_no_outliers_stud_dur$Group == "Expert"],
+  y = df_no_outliers_stud_dur$Average_duration_stud[df_no_outliers_stud_dur$Group == "Novice"],
   var.equal = TRUE
@@
 d_aver_stud <- CohenD(
-  x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
-  y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+  x = df_no_outliers_stud_dur$Average_duration_stud[df_no_outliers_stud_dur$Group == "Expert"],
+  y = df_no_outliers_stud_dur$Average_duration_stud[df_no_outliers_stud_dur$Group == "Novice"],
   na.rm = TRUE
@@
 
-# N, M, SD, min & max average duration of fixations in milliseconds (AOI disruptive person)"
+######## Statistical Methods for Outlier Detection
+
+# Boxplot showing outliers
+ggplot(df_aoi_disrup, aes(x = "", y = Average_duration_disrup)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of average duration of fixations (AOI disruptive person)",
+       y = "Average duration of fixations") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_disrup$Average_duration_disrup, 0.25)
+Q3 <- quantile(df_aoi_disrup$Average_duration_disrup, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_disrup_dur <- df_aoi_disrup %>%
+  filter(Average_duration_disrup >= LowerBound & Average_duration_disrup <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_disrup)  # Original data
+nrow(df_no_outliers_disrup_dur)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_disrup_dur <- df_aoi_disrup %>%
+  filter(Average_duration_disrup < LowerBound | Average_duration_disrup > UpperBound)
+
+# View the removed outliers
+df_outliers_disrup_dur
+
+######## N, M, SD, min & max average duration of fixations in milliseconds (AOI disruptive person)"
 dur.disrup.table <-
-  df_aoi_disrup %>%
+  df_no_outliers_disrup_dur %>%
   group_by(Group) %>%
@@
 
+######## PLOTTING
+
 # plotting average duration on AOI Disruptive person
-df_aoi_disrup %>% 
+df_no_outliers_disrup_dur %>% 
   ggplot(mapping = aes(x = Group,
@@
                                         height = 0.1)) +
-  ylim(0, 1500) +
+  ylim(0, 1000) +
   labs(x ="",
@@
 # t-test for expertise differences
-t.test(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
-       y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"],
+t.test(x = df_no_outliers_disrup_dur$Average_duration_disrup[df_no_outliers_disrup_dur$Group == "Expert"],
+       y = df_no_outliers_disrup_dur$Average_duration_disrup[df_no_outliers_disrup_dur$Group == "Novice"],
        var.equal = TRUE)
@@
 # effect size for expertise differences
-d_dur_disrup <- CohenD(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
-                        y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"],
+d_dur_disrup <- CohenD(x = df_no_outliers_disrup_dur$Average_duration_disrup[df_no_outliers_disrup_dur$Group == "Expert"],
+                        y = df_no_outliers_disrup_dur$Average_duration_disrup[df_no_outliers_disrup_dur$Group == "Novice"],
                         na.rm = TRUE)
@@
 
-# N, M, SD, min & max number of fixation (micro-teaching unit)
+######## Statistical Methods for Outlier Detection
+
+# Boxplot showing outliers
+ggplot(df_gri, aes(x = "", y = GRI)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of the Gaze Relational Index",
+       y = "Mean duration of fixations/\nmean number of fixations") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_gri$GRI, 0.25)
+Q3 <- quantile(df_gri$GRI, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_gri <- df_gri %>%
+  filter(GRI >= LowerBound & GRI <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_gri)  # Original data
+nrow(df_no_outliers_gri)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_gri <- df_gri %>%
+  filter(GRI < LowerBound | GRI > UpperBound)
+
+# View the removed outliers
+df_outliers_gri
+
+######## N, M, SD, min & max number of fixation (micro-teaching unit)
 gri.table <-
-  df_gri %>%
+  df_no_outliers_gri %>%
   group_by(Group) %>%
@@
 
+######## PLOTTING
+
 # plotting number of fixations on ALL AOIS
-df_gri %>%
+df_no_outliers_gri %>%
   ggplot(mapping = aes(x = Group, y = GRI)) +
@@
 # t-test for expertise differences
-t.test(x = df_gri$GRI[df_gri$Group == "Expert"],
-       y = df_gri$GRI[df_gri$Group == "Novice"],
+t.test(x = df_no_outliers_gri$GRI[df_no_outliers_gri$Group == "Expert"],
+       y = df_no_outliers_gri$GRI[df_no_outliers_gri$Group == "Novice"],
        var.equal = TRUE)
@@
 # effect size for expertise differences
-d_gri_all <- CohenD(x = df_gri$GRI[df_gri$Group == "Expert"],
-                        y = df_gri$GRI[df_gri$Group == "Novice"],
+d_gri_all <- CohenD(x = df_no_outliers_gri$GRI[df_no_outliers_gri$Group == "Expert"],
+                        y = df_no_outliers_gri$GRI[df_no_outliers_gri$Group == "Novice"],
                         na.rm = TRUE)
@@
   group_by(Participant) %>% 
-  filter(!Time_to_first_fixation.Disruptive_Person == 0,
+  filter(!Time_to_first_fixation.Disruptive_Person == 0, # exclude all participants with 0 msec
          !Time_to_first_fixation.Disruptive_Person > 30000) %>% # cut-off 30sec
@@
   mutate(Group = ifelse(Participant < 200, "Novice", "Expert"),
+         Sum_disruptions = sum(N),
          Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000, 
@@
 
-# M, SD, min, max time to first fixation "Disruptive Person"
+######## Statistical Methods for Outlier Detection
+
+# Boxplot showing outliers
+ggplot(df_ttff_disrup, aes(x = "", y = Disrup_time_fixation_sec)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of time to first fixation in seconds (AOI disruptive person)",
+       y = "Time to first fixation in seconds") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_ttff_disrup$Disrup_time_fixation_sec, 0.25)
+Q3 <- quantile(df_ttff_disrup$Disrup_time_fixation_sec, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_ttff <- df_ttff_disrup %>%
+  filter(Disrup_time_fixation_sec >= LowerBound & Disrup_time_fixation_sec <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_ttff_disrup)  # Original data
+nrow(df_no_outliers_ttff)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_ttff <- df_ttff_disrup %>%
+  filter(Disrup_time_fixation_sec < LowerBound | Disrup_time_fixation_sec > UpperBound)
+
+# View the removed outliers
+df_outliers_ttff
+
+############### M, SD, min, max time to first fixation "Disruptive Person"
 ttff.disrup.table <-
-  df_ttff_disrup %>%
+  df_no_outliers_ttff %>%
   group_by(Group) %>%
@@
 
+############### PLOTTING
+
 ##################### plotting time to first fixation for groups ##################### 
 plot_time_disrup <- 
-  ggplot(data = df_ttff_disrup,
+  ggplot(data = df_no_outliers_ttff,
          mapping = aes(x = Group,
@@
                                         height = 0.1)) +
-  ylim(0,14) +
+  ylim(0,12) +
   labs(x ="",
@@
 plot_time_disrup
+
 ```
@@
 # t-test for expertise differences
-t.test(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
-       y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
+t.test(x = df_no_outliers_ttff$Disrup_time_fixation_sec[df_no_outliers_ttff$Group == "Expert"],
+       y = df_no_outliers_ttff$Disrup_time_fixation_sec[df_no_outliers_ttff$Group == "Novice"],
        var.equal = TRUE)
@@
 # effect size for expertise differences
-d_time_disrup <- CohenD(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
-                    y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
+d_time_disrup <- CohenD(x = df_no_outliers_ttff$Disrup_time_fixation_sec[df_no_outliers_ttff$Group == "Expert"],
+                    y = df_no_outliers_ttff$Disrup_time_fixation_sec[df_no_outliers_ttff$Group == "Novice"],
                     na.rm = TRUE)
@@
   dplyr::select(.,
-                -"Participant")
+                -"Participant",
+                -"Teaching Experience")
 
@@
   df_merge %>% 
+  cor(method = "pearson") %>% 
+  round(., digits = 2)
+
+# p-value for GRI x STJ_All
+cor.test(df_merge$GRI_mtu, df_merge$SJT_All)
+
+# teaching experience only with experts
+df_merge_teaching_experience <-
+  df_list %>% reduce(full_join, by='Participant') %>%
+  filter(Participant > 200) %>% 
+  dplyr::select(.,
+                -"Participant")
+
+# create a correlation matrix
+cor_tab_teaching_experience <- 
+  df_merge_teaching_experience %>% 
   cor(method = "pearson") %>% 

### 2024-09-10 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex

@@
 \documentclass[preprint, 3p,
-authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
+sort,]{elsarticle} %review=doublespace preprint=single 5p=2 column
 %%% Begin My package additions %%%%%%%%%%%%%%%%%%%
@@
 \usepackage{longtable}
+\usepackage{geometry}
 
@@
 mindfulness techniques (e.g., deep breathing or body scans)
-{[}agyapong2023interventions{]}. Integrating fitness trackers into
+\citep{agyapong2023interventions}. Integrating fitness trackers into
 teacher training and everyday practice could offer an affordable and

### 2024-09-11 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x

@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of mumber of fixations per minute (micro-teaching unit)",
+  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
        y = "Number of fixations per minute") +

### 2024-09-12 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x paper

@@
   drop_na() %>% 
+  filter(!Participant %in% c(216)) %>% 
   dplyr::select(Participant,
@@
                 SJT_KF_gek) %>% # All
-  filter(!UI06_05 %in% c(201, 223)) %>%  # exclude ID with no eye tracking data
+  filter(!UI06_05 %in% c(201, 223, 216)) %>%  # exclude ID with no eye tracking data
   transmute(
@@
     SJT_All = round(SJT_KF_gek, 2)
-  )
+    ) %>% 
+    arrange(Participant)
 
@@
   df_list %>% reduce(full_join, by='Participant') %>%
-  # filter(Participant > 200) %>% 
+  arrange(Participant) %>% 
+  # filter(!Participant %in% c(216)) %>% 
   dplyr::select(.,
@@
 # p-value for GRI x STJ_All
-cor.test(df_merge$GRI_mtu, df_merge$SJT_All)
+cor.test(df_aoi_numb_dur$GRI_mtu, df_sjt$SJT_All)
+cor.test(df_merge$GRI_mtu, df_merge$SJT_Monitoring)
 

### 2024-09-14 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x

@@
 
+############### M, SD, min, max of the perceived "Disruptive Person"
+number.perceived.disrup.table <-
+  df_no_outliers_ttff %>%
+  group_by(Group, N) %>%
+  summarise(
+    N = n(),
+    "M in sec" = round(mean(N), digits = 2),
+    "SD in sec" = round(sd(N), digits = 2),
+    "Min in sec" = round(min(N), digits = 2),
+    "Max in sec" = round(max(N), digits = 2)
+  )
+
+knitr::kable(number.perceived.disrup.table,
+             caption = "N, M, SD, min & max time to first fixation in seconds (AOI disruptive person)")
+
 ############### PLOTTING

### 2024-09-16 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
Literatur Sachen

@@
 date: "`r Sys.Date()`"
-classoption: preprint, 3p, sort,
+classoption: preprint, 3p, sort
 bibliography: r-references.bib

### 2024-09-16 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
stuff

@@
 date: "`r Sys.Date()`"
-classoption: preprint, 3p, sort
+classoption: preprint, 3p, authoryear
 bibliography: r-references.bib
@@
            sd_heart)
-
-## count for individuals
-
-main_single_hr |> 
-  filter(time >= 7200) |> 
-  distinct(ID, .keep_all = TRUE) -> filter_overall
-
-N_prewrangling <- as.numeric(nrow(df_demo))
-
-N_postwrangling <- as.numeric(length(unique(main_single_hr$ID)))
-
 ```
@@
         \toprule
-        Interval & \textit{M HR} & \textit{SD HR} & Min & Max \\
+        Interval & \textit{M} HR & \textit{SD} HR & Min & Max \\
         \midrule
@@
     \end{tabularx}
-    \caption{Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
+    \caption{Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
     \label{tab_1}
@@
 \end{table}
- \footnotetext[9]{Please note that standardized M and SD of the overall course were not exactly 0 and 1 due to rounding differences.}
+ \footnotetext[9]{Please note that standardized \textit{M} and \textit{SD} of the overall course were not exactly 0 and 1 due to rounding differences.}
  \footnotetext[10]{Deviations of the minimum values in the overall course vs. the end interval ($I_5$) are due to data of a few participants who needed more than two hours to finish the study.}

### 2024-09-16 02_paper/02_study/01_fitbit paper/analysis_270423.Rmd
fb

@@
 
-list(`Preparation Phase` = list(name = "Pre-Teaching ", mod = mods$preparation, data = graph_data$preparation),
-     `Teaching Phase` = list(name = "Teaching Phase", mod = mods$teaching, data = graph_data$teaching),
-     `Post Teaching Phase` = list(name = "Post Teaching Phase",mod = mods$post, data = graph_data$post),
-     `Interview Phase` = list(name = "Interview Phase",mod = mods$interview, data = graph_data$interview),
-     `End Phase` = list(name = "End Phase",mod = mods$end, data = graph_data$end)
+list(`Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
+     `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
+     `Post Teaching Phase` = list(name = "Post-Teaching Interval",mod = mods$post, data = graph_data$post),
+     `Interview Phase` = list(name = "Interview Interval",mod = mods$interview, data = graph_data$interview),
+     `End Phase` = list(name = "End Interval",mod = mods$end, data = graph_data$end)
      ) %>% 

### 2024-09-16 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
Literatur Sachen

@@
 \documentclass[preprint, 3p,
-sort,]{elsarticle} %review=doublespace preprint=single 5p=2 column
+authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
 %%% Begin My package additions %%%%%%%%%%%%%%%%%%%

### 2024-09-16 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
whatever

--- 2024-09-12 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
@@
 
-############### PLOTTING
+############### M, SD, min, max of the perceived "Disruptive Person" ############### 
+number.perceived.disrup.table <-
+  df_no_outliers_ttff %>%
+  group_by(Group) %>%
+  summarise(
+    Mean = round(mean(N, na.rm = TRUE), digits = 2),
+    SD = round(sd(N, na.rm = TRUE), digits = 2), 
+    Min = min(N, na.rm = TRUE),
+    Max = max(N, na.rm = TRUE)
+  )
+
+knitr::kable(number.perceived.disrup.table,
+             caption = "N, M, SD, min & max of the perceived ´disruptive person´")
+
+############### PLOTTING ###############
+
+##################### plotting "perceived disruptive person" for groups ##################### 
+plot_n_disrup <- 
+  ggplot(data = df_no_outliers_ttff,
+         mapping = aes(x = Group,
+                       y = N)) +
+ geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  ylim(0,10) +
+  labs(x ="",
+       y = "Counts") + 
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("Counts of the perceived ´disruptive person´\n") +
+  theme_cowplot() +
+  theme(legend.position="none")
+
+plot_n_disrup
 
@@
 
+#### t-test & effect size "Counts of the perceived ´disruptive person´")
+```{r ttff_n_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# TIME TO FIRST FIXATIONS on disruptive person 
+# t-test for expertise differences
+t.test(x = df_no_outliers_ttff$N[df_no_outliers_ttff$Group == "Expert"],
+       y = df_no_outliers_ttff$N[df_no_outliers_ttff$Group == "Novice"],
+       var.equal = TRUE)
+
+# TIME TO FIRST FIXATIONS on disruptive person 
+# effect size for expertise differences
+d_n_disrup <- CohenD(x = df_no_outliers_ttff$N[df_no_outliers_ttff$Group == "Expert"],
+                    y = df_no_outliers_ttff$N[df_no_outliers_ttff$Group == "Novice"],
+                    na.rm = TRUE)
+
+round(d_n_disrup, 2)
+
+```
+
 #### t-test & effect size "Time to first fixation" (AOI disruptive person)
@@
 
-### 2.2 Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
+### 2.2 Rating Scales (Disruption Appraisal, Confidence Appraisal)
 ```{r rating_scales, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
+############## N, M, SD, min & max for disruption appraisal ############## 
 sri.disrup.table <-
@@
              caption = "Disruption appraisal with event")
+
+############## PLOTTING ##############
 
@@
 
+### Perform Exploratory Factor Analysis (EFA)
+```{r sri_efa, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# Select the relevant columns (e.g., Disruption Appraisal and Confidence Appraisal)
+sri <-
+  excel_sheets("data/Coding_SRI.xlsx") %>%
+  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+  filter(
+    !ID %in% c(201),
+    !disruption_appraisal == -100,
+    !confidence_appraisal == -100,
+    !disruption_appraisal == -99,
+    !confidence_appraisal == -99,
+    !disruption_appraisal == -88,
+    !confidence_appraisal == -88,
+    !prevalence_rating == -100,
+    !prevalence_rating == -99,
+    !prevalence_rating == -88
+    )
+
+sri <- sri %>% 
+  group_by(ID) %>% 
+  summarise(mean_disrup = mean(disruption_appraisal),
+            mean_confi = mean(confidence_appraisal)
+  ) %>% 
+  dplyr::select(mean_disrup,
+                mean_confi)
+
+# Perform exploratory factor analysis (EFA) with 2 factors
+sri_efa_result <- fa(sri, 
+                     nfactors = 2, 
+                     rotate = "varimax"
+                     )
+
+# Display the result
+print(sri_efa_result)
+
+sri_efa_result$communality
+print(sri_efa_result$loadings, cutoff = 0.4)
+
+# Cronbach's Alpha
+alpha((sri), check.keys =TRUE)
+
+```
+
+### Prevalence Rating as manipulation check
 ```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-############## Prevalence Rating #########################
+############## Prevalence Rating as manipulation check #########################
 
@@
 
-#### t-Test & effect size "Prevalence rating"
 ```{r sri_pr_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-#################### T-TEST & EFFECT SIZE ############
-
-# Prevalence Rating 
-# t-test for expertise differences
-t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
-       y = sri$prevalence_rating[sri$ID == "Novice"],
-       var.equal = TRUE)
-
-# Prevalence Rating 
-# effect size for expertise differences
-d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
-                      y = sri$prevalence_rating[sri$ID == "Novice"],
-                      na.rm = TRUE)
-
-round(d_sri_preva, 2)
+# #################### T-TEST & EFFECT SIZE ############
+# 
+# # Prevalence Rating 
+# # t-test for expertise differences
+# t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
+#        y = sri$prevalence_rating[sri$ID == "Novice"],
+#        var.equal = TRUE)
+# 
+# # Prevalence Rating 
+# # effect size for expertise differences
+# d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
+#                       y = sri$prevalence_rating[sri$ID == "Novice"],
+#                       na.rm = TRUE)
+# 
+# round(d_sri_preva, 2)
 

### 2024-09-17 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
appendix angefangen
appendix formatierung & plots

@@
 
+\begin{verbatim}
+## Warning: Using `size` aesthetic for lines was deprecated in ggplot2 3.4.0.
+## i Please use `linewidth` instead.
+## This warning is displayed once every 8 hours.
+## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
+## generated.
+\end{verbatim}
+
+\newpage
+\appendix
+\section*{Appendix}
+
+\setcounter{figure}{0}  % Reset figure numbering
+
+\renewcommand{\thefigure}{A\arabic{figure}}  % Figures labeled A1, A2, etc.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
+  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
+  \label{micro-teaching}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
+  \caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
+  \label{laboratory}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
+  \caption{bla..}
+  \label{preparation}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
+  \caption{bla..}
+  \label{preparation}
+\end{figure}
+
 \bibliography{r-references.bib}

### 2024-09-17 02_paper/02_study/01_fitbit paper/analysis_270423.Rmd
appendix formatierung & plots

--- 2024-09-04 02_paper/02_study/01_fitbit paper/analysis_270423.Rmd
@@
 
-list(`Preparation Phase` = list(name = "Pre-Teaching ", mod = mods$preparation, data = graph_data$preparation),
-     `Teaching Phase` = list(name = "Teaching Phase", mod = mods$teaching, data = graph_data$teaching),
-     `Post Teaching Phase` = list(name = "Post Teaching Phase",mod = mods$post, data = graph_data$post),
-     `Interview Phase` = list(name = "Interview Phase",mod = mods$interview, data = graph_data$interview),
-     `End Phase` = list(name = "End Phase",mod = mods$end, data = graph_data$end)
+plot_list_appendix <- list(
+  `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
+     `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
+     `Post Teaching Phase` = list(name = "Post-Teaching Interval",mod = mods$post, data = graph_data$post),
+     `Interview Phase` = list(name = "Interview Interval",mod = mods$interview, data = graph_data$interview),
+     `End Phase` = list(name = "End Interval",mod = mods$end, data = graph_data$end)
      ) %>% 
@@
       )
+
+preparation_plot <- plot_list_appendix$`Preparation Phase`
+
+teaching_plot <- plot_list$`Teaching Phase`
+
+post_teaching_plot <- plot_list$`Post Teaching Phase`
+
+interview_plot <- plot_list$`Interview Phase`
+
+end_plot <- plot_list$`End Phase`
+
+ggsave(preparation_plot,
+       filename = "plots_publication/plot_preparation_appendix.pdf",
+       width = 20,
+       height = 12,
+       units = "cm")
 ```

### 2024-09-18 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x paper

@@
       apaTables,
-      rstatix )
+      rstatix,
+      MBESS)
 
@@
 
-### Perform Exploratory Factor Analysis (EFA)
-```{r sri_efa, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+### Internal consistency (Omega) for disruption and confidence appraisal
+```{r sri_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 
-sri <- sri %>% 
-  group_by(ID) %>% 
-  summarise(mean_disrup = mean(disruption_appraisal),
-            mean_confi = mean(confidence_appraisal)
-  ) %>% 
-  dplyr::select(mean_disrup,
-                mean_confi)
-
-# Perform exploratory factor analysis (EFA) with 2 factors
-sri_efa_result <- fa(sri, 
-                     nfactors = 2, 
-                     rotate = "varimax"
-                     )
-
-# Display the result
-print(sri_efa_result)
-
-sri_efa_result$communality
-print(sri_efa_result$loadings, cutoff = 0.4)
-
-# Cronbach's Alpha
-alpha((sri), check.keys =TRUE)
+# change long to wide format
+sri_wide <- sri %>%
+  pivot_wider(names_from = event, 
+              values_from = c(disruption_appraisal, confidence_appraisal, prevalence_rating))
+
+### DISRUPTIONS APPRAISAL
+
+# create new data frame with only disruption items
+sri_wide_disrup <- sri_wide %>%
+  dplyr::select(starts_with("disruption_appraisal")) %>% 
+  drop_na()
+
+# calculate omega with omega() function  
+omega_disrup <- omega(sri_wide_disrup)
+
+# display the results 
+print(omega_disrup)
+
+### CONFIDENCE APPRAISAL
+
+# create new data frame with only confidence items
+sri_wide_confi <- sri_wide %>%
+  dplyr::select(starts_with("confidence_appraisal")) %>% 
+  drop_na()
+
+# calculate omega with omega() function  
+omega_confi <- omega(sri_wide_confi)
+
+# display the results 
+print(omega_confi)
 
@@
 ```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-############## Prevalence Rating as manipulation check #########################
-
-sri.preva.table <-
-  sri %>%
-  group_by(ID) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(prevalence_rating), digits = 2),
-    "SD" = round(sd(prevalence_rating), digits = 2),
-    "Min" = min(prevalence_rating),
-    "Max" = max(prevalence_rating)
-  )
-
-# insert a table into HTML
-knitr::kable(sri.preva.table,
-             caption = "Prevalence rating")
-
-#### with event 
-sri.preva.event.table <-
-  sri %>%
-  group_by(ID, event) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(prevalence_rating), digits = 2),
-    "SD" = round(sd(prevalence_rating), digits = 2),
-    "Min" = min(prevalence_rating),
-    "Max" = max(prevalence_rating)
-  )
-
-# insert a table into HTML
-knitr::kable(sri.preva.event.table,
-             caption = "Prevalence rating with events")
-
-# create a new data frame with rating
-sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
-
-# plotting prevalence rating for groups
-preva_group_plot <- 
-  sri_preva %>% 
-  mutate(ID = factor(ID,
-                     levels = c("Novice",
-                                "Expert"
-                                )
-                     )
-         ) %>% 
-  ggplot(mapping = aes(x = ID,
-                       y = prevalence_rating)) +
-  geom_boxplot(mapping = aes(fill = ID),
-               outlier.shape = NA) +
-  geom_point(size = 1,
-             alpha = 0.4,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  scale_x_discrete(limits = c("Novice", "Expert")) +
-  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
-  labs(x = "",
-       y = "Prevalence Rating") + 
-  scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("How widespread is this event in the classroom?") +
-  theme_cowplot()
-
-preva_group_plot
+# 
+# ############## Prevalence Rating as manipulation check #########################
+# 
+# sri.preva.table <-
+#   sri %>%
+#   group_by(ID) %>%
+#   summarise(
+#     N = n(),
+#     "M" = round(mean(prevalence_rating), digits = 2),
+#     "SD" = round(sd(prevalence_rating), digits = 2),
+#     "Min" = min(prevalence_rating),
+#     "Max" = max(prevalence_rating)
+#   )
+# 
+# # insert a table into HTML
+# knitr::kable(sri.preva.table,
+#              caption = "Prevalence rating")
+# 
+# #### with event 
+# sri.preva.event.table <-
+#   sri %>%
+#   group_by(ID, event) %>%
+#   summarise(
+#     N = n(),
+#     "M" = round(mean(prevalence_rating), digits = 2),
+#     "SD" = round(sd(prevalence_rating), digits = 2),
+#     "Min" = min(prevalence_rating),
+#     "Max" = max(prevalence_rating)
+#   )
+# 
+# # insert a table into HTML
+# knitr::kable(sri.preva.event.table,
+#              caption = "Prevalence rating with events")
+# 
+# # create a new data frame with rating
+# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
+# 
+# # plotting prevalence rating for groups
+# preva_group_plot <- 
+#   sri_preva %>% 
+#   mutate(ID = factor(ID,
+#                      levels = c("Novice",
+#                                 "Expert"
+#                                 )
+#                      )
+#          ) %>% 
+#   ggplot(mapping = aes(x = ID,
+#                        y = prevalence_rating)) +
+#   geom_boxplot(mapping = aes(fill = ID),
+#                outlier.shape = NA) +
+#   geom_point(size = 1,
+#              alpha = 0.4,
+#              position = position_jitter(seed = 1,
+#                                         width = 0.1,
+#                                         height = 0.1)) +
+#   scale_x_discrete(limits = c("Novice", "Expert")) +
+#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
+#   labs(x = "",
+#        y = "Prevalence Rating") + 
+#   scale_fill_brewer(palette  = "RdBu") +  
+#   ggtitle("How widespread is this event in the classroom?") +
+#   theme_cowplot()
+# 
+# preva_group_plot
 
@@
 # select relevant columns --> only subject ID and mean 
-df_sjt <- df_sjt %>%
+df_sjt_mean <- df_sjt %>%
   dplyr::select(UI06_05, # ID
@@
 # remove NAs
-df_sjt <- na.omit(df_sjt)
+df_sjt <- na.omit(df_sjt_mean)
 
 # rename columns
-df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
+df_sjt_mean <- rename(df_sjt_mean, c("Group" = "UI06_05",
                            "Monitoring" = "SJT_AL_gek",
@@
 # changing from wide to long format
-df_sjt_long <- df_sjt %>% 
+df_sjt_long <- df_sjt_mean %>% 
   pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")
@@
 # define expert and novice with ifelse function in wide format
-df_sjt$Group = ifelse(df_sjt$Group < 200, "Novice","Expert")
+df_sjt_mean$Group = ifelse(df_sjt_mean$Group < 200, "Novice","Expert")
 
@@
 # t-test for expertise differences 
-t.test(x = df_sjt$All[df_sjt$Group == "Expert"],
-       y = df_sjt$All[df_sjt$Group == "Novice"],
+t.test(x = df_sjt_mean$All[df_sjt_mean$Group == "Expert"],
+       y = df_sjt_mean$All[df_sjt_mean$Group == "Novice"],
        var.equal = TRUE)
@@
 # effect size for expertise differences
-d_sjt_all <- CohenD(x = df_sjt$All[df_sjt$Group == "Expert"],
-                    y = df_sjt$All[df_sjt$Group == "Novice"],
+d_sjt_all <- CohenD(x = df_sjt_mean$All[df_sjt_mean$Group == "Expert"],
+                    y = df_sjt_mean$All[df_sjt_mean$Group == "Novice"],
                     na.rm = TRUE
@@
 # t-test for expertise differences 
-t.test(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
-       y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
+t.test(x = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Expert"],
+       y = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Novice"],
        var.equal = TRUE
@@
 # effect size for expertise differences
-d_sjt_mm <- CohenD(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
-                   y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
+d_sjt_mm <- CohenD(x = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Expert"],
+                   y = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Novice"],
                    na.rm = TRUE
@@
 # t-test for expertise differences 
-t.test(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
-       y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
+t.test(x = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Expert"],
+       y = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Novice"],
        var.equal = TRUE
@@
 # effect size for expertise differences
-d_sjt_moni <- CohenD(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
-                     y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
+d_sjt_moni <- CohenD(x = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Expert"],
+                     y = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Novice"],
                      na.rm = TRUE
@@
 # t-test for expertise differences 
-t.test(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
-       y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"],
+t.test(x = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Expert"],
+       y = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Novice"],
        var.equal = TRUE
@@
 # effect size for expertise differences
-d_sjt_rr <- CohenD(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
-                   y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"],
+d_sjt_rr <- CohenD(x = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Expert"],
+                   y = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Novice"],
                    na.rm = TRUE
@@
 round(d_sjt_rr, 2)
+
+```
+
+### Internal consistency (Omega) for SJT
+```{r sjt_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# read in data
+df_sjt <- 
+  read_excel("./data/SJT.xlsx")
+
+### MANAGING MOMENTUM
+
+# select relevant columns
+df_sjt_mm <- df_sjt %>%
+    dplyr::select(WT_S1_F1F2_AL:WT_S4_F4F6_AL)
+
+# remove NAs
+df_sjt_mm <- na.omit(df_sjt_mm)
+
+# calculate omega with omega() function  
+omega_sjt_mm <- omega(df_sjt_mm)
+
+# display the results 
+print(omega_sjt_mm)
+
+### MONITORING
+
+# select relevant columns
+df_sjt_m <- df_sjt %>%
+    dplyr::select(WT_S5_F1F2_ST:WT_S9_F4F5_ST)
+
+# remove NAs
+df_sjt_m <- na.omit(df_sjt_m)
+
+# calculate omega with omega() function  
+omega_sjt_m <- omega(df_sjt_m)
+
+# display the results 
+print(omega_sjt_m)
+
+### RULES & ROUTINES
+
+# select relevant columns
+df_sjt_r <- df_sjt %>%
+  dplyr::select(WT_S11_F1F5_R:WT_S14_F4F6_R)
+
+# remove NAs
+df_sjt_r <- na.omit(df_sjt_r)
+
+# calculate omega with omega() function  
+omega_sjt_r <- omega(df_sjt_r)
+
+# display the results 
+print(omega_sjt_r)
 
@@
 
+### Internal consistency (Omega) for Classroom Questionnaire
+```{r cm_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# read in data
+df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  dplyr::select(LM01_01:LM01_08, # classroom management 
+                LP01_01:LP01_08) # non- & paraverbal communication
+
+### CLASSROOM MANAGEMENT
+
+# select relevant columns
+df_quest_cm <- df_quest %>%
+    dplyr::select(LM01_01:LM01_08)
+
+# remove NAs
+df_quest_cm <- na.omit(df_quest_cm)
+
+# calculate omega with omega() function  
+omega_quest_cm <- omega(df_quest_cm)
+
+# display the results 
+print(omega_quest_cm)
+
+### NON- & PARAVERBAL COMMUNICATION
+
+# select relevant columns
+df_quest_npvc <- df_quest %>%
+    dplyr::select(LP01_01:LP01_08)
+
+# remove NAs
+df_quest_npvc <- na.omit(df_quest_npvc)
+
+# calculate omega with omega() function  
+omega_quest_npvc <- omega(df_quest_npvc)
+
+# display the results 
+print(omega_quest_npvc)
+
+```
+
 ## 3. Correlations

### 2024-09-18 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
appendix angefangen

@@
 By harnessing the power of wearable technology, we can provide teachers with the tools needed to better understand and manage their stress, ultimately enhancing their overall well-being.
+
+```{r plots_appendix, include=FALSE}
+mods <-   
+  df_regression %>% 
+  split(.$time_span) %>% 
+  map(~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
+       data = .
+       )
+      )
+
+graph_data <- 
+  df_regression %>% 
+  split(.$time_span)
+
+example <- list(mod = mods$preparation, data = graph_data$preparation)
+
+plot_list_appendix <- list(
+  `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
+     `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
+     `Post Teaching Phase` = list(name = "Post-Teaching Interval",mod = mods$post, data = graph_data$post),
+     `Interview Phase` = list(name = "Interview Interval",mod = mods$interview, data = graph_data$interview),
+     `End Phase` = list(name = "End Interval",mod = mods$end, data = graph_data$end)
+     ) %>% 
+  map(~ ggplot(data = .$data,
+               mapping = aes(x = time,
+                             y = heart_rate_std,
+                             group = ID)) +
+        geom_line(mapping = aes(y = fitted(.$mod)),
+                  color = "blue",
+                  size = 1) +
+        geom_point(alpha = 0.5,
+                   size = 0.5) +
+        scale_x_continuous(breaks = c(0, 5, 10)) +
+        labs(title = .$name,
+             y = "Heart Rate (Standardized)",
+             x = "Time (in Seconds)") +
+        facet_wrap( ~ ID, nrow = 6) +
+        theme_apa()
+      )
+
+preparation_plot <- plot_list_appendix$`Preparation Phase`
+
+teaching_plot <- plot_list_appendix$`Teaching Phase`
+
+post_teaching_plot <- plot_list_appendix$`Post Teaching Phase`
+
+interview_plot <- plot_list_appendix$`Interview Phase`
+
+end_plot <- plot_list_appendix$`End Phase`
+
+ggsave(preparation_plot,
+       filename = "plots_publication/plot_preparation_appendix.pdf",
+       width = 25,
+       height = 25,
+       units = "cm")
+
+ggsave(teaching_plot,
+       filename = "plots_publication/plot_teaching_appendix.pdf",
+       width = 15,
+       height = 25,
+       units = "cm")
+
+ggsave(post_teaching_plot,
+       filename = "plots_publication/plot_post_teaching_appendix.pdf",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+ggsave(interview_plot,
+       filename = "plots_publication/plot_interview_appendix.pdf",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+ggsave(end_plot,
+       filename = "plots_publication/plot_end_appendix.pdf",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+```
+
+```{=latex}
+\newpage
+\appendix
+\section*{Appendix}
+
+\setcounter{figure}{0}  % Reset figure numbering
+
+\renewcommand{\thefigure}{A\arabic{figure}}  % Figures labeled A1, A2, etc.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
+  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
+  \label{micro-teaching}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
+  \caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
+  \label{laboratory}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
+  \caption{bla..}
+  \label{preparation}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
+  \caption{bla..}
+  \label{teaching}
+\end{figure}
+```

### 2024-09-19 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x

@@
       apaTables,
-      rstatix,
-      MBESS)
+      rstatix)
 
@@
 df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")
+
+######## Statistical Methods for Outlier Detection
+
+### OVERALL SCORE (All)
+# Boxplot showing outliers (All)
+ggplot(df_sjt_mean, aes(x = "", y = All)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of SJT (All)",
+       y = "Overall score") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_sjt_mean$All, 0.25)
+Q3 <- quantile(df_sjt_mean$All, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_sjt_all <- df_sjt_mean %>%
+  filter(All >= LowerBound & All <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_sjt_mean)  # Original data
+nrow(df_no_outliers_sjt_all)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_sjt_all <- df_sjt_mean %>%
+  filter(All < LowerBound | All > UpperBound)
+
+# View the removed outliers
+df_outliers_sjt_all
+
+### MANAGING MOMENTUM
+# Boxplot showing outliers (All)
+ggplot(df_sjt_mean, aes(x = "", y = `Managing momentum`)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of SJT (Managing Momentum)",
+       y = "Score") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_sjt_mean$`Managing momentum`, 0.25)
+Q3 <- quantile(df_sjt_mean$`Managing momentum`, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_sjt_mm <- df_sjt_mean %>%
+  filter(`Managing momentum` >= LowerBound & `Managing momentum` <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_sjt_mean)  # Original data
+nrow(df_no_outliers_sjt_mm)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_sjt_mm <- df_sjt_mean %>%
+  filter(`Managing momentum` < LowerBound | `Managing momentum` > UpperBound)
+
+# View the removed outliers
+df_outliers_sjt_mm
+
+### MONITORING
+# Boxplot showing outliers (All)
+ggplot(df_sjt_mean, aes(x = "", y = Monitoring)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of SJT (Monitoring)",
+       y = "Score") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_sjt_mean$Monitoring, 0.25)
+Q3 <- quantile(df_sjt_mean$Monitoring, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_sjt_m <- df_sjt_mean %>%
+  filter(Monitoring >= LowerBound & Monitoring <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_sjt_mean)  # Original data
+nrow(df_no_outliers_sjt_m)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_sjt_m <- df_sjt_mean %>%
+  filter(Monitoring < LowerBound | Monitoring > UpperBound)
+
+# View the removed outliers
+df_outliers_sjt_m
+
+### RULES & ROUTINES
+# Boxplot showing outliers (All)
+ggplot(df_sjt_mean, aes(x = "", y = `Rules and routines`)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of SJT (Rules & routines)",
+       y = "Score") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_sjt_mean$`Rules and routines`, 0.25)
+Q3 <- quantile(df_sjt_mean$`Rules and routines`, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_sjt_r <- df_sjt_mean %>%
+  filter(`Rules and routines` >= LowerBound & `Rules and routines` <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_sjt_mean)  # Original data
+nrow(df_no_outliers_sjt_r)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_sjt_r <- df_sjt_mean %>%
+  filter(`Rules and routines` < LowerBound | `Rules and routines` > UpperBound)
+
+# View the removed outliers
+df_outliers_sjt_r
 

### 2024-09-20 05_automatisation-review/auto-review.Rmd
bla

---
title             : "Automatisation in Classroom Research: reviewing the state of the field. "
shorttitle        : "Automatisation in Classroom Research"

author: 
  - name          : "Gregor Kachel"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Education, Dittrichring 5-7, 04109 Leipzig"
    email         : "gregor.kachel@uni-leipzig.de"
  - name          : "Mandy Klatt"
    affiliation   : "1"
  - name          : "Anne Deiglmayr"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Leipzig University"
  - id            : "2"
    institution   : "MPI for Evolutionary Anthropology, Leipzig"

authornote: |
  The authors declare no conflict of interest.

abstract: |
  Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

keywords          : "Classroom Research; Computer Vision; Pose Estimation; Audio Analysis"
wordcount         : "XXX"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

# Automatic Audio Analyses
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

# Automatic Video Analyses
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

# Limits of Automatisation
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

# Current Developments
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

# A Plea for Automatisation
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2024-09-20 05_automatisation-review/auto-review.tex
bla

--- 2023-04-21 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/TEST.tex
@@
   man]{apa6}
-\title{The title}
-\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
-\date{}
-
-\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[T1]{fontenc}
@@
 \hypersetup{
-  pdftitle={The title},
-  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdftitle={Automatisation in Classroom Research: reviewing the state of the field.},
+  pdfauthor={Gregor Kachel1, 2, Mandy Klatt1, \& Anne Deiglmayr1},
+  pdfkeywords={Classroom Research; Computer Vision; Pose Estimation; Audio Analysis},
   hidelinks,
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx}
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
-
 % \usepackage{etoolbox}
@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
-\keywords{keywords\newline\indent Word count: X}
+\shorttitle{Automatisation in Classroom Research}
+\keywords{Classroom Research; Computer Vision; Pose Estimation; Audio Analysis\newline\indent Word count: XXX}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \usepackage{csquotes}
-\ifXeTeX
+\ifxetex
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
+  \usepackage[shorthands=off,main=english]{babel}
 \fi
 
-\shorttitle{Title}
+\title{Automatisation in Classroom Research: reviewing the state of the field.}
+\author{Gregor Kachel\textsuperscript{1, 2}, Mandy Klatt\textsuperscript{1}, \& Anne Deiglmayr\textsuperscript{1}}
+\date{}
 
@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+The authors declare no conflict of interest.
 
-Enter author note here.
-
-The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.
-
-Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
+Correspondence concerning this article should be addressed to Gregor Kachel, Department of Education, Dittrichring 5-7, 04109 Leipzig.
+E-mail: \href{mailto:gregor.kachel@uni-leipzig.de}{\nolinkurl{gregor.kachel@uni-leipzig.de}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Leipzig University\\\textsuperscript{2} MPI for Evolutionary Anthropology, Leipzig}
 
-\abstract{%
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+\abstract{
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 }
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\hypertarget{automatic-audio-analyses}{%
+\section{Automatic Audio Analyses}\label{automatic-audio-analyses}}
 
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\hypertarget{automatic-video-analyses}{%
+\section{Automatic Video Analyses}\label{automatic-video-analyses}}
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
-We used R (Version 4.1.2; R Core Team, 2020) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2020), \emph{forcats} (Version 0.5.1; Wickham, 2020a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2020), \emph{tidyr} (Version 1.2.0; Wickham, 2020b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.4.0; Garnier, 2018b) for all our analyses.
+\hypertarget{limits-of-automatisation}{%
+\section{Limits of Automatisation}\label{limits-of-automatisation}}
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\hypertarget{current-developments}{%
+\section{Current Developments}\label{current-developments}}
+
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+
+\hypertarget{a-plea-for-automatisation}{%
+\section{A Plea for Automatisation}\label{a-plea-for-automatisation}}
+
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-R-gridExtra}{}}%
-Auguie, B. (2017). \emph{gridExtra: Miscellaneous functions for "grid" graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridExtra}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
-Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
-Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
-Garnier, S. (2018b). \emph{viridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-lubridate}{}}%
-Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with {lubridate}. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{https://www.jstatsoft.org/v40/i03/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
-Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-needs}{}}%
-Katz, J. (2016). \emph{Needs: Attaches and installs packages}. Retrieved from \url{https://CRAN.R-project.org/package=needs}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
-Müller, K., \& Wickham, H. (2020). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
-Wickham, H. (2020a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
-Wickham, H. (2020b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
-Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2020). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
-Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
-Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ARTofR}{}}%
-Zhang, H. (2021). \emph{ARTofR: Who ever care about the {[}art of r{]} scripts?} Retrieved from \url{https://CRAN.R-project.org/package=ARTofR}
-
-\end{CSLReferences}
+\endgroup
 

### 2024-09-23 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
soweit final

--- 2024-09-16 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
@@
 By harnessing the power of wearable technology, we can provide teachers with the tools needed to better understand and manage their stress, ultimately enhancing their overall well-being.
+
+```{r plots_appendix, include=FALSE}
+mods <-   
+  df_regression %>% 
+  split(.$time_span) %>% 
+  map(~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
+       data = .
+       )
+      )
+
+graph_data <- 
+  df_regression %>% 
+  split(.$time_span)
+
+example <- list(mod = mods$preparation, data = graph_data$preparation)
+
+plot_list_appendix <- list(
+  `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
+  `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
+  `Post Teaching Phase` = list(name = "Post-Teaching Interval", mod = mods$post, data = graph_data$post),
+  `Interview Phase` = list(name = "Interview Interval", mod = mods$interview, data = graph_data$interview),
+  `End Phase` = list(name = "End Interval", mod = mods$end, data = graph_data$end)
+) %>% 
+  map(~ ggplot(data = .$data,
+               mapping = aes(x = time,  # Use the appropriate 'x' value (like 'work_hrs' in the original)
+                             y = heart_rate_std,  # Use the appropriate 'y' value (like 'inc')
+                             group = ID)) +
+        geom_line(mapping = aes(y = fitted(.$mod)),  # Line for fitted values from the model
+                  color = "blue",  # Adjust color for clarity
+                  size = 1) +  # Line thickness
+        geom_point(alpha = 0.5, size = 0.5) +  # Points with transparency and size
+        facet_wrap(~ ID, nrow = 8) +  # Arrange plots by 'ID'
+        xlab('Time (in Seconds)') +  # X-axis label (similar to 'Arbeitsstunden pro Woche')
+        ylab('Heart Rate (Standardized)') +  # Y-axis label (similar to 'Nettoeinkommen')
+        scale_x_continuous(breaks = c(0, 5, 10)) +  # Customize x-axis breaks as needed
+        labs(title = .$name) +  # Title for each plot based on phase name
+        theme_bw()  # Use a clean theme
+      )
+
+# 
+# plot_list_appendix <- list(
+#   `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
+#      `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
+#      `Post Teaching Phase` = list(name = "Post-Teaching Interval",mod = mods$post, data = graph_data$post),
+#      `Interview Phase` = list(name = "Interview Interval",mod = mods$interview, data = graph_data$interview),
+#      `End Phase` = list(name = "End Interval",mod = mods$end, data = graph_data$end)
+#      ) %>% 
+#   map(~ ggplot(data = .$data,
+#                mapping = aes(x = time,
+#                              y = heart_rate_std,
+#                              group = ID)) +
+#         geom_line(mapping = aes(y = fitted(.$mod)),
+#                   color = "blue",
+#                   size = 1) +
+#         geom_point(alpha = 0.5,
+#                    size = 0.5) +
+#         scale_x_continuous(breaks = c(0, 5, 10)) +
+#         labs(title = .$name,
+#              y = "Heart Rate (Standardized)",
+#              x = "Time (in Seconds)") +
+#         facet_wrap( ~ ID, nrow = 8) +
+#         theme_apa()
+#       )
+
+preparation_plot <- plot_list_appendix$`Preparation Phase`
+
+teaching_plot <- plot_list_appendix$`Teaching Phase`
+
+post_teaching_plot <- plot_list_appendix$`Post Teaching Phase`
+
+interview_plot <- plot_list_appendix$`Interview Phase`
+
+end_plot <- plot_list_appendix$`End Phase`
+
+ggsave(preparation_plot,
+       filename = "plots_publication/plot_preparation_appendix.pdf",
+       width = 25,
+       height = 30,
+       units = "cm")
+
+ggsave(teaching_plot,
+       filename = "plots_publication/plot_teaching_appendix.pdf",
+       width = 25,
+       height = 30,
+       units = "cm")
+
+ggsave(post_teaching_plot,
+       filename = "plots_publication/plot_post_teaching_appendix.pdf",
+       width = 25,
+       height = 30,
+       units = "cm")
+
+ggsave(interview_plot,
+       filename = "plots_publication/plot_interview_appendix.pdf",
+       width = 25,
+       height = 30,
+       units = "cm")
+
+ggsave(end_plot,
+       filename = "plots_publication/plot_end_appendix.pdf",
+       width = 25,
+       height = 30,
+       units = "cm")
+
+```
+
+```{=latex}
+\newpage
+\appendix
+\section*{Appendix}
+
+\setcounter{figure}{0}  % Reset figure numbering
+
+\renewcommand{\thefigure}{A\arabic{figure}}  % Figures labeled A1, A2, etc.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
+  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
+  \label{micro-teaching}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
+  \caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
+  \label{laboratory}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
+  \caption{bla..}
+  \label{preparation}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
+  \caption{bla..}
+  \label{teaching}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
+  \caption{bla..}
+  \label{post_teaching}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
+  \caption{bla..}
+  \label{interview}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
+  \caption{bla..}
+  \label{end}
+\end{figure}
+```

### 2024-09-23 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
soweit final

@@
 
-\begin{verbatim}
-## Warning: Using `size` aesthetic for lines was deprecated in ggplot2 3.4.0.
-## i Please use `linewidth` instead.
-## This warning is displayed once every 8 hours.
-## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
-## generated.
-\end{verbatim}
-
 \newpage
@@
   \caption{bla..}
-  \label{preparation}
+  \label{teaching}
 \end{figure}
 
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
+  \caption{bla..}
+  \label{post_teaching}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
+  \caption{bla..}
+  \label{interview}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
+  \caption{bla..}
+  \label{end}
+\end{figure}
+
+\newpage
+
 \bibliography{r-references.bib}

### 2024-09-24 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
plot font angepasst

@@
       grid,
-      purrr)
+      purrr,
+      extrafont)
+
+loadfonts(device = 'win')
 ```
@@
                              t = 20,
-                             b = 10)
+                             b = 5),
+        text = element_text(family = "Times",
+                            size = 14)
         ) -> loess_hr
@@
                              t = 20,
-                             b = 10)
+                             b = 5),
+        text = element_text(family = "Times",
+                            size = 14)
         ) -> loess_hr_std
@@
 loess_comp <- annotate_figure(p = loess_comp,
-                              bottom = 'Time (in Minutes)')
+                              bottom = text_grob("Time (in Minutes)",
+                                                 face = "plain",
+                                                 size = 14,       
+                                                 family = "Times")
+                              )
 
@@
        filename = "plots_publication/loess_plot_std_unstd_new.pdf",
-       width = 20,
-       height = 12,
+       width = 25,
+       height = 15,
        units = "cm")
@@
   theme_apa() + 
-  theme(axis.text.x = 
-          element_text(
+  theme(text = element_text(family = "Times"),
+        axis.text.x = element_text(
             color="black",
-            size = 12),
+            size = 14,
+            family = "Times"),
         plot.caption = element_text(hjust = 0)
@@
        plot = box_plot,
-       width = 20,
-       height = 12,
+       width = 25,
+       height = 15,
        units = "cm")
@@
         scale_x_continuous(breaks = c(0, 5, 10)) +  # Customize x-axis breaks as needed
-        labs(title = .$name) +  # Title for each plot based on phase name
-        theme_bw()  # Use a clean theme
+        #labs(title = .$name) +  # Title for each plot based on phase name
+        theme_bw() + # Use a clean theme
+        theme(text = element_text(family = "Times",
+                                  size = 14)
+              )
       )
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
-  \caption{bla..}
+  \caption{Preparation Phase}
   \label{preparation}
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
-  \caption{bla..}
+  \caption{Teaching Phase}
   \label{teaching}
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
-  \caption{bla..}
+  \caption{Post-Teachin Phase}
   \label{post_teaching}
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
-  \caption{bla..}
+  \caption{Interview Phase}
   \label{interview}
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
-  \caption{bla..}
+  \caption{End Phase}
   \label{end}

### 2024-09-24 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
fig+tab references

@@
   - name: Peer Keßler
-    email: Peer@example.com
-    affiliation: Leipzig University
+    email: peer.kessler@uni-greifswald.de.com
+    affiliation: University of Greifswald
     footnote: 2
@@
   - name: Christin Lotz
-    email: christin@example.com
+    email: christin.lotz@uni-leipzig.de
     affiliation: Leipzig University
@@
   - name: Anne Deiglmayr
-    email: anne@example.com
+    email: anne.deiglmayr@uni-leipzig.de
     affiliation: Leipzig University
@@
     country: Germany
+  - code: University of Greifswald
+    organization: Institute of Psychology
+    addressline: Robert-Blum-Str. 13
+    city: Greifswald
+    state: Mecklenburg-Vorpommern
+    postcode: 17489  
 footnote:
@@
     text: 
-      - "Conceptualization"
-      - "Writing - Original Draft Preparation"
+      - "Conceptualization, "
+      - "Writing - Original Draft Preparation, "
       - "Writing - Review & Editing"
@@
     text: 
-      - "Writing - Original Draft Preparation"
+      - "Writing - Original Draft Preparation, "
       - "Writing - Review & Editing"
@@
   \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
-  \label{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
+  \label{fig.1}
 \end{figure}
@@
 
-In addition, we selected five representative 10-minute intervals from the five phases of the lab study (see Figure 2) in order to test the hypotheses that, regarding HR levels, teachers’ HR would be the highest during the micro-teaching unit, compared to all other phases (**Hypothesis 1a**), and, regarding HR slopes, that teachers’ HR would increase while they were preparing for teaching (pre-teaching interval), but decrease in all of the following intervals, i.e.
+In addition, we selected five representative 10-minute intervals from the five phases of the lab study (see Figure \ref{fig.2}) in order to test the hypotheses that, regarding HR levels, teachers’ HR would be the highest during the micro-teaching unit, compared to all other phases (**Hypothesis 1a**), and, regarding HR slopes, that teachers’ HR would increase while they were preparing for teaching (pre-teaching interval), but decrease in all of the following intervals, i.e.
 when they were habituating to and recovering from the stressful micro-teaching unit (**Hypothesis 1b**).
@@
   \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
-  \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
+  \label{fig.2}
 \end{wrapfigure}
@@
   \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
-  \label{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
+  \label{fig.3}
 \end{figure}
@@
 
-Figure 4 shows the distribution of teachers’ mean standardized HR for the five intervals.
+Figure \ref{fig.4} shows the distribution of teachers’ mean standardized HR for the five intervals.
 Repeated measures ANOVA revealed significant differences in mean standardized HR between intervals, $F(4, 400) = 260.62$, $p < .05$, $d = 1.60$ (large effect).
@@
   \caption{Distribution of the standardized heart rate means in the five intervals}
-  \label{Distribution of the standardized heart rate means in the five intervals}
+  \label{fig.4}
 \end{figure}
@@
 
-% Set longtable to stretch the entire width of the page
 \setlength{\LTleft}{0pt}
@@
 
-# 
-# plot_list_appendix <- list(
-#   `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
-#      `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
-#      `Post Teaching Phase` = list(name = "Post-Teaching Interval",mod = mods$post, data = graph_data$post),
-#      `Interview Phase` = list(name = "Interview Interval",mod = mods$interview, data = graph_data$interview),
-#      `End Phase` = list(name = "End Interval",mod = mods$end, data = graph_data$end)
-#      ) %>% 
-#   map(~ ggplot(data = .$data,
-#                mapping = aes(x = time,
-#                              y = heart_rate_std,
-#                              group = ID)) +
-#         geom_line(mapping = aes(y = fitted(.$mod)),
-#                   color = "blue",
-#                   size = 1) +
-#         geom_point(alpha = 0.5,
-#                    size = 0.5) +
-#         scale_x_continuous(breaks = c(0, 5, 10)) +
-#         labs(title = .$name,
-#              y = "Heart Rate (Standardized)",
-#              x = "Time (in Seconds)") +
-#         facet_wrap( ~ ID, nrow = 8) +
-#         theme_apa()
-#       )
-
 preparation_plot <- plot_list_appendix$`Preparation Phase`
@@
   \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
-  \label{micro-teaching}
+  \label{fig.a1}
 \end{figure}
@@
   \caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
-  \label{laboratory}
+  \label{fig.a2}
 \end{figure}
@@
   \caption{Preparation Phase}
-  \label{preparation}
+  \label{fig.a3}
 \end{figure}
@@
   \caption{Teaching Phase}
-  \label{teaching}
+  \label{fig.a4}
 \end{figure}
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
-  \caption{Post-Teachin Phase}
-  \label{post_teaching}
+  \caption{Post-Teaching Phase}
+  \label{fig.a5}
 \end{figure}
@@
   \caption{Interview Phase}
-  \label{interview}
+  \label{fig.a6}
 \end{figure}
@@
   \caption{End Phase}
-  \label{end}
+  \label{fig.a7}
 \end{figure}

### 2024-09-24 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
plot font angepasst
fig+tab references

@@
    \ead{mandy.klatt@uni-leipzig.de} 
-    \author[Leipzig University]{Peer Keßler%
+    \author[University of Greifswald]{Peer Keßler%
   %
   \fnref{2}}
-   \ead{Peer@example.com} 
+   \ead{peer.kessler@uni-greifswald.de.com} 
     \author[Leipzig University, Max Planck Institute for Evolutionary
@@
   \fnref{1}}
-   \ead{christin@example.com} 
+   \ead{christin.lotz@uni-leipzig.de} 
     \author[Leipzig University]{Anne Deiglmayr%
@@
   \fnref{3}}
-   \ead{anne@example.com} 
+   \ead{anne.deiglmayr@uni-leipzig.de} 
       \affiliation[Leipzig University]{
@@
 6},city={Leipzig},postcode={4103},state={Sachsen},country={Germany},}
+    \affiliation[University of Greifswald]{
+    organization={Institute of Psychology},addressline={Robert-Blum-Str.
+13},city={Greifswald},postcode={17489},state={Mecklenburg-Vorpommern},}
     \cortext[cor1]{Corresponding author}
-    \fntext[1]{ConceptualizationWriting - Original Draft
-PreparationWriting - Review \& Editing}
-    \fntext[2]{Writing - Original Draft PreparationWriting - Review \&
+    \fntext[1]{Conceptualization,Writing - Original Draft
+Preparation,Writing - Review \& Editing}
+    \fntext[2]{Writing - Original Draft Preparation,Writing - Review \&
 Editing}
@@
 In addition, we selected five representative 10-minute intervals from
-the five phases of the lab study (see Figure 2) in order to test the
-hypotheses that, regarding HR levels, teachers' HR would be the highest
-during the micro-teaching unit, compared to all other phases
+the five phases of the lab study (see Figure \ref{fig.2}) in order to
+test the hypotheses that, regarding HR levels, teachers' HR would be the
+highest during the micro-teaching unit, compared to all other phases
 (\textbf{Hypothesis 1a}), and, regarding HR slopes, that teachers' HR
@@
 
-Figure 4 shows the distribution of teachers' mean standardized HR for
-the five intervals. Repeated measures ANOVA revealed significant
+Figure \ref{fig.4} shows the distribution of teachers' mean standardized
+HR for the five intervals. Repeated measures ANOVA revealed significant
 differences in mean standardized HR between intervals,
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
-  \caption{bla..}
-  \label{preparation}
+  \caption{Preparation Phase}
+  \label{fig.a3}
 \end{figure}
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
-  \caption{bla..}
-  \label{teaching}
+  \caption{Teaching Phase}
+  \label{fig.a4}
 \end{figure}
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
-  \caption{bla..}
-  \label{post_teaching}
+  \caption{Post-Teaching Phase}
+  \label{fig.a5}
 \end{figure}
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
-  \caption{bla..}
-  \label{interview}
+  \caption{Interview Phase}
+  \label{fig.a6}
 \end{figure}
@@
   \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
-  \caption{bla..}
-  \label{end}
+  \caption{End Phase}
+  \label{fig.a7}
 \end{figure}
 
-\newpage
-
 \bibliography{r-references.bib}

### 2024-09-24 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
Format Sachen

@@
   - \usepackage{geometry}
+  - \usepackage{caption}
 ---
@@
 ```{=latex}
+\captionsetup[figure]{
+    labelfont=bf,         % Figure label bold (not italic)
+    parskip=12pt,
+    labelsep=newline,      % Period after Figure label
+    textfont=it,          % Italic font for the caption text
+    font=small,           % Smaller font size for APA style
+    justification=justified, % Left-justified captions, as per APA guidelines
+    singlelinecheck=false % Avoid centering if the caption is single-line
+}
+
+\captionsetup[table]{
+    labelfont=bf,         % Figure label bold (not italic)
+    parskip=12pt,
+    labelsep=newline,      % Period after Figure label
+    textfont=it,          % Italic font for the caption text
+    font=small,           % Smaller font size for APA style
+    justification=justified, % Left-justified captions, as per APA guidelines
+    singlelinecheck=false % Avoid centering if the caption is single-line
+}
+
 \begin{figure}[htbp]
+  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
   \centering
   \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
-  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
   \label{fig.1}
@@
 This phase took about 10-15 minutes and participants spent this time mostly standing or slowly walking around.
-During the *teaching phase*, the participants held their self-prepared micro-teaching unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table ## in the supplementary material for an overview and categorization of all events; and Fig## in the supplementary material for a depiction of the laboratory setting of the micro-teaching unit).
+During the *teaching phase*, the participants held their self-prepared micro-teaching unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table ## in the supplementary material for an overview and categorization of all events; and Figure \ref{fig.a2} in the supplementary material for a depiction of the laboratory setting of the micro-teaching unit).
 The topic and class level of the teaching unit could be freely chosen by the teachers with the only requirement that the unit had to be an introductory lesson, and had to consist of supervised individual work and / or frontal teaching.
@@
   \centering
+  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
   \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
-  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
   \label{fig.2}
@@
 
-## Mapping teachers’ HR over the course of the study phases
-
-Means, standard deviations, and range of teachers’ unstandardized and standardized HR for the entire study period, and for the five intervals, are shown in Table 1.
-Fig.
-3 a.
-and b.
-display the unstandardized and standardized HR trends, respectively, over the course of the entire study period.
-HR initially increased, peaked, and then decreased, with the unstandardized and standardized HR graphs showing high similarity.
-Thus, for all further analyses, we used participants’ standardized HR values.
-
 ```{=latex}
@@
     \centering
+    \caption{Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
     \begin{tabularx}{\textwidth}{lXXXXX}
@@
     \end{tabularx}
-    \caption{Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
     \label{tab_1}
@@
   \centering
+  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
   \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
-  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
   \label{fig.3}
@@
 
-\newpage
+## Mapping teachers’ HR over the course of the study phases
+
+Means, standard deviations, and range of teachers’ unstandardized and standardized HR for the entire study period, and for the five intervals, are shown in Table \ref{tab_1}.
+Figure \ref{fig.3} displays the unstandardized and standardized HR trends, respectively, over the course of the entire study period.
+HR initially increased, peaked, and then decreased, with the unstandardized and standardized HR graphs showing high similarity.
+Thus, for all further analyses, we used participants’ standardized HR values.
 
@@
   \centering
+  \caption{Distribution of the standardized heart rate means in the five intervals}
   \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
-  \caption{Distribution of the standardized heart rate means in the five intervals}
   \label{fig.4}
@@
     \centering
+    \caption{Analysis (\textit{M, SD, p-values}) for the mean intercepts and the mean slopes for the five intervals.}
     \begin{tabularx}{\textwidth}{lXXXXXX}
@@
     \end{tabularx}
-    \caption{Analysis (\textit{M, SD, p-values}) for the mean intercepts and the mean slopes for the five intervals }
     \label{tab_2}
@@
 
-Concerning the explorative investigation of the effects of teaching experience and subjective appraisals on *changes* (i.e., mean slopes) in teachers’ HR, teaching experience significantly predicted the mean slope in the *pre-teaching interval* (Table 4, Pre-teaching interval, Model 1), indicating a less steep HR increase in teachers with more teaching experience.
-For all other intervals, no variable had significant predictive value.
-
 ```{=latex}
@@
 
-\begin{table}[ht]
+\begin{table}[h]
     \centering
+    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
     \begin{tabularx}{\textwidth}{lccccc}
@@
     \end{tabularx}
-    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
     \label{tab_3}
@@
 ```
+
+Concerning the explorative investigation of the effects of teaching experience and subjective appraisals on *changes* (i.e., mean slopes) in teachers’ HR, teaching experience significantly predicted the mean slope in the *pre-teaching interval* (Table 4, Pre-teaching interval, Model 1), indicating a less steep HR increase in teachers with more teaching experience.
+For all other intervals, no variable had significant predictive value.
 
@@
 
+\captionof{table}{Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
+
 \begin{longtable}{@{\extracolsep{\fill}} p{1.8cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} @{}}
@@
 
-    \multicolumn{17}{c}{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
     \toprule
@@
 
-    Pre-teaching \newline interval (I1) & & & & & & & & & & & & & & & & \\
+    Pre-teaching \newline interval ($I_1$) & & & & & & & & & & & & & & & & \\
     Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.17$\\$(.005)$\end{tabular} & $.12$ & \begin{tabular}{@{}c@{}}$-.27^*$\\$(.002)$\end{tabular} & $<.05$ & & & & & & & & & & & & \\
@@
     \midrule
-    Teaching \newline interval (I2) & & & & & & & & & & & & & & & & \\
+    Teaching \newline interval ($I_2$) & & & & & & & & & & & & & & & & \\
     Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.11$\\$(.002)$\end{tabular} & $.34$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.83$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.73$ & \begin{tabular}{@{}c@{}}$.01$\\$(.001)$\end{tabular} & $.96$ & \begin{tabular}{@{}c@{}}$.10$\\$(.006)$\end{tabular} & $.42$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.001)$\end{tabular} & $.54$ & \begin{tabular}{@{}c@{}}$.05$\\$(.006)$\end{tabular} & $.67$ & \begin{tabular}{@{}c@{}}$-.05$\\$(.001)$\end{tabular} & $.72$ \\
@@
     \midrule
-    Post-teaching \newline interval (I3) & & & & & & & & & & & & & & & & \\
+    Post-teaching \newline interval ($I_3$) & & & & & & & & & & & & & & & & \\
     Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.04$\\$(.005)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$-.03$\\$(.001)$\end{tabular} & $.80$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$-.09$\\$(.001)$\end{tabular} & $.44$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.006)$\end{tabular} & $.55$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.89$ & \begin{tabular}{@{}c@{}}$-.01$\\$(.006)$\end{tabular} & $.91$ & \begin{tabular}{@{}c@{}}$-.07$\\$(.001)$\end{tabular} & $.61$ \\
@@
     \midrule
-    Interview \newline interval (I4) & & & & & & & & & & & & & & & & \\
+    Interview \newline interval ($I_4$) & & & & & & & & & & & & & & & & \\
     Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.24^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.20$\\$(.001)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$.22$\\$(.006)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$-.23$\\$(.001)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$.25^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.14$\\$(.001)$\end{tabular} & $.25$ & \begin{tabular}{@{}c@{}}$.23$\\$(.007)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$-.17$\\$(.001)$\end{tabular} & $.18$ \\
@@
     \midrule
-    End \newline interval (I5) & & & & & & & & & & & & & & & & \\
+    End \newline interval ($I_5$) & & & & & & & & & & & & & & & & \\
     Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.04$\\$(.004)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$.11$\\$(.001)$\end{tabular} & $.32$ & \begin{tabular}{@{}c@{}}$.07$\\$(.005)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.18$\\$(.001)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.09$\\$(.005)$\end{tabular} & $.46$ & \begin{tabular}{@{}c@{}}$.07$\\$(.001)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.10$\\$(.005)$\end{tabular} & $.43$ & \begin{tabular}{@{}c@{}}$.12$\\$(.001)$\end{tabular} & $.33$ \\
@@
 In Model 4, all three predictors were considered in concert.
-\item * $p < .05$.
+* $p < .05$.
 \end{tablenotes}
@@
 
+\renewcommand{\arraystretch}{1.5}
+
+\begin{table}[ht]
+    \centering
+    \caption{Classification of nine, typical classroom disruptions according to @lohmann2003schulern performed in the micro-teaching unit by actors.}
+    \begin{tabularx}{\textwidth}{XXX}
+        \toprule
+        \textbf{Verbal disruptions} & \textbf{Physical disruptions} & \textbf{Lack of eagerness to learn} \\
+        \midrule
+        Heckling & Clicking pen & Looking at phone \\
+        Chatting & Snipping hands & Drawing \\
+        Whispering & Drumming hands & Head on table \\
+        \bottomrule
+    \end{tabularx}
+    \label{tab.a1}
+\end{table}
+
 \begin{figure}[htbp]
   \centering
+  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
   \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
-  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
   \label{fig.a1}
@@
 \begin{figure}[htbp]
-  \centering
+  \centering\caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
   \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
-  \caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
   \label{fig.a2}
@@
   \centering
+  \caption{Linear estimation of individual HR changes over time during the preparation phase for $N$ = 81 participants.
+Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
   \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
-  \caption{Preparation Phase}
   \label{fig.a3}
@@
   \centering
+  \caption{Linear estimation of individual HR changes over time during the teaching phase for $N$ = 81 participants.
+Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
   \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
-  \caption{Teaching Phase}
   \label{fig.a4}
@@
   \centering
+  \caption{Linear estimation of individual HR changes over time during the post-teaching phase for $N$ = 81 participants.
+Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
   \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
-  \caption{Post-Teaching Phase}
   \label{fig.a5}
@@
   \centering
+  \caption{Linear estimation of individual HR changes over time during the interview phase for $N$ = 81 participants.
+Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
   \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
-  \caption{Interview Phase}
   \label{fig.a6}
@@
   \centering
+  \caption{Linear estimation of individual HR changes over time during the end phase for $N$ = 81 participants.
+Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
   \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
-  \caption{End Phase}
   \label{fig.a7}

### 2024-09-24 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
Format Sachen

@@
 \usepackage{geometry}
+\usepackage{caption}
 
@@
 
+\captionsetup[figure]{
+    labelfont=bf,         % Figure label bold (not italic)
+    parskip=12pt,
+    labelsep=newline,      % Period after Figure label
+    textfont=it,          % Italic font for the caption text
+    font=small,           % Smaller font size for APA style
+    justification=justified, % Left-justified captions, as per APA guidelines
+    singlelinecheck=false % Avoid centering if the caption is single-line
+}
+
+\captionsetup[table]{
+    labelfont=bf,         % Figure label bold (not italic)
+    parskip=12pt,
+    labelsep=newline,      % Period after Figure label
+    textfont=it,          % Italic font for the caption text
+    font=small,           % Smaller font size for APA style
+    justification=justified, % Left-justified captions, as per APA guidelines
+    singlelinecheck=false % Avoid centering if the caption is single-line
+}
+
 \begin{figure}[htbp]
+  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
   \centering
   \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
-  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
   \label{fig.1}
@@
 supplementary material for an overview and categorization of all events;
-and Fig\#\# in the supplementary material for a depiction of the
-laboratory setting of the micro-teaching unit). The topic and class
+and Figure \ref{fig.a2} in the supplementary material for a depiction of
+the laboratory setting of the micro-teaching unit). The topic and class
 level of the teaching unit could be freely chosen by the teachers with
@@
 
-\subsection{Mapping teachers' HR over the course of the study
-phases}\label{mapping-teachers-hr-over-the-course-of-the-study-phases}
-
-Means, standard deviations, and range of teachers' unstandardized and
-standardized HR for the entire study period, and for the five intervals,
-are shown in Table 1. Fig. 3 a. and b. display the unstandardized and
-standardized HR trends, respectively, over the course of the entire
-study period. HR initially increased, peaked, and then decreased, with
-the unstandardized and standardized HR graphs showing high similarity.
-Thus, for all further analyses, we used participants' standardized HR
-values.
-
 \renewcommand{\arraystretch}{1.5}
@@
 
-\newpage
+\subsection{Mapping teachers' HR over the course of the study
+phases}\label{mapping-teachers-hr-over-the-course-of-the-study-phases}
+
+Means, standard deviations, and range of teachers' unstandardized and
+standardized HR for the entire study period, and for the five intervals,
+are shown in Table \ref{tab_1}. Figure \ref{fig.3} displays the
+unstandardized and standardized HR trends, respectively, over the course
+of the entire study period. HR initially increased, peaked, and then
+decreased, with the unstandardized and standardized HR graphs showing
+high similarity. Thus, for all further analyses, we used participants'
+standardized HR values.
 
@@
 
-Concerning the explorative investigation of the effects of teaching
-experience and subjective appraisals on \emph{changes} (i.e., mean
-slopes) in teachers' HR, teaching experience significantly predicted the
-mean slope in the \emph{pre-teaching interval} (Table 4, Pre-teaching
-interval, Model 1), indicating a less steep HR increase in teachers with
-more teaching experience. For all other intervals, no variable had
-significant predictive value.
-
 \renewcommand{\arraystretch}{1.5}
 
-\begin{table}[ht]
-    \centering
+\begin{table}[h]
+    \centering
+    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
     \begin{tabularx}{\textwidth}{lccccc}
@@
 
+Concerning the explorative investigation of the effects of teaching
+experience and subjective appraisals on \emph{changes} (i.e., mean
+slopes) in teachers' HR, teaching experience significantly predicted the
+mean slope in the \emph{pre-teaching interval} (Table 4, Pre-teaching
+interval, Model 1), indicating a less steep HR increase in teachers with
+more teaching experience. For all other intervals, no variable had
+significant predictive value.
+
 \begin{landscape}
@@
 \setlength{\LTright}{0pt}
+
+\captionof{table}{Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
 

### 2024-09-24 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_24_MK.Rmd
expertise

--- 2024-09-18 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
@@
 
+# filter only for experts
+df_aoi_sum_expert <- df_aoi_sum %>% 
+  filter(Group == "Expert")
+
+# filter only for novices
+df_aoi_sum_novice <- df_aoi_sum %>% 
+  filter(Group == "Novice")
+
 ######## Statistical Methods for Outlier Detection
 
-# Boxplot showing outliers
-ggplot(df_aoi_sum, aes(x = "", y = Number_fixation_min_mtu)) + 
+### EXPERTS ###
+
+# Boxplot showing outliers for experts
+ggplot(df_aoi_sum_expert, aes(x = "", y = Number_fixation_min_mtu)) + 
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
@@
 # Calculate the IQR and bounds
-Q1 <- quantile(df_aoi_sum$Number_fixation_min_mtu, 0.25)
-Q3 <- quantile(df_aoi_sum$Number_fixation_min_mtu, 0.75)
+Q1 <- quantile(df_aoi_sum_expert$Number_fixation_min_mtu, 0.25)
+Q3 <- quantile(df_aoi_sum_expert$Number_fixation_min_mtu, 0.75)
 IQR <- Q3 - Q1
@@
 # Filter to remove outliers
-df_no_outliers_mtu <- df_aoi_sum %>%
+df_no_outliers_mtu_exp <- df_aoi_sum_expert %>%
   filter(Number_fixation_min_mtu >= LowerBound & Number_fixation_min_mtu <= UpperBound)
@@
 # Check the number of rows before and after filtering
-nrow(df_aoi_sum)  # Original data
-nrow(df_no_outliers_mtu)  # After removing outliers
+nrow(df_aoi_sum_expert)  # Original data
+nrow(df_no_outliers_mtu_exp)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_mtu_exp <- df_aoi_sum_expert %>%
+  filter(Number_fixation_min_mtu < LowerBound | Number_fixation_min_mtu > UpperBound)
+
+# View the removed outliers
+df_outliers_mtu_exp # ID 205
+
+### NOVICES ###
+
+# Boxplot showing outliers for novices
+ggplot(df_aoi_sum_novice, aes(x = "", y = Number_fixation_min_mtu)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
+       y = "Number of fixations per minute") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_sum_novice$Number_fixation_min_mtu, 0.25)
+Q3 <- quantile(df_aoi_sum_novice$Number_fixation_min_mtu, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_mtu_nov <- df_aoi_sum_novice %>%
+  filter(Number_fixation_min_mtu >= LowerBound & Number_fixation_min_mtu <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_sum_novice)  # Original data
+nrow(df_no_outliers_mtu_nov)  # After removing outliers
 
@@
   df_aoi_sum %>%
+  filter(!Participant == "205") %>% # exclude outlier
   group_by(Group) %>%
@@
 df_aoi_sum %>%
+  filter(!Participant == "205") %>% 
   ggplot(mapping = aes(x = Group, y = Number_fixation_min_mtu)) +
@@
 # NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit) 
+# create data frame without oulier 
+df_aoi_sum_no_out <- df_aoi_sum %>% 
+  filter(!Participant == "205")
+
 # t-test for expertise differences
 t.test(
-  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
-  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
+  x = df_aoi_sum_no_out$Number_fixation_min_mtu[df_aoi_sum_no_out$Group == "Expert"],
+  y = df_aoi_sum_no_out$Number_fixation_min_mtu[df_aoi_sum_no_out$Group == "Novice"],
   var.equal = TRUE
@@
 d_number_all <- CohenD(
-  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
-  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
+  x = df_aoi_sum_no_out$Number_fixation_min_mtu[df_aoi_sum_no_out$Group == "Expert"],
+  y = df_aoi_sum_no_out$Number_fixation_min_mtu[df_aoi_sum_no_out$Group == "Novice"],
   na.rm = TRUE
@@
     Group = as_factor(Group),
+    Participant = Participant,
     Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
     Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
-    Participant = Participant,
     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
@@
 
+# filter only for experts
+df_aoi_stud_expert <- df_aoi_stud %>% 
+  filter(Group == "Expert")
+
+# filter only for novices
+df_aoi_stud_novice <- df_aoi_stud %>% 
+  filter(Group == "Novice")
+
 ######## Statistical Methods for Outlier Detection
 
-# Boxplot showing outliers
-ggplot(df_aoi_stud, aes(x = "", y = Stud_number_fixation_min)) + 
+### EXPERTS ###
+
+# Boxplot showing outliers for experts
+ggplot(df_aoi_stud_expert, aes(x = "", y = Stud_number_fixation_min)) + 
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
@@
 # Calculate the IQR and bounds
-Q1 <- quantile(df_aoi_stud$Stud_number_fixation_min, 0.25)
-Q3 <- quantile(df_aoi_stud$Stud_number_fixation_min, 0.75)
+Q1 <- quantile(df_aoi_stud_expert$Stud_number_fixation_min, 0.25)
+Q3 <- quantile(df_aoi_stud_expert$Stud_number_fixation_min, 0.75)
 IQR <- Q3 - Q1
@@
 # Filter to remove outliers
-df_no_outliers_stud <- df_aoi_stud %>%
+df_no_outliers_stud_exp <- df_aoi_stud_expert %>%
   filter(Stud_number_fixation_min >= LowerBound & Stud_number_fixation_min <= UpperBound)
@@
 # Check the number of rows before and after filtering
-nrow(df_aoi_stud)  # Original data
-nrow(df_no_outliers_stud)  # After removing outliers
+nrow(df_aoi_stud_expert)  # Original data
+nrow(df_no_outliers_stud_exp)  # After removing outliers
 
 # Create a dataframe with only the outliers
-df_outliers_stud <- df_aoi_stud %>%
+df_outliers_stud_exp <- df_aoi_stud_expert %>%
   filter(Stud_number_fixation_min < LowerBound | Stud_number_fixation_min > UpperBound)
@@
 # View the removed outliers
-df_outliers_stud
+df_outliers_stud_exp
+
+### NOVICES ###
+
+# Boxplot showing outliers for novices
+ggplot(df_aoi_stud_novice, aes(x = "", y = Stud_number_fixation_min)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of number of fixations per minute (AOI students)",
+       y = "Number of fixations per minute") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_stud_novice$Stud_number_fixation_min, 0.25)
+Q3 <- quantile(df_aoi_stud_novice$Stud_number_fixation_min, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_stud_nov <- df_aoi_stud_novice %>%
+  filter(Stud_number_fixation_min >= LowerBound & Stud_number_fixation_min <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_stud_novice)  # Original data
+nrow(df_no_outliers_stud_nov)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_stud_nov <- df_aoi_stud_novice %>%
+  filter(Stud_number_fixation_min < LowerBound | Stud_number_fixation_min > UpperBound)
+
+# View the removed outliers
+df_outliers_stud_nov
 
@@
 nof.min.stud.table <-
-  df_no_outliers_stud %>%
+  df_aoi_stud %>%
+  filter(!Participant %in% c("205", "236", "241")) %>%
   group_by(Group) %>%
@@
 df_aoi_stud %>%
+  filter(!Participant %in% c("205", "236", "241")) %>%
   ggplot(mapping = aes(x = Group, y = Stud_number_fixation_min)) +
@@
 # NUMBER OF FIXATIONS on AOI students 
+# create data frame without oulier 
+df_aoi_stud_no_out <- df_aoi_stud %>% 
+  filter(!Participant %in% c("205", "236", "241"))
+
 # t-test for expertise differences
 t.test(
-  x = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Expert"],
-  y = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Novice"],
+  x = df_aoi_stud_no_out$Stud_number_fixation_min[df_aoi_stud_no_out$Group == "Expert"],
+  y = df_aoi_stud_no_out$Stud_number_fixation_min[df_aoi_stud_no_out$Group == "Novice"],
   var.equal = TRUE
@@
 d_number_stud <- CohenD(
-  x = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Expert"],
-  y = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Novice"],
+  x = df_aoi_stud_no_out$Stud_number_fixation_min[df_aoi_stud_no_out$Group == "Expert"],
+  y = df_aoi_stud_no_out$Stud_number_fixation_min[df_aoi_stud_no_out$Group == "Novice"],
   na.rm = TRUE
@@
 
+# filter only for experts
+df_aoi_disrup_expert <- df_aoi_disrup %>% 
+  filter(Group == "Expert")
+
+# filter only for novices
+df_aoi_disrup_novice <- df_aoi_disrup %>% 
+  filter(Group == "Novice")
+
 ######## Statistical Methods for Outlier Detection
 
-# Boxplot showing outliers
-ggplot(df_aoi_disrup, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
+### EXPERTS ###
+
+# Boxplot showing outliers for experts
+ggplot(df_aoi_disrup_expert, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
@@
 # Calculate the IQR and bounds
-Q1 <- quantile(df_aoi_disrup$Number_of_fixations.Disruptive_Person, 0.25)
-Q3 <- quantile(df_aoi_disrup$Number_of_fixations.Disruptive_Person, 0.75)
+Q1 <- quantile(df_aoi_disrup_expert$Number_of_fixations.Disruptive_Person, 0.25)
+Q3 <- quantile(df_aoi_disrup_expert$Number_of_fixations.Disruptive_Person, 0.75)
 IQR <- Q3 - Q1
@@
 # Filter to remove outliers
-df_no_outliers_disrup <- df_aoi_disrup %>%
+df_no_outliers_disrup_exp <- df_aoi_disrup_expert %>%
   filter(Number_of_fixations.Disruptive_Person >= LowerBound & Number_of_fixations.Disruptive_Person <= UpperBound)
@@
 # Check the number of rows before and after filtering
-nrow(df_aoi_disrup)  # Original data
-nrow(df_no_outliers_disrup)  # After removing outliers
+nrow(df_aoi_disrup_expert)  # Original data
+nrow(df_no_outliers_disrup_exp)  # After removing outliers
 
 # Create a dataframe with only the outliers
-df_outliers_disrup <- df_aoi_disrup %>%
+df_outliers_disrup_exp <- df_aoi_disrup_expert %>%
   filter(Number_of_fixations.Disruptive_Person < LowerBound | Number_of_fixations.Disruptive_Person > UpperBound)
@@
 # View the removed outliers
-df_outliers_disrup
+df_outliers_disrup_exp
+
+### NOVICES ###
+
+# Boxplot showing outliers for novices
+ggplot(df_aoi_disrup_novice, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of number of fixations per minute (AOI disruptive person)",
+       y = "Number of fixations per minute") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_disrup_novice$Number_of_fixations.Disruptive_Person, 0.25)
+Q3 <- quantile(df_aoi_disrup_novice$Number_of_fixations.Disruptive_Person, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_disrup_nov <- df_aoi_disrup_novice %>%
+  filter(Number_of_fixations.Disruptive_Person >= LowerBound & Number_of_fixations.Disruptive_Person <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_disrup_novice)  # Original data
+nrow(df_no_outliers_disrup_nov)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_disrup_nov <- df_aoi_disrup_novice %>%
+  filter(Number_of_fixations.Disruptive_Person < LowerBound | Number_of_fixations.Disruptive_Person > UpperBound)
+
+# View the removed outliers
+df_outliers_disrup_nov
 
 ######## N, M, SD, min & max number of fixation on AOI "disruptive person"
-nof.disrup.table <-
-  df_no_outliers_disrup %>%
+nof.disrup.table <- df_aoi_disrup %>% 
+  filter(!Participant %in% c("207", "226", "101", "108", "116")) %>% 
   group_by(Group) %>%
@@
 # plotting average duration on AOI Disruptive person
-df_no_outliers_disrup %>%
+df_aoi_disrup %>% 
+  filter(!Participant %in% c("207", "226", "101", "108", "116")) %>% 
   ggplot(mapping = aes(x = Group, y = Number_of_fixations.Disruptive_Person)) +
@@
 # NUMBER OF FIXATIONS on AOI disruptive person
+# create data frame without oulier 
+df_no_outliers_disrup <- df_aoi_disrup %>% 
+  filter(!Participant %in% c("207", "226", "101", "108", "116"))
+
 # t-test for expertise differences
@@
 
-# Boxplot showing outliers
-ggplot(df_aoi_sum, aes(x = "", y = Average_duration_mtu)) + 
+### EXPERTS ###
+
+# Boxplot showing outliers for experts
+ggplot(df_aoi_sum_expert, aes(x = "", y = Average_duration_mtu)) + 
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of Average duration of fixations per minute",
-       y = "Average duration of fixations per minute") +
+  labs(title = "Boxplot of Average duration of fixations",
+       y = "Average duration of fixations in msec") +
+  theme_minimal()
+
+### NOVICES ###
+
+# Boxplot showing outliers for experts
+ggplot(df_aoi_sum_novice, aes(x = "", y = Average_duration_mtu)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of Average duration of fixations",
+       y = "Average duration of fixations in msec") +
   theme_minimal()
@@
     Group,
+    Participant,
     "Total_duration_of_fixations.Anna",
@@
     Group = Group,
+    Participant = Participant,
     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
@@
 
+# filter only for experts
+df_aoi_stud_expert <- df_aoi_stud %>% 
+  filter(Group == "Expert")
+
+# filter only for novices
+df_aoi_stud_novice <- df_aoi_stud %>% 
+  filter(Group == "Novice")
+
 ######## Statistical Methods for Outlier Detection
 
+### EXPERTS ###
+
 # Boxplot showing outliers
-ggplot(df_aoi_stud, aes(x = "", y = Average_duration_stud)) + 
+ggplot(df_aoi_stud_expert, aes(x = "", y = Average_duration_stud)) + 
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of average duration of fixations (AOI students)",
+  labs(title = "EXPERTS: Boxplot of average duration of fixations (AOI students)",
        y = "Average duration of fixations") +
@@
 
+### NOVICES ###
+
+# Boxplot showing outliers
+ggplot(df_aoi_stud_novice, aes(x = "", y = Average_duration_stud)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "NOVICES: Boxplot of average duration of fixations (AOI students)",
+       y = "Average duration of fixations") +
+  theme_minimal()
+
 # Calculate the IQR and bounds
-Q1 <- quantile(df_aoi_stud$Average_duration_stud, 0.25)
-Q3 <- quantile(df_aoi_stud$Average_duration_stud, 0.75)
+Q1 <- quantile(df_aoi_stud_novice$Average_duration_stud, 0.25)
+Q3 <- quantile(df_aoi_stud_novice$Average_duration_stud, 0.75)
 IQR <- Q3 - Q1
@@
 # Filter to remove outliers
-df_no_outliers_stud_dur <- df_aoi_stud %>%
+df_no_outliers_stud_dur_nov <- df_aoi_stud_novice %>%
   filter(Average_duration_stud >= LowerBound & Average_duration_stud <= UpperBound)
@@
 # Check the number of rows before and after filtering
-nrow(df_aoi_stud)  # Original data
-nrow(df_no_outliers_stud_dur)  # After removing outliers
+nrow(df_aoi_stud_novice)  # Original data
+nrow(df_no_outliers_stud_dur_nov)  # After removing outliers
 
 # Create a dataframe with only the outliers
-df_outliers_stud_dur <- df_aoi_stud %>%
+df_outliers_dur_stud_nov <- df_aoi_stud_novice %>%
   filter(Average_duration_stud < LowerBound | Average_duration_stud > UpperBound)
@@
 # View the removed outliers
-df_outliers_stud_dur
+df_outliers_dur_stud_nov
 
@@
 dur.stud.table <-
-  df_no_outliers_stud_dur %>%
+  df_aoi_stud %>%
+  filter(!Participant %in% c("105", "133")) %>% 
   group_by(Group) %>%
@@
 # plotting average duration on AOI Students
-df_no_outliers_stud_dur %>%
+df_aoi_stud %>%
+  filter(!Participant %in% c("105", "133")) %>% 
   ggplot(mapping = aes(x = Group, y = Average_duration_stud)) +
@@
 # AVERAGE DURATION OF FIXATIONS on AOI Students 
+# create data frame without outlier
+df_no_outliers_stud_dur <- df_aoi_stud %>%
+  filter(!Participant %in% c("105", "133"))
+
 # t-test for expertise differences
@@
     Group,
+    Participant,
     "Total_duration_of_fixations.Disruptive_Person",
@@
 
+# filter only for experts
+df_aoi_disrup_expert <- df_aoi_disrup %>% 
+  filter(Group == "Expert")
+
+# filter only for novices
+df_aoi_disrup_novice <- df_aoi_disrup %>% 
+  filter(Group == "Novice")
+
 ######## Statistical Methods for Outlier Detection
 
+### EXPERTS ###
+
 # Boxplot showing outliers
-ggplot(df_aoi_disrup, aes(x = "", y = Average_duration_disrup)) + 
+ggplot(df_aoi_disrup_expert, aes(x = "", y = Average_duration_disrup)) + 
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
@@
 # Calculate the IQR and bounds
-Q1 <- quantile(df_aoi_disrup$Average_duration_disrup, 0.25)
-Q3 <- quantile(df_aoi_disrup$Average_duration_disrup, 0.75)
+Q1 <- quantile(df_aoi_disrup_expert$Average_duration_disrup, 0.25)
+Q3 <- quantile(df_aoi_disrup_expert$Average_duration_disrup, 0.75)
 IQR <- Q3 - Q1
@@
 # Filter to remove outliers
-df_no_outliers_disrup_dur <- df_aoi_disrup %>%
+df_no_outliers_disrup_dur <- df_aoi_disrup_expert %>%
   filter(Average_duration_disrup >= LowerBound & Average_duration_disrup <= UpperBound)
@@
 # Check the number of rows before and after filtering
-nrow(df_aoi_disrup)  # Original data
+nrow(df_aoi_disrup_expert)  # Original data
 nrow(df_no_outliers_disrup_dur)  # After removing outliers
@@
 # Create a dataframe with only the outliers
-df_outliers_disrup_dur <- df_aoi_disrup %>%
+df_outliers_disrup_dur_expert <- df_aoi_disrup_expert %>%
   filter(Average_duration_disrup < LowerBound | Average_duration_disrup > UpperBound)
@@
 # View the removed outliers
-df_outliers_disrup_dur
+df_outliers_disrup_dur_expert
+
+### NOVICES ###
+
+# Boxplot showing outliers
+ggplot(df_aoi_disrup_novice, aes(x = "", y = Average_duration_disrup)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "Boxplot of average duration of fixations (AOI disruptive person)",
+       y = "Average duration of fixations") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_disrup_novice$Average_duration_disrup, 0.25)
+Q3 <- quantile(df_aoi_disrup_novice$Average_duration_disrup, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_disrup_dur_nov <- df_aoi_disrup_novice %>%
+  filter(Average_duration_disrup >= LowerBound & Average_duration_disrup <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_disrup_novice)  # Original data
+nrow(df_no_outliers_disrup_dur_nov)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_disrup_dur_novice <- df_aoi_disrup_novice %>%
+  filter(Average_duration_disrup < LowerBound | Average_duration_disrup > UpperBound)
+
+# View the removed outliers
+df_outliers_disrup_dur_novice
 
@@
 dur.disrup.table <-
-  df_no_outliers_disrup_dur %>%
+  df_aoi_disrup %>%
+  filter(!Participant %in% c("216", "105", "109", "133")) %>% 
   group_by(Group) %>%
@@
 # plotting average duration on AOI Disruptive person
-df_no_outliers_disrup_dur %>% 
+df_aoi_disrup %>%
+  filter(!Participant %in% c("216", "105", "109", "133")) %>% 
   ggplot(mapping = aes(x = Group,
@@
 # AVERAGDE DURATION OF FIXATIONS on AOI disruptive person 
+# create data frame without outliers
+df_no_outliers_disrup_dur <- df_aoi_disrup %>%
+  filter(!Participant %in% c("216", "105", "109", "133"))
+
 # t-test for expertise differences
@@
 
-# filter group, participants, total duration & number fixation in entire micro-teaching unit
+# GRI = Average_duration_mtu / Sum_number_fixation
+
+######## Statistical Methods for Outlier Detection
+
+### EXPERTS ###
+# filter only for experts
+df_gri_expert <- df_aoi_sum %>% 
+  filter(Group == "Expert")
+
+# Boxplot showing outliers
+ggplot(df_gri_expert, aes(x = "", y = Average_duration_mtu)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "EXPERT: Boxplot average duration (mtu)",
+       y = "Mean duration of fixations/\nmean number of fixations") +
+  theme_minimal()
+
+# Boxplot showing outliers
+ggplot(df_gri_expert, aes(x = "", y = Sum_number_fixation)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "EXPERT: Boxplot of summarized number of fixations (mtu)",
+       y = "Mean duration of fixations/\nmean number of fixations") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_gri_expert$Sum_number_fixation, 0.25)
+Q3 <- quantile(df_gri_expert$Sum_number_fixation, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_gri_expert <- df_gri_expert %>%
+  filter(Sum_number_fixation >= LowerBound & Sum_number_fixation <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_gri_expert)  # Original data
+nrow(df_no_outliers_gri_expert)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_gri_expert <- df_gri_expert %>%
+  filter(Sum_number_fixation < LowerBound | Sum_number_fixation > UpperBound)
+
+# View the removed outliers
+df_outliers_gri_expert
+
+### NOVICES ###
+# filter only for novices
+df_gri_novice <- df_aoi_sum %>% 
+  filter(Group == "Novice")
+
+# Boxplot showing outliers
+ggplot(df_gri_novice, aes(x = "", y = Average_duration_mtu)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "NOVICE: Boxplot average duration (mtu)",
+       y = "Mean duration of fixations/\nmean number of fixations") +
+  theme_minimal()
+
+# Boxplot showing outliers
+ggplot(df_gri_novice, aes(x = "", y = Sum_number_fixation)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "NOVICE: Boxplot of summarized number of fixations (mtu)",
+       y = "Mean duration of fixations/\nmean number of fixations") +
+  theme_minimal()
+
+# calculate GRI without outliers
 df_aoi_sum %>%
+  filter(!Participant == "205") %>% 
   group_by(Group) %>% 
@@
     GRI = round(Average_duration_mtu / Sum_number_fixation, digits = 2),
-    )-> df_gri
-
-######## Statistical Methods for Outlier Detection
-
-# Boxplot showing outliers
-ggplot(df_gri, aes(x = "", y = GRI)) + 
-  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of the Gaze Relational Index",
-       y = "Mean duration of fixations/\nmean number of fixations") +
-  theme_minimal()
-
-# Calculate the IQR and bounds
-Q1 <- quantile(df_gri$GRI, 0.25)
-Q3 <- quantile(df_gri$GRI, 0.75)
-IQR <- Q3 - Q1
-
-LowerBound <- Q1 - 1.5 * IQR
-UpperBound <- Q3 + 1.5 * IQR
-
-# Filter to remove outliers
-df_no_outliers_gri <- df_gri %>%
-  filter(GRI >= LowerBound & GRI <= UpperBound)
-
-# Check the number of rows before and after filtering
-nrow(df_gri)  # Original data
-nrow(df_no_outliers_gri)  # After removing outliers
-
-# Create a dataframe with only the outliers
-df_outliers_gri <- df_gri %>%
-  filter(GRI < LowerBound | GRI > UpperBound)
-
-# View the removed outliers
-df_outliers_gri
+    )-> df_no_outliers_gri
 
@@
 
+### EXPERTS ###
+
+# filter only for experts
+df_ttff_disrup_expert <- df_ttff_disrup %>% 
+  filter(Group == "Expert")
+
 # Boxplot showing outliers
-ggplot(df_ttff_disrup, aes(x = "", y = Disrup_time_fixation_sec)) + 
+ggplot(df_ttff_disrup_expert, aes(x = "", y = Disrup_time_fixation_sec)) + 
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of time to first fixation in seconds (AOI disruptive person)",
+  labs(title = "EXPERTS: Boxplot of time to first fixation in seconds (AOI disruptive person)",
        y = "Time to first fixation in seconds") +
@@
 # Calculate the IQR and bounds
-Q1 <- quantile(df_ttff_disrup$Disrup_time_fixation_sec, 0.25)
-Q3 <- quantile(df_ttff_disrup$Disrup_time_fixation_sec, 0.75)
+Q1 <- quantile(df_ttff_disrup_expert$Disrup_time_fixation_sec, 0.25)
+Q3 <- quantile(df_ttff_disrup_expert$Disrup_time_fixation_sec, 0.75)
 IQR <- Q3 - Q1
@@
 # Filter to remove outliers
-df_no_outliers_ttff <- df_ttff_disrup %>%
+df_no_outliers_ttff_expert <- df_ttff_disrup_expert %>%
   filter(Disrup_time_fixation_sec >= LowerBound & Disrup_time_fixation_sec <= UpperBound)
@@
 # Check the number of rows before and after filtering
-nrow(df_ttff_disrup)  # Original data
-nrow(df_no_outliers_ttff)  # After removing outliers
+nrow(df_ttff_disrup_expert)  # Original data
+nrow(df_no_outliers_ttff_expert)  # After removing outliers
 
 # Create a dataframe with only the outliers
-df_outliers_ttff <- df_ttff_disrup %>%
+df_outliers_ttff_expert <- df_ttff_disrup_expert %>%
   filter(Disrup_time_fixation_sec < LowerBound | Disrup_time_fixation_sec > UpperBound)
@@
 # View the removed outliers
-df_outliers_ttff
+df_outliers_ttff_expert
+
+### NOVICES ###
+
+  # filter only for novice
+df_ttff_disrup_novice <- df_ttff_disrup %>% 
+  filter(Group == "Novice")
+
+# Boxplot showing outliers
+ggplot(df_ttff_disrup_novice, aes(x = "", y = Disrup_time_fixation_sec)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "NOVICE: Boxplot of time to first fixation in seconds (AOI disruptive person)",
+       y = "Time to first fixation in seconds") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_ttff_disrup_novice$Disrup_time_fixation_sec, 0.25)
+Q3 <- quantile(df_ttff_disrup_novice$Disrup_time_fixation_sec, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_ttff_novice <- df_ttff_disrup_novice %>%
+  filter(Disrup_time_fixation_sec >= LowerBound & Disrup_time_fixation_sec <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_ttff_disrup_novice)  # Original data
+nrow(df_no_outliers_ttff_novice)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_ttff_novice <- df_ttff_disrup_novice %>%
+  filter(Disrup_time_fixation_sec < LowerBound | Disrup_time_fixation_sec > UpperBound)
+
+# View the removed outliers
+df_outliers_ttff_novice
 
@@
 ttff.disrup.table <-
-  df_no_outliers_ttff %>%
+  df_ttff_disrup %>%
+  filter(!Participant %in% c("216", "113", "123")) %>% 
   group_by(Group) %>%
@@
 number.perceived.disrup.table <-
-  df_no_outliers_ttff %>%
+ df_ttff_disrup %>%
+  filter(!Participant %in% c("216", "113", "123")) %>%
   group_by(Group) %>%
@@
 plot_n_disrup <- 
-  ggplot(data = df_no_outliers_ttff,
-         mapping = aes(x = Group,
+  df_ttff_disrup %>%
+  filter(!Participant %in% c("216", "113", "123")) %>%
+  ggplot(mapping = aes(x = Group,
                        y = N)) +
@@
 plot_time_disrup <- 
-  ggplot(data = df_no_outliers_ttff,
-         mapping = aes(x = Group,
+  df_ttff_disrup %>%
+  filter(!Participant %in% c("216", "113", "123")) %>%
+  ggplot(mapping = aes(x = Group,
                        y = Disrup_time_fixation_sec)) +
@@
                                         height = 0.1)) +
-  ylim(0,12) +
+  ylim(0,10) +
   labs(x ="",
@@
 # TIME TO FIRST FIXATIONS on disruptive person 
+# create data frame without outliers
+df_no_outliers_ttff <- 
+  df_ttff_disrup %>%
+  filter(!Participant %in% c("216", "113", "123"))
+
 # t-test for expertise differences
@@
 # rename columns
-df_sjt_mean <- rename(df_sjt_mean, c("Group" = "UI06_05",
+df_sjt_mean <- rename(
+  df_sjt_mean,
+  c(
+    "Participant" = "UI06_05",
     "Monitoring" = "SJT_AL_gek",
@@
     "Rules and routines" = "SJT_R_gek",
-                           "All" = "SJT_KF_gek"))
+    "All" = "SJT_KF_gek"
+  )
+)
+
+# add a new column with expert and novice with ifelse function
+df_sjt_mean <- df_sjt_mean %>% 
+  mutate(Group = ifelse(Participant < 200, "Novice", "Expert"))
 
@@
 df_sjt_long <- df_sjt_mean %>%
-  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")
-
-# define expert and novice with ifelse function
-df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")
+  pivot_longer(cols = c(Monitoring, `Managing momentum`, `Rules and routines`, All),
+               names_to = "Facets Classroom Management", 
+               values_to = "Mean")
+
+######## Statistical Methods for Outlier Detection
+
+### OVERALL SCORE (All)
+
+### EXPERTS ###
+
+# filter only for experts
+df_sjt_mean_expert <- df_sjt_mean %>% 
+  filter(Group == "Expert")
+
+# Boxplot showing outliers (All)
+ggplot(df_sjt_mean_expert, aes(x = "", y = All)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "EXPERT: Boxplot of SJT (All)",
+       y = "Overall score") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_sjt_mean_expert$All, 0.25)
+Q3 <- quantile(df_sjt_mean_expert$All, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_sjt_all_expert <- df_sjt_mean_expert %>%
+  filter(All >= LowerBound & All <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_sjt_mean_expert)  # Original data
+nrow(df_no_outliers_sjt_all_expert)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_sjt_all_expert <- df_sjt_mean_expert %>%
+  filter(All < LowerBound | All > UpperBound)
+
+# View the removed outliers
+df_outliers_sjt_all_expert
+
+### NOVICES ###
+
+# filter only for experts
+df_sjt_mean_novice <- df_sjt_mean %>% 
+  filter(Group == "Novice")
+
+# Boxplot showing outliers (All)
+ggplot(df_sjt_mean_novice, aes(x = "", y = All)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "NOVICE: Boxplot of SJT (All)",
+       y = "Overall score") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_sjt_mean_novice$All, 0.25)
+Q3 <- quantile(df_sjt_mean_novice$All, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_sjt_all_novice <- df_sjt_mean_novice %>%
+  filter(All >= LowerBound & All <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_sjt_mean_novice)  # Original data
+nrow(df_no_outliers_sjt_all_novice)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_sjt_all_novice <- df_sjt_mean_novice %>%
+  filter(All < LowerBound | All > UpperBound)
+
+# View the removed outliers
+df_outliers_sjt_all_novice
+
+### MANAGING MOMENTUM
+
+### EXPERTS ###
+
+# Boxplot showing outliers (MANAGING MOMENTUM)
+ggplot(df_sjt_mean_expert, aes(x = "", y = `Managing momentum`)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "EXPERTS: Boxplot of SJT (Managing Momentum)",
+       y = "Score") +
+  theme_minimal()
+
+### NOVICES ###
+
+# Boxplot showing outliers (MANAGING MOMENTUM)
+ggplot(df_sjt_mean_novice, aes(x = "", y = `Managing momentum`)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "NOVICES: Boxplot of SJT (Managing Momentum)",
+       y = "Score") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_sjt_mean_novice$`Managing momentum`, 0.25)
+Q3 <- quantile(df_sjt_mean_novice$`Managing momentum`, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_sjt_mm_novice <- df_sjt_mean_novice %>%
+  filter(`Managing momentum` >= LowerBound & `Managing momentum` <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_sjt_mean_novice)  # Original data
+nrow(df_no_outliers_sjt_mm_novice)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_sjt_mm_novice <- df_sjt_mean_novice %>%
+  filter(`Managing momentum` < LowerBound | `Managing momentum` > UpperBound)
+
+# View the removed outliers
+df_outliers_sjt_mm_novice
+
+### MONITORING
+
+### EXPERTS ###
+
+# Boxplot showing outliers (MONITORING)
+ggplot(df_sjt_mean_expert, aes(x = "", y = Monitoring)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "EXPERTS: Boxplot of SJT (Monitoring)",
+       y = "Score") +
+  theme_minimal()
+
+### NOVICES ###
+
+# Boxplot showing outliers (MONITORING)
+ggplot(df_sjt_mean_novice, aes(x = "", y = Monitoring)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "NOVICES: Boxplot of SJT (Monitoring)",
+       y = "Score") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_sjt_mean_novice$Monitoring, 0.25)
+Q3 <- quantile(df_sjt_mean_novice$Monitoring, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_sjt_novice_m <- df_sjt_mean_novice %>%
+  filter(Monitoring >= LowerBound & Monitoring <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_sjt_mean_novice)  # Original data
+nrow(df_no_outliers_sjt_novice_m)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_sjt_novice_m <- df_sjt_mean_novice %>%
+  filter(Monitoring < LowerBound | Monitoring > UpperBound)
+
+# View the removed outliers
+df_outliers_sjt_novice_m
+
+### RULES & ROUTINES
+
+### EXPERTS ###
+
+# Boxplot showing outliers (RULES & ROUTINES)
+ggplot(df_sjt_mean_expert, aes(x = "", y = `Rules and routines`)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "EXPERTS: Boxplot of SJT (Rules & routines)",
+       y = "Score") +
+  theme_minimal()
+
+### NOVICES ###
+
+# Boxplot showing outliers (RULES & ROUTINES)
+ggplot(df_sjt_mean_novice, aes(x = "", y = `Rules and routines`)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "NOVICES: Boxplot of SJT (Rules & routines)",
+       y = "Score") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_sjt_mean_novice$`Rules and routines`, 0.25)
+Q3 <- quantile(df_sjt_mean_novice$`Rules and routines`, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_sjt_novice_r <- df_sjt_mean_novice %>%
+  filter(`Rules and routines` >= LowerBound & `Rules and routines` <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_sjt_mean_novice)  # Original data
+nrow(df_no_outliers_sjt_novice_r)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_sjt_novice_r <- df_sjt_mean_novice %>%
+  filter(`Rules and routines` < LowerBound | `Rules and routines` > UpperBound)
+
+# View the removed outliers
+df_outliers_sjt_novice_r
 
@@
 sjt_mean <- df_sjt_long %>%
+  filter(!Participant %in% c("216", "217", "127")) %>% 
   filter(`Facets Classroom Management` == "All") %>%
@@
 sjt_mm <- df_sjt_long %>%
+  filter(!Participant %in% c("105", "127")) %>% 
   filter(`Facets Classroom Management` == "Managing momentum") %>%
@@
 sjt_m <- df_sjt_long %>%
+  filter(!Participant %in% c("121", "127", "137")) %>% 
   filter(`Facets Classroom Management` == "Monitoring") %>%
@@
 sjt_r <- df_sjt_long %>%
+  filter(!Participant %in% c("127")) %>% 
   filter(`Facets Classroom Management` == "Rules and routines") %>%
@@
 df_sjt_long %>% 
+  filter(!Participant %in% c("216", 
+                             "217", 
+                             "127",
+                             "105",
+                             "121",
+                             "137")) %>% 
   mutate(Group = factor(Group,
@@
 
-# define expert and novice with ifelse function in wide format
-df_sjt_mean$Group = ifelse(df_sjt_mean$Group < 200, "Novice","Expert")
-
 #### ALL #### 
+# create data frame without outliers
+df_sjt_mean_all_no_out <- df_sjt_mean %>% 
+  filter(!Participant %in% c("216", "217", "127"))
+
 # t-test for expertise differences 
-t.test(x = df_sjt_mean$All[df_sjt_mean$Group == "Expert"],
-       y = df_sjt_mean$All[df_sjt_mean$Group == "Novice"],
+t.test(x = df_sjt_mean_all_no_out$All[df_sjt_mean_all_no_out$Group == "Expert"],
+       y = df_sjt_mean_all_no_out$All[df_sjt_mean_all_no_out$Group == "Novice"],
        var.equal = TRUE)
@@
 # effect size for expertise differences
-d_sjt_all <- CohenD(x = df_sjt_mean$All[df_sjt_mean$Group == "Expert"],
-                    y = df_sjt_mean$All[df_sjt_mean$Group == "Novice"],
+d_sjt_all <- CohenD(x = df_sjt_mean_all_no_out$All[df_sjt_mean_all_no_out$Group == "Expert"],
+                    y = df_sjt_mean_all_no_out$All[df_sjt_mean_all_no_out$Group == "Novice"],
                     na.rm = TRUE

### 2024-09-25 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
nochmal quasi final

@@
 However, previous studies have often relied on expensive and obtrusive electrocardiographs (ECG).
-Modern fitness trackers represent a non-invasive and convenient alternative.
-[@ferguson2015]
+Modern fitness trackers represent a non-invasive and convenient alternative [@ferguson2015].
 
@@
 Physiologically, HR is regulated by the sympathetic and parasympathetic nervous systems [@pham2021].
-An increase in sympathetic activity results in HR being sped up (“fight or flight” response) [@taelman2009influence]; whereas an increase in parasympathetic activity results in HR being slowed down (“rest and digest” response) [@battipaglia2015].
+An increase in sympathetic activity results in HR being sped up (“fight or flight” response) [@taelman2009influence]; whereas an increase in parasympathetic activity results in HR being slowed down (“rest and digest” response, @battipaglia2015).
 Stress or mental and physical strain directly increases HR [@custodis2014heart; @sachs2014].
@@
 
+Figure \ref{fig.1} shows, in a simplified way, how classroom events affect teachers’ stress level, according to the adaptation of the Lazarus model to teacher stress proposed by @van2006stress: When potential stressors (e.g., classroom disruptions) occur during teaching (1), teachers intuitively judge how disruptive the event is in a primary appraisal (2).
+If potential stressors are judged as threatening, i.e., as actual stressors (3), teachers consider whether they have sufficient resources for coping with the stressors (4).
+Teachers utilize these resources in trying to cope with the stressors, e.g., by employing classroom management strategies (5).
+In cases when coping fails, stress ensues, often accompanied by physiological reactions like increased HR (6).
+As part of the coping process, and dependent on its outcomes, teachers re-evaluate the stressor (7).
+
+As shown in Figure \ref{fig.1}, teachers’ primary and secondary appraisal as well as coping attempts are influenced by professional experience.
+As professional experience grows, teachers develop cognitive scripts for managing classroom events, resulting in more complex and problem-focused classroom management skills [@wolff2021classroom], and thus more effective coping and less stress.
+Empirically, classroom management skills and problem-focused coping styles are linked to fewer instances of emotional exhaustion [@maslach2001job; @clunies2008self].
+Novices in the teaching profession, on the other hand, face considerable stress and often feel overwhelmed by the demands of teaching [@ophardt2017klassenmanagement; @wolff2015keeping; @klusmann2012berufliche] with many leaving the profession within the first five years [@ingersoll2003].
+Accordingly, when resources are lacking and coping fails, negative consequences for health (e.g., burnout) and for work (e.g., high turnover rates) can arise [@jalongo2006; @unterbrink2007; @aloe2014multivariate], highlighting the importance of professional expertise for managing teacher stress [@fisher2011].
+
 ```{=latex}
@@
     labelfont=bf,       % Figure label bold (not italic)
-    parskip=12pt,
     labelsep=newline,      % Period after Figure label
@@
     labelfont=bf,        % Figure label bold (not italic)
-    parskip=12pt,
     labelsep=newline,      % Period after Figure label
@@
 \begin{figure}[htbp]
-  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
+  \caption{\\
+  A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
   \centering
@@
 ```
-
-Fig.
-1 shows, in a simplified way, how classroom events affect teachers’ stress level, according to the adaptation of the Lazarus model to teacher stress proposed by @van2006stress: When potential stressors (e.g., classroom disruptions) occur during teaching (1), teachers intuitively judge how disruptive the event is in a primary appraisal (2).
-If potential stressors are judged as threatening, i.e., as actual stressors (3), teachers consider whether they have sufficient resources for coping with the stressors (4).
-Teachers utilize these resources in trying to cope with the stressors, e.g., by employing classroom management strategies (5).
-In cases when coping fails, stress ensues, often accompanied by physiological reactions like increased HR (6).
-As part of the coping process, and dependent on its outcomes, teachers re-evaluate the stressor (7).
-
-As shown in Fig.
-1, teachers’ primary and secondary appraisal as well as coping attempts are influenced by professional experience.
-As professional experience grows, teachers develop cognitive scripts for managing classroom events, resulting in more complex and problem-focused classroom management skills [@wolff2021classroom], and thus more effective coping and less stress.
-Empirically, classroom management skills and problem-focused coping styles are linked to fewer instances of emotional exhaustion [@maslach2001job; @clunies2008self].
-Novices in the teaching profession, on the other hand, face considerable stress and often feel overwhelmed by the demands of teaching [@ophardt2017klassenmanagement; @wolff2015keeping; @klusmann2012berufliche] with many leaving the profession within the first five years [@ingersoll2003].
-Accordingly, when resources are lacking and coping fails, negative consequences for health (e.g., burnout) and for work (e.g., high turnover rates) can arise [@jalongo2006; @unterbrink2007; @aloe2014multivariate], highlighting the importance of professional expertise for managing teacher stress [@fisher2011].
 
@@
 In addition, we examined the relations between teachers’ subjective appraisals of the classroom events (specifically, the disruptiveness of the events, and their confidence in dealing with them) and teachers’ HR level, beyond the explanatory power of teaching experience.
-We expected higher HR levels for teachers who felt more disrupted, regardless of their teaching experience (**Hypotheses 2b**), and lower HR levels for teachers who felt more confident, regardless of teaching experience (**Hypothesis 2c**).
+We expected higher HR levels for teachers who felt more disrupted, regardless of their teaching experience (**Hypothesis 2b**), and lower HR levels for teachers who felt more confident, regardless of teaching experience (**Hypothesis 2c**).
 We hypothesized that each of the three predictors (*teaching experience, disruption appraisal, confidence appraisal*) uniquely contributed to explaining variance in teachers’ HR levels (**Hypothesis 2d**).
@@
 
-Each participant came to the lab for a period of approximately two hours in total, and each participant underwent the same phases (see Fig.
-2): In the *pre-teaching phase*, the experimenter welcomed the participants and helped them put on the fitness tracker.
+Each participant came to the lab for a period of approximately two hours in total, and each participant underwent the same phases (see Figure \ref{fig.2}): In the *pre-teaching phase*, the experimenter welcomed the participants and helped them put on the fitness tracker.
 This was followed by a warm-up session to familiarize the participants with the laboratory setting and the class.
@@
 While teaching, participants wore eye-tracking glasses, and their lesson was video-recorded.
-After having completed the micro-teaching unit, in the *post-teaching phase*, participants filled in questionnaires for approximately 10-15 minutes: a brief computer-based survey of sociodemographic data (e.g., teaching experience, gender, studied school type, studied school subjects, extracurricular teaching activities), and a short knowledge test that was irrelevant to the
-present study. In the *interview phase*,
+After having completed the micro-teaching unit, in the *post-teaching phase*, participants filled in questionnaires for approximately 10-15 minutes: a brief computer-based survey of sociodemographic
 ```{=latex}
-\begin{wrapfigure}{r}{0.5\textwidth}
+\begin{wrapfigure}[36]{r}{0.5\textwidth}
   \centering
-  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
+  \caption{\\
+  Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
   \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
@@
 ```
-\noindent
+\noindent data (e.g., teaching experience, gender, studied school type, studied school subjects, extracurricular teaching activities), and a short knowledge test that was irrelevant to the present study.
+In the *interview phase*,
 participants engaged in a Stimulated Recall Interview (SRI).
@@
 Please note: HR levels and changes were not regressed on the disruption and confidence appraisals in the *pre-teaching interval* ($I_1$), because the appraised classroom events had not yet taken place in that phase.
+
+# Results
+
+## Mapping teachers’ HR over the course of the study phases
+
+Means, standard deviations, and range of teachers’ unstandardized and standardized HR for the entire study period, and for the five intervals, are shown in Table \ref{tab_1}.
+Figure \ref{fig.3} displays the unstandardized and standardized HR trends, respectively, over the course of the entire study period.
+HR initially increased, peaked, and then decreased, with the unstandardized and standardized HR graphs showing high similarity.
+Thus, for all further analyses, we used participants’ standardized HR values.
+
+Figure \ref{fig.4} shows the distribution of teachers’ mean standardized HR for the five intervals.
+Repeated measures ANOVA revealed significant differences in mean standardized HR between intervals, $F(4, 400) = 260.62$, $p < .05$, $d = 1.60$ (large effect).
+Planned contrasts indicated that, as hypothesized (Hypothesis 1a), mean standardized HR was significantly higher in the *teaching interval* ($I_2$) than in all other intervals, specifically, the *pre-teaching interval* ($I_1$; $t(400) = -10.08$, $p < .05$, $d = 1.034$; large effect), the post-teaching interval ($I_3$; $t(400) = -6.94$, $p < .05$, $d = 1.37$; large effect), the interview interval ($I_4$; $t(400) = 15.00$, $p < .05$, $d = 3.29$; large effect), and the end interval ($I_5$); $t(400) = 22.54$, $p < .05$, $d = 4.64$; large effect).
+
+Next, we examined HR changes (i.e., mean slopes) within each interval to test the hypothesis that HR increased during the *pre-teaching phase* and decreased during all other phases (Hypothesis 1b).
+The mean intercepts and mean slopes, complemented by their standard deviations for each interval, are shown in Table 2.
+The mean slope of the *pre-teaching interval* ($I_1$) was significantly positive, indicating an increase in HR, as hypothesized.
+Further, the mean slopes of the *teaching interval* ($I_2$), *post-teaching interval* ($I_3$), and *interview interval* ($I_4$) were significantly negative, indicating a decrease in HR.
+For the last interval, the *end interval* ($I_5$), the mean slope was negative, but did not differ significantly from zero.
 
@@
 ```
-# Results
 
@@
     \centering
-    \caption{Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
+    \caption{\\
+    Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
     \begin{tabularx}{\textwidth}{lXXXXX}
@@
   \centering
-  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
+  \caption{\\
+  Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
   \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
@@
 
-## Mapping teachers’ HR over the course of the study phases
-
-Means, standard deviations, and range of teachers’ unstandardized and standardized HR for the entire study period, and for the five intervals, are shown in Table \ref{tab_1}.
-Figure \ref{fig.3} displays the unstandardized and standardized HR trends, respectively, over the course of the entire study period.
-HR initially increased, peaked, and then decreased, with the unstandardized and standardized HR graphs showing high similarity.
-Thus, for all further analyses, we used participants’ standardized HR values.
-
-Figure \ref{fig.4} shows the distribution of teachers’ mean standardized HR for the five intervals.
-Repeated measures ANOVA revealed significant differences in mean standardized HR between intervals, $F(4, 400) = 260.62$, $p < .05$, $d = 1.60$ (large effect).
-Planned contrasts indicated that, as hypothesized (Hypothesis 1a), mean standardized HR was significantly higher in the *teaching interval* ($I_2$) than in all other intervals, specifically, the *pre-teaching interval* ($I_1$; $t(400) = -10.08$, $p < .05$, $d = 1.034$; large effect), the post-teaching interval ($I_3$; $t(400) = -6.94$, $p < .05$, $d = 1.37$; large effect), the interview interval ($I_4$; $t(400) = 15.00$, $p < .05$, $d = 3.29$; large effect), and the end interval ($I_5$); $t(400) = 22.54$, $p < .05$, $d = 4.64$; large effect).
+```{r table_2, include=FALSE}
+df_regression <- 
+  main_single_hr |> 
+  filter(time_span != "overall") |> 
+  dplyr::select("ID",
+                "time_span",
+                "time",
+                "heart_rate_std",
+                "heart_rate") |> 
+  distinct() |> 
+  mutate(time = time / 60) |> 
+  mutate(ID = as_factor(ID),
+         Phase = factor(time_span,
+                        levels = c("preparation",
+                                   "teaching",
+                                   "post",
+                                   "interview",
+                                   "end"),
+                        labels = c("Pre Teaching Phase",
+                                   "Teaching Phase",
+                                   "Post Teaching Phase",
+                                   "Interview Phase",
+                                   "End Phase")
+                           )
+         )
+
+fix_models <-
+  df_regression %>%
+  split(.$Phase) %>%
+  map( ~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
+            data = .)) %>%
+  map(
+    ~ coef(.) %>%
+      tibble::as_tibble(.,
+                        rownames = "name") %>%
+      transmute(
+        type = if_else(str_detect(name,
+                                  ":"),
+                       true = "slope",
+                       false = "intercept"),
+        id = str_remove_all(name,
+                            "[^[:digit:]]"),
+        value = value
+      ),
+
+  ) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_wider(names_from = type,
+              values_from = value)
+
+p.values_slope <-
+  fix_models %>%
+  split(.$Phase) %>%
+  map( ~ t.test(x = .$slope,
+                mu = 0)$p.value) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_slope")
+
+p.values_intercept <-
+  fix_models %>%
+  split(.$Phase) %>%
+  map( ~ t.test(x = .$intercept,
+                mu = 0)$p.value) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_intercept")
+
+sd_mean <-
+  fix_models %>%
+  group_by(Phase) %>%
+  dplyr::summarise(
+    mean_slope = mean(slope),
+    sd_slope = sd(slope),
+    mean_intercept = mean(intercept),
+    sd_intercept = sd(intercept)
+  )
+
+table_data <- 
+  right_join(x = sd_mean,
+             y = p.values_intercept,
+             by = "Phase") %>% 
+  right_join(x = .,
+             y = p.values_slope,
+             by = "Phase") %>% 
+  transmute(Phase = factor(Phase,
+                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
+                           ),
+            n = NA,
+            `Mean(Intercept)` = round(mean_intercept, digits = 3),
+            `SD(Intercept)` = round(sd_intercept, digits = 3),
+            `p-Value (Intercept)` = p.value_intercept,
+            `Mean(Slope)` = round(mean_slope, digits = 3), 
+            `SD(Slope)` = round(sd_slope,digits = 3),
+            `p-Value (Slope)` = p.value_slope, 
+            ) %>% 
+  arrange(Phase)
+
+table_data$n[table_data$Phase == "Pre Teaching Phase"] <- df_regression %>% filter(Phase == "Pre Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Teaching Phase"] <- df_regression %>% filter(Phase == "Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Post Teaching Phase"] <- df_regression %>% filter(Phase == "Post Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Interview Phase"] <- df_regression %>% filter(Phase == "Interview Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "End Phase"] <- df_regression %>% filter(Phase == "End Phase") %>% pull(heart_rate_std) %>% length()
+```
+
+```{=latex}
+
+\renewcommand{\arraystretch}{1.5}
+
+\begin{table}[ht]
+    \centering
+    \caption{\\
+    Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
+    \begin{tabularx}{\textwidth}{lXXXXXX}
+        \toprule
+        Interval  & \multicolumn{2}{c}{M (SD)} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
+        \midrule
+        (1) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
+        (2) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
+        (3) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
+        (4) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
+        (5) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
+        \bottomrule
+    \end{tabularx}
+    \label{tab_2}
+\end{table}
+
+```
 
@@
   \centering
-  \caption{Distribution of the standardized heart rate means in the five intervals}
+  \caption{\\
+  Distribution of the standardized heart rate means in the five intervals}
   \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
@@
 \end{figure}
-```
-
-```{r table_2, include=FALSE}
-df_regression <- 
-  main_single_hr |> 
-  filter(time_span != "overall") |> 
-  dplyr::select("ID",
-                "time_span",
-                "time",
-                "heart_rate_std",
-                "heart_rate") |> 
-  distinct() |> 
-  mutate(time = time / 60) |> 
-  mutate(ID = as_factor(ID),
-         Phase = factor(time_span,
-                        levels = c("preparation",
-                                   "teaching",
-                                   "post",
-                                   "interview",
-                                   "end"),
-                        labels = c("Pre Teaching Phase",
-                                   "Teaching Phase",
-                                   "Post Teaching Phase",
-                                   "Interview Phase",
-                                   "End Phase")
-                           )
-         )
-
-fix_models <-
-  df_regression %>%
-  split(.$Phase) %>%
-  map( ~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
-            data = .)) %>%
-  map(
-    ~ coef(.) %>%
-      tibble::as_tibble(.,
-                        rownames = "name") %>%
-      transmute(
-        type = if_else(str_detect(name,
-                                  ":"),
-                       true = "slope",
-                       false = "intercept"),
-        id = str_remove_all(name,
-                            "[^[:digit:]]"),
-        value = value
-      ),
-
-  ) %>%
-  bind_rows(.id = "Phase") %>%
-  pivot_wider(names_from = type,
-              values_from = value)
-
-p.values_slope <-
-  fix_models %>%
-  split(.$Phase) %>%
-  map( ~ t.test(x = .$slope,
-                mu = 0)$p.value) %>%
-  bind_rows(.id = "Phase") %>%
-  pivot_longer(cols = everything(),
-               names_to = "Phase",
-               values_to = "p.value_slope")
-
-p.values_intercept <-
-  fix_models %>%
-  split(.$Phase) %>%
-  map( ~ t.test(x = .$intercept,
-                mu = 0)$p.value) %>%
-  bind_rows(.id = "Phase") %>%
-  pivot_longer(cols = everything(),
-               names_to = "Phase",
-               values_to = "p.value_intercept")
-
-sd_mean <-
-  fix_models %>%
-  group_by(Phase) %>%
-  dplyr::summarise(
-    mean_slope = mean(slope),
-    sd_slope = sd(slope),
-    mean_intercept = mean(intercept),
-    sd_intercept = sd(intercept)
-  )
-
-table_data <- 
-  right_join(x = sd_mean,
-             y = p.values_intercept,
-             by = "Phase") %>% 
-  right_join(x = .,
-             y = p.values_slope,
-             by = "Phase") %>% 
-  transmute(Phase = factor(Phase,
-                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
-                           ),
-            n = NA,
-            `Mean(Intercept)` = round(mean_intercept, digits = 3),
-            `SD(Intercept)` = round(sd_intercept, digits = 3),
-            `p-Value (Intercept)` = p.value_intercept,
-            `Mean(Slope)` = round(mean_slope, digits = 3), 
-            `SD(Slope)` = round(sd_slope,digits = 3),
-            `p-Value (Slope)` = p.value_slope, 
-            ) %>% 
-  arrange(Phase)
-
-table_data$n[table_data$Phase == "Pre Teaching Phase"] <- df_regression %>% filter(Phase == "Pre Teaching Phase") %>% pull(heart_rate_std) %>% length()
-table_data$n[table_data$Phase == "Teaching Phase"] <- df_regression %>% filter(Phase == "Teaching Phase") %>% pull(heart_rate_std) %>% length()
-table_data$n[table_data$Phase == "Post Teaching Phase"] <- df_regression %>% filter(Phase == "Post Teaching Phase") %>% pull(heart_rate_std) %>% length()
-table_data$n[table_data$Phase == "Interview Phase"] <- df_regression %>% filter(Phase == "Interview Phase") %>% pull(heart_rate_std) %>% length()
-table_data$n[table_data$Phase == "End Phase"] <- df_regression %>% filter(Phase == "End Phase") %>% pull(heart_rate_std) %>% length()
-```
-
-Next, we examined HR changes (i.e., mean slopes) within each interval to test the hypothesis that HR increased during the *pre-teaching phase* and decreased during all other phases (Hypothesis 1b).
-The mean intercepts and mean slopes, complemented by their standard deviations for each interval, are shown in Table 2.
-The mean slope of the *pre-teaching interval* ($I_1$) was significantly positive, indicating an increase in HR, as hypothesized.
-Further, the mean slopes of the *teaching interval* ($I_2$), *post-teaching interval* ($I_3$), and *interview interval* ($I_4$) were significantly negative, indicating a decrease in HR.
-For the last interval, the *end interval* ($I_5$), the mean slope was negative, but did not differ significantly from zero.
-
-```{=latex}
-
-\renewcommand{\arraystretch}{1.5}
-
-\begin{table}[ht]
-    \centering
-    \caption{Analysis (\textit{M, SD, p-values}) for the mean intercepts and the mean slopes for the five intervals.}
-    \begin{tabularx}{\textwidth}{lXXXXXX}
-        \toprule
-        Interval  & \multicolumn{2}{c}{M (SD)} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
-        \midrule
-        (1) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
-        (2) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
-        (3) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
-        (4) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
-        (5) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
-        \bottomrule
-    \end{tabularx}
-    \label{tab_2}
-\end{table}
-
 ```
@@
     \centering
-    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
+    \caption{\\
+    Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
     \begin{tabularx}{\textwidth}{lccccc}
@@
 
+\newpage
+
 Concerning the explorative investigation of the effects of teaching experience and subjective appraisals on *changes* (i.e., mean slopes) in teachers’ HR, teaching experience significantly predicted the mean slope in the *pre-teaching interval* (Table 4, Pre-teaching interval, Model 1), indicating a less steep HR increase in teachers with more teaching experience.
 For all other intervals, no variable had significant predictive value.
+
+# Discussion
+
+## Key findings
+
+Overall, our findings indicate that wrist-worn fitness trackers are a useful tool for tracking teachers’ HR and identifying stressful periods during teaching.
+Using HR data from a commercially available and relatively low-cost Fitbit® fitness tracker, we were able to map teachers’ HR before, during, and after a stressful micro-teaching unit, with HR increasing in preparation for teaching, peaking during the teaching phase, and decreasing afterward.
+
+These findings are in line with prior studies showing that teachers’ HR varies depending on their activities and encountered stressors with increases during phases where teachers are in an exposed position [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021], as well as with findings showing how HR changes align with activating events and stress-inducing tasks [@Darnell2019; @chalmers2021].
+
+Building on the model of teacher stress [@kyriacou1978, see Fig.
+2], we had hypothesized that more experienced teachers, with better classroom management skills at their disposal, experience less physiological stress when dealing with classroom disruptions.
+Contrary to our expectations, we found no buffering effect of teaching experience on teachers’ HR, i.e., more experienced teachers did not show lower mean standardized HR during the stressful teaching phase than less experienced teachers.
+Rather, at least descriptively, we observed the opposite trend.
+There are several possible explanations for this finding.
+First, teaching experience is inherently confounded with age (the two variables correlated at $r = .94$ in our sample), and age has been shown to affect indicators of cardiovascular reactivity in various ways [@uchino2010older].
+However, to avoid this kind of confounding influence, we had used not raw BPM but rather standardized mean HR for all our analyses, thus controlling at least for inter-individual differences in mean HR.
+Second, as research on teacher professionalization has repeatedly shown, professional experience is not a guarantee for higher professional knowledge and skills [@kirschner2016professionswissen].
+Rather, honing skills from professional experience necessitates a deliberate practice of choosing to improve, learning through experience, and integrating new knowledge into future performances [@dunn1999deliberate].
+Thus, rather than professional experience alone, more direct assessments of classroom management skills, such as objective behavior-based tests, would be a better indicator of expertise that future studies could explore.
+Finally, and most importantly, the highly controlled teaching situation that we created in the lab might not have provided sufficient resemblance to the expert teachers’ working conditions to let them effectively use their coping resources.
+In other words, since the situation was unfamiliar to both experienced and unexperienced teachers, their stress levels might have been more similar than they would have been in a more authentic classroom setting.
+
+While we did not find a buffering effect of teaching experience on mean HR during teaching, we did, however, find a less steep HR increase in more experienced, compared to less experienced teachers during the pre-teaching phase ($\beta = -.27$), i.e., in preparation for the micro-teaching unit.
+This finding supports the idea that, even though teaching experience guarantees neither superior expertise nor stress resistance, the habits and routines formed by experienced teachers may at least lead to lower arousal levels (e.g., experienced as feeling less nervous and tense) when they anticipate potentially stressful teaching situations.
+
+An interesting observation beyond our hypotheses was that teaching experience was predictive of HR differences, not during teaching, but in the interview phase: compared to less experienced teachers, more experienced teachers showed a higher mean standardized HR ($\beta = .24$) and, thus, probably experienced higher levels of physiological stress during the SRI.
+One possible explanation for this finding could again be the higher age of the more experienced teachers, along with slower recovery from stress in older teachers.
+For instance, @ritvanen2006responses observed that, compared to their younger colleagues, older teachers did not experience a decrease in their HR during periods of low stress levels, from which they concluded that recovery from stress was insufficient in the older teachers [@ritvanen2006responses].
+Alternatively, the finding could also be attributed to the fact that less experienced teachers, due to their ongoing or only recently concluded training, may have been more accustomed to reflecting on their work and receiving feedback as was the case during the SRI, whereas, these activities were less routine and possibly more face-threatening for experienced teachers.
+Therefore, it is possible that more experienced teachers found the interview itself to be more stressful and therefore showed a higher mean standardized HR during this phase.
+
+With regards to the predictive power of teachers’ subjective appraisals of the classroom disruption during teaching, we, first of all, have to conclude that our hypotheses were not supported, as neither confidence appraisal nor disruptiveness appraisal showed any notable correlations with teachers’ means standardized HR or any explanatory power over and beyond teaching experience.
+Possibly, teachers’ self-reported appraisals, and their actual physiological stress responses, tap into quite different phenomena, or at least, quite different aspects of the multifaceted stress response [@kyriacou1978].
+In addition, while HR was assessed online during teaching, self-reported appraisals were given in retrospect during the SRI, and may be subject to biased (e.g., self-serving) reporting or simply an inability to recall one´s immediate stress reactions.
+
+On the other hand, when controlling for all other factors, teachers who reported to have perceived the events as more disruptive showed a higher HR ($\beta = .25$) in the phase immediately following the micro-teaching unit.
+This finding would be consistent with the idea that differences in mean HR, as an indicator of the physiological stress response, can be linked to the cognitive appraisal of stressors.
+
+## Limitations and future directions
+
+While the laboratory setting of the study allowed for a controlled implementation of stressors and high internal validity, it was not an authentic classroom environment, raising questions about its external validity.
+Most importantly, the teacher and their students did not have a shared history, and only a very thin basis for establishing a positive teacher-student relationship, which is a core characteristic of effective classroom management [@ruedi2014; @beaty2010].
+In addition, the micro-teaching unit was only about 15 minutes long, and thus much shorter than a regular school lesson, providing less opportunities for experienced teachers to build up an engaging lesson.
+Finally, student behavior was scripted, with classroom disruptions following the experimental schedule, irrelevant of the behavior of the teacher.
+Thus, the setting may have masked effects of teaching experience by providing too little opportunities of experienced teachers to demonstrate their true classroom management skills, in particular regarding the prevention of disruptions.
+In subsequent studies, it would therefore be insightful to assess teachers’ HR in more authentic classroom settings over a longer period of time (e.g., days, weeks, or even months).
+Extended observation of teachers’ HR in authentic classroom settings could reveal how factors such as student behavior, teaching methods, or organizational and administrative demands contribute to fluctuations in physiological arousal, uncovering insights into the sustained physiological demands of teaching that short-term studies may overlook.
+Finally, linking actual teacher behavior to potential stressors (e.g., classroom disruptions, noise level, etc.) would offer insights into teacher coping strategies and their links with physiological indicators of stress.
+
+Another limitation concerns the assessment of teachers’ HR.
+While our results demonstrate the usefulness of drawing upon easily available HR data from ubiquitous, low-cost, un-intrusive fitness trackers to estimate teacher stress, there also are shortcomings of this type of assessment.
+First, while fitness trackers typically yield HR data, heart rate variability (HRV) has been demonstrated to be an even more accurate indicator of stress [@wettstein2020ambulatory].
+While standard fitness trackers did not provide this measure at the time of our data collection, more recent products do offer this function.
+Thus, future studies might consider assessing HRV instead of HR.
+Second, we did not record participants’ resting HR, which is generally considered an important baseline for determining inter- and intrapersonal differences in cardiovascular health and reactivity [@nanchen2018; @heneghan2019].
+A clean baseline HR requires a resting phase without physical movement or emotional stress, ideally fifteen minutes before the beginning of the activity, which is very difficult to achieve in practice [@sammito2015guideline], e.g., when assessing teacher HR before and during teaching.
+Thus, our study explored the possibility of substituting baseline HR measurement via z-standardization within participants.
+As a result, the absolute standardized values of each participant must always be interpreted in the context of the standardization sample, and thus are less interpretable than individual BPM values together with a baseline HR.
+However, for statistical analyses based on the whole sample, the standardization fulfills the aim of controlling for differences in individual HR due to, for example, age-related differences.
+Finally, depending on the brand and model of fitness trackers used, the precision of the HR measurement varies.
+Research on the reliability of our deployed Fitbit® device has proven that this brand is generally accurate in controlled settings and for moderate activity levels [@wallen2016accuracy; @hajj2023; @fuller2020; @jo2016], as in our study.
+For example, the Fitbit® fitness tracker has previously shown good HR measurement accuracy during resting phases [@jo2016; @muggeridge2021measurement] and for activities such as walking, jogging, and running [@hajj2023].
+At higher exercise intensities such as cycling, the Fitbit® tracker may underestimate HR [@thomson2019heart; @montoye2017comparative; @jo2016; @jachymek2021] but is still within an acceptable range according to systematic reviews [@chevance2022accuracy].
+Nevertheless, @gagnon2022 stressed that Fitbit® trackers cannot replace ECG when precision is paramount.
+Despite these considerations, the Fitbit® model appears suitable for our study purposes, as physical strain was moderate.
+
+Furthermore, while we assessed teachers’ appraisals of the stressful classroom disruptions using a SRI in which they could review the exact situation, these appraisal ratings were still post-hoc self-reports, which limits the interpretation of our results.
+One of the main issues with post-hoc self-reports is that they rely on the teachers’ memories and subjective interpretations of past events, which may be prone to various biases such as social desirability [@razavi2001self] or recall errors [@van2016accuracy].
+Moreover, stress is not a fixed or stable construct; it is a dynamic, constantly evolving affective response that can vary depending on context, individual disposition, and prior experiences, making it particularly challenging to pinpoint valid and reliable process markers for how individuals appraise stress in real-time [@lazarus1990theory].
+While SRIs provide a more detailed and reflective understanding of the stressor in question, the delayed nature of the response makes it difficult to capture the immediate, in-the-moment appraisal that occurs when the stressful event actually takes place.
+
+## Hands-on advice for using wrist-worn fitness trackers for research
+
+For researchers aiming to use fitness trackers to collect data, there are practical aspects to consider concerning the design, data collection, and data analysis phases of research projects [for an additional overview, see @nelson2020guidelines]:
 
@@
 
-\captionof{table}{Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
+\captionof{table}{\\
+Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
 
@@
 
-# Discussion
-
-## Key findings
-
-Overall, our findings indicate that wrist-worn fitness trackers are a useful tool for tracking teachers’ HR and identifying stressful periods during teaching.
-Using HR data from a commercially available and relatively low-cost Fitbit® fitness tracker, we were able to map teachers’ HR before, during, and after a stressful micro-teaching unit, with HR increasing in preparation for teaching, peaking during the teaching phase, and decreasing afterward.
-
-These findings are in line with prior studies showing that teachers’ HR varies depending on their activities and encountered stressors with increases during phases where teachers are in an exposed position [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021], as well as with findings showing how HR changes align with activating events and stress-inducing tasks [@Darnell2019; @chalmers2021].
-
-Building on the model of teacher stress [@kyriacou1978, see Fig.
-2], we had hypothesized that more experienced teachers, with better classroom management skills at their disposal, experience less physiological stress when dealing with classroom disruptions.
-Contrary to our expectations, we found no buffering effect of teaching experience on teachers’ HR, i.e., more experienced teachers did not show lower mean standardized HR during the stressful teaching phase than less experienced teachers.
-Rather, at least descriptively, we observed the opposite trend.
-There are several possible explanations for this finding.
-First, teaching experience is inherently confounded with age (the two variables correlated at $r = .94$ in our sample), and age has been shown to affect indicators of cardiovascular reactivity in various ways [@uchino2010older].
-However, to avoid this kind of confounding influence, we had used not raw BPM but rather standardized mean HR for all our analyses, thus controlling at least for inter-individual differences in mean HR.
-Second, as research on teacher professionalization has repeatedly shown, professional experience is not a guarantee for higher professional knowledge and skills [@kirschner2016professionswissen].
-Rather, honing skills from professional experience necessitates a deliberate practice of choosing to improve, learning through experience, and integrating new knowledge into future performances [@dunn1999deliberate].
-Thus, rather than professional experience alone, more direct assessments of classroom management skills, such as objective behavior-based tests, would be a better indicator of expertise that future studies could explore.
-Finally, and most importantly, the highly controlled teaching situation that we created in the lab might not have provided sufficient resemblance to the expert teachers’ working conditions to let them effectively use their coping resources.
-In other words, since the situation was unfamiliar to both experienced and unexperienced teachers, their stress levels might have been more similar than they would have been in a more authentic classroom setting.
-
-While we did not find a buffering effect of teaching experience on mean HR during teaching, we did, however, find a less steep HR increase in more experienced, compared to less experienced teachers during the pre-teaching phase ($\beta = -.27$), i.e., in preparation for the micro-teaching unit.
-This finding supports the idea that, even though teaching experience guarantees neither superior expertise nor stress resistance, the habits and routines formed by experienced teachers may at least lead to lower arousal levels (e.g., experienced as feeling less nervous and tense) when they anticipate potentially stressful teaching situations.
-
-An interesting observation beyond our hypotheses was that teaching experience was predictive of HR differences, not during teaching, but in the interview phase: compared to less experienced teachers, more experienced teachers showed a higher mean standardized HR ($\beta = .24$) and, thus, probably experienced higher levels of physiological stress during the SRI.
-One possible explanation for this finding could again be the higher age of the more experienced teachers, along with slower recovery from stress in older teachers.
-For instance, @ritvanen2006responses observed that, compared to their younger colleagues, older teachers did not experience a decrease in their HR during periods of low stress levels, from which they concluded that recovery from stress was insufficient in the older teachers [@ritvanen2006responses].
-Alternatively, the finding could also be attributed to the fact that less experienced teachers, due to their ongoing or only recently concluded training, may have been more accustomed to reflecting on their work and receiving feedback as was the case during the SRI, whereas, these activities were less routine and possibly more face-threatening for experienced teachers.
-Therefore, it is possible that more experienced teachers found the interview itself to be more stressful and therefore showed a higher mean standardized HR during this phase.
-
-With regards to the predictive power of teachers’ subjective appraisals of the classroom disruption during teaching, we, first of all, have to conclude that our hypotheses were not supported, as neither confidence appraisal nor disruptiveness appraisal showed any notable correlations with teachers’ means standardized HR or any explanatory power over and beyond teaching experience.
-Possibly, teachers’ self-reported appraisals, and their actual physiological stress responses, tap into quite different phenomena, or at least, quite different aspects of the multifaceted stress response [@kyriacou1978].
-In addition, while HR was assessed online during teaching, self-reported appraisals were given in retrospect during the SRI, and may be subject to biased (e.g., self-serving) reporting or simply an inability to recall one´s immediate stress reactions.
-
-On the other hand, when controlling for all other factors, teachers who reported to have perceived the events as more disruptive showed a higher HR ($\beta = .25$) in the phase immediately following the micro-teaching unit.
-This finding would be consistent with the idea that differences in mean HR, as an indicator of the physiological stress response, can be linked to the cognitive appraisal of stressors.
-
-## Limitations and future directions
-
-While the laboratory setting of the study allowed for a controlled implementation of stressors and high internal validity, it was not an authentic classroom environment, raising questions about its external validity.
-Most importantly, the teacher and their students did not have a shared history, and only a very thin basis for establishing a positive teacher-student relationship, which is a core characteristic of effective classroom management [@ruedi2014; @beaty2010].
-In addition, the micro-teaching unit was only about 15 minutes long, and thus much shorter than a regular school lesson, providing less opportunities for experienced teachers to build up an engaging lesson.
-Finally, student behavior was scripted, with classroom disruptions following the experimental schedule, irrelevant of the behavior of the teacher.
-Thus, the setting may have masked effects of teaching experience by providing too little opportunities of experienced teachers to demonstrate their true classroom management skills, in particular regarding the prevention of disruptions.
-In subsequent studies, it would therefore be insightful to assess teachers’ HR in more authentic classroom settings over a longer period of time (e.g., days, weeks, or even months).
-Extended observation of teachers’ HR in authentic classroom settings could reveal how factors such as student behavior, teaching methods, or organizational and administrative demands contribute to fluctuations in physiological arousal, uncovering insights into the sustained physiological demands of teaching that short-term studies may overlook.
-Finally, linking actual teacher behavior to potential stressors (e.g., classroom disruptions, noise level, etc.) would offer insights into teacher coping strategies and their links with physiological indicators of stress.
-
-Another limitation concerns the assessment of teachers’ HR.
-While our results demonstrate the usefulness of drawing upon easily available HR data from ubiquitous, low-cost, un-intrusive fitness trackers to estimate teacher stress, there also are shortcomings of this type of assessment.
-First, while fitness trackers typically yield HR data, heart rate variability (HRV) has been demonstrated to be an even more accurate indicator of stress [@wettstein2020ambulatory].
-While standard fitness trackers did not provide this measure at the time of our data collection, more recent products do offer this function.
-Thus, future studies might consider assessing HRV instead of HR.
-Second, we did not record participants’ resting HR, which is generally considered an important baseline for determining inter- and intrapersonal differences in cardiovascular health and reactivity [@nanchen2018; @heneghan2019].
-A clean baseline HR requires a resting phase without physical movement or emotional stress, ideally fifteen minutes before the beginning of the activity, which is very difficult to achieve in practice [@sammito2015guideline], e.g., when assessing teacher HR before and during teaching.
-Thus, our study explored the possibility of substituting baseline HR measurement via z-standardization within participants.
-As a result, the absolute standardized values of each participant must always be interpreted in the context of the standardization sample, and thus are less interpretable than individual BPM values together with a baseline HR.
-However, for statistical analyses based on the whole sample, the standardization fulfills the aim of controlling for differences in individual HR due to, for example, age-related differences.
-Finally, depending on the brand and model of fitness trackers used, the precision of the HR measurement varies.
-Research on the reliability of our deployed Fitbit® device has proven that this brand is generally accurate in controlled settings and for moderate activity levels [@wallen2016accuracy; @hajj2023; @fuller2020; @jo2016], as in our study.
-For example, the Fitbit® fitness tracker has previously shown good HR measurement accuracy during resting phases [@jo2016; @muggeridge2021measurement] and for activities such as walking, jogging, and running [@hajj2023].
-At higher exercise intensities such as cycling, the Fitbit® tracker may underestimate HR [@thomson2019heart; @montoye2017comparative; @jo2016; @jachymek2021] but is still within an acceptable range according to systematic reviews [@chevance2022accuracy].
-Nevertheless, @gagnon2022 stressed that Fitbit® trackers cannot replace ECG when precision is paramount.
-Despite these considerations, the Fitbit® model appears suitable for our study purposes, as physical strain was moderate.
-
-Furthermore, while we assessed teachers’ appraisals of the stressful classroom disruptions using a SRI in which they could review the exact situation, these appraisal ratings were still post-hoc self-reports, which limits the interpretation of our results.
-One of the main issues with post-hoc self-reports is that they rely on the teachers’ memories and subjective interpretations of past events, which may be prone to various biases such as social desirability [@razavi2001self] or recall errors [@van2016accuracy].
-Moreover, stress is not a fixed or stable construct; it is a dynamic, constantly evolving affective response that can vary depending on context, individual disposition, and prior experiences, making it particularly challenging to pinpoint valid and reliable process markers for how individuals appraise stress in real-time [@lazarus1990theory].
-While SRIs provide a more detailed and reflective understanding of the stressor in question, the delayed nature of the response makes it difficult to capture the immediate, in-the-moment appraisal that occurs when the stressful event actually takes place.
-
-## Hands-on advice for using wrist-worn fitness trackers for research
-
-For researchers aiming to use fitness trackers to collect data, there are practical aspects to consider concerning the design, data collection, and data analysis phases of research projects [for an additional overview, see @nelson2020guidelines]:
-
 1)	Choosing a suitable model:
@@
 For instance, while our fitness tracker was designed to record HR every 1-5 seconds, we occasionally observed recordings only every 15 seconds, possibly due to participant movement and tracker placement.
+
+\newpage
 
@@
         facet_wrap(~ ID, nrow = 8) +  # Arrange plots by 'ID'
-        xlab('Time (in Seconds)') +  # X-axis label (similar to 'Arbeitsstunden pro Woche')
+        xlab('Time (in Minutes)') +  # X-axis label (similar to 'Arbeitsstunden pro Woche')
         ylab('Heart Rate (Standardized)') +  # Y-axis label (similar to 'Nettoeinkommen')
@@
        width = 25,
-       height = 30,
+       height = 29,
        units = "cm")
@@
 ```{=latex}
-\newpage
 \appendix
@@
 
+\setcounter{table}{0}
+
 \renewcommand{\thefigure}{A\arabic{figure}}  % Figures labeled A1, A2, etc.
+
+\renewcommand{\thetable}{A\arabic{table}}
 
@@
     \centering
-    \caption{Classification of nine, typical classroom disruptions according to @lohmann2003schulern performed in the micro-teaching unit by actors.}
+    \caption{\\
+    Classification of nine, typical classroom disruptions according to \cite{lohmann2003schulern} performed in the micro-teaching unit by actors.}
     \begin{tabularx}{\textwidth}{XXX}
@@
   \centering
-  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
-  \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
+  \caption{\\
+  Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
+  \includegraphics[width=0.5\textwidth]{appendix_figure1.png}
   \label{fig.a1}
@@
 \begin{figure}[htbp]
-  \centering\caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
-  \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
+  \centering\caption{\\
+  Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
+  \includegraphics[width=0.5\textwidth]{appendix_figure2.png}
   \label{fig.a2}
@@
   \centering
-  \caption{Linear estimation of individual HR changes over time during the preparation phase for $N$ = 81 participants.
+  \caption{\\
+  Linear estimation of individual HR changes over time during the preparation phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
@@
   \centering
-  \caption{Linear estimation of individual HR changes over time during the teaching phase for $N$ = 81 participants.
+  \caption{\\
+  Linear estimation of individual HR changes over time during the teaching phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
@@
   \centering
-  \caption{Linear estimation of individual HR changes over time during the post-teaching phase for $N$ = 81 participants.
+  \caption{\\
+  Linear estimation of individual HR changes over time during the post-teaching phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
@@
   \centering
-  \caption{Linear estimation of individual HR changes over time during the interview phase for $N$ = 81 participants.
+  \caption{\\
+  Linear estimation of individual HR changes over time during the interview phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
@@
   \centering
-  \caption{Linear estimation of individual HR changes over time during the end phase for $N$ = 81 participants.
+  \caption{\\
+  Linear estimation of individual HR changes over time during the end phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
@@
 \end{figure}
-```
+
+\newpage
+```

### 2024-09-25 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
nochmal quasi final

@@
 electrocardiographs (ECG). Modern fitness trackers represent a
-non-invasive and convenient alternative. \citep{ferguson2015}
+non-invasive and convenient alternative \citep{ferguson2015}.
 
@@
 \citep{taelman2009influence}; whereas an increase in parasympathetic
-activity results in HR being slowed down (``rest and digest'' response)
-\citep{battipaglia2015}. Stress or mental and physical strain directly
+activity results in HR being slowed down (``rest and digest'' response,
+\citet{battipaglia2015}). Stress or mental and physical strain directly
 increases HR \citep{custodis2014heart, sachs2014}. Therefore, an
@@
 
-\captionsetup[figure]{
-    labelfont=bf,         % Figure label bold (not italic)
-    parskip=12pt,
-    labelsep=newline,      % Period after Figure label
-    textfont=it,          % Italic font for the caption text
-    font=small,           % Smaller font size for APA style
-    justification=justified, % Left-justified captions, as per APA guidelines
-    singlelinecheck=false % Avoid centering if the caption is single-line
-}
-
-\captionsetup[table]{
-    labelfont=bf,         % Figure label bold (not italic)
-    parskip=12pt,
-    labelsep=newline,      % Period after Figure label
-    textfont=it,          % Italic font for the caption text
-    font=small,           % Smaller font size for APA style
-    justification=justified, % Left-justified captions, as per APA guidelines
-    singlelinecheck=false % Avoid centering if the caption is single-line
-}
-
-\begin{figure}[htbp]
-  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
-  \centering
-  \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
-  \label{fig.1}
-\end{figure}
-
-Fig. 1 shows, in a simplified way, how classroom events affect teachers'
-stress level, according to the adaptation of the Lazarus model to
-teacher stress proposed by \citet{van2006stress}: When potential
-stressors (e.g., classroom disruptions) occur during teaching (1),
-teachers intuitively judge how disruptive the event is in a primary
+Figure \ref{fig.1} shows, in a simplified way, how classroom events
+affect teachers' stress level, according to the adaptation of the
+Lazarus model to teacher stress proposed by \citet{van2006stress}: When
+potential stressors (e.g., classroom disruptions) occur during teaching
+(1), teachers intuitively judge how disruptive the event is in a primary
 appraisal (2). If potential stressors are judged as threatening, i.e.,
@@
 
-As shown in Fig. 1, teachers' primary and secondary appraisal as well as
-coping attempts are influenced by professional experience. As
-professional experience grows, teachers develop cognitive scripts for
-managing classroom events, resulting in more complex and problem-focused
-classroom management skills \citep{wolff2021classroom}, and thus more
-effective coping and less stress. Empirically, classroom management
-skills and problem-focused coping styles are linked to fewer instances
-of emotional exhaustion \citep{maslach2001job, clunies2008self}. Novices
-in the teaching profession, on the other hand, face considerable stress
-and often feel overwhelmed by the demands of teaching
+As shown in Figure \ref{fig.1}, teachers' primary and secondary
+appraisal as well as coping attempts are influenced by professional
+experience. As professional experience grows, teachers develop cognitive
+scripts for managing classroom events, resulting in more complex and
+problem-focused classroom management skills \citep{wolff2021classroom},
+and thus more effective coping and less stress. Empirically, classroom
+management skills and problem-focused coping styles are linked to fewer
+instances of emotional exhaustion
+\citep{maslach2001job, clunies2008self}. Novices in the teaching
+profession, on the other hand, face considerable stress and often feel
+overwhelmed by the demands of teaching
 \citep{ophardt2017klassenmanagement, wolff2015keeping, klusmann2012berufliche}
@@
 \citep{fisher2011}.
+
+\captionsetup[figure]{
+    labelfont=bf,       % Figure label bold (not italic)
+    labelsep=newline,      % Period after Figure label
+    textfont=it,          % Italic font for the caption text
+    font=small,           % Smaller font size for APA style
+    justification=justified, % Left-justified captions, as per APA guidelines
+    singlelinecheck=false % Avoid centering if the caption is single-line
+}
+
+\captionsetup[table]{
+    labelfont=bf,        % Figure label bold (not italic)
+    labelsep=newline,      % Period after Figure label
+    textfont=it,          % Italic font for the caption text
+    font=small,           % Smaller font size for APA style
+    justification=justified, % Left-justified captions, as per APA guidelines
+    singlelinecheck=false % Avoid centering if the caption is single-line
+}
+
+\begin{figure}[htbp]
+  \caption{\\
+  A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
+  \centering
+  \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
+  \label{fig.1}
+\end{figure}
 
@@
   teachers who felt more disrupted, regardless of their teaching
-  experience (\textbf{Hypotheses 2b}), and lower HR levels for teachers
+  experience (\textbf{Hypothesis 2b}), and lower HR levels for teachers
   who felt more confident, regardless of teaching experience
@@
 Each participant came to the lab for a period of approximately two hours
-in total, and each participant underwent the same phases (see Fig. 2):
-In the \emph{pre-teaching phase}, the experimenter welcomed the
-participants and helped them put on the fitness tracker. This was
-followed by a warm-up session to familiarize the participants with the
-laboratory setting and the class. This phase took about 10-15 minutes
-and participants spent this time mostly standing or slowly walking
-around. During the \emph{teaching phase}, the participants held their
-self-prepared micro-teaching unit to a class of three trained actors who
-performed nine, potentially disruptive, classroom events (e.g., chatting
-with a neighbor, heckling, looking at the phone; see Table \#\# in the
-supplementary material for an overview and categorization of all events;
-and Figure \ref{fig.a2} in the supplementary material for a depiction of
-the laboratory setting of the micro-teaching unit). The topic and class
-level of the teaching unit could be freely chosen by the teachers with
-the only requirement that the unit had to be an introductory lesson, and
-had to consist of supervised individual work and / or frontal teaching.
-The micro-teaching unit lasted about 15-20 minutes. Participants spent
-this time mostly standing or slowly walking around. While teaching,
-participants wore eye-tracking glasses, and their lesson was
-video-recorded. After having completed the micro-teaching unit, in the
-\emph{post-teaching phase}, participants filled in questionnaires for
-approximately 10-15 minutes: a brief computer-based survey of
-sociodemographic data (e.g., teaching experience, gender, studied school
-type, studied school subjects, extracurricular teaching activities), and
-a short knowledge test that was irrelevant to the present study. In the
-\emph{interview phase},
-
-\begin{wrapfigure}{r}{0.5\textwidth}
+in total, and each participant underwent the same phases (see Figure
+\ref{fig.2}): In the \emph{pre-teaching phase}, the experimenter
+welcomed the participants and helped them put on the fitness tracker.
+This was followed by a warm-up session to familiarize the participants
+with the laboratory setting and the class. This phase took about 10-15
+minutes and participants spent this time mostly standing or slowly
+walking around. During the \emph{teaching phase}, the participants held
+their self-prepared micro-teaching unit to a class of three trained
+actors who performed nine, potentially disruptive, classroom events
+(e.g., chatting with a neighbor, heckling, looking at the phone; see
+Table \#\# in the supplementary material for an overview and
+categorization of all events; and Figure \ref{fig.a2} in the
+supplementary material for a depiction of the laboratory setting of the
+micro-teaching unit). The topic and class level of the teaching unit
+could be freely chosen by the teachers with the only requirement that
+the unit had to be an introductory lesson, and had to consist of
+supervised individual work and / or frontal teaching. The micro-teaching
+unit lasted about 15-20 minutes. Participants spent this time mostly
+standing or slowly walking around. While teaching, participants wore
+eye-tracking glasses, and their lesson was video-recorded. After having
+completed the micro-teaching unit, in the \emph{post-teaching phase},
+participants filled in questionnaires for approximately 10-15 minutes: a
+brief computer-based survey of sociodemographic
+
+\begin{wrapfigure}[36]{r}{0.5\textwidth}
   \centering
-  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
+  \caption{\\
+  Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
   \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
@@
 
-\noindent participants engaged in a Stimulated Recall Interview (SRI).
-During the SRI, participants sat in front of a computer monitor and
-watched the video of their own lesson from the ego perspective, as
-recorded through the eye-tracking glasses. The experimenter stopped the
-video each time one of the nine classroom events happened, and asked
-five open-ended, and three rating questions per event. Two of the rating
-questions are relevant to the present study: the disruption and the
-confidence appraisal ratings (see Measures). The interview lasted about
-45-60 minutes. Finally, in the \emph{end phase}, participants filled in
-another questionnaire irrelevant to the present study, which lasted
-about 10-15 minutes.
+\noindent data (e.g., teaching experience, gender, studied school type,
+studied school subjects, extracurricular teaching activities), and a
+short knowledge test that was irrelevant to the present study. In the
+\emph{interview phase}, participants engaged in a Stimulated Recall
+Interview (SRI). During the SRI, participants sat in front of a computer
+monitor and watched the video of their own lesson from the ego
+perspective, as recorded through the eye-tracking glasses. The
+experimenter stopped the video each time one of the nine classroom
+events happened, and asked five open-ended, and three rating questions
+per event. Two of the rating questions are relevant to the present
+study: the disruption and the confidence appraisal ratings (see
+Measures). The interview lasted about 45-60 minutes. Finally, in the
+\emph{end phase}, participants filled in another questionnaire
+irrelevant to the present study, which lasted about 10-15 minutes.
 
@@
 
+\subsection{Mapping teachers' HR over the course of the study
+phases}\label{mapping-teachers-hr-over-the-course-of-the-study-phases}
+
+Means, standard deviations, and range of teachers' unstandardized and
+standardized HR for the entire study period, and for the five intervals,
+are shown in Table \ref{tab_1}. Figure \ref{fig.3} displays the
+unstandardized and standardized HR trends, respectively, over the course
+of the entire study period. HR initially increased, peaked, and then
+decreased, with the unstandardized and standardized HR graphs showing
+high similarity. Thus, for all further analyses, we used participants'
+standardized HR values.
+
+Figure \ref{fig.4} shows the distribution of teachers' mean standardized
+HR for the five intervals. Repeated measures ANOVA revealed significant
+differences in mean standardized HR between intervals,
+\(F(4, 400) = 260.62\), \(p < .05\), \(d = 1.60\) (large effect).
+Planned contrasts indicated that, as hypothesized (Hypothesis 1a), mean
+standardized HR was significantly higher in the \emph{teaching interval}
+(\(I_2\)) than in all other intervals, specifically, the
+\emph{pre-teaching interval} (\(I_1\); \(t(400) = -10.08\), \(p < .05\),
+\(d = 1.034\); large effect), the post-teaching interval (\(I_3\);
+\(t(400) = -6.94\), \(p < .05\), \(d = 1.37\); large effect), the
+interview interval (\(I_4\); \(t(400) = 15.00\), \(p < .05\),
+\(d = 3.29\); large effect), and the end interval (\(I_5\));
+\(t(400) = 22.54\), \(p < .05\), \(d = 4.64\); large effect).
+
+Next, we examined HR changes (i.e., mean slopes) within each interval to
+test the hypothesis that HR increased during the \emph{pre-teaching
+phase} and decreased during all other phases (Hypothesis 1b). The mean
+intercepts and mean slopes, complemented by their standard deviations
+for each interval, are shown in Table 2. The mean slope of the
+\emph{pre-teaching interval} (\(I_1\)) was significantly positive,
+indicating an increase in HR, as hypothesized. Further, the mean slopes
+of the \emph{teaching interval} (\(I_2\)), \emph{post-teaching interval}
+(\(I_3\)), and \emph{interview interval} (\(I_4\)) were significantly
+negative, indicating a decrease in HR. For the last interval, the
+\emph{end interval} (\(I_5\)), the mean slope was negative, but did not
+differ significantly from zero.
+
 \renewcommand{\arraystretch}{1.5}
@@
 
-\subsection{Mapping teachers' HR over the course of the study
-phases}\label{mapping-teachers-hr-over-the-course-of-the-study-phases}
-
-Means, standard deviations, and range of teachers' unstandardized and
-standardized HR for the entire study period, and for the five intervals,
-are shown in Table \ref{tab_1}. Figure \ref{fig.3} displays the
-unstandardized and standardized HR trends, respectively, over the course
-of the entire study period. HR initially increased, peaked, and then
-decreased, with the unstandardized and standardized HR graphs showing
-high similarity. Thus, for all further analyses, we used participants'
-standardized HR values.
-
-Figure \ref{fig.4} shows the distribution of teachers' mean standardized
-HR for the five intervals. Repeated measures ANOVA revealed significant
-differences in mean standardized HR between intervals,
-\(F(4, 400) = 260.62\), \(p < .05\), \(d = 1.60\) (large effect).
-Planned contrasts indicated that, as hypothesized (Hypothesis 1a), mean
-standardized HR was significantly higher in the \emph{teaching interval}
-(\(I_2\)) than in all other intervals, specifically, the
-\emph{pre-teaching interval} (\(I_1\); \(t(400) = -10.08\), \(p < .05\),
-\(d = 1.034\); large effect), the post-teaching interval (\(I_3\);
-\(t(400) = -6.94\), \(p < .05\), \(d = 1.37\); large effect), the
-interview interval (\(I_4\); \(t(400) = 15.00\), \(p < .05\),
-\(d = 3.29\); large effect), and the end interval (\(I_5\));
-\(t(400) = 22.54\), \(p < .05\), \(d = 4.64\); large effect).
-
-\begin{figure}[H]
-  \centering
-  \caption{Distribution of the standardized heart rate means in the five intervals}
-  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
-  \label{fig.4}
-\end{figure}
-
-Next, we examined HR changes (i.e., mean slopes) within each interval to
-test the hypothesis that HR increased during the \emph{pre-teaching
-phase} and decreased during all other phases (Hypothesis 1b). The mean
-intercepts and mean slopes, complemented by their standard deviations
-for each interval, are shown in Table 2. The mean slope of the
-\emph{pre-teaching interval} (\(I_1\)) was significantly positive,
-indicating an increase in HR, as hypothesized. Further, the mean slopes
-of the \emph{teaching interval} (\(I_2\)), \emph{post-teaching interval}
-(\(I_3\)), and \emph{interview interval} (\(I_4\)) were significantly
-negative, indicating a decrease in HR. For the last interval, the
-\emph{end interval} (\(I_5\)), the mean slope was negative, but did not
-differ significantly from zero.
-
 \renewcommand{\arraystretch}{1.5}
@@
     \centering
-    \caption{Analysis (\textit{M, SD, p-values}) for the mean intercepts and the mean slopes for the five intervals.}
+    \caption{\\
+    Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
     \begin{tabularx}{\textwidth}{lXXXXXX}
@@
 
+\begin{figure}[H]
+  \centering
+  \caption{\\
+  Distribution of the standardized heart rate means in the five intervals}
+  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
+  \label{fig.4}
+\end{figure}
+
 \subsection{Predicting mean standardized HR and mean
@@
 
+\newpage
+
 Concerning the explorative investigation of the effects of teaching
@@
 
+\section{Discussion}\label{discussion}
+
+\subsection{Key findings}\label{key-findings}
+
+Overall, our findings indicate that wrist-worn fitness trackers are a
+useful tool for tracking teachers' HR and identifying stressful periods
+during teaching. Using HR data from a commercially available and
+relatively low-cost Fitbit® fitness tracker, we were able to map
+teachers' HR before, during, and after a stressful micro-teaching unit,
+with HR increasing in preparation for teaching, peaking during the
+teaching phase, and decreasing afterward.
+
+These findings are in line with prior studies showing that teachers' HR
+varies depending on their activities and encountered stressors with
+increases during phases where teachers are in an exposed position
+\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021},
+as well as with findings showing how HR changes align with activating
+events and stress-inducing tasks \citep{Darnell2019, chalmers2021}.
+
+Building on the model of teacher stress \citep[see Fig.
+2]{kyriacou1978}, we had hypothesized that more experienced teachers,
+with better classroom management skills at their disposal, experience
+less physiological stress when dealing with classroom disruptions.
+Contrary to our expectations, we found no buffering effect of teaching
+experience on teachers' HR, i.e., more experienced teachers did not show
+lower mean standardized HR during the stressful teaching phase than less
+experienced teachers. Rather, at least descriptively, we observed the
+opposite trend. There are several possible explanations for this
+finding. First, teaching experience is inherently confounded with age
+(the two variables correlated at \(r = .94\) in our sample), and age has
+been shown to affect indicators of cardiovascular reactivity in various
+ways \citep{uchino2010older}. However, to avoid this kind of confounding
+influence, we had used not raw BPM but rather standardized mean HR for
+all our analyses, thus controlling at least for inter-individual
+differences in mean HR. Second, as research on teacher
+professionalization has repeatedly shown, professional experience is not
+a guarantee for higher professional knowledge and skills
+\citep{kirschner2016professionswissen}. Rather, honing skills from
+professional experience necessitates a deliberate practice of choosing
+to improve, learning through experience, and integrating new knowledge
+into future performances \citep{dunn1999deliberate}. Thus, rather than
+professional experience alone, more direct assessments of classroom
+management skills, such as objective behavior-based tests, would be a
+better indicator of expertise that future studies could explore.
+Finally, and most importantly, the highly controlled teaching situation
+that we created in the lab might not have provided sufficient
+resemblance to the expert teachers' working conditions to let them
+effectively use their coping resources. In other words, since the
+situation was unfamiliar to both experienced and unexperienced teachers,
+their stress levels might have been more similar than they would have
+been in a more authentic classroom setting.
+
+While we did not find a buffering effect of teaching experience on mean
+HR during teaching, we did, however, find a less steep HR increase in
+more experienced, compared to less experienced teachers during the
+pre-teaching phase (\(\beta = -.27\)), i.e., in preparation for the
+micro-teaching unit. This finding supports the idea that, even though
+teaching experience guarantees neither superior expertise nor stress
+resistance, the habits and routines formed by experienced teachers may
+at least lead to lower arousal levels (e.g., experienced as feeling less
+nervous and tense) when they anticipate potentially stressful teaching
+situations.
+
+An interesting observation beyond our hypotheses was that teaching
+experience was predictive of HR differences, not during teaching, but in
+the interview phase: compared to less experienced teachers, more
+experienced teachers showed a higher mean standardized HR
+(\(\beta = .24\)) and, thus, probably experienced higher levels of
+physiological stress during the SRI. One possible explanation for this
+finding could again be the higher age of the more experienced teachers,
+along with slower recovery from stress in older teachers. For instance,
+\citet{ritvanen2006responses} observed that, compared to their younger
+colleagues, older teachers did not experience a decrease in their HR
+during periods of low stress levels, from which they concluded that
+recovery from stress was insufficient in the older teachers
+\citep{ritvanen2006responses}. Alternatively, the finding could also be
+attributed to the fact that less experienced teachers, due to their
+ongoing or only recently concluded training, may have been more
+accustomed to reflecting on their work and receiving feedback as was the
+case during the SRI, whereas, these activities were less routine and
+possibly more face-threatening for experienced teachers. Therefore, it
+is possible that more experienced teachers found the interview itself to
+be more stressful and therefore showed a higher mean standardized HR
+during this phase.
+
+With regards to the predictive power of teachers' subjective appraisals
+of the classroom disruption during teaching, we, first of all, have to
+conclude that our hypotheses were not supported, as neither confidence
+appraisal nor disruptiveness appraisal showed any notable correlations
+with teachers' means standardized HR or any explanatory power over and
+beyond teaching experience. Possibly, teachers' self-reported
+appraisals, and their actual physiological stress responses, tap into
+quite different phenomena, or at least, quite different aspects of the
+multifaceted stress response \citep{kyriacou1978}. In addition, while HR
+was assessed online during teaching, self-reported appraisals were given
+in retrospect during the SRI, and may be subject to biased (e.g.,
+self-serving) reporting or simply an inability to recall one´s immediate
+stress reactions.
+
+On the other hand, when controlling for all other factors, teachers who
+reported to have perceived the events as more disruptive showed a higher
+HR (\(\beta = .25\)) in the phase immediately following the
+micro-teaching unit. This finding would be consistent with the idea that
+differences in mean HR, as an indicator of the physiological stress
+response, can be linked to the cognitive appraisal of stressors.
+
+\subsection{Limitations and future
+directions}\label{limitations-and-future-directions}
+
+While the laboratory setting of the study allowed for a controlled
+implementation of stressors and high internal validity, it was not an
+authentic classroom environment, raising questions about its external
+validity. Most importantly, the teacher and their students did not have
+a shared history, and only a very thin basis for establishing a positive
+teacher-student relationship, which is a core characteristic of
+effective classroom management \citep{ruedi2014, beaty2010}. In
+addition, the micro-teaching unit was only about 15 minutes long, and
+thus much shorter than a regular school lesson, providing less
+opportunities for experienced teachers to build up an engaging lesson.
+Finally, student behavior was scripted, with classroom disruptions
+following the experimental schedule, irrelevant of the behavior of the
+teacher. Thus, the setting may have masked effects of teaching
+experience by providing too little opportunities of experienced teachers
+to demonstrate their true classroom management skills, in particular
+regarding the prevention of disruptions. In subsequent studies, it would
+therefore be insightful to assess teachers' HR in more authentic
+classroom settings over a longer period of time (e.g., days, weeks, or
+even months). Extended observation of teachers' HR in authentic
+classroom settings could reveal how factors such as student behavior,
+teaching methods, or organizational and administrative demands
+contribute to fluctuations in physiological arousal, uncovering insights
+into the sustained physiological demands of teaching that short-term
+studies may overlook. Finally, linking actual teacher behavior to
+potential stressors (e.g., classroom disruptions, noise level, etc.)
+would offer insights into teacher coping strategies and their links with
+physiological indicators of stress.
+
+Another limitation concerns the assessment of teachers' HR. While our
+results demonstrate the usefulness of drawing upon easily available HR
+data from ubiquitous, low-cost, un-intrusive fitness trackers to
+estimate teacher stress, there also are shortcomings of this type of
+assessment. First, while fitness trackers typically yield HR data, heart
+rate variability (HRV) has been demonstrated to be an even more accurate
+indicator of stress \citep{wettstein2020ambulatory}. While standard
+fitness trackers did not provide this measure at the time of our data
+collection, more recent products do offer this function. Thus, future
+studies might consider assessing HRV instead of HR. Second, we did not
+record participants' resting HR, which is generally considered an
+important baseline for determining inter- and intrapersonal differences
+in cardiovascular health and reactivity
+\citep{nanchen2018, heneghan2019}. A clean baseline HR requires a
+resting phase without physical movement or emotional stress, ideally
+fifteen minutes before the beginning of the activity, which is very
+difficult to achieve in practice \citep{sammito2015guideline}, e.g.,
+when assessing teacher HR before and during teaching. Thus, our study
+explored the possibility of substituting baseline HR measurement via
+z-standardization within participants. As a result, the absolute
+standardized values of each participant must always be interpreted in
+the context of the standardization sample, and thus are less
+interpretable than individual BPM values together with a baseline HR.
+However, for statistical analyses based on the whole sample, the
+standardization fulfills the aim of controlling for differences in
+individual HR due to, for example, age-related differences. Finally,
+depending on the brand and model of fitness trackers used, the precision
+of the HR measurement varies. Research on the reliability of our
+deployed Fitbit® device has proven that this brand is generally accurate
+in controlled settings and for moderate activity levels
+\citep{wallen2016accuracy, hajj2023, fuller2020, jo2016}, as in our
+study. For example, the Fitbit® fitness tracker has previously shown
+good HR measurement accuracy during resting phases
+\citep{jo2016, muggeridge2021measurement} and for activities such as
+walking, jogging, and running \citep{hajj2023}. At higher exercise
+intensities such as cycling, the Fitbit® tracker may underestimate HR
+\citep{thomson2019heart, montoye2017comparative, jo2016, jachymek2021}
+but is still within an acceptable range according to systematic reviews
+\citep{chevance2022accuracy}. Nevertheless, \citet{gagnon2022} stressed
+that Fitbit® trackers cannot replace ECG when precision is paramount.
+Despite these considerations, the Fitbit® model appears suitable for our
+study purposes, as physical strain was moderate.
+
+Furthermore, while we assessed teachers' appraisals of the stressful
+classroom disruptions using a SRI in which they could review the exact
+situation, these appraisal ratings were still post-hoc self-reports,
+which limits the interpretation of our results. One of the main issues
+with post-hoc self-reports is that they rely on the teachers' memories
+and subjective interpretations of past events, which may be prone to
+various biases such as social desirability \citep{razavi2001self} or
+recall errors \citep{van2016accuracy}. Moreover, stress is not a fixed
+or stable construct; it is a dynamic, constantly evolving affective
+response that can vary depending on context, individual disposition, and
+prior experiences, making it particularly challenging to pinpoint valid
+and reliable process markers for how individuals appraise stress in
+real-time \citep{lazarus1990theory}. While SRIs provide a more detailed
+and reflective understanding of the stressor in question, the delayed
+nature of the response makes it difficult to capture the immediate,
+in-the-moment appraisal that occurs when the stressful event actually
+takes place.
+
+\subsection{Hands-on advice for using wrist-worn fitness trackers for
+research}\label{hands-on-advice-for-using-wrist-worn-fitness-trackers-for-research}
+
+For researchers aiming to use fitness trackers to collect data, there
+are practical aspects to consider concerning the design, data
+collection, and data analysis phases of research projects \citep[for an
+additional overview, see][]{nelson2020guidelines}:
+
 \begin{landscape}
@@
 
-\section{Discussion}\label{discussion}
-
-\subsection{Key findings}\label{key-findings}
-
-Overall, our findings indicate that wrist-worn fitness trackers are a
-useful tool for tracking teachers' HR and identifying stressful periods
-during teaching. Using HR data from a commercially available and
-relatively low-cost Fitbit® fitness tracker, we were able to map
-teachers' HR before, during, and after a stressful micro-teaching unit,
-with HR increasing in preparation for teaching, peaking during the
-teaching phase, and decreasing afterward.
-
-These findings are in line with prior studies showing that teachers' HR
-varies depending on their activities and encountered stressors with
-increases during phases where teachers are in an exposed position
-\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021},
-as well as with findings showing how HR changes align with activating
-events and stress-inducing tasks \citep{Darnell2019, chalmers2021}.
-
-Building on the model of teacher stress \citep[see Fig.
-2]{kyriacou1978}, we had hypothesized that more experienced teachers,
-with better classroom management skills at their disposal, experience
-less physiological stress when dealing with classroom disruptions.
-Contrary to our expectations, we found no buffering effect of teaching
-experience on teachers' HR, i.e., more experienced teachers did not show
-lower mean standardized HR during the stressful teaching phase than less
-experienced teachers. Rather, at least descriptively, we observed the
-opposite trend. There are several possible explanations for this
-finding. First, teaching experience is inherently confounded with age
-(the two variables correlated at \(r = .94\) in our sample), and age has
-been shown to affect indicators of cardiovascular reactivity in various
-ways \citep{uchino2010older}. However, to avoid this kind of confounding
-influence, we had used not raw BPM but rather standardized mean HR for
-all our analyses, thus controlling at least for inter-individual
-differences in mean HR. Second, as research on teacher
-professionalization has repeatedly shown, professional experience is not
-a guarantee for higher professional knowledge and skills
-\citep{kirschner2016professionswissen}. Rather, honing skills from
-professional experience necessitates a deliberate practice of choosing
-to improve, learning through experience, and integrating new knowledge
-into future performances \citep{dunn1999deliberate}. Thus, rather than
-professional experience alone, more direct assessments of classroom
-management skills, such as objective behavior-based tests, would be a
-better indicator of expertise that future studies could explore.
-Finally, and most importantly, the highly controlled teaching situation
-that we created in the lab might not have provided sufficient
-resemblance to the expert teachers' working conditions to let them
-effectively use their coping resources. In other words, since the
-situation was unfamiliar to both experienced and unexperienced teachers,
-their stress levels might have been more similar than they would have
-been in a more authentic classroom setting.
-
-While we did not find a buffering effect of teaching experience on mean
-HR during teaching, we did, however, find a less steep HR increase in
-more experienced, compared to less experienced teachers during the
-pre-teaching phase (\(\beta = -.27\)), i.e., in preparation for the
-micro-teaching unit. This finding supports the idea that, even though
-teaching experience guarantees neither superior expertise nor stress
-resistance, the habits and routines formed by experienced teachers may
-at least lead to lower arousal levels (e.g., experienced as feeling less
-nervous and tense) when they anticipate potentially stressful teaching
-situations.
-
-An interesting observation beyond our hypotheses was that teaching
-experience was predictive of HR differences, not during teaching, but in
-the interview phase: compared to less experienced teachers, more
-experienced teachers showed a higher mean standardized HR
-(\(\beta = .24\)) and, thus, probably experienced higher levels of
-physiological stress during the SRI. One possible explanation for this
-finding could again be the higher age of the more experienced teachers,
-along with slower recovery from stress in older teachers. For instance,
-\citet{ritvanen2006responses} observed that, compared to their younger
-colleagues, older teachers did not experience a decrease in their HR
-during periods of low stress levels, from which they concluded that
-recovery from stress was insufficient in the older teachers
-\citep{ritvanen2006responses}. Alternatively, the finding could also be
-attributed to the fact that less experienced teachers, due to their
-ongoing or only recently concluded training, may have been more
-accustomed to reflecting on their work and receiving feedback as was the
-case during the SRI, whereas, these activities were less routine and
-possibly more face-threatening for experienced teachers. Therefore, it
-is possible that more experienced teachers found the interview itself to
-be more stressful and therefore showed a higher mean standardized HR
-during this phase.
-
-With regards to the predictive power of teachers' subjective appraisals
-of the classroom disruption during teaching, we, first of all, have to
-conclude that our hypotheses were not supported, as neither confidence
-appraisal nor disruptiveness appraisal showed any notable correlations
-with teachers' means standardized HR or any explanatory power over and
-beyond teaching experience. Possibly, teachers' self-reported
-appraisals, and their actual physiological stress responses, tap into
-quite different phenomena, or at least, quite different aspects of the
-multifaceted stress response \citep{kyriacou1978}. In addition, while HR
-was assessed online during teaching, self-reported appraisals were given
-in retrospect during the SRI, and may be subject to biased (e.g.,
-self-serving) reporting or simply an inability to recall one´s immediate
-stress reactions.
-
-On the other hand, when controlling for all other factors, teachers who
-reported to have perceived the events as more disruptive showed a higher
-HR (\(\beta = .25\)) in the phase immediately following the
-micro-teaching unit. This finding would be consistent with the idea that
-differences in mean HR, as an indicator of the physiological stress
-response, can be linked to the cognitive appraisal of stressors.
-
-\subsection{Limitations and future
-directions}\label{limitations-and-future-directions}
-
-While the laboratory setting of the study allowed for a controlled
-implementation of stressors and high internal validity, it was not an
-authentic classroom environment, raising questions about its external
-validity. Most importantly, the teacher and their students did not have
-a shared history, and only a very thin basis for establishing a positive
-teacher-student relationship, which is a core characteristic of
-effective classroom management \citep{ruedi2014, beaty2010}. In
-addition, the micro-teaching unit was only about 15 minutes long, and
-thus much shorter than a regular school lesson, providing less
-opportunities for experienced teachers to build up an engaging lesson.
-Finally, student behavior was scripted, with classroom disruptions
-following the experimental schedule, irrelevant of the behavior of the
-teacher. Thus, the setting may have masked effects of teaching
-experience by providing too little opportunities of experienced teachers
-to demonstrate their true classroom management skills, in particular
-regarding the prevention of disruptions. In subsequent studies, it would
-therefore be insightful to assess teachers' HR in more authentic
-classroom settings over a longer period of time (e.g., days, weeks, or
-even months). Extended observation of teachers' HR in authentic
-classroom settings could reveal how factors such as student behavior,
-teaching methods, or organizational and administrative demands
-contribute to fluctuations in physiological arousal, uncovering insights
-into the sustained physiological demands of teaching that short-term
-studies may overlook. Finally, linking actual teacher behavior to
-potential stressors (e.g., classroom disruptions, noise level, etc.)
-would offer insights into teacher coping strategies and their links with
-physiological indicators of stress.
-
-Another limitation concerns the assessment of teachers' HR. While our
-results demonstrate the usefulness of drawing upon easily available HR
-data from ubiquitous, low-cost, un-intrusive fitness trackers to
-estimate teacher stress, there also are shortcomings of this type of
-assessment. First, while fitness trackers typically yield HR data, heart
-rate variability (HRV) has been demonstrated to be an even more accurate
-indicator of stress \citep{wettstein2020ambulatory}. While standard
-fitness trackers did not provide this measure at the time of our data
-collection, more recent products do offer this function. Thus, future
-studies might consider assessing HRV instead of HR. Second, we did not
-record participants' resting HR, which is generally considered an
-important baseline for determining inter- and intrapersonal differences
-in cardiovascular health and reactivity
-\citep{nanchen2018, heneghan2019}. A clean baseline HR requires a
-resting phase without physical movement or emotional stress, ideally
-fifteen minutes before the beginning of the activity, which is very
-difficult to achieve in practice \citep{sammito2015guideline}, e.g.,
-when assessing teacher HR before and during teaching. Thus, our study
-explored the possibility of substituting baseline HR measurement via
-z-standardization within participants. As a result, the absolute
-standardized values of each participant must always be interpreted in
-the context of the standardization sample, and thus are less
-interpretable than individual BPM values together with a baseline HR.
-However, for statistical analyses based on the whole sample, the
-standardization fulfills the aim of controlling for differences in
-individual HR due to, for example, age-related differences. Finally,
-depending on the brand and model of fitness trackers used, the precision
-of the HR measurement varies. Research on the reliability of our
-deployed Fitbit® device has proven that this brand is generally accurate
-in controlled settings and for moderate activity levels
-\citep{wallen2016accuracy, hajj2023, fuller2020, jo2016}, as in our
-study. For example, the Fitbit® fitness tracker has previously shown
-good HR measurement accuracy during resting phases
-\citep{jo2016, muggeridge2021measurement} and for activities such as
-walking, jogging, and running \citep{hajj2023}. At higher exercise
-intensities such as cycling, the Fitbit® tracker may underestimate HR
-\citep{thomson2019heart, montoye2017comparative, jo2016, jachymek2021}
-but is still within an acceptable range according to systematic reviews
-\citep{chevance2022accuracy}. Nevertheless, \citet{gagnon2022} stressed
-that Fitbit® trackers cannot replace ECG when precision is paramount.
-Despite these considerations, the Fitbit® model appears suitable for our
-study purposes, as physical strain was moderate.
-
-Furthermore, while we assessed teachers' appraisals of the stressful
-classroom disruptions using a SRI in which they could review the exact
-situation, these appraisal ratings were still post-hoc self-reports,
-which limits the interpretation of our results. One of the main issues
-with post-hoc self-reports is that they rely on the teachers' memories
-and subjective interpretations of past events, which may be prone to
-various biases such as social desirability \citep{razavi2001self} or
-recall errors \citep{van2016accuracy}. Moreover, stress is not a fixed
-or stable construct; it is a dynamic, constantly evolving affective
-response that can vary depending on context, individual disposition, and
-prior experiences, making it particularly challenging to pinpoint valid
-and reliable process markers for how individuals appraise stress in
-real-time \citep{lazarus1990theory}. While SRIs provide a more detailed
-and reflective understanding of the stressor in question, the delayed
-nature of the response makes it difficult to capture the immediate,
-in-the-moment appraisal that occurs when the stressful event actually
-takes place.
-
-\subsection{Hands-on advice for using wrist-worn fitness trackers for
-research}\label{hands-on-advice-for-using-wrist-worn-fitness-trackers-for-research}
-
-For researchers aiming to use fitness trackers to collect data, there
-are practical aspects to consider concerning the design, data
-collection, and data analysis phases of research projects \citep[for an
-additional overview, see][]{nelson2020guidelines}:
-
 \begin{enumerate}
@@
 
+\newpage
+
 \subsection{Conclusion}\label{conclusion}
@@
 
-\newpage
 \appendix
@@
 
+\newpage
+
 \bibliography{r-references.bib}

### 2024-09-26 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
paar fehler behoben

@@
   - name: Peer Keßler
-    email: peer.kessler@uni-greifswald.de.com
+    email: peer.kessler@uni-greifswald.de
     affiliation: University of Greifswald
@@
     email: gregor@example.com
-    affiliation: Leipzig University, Max Planck Institute for Evolutionary Anthropology
-    footnote: 1
+    affiliation: Max Planck Institute for Evolutionary Anthropology
+    footnote: 3
   - name: Christin Lotz
@@
     affiliation: Leipzig University
-    footnote: 1
+    footnote: 4
   - name: Anne Deiglmayr
@@
     affiliation: Leipzig University
-    footnote: 3
+    footnote: 5
 address:
@@
     text: 
-      - "Conceptualization, "
-      - "Writing - Original Draft Preparation, "
-      - "Writing - Review & Editing"
+      - "Conceptualization, Methodology, Formal analysis, Investigation, Data Curation, Writing - Original Draft"
   - code: 2
     text: 
-      - "Writing - Original Draft Preparation, "
-      - "Writing - Review & Editing"
+      - "Conceptualization, Methodology, Writing - Review & Editing, Supervision"
   - code: 3
-    text: "Supervision"
+    text: "Formal analysis, Data Curation, Writing - Review & Editing"
+  - code: 4
+    text: "Conceptualization, Methodology, Writing - Review & Editing"
+  - code: 5
+    text: "Conzeptualization, Methodology, Writing - Review & Editing, Supervision"
 abstract: "
@@
 This phase took about 10-15 minutes and participants spent this time mostly standing or slowly walking around.
-During the *teaching phase*, the participants held their self-prepared micro-teaching unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table ## in the supplementary material for an overview and categorization of all events; and Figure \ref{fig.a2} in the supplementary material for a depiction of the laboratory setting of the micro-teaching unit).
+During the *teaching phase*, the participants held their self-prepared micro-teaching unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table \ref{tab_a1} in the supplementary material for an overview and categorization of all events; and Figure \ref{fig.a2} in the supplementary material for a depiction of the laboratory setting of the micro-teaching unit).
 The topic and class level of the teaching unit could be freely chosen by the teachers with the only requirement that the unit had to be an introductory lesson, and had to consist of supervised individual work and / or frontal teaching.
@@
 Since we aimed to keep measurement intervals comparable between study phases, we aggregated HR over a representative 10-minute interval within each phase (cf.
-Fig.
-2).
+Figure \ref{fig.2}).
 Previous research has indicated that 10-minute intervals are a useful duration for analyzing PPG data [@lu2008can].
@@
 All participants were being interviewed during this interval.
-The end interval (I5) comprised the last 10 minutes before the fitness tracker was taken off.
+The end interval ($I_5$) comprised the last 10 minutes before the fitness tracker was taken off.
 
@@
 
-To enable visual inspection of HR trends, we displayed smoothed teacher HR over the course of the recording[^2].
-We visually compared unstandardized and standardized HR trends over the two-hour recording period[^3].
-For all further analyses, we used standardized rather than unstandardized HR values.
+To enable visual inspection of HR trends, we displayed smoothed teacher HR over the course of the recording.[^2] We visually compared unstandardized and standardized HR trends over the two-hour recording period.[^3] For all further analyses, we used standardized rather than unstandardized HR values.
 
@@
 [^3]: Note that the study exceeded the planned duration of two hours for a few participants.
-To avoid distortions when mapping the HR over the course of the study (see Fig.
-3), the endpoint was set at two hours for all participants, even though data from later time points was used in the *end interval* for a few participants.
+To avoid distortions when mapping the HR over the course of the study (see Figure \ref{fig.3}), the endpoint was set at two hours for all participants, even though data from later time points was used in the *end interval* for a few participants.
 
@@
 To test Hypothesis 2d, we examined the effects of all three predictors in one regression model.
-Furthermore, we repeated these steps to explore the effects of teaching experience and subjective appraisals on *changes* in teachers’ HR (i.e., mean slopes).
-Please note: HR levels and changes were not regressed on the disruption and confidence appraisals in the *pre-teaching interval* ($I_1$), because the appraised classroom events had not yet taken place in that phase.
+Furthermore, we repeated these steps to explore the effects of teaching experience and subjective appraisals on *changes* in teachers’ HR (i.e., mean slopes).[^12]
+
+[^12]: Please note: HR levels and changes were not regressed on the disruption and confidence appraisals in the *pre-teaching interval* ($I_1$), because the appraised classroom events had not yet taken place in that phase.
 
@@
         \midrule
-        Overall Course of 2h & 90.09/0.04\footnotemark[9] & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
+        Overall Course of 2h & 90.09/0.04\footnotemark[12] & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
         Pre-teaching interval ($I_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
@@
         Interview interval ($I_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
-        End interval ($I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\footnotemark[10]/-2.68 & 120/2.96 \\
+        End interval ($I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\footnotemark[13]/-2.68 & 120/2.96 \\
         \bottomrule
@@
 \end{table}
- \footnotetext[9]{Please note that standardized \textit{M} and \textit{SD} of the overall course were not exactly 0 and 1 due to rounding differences.}
- \footnotetext[10]{Deviations of the minimum values in the overall course vs. the end interval ($I_5$) are due to data of a few participants who needed more than two hours to finish the study.}
+ \footnotetext[12]{Please note that standardized \textit{M} and \textit{SD} of the overall course were not exactly 0 and 1 due to rounding differences.}
+ \footnotetext[13]{Deviations of the minimum values in the overall course vs.
+the \textit{end interval} ($I_5$) are due to data of a few participants who needed more than two hours to finish the study.}
 
@@
         \toprule
-        Interval  & \multicolumn{2}{c}{M (SD)} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
+        Interval  & \multicolumn{2}{c}{\textit{M} (\textit{SD})} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
         \midrule
@@
 
-Table 3 shows the raw correlations among mean standardized HR/mean slopes (see Table 2 for means and standard deviations), teaching experience ($M = 5.64$, $SD = 9.46$), disruption appraisal ($M = 5.19$, $SD = 2.87$), and confidence appraisal ($M = 7.81$, $SD = 1.97$).
+Table \ref{tab_3} shows the raw correlations among mean standardized HR/mean slopes (see Table \ref{tab_2} for means and standard deviations), teaching experience ($M = 5.64$, $SD = 9.46$), disruption appraisal ($M = 5.19$, $SD = 2.87$), and confidence appraisal ($M = 7.81$, $SD = 1.97$).
 With a few notable exceptions, correlations with HR measures were mostly very small and statistically non-significant (Table 3).
-Correlations between teaching experience and appraisals (not shown in Table 3) were substantial: more experienced teachers gave lower disruption appraisals ($r = -.36$), and higher confidence appraisals ($r = .44$).
+Correlations between teaching experience and appraisals (not shown in Table \ref{tab_3}) were substantial: more experienced teachers gave lower disruption appraisals ($r = -.36$), and higher confidence appraisals ($r = .44$).
 Moreover, the two appraisal variables were negatively correlated ($r = -.37$).
@@
 
-Table 4 shows the results of the regression analyses.
-Teaching experience significantly predicted mean standardized HR only in the *interview interval* (Table 4, Interview interval, Model 1), indicating a higher mean standardized HR for teachers with more teaching experience.
+Table \ref{tab_4} shows the results of the regression analyses.
+Teaching experience significantly predicted mean standardized HR only in the *interview interval* (Table \ref{tab_4}, *interview interval*, Model 1), indicating a higher mean standardized HR for teachers with more teaching experience.
 This relationship is, in fact, in the opposite direction as predicted by Hypothesis 2a.
-Neither adding disruption appraisal (**Hypothesis 2b**) nor adding confidence appraisal (**Hypothesis 2c**) increased the amount of explained variance to a statistically significant extent.
-
-When considering the effects of the three predictors in concert (**Hypothesis 2d**), mean standardized HR was significantly predicted only by disruption appraisal, and only in the *post-teaching interval* (Table 4, Post-teaching interval, Model 4), indicating a higher mean standardized HR for teachers who felt more disrupted by the classroom events, when controlling for the other variables.
+Neither adding disruption appraisal (Hypothesis 2b) nor adding confidence appraisal (Hypothesis 2c) increased the amount of explained variance to a statistically significant extent.
+
+When considering the effects of the three predictors in concert (Hypothesis 2d), mean standardized HR was significantly predicted only by disruption appraisal, and only in the *post-teaching interval* (Table \ref{tab_4}, *post-teaching interval*, Model 4), indicating a higher mean standardized HR for teachers who felt more disrupted by the classroom events, when controlling for the other variables.
 
@@
         \bottomrule \\
-          Note. * $p < .05$.
+          \textit{Note. *} $p < .05$.
     \end{tabularx}
@@
 Thus, rather than professional experience alone, more direct assessments of classroom management skills, such as objective behavior-based tests, would be a better indicator of expertise that future studies could explore.
-Finally, and most importantly, the highly controlled teaching situation that we created in the lab might not have provided sufficient resemblance to the expert teachers’ working conditions to let them effectively use their coping resources.
-In other words, since the situation was unfamiliar to both experienced and unexperienced teachers, their stress levels might have been more similar than they would have been in a more authentic classroom setting.
-
-While we did not find a buffering effect of teaching experience on mean HR during teaching, we did, however, find a less steep HR increase in more experienced, compared to less experienced teachers during the pre-teaching phase ($\beta = -.27$), i.e., in preparation for the micro-teaching unit.
-This finding supports the idea that, even though teaching experience guarantees neither superior expertise nor stress resistance, the habits and routines formed by experienced teachers may at least lead to lower arousal levels (e.g., experienced as feeling less nervous and tense) when they anticipate potentially stressful teaching situations.
-
-An interesting observation beyond our hypotheses was that teaching experience was predictive of HR differences, not during teaching, but in the interview phase: compared to less experienced teachers, more experienced teachers showed a higher mean standardized HR ($\beta = .24$) and, thus, probably experienced higher levels of physiological stress during the SRI.
-One possible explanation for this finding could again be the higher age of the more experienced teachers, along with slower recovery from stress in older teachers.
-For instance, @ritvanen2006responses observed that, compared to their younger colleagues, older teachers did not experience a decrease in their HR during periods of low stress levels, from which they concluded that recovery from stress was insufficient in the older teachers [@ritvanen2006responses].
-Alternatively, the finding could also be attributed to the fact that less experienced teachers, due to their ongoing or only recently concluded training, may have been more accustomed to reflecting on their work and receiving feedback as was the case during the SRI, whereas, these activities were less routine and possibly more face-threatening for experienced teachers.
-Therefore, it is possible that more experienced teachers found the interview itself to be more stressful and therefore showed a higher mean standardized HR during this phase.
-
-With regards to the predictive power of teachers’ subjective appraisals of the classroom disruption during teaching, we, first of all, have to conclude that our hypotheses were not supported, as neither confidence appraisal nor disruptiveness appraisal showed any notable correlations with teachers’ means standardized HR or any explanatory power over and beyond teaching experience.
-Possibly, teachers’ self-reported appraisals, and their actual physiological stress responses, tap into quite different phenomena, or at least, quite different aspects of the multifaceted stress response [@kyriacou1978].
-In addition, while HR was assessed online during teaching, self-reported appraisals were given in retrospect during the SRI, and may be subject to biased (e.g., self-serving) reporting or simply an inability to recall one´s immediate stress reactions.
-
-On the other hand, when controlling for all other factors, teachers who reported to have perceived the events as more disruptive showed a higher HR ($\beta = .25$) in the phase immediately following the micro-teaching unit.
-This finding would be consistent with the idea that differences in mean HR, as an indicator of the physiological stress response, can be linked to the cognitive appraisal of stressors.
-
-## Limitations and future directions
-
-While the laboratory setting of the study allowed for a controlled implementation of stressors and high internal validity, it was not an authentic classroom environment, raising questions about its external validity.
-Most importantly, the teacher and their students did not have a shared history, and only a very thin basis for establishing a positive teacher-student relationship, which is a core characteristic of effective classroom management [@ruedi2014; @beaty2010].
-In addition, the micro-teaching unit was only about 15 minutes long, and thus much shorter than a regular school lesson, providing less opportunities for experienced teachers to build up an engaging lesson.
-Finally, student behavior was scripted, with classroom disruptions following the experimental schedule, irrelevant of the behavior of the teacher.
-Thus, the setting may have masked effects of teaching experience by providing too little opportunities of experienced teachers to demonstrate their true classroom management skills, in particular regarding the prevention of disruptions.
-In subsequent studies, it would therefore be insightful to assess teachers’ HR in more authentic classroom settings over a longer period of time (e.g., days, weeks, or even months).
-Extended observation of teachers’ HR in authentic classroom settings could reveal how factors such as student behavior, teaching methods, or organizational and administrative demands contribute to fluctuations in physiological arousal, uncovering insights into the sustained physiological demands of teaching that short-term studies may overlook.
-Finally, linking actual teacher behavior to potential stressors (e.g., classroom disruptions, noise level, etc.) would offer insights into teacher coping strategies and their links with physiological indicators of stress.
-
-Another limitation concerns the assessment of teachers’ HR.
-While our results demonstrate the usefulness of drawing upon easily available HR data from ubiquitous, low-cost, un-intrusive fitness trackers to estimate teacher stress, there also are shortcomings of this type of assessment.
-First, while fitness trackers typically yield HR data, heart rate variability (HRV) has been demonstrated to be an even more accurate indicator of stress [@wettstein2020ambulatory].
-While standard fitness trackers did not provide this measure at the time of our data collection, more recent products do offer this function.
-Thus, future studies might consider assessing HRV instead of HR.
-Second, we did not record participants’ resting HR, which is generally considered an important baseline for determining inter- and intrapersonal differences in cardiovascular health and reactivity [@nanchen2018; @heneghan2019].
-A clean baseline HR requires a resting phase without physical movement or emotional stress, ideally fifteen minutes before the beginning of the activity, which is very difficult to achieve in practice [@sammito2015guideline], e.g., when assessing teacher HR before and during teaching.
-Thus, our study explored the possibility of substituting baseline HR measurement via z-standardization within participants.
-As a result, the absolute standardized values of each participant must always be interpreted in the context of the standardization sample, and thus are less interpretable than individual BPM values together with a baseline HR.
-However, for statistical analyses based on the whole sample, the standardization fulfills the aim of controlling for differences in individual HR due to, for example, age-related differences.
-Finally, depending on the brand and model of fitness trackers used, the precision of the HR measurement varies.
-Research on the reliability of our deployed Fitbit® device has proven that this brand is generally accurate in controlled settings and for moderate activity levels [@wallen2016accuracy; @hajj2023; @fuller2020; @jo2016], as in our study.
-For example, the Fitbit® fitness tracker has previously shown good HR measurement accuracy during resting phases [@jo2016; @muggeridge2021measurement] and for activities such as walking, jogging, and running [@hajj2023].
-At higher exercise intensities such as cycling, the Fitbit® tracker may underestimate HR [@thomson2019heart; @montoye2017comparative; @jo2016; @jachymek2021] but is still within an acceptable range according to systematic reviews [@chevance2022accuracy].
-Nevertheless, @gagnon2022 stressed that Fitbit® trackers cannot replace ECG when precision is paramount.
-Despite these considerations, the Fitbit® model appears suitable for our study purposes, as physical strain was moderate.
-
-Furthermore, while we assessed teachers’ appraisals of the stressful classroom disruptions using a SRI in which they could review the exact situation, these appraisal ratings were still post-hoc self-reports, which limits the interpretation of our results.
-One of the main issues with post-hoc self-reports is that they rely on the teachers’ memories and subjective interpretations of past events, which may be prone to various biases such as social desirability [@razavi2001self] or recall errors [@van2016accuracy].
-Moreover, stress is not a fixed or stable construct; it is a dynamic, constantly evolving affective response that can vary depending on context, individual disposition, and prior experiences, making it particularly challenging to pinpoint valid and reliable process markers for how individuals appraise stress in real-time [@lazarus1990theory].
-While SRIs provide a more detailed and reflective understanding of the stressor in question, the delayed nature of the response makes it difficult to capture the immediate, in-the-moment appraisal that occurs when the stressful event actually takes place.
-
-## Hands-on advice for using wrist-worn fitness trackers for research
-
-For researchers aiming to use fitness trackers to collect data, there are practical aspects to consider concerning the design, data collection, and data analysis phases of research projects [for an additional overview, see @nelson2020guidelines]:
-
 ```{r regressions, include=FALSE}
@@
 
-\captionof{table}{\\
-Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
+\captionof{table}{Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
 
@@
     $\Delta$ R\textsuperscript{2} & & & $.003$ & & $.040$ & & $.010$ & & $.012$ & & $.011$ & & $.065$ \\
+    \label{tab_4}
 \end{longtable}
@@
 \footnotesize
-\item Note.
-In Model 1, mean standardized HR and mean slopes were predicted only by teaching experience.
+\item \textit{Note.} In Model 1, mean standardized HR and mean slopes were predicted only by teaching experience.
 In Model 2, solely disruption appraisal was added to teaching experience as a predictor.
@@
 ```
+\noindent Finally, and most importantly, the highly controlled teaching situation that we created in the lab might not have provided sufficient resemblance to the expert teachers’ working conditions to let them effectively use their coping resources.
+In other words, since the situation was unfamiliar to both experienced and unexperienced teachers, their stress levels might have been more similar than they would have been in a more authentic classroom setting.
+
+While we did not find a buffering effect of teaching experience on mean HR during teaching, we did, however, find a less steep HR increase in more experienced, compared to less experienced teachers during the *pre-teaching phase* ($\beta = -.27$), i.e., in preparation for the micro-teaching unit.
+This finding supports the idea that, even though teaching experience guarantees neither superior expertise nor stress resistance, the habits and routines formed by experienced teachers may at least lead to lower arousal levels (e.g., experienced as feeling less nervous and tense) when they anticipate potentially stressful teaching situations.
+
+An interesting observation beyond our hypotheses was that teaching experience was predictive of HR differences, not during teaching, but in the *interview phase*: compared to less experienced teachers, more experienced teachers showed a higher mean standardized HR ($\beta = .24$) and, thus, probably experienced higher levels of physiological stress during the SRI.
+One possible explanation for this finding could again be the higher age of the more experienced teachers, along with slower recovery from stress in older teachers.
+For instance, @ritvanen2006responses observed that, compared to their younger colleagues, older teachers did not experience a decrease in their HR during periods of low stress levels, from which they concluded that recovery from stress was insufficient in the older teachers [@ritvanen2006responses].
+Alternatively, the finding could also be attributed to the fact that less experienced teachers, due to their ongoing or only recently concluded training, may have been more accustomed to reflecting on their work and receiving feedback as was the case during the SRI, whereas, these activities were less routine and possibly more face-threatening for experienced teachers.
+Therefore, it is possible that more experienced teachers found the interview itself to be more stressful and therefore showed a higher mean standardized HR during this phase.
+
+With regards to the predictive power of teachers’ subjective appraisals of the classroom disruption during teaching, we, first of all, have to conclude that our hypotheses were not supported, as neither confidence appraisal nor disruptiveness appraisal showed any notable correlations with teachers’ mean standardized HR or any explanatory power over and beyond teaching experience.
+Possibly, teachers’ self-reported appraisals, and their actual physiological stress responses, tap into quite different phenomena, or at least, quite different aspects of the multifaceted stress response [@kyriacou1978].
+In addition, while HR was assessed online during teaching, self-reported appraisals were given in retrospect during the SRI, and may be subject to biased (e.g., self-serving) reporting or simply an inability to recall ones immediate stress reactions.
+
+On the other hand, when controlling for all other factors, teachers who reported to have perceived the events as more disruptive showed a higher HR ($\beta = .25$) in the phase immediately following the micro-teaching unit.
+This finding would be consistent with the idea that differences in mean HR, as an indicator of the physiological stress response, can be linked to the cognitive appraisal of stressors.
+
+## Limitations and future directions
+
+While the laboratory setting of the study allowed for a controlled implementation of stressors and high internal validity, it was not an authentic classroom environment, raising questions about its external validity.
+Most importantly, the teacher and their students did not have a shared history, and only a very thin basis for establishing a positive teacher-student relationship, which is a core characteristic of effective classroom management [@ruedi2014; @beaty2010].
+In addition, the micro-teaching unit was only about 15 minutes long, and thus much shorter than a regular school lesson, providing less opportunities for experienced teachers to build up an engaging lesson.
+Finally, student behavior was scripted, with classroom disruptions following the experimental schedule, irrelevant of the behavior of the teacher.
+Thus, the setting may have masked effects of teaching experience by providing too little opportunities of experienced teachers to demonstrate their true classroom management skills, in particular regarding the prevention of disruptions.
+In subsequent studies, it would therefore be insightful to assess teachers’ HR in more authentic classroom settings over a longer period of time (e.g., days, weeks, or even months).
+Extended observation of teachers’ HR in authentic classroom settings could reveal how factors such as student behavior, teaching methods, or organizational and administrative demands contribute to fluctuations in physiological arousal, uncovering insights into the sustained physiological demands of teaching that short-term studies may overlook.
+Finally, linking actual teacher behavior to potential stressors (e.g., classroom disruptions, noise level, etc.) would offer insights into teacher coping strategies and their links with physiological indicators of stress.
+
+Another limitation concerns the assessment of teachers’ HR.
+While our results demonstrate the usefulness of drawing upon easily available HR data from ubiquitous, low-cost, un-intrusive fitness trackers to estimate teacher stress, there also are shortcomings of this type of assessment.
+First, while fitness trackers typically yield HR data, heart rate variability (HRV) has been demonstrated to be an even more accurate indicator of stress [@wettstein2020ambulatory].
+While standard fitness trackers did not provide this measure at the time of our data collection, more recent products do offer this function.
+Thus, future studies might consider assessing HRV instead of HR.
+Second, we did not record participants’ resting HR, which is generally considered an important baseline for determining inter- and intrapersonal differences in cardiovascular health and reactivity [@nanchen2018; @heneghan2019].
+A clean baseline HR requires a resting phase without physical movement or emotional stress, ideally fifteen minutes before the beginning of the activity, which is very difficult to achieve in practice [@sammito2015guideline], e.g., when assessing teacher HR before and during teaching.
+Thus, our study explored the possibility of substituting baseline HR measurement via z-standardization within participants.
+As a result, the absolute standardized values of each participant must always be interpreted in the context of the standardization sample, and thus are less interpretable than individual BPM values together with a baseline HR.
+However, for statistical analyses based on the whole sample, the standardization fulfills the aim of controlling for differences in individual HR due to, for example, age-related differences.
+Finally, depending on the brand and model of fitness trackers used, the precision of the HR measurement varies.
+Research on the reliability of our deployed Fitbit® device has proven that this brand is generally accurate in controlled settings and for moderate activity levels [@wallen2016accuracy; @hajj2023; @fuller2020; @jo2016], as in our study.
+For example, the Fitbit® fitness tracker has previously shown good HR measurement accuracy during resting phases [@jo2016; @muggeridge2021measurement] and for activities such as walking, jogging, and running [@hajj2023].
+At higher exercise intensities such as cycling, the Fitbit® tracker may underestimate HR [@thomson2019heart; @montoye2017comparative; @jo2016; @jachymek2021] but is still within an acceptable range according to systematic reviews [@chevance2022accuracy].
+Nevertheless, @gagnon2022 stressed that Fitbit® trackers cannot replace ECG when precision is paramount.
+Despite these considerations, the Fitbit® model appears suitable for our study purposes, as physical strain was moderate.
+
+Furthermore, while we assessed teachers’ appraisals of the stressful classroom disruptions using a SRI in which they could review the exact situation, these appraisal ratings were still post-hoc self-reports, which limits the interpretation of our results.
+One of the main issues with post-hoc self-reports is that they rely on the teachers’ memories and subjective interpretations of past events, which may be prone to various biases such as social desirability [@razavi2001self] or recall errors [@van2016accuracy].
+Moreover, stress is not a fixed or stable construct; it is a dynamic, constantly evolving affective response that can vary depending on context, individual disposition, and prior experiences, making it particularly challenging to pinpoint valid and reliable process markers for how individuals appraise stress in real-time [@lazarus1990theory].
+While SRIs provide a more detailed and reflective understanding of the stressor in question, the delayed nature of the response makes it difficult to capture the immediate, in-the-moment appraisal that occurs when the stressful event actually takes place.
+
+## Hands-on advice for using wrist-worn fitness trackers for research
+
+For researchers aiming to use fitness trackers to collect data, there are practical aspects to consider concerning the design, data collection, and data analysis phases of research projects [for an additional overview, see @nelson2020guidelines]:
 
@@
 Results suggest that the widespread availability of HR data from wearable fitness trackers, moving “from heartbeat to data”, presents opportunities both to teachers for self-monitoring stress levels, and to researchers for assessing physiological indicators of stress.
-For example, using fitness trackers could enable teachers to strengthen their self-awareness in stressful situations and allow for early self-intervention such as mindfulness techniques (e.g., deep breathing or body scans) [@agyapong2023interventions].
+For example, using fitness trackers could enable teachers to strengthen their self-awareness in stressful situations and allow for early self-intervention such as mindfulness techniques (e.g., deep breathing or body scans; @agyapong2023interventions).
 Integrating fitness trackers into teacher training and everyday practice could offer an affordable and practical method for assessing and managing teacher stress.
@@
         \toprule
-        \textbf{Verbal disruptions} & \textbf{Physical disruptions} & \textbf{Lack of eagerness to learn} \\
+        Verbal disruptions & Physical disruptions & Lack of eagerness to learn \\
         \midrule
@@
     \end{tabularx}
-    \label{tab.a1}
+    \label{tab_a1}
 \end{table}
@@
   \caption{\\
-  Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
+  Laboratory setting of the micro-teaching unit. .}
   \includegraphics[width=0.5\textwidth]{appendix_figure1.png}
+  \caption*{\textit{Note.} The setting included three actors as the class (left) and a teacher (participant, right).}
   \label{fig.a1}
@@
   \centering\caption{\\
-  Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
+  Laboratory setting of the interview.}
   \includegraphics[width=0.5\textwidth]{appendix_figure2.png}
+  \caption*{\textit{Note.} The experimenter and participant watched the previously taught micro-teaching unit on video.}
   \label{fig.a2}

### 2024-09-26 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
paar fehler behoben

@@
   \fnref{2}}
-   \ead{peer.kessler@uni-greifswald.de.com} 
-    \author[Leipzig University, Max Planck Institute for Evolutionary
-Anthropology]{Gregor Kachel%
+   \ead{peer.kessler@uni-greifswald.de} 
+    \author[Max Planck Institute for Evolutionary Anthropology]{Gregor
+Kachel%
   %
-  \fnref{1}}
+  \fnref{3}}
    \ead{gregor@example.com} 
@@
   %
-  \fnref{1}}
+  \fnref{4}}
    \ead{christin.lotz@uni-leipzig.de} 
@@
   %
-  \fnref{3}}
+  \fnref{5}}
    \ead{anne.deiglmayr@uni-leipzig.de} 
@@
     \cortext[cor1]{Corresponding author}
-    \fntext[1]{Conceptualization,Writing - Original Draft
-Preparation,Writing - Review \& Editing}
-    \fntext[2]{Writing - Original Draft Preparation,Writing - Review \&
+    \fntext[1]{Conceptualization, Methodology, Formal analysis,
+Investigation, Data Curation, Writing - Original Draft}
+    \fntext[2]{Conceptualization, Methodology, Writing - Review \&
+Editing, Supervision}
+    \fntext[3]{Formal analysis, Data Curation, Writing - Review \&
 Editing}
-    \fntext[3]{Supervision}
+    \fntext[4]{Conceptualization, Methodology, Writing - Review \&
+Editing}
+    \fntext[5]{Conzeptualization, Methodology, Writing - Review \&
+Editing, Supervision}
 
@@
 (e.g., chatting with a neighbor, heckling, looking at the phone; see
-Table \#\# in the supplementary material for an overview and
+Table \ref{tab_a1} in the supplementary material for an overview and
 categorization of all events; and Figure \ref{fig.a2} in the
@@
 phases, we aggregated HR over a representative 10-minute interval within
-each phase (cf.~Fig. 2). Previous research has indicated that 10-minute
-intervals are a useful duration for analyzing PPG data
+each phase (cf.~Figure \ref{fig.2}). Previous research has indicated
+that 10-minute intervals are a useful duration for analyzing PPG data
 \citep{lu2008can}. The intervals were selected based on the following
@@
 fitness tracker was taken off. All participants were being interviewed
-during this interval. The end interval (I5) comprised the last 10
+during this interval. The end interval (\(I_5\)) comprised the last 10
 minutes before the fitness tracker was taken off.
@@
 To enable visual inspection of HR trends, we displayed smoothed teacher
-HR over the course of the recording\footnote{The curve was smoothed
+HR over the course of the recording.\footnote{The curve was smoothed
   using the geom\_smooth() function from the ggplot2 package in R
@@
   Scatterplot Smoothing). This method fits a polynomial surface
-  determined by one or more numerical predictors, using local fitting.}.
+  determined by one or more numerical predictors, using local fitting.}
 We visually compared unstandardized and standardized HR trends over the
-two-hour recording period\footnote{Note that the study exceeded the
+two-hour recording period.\footnote{Note that the study exceeded the
   planned duration of two hours for a few participants. To avoid
-  distortions when mapping the HR over the course of the study (see Fig.
-  3), the endpoint was set at two hours for all participants, even
-  though data from later time points was used in the \emph{end interval}
-  for a few participants.}. For all further analyses, we used
-standardized rather than unstandardized HR values.
+  distortions when mapping the HR over the course of the study (see
+  Figure \ref{fig.3}), the endpoint was set at two hours for all
+  participants, even though data from later time points was used in the
+  \emph{end interval} for a few participants.} For all further analyses,
+we used standardized rather than unstandardized HR values.
 
@@
 experience and subjective appraisals on \emph{changes} in teachers' HR
-(i.e., mean slopes). Please note: HR levels and changes were not
-regressed on the disruption and confidence appraisals in the
-\emph{pre-teaching interval} (\(I_1\)), because the appraised classroom
-events had not yet taken place in that phase.
+(i.e., mean slopes).\footnote{Please note: HR levels and changes were
+  not regressed on the disruption and confidence appraisals in the
+  \emph{pre-teaching interval} (\(I_1\)), because the appraised
+  classroom events had not yet taken place in that phase.}
 
@@
 
-Table 3 shows the raw correlations among mean standardized HR/mean
-slopes (see Table 2 for means and standard deviations), teaching
-experience (\(M = 5.64\), \(SD = 9.46\)), disruption appraisal
-(\(M = 5.19\), \(SD = 2.87\)), and confidence appraisal (\(M = 7.81\),
-\(SD = 1.97\)). With a few notable exceptions, correlations with HR
-measures were mostly very small and statistically non-significant (Table
-3). Correlations between teaching experience and appraisals (not shown
-in Table 3) were substantial: more experienced teachers gave lower
-disruption appraisals (\(r = -.36\)), and higher confidence appraisals
-(\(r = .44\)). Moreover, the two appraisal variables were negatively
-correlated (\(r = -.37\)).
-
-Table 4 shows the results of the regression analyses. Teaching
+Table \ref{tab_3} shows the raw correlations among mean standardized
+HR/mean slopes (see Table \ref{tab_2} for means and standard
+deviations), teaching experience (\(M = 5.64\), \(SD = 9.46\)),
+disruption appraisal (\(M = 5.19\), \(SD = 2.87\)), and confidence
+appraisal (\(M = 7.81\), \(SD = 1.97\)). With a few notable exceptions,
+correlations with HR measures were mostly very small and statistically
+non-significant (Table 3). Correlations between teaching experience and
+appraisals (not shown in Table \ref{tab_3}) were substantial: more
+experienced teachers gave lower disruption appraisals (\(r = -.36\)),
+and higher confidence appraisals (\(r = .44\)). Moreover, the two
+appraisal variables were negatively correlated (\(r = -.37\)).
+
+Table \ref{tab_4} shows the results of the regression analyses. Teaching
 experience significantly predicted mean standardized HR only in the
-\emph{interview interval} (Table 4, Interview interval, Model 1),
-indicating a higher mean standardized HR for teachers with more teaching
-experience. This relationship is, in fact, in the opposite direction as
-predicted by Hypothesis 2a. Neither adding disruption appraisal
-(\textbf{Hypothesis 2b}) nor adding confidence appraisal
-(\textbf{Hypothesis 2c}) increased the amount of explained variance to a
-statistically significant extent.
+\emph{interview interval} (Table \ref{tab_4}, \emph{interview interval},
+Model 1), indicating a higher mean standardized HR for teachers with
+more teaching experience. This relationship is, in fact, in the opposite
+direction as predicted by Hypothesis 2a. Neither adding disruption
+appraisal (Hypothesis 2b) nor adding confidence appraisal (Hypothesis
+2c) increased the amount of explained variance to a statistically
+significant extent.
 
 When considering the effects of the three predictors in concert
-(\textbf{Hypothesis 2d}), mean standardized HR was significantly
-predicted only by disruption appraisal, and only in the
-\emph{post-teaching interval} (Table 4, Post-teaching interval, Model
-4), indicating a higher mean standardized HR for teachers who felt more
-disrupted by the classroom events, when controlling for the other
-variables.
+(Hypothesis 2d), mean standardized HR was significantly predicted only
+by disruption appraisal, and only in the \emph{post-teaching interval}
+(Table \ref{tab_4}, \emph{post-teaching interval}, Model 4), indicating
+a higher mean standardized HR for teachers who felt more disrupted by
+the classroom events, when controlling for the other variables.
 
@@
 better indicator of expertise that future studies could explore.
-Finally, and most importantly, the highly controlled teaching situation
-that we created in the lab might not have provided sufficient
+
+\begin{landscape}
+
+\setlength{\LTleft}{0pt}
+\setlength{\LTright}{0pt}
+
+\captionof{table}{Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
+
+\begin{longtable}{@{\extracolsep{\fill}} p{1.8cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} @{}}
+
+    \toprule
+    & \multicolumn{4}{c}{Model 1} & \multicolumn{4}{c}{Model 2} & \multicolumn{4}{c}{Model 3} & \multicolumn{4}{c}{Model 4} \\
+    \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13} \cmidrule(lr){14-17}
+    Dependent \newline variable: & \multicolumn{16}{c}{Mean standardized HR and mean slopes} \\
+    \cmidrule(lr){2-17}
+    & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
+HR} & \multicolumn{2}{c}{Mean slopes} \\
+    & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ \\
+    \midrule
+    \endfirsthead
+
+    \toprule
+    & \multicolumn{4}{c}{Model 1} & \multicolumn{4}{c}{Model 2} & \multicolumn{4}{c}{Model 3} & \multicolumn{4}{c}{Model 4} \\
+    \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13} \cmidrule(lr){14-17}
+    Dependent variable: & \multicolumn{16}{c}{Mean standardized HR and mean slopes} \\
+    \cmidrule(lr){2-17}
+    & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ \\
+    \midrule
+    \endhead
+
+    \bottomrule
+    \multicolumn{17}{c}{{Continued on next page}} \\
+    \endfoot
+
+    \bottomrule
+    \endlastfoot
+
+    Pre-teaching \newline interval ($I_1$) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.17$\\$(.005)$\end{tabular} & $.12$ & \begin{tabular}{@{}c@{}}$-.27^*$\\$(.002)$\end{tabular} & $<.05$ & & & & & & & & & & & & \\
+    R\textsuperscript{2} & $.030$ & & $.071$ & & & & & & & & & & & & & \\
+    \midrule
+    Teaching \newline interval ($I_2$) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.11$\\$(.002)$\end{tabular} & $.34$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.83$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.73$ & \begin{tabular}{@{}c@{}}$.01$\\$(.001)$\end{tabular} & $.96$ & \begin{tabular}{@{}c@{}}$.10$\\$(.006)$\end{tabular} & $.42$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.001)$\end{tabular} & $.54$ & \begin{tabular}{@{}c@{}}$.05$\\$(.006)$\end{tabular} & $.67$ & \begin{tabular}{@{}c@{}}$-.05$\\$(.001)$\end{tabular} & $.72$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$-.18$\\$(.041)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.08$\\$(.010)$\end{tabular} & $.50$ & \begin{tabular}{@{}c@{}}$-.19$\\$(.042)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.12$\\$(.010)$\end{tabular} & $.34$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$.01$\\$(.046)$\end{tabular} & $.92$ & \begin{tabular}{@{}c@{}}$.12$\\$(.011)$\end{tabular} & $.34$ & \begin{tabular}{@{}c@{}}$-.04$\\$(.047)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$.15$\\$(.012)$\end{tabular} & $.24$ \\
+    R\textsuperscript{2} & $.012$ & & $.000$ & & $.040$ & & $.015$ & & $.012$ & & $.010$ & & $.042$ & & $.031$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.028$ & & $.015$ & & $.000$ & & $.010$ & & $.030$ & & $.031$ \\
+    \midrule
+    Post-teaching \newline interval ($I_3$) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.04$\\$(.005)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$-.03$\\$(.001)$\end{tabular} & $.80$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$-.09$\\$(.001)$\end{tabular} & $.44$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.006)$\end{tabular} & $.55$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.89$ & \begin{tabular}{@{}c@{}}$-.01$\\$(.006)$\end{tabular} & $.91$ & \begin{tabular}{@{}c@{}}$-.07$\\$(.001)$\end{tabular} & $.61$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$.22$\\$(.040)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$-.18$\\$(.009)$\end{tabular} & $.14$ & \begin{tabular}{@{}c@{}}$.25^*$\\$(.041)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.20$\\$(.010)$\end{tabular} & $.12$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$.08$\\$(.045)$\end{tabular} & $.55$ & \begin{tabular}{@{}c@{}}$-.03$\\$(.011)$\end{tabular} & $.83$ & \begin{tabular}{@{}c@{}}$.14$\\$(.046)$\end{tabular} & $.27$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.011)$\end{tabular} & $.54$ \\
+    R\textsuperscript{2} & $.002$ & & $.001$ & & $.043$ & & $.020$ & & $.006$ & & $.002$ & & $.058$ & & $.023$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.041$ & & $.019$ & & $.004$ & & $.001$ & & $.056$ & & $.022$ \\
+    \midrule
+    Interview \newline interval ($I_4$) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.24^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.20$\\$(.001)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$.22$\\$(.006)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$-.23$\\$(.001)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$.25^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.14$\\$(.001)$\end{tabular} & $.25$ & \begin{tabular}{@{}c@{}}$.23$\\$(.007)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$-.17$\\$(.001)$\end{tabular} & $.18$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$-.05$\\$(.045)$\end{tabular} & $.66$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.006)$\end{tabular} & $.52$ & \begin{tabular}{@{}c@{}}$-.06$\\$(.047)$\end{tabular} & $.61$ & \begin{tabular}{@{}c@{}}$-.12$\\$(.007)$\end{tabular} & $.34$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$-.02$\\$(.050)$\end{tabular} & $.85$ & \begin{tabular}{@{}c@{}}$-.13$\\$(.007)$\end{tabular} & $.29$ & \begin{tabular}{@{}c@{}}$-.04$\\$(.052)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$-.16$\\$(.007)$\end{tabular} & $.20$ \\
+    R\textsuperscript{2} & $.058$ & & $.040$ & & $.060$ & & $.050$ & & $.058$ & & $.054$ & & $.061$ & & $.069$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.002$ & & $.010$ & & $.000$ & & $.014$ & & $.003$ & & $.029$ \\
+    \midrule
+    End \newline interval ($I_5$) & & & & & & & & & & & & & & & & \\
+    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.04$\\$(.004)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$.11$\\$(.001)$\end{tabular} & $.32$ & \begin{tabular}{@{}c@{}}$.07$\\$(.005)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.18$\\$(.001)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.09$\\$(.005)$\end{tabular} & $.46$ & \begin{tabular}{@{}c@{}}$.07$\\$(.001)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.10$\\$(.005)$\end{tabular} & $.43$ & \begin{tabular}{@{}c@{}}$.12$\\$(.001)$\end{tabular} & $.33$ \\
+    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$.06$\\$(.035)$\end{tabular} & $.60$ & \begin{tabular}{@{}c@{}}$.19$\\$(.007)$\end{tabular} & $.12$ & \begin{tabular}{@{}c@{}}$.04$\\$(.037)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$.23$\\$(.007)$\end{tabular} & $.07$ \\
+    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$-.11$\\$(.039)$\end{tabular} & $.38$ & \begin{tabular}{@{}c@{}}$.10$\\$(.008)$\end{tabular} & $.43$ & \begin{tabular}{@{}c@{}}$-.10$\\$(.041)$\end{tabular} & $.44$ & \begin{tabular}{@{}c@{}}$.16$\\$(.008)$\end{tabular} & $.22$ \\
+    R\textsuperscript{2} & $.002$ & & $.013$ & & $.005$ & & $.053$ & & $.012$ & & $.025$ & & $.013$ & & $.078$ \\
+    $\Delta$ R\textsuperscript{2} & & & $.003$ & & $.040$ & & $.010$ & & $.012$ & & $.011$ & & $.065$ \\
+    \label{tab_4}
+\end{longtable}
+\begin{tablenotes}
+\footnotesize
+\item \textit{Note.} In Model 1, mean standardized HR and mean slopes were predicted only by teaching experience.
+In Model 2, solely disruption appraisal was added to teaching experience as a predictor.
+In Model 3, solely confidence appraisal was added to teaching experience as a predictor.
+In Model 4, all three predictors were considered in concert.
+* $p < .05$.
+\end{tablenotes}
+\end{landscape}
+
+\noindent Finally, and most importantly, the highly controlled teaching
+situation that we created in the lab might not have provided sufficient
 resemblance to the expert teachers' working conditions to let them
@@
 more experienced, compared to less experienced teachers during the
-pre-teaching phase (\(\beta = -.27\)), i.e., in preparation for the
-micro-teaching unit. This finding supports the idea that, even though
-teaching experience guarantees neither superior expertise nor stress
-resistance, the habits and routines formed by experienced teachers may
-at least lead to lower arousal levels (e.g., experienced as feeling less
-nervous and tense) when they anticipate potentially stressful teaching
-situations.
+\emph{pre-teaching phase} (\(\beta = -.27\)), i.e., in preparation for
+the micro-teaching unit. This finding supports the idea that, even
+though teaching experience guarantees neither superior expertise nor
+stress resistance, the habits and routines formed by experienced
+teachers may at least lead to lower arousal levels (e.g., experienced as
+feeling less nervous and tense) when they anticipate potentially
+stressful teaching situations.
 
@@
 experience was predictive of HR differences, not during teaching, but in
-the interview phase: compared to less experienced teachers, more
+the \emph{interview phase}: compared to less experienced teachers, more
 experienced teachers showed a higher mean standardized HR
@@
 appraisal nor disruptiveness appraisal showed any notable correlations
-with teachers' means standardized HR or any explanatory power over and
+with teachers' mean standardized HR or any explanatory power over and
 beyond teaching experience. Possibly, teachers' self-reported
@@
 in retrospect during the SRI, and may be subject to biased (e.g.,
-self-serving) reporting or simply an inability to recall one´s immediate
+self-serving) reporting or simply an inability to recall ones immediate
 stress reactions.
@@
 
-\begin{landscape}
-
-\setlength{\LTleft}{0pt}
-\setlength{\LTright}{0pt}
-
-\captionof{table}{\\
-Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
-
-\begin{longtable}{@{\extracolsep{\fill}} p{1.8cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} @{}}
-
-    \toprule
-    & \multicolumn{4}{c}{Model 1} & \multicolumn{4}{c}{Model 2} & \multicolumn{4}{c}{Model 3} & \multicolumn{4}{c}{Model 4} \\
-    \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13} \cmidrule(lr){14-17}
-    Dependent \newline variable: & \multicolumn{16}{c}{Mean standardized HR and mean slopes} \\
-    \cmidrule(lr){2-17}
-    & \multicolumn{2}{c}{Mean std.
-HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
-HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
-HR} & \multicolumn{2}{c}{Mean slopes} & \multicolumn{2}{c}{Mean std.
-HR} & \multicolumn{2}{c}{Mean slopes} \\
-    & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ \\
-    \midrule
-    \endfirsthead
-
-    \toprule
-    & \multicolumn{4}{c}{Model 1} & \multicolumn{4}{c}{Model 2} & \multicolumn{4}{c}{Model 3} & \multicolumn{4}{c}{Model 4} \\
-    \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13} \cmidrule(lr){14-17}
-    Dependent variable: & \multicolumn{16}{c}{Mean standardized HR and mean slopes} \\
-    \cmidrule(lr){2-17}
-    & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ & $\beta$ (SE) & $p$ \\
-    \midrule
-    \endhead
-
-    \bottomrule
-    \multicolumn{17}{c}{{Continued on next page}} \\
-    \endfoot
-
-    \bottomrule
-    \endlastfoot
-
-    Pre-teaching \newline interval ($I_1$) & & & & & & & & & & & & & & & & \\
-    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.17$\\$(.005)$\end{tabular} & $.12$ & \begin{tabular}{@{}c@{}}$-.27^*$\\$(.002)$\end{tabular} & $<.05$ & & & & & & & & & & & & \\
-    R\textsuperscript{2} & $.030$ & & $.071$ & & & & & & & & & & & & & \\
-    \midrule
-    Teaching \newline interval ($I_2$) & & & & & & & & & & & & & & & & \\
-    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.11$\\$(.002)$\end{tabular} & $.34$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.83$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.73$ & \begin{tabular}{@{}c@{}}$.01$\\$(.001)$\end{tabular} & $.96$ & \begin{tabular}{@{}c@{}}$.10$\\$(.006)$\end{tabular} & $.42$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.001)$\end{tabular} & $.54$ & \begin{tabular}{@{}c@{}}$.05$\\$(.006)$\end{tabular} & $.67$ & \begin{tabular}{@{}c@{}}$-.05$\\$(.001)$\end{tabular} & $.72$ \\
-    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$-.18$\\$(.041)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.08$\\$(.010)$\end{tabular} & $.50$ & \begin{tabular}{@{}c@{}}$-.19$\\$(.042)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.12$\\$(.010)$\end{tabular} & $.34$ \\
-    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$.01$\\$(.046)$\end{tabular} & $.92$ & \begin{tabular}{@{}c@{}}$.12$\\$(.011)$\end{tabular} & $.34$ & \begin{tabular}{@{}c@{}}$-.04$\\$(.047)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$.15$\\$(.012)$\end{tabular} & $.24$ \\
-    R\textsuperscript{2} & $.012$ & & $.000$ & & $.040$ & & $.015$ & & $.012$ & & $.010$ & & $.042$ & & $.031$ \\
-    $\Delta$ R\textsuperscript{2} & & & $.028$ & & $.015$ & & $.000$ & & $.010$ & & $.030$ & & $.031$ \\
-    \midrule
-    Post-teaching \newline interval ($I_3$) & & & & & & & & & & & & & & & & \\
-    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$-.04$\\$(.005)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$-.03$\\$(.001)$\end{tabular} & $.80$ & \begin{tabular}{@{}c@{}}$.04$\\$(.005)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$-.09$\\$(.001)$\end{tabular} & $.44$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.006)$\end{tabular} & $.55$ & \begin{tabular}{@{}c@{}}$-.02$\\$(.001)$\end{tabular} & $.89$ & \begin{tabular}{@{}c@{}}$-.01$\\$(.006)$\end{tabular} & $.91$ & \begin{tabular}{@{}c@{}}$-.07$\\$(.001)$\end{tabular} & $.61$ \\
-    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$.22$\\$(.040)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$-.18$\\$(.009)$\end{tabular} & $.14$ & \begin{tabular}{@{}c@{}}$.25^*$\\$(.041)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.20$\\$(.010)$\end{tabular} & $.12$ \\
-    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$.08$\\$(.045)$\end{tabular} & $.55$ & \begin{tabular}{@{}c@{}}$-.03$\\$(.011)$\end{tabular} & $.83$ & \begin{tabular}{@{}c@{}}$.14$\\$(.046)$\end{tabular} & $.27$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.011)$\end{tabular} & $.54$ \\
-    R\textsuperscript{2} & $.002$ & & $.001$ & & $.043$ & & $.020$ & & $.006$ & & $.002$ & & $.058$ & & $.023$ \\
-    $\Delta$ R\textsuperscript{2} & & & $.041$ & & $.019$ & & $.004$ & & $.001$ & & $.056$ & & $.022$ \\
-    \midrule
-    Interview \newline interval ($I_4$) & & & & & & & & & & & & & & & & \\
-    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.24^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.20$\\$(.001)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$.22$\\$(.006)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$-.23$\\$(.001)$\end{tabular} & $.06$ & \begin{tabular}{@{}c@{}}$.25^*$\\$(.006)$\end{tabular} & $<.05$ & \begin{tabular}{@{}c@{}}$-.14$\\$(.001)$\end{tabular} & $.25$ & \begin{tabular}{@{}c@{}}$.23$\\$(.007)$\end{tabular} & $.07$ & \begin{tabular}{@{}c@{}}$-.17$\\$(.001)$\end{tabular} & $.18$ \\
-    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$-.05$\\$(.045)$\end{tabular} & $.66$ & \begin{tabular}{@{}c@{}}$-.08$\\$(.006)$\end{tabular} & $.52$ & \begin{tabular}{@{}c@{}}$-.06$\\$(.047)$\end{tabular} & $.61$ & \begin{tabular}{@{}c@{}}$-.12$\\$(.007)$\end{tabular} & $.34$ \\
-    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$-.02$\\$(.050)$\end{tabular} & $.85$ & \begin{tabular}{@{}c@{}}$-.13$\\$(.007)$\end{tabular} & $.29$ & \begin{tabular}{@{}c@{}}$-.04$\\$(.052)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$-.16$\\$(.007)$\end{tabular} & $.20$ \\
-    R\textsuperscript{2} & $.058$ & & $.040$ & & $.060$ & & $.050$ & & $.058$ & & $.054$ & & $.061$ & & $.069$ \\
-    $\Delta$ R\textsuperscript{2} & & & $.002$ & & $.010$ & & $.000$ & & $.014$ & & $.003$ & & $.029$ \\
-    \midrule
-    End \newline interval ($I_5$) & & & & & & & & & & & & & & & & \\
-    Teaching \newline Experience & \begin{tabular}{@{}c@{}}$.04$\\$(.004)$\end{tabular} & $.70$ & \begin{tabular}{@{}c@{}}$.11$\\$(.001)$\end{tabular} & $.32$ & \begin{tabular}{@{}c@{}}$.07$\\$(.005)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.18$\\$(.001)$\end{tabular} & $.13$ & \begin{tabular}{@{}c@{}}$.09$\\$(.005)$\end{tabular} & $.46$ & \begin{tabular}{@{}c@{}}$.07$\\$(.001)$\end{tabular} & $.58$ & \begin{tabular}{@{}c@{}}$.10$\\$(.005)$\end{tabular} & $.43$ & \begin{tabular}{@{}c@{}}$.12$\\$(.001)$\end{tabular} & $.33$ \\
-    Disruption \newline Appraisal & \begin{tabular}{@{}c@{}}$.06$\\$(.035)$\end{tabular} & $.60$ & \begin{tabular}{@{}c@{}}$.19$\\$(.007)$\end{tabular} & $.12$ & \begin{tabular}{@{}c@{}}$.04$\\$(.037)$\end{tabular} & $.76$ & \begin{tabular}{@{}c@{}}$.23$\\$(.007)$\end{tabular} & $.07$ \\
-    Confidence \newline Appraisal & \begin{tabular}{@{}c@{}}$-.11$\\$(.039)$\end{tabular} & $.38$ & \begin{tabular}{@{}c@{}}$.10$\\$(.008)$\end{tabular} & $.43$ & \begin{tabular}{@{}c@{}}$-.10$\\$(.041)$\end{tabular} & $.44$ & \begin{tabular}{@{}c@{}}$.16$\\$(.008)$\end{tabular} & $.22$ \\
-    R\textsuperscript{2} & $.002$ & & $.013$ & & $.005$ & & $.053$ & & $.012$ & & $.025$ & & $.013$ & & $.078$ \\
-    $\Delta$ R\textsuperscript{2} & & & $.003$ & & $.040$ & & $.010$ & & $.012$ & & $.011$ & & $.065$ \\
-\end{longtable}
-\begin{tablenotes}
-\footnotesize
-\item Note.
-In Model 1, mean standardized HR and mean slopes were predicted only by teaching experience.
-In Model 2, solely disruption appraisal was added to teaching experience as a predictor.
-In Model 3, solely confidence appraisal was added to teaching experience as a predictor.
-In Model 4, all three predictors were considered in concert.
-* $p < .05$.
-\end{tablenotes}
-\end{landscape}
-
 \begin{enumerate}
@@
 stressful situations and allow for early self-intervention such as
-mindfulness techniques (e.g., deep breathing or body scans)
-\citep{agyapong2023interventions}. Integrating fitness trackers into
+mindfulness techniques (e.g., deep breathing or body scans;
+\citet{agyapong2023interventions}). Integrating fitness trackers into
 teacher training and everyday practice could offer an affordable and

### 2024-09-27 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission_template.Rmd
nochmal formatiert

--- 2024-09-26 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
@@
   - code: Leipzig University
-    organization: Empirische Schul- und Unterrichtsforschung
+    organization: Division of Empirical School and Classroom Research, Institute of Educational Sciences
     addressline: Marschnerstr. 29
@@
   - code: University of Greifswald
-    organization: Institute of Psychology
+    organization: Division of Health and Prevention, Institute of Psychology
     addressline: Robert-Blum-Str. 13
@@
 date: "`r Sys.Date()`"
-classoption: preprint, 3p, authoryear
+classoption: preprint, 3p
 bibliography: r-references.bib
@@
 header-includes:
+  - \setcitestyle{sort&compress}
   - \usepackage{tabularx}
@@
 
-Figure \ref{fig.1} shows, in a simplified way, how classroom events affect teachers’ stress level, according to the adaptation of the Lazarus model to teacher stress proposed by @van2006stress: When potential stressors (e.g., classroom disruptions) occur during teaching (1), teachers intuitively judge how disruptive the event is in a primary appraisal (2).
+Fig.\ref{fig.1} shows, in a simplified way, how classroom events affect teachers’ stress level, according to the adaptation of the Lazarus model to teacher stress proposed by @van2006stress: When potential stressors (e.g., classroom disruptions) occur during teaching (1), teachers intuitively judge how disruptive the event is in a primary appraisal (2).
 If potential stressors are judged as threatening, i.e., as actual stressors (3), teachers consider whether they have sufficient resources for coping with the stressors (4).
@@
 
-As shown in Figure \ref{fig.1}, teachers’ primary and secondary appraisal as well as coping attempts are influenced by professional experience.
+As shown in Fig.\ref{fig.1}, teachers’ primary and secondary appraisal as well as coping attempts are influenced by professional experience.
 As professional experience grows, teachers develop cognitive scripts for managing classroom events, resulting in more complex and problem-focused classroom management skills [@wolff2021classroom], and thus more effective coping and less stress.
@@
 \captionsetup[figure]{
-    labelfont=bf,       % Figure label bold (not italic)
-    labelsep=newline,      % Period after Figure label
-    textfont=it,          % Italic font for the caption text
-    font=small,           % Smaller font size for APA style
+    labelsep=colon,      % Period after Figure label
+    font=footnotesize,           % Smaller font size for APA style
     justification=justified, % Left-justified captions, as per APA guidelines
@@
 \captionsetup[table]{
-    labelfont=bf,        % Figure label bold (not italic)
-    labelsep=newline,      % Period after Figure label
-    textfont=it,          % Italic font for the caption text
-    font=small,           % Smaller font size for APA style
+    labelsep=colon,      % Period after Figure label
+    font=footnotesize,           % Smaller font size for APA style
     justification=justified, % Left-justified captions, as per APA guidelines
@@
 \begin{figure}[htbp]
-  \caption{\\
-  A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
   \centering
   \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
+  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors).}
   \label{fig.1}
@@
 ```
-
 ## Present Study
@@
 
-In addition, we selected five representative 10-minute intervals from the five phases of the lab study (see Figure \ref{fig.2}) in order to test the hypotheses that, regarding HR levels, teachers’ HR would be the highest during the micro-teaching unit, compared to all other phases (**Hypothesis 1a**), and, regarding HR slopes, that teachers’ HR would increase while they were preparing for teaching (pre-teaching interval), but decrease in all of the following intervals, i.e.
-when they were habituating to and recovering from the stressful micro-teaching unit (**Hypothesis 1b**).
+In addition, we selected five representative 10-minute intervals from the five phases of the lab study (see Fig.\ref{fig.2}) in order to test the hypotheses that, regarding HR levels, teachers’ HR would be the highest during the micro-teaching unit, compared to all other phases (Hypothesis 1a), and, regarding HR slopes, that teachers’ HR would increase while they were preparing for teaching (pre-teaching interval), but decrease in all of the following intervals, i.e.
+when they were habituating to and recovering from the stressful micro-teaching unit (Hypothesis 1b).
 
 (2)	We further explored whether teaching experience made a difference in how teachers’ HR reacted to the classroom disruptions.
-We expected more experienced teachers to be less stressed by the classroom events (**Hypothesis 2a**).
+We expected more experienced teachers to be less stressed by the classroom events (Hypothesis 2a).
 In addition, we examined the relations between teachers’ subjective appraisals of the classroom events (specifically, the disruptiveness of the events, and their confidence in dealing with them) and teachers’ HR level, beyond the explanatory power of teaching experience.
-We expected higher HR levels for teachers who felt more disrupted, regardless of their teaching experience (**Hypothesis 2b**), and lower HR levels for teachers who felt more confident, regardless of teaching experience (**Hypothesis 2c**).
-We hypothesized that each of the three predictors (*teaching experience, disruption appraisal, confidence appraisal*) uniquely contributed to explaining variance in teachers’ HR levels (**Hypothesis 2d**).
+We expected higher HR levels for teachers who felt more disrupted, regardless of their teaching experience (Hypothesis 2b), and lower HR levels for teachers who felt more confident, regardless of teaching experience (Hypothesis 2c).
+We hypothesized that each of the three predictors (*teaching experience, disruption appraisal, confidence appraisal*) uniquely contributed to explaining variance in teachers’ HR levels (Hypothesis 2d).
 In addition, we exploratively ran analogous analyses for the *changes* in HR (i.e., slopes).
@@
 
-Each participant came to the lab for a period of approximately two hours in total, and each participant underwent the same phases (see Figure \ref{fig.2}): In the *pre-teaching phase*, the experimenter welcomed the participants and helped them put on the fitness tracker.
+Each participant came to the lab for a period of approximately two hours in total, and each participant underwent the same phases (see Fig.\ref{fig.2}): In the *pre-teaching phase*, the experimenter welcomed the participants and helped them put on the fitness tracker.
 This was followed by a warm-up session to familiarize the participants with the laboratory setting and the class.
 This phase took about 10-15 minutes and participants spent this time mostly standing or slowly walking around.
-During the *teaching phase*, the participants held their self-prepared micro-teaching unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table \ref{tab_a1} in the supplementary material for an overview and categorization of all events; and Figure \ref{fig.a2} in the supplementary material for a depiction of the laboratory setting of the micro-teaching unit).
+During the *teaching phase*, the participants held their self-prepared micro-teaching unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Tab.\ref{tab_a1} in the supplementary material for an overview and categorization of all events; and Fig.\ref{fig.a2} in the supplementary material for a depiction of the laboratory setting of the micro-teaching unit).
 The topic and class level of the teaching unit could be freely chosen by the teachers with the only requirement that the unit had to be an introductory lesson, and had to consist of supervised individual work and / or frontal teaching.
@@
 While teaching, participants wore eye-tracking glasses, and their lesson was video-recorded.
-After having completed the micro-teaching unit, in the *post-teaching phase*, participants filled in questionnaires for approximately 10-15 minutes: a brief computer-based survey of sociodemographic
-```{=latex}
-\begin{wrapfigure}[36]{r}{0.5\textwidth}
-  \centering
-  \caption{\\
-  Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
-  \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
-  \label{fig.2}
-\end{wrapfigure}
-```
-\noindent data (e.g., teaching experience, gender, studied school type, studied school subjects, extracurricular teaching activities), and a short knowledge test that was irrelevant to the present study.
+After having completed the micro-teaching unit, in the *post-teaching phase*, participants filled in questionnaires for approximately 10-15 minutes: a brief computer-based survey of sociodemographic data (e.g., teaching experience, gender, studied school type, studied school subjects, extracurricular teaching activities), and a short knowledge test that was irrelevant to the present study.
 In the *interview phase*,
@@
 Finally, in the *end phase*, participants filled in another questionnaire irrelevant to the present study, which lasted about 10-15 minutes.
-
+\newpage
+```{=latex}
+\begin{wrapfigure}[36]{r}{0.5\textwidth}
+  \centering
+  \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
+  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals.}
+  \label{fig.2}
+\end{wrapfigure}
+```
 ## Measures
@@
 Since we aimed to keep measurement intervals comparable between study phases, we aggregated HR over a representative 10-minute interval within each phase (cf.
-Figure \ref{fig.2}).
+Fig.\ref{fig.2}).
 Previous research has indicated that 10-minute intervals are a useful duration for analyzing PPG data [@lu2008can].
@@
 [^3]: Note that the study exceeded the planned duration of two hours for a few participants.
-To avoid distortions when mapping the HR over the course of the study (see Figure \ref{fig.3}), the endpoint was set at two hours for all participants, even though data from later time points was used in the *end interval* for a few participants.
+To avoid distortions when mapping the HR over the course of the study (see Fig.\ref{fig.3}), the endpoint was set at two hours for all participants, even though data from later time points was used in the *end interval* for a few participants.
 
@@
 
-[^5]: Although this procedure does not account for nonmonotonic progressions in individual HR, a graphical evaluation revealed that the linear estimates corresponded well to the majority of the cases (see XX in the supplementary material).
+[^5]: Although this procedure does not account for nonmonotonic progressions in individual HR, a graphical evaluation revealed that the linear estimates corresponded well to the majority of the cases (see Fig.\ref{fig.a3} to \ref{fig.a7} in the supplementary material).
 
@@
 
-Means, standard deviations, and range of teachers’ unstandardized and standardized HR for the entire study period, and for the five intervals, are shown in Table \ref{tab_1}.
-Figure \ref{fig.3} displays the unstandardized and standardized HR trends, respectively, over the course of the entire study period.
+Means, standard deviations, and range of teachers’ unstandardized and standardized HR for the entire study period, and for the five intervals, are shown in Tab.\ref{tab_1}.
+Fig.\ref{fig.3} displays the unstandardized and standardized HR trends, respectively, over the course of the entire study period.
 HR initially increased, peaked, and then decreased, with the unstandardized and standardized HR graphs showing high similarity.
@@
 
-Figure \ref{fig.4} shows the distribution of teachers’ mean standardized HR for the five intervals.
+Fig.\ref{fig.4} shows the distribution of teachers’ mean standardized HR for the five intervals.
 Repeated measures ANOVA revealed significant differences in mean standardized HR between intervals, $F(4, 400) = 260.62$, $p < .05$, $d = 1.60$ (large effect).
@@
 Next, we examined HR changes (i.e., mean slopes) within each interval to test the hypothesis that HR increased during the *pre-teaching phase* and decreased during all other phases (Hypothesis 1b).
-The mean intercepts and mean slopes, complemented by their standard deviations for each interval, are shown in Table 2.
+The mean intercepts and mean slopes, complemented by their standard deviations for each interval, are shown in Tab.\ref{tab_2}.
 The mean slope of the *pre-teaching interval* ($I_1$) was significantly positive, indicating an increase in HR, as hypothesized.
@@
     \centering
-    \caption{\\
-    Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
     \begin{tabularx}{\textwidth}{lXXXXX}
@@
     \end{tabularx}
+    \caption{Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
     \label{tab_1}
@@
 the \textit{end interval} ($I_5$) are due to data of a few participants who needed more than two hours to finish the study.}
+
+```
+
+```{r table_2, include=FALSE}
+df_regression <- 
+  main_single_hr |> 
+  filter(time_span != "overall") |> 
+  dplyr::select("ID",
+                "time_span",
+                "time",
+                "heart_rate_std",
+                "heart_rate") |> 
+  distinct() |> 
+  mutate(time = time / 60) |> 
+  mutate(ID = as_factor(ID),
+         Phase = factor(time_span,
+                        levels = c("preparation",
+                                   "teaching",
+                                   "post",
+                                   "interview",
+                                   "end"),
+                        labels = c("Pre Teaching Phase",
+                                   "Teaching Phase",
+                                   "Post Teaching Phase",
+                                   "Interview Phase",
+                                   "End Phase")
+                           )
+         )
+
+fix_models <-
+  df_regression %>%
+  split(.$Phase) %>%
+  map( ~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
+            data = .)) %>%
+  map(
+    ~ coef(.) %>%
+      tibble::as_tibble(.,
+                        rownames = "name") %>%
+      transmute(
+        type = if_else(str_detect(name,
+                                  ":"),
+                       true = "slope",
+                       false = "intercept"),
+        id = str_remove_all(name,
+                            "[^[:digit:]]"),
+        value = value
+      ),
+
+  ) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_wider(names_from = type,
+              values_from = value)
+
+p.values_slope <-
+  fix_models %>%
+  split(.$Phase) %>%
+  map( ~ t.test(x = .$slope,
+                mu = 0)$p.value) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_slope")
+
+p.values_intercept <-
+  fix_models %>%
+  split(.$Phase) %>%
+  map( ~ t.test(x = .$intercept,
+                mu = 0)$p.value) %>%
+  bind_rows(.id = "Phase") %>%
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_intercept")
+
+sd_mean <-
+  fix_models %>%
+  group_by(Phase) %>%
+  dplyr::summarise(
+    mean_slope = mean(slope),
+    sd_slope = sd(slope),
+    mean_intercept = mean(intercept),
+    sd_intercept = sd(intercept)
+  )
+
+table_data <- 
+  right_join(x = sd_mean,
+             y = p.values_intercept,
+             by = "Phase") %>% 
+  right_join(x = .,
+             y = p.values_slope,
+             by = "Phase") %>% 
+  transmute(Phase = factor(Phase,
+                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
+                           ),
+            n = NA,
+            `Mean(Intercept)` = round(mean_intercept, digits = 3),
+            `SD(Intercept)` = round(sd_intercept, digits = 3),
+            `p-Value (Intercept)` = p.value_intercept,
+            `Mean(Slope)` = round(mean_slope, digits = 3), 
+            `SD(Slope)` = round(sd_slope,digits = 3),
+            `p-Value (Slope)` = p.value_slope, 
+            ) %>% 
+  arrange(Phase)
+
+table_data$n[table_data$Phase == "Pre Teaching Phase"] <- df_regression %>% filter(Phase == "Pre Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Teaching Phase"] <- df_regression %>% filter(Phase == "Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Post Teaching Phase"] <- df_regression %>% filter(Phase == "Post Teaching Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "Interview Phase"] <- df_regression %>% filter(Phase == "Interview Phase") %>% pull(heart_rate_std) %>% length()
+table_data$n[table_data$Phase == "End Phase"] <- df_regression %>% filter(Phase == "End Phase") %>% pull(heart_rate_std) %>% length()
+```
+
+```{=latex}
+
+\renewcommand{\arraystretch}{1.5}
+
+\begin{table}[ht]
+    \centering
+    \begin{tabularx}{\textwidth}{lXXXXXX}
+        \toprule
+        Interval  & \multicolumn{2}{c}{\textit{M} (\textit{SD})} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
+        \midrule
+        ($I_1$) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
+        ($I_2$) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
+        ($I_3$) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
+        ($I_4$) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
+        ($I_5$) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
+        \bottomrule
+    \end{tabularx}
+    \caption{Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
+    \label{tab_2}
+\end{table}
 
@@
        width = 25,
-       height = 15,
+       height = 14,
        units = "cm")
@@
   \centering
-  \caption{\\
-  Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
   \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
+  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig.3a. and the z-standardized HR shown in Fig.3b. for the planned 2-hour study.}
   \label{fig.3}
 \end{figure}
-```
-
-```{r table_2, include=FALSE}
-df_regression <- 
-  main_single_hr |> 
-  filter(time_span != "overall") |> 
-  dplyr::select("ID",
-                "time_span",
-                "time",
-                "heart_rate_std",
-                "heart_rate") |> 
-  distinct() |> 
-  mutate(time = time / 60) |> 
-  mutate(ID = as_factor(ID),
-         Phase = factor(time_span,
-                        levels = c("preparation",
-                                   "teaching",
-                                   "post",
-                                   "interview",
-                                   "end"),
-                        labels = c("Pre Teaching Phase",
-                                   "Teaching Phase",
-                                   "Post Teaching Phase",
-                                   "Interview Phase",
-                                   "End Phase")
-                           )
-         )
-
-fix_models <-
-  df_regression %>%
-  split(.$Phase) %>%
-  map( ~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
-            data = .)) %>%
-  map(
-    ~ coef(.) %>%
-      tibble::as_tibble(.,
-                        rownames = "name") %>%
-      transmute(
-        type = if_else(str_detect(name,
-                                  ":"),
-                       true = "slope",
-                       false = "intercept"),
-        id = str_remove_all(name,
-                            "[^[:digit:]]"),
-        value = value
-      ),
-
-  ) %>%
-  bind_rows(.id = "Phase") %>%
-  pivot_wider(names_from = type,
-              values_from = value)
-
-p.values_slope <-
-  fix_models %>%
-  split(.$Phase) %>%
-  map( ~ t.test(x = .$slope,
-                mu = 0)$p.value) %>%
-  bind_rows(.id = "Phase") %>%
-  pivot_longer(cols = everything(),
-               names_to = "Phase",
-               values_to = "p.value_slope")
-
-p.values_intercept <-
-  fix_models %>%
-  split(.$Phase) %>%
-  map( ~ t.test(x = .$intercept,
-                mu = 0)$p.value) %>%
-  bind_rows(.id = "Phase") %>%
-  pivot_longer(cols = everything(),
-               names_to = "Phase",
-               values_to = "p.value_intercept")
-
-sd_mean <-
-  fix_models %>%
-  group_by(Phase) %>%
-  dplyr::summarise(
-    mean_slope = mean(slope),
-    sd_slope = sd(slope),
-    mean_intercept = mean(intercept),
-    sd_intercept = sd(intercept)
-  )
-
-table_data <- 
-  right_join(x = sd_mean,
-             y = p.values_intercept,
-             by = "Phase") %>% 
-  right_join(x = .,
-             y = p.values_slope,
-             by = "Phase") %>% 
-  transmute(Phase = factor(Phase,
-                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
-                           ),
-            n = NA,
-            `Mean(Intercept)` = round(mean_intercept, digits = 3),
-            `SD(Intercept)` = round(sd_intercept, digits = 3),
-            `p-Value (Intercept)` = p.value_intercept,
-            `Mean(Slope)` = round(mean_slope, digits = 3), 
-            `SD(Slope)` = round(sd_slope,digits = 3),
-            `p-Value (Slope)` = p.value_slope, 
-            ) %>% 
-  arrange(Phase)
-
-table_data$n[table_data$Phase == "Pre Teaching Phase"] <- df_regression %>% filter(Phase == "Pre Teaching Phase") %>% pull(heart_rate_std) %>% length()
-table_data$n[table_data$Phase == "Teaching Phase"] <- df_regression %>% filter(Phase == "Teaching Phase") %>% pull(heart_rate_std) %>% length()
-table_data$n[table_data$Phase == "Post Teaching Phase"] <- df_regression %>% filter(Phase == "Post Teaching Phase") %>% pull(heart_rate_std) %>% length()
-table_data$n[table_data$Phase == "Interview Phase"] <- df_regression %>% filter(Phase == "Interview Phase") %>% pull(heart_rate_std) %>% length()
-table_data$n[table_data$Phase == "End Phase"] <- df_regression %>% filter(Phase == "End Phase") %>% pull(heart_rate_std) %>% length()
-```
-
-```{=latex}
-
-\renewcommand{\arraystretch}{1.5}
-
-\begin{table}[ht]
-    \centering
-    \caption{\\
-    Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
-    \begin{tabularx}{\textwidth}{lXXXXXX}
-        \toprule
-        Interval  & \multicolumn{2}{c}{\textit{M} (\textit{SD})} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
-        \midrule
-        (1) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
-        (2) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
-        (3) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
-        (4) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
-        (5) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
-        \bottomrule
-    \end{tabularx}
-    \label{tab_2}
-\end{table}
-
 ```
@@
   \centering
-  \caption{\\
-  Distribution of the standardized heart rate means in the five intervals}
   \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
+  \caption{Distribution of the standardized heart rate means in the five intervals.}
   \label{fig.4}
@@
 
-Table \ref{tab_3} shows the raw correlations among mean standardized HR/mean slopes (see Table \ref{tab_2} for means and standard deviations), teaching experience ($M = 5.64$, $SD = 9.46$), disruption appraisal ($M = 5.19$, $SD = 2.87$), and confidence appraisal ($M = 7.81$, $SD = 1.97$).
-With a few notable exceptions, correlations with HR measures were mostly very small and statistically non-significant (Table 3).
-Correlations between teaching experience and appraisals (not shown in Table \ref{tab_3}) were substantial: more experienced teachers gave lower disruption appraisals ($r = -.36$), and higher confidence appraisals ($r = .44$).
+Tab.\ref{tab_3} shows the raw correlations among mean standardized HR/mean slopes (see Tab.\ref{tab_2} for means and standard deviations), teaching experience ($M = 5.64$, $SD = 9.46$), disruption appraisal ($M = 5.19$, $SD = 2.87$), and confidence appraisal ($M = 7.81$, $SD = 1.97$).
+With a few notable exceptions, correlations with HR measures were mostly very small and statistically non-significant (Tab.\ref{tab_3}).
+Correlations between teaching experience and appraisals (not shown in Tab.\ref{tab_3}) were substantial: more experienced teachers gave lower disruption appraisals ($r = -.36$), and higher confidence appraisals ($r = .44$).
 Moreover, the two appraisal variables were negatively correlated ($r = -.37$).
@@
 
-Table \ref{tab_4} shows the results of the regression analyses.
-Teaching experience significantly predicted mean standardized HR only in the *interview interval* (Table \ref{tab_4}, *interview interval*, Model 1), indicating a higher mean standardized HR for teachers with more teaching experience.
+Tab.\ref{tab_4} shows the results of the regression analyses.
+Teaching experience significantly predicted mean standardized HR only in the *interview interval* (Tab.\ref{tab_4}, *interview interval*, Model 1), indicating a higher mean standardized HR for teachers with more teaching experience.
 This relationship is, in fact, in the opposite direction as predicted by Hypothesis 2a.
@@
 
-When considering the effects of the three predictors in concert (Hypothesis 2d), mean standardized HR was significantly predicted only by disruption appraisal, and only in the *post-teaching interval* (Table \ref{tab_4}, *post-teaching interval*, Model 4), indicating a higher mean standardized HR for teachers who felt more disrupted by the classroom events, when controlling for the other variables.
+When considering the effects of the three predictors in concert (Hypothesis 2d), mean standardized HR was significantly predicted only by disruption appraisal, and only in the *post-teaching interval* (Tab.\ref{tab_4}, *post-teaching interval*, Model 4), indicating a higher mean standardized HR for teachers who felt more disrupted by the classroom events, when controlling for the other variables.
+
+Concerning the explorative investigation of the effects of teaching experience and subjective appraisals on *changes* (i.e., mean slopes) in teachers’ HR, teaching experience significantly predicted the mean slope in the *pre-teaching interval* (Tab.\ref{tab_4}, Pre-teaching interval, Model 1), indicating a less steep HR increase in teachers with more teaching experience.
+For all other intervals, no variable had significant predictive value.
 
@@
     \centering
-    \caption{\\
-    Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
     \begin{tabularx}{\textwidth}{lccccc}
@@
     \end{tabularx}
+    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
     \label{tab_3}
@@
 
-Concerning the explorative investigation of the effects of teaching experience and subjective appraisals on *changes* (i.e., mean slopes) in teachers’ HR, teaching experience significantly predicted the mean slope in the *pre-teaching interval* (Table 4, Pre-teaching interval, Model 1), indicating a less steep HR increase in teachers with more teaching experience.
-For all other intervals, no variable had significant predictive value.
-
-# Discussion
-
-## Key findings
-
-Overall, our findings indicate that wrist-worn fitness trackers are a useful tool for tracking teachers’ HR and identifying stressful periods during teaching.
-Using HR data from a commercially available and relatively low-cost Fitbit® fitness tracker, we were able to map teachers’ HR before, during, and after a stressful micro-teaching unit, with HR increasing in preparation for teaching, peaking during the teaching phase, and decreasing afterward.
-
-These findings are in line with prior studies showing that teachers’ HR varies depending on their activities and encountered stressors with increases during phases where teachers are in an exposed position [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021], as well as with findings showing how HR changes align with activating events and stress-inducing tasks [@Darnell2019; @chalmers2021].
-
-Building on the model of teacher stress [@kyriacou1978, see Fig.
-2], we had hypothesized that more experienced teachers, with better classroom management skills at their disposal, experience less physiological stress when dealing with classroom disruptions.
-Contrary to our expectations, we found no buffering effect of teaching experience on teachers’ HR, i.e., more experienced teachers did not show lower mean standardized HR during the stressful teaching phase than less experienced teachers.
-Rather, at least descriptively, we observed the opposite trend.
-There are several possible explanations for this finding.
-First, teaching experience is inherently confounded with age (the two variables correlated at $r = .94$ in our sample), and age has been shown to affect indicators of cardiovascular reactivity in various ways [@uchino2010older].
-However, to avoid this kind of confounding influence, we had used not raw BPM but rather standardized mean HR for all our analyses, thus controlling at least for inter-individual differences in mean HR.
-Second, as research on teacher professionalization has repeatedly shown, professional experience is not a guarantee for higher professional knowledge and skills [@kirschner2016professionswissen].
-Rather, honing skills from professional experience necessitates a deliberate practice of choosing to improve, learning through experience, and integrating new knowledge into future performances [@dunn1999deliberate].
-Thus, rather than professional experience alone, more direct assessments of classroom management skills, such as objective behavior-based tests, would be a better indicator of expertise that future studies could explore.
 ```{r regressions, include=FALSE}
@@
 \setlength{\LTright}{0pt}
-
-\captionof{table}{Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
 
@@
 \end{longtable}
+    \captionof{table}{Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
 \begin{tablenotes}
@@
 ```
-\noindent Finally, and most importantly, the highly controlled teaching situation that we created in the lab might not have provided sufficient resemblance to the expert teachers’ working conditions to let them effectively use their coping resources.
+
+# Discussion
+
+## Key findings
+
+Overall, our findings indicate that wrist-worn fitness trackers are a useful tool for tracking teachers’ HR and identifying stressful periods during teaching.
+Using HR data from a commercially available and relatively low-cost Fitbit® fitness tracker, we were able to map teachers’ HR before, during, and after a stressful micro-teaching unit, with HR increasing in preparation for teaching, peaking during the teaching phase, and decreasing afterward.
+
+These findings are in line with prior studies showing that teachers’ HR varies depending on their activities and encountered stressors with increases during phases where teachers are in an exposed position [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021], as well as with findings showing how HR changes align with activating events and stress-inducing tasks [@Darnell2019; @chalmers2021].
+
+Building on the model of teacher stress (@kyriacou1978, see Fig.\ref{fig.2}), we had hypothesized that more experienced teachers, with better classroom management skills at their disposal, experience less physiological stress when dealing with classroom disruptions.
+Contrary to our expectations, we found no buffering effect of teaching experience on teachers’ HR, i.e., more experienced teachers did not show lower mean standardized HR during the stressful teaching phase than less experienced teachers.
+Rather, at least descriptively, we observed the opposite trend.
+There are several possible explanations for this finding.
+First, teaching experience is inherently confounded with age (the two variables correlated at $r = .94$ in our sample), and age has been shown to affect indicators of cardiovascular reactivity in various ways [@uchino2010older].
+However, to avoid this kind of confounding influence, we had used not raw BPM but rather standardized mean HR for all our analyses, thus controlling at least for inter-individual differences in mean HR.
+Second, as research on teacher professionalization has repeatedly shown, professional experience is not a guarantee for higher professional knowledge and skills [@kirschner2016professionswissen].
+Rather, honing skills from professional experience necessitates a deliberate practice of choosing to improve, learning through experience, and integrating new knowledge into future performances [@dunn1999deliberate].
+Thus, rather than professional experience alone, more direct assessments of classroom management skills, such as objective behavior-based tests, would be a better indicator of expertise that future studies could explore.
+Finally, and most importantly, the highly controlled teaching situation that we created in the lab might not have provided sufficient resemblance to the expert teachers’ working conditions to let them effectively use their coping resources.
 In other words, since the situation was unfamiliar to both experienced and unexperienced teachers, their stress levels might have been more similar than they would have been in a more authentic classroom setting.
@@
 For instance, while our fitness tracker was designed to record HR every 1-5 seconds, we occasionally observed recordings only every 15 seconds, possibly due to participant movement and tracker placement.
-
-\newpage
 
@@
 ```{=latex}
+\newpage
+
 \appendix
@@
     \centering
-    \caption{\\
-    Classification of nine, typical classroom disruptions according to \cite{lohmann2003schulern} performed in the micro-teaching unit by actors.}
     \begin{tabularx}{\textwidth}{XXX}
@@
     \end{tabularx}
+    \caption{Classification of nine, typical classroom disruptions according to \cite{lohmann2003schulern} performed in the micro-teaching unit by actors.}
     \label{tab_a1}
@@
   \centering
-  \caption{\\
-  Laboratory setting of the micro-teaching unit. .}
-  \includegraphics[width=0.5\textwidth]{appendix_figure1.png}
+  \includegraphics[width=0.45\textwidth]{appendix_figure1.png}
   \caption*{\textit{Note.} The setting included three actors as the class (left) and a teacher (participant, right).}
+  \caption{Laboratory setting of the micro-teaching unit.}
   \label{fig.a1}
@@
 \begin{figure}[htbp]
-  \centering\caption{\\
-  Laboratory setting of the interview.}
-  \includegraphics[width=0.5\textwidth]{appendix_figure2.png}
+  \centering
+  \includegraphics[width=0.45\textwidth]{appendix_figure2.png}
   \caption*{\textit{Note.} The experimenter and participant watched the previously taught micro-teaching unit on video.}
+  \centering\caption{Laboratory setting of the interview.}
   \label{fig.a2}
@@
   \centering
-  \caption{\\
-  Linear estimation of individual HR changes over time during the preparation phase for $N$ = 81 participants.
+  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
+  \caption{Linear estimation of individual HR changes over time during the preparation phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
-  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
   \label{fig.a3}
@@
   \centering
-  \caption{\\
-  Linear estimation of individual HR changes over time during the teaching phase for $N$ = 81 participants.
+  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
+  \caption{Linear estimation of individual HR changes over time during the teaching phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
-  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
   \label{fig.a4}
@@
   \centering
-  \caption{\\
-  Linear estimation of individual HR changes over time during the post-teaching phase for $N$ = 81 participants.
+  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
+    \caption{Linear estimation of individual HR changes over time during the post-teaching phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
-  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
   \label{fig.a5}
@@
   \centering
-  \caption{\\
-  Linear estimation of individual HR changes over time during the interview phase for $N$ = 81 participants.
+  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
+  \caption{Linear estimation of individual HR changes over time during the interview phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
-  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
   \label{fig.a6}
@@
   \centering
-  \caption{\\
-  Linear estimation of individual HR changes over time during the end phase for $N$ = 81 participants.
+  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
+    \caption{Linear estimation of individual HR changes over time during the end phase for $N$ = 81 participants.
 Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
-  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
   \label{fig.a7}

### 2024-09-27 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission_template.tex
nochmal formatiert

--- 2024-09-26 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
@@
-\documentclass[preprint, 3p,
-authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
+\documentclass[preprint,
+3p]{elsarticle} %review=doublespace preprint=single 5p=2 column
 %%% Begin My package additions %%%%%%%%%%%%%%%%%%%
@@
 
+\setcitestyle{sort&compress}
 \usepackage{tabularx}
@@
       \affiliation[Leipzig University]{
-    organization={Empirische Schul- und
-Unterrichtsforschung},addressline={Marschnerstr.
+    organization={Division of Empirical School and Classroom Research,
+Institute of Educational Sciences},addressline={Marschnerstr.
 29},city={Leipzig},postcode={4109},state={Sachsen},country={Germany},}
@@
     \affiliation[University of Greifswald]{
-    organization={Institute of Psychology},addressline={Robert-Blum-Str.
+    organization={Division of Health and Prevention, Institute of
+Psychology},addressline={Robert-Blum-Str.
 13},city={Greifswald},postcode={17489},state={Mecklenburg-Vorpommern},}
@@
 
-Figure \ref{fig.1} shows, in a simplified way, how classroom events
-affect teachers' stress level, according to the adaptation of the
-Lazarus model to teacher stress proposed by \citet{van2006stress}: When
-potential stressors (e.g., classroom disruptions) occur during teaching
-(1), teachers intuitively judge how disruptive the event is in a primary
+Fig.\ref{fig.1} shows, in a simplified way, how classroom events affect
+teachers' stress level, according to the adaptation of the Lazarus model
+to teacher stress proposed by \citet{van2006stress}: When potential
+stressors (e.g., classroom disruptions) occur during teaching (1),
+teachers intuitively judge how disruptive the event is in a primary
 appraisal (2). If potential stressors are judged as threatening, i.e.,
@@
 
-As shown in Figure \ref{fig.1}, teachers' primary and secondary
-appraisal as well as coping attempts are influenced by professional
-experience. As professional experience grows, teachers develop cognitive
-scripts for managing classroom events, resulting in more complex and
-problem-focused classroom management skills \citep{wolff2021classroom},
-and thus more effective coping and less stress. Empirically, classroom
-management skills and problem-focused coping styles are linked to fewer
-instances of emotional exhaustion
-\citep{maslach2001job, clunies2008self}. Novices in the teaching
-profession, on the other hand, face considerable stress and often feel
-overwhelmed by the demands of teaching
+As shown in Fig.\ref{fig.1}, teachers' primary and secondary appraisal
+as well as coping attempts are influenced by professional experience. As
+professional experience grows, teachers develop cognitive scripts for
+managing classroom events, resulting in more complex and problem-focused
+classroom management skills \citep{wolff2021classroom}, and thus more
+effective coping and less stress. Empirically, classroom management
+skills and problem-focused coping styles are linked to fewer instances
+of emotional exhaustion \citep{maslach2001job, clunies2008self}. Novices
+in the teaching profession, on the other hand, face considerable stress
+and often feel overwhelmed by the demands of teaching
 \citep{ophardt2017klassenmanagement, wolff2015keeping, klusmann2012berufliche}
@@
 In addition, we selected five representative 10-minute intervals from
-the five phases of the lab study (see Figure \ref{fig.2}) in order to
-test the hypotheses that, regarding HR levels, teachers' HR would be the
+the five phases of the lab study (see Fig.\ref{fig.2}) in order to test
+the hypotheses that, regarding HR levels, teachers' HR would be the
 highest during the micro-teaching unit, compared to all other phases
-(\textbf{Hypothesis 1a}), and, regarding HR slopes, that teachers' HR
-would increase while they were preparing for teaching (pre-teaching
-interval), but decrease in all of the following intervals, i.e.~when
-they were habituating to and recovering from the stressful
-micro-teaching unit (\textbf{Hypothesis 1b}).
+(Hypothesis 1a), and, regarding HR slopes, that teachers' HR would
+increase while they were preparing for teaching (pre-teaching interval),
+but decrease in all of the following intervals, i.e.~when they were
+habituating to and recovering from the stressful micro-teaching unit
+(Hypothesis 1b).
 
@@
   more experienced teachers to be less stressed by the classroom events
-  (\textbf{Hypothesis 2a}). In addition, we examined the relations
-  between teachers' subjective appraisals of the classroom events
-  (specifically, the disruptiveness of the events, and their confidence
-  in dealing with them) and teachers' HR level, beyond the explanatory
-  power of teaching experience. We expected higher HR levels for
-  teachers who felt more disrupted, regardless of their teaching
-  experience (\textbf{Hypothesis 2b}), and lower HR levels for teachers
-  who felt more confident, regardless of teaching experience
-  (\textbf{Hypothesis 2c}). We hypothesized that each of the three
-  predictors (\emph{teaching experience, disruption appraisal,
+  (Hypothesis 2a). In addition, we examined the relations between
+  teachers' subjective appraisals of the classroom events (specifically,
+  the disruptiveness of the events, and their confidence in dealing with
+  them) and teachers' HR level, beyond the explanatory power of teaching
+  experience. We expected higher HR levels for teachers who felt more
+  disrupted, regardless of their teaching experience (Hypothesis 2b),
+  and lower HR levels for teachers who felt more confident, regardless
+  of teaching experience (Hypothesis 2c). We hypothesized that each of
+  the three predictors (\emph{teaching experience, disruption appraisal,
   confidence appraisal}) uniquely contributed to explaining variance in
-  teachers' HR levels (\textbf{Hypothesis 2d}). In addition, we
-  exploratively ran analogous analyses for the \emph{changes} in HR
-  (i.e., slopes).
+  teachers' HR levels (Hypothesis 2d). In addition, we exploratively ran
+  analogous analyses for the \emph{changes} in HR (i.e., slopes).
 \end{enumerate}
@@
 Each participant came to the lab for a period of approximately two hours
-in total, and each participant underwent the same phases (see Figure
-\ref{fig.2}): In the \emph{pre-teaching phase}, the experimenter
+in total, and each participant underwent the same phases (see
+Fig.\ref{fig.2}): In the \emph{pre-teaching phase}, the experimenter
 welcomed the participants and helped them put on the fitness tracker.
@@
 (e.g., chatting with a neighbor, heckling, looking at the phone; see
-Table \ref{tab_a1} in the supplementary material for an overview and
-categorization of all events; and Figure \ref{fig.a2} in the
-supplementary material for a depiction of the laboratory setting of the
-micro-teaching unit). The topic and class level of the teaching unit
-could be freely chosen by the teachers with the only requirement that
-the unit had to be an introductory lesson, and had to consist of
-supervised individual work and / or frontal teaching. The micro-teaching
-unit lasted about 15-20 minutes. Participants spent this time mostly
-standing or slowly walking around. While teaching, participants wore
-eye-tracking glasses, and their lesson was video-recorded. After having
-completed the micro-teaching unit, in the \emph{post-teaching phase},
-participants filled in questionnaires for approximately 10-15 minutes: a
-brief computer-based survey of sociodemographic
+Tab.\ref{tab_a1} in the supplementary material for an overview and
+categorization of all events; and Fig.\ref{fig.a2} in the supplementary
+material for a depiction of the laboratory setting of the micro-teaching
+unit). The topic and class level of the teaching unit could be freely
+chosen by the teachers with the only requirement that the unit had to be
+an introductory lesson, and had to consist of supervised individual work
+and / or frontal teaching. The micro-teaching unit lasted about 15-20
+minutes. Participants spent this time mostly standing or slowly walking
+around. While teaching, participants wore eye-tracking glasses, and
+their lesson was video-recorded. After having completed the
+micro-teaching unit, in the \emph{post-teaching phase}, participants
+filled in questionnaires for approximately 10-15 minutes: a brief
+computer-based survey of sociodemographic data (e.g., teaching
+experience, gender, studied school type, studied school subjects,
+extracurricular teaching activities), and a short knowledge test that
+was irrelevant to the present study. In the \emph{interview phase},
+participants engaged in a Stimulated Recall Interview (SRI). During the
+SRI, participants sat in front of a computer monitor and watched the
+video of their own lesson from the ego perspective, as recorded through
+the eye-tracking glasses. The experimenter stopped the video each time
+one of the nine classroom events happened, and asked five open-ended,
+and three rating questions per event. Two of the rating questions are
+relevant to the present study: the disruption and the confidence
+appraisal ratings (see Measures). The interview lasted about 45-60
+minutes. Finally, in the \emph{end phase}, participants filled in
+another questionnaire irrelevant to the present study, which lasted
+about 10-15 minutes. \newpage
 
@@
   \centering
-  \caption{\\
-  Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
   \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
+  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals.}
   \label{fig.2}
 \end{wrapfigure}
-
-\noindent data (e.g., teaching experience, gender, studied school type,
-studied school subjects, extracurricular teaching activities), and a
-short knowledge test that was irrelevant to the present study. In the
-\emph{interview phase}, participants engaged in a Stimulated Recall
-Interview (SRI). During the SRI, participants sat in front of a computer
-monitor and watched the video of their own lesson from the ego
-perspective, as recorded through the eye-tracking glasses. The
-experimenter stopped the video each time one of the nine classroom
-events happened, and asked five open-ended, and three rating questions
-per event. Two of the rating questions are relevant to the present
-study: the disruption and the confidence appraisal ratings (see
-Measures). The interview lasted about 45-60 minutes. Finally, in the
-\emph{end phase}, participants filled in another questionnaire
-irrelevant to the present study, which lasted about 10-15 minutes.
 
@@
 phases, we aggregated HR over a representative 10-minute interval within
-each phase (cf.~Figure \ref{fig.2}). Previous research has indicated
-that 10-minute intervals are a useful duration for analyzing PPG data
+each phase (cf.~Fig.\ref{fig.2}). Previous research has indicated that
+10-minute intervals are a useful duration for analyzing PPG data
 \citep{lu2008can}. The intervals were selected based on the following
@@
   distortions when mapping the HR over the course of the study (see
-  Figure \ref{fig.3}), the endpoint was set at two hours for all
+  Fig.\ref{fig.3}), the endpoint was set at two hours for all
   participants, even though data from later time points was used in the
@@
   revealed that the linear estimates corresponded well to the majority
-  of the cases (see XX in the supplementary material).} We tested
-Hypothesis 1b based on the unstandardized estimates of mean slopes (one
-estimate per participant per interval).
+  of the cases (see Fig.\ref{fig.a3} to \ref{fig.a7} in the
+  supplementary material).} We tested Hypothesis 1b based on the
+unstandardized estimates of mean slopes (one estimate per participant
+per interval).
 
@@
 standardized HR for the entire study period, and for the five intervals,
-are shown in Table \ref{tab_1}. Figure \ref{fig.3} displays the
+are shown in Tab.\ref{tab_1}. Fig.\ref{fig.3} displays the
 unstandardized and standardized HR trends, respectively, over the course
@@
 
-Figure \ref{fig.4} shows the distribution of teachers' mean standardized
-HR for the five intervals. Repeated measures ANOVA revealed significant
+Fig.\ref{fig.4} shows the distribution of teachers' mean standardized HR
+for the five intervals. Repeated measures ANOVA revealed significant
 differences in mean standardized HR between intervals,
@@
 intercepts and mean slopes, complemented by their standard deviations
-for each interval, are shown in Table 2. The mean slope of the
+for each interval, are shown in Tab.\ref{tab_2}. The mean slope of the
 \emph{pre-teaching interval} (\(I_1\)) was significantly positive,
@@
 
-\begin{figure}[H]
-  \centering
-  \caption{\\
-  Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
-  \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
-  \label{fig.3}
-\end{figure}
-
 \renewcommand{\arraystretch}{1.5}
@@
     \centering
-    \caption{\\
-    Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
     \begin{tabularx}{\textwidth}{lXXXXXX}
@@
         \midrule
-        (1) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
-        (2) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
-        (3) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
-        (4) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
-        (5) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
+        ($I_1$) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
+        ($I_2$) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
+        ($I_3$) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
+        ($I_4$) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
+        ($I_5$) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
         \bottomrule
     \end{tabularx}
+    \caption{Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
     \label{tab_2}
@@
   \centering
-  \caption{\\
-  Distribution of the standardized heart rate means in the five intervals}
+  \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
+  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig.3a. and the z-standardized HR shown in Fig.3b. for the planned 2-hour study.}
+  \label{fig.3}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
   \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
+  \caption{Distribution of the standardized heart rate means in the five intervals.}
   \label{fig.4}
@@
 
-Table \ref{tab_3} shows the raw correlations among mean standardized
-HR/mean slopes (see Table \ref{tab_2} for means and standard
-deviations), teaching experience (\(M = 5.64\), \(SD = 9.46\)),
-disruption appraisal (\(M = 5.19\), \(SD = 2.87\)), and confidence
-appraisal (\(M = 7.81\), \(SD = 1.97\)). With a few notable exceptions,
-correlations with HR measures were mostly very small and statistically
-non-significant (Table 3). Correlations between teaching experience and
-appraisals (not shown in Table \ref{tab_3}) were substantial: more
+Tab.\ref{tab_3} shows the raw correlations among mean standardized
+HR/mean slopes (see Tab.\ref{tab_2} for means and standard deviations),
+teaching experience (\(M = 5.64\), \(SD = 9.46\)), disruption appraisal
+(\(M = 5.19\), \(SD = 2.87\)), and confidence appraisal (\(M = 7.81\),
+\(SD = 1.97\)). With a few notable exceptions, correlations with HR
+measures were mostly very small and statistically non-significant
+(Tab.\ref{tab_3}). Correlations between teaching experience and
+appraisals (not shown in Tab.\ref{tab_3}) were substantial: more
 experienced teachers gave lower disruption appraisals (\(r = -.36\)),
@@
 
-Table \ref{tab_4} shows the results of the regression analyses. Teaching
+Tab.\ref{tab_4} shows the results of the regression analyses. Teaching
 experience significantly predicted mean standardized HR only in the
-\emph{interview interval} (Table \ref{tab_4}, \emph{interview interval},
+\emph{interview interval} (Tab.\ref{tab_4}, \emph{interview interval},
 Model 1), indicating a higher mean standardized HR for teachers with
@@
 by disruption appraisal, and only in the \emph{post-teaching interval}
-(Table \ref{tab_4}, \emph{post-teaching interval}, Model 4), indicating
-a higher mean standardized HR for teachers who felt more disrupted by
-the classroom events, when controlling for the other variables.
+(Tab.\ref{tab_4}, \emph{post-teaching interval}, Model 4), indicating a
+higher mean standardized HR for teachers who felt more disrupted by the
+classroom events, when controlling for the other variables.
+
+Concerning the explorative investigation of the effects of teaching
+experience and subjective appraisals on \emph{changes} (i.e., mean
+slopes) in teachers' HR, teaching experience significantly predicted the
+mean slope in the \emph{pre-teaching interval} (Tab.\ref{tab_4},
+Pre-teaching interval, Model 1), indicating a less steep HR increase in
+teachers with more teaching experience. For all other intervals, no
+variable had significant predictive value.
 
@@
 
-Concerning the explorative investigation of the effects of teaching
-experience and subjective appraisals on \emph{changes} (i.e., mean
-slopes) in teachers' HR, teaching experience significantly predicted the
-mean slope in the \emph{pre-teaching interval} (Table 4, Pre-teaching
-interval, Model 1), indicating a less steep HR increase in teachers with
-more teaching experience. For all other intervals, no variable had
-significant predictive value.
-
-\section{Discussion}\label{discussion}
-
-\subsection{Key findings}\label{key-findings}
-
-Overall, our findings indicate that wrist-worn fitness trackers are a
-useful tool for tracking teachers' HR and identifying stressful periods
-during teaching. Using HR data from a commercially available and
-relatively low-cost Fitbit® fitness tracker, we were able to map
-teachers' HR before, during, and after a stressful micro-teaching unit,
-with HR increasing in preparation for teaching, peaking during the
-teaching phase, and decreasing afterward.
-
-These findings are in line with prior studies showing that teachers' HR
-varies depending on their activities and encountered stressors with
-increases during phases where teachers are in an exposed position
-\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021},
-as well as with findings showing how HR changes align with activating
-events and stress-inducing tasks \citep{Darnell2019, chalmers2021}.
-
-Building on the model of teacher stress \citep[see Fig.
-2]{kyriacou1978}, we had hypothesized that more experienced teachers,
-with better classroom management skills at their disposal, experience
-less physiological stress when dealing with classroom disruptions.
-Contrary to our expectations, we found no buffering effect of teaching
-experience on teachers' HR, i.e., more experienced teachers did not show
-lower mean standardized HR during the stressful teaching phase than less
-experienced teachers. Rather, at least descriptively, we observed the
-opposite trend. There are several possible explanations for this
-finding. First, teaching experience is inherently confounded with age
-(the two variables correlated at \(r = .94\) in our sample), and age has
-been shown to affect indicators of cardiovascular reactivity in various
-ways \citep{uchino2010older}. However, to avoid this kind of confounding
-influence, we had used not raw BPM but rather standardized mean HR for
-all our analyses, thus controlling at least for inter-individual
-differences in mean HR. Second, as research on teacher
-professionalization has repeatedly shown, professional experience is not
-a guarantee for higher professional knowledge and skills
-\citep{kirschner2016professionswissen}. Rather, honing skills from
-professional experience necessitates a deliberate practice of choosing
-to improve, learning through experience, and integrating new knowledge
-into future performances \citep{dunn1999deliberate}. Thus, rather than
-professional experience alone, more direct assessments of classroom
-management skills, such as objective behavior-based tests, would be a
-better indicator of expertise that future studies could explore.
-
 \begin{landscape}
@@
 
-\noindent Finally, and most importantly, the highly controlled teaching
-situation that we created in the lab might not have provided sufficient
+\section{Discussion}\label{discussion}
+
+\subsection{Key findings}\label{key-findings}
+
+Overall, our findings indicate that wrist-worn fitness trackers are a
+useful tool for tracking teachers' HR and identifying stressful periods
+during teaching. Using HR data from a commercially available and
+relatively low-cost Fitbit® fitness tracker, we were able to map
+teachers' HR before, during, and after a stressful micro-teaching unit,
+with HR increasing in preparation for teaching, peaking during the
+teaching phase, and decreasing afterward.
+
+These findings are in line with prior studies showing that teachers' HR
+varies depending on their activities and encountered stressors with
+increases during phases where teachers are in an exposed position
+\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021},
+as well as with findings showing how HR changes align with activating
+events and stress-inducing tasks \citep{Darnell2019, chalmers2021}.
+
+Building on the model of teacher stress (\citet{kyriacou1978}, see
+Fig.\ref{fig.2}), we had hypothesized that more experienced teachers,
+with better classroom management skills at their disposal, experience
+less physiological stress when dealing with classroom disruptions.
+Contrary to our expectations, we found no buffering effect of teaching
+experience on teachers' HR, i.e., more experienced teachers did not show
+lower mean standardized HR during the stressful teaching phase than less
+experienced teachers. Rather, at least descriptively, we observed the
+opposite trend. There are several possible explanations for this
+finding. First, teaching experience is inherently confounded with age
+(the two variables correlated at \(r = .94\) in our sample), and age has
+been shown to affect indicators of cardiovascular reactivity in various
+ways \citep{uchino2010older}. However, to avoid this kind of confounding
+influence, we had used not raw BPM but rather standardized mean HR for
+all our analyses, thus controlling at least for inter-individual
+differences in mean HR. Second, as research on teacher
+professionalization has repeatedly shown, professional experience is not
+a guarantee for higher professional knowledge and skills
+\citep{kirschner2016professionswissen}. Rather, honing skills from
+professional experience necessitates a deliberate practice of choosing
+to improve, learning through experience, and integrating new knowledge
+into future performances \citep{dunn1999deliberate}. Thus, rather than
+professional experience alone, more direct assessments of classroom
+management skills, such as objective behavior-based tests, would be a
+better indicator of expertise that future studies could explore.
+Finally, and most importantly, the highly controlled teaching situation
+that we created in the lab might not have provided sufficient
 resemblance to the expert teachers' working conditions to let them
@@
 
-\newpage
-
 \subsection{Conclusion}\label{conclusion}
@@
 
+\newpage
+
 \appendix

### 2024-09-30 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_24_outlierdetection_MK.Rmd
xpaper

--- 2024-09-24 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_24_MK.Rmd
@@
 
+######## Statistical Methods for Outlier Detection
+
+### EXPERTS ###
+
 # filter only for experts
@@
 
-# filter only for novices
-df_aoi_sum_novice <- df_aoi_sum %>% 
-  filter(Group == "Novice")
-
-######## Statistical Methods for Outlier Detection
-
-### EXPERTS ###
-
 # Boxplot showing outliers for experts
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
+  labs(title = "EXPERTS: Boxplot of number of fixations per minute (micro-teaching unit)",
        y = "Number of fixations per minute") +
@@
 
+# filter only for novices
+df_aoi_sum_novice <- df_aoi_sum %>% 
+  filter(Group == "Novice")
+
 # Boxplot showing outliers for novices
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
+  labs(title = "NOVICES: Boxplot of number of fixations per minute (micro-teaching unit)",
        y = "Number of fixations per minute") +
   theme_minimal()
-
-# Calculate the IQR and bounds
-Q1 <- quantile(df_aoi_sum_novice$Number_fixation_min_mtu, 0.25)
-Q3 <- quantile(df_aoi_sum_novice$Number_fixation_min_mtu, 0.75)
-IQR <- Q3 - Q1
-
-LowerBound <- Q1 - 1.5 * IQR
-UpperBound <- Q3 + 1.5 * IQR
-
-# Filter to remove outliers
-df_no_outliers_mtu_nov <- df_aoi_sum_novice %>%
-  filter(Number_fixation_min_mtu >= LowerBound & Number_fixation_min_mtu <= UpperBound)
-
-# Check the number of rows before and after filtering
-nrow(df_aoi_sum_novice)  # Original data
-nrow(df_no_outliers_mtu_nov)  # After removing outliers
 
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of number of fixations per minute (AOI students)",
+  labs(title = "EXPERTS: Boxplot of number of fixations per minute (AOI students)",
        y = "Number of fixations per minute") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of number of fixations per minute (AOI students)",
+  labs(title = "NOVICES: Boxplot of number of fixations per minute (AOI students)",
        y = "Number of fixations per minute") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of number of fixations per minute (AOI disruptive person)",
+  labs(title = "EXPERTS: Boxplot of number of fixations per minute (AOI disruptive person)",
        y = "Number of fixations per minute") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of number of fixations per minute (AOI disruptive person)",
+  labs(title = "NOVICES: Boxplot of number of fixations per minute (AOI disruptive person)",
        y = "Number of fixations per minute") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of Average duration of fixations",
+  labs(title = "EXPERTS: Boxplot of Average duration of fixations",
        y = "Average duration of fixations in msec") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of Average duration of fixations",
+  labs(title = "NOVICES: Boxplot of Average duration of fixations",
        y = "Average duration of fixations in msec") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of average duration of fixations (AOI disruptive person)",
+  labs(title = "EXPERTS: Boxplot of average duration of fixations (AOI disruptive person)",
        y = "Average duration of fixations") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of average duration of fixations (AOI disruptive person)",
+  labs(title = "NOVICES: Boxplot of average duration of fixations (AOI disruptive person)",
        y = "Average duration of fixations") +
@@
 #### 2.2.7 Gaze Relational Index (GRI; micro-teaching unit)
+
+GRI = Average duration of fixations (mtu) / Sum number of fixations (mtu)
+
 ```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-# GRI = Average_duration_mtu / Sum_number_fixation
-
 ######## Statistical Methods for Outlier Detection
@@
 ### EXPERTS ###
+
 # filter only for experts
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "EXPERT: Boxplot average duration (mtu)",
+  labs(title = "EXPERTS: Boxplot average duration (mtu)",
        y = "Mean duration of fixations/\nmean number of fixations") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "EXPERT: Boxplot of summarized number of fixations (mtu)",
+  labs(title = "EXPERTS: Boxplot of summarized number of fixations (mtu)",
        y = "Mean duration of fixations/\nmean number of fixations") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "NOVICE: Boxplot average duration (mtu)",
+  labs(title = "NOVICES: Boxplot average duration (mtu)",
        y = "Mean duration of fixations/\nmean number of fixations") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "NOVICE: Boxplot of summarized number of fixations (mtu)",
+  labs(title = "NOVICES: Boxplot of summarized number of fixations (mtu)",
        y = "Mean duration of fixations/\nmean number of fixations") +
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "NOVICE: Boxplot of time to first fixation in seconds (AOI disruptive person)",
+  labs(title = "NOVICES: Boxplot of time to first fixation in seconds (AOI disruptive person)",
        y = "Time to first fixation in seconds") +
@@
 #### ALL ####
+
 # create data frame without outliers
@@
 #### MANAGING MOMENTUM ####
+
+# create data frame without outliers
+df_sjt_mean_mm_no_out <- df_sjt_mean %>% 
+  filter(!Participant %in% c("105", "127"))
+
 # t-test for expertise differences 
-t.test(x = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Expert"],
-       y = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Novice"],
+t.test(x = df_sjt_mean_mm_no_out$`Managing momentum`[df_sjt_mean_mm_no_out$Group == "Expert"],
+       y = df_sjt_mean_mm_no_out$`Managing momentum`[df_sjt_mean_mm_no_out$Group == "Novice"],
        var.equal = TRUE
@@
 # effect size for expertise differences
-d_sjt_mm <- CohenD(x = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Expert"],
-                   y = df_sjt_mean$`Managing momentum`[df_sjt_mean$Group == "Novice"],
+d_sjt_mm <- CohenD(x = df_sjt_mean_mm_no_out$`Managing momentum`[df_sjt_mean_mm_no_out$Group == "Expert"],
+                   y = df_sjt_mean_mm_no_out$`Managing momentum`[df_sjt_mean_mm_no_out$Group == "Novice"],
                    na.rm = TRUE
@@
 #### MONITORING ####
+
+# create data frame without outliers
+df_sjt_mean_m_no_out <- df_sjt_mean %>% 
+  filter(!Participant %in% c("121", "127", "137"))
+
 # t-test for expertise differences 
-t.test(x = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Expert"],
-       y = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Novice"],
+t.test(x = df_sjt_mean_m_no_out$Monitoring[df_sjt_mean_m_no_out$Group == "Expert"],
+       y = df_sjt_mean_m_no_out$Monitoring[df_sjt_mean_m_no_out$Group == "Novice"],
        var.equal = TRUE
@@
 # effect size for expertise differences
-d_sjt_moni <- CohenD(x = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Expert"],
-                     y = df_sjt_mean$Monitoring[df_sjt_mean$Group == "Novice"],
+d_sjt_moni <- CohenD(x = df_sjt_mean_m_no_out$Monitoring[df_sjt_mean_m_no_out$Group == "Expert"],
+                     y = df_sjt_mean_m_no_out$Monitoring[df_sjt_mean_m_no_out$Group == "Novice"],
                      na.rm = TRUE
@@
 #### RULES & ROUTINES ####
+
+# create data frame without outliers
+df_sjt_mean_r_no_out <- df_sjt_mean %>% 
+  filter(!Participant %in% c("127"))
+
 # t-test for expertise differences 
-t.test(x = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Expert"],
-       y = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Novice"],
+t.test(x = df_sjt_mean_r_no_out$`Rules and routines`[df_sjt_mean_r_no_out$Group == "Expert"],
+       y = df_sjt_mean_r_no_out$`Rules and routines`[df_sjt_mean_r_no_out$Group == "Novice"],
        var.equal = TRUE
@@
 # effect size for expertise differences
-d_sjt_rr <- CohenD(x = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Expert"],
-                   y = df_sjt_mean$`Rules and routines`[df_sjt_mean$Group == "Novice"],
+d_sjt_rr <- CohenD(x = df_sjt_mean_r_no_out$`Rules and routines`[df_sjt_mean_r_no_out$Group == "Expert"],
+                   y = df_sjt_mean_r_no_out$`Rules and routines`[df_sjt_mean_r_no_out$Group == "Novice"],
                    na.rm = TRUE
@@
 # read in data
-df_sjt <- 
+df_sjt_no_out <-
   read_excel("./data/SJT.xlsx")
 
+### ALL
+df_sjt_all <- df_sjt_no_out %>% 
+  dplyr::select(WT_S1_F1F2_AL:WT_S14_F4F6_R)
+
+# calculate omega with omega() function  
+df_sjt_all <- omega(df_sjt_all)
+
+# display the results 
+print(df_sjt_all)
+
 ### MANAGING MOMENTUM
@@
 # select relevant columns
-df_sjt_mm <- df_sjt %>%
+df_sjt_mm <- df_sjt_no_out %>%
     dplyr::select(WT_S1_F1F2_AL:WT_S4_F4F6_AL)
@@
 # select relevant columns
-df_sjt_m <- df_sjt %>%
+df_sjt_m <- df_sjt_no_out %>%
     dplyr::select(WT_S5_F1F2_ST:WT_S9_F4F5_ST)
@@
 # select relevant columns
-df_sjt_r <- df_sjt %>%
+df_sjt_r <- df_sjt_no_out %>%
   dplyr::select(WT_S11_F1F5_R:WT_S14_F4F6_R)
@@
 
+# calculate omega with omega() function  
+df_quest <- omega(df_quest)
+
+# display the results 
+print(df_quest)
+
 ### CLASSROOM MANAGEMENT
@@
 
-# demo data 
-df_demo <- 
-  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
-  filter(!LI06_05 == 201,
-         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
-  transmute(Participant = LI06_05,
-            `Teaching Experience` = LI04_01,
-            )
-
-# average duration, number fixation, GRI (micro-teaching unit)
-df_aoi %>%
-  filter(TOI == "Lesson") %>% 
-  dplyr::select(
-    Duration_of_interval,
-    Participant,
-    starts_with("Total_duration_of_fixations"),
-    starts_with("Number_of_fixations"),
-    starts_with("Average_duration"),
-    !"Total_duration_of_fixations.Disruptive_Person",
-    !"Number_of_fixations.Disruptive_Person",
-    !"Average_duration_of_fixations.Disruptive_Person"
-  ) %>%
-  rowwise() %>%
-  transmute(
-    Participant = Participant,
-    Duration_of_interval = Duration_of_interval, 
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
-    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
-    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
-    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
-    GRI_mtu = round(Average_duration_mtu / Sum_number_fixation, digits = 2)
-    ) %>%
-  drop_na() %>% 
-  filter(!Participant %in% c(216)) %>% 
-  dplyr::select(Participant,
-         Number_fixation_min_mtu, 
-         Average_duration_mtu,
-         GRI_mtu) -> df_aoi_numb_dur
-
-# average duration, number fixation, GRI (AOI student)
-df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select (
-    Participant,
-    Duration_of_interval,
-    "Total_duration_of_fixations.Anna",
-    "Total_duration_of_fixations.Bianca",
-    "Total_duration_of_fixations.Carl(a)",
-    "Number_of_fixations.Anna",
-    "Number_of_fixations.Bianca",
-    "Number_of_fixations.Carl(a)"
-  ) %>%
-  rowwise() %>%
-  transmute(
-    Participant = Participant,
-    Duration_of_interval = Duration_of_interval,
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
-    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Stud_number_fixation_min = round(Duration_of_interval_min / Stud_number_fixation, digits = 2),
-    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
-    GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2)
-    ) %>% 
-  dplyr::select(Participant,
-                Stud_number_fixation_min,
-                Average_duration_stud,
-                GRI_stud) -> df_aoi_stud
-
-# average duration, number fixation, GRI (AOI disruptive person)
-df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select(Participant,
-                "Total_duration_of_fixations.Disruptive_Person",
-                "Number_of_fixations.Disruptive_Person"
-                ) %>%
-  rowwise() %>%
-  mutate(
-    Average_duration_disrup = round(
-      Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person,
-      digits = 0),
-    GRI_disrup = round(
-      Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2)) %>% 
-  dplyr::select(Participant,
-                Number_of_fixations.Disruptive_Person,
-                Average_duration_disrup,
-                GRI_disrup
-                ) -> df_aoi_disrup
-
-# time to first fixatoin (AOI disruptive person)
-df_aoi %>%
-  filter(
-    TOI %in% c(
-      "Chatting_with_neighbour",
-      "Clicking_pen",
-      "Drawing",
-      "Drumming_with_hands",
-      "Head_on_table",
-      "Heckling",
-      "Looking_at_phone",
-      "Snipping_with_fingers",
-      "Whispering"
-    )
-  ) %>%
-  dplyr::select(Participant, TOI, Time_to_first_fixation.Disruptive_Person, ) %>%
-  rowwise() %>%
-  drop_na() %>%
-  group_by(Participant) %>%
-  summarise(
-    Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person)
-  ) %>%
-  mutate(
-    Group = ifelse(Participant < 200, "Novice", "Expert"),
-    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000,
-      digits = 2
-    )
-  ) -> df_ttff_disrup
-
-# rating scales
-df_sri <-
-  excel_sheets("data/Coding_SRI.xlsx") %>%
-  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
-  filter(
-    !ID %in% c(201,
-               223),
-    !disruption_appraisal == -100,
-    !confidence_appraisal == -100,
-    !disruption_appraisal == -99,
-    !confidence_appraisal == -99,
-    !disruption_appraisal == -88,
-    !confidence_appraisal == -88,
-    !prevalence_rating == -100,
-    !prevalence_rating == -99,
-    !prevalence_rating == -88
-    ) %>% 
-  rename(Participant = ID) %>%
-  group_by(Participant) %>% 
-  summarise(
-    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
-    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
-    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
-    )%>% 
-  dplyr::select(Participant,
-                Mean_disrupption_appraisal,
-                Mean_confidence_appraisal,
-                Mean_prevalence_rating)
-
-# sjt
-df_sjt <-
-  read_excel("./data/SJT.xlsx") %>%
-  dplyr::select(UI06_05, # Participant
-                SJT_AL_gek, # Monitoring
-                SJT_ST_gek, # Managing momentum
-                SJT_R_gek, # Rules and routines
-                SJT_KF_gek) %>% # All
-  filter(!UI06_05 %in% c(201, 223, 216)) %>%  # exclude ID with no eye tracking data
-  transmute(
-    Participant = UI06_05,
-    SJT_Monitoring = round(SJT_AL_gek, 2),
-    SJT_Managing_momentum = round(SJT_ST_gek, 2),
-    SJT_Rules_routines = round(SJT_R_gek, 2),
-    SJT_All = round(SJT_KF_gek, 2)
-    ) %>% 
-    arrange(Participant)
-
-# classroom questionnaire
-df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LI06_05, LM01_01:LM01_08, # classroom management
-                LP01_01:LP01_08) %>% # non- & paraverbal communication
-  filter(!LI06_05 %in% c(201, 223)) %>% # exclude ID with no eye tracking data
-  rename(Participant = LI06_05) %>%
-  group_by(Participant) %>%
-  transmute(
-    Participant = Participant,
-    "Quest_All" = round(mean(c_across(starts_with(
-      "L"
-    )), na.rm = TRUE), 2),
-    "Quest_classroom_management" = round(mean(c_across(starts_with(
-      "LM"
-    )), na.rm = TRUE), 2),
-    "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with(
-      "LP"
-    )), na.rm = TRUE), 2)
-  )
-
-# create a big data frame with all measures 
-# put all data frames into list
-df_list <- list(df_demo,
-                df_aoi_numb_dur,
-                df_aoi_stud,
-                df_aoi_disrup,
-                df_sri,
-                df_sjt,
-                df_quest)
-
-# merge all data frames in list
-df_merge <-
-  df_list %>% reduce(full_join, by='Participant') %>%
-  arrange(Participant) %>% 
+# # demo data 
+# df_demo <- 
+#   read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
+#   filter(!LI06_05 == 201,
+#          !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
+#   transmute(Participant = LI06_05,
+#             `Teaching Experience` = LI04_01,
+#             ) %>% 
+#   filter(!Participant %in% c("216", "217", "127", "105", "121", "137")) # filter SJT outlier
+# 
+# 
+# # average duration, number fixation, GRI (micro-teaching unit)
+# df_aoi %>%
+#   filter(TOI == "Lesson") %>% 
+#   dplyr::select(
+#     Duration_of_interval,
+#     Participant,
+#     starts_with("Total_duration_of_fixations"),
+#     starts_with("Number_of_fixations"),
+#     starts_with("Average_duration"),
+#     !"Total_duration_of_fixations.Disruptive_Person",
+#     !"Number_of_fixations.Disruptive_Person",
+#     !"Average_duration_of_fixations.Disruptive_Person"
+#   ) %>%
+#   rowwise() %>%
+#   transmute(
+#     Participant = Participant,
+#     Duration_of_interval = Duration_of_interval, 
+#     Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
+#     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+#     Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
+#     Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+#     Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
+#     Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
+#     GRI_mtu = round(Average_duration_mtu / Sum_number_fixation, digits = 2)
+#     ) %>%
+#   drop_na() %>% 
 #   filter(!Participant %in% c(216)) %>% 
-  dplyr::select(.,
-                -"Participant",
-                -"Teaching Experience")
-
-# create a correlation matrix
-cor_tab <- 
-  df_merge %>% 
-  cor(method = "pearson") %>% 
-  round(., digits = 2)
-
-# p-value for GRI x STJ_All
-cor.test(df_aoi_numb_dur$GRI_mtu, df_sjt$SJT_All)
-cor.test(df_merge$GRI_mtu, df_merge$SJT_Monitoring)
-
-# teaching experience only with experts
-df_merge_teaching_experience <-
-  df_list %>% reduce(full_join, by='Participant') %>%
-  filter(Participant > 200) %>% 
-  dplyr::select(.,
-                -"Participant")
-
-# create a correlation matrix
-cor_tab_teaching_experience <- 
-  df_merge_teaching_experience %>% 
-  cor(method = "pearson") %>% 
-  round(., digits = 2)
-
-# create a scatter plot 
-# pairs(~ Gender + 
-#         Age + 
-#         `Teaching Experience` + 
-#         Sum_number_fixation + 
-#         Stud_number_fixation + 
-#         Number_of_fixations.Disruptive_Person + 
-#         Average_duration_mtu + 
-#         Average_duration_stud + 
-#         Average_duration_disrup + 
-#         GRI_mtu + 
-#         GRI_stud + 
-#         GRI_disrup + 
-#         Mean_disrupption_appraisal + 
-#         Mean_confidence_appraisal + 
-#         Mean_prevalence_rating + 
-#         SJT_Monitoring + 
-#         SJT_Managing_momentum + 
-#         SJT_Rules_routines + 
-#         SJT_All + 
-#         Quest_classroom_management + 
-#         Quest_non_paraverbal_communication + 
-#         Quest_All,
-#       upper.panel = NULL,
-#       pch = 20,
-#       cex = 3, 
-#       main = "Correlation Table Expertise Measures",
-#       col = Gender)
-
-# apa.cor.table(cor_tab)
-
-```
+#   filter(!Participant %in% c("216", "217", "127", "105", "121", "137")) %>%  # filter SJT outlier
+#   filter(!Participant %in% c("205")) %>%  # filter GRI outlier
+#   dplyr::select(Participant,
+#          Number_fixation_min_mtu, 
+#          Average_duration_mtu,
+#          GRI_mtu) -> df_aoi_numb_dur
+# 
+# 
+# # average duration, number fixation, GRI (AOI student)
+# df_aoi %>%
+#   filter(TOI == "Lesson") %>%
+#   dplyr::select (
+#     Participant,
+#     Duration_of_interval,
+#     "Total_duration_of_fixations.Anna",
+#     "Total_duration_of_fixations.Bianca",
+#     "Total_duration_of_fixations.Carl(a)",
+#     "Number_of_fixations.Anna",
+#     "Number_of_fixations.Bianca",
+#     "Number_of_fixations.Carl(a)"
+#   ) %>%
+#   rowwise() %>%
+#   transmute(
+#     Participant = Participant,
+#     Duration_of_interval = Duration_of_interval,
+#     Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
+#     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+#     Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+#     Stud_number_fixation_min = round(Duration_of_interval_min / Stud_number_fixation, digits = 2),
+#     Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
+#     GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2)
+#     ) %>%
+#   dplyr::select(Participant,
+#                 Stud_number_fixation_min,
+#                 Average_duration_stud,
+#                 GRI_stud) -> df_aoi_stud
+# 
+# 
+# # average duration, number fixation, GRI (AOI disruptive person)
+# df_aoi %>%
+#   filter(TOI == "Lesson") %>%
+#   dplyr::select(Participant,
+#                 "Total_duration_of_fixations.Disruptive_Person",
+#                 "Number_of_fixations.Disruptive_Person"
+#                 ) %>%
+#   rowwise() %>%
+#   mutate(
+#     Average_duration_disrup = round(
+#       Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person,
+#       digits = 0),
+#     GRI_disrup = round(
+#       Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2)) %>%
+#   dplyr::select(Participant,
+#                 Number_of_fixations.Disruptive_Person,
+#                 Average_duration_disrup,
+#                 GRI_disrup
+#                 ) -> df_aoi_disrup
+# 
+# # time to first fixation (AOI disruptive person)
+# df_aoi %>%
+#   filter(
+#     TOI %in% c(
+#       "Chatting_with_neighbour",
+#       "Clicking_pen",
+#       "Drawing",
+#       "Drumming_with_hands",
+#       "Head_on_table",
+#       "Heckling",
+#       "Looking_at_phone",
+#       "Snipping_with_fingers",
+#       "Whispering"
+#     )
+#   ) %>%
+#   dplyr::select(Participant, TOI, Time_to_first_fixation.Disruptive_Person, ) %>%
+#   rowwise() %>%
+#   drop_na() %>%
+#   group_by(Participant) %>%
+#   summarise(
+#     Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person)
+#   ) %>%
+#   mutate(
+#     Group = ifelse(Participant < 200, "Novice", "Expert"),
+#     Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000,
+#       digits = 2
+#     )
+#   ) -> df_ttff_disrup
+# 
+# # rating scales
+# df_sri <-
+#   excel_sheets("data/Coding_SRI.xlsx") %>%
+#   map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+#   filter(
+#     !ID %in% c(201,
+#                223),
+#     !disruption_appraisal == -100,
+#     !confidence_appraisal == -100,
+#     !disruption_appraisal == -99,
+#     !confidence_appraisal == -99,
+#     !disruption_appraisal == -88,
+#     !confidence_appraisal == -88,
+#     !prevalence_rating == -100,
+#     !prevalence_rating == -99,
+#     !prevalence_rating == -88
+#     ) %>% 
+#   rename(Participant = ID) %>%
+#   group_by(Participant) %>% 
+#   summarise(
+#     Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
+#     Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
+#     Mean_prevalence_rating = round(mean(prevalence_rating), 2)
+#     )%>% 
+#   dplyr::select(Participant,
+#                 Mean_disrupption_appraisal,
+#                 Mean_confidence_appraisal,
+#                 Mean_prevalence_rating)
+# 
+# # sjt
+# df_sjt <-
+#   read_excel("./data/SJT.xlsx") %>%
+#   dplyr::select(UI06_05, # Participant
+#                 SJT_AL_gek, # Monitoring
+#                 SJT_ST_gek, # Managing momentum
+#                 SJT_R_gek, # Rules and routines
+#                 SJT_KF_gek) %>% # All
+#   filter(!UI06_05 %in% c(201, 223, 216)) %>%  # exclude ID with no eye tracking data
+#   filter(!UI06_05 %in% c("216", "217", "127", "105", "121", "137")) %>%  # filter SJT outlier
+#   filter(!UI06_05 %in% c("205")) %>%  # filter GRI outlier
+#   transmute(
+#     Participant = UI06_05,
+#     SJT_Monitoring = round(SJT_AL_gek, 2),
+#     SJT_Managing_momentum = round(SJT_ST_gek, 2),
+#     SJT_Rules_routines = round(SJT_R_gek, 2),
+#     SJT_All = round(SJT_KF_gek, 2)
+#     ) %>% 
+#     arrange(Participant)
+# 
+# # classroom questionnaire
+# df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+#   dplyr::select(LI06_05, LM01_01:LM01_08, # classroom management
+#                 LP01_01:LP01_08) %>% # non- & paraverbal communication
+#   filter(!LI06_05 %in% c(201, 223)) %>% # exclude ID with no eye tracking data
+#   rename(Participant = LI06_05) %>%
+#   group_by(Participant) %>%
+#   transmute(
+#     Participant = Participant,
+#     "Quest_All" = round(mean(c_across(starts_with(
+#       "L"
+#     )), na.rm = TRUE), 2),
+#     "Quest_classroom_management" = round(mean(c_across(starts_with(
+#       "LM"
+#     )), na.rm = TRUE), 2),
+#     "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with(
+#       "LP"
+#     )), na.rm = TRUE), 2)
+#   )
+# 
+# # create a big data frame with all measures 
+# # put all data frames into list
+# df_list <- list(df_demo,
+#                 df_aoi_numb_dur,
+#                 df_aoi_stud,
+#                 df_aoi_disrup,
+#                 df_sri,
+#                 df_sjt,
+#                 df_quest)
+# 
+# df_list_gri_sjt <- list(df_sjt,
+#                    df_aoi_numb_dur)
+# 
+# df_merge_gri_sjt <- df_list_gri_sjt %>% 
+#   reduce(full_join, by='Participant') %>%
+#   arrange(Participant) %>% 
+#   dplyr::select(.,
+#                 -"Participant")
+# 
+# # p-value for GRI x STJ_All
+# cor.test(df_aoi_numb_dur$GRI_mtu, df_sjt$SJT_Monitoring)
+# 
+# # merge all data frames in list
+# df_merge <-
+#   df_list %>% reduce(full_join, by='Participant') %>%
+#   arrange(Participant) %>% 
+#   # filter(!Participant %in% c(216)) %>% 
+#   dplyr::select(.,
+#                 -"Participant",
+#                 -"Teaching Experience")
+# 
+# # create a correlation matrix
+# cor_tab <- 
+#   df_merge %>% 
+#   cor(method = "pearson") %>% 
+#   round(., digits = 2)
+# 
+# # p-value for GRI x STJ_All
+# cor.test(df_aoi_numb_dur$GRI_mtu, df_sjt$SJT_All)
+# cor.test(df_merge$GRI_mtu, df_merge$SJT_Monitoring)
+# 
+# # teaching experience only with experts
+# df_merge_teaching_experience <-
+#   df_list %>% reduce(full_join, by='Participant') %>%
+#   filter(Participant > 200) %>% 
+#   dplyr::select(.,
+#                 -"Participant")
+# 
+# # create a correlation matrix
+# cor_tab_teaching_experience <- 
+#   df_merge_teaching_experience %>% 
+#   cor(method = "pearson") %>% 
+#   round(., digits = 2)
+# 
+# # create a scatter plot 
+# # pairs(~ Gender + 
+# #         Age + 
+# #         `Teaching Experience` + 
+# #         Sum_number_fixation + 
+# #         Stud_number_fixation + 
+# #         Number_of_fixations.Disruptive_Person + 
+# #         Average_duration_mtu + 
+# #         Average_duration_stud + 
+# #         Average_duration_disrup + 
+# #         GRI_mtu + 
+# #         GRI_stud + 
+# #         GRI_disrup + 
+# #         Mean_disrupption_appraisal + 
+# #         Mean_confidence_appraisal + 
+# #         Mean_prevalence_rating + 
+# #         SJT_Monitoring + 
+# #         SJT_Managing_momentum + 
+# #         SJT_Rules_routines + 
+# #         SJT_All + 
+# #         Quest_classroom_management + 
+# #         Quest_non_paraverbal_communication + 
+# #         Quest_All,
+# #       upper.panel = NULL,
+# #       pch = 20,
+# #       cex = 3, 
+# #       main = "Correlation Table Expertise Measures",
+# #       col = Gender)
+# 
+# # apa.cor.table(cor_tab)
+
+```

### 2024-09-30 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex

@@
   revealed that the linear estimates corresponded well to the majority
-  of the cases (see XX in the supplementary material).} We tested
-Hypothesis 1b based on the unstandardized estimates of mean slopes (one
-estimate per participant per interval).
+  of the cases (see Figures \ref{fig.a3} to \ref{fig.a7} in the
+  supplementary material).} We tested Hypothesis 1b based on the
+unstandardized estimates of mean slopes (one estimate per participant
+per interval).
 
@@
         \midrule
-        (1) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
-        (2) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
-        (3) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
-        (4) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
-        (5) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
+        ($I_1$) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
+        ($I_2$) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
+        ($I_3$) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
+        ($I_4$) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
+        ($I_5$) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
         \bottomrule
@@
     \caption{\\
-    Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
+    Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}
     \begin{tabularx}{\textwidth}{lccccc}
@@
   \caption{\\
-  Laboratory setting of the micro-teaching unit. .}
+  Laboratory setting of the micro-teaching unit.}
   \includegraphics[width=0.5\textwidth]{appendix_figure1.png}

### 2024-10-03 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission_template.Rmd
affiliationen angepasst

@@
     footnote: 1
-  - name: Peer Keßler
-    email: peer.kessler@uni-greifswald.de
-    affiliation: University of Greifswald
+  - name: Christin Lotz
+    email: christin.lotz@uni-leipzig.de
+    affiliation: Leipzig University
     footnote: 2
@@
     footnote: 3
-  - name: Christin Lotz
-    email: christin.lotz@uni-leipzig.de
-    affiliation: Leipzig University
+  - name: Peer Keßler
+    email: peer.kessler@uni-greifswald.de
+    affiliation: University of Greifswald
     footnote: 4
@@
     city: Leipzig
-    state: Sachsen
-    postcode: 04109
+    postcode: "04109"
     country: Germany
@@
     addressline: Deutscher Pl. 6
-    postcode: 04103
+    postcode: "04103"
     city: Leipzig
-    state: Sachsen
     country: Germany
@@
     city: Greifswald
-    state: Mecklenburg-Vorpommern
-    postcode: 17489  
+    postcode: "17489" 
+    country: Germany 
 footnote:
   - code: 1
-    text: 
-      - "Conceptualization, Methodology, Formal analysis, Investigation, Data Curation, Writing - Original Draft"
+    text: "Conceptualization, Methodology, Formal analysis, Investigation, Data Curation, Writing - Original Draft"
   - code: 2
-    text: 
-      - "Conceptualization, Methodology, Writing - Review & Editing, Supervision"
+    text: "Conceptualization, Methodology, Writing - Review & Editing, Supervision"
   - code: 3
@@
         \midrule
-        ($I_1$) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
-        ($I_2$) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
-        ($I_3$) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
-        ($I_4$) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
-        ($I_5$) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
+        Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ ($I_1$)\\
+        Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ ($I_2$)\\
+        Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ ($I_3$)\\
+        Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ ($I_4$)\\
+        End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 ($I_5$)\\
         \bottomrule

### 2024-10-18 02_paper/02_study/01_fitbit_paper/R_scripts/analysis_190423 Kopie.Rmd
x paper

--- 2023-04-24 02_paper/02_study/02_fitbit paper/analysis_190423.Rmd
@@
 
-plot_overall
+lm_plot_phases
+
+ggsave(filename = "plots/test.pdf")
 ```
@@
   split(.$Phase) %>% 
-  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
+  map(~ lmerTest::lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
        data = .
@@
   map(~ tibble(time_span = names(.),
-               intercept = fixef(.)[[1]],
-               intercept_sd = VarCorr(.) %>% as_tibble() %>% .[1,5],
+               intercept = fixef(.)[1],
+               intercept_sd = VarCorr(.) %>% as_tibble(.) %>% .[1,5],
                intercept_p = coef(summary(.))[1, 5],
-               slope = fixef(.)[[2]],
-               slope_sd = VarCorr(.) %>% as_tibble() %>% .[2,5],
+               slope = fixef(.)[2],
+               slope_sd = VarCorr(.) %>% as_tibble(.) %>% .[2,5],
                slope_p = coef(summary(.))[2, 5]
@@
             n = NA,
-            `Mean(Intercept)` = round(intercept, digits = 3),
-            `SD(Intercept)` = round(intercept_sd$sdcor, digits = 3),
-            `p-Value (Intercept)` = round(intercept_p, digits = 3),
-            `Mean(Slope)` = round(slope, digits = 3),
-            `SD(Slope)` = round(slope_sd$sdcor, digits = 3),
-            `p-Value (Slope)` = round(slope_p, digits = 3)
+            `Mean(Intercept)` = intercept,
+            `SD(Intercept)` = intercept_sd$sdcor,
+            `p-Value (Intercept)` = intercept_p,
+            `Mean(Slope)` = slope, 
+            `SD(Slope)` = slope_sd$sdcor,
+            `p-Value (Slope)` = slope_p, 
             )
@@
 knitr::kable(., caption = "Overview")
+
+model_hurensohn <- 
+  df_regression %>% 
+  filter(time_span == "teaching") %$% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
+       data = .) %>% 
+  fixef(.)[2]
+
+fixef(model_hurensohn)[2]
+
+model_pre <- 
+  df_regression %>% 
+  filter(Phase == "Pre Teaching Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
+       data = .)
+model_teach <- 
+  df_regression %>% 
+  filter(Phase == "Teaching Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
+model_post <- 
+  df_regression %>% 
+  filter(Phase == "Post Teaching Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
+model_int <- 
+  df_regression %>% 
+  filter(Phase == "Interview Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
+model_end <- 
+  df_regression %>% 
+  filter(Phase == "End Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
+
+tib_pre <-
+
+```
+
+```{r}
+df_regression <- 
+  main %>% 
+  filter(time_span != "overall") %>%
+  dplyr::select("ID", "time_span","time","heart_rate_std") %>% 
+  distinct() %>% 
+  mutate(time = time / 100) %>% 
+  mutate(ID = as_factor(ID),
+         Phase = factor(time_span,
+                           levels = c("preparation","teaching","post","interview","end"),
+                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
+                           )
+         )
+
+fix_models <-
+  df_regression %>% 
+  split(.$Phase) %>% 
+  map(~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
+       data = .
+       )
+      ) %>% 
+    map(~ coef(.) %>%
+          tibble::as_tibble(.,
+                            rownames = "name") %>%
+          transmute(type = if_else(str_detect(name,
+                                              ":"),
+                                   true = "slope",
+                                   false = "intercept"),
+                    id = str_remove_all(name,
+                                        "[^[:digit:]]"),
+                    value = value
+                    ),
+
+    ) %>% 
+    bind_rows(.id = "Phase") %>% 
+    pivot_wider(names_from = type,
+                values_from = value
+                )
+p.values_slope <- 
+  fix_models %>% 
+  split(.$Phase) %>% 
+  map(~ t.test(x = .$slope,
+             mu = 0)$p.value
+      ) %>% 
+  bind_rows(.id = "Phase") %>% 
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_slope")
+
+p.values_intercept <- 
+  fix_models %>% 
+  split(.$Phase) %>% 
+  map(~ t.test(x = .$intercept,
+             mu = 0)$p.value
+      ) %>% 
+  bind_rows(.id = "Phase") %>% 
+  pivot_longer(cols = everything(),
+               names_to = "Phase",
+               values_to = "p.value_intercept")
+
+sd_mean <- 
+  fix_models %>% 
+  group_by(Phase) %>% 
+  summarize(mean_slope = mean(slope),
+            sd_slope = sd(slope),
+            mean_intercept = mean(intercept),
+            sd_intercept = sd(intercept))
+
+model_teach_fix <- 
+  df_regression %>% 
+  filter(Phase == "Pre Teaching Phase") %>% 
+  mutate(time = time / 60) %>% 
+  lm(formula = heart_rate_std ~ 0 + ID + time:ID,
+       data = .)
+
+table_data <- 
+  right_join(x = sd_mean,
+             y = p.values_intercept,
+             by = "Phase") %>% 
+  right_join(x = .,
+             y = p.values_slope,
+             by = "Phase") %>% 
+  transmute(Phase = factor(Phase,
+                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
+                           ),
+            n = NA,
+            `Mean(Intercept)` = mean_intercept,
+            `SD(Intercept)` = sd_intercept,
+            `p-Value (Intercept)` = p.value_intercept,
+            `Mean(Slope)` = mean_slope, 
+            `SD(Slope)` = sd_slope,
+            `p-Value (Slope)` = p.value_slope, 
+            ) %>% 
+  arrange(Phase)
+
+model_teach_fix %>% 
+  coef(.) %>% 
+  tibble::as_tibble(.,
+                    rownames = "name"
+                    ) %>% 
+  mutate(type = if_else(str_detect(name,
+                                   ":"),
+                        true = "slope",
+                        false = "intercept"
+                        )
+         ) %>% 
+  filter(type == "slope") %$% 
+  t.test(x = value,
+         mu = 0) -> test
+
+test$
+
+model_pre <- 
+  df_regression %>% 
+  filter(Phase == "Pre Teaching Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
+       data = .)
+model_teach <- 
+  df_regression %>% 
+  filter(Phase == "Teaching Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
+model_post <- 
+  df_regression %>% 
+  filter(Phase == "Post Teaching Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
+model_int <- 
+  df_regression %>% 
+  filter(Phase == "Interview Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
+model_end <- 
+  df_regression %>% 
+  filter(Phase == "End Phase") %>% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
+
+summary(model_teach_fix)
+
 ```

### 2024-10-18 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission.Rmd
x paper

--- 2024-09-26 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
@@
 
-[^5]: Although this procedure does not account for nonmonotonic progressions in individual HR, a graphical evaluation revealed that the linear estimates corresponded well to the majority of the cases (see XX in the supplementary material).
+[^5]: Although this procedure does not account for nonmonotonic progressions in individual HR, a graphical evaluation revealed that the linear estimates corresponded well to the majority of the cases (see Figures \ref{fig.a3} to \ref{fig.a7} in the supplementary material).
 

### 2024-10-18 02_paper/02_study/01_fitbit_paper/Submission/analysis_270423.Rmd
x paper

--- 2024-08-07 02_paper/02_study/01_fitbit paper/Submission/analysis_270423.Rmd
@@
 
-# Hier habe ich immer nur die Modelle getauscht. Also statt regr_end1 regr_teaching1 usw.
-
 summary(regr_preparation1)
+summary(regr_preparation2)
+summary(regr_preparation3)
+summary(regr_preparation4)
+summary(regr_teaching1)
+summary(regr_teaching2)
+summary(regr_teaching3)
+summary(regr_teaching4)
+summary(regr_post1)
+summary(regr_post2)
+summary(regr_post3)
+summary(regr_post4)
+summary(regr_interview1)
+summary(regr_interview2)
+summary(regr_interview3)
+summary(regr_interview4)
+summary(regr_end1)
 summary(regr_end2)
 summary(regr_end3)
-summary(regr_post4)
+summary(regr_end4)
 
@@
   df_multi %>% 
-  filter(Phase == "Pre Teaching Phase") %$% 
-  lm(slope ~ teaching_experience)
+  filter(Phase == "Pre Teaching Phase") %>% 
+  lm(slope ~ teaching_experience,
+     data = .)
 

### 2024-10-18 02_paper/02_study/01_fitbit_paper/Submission/tab_1.tex
x paper

--- 2024-08-02 02_paper/02_study/01_fitbit paper/Submission/tab_1.tex
@@
 
-\caption{Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)}
+\caption{\label{tab:table_1}Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)}
 

### 2024-10-18 02_paper/02_study/01_fitbit_paper/Submission/tab_2.tex
x paper

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-2}Descriptive statistics (n, M, SD) for the mean intercepts and the mean slopes for the five intervals}

\begin{tabular}{llllllll}
\toprule
Phase & \multicolumn{1}{c}{n} & \multicolumn{1}{c}{Mean(Intercept)} & \multicolumn{1}{c}{SD(Intercept)} & \multicolumn{1}{c}{p-Value (Intercept)} & \multicolumn{1}{c}{Mean(Slope)} & \multicolumn{1}{c}{SD(Slope)} & \multicolumn{1}{c}{p-Value (Slope)}\\
\midrule
Pre Teaching Phase & 6896 & 0.05 & 0.82 & 0.57 & 0.08 & 0.13 & 0.00\\
Teaching Phase & 7150 & 1.02 & 0.69 & 0.00 & -0.04 & 0.11 & 0.00\\
Post Teaching Phase & 6664 & 0.55 & 0.55 & 0.00 & -0.06 & 0.10 & 0.00\\
Interview Phase & 6287 & -0.62 & 0.61 & 0.00 & -0.02 & 0.07 & 0.01\\
End Phase & 5990 & -1.00 & 0.50 & 0.00 & -0.01 & 0.07 & 0.14\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Please note that M and SD of the overall course vs. the individual intervals were not exactly 0 and 1 due to rounding differences.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

### 2024-10-18 02_paper/02_study/01_fitbit_paper/Untitled/Untitled.tex
x paper

--- 2023-05-22 02_paper/02_study/02_fitbit paper/fitbit_paper_elsevier.tex
@@
 \usepackage[hyphens]{url}
+
+  \journal{An awesome journal} % Sets Journal name
 
@@
 \usepackage{lineno} % add
-  \linenumbers % turns line numbering on
 \usepackage{ifxetex,ifluatex}
@@
             pdfauthor={},
-            pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
+            pdftitle={Short Paper},
             colorlinks=false,
@@
 
+% From pandoc table feature
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+
 \begin{document}
@@
 
-  \title{New approaches to teachers' experience of stress: Do heart rate
-measurements with fitness trackers provide an efficient, inexpensive,
-and robust measurement method?}
-    \author[1]{Mandy Klatt%
+  \title{Short Paper}
+    \author[Some Institute of Technology]{Alice Anonymous%
+  \corref{cor1}%
+  \fnref{1}}
+   \ead{alice@example.com} 
+    \author[Another University]{Bob Security%
   %
   }
-   \ead{mandy.klatt@uni-leipzig.de} 
-    \author[1]{Peer Keßler%
+   \ead{bob@example.com} 
+    \author[Another University]{Cat Memes%
   %
-  }
-
-    \author[1,2]{Gregor Kachel%
+  \fnref{2}}
+   \ead{cat@example.com} 
+    \author[Some Institute of Technology]{Derek Zoolander%
   %
-  }
-
-    \author[1]{Christin Lotz%
-  %
-  }
-
-    \author[1]{Anne Deiglmayr%
-  %
-  }
-
+  \fnref{2}}
+   \ead{derek@example.com} 
+      \affiliation[Some Institute of Technology]{
+    organization={Big Wig University},addressline={1 main
+street},city={Gotham},postcode={123456},state={State},country={United
+States},}
+    \affiliation[Another University]{
+    organization={Department},addressline={A street
+29},city={Manchester,},postcode={2054 NX},country={The Netherlands},}
     \cortext[cor1]{Corresponding author}
+    \fntext[1]{This is the first author footnote.}
+    \fntext[2]{Another author footnote.}
 
   \begin{abstract}
-  One or two sentences providing a \textbf{basic introduction} to the
-  field, comprehensible to a scientist in any discipline.
+  This is the abstract.
 
-  Two to three sentences of \textbf{more detailed background},
-  comprehensible to scientists in related disciplines.
-
-  One sentence clearly stating the \textbf{general problem} being
-  addressed by this particular study.
-
-  One sentence summarizing the main result (with the words
-  ``\textbf{here we show}'' or their equivalent).
-
-  Two or three sentences explaining what the \textbf{main result}
-  reveals in direct comparison to what was thought to be the case
-  previously, or how the main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more \textbf{general
-  context}.
-
-  Two or three sentences to provide a \textbf{broader perspective},
-  readily comprehensible to a scientist in any discipline.
-
-  XXX In this proof-of-concept study, we aimed to advance the field of
-  teacher stress by collecting heart rate data with wrist-worn devices
-  and testing a methodology that has the potential to provide more
-  insights on the non-invasive assessment of teacher stress. XXX
+  It consists of two paragraphs.
   \end{abstract}
     \begin{keyword}
-    heart rate; photoplethysmography; wearable electronic device;
-teaching \sep 
-    heart rate; photoplethysmography; wearable electronic device;
-teaching
+    keyword1 \sep 
+    keyword2
   \end{keyword}
@@
 
+Please make sure that your manuscript follows the guidelines in the
+Guide for Authors of the relevant journal. It is not necessary to
+typeset your manuscript in exactly the same way as an article, unless
+you are submitting to a camera-ready copy (CRC) journal.
+
+For detailed instructions regarding the elsevier article class, see
+\url{https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions}
+
+\hypertarget{bibliography-styles}{%
+\section{Bibliography styles}\label{bibliography-styles}}
+
+Here are two sample references: \citeauthor{Feynman1963118}
+\citetext{\citeyear{Feynman1963118}; \citealp{Dirac1953888}}.
+
+By default, natbib will be used with the \texttt{authoryear} style, set
+in \texttt{classoption} variable in YAML. You can sets extra options
+with \texttt{natbiboptions} variable in YAML header. Example
+
 \begin{Shaded}
 \begin{Highlighting}[]
-\CommentTok{\# Seed for random number generation}
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{42}\NormalTok{)}
-\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{cache.extra =}\NormalTok{ knitr}\SpecialCharTok{::}\NormalTok{rand\_seed)}
+\FunctionTok{natbiboptions}\KeywordTok{:}\AttributeTok{ longnamesfirst,angle,semicolon}
 \end{Highlighting}
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+There are various more specific bibliography styles available at
+\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
+To use one of these, add it in the header using, for example,
+\texttt{biblio-style:\ model1-num-names}.
 
-Physiological data such as heart rate are becoming increasingly
-important in research on stress experience. They represent an important
-indicator of physical or emotional stress, as increased workload is
-associated with increased heart rate \citep{sachs2014physiologische}.
-Furthermore, they allow a more objective recording of stress than
-self-reports \citep{rungeusing}. However, capturing heart rate in an
-educational context requires the use of low-cost and non-invasive
-instruments. Fitness trackers worn on the wrist have the potential to be
-such a useful tool \citep{ferguson2015validity}.
+\hypertarget{using-csl}{%
+\subsection{Using CSL}\label{using-csl}}
 
-To date, there is still little evidence on the usefulness of heart rate
-measurements using fitness trackers in teaching and learning settings
-\citep{ertzberger2016use, lowe2016educational}. \citet{rungeusing} alone
-examined teacher stress in a relatively small sample (\emph{N} = 4
-teachers) and showed that high heart rate indicates more stress in
-teachers.
+If \texttt{citation\_package} is set to \texttt{default} in
+\texttt{elsevier\_article()}, then pandoc is used for citations instead
+of \texttt{natbib}. In this case, the \texttt{csl} option is used to
+format the references. Alternative \texttt{csl} files are available from
+\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
+and stored locally, or the url can be used as in the example header.
 
-Thus, there remains a lack of robust studies on whether fitness trackers
-are an efficient, low-cost, and robust measurement method for assessing
-teachers' experience of arousal during teaching.
+\hypertarget{equations}{%
+\section{Equations}\label{equations}}
 
-\hypertarget{theoretical-background}{%
-\section{Theoretical Background}\label{theoretical-background}}
+Here is an equation: \[ 
+  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
+  \left(\frac{x}{\beta}\right)^{\alpha-1}
+  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
+  \alpha,\beta,x > 0 .
+\]
 
-\hypertarget{stress-in-teaching-profession}{%
-\subsection{Stress in Teaching
-Profession}\label{stress-in-teaching-profession}}
+Here is another: \begin{align}
+  a^2+b^2=c^2.
+\end{align}
 
---\textgreater{} teacher profession is one of the most stressful
-professions.
+Inline equations: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)
 
-Teacher stress can be defined as ``{[}\ldots{]} the experience by a
-teacher of unpleasant, negative emotions, such as anger, anxiety,
-tension, frustration or depression, resulting from some aspect of their
-work as a teacher.'' \citep{kyriacou2001teacher}.
+\hypertarget{figures-and-tables}{%
+\section{Figures and tables}\label{figures-and-tables}}
 
-Teachers' individual perceptions of student misbehavior in the classroom
-are closely related to their well-being \citep{ALDRUP2018126}.
+Figure \ref{fig2} is generated using an R chunk.
 
---\textgreater{} wie entsteht Stress
+\begin{figure}
 
---\textgreater{} wie wurde Stress bisher gemessen
+{\centering \includegraphics[width=0.5\linewidth]{Untitled_files/figure-latex/fig2-1}
 
-\hypertarget{heart-rate-as-an-indicator-for-stress-or-arousal}{%
-\subsection{Heart rate as an indicator for stress or
-arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}
+}
 
-Heart rate is physiologically regulated by the autonomic nervous system.
-An increase in the activity of the sympathetic as part of the autonomic
-nervous system results in the heart rate being speeded up (``fight or
-flight''). On the other hand, an increased activity of the
-parasympathetic as the counterpart has the effect of slowing down the
-heart rate (``rest and digest'') \citep{Battipaglia2015}. In addition to
-the autonomic nervous system and genetic factors, heart rate is
-influenced by numerous external factors such as social, personal,
-psychological, environmental and behavioural factors
-\citep{wang2022using}.
+\caption{\label{fig2}A meaningless scatterplot.}\label{fig:fig2}
+\end{figure}
 
-\hypertarget{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}{%
-\subsection{Wrist-worn devices as a new approach to assess physiological
-measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}
+\hypertarget{tables-coming-from-r}{%
+\section{Tables coming from R}\label{tables-coming-from-r}}
 
-\citet{fuller2020reliability} showed in their review article that
-wearable devices such as Fitbit watches are accurate and reliable for
-measuring heart rate in controlled settings.
+Tables can also be generated using R chunks, as shown in Table
+\ref{tab1} for example.
 
-``The use of physiological measures enabled us to get some insight into
-teachers' affective responses without disrupting the teaching process
-(Mauss \& Robinson, 2009) and to reduce issues with social desirability,
-retrospective bias, and high cognitive load (Becker et al., 2015; Goetz
-et al., 2015; Scollon et al.,2009; Wilhelm \& Grossman, 2010). Moreover,
-we found that heart rate measures discriminated between both teachers,
-even when their interpersonal behavior during the lesson start was
-relatively similar.''
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{], }
+    \AttributeTok{caption =} \StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{label\{tab1\}Caption centered above table"}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{19}
-\tightlist
-\item
-  (PDF) A Quantitative Exploration of Two Teachers with Contrasting
-  Emotions: Intra-Individual Process Analyses of Physiology and
-  Interpersonal Behavior. Available from:
-  https://www.researchgate.net/publication/329787434\_A\_Quantitative\_Exploration\_of\_Two\_Teachers\_with\_Contrasting\_Emotions\_Intra-Individual\_Process\_Analyses\_of\_Physiology\_and\_Interpersonal\_Behavior
-  {[}accessed Dec 07 2022{]}.
-\end{enumerate}
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{\label{tab1}Caption centered above table}\tabularnewline
+\toprule()
+& mpg & cyl & disp & hp \\
+\midrule()
+\endfirsthead
+\toprule()
+& mpg & cyl & disp & hp \\
+\midrule()
+\endhead
+Mazda RX4 & 21.0 & 6 & 160 & 110 \\
+Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
+Datsun 710 & 22.8 & 4 & 108 & 93 \\
+Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
+Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
+Valiant & 18.1 & 6 & 225 & 105 \\
+\bottomrule()
+\end{longtable}
 
-\hypertarget{aim-of-the-study}{%
-\subsection{Aim of the study}\label{aim-of-the-study}}
-
-In the present study, we assessed HR measures and self-report data of
-pre- and in-service teachers in a controlled teaching-learning setting.
-The aim was to investigate whether heart rate measurements using
-wrist-worn fitness trackers are a suitable and effective method
-\textbf{(1)} to map differences in states of arousal between five
-different phases (pre-teaching phase, teaching phase, post-teaching
-phase, interview phase and end phase) and \textbf{(2)} to evaluate the
-correlation between self-reported evaluations and HR measures.
-
-\textbf{(H1)} We expected heart rates to be higher during the teaching
-phase than during the pre- and the three post-teaching phases, and that
-the HR measures would decrease over the course of the study.
-\textbf{(H2)} We also predicted that HR and a high ranking on the
-negative scale on our survey (feeling disturbed by disruptions) would
-correlate positively and a high ranking on the positive scale (feeling
-confident in dealing with disruptions) would follow the inverse pattern.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We report how we determined our sample size, all data exclusions (if
-any), all manipulations, and all measures in the study.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-\bibliography{r-references.bib}
+\renewcommand\refname{References}
+\bibliography{mybibfile.bib}
 

### 2024-10-18 02_paper/02_study/01_fitbit_paper/analysis_171123.Rmd
x paper

--- 2024-01-29 02_paper/02_study/02_fitbit paper/analysis_171123.Rmd
@@
 
-### Correlation
+### Correlations
 
@@
 ```{r}
+
+fix_models %>% 
+  filter(Phase == "Pre Teaching Phase") %>% 
+  select(slope) -> cor_pre_slope
+
 main %>% 
@@
           teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) -> cor_pre
+         ) -> cor_pre_hr
+
+cor_pre <- bind_cols(cor_pre_slope, cor_pre_hr)
 
@@
 
+# mean slope 
+cor.test(cor_pre$slope, cor_pre$teaching_experience)
+cor.test(cor_pre$slope, cor_pre$disruption_factor_m)
+cor.test(cor_pre$slope, cor_pre$confidence_factor_m)
+
 # teaching experience ~
@@
 ```{r}
+
+fix_models %>% 
+  filter(Phase == "Teaching Phase") %>% 
+  select(slope) -> cor_teaching_slope
+
 main %>% 
@@
           teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) -> cor_teaching
+         ) -> cor_teaching_hr
+
+cor_teaching <- bind_cols(cor_teaching_slope, cor_teaching_hr)
 
@@
 
+# slope ~
+cor.test(cor_teaching$slope, cor_teaching$teaching_experience)
+cor.test(cor_teaching$slope, cor_teaching$disruption_factor_m)
+cor.test(cor_teaching$slope, cor_teaching$confidence_factor_m)
+
 # teaching experience ~
@@
 ```{r}
+
+fix_models %>% 
+  filter(Phase == "Post Teaching Phase") %>% 
+  select(slope) -> cor_post_slope
+
 main %>% 
@@
           teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) -> cor_post
+         ) -> cor_post_hr
+
+cor_post <- bind_cols(cor_post_slope, cor_post_hr)
 
@@
 
+# slope ~
+cor.test(cor_post$slope, cor_post$teaching_experience)
+cor.test(cor_post$slope, cor_post$disruption_factor_m)
+cor.test(cor_post$slope, cor_post$confidence_factor_m)
+
 # teaching experience ~
@@
 ```{r}
+
+fix_models %>% 
+  filter(Phase == "Interview Phase") %>% 
+  select(slope) -> cor_interview_slope
+
 main %>% 
@@
          teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) -> cor_interview
+         ) -> cor_interview_hr
+
+cor_interview <- bind_cols(cor_interview_slope, cor_interview_hr)
 
@@
 
+# slope ~
+cor.test(cor_interview$slope, cor_interview$teaching_experience)
+cor.test(cor_interview$slope, cor_interview$disruption_factor_m)
+cor.test(cor_interview$slope, cor_interview$confidence_factor_m)
+
 # teaching experience ~
@@
 ```{r}
+
+fix_models %>% 
+  filter(Phase == "End Phase") %>% 
+  select(slope) -> cor_end_slope
+
 main %>% 
@@
           teaching_experience = (teaching_experience - mean(.$teaching_experience))/sd(.$teaching_experience)
-         ) -> cor_end
+         ) -> cor_end_hr
+
+cor_end <- bind_cols(cor_end_slope, cor_end_hr)
 
@@
 cor.test(cor_end$heart_rate_m, cor_end$confidence_factor_m)
+
+# slope ~
+cor.test(cor_end$slope, cor_end$teaching_experience)
+cor.test(cor_end$slope, cor_end$disruption_factor_m)
+cor.test(cor_end$slope, cor_end$confidence_factor_m)
 

### 2024-10-18 02_paper/02_study/02_expertise_paper/emu_questionnaire.tex
x paper

--- 2024-07-04 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.tex
@@
 \documentclass[
-  man]{apa6}
+]{article}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{xcolor}
+\usepackage[margin=1in]{geometry}
 \usepackage{graphicx}
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
- {\begin{list}{}{%
-  \setlength{\itemindent}{0pt}
-  \setlength{\leftmargin}{0pt}
-  \setlength{\parsep}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-   \setlength{\leftmargin}{\cslhangindent}
-   \setlength{\itemindent}{-1\cslhangindent}
-  \fi
-  % set entry spacing
-  \setlength{\itemsep}{#2\baselineskip}}}
- {\end{list}}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\ifLuaTeX
-\usepackage[bidi=basic]{babel}
-\else
-\usepackage[bidi=default]{babel}
-\fi
-\babelprovide[main,import]{english}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-% Table formatting
+\usepackage{booktabs}
 \usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
-
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
-
-\makeatletter
-\usepackage{etoolbox}
-\patchcmd{\maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
-\keywords{professional vision, expertise, classroom management, mobile eye-tracking\newline\indent Word count: XXX}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
-\usepackage{lineno}
-
-\linenumbers
-\usepackage{csquotes}
-\usepackage[titles]{tocloft}
-\cftpagenumbersoff{table}
-\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
-\renewcommand{\cfttabaftersnum}{.\space}
-\setlength{\cfttabindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cfttabnumwidth}{Table 10.\qquad}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \ifLuaTeX
@@
 \hypersetup{
-  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
-  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
-  pdflang={en-EN},
-  pdfkeywords={professional vision, expertise, classroom management, mobile eye-tracking},
+  pdftitle={EMU Questionnaire - Item \& Scale Analysis},
   hidelinks,
@@
 
-\title{Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions}
-\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
-\date{}
-
-\shorttitle{Professional Vision in Micro-Teaching-Units}
-
-\authornote{
-
-We received funding from QualiFond of University Leipzig.
-We have no conflicts of interest to disclose.
-This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).
-
-Correspondence concerning this article should be addressed to Mandy Klatt, Dittrichring 5-7, 04109 Leipzig. E-mail: \href{mailto:mandy.klatt@uni-leipzig.de}{\nolinkurl{mandy.klatt@uni-leipzig.de}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Leipzig University\\\textsuperscript{2} Max Planck Institute for Evolutionary Anthropology}
+\title{EMU Questionnaire - Item \& Scale Analysis}
+\author{}
+\date{\vspace{-2.5em}}
 
@@
 
-\section{Introduction}\label{introduction}
+\section{Presence Questionnaire}\label{presence-questionnaire}
 
-Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson, Weinstein, et al., 2006; Kounin, 2006).
-Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom.
-This ability is referred to as classroom professional vision (\textbf{goodwin2015?} professional; Sherin, 2007).
-The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (``noticing'') and applying knowledge to draw appropriate conclusions in these situations {[}``knowledge-based reasoning''; Seidel and Stürmer (2014){]}.
-Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students' learning time and minimize classroom interruptions.
-According to Kounin (2006), these important classroom management strategies are called ``withitness'' and ``overlapping'' and can be summarized under the concept of monitoring (Gold \& Holodynski, 2017).
-Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017).
-Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, ``{[}\ldots{]} whereas only a few studies have focused on the basal process of noticing, i.e.~the recognition of possible disturbing situations'' (\textbf{grub2020processp?}).
-Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner, Jarodzka, \& Nückles, 2016; Wolff, Jarodzka, Bogert, \& Boshuizen, 2016).
-
-\section{Theoretical background}\label{theoretical-background}
-
-\subsection{Professional competence in teaching profession}\label{professional-competence-in-teaching-profession}
-
-Competence is a common term in everyday school life.
-In most cases, it refers to the acquisition of competencies by students and how to promote them and make them effective.
-In the same way, the term competence can be applied to teachers.
-Teachers have to be competent in things such as teaching, educating, evaluating or innovating.
-Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig, \& Rauch, 2008).
-They replace the rigid canon of knowledge that defined professional qualification for generations.
-In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.).
-To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf.
-Klieme et al., 2008, p.
-4).
-In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.
-
-In science, there is some agreement on the two opposing perspectives of competence versus empowerment.
-The former means a broad, concept, whereas empowerment refers to the different components of competence (cf.~of competence (cf.~Blömeke, Gustafsson \& Shavelson, 2015, p.5).
-These can be of a cognitive, conative, affective, or motivational nature (ibid.).
-To determining professional qualification, competence is an irreplaceable tool.
-
-Competence is learnable and can thus be improved through targeted practice (cf.~Weinert 2001; cited in Blömeke et al.~2015, p.~5).
-This is one reason, among others, why this concept is so relevant for empirical school and development research.
-Another crucial step in clarifying the concept of competence is to understand that the framework of competence recognizes the importance of everyday life situations (Blömeke et al., 2015).
-Therefore scholars argue, a definition must start from an authentic ``analysis of occupational or societal situations and must take into account the tasks and associated associated cognitive, conceptual, affective, and motivational aspects'' (Blömeke et al., 2015, p.~5).
-Through this comprehensive approach, many inconsistencies in the definition of the term can be resolved.
-The definition of competence is now no longer a question of whether it is a number of cognitive skills or a combination of cognition, conation, affect, or motivation.
-It combines ``complex intellectual characteristics together with affect-motivation, which underlies observable underlying performances'' (Blömeke et al.~2015, p.~6).
-This is best defined as a process or even continuum (see Figure 1), which consists of different levels and should be understood as a multidimensional construct with stronger and weaker Domains (ibid.).
-
-The term competence finds its place in a variety of disciplines as an assessment standard of qualifications.
-In this context, the term professional competence has become established in research, which defines competence in a specific professional field.
-Thus, based on the assumption that competence is more than mere knowledge, professional competence offers a way to make teacher success in schools tangible (Kunter et al., 2013).
-
-The term ``professional competence'' is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation.'' {[}cf.
-Epstein and Hundert (2002); cited in Kunter et al.~2013, p.~807{]}.
-Several studies could prove that this idea can be successfully transferred to the teaching profession {[}cf.~Goodmann et al., 2008; Oser, Achtenhagen, and Renold (2006), Achtenhagen \& Renold, 2006; Tannenbaum \& Rosenfeld, 1994; cited in Kunter et al., 2013, p.~807{]}.
-Accordingly, a quality standard can be applied to assess the quality of a teacher.
-This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano, \& Pickering, 2003).
-Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher.
-Research has shown that this component can even offset the influence of an ineffective school setting (Marzano et al., 2003).
-This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.
-
-\subsection{Classroom Management}\label{classroom-management}
-
-Teachers and students are in the classroom in a place that is always alive, characteristic of its heterogeneity and the interests of different groups.
-These the circumstances of a classroom are also characterized as multidimensional, simultaneous, immediate, unpredictable, public, and shared (Doyle, 2011, p.~99).
-All of these circumstances place a number of demands on teachers, which primarily involve planning and monitoring activities (ibid.).
-``Order in classrooms is not a consequence of reactions to misbehavior but a condition established and sustained by the way a teacher organizes and guides a complex system of classroom activities'' (Doyle, 1989, p.12).
-Thus, ``good'' teachers create the conditions for effective teaching through pre-planned actions and activities that they are always in control of while teaching.
-This enables them to maximize work time while keeping disruptions of any kind to a minimum to facilitate learning for all participants (Doyle, 1989).
-
-However, lessons, and specifically classroom disruptions, are unpredictable as well as multifaceted and require a high level of expertise and competence on the part of the teacher to handle.
-This trained handling, as described above, can be summarized under the aspect of professional competence.
-It is expressed, among other things, in knowledge about classroom management (Grub, Biermann, \& Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
-
-Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, Bogert, Jarodzka, \& Boshuizen, 2015).
-Marzano et al.
-(2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching.
-In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015).
-Therefore, it is often referred to as the central variable of successful teaching (Helmke \& Helmke, 2015).
-Good classroom management is thus the prerequisite for learning to take place (Wolff et al., 2015).
-While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.
-
-An initial explanatory approach to classroom management was provided by Doyle (1990, p.355) with his definition of teaching, which he described as a ``cognitive activity based on knowledge of the probable course of events in the classroom and the ways in which actions affect situations.'' From this, it is clear that in order to teach successfully, a teacher needs knowledge of how to process as well as represent the full range of classroom events.
-In addition, it is necessary to be able to respond or interact proactively and effectively to potential events at best.
-
-Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf.
-Wolff et al., 2015, p.
-71).
-These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.).
-If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction.
-This is crucial to maximize students' active learning time (Helmke \& Helmke, 2015).
-It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research.
-In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise (Wolff et al., 2015).
-
-\subsubsection{Interdependence of classroom management}\label{interdependence-of-classroom-management}
-
-In research, various models exist for approaching the concept of classroom management.
-However, they are very similar in their core statements.
-Therefore, it is merely a matter of preference which concept is consulted to explain connections and terms.
-In the following, the network of effects of classroom management according to Helmke et al.
-(2014) is used as a reference model in order to be able to understand the embedding of the concept accordingly.
-
-As was made clear in the definition, classroom management is a complex construct that attempts to accommodate the various modes and challenging characteristics of a classroom.
-Helmke et al.
-(2014) therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time.
-This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (\emph{d} = 0.39; Hattie, 2013, p.219).
-Due to this diversity of aspects to be investigated, classroom management is a fundamental research topic.
-
-The concepts, strategies and techniques used to implement successful classroom management depend first and foremost on various teacher characteristics and are ``interrelated with the quality of teaching and personal relationships'' (Helmke \& Helmke, 2015, p.5).
-It should not be forgotten that this space never functions in isolation and independently of other influences.
-It is embedded in diverse contexts, especially in the school and class context (Helmke \& Helmke, 2015).
-But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led (Helmke et al., 2014).
-
-Classroom management itself is made up of various components which, according to Helmke et al.
-(2014), can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior.
-Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke \& Helmke, 2015).
-
-The importance of rules in the classroom has been known and researched for some time.
-Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules {[}cf.~Emmer, Evertson \& Anderson, 1980; Emmer, Sanford, Clements, and Martin (1982); cited in Doyle, 1989, p.~15{]}.
-Although he also stresses that establishing a system of rules is a difficult task.
-Classroom rules are situation-dependent, as certain agreements only apply to certain phases of the lesson (for example, speaking quietly during group work; Doyle, 1989).
-Furthermore, order is always established jointly, in cooperation with the learners (Doyle, 1989).
-
-As a result, students significantly influence these rules by their willingness to follow them.
-Procedures are another tool to maintain the flow of the lesson, as recurring routines provide learners with security and clarity (Helmke \& Helmke, 2015).
-This inevitably reduces the teacher's workload, eliminates additional explanations are no longer necessary, and it is clear to the learners at all times what needs to be done.
-needs to be done.
-In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time (Helmke et al., 2014).
-For the reasons just reasons just explained, it is clear why Hattie (2013, p.~122) gives this component of classroom classroom management an effect size of \emph{d} = 0.76.
-
-No other aspect of classroom management is as effective for classroom interruptions as the teacher's omnipresence (Hattie, 2013, p.~122); the effect size is \emph{d} = 1.42.
-(Helmke \& Helmke, 2015, p.~6).
-The behavioral pattern of presence is not a new concept.
-It was already recorded by kounin1970discipline under the term \emph{withitness}.
-Later research confirmed and validated his assumptions and definition of the term (cf.
-Helmke et al., 2014, p.
-10).
-In order to be present, the teacher must be able to control the classroom adequately and superficially effectively at all times.
-This means she must be able to recognize relevant cues or situations that require possible action (Wolff et al., 2015).
-Presence can consequently be illustrated very vividly by means of the image of ``eyes in the back of the head'' (Kounin, 2006).
-In addition to presence, Kounin (2006) uses the term overlap.
-It is a kind of multitasking ability to be able to cope with parallel processes and situations in the classroom.
-The two dimensions of overlap and presence can also be summarized together under the term monitoring (Gold \& Holodynski, 2017).
-When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners (Grub et al., 2020).
-Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness of relevant events in the classroom (ibid.).
-From this point of view, it becomes clear why awareness is a core component of teacher competence.
-
-As a third component influencing the quality of classroom management, cites Helmke et al.
-(2014) time use and management.
-This seems trivial at first, considering that classroom management serves the goal of maximizing learning time anyway.
-However, Helmke \& Helmke (2015, p.~6) emphasize how elementary it is to identify and minimize possible ``time thieves''.
-This includes factors such as unpunctuality or slow transitions, as well as the underemployment of learners (ibid.).
-If these take up too much space in the classroom, less time is available for teaching important lesson content.
-This can be prevented by teachers minimizing such ``time thieves'' in advance through well-planned classroom management.
-
-In order to enforce desired student behavior or to reduce contradictory behavior, teachers can use various discipline-related interventions and also make use of negative sanctions and positive reinforcement (Helmke \& Helmke, 2015).
-The authors emphasize that a healthy balance must be found when using these strategies.
-Over the years, this constructive approach has fallen into disrepute due to its behaviorist character.
-However, elements such as reinforcement, extinction or punishment are not negligible laws of learning psychology whose effectiveness has been proven by Hattie (2013), among others.
-These behavioral psychological measures have an effect size of \emph{d} = 0.76 (cf.~Hattie, 2013, p.215) and are therefore an effective means of reducing disruptions (Helmke \& Helmke, 2015).
-
-Researchers in pedagogy also point out, however, that it is not only pure knowledge about classroom management that determines its effectiveness and influences it (Helmke \& Helmke, 2015).
-The teacher personality, which includes characteristics such as subjective tolerance margins, i.e.~at what point does one perceive a certain behavior as disruptive, also plays a role.
-This includes further aspects such as emotion control, empathy or the credibility of a teaching person that arises through appearance.
-These characteristics, which occur in many ways, have a direct impact on the quality of teaching and classroom management, as they influence the planning behavior, perception and reaction of teachers.
-
-\subsection{Professional vision}\label{professional-vision}
-
-Competence assessment plays a central role in the teaching profession and its training.
-It follows the approach of concentrating on action-relevant as well as lesson-related content in order to train corresponding competences for teaching practice (KMK, 2004).
-In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes (V.
-L.
-Barth, 2017).
-Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel, \& Prenzel, 2014).
-The concept of professional vision can originally be traced back to the anthropologist Charles Goodwin and became known under the term Professional Vision (Sherin, 2001).
-It provided the answer to Goodwin's question regarding the development of a professional vision, in the context of the profession, compared to the vision of everyday situations.
-Goodwin uses the comparison of an archaeologist and a layperson to figuratively describe the differences.
-In doing so, he investigated which ability it is that makes the archaeologist see and interpret a landscape differently than the layperson (cf.~Sherin, 2001, p.~75).
-What looks to the former merely like sand, rocks and stones, is to the trained eye of the archaeologist a base of a column or architectural fragments.
-Goodwin (1994, p.606) defines professional vision as ``socially organized ways of seeing and understanding events that are answerable to the distinctive interests of a particular social group'' (cited in Sherin, 2001, p.~75).
-It is assumed that one can see certain phenomena or occurring events in a certain way due to one's professional affiliation (Sherin, 2001).
-Particularities are more easily recognized because the gaze becomes more trained over time and thus profession-relevant features appear more distinctive.
-In the previous example of the archaeologist, this would mean that he noticed variations in color, texture and sand and saw a cluster of stones as a possible element of a larger structure (cf.~Sherin, 2001, p.75).
-This distinguishes experts significantly in their visions from non-experts in the field, as they had learned to filter their environment for crucial features.
-
-\subsubsection{Teachers' professional vision}\label{teachers-professional-vision}
-
-Based on the assumption that the professional vision can develop over time, Sherin (2001) postulates that teachers can also acquire a professional vision.
-As teachers develop from novices to experts in their field, they accumulate expertise in a variety of areas (cf.~Sherin, 2001, p.~76).
-This can be seen, among other things, in flexible reactions to unexpected events or the smooth implementation of routines in the classroom Leinhardt \& Greeno (1986).
-This type of action can be described as a skill that helps teachers make decisions about what is relevant and what is not within the complex classroom setting (van Es \& Sherin, 2002).
-Such decisions are based on professional knowledge that guarantees effective teaching and learning in actual classroom situations (Jahn et al., 2014).
-Professional awareness is therefore referred to as an indicator of how knowledge is represented in teachers (Stürmer et al., 2017).
-It can also be seen as a bridge or link between knowledge and action, or professional competence and behavior (\textbf{grub2020process0?}).
-It is important to understand that professional vision is acquired and not inherent.
-Rather, it is subject to a process of acquisition that is constantly progressing as teachers are exposed to events and learn to interpret them (Wolff et al., 2016).
-Fundamentally, then, prospective teachers must select what to focus their attention on in the classroom and how to understand these events (Stürmer et al., 2017).
-Finally, teaching and learning take place in a complex environment.
-Simultaneous events and situations cannot be given the same attention.
-``Selective perception is necessary in order to distinguish important from unimportant features and to focus attention on relevant aspects'' (V.
-L.
-Barth, 2017, p.
-19).
-Furthermore, teachers benefit from from a trained perception of problems, as this is a significant factor in being able to preventively counteract preventive measures (Wettstein, 2013).
-
-Basically, the complex process of professional vision is divided into three sub-processes (Grub et al., 2020).
-First of all, the identification, the recognition, of an event takes place.
-Then connections are made, which are finally evaluated by the teacher using his or her professional knowledge.
-In research, these processes are often combined and one speaks of noticing to describe recognition (Grub et al., 2020).
-Knowledge-based reasoning includes the last two processes of applying knowledge to make appropriate decisions (ibid.).
-During this process, it becomes clear that the recognition of relevant situations, such as disruptions, precedes all others.
-This process is therefore considered necessary, without which professional vision cannot take place (Grub et al., 2020).
-As described in the chapter on competence, perceptions is also of particular importance in the competence model according to Blömeke et al.~(2015).
-This is because the process of perception forms an essential basis for situation-specific skills of teachers (Grub et al., 2020).
-Inferentially, recognition is inevitable for the perception of classroom events and therefore highly relevant for effective classroom management (ibid.).
-
-Even though the recognition of relevant situations in the classroom is the starting point for all further subsequent actions, the processes of knowledge-based reasoning within professional vision are not to be neglected.
-It is also said that this process is an indicator of the quality of how knowledge is applied to a given situation (Grub et al., 2020), as teachers need to make knowledge-based inferences.
-Qualitative research on knowledge-based reasoning concluded that it can be subdivided into three further sub-processes.
-Sherin (2007; cited in V.
-L.
-Barth, 2017, p.
-20) made a first subdivision, which consists of the processes of describing, evaluating and interpreting.
-When a teacher describes what she notices, she concentrates on observable characteristics, i.e.~important aspects of teaching (ibid.).
-When evaluating, statements are made about the quality of the teaching actions, and when interpreting, conclusions are drawn about possible mechanisms of the event (cf.
-V.
-L.
-Barth, 2017, p.
-19).
-Seidel et al.~(2010), on the other hand, focus on German-speaking countries in their research on professional vision and modified Sherin's original concept.
-They also divide knowledge-based-reasoning into three levels, but these differ: describing, explaining and predicting (V.
-L.
-Barth, 2017).
-More precisely, these processes encompass the ability to differentially describe instructional components that have an impact on learning; to make theoretically sound explanations about instructional situations; and to predict the effects of these events in relation to the teaching-learning process (cf.~Seidel et al., 2010, p.~297).
-This scientific work examines only the processes of noticing, which is why these two approaches have been presented for the sake of completeness.
-However, it is not useful to specify which classification of knowledge-based reasoning is referred to in arguments.
-is referred to in argumentation.
-
-Against this scientific background, it can be deduced that the two processes of noticing and knowledge-based-reasoning in professional vision cannot be considered separately from each other, but that they have a reciprocal effect (\textbf{sherin2007development7?}; cited in \textbf{barth2017professionelle7?}).
-What is considered and perceived as relevant in a teacher's selective vision (noticing) functions as the basis of the subsequent processes of describing, evaluating, and interpreting (knowledge-based-reasoning).
-Conversely, by engaging with these processes, the teacher's perception is sensitized.
-This leads to the fact that in the future certain characteristics of this situation can be recognized rather.
-
-\subsection{Measuring professional vision: eye-tracking technology in research}\label{measuring-professional-vision-eye-tracking-technology-in-research}
-
-Professional vision of teachers is a complex undertaking, consisting of various cognitive and visual processes.
-In the previous chapter, the importance of perception and its associated visuality was emphasized, which places the eye at the center of investigations.
-In research, process-based methods are used to make these perceptual processes visible.
-In this context, eye-tracking (ET), a modern method of recording gaze, has proven to be an effective tool in research.
-It allows us to literally see through the eyes of recipients and provides insight into another perspective.
-Intrinsic human cognitive processes are often compared to a black box in science, as these activities are not directly measurable (Rakoczi, 2012).
-Until now, cognitive processes could only be studied by verbalizing the respective subjects.
-However, this method is highly susceptible to interference due to its incomplete accessibility (Dessus, 2016).
-The increasingly popular research method of eye-tracking technology therefore represents an innovative means of externalizing, i.e., making visible, internalized processes by means of eye movements (Gegenfurtner et al., 2018) Stimuli in the environment are always perceived by our eyes as the first receiver.
-They take in the information and pass it on to our brain so that it can finally be processed there.
-By measuring this complex process, eye movements can be recorded and subsequently analyzed (Rakoczi, 2012).
-Information is obtained about the visual behavior, attentional focus, selection decisions, and even learning processes of the investigator (ibid).
-In addition to these qualitative results, which provide information about underlying cognitive processes, quantitative data can also be collected through eye-tracking (Cullipher, 2018).
-These provide information, for example, about how long and in what order stimuli are looked at, or whether certain parts are looked at more often than others (ibid.).
-This enables research to make data objectively assessable.
-
-Eye-tracking technology can be roughly divided into two types of devices: Stationary and mobile systems (Blake, 2013).
-In research so far, mainly eye-tracking devices have been used, which phenotypically resemble a computer (ibid.).
-They are also referred to as remote devices and, once calibrated, measure eye movements in a non-contact manner using infrared light (\textbf{egenfurtner2018mobiles?}).
-However, this technique reaches its limits when it comes to collecting data in everyday situations.
-For this purpose, the more flexible variant, mobile eye tracking (MET) or head-mounted or wearable eye trackers, can be used.
-Typically, the technology is found as a head-mounted device on helmets or integrated into an eyeglass frame (Blake, 2013).
-The difference with stationary tracking is that in addition to an eye camera and infrared light source, additional cameras are built in to capture head movements (ibid.).
-These are intended to help document the subject's field of view.
-Therefore, such systems are particularly suitable for applied sciences, as is the case in empirical school and development research (Gegenfurtner et al., 2018).
-
-Eye-tracking research is based on several fundamental assumptions.
-The connection between mental processing and eye movements has already been carefully investigated and provides viable empirical evidence to date (cf.
-Blake, 2013, p.
-380).
-In this regard, hoffman1995role obtained the finding that when the eyes are focused on an object, this is associated with an attentional focus of the person.
-Based on these findings, ET technology is based on the following two assumptions: The immediacy assumption and the eye-mind assumption (cf.~Rakoczi, 2012, p.87).
-The former defines that cognitive evaluation processes begin immediately upon fixation on an object (Cullipher, 2018).
-If a new stimulus attracts attention and is fixated, the observer starts processing this new information (ibid.).
-The eye-mind hypothesis assumes that whatever is fixated by the eye, is subsequently processed by the mind (ibid.).
-It thereby expansively defines, that objects are visually focused only until they are cognitively evaluated or until there is have been cognitively evaluated or there is still an interest (cf.~Rakoczi, 2012, p.87).
-However, a situational context must exist for the assumptions just explained to be are valid (ibid.).
-Through these functions, it becomes clear that the intrinsic processes of recognition in professional vision can be measured by eye-tracking technology.
-
-Despite the externalization of internalized processes and the resulting multitude of data potentially to be collected, ET technology cannot provide answers about the exact thoughts during stimulus processing.
-ET can identify where and when people are looking, but it does not answer why.
-For this, it is helpful to triangulate the data and apply alternative elicitation (Cullipher, 2018).
-One proven method is to conduct reflective interviews, which can be conducted in the format of a think aloud protocol (Konrad, 2020).
-This thinking aloud opens up the possibility of gaining insights into subjects' thinking, feeling, and intentions (edb.).
-An elaborated form of the Think Aloud Protocol is a Stimulated-Recall Interview (SRI).
-This is a qualitative scientific method to obtain data on preactional thought processes (cf.~Messmer, 2015, p.4).
-The pre-recorded lesson sequences are played back and subjects have the opportunity to express themselves about their ``thoughts, beliefs, norms, and decisions'' (Messmer, 2015, p.4) during the interview process.
-Thus, the visual data of the ET can be matched with cognitive processes and processes of knowledge-based-reasoning can be better understood.
-Individual-dependent thinking is now no longer pure speculation and can be made objectively observable in a way (Messmer, 2015).
-Subjects also have the opportunity to explain their actions and become aware of the basis for their decisions (ibid.).
-
-\subsubsection{Parameters and indicators of teachers' professional vision}\label{parameters-and-indicators-of-teachers-professional-vision}
-
-In university education, there is an increasing focus on developing the professional vision of future teachers (Stürmer et al., 2017).
-In order to determine the professional vision of teachers by means of mobile eye-tracking (MET), different indicators are worth considering.
-This scientific work focuses primarily on processes of noticing, i.e., the identification of relevant teaching situations as well as perception time.
-Therefore, in the following we will focus more on the parameters and indicators necessary for these processes.
-
-In MET, collected data sets are usually output according to different parameters: Fixations and Saccades (Gegenfurtner et al., 2018).
-The latter describes gaze jumps, i.e., movements of both eyes, which are useful to capture new fixations (Eye-Tracking Kompetenzzentrum Schweiz, 2021).
-Significant for this scientific work and the analysis of professional vision are the fixations as well as subjects' areas of interests.
-Fixations describe the period of time in which no movements are emitted by the eye (Holmquist et al.~2011) and are based on the eye-mind hypothesis described in the previous chapter.
-A fixation of an object can be characterized according to its duration, frequency, and distribution.
-In the illustration, the radius of a circle defines the duration of a fixation (Gegenfurtner et al., 2018).
-These data can also be used to describe perception times, such as the time until the first fixation on a particular object.
-In order to make this time period objectively measurable make it objectively measurable, a concept developed by Tobii Pro Lab Analyzer Software is used.
-In this software these organized recorded data are called Time of Interests (short TOIs), which describe time intervals of corresponding events or behaviors (Tobii Pro, 2021).
-Specifically, they are defined by the beginning and end of the corresponding event.
-
-By means of eye movement measurement, attention allocations to areas of interest or objects are made accessible in addition to pure fixations (Gegenfurtner et al., 2018).
-In research, these regions in the field of view of subjects are referred to as areas of interest (AOI) (edb.).
-They are significant in that, for the measurement of perceptual velocities of a relevant instructional event, not only TOIs but also the locations of fixations are crucial.
-Thus, it can be determined how subjects distribute their attentional resources and whether they recognize and perceive relevant events.
-
-\subsubsection{Expertise differences in professional vision}\label{expertise-differences-in-professional-vision}
-
-Since it is assumed that professional vision is a preferably knowledge-based process, differences between experienced and inexperienced teachers have already been identified.
-These differences were in favor of experts, since a connection between teaching experience and the associated increase in knowledge acquisition is assumed (Grub et al., 2020).
-Student teachers do not have well-structured experiential knowledge due to their almost non-existent practice in everyday school life (Wolff et al., 2016).
-This causes them selection difficulties in perception and is called pedagogical knowledge gap (cf.
-Wolff et al., 2016, pp.
-2016, p.260).
-Through newly gained experiences, the professional vision of a teacher is continuously restructured and updated, and mental representation is constantly realigned accordingly (ibid.).
-This has been proven in research as a positive correlation of input to teaching and learning theories in studies and professional classroom perception has been found (Stürmer et al., 2012).
-Therefore, it can be assumed that there is a relationship between teacher expertise, their visual processing, and mindfulness for classroom management (Wolff et al., 2016).
-Research has also shown that declarative knowledge acquisition, i.e., acquisition of factual knowledge, supports perceptual processes {[}Seidel et al., 2012; cited in Treisch (2018), p.26{]} Accordingly, this increased knowledge acquisition would explain a positive impact on professional teaching perception.
-Among the most important prerequisites for this acquisition, baumert2006key include prior knowledge and interest.
-The former is elementary for new knowledge acquisition about effective teaching and learning, as it supports processing, integration, and consolidation of it (Stürmer, 2011).
-Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions (cf.
-Sabers, Cushing, \& Berliner, 1991; cited in Treisch, 2018).
-This is explained by increased filtering mechanisms that support perceptual processes, i.e., recognition.
-Specifically, it has been shown that experienced teachers have more fixations on relevant areas because they have already learned theories on how to detect potential clutter in the classroom (Grub et al., 2020).
-Furthermore, experts have an advantage when it comes to coding information.
-Novices, on average, have a longer viewing times, so-called fixation durations, which is due to their still weakly developed expert knowledge (ibid.).
-
-\subsubsection{Mobile eye tracking in teaching-learning situations}\label{mobile-eye-tracking-in-teaching-learning-situations}
-
-As explained in detail earlier, teachers face a number of challenges during teaching.
-The teacher as organizer has to permanently scan the classroom for potential interruptions or possible events occurring such as classroom disruptions.
-In the worst case, they force a standstill in the flow of instruction, which is naturally to be avoided.
-Lohmann (2015, p.13) describes classroom disruptions as ``events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place.'' However, such an event only becomes a disruption when actors inside the classroom, perceive, interpret and finally evaluate it as disruptive {[}cf.
-Eckstein, Grob, and Reusser (2016); cited in, Eckstein, 2018, p.11{]}.
-Thus, instructional disruptions are strongly dependent on perception and involve elements of production as well as reception (ibid.).
-These discipline conflicts can be divided into four categories of disruptive student behavior: Verbal disruptive behavior (chattering, heckling), lack of eagerness to learn (mental absence in the form of drawing or playing on the cell phone), physical disruptions (snapping, drumming, pen clicking), and aggressive behavior (temper tantrums, attacking people; Lohmann, 2015).
-
-In order to be able to recognize inappropriate behavior in a timely manner, the teacher must have a pronounced omnipresence, as well as pedagogical-psychological knowledge about teaching and learning processes (Cortina et al., 2018).
-These skills and competencies are reflected in how teaching situations relevant to learning are perceived and interpreted by teachers (ibid.).
-In this context, a multitude of visual attention processes occur during classroom activities.
-This simply means the attention or the conscious non-attention to visual stimuli (Rüth et al., 2020).
-This situational awareness of a teacher and the accompanying control of his or her visual attention forms the foundation of situation-specific skills (cf.~Rüth et al.~2020).
-These data and insights potentially to be collected form an interesting field of research and useful tool for problem-based teaching education (Cortina et al., 2018).
-
-In the last decade, visual input through recorded teaching situations has been preferred (ibid.).
-Subjects are thus shown an outside perspective from different points of view.
-This can happen either as self or external video and allows micro-analysis or interaction sequences through the characteristic of repeated playing of a video (ibid.).
-This characteristic makes it possible to analyze corresponding scenes more intensively and in more detail.
-This results in a potential for reflection on teaching situations in teacher education that should not be underestimated (cf.~Rüth et al., 2020).
-The problem with these videotaped sequences, however, is the lack of access to the first-person perspective (ibid.).
-As a result, students usually evaluate and comment on their own videos more negatively than those of others afterwards (Cortina et al., 2018).
-They find it difficult to analyze the sequences objectively and to leave out unimportant details that concern their person.
-However, this is not purposeful and conducive to the intended learning process of the participating teachers.
-This is due to the fact that self-drawn cognition is activated in self-videos and that when negative events occur, subjects tend to defend their actions (ibid.).
-Kleinknecht and Schneider (2013) analyzed this process in more detail and found that this is particularly problematic for the reflective learning process, as it has a counterproductive effect on analyzing possible alternative actions.
-They also found that in third-party videos, reflection on potential alternative actions was twice as frequent as in self-recorded videos (ibid.)!
-In addition, recorded video sequences differ significantly from real classroom settings in which the teacher can independently determine her field of view.
-The observers cannot decide for themselves what to pay attention to and for how long to pay attention to a situation or event (Sherin, 2001).
-Based on this finding, it was significant for researchers to use an alternative elicitation technique to factor out the negative effects of self and other videos.
-
-A successful method to reduce this hindering factor of self-drawn cognition and still use self videos for teacher education is to use recordings that show the teacher's perspective and furthermore make it known where the teacher was looking (cf.~Cortina et al., 2018).
-In MET's video material, teachers can never see their teaching through their own eyes.
-This makes it possible to focus more specifically on essential aspects, such as classroom disruptions and interactions with learners.
-Although it has not yet been clearly demonstrated that significantly less self-referential cognition was elicited, self-videos counteract over-focusing on the acting person (cf.~Cortina et al., 2018).
-Therefore, MET represents a target-rich method for capturing teachers' attentional processes in the classroom.
-Previous studies with large data sets on teachers' visual expertise have predominantly used stationary ET (Wolff et al., 2016).
-In MET studies, the samples turn out to be much smaller; here, the largest study to be mentioned is with 12 experienced and 12 inexperienced teachers by Cortina et al.~(2015).
-
-\subsubsection{Perceptions of classroom disruptions and their parameters}\label{perceptions-of-classroom-disruptions-and-their-parameters}
-
-The attentional processes of teachers in the classroom that can be captured by MET are complex, as already explained, and are related to various parameters.
-Individual personality characteristics play a central role when it comes to the perception of relevant classroom events.
-In general, it should be noted that novices have greater problems in classroom management as well as in dealing with difficult student behavior (V.
-L.
-Barth, 2017).
-Often, this is due to their late or even lack of awareness of classroom disruptions.
-However, their lack of expertise is not the sole reason for this phenomenon.
-Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher (Baumert \& Kunter, 2006) Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors.
-Individual person characteristics as well as contextual factors not only have an effect on teaching perception, but likewise on the sense of disturbance of a situation (Eckstein, 2019).
-These specific characteristics include aspects such as self-image, motivation, level of aspiration, attitudes, coping goals, and value orientations (Bakker \& Demerouti, 2006; cited in Wickeren, 2019, p.~33).
-Contextual characteristics include didactic staging or general level of disruption.
-Undesirable behavior is perceived more strongly by teachers when the class usually displays disciplined and orderly behavior (Eckstein, 2018).
-This reference group effect is also known as the Big-Fish-Little-Pond effect.
-Thus, it can be said that teachers' perceptions of situations and people are significantly shaped by their expectations and biases is shaped (cf.~Eckstein, 2018).
-How strongly a disturbance is perceived and felt can also depend on psychological characteristics such as self-efficacy beliefs (ibid.
-(ibid.).
-With decreasing self-efficacy, an increasing sense of disturbance was found (ibid.).
-
-The teacher-student relationship aspect, which includes recognizing student needs, must also be considered.
-In order to be able to adequately counteract classroom disruptions and thus automatically reduce the sense of disruption and the experience of stress, it is important to address the concerns of the learners with empathy (Wickeren, 2019).
-Regarding gender as a factor, it should be noted that previous research has found higher levels of disruptiveness in discipline problems among female teachers (Kovess-Masféty, Rios-Seidel \& Sevilla-Dedieu, 2007; cited in Wickeren, 2019, p.~33).
-In summary can thus be summarized that the extent and perception of disturbances are based on individual cognitive evaluation processes, the situational context, attentional focus, didactic staging, and, indeed, professional experience (cf.~Wickeren, 2019).
-
-\section{Research Questions and hypothesis}\label{research-questions-and-hypothesis}
-
-This study examined how the degree of teaching experience of novice and expert teachers influences (1) the number of fixations on relevant areas, (2) the fixation duration on relevant areas and (3) the time to first fixation on relevant events (e.g., the student performing the disruption), using mobile eye-tracking data in a controlled, micro-teaching setting.
-Furthermore, the study examined the individual evaluation of classroom disruptions among experts and novices by assessing (4) how disruptive an event was and (5) how confident the subjects felt dealing with the events.
-In addition, subjects' (6) strategic knowledge of classroom management was assessed.
-
-Based on the existing literature, we expected expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation duration and (H3) perceiving classroom disruptions faster (cf.
-\textbf{van2014first?}), (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions (V.
-L.
-Barth, 2017), and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
-
-\section{Materials and Methods}\label{materials-and-methods}
-
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-
-This study had a quasi-experimental study design, as there was no random assignment of the subjects to experimental conditions.
-Due to the use of mobile eye-tracking technology, the study had a high external validity (Gegenfurtner et al., 2018).
-Internal validity could be ensured to the extent that the disruptive events that occurred were exactly the same for all subjects, as the actors received precise behavioral instructions.
-These disruptions followed a script and coding scheme in which the actions of the class were precisely described.
-The order of the disruptions as well as the performing actors were fully balanced with Latin Square to exclude row effects.
-
-The scripted behavioral instructions during the micro-teaching unit characterized the study with a high degree of standardization, especially when compared to events taking place in a real classroom.
-The study was based on an experimental manual, script and coding, which explicitly described the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable.
-
-\subsection{Participants}\label{participants}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:demographicstable}Demographic Information}
-
-\tiny{
-
-\begin{tabular}{lllllll}
-\toprule
-Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years}\\
-\midrule
-Expert & 42 & 59.52 & 39.31 & 10.64 & 26.00 & 60.00\\
-Novice & 42 & 69.05 & 22.83 & 1.85 & 19.00 & 27.00\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:demographicstable}Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent}
-
-\tiny{
-
-\begin{tabular}{llllllllllllllll}
-\toprule
-Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
-\midrule
-Expert & 42 & 11.79 & 11.43 & 1.00 & 38.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & NA\\
-Novice & 42 & 0.00 & 0.00 & 0.00 & 0.00 & 6.74 & 2.65 & 3.00 & 11.00 & 9.62 & 7.19 & 0.00 & 36.00 & 88.10 & NA\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-The sample consisted of \emph{N} = 84 participants with \emph{n} = 42 expert teachers and \emph{n} = 42 novice teachers.
-
-The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
-According to Palmer, Stough, Burdenski, and Gonzales (2005), we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
-Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
-
-The expert teachers (25 women; 59.52\%) had a mean age of 39.30 years (\emph{SD} = 10.60; range: 26-60) and an average teaching experience of 11.80 years (\emph{SD} = 11.40; range: 1-38).
-9.52\% of the experts were primary school teachers and 80.95\% were secondary school teachers.
-NA\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
-
-The novice teachers (29 women; 69.05\%) had a mean age of 22.80 years (\emph{SD} = 1.90; range: 19-27) with an average teaching experience of 0 years.
-On average, the student teachers were in their 6.70 semester (\emph{SD} = 2.60; range: 3-11).
-Furthermore, they had an average teaching experience of 9.60 teaching units à 45min (\emph{SD} = 7.20; range: 0-36) through the internships during their studies.
-21.43\% of the novices were studying to become primary school teachers, 57.14\% to become secondary school teachers and 19.05\% to become special education teachers.
-88.10\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
-
-The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at the University Leipzig.
-All study procedures were carried out in accordance with the ethical standards of the University's Institutional Review Board.
-The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
-All participants were informed in detail about the aim and intention of the study prior to testing.
-Participation in the study was voluntary and only took place after written consent has been given.
-
-\subsection{Design}\label{design}
-
-The underlying research was conducted as a laboratory study in a cross-sectional study design as part of the dissertation project \emph{ProVisioNET}.
-This project investigates whether and how a teacher's classroom experiences have an impact on the perception of and response to classroom disruptions.
-
-The study was based on a quasi-experimental study design, as there was no random assignment of subjects to experimental conditions.
-Due to the use of MET technology, the study had a high external validity (Gegenfurtner et al., 2018) To ensure internal validity the occurring instructional events were exactly the same for all subjects, as the learners received precise behavioral instructions.
-These disruptions followed a script and coding guide in which the actions of the class were precisely described.
-The order of the disruptions as well as the performing actors were prompted and fully balanced with Latin Square.
-The scripted behavioral instructions during the classroom sequence distinguish this study with a high degree of standardization, especially when compared to events that take place in a real classroom.
-The study was based on an experimental manual, script, and coding guide which explicitly describes the execution, evaluation and interpretation of the data and thus and interpretation of the data, thus making them objectively ascertainable and measurable.
-
-\subsection{Materials and Measures}\label{materials-and-measures}
-
-\subsubsection{Eye-Tracking Data}\label{eye-tracking-data}
-
-\paragraph{Apparatus}\label{apparatus}
-
-To record eye-tracking data, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker during the micro-teaching-unit.
-The system consisted of a wearable head unit and a recording unit.
-As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors.
-A high-definition scene camera captured a full HD video of the teacher's field of vision.
-An integrated microphone recorded the surrounding sounds.
-Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \ref{fig:teachersgaze}.
-The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera had a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).
-
-\begin{figure}
-
-{\centering \includegraphics[width=14.07in]{./pictures/tobiiglasses2}
-
-}
-
-\caption{Tobii Pro Glasses 2; Source: https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}\label{fig:tobiiglasses2}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics{./pictures/teachersgaze}
-
-}
-
-\caption{Teacher's Gaze Point}\label{fig:teachersgaze}
-\end{figure}
-
-\paragraph{Teachers' visual focus of attention}\label{teachers-visual-focus-of-attention}
-
-Teachers' areas of interest (AOI) were identified as targets where teachers looked during the micro-teaching-unit using Tobii Pro Lab Analyzer Software Version 1.171.
-In the present study, general AOIs where defined as the student group, the students' nametags, the teacher material, the students' material, the board and non-instructional material in the classroom (wall, window, floor).
-These AOIs were coded during the manual fixation mapping process during the entire micro-teaching-unit.
-Additionally, the disruptive person was coded as an event-based AOI only over the duration of the disruption.
-
---\textgreater{} Only eye-tracking video recordings with 70 \% and above gaze sample percentages were selected for the study to ensure that one or both eyes were detected during 70 \% of the recording's duration (Chaudhuri et al, 2022).
-Screenshots of the video recordings were used to define the AOI in the eye-tracking videos.
-The coder started manual gaze mapping when the teacher entered the classroom and ended coding when the micro-teaching-unit ended.
-The start and end of the micro-teaching-unit was defined by a visual and acoustical signal.
-The two coders who were assigned to code the eye-tracking videos student employees who studied to be teachers and received a detailed introduction to the software.
-The intercoder reliability was checked by double coding 20 \% of the videos from the whole dataset.
-Double coding agreement ranged from XXX \% to XXX \%.
-
-We coded each fixation using the Attention Filter in Pro Lab with the velocity threshold parameter set to 100 degrees/second instead of the default 30 degrees/second.
-This filter is suitable for dynamic situations to study attention without separating any eye movements.
-By choosing the Attention Filter typical fixations, most VOR (Vestibulo-ocular reflex), smooth pursuit eye movements, and slow saccades are classified as fixations.
-
-The relevant fixation metrics such as number of fixations, the total duration of fixations and time to first fixation on the relevant event (disruptive person) were obtained by exporting an interval-based TSV file from the Tobii Pro Lab Analyzer Software.
-The total fixation duration and the time to first fixation metrics were measured in milliseconds (ms) and the number of fixation in counts as an integer.
-To calculate the average fixation of durations for all AOIs, we divided the total duration of fixations by the number of fixations for each AOI.
-
-\subsubsection{Video data}\label{video-data}
-
-\paragraph{Apparatus}\label{apparatus-1}
-
-The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \ref{fig:setup}.
-The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
-Movements, facial expressions and gestures of the subjects were recorded with four Go Pro Hero 7 black cameras from different angles (see set up plan \ref{fig:setup}.
-The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
-
-\paragraph{Videography: Coding scheme for expertise indicators}\label{videography-coding-scheme-for-expertise-indicators}
-
-Part of the test procedure was that the subject taught a 15min micro-teaching-unit and was disrupted by the students in the class.
-The participant's behavior and reaction to the disruption were recorded using video cameras and then evaluated with two self developed coding schemes to assess the teacher's reaction on the one hand and the time on task during the unit.
-Both aspects are important indicators of teaching quality and are therefore used as another measure to make differences in expertise visible and measurable.
-
-Video analysis was chosen as the research method for evaluating the teacher's reaction to classroom disruptions because it offers numerous advantages.
-In contrast to transcripts or audio-only recordings, a video also shows nonverbal forms of communication, which is emphasized here, as well as the entire complex lesson excerpt in which many things happen simultaneously (cf.~Krammer \& Reusser, 2012, p.~47f).
-Video data can also be viewed and analyzed over and over again from different perspectives (Petko et al., 2003, p.~265).
-The possible problem of selectivity (cf.~Petko et al., 2003, p.~271), i.e., the fact that only a section of the events can be shown due to the position and perspective of the camera, was countered by recording the lessons from a total of four cameras.
-In this way, a case of doubt can be analyzed from several angles.
-Another challenge can be the so-called `camera effect', i.e.~that the filmed persons feel disturbed and act differently than usual and less naturally.
-However, Petko et al.~(2003) conclude, despite filming with a camera person at the time, that there is little reason to believe that teachers can easily change their teaching style from one lesson to the next (p.~270) and that it should not be assumed that the mere presence of a camera has significantly improved or worsened teaching' (p.~270).
-In the `ProVisioNET' survey, four very small cameras were placed in the room and their presence was barely noticeable.
-Accordingly, it is assumed that no major nuisance emanates from them.
-
-Schnettler and Knoblauch (2009, p.~227) distinguish `natural' and edited video data, depending on whether the situation was created specifically for the recording or whether the situation was influenced as little as possible or not at all.
-In the survey for this paper, although the subjects were to act exactly as they would have done without a camera, the classroom disruptions were scripted events that were performed by the actors.
-
-\subparagraph{Teachers' Reaction to disruptions}\label{teachers-reaction-to-disruptions}
-
-The evaluation of the teacher's reaction to the disruptions was conducted as a systematic observation using a category system with fixed categories and instructions.
-This corresponds to a highly inferential procedure, which is combined with an event sampling procedure (cf.~Lotz et al., 2013, p.~359).
-
-A theory-based coding scheme was developed as an observation tool for classroom observation.
-The coding of the reactions was done in seven levels.
-Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping (Gold \& Holodynski, 2015; cf.
-Kounin, 2006) by not interrupting the flow of instruction.
-Code 2 or Code 3 was assigned for a brief verbal expression with or without a preceding nonverbal response.
-A brief, timely, and purposeful rebuke of the disruptive student is considered by Kounin (2009, p.~99), among others, to be an important component of the strategy of presence and thus demonstrates good classroom management.
-If the teacher reacts non-verbally and at the same time with a longer verbal statement, code 4 was assigned, because the flow of the lesson was already noticeably delayed.
-There were two possibilities, if there was no reaction: If the teacher deliberately ignored the disruption, code 5 was assigned.
-If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized (cf.
-Gold \& Holodynski, 2015).If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned.
-According to Gippert et al.~(2019), there is a relational error in such cases, as the intensity of the student response should be relative to the disruptive behavior (p.~2).
-
-In developing the coding system, questions initially aroused about how descriptions of responses should be made and in what order (especially codes 3-4).
-Initially, it was planned to assign code 3 for a nonverbal and simultaneously long verbal response and code 4 for a purely verbal response.
-However, during the initial trial coding of the videos, it became apparent that it was difficult to reliably distinguish nonverbal reactions to a classroom disruption from normal facial expressions and gestures of the teacher when talking.
-Moreover, during a prolonged verbal utterance, nonverbal signs could virtually always be detected.
-Furthermore, a category for short, purely verbal reactions was missing.
-
-After developing and reviewing the coding system, the observers coordinated and the consistency of their ratings was verified.
-For the evaluation, the individual videos of the sample were then coded and the data transferred to an Excel file.
-
-Test quality criteria
-
-In the construction of the video analysis method, attention was paid to compliance with the quality criteria of objectivity, reliability and validity.
-
-In order to ensure implementation objectivity, uniform implementation conditions were created.
-In the experimental manual of the ProVisioNET study, the survey procedure is described in detail, so that it is the same for each participant.
-On the one hand, the objectivity of the evaluation was given by the processing in the R.
-On the other hand, prior to the analysis of the videos, a precise coding scheme, which precisely describes the individual codes, explains them and contains examples, was created and discursively discussed in the team (see chapter 4.4.1).
-This coding scheme was tested and revised in a piloting process, which increased the internal validity of the method.
-Interrater reliability was determined for the two raters using sample ratings of the same videos.
-Percent agreement yielded 77.8\% and a Cohen's Kappa of k = 0.6, which is a satisfactory value according to Landis \& Koch (1977).
-Interpretive objectivity was ensured by specifying scientific hypotheses that then had to be neutrally tested.
-
-With the help of scripted behavioral instructions for students in the instructional unit, a high degree of standardization was achieved that is not present in the normal school setting.
-The lessons were recorded with several video cameras from different angles and an audio recorder.
-This means a big advantage compared to the subjective evaluation of observers in real time.
-In addition, video recordings can be viewed multiple times, by different people or from different perspectives.
-Thus, a high measurement accuracy (reliability) is given {[}cf.@mayring2005auswertung{]}.
-All measures taken contribute to increase the validity of the method.
-However, it cannot be answered whether the coding scheme is completely valid, because a validation with the help of another measuring instrument was not possible.
-Therefore, it could not be controlled whether the collected construct is related to other similar constructs.
-
-\subparagraph{Coding Time on Task}\label{coding-time-on-task}
-
-XXX
-
-\subsubsection{Questionnaie data}\label{questionnaie-data}
-
-\paragraph{Presence Questionnaire}\label{presence-questionnaire}
-
-After each micro-teaching-unit, the three actors answered items on teaching quality using a validated questionnaire (Helmke et al., 2014) and self developed scales on the teacher's presence behavior derived from the research literature.
-In addition, subjects were asked to give a self-assessment on classroom management by completing the same questionnaire after each micro-teaching-unit.
-The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
-
-Bilanz:
-LB01\_01 Bilanz: Die Lernenden haben in dieser Unterrichtslektion etwas dazu gelernt.
-LB01\_02 Bilanz: Die Lernenden haben sich in dieser Unterrichtslektion wohl gefühlt.
-LB01\_03 Bilanz: Mediennutzung und Sozialformen waren dem Inhalt und der Situation der Unterrichtslektion angemessen.
+After each micro-teaching-unit, participants answered items on teaching
+quality using a validated questionnaire
+{[}@helmke2014unterrichtsdiagnostik{]} and self developed scales on the
+teacher's presence behavior derived from the research literature. The
+questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 4 =
+Strongly Agree).
 
 Klassenmanagement:
-LM01\_01 Klassenmanagement: Die gesamte Unterrichtslektion wurde für den Lernstoff verwendet.
-LM01\_02 Klassenmanagement: Ich habe alles mitbekommen, was in der Klasse passiert ist.
-LM01\_03 Klassenmanagement: Den Lernenden war jederzeit klar, was sie tun sollten.
+
+LM01\_01 Klassenmanagement: Die gesamte Unterrichtslektion wurde für den
+Lernstoff verwendet.
+
+LM01\_02 Klassenmanagement: Ich habe alles mitbekommen, was in der
+Klasse passiert ist.
+
+LM01\_03 Klassenmanagement: Den Lernenden war jederzeit klar, was sie
+tun sollten.
+
 LM01\_04 Klassenmanagement: Die Lernenden konnten ungestört arbeiten.
-LM01\_05 Klassenmanagement: Die Lernenden waren die ganze Unterrichtslektion über aktiv bei der Sache.
-LM01\_06 Klassenmanagement: Ich habe vieles mit kurzen Blicken und knappen Gesten geregelt.
+
+LM01\_05 Klassenmanagement: Die Lernenden waren die ganze
+Unterrichtslektion über aktiv bei der Sache.
+
+LM01\_06 Klassenmanagement: Ich habe vieles mit kurzen Blicken und
+knappen Gesten geregelt.
+
 LM01\_07 Klassenmanagement: Auf Störungen habe ich angemessen reagiert.
-LM01\_08 Klassenmanagement: Bei Störungen gab ich den Lernenden ein klares STOP-Signal.
 
-Redeanteil:
-LO01\_01 Redeanteil: Wieviel Prozent der gesamten Unterrichtslektion hat nach Ihrer Schätzung Ihr eigener Redeanteil eingenommen? \ldots{} \%
-LO01\_02 Redeanteil: Wenn ich Fragen oder Aufgaben gestellt habe, habe ich den Lernenden folgende Zeit (in Sekunden) zum Nachdenken gegeben \ldots{} Sekunden
+LM01\_08 Klassenmanagement: Bei Störungen gab ich den Lernenden ein
+klares STOP-Signal.
 
 Präsenz:
-LP01\_01 Präsenzindikatoren: Ich hatte eine aufrechte, der Klasse zugewandte Körperhaltung.
-LP01\_02 Präsenzindikatoren: Ich habe den Lernenden direkt in die Augen geschaut.
-LP01\_03 Präsenzindikatoren: Ich habe meine Position im Raum bewusst eingesetzt und variiert.
+
+LP01\_01 Präsenzindikatoren: Ich hatte eine aufrechte, der Klasse
+zugewandte Körperhaltung.
+
+LP01\_02 Präsenzindikatoren: Ich habe den Lernenden direkt in die Augen
+geschaut.
+
+LP01\_03 Präsenzindikatoren: Ich habe meine Position im Raum bewusst
+eingesetzt und variiert.
+
 LP01\_04 Präsenzindikatoren: Ich habe alle oft angesehen.
-LP01\_05 Präsenzindikatoren: Meine Artikulation, Lautstärke und Tonhöhe waren angemessen.
-LP01\_06 Präsenzindikatoren: Meine Sprechgeschwindigkeit und Sprechpausen waren angemessen.
-LP01\_07 Präsenzindikatoren: Mein Sprechanteil an der gesamten Sprechzeit der Unterrichtslektion war angemessen.
-LP01\_08 Präsenzindikatoren: Meine Gestik und Mimik waren abwechslungsreich und ausdrucksstark.
+
+LP01\_05 Präsenzindikatoren: Meine Artikulation, Lautstärke und Tonhöhe
+waren angemessen.
+
+LP01\_06 Präsenzindikatoren: Meine Sprechgeschwindigkeit und
+Sprechpausen waren angemessen.
+
+LP01\_07 Präsenzindikatoren: Mein Sprechanteil an der gesamten
+Sprechzeit der Unterrichtslektion war angemessen.
+
+LP01\_08 Präsenzindikatoren: Meine Gestik und Mimik waren
+abwechslungsreich und ausdrucksstark.
 
 Natürliches Verhalten:
-LV01\_01 Natürliches Verhalten: Während der Unterrichtslektion habe ich mich sehr natürlich verhalten.
-LV01\_02 Natürliches Verhalten: Es war für mich kein Problem, vor einer fiktiven Klasse zu unterrichten.
-LV01\_03 Natürliches Verhalten: Beim Unterrichten vor einer fiktiven Klasse habe ich mich so verhalten, wie ich es auch in der Schule tun würde.
+
+LV01\_01 Natürliches Verhalten: Während der Unterrichtslektion habe ich
+mich sehr natürlich verhalten.
+
+LV01\_02 Natürliches Verhalten: Es war für mich kein Problem, vor einer
+fiktiven Klasse zu unterrichten.
+
+LV01\_03 Natürliches Verhalten: Beim Unterrichten vor einer fiktiven
+Klasse habe ich mich so verhalten, wie ich es auch in der Schule tun
+würde.
 
@@
 
-\paragraph{Teachers' perception of disruption and confidence using Rating scales}\label{teachers-perception-of-disruption-and-confidence-using-rating-scales}
+Component 1
 
-Two self-developed 11-point rating scales were used to record how disruptive the individual disruptions were perceived by the subjects and how confident they felt in dealing with the disruptions.
-Data for rating scales were collected during the Stimulted Recall Interview, where the experimenter watched the pre-recorded eye-tracking video with the subject.
+Row
 
-The questionnaire included nine questions for each scripted disruptive event. The subjects did not have to complete the questionnaire themselves at any time, as this was done by the experimenter.
+Missings
 
-For the present study, the following two questions from the interview were relevant:
-1. ``How disruptive was this event for you?''
-2. ``How confident did you feel in dealing with this event?''
+Mean
 
-Both questions were answered using a scale ranging from 0 to 10. On this scale, 0 stood for ``not at all disruptive'' or ``not at all safe'' and 10 for ``extremely disturbing'' or ``extremely safe.''
+SD
 
-With these rating scales, the subjects indicated their personal subjective feeling towards the individual lesson disruption.
-Rating scales usually consist of a number of clearly arranged categories that can be presented visually in a variety of ways (Albers, Klapper, Konradt, Walter, \& Wolf, 2009, p.
-67f).
-In the present questionnaire, the numerical representation with eleven answer options (0-10) was used.
-There was no specific designated neutral position.
-In this questionnaire, the middle category 5 was not interpreted as a neutral position.
-In order to avoid misinterpretations of the scaling, the questionnaire was described verbally by the experimenter and follow-up questions from the test subjects were possible at any time.
-With regard to the quality criteria, it should be made clear that complete objectivity in answering the two questions is given by the rating scales.
-The question remained the same for all subjects and no additional comments were made.
-Validity can also be assumed for the questionnaire, since the subjects couls ask follow-up questions and thus uncertainties were clarified.
-However, similar to the video data, there was no perfect reliability with this survey instrument, because in a few exceptional cases, for example, the experimenter forgot to ask the subject the relevant questions.
+Skew
 
-\begin{table}[h]
+Item Difficulty
 
-\begin{center}
-\begin{threeparttable}
+Item Discrimination
 
-\caption{\label{tab:rating_scales}Table Rating Scales Disruption Factor}
+α if deleted
 
-\tiny{
+LM01\_01
 
-\begin{tabular}{llllll}
-\toprule
-Group & \multicolumn{1}{c}{Event} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
-\midrule
-Expert & chatting & 6.44 & 3.33 & 1.00 & 10.00\\
-Expert & clicking pen & 5.57 & 2.87 & 0.00 & 10.00\\
-Expert & drawing & 1.85 & 1.46 & 0.00 & 6.00\\
-Expert & drumming & 4.60 & 2.44 & 1.00 & 8.00\\
-Expert & head on table & 3.73 & 2.25 & 0.00 & 8.00\\
-Expert & heckling & 7.19 & 2.37 & 2.00 & 10.00\\
-Expert & looking at phone & 4.71 & 3.10 & 1.00 & 10.00\\
-Expert & snipping & 4.00 & 3.61 & 0.00 & 10.00\\
-Expert & whispering & 4.56 & 2.50 & 0.00 & 9.00\\
-Novice & chatting & 8.62 & 1.35 & 5.00 & 10.00\\
-Novice & clicking pen & 7.00 & 2.11 & 3.00 & 10.00\\
-Novice & drawing & 2.24 & 1.48 & 0.00 & 4.00\\
-Novice & drumming & 6.57 & 2.27 & 0.00 & 10.00\\
-Novice & head on table & 4.09 & 2.09 & 1.00 & 8.00\\
-Novice & heckling & 6.96 & 2.57 & 2.00 & 10.00\\
-Novice & looking at phone & 3.90 & 1.94 & 1.00 & 8.00\\
-Novice & snipping & 4.67 & 3.33 & 0.00 & 9.00\\
-Novice & whispering & 6.08 & 2.36 & 1.00 & 10.00\\
-\bottomrule
-\end{tabular}
+0.00 \%
 
-}
+3.32
 
-\end{threeparttable}
-\end{center}
+0.73
 
-\end{table}
+-0.97
 
-\begin{table}[h]
+0.83
 
-\begin{center}
-\begin{threeparttable}
+0.34
 
-\caption{\label{tab:rating_scales}Table Rating Scales Confident Factor}
+0.55
 
-\tiny{
+LM01\_02
 
-\begin{tabular}{llllll}
-\toprule
-Group & \multicolumn{1}{c}{Event} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
-\midrule
-Expert & chatting & 8.44 & 2.03 & 2.00 & 10.00\\
-Expert & clicking pen & 8.93 & 1.00 & 7.00 & 10.00\\
-Expert & drawing & 9.23 & 1.36 & 5.00 & 10.00\\
-Expert & drumming & 9.07 & 0.96 & 7.00 & 10.00\\
-Expert & head on table & 9.00 & 1.41 & 5.00 & 10.00\\
-Expert & heckling & 6.75 & 2.89 & 2.00 & 10.00\\
-Expert & looking at phone & 9.21 & 1.05 & 7.00 & 10.00\\
-Expert & snipping & 9.06 & 1.48 & 4.00 & 10.00\\
-Expert & whispering & 8.06 & 2.11 & 3.00 & 10.00\\
-Novice & chatting & 6.42 & 2.39 & 0.00 & 10.00\\
-Novice & clicking pen & 7.54 & 1.89 & 3.00 & 10.00\\
-Novice & drawing & 8.81 & 1.25 & 5.00 & 10.00\\
-Novice & drumming & 7.57 & 2.11 & 3.00 & 10.00\\
-Novice & head on table & 7.30 & 1.96 & 3.00 & 10.00\\
-Novice & heckling & 5.35 & 2.53 & 1.00 & 10.00\\
-Novice & looking at phone & 7.65 & 1.73 & 3.00 & 10.00\\
-Novice & snipping & 8.04 & 1.73 & 3.00 & 10.00\\
-Novice & whispering & 7.25 & 2.03 & 2.00 & 10.00\\
-\bottomrule
-\end{tabular}
+0.00 \%
 
-}
+3.27
 
-\end{threeparttable}
-\end{center}
+0.66
 
-\end{table}
+-0.88
 
-\paragraph{Situational Jugdement Test of Strategic Knowledge of Classroom Management}\label{situational-jugdement-test-of-strategic-knowledge-of-classroom-management}
+0.82
 
-To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)).
-In the questionnaire, participants were given hypothetical school scenarios with five to six response strategies for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).
-Depending on the grade given to each strategy, scores were converted in an SPSS syntax resulting in scores ranging from 0 to 1 for each participant.
+0.06
 
-In developing the test procedure, the authors divided the concept of classroom management into three main aspects: \emph{Monitoring}, \emph{managing momentum} (structuring) and \emph{rules and routines} (Gold \& Holodynski, 2015, p.
-230f).
+0.63
 
-\emph{Monitoring} includes proactive strategies such as omnipresence.
-This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them.
-The second strategy is overlapping.
-In this case, the teacher is able to control several teaching processes at the same time.
-Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions {[}cf.~ibid.; Kounin (2006), p.~89ff{]}.
+LM01\_03
 
-By \emph{managing momentum} (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention (Kounin, 2006, p.
-101ff).
-They also include the group focus specifically identified by Kounin (Kounin, 2006, p.
-117ff), i.e.~mobilizing the whole class and demanding accountability (Gold \& Holodynski, 2015, p.
-231).
+0.00 \%
 
-The third facet of classroom management, establishing \emph{rules, routines and rituals}, supports the other two facets and offers pupils orientation and structure in everyday school life (cf.~ibid.).
+3.36
 
-The construction of the SJT included 14 scenarios that were based on transcribed classroom videos from Germany.
-For the 14 scenarios, response strategies were derived from evidence-based and theoretical principles by 17 experts on classroom management.
-With the exception of scenario 5, which was subsequently excluded, the 17 experts agreed on an appropriate level of content validity for all other scenarios (cf.~ibid.).
-For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf.~ibid., p.~238).
-Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf.~ibid.).
+0.53
 
-The construct validity of the SJT with the other 11 scenarios and the sensitivity to differences in strategic knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf.~ibid., p.~238ff).
-Despite limitations in reliability, the test was confirmed to have content and construct validity (cf.~ibid., p.~243).
-On the basis of these results, sufficient reliability and validity of the SJT test procedure was assumed.
+0.1
 
-The scenarios could each be assigned to one facet of the mentioned classroom management: Scenarios 1-4 cover the facet \emph{monitoring}, scenarios 6-9 the facet \emph{managing momentum} and scenarios 11-14 the facet \emph{rules and routines}.
+0.84
 
-In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}.
-The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.50; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.1.3; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{ggrepel} (Version 0.9.4; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.3; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.45; Xie, 2015), \emph{lme4} (Version 1.1.35.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.4; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
-Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.15; Lüdecke, 2021), \emph{sp} (E.
-J.
-Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M.
-Barth, 2022), \emph{viridis} (Version 0.6.4; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
+0.23
 
-Since the test was a questionnaire designed to assess strategic knowledge of classroom management of \emph{primary school teachers}, but the sample of the study included several types of schools, changes were made in 10 out of 12 scenarios by deleting the indicated class grade.
-Only in two scenarios was the class grade information not deleted, as the action alternatives would otherwise not be appropriate without the information.
+0.58
 
-\begin{table}[h]
+LM01\_04
 
-\begin{center}
-\begin{threeparttable}
+0.00 \%
 
-\caption{\label{tab:sjt}Scale analysis SJT novices}
+3.23
 
-\tiny{
+0.65
 
-\begin{tabular}{lllllllll}
-\toprule
- & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
-\midrule
-Monitoring & 4.00 & 0.71 & 0.11 & 0.44 & 0.96 & -0.11 & 3.76 & 0.37\\
-Managing Momentum & 5.00 & 0.74 & 0.11 & 0.51 & 0.94 & -0.25 & 2.85 & 0.19\\
-Rules and routines & 3.00 & 0.75 & 0.11 & 0.46 & 0.90 & -0.74 & 3.25 & -0.28\\
-\bottomrule
-\end{tabular}
+-0.25
 
-}
+0.81
 
-\end{threeparttable}
-\end{center}
+0.45
 
-\end{table}
+0.52
 
-\begin{table}[h]
+LM01\_05
 
-\begin{center}
-\begin{threeparttable}
+0.00 \%
 
-\caption{\label{tab:sjt}Scale analysis SJT novices}
+2.71
 
-\tiny{
+0.69
 
-\begin{tabular}{lllllllll}
-\toprule
- & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
-\midrule
-Monitoring & 4.00 & 0.71 & 0.15 & 0.52 & 0.92 & 0.17 & 1.76 & 0.38\\
-Managing Momentum & 5.00 & 0.70 & 0.13 & 0.52 & 0.89 & 0.31 & 1.77 & 0.34\\
-Rules and routines & 3.00 & 0.70 & 0.13 & 0.47 & 0.89 & -0.27 & 2.20 & 0.46\\
-\bottomrule
-\end{tabular}
+-0.02
 
-}
+0.68
 
-\end{threeparttable}
-\end{center}
+0.28
 
-\end{table}
+0.57
 
-XXX FRANZI
+LM01\_06
 
-\subsection{Procedure}\label{procedure}
+0.00 \%
 
-The project was conducted as a laboratory study in a cross-sectional study design to investigate whether and how teachers' experience has an influence on the perception of and reaction to classroom disruptions.
+2.54
 
-In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and Septemper 2022.
+0.84
 
-Before the data collection, each subject received a personal digital meeting with the experimenter to go over the study procedure and to arrange a date for the data collection.
-During the digital meeting, the subjects were asked to prepare a 15-minute lesson in a subject and grade of their choice for the data collection.
+0.19
 
-On the day of a data collection, the first step was to set up the study room at the University of Leipzig.
-For this, all the appropriate technical equipment was charged and installed in the room (see set up plan {[}REFERENZ EINFÜGEN{]}).
-Next, all four cameras and the audio recorder were synced via Timecode System.
+0.63
 
-After the subject arrived, a smart watch was put on to measure the heart rate during the session and to get a pretest time at least 15min before the session started.
-In addition to the experimenter and the subject, three student assistants from the working group always took part in the data collection, as they represented the class.
+0.24
 
-After the welcome, the subject was again briefed about the study.
-It was explicitly pointed out that the student assistants would act as the class and simulate typical class events during the lesson.
-The subject was asked in advance to behave as naturally as possible during the entire time.
-Next, the subjects' written informed consent was obtained and contact details were collected in order to inform all persons participating in the study if a covid infection should occur.
+0.59
 
-After the introduction, the eye-tracking glasses were adjusted for the subject by inserting contact lenses if necessary and changing the nose pad.
-To start the eye tracking glasses, the Tobii Glasses must be fitted onto the subject's head via an one-point-calibration.
-In the calibration process the subject was asked to look at a Calibration Card held in-front of the subject for a few seconds.
-The experimenter started the recording from Tobii Glasses Controller Software running on a computer.
+LM01\_07
 
-After starting the eye tracking recording, all other technical devices were also switched on: The four cameras and the audio recorder were controlled via iPad using the BLINK Hup app and could be started simultaneously by synchronization.
-The ZED camera was started manually on another laptop.
+0.00 \%
 
-Before the 15-minute lesson, there was a short 10-minute warm-up phase.
-The phase was divided into two parts and served on the one hand to get the subjects used to the eye-tracking glasses and on the other hand to get used to their class.
-In the first phase of the warm-up, the game ``name juggling'' was played using two balls.
-In the game, the subject and the three actors threw two balls at each other and, depending on the color of the ball, called either their own name or that of the target person.
-After the name juggling, the subjects were supposed to start a conversation.
-For this, the subject thought of a question for each student and was also asked a question of each student.
-The content could be anything that interested the participants.
+3.27
 
-After the warm up phase, the experimenter ensured a manual synchronization of the technique by an acoustic signal in which she clapped her hands loudly twice standing in the middle of the room.
-After this, another nine-point calibration followed outside the study room in a neighboring room.
-Before the subject left the room for calibration, the time on the smartwatch was noted, as well as the steps recorded until that point.
-The subject had to stand at a marked point and look at a board three meters away with nine april tags.
-The subject was asked to read the nine points aloud in order at a normal speaking speed.
-This procedure was important to validate the one-point calibration on the one hand and on the other hand to give the subject the feeling of a lesson start, because after this calibration the subject came into the study room to start the 15-minute lesson.
+0.65
 
-For the micro-teaching lesson, student teachers and experienced teachers were asked to prepare an introduction of 15 minutes which they taught in front of the fictitious class consisting of three student assistants.
-The actors simulated the nine classroom events during the lesson, derived by research literature.
-The order of the disruptions as well as the students performing them were fully balanced using Latin Square.
-The disruptions were only visible for the class on a screen.
+-0.33
 
-\begin{table}[h]
+0.82
 
-\begin{center}
-\begin{threeparttable}
+0.51
 
-\caption{\label{tab:disruption_categories}Categories of Disruptions (Lohmann, 2015)}
+0.50
 
-\tiny{
+LM01\_08
 
-\begin{tabular}{lll}
-\toprule
-Verbal.Disruption & \multicolumn{1}{c}{Agitation} & \multicolumn{1}{c}{Lack.of.eagerness.to.learn}\\
-\midrule
-chatting with neighbor & drumming hands & putting head on table\\
-whispering with neighbor & clicking pen & looking at phone\\
-heckling & snipping with fingers & drawing on a sheet of paper\\
-\bottomrule
-\end{tabular}
+0.00 \%
 
-}
+3.02
 
-\end{threeparttable}
-\end{center}
+0.76
 
-\end{table}
+-0.55
 
-During the lesson, a mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson.
-All other sounds and voices were recorded by an audio recorder.
-To record facial expressions, gestures and movements, four mobile cameras were installed to record the classroom from all perspectives (!!!see figures).
+0.76
 
-After the lesson, the time was again noted from the smartwatch as well as the subject's steps.
-The nine-point calibration was also performed again in the neighboring room.
-This time, however, the subject was asked to wait outside the room until he or she was called in, because four letters from A to D were placed in the study room.
-The subject was asked to stand facing the board at a marked point in the room and, when given an acoustic signal, to turn around and search the letters and read them aloud in order.
-This served as a control condition for the speed of the subjects' perceptual ability as no expertise is required for searching letters.
+0.31
 
-After the letter search, the experimenter clapped twice with the hands to record an acoustic signal for the synchronization of all technical devices.
-Afterwards, all devices were switched off and the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire (Helmke et al., 2014) and self developed scales on the teacher's presence behavior derived from the research literature.
-The completion of the questionnaire took approximately 5 minutes.
+0.56
 
-In the second part of the study, the experimenter conducted a Stimulated Recall Interview (SRI) with the subject(see in Figure \ref{fig:sri}.
-The interview was recorded by the ambient recorder and additionally with a software called OBS to record the speech and screen.
-The recorded eye-tracking video was watched and commented on by the subject while thinking aloud.
-The interview was structured by a guideline based on a fixed sequence of questions, however the subjects were allowed to answer completely open to these questions.
-The objective was to collect data that would provide insight into the subjects' thoughts and reactions in relation to the scripted classroom disruptions.
-The eye-tracking video was not completely re-watched, but stopped at the points where disruptions occurred.
-After the disruption occurred, the subject was asked to describe what had just happened.
-If the disruption was noticed, the subject was asked how disruptive the event was at that moment on a scale from 0 to 10.
-In addition, the subject was asked to reason the given number.
-In a next step, the experimenter re-played the subject's reaction to the disruption and asked to describe and reason the reaction.
-The experimenter then asked the subject to rate on a scale from 0 to 10 how confident he/she felt in dealing with the disruption and again to reason the number (for a detailed description of the scale question, see Rating Scales).
+Mean inter-item-correlation=0.160 · Cronbach's α=0.596
 
-\begin{figure}
+Component 1
 
-{\centering \includegraphics{./pictures/sri}
+Row
 
-}
+Missings
 
-\caption{Subject and experimenter during the Stimulated Recall Interview}\label{fig:sri}
-\end{figure}
+Mean
 
-Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management (SJT, Gold \& Holodynski, 2015) in the form of a questionnaire.
-Here they had to assess teaching scenarios and evaluate their behavior in response to them.
-The SJT was used to assess strategic knowledge about classroom management.
-The completion of the entire survey took 15 min on average.
+SD
 
-\subsection{Data analysis}\label{data-analysis}
+Skew
 
-We investigated whether experts and novice teachers differed
+Item Difficulty
 
-All reported data analyses were conducted with the R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.50; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.1.3; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{ggrepel} (Version 0.9.4; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.3; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.45; Xie, 2015), \emph{lme4} (Version 1.1.35.1; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.4; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
-Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.15; Lüdecke, 2021), \emph{sp} (E.
-J.
-Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M.
-Barth, 2022), \emph{viridis} (Version 0.6.4; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.
+Item Discrimination
 
-\section{Results}\label{results}
+α if deleted
 
-\section{Discussion}\label{discussion}
+LB01\_01
 
-\newpage
+0.00 \%
 
-\section{References}\label{references}
+3.33
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+0.66
 
-\phantomsection\label{refs}
-\begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-albers2009methodik}
-Albers, S., Klapper, D., Konradt, U., Walter, A., \& Wolf, J. (2009). \emph{Methodik der empirischen forschung} (Vol. 3). Springer.
+-0.75
 
-\bibitem[\citeproctext]{ref-R-DescTools}
-Andri et mult. al., S. (2022). \emph{{DescTools}: Tools for descriptive statistics}. Retrieved from \url{https://cran.r-project.org/package=DescTools}
+0.83
 
-\bibitem[\citeproctext]{ref-R-ggthemes}
-Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
+0.50
 
-\bibitem[\citeproctext]{ref-R-gridExtra}
-Auguie, B. (2017). \emph{gridExtra: Miscellaneous functions for "grid" graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridExtra}
+0.61
 
-\bibitem[\citeproctext]{ref-R-papaja}
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+LB01\_02
 
-\bibitem[\citeproctext]{ref-R-tinylabels}
-Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
+0.00 \%
 
-\bibitem[\citeproctext]{ref-barth2017professionelle}
-Barth, V. L. (2017). \emph{Professionelle wahrnehmung von st{ö}rungen im unterricht}. Springer.
+3.11
 
-\bibitem[\citeproctext]{ref-R-lme4}
-Bates, D., Mächler, M., Bolker, B., \& Walker, S.
-(2015).
-Fitting linear mixed-effects models using {lme4}.
-\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
-\url{https://doi.org/10.18637/jss.v067.i01}
+0.68
 
-\bibitem[\citeproctext]{ref-R-Matrix}
-Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+-0.61
 
-\bibitem[\citeproctext]{ref-baumert2006key}
-Baumert, J., \& Kunter, M. (2006). Key word: Professional competence of teachers. \emph{ZEITSCHRIFT FUR ERZIEHUNGSWISSENSCHAFT}, \emph{9}(4), 469--520.
+0.78
 
-\bibitem[\citeproctext]{ref-berliner1994expertise}
-Berliner, D. C. (1994). Expertise: The wonders of exemplary performance. \emph{Creating Powerful Thinking in Teachers and Students}, 161--186.
+0.58
 
-\bibitem[\citeproctext]{ref-R-rgeos}
-Bivand, R., \& Rundel, C. (2021). \emph{Rgeos: Interface to geometry engine - open source ('GEOS')}. Retrieved from \url{https://CRAN.R-project.org/package=rgeos}
+0.50
 
-\bibitem[\citeproctext]{ref-blake2013eye}
-Blake, C. (2013). Eye-tracking: Grundlagen und anwendungsfelder. In \emph{Handbuch standardisierte erhebungsverfahren in der kommunikationswissenschaft} (pp. 367--387). Springer.
+LB01\_03
 
-\bibitem[\citeproctext]{ref-R-xtable}
-Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
+0.00 \%
 
-\bibitem[\citeproctext]{ref-eckstein2016unterrichtliche}
-Eckstein, B., Grob, U., \& Reusser, K.
-(2016).
-Unterrichtliche devianz und subjektives st{ö}rungsempfinden.
-Entwicklung eines instrumentariums zur erfassung von unterrichtsst{ö}rungen.
-\emph{Empirische P{ä}dagogik (EP)}, \emph{30}(1), 113--129.
+3.37
 
-\bibitem[\citeproctext]{ref-emmer1982improving}
-Emmer, E., Sanford, J., Clements, B., \& Martin, J.
-(1982).
-Improving classroom management and organization in junior high schools.
-\emph{An.
-Experimental, Investigation.
-Washington, DC: National Institute}.
+0.64
 
-\bibitem[\citeproctext]{ref-epstein2002defining}
-Epstein, R. M., \& Hundert, E. M. (2002). Defining and assessing professional competence. \emph{Jama}, \emph{287}(2), 226--235.
+-0.5
 
-\bibitem[\citeproctext]{ref-evertson2006classroom}
-Evertson, C. M., Weinstein, C. S., et al. (2006). Classroom management as a field of inquiry. \emph{Handbook of Classroom Management: Research, Practice, and Contemporary Issues}, \emph{3}(1), 16.
+0.84
 
-\bibitem[\citeproctext]{ref-R-janitor}
-Firke, S. (2021). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
+0.44
 
-\bibitem[\citeproctext]{ref-R-polycor}
-Fox, J. (2022). \emph{Polycor: Polychoric and polyserial correlations}. Retrieved from \url{https://CRAN.R-project.org/package=polycor}
+0.67
 
-\bibitem[\citeproctext]{ref-R-viridis}
-Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+Mean inter-item-correlation=0.427 · Cronbach's α=0.692
 
-\bibitem[\citeproctext]{ref-R-viridisLite}
-Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+Component 1
 
-\bibitem[\citeproctext]{ref-gegenfurtner2018mobiles}
-Gegenfurtner, A., Eichinger, A., Latzel, R., Dietrich, M. P., Barkowsky, M., Glufke, A., \ldots{} Stern, W. (2018). \emph{Mobiles eye-tracking in den angewandten wissenschaften}.
+Row
 
-\bibitem[\citeproctext]{ref-gold2015development}
-Gold, B., \& Holodynski, M.
-(2015).
-Development and construct validation of a situational judgment test of strategic knowledge of classroom management in elementary schools.
-\emph{Educational Assessment}, \emph{20}(3), 226--248.
+Missings
 
-\bibitem[\citeproctext]{ref-gold2017using}
-Gold, B., \& Holodynski, M.
-(2017).
-Using digital video to measure the professional vision of elementary classroom management: Test validation and methodological challenges.
-\emph{Computers \& Education}, \emph{107}, 13--30.
+Mean
 
-\bibitem[\citeproctext]{ref-R-lubridate}
-Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with {lubridate}. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{https://www.jstatsoft.org/v40/i03/}
+SD
 
-\bibitem[\citeproctext]{ref-grub2020process}
-Grub, A.-S., Biermann, A., \& Brünken, R.
-(2020).
-Process-based measurement of professional vision of (prospective) teachers in the field of classroom management.
-A systematic review.
-\emph{Journal for Educational Research Online}, \emph{12}(3), 75--102.
+Skew
 
-\bibitem[\citeproctext]{ref-helmke2014unterrichtsdiagnostik}
-Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M.
-(2014).
-Unterrichtsdiagnostik mit EMU.
-\emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
+Item Difficulty
 
-\bibitem[\citeproctext]{ref-R-purrr}
-Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+Item Discrimination
 
-\bibitem[\citeproctext]{ref-R-rlang}
-Henry, L., \& Wickham, H. (2022). \emph{Rlang: Functions for base types and core r and 'tidyverse' features}. Retrieved from \url{https://CRAN.R-project.org/package=rlang}
+α if deleted
 
-\bibitem[\citeproctext]{ref-R-msm}
-Jackson, C.
-H.
-(2011).
-Multi-state models for panel data: The {msm} package for {R}.
-\emph{Journal of Statistical Software}, \emph{38}(8), 1--29.
-Retrieved from \url{https://www.jstatsoft.org/v38/i08/}
+LP01\_01
 
-\bibitem[\citeproctext]{ref-jahn2014professionelle}
-Jahn, G., Stürmer, K., Seidel, T., \& Prenzel, M.
-(2014).
-Professionelle unterrichtswahrnehmung von lehramtsstudierenden: Eine scaling-up studie des observe-projekts.
-\emph{Zeitschrift f{ü}r Entwicklungspsychologie Und p{ä}dagogische Psychologie}, \emph{46}(4), 171--180.
+0.00 \%
 
-\bibitem[\citeproctext]{ref-R-ggmosaic}
-Jeppson, H., Hofmann, H., \& Cook, D. (2021). \emph{Ggmosaic: Mosaic plots in the 'ggplot2' framework}. Retrieved from \url{https://CRAN.R-project.org/package=ggmosaic}
+3.33
 
-\bibitem[\citeproctext]{ref-R-needs}
-Katz, J. (2016). \emph{Needs: Attaches and installs packages}. Retrieved from \url{https://CRAN.R-project.org/package=needs}
+0.65
 
-\bibitem[\citeproctext]{ref-kleinknecht2013teachers}
-Kleinknecht, M., \& Schneider, J. (2013). What do teachers think and feel when analyzing videos of themselves and other teachers teaching? \emph{Teaching and Teacher Education}, \emph{33}, 13--23.
+-0.45
 
-\bibitem[\citeproctext]{ref-klieme2008concept}
-Klieme, E., Hartig, J., \& Rauch, D. (2008). The concept of competence in educational contexts. \emph{Assessment of Competencies in Educational Contexts}, \emph{3}, 22.
+0.83
 
-\bibitem[\citeproctext]{ref-R-moments}
-Komsta, L., \& Novomestky, F. (2015). \emph{Moments: Moments, cumulants, skewness, kurtosis and related tests}. Retrieved from \url{https://CRAN.R-project.org/package=moments}
+0.46
 
-\bibitem[\citeproctext]{ref-kounin2006techniken}
-Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.
+0.71
 
-\bibitem[\citeproctext]{ref-lachner2016makes}
-Lachner, A., Jarodzka, H., \& Nückles, M.
-(2016).
-What makes an expert teacher?
-Investigating teachers' professional vision and discourse abilities.
-\emph{Instructional Science}, \emph{44}(3), 197--203.
+LP01\_02
 
-\bibitem[\citeproctext]{ref-leinhardt1986cognitive}
-Leinhardt, G., \& Greeno, J. G. (1986). The cognitive skill of teaching. \emph{Journal of Educational Psychology}, \emph{78}(2), 75.
+0.00 \%
 
-\bibitem[\citeproctext]{ref-R-sjPlot}
-Lüdecke, D. (2021). \emph{sjPlot: Data visualization for statistics in social science}. Retrieved from \url{https://CRAN.R-project.org/package=sjPlot}
+3.33
 
-\bibitem[\citeproctext]{ref-R-sjlabelled}
-Lüdecke, D. (2022). \emph{Sjlabelled: Labelled data utility functions (version 1.2.0)}. \url{https://doi.org/10.5281/zenodo.1249215}
+0.63
 
-\bibitem[\citeproctext]{ref-marzano2003classroom}
-Marzano, R. J., Marzano, J. S., \& Pickering, D. (2003). \emph{Classroom management that works: Research-based strategies for every teacher}. ASCD.
+-0.39
 
-\bibitem[\citeproctext]{ref-R-imputeTS}
-Moritz, S., \& Bartz-Beielstein, T. (2017). {imputeTS: Time Series Missing Value Imputation in R}. \emph{{The R Journal}}, \emph{9}(1), 207--218. \url{https://doi.org/10.32614/RJ-2017-009}
+0.83
 
-\bibitem[\citeproctext]{ref-R-tibble}
-Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+0.30
 
-\bibitem[\citeproctext]{ref-oser2006competence}
-Oser, F. K., Achtenhagen, F., \& Renold, U. (2006). Competence-oriented teacher training: Old research demands and new pathways. In \emph{Competence oriented teacher training} (pp. 1--7). Brill.
+0.74
 
-\bibitem[\citeproctext]{ref-palmer2005identifying}
-Palmer, D.
-J., Stough, L.
-M., Burdenski, T.
-K., Jr, \& Gonzales, M.
-(2005).
-Identifying teacher expertise: An examination of researchers' decision making.
-\emph{Educational Psychologist}, \emph{40}(1), 13--25.
+LP01\_03
 
-\bibitem[\citeproctext]{ref-R-sf}
-Pebesma, E. (2018). {Simple Features for R: Standardized Support for Spatial Vector Data}. \emph{{The R Journal}}, \emph{10}(1), 439--446. \url{https://doi.org/10.32614/RJ-2018-009}
+0.00 \%
 
-\bibitem[\citeproctext]{ref-R-sp}
-Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. Retrieved from \url{https://CRAN.R-project.org/doc/Rnews/}
+2.89
 
-\bibitem[\citeproctext]{ref-R-base}
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+0.78
 
-\bibitem[\citeproctext]{ref-R-formattable}
-Ren, K., \& Russell, K. (2021). \emph{Formattable: Create 'formattable' data structures}. Retrieved from \url{https://CRAN.R-project.org/package=formattable}
+0.03
 
-\bibitem[\citeproctext]{ref-R-ltm}
-Rizopoulos, D.
-(2006).
-Ltm: An r package for latent variable modelling and item response theory analyses.
-\emph{Journal of Statistical Software}, \emph{17}(5), 1--25.
-Retrieved from \url{https://doi.org/10.18637/jss.v017.i05}
+0.72
 
-\bibitem[\citeproctext]{ref-sabers1991differences}
-Sabers, D.
-S., Cushing, K.
-S., \& Berliner, D.
-C.
-(1991).
-Differences among teachers in a task characterized by simultaneity, multidimensional, and immediacy.
-\emph{American Educational Research Journal}, \emph{28}(1), 63--88.
+0.46
 
-\bibitem[\citeproctext]{ref-seidel2014modeling}
-Seidel, T., \& Stürmer, K. (2014). Modeling and measuring the structure of professional vision in preservice teachers. \emph{American Educational Research Journal}, \emph{51}(4), 739--771.
+0.71
 
-\bibitem[\citeproctext]{ref-sherin2007development}
-Sherin, M.
-(2007).
-\emph{The development of teachers' professional vision in video clubs.
-Video research in the learning sciences.
-R.
-Goldman, r.
-Pea, b.
-Barron and SJ derry}.
-Mahwah, NJ, Lawrence Erlbaum.
+LP01\_04
 
-\bibitem[\citeproctext]{ref-R-ggrepel}
-Slowikowski, K. (2021). \emph{Ggrepel: Automatically position non-overlapping text labels with 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggrepel}
+0.00 \%
 
-\bibitem[\citeproctext]{ref-R-rnaturalearth}
-South, A. (2017a). \emph{Rnaturalearth: World map data from natural earth}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearth}
+3.52
 
-\bibitem[\citeproctext]{ref-R-rnaturalearthdata}
-South, A. (2017b). \emph{Rnaturalearthdata: World vector map data from natural earth used in 'rnaturalearth'}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearthdata}
+0.59
 
-\bibitem[\citeproctext]{ref-treisch2018entwicklung}
-Treisch, F. (2018). \emph{Die entwicklung der professionellen unterrichtswahrnehmung im lehr-lern-labor seminar}. Bayerische Julius-Maximilians-Universitaet Wuerzburg (Germany).
+-0.81
 
-\bibitem[\citeproctext]{ref-R-MASS}
-Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
+0.88
 
-\bibitem[\citeproctext]{ref-R-ggplot2}
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+0.53
 
-\bibitem[\citeproctext]{ref-R-stringr}
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+0.70
 
-\bibitem[\citeproctext]{ref-R-forcats}
-Wickham, H. (2021). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+LP01\_05
 
-\bibitem[\citeproctext]{ref-R-tidyverse}
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
+0.00 \%
 
-\bibitem[\citeproctext]{ref-R-readxl}
-Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
+3.49
 
-\bibitem[\citeproctext]{ref-R-dplyr}
-Wickham, H., François, R., Henry, L., \& Müller, K. (2022). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+0.57
 
-\bibitem[\citeproctext]{ref-R-tidyr}
-Wickham, H., \& Girlich, M. (2022). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+-0.55
 
-\bibitem[\citeproctext]{ref-R-readr}
-Wickham, H., Hester, J., \& Bryan, J. (2021). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+0.87
 
-\bibitem[\citeproctext]{ref-R-haven}
-Wickham, H., \& Miller, E. (2021). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. Retrieved from \url{https://CRAN.R-project.org/package=haven}
+0.56
 
-\bibitem[\citeproctext]{ref-R-cowplot}
-Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+0.70
 
-\bibitem[\citeproctext]{ref-wolff2015keeping}
-Wolff, C.
-E., Bogert, N.
-van den, Jarodzka, H., \& Boshuizen, H.
-P.
-(2015).
-Keeping an eye on learning: Differences between expert and novice teachers' representations of classroom management events.
-\emph{Journal of Teacher Education}, \emph{66}(1), 68--85.
+LP01\_06
 
-\bibitem[\citeproctext]{ref-wolff2016teacher}
-Wolff, C.
-E., Jarodzka, H., Bogert, N.
-van den, \& Boshuizen, H.
-(2016).
-Teacher vision: Expert and novice teachers' perception of problematic classroom management scenes.
-\emph{Instructional Science}, \emph{44}(3), 243--265.
+0.00 \%
 
-\bibitem[\citeproctext]{ref-R-knitr}
-Xie, Y. (2015). \emph{Dynamic documents with {R} and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.org/knitr/}
+3.19
 
-\bibitem[\citeproctext]{ref-R-ARTofR}
-Zhang, H. (2021). \emph{ARTofR: Who ever care about the {[}art of r{]} scripts?} Retrieved from \url{https://CRAN.R-project.org/package=ARTofR}
+0.7
 
-\bibitem[\citeproctext]{ref-R-kableExtra}
-Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
+-0.28
 
-\end{CSLReferences}
+0.80
 
-\endgroup
+0.41
 
-\clearpage
-\renewcommand{\listtablename}{Table captions}
+0.72
+
+LP01\_07
+
+0.00 \%
+
+3
+
+0.68
+
+-0.24
+
+0.75
+
+0.33
+
+0.74
+
+LP01\_08
+
+0.00 \%
+
+2.9
+
+0.67
+
+-0.14
+
+0.73
+
+0.50
+
+0.71
+
+Mean inter-item-correlation=0.273 · Cronbach's α=0.745
+
+Component 1
+
+Row
+
+Missings
+
+Mean
+
+SD
+
+Skew
+
+Item Difficulty
+
+Item Discrimination
+
+α if deleted
+
+LV01\_01
+
+0.00 \%
+
+3.23
+
+0.68
+
+-0.55
+
+0.81
+
+0.61
+
+0.71
+
+LV01\_02
+
+0.00 \%
+
+3.32
+
+0.84
+
+-1.05
+
+0.83
+
+0.63
+
+0.69
+
+LV01\_03
+
+0.00 \%
+
+3.19
+
+0.75
+
+-0.51
+
+0.80
+
+0.61
+
+0.70
+
+Mean inter-item-correlation=0.540 · Cronbach's α=0.776
 

### 2024-10-18 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x paper

--- 2024-09-02 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
@@
       psych,
-      apaTables)
+      apaTables,
+      rstatix)
 
@@
   mutate(
-    GRI = round(Average_duration_mtu / Sum_number_fixation, digits = 2),
+    GRI = round(Average_duration_mtu / Number_fixation_min_mtu, digits = 2),
     )-> df_gri
@@
   ) +
-  ylim(0, 1) +
-  labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
+  ylim(0, 12) +
+  labs(x = "", y = "average duration of fixations/\nnumber of fixations per minute") +
   scale_fill_brewer(palette  = "RdBu") +
@@
 
-# M, SD, min, max time to first fixation "Disruptive Person"
+############### M, SD, min, max time to first fixation "Disruptive Person"
 ttff.disrup.table <-
   df_ttff_disrup %>%
+  filter(!Participant %in% c("216", "113", "123")) %>% 
   group_by(Group) %>%
@@
 
+############### M, SD, min, max of the perceived "Disruptive Person" ############### 
+number.perceived.disrup.table <-
+ df_ttff_disrup %>%
+  filter(!Participant %in% c("216", "113", "123")) %>%
+  group_by(Group) %>%
+  summarise(
+    Mean = round(mean(N, na.rm = TRUE), digits = 2),
+    SD = round(sd(N, na.rm = TRUE), digits = 2), 
+    Min = min(N, na.rm = TRUE),
+    Max = max(N, na.rm = TRUE)
+  )
+
+knitr::kable(number.perceived.disrup.table,
+             caption = "N, M, SD, min & max of the perceived ´disruptive person´")
+
+############### PLOTTING ###############
+
+##################### plotting "perceived disruptive person" for groups ##################### 
+plot_n_disrup <- 
+  df_ttff_disrup %>%
+  filter(!Participant %in% c("216", "113", "123")) %>%
+  ggplot(mapping = aes(x = Group,
+                       y = N)) +
+ geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  ylim(0,10) +
+  labs(x ="",
+       y = "Counts") + 
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("Counts of the perceived ´disruptive person´\n") +
+  theme_cowplot() +
+  theme(legend.position="none")
+
+plot_n_disrup
+
 ##################### plotting time to first fixation for groups ##################### 
 plot_time_disrup <- 
-  ggplot(data = df_ttff_disrup,
-         mapping = aes(x = Group,
+  df_ttff_disrup %>%
+  filter(!Participant %in% c("216", "113", "123")) %>%
+  ggplot(mapping = aes(x = Group,
                        y = Disrup_time_fixation_sec)) +
@@
                                         height = 0.1)) +
-  ylim(0,14) +
+  ylim(0,10) +
   labs(x ="",
@@
     Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
-    GRI_mtu = round(Average_duration_mtu / Sum_number_fixation, digits = 2)
+    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, digits = 2)
     ) %>%
@@
 
-# time to first fixatoin (AOI disruptive person)
 df_aoi %>% 
-  filter(
-    TOI %in% c(
-      "Chatting_with_neighbour",
+  filter(TOI %in% c("Chatting_with_neighbour",
                     "Clicking_pen",
@@
          ) %>% 
-  dplyr::select(Participant, TOI, Time_to_first_fixation.Disruptive_Person, ) %>%
+  dplyr::select(Participant,
+                TOI,
+                Time_to_first_fixation.Disruptive_Person,
+                ) %>% 
   rowwise() %>% 
@@
   group_by(Participant) %>% 
-  summarise(
-    Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person)
-  ) %>%
-  mutate(
-    Group = ifelse(Participant < 200, "Novice", "Expert"),
+  filter(!Time_to_first_fixation.Disruptive_Person == 0, # exclude all participants with 0 msec
+         !Time_to_first_fixation.Disruptive_Person > 30000) %>% # cut-off 30sec
+  summarise(N = n(),
+            Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person/N)
+            ) %>% 
+  mutate(Group = ifelse(Participant < 200, "Novice", "Expert"),
+         Sum_disruptions = sum(N),
          Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000, 
-      digits = 2
-    )
-  ) -> df_ttff_disrup
+                                          digits = 2)) -> df_ttff_disrup # changing milliseconds into seconds
 
@@
                 Mean_disrupption_appraisal,
-                Mean_confidence_appraisal,
-                Mean_prevalence_rating)
+                Mean_confidence_appraisal)
 
@@
     SJT_Monitoring = round(SJT_AL_gek, 2),
-    SJT_Managing_momentum = round(SJT_ST_gek, 2),
-    SJT_Rules_routines = round(SJT_R_gek, 2),
-    SJT_All = round(SJT_KF_gek, 2)
-  )
+    SJT_All = round(SJT_KF_gek, 2),
+  ) %>%
+  arrange(Participant)
 
@@
                 df_aoi_disrup,
+                df_ttff_disrup,
                 df_sri,
@@
   df_list %>% reduce(full_join, by='Participant') %>%
-  # filter(Participant > 200) %>% 
-  dplyr::select(.,
-                -"Participant")
+  # filter(`Teaching Experience` > 0) %>% 
+  dplyr::select(Stud_number_fixation_min,
+                Average_duration_stud,
+                Number_of_fixations.Disruptive_Person,
+                Average_duration_disrup,
+                Disrup_time_fixation_sec,
+                GRI_mtu,
+                SJT_All,
+                SJT_Monitoring,
+                Quest_All
+                )
 
@@
 
-# create a scatter plot 
-# pairs(~ Gender + 
-#         Age + 
-#         `Teaching Experience` + 
-#         Sum_number_fixation + 
-#         Stud_number_fixation + 
-#         Number_of_fixations.Disruptive_Person + 
-#         Average_duration_mtu + 
-#         Average_duration_stud + 
-#         Average_duration_disrup + 
-#         GRI_mtu + 
-#         GRI_stud + 
-#         GRI_disrup + 
-#         Mean_disrupption_appraisal + 
-#         Mean_confidence_appraisal + 
-#         Mean_prevalence_rating + 
-#         SJT_Monitoring + 
-#         SJT_Managing_momentum + 
-#         SJT_Rules_routines + 
-#         SJT_All + 
-#         Quest_classroom_management + 
-#         Quest_non_paraverbal_communication + 
-#         Quest_All,
-#       upper.panel = NULL,
-#       pch = 20,
-#       cex = 3, 
-#       main = "Correlation Table Expertise Measures",
-#       col = Gender)
-
-# apa.cor.table(cor_tab)
-
-```
+### Teaching experience with only experts
+# merge all data frames in list
+df_merge_experts <-
+  df_list %>% reduce(full_join, by='Participant') %>%
+  filter(`Teaching Experience` > 0) %>% 
+  dplyr::select(`Teaching Experience`,
+                Stud_number_fixation_min,
+                Average_duration_stud,
+                Number_of_fixations.Disruptive_Person,
+                Average_duration_disrup,
+                Disrup_time_fixation_sec,
+                GRI_mtu,
+                SJT_All,
+                SJT_Monitoring,
+                Quest_All
+                )
+
+# create a correlation matrix
+cor_tab_experts <- 
+  df_merge_experts %>% 
+  cor(method = "pearson") %>% 
+  round(., digits = 2)
+
+# p-value for GRI x STJ_All
+cor.test(df_merge$GRI_mtu, df_merge$SJT_All)
+
+# p-value for GRI x STJ_Monitoring
+cor.test(df_merge$GRI_mtu, df_merge$SJT_Monitoring)
+
+# p-value for GRI x Teaching Experience
+cor.test(df_merge_experts$GRI_mtu, df_merge_experts$`Teaching Experience`)
+
+```

### 2024-10-21 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x

@@
 
-# # create a basic table (tibble) using tidyverse functions
-# exp.table <- demo.data %>%
-#   group_by(Group) %>%
-#   summarise(N=n(),
-#            "M Exp." = round(mean(`Teaching Experience`), 2),
-#             "SD Exp." = round(sd(`Teaching Experience`), 2),
-#             "Min Exp." = min(`Teaching Experience`),
-#             "Max Exp." = max(`Teaching Experience`),
-#             "M Semester" = round(mean(Semester), 2),
-#             "SD Semester" = round(sd(Semester), 2),
-#             "Min Semester" = min(Semester),
-#             "Max Semester" = max(Semester),
-#             "M Internship" = round(mean(Internship), 2),
-#             "SD Internship" = round(sd(Internship), 2),
-#             "Min Internship" = min(Internship),
-#             "Max Internship" = max(Internship),
-#             "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
-#             "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
-#            )
+# create a basic table (tibble) using tidyverse functions
+exp.table <- demo.data %>%
+  group_by(Group) %>%
+  summarise(N=n(),
+           "M Exp." = round(mean(`Teaching Experience`), 2),
+            "SD Exp." = round(sd(`Teaching Experience`), 2),
+            "Min Exp." = min(`Teaching Experience`),
+            "Max Exp." = max(`Teaching Experience`),
+            "M Semester" = round(mean(Semester), 2),
+            "SD Semester" = round(sd(Semester), 2),
+            "Min Semester" = min(Semester),
+            "Max Semester" = max(Semester),
+            "M Internship" = round(mean(Internship), 2),
+            "SD Internship" = round(sd(Internship), 2),
+            "Min Internship" = min(Internship),
+            "Max Internship" = max(Internship),
+            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
+            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
+           )
 

### 2024-10-23 02_paper/02_study/02_expertise_paper/paper_methods.Rmd
x paper

--- 2024-07-05 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.Rmd
@@
   read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
+  filter(!LI06_05 == 201,
+         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
   transmute(Group = LI06_05,
@@
 # 3: Gymnasium
-# 4: Förderschule/Sondershausen
+# 4: Förderschule
 # 5: Berufsbildende Schule
@@
 The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`).
-`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers.
+`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Vocational School") %>% pull("Percent_schooltype") %>% unique()`% were vocational school teachers.
 `r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
@@
 
-# read in data and combine multiple excel sheets into a single table 
-sri <- 
-  excel_sheets("data/Coding_SRI.xlsx") %>% 
-  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% 
-  dplyr::select(Group, Event, `Disruption Factor`, `Confident Factor`) %>% # select relevant columns
-  dplyr::filter(!`Disruption Factor` == -100,
-           !`Confident Factor` == -100,
-           !`Disruption Factor`== -99,
-           !`Confident Factor` == -99)
-
-############## Disruption Factor #########################
-
-sri.disrup.table <- 
-  sri %>%
-  group_by(Group, Event) %>%
-  mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
-  summarise("M" = round(mean(`Disruption Factor`), 
-                        digits = 2),
-            "SD" = round(sd(`Disruption Factor`),
-                         digits = 2),
-            "Min" = min(`Disruption Factor`),
-            "Max" = max(`Disruption Factor`))
-
-# format and insert table in manuscript
-papaja::apa_table(
-sri.disrup.table,
-  caption = "Table Rating Scales Disruption Factor",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-############## Confident Factor #########################
-
-sri.confi.table <- 
-  sri %>%
-  group_by(Group, Event) %>%
-  mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
-  summarise("M" = round(mean(`Confident Factor`), 
-                        digits = 2),
-            "SD" = round(sd(`Confident Factor`),
-                         digits = 2),
-            "Min" = min(`Confident Factor`),
-            "Max" = max(`Confident Factor`))
-
-# format and insert table in manuscript
-papaja::apa_table(
-sri.confi.table,
-  caption = "Table Rating Scales Confident Factor",
-  # note = "Write Note here",
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
+# # read in data and combine multiple excel sheets into a single table 
+# sri <- 
+#   excel_sheets("data/Coding_SRI.xlsx") %>% 
+#   map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% 
+#   dplyr::select(Group, Event, `Disruption Factor`, `Confident Factor`) %>% # select relevant columns
+#   dplyr::filter(!`Disruption Factor` == -100,
+#            !`Confident Factor` == -100,
+#            !`Disruption Factor`== -99,
+#            !`Confident Factor` == -99)
+# 
+# ############## Disruption Factor #########################
+# 
+# sri.disrup.table <- 
+#   sri %>%
+#   group_by(Group, Event) %>%
+#   mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
+#   summarise("M" = round(mean(`Disruption Factor`), 
+#                         digits = 2),
+#             "SD" = round(sd(`Disruption Factor`),
+#                          digits = 2),
+#             "Min" = min(`Disruption Factor`),
+#             "Max" = max(`Disruption Factor`))
+# 
+# # format and insert table in manuscript
+# papaja::apa_table(
+# sri.disrup.table,
+#   caption = "Table Rating Scales Disruption Factor",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+# )
+# 
+# ############## Confident Factor #########################
+# 
+# sri.confi.table <- 
+#   sri %>%
+#   group_by(Group, Event) %>%
+#   mutate(Group = ifelse(Group < 200, "Novice","Expert")) %>%
+#   summarise("M" = round(mean(`Confident Factor`), 
+#                         digits = 2),
+#             "SD" = round(sd(`Confident Factor`),
+#                          digits = 2),
+#             "Min" = min(`Confident Factor`),
+#             "Max" = max(`Confident Factor`))
+# 
+# # format and insert table in manuscript
+# papaja::apa_table(
+# sri.confi.table,
+#   caption = "Table Rating Scales Confident Factor",
+#   # note = "Write Note here",
+#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+# )
 
@@
 89ff].
+-->
 

### 2024-10-23 02_paper/02_study/02_expertise_paper/paper_methods.tex
x paper

--- 2024-07-05 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.tex
@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
 % definitions for citeproc citations
@@
 \midrule
-Expert & 42 & 59.52 & 39.31 & 10.64 & 26.00 & 60.00\\
+Expert & 40 & 60.00 & 39.10 & 10.55 & 26.00 & 60.00\\
 Novice & 42 & 69.05 & 22.83 & 1.85 & 19.00 & 27.00\\
@@
 \midrule
-Expert & 42 & 11.79 & 11.43 & 1.00 & 38.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & NA\\
+Expert & 40 & 11.55 & 11.32 & 1.00 & 38.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 52.00\\
 Novice & 42 & 0.00 & 0.00 & 0.00 & 0.00 & 6.74 & 2.65 & 3.00 & 11.00 & 9.62 & 7.19 & 0.00 & 36.00 & 88.10 & NA\\
@@
 
-The sample consisted of \emph{N} = 84 participants with \emph{n} = 42 expert teachers and \emph{n} = 42 novice teachers.
+The sample consisted of \emph{N} = 82 participants with \emph{n} = 40 expert teachers and \emph{n} = 42 novice teachers.
 
@@
 
-The expert teachers (25 women; 59.52\%) had a mean age of 39.30 years (\emph{SD} = 10.60; range: 26-60) and an average teaching experience of 11.80 years (\emph{SD} = 11.40; range: 1-38).
-9.52\% of the experts were primary school teachers and 80.95\% were secondary school teachers.
-NA\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+The expert teachers (24 women; 60\%) had a mean age of 39.10 years (\emph{SD} = 10.60; range: 26-60) and an average teaching experience of 11.60 years (\emph{SD} = 11.30; range: 1-38).
+10\% of the experts were primary school teachers and 85\% were secondary school teachers and 5\% were vocational school teachers.
+52\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
 
@@
 Furthermore, they had an average teaching experience of 9.60 teaching units à 45min (\emph{SD} = 7.20; range: 0-36) through the internships during their studies.
-21.43\% of the novices were studying to become primary school teachers, 57.14\% to become secondary school teachers and 19.05\% to become special education teachers.
+21.43\% of the novices were studying to become primary school teachers, 59.52\% to become secondary school teachers and 19.05\% to become special education teachers.
 88.10\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
@@
 
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:rating_scales}Table Rating Scales Disruption Factor}
-
-\tiny{
-
-\begin{tabular}{llllll}
-\toprule
-Group & \multicolumn{1}{c}{Event} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
-\midrule
-Expert & chatting & 6.44 & 3.33 & 1.00 & 10.00\\
-Expert & clicking pen & 5.57 & 2.87 & 0.00 & 10.00\\
-Expert & drawing & 1.85 & 1.46 & 0.00 & 6.00\\
-Expert & drumming & 4.60 & 2.44 & 1.00 & 8.00\\
-Expert & head on table & 3.73 & 2.25 & 0.00 & 8.00\\
-Expert & heckling & 7.19 & 2.37 & 2.00 & 10.00\\
-Expert & looking at phone & 4.71 & 3.10 & 1.00 & 10.00\\
-Expert & snipping & 4.00 & 3.61 & 0.00 & 10.00\\
-Expert & whispering & 4.56 & 2.50 & 0.00 & 9.00\\
-Novice & chatting & 8.62 & 1.35 & 5.00 & 10.00\\
-Novice & clicking pen & 7.00 & 2.11 & 3.00 & 10.00\\
-Novice & drawing & 2.24 & 1.48 & 0.00 & 4.00\\
-Novice & drumming & 6.57 & 2.27 & 0.00 & 10.00\\
-Novice & head on table & 4.09 & 2.09 & 1.00 & 8.00\\
-Novice & heckling & 6.96 & 2.57 & 2.00 & 10.00\\
-Novice & looking at phone & 3.90 & 1.94 & 1.00 & 8.00\\
-Novice & snipping & 4.67 & 3.33 & 0.00 & 9.00\\
-Novice & whispering & 6.08 & 2.36 & 1.00 & 10.00\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:rating_scales}Table Rating Scales Confident Factor}
-
-\tiny{
-
-\begin{tabular}{llllll}
-\toprule
-Group & \multicolumn{1}{c}{Event} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
-\midrule
-Expert & chatting & 8.44 & 2.03 & 2.00 & 10.00\\
-Expert & clicking pen & 8.93 & 1.00 & 7.00 & 10.00\\
-Expert & drawing & 9.23 & 1.36 & 5.00 & 10.00\\
-Expert & drumming & 9.07 & 0.96 & 7.00 & 10.00\\
-Expert & head on table & 9.00 & 1.41 & 5.00 & 10.00\\
-Expert & heckling & 6.75 & 2.89 & 2.00 & 10.00\\
-Expert & looking at phone & 9.21 & 1.05 & 7.00 & 10.00\\
-Expert & snipping & 9.06 & 1.48 & 4.00 & 10.00\\
-Expert & whispering & 8.06 & 2.11 & 3.00 & 10.00\\
-Novice & chatting & 6.42 & 2.39 & 0.00 & 10.00\\
-Novice & clicking pen & 7.54 & 1.89 & 3.00 & 10.00\\
-Novice & drawing & 8.81 & 1.25 & 5.00 & 10.00\\
-Novice & drumming & 7.57 & 2.11 & 3.00 & 10.00\\
-Novice & head on table & 7.30 & 1.96 & 3.00 & 10.00\\
-Novice & heckling & 5.35 & 2.53 & 1.00 & 10.00\\
-Novice & looking at phone & 7.65 & 1.73 & 3.00 & 10.00\\
-Novice & snipping & 8.04 & 1.73 & 3.00 & 10.00\\
-Novice & whispering & 7.25 & 2.03 & 2.00 & 10.00\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 \paragraph{Situational Jugdement Test of Strategic Knowledge of Classroom Management}\label{situational-jugdement-test-of-strategic-knowledge-of-classroom-management}
@@
 Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions {[}cf.~ibid.; Kounin (2006), p.~89ff{]}.
+--\textgreater{}
 
@@
 In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}.
-The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{psych} (Version 2.4.6.26; William Revelle, 2024), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
+The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{apaTables} (Version 2.0.8; Stanley, 2021), \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{psych} (Version 2.4.6.26; William Revelle, 2024), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{rstatix} (Version 0.7.2; Kassambara, 2023), \emph{sf} (E.
 Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E.
@@
 \midrule
-Monitoring & 4.00 & 0.71 & 0.11 & 0.44 & 0.96 & -0.11 & 3.76 & 0.37\\
-Managing Momentum & 5.00 & 0.74 & 0.11 & 0.51 & 0.94 & -0.25 & 2.85 & 0.19\\
-Rules and routines & 3.00 & 0.75 & 0.11 & 0.46 & 0.90 & -0.74 & 3.25 & -0.28\\
+Monitoring & 4.00 & 0.68 & 0.13 & 0.17 & 0.96 & -1.15 & 6.34 & 0.53\\
+Managing Momentum & 5.00 & 0.72 & 0.13 & 0.22 & 0.94 & -1.55 & 6.75 & 0.53\\
+Rules and routines & 3.00 & 0.71 & 0.15 & 0.02 & 0.90 & -2.46 & 12.55 & 0.46\\
 \bottomrule
@@
 \midrule
-Monitoring & 4.00 & 0.71 & 0.15 & 0.52 & 0.92 & 0.17 & 1.76 & 0.38\\
-Managing Momentum & 5.00 & 0.70 & 0.13 & 0.52 & 0.89 & 0.31 & 1.77 & 0.34\\
-Rules and routines & 3.00 & 0.70 & 0.13 & 0.47 & 0.89 & -0.27 & 2.20 & 0.46\\
+Monitoring & 4.00 & 0.71 & 0.11 & 0.51 & 0.93 & 0.07 & 2.49 & 0.40\\
+Managing Momentum & 5.00 & 0.72 & 0.12 & 0.51 & 0.95 & -0.02 & 1.86 & 0.41\\
+Rules and routines & 3.00 & 0.72 & 0.11 & 0.47 & 0.92 & -0.15 & 2.39 & 0.25\\
 \bottomrule
@@
 
-All reported data analyses were conducted with the R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.1.4; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{psych} (Version 2.4.6.26; William Revelle, 2024), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E.
+All reported data analyses were conducted with the R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{apaTables} (Version 2.0.8; Stanley, 2021), \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.1.4; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{psych} (Version 2.4.6.26; William Revelle, 2024), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{rstatix} (Version 0.7.2; Kassambara, 2023), \emph{sf} (E.
 Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E.
@@
 Jeppson, H., Hofmann, H., \& Cook, D. (2021). \emph{Ggmosaic: Mosaic plots in the 'ggplot2' framework}. Retrieved from \url{https://CRAN.R-project.org/package=ggmosaic}
+
+\bibitem[\citeproctext]{ref-R-rstatix}
+Kassambara, A. (2023). \emph{Rstatix: Pipe-friendly framework for basic statistical tests}. Retrieved from \url{https://CRAN.R-project.org/package=rstatix}
 
@@
 
+\bibitem[\citeproctext]{ref-R-apaTables}
+Stanley, D. (2021). \emph{apaTables: Create american psychological association (APA) style tables}. Retrieved from \url{https://CRAN.R-project.org/package=apaTables}
+
 \bibitem[\citeproctext]{ref-treisch2018entwicklung}

### 2024-10-25 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.tex
bla

--- 2024-09-27 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission_template.tex
@@
    \ead{mandy.klatt@uni-leipzig.de} 
-    \author[University of Greifswald]{Peer Keßler%
+    \author[Leipzig University]{Christin Lotz%
   %
   \fnref{2}}
-   \ead{peer.kessler@uni-greifswald.de} 
+   \ead{christin.lotz@uni-leipzig.de} 
     \author[Max Planck Institute for Evolutionary Anthropology]{Gregor
@@
    \ead{gregor@example.com} 
-    \author[Leipzig University]{Christin Lotz%
+    \author[University of Greifswald]{Peer Keßler%
   %
   \fnref{4}}
-   \ead{christin.lotz@uni-leipzig.de} 
+   \ead{peer.kessler@uni-greifswald.de} 
     \author[Leipzig University]{Anne Deiglmayr%
@@
 Institute of Educational Sciences},addressline={Marschnerstr.
-29},city={Leipzig},postcode={4109},state={Sachsen},country={Germany},}
+29},city={Leipzig},postcode={04109},country={Germany},}
     \affiliation[Max Planck Institute for Evolutionary Anthropology]{
     organization={Department},addressline={Deutscher Pl.
-6},city={Leipzig},postcode={4103},state={Sachsen},country={Germany},}
+6},city={Leipzig},postcode={04103},country={Germany},}
     \affiliation[University of Greifswald]{
@@
 Psychology},addressline={Robert-Blum-Str.
-13},city={Greifswald},postcode={17489},state={Mecklenburg-Vorpommern},}
+13},city={Greifswald},postcode={17489},country={Germany},}
     \cortext[cor1]{Corresponding author}
@@
 
+\bibliography{r-references.bib}
+
 \appendix
@@
 
-\bibliography{r-references.bib}
-
 \end{document}

### 2024-10-25 02_paper/02_study/01_fitbit_paper/R_scripts/analysis_190423.Rmd

--- 2023-04-24 02_paper/02_study/02_fitbit paper/analysis_190423.Rmd
@@
   map(~ tibble(time_span = names(.),
-               intercept = fixef(.)[[1]],
+               intercept = fixef(.)[1],
                intercept_sd = VarCorr(.) %>% as_tibble() %>% .[1,5],
                intercept_p = coef(summary(.))[1, 5],
-               slope = fixef(.)[[2]],
+               slope = fixef(.)[2],
                slope_sd = VarCorr(.) %>% as_tibble() %>% .[2,5],
@@
 knitr::kable(., caption = "Overview")
+
+model_hurensohn <- 
+  df_regression %>% 
+  filter(time_span == "teaching") %$% 
+  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
+       data = .) %>% 
+  fixef(.)[2]
+
+fixef(model_hurensohn)[2]
+
 ```

### 2024-10-25 02_paper/02_study/01_fitbit_paper/R_scripts/fitbit_paper.tex

--- 2023-05-22 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 \midrule
-N & 76.00\\
-Gender female in percent & 63.16\\
-M Age in years & 30.26\\
-SD Age in years & 10.52\\
+N & 81.00\\
+Gender female in percent & 64.20\\
+M Age in years & 30.95\\
+SD Age in years & 10.87\\
 Min Age in years & 19.00\\
-Max Age in years & 59.00\\
-M Teaching Experience in years & 5.17\\
-SD Teaching Experience in years & 9.12\\
+Max Age in years & 60.00\\
+M Teaching Experience in years & 5.64\\
+SD Teaching Experience in years & 9.46\\
 Min Teaching Experience in years & 0.00\\
@@
 
-The sample consisted in total of \emph{N} = 76 pre- and in-service teachers.
+The sample consisted in total of \emph{N} = 81 pre- and in-service teachers.
 The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers.
-Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 76 subjects.
+Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 81 subjects.
 
-The subjects (48 women; 63.16 \%) had a mean age of 30.30 years (\emph{SD} = 10.50; range: 19-59) and an average teaching experience of 5.17 years (\emph{SD} = 9.12; range: 0-37).
+The subjects (52 women; 64.20 \%) had a mean age of 31 years (\emph{SD} = 10.90; range: 19-60) and an average teaching experience of 5.64 years (\emph{SD} = 9.46; range: 0-37).
 
-15.79\% of the subjects were (studying to become) teachers for primary school, 71.05\% were (studying to become) teachers for secondary school and 10.53\% were (studying to become) teachers for special education needs.
+14.81\% of the subjects were (studying to become) teachers for primary school, 70.37\% were (studying to become) teachers for secondary school and 9.88\% were (studying to become) teachers for special education needs.
 
@@
 
-We used R (Version 4.2.2; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.48; Andri et mult.
-al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.2; Wickham, 2021), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{jtools} (Version 2.2.1; Long, 2022), \emph{lm.beta} (Version 1.7.2; Behrendt, 2022), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.58.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.1.9001; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Version 2.3.3; Revelle, 2022), \emph{purrr} (Version 0.3.5; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.1; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.1; Kassambara, 2021), \emph{rticles} (Version 0.25; Allaire et al., 2023), \emph{stringr} (Version 1.4.1; Wickham, 2019), \emph{tibble} (Version 3.1.8; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.2; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.38; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression).
+We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{corrplot2021} (Wei \& Simko, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020a), \emph{DescTools} (Version 0.99.45; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{gridtext} (Version 0.1.4; Wilke, 2020b), \emph{Hmisc} (Version 5.0.1; Harrell Jr, 2023), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{magrittr} (Version 2.0.3; Bache \& Wickham, 2022), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{PerformanceAnalytics} (Version 2.0.4; Peterson \& Carl, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Version 2.2.9; Revelle, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{rticles} (Version 0.25; Allaire et al., 2023), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), \emph{xfun} (Version 0.36; Xie, 2022), \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019), \emph{xts} (Version 0.12.1; Ryan \& Ulrich, 2020), and \emph{zoo} (Version 1.8.10; Zeileis \& Grothendieck, 2005) for all our analyses (descriptive statistics, correlations, and multilevel regression).
 Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}.
@@
 
-Teachers' average heart rate during the entire course of the study was approximately 90.40 bpm with a standard deviation of 15.82 and a range from 51 to 164 bpm.
+Teachers' average heart rate during the entire course of the study was approximately 90.09 bpm with a standard deviation of 15.76 and a range from 51 to 164 bpm.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-magrittr}{}}%
+Bache, S. M., \& Wickham, H. (2022). \emph{Magrittr: A forward-pipe operator for r}. Retrieved from \url{https://CRAN.R-project.org/package=magrittr}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
@@
 \emph{The Journal of Educational Research}, \emph{110}(5), 478--493.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-xtable}{}}%
+Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-Hmisc}{}}%
+Harrell Jr, F. E. (2023). \emph{Hmisc: Harrell miscellaneous}. Retrieved from \url{https://CRAN.R-project.org/package=Hmisc}
+
 \leavevmode\vadjust pre{\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-lmerTest}{}}%
+Kuznetsova, A., Brockhoff, P.
+B., \& Christensen, R.
+H.
+B.
+(2017).
+{lmerTest} package: Tests in linear mixed effects models.
+\emph{Journal of Statistical Software}, \emph{82}(13), 1--26.
+\url{https://doi.org/10.18637/jss.v082.i13}
+
 \leavevmode\vadjust pre{\hypertarget{ref-kyriacou2001teacher}{}}%
@@
 Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-PerformanceAnalytics}{}}%
+Peterson, B. G., \& Carl, P. (2020). \emph{PerformanceAnalytics: Econometric tools for performance and risk analysis}. Retrieved from \url{https://CRAN.R-project.org/package=PerformanceAnalytics}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-xts}{}}%
+Ryan, J. A., \& Ulrich, J. M. (2020). \emph{Xts: eXtensible time series}. Retrieved from \url{https://CRAN.R-project.org/package=xts}
+
 \leavevmode\vadjust pre{\hypertarget{ref-sachs2014physiologische}{}}%
@@
 Wang, C., Lizardo, O., \& Hachen, D. S. (2022). Using fitbit data to monitor the heart rate evolution patterns of college students. \emph{Journal of American College Health}, \emph{70}(3), 875--882.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-corrplot2021}{}}%
+Wei, T., \& Simko, V. (2021). \emph{R package 'corrplot': Visualization of a correlation matrix}. Retrieved from \url{https://github.com/taiyun/corrplot}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
-Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+Wilke, C. O. (2020a). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-gridtext}{}}%
+Wilke, C. O. (2020b). \emph{Gridtext: Improved text rendering support for 'grid' graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridtext}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-zoo}{}}%
+Zeileis, A., \& Grothendieck, G.
+(2005).
+Zoo: S3 infrastructure for regular and irregular time series.
+\emph{Journal of Statistical Software}, \emph{14}(6), 1--27.
+\url{https://doi.org/10.18637/jss.v014.i06}
+
 \end{CSLReferences}

### 2024-10-25 02_paper/02_study/01_fitbit_paper/Submission/FitBit_Plots_MK.Rmd

--- 2023-10-10 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
@@
 main <-
-  left_join(main, df_merge,
+  left_join(x = main, y = df_merge,
             by = "ID")
@@
 # standardisierte Koeffizienten
-zmodell <- lm(scale(mean_hr_std) ~ scale(mean_confi) + scale (mean_disrup) + scale(mean_te), 
+zmodell <- lm(scale(mean_hr_std) ~ scale(mean_confi) + scale(mean_disrup) + scale(mean_te), 
               data = df_lm_subset)

### 2024-10-25 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd

@@
  rm(i)
+
+```
+
+#### 2.2.2 Letter search
+```{r letter_search, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### LETTER SEARCH ########################
+
+# filter
+df_aoi %>%
+  filter(TOI == "Letter_search") %>% 
+  dplyr::select (
+    TOI,
+    Group,
+    Participant,
+    Duration_of_interval) %>% 
+  mutate(Duration_of_interval_sec = 
+           round(Duration_of_interval/1000, digits = 2)
+         ) -> df_letter
+# missing IDs: 101, 111, 205
+
+# N, M, SD, min & max 
+letter.table <-
+  df_letter %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Duration_of_interval_sec), digits = 2),
+    "SD" = round(sd(Duration_of_interval_sec), digits = 2),
+    "Min" = round(min(Duration_of_interval_sec), digits = 2),
+    "Max" = round(max(Duration_of_interval_sec), digits = 2)
+  )
+
+knitr::kable(letter.table,
+             caption = "N, M, SD, min & max letter search in seconds")
+
+```
+
+#### t-test & effect size "Letter search"
+```{r letter_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# LETTER SEARCH 
+# t-test for expertise differences
+t.test(
+  x = df_letter$Duration_of_interval_sec[df_letter$Group == "Expert"],
+  y = df_letter$Duration_of_interval_sec[df_letter$Group == "Novice"],
+  var.equal = TRUE
+)
+
+# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit)
+# effect size for expertise differences
+d_letter <- CohenD(
+  x = df_letter$Duration_of_interval_sec[df_letter$Group == "Expert"],
+  y = df_letter$Duration_of_interval_sec[df_letter$Group == "Novice"],
+  na.rm = TRUE
+)
+
+round(d_letter, 2)
 

### 2024-10-25 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.Rmd
fb

--- 2024-10-03 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission_template.Rmd
@@
          ) +
-  geom_smooth(se = T,
+  geom_smooth(se = F,
               size = 0.5,
-              colour = "black",
-              level = 0.95
+              colour = "black"              
               ) +
@@
          ) +
-  geom_smooth(se = T,
+  geom_smooth(se = F,
               size = 0.5,
-              colour = "black",
-              level = 0.95) +
+              colour = "black"
+              ) +
   scale_color_viridis_d(option = "A",

### 2024-10-25 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.tex
verschiedenes

@@
         Overall Course of 2h & 90.09/0.04\footnotemark[12] & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
-        Pre-teaching interval ($I_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
-        Teaching interval ($I_2$) & 100.80/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\
-        Post-teaching interval ($I_3$) & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\
-        Interview interval ($I_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
-        End interval ($I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\footnotemark[13]/-2.68 & 120/2.96 \\
+        Pre-teaching interval (I$_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
+        Teaching interval (I$_2$) & 100.80/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\
+        Post-teaching interval (I$_3$) & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\
+        Interview interval (I$_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
+        End interval (I$_5$) & 77.95/-1.07 & 11.14/0.57 & 50\footnotemark[13]/-2.68 & 120/2.96 \\
         \bottomrule
@@
 
-\bibliography{r-references.bib}
-
 \appendix
@@
 
+\bibliography{r-references.bib}
+
 \end{document}

### 2024-10-29 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.Rmd
bla bla bla.. affiliations und so

@@
 shorttitle: "From heartbeat to data"
-authornote: |
+authornote: "|
  We received funding from QualiFond of University Leipzig.
 We have no conflicts of interest to disclose.
-This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).
+This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022)."
 author:
@@
     footnote: 2
-  - name: Gregor Kachel
-    email: gregor@example.com
-    affiliation: Max Planck Institute for Evolutionary Anthropology
-    footnote: 3
   - name: Peer Keßler
     email: peer.kessler@uni-greifswald.de
-    affiliation: University of Greifswald
+    affiliation: UoG, DZKJ
+    footnote: 3
+  - name: Gregor Kachel
+    email: gregor.kachel@gmail.com
+    affiliation: Leipzig University
     footnote: 4
@@
   - code: Leipzig University
-    organization: Division of Empirical School and Classroom Research, Institute of Educational Sciences
+    organization: Leipzig University Division of Empirical School and Classroom Research, Institute of Educational Sciences
     addressline: Marschnerstr. 29
@@
     country: Germany
-  - code: Max Planck Institute for Evolutionary Anthropology
-    organization: Department
-    addressline: Deutscher Pl. 6
-    postcode: "04103"
-    city: Leipzig
+  - code: UoG
+    organization: University of Greifswald, Division of Health and Prevention, Institute of Psychology
+    addressline: Robert-Blum-Str. 13
+    city: Greifswald
+    postcode: "17489" 
     country: Germany 
-  - code: University of Greifswald
-    organization: Division of Health and Prevention, Institute of Psychology
+  - code: DZKJ
+    organization: German Center for Child and Adolescent Health (DZKJ)
     addressline: Robert-Blum-Str. 13
@@
   - code: 3
+    text: "Conceptualization, Methodology, Writing - Review & Editing"
+  - code: 4
     text: "Formal analysis, Data Curation, Writing - Review & Editing"
-  - code: 4
-    text: "Conceptualization, Methodology, Writing - Review & Editing"
   - code: 5
@@
         \midrule
-        Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ ($I_1$)\\
-        Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ ($I_2$)\\
-        Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ ($I_3$)\\
-        Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ ($I_4$)\\
-        End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 ($I_5$)\\
+        Pre-teaching interval (I$_1$) & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
+        Teaching interval (I$_2$) & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
+        Post-teaching interval (I$_3$) & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
+        Interview interval (I$_4$) & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
+        End interval (I$_5$) & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
         \bottomrule

### 2024-10-29 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.tex
bla bla bla.. affiliations und so

@@
    \ead{christin.lotz@uni-leipzig.de} 
-    \author[Max Planck Institute for Evolutionary Anthropology]{Gregor
-Kachel%
+    \author[UoG, DZKJ]{Peer Keßler%
   %
   \fnref{3}}
-   \ead{gregor@example.com} 
-    \author[University of Greifswald]{Peer Keßler%
+   \ead{peer.kessler@uni-greifswald.de} 
+    \author[Leipzig University]{Gregor Kachel%
   %
   \fnref{4}}
-   \ead{peer.kessler@uni-greifswald.de} 
+   \ead{gregor.kachel@gmail.com} 
     \author[Leipzig University]{Anne Deiglmayr%
@@
       \affiliation[Leipzig University]{
-    organization={Division of Empirical School and Classroom Research,
-Institute of Educational Sciences},addressline={Marschnerstr.
+    organization={Leipzig University Division of Empirical School and
+Classroom Research, Institute of Educational
+Sciences},addressline={Marschnerstr.
 29},city={Leipzig},postcode={04109},country={Germany},}
-    \affiliation[Max Planck Institute for Evolutionary Anthropology]{
-    organization={Department},addressline={Deutscher Pl.
-6},city={Leipzig},postcode={04103},country={Germany},}
-    \affiliation[University of Greifswald]{
-    organization={Division of Health and Prevention, Institute of
-Psychology},addressline={Robert-Blum-Str.
+    \affiliation[UoG]{
+    organization={University of Greifswald, Division of Health and
+Prevention, Institute of Psychology},addressline={Robert-Blum-Str.
+13},city={Greifswald},postcode={17489},country={Germany},}
+    \affiliation[DZKJ]{
+    organization={German Center for Child and Adolescent Health
+(DZKJ)},addressline={Robert-Blum-Str.
 13},city={Greifswald},postcode={17489},country={Germany},}
@@
 Editing, Supervision}
-    \fntext[3]{Formal analysis, Data Curation, Writing - Review \&
+    \fntext[3]{Conceptualization, Methodology, Writing - Review \&
 Editing}
-    \fntext[4]{Conceptualization, Methodology, Writing - Review \&
+    \fntext[4]{Formal analysis, Data Curation, Writing - Review \&
 Editing}

### 2024-10-30 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
expertise added median

@@
             "SD Exp." = round(sd(`Teaching Experience`), 2),
+            "Median Exp." = round(median(`Teaching Experience`), 2),
             "Min Exp." = min(`Teaching Experience`),
@@
   geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
-  labs(title = "Boxplot of Average duration of fixations per minute",
-       y = "Average duration of fixations per minute") +
+  labs(title = "Boxplot of Average duration of fixations",
+       y = "Average duration of fixations in msec") +
   theme_minimal()

### 2024-10-30 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
Update expertise_2024_09_26_no_outlierdetection_MK.Rmd

--- 2024-10-18 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
@@
             "M Exp." = round(mean(`Teaching Experience`), 2),
+            "Median Exp." = round(median(`Teaching Experience`), 2),
             "SD Exp." = round(sd(`Teaching Experience`), 2),

### 2024-10-30 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
correlations added

@@
   filter(
-    !ID %in% c(201),
+    !ID %in% c(201, 223),
     !disruption_appraisal == -100,
@@
          SJT_KF_gek) %>% # All
-  filter(!UI06_05 == 201) # exclude ID with no eye tracking data
+  filter(!UI06_05 == 201,
+         !UI06_05 == 223) # exclude ID with no eye tracking data
 

### 2024-10-30 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
correlations added

@@
 
+### Prevalence Rating as Manipulation check 
 ```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 round(d_sri_preva, 2)
+
+```
+
+### Internal consistency (Omega) for disruption and confidence appraisal
+```{r sri_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# Select the relevant columns (e.g., Disruption Appraisal and Confidence Appraisal)
+sri <-
+  excel_sheets("data/Coding_SRI.xlsx") %>%
+  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+  filter(
+    !ID %in% c(201, 223),
+    !disruption_appraisal == -100,
+    !confidence_appraisal == -100,
+    !disruption_appraisal == -99,
+    !confidence_appraisal == -99,
+    !disruption_appraisal == -88,
+    !confidence_appraisal == -88,
+    !prevalence_rating == -100,
+    !prevalence_rating == -99,
+    !prevalence_rating == -88
+    )
+
+# change long to wide format
+sri_wide <- sri %>%
+  pivot_wider(names_from = event, 
+              values_from = c(disruption_appraisal, confidence_appraisal, prevalence_rating))
+
+### DISRUPTIONS APPRAISAL
+
+# create new data frame with only disruption items
+sri_wide_disrup <- sri_wide %>%
+  dplyr::select(starts_with("disruption_appraisal")) %>% 
+  drop_na()
+
+# calculate omega with omega() function  
+omega_disrup <- omega(sri_wide_disrup)
+
+# display the results 
+print(omega_disrup)
+
+### CONFIDENCE APPRAISAL
+
+# create new data frame with only confidence items
+sri_wide_confi <- sri_wide %>%
+  dplyr::select(starts_with("confidence_appraisal")) %>% 
+  drop_na()
+
+# calculate omega with omega() function  
+omega_confi <- omega(sri_wide_confi)
+
+# display the results 
+print(omega_confi)
 
@@
 
-# demo data 
-df_demo <- 
-  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
-  filter(!LI06_05 == 201,
-         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
-  transmute(Participant = LI06_05,
-            `Teaching Experience` = LI04_01,
-            )
-
-# average duration, number fixation, GRI (micro-teaching unit)
-df_aoi %>%
+# Define excluded IDs for easy updating
+excluded_ids <- c(201, 223)
+
+# 1. Demo Data
+df_demo <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  filter(!LI06_05 %in% excluded_ids) %>% # Exclude participants based on IDs
+  transmute(Participant = LI06_05, Teaching_Experience = LI04_01) %>%
+  arrange(Participant)
+
+# 2. Aggregate AOI Data (Micro-teaching Unit)
+df_aoi_numb_dur <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  dplyr::select(
+  select(
+    Participant,
     Duration_of_interval,
-    Participant,
     starts_with("Total_duration_of_fixations"),
     starts_with("Number_of_fixations"),
-    starts_with("Average_duration"),
-    !"Total_duration_of_fixations.Disruptive_Person",
-    !"Number_of_fixations.Disruptive_Person",
-    !"Average_duration_of_fixations.Disruptive_Person"
-  ) %>%
+    starts_with("Average_duration")
+  ) %>%
+  select(-ends_with("Disruptive_Person")) %>% # Exclude "Disruptive_Person" columns
+  mutate(Duration_of_interval_min = Duration_of_interval / 60000) %>%
   rowwise() %>%
-  transmute(
-    Participant = Participant,
-    Duration_of_interval = Duration_of_interval, 
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
+  summarize(
+    Participant,
     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
     Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
@@
   ) %>%
-  drop_na() %>% 
-  dplyr::select(Participant,
+  select(Participant,
          Number_fixation_min_mtu,
          Average_duration_mtu,
-         GRI_mtu) -> df_aoi_numb_dur
-
-# average duration, number fixation, GRI (AOI student)
-df_aoi %>%
+         GRI_mtu)
+
+# 3. Aggregate AOI Data (Students)
+df_aoi_stud <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  dplyr::select (
+  select(
     Participant,
     Duration_of_interval,
-    "Total_duration_of_fixations.Anna",
-    "Total_duration_of_fixations.Bianca",
-    "Total_duration_of_fixations.Carl(a)",
-    "Number_of_fixations.Anna",
-    "Number_of_fixations.Bianca",
-    "Number_of_fixations.Carl(a)"
-  ) %>%
+    starts_with("Total_duration_of_fixations."),
+    starts_with("Number_of_fixations.")
+  ) %>%
+  mutate(Duration_of_interval_min = Duration_of_interval / 60000) %>%
   rowwise() %>%
-  transmute(
-    Participant = Participant,
-    Duration_of_interval = Duration_of_interval,
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
+  summarize(
+    Participant,
     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
@@
     Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
-    GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2)
-    ) %>%
-  dplyr::select(Participant,
+    GRI_stud = round(Average_duration_stud / Stud_number_fixation_min, digits = 2)
+  ) %>%
+  select(Participant,
          Stud_number_fixation_min,
          Average_duration_stud,
-                GRI_stud) -> df_aoi_stud
-
-# average duration, number fixation, GRI (AOI disruptive person)
-df_aoi %>%
+         GRI_stud)
+
+# 4. Aggregate AOI Data (Disruptive Person)
+df_aoi_disrup <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  dplyr::select(Participant,
-                "Total_duration_of_fixations.Disruptive_Person",
-                "Number_of_fixations.Disruptive_Person"
-                ) %>%
-  rowwise() %>%
+  select(
+    Participant,
+    Total_duration_of_fixations.Disruptive_Person,
+    Number_of_fixations.Disruptive_Person
+  ) %>%
   mutate(
@@
       Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person,
-      digits = 0),
+      digits = 0
+    ),
     GRI_disrup = round(
-      Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2)) %>%
-  dplyr::select(Participant,
+      Average_duration_disrup / Number_of_fixations.Disruptive_Person,
+      digits = 2
+    )
+  ) %>%
+  select(
+    Participant,
     Number_of_fixations.Disruptive_Person,
@@
     GRI_disrup
-                ) -> df_aoi_disrup
-
-df_aoi %>% 
-  filter(TOI %in% c("Chatting_with_neighbour",
+  )
+
+# 5. Time to First Fixation on Disruptive Person
+df_ttff_disrup <- df_aoi %>%
+  filter(
+    TOI %in% c(
+      "Chatting_with_neighbour",
       "Clicking_pen",
@@
   ) %>%
-  dplyr::select(Participant,
-                TOI,
-                Time_to_first_fixation.Disruptive_Person,
-                ) %>% 
-  rowwise() %>% 
-  drop_na() %>% 
+  select(Participant, TOI, Time_to_first_fixation.Disruptive_Person) %>%
+  filter(
+    !is.na(Time_to_first_fixation.Disruptive_Person) &
+      Time_to_first_fixation.Disruptive_Person > 0 &
+      Time_to_first_fixation.Disruptive_Person <= 30000
+  ) %>%
   group_by(Participant) %>%
-  filter(!Time_to_first_fixation.Disruptive_Person == 0, # exclude all participants with 0 msec
-         !Time_to_first_fixation.Disruptive_Person > 30000) %>% # cut-off 30sec
-  summarise(N = n(),
-            Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person/N)
-            ) %>% 
-  mutate(Group = ifelse(Participant < 200, "Novice", "Expert"),
+  summarize(
+    N = n(),
+    Time_to_first_fixation_Disruptive_Person_Sum = mean(Time_to_first_fixation.Disruptive_Person),
+    Group = ifelse(Participant < 200, "Novice", "Expert"),
     Sum_disruptions = sum(N),
-         Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000, 
-                                          digits = 2)) -> df_ttff_disrup # changing milliseconds into seconds
-
-# rating scales
-df_sri <-
-  excel_sheets("data/Coding_SRI.xlsx") %>%
-  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+    Disrup_time_fixation_sec = round(Time_to_first_fixation_Disruptive_Person_Sum / 1000, 2)
+  )
+
+# 6. Rating Scales
+df_sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
+  map_df( ~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
   filter(
-    !ID %in% c(201,
-               223),
-    !disruption_appraisal == -100,
-    !confidence_appraisal == -100,
-    !disruption_appraisal == -99,
-    !confidence_appraisal == -99,
-    !disruption_appraisal == -88,
-    !confidence_appraisal == -88,
-    !prevalence_rating == -100,
-    !prevalence_rating == -99,
-    !prevalence_rating == -88
+    !ID %in% excluded_ids,
+    !disruption_appraisal %in% c(-100, -99, -88),
+    !confidence_appraisal %in% c(-100, -99, -88),
+    !prevalence_rating %in% c(-100, -99, -88)
   ) %>%
@@
   group_by(Participant) %>%
-  summarise(
-    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
+  summarize(
+    Mean_disruption_appraisal = round(mean(disruption_appraisal), 2),
     Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
     Mean_prevalence_rating = round(mean(prevalence_rating), 2)
-    )%>% 
-  dplyr::select(Participant,
-                Mean_disrupption_appraisal,
-                Mean_confidence_appraisal)
-
-# sjt
-df_sjt <-
-  read_excel("./data/SJT.xlsx") %>%
-  dplyr::select(UI06_05, # Participant
-                SJT_AL_gek, # Monitoring
-                SJT_ST_gek, # Managing momentum
-                SJT_R_gek, # Rules and routines
-                SJT_KF_gek) %>% # All
-  filter(!UI06_05 %in% c(201, 223)) %>%  # exclude ID with no eye tracking data
+  )
+
+# 7. Situational Judgment Test (SJT) Data
+df_sjt <- read_excel("./data/SJT.xlsx") %>%
+  filter(!UI06_05 %in% excluded_ids) %>%
   transmute(
@@
     SJT_Monitoring = round(SJT_AL_gek, 2),
-    SJT_All = round(SJT_KF_gek, 2),
-  ) %>%
-  arrange(Participant)
-
-# classroom questionnaire
+    SJT_All = round(SJT_KF_gek, 2)
+  )
+
+# 8. Classroom Questionnaire
 df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
@@
                 LP01_01:LP01_08) %>% # non- & paraverbal communication
-  filter(!LI06_05 %in% c(201, 223)) %>% # exclude ID with no eye tracking data
+  filter(!LI06_05 %in% excluded_ids) %>% # exclude ID with no eye tracking data
   rename(Participant = LI06_05) %>%
@@
 
-# create a big data frame with all measures 
-# put all data frames into list
-df_list <- list(df_demo,
+# 9. Combine All Data Frames into a Single Data Frame
+df_list <- list(
+  df_demo,
   df_aoi_numb_dur,
@@
   df_sjt,
-                df_quest)
-
-# merge all data frames in list
-df_merge <-
-  df_list %>% reduce(full_join, by='Participant') %>%
-  # filter(`Teaching Experience` > 0) %>% 
-  dplyr::select(Stud_number_fixation_min,
-                Average_duration_stud,
-                Number_of_fixations.Disruptive_Person,
-                Average_duration_disrup,
-                Disrup_time_fixation_sec,
+  df_quest
+)
+
+df_merge <- df_list %>%
+  reduce(full_join, by = "Participant") %>%
+  select(
+    Participant,
+    Teaching_Experience,
     GRI_mtu,
     SJT_All,
-                SJT_Monitoring,
-                Quest_All
-                )
+    Quest_All,
+    Mean_disruption_appraisal,
+    Mean_confidence_appraisal
+  ) %>%
+  drop_na()  # Drop rows with any NA values (if needed)
+
+# Display the merged dataframe (optional)
+print(df_merge)
 
@@
 
-### Teaching experience with only experts
+### Only experts
 # merge all data frames in list
 df_merge_experts <-
-  df_list %>% reduce(full_join, by='Participant') %>%
-  filter(`Teaching Experience` > 0) %>% 
-  dplyr::select(`Teaching Experience`,
-                Stud_number_fixation_min,
-                Average_duration_stud,
-                Number_of_fixations.Disruptive_Person,
-                Average_duration_disrup,
-                Disrup_time_fixation_sec,
+df_merge %>% 
+  filter(Teaching_Experience > 0) %>% 
+  dplyr::select(
+    Participant,
+    Teaching_Experience,
     GRI_mtu,
     SJT_All,
-                SJT_Monitoring,
-                Quest_All
-                )
+    Quest_All,
+    Mean_disruption_appraisal,
+    Mean_confidence_appraisal
+  ) %>%
+  drop_na()  # Drop rows with any NA values (if needed)
 
@@
 
+### Only novices
+# merge all data frames in list
+df_merge_novice <-
+df_merge %>% 
+  filter(Teaching_Experience == 0) %>% 
+  dplyr::select(
+    Participant,
+    Teaching_Experience,
+    GRI_mtu,
+    SJT_All,
+    Quest_All,
+    Mean_disruption_appraisal,
+    Mean_confidence_appraisal
+  ) %>%
+  drop_na()  # Drop rows with any NA values (if needed)
+
+# create a correlation matrix
+cor_tab_novices <- 
+  df_merge_novice %>% 
+  cor(method = "pearson") %>% 
+  round(., digits = 2)
+
 # p-value for GRI x STJ_All
-cor.test(df_merge$GRI_mtu, df_merge$SJT_All)
-
-# p-value for GRI x STJ_Monitoring
-cor.test(df_merge$GRI_mtu, df_merge$SJT_Monitoring)
+cor.test(df_merge_novice$GRI_mtu, df_merge_novice$SJT_All)
+
+# p-value for GRI x Rating
+cor.test(df_merge_novice$Quest_All, df_merge_novice$Mean_confidence_appraisal)
 

### 2024-10-31 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x paper omega added

@@
 ---
-title: "Through the eyes of the teacher - Multimodal exploration of expertise differences
-  in the perception of classroom disruptions in a laboratory study"
+title: "Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study"
 output: 
-  html_document:
-    df_print: paged
-  pdf_document: default
+  pdf_document:
+    toc: true           # Add a table of contents
+    number_sections: true
+    latex_engine: xelatex  # Specify LaTeX engine if needed
+    keep_tex: true      # Keep .tex file for debugging or customization
 ---
@@
 
+# ```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+# 
+# ############## Prevalence Rating #########################
+# 
+# sri.preva.table <-
+#   sri %>%
+#   group_by(ID) %>%
+#   summarise(
+#     N = n(),
+#     "M" = round(mean(prevalence_rating), digits = 2),
+#     "SD" = round(sd(prevalence_rating), digits = 2),
+#     "Min" = min(prevalence_rating),
+#     "Max" = max(prevalence_rating)
+#   )
+# 
+# # insert a table into HTML
+# knitr::kable(sri.preva.table,
+#              caption = "Prevalence rating")
+# 
+# #### with event 
+# sri.preva.event.table <-
+#   sri %>%
+#   group_by(ID, event) %>%
+#   summarise(
+#     N = n(),
+#     "M" = round(mean(prevalence_rating), digits = 2),
+#     "SD" = round(sd(prevalence_rating), digits = 2),
+#     "Min" = min(prevalence_rating),
+#     "Max" = max(prevalence_rating)
+#   )
+# 
+# # insert a table into HTML
+# knitr::kable(sri.preva.event.table,
+#              caption = "Prevalence rating with events")
+# 
+# # create a new data frame with rating
+# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
+# 
+# # plotting prevalence rating for groups
+# preva_group_plot <- 
+#   sri_preva %>% 
+#   mutate(ID = factor(ID,
+#                      levels = c("Novice",
+#                                 "Expert"
+#                                 )
+#                      )
+#          ) %>% 
+#   ggplot(mapping = aes(x = ID,
+#                        y = prevalence_rating)) +
+#   geom_boxplot(mapping = aes(fill = ID),
+#                outlier.shape = NA) +
+#   geom_point(size = 1,
+#              alpha = 0.4,
+#              position = position_jitter(seed = 1,
+#                                         width = 0.1,
+#                                         height = 0.1)) +
+#   scale_x_discrete(limits = c("Novice", "Expert")) +
+#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
+#   labs(x = "",
+#        y = "Prevalence Rating") + 
+#   scale_fill_brewer(palette  = "RdBu") +  
+#   ggtitle("How widespread is this event in the classroom?") +
+#   theme_cowplot()
+# 
+# preva_group_plot
+# 
+# ```
+
+#### t-Test & effect size "Prevalence rating"
+# ```{r sri_pr_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+# 
+# #################### T-TEST & EFFECT SIZE ############
+# 
+# # Prevalence Rating 
+# # t-test for expertise differences
+# t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
+#        y = sri$prevalence_rating[sri$ID == "Novice"],
+#        var.equal = TRUE)
+# 
+# # Prevalence Rating 
+# # effect size for expertise differences
+# d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
+#                       y = sri$prevalence_rating[sri$ID == "Novice"],
+#                       na.rm = TRUE)
+# 
+# round(d_sri_preva, 2)
+# 
+# ```
+
+### Internal consistency (Omega) for disruption and confidence appraisal
+```{r sri_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# Select the relevant columns (e.g., Disruption Appraisal and Confidence Appraisal)
+sri <-
+  excel_sheets("data/Coding_SRI.xlsx") %>%
+  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+  filter(
+    !ID %in% c(201),
+    !disruption_appraisal == -100,
+    !confidence_appraisal == -100,
+    !disruption_appraisal == -99,
+    !confidence_appraisal == -99,
+    !disruption_appraisal == -88,
+    !confidence_appraisal == -88,
+    !prevalence_rating == -100,
+    !prevalence_rating == -99,
+    !prevalence_rating == -88
+    )
+
+# change long to wide format
+sri_wide <- sri %>%
+  pivot_wider(names_from = event, 
+              values_from = c(disruption_appraisal, confidence_appraisal, prevalence_rating))
+
+### DISRUPTIONS APPRAISAL
+
+# create new data frame with only disruption items
+sri_wide_disrup <- sri_wide %>%
+  dplyr::select(starts_with("disruption_appraisal")) %>% 
+  drop_na()
+
+# calculate omega with omega() function  
+omega_disrup <- omega(sri_wide_disrup)
+
+# display the results 
+print(omega_disrup)
+
+### CONFIDENCE APPRAISAL
+
+# create new data frame with only confidence items
+sri_wide_confi <- sri_wide %>%
+  dplyr::select(starts_with("confidence_appraisal")) %>% 
+  drop_na()
+
+# calculate omega with omega() function  
+omega_confi <- omega(sri_wide_confi)
+
+# display the results 
+print(omega_confi)
+
+```
+
+### Prevalence Rating as manipulation check
 ```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-############## Prevalence Rating #########################
-
-sri.preva.table <-
-  sri %>%
-  group_by(ID) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(prevalence_rating), digits = 2),
-    "SD" = round(sd(prevalence_rating), digits = 2),
-    "Min" = min(prevalence_rating),
-    "Max" = max(prevalence_rating)
-  )
-
-# insert a table into HTML
-knitr::kable(sri.preva.table,
-             caption = "Prevalence rating")
-
-#### with event 
-sri.preva.event.table <-
-  sri %>%
-  group_by(ID, event) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(prevalence_rating), digits = 2),
-    "SD" = round(sd(prevalence_rating), digits = 2),
-    "Min" = min(prevalence_rating),
-    "Max" = max(prevalence_rating)
-  )
-
-# insert a table into HTML
-knitr::kable(sri.preva.event.table,
-             caption = "Prevalence rating with events")
-
-# create a new data frame with rating
-sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
-
-# plotting prevalence rating for groups
-preva_group_plot <- 
-  sri_preva %>% 
-  mutate(ID = factor(ID,
-                     levels = c("Novice",
-                                "Expert"
-                                )
-                     )
-         ) %>% 
-  ggplot(mapping = aes(x = ID,
-                       y = prevalence_rating)) +
-  geom_boxplot(mapping = aes(fill = ID),
-               outlier.shape = NA) +
-  geom_point(size = 1,
-             alpha = 0.4,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  scale_x_discrete(limits = c("Novice", "Expert")) +
-  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
-  labs(x = "",
-       y = "Prevalence Rating") + 
-  scale_fill_brewer(palette  = "RdBu") +  
-  ggtitle("How widespread is this event in the classroom?") +
-  theme_cowplot()
-
-preva_group_plot
-
-```
-
-#### t-Test & effect size "Prevalence rating"
-```{r sri_pr_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-#################### T-TEST & EFFECT SIZE ############
-
-# Prevalence Rating 
-# t-test for expertise differences
-t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
-       y = sri$prevalence_rating[sri$ID == "Novice"],
-       var.equal = TRUE)
-
-# Prevalence Rating 
-# effect size for expertise differences
-d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
-                      y = sri$prevalence_rating[sri$ID == "Novice"],
-                      na.rm = TRUE)
-
-round(d_sri_preva, 2)
+# 
+# ############## Prevalence Rating as manipulation check #########################
+# 
+# sri.preva.table <-
+#   sri %>%
+#   group_by(ID) %>%
+#   summarise(
+#     N = n(),
+#     "M" = round(mean(prevalence_rating), digits = 2),
+#     "SD" = round(sd(prevalence_rating), digits = 2),
+#     "Min" = min(prevalence_rating),
+#     "Max" = max(prevalence_rating)
+#   )
+# 
+# # insert a table into HTML
+# knitr::kable(sri.preva.table,
+#              caption = "Prevalence rating")
+# 
+# #### with event 
+# sri.preva.event.table <-
+#   sri %>%
+#   group_by(ID, event) %>%
+#   summarise(
+#     N = n(),
+#     "M" = round(mean(prevalence_rating), digits = 2),
+#     "SD" = round(sd(prevalence_rating), digits = 2),
+#     "Min" = min(prevalence_rating),
+#     "Max" = max(prevalence_rating)
+#   )
+# 
+# # insert a table into HTML
+# knitr::kable(sri.preva.event.table,
+#              caption = "Prevalence rating with events")
+# 
+# # create a new data frame with rating
+# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
+# 
+# # plotting prevalence rating for groups
+# preva_group_plot <- 
+#   sri_preva %>% 
+#   mutate(ID = factor(ID,
+#                      levels = c("Novice",
+#                                 "Expert"
+#                                 )
+#                      )
+#          ) %>% 
+#   ggplot(mapping = aes(x = ID,
+#                        y = prevalence_rating)) +
+#   geom_boxplot(mapping = aes(fill = ID),
+#                outlier.shape = NA) +
+#   geom_point(size = 1,
+#              alpha = 0.4,
+#              position = position_jitter(seed = 1,
+#                                         width = 0.1,
+#                                         height = 0.1)) +
+#   scale_x_discrete(limits = c("Novice", "Expert")) +
+#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
+#   labs(x = "",
+#        y = "Prevalence Rating") + 
+#   scale_fill_brewer(palette  = "RdBu") +  
+#   ggtitle("How widespread is this event in the classroom?") +
+#   theme_cowplot()
+# 
+# preva_group_plot
 

### 2024-10-31 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.tex
x paper omega added

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Through the eyes of the teacher - Multimodal exploration of
expertise differences in the perception of classroom disruptions in a
laboratory study}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\subsection{1. Participants}\label{participants}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0560}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0240}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.1360}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.1200}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.1280}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.1360}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.1360}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0560}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0640}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0720}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0720}}@{}}
\caption{Demographic information \& teaching experience}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Group
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
N
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Women in percent
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
M Age in years
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
SD Age in years
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Min Age in years
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Max Age in years
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
M Exp.
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
SD Exp.
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Min Exp.
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Max Exp.
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Group
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
N
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Women in percent
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
M Age in years
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
SD Age in years
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Min Age in years
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Max Age in years
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
M Exp.
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
SD Exp.
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Min Exp.
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Max Exp.
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 40 & 60.00 & 39.10 & 10.55 & 26 & 60 & 11.55 & 11.32 & 1 &
38 \\
Novice & 42 & 69.05 & 22.83 & 1.85 & 19 & 27 & 0.00 & 0.00 & 0 & 0 \\
\end{longtable}

\subsection{2. Measures}\label{measures}

\subsubsection{2.1 Eye-Tracking Data}\label{eye-tracking-data}

\paragraph{2.2.2 Letter search}\label{letter-search}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max letter search in seconds}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 39 & 12.97 & 6.75 & 2.72 & 29.24 \\
Novice & 40 & 12.22 & 8.79 & 2.28 & 48.26 \\
\end{longtable}

\paragraph{t-test \& effect size ``Letter
search''}\label{t-test-effect-size-letter-search}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_letter\(Duration_of_interval_sec[df_letter\)Group ==
``Expert''{]} and df\_letter\(Duration_of_interval_sec[df_letter\)Group
== ``Novice''{]} t = 0.42858, df = 77, p-value = 0.6694 alternative
hypothesis: true difference in means is not equal to 0 95 percent
confidence interval: -2.760420 4.274574 sample estimates: mean of x mean
of y 12.97308 12.21600

{[}1{]} 0.1 attr(,``magnitude'') {[}1{]} ``negligible''

\paragraph{2.2.1 Number of fixations per minute (micro-teaching
unit)}\label{number-of-fixations-per-minute-micro-teaching-unit}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max number of fixation per minute
(micro-teaching unit)}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Novice & 42 & 91.26 & 14.43 & 69 & 123 \\
Expert & 40 & 98.58 & 19.04 & 49 & 136 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/nof_all-1.pdf}

\paragraph{t-test \& effect size ``Number of fixation (micro-teaching
unit)''}\label{t-test-effect-size-number-of-fixation-micro-teaching-unit}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_aoi\_sum\(Number_fixation_min_mtu[df_aoi_sum\)Group ==
``Expert''{]} and
df\_aoi\_sum\(Number_fixation_min_mtu[df_aoi_sum\)Group == ``Novice''{]}
t = 1.966, df = 80, p-value = 0.05276 alternative hypothesis: true
difference in means is not equal to 0 95 percent confidence interval:
-0.08935625 14.71554673 sample estimates: mean of x mean of y 98.5750
91.2619

{[}1{]} 0.43 attr(,``magnitude'') {[}1{]} ``small''

\paragraph{2.2.2 Number of fixations per minute (AOI
students)}\label{number-of-fixations-per-minute-aoi-students}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max number of fixations per minute (AOI
students)}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Novice & 42 & 40.08 & 11.58 & 16.91 & 61.53 \\
Expert & 40 & 43.26 & 12.55 & 25.06 & 74.31 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/nof_students-1.pdf}

\paragraph{t-test \& effect size ``Number of fixation'' (AOI
students)}\label{t-test-effect-size-number-of-fixation-aoi-students}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_aoi\_stud\(Stud_number_fixation_min[df_aoi_stud\)Group ==
``Expert''{]} and
df\_aoi\_stud\(Stud_number_fixation_min[df_aoi_stud\)Group ==
``Novice''{]} t = 1.1925, df = 80, p-value = 0.2366 alternative
hypothesis: true difference in means is not equal to 0 95 percent
confidence interval: -2.125346 8.480489 sample estimates: mean of x mean
of y 43.25900 40.08143

{[}1{]} 0.26 attr(,``magnitude'') {[}1{]} ``small''

\paragraph{2.2.3 Number of fixations (AOI disruptive
person)}\label{number-of-fixations-aoi-disruptive-person}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max number of fixation (AOI disruptive
person)}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Novice & 42 & 48.14 & 21.87 & 25 & 133 \\
Expert & 40 & 44.12 & 13.31 & 15 & 88 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/nof_disrup-1.pdf}

\paragraph{t-test \& effect size ``Number of fixations'' (AOI disruptive
person)}\label{t-test-effect-size-number-of-fixations-aoi-disruptive-person}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data:
df\_aoi\_disrup\(Number_of_fixations.Disruptive_Person[df_aoi_disrup\)Group
== ``Expert''{]} and
df\_aoi\_disrup\(Number_of_fixations.Disruptive_Person[df_aoi_disrup\)Group
== ``Novice''{]} t = -0.99886, df = 80, p-value = 0.3209 alternative
hypothesis: true difference in means is not equal to 0 95 percent
confidence interval: -12.022778 3.987063 sample estimates: mean of x
mean of y 44.12500 48.14286

{[}1{]} -0.22 attr(,``magnitude'') {[}1{]} ``small''

\paragraph{2.2.4 Average duration of fixations in milliseconds
(micro-teaching
unit)}\label{average-duration-of-fixations-in-milliseconds-micro-teaching-unit}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max duration of fixations in milliseconds
(micro-teaching unit)}\tabularnewline
\toprule\noalign{}
Group & N & M in ms & SD in ms & Min in ms & Max in ms \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M in ms & SD in ms & Min in ms & Max in ms \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Novice & 42 & 513.81 & 117.71 & 247 & 749 \\
Expert & 40 & 472.92 & 106.18 & 295 & 712 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/dur_all-1.pdf}

\paragraph{t-test \& effect size ``Average duration of fixations''
(micro-teaching
unit)}\label{t-test-effect-size-average-duration-of-fixations-micro-teaching-unit}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_aoi\_sum\(Average_duration_mtu[df_aoi_sum\)Group ==
``Expert''{]} and df\_aoi\_sum\(Average_duration_mtu[df_aoi_sum\)Group
== ``Novice''{]} t = -1.6488, df = 80, p-value = 0.1031 alternative
hypothesis: true difference in means is not equal to 0 95 percent
confidence interval: -90.231822 8.462774 sample estimates: mean of x
mean of y 472.9250 513.8095

{[}1{]} -0.36 attr(,``magnitude'') {[}1{]} ``small''

\paragraph{2.2.5 Average duration of fixations (AOI
students)}\label{average-duration-of-fixations-aoi-students}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max average duration of fixations in
milliseconds (AOI students)}\tabularnewline
\toprule\noalign{}
Group & N & M in ms & SD in ms & Min in ms & Max in ms \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M in ms & SD in ms & Min in ms & Max in ms \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Novice & 42 & 613.67 & 191.19 & 254 & 1115 \\
Expert & 40 & 552.55 & 146.32 & 309 & 925 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/dur_students-1.pdf}

\paragraph{t-test \& effect size ``Average duration of fixations'' (AOI
students)}\label{t-test-effect-size-average-duration-of-fixations-aoi-students}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_aoi\_stud\(Average_duration_stud[df_aoi_stud\)Group ==
``Expert''{]} and
df\_aoi\_stud\(Average_duration_stud[df_aoi_stud\)Group == ``Novice''{]}
t = -1.6197, df = 80, p-value = 0.1092 alternative hypothesis: true
difference in means is not equal to 0 95 percent confidence interval:
-136.20902 13.97569 sample estimates: mean of x mean of y 552.5500
613.6667

{[}1{]} -0.36 attr(,``magnitude'') {[}1{]} ``small''

\paragraph{2.2.6 Average duration of fixations (AOI disruptive
person)}\label{average-duration-of-fixations-aoi-disruptive-person}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max average duration of fixations in
milliseconds (AOI disruptive person)}\tabularnewline
\toprule\noalign{}
Group & N & M in ms & SD in ms & Min in ms & Max in ms \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M in ms & SD in ms & Min in ms & Max in ms \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Novice & 42 & 584.57 & 216.40 & 266 & 1150 \\
Expert & 40 & 503.05 & 153.92 & 303 & 1081 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/dur_disrup-1.pdf}

\paragraph{t-test \& effect size ``Average duration of fixations'' (AOI
disruptive
person)}\label{t-test-effect-size-average-duration-of-fixations-aoi-disruptive-person}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_aoi\_disrup\(Average_duration_disrup[df_aoi_disrup\)Group ==
``Expert''{]} and
df\_aoi\_disrup\(Average_duration_disrup[df_aoi_disrup\)Group ==
``Novice''{]} t = -1.957, df = 80, p-value = 0.05383 alternative
hypothesis: true difference in means is not equal to 0 95 percent
confidence interval: -164.418963 1.376106 sample estimates: mean of x
mean of y 503.0500 584.5714

{[}1{]} -0.43 attr(,``magnitude'') {[}1{]} ``small''

\paragraph{2.2.7 Gaze Relational Index (GRI; micro-teaching
unit)}\label{gaze-relational-index-gri-micro-teaching-unit}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max GRI (micro-teaching unit)}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Novice & 42 & 5.93 & 2.11 & 2.08 & 10.70 \\
Expert & 40 & 5.18 & 2.13 & 2.17 & 11.48 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/gri_all-1.pdf}

\paragraph{t-test \& effect size ``GRI'' (micro-teaching
unit)}\label{t-test-effect-size-gri-micro-teaching-unit}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_gri\(GRI[df_gri\)Group == ``Expert''{]} and
df\_gri\(GRI[df_gri\)Group == ``Novice''{]} t = -1.5975, df = 80,
p-value = 0.1141 alternative hypothesis: true difference in means is not
equal to 0 95 percent confidence interval: -1.682021 0.184045 sample
estimates: mean of x mean of y 5.176250 5.925238

{[}1{]} -0.35 attr(,``magnitude'') {[}1{]} ``small''

\paragraph{2.2.10 Time to first fixation in seconds (AOI disruptive
person)}\label{time-to-first-fixation-in-seconds-aoi-disruptive-person}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M, SD, min \& max time to first fixation in seconds (AOI
disruptive person)}\tabularnewline
\toprule\noalign{}
Group & N & M in sec & SD in sec & Min in sec & Max in sec \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M in sec & SD in sec & Min in sec & Max in sec \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 39 & 3.57 & 2.18 & 0.25 & 8.78 \\
Novice & 40 & 3.79 & 1.80 & 0.72 & 8.89 \\
\end{longtable}

\begin{longtable}[]{@{}lrrrr@{}}
\caption{N, M, SD, min \& max of the perceived ´disruptive
person´}\tabularnewline
\toprule\noalign{}
Group & Mean & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & Mean & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 6.82 & 1.60 & 4 & 9 \\
Novice & 6.90 & 1.43 & 3 & 9 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/ttff_disrup-1.pdf}
\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/ttff_disrup-2.pdf}

\paragraph{t-test \& effect size ``Time to first fixation'' (AOI
disruptive
person)}\label{t-test-effect-size-time-to-first-fixation-aoi-disruptive-person}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_ttff\_disrup\(Disrup_time_fixation_sec[df_ttff_disrup\)Group
== ``Expert''{]} and
df\_ttff\_disrup\(Disrup_time_fixation_sec[df_ttff_disrup\)Group ==
``Novice''{]} t = -0.67144, df = 80, p-value = 0.5039 alternative
hypothesis: true difference in means is not equal to 0 95 percent
confidence interval: -1.4276630 0.7073296 sample estimates: mean of x
mean of y 3.766500 4.126667

{[}1{]} -0.15 attr(,``magnitude'') {[}1{]} ``negligible''

\subsubsection{2.2 Rating Scales (Disruption Appraisal, Confidence
Appraisal, Prevalence
Rating)}\label{rating-scales-disruption-appraisal-confidence-appraisal-prevalence-rating}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{Disruption Appraisal}\tabularnewline
\toprule\noalign{}
ID & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
ID & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 352 & 4.84 & 2.90 & 0 & 10 \\
Novice & 357 & 5.55 & 2.81 & 0 & 10 \\
\end{longtable}

\begin{longtable}[]{@{}llrrrrr@{}}
\caption{Disruption appraisal with event}\tabularnewline
\toprule\noalign{}
ID & event & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
ID & event & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & chatting & 41 & 6.78 & 2.53 & 1 & 10 \\
Expert & clicking pen & 38 & 5.34 & 2.60 & 0 & 10 \\
Expert & drawing & 35 & 1.80 & 1.89 & 0 & 7 \\
Expert & drumming & 39 & 4.95 & 2.45 & 1 & 10 \\
Expert & head on table & 40 & 4.12 & 2.56 & 0 & 10 \\
Expert & heckling & 41 & 6.29 & 2.69 & 2 & 10 \\
Expert & looking at phone & 36 & 4.94 & 2.89 & 0 & 10 \\
Expert & snipping & 41 & 3.85 & 3.08 & 0 & 10 \\
Expert & whispering & 41 & 5.07 & 2.46 & 0 & 9 \\
Novice & chatting & 42 & 8.12 & 2.04 & 0 & 10 \\
Novice & clicking pen & 40 & 6.28 & 2.51 & 0 & 10 \\
Novice & drawing & 35 & 2.14 & 1.48 & 0 & 5 \\
Novice & drumming & 40 & 6.47 & 2.08 & 0 & 10 \\
Novice & head on table & 40 & 4.15 & 1.81 & 1 & 8 \\
Novice & heckling & 41 & 6.98 & 2.62 & 2 & 10 \\
Novice & looking at phone & 35 & 4.14 & 2.00 & 0 & 8 \\
Novice & snipping & 42 & 4.38 & 2.92 & 0 & 9 \\
Novice & whispering & 42 & 6.55 & 2.19 & 1 & 10 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/rating_scales-1.pdf}

\paragraph{t-Test \& effect size ``Disruption
appraisal''}\label{t-test-effect-size-disruption-appraisal}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: sri\(disruption_appraisal[sri\)ID == ``Expert''{]} and
sri\(disruption_appraisal[sri\)ID == ``Novice''{]} t = -3.3143, df =
707, p-value = 0.0009655 alternative hypothesis: true difference in
means is not equal to 0 95 percent confidence interval: -1.1320397
-0.2897835 sample estimates: mean of x mean of y 4.840909 5.551821

{[}1{]} -0.25 attr(,``magnitude'') {[}1{]} ``small''

\begin{longtable}[]{@{}lrrrr@{}}
\caption{Confidence appraisal}\tabularnewline
\toprule\noalign{}
ID & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
ID & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 8.42 & 1.70 & 2 & 10 \\
Novice & 7.18 & 2.04 & 0 & 10 \\
\end{longtable}

\begin{longtable}[]{@{}llrrrrr@{}}
\caption{Confidence appraisal with event}\tabularnewline
\toprule\noalign{}
ID & event & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
ID & event & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & chatting & 41 & 8.10 & 1.76 & 2 & 10 \\
Expert & clicking pen & 38 & 8.50 & 1.25 & 5 & 10 \\
Expert & drawing & 35 & 9.23 & 1.00 & 5 & 10 \\
Expert & drumming & 39 & 8.74 & 1.21 & 6 & 10 \\
Expert & head on table & 40 & 8.72 & 1.22 & 5 & 10 \\
Expert & heckling & 41 & 6.78 & 2.41 & 2 & 10 \\
Expert & looking at phone & 36 & 8.75 & 1.44 & 4 & 10 \\
Expert & snipping & 41 & 8.83 & 1.60 & 4 & 10 \\
Expert & whispering & 41 & 8.32 & 1.71 & 3 & 10 \\
Novice & chatting & 42 & 6.69 & 1.97 & 0 & 10 \\
Novice & clicking pen & 40 & 7.40 & 1.72 & 3 & 10 \\
Novice & drawing & 35 & 8.63 & 1.29 & 5 & 10 \\
Novice & drumming & 40 & 7.32 & 2.12 & 1 & 10 \\
Novice & head on table & 40 & 7.03 & 1.78 & 3 & 10 \\
Novice & heckling & 41 & 5.41 & 2.55 & 1 & 10 \\
Novice & looking at phone & 35 & 7.34 & 1.59 & 3 & 10 \\
Novice & snipping & 42 & 8.02 & 1.63 & 3 & 10 \\
Novice & whispering & 42 & 7.05 & 1.91 & 2 & 10 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/sri_ca-1.pdf}

\paragraph{t-Test \& effect size ``Confidence
appraisal''}\label{t-test-effect-size-confidence-appraisal}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: sri\(confidence_appraisal[sri\)ID == ``Expert''{]} and
sri\(confidence_appraisal[sri\)ID == ``Novice''{]} t = 8.766, df = 707,
p-value \textless{} 2.2e-16 alternative hypothesis: true difference in
means is not equal to 0 95 percent confidence interval: 0.9588466
1.5123145 sample estimates: mean of x mean of y 8.420455 7.184874

{[}1{]} 0.66 attr(,``magnitude'') {[}1{]} ``medium''

\section{\texorpdfstring{\texttt{\{r\ sri\_pr,\ echo=FALSE,\ message=FALSE,\ warning=FALSE,\ results=\textquotesingle{}asis\textquotesingle{}\}\ \#\ \ \#\ \#\#\#\#\#\#\#\#\#\#\#\#\#\#\ Prevalence\ Rating\ \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\ \#\ \ \#\ sri.preva.table\ \textless{}-\ \#\ \ \ sri\ \%\textgreater{}\%\ \#\ \ \ group\_by(ID)\ \%\textgreater{}\%\ \#\ \ \ summarise(\ \#\ \ \ \ \ N\ =\ n(),\ \#\ \ \ \ \ "M"\ =\ round(mean(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "SD"\ =\ round(sd(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "Min"\ =\ min(prevalence\_rating),\ \#\ \ \ \ \ "Max"\ =\ max(prevalence\_rating)\ \#\ \ \ )\ \#\ \ \#\ \#\ insert\ a\ table\ into\ HTML\ \#\ knitr::kable(sri.preva.table,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ caption\ =\ "Prevalence\ rating")\ \#\ \ \#\ \#\#\#\#\ with\ event\ \ \#\ sri.preva.event.table\ \textless{}-\ \#\ \ \ sri\ \%\textgreater{}\%\ \#\ \ \ group\_by(ID,\ event)\ \%\textgreater{}\%\ \#\ \ \ summarise(\ \#\ \ \ \ \ N\ =\ n(),\ \#\ \ \ \ \ "M"\ =\ round(mean(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "SD"\ =\ round(sd(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "Min"\ =\ min(prevalence\_rating),\ \#\ \ \ \ \ "Max"\ =\ max(prevalence\_rating)\ \#\ \ \ )\ \#\ \ \#\ \#\ insert\ a\ table\ into\ HTML\ \#\ knitr::kable(sri.preva.event.table,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ caption\ =\ "Prevalence\ rating\ with\ events")\ \#\ \ \#\ \#\ create\ a\ new\ data\ frame\ with\ rating\ \#\ sri\_preva\ \textless{}-\ subset.data.frame(sri,\ select\ =\ c(ID,\ event,\ prevalence\_rating))\ \#\ \ \#\ \#\ plotting\ prevalence\ rating\ for\ groups\ \#\ preva\_group\_plot\ \textless{}-\ \ \#\ \ \ sri\_preva\ \%\textgreater{}\%\ \ \#\ \ \ mutate(ID\ =\ factor(ID,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ levels\ =\ c("Novice",\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ "Expert"\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ )\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ )\ \#\ \ \ \ \ \ \ \ \ \ )\ \%\textgreater{}\%\ \ \#\ \ \ ggplot(mapping\ =\ aes(x\ =\ ID,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ =\ prevalence\_rating))\ +\ \#\ \ \ geom\_boxplot(mapping\ =\ aes(fill\ =\ ID),\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ outlier.shape\ =\ NA)\ +\ \#\ \ \ geom\_point(size\ =\ 1,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ alpha\ =\ 0.4,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ position\ =\ position\_jitter(seed\ =\ 1,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ width\ =\ 0.1,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ height\ =\ 0.1))\ +\ \#\ \ \ scale\_x\_discrete(limits\ =\ c("Novice",\ "Expert"))\ +\ \#\ \ \ scale\_y\_continuous(breaks\ =\ seq(from\ =\ 0,\ to\ =\ 10,\ by\ =\ 1))\ +\ \ \#\ \ \ labs(x\ =\ "",\ \#\ \ \ \ \ \ \ \ y\ =\ "Prevalence\ Rating")\ +\ \ \#\ \ \ scale\_fill\_brewer(palette\ \ =\ "RdBu")\ +\ \ \ \#\ \ \ ggtitle("How\ widespread\ is\ this\ event\ in\ the\ classroom?")\ +\ \#\ \ \ theme\_cowplot()\ \#\ \ \#\ preva\_group\_plot\ \#\ \ \#}}{\{r sri\_pr, echo=FALSE, message=FALSE, warning=FALSE, results=\textquotesingle asis\textquotesingle\} \#  \# \#\#\#\#\#\#\#\#\#\#\#\#\#\# Prevalence Rating \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\# \#  \# sri.preva.table \textless- \#   sri \%\textgreater\% \#   group\_by(ID) \%\textgreater\% \#   summarise( \#     N = n(), \#     "M" = round(mean(prevalence\_rating), digits = 2), \#     "SD" = round(sd(prevalence\_rating), digits = 2), \#     "Min" = min(prevalence\_rating), \#     "Max" = max(prevalence\_rating) \#   ) \#  \# \# insert a table into HTML \# knitr::kable(sri.preva.table, \#              caption = "Prevalence rating") \#  \# \#\#\#\# with event  \# sri.preva.event.table \textless- \#   sri \%\textgreater\% \#   group\_by(ID, event) \%\textgreater\% \#   summarise( \#     N = n(), \#     "M" = round(mean(prevalence\_rating), digits = 2), \#     "SD" = round(sd(prevalence\_rating), digits = 2), \#     "Min" = min(prevalence\_rating), \#     "Max" = max(prevalence\_rating) \#   ) \#  \# \# insert a table into HTML \# knitr::kable(sri.preva.event.table, \#              caption = "Prevalence rating with events") \#  \# \# create a new data frame with rating \# sri\_preva \textless- subset.data.frame(sri, select = c(ID, event, prevalence\_rating)) \#  \# \# plotting prevalence rating for groups \# preva\_group\_plot \textless-  \#   sri\_preva \%\textgreater\%  \#   mutate(ID = factor(ID, \#                      levels = c("Novice", \#                                 "Expert" \#                                 ) \#                      ) \#          ) \%\textgreater\%  \#   ggplot(mapping = aes(x = ID, \#                        y = prevalence\_rating)) + \#   geom\_boxplot(mapping = aes(fill = ID), \#                outlier.shape = NA) + \#   geom\_point(size = 1, \#              alpha = 0.4, \#              position = position\_jitter(seed = 1, \#                                         width = 0.1, \#                                         height = 0.1)) + \#   scale\_x\_discrete(limits = c("Novice", "Expert")) + \#   scale\_y\_continuous(breaks = seq(from = 0, to = 10, by = 1)) +  \#   labs(x = "", \#        y = "Prevalence Rating") +  \#   scale\_fill\_brewer(palette  = "RdBu") +   \#   ggtitle("How widespread is this event in the classroom?") + \#   theme\_cowplot() \#  \# preva\_group\_plot \#  \#}}\label{r-sri_pr-echofalse-messagefalse-warningfalse-resultsasis-prevalence-rating-sri.preva.table---sri-group_byid-summarise-n-n-m-roundmeanprevalence_rating-digits-2-sd-roundsdprevalence_rating-digits-2-min-minprevalence_rating-max-maxprevalence_rating-insert-a-table-into-html-knitrkablesri.preva.table-caption-prevalence-rating-with-event-sri.preva.event.table---sri-group_byid-event-summarise-n-n-m-roundmeanprevalence_rating-digits-2-sd-roundsdprevalence_rating-digits-2-min-minprevalence_rating-max-maxprevalence_rating-insert-a-table-into-html-knitrkablesri.preva.event.table-caption-prevalence-rating-with-events-create-a-new-data-frame-with-rating-sri_preva---subset.data.framesri-select-cid-event-prevalence_rating-plotting-prevalence-rating-for-groups-preva_group_plot---sri_preva-mutateid-factorid-levels-cnovice-expert-ggplotmapping-aesx-id-y-prevalence_rating-geom_boxplotmapping-aesfill-id-outlier.shape-na-geom_pointsize-1-alpha-0.4-position-position_jitterseed-1-width-0.1-height-0.1-scale_x_discretelimits-cnovice-expert-scale_y_continuousbreaks-seqfrom-0-to-10-by-1-labsx-y-prevalence-rating-scale_fill_brewerpalette-rdbu-ggtitlehow-widespread-is-this-event-in-the-classroom-theme_cowplot-preva_group_plot}

\paragraph{t-Test \& effect size ``Prevalence
rating''}\label{t-test-effect-size-prevalence-rating}

\section{\texorpdfstring{\texttt{\{r\ sri\_pr\_ttest,\ echo=FALSE,\ message=FALSE,\ warning=FALSE,\ results=\textquotesingle{}asis\textquotesingle{}\}\ \#\ \ \#\ \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\ T-TEST\ \&\ EFFECT\ SIZE\ \#\#\#\#\#\#\#\#\#\#\#\#\ \#\ \ \#\ \#\ Prevalence\ Rating\ \ \#\ \#\ t-test\ for\ expertise\ differences\ \#\ t.test(x\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Expert"{]},\ \#\ \ \ \ \ \ \ \ y\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Novice"{]},\ \#\ \ \ \ \ \ \ \ var.equal\ =\ TRUE)\ \#\ \ \#\ \#\ Prevalence\ Rating\ \ \#\ \#\ effect\ size\ for\ expertise\ differences\ \#\ d\_sri\_preva\ \textless{}-\ CohenD(x\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Expert"{]},\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Novice"{]},\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ na.rm\ =\ TRUE)\ \#\ \ \#\ round(d\_sri\_preva,\ 2)\ \#\ \ \#}}{\{r sri\_pr\_ttest, echo=FALSE, message=FALSE, warning=FALSE, results=\textquotesingle asis\textquotesingle\} \#  \# \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\# T-TEST \& EFFECT SIZE \#\#\#\#\#\#\#\#\#\#\#\# \#  \# \# Prevalence Rating  \# \# t-test for expertise differences \# t.test(x = sri\$prevalence\_rating{[}sri\$ID == "Expert"{]}, \#        y = sri\$prevalence\_rating{[}sri\$ID == "Novice"{]}, \#        var.equal = TRUE) \#  \# \# Prevalence Rating  \# \# effect size for expertise differences \# d\_sri\_preva \textless- CohenD(x = sri\$prevalence\_rating{[}sri\$ID == "Expert"{]}, \#                       y = sri\$prevalence\_rating{[}sri\$ID == "Novice"{]}, \#                       na.rm = TRUE) \#  \# round(d\_sri\_preva, 2) \#  \#}}\label{r-sri_pr_ttest-echofalse-messagefalse-warningfalse-resultsasis-t-test-effect-size-prevalence-rating-t-test-for-expertise-differences-t.testx-sriprevalence_ratingsriid-expert-y-sriprevalence_ratingsriid-novice-var.equal-true-prevalence-rating-effect-size-for-expertise-differences-d_sri_preva---cohendx-sriprevalence_ratingsriid-expert-y-sriprevalence_ratingsriid-novice-na.rm-true-roundd_sri_preva-2}

\subsubsection{Internal consistency (Omega) for disruption and
confidence
appraisal}\label{internal-consistency-omega-for-disruption-and-confidence-appraisal}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/sri_omega-1.pdf}
Omega Call: omegah(m = m, nfactors = nfactors, fm = fm, key = key, flip
= flip, digits = digits, title = title, sl = sl, labels = labels, plot =
plot, n.obs = n.obs, rotate = rotate, Phi = Phi, option = option, covar
= covar) Alpha: 0.76 G.6: 0.81 Omega Hierarchical: 0.62 Omega H
asymptotic: 0.73 Omega Total 0.84

Schmid Leiman Factor loadings greater than 0.2 g F1* F2* F3* h2 h2 u2
disruption\_appraisal\_whispering 0.60 0.22 0.45 0.45 0.55
disruption\_appraisal\_heckling 0.63 0.24 0.47 0.47 0.53
disruption\_appraisal\_drawing 0.47 0.27 0.27 0.73
disruption\_appraisal\_snipping 0.50 0.26 0.35 0.35 0.65
disruption\_appraisal\_looking at phone 0.38 0.32 0.26 0.26 0.74
disruption\_appraisal\_head on table 0.22 0.98 1.00 1.00 0.00
disruption\_appraisal\_clicking pen 0.34 0.95 1.02 1.02 -0.02
disruption\_appraisal\_drumming 0.34 0.37 0.28 0.28 0.72
disruption\_appraisal\_chatting 0.67 0.28 0.57 0.57 0.43 p2 com
disruption\_appraisal\_whispering 0.80 1.52
disruption\_appraisal\_heckling 0.84 1.39 disruption\_appraisal\_drawing
0.82 1.45 disruption\_appraisal\_snipping 0.71 1.85
disruption\_appraisal\_looking at phone 0.57 2.12
disruption\_appraisal\_head on table 0.05 1.10
disruption\_appraisal\_clicking pen 0.11 1.25
disruption\_appraisal\_drumming 0.42 2.35
disruption\_appraisal\_chatting 0.80 1.52

With Sums of squares of: g F1* F2* F3* h2 2.10 0.19 1.22 1.16 3.13

general/max 0.67 max/min = 16.24 mean percent general = 0.57 with sd =
0.31 and cv of 0.54 Explained Common Variance of the general factor =
0.45

The degrees of freedom are 12 and the fit is 0.35 The number of
observations was 53 with Chi Square = 16.18 with prob \textless{} 0.18
The root mean square of the residuals is 0.05 The df corrected root mean
square of the residuals is 0.09 RMSEA index = 0.079 and the 10 \%
confidence intervals are 0 0.174 BIC = -31.47

Compare this with the adequacy of just a general factor and no group
factors The degrees of freedom for just the general factor are 27 and
the fit is 1.18 The number of observations was 53 with Chi Square = 56
with prob \textless{} 0.00086 The root mean square of the residuals is
0.13 The df corrected root mean square of the residuals is 0.16

RMSEA index = 0.141 and the 10 \% confidence intervals are 0.09 0.197
BIC = -51.2

Measures of factor score adequacy\\
g F1* F2* F3* Correlation of scores with factors 0.84 0.30 1.01 1.00
Multiple R square of scores with factors 0.70 0.09 1.02 0.99 Minimum
correlation of factor score estimates 0.41 -0.82 1.03 0.99

Total, General and Subset omega for each subset g F1* F2* F3* Omega
total for total scores and subscales 0.84 0.54 0.79 0.72 Omega general
for total scores and subscales 0.62 0.47 0.39 0.28 Omega group for total
scores and subscales 0.21 0.06 0.39 0.44
\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/sri_omega-2.pdf}
Omega Call: omegah(m = m, nfactors = nfactors, fm = fm, key = key, flip
= flip, digits = digits, title = title, sl = sl, labels = labels, plot =
plot, n.obs = n.obs, rotate = rotate, Phi = Phi, option = option, covar
= covar) Alpha: 0.82 G.6: 0.84 Omega Hierarchical: 0.66 Omega H
asymptotic: 0.76 Omega Total 0.87

Schmid Leiman Factor loadings greater than 0.2 g F1* F2* F3* h2 h2 u2
confidence\_appraisal\_whispering 0.39 0.48 0.40 0.40 0.60
confidence\_appraisal\_heckling 0.59 0.28 0.45 0.45 0.55
confidence\_appraisal\_drawing 0.70 0.36 0.62 0.62 0.38
confidence\_appraisal\_snipping 0.41 0.23 0.23 0.31 0.31 0.69
confidence\_appraisal\_looking at phone 0.66 0.32 0.57 0.57 0.43
confidence\_appraisal\_head on table 0.56 0.56 0.63 0.63 0.37
confidence\_appraisal\_clicking pen 0.48 0.20 0.31 0.31 0.69
confidence\_appraisal\_drumming 0.42 0.42 0.37 0.37 0.63
confidence\_appraisal\_chatting 0.50 0.87 1.00 1.00 0.00 p2 com
confidence\_appraisal\_whispering 0.38 2.11
confidence\_appraisal\_heckling 0.76 1.62 confidence\_appraisal\_drawing
0.79 1.50 confidence\_appraisal\_snipping 0.55 2.69
confidence\_appraisal\_looking at phone 0.75 1.67
confidence\_appraisal\_head on table 0.50 2.03
confidence\_appraisal\_clicking pen 0.74 1.74
confidence\_appraisal\_drumming 0.49 2.10
confidence\_appraisal\_chatting 0.25 1.60

With Sums of squares of: g F1* F2* F3* h2 2.55 0.82 0.39 0.90 2.80

general/max 0.91 max/min = 7.18 mean percent general = 0.58 with sd =
0.19 and cv of 0.33 Explained Common Variance of the general factor =
0.55

The degrees of freedom are 12 and the fit is 0.33 The number of
observations was 53 with Chi Square = 15.22 with prob \textless{} 0.23
The root mean square of the residuals is 0.05 The df corrected root mean
square of the residuals is 0.09 RMSEA index = 0.069 and the 10 \%
confidence intervals are 0 0.167 BIC = -32.43

Compare this with the adequacy of just a general factor and no group
factors The degrees of freedom for just the general factor are 27 and
the fit is 0.87 The number of observations was 53 with Chi Square = 41.5
with prob \textless{} 0.037 The root mean square of the residuals is
0.12 The df corrected root mean square of the residuals is 0.14

RMSEA index = 0.099 and the 10 \% confidence intervals are 0.026 0.16
BIC = -65.7

Measures of factor score adequacy\\
g F1* F2* F3* Correlation of scores with factors 0.84 0.72 0.48 0.96
Multiple R square of scores with factors 0.70 0.52 0.23 0.92 Minimum
correlation of factor score estimates 0.41 0.04 -0.55 0.83

Total, General and Subset omega for each subset g F1* F2* F3* Omega
total for total scores and subscales 0.87 0.71 0.77 1.00 Omega general
for total scores and subscales 0.66 0.40 0.61 0.25 Omega group for total
scores and subscales 0.15 0.32 0.16 0.75

\subsubsection{Prevalence Rating as manipulation
check}\label{prevalence-rating-as-manipulation-check}

\subsubsection{2.3 Situational Jugdement
Test}\label{situational-jugdement-test}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M and SD for overall value}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 41 & 0.75 & 0.08 & 0.54 & 0.88 \\
Novice & 42 & 0.72 & 0.13 & 0.10 & 0.91 \\
\end{longtable}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M and SD for managing momentum}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 41 & 0.81 & 0.10 & 0.60 & 1 \\
Novice & 42 & 0.80 & 0.17 & 0.08 & 1 \\
\end{longtable}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M and SD for monitoring}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 41 & 0.69 & 0.13 & 0.41 & 0.91 \\
Novice & 42 & 0.64 & 0.16 & 0.15 & 0.99 \\
\end{longtable}

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{N, M and SD for rules and routines}\tabularnewline
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Group & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 41 & 0.74 & 0.10 & 0.49 & 0.91 \\
Novice & 42 & 0.72 & 0.13 & 0.07 & 0.92 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/sjt-1.pdf}

\paragraph{t-test \& effect size ``STJ -
All''}\label{t-test-effect-size-stj---all}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_sjt\(All[df_sjt\)Group == ``Expert''{]} and
df\_sjt\(All[df_sjt\)Group == ``Novice''{]} t = 0.94245, df = 81,
p-value = 0.3488 alternative hypothesis: true difference in means is not
equal to 0 95 percent confidence interval: -0.02434447 0.06816136 sample
estimates: mean of x mean of y 0.7456548 0.7237464

{[}1{]} 0.21 attr(,``magnitude'') {[}1{]} ``small''

\paragraph{t-test \& effect size ``SJT - Managing
momentum''}\label{t-test-effect-size-sjt---managing-momentum}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_sjt\(`Managing momentum`[df_sjt\)Group == ``Expert''{]} and
df\_sjt\(`Managing momentum`[df_sjt\)Group == ``Novice''{]} t = 0.15193,
df = 81, p-value = 0.8796 alternative hypothesis: true difference in
means is not equal to 0 95 percent confidence interval: -0.05469659
0.06374016 sample estimates: mean of x mean of y 0.8092270 0.8047052

{[}1{]} 0.03 attr(,``magnitude'') {[}1{]} ``negligible''

\paragraph{t-test \& effect size ``SJT -
Monitoring''}\label{t-test-effect-size-sjt---monitoring}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_sjt\(Monitoring[df_sjt\)Group == ``Expert''{]} and
df\_sjt\(Monitoring[df_sjt\)Group == ``Novice''{]} t = 1.4415, df = 81,
p-value = 0.1533 alternative hypothesis: true difference in means is not
equal to 0 95 percent confidence interval: -0.01732034 0.10841421 sample
estimates: mean of x mean of y 0.6877186 0.6421717

{[}1{]} 0.32 attr(,``magnitude'') {[}1{]} ``small''

\paragraph{t-test \& effect size ``SJT - Rules \&
routines''}\label{t-test-effect-size-sjt---rules-routines}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_sjt\(`Rules and routines`[df_sjt\)Group == ``Expert''{]} and
df\_sjt\(`Rules and routines`[df_sjt\)Group == ``Novice''{]} t =
0.59927, df = 81, p-value = 0.5507 alternative hypothesis: true
difference in means is not equal to 0 95 percent confidence interval:
-0.03632644 0.06763970 sample estimates: mean of x mean of y 0.7400189
0.7243622

{[}1{]} 0.13 attr(,``magnitude'') {[}1{]} ``negligible''

\subsubsection{Internal consistency (Omega) for
SJT}\label{internal-consistency-omega-for-sjt}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/sjt_omega-1.pdf}
Omega Call: omegah(m = m, nfactors = nfactors, fm = fm, key = key, flip
= flip, digits = digits, title = title, sl = sl, labels = labels, plot =
plot, n.obs = n.obs, rotate = rotate, Phi = Phi, option = option, covar
= covar) Alpha: 0.68 G.6: 0.9 Omega Hierarchical: 0.66 Omega H
asymptotic: 0.88 Omega Total 0.75

Schmid Leiman Factor loadings greater than 0.2 g F1* F2* F3* h2 h2 u2 p2
com WT\_S1\_F1F2\_AL 0.35 0.15 0.85 0.13 1.47 WT\_S1\_F1F3\_AL 0.25 0.33
0.19 0.81 0.32 2.20 WT\_S1\_F1F5\_AL 0.26 -0.55 0.38 0.38 0.62 0.04 1.54
WT\_S1\_F2F4\_AL 0.49 0.31 0.35 0.35 0.65 0.69 1.81 WT\_S1\_F2F5\_AL
0.63 0.42 0.42 0.58 0.00 1.13 WT\_S1\_F2F6\_AL 0.57 0.35 0.35 0.65 0.01
1.16 WT\_S1\_F3F4\_AL 0.57 0.36 0.36 0.64 0.90 1.21 WT\_S1\_F3F5\_AL
0.78 0.61 0.61 0.39 0.00 1.02 WT\_S1\_F3F6\_AL 0.44 0.23 0.23 0.77 0.05
1.33 WT\_S1\_F4F5\_AL 0.60 -0.39 0.52 0.52 0.48 0.69 1.75
WT\_S1\_F4F6\_AL 0.47 -0.20 0.27 0.27 0.73 0.84 1.38 WT\_S1\_F5F6\_AL
0.42 -0.50 0.45 0.45 0.55 0.07 2.20 WT\_S2\_F1F3\_AL 0.33 0.14 0.86 0.02
1.52 WT\_S2\_F1F4\_AL- -0.24 0.10 0.90 0.07 2.13 WT\_S2\_F1F6\_AL 0.49
-0.24 0.32 0.32 0.68 0.11 1.78 WT\_S2\_F2F3\_AL 0.22 0.44 0.24 0.24 0.76
0.20 1.48 WT\_S2\_F2F5\_AL 0.32 -0.35 0.23 0.23 0.77 0.45 2.06
WT\_S2\_F2F6\_AL 0.26 0.54 0.37 0.37 0.63 0.19 1.48 WT\_S2\_F3F4\_AL-
0.31 -0.52 0.38 0.38 0.62 0.26 1.66 WT\_S2\_F3F5\_AL- -0.33 -0.35 0.26
0.26 0.74 0.09 2.37 WT\_S2\_F4F5\_AL- -0.31 0.15 0.85 0.14 2.13
WT\_S2\_F4F6\_AL- -0.69 0.48 0.48 0.52 0.01 1.01 WT\_S2\_F5F6\_AL 0.51
0.38 0.42 0.42 0.58 0.01 1.89 WT\_S3\_F1F2\_AL- 0.25 -0.24 0.13 0.87
0.50 2.14 WT\_S3\_F1F3\_AL 0.32 0.12 0.88 0.11 1.31 WT\_S3\_F1F4\_AL-
-0.20 0.05 0.95 0.04 1.27 WT\_S3\_F1F5\_AL- 0.26 -0.24 0.13 0.87 0.54
2.02 WT\_S3\_F2F7\_AL 0.31 0.21 0.16 0.84 0.57 2.37 WT\_S3\_F3F7\_AL
0.38 0.15 0.85 0.94 1.13 WT\_S3\_F4F7\_AL 0.24 0.06 0.94 0.86 1.33
WT\_S3\_F5F7\_AL 0.34 0.13 0.87 0.89 1.24 WT\_S4\_F1F2\_AL 0.29 0.21
0.16 0.84 0.53 2.49 WT\_S4\_F1F3\_AL 0.30 0.36 0.23 0.23 0.77 0.38 2.21
WT\_S4\_F1F4\_AL 0.20 0.06 0.94 0.64 1.86 WT\_S4\_F1F5\_AL- 0.27 -0.29
0.16 0.84 0.46 2.10 WT\_S4\_F1F6\_AL- -0.63 0.43 0.43 0.57 0.08 1.18
WT\_S4\_F2F3\_AL -0.22 0.06 0.94 0.07 1.50 WT\_S4\_F2F6\_AL- 0.47 -0.35
0.24 0.40 0.40 0.60 0.56 2.40 WT\_S4\_F3F4\_AL 0.23 0.06 0.94 0.00 1.08
WT\_S4\_F4F6\_AL- 0.26 -0.26 0.14 0.86 0.49 2.10

With Sums of squares of: g F1* F2* F3* h2 2.88 4.10 3.00 0.01 3.35

general/max 0.7 max/min = 293.69 mean percent general = 0.32 with sd =
0.31 and cv of 0.95 Explained Common Variance of the general factor =
0.29

The degrees of freedom are 663 and the fit is 18.76 The number of
observations was 84 with Chi Square = 1253.73 with prob \textless{}
6.8e-39 The root mean square of the residuals is 0.11 The df corrected
root mean square of the residuals is 0.12 RMSEA index = 0.102 and the 10
\% confidence intervals are 0.095 0.112 BIC = -1683.9

Compare this with the adequacy of just a general factor and no group
factors The degrees of freedom for just the general factor are 740 and
the fit is 24.06 The number of observations was 84 with Chi Square =
1639.81 with prob \textless{} 5e-70 The root mean square of the
residuals is 0.17 The df corrected root mean square of the residuals is
0.17

RMSEA index = 0.12 and the 10 \% confidence intervals are 0.113 0.129
BIC = -1639

Measures of factor score adequacy\\
g F1* F2* F3* Correlation of scores with factors 0.90 0.93 0.92 0.06
Multiple R square of scores with factors 0.81 0.87 0.84 0.00 Minimum
correlation of factor score estimates 0.62 0.73 0.69 -0.99

Total, General and Subset omega for each subset g F1* F2* F3* Omega
total for total scores and subscales 0.75 0.56 0.39 NA Omega general for
total scores and subscales 0.66 0.53 0.38 NA Omega group for total
scores and subscales 0.01 0.03 0.00 NA
\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/sjt_omega-2.pdf}
Omega Call: omegah(m = m, nfactors = nfactors, fm = fm, key = key, flip
= flip, digits = digits, title = title, sl = sl, labels = labels, plot =
plot, n.obs = n.obs, rotate = rotate, Phi = Phi, option = option, covar
= covar) Alpha: 0.81 G.6: 0.95 Omega Hierarchical: 0.13 Omega H
asymptotic: 0.16 Omega Total 0.84

Schmid Leiman Factor loadings greater than 0.2 g F1* F2* F3* h2 h2 u2 p2
com WT\_S5\_F1F2\_ST 0.28 0.11 0.89 0.09 1.90 WT\_S5\_F1F3\_ST 0.41 0.20
0.20 0.80 0.07 1.46 WT\_S5\_F1F4\_ST 0.37 0.19 0.81 0.06 1.74
WT\_S5\_F1F5\_ST 0.27 -0.22 0.53 0.42 0.42 0.58 0.05 2.08
WT\_S5\_F2F6\_ST- 0.04 0.96 0.00 1.68 WT\_S5\_F3F5\_ST- 0.20 0.08 0.92
0.02 2.57 WT\_S5\_F3F6\_ST 0.20 0.05 0.95 0.10 1.30 WT\_S5\_F4F6\_ST
0.05 0.95 0.14 2.61 WT\_S6\_F1F2\_ST 0.26 0.55 0.34 0.49 0.49 0.51 0.13
2.15 WT\_S6\_F1F3\_ST 0.25 0.64 0.50 0.50 0.50 0.13 1.44
WT\_S6\_F1F5\_ST 0.23 0.51 0.34 0.34 0.66 0.15 1.61 WT\_S6\_F1F6\_ST
0.25 0.64 0.48 0.48 0.52 0.13 1.35 WT\_S6\_F2F3\_ST 0.07 0.93 0.02 2.50
WT\_S6\_F2F4\_ST 0.55 0.35 0.35 0.65 0.09 1.34 WT\_S6\_F2F5\_ST 0.24
-0.21 0.13 0.87 0.05 2.87 WT\_S6\_F3F4\_ST 0.22 0.62 0.45 0.45 0.55 0.11
1.39 WT\_S6\_F4F5\_ST 0.25 0.71 0.58 0.58 0.42 0.10 1.32
WT\_S6\_F4F6\_ST 0.43 0.21 0.21 0.79 0.11 1.33 WT\_S7\_F1F6\_ST 0.64
0.48 0.48 0.52 0.07 1.37 WT\_S7\_F1F7\_ST 0.47 0.30 0.35 0.35 0.65 0.08
2.09 WT\_S7\_F2F6\_ST 0.24 0.29 0.17 0.83 0.09 2.78 WT\_S7\_F3F6\_ST
0.32 0.30 -0.30 0.30 0.30 0.70 0.06 3.30 WT\_S7\_F3F7\_ST 0.23 0.37 0.24
0.24 0.76 0.07 2.42 WT\_S7\_F4F6\_ST 0.30 0.37 0.28 0.28 0.72 0.08 2.78
WT\_S7\_F5F6\_ST 0.21 0.55 0.37 0.37 0.63 0.12 1.49 WT\_S7\_F5F7\_ST
0.25 0.46 0.31 0.39 0.39 0.61 0.16 2.64 WT\_S7\_F6F7\_ST 0.27 -0.37 0.23
0.23 0.77 0.02 2.02 WT\_S8\_F1F2\_ST 0.59 0.37 0.37 0.63 0.00 1.13
WT\_S8\_F2F3\_ST 0.24 0.63 0.47 0.47 0.53 0.03 1.37 WT\_S8\_F2F5\_ST
0.58 0.35 0.35 0.65 0.03 1.09 WT\_S8\_F3F4\_ST 0.22 0.05 0.95 0.04 1.21
WT\_S8\_F4F5\_ST 0.23 0.08 0.92 0.10 2.24 WT\_S9\_F1F2\_ST 0.24 -0.25
0.12 0.88 0.02 2.07 WT\_S9\_F1F5\_ST 0.41 0.19 0.81 0.06 1.36
WT\_S9\_F2F3\_ST 0.28 -0.27 0.16 0.84 0.03 2.14 WT\_S9\_F2F4\_ST 0.32
0.15 0.85 0.10 1.97 WT\_S9\_F2F5\_ST 0.35 -0.64 0.53 0.53 0.47 0.00 1.55
WT\_S9\_F3F5\_ST 0.48 0.27 0.27 0.73 0.01 1.33 WT\_S9\_F4F5\_ST 0.54
0.35 0.35 0.65 0.06 1.42

With Sums of squares of: g F1* F2* F3* h2 0.82 4.38 2.79 2.65 3.86

general/max 0.19 max/min = 1.65 mean percent general = 0.07 with sd =
0.04 and cv of 0.63 Explained Common Variance of the general factor =
0.08

The degrees of freedom are 627 and the fit is 18.95 The number of
observations was 84 with Chi Square = 1273.13 with prob \textless{}
2.9e-46 The root mean square of the residuals is 0.11 The df corrected
root mean square of the residuals is 0.12 RMSEA index = 0.11 and the 10
\% confidence intervals are 0.103 0.12 BIC = -1504.99

Compare this with the adequacy of just a general factor and no group
factors The degrees of freedom for just the general factor are 702 and
the fit is 24.66 The number of observations was 84 with Chi Square =
1689.12 with prob \textless{} 4.7e-83 The root mean square of the
residuals is 0.18 The df corrected root mean square of the residuals is
0.19

RMSEA index = 0.129 and the 10 \% confidence intervals are 0.122 0.138
BIC = -1421.31

Measures of factor score adequacy\\
g F1* F2* F3* Correlation of scores with factors 0.39 0.89 0.90 0.89
Multiple R square of scores with factors 0.15 0.80 0.81 0.80 Minimum
correlation of factor score estimates -0.70 0.60 0.61 0.59

Total, General and Subset omega for each subset g F1* F2* F3* Omega
total for total scores and subscales 0.84 0.84 0.39 0.49 Omega general
for total scores and subscales 0.13 0.11 0.06 0.04 Omega group for total
scores and subscales 0.37 0.73 0.33 0.45
\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/sjt_omega-3.pdf}
Omega Call: omegah(m = m, nfactors = nfactors, fm = fm, key = key, flip
= flip, digits = digits, title = title, sl = sl, labels = labels, plot =
plot, n.obs = n.obs, rotate = rotate, Phi = Phi, option = option, covar
= covar) Alpha: 0.65 G.6: 0.84 Omega Hierarchical: 0.69 Omega H
asymptotic: 0.94 Omega Total 0.74

Schmid Leiman Factor loadings greater than 0.2 g F1* F2* F3* h2 h2 u2 p2
com WT\_S11\_F1F5\_R 0.06 0.94 0.51 2.02 WT\_S11\_F1F6\_R 0.58 0.24 0.26
0.46 0.46 0.54 0.73 1.76 WT\_S11\_F2F3\_R- 0.62 -0.29 0.49 0.49 0.51
0.78 1.57 WT\_S11\_F2F5\_R- -0.38 0.16 0.84 0.11 1.26 WT\_S11\_F2F6\_R
0.80 0.68 0.68 0.32 0.04 1.12 WT\_S11\_F3F5\_R 0.60 0.37 0.37 0.63 0.96
1.09 WT\_S11\_F3F6\_R 0.79 0.33 0.73 0.73 0.27 0.84 1.36
WT\_S11\_F4F5\_R 0.41 0.22 0.22 0.78 0.76 1.64 WT\_S11\_F4F6\_R 0.51
0.27 0.36 0.36 0.64 0.72 1.80 WT\_S11\_F5F6\_R- 0.21 0.59 0.40 0.40 0.60
0.11 1.26 WT\_S13\_F1F4\_R -0.33 0.41 0.29 0.29 0.71 0.02 1.99
WT\_S13\_F1F6\_R- -0.50 0.29 0.29 0.71 0.11 1.28 WT\_S13\_F2F4\_R 0.26
0.38 0.21 0.21 0.79 0.33 1.81 WT\_S13\_F3F4\_R 0.25 0.37 0.21 0.21 0.79
0.07 2.01 WT\_S13\_F3F6\_R- -0.38 -0.33 0.26 0.26 0.74 0.05 2.17
WT\_S13\_F4F6\_R 0.40 0.19 0.81 0.85 1.35 WT\_S14\_F1F3\_R- 0.34 0.24
0.18 0.82 0.67 1.81 WT\_S14\_F1F4\_R 0.55 0.32 0.32 0.68 0.01 1.12
WT\_S14\_F3F4\_R- -0.22 0.07 0.93 0.22 2.00 WT\_S14\_F3F5\_R- 0.49 0.30
0.30 0.70 0.10 1.49 WT\_S14\_F3F6\_R- 0.24 0.07 0.93 0.19 1.48
WT\_S14\_F4F5\_R- -0.64 0.43 0.43 0.57 0.01 1.14 WT\_S14\_F4F6\_R- 0.26
-0.23 0.12 0.88 0.54 2.13

With Sums of squares of: g F1* F2* F3* h2 2.80 0.01 1.97 2.11 2.75

general/max 1.02 max/min = 211.46 mean percent general = 0.38 with sd =
0.34 and cv of 0.89 Explained Common Variance of the general factor =
0.41

The degrees of freedom are 187 and the fit is 6.03 The number of
observations was 72 with Chi Square = 365.08 with prob \textless{}
1.3e-13 The root mean square of the residuals is 0.1 The df corrected
root mean square of the residuals is 0.12 RMSEA index = 0.114 and the 10
\% confidence intervals are 0.098 0.133 BIC = -434.66

Compare this with the adequacy of just a general factor and no group
factors The degrees of freedom for just the general factor are 230 and
the fit is 8.49 The number of observations was 72 with Chi Square =
525.16 with prob \textless{} 4e-25 The root mean square of the residuals
is 0.15 The df corrected root mean square of the residuals is 0.16

RMSEA index = 0.133 and the 10 \% confidence intervals are 0.119 0.15
BIC = -458.47

Measures of factor score adequacy\\
g F1* F2* F3* Correlation of scores with factors 0.93 0.06 0.9 0.87
Multiple R square of scores with factors 0.86 0.00 0.8 0.76 Minimum
correlation of factor score estimates 0.72 -0.99 0.6 0.52

Total, General and Subset omega for each subset g F1* F2* F3* Omega
total for total scores and subscales 0.74 NA 0.67 0.44 Omega general for
total scores and subscales 0.69 NA 0.63 0.35 Omega group for total
scores and subscales 0.05 NA 0.04 0.09

\subsubsection{2.4 Classroom
Questionnaire}\label{classroom-questionnaire}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0833}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0357}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0595}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0714}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0833}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0833}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1310}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1429}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1548}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1548}}@{}}
\caption{Mean, SD, min, max for classroom managament (cm) and
non-/paraverbal communication (n\&pv com)}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Group
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
N
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
M cm
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
SD cm
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Min cm
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Max cm
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
M n\&pv com
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
SD n\&pv com
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Min n\&pv com
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Max n\&pv com
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Group
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
N
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
M cm
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
SD cm
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Min cm
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Max cm
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
M n\&pv com
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
SD n\&pv com
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Min n\&pv com
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Max n\&pv com
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 41 & 3.2 & 0.72 & 1 & 4 & 3.30 & 0.65 & 1 & 4 \\
Novice & 42 & 3.0 & 0.77 & 1 & 4 & 3.13 & 0.73 & 1 & 4 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/classroom questionnaire-1.pdf}

\paragraph{t-test \& effect size ``Classroom Questionnaire -
All''}\label{t-test-effect-size-classroom-questionnaire---all}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_quest\_plot\(All[df_quest_plot\)Group == ``Expert''{]} and
df\_quest\_plot\(All[df_quest_plot\)Group == ``Novice''{]} t = 2.7419,
df = 81, p-value = 0.007516 alternative hypothesis: true difference in
means is not equal to 0 95 percent confidence interval: 0.05014992
0.31545984 sample estimates: mean of x mean of y 3.247805 3.065000

{[}1{]} 0.6 attr(,``magnitude'') {[}1{]} ``medium''

\paragraph{t-test \& effect size ``Classroom Questionnaire - Classroom
Management''}\label{t-test-effect-size-classroom-questionnaire---classroom-management}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data: df\_quest\_plot\(`Classroom management`[df_quest_plot\)Group ==
``Expert''{]} and
df\_quest\_plot\(`Classroom management`[df_quest_plot\)Group ==
``Novice''{]} t = 2.6421, df = 81, p-value = 0.009887 alternative
hypothesis: true difference in means is not equal to 0 95 percent
confidence interval: 0.04912362 0.34875094 sample estimates: mean of x
mean of y 3.195366 2.996429

{[}1{]} 0.58 attr(,``magnitude'') {[}1{]} ``medium''

\paragraph{t-test \& effect size ``Classroom Questionnaire -
Non-/paraverbal
communication''}\label{t-test-effect-size-classroom-questionnaire---non-paraverbal-communication}

\begin{verbatim}
Two Sample t-test
\end{verbatim}

data:
df\_quest\_plot\(`Non-/paraverbal communication`[df_quest_plot\)Group ==
``Expert''{]} and
df\_quest\_plot\(`Non-/paraverbal communication`[df_quest_plot\)Group ==
``Novice''{]} t = 1.997, df = 81, p-value = 0.04919 alternative
hypothesis: true difference in means is not equal to 0 95 percent
confidence interval: 0.0006129687 0.3361233844 sample estimates: mean of
x mean of y 3.301463 3.133095

{[}1{]} 0.44 attr(,``magnitude'') {[}1{]} ``small''

\subsection{3. Correlations}\label{correlations}

\begin{verbatim}
## 
##  Pearson's product-moment correlation
## 
## data:  df_merge$GRI_mtu and df_merge$SJT_All
## t = -2.1712, df = 80, p-value = 0.03288
## alternative hypothesis: true correlation is not equal to 0
## 95 percent confidence interval:
##  -0.43084846 -0.01990909
## sample estimates:
##       cor 
## -0.235897
\end{verbatim}

\begin{verbatim}
## 
##  Pearson's product-moment correlation
## 
## data:  df_merge$GRI_mtu and df_merge$SJT_Monitoring
## t = -1.9731, df = 80, p-value = 0.05194
## alternative hypothesis: true correlation is not equal to 0
## 95 percent confidence interval:
##  -0.413114345  0.001665702
## sample estimates:
##        cor 
## -0.2154193
\end{verbatim}

\begin{verbatim}
## 
##  Pearson's product-moment correlation
## 
## data:  df_merge_experts$GRI_mtu and df_merge_experts$`Teaching Experience`
## t = -1.4152, df = 38, p-value = 0.1652
## alternative hypothesis: true correlation is not equal to 0
## 95 percent confidence interval:
##  -0.50038371  0.09433299
## sample estimates:
##        cor 
## -0.2237514
\end{verbatim}

\end{document}

### 2024-11-04 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x

@@
   summarise(
-    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
+    Mean_disruption_appraisal = round(mean(disruption_appraisal), 2),
     Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
@@
   dplyr::select(Participant,
-                Mean_disrupption_appraisal,
+                Mean_disruption_appraisal,
                 Mean_confidence_appraisal)
@@
   # filter(`Teaching Experience` > 0) %>% 
-  dplyr::select(Stud_number_fixation_min,
-                Average_duration_stud,
-                Number_of_fixations.Disruptive_Person,
-                Average_duration_disrup,
-                Disrup_time_fixation_sec,
-                GRI_mtu,
+  dplyr::select(GRI_mtu,
                 SJT_All,
-                SJT_Monitoring,
-                Quest_All
+                Quest_All,
+                Mean_disruption_appraisal,
+                Mean_confidence_appraisal
                 )
@@
 
-# p-value for GRI x STJ_Monitoring
-cor.test(df_merge$GRI_mtu, df_merge$SJT_Monitoring)
+# p-value for GRI x Quest_All
+cor.test(df_merge$GRI_mtu, df_merge$Quest_All)
+
+# p-value for GRI x Disruption Rating
+cor.test(df_merge$GRI_mtu, df_merge$Mean_disruption_appraisal)
+
+# p-value for GRI x Confidence Rating
+cor.test(df_merge$GRI_mtu, df_merge$Mean_confidence_appraisal)
 

### 2024-11-04 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.tex
x

@@
 ## 
-## data:  df_merge$GRI_mtu and df_merge$SJT_Monitoring
-## t = -1.9731, df = 80, p-value = 0.05194
+## data:  df_merge$GRI_mtu and df_merge$Quest_All
+## t = 0.64655, df = 80, p-value = 0.5198
 ## alternative hypothesis: true correlation is not equal to 0
 ## 95 percent confidence interval:
-##  -0.413114345  0.001665702
+##  -0.1472121  0.2846518
 ## sample estimates:
 ##        cor 
-## -0.2154193
+## 0.07209825
+\end{verbatim}
+
+\begin{verbatim}
+## 
+##  Pearson's product-moment correlation
+## 
+## data:  df_merge$GRI_mtu and df_merge$Mean_disruption_appraisal
+## t = 0.60918, df = 80, p-value = 0.5441
+## alternative hypothesis: true correlation is not equal to 0
+## 95 percent confidence interval:
+##  -0.1512868  0.2808174
+## sample estimates:
+##        cor 
+## 0.06795118
+\end{verbatim}
+
+\begin{verbatim}
+## 
+##  Pearson's product-moment correlation
+## 
+## data:  df_merge$GRI_mtu and df_merge$Mean_confidence_appraisal
+## t = -0.11168, df = 80, p-value = 0.9114
+## alternative hypothesis: true correlation is not equal to 0
+## 95 percent confidence interval:
+##  -0.2288719  0.2050778
+## sample estimates:
+##        cor 
+## -0.0124849
 \end{verbatim}

### 2024-11-06 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.tex
x paper

@@
 
+\paragraph{2.2.2 Number of fixations per minute (AOI
+others)}\label{number-of-fixations-per-minute-aoi-others}
+
+\begin{longtable}[]{@{}lrrrrr@{}}
+\caption{N, M, SD, min \& max number of fixations per minute (AOI
+others)}\tabularnewline
+\toprule\noalign{}
+Group & N & M & SD & Min & Max \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Group & N & M & SD & Min & Max \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Novice & 42 & 48.51 & 13.08 & 29.70 & 80.89 \\
+Expert & 40 & 52.79 & 15.14 & 18.85 & 99.66 \\
+\end{longtable}
+
+\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/nof_others-1.pdf}
+
+\paragraph{t-test \& effect size ``Number of fixation'' (AOI
+others)}\label{t-test-effect-size-number-of-fixation-aoi-others}
+
+\begin{verbatim}
+Two Sample t-test
+\end{verbatim}
+
+data: df\_aoi\_others\(Others_number_fixation_min[df_aoi_others\)Group
+== ``Expert''{]} and
+df\_aoi\_others\(Others_number_fixation_min[df_aoi_others\)Group ==
+``Novice''{]} t = 1.3722, df = 80, p-value = 0.1738 alternative
+hypothesis: true difference in means is not equal to 0 95 percent
+confidence interval: -1.927317 10.487650 sample estimates: mean of x
+mean of y 52.79350 48.51333
+
+{[}1{]} 0.3 attr(,``magnitude'') {[}1{]} ``small''
+
 \paragraph{2.2.3 Number of fixations (AOI disruptive

### 2024-11-07 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.tex
literaturverzeichnis

@@
 \IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-\usepackage[]{natbib}
-\bibliographystyle{plainnat}
 
@@
 
-\setcitestyle{sort&compress}
+% Pandoc citation processing
+%From Pandoc 3.1.8
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\bibliographystyle{elsarticle-num}
+\setcitestyle{numbered}
 \usepackage{tabularx}
@@
 The teaching profession is one of the most stressful professions, with
-teachers facing a host of stressors during their everyday work
-\citep{smith2000, herman2020, schult2014belastet}. To better understand
-mechanisms in teacher stress, there is a growing research interest in
-physiological measures such as heart rate (HR) as online measures of
-teachers' stress during teaching
-\citep{karner2021teachers, wettstein2020ambulatory}. For example, it has
-been shown that teacher-centered activities and typical
-classroom-related stressors increase teacher HR during teaching
-activities
-\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021, huang2022class}.
-However, previous studies have often relied on expensive and obtrusive
-electrocardiographs (ECG). Modern fitness trackers represent a
-non-invasive and convenient alternative \citep{ferguson2015}.
+teachers facing a host of stressors during their everyday work (Smith
+2000; Herman et al. 2020; Schult, Münzer-Schrobildgen, and Sparfeldt
+2014). To better understand mechanisms in teacher stress, there is a
+growing research interest in physiological measures such as heart rate
+(HR) as online measures of teachers' stress during teaching (Kärner and
+Höning 2021; Wettstein et al. 2020). For example, it has been shown that
+teacher-centered activities and typical classroom-related stressors
+increase teacher HR during teaching activities (Sperka and Kittler 1995;
+Scheuch and Knothe 1997; Donker, Van Gog, and Mainhard 2018; Junker,
+Donker, and Mainhard 2021; Huang et al. 2022). However, previous studies
+have often relied on expensive and obtrusive electrocardiographs (ECG).
+Modern fitness trackers represent a non-invasive and convenient
+alternative (Ferguson et al. 2015).
 
 Classroom disruptions are a major stressor in teachers' daily work
-\citep{boyle1995structural, aloe2014multivariate}, and learning how to
-deal with them is an important aspect of professional expertise
-\citep{wolff2015keeping}. According to \citet{lazarus1990theory}
-transactional model of stress and coping, the experience of stress in
-response to stressors such as classroom disruptions depends on the
-teacher´s subjective appraisal, which, in turn, depends on their coping
-resources, such as their professional knowledge. The resulting stress
-response has a psychological, physiological, or behavioral dimension
-\citep{kyriacou1978}. Therefore, in order to better understand how
-classroom stressors affect teachers' stress response, subjective
-self-reports should be accompanied by objective, physiological measures
-\citep{wettstein2021}. Teachers' use of wrist-worn fitness trackers in
-educational research provides fine-grained, in vivo data, allowing
-researchers as well as teachers themselves to monitor their
-physiological stress response continuously during teaching, across
-settings, and at low costs. Being able to monitor, and eventually
-counteract, teacher stress levels appears particularly relevant given
-the profession's generally high stress levels and associated negative
-health effects \citep{johnson2005experience, montgomery2005meta}. To
-harness this potential, the present study explored the use of
-wrist-based fitness trackers as a tool to assess teachers' HR, as an
-indicator of stress, before, during, and after a teaching session during
-which typical, potentially stressful, classroom disruptions occurred.
-Further, we explored to what extent teachers' subjective appraisals of
-classroom disruptions and their teaching experience predicted teacher
-stress as assessed by the fitness tracker.
+(Boyle et al. 1995; Aloe et al. 2014), and learning how to deal with
+them is an important aspect of professional expertise (Wolff et al.
+2015). According to Lazarus (1990) transactional model of stress and
+coping, the experience of stress in response to stressors such as
+classroom disruptions depends on the teacher´s subjective appraisal,
+which, in turn, depends on their coping resources, such as their
+professional knowledge. The resulting stress response has a
+psychological, physiological, or behavioral dimension (Kyriacou and
+Sutcliffe 1978). Therefore, in order to better understand how classroom
+stressors affect teachers' stress response, subjective self-reports
+should be accompanied by objective, physiological measures (Wettstein et
+al. 2021). Teachers' use of wrist-worn fitness trackers in educational
+research provides fine-grained, in vivo data, allowing researchers as
+well as teachers themselves to monitor their physiological stress
+response continuously during teaching, across settings, and at low
+costs. Being able to monitor, and eventually counteract, teacher stress
+levels appears particularly relevant given the profession's generally
+high stress levels and associated negative health effects (Johnson et
+al. 2005; Montgomery and Rupp 2005). To harness this potential, the
+present study explored the use of wrist-based fitness trackers as a tool
+to assess teachers' HR, as an indicator of stress, before, during, and
+after a teaching session during which typical, potentially stressful,
+classroom disruptions occurred. Further, we explored to what extent
+teachers' subjective appraisals of classroom disruptions and their
+teaching experience predicted teacher stress as assessed by the fitness
+tracker.
 
@@
 Fitness trackers provide data on physical activity and cardiovascular
-parameters such as HR, supporting personalized fitness goals
-\citep{nuss2021effects} and stress management \citep{hao2018chrv}. They
-can be used as ubiquitous, low-cost, and unintrusive data collection
-instruments \citep{godfrey2018z}, and their wide-spread use and everyday
+parameters such as HR, supporting personalized fitness goals (Nuss et
+al. 2021) and stress management (Hao et al. 2017). They can be used as
+ubiquitous, low-cost, and unintrusive data collection instruments
+(Godfrey et al. 2018), and their wide-spread use and everyday
 availability align with the increasing popularity and acceptance of
-wearables among the general population \citep{peng2022acceptance}. In
-contrast to self-reported questionnaires on stress
-\citep{chaplain2008, liu2020} that are prone to biases like social
-desirability \citep{razavi2001self} or recall errors
-\citep{van2016accuracy}, fitness trackers, as ambulatory assessment
-methods \citep{trull2013ambulatory, wettstein2020ambulatory}, offer more
-objective insights into teachers' stress levels by monitoring teachers'
-physiological stress responses without disrupting teaching
-\citep{donker2018, runge2020}.
+wearables among the general population (Peng et al. 2022). In contrast
+to self-reported questionnaires on stress (Chaplain 2008; Liu and Yan
+2020) that are prone to biases like social desirability (Razavi 2001) or
+recall errors (Van den Bergh and Walentynowicz 2016), fitness trackers,
+as ambulatory assessment methods (Trull and Ebner-Priemer 2013;
+Wettstein et al. 2020), offer more objective insights into teachers'
+stress levels by monitoring teachers' physiological stress responses
+without disrupting teaching (Donker, Van Gog, and Mainhard 2018; Runge,
+Haarman, and Fisher 2020).
 
 One important health parameter assessed by nearly all wrist-worn fitness
-trackers is heart rate \citep{scalise2018wearables}. HR indicates the
+trackers is heart rate (Scalise and Cosoli 2018). HR indicates the
 number of heartbeats within one minute and is typically expressed as
-beats per minute (BPM)
-\citep{berntson2007cardiovascular, hottenrott2007}. At rest, the average
-HR of adults typically ranges between 60 and 80 BPM
-\citep{sammito2015guideline}. HR can be detected and measured in
+beats per minute (BPM) (Berntson, Quigley, and Lozano 2007; Hottenrot
+2007). At rest, the average HR of adults typically ranges between 60 and
+80 BPM (Sammito et al. 2015). HR can be detected and measured in
 different ways using sensors, such as electrocardiography (ECG) or
-photoplethysmography (PPG) \citep{mukhopadhyay2017wearable}. While ECG
+photoplethysmography (PPG) (Mukhopadhyay and Islam 2017). While ECG
 sensors offer precise measurements by detecting the heart's electrical
 activity, their intrusive nature and requirement of direct skin contact
-may limit their suitability \citep{kranjec2014non}, particularly in
+may limit their suitability (Kranjec et al. 2014), particularly in
 educational settings. In contrast, photoplethysmography (PPG) is a
 rather uncomplicated and inexpensive technique to measure HR, commonly
-found in commercially available fitness trackers
-\citep{castaneda2018review}. This optical method assesses HR by flashing
-green or red lights to measure changes in blood volume in the
-capillaries of the skin \citep{allen2007photoplethysmography}.
+found in commercially available fitness trackers (Castaneda et al.
+2018). This optical method assesses HR by flashing green or red lights
+to measure changes in blood volume in the capillaries of the skin (Allen
+2007).
 
 Physiologically, HR is regulated by the sympathetic and parasympathetic
-nervous systems \citep{pham2021}. An increase in sympathetic activity
-results in HR being sped up (``fight or flight'' response)
-\citep{taelman2009influence}; whereas an increase in parasympathetic
-activity results in HR being slowed down (``rest and digest'' response,
-\citet{battipaglia2015}). Stress or mental and physical strain directly
-increases HR \citep{custodis2014heart, sachs2014}. Therefore, an
-increase in HR can be regarded as an indicator of increasing stress, and
-a decrease as an indicator of relaxation and ease \citep{kyriacou1978}.
-Thus, fitness trackers offer low-cost and unobtrusive access to
-psychological stress data.
+nervous systems (Pham et al. 2021). An increase in sympathetic activity
+results in HR being sped up (``fight or flight'' response) (Taelman et
+al. 2009); whereas an increase in parasympathetic activity results in HR
+being slowed down (``rest and digest'' response, Battipaglia and Lanza
+(2015)). Stress or mental and physical strain directly increases HR
+(Custodis et al. 2014; Sachs 2014). Therefore, an increase in HR can be
+regarded as an indicator of increasing stress, and a decrease as an
+indicator of relaxation and ease (Kyriacou and Sutcliffe 1978). Thus,
+fitness trackers offer low-cost and unobtrusive access to psychological
+stress data.
 
@@
 teaching. For example, teachers' HR tends to increase when teachers take
-an exposed position in student-teacher interaction
-\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021}.
-\citet{sperka1995} for example recorded the HR of 16 pre-service
-teachers during their first lesson and showed that teachers' HR
-increased significantly during teaching. The activation was particularly
-prominent at the beginning of the lesson and decreased over the course
-of the lesson. The authors suggested that pre-service teachers'
-proactive coping strategies, such as actively managing student
-interactions, helped lower their HR levels. Other ECG studies identified
-typical stressors predicting increases in HR, such as class size
-\citep{huang2022class}, or low student engagement and motivation
-\citep{junker2021}. \citet{junker2021} recorded the HR of 40 teachers
-during a real classroom lesson. Again, teacher stress, induced by
-factors such as low student engagement (e.g., lack of motivation or
-interest in tasks) or teacher-centered activities (e.g., teacher-focused
-classroom activities), resulted in elevated HR.
+an exposed position in student-teacher interaction (Sperka and Kittler
+1995; Scheuch and Knothe 1997; Donker, Van Gog, and Mainhard 2018;
+Junker, Donker, and Mainhard 2021). Sperka and Kittler (1995) for
+example recorded the HR of 16 pre-service teachers during their first
+lesson and showed that teachers' HR increased significantly during
+teaching. The activation was particularly prominent at the beginning of
+the lesson and decreased over the course of the lesson. The authors
+suggested that pre-service teachers' proactive coping strategies, such
+as actively managing student interactions, helped lower their HR levels.
+Other ECG studies identified typical stressors predicting increases in
+HR, such as class size (Huang et al. 2022), or low student engagement
+and motivation (Junker, Donker, and Mainhard 2021). Junker, Donker, and
+Mainhard (2021) recorded the HR of 40 teachers during a real classroom
+lesson. Again, teacher stress, induced by factors such as low student
+engagement (e.g., lack of motivation or interest in tasks) or
+teacher-centered activities (e.g., teacher-focused classroom
+activities), resulted in elevated HR.
 
 More recent studies have begun using wrist-worn fitness trackers to
-investigate HR trends in instructional settings
-\citep{Darnell2019, chalmers2021}. \citet{Darnell2019} measured the HR
-of 15 medical college students listening to lectures, using wrist-worn
+investigate HR trends in instructional settings (Darnell and Krieg 2019;
+Chalmers et al. 2021). Darnell and Krieg (2019) measured the HR of 15
+medical college students listening to lectures, using wrist-worn
 devices. The analysis revealed a constant decrease in HR throughout the
-lecture, with HR peaks during more interactive learning phases.
-\citet{chalmers2021} used HR data from a fitness tracker to identify
+lecture, with HR peaks during more interactive learning phases. Chalmers
+et al. (2021) used HR data from a fitness tracker to identify
 physiological changes during stress-inducing tasks (i.e., the Trier
-Social Stress Test; \citet{kirschbaum1993trier}). Average HR increased
-significantly from the resting to the stress inducing phases. Even
-though the participants of these previous studies
-\citep{Darnell2019, chalmers2021} were not teachers but learners, the
-results are relevant for studying teacher stress as they demonstrated
-that HR can be effectively recorded using fitness trackers over the
-course of a whole learning unit, and HR changes are in line with the
-occurrence of activating or stress-inducing tasks.
+Social Stress Test; Kirschbaum, Pirke, and Hellhammer (1993)). Average
+HR increased significantly from the resting to the stress inducing
+phases. Even though the participants of these previous studies (Darnell
+and Krieg 2019; Chalmers et al. 2021) were not teachers but learners,
+the results are relevant for studying teacher stress as they
+demonstrated that HR can be effectively recorded using fitness trackers
+over the course of a whole learning unit, and HR changes are in line
+with the occurrence of activating or stress-inducing tasks.
 
 To the best of our knowledge, only one study has directly assessed
-teachers' HR during teaching using a wrist-worn fitness tracker:
-\citet{runge2020} assessed HR as an indicator of stress in four
+teachers' HR during teaching using a wrist-worn fitness tracker: Runge,
+Haarman, and Fisher (2020) assessed HR as an indicator of stress in four
 in-service teachers during authentic lessons. They used fitness
@@
 experience, with an increase in HR already before the expected stressors
-occur, and with peaks in activating phases
-\citep{Darnell2019, chalmers2021}. For teachers, teacher-centered phases
-led to an increase in HR
-\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021}.
+occur, and with peaks in activating phases (Darnell and Krieg 2019;
+Chalmers et al. 2021). For teachers, teacher-centered phases led to an
+increase in HR (Sperka and Kittler 1995; Scheuch and Knothe 1997;
+Donker, Van Gog, and Mainhard 2018; Junker, Donker, and Mainhard 2021).
 However, there is a lack of studies using teacher-worn fitness trackers
@@
 
-According to \citet{kyriacou1978}, teacher stress can be defined as a
-negative affective response, typically accompanied by physiological
-changes such as increased HR, triggered by job-related demands, and
-perceived as threatening to one's self-esteem or well-being. Coping
-mechanisms help to reduce the perceived threat. Kyriacou's definition of
-teacher stress (see \citet{kyriacou1978} and, for a more recent
-adaptation, \citet{van2006stress}) is based on the transactional stress
-model by Lazarus and colleagues
-\citep{lazarus1966psychological, lazarus1990theory}, which highlights
-the interaction between an individual and the environment, whereby
-stress refers to a person's subjective reaction to an event (a stressor)
-that exceeds the person's adaptive resources.
+According to Kyriacou and Sutcliffe (1978), teacher stress can be
+defined as a negative affective response, typically accompanied by
+physiological changes such as increased HR, triggered by job-related
+demands, and perceived as threatening to one's self-esteem or
+well-being. Coping mechanisms help to reduce the perceived threat.
+Kyriacou's definition of teacher stress (see Kyriacou and Sutcliffe
+(1978) and, for a more recent adaptation, Van Dick (2006)) is based on
+the transactional stress model by Lazarus and colleagues (Lazarus 1966,
+1990), which highlights the interaction between an individual and the
+environment, whereby stress refers to a person's subjective reaction to
+an event (a stressor) that exceeds the person's adaptive resources.
 
@@
 teachers' stress level, according to the adaptation of the Lazarus model
-to teacher stress proposed by \citet{van2006stress}: When potential
-stressors (e.g., classroom disruptions) occur during teaching (1),
-teachers intuitively judge how disruptive the event is in a primary
-appraisal (2). If potential stressors are judged as threatening, i.e.,
-as actual stressors (3), teachers consider whether they have sufficient
-resources for coping with the stressors (4). Teachers utilize these
-resources in trying to cope with the stressors, e.g., by employing
-classroom management strategies (5). In cases when coping fails, stress
-ensues, often accompanied by physiological reactions like increased HR
-(6). As part of the coping process, and dependent on its outcomes,
-teachers re-evaluate the stressor (7).
+to teacher stress proposed by Van Dick (2006): When potential stressors
+(e.g., classroom disruptions) occur during teaching (1), teachers
+intuitively judge how disruptive the event is in a primary appraisal
+(2). If potential stressors are judged as threatening, i.e., as actual
+stressors (3), teachers consider whether they have sufficient resources
+for coping with the stressors (4). Teachers utilize these resources in
+trying to cope with the stressors, e.g., by employing classroom
+management strategies (5). In cases when coping fails, stress ensues,
+often accompanied by physiological reactions like increased HR (6). As
+part of the coping process, and dependent on its outcomes, teachers
+re-evaluate the stressor (7).
 
@@
 managing classroom events, resulting in more complex and problem-focused
-classroom management skills \citep{wolff2021classroom}, and thus more
-effective coping and less stress. Empirically, classroom management
-skills and problem-focused coping styles are linked to fewer instances
-of emotional exhaustion \citep{maslach2001job, clunies2008self}. Novices
-in the teaching profession, on the other hand, face considerable stress
-and often feel overwhelmed by the demands of teaching
-\citep{ophardt2017klassenmanagement, wolff2015keeping, klusmann2012berufliche}
-with many leaving the profession within the first five years
-\citep{ingersoll2003}. Accordingly, when resources are lacking and
-coping fails, negative consequences for health (e.g., burnout) and for
-work (e.g., high turnover rates) can arise
-\citep{jalongo2006, unterbrink2007, aloe2014multivariate}, highlighting
-the importance of professional expertise for managing teacher stress
-\citep{fisher2011}.
+classroom management skills (Wolff, Jarodzka, and Boshuizen 2021), and
+thus more effective coping and less stress. Empirically, classroom
+management skills and problem-focused coping styles are linked to fewer
+instances of emotional exhaustion (Maslach, Schaufeli, and Leiter 2001;
+Clunies-Ross, Little, and Kienhuis 2008). Novices in the teaching
+profession, on the other hand, face considerable stress and often feel
+overwhelmed by the demands of teaching (Ophardt and Thiel 2017; Wolff et
+al. 2015; Klusmann et al. 2012) with many leaving the profession within
+the first five years (Ingersoll and Smith 2003). Accordingly, when
+resources are lacking and coping fails, negative consequences for health
+(e.g., burnout) and for work (e.g., high turnover rates) can arise
+(Jalongo and Heider 2006; Unterbrink et al. 2007; Aloe et al. 2014),
+highlighting the importance of professional expertise for managing
+teacher stress (Fisher 2011).
 
@@
 To measure teachers' HR, we used the wrist-based fitness tracker Fitbit®
-Charge 4. In line with the manufacturer's instructions \citep{fitbitnd},
+Charge 4. In line with the manufacturer's instructions (Fitbit 2020),
 the device was attached to the participants' nondominant hand, a
@@
 each phase (cf.~Fig.\ref{fig.2}). Previous research has indicated that
-10-minute intervals are a useful duration for analyzing PPG data
-\citep{lu2008can}. The intervals were selected based on the following
-rules: The \emph{pre-teaching interval} (\(I_1\)) comprised the first 10
-minutes after the fitness tracker had been put on. The \emph{teaching
-interval} (\(I_2\)) started two minutes after the lesson had started.
-This interval was of the highest relevance to our study. We explicitly
-chose an early 10-minute interval within the teaching phase, as previous
+10-minute intervals are a useful duration for analyzing PPG data (Lu et
+al. 2008). The intervals were selected based on the following rules: The
+\emph{pre-teaching interval} (\(I_1\)) comprised the first 10 minutes
+after the fitness tracker had been put on. The \emph{teaching interval}
+(\(I_2\)) started two minutes after the lesson had started. This
+interval was of the highest relevance to our study. We explicitly chose
+an early 10-minute interval within the teaching phase, as previous
 studies revealed that the beginning of a lesson is most demanding and
 potentially stressful with regards to teacher-student interaction
-\citep{donker2018, claessens2017positive}. The \emph{post-teaching
-interval} (\(I_3\)) started immediately after the end of the teaching
-unit. The \emph{interview interval} (\(I_4\)) was defined as the mid-10
-minutes between the end of the teaching unit and the time point when the
-fitness tracker was taken off. All participants were being interviewed
-during this interval. The end interval (\(I_5\)) comprised the last 10
-minutes before the fitness tracker was taken off.
+(Donker, Van Gog, and Mainhard 2018; Claessens et al. 2017). The
+\emph{post-teaching interval} (\(I_3\)) started immediately after the
+end of the teaching unit. The \emph{interview interval} (\(I_4\)) was
+defined as the mid-10 minutes between the end of the teaching unit and
+the time point when the fitness tracker was taken off. All participants
+were being interviewed during this interval. The end interval (\(I_5\))
+comprised the last 10 minutes before the fitness tracker was taken off.
 
@@
 
-We conducted all analyses with R \citep{RStudio2020}. Graphics were
-created using ggplot2 \citep{ggplot2}.
+We conducted all analyses with R (RStudio Team 2020). Graphics were
+created using ggplot2 (Wickham 2016).
 
@@
   using the geom\_smooth() function from the ggplot2 package in R
-  \citep{ggplot2} based on the smoothing method LOESS (Locally Estimated
+  (Wickham 2016) based on the smoothing method LOESS (Locally Estimated
   Scatterplot Smoothing). This method fits a polynomial surface
@@
 \emph{teaching interval} (\(I_2\)) and the other four intervals by
-planned contrasts and inspection of effect size \(d\)
-\citep{cohen1988statistical}.
+planned contrasts and inspection of effect size \(d\) (Cohen 1988).
 
@@
 standardized HR values over time for each participant. To this end, we
-used fixed intercept fixed slope regression models
-\citep{gelman2006data} for each interval to estimate intercepts and
-linear slopes for each individual, which were then averaged across
-individuals.\footnote{Although this procedure does not account for
-  nonmonotonic progressions in individual HR, a graphical evaluation
-  revealed that the linear estimates corresponded well to the majority
-  of the cases (see Fig.\ref{fig.a3} to \ref{fig.a7} in the
-  supplementary material).} We tested Hypothesis 1b based on the
-unstandardized estimates of mean slopes (one estimate per participant
-per interval).
+used fixed intercept fixed slope regression models (Gelman and Hill
+2006) for each interval to estimate intercepts and linear slopes for
+each individual, which were then averaged across individuals.\footnote{Although
+  this procedure does not account for nonmonotonic progressions in
+  individual HR, a graphical evaluation revealed that the linear
+  estimates corresponded well to the majority of the cases (see
+  Fig.\ref{fig.a3} to \ref{fig.a7} in the supplementary material).} We
+tested Hypothesis 1b based on the unstandardized estimates of mean
+slopes (one estimate per participant per interval).
 
@@
 increases during phases where teachers are in an exposed position
-\citep{sperka1995, scheuch1997psychophysische, donker2018, junker2021},
-as well as with findings showing how HR changes align with activating
-events and stress-inducing tasks \citep{Darnell2019, chalmers2021}.
-
-Building on the model of teacher stress (\citet{kyriacou1978}, see
-Fig.\ref{fig.2}), we had hypothesized that more experienced teachers,
-with better classroom management skills at their disposal, experience
-less physiological stress when dealing with classroom disruptions.
-Contrary to our expectations, we found no buffering effect of teaching
-experience on teachers' HR, i.e., more experienced teachers did not show
-lower mean standardized HR during the stressful teaching phase than less
-experienced teachers. Rather, at least descriptively, we observed the
-opposite trend. There are several possible explanations for this
-finding. First, teaching experience is inherently confounded with age
-(the two variables correlated at \(r = .94\) in our sample), and age has
-been shown to affect indicators of cardiovascular reactivity in various
-ways \citep{uchino2010older}. However, to avoid this kind of confounding
-influence, we had used not raw BPM but rather standardized mean HR for
-all our analyses, thus controlling at least for inter-individual
-differences in mean HR. Second, as research on teacher
+(Sperka and Kittler 1995; Scheuch and Knothe 1997; Donker, Van Gog, and
+Mainhard 2018; Junker, Donker, and Mainhard 2021), as well as with
+findings showing how HR changes align with activating events and
+stress-inducing tasks (Darnell and Krieg 2019; Chalmers et al. 2021).
+
+Building on the model of teacher stress (Kyriacou and Sutcliffe (1978),
+see Fig.\ref{fig.2}), we had hypothesized that more experienced
+teachers, with better classroom management skills at their disposal,
+experience less physiological stress when dealing with classroom
+disruptions. Contrary to our expectations, we found no buffering effect
+of teaching experience on teachers' HR, i.e., more experienced teachers
+did not show lower mean standardized HR during the stressful teaching
+phase than less experienced teachers. Rather, at least descriptively, we
+observed the opposite trend. There are several possible explanations for
+this finding. First, teaching experience is inherently confounded with
+age (the two variables correlated at \(r = .94\) in our sample), and age
+has been shown to affect indicators of cardiovascular reactivity in
+various ways (Uchino, Birmingham, and Berg 2010). However, to avoid this
+kind of confounding influence, we had used not raw BPM but rather
+standardized mean HR for all our analyses, thus controlling at least for
+inter-individual differences in mean HR. Second, as research on teacher
 professionalization has repeatedly shown, professional experience is not
-a guarantee for higher professional knowledge and skills
-\citep{kirschner2016professionswissen}. Rather, honing skills from
-professional experience necessitates a deliberate practice of choosing
-to improve, learning through experience, and integrating new knowledge
-into future performances \citep{dunn1999deliberate}. Thus, rather than
-professional experience alone, more direct assessments of classroom
-management skills, such as objective behavior-based tests, would be a
-better indicator of expertise that future studies could explore.
-Finally, and most importantly, the highly controlled teaching situation
-that we created in the lab might not have provided sufficient
-resemblance to the expert teachers' working conditions to let them
-effectively use their coping resources. In other words, since the
-situation was unfamiliar to both experienced and unexperienced teachers,
-their stress levels might have been more similar than they would have
-been in a more authentic classroom setting.
+a guarantee for higher professional knowledge and skills (Kirschner et
+al. 2016). Rather, honing skills from professional experience
+necessitates a deliberate practice of choosing to improve, learning
+through experience, and integrating new knowledge into future
+performances (Dunn and Shriner 1999). Thus, rather than professional
+experience alone, more direct assessments of classroom management
+skills, such as objective behavior-based tests, would be a better
+indicator of expertise that future studies could explore. Finally, and
+most importantly, the highly controlled teaching situation that we
+created in the lab might not have provided sufficient resemblance to the
+expert teachers' working conditions to let them effectively use their
+coping resources. In other words, since the situation was unfamiliar to
+both experienced and unexperienced teachers, their stress levels might
+have been more similar than they would have been in a more authentic
+classroom setting.
 
@@
 along with slower recovery from stress in older teachers. For instance,
-\citet{ritvanen2006responses} observed that, compared to their younger
+Ritvanen et al. (2006) observed that, compared to their younger
 colleagues, older teachers did not experience a decrease in their HR
 during periods of low stress levels, from which they concluded that
-recovery from stress was insufficient in the older teachers
-\citep{ritvanen2006responses}. Alternatively, the finding could also be
-attributed to the fact that less experienced teachers, due to their
-ongoing or only recently concluded training, may have been more
-accustomed to reflecting on their work and receiving feedback as was the
-case during the SRI, whereas, these activities were less routine and
-possibly more face-threatening for experienced teachers. Therefore, it
-is possible that more experienced teachers found the interview itself to
-be more stressful and therefore showed a higher mean standardized HR
-during this phase.
+recovery from stress was insufficient in the older teachers (Ritvanen et
+al. 2006). Alternatively, the finding could also be attributed to the
+fact that less experienced teachers, due to their ongoing or only
+recently concluded training, may have been more accustomed to reflecting
+on their work and receiving feedback as was the case during the SRI,
+whereas, these activities were less routine and possibly more
+face-threatening for experienced teachers. Therefore, it is possible
+that more experienced teachers found the interview itself to be more
+stressful and therefore showed a higher mean standardized HR during this
+phase.
 
@@
 quite different phenomena, or at least, quite different aspects of the
-multifaceted stress response \citep{kyriacou1978}. In addition, while HR
-was assessed online during teaching, self-reported appraisals were given
-in retrospect during the SRI, and may be subject to biased (e.g.,
-self-serving) reporting or simply an inability to recall ones immediate
-stress reactions.
+multifaceted stress response (Kyriacou and Sutcliffe 1978). In addition,
+while HR was assessed online during teaching, self-reported appraisals
+were given in retrospect during the SRI, and may be subject to biased
+(e.g., self-serving) reporting or simply an inability to recall ones
+immediate stress reactions.
 
@@
 teacher-student relationship, which is a core characteristic of
-effective classroom management \citep{ruedi2014, beaty2010}. In
-addition, the micro-teaching unit was only about 15 minutes long, and
-thus much shorter than a regular school lesson, providing less
-opportunities for experienced teachers to build up an engaging lesson.
-Finally, student behavior was scripted, with classroom disruptions
-following the experimental schedule, irrelevant of the behavior of the
-teacher. Thus, the setting may have masked effects of teaching
-experience by providing too little opportunities of experienced teachers
-to demonstrate their true classroom management skills, in particular
-regarding the prevention of disruptions. In subsequent studies, it would
-therefore be insightful to assess teachers' HR in more authentic
-classroom settings over a longer period of time (e.g., days, weeks, or
-even months). Extended observation of teachers' HR in authentic
-classroom settings could reveal how factors such as student behavior,
-teaching methods, or organizational and administrative demands
+effective classroom management (Rüedi 2014; Beaty-O'Ferrall, Green, and
+Hanna 2010). In addition, the micro-teaching unit was only about 15
+minutes long, and thus much shorter than a regular school lesson,
+providing less opportunities for experienced teachers to build up an
+engaging lesson. Finally, student behavior was scripted, with classroom
+disruptions following the experimental schedule, irrelevant of the
+behavior of the teacher. Thus, the setting may have masked effects of
+teaching experience by providing too little opportunities of experienced
+teachers to demonstrate their true classroom management skills, in
+particular regarding the prevention of disruptions. In subsequent
+studies, it would therefore be insightful to assess teachers' HR in more
+authentic classroom settings over a longer period of time (e.g., days,
+weeks, or even months). Extended observation of teachers' HR in
+authentic classroom settings could reveal how factors such as student
+behavior, teaching methods, or organizational and administrative demands
 contribute to fluctuations in physiological arousal, uncovering insights
@@
 rate variability (HRV) has been demonstrated to be an even more accurate
-indicator of stress \citep{wettstein2020ambulatory}. While standard
-fitness trackers did not provide this measure at the time of our data
+indicator of stress (Wettstein et al. 2020). While standard fitness
+trackers did not provide this measure at the time of our data
 collection, more recent products do offer this function. Thus, future
@@
 important baseline for determining inter- and intrapersonal differences
-in cardiovascular health and reactivity
-\citep{nanchen2018, heneghan2019}. A clean baseline HR requires a
-resting phase without physical movement or emotional stress, ideally
-fifteen minutes before the beginning of the activity, which is very
-difficult to achieve in practice \citep{sammito2015guideline}, e.g.,
-when assessing teacher HR before and during teaching. Thus, our study
-explored the possibility of substituting baseline HR measurement via
-z-standardization within participants. As a result, the absolute
-standardized values of each participant must always be interpreted in
-the context of the standardization sample, and thus are less
-interpretable than individual BPM values together with a baseline HR.
-However, for statistical analyses based on the whole sample, the
-standardization fulfills the aim of controlling for differences in
-individual HR due to, for example, age-related differences. Finally,
-depending on the brand and model of fitness trackers used, the precision
-of the HR measurement varies. Research on the reliability of our
-deployed Fitbit® device has proven that this brand is generally accurate
-in controlled settings and for moderate activity levels
-\citep{wallen2016accuracy, hajj2023, fuller2020, jo2016}, as in our
-study. For example, the Fitbit® fitness tracker has previously shown
-good HR measurement accuracy during resting phases
-\citep{jo2016, muggeridge2021measurement} and for activities such as
-walking, jogging, and running \citep{hajj2023}. At higher exercise
-intensities such as cycling, the Fitbit® tracker may underestimate HR
-\citep{thomson2019heart, montoye2017comparative, jo2016, jachymek2021}
-but is still within an acceptable range according to systematic reviews
-\citep{chevance2022accuracy}. Nevertheless, \citet{gagnon2022} stressed
-that Fitbit® trackers cannot replace ECG when precision is paramount.
-Despite these considerations, the Fitbit® model appears suitable for our
-study purposes, as physical strain was moderate.
+in cardiovascular health and reactivity (Nanchen 2018; Heneghan,
+Venkatraman, and Russell 2019). A clean baseline HR requires a resting
+phase without physical movement or emotional stress, ideally fifteen
+minutes before the beginning of the activity, which is very difficult to
+achieve in practice (Sammito et al. 2015), e.g., when assessing teacher
+HR before and during teaching. Thus, our study explored the possibility
+of substituting baseline HR measurement via z-standardization within
+participants. As a result, the absolute standardized values of each
+participant must always be interpreted in the context of the
+standardization sample, and thus are less interpretable than individual
+BPM values together with a baseline HR. However, for statistical
+analyses based on the whole sample, the standardization fulfills the aim
+of controlling for differences in individual HR due to, for example,
+age-related differences. Finally, depending on the brand and model of
+fitness trackers used, the precision of the HR measurement varies.
+Research on the reliability of our deployed Fitbit® device has proven
+that this brand is generally accurate in controlled settings and for
+moderate activity levels (Wallen et al. 2016; Hajj-Boutros et al. 2023;
+Fuller et al. 2020; Jo et al. 2016), as in our study. For example, the
+Fitbit® fitness tracker has previously shown good HR measurement
+accuracy during resting phases (Jo et al. 2016; Muggeridge et al. 2021)
+and for activities such as walking, jogging, and running (Hajj-Boutros
+et al. 2023). At higher exercise intensities such as cycling, the
+Fitbit® tracker may underestimate HR (Thomson et al. 2019; Montoye,
+Mitrzyk, and Molesky 2017; Jo et al. 2016; Jachymek et al. 2021) but is
+still within an acceptable range according to systematic reviews
+(Chevance et al. 2022). Nevertheless, Gagnon et al. (2022) stressed that
+Fitbit® trackers cannot replace ECG when precision is paramount. Despite
+these considerations, the Fitbit® model appears suitable for our study
+purposes, as physical strain was moderate.
 
@@
 and subjective interpretations of past events, which may be prone to
-various biases such as social desirability \citep{razavi2001self} or
-recall errors \citep{van2016accuracy}. Moreover, stress is not a fixed
-or stable construct; it is a dynamic, constantly evolving affective
-response that can vary depending on context, individual disposition, and
-prior experiences, making it particularly challenging to pinpoint valid
-and reliable process markers for how individuals appraise stress in
-real-time \citep{lazarus1990theory}. While SRIs provide a more detailed
-and reflective understanding of the stressor in question, the delayed
-nature of the response makes it difficult to capture the immediate,
-in-the-moment appraisal that occurs when the stressful event actually
-takes place.
+various biases such as social desirability (Razavi 2001) or recall
+errors (Van den Bergh and Walentynowicz 2016). Moreover, stress is not a
+fixed or stable construct; it is a dynamic, constantly evolving
+affective response that can vary depending on context, individual
+disposition, and prior experiences, making it particularly challenging
+to pinpoint valid and reliable process markers for how individuals
+appraise stress in real-time (Lazarus 1990). While SRIs provide a more
+detailed and reflective understanding of the stressor in question, the
+delayed nature of the response makes it difficult to capture the
+immediate, in-the-moment appraisal that occurs when the stressful event
+actually takes place.
 
@@
 are practical aspects to consider concerning the design, data
-collection, and data analysis phases of research projects \citep[for an
-additional overview, see][]{nelson2020guidelines}:
+collection, and data analysis phases of research projects (for an
+additional overview, see Nelson et al. 2020):
 
@@
 accuracy, such as in medical contexts, as they cannot replace the
-accuracy of ECG measurements \citep{gagnon2022}. Moreover, researchers
+accuracy of ECG measurements (Gagnon et al. 2022). Moreover, researchers
 should consider that measurement accuracy also depends on the intensity
@@
 Fitbit® fitness trackers, for example, underestimate HR at higher
-exercise intensities such as cycling
-\citep{thomson2019heart, montoye2017comparative, jo2016, jachymek2021}.
-For reference, the systematic review by \citet{fuller2020} provides a
+exercise intensities such as cycling (Thomson et al. 2019; Montoye,
+Mitrzyk, and Molesky 2017; Jo et al. 2016; Jachymek et al. 2021). For
+reference, the systematic review by Fuller et al. (2020) provides a
 detailed overview of studies that used wrist-worn fitness trackers
@@
 stressful situations and allow for early self-intervention such as
-mindfulness techniques (e.g., deep breathing or body scans;
-\citet{agyapong2023interventions}). Integrating fitness trackers into
-teacher training and everyday practice could offer an affordable and
-practical method for assessing and managing teacher stress. In teacher
-training as well as in research, triangulating data from fitness
-trackers, lesson videos, and interviews could provide teachers with
-insights into their own stress management, and foster the implementation
-of effective stress and classroom management strategies. Taken together,
-our findings cater to \citet{wettstein2021} call for the use of
-ambulatory assessment methods, particularly in the context of classroom
-disruptions, for gaining a deeper understanding of teacher stress and
-its impact on both psychological and physiological variables.
+mindfulness techniques (e.g., deep breathing or body scans; Agyapong et
+al. (2023)). Integrating fitness trackers into teacher training and
+everyday practice could offer an affordable and practical method for
+assessing and managing teacher stress. In teacher training as well as in
+research, triangulating data from fitness trackers, lesson videos, and
+interviews could provide teachers with insights into their own stress
+management, and foster the implementation of effective stress and
+classroom management strategies. Taken together, our findings cater to
+Wettstein et al. (2021) call for the use of ambulatory assessment
+methods, particularly in the context of classroom disruptions, for
+gaining a deeper understanding of teacher stress and its impact on both
+psychological and physiological variables.
 
@@
 
-\bibliography{r-references.bib}
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-agyapong2023interventions}
+Agyapong, B., P. Brett-MacLean, L. Burback, V. I. O. Agyapong, and Y.
+Wei. 2023. {``Interventions to Reduce Stress and Burnout Among Teachers:
+A Scoping Review.''} \emph{International Journal of Environmental
+Research and Public Health} 20 (9): 5625.
+\url{https://doi.org/10.3390/ijerph20095625}.
+
+\bibitem[\citeproctext]{ref-allen2007photoplethysmography}
+Allen, J. 2007. {``Photoplethysmography and Its Application in Clinical
+Physiological Measurement.''} \emph{Physiological Measurement} 28 (3):
+R1. \url{https://doi.org/10.1088/0967-3334/28/3/R01}.
+
+\bibitem[\citeproctext]{ref-aloe2014multivariate}
+Aloe, A. M., S. M. Shisler, B. D. Norris, A. B. Nickerson, and T. W.
+Rinker. 2014. {``A Multivariate Meta-Analysis of Student Misbehavior and
+Teacher Burnout.''} \emph{Educational Research Review} 12: 30--44.
+\url{https://doi.org/10.1016/j.edurev.2014.05.003}.
+
+\bibitem[\citeproctext]{ref-battipaglia2015}
+Battipaglia, I., and G. A. Lanza. 2015. {``The Autonomic Nervous System
+of the Heart.''} In \emph{Autonomic Innervation of the Heart: Role of
+Molecular Imaging}, edited by R. H. J. A. Slart, R. A. Tio, P. H.
+Elsinga, and M. Schwaiger, 1--12. Berlin, Heidelberg: Springer Berlin
+Heidelberg. \url{https://doi.org/10.1007/978-3-662-45074-1_1}.
+
+\bibitem[\citeproctext]{ref-beaty2010}
+Beaty-O'Ferrall, M. E., A. Green, and F. Hanna. 2010. {``Classroom
+Management Strategies for Difficult Students: Promoting Change Through
+Relationships.''} \emph{Middle School Journal} 41 (4): 4--11.
+\url{https://doi.org/10.2307/23044778}.
+
+\bibitem[\citeproctext]{ref-berntson2007cardiovascular}
+Berntson, G., K. Quigley, and D. Lozano. 2007. {``Cardiovascular
+Psychophysiology.''} \emph{Handbook of Psychophysiology} 3: 182--210.
+\url{https://doi.org/10.1017/CBO9780511546396.008}.
+
+\bibitem[\citeproctext]{ref-boyle1995structural}
+Boyle, G. J., M. G. Borg, J. M. Falzon, and A. J. Baglioni Jr. 1995.
+{``A Structural Model of the Dimensions of Teacher Stress.''}
+\emph{British Journal of Educational Psychology} 65 (1): 49--67.
+\url{https://doi.org/10.1111/j.2044-8279.1995.tb01130.x}.
+
+\bibitem[\citeproctext]{ref-castaneda2018review}
+Castaneda, D., A. Esparza, M. Ghamari, C. Soltanpur, and H. Nazeran.
+2018. {``A Review on Wearable Photoplethysmography Sensors and Their
+Potential Future Applications in Health Care.''} \emph{International
+Journal of Biosensors \& Bioelectronics} 4 (4): 195.
+\url{https://doi.org/10.15406/ijbsbe.2018.04.00125}.
+
+\bibitem[\citeproctext]{ref-chalmers2021}
+Chalmers, T., B. A. Hickey, P. Newton, C. Lin, D. Sibbritt, C. S.
+McLachlan, R. Clifton-Bligh, J. Morley, and S. Lal. 2021. {``Stress
+Watch: The Use of Heart Rate and Heart Rate Variability to Detect
+Stress: A Pilot Study Using Smart Watch Wearables.''} \emph{Sensors} 22
+(1): 151. \url{https://doi.org/10.3390/s22010151}.
+
+\bibitem[\citeproctext]{ref-chaplain2008}
+Chaplain, R. P. 2008. {``Stress and Psychological Distress Among Trainee
+Secondary Teachers in England.''} \emph{Educational Psychology} 28 (2):
+195--209. \url{https://doi.org/10.1080/01443410701491858}.
+
+\bibitem[\citeproctext]{ref-chevance2022accuracy}
+Chevance, G., N. M. Golaszewski, E. Tipton, E. B. Hekler, M. Buman, G.
+J. Welk, K. Patrick, J. G. Godino, et al. 2022. {``Accuracy and
+Precision of Energy Expenditure, Heart Rate, and Steps Measured by
+Combined-Sensing Fitbits Against Reference Measures: Systematic Review
+and Meta-Analysis.''} \emph{JMIR mHealth and uHealth} 10 (4): e35626.
+\url{https://doi.org/10.2196/35626}.
+
+\bibitem[\citeproctext]{ref-claessens2017positive}
+Claessens, L. C. A., J. van Tartwijk, A. C. van der Want, H. J. M.
+Pennings, N. Verloop, P. J. den Brok, and T. Wubbels. 2017. {``Positive
+Teacher--Student Relationships Go Beyond the Classroom, Problematic Ones
+Stay Inside.''} \emph{The Journal of Educational Research} 110 (5):
+478--93. \url{https://doi.org/10.1080/00220671.2015.1129595}.
+
+\bibitem[\citeproctext]{ref-clunies2008self}
+Clunies-Ross, P., E. Little, and M. Kienhuis. 2008. {``Self-Reported and
+Actual Use of Proactive and Reactive Classroom Management Strategies and
+Their Relationship with Teacher Stress and Student Behaviour.''}
+\emph{Educational Psychology} 28 (6): 693--710.
+\url{https://doi.org/10.1080/01443410802206700}.
+
+\bibitem[\citeproctext]{ref-cohen1988statistical}
+Cohen, J. 1988. {``Statistical Power for the Behavioural Sciences.
+Hilsdale.''} \emph{NY: Lawrence Erlbaum} 58 (1): 7--19.
+
+\bibitem[\citeproctext]{ref-custodis2014heart}
+Custodis, F., J. C. Reil, S. H. Schirmer, O. Adam, S. Möhlenkamp, U.
+Laufs, and M. Boehm. 2014. {``Heart Rate: Clinical Variable and Risk
+Marker.''} \emph{Deutsche Medizinische Wochenschrift (1946)} 139 (33):
+1661--68. \url{https://doi.org/10.1055/s-0034-1370223}.
+
+\bibitem[\citeproctext]{ref-Darnell2019}
+Darnell, D., and P. Krieg. 2019. {``Student Engagement, Assessed Using
+Heart Rate, Shows No Reset Following Active Learning Sessions in
+Lectures.''} \emph{PLoS ONE} 14.
+\url{https://doi.org/10.1371/journal.pone.0225709}.
+
+\bibitem[\citeproctext]{ref-donker2018}
+Donker, M. H., T. Van Gog, and M. T. Mainhard. 2018. {``A Quantitative
+Exploration of Two Teachers with Contrasting Emotions: Intra-Individual
+Process Analyses of Physiology and Interpersonal Behavior.''}
+\emph{Frontline Learning Research} 6 (3): 162--84.
+\url{https://doi.org/10.14786/flr.v6i3.372}.
+
+\bibitem[\citeproctext]{ref-dunn1999deliberate}
+Dunn, T. G., and C. Shriner. 1999. {``Deliberate Practice in Teaching:
+What Teachers Do for Self-Improvement.''} \emph{Teaching and Teacher
+Education} 15 (6): 631--51.
+\url{https://doi.org/10.1016/S0742-051X(98)00068-7}.
+
+\bibitem[\citeproctext]{ref-ferguson2015}
+Ferguson, T., A. V. Rowlands, T. Olds, and C. Maher. 2015. {``The
+Validity of Consumer-Level, Activity Monitors in Healthy Adults Worn in
+Free-Living Conditions: A Cross-Sectional Study.''} \emph{International
+Journal of Behavioral Nutrition and Physical Activity} 12 (1): 1--9.
+\url{https://doi.org/10.1186/s12966-015-0201-9}.
+
+\bibitem[\citeproctext]{ref-fisher2011}
+Fisher, M. H. 2011. {``Factors Influencing Stress, Burnout, and
+Retention of Secondary Teachers.''} \emph{Current Issues in Education}
+14 (1).
+
+\bibitem[\citeproctext]{ref-fitbitnd}
+Fitbit, Inc. 2020. \emph{Fitbit Charge 4 User Manual Version 1.2}.
+Fitbit, Inc.
+
+\bibitem[\citeproctext]{ref-fuller2020}
+Fuller, D., E. Colwell, J. Low, K. Orychock, M. A. Tobin, B. Simango, R.
+Buote, et al. 2020. {``Reliability and Validity of Commercially
+Available Wearable Devices for Measuring Steps, Energy Expenditure, and
+Heart Rate: Systematic Review.''} \emph{JMIR mHealth and uHealth} 8 (9):
+e18694. \url{https://doi.org/10.2196/18694}.
+
+\bibitem[\citeproctext]{ref-gagnon2022}
+Gagnon, J., M. Khau, L. Lavoie-Hudon, F. Vachon, V. Drapeau, and S.
+Tremblay. 2022. {``Comparing a Fitbit Wearable to an Electrocardiogram
+Gold Standard as a Measure of Heart Rate Under Psychological Stress: A
+Validation Study.''} \emph{JMIR Formative Research} 6 (12): e37885.
+\url{https://doi.org/10.2196/37885}.
+
+\bibitem[\citeproctext]{ref-gelman2006data}
+Gelman, A., and J. Hill. 2006. \emph{Data Analysis Using Regression and
+Multilevel/Hierarchical Models}. Cambridge university press.
+\url{https://doi.org/10.1017/CBO9780511790942}.
+
+\bibitem[\citeproctext]{ref-godfrey2018z}
+Godfrey, A., V. Hetherington, H. Shum, P. Bonato, N. H. Lovell, and S.
+Stuart. 2018. {``From a to z: Wearable Technology Explained.''}
+\emph{Maturitas} 113: 40--47.
+\url{https://doi.org/10.1016/j.maturitas.2018.04.012}.
+
+\bibitem[\citeproctext]{ref-hajj2023}
+Hajj-Boutros, G., M. Landry-Duval, A. S. Comtois, G. Gouspillou, and A.
+D. Karelis. 2023. {``Wrist-Worn Devices for the Measurement of Heart
+Rate and Energy Expenditure: A Validation Study for the Apple Watch 6,
+Polar Vantage v and Fitbit Sense.''} \emph{European Journal of Sport
+Science} 23 (2): 165--77.
+\url{https://doi.org/10.1080/17461391.2021.2023656}.
+
+\bibitem[\citeproctext]{ref-hao2018chrv}
+Hao, T., H. Chang, M. Ball, K. Lin, and X. Zhu. 2017. {``cHRV Uncovering
+Daily Stress Dynamics Using Bio-Signal from Consumer Wearables.''} In
+\emph{MEDINFO 2017: Precision Healthcare Through Informatics}, 98--102.
+IOS Press. \url{https://doi.org/10.3233/978-1-61499-830-3-98}.
+
+\bibitem[\citeproctext]{ref-heneghan2019}
+Heneghan, C., S. Venkatraman, and A. Russell. 2019. {``Investigation of
+an Estimate of Daily Resting Heart Rate Using a Consumer Wearable
+Device.''} \emph{medRxiv}, 19008771.
+\url{https://doi.org/10.1101/19008771}.
+
+\bibitem[\citeproctext]{ref-herman2020}
+Herman, K. C., S. L. Prewett, C. L. Eddy, A. Savala, and W. M. Reinke.
+2020. {``Profiles of Middle School Teacher Stress and Coping: Concurrent
+and Prospective Correlates.''} \emph{Journal of School Psychology} 78:
+54--68. \url{https://doi.org/10.1016/j.jsp.2019.11.003}.
+
+\bibitem[\citeproctext]{ref-hottenrott2007}
+Hottenrot, K. 2007. \emph{Trainingskontrolle: Mit
+Herzfrequenz-Messgeräten, 2. Auflage}. Meyer \& Meyer Verlag.
+
+\bibitem[\citeproctext]{ref-huang2022class}
+Huang, Y., E. Richter, T. Kleickmann, and D. Richter. 2022. {``Class
+Size Affects Preservice Teachers' Physiological and Psychological Stress
+Reactions: An Experiment in a Virtual Reality Classroom.''}
+\emph{Computers \& Education} 184: 104503.
+\url{https://doi.org/10.1016/j.compedu.2022.104503}.
+
+\bibitem[\citeproctext]{ref-ingersoll2003}
+Ingersoll, R. M., and T. M. Smith. 2003. {``The Wrong Solution to the
+Teacher Shortage.''} \emph{Educational Leadership} 60 (8): 30--33.
+
+\bibitem[\citeproctext]{ref-jachymek2021}
+Jachymek, M., M. T. Jachymek, R. M. Kiedrowicz, J. Kaźmierczak, E.
+Płońska-Gościniak, and M. Peregud-Pogorzelska. 2021. {``Wristbands in
+Home-Based Rehabilitation---Validation of Heart Rate Measurement.''}
+\emph{Sensors} 22 (1): 60. \url{https://doi.org/10.3390/s22010060}.
+
+\bibitem[\citeproctext]{ref-jalongo2006}
+Jalongo, M. R., and K. Heider. 2006. {``Editorial Teacher Attrition: An
+Issue of National Concern.''} \emph{Early Childhood Education Journal}
+33: 379--80. \url{https://doi.org/10.1007/s10643-006-0122-y}.
+
+\bibitem[\citeproctext]{ref-jo2016}
+Jo, E., K. Lewis, D. Directo, M. J. Kim, and B. A. Dolezal. 2016.
+{``Validation of Biofeedback Wearables for Photoplethysmographic Heart
+Rate Tracking.''} \emph{Journal of Sports Science \& Medicine} 15 (3):
+540.
+
+\bibitem[\citeproctext]{ref-johnson2005experience}
+Johnson, S., C. Cooper, S. Cartwright, I. Donald, P. Taylor, and C.
+Millet. 2005. {``The Experience of Work-Related Stress Across
+Occupations.''} \emph{Journal of Managerial Psychology} 20 (2): 178--87.
+\url{https://doi.org/10.1108/02683940510579803}.
+
+\bibitem[\citeproctext]{ref-junker2021}
+Junker, R., M. H. Donker, and T. Mainhard. 2021. {``Potential Classroom
+Stressors of Teachers: An Audiovisual and Physiological Approach.''}
+\emph{Learning and Instruction} 75: 101495.
+\url{https://doi.org/10.1016/j.learninstruc.2021.101495}.
+
+\bibitem[\citeproctext]{ref-karner2021teachers}
+Kärner, T., and J. Höning. 2021. {``Teachers' Experienced Classroom
+Demands and Autonomic Stress Reactions: Results of a Pilot Study and
+Implications for Process-Oriented Research in Vocational Education and
+Training.''} \emph{Empirical Research in Vocational Education and
+Training} 13: 1--22. \url{https://doi.org/10.1186/s40461-021-00113-3}.
+
+\bibitem[\citeproctext]{ref-kirschbaum1993trier}
+Kirschbaum, C., K. M. Pirke, and D. H. Hellhammer. 1993. {``The {`Trier
+Social Stress Test'}--a Tool for Investigating Psychobiological Stress
+Responses in a Laboratory Setting.''} \emph{Neuropsychobiology} 28
+(1-2): 76--81. \url{https://doi.org/10.1159/000119004}.
+
+\bibitem[\citeproctext]{ref-kirschner2016professionswissen}
+Kirschner, S., M. Sczudlek, O. Tepner, A. Borowski, H. E. Fischer, G.
+Lenske, D. Leutner, et al. 2016. {``Professionswissen in Den
+Naturwissenschaften (ProwiN).''} In \emph{Entwicklung von
+Professionalit{ä}t p{ä}dagogischen Personals: Interdisziplin{ä}re
+Betrachtungen, Befunde Und Perspektiven}, 113--30. Springer.
+\url{https://doi.org/10.1007/978-3-658-07274-2_7}.
+
+\bibitem[\citeproctext]{ref-klusmann2012berufliche}
+Klusmann, U., M. Kunter, T. Voss, and J. Baumert. 2012. {``Berufliche
+Beanspruchung Angehender Lehrkr{ä}fte: Die Effekte von Pers{ö}nlichkeit,
+p{ä}dagogischer Vorerfahrung Und Professioneller Kompetenz.''}
+\emph{Zeitschrift f{ü}r p{ä}dagogische Psychologie}.
+\url{https://doi.org/10.1024/1010-0652/a000078}.
+
+\bibitem[\citeproctext]{ref-kranjec2014non}
+Kranjec, J., S. Beguš, G. Geršak, and J. Drnovšek. 2014. {``Non-Contact
+Heart Rate and Heart Rate Variability Measurements: A Review.''}
+\emph{Biomedical Signal Processing and Control} 13: 102--12.
+\url{https://doi.org/10.1016/j.bspc.2014.03.004}.
+
+\bibitem[\citeproctext]{ref-kyriacou1978}
+Kyriacou, C., and J. Sutcliffe. 1978. {``Teacher Stress: Prevalence,
+Sources, and Symptoms.''} \emph{British Journal of Educational
+Psychology} 48 (2): 159--67.
+\url{https://doi.org/10.1111/j.2044-8279.1978.tb02381.x}.
+
+\bibitem[\citeproctext]{ref-lazarus1966psychological}
+Lazarus, R. S. 1966. {``Psychological Stress and the Coping Process.''}
+\emph{Mc Grew-Hill}.
+
+\bibitem[\citeproctext]{ref-lazarus1990theory}
+---------. 1990. {``Theory-Based Stress Measurement.''}
+\emph{Psychological Inquiry} 1 (1): 3--13.
+\url{https://doi.org/10.1207/s15327965pli0101_1}.
+
+\bibitem[\citeproctext]{ref-liu2020}
+Liu, M., and Y. Yan. 2020. {``Anxiety and Stress in in-Service Chinese
+University Teachers of Arts.''} \emph{International Journal of Higher
+Education} 9 (1): 237--48. \url{https://doi.org/10.5430/ijhe.v9n1p237}.
+
+\bibitem[\citeproctext]{ref-lu2008can}
+Lu, S., H. Zhao, K. Ju, K. Shin, M. Lee, K. Shelley, and K. H. Chon.
+2008. {``Can Photoplethysmography Variability Serve as an Alternative
+Approach to Obtain Heart Rate Variability Information?''} \emph{Journal
+of Clinical Monitoring and Computing} 22 (1): 23--29.
+\url{https://doi.org/10.1007/s10877-007-9103-y}.
+
+\bibitem[\citeproctext]{ref-maslach2001job}
+Maslach, C., W. B. Schaufeli, and M. P. Leiter. 2001. {``Job Burnout.''}
+\emph{Annual Review of Psychology} 52 (1): 397--422.
+\url{https://doi.org/10.1146/annurev.psych.52.1.397}.
+
+\bibitem[\citeproctext]{ref-montgomery2005meta}
+Montgomery, C., and A. A. Rupp. 2005. {``A Meta-Analysis for Exploring
+the Diverse Causes and Effects of Stress in Teachers.''} \emph{Canadian
+Journal of Education/Revue Canadienne de l'{é}ducation}, 458--86.
+\url{https://doi.org/10.2307/4126479}.
+
+\bibitem[\citeproctext]{ref-montoye2017comparative}
+Montoye, A. H. K., J. R. Mitrzyk, and M. J. Molesky. 2017.
+{``Comparative Accuracy of a Wrist-Worn Activity Tracker and a Smart
+Shirt for Physical Activity Assessment.''} \emph{Measurement in Physical
+Education and Exercise Science} 21 (4): 201--11.
+\url{https://doi.org/10.1080/1091367X.2017.1331166}.
+
+\bibitem[\citeproctext]{ref-muggeridge2021measurement}
+Muggeridge, D. J., K. Hickson, A. V. Davies, O. M. Giggins, I. L.
+Megson, T. Gorely, and D. R. Crabtree. 2021. {``Measurement of Heart
+Rate Using the Polar OH1 and Fitbit Charge 3 Wearable Devices in Healthy
+Adults During Light, Moderate, Vigorous, and Sprint-Based Exercise:
+Validation Study.''} \emph{JMIR mHealth and uHealth} 9 (3): e25313.
+\url{https://doi.org/10.2196/25313}.
+
+\bibitem[\citeproctext]{ref-mukhopadhyay2017wearable}
+Mukhopadhyay, S. C., and T. Islam. 2017. \emph{Wearable Sensors:
+Applications, Design and Implementation}. IOP Publishing.
+\url{https://doi.org/10.1088/978-0-7503-1505-0}.
+
+\bibitem[\citeproctext]{ref-nanchen2018}
+Nanchen, D. 2018. {``Resting Heart Rate: What Is Normal?''}
+\emph{Heart}. BMJ Publishing Group Ltd; British Cardiovascular Society.
+\url{https://doi.org/10.1136/heartjnl-2017-312731}.
+
+\bibitem[\citeproctext]{ref-nelson2020guidelines}
+Nelson, B. W., C. A. Low, N. Jacobson, P. Areán, J. Torous, and N. B.
+Allen. 2020. {``Guidelines for Wrist-Worn Consumer Wearable Assessment
+of Heart Rate in Biobehavioral Research.''} \emph{NPJ Digital Medicine}
+3 (1): 90. \url{https://doi.org/10.1038/s41746-020-0297-4}.
+
+\bibitem[\citeproctext]{ref-nuss2021effects}
+Nuss, K., K. Moore, T. Nelson, and K. Li. 2021. {``Effects of
+Motivational Interviewing and Wearable Fitness Trackers on Motivation
+and Physical Activity: A Systematic Review.''} \emph{American Journal of
+Health Promotion} 35 (2): 226--35.
+\url{https://doi.org/10.1177/0890117120939030}.
+
+\bibitem[\citeproctext]{ref-ophardt2017klassenmanagement}
+Ophardt, D., and F. Thiel. 2017. {``Klassenmanagement Als Basisdimension
+Der Unterrichtsqualit{ä}t.''} \emph{Lehrer-Sch{ü}ler-Interaktion:
+Inhaltsfelder, Forschungsperspektiven Und Methodische Zug{ä}nge},
+245--66.
+
+\bibitem[\citeproctext]{ref-peng2022acceptance}
+Peng, C., N. Xi, H. Zhao, and J. Hamari. 2022. {``Acceptance of Wearable
+Technology: A Meta-Analysis.''} In \emph{Hawaii International Conference
+on System Sciences}, 5101--10.
+\url{https://doi.org/10.24251/HICSS.2022.621}.
+
+\bibitem[\citeproctext]{ref-pham2021}
+Pham, T., Z. J. Lau, S. H. A. Chen, and D. Makowski. 2021. {``Heart Rate
+Variability in Psychology: A Review of HRV Indices and an Analysis
+Tutorial.''} \emph{Sensors} 21 (12): 3998.
+\url{https://doi.org/10.3390/s21123998}.
+
+\bibitem[\citeproctext]{ref-razavi2001self}
+Razavi, T. 2001. {``Self-Report Measures: An Overview of Concerns and
+Limitations of Questionnaire Use in Occupational Stress Research.''}
+
+\bibitem[\citeproctext]{ref-ritvanen2006responses}
+Ritvanen, T., V. Louhevaara, P. Helin, S. Väisänen, and O. Hänninen.
+2006. {``Responses of the Autonomic Nervous System During Periods of
+Perceived High and Low Work Stress in Younger and Older Female
+Teachers.''} \emph{Applied Ergonomics} 37 (3): 311--18.
+\url{https://doi.org/10.1016/j.apergo.2005.06.013}.
+
+\bibitem[\citeproctext]{ref-RStudio2020}
+RStudio Team. 2020. \emph{RStudio: Integrated Development Environment
+for r}. Boston, MA: RStudio, PBC.
+
+\bibitem[\citeproctext]{ref-ruedi2014}
+Rüedi, J. 2014. {``Zur Bedeutung Positive Beziehungen f{ü}r Die
+Klassenf{ü}hrung Und Den Umgang Mit Unterrichtsst{ö}rungen.''}
+\emph{Beziehungen in Schule Und Unterricht. Teil} 3: 105--26.
+
+\bibitem[\citeproctext]{ref-runge2020}
+Runge, N., S. Haarman, and M. Fisher. 2020. {``Using Fitbit Fitness
+Trackers to Measure Teacher Stress and Coping.''} \emph{International
+Journal of Social Policy and Education} 2: 56--70.
+
+\bibitem[\citeproctext]{ref-sachs2014}
+Sachs, S. 2014. {``Physiologische Parameter Zur Bewertung Der
+Lernwirksamkeit von Lernsituationen.''} PhD thesis, Universit{ä}t Ulm.
+
+\bibitem[\citeproctext]{ref-sammito2015guideline}
+Sammito, S., B. Thielmann, R. Seibt, A. Klussmann, M. Weippert, and I.
+Böckelmann. 2015. {``Guideline for the Application of Heart Rate and
+Heart Rate Variability in Occupational Medicine and Occupational
+Science.''} \emph{ASU Int} 2015 (06): 1--29.
+\url{https://doi.org/10.17147/ASUI.2015-06-09-03}.
+
+\bibitem[\citeproctext]{ref-scalise2018wearables}
+Scalise, L., and G. Cosoli. 2018. {``Wearables for Health and Fitness:
+Measurement Characteristics and Accuracy.''} In \emph{2018 IEEE
+International Instrumentation and Measurement Technology Conference
+(I2MTC)}, 1--6. IEEE. \url{https://doi.org/10.1109/I2MTC.2018.8409635}.
+
+\bibitem[\citeproctext]{ref-scheuch1997psychophysische}
+Scheuch, K., and M. Knothe. 1997. {``Psychophysische Beanspruchung von
+Lehrern in Der Unterrichtst{ä}tigkeit.''} \emph{Jahrbuch f{ü}r
+Lehrerforschung} 1 (S 285): 299.
+
+\bibitem[\citeproctext]{ref-schult2014belastet}
+Schult, J., M. Münzer-Schrobildgen, and J. R. Sparfeldt. 2014.
+{``Belastet, Aber Hochzufrieden?''} \emph{Zeitschrift f{ü}r
+Gesundheitspsychologie}.
+\url{https://doi.org/10.1026/0943-8149/a000114}.
+
+\bibitem[\citeproctext]{ref-smith2000}
+Smith, A. 2000. {``The Scale of Perceived Occupational Stress.''}
+\emph{Occupational Medicine} 50 (5): 294--98.
+\url{https://doi.org/10.1093/occmed/50.5.294}.
+
+\bibitem[\citeproctext]{ref-sperka1995}
+Sperka, M., and U.. Kittler. 1995. {``Psychophysiologische Beanspruchung
+von Lehramtskandidatinnen Und -Kandidaten Im Schulunterricht.''} In
+\emph{Psychische Potentiale Für Eine Interdisziplinäre Lehrerausbildung:
+Motivation - Kognition -- Entwicklung}, edited by K. Bräuer, 182--97.
+Essen: Die Blaue Eule.
+
+\bibitem[\citeproctext]{ref-taelman2009influence}
+Taelman, J., S. Vandeput, A. Spaepen, and S. Van Huffel. 2009.
+{``Influence of Mental Stress on Heart Rate and Heart Rate
+Variability.''} In \emph{4th European Conference of the International
+Federation for Medical and Biological Engineering}, 1366--69. Springer.
+\url{https://doi.org/10.1007/978-3-540-89208-3_324}.
+
+\bibitem[\citeproctext]{ref-thomson2019heart}
+Thomson, E. A., K. Nuss, A. Comstock, S. Reinwald, S. Blake, R. E.
+Pimentel, B. L. Tracy, and K. Li. 2019. {``Heart Rate Measures from the
+Apple Watch, Fitbit Charge HR 2, and Electrocardiogram Across Different
+Exercise Intensities.''} \emph{Journal of Sports Sciences} 37 (12):
+1411--19. \url{https://doi.org/10.1080/02640414.2018.1560644}.
+
+\bibitem[\citeproctext]{ref-trull2013ambulatory}
+Trull, T. J., and U. Ebner-Priemer. 2013. {``Ambulatory Assessment.''}
+\emph{Annual Review of Clinical Psychology} 9 (1): 151--76.
+\url{https://doi.org/10.1146/annurev-clinpsy-050212-185510}.
+
+\bibitem[\citeproctext]{ref-uchino2010older}
+Uchino, B. N., W. Birmingham, and C. A. Berg. 2010. {``Are Older Adults
+Less or More Physiologically Reactive? A Meta-Analysis of Age-Related
+Differences in Cardiovascular Reactivity to Laboratory Tasks.''}
+\emph{Journals of Gerontology Series B: Psychological Sciences and
+Social Sciences} 65 (2): 154--62.
+\url{https://doi.org/10.1093/geronb/gbp127}.
+
+\bibitem[\citeproctext]{ref-unterbrink2007}
+Unterbrink, T., A. Hack, R. Pfeifer, V. Buhl-Grießhaber, U. Müller, H.
+Wesche, M. Frommhold, et al. 2007. {``Burnout and
+Effort--Reward-Imbalance in a Sample of 949 German Teachers.''}
+\emph{International Archives of Occupational and Environmental Health}
+80: 433--41. \url{https://doi.org/10.1007/s00420-007-0169-0}.
+
+\bibitem[\citeproctext]{ref-van2016accuracy}
+Van den Bergh, O., and M. Walentynowicz. 2016. {``Accuracy and Bias in
+Retrospective Symptom Reporting.''} \emph{Current Opinion in Psychiatry}
+29 (5): 302--8. \url{https://doi.org/10.1097/YCO.0000000000000267}.
+
+\bibitem[\citeproctext]{ref-van2006stress}
+Van Dick, R. 2006. {``Stress Und Arbeitszufriedenheit Bei Lehrerinnen
+Und Lehrern.''} \emph{Zwischen „Horrorjob ``Und Erf{ü}llung} 2.
+
+\bibitem[\citeproctext]{ref-wallen2016accuracy}
+Wallen, M. P., S. R. Gomersall, S. E. Keating, U. Wisløff, and J. S.
+Coombes. 2016. {``Accuracy of Heart Rate Watches: Implications for
+Weight Management.''} \emph{PloS One} 11 (5): e0154420.
+\url{https://doi.org/10.1371/journal.pone.0154420}.
+
+\bibitem[\citeproctext]{ref-wettstein2020ambulatory}
+Wettstein, A., F. Kühne, W. Tschacher, and R. La Marca. 2020.
+{``Ambulatory Assessment of Psychological and Physiological Stress on
+Workdays and Free Days Among Teachers. A Preliminary Study.''}
+\emph{Frontiers in Neuroscience} 14: 495378.
+\url{https://doi.org/10.3389/fnins.2020.00112}.
+
+\bibitem[\citeproctext]{ref-wettstein2021}
+Wettstein, A., S. Schneider, M. Grosse Holtforth, and R. La Marca. 2021.
+{``Teacher {Stress}: {A} {Psychobiological} {Approach} to {Stressful}
+{Interactions} in the {Classroom}.''} \emph{Frontiers in Education} 6.
+\url{https://doi.org/10.3389/feduc.2021.681258}.
+
+\bibitem[\citeproctext]{ref-ggplot2}
+Wickham, H. 2016. \emph{Ggplot2: Elegant Graphics for Data Analysis}.
+Springer-Verlag New York.
+\url{https://doi.org/10.1007/978-0-387-98141-3}.
+
+\bibitem[\citeproctext]{ref-wolff2015keeping}
+Wolff, C. E., N. van den Bogert, H. Jarodzka, and H. P. A. Boshuizen.
+2015. {``Keeping an Eye on Learning: Differences Between Expert and
+Novice Teachers' Representations of Classroom Management Events.''}
+\emph{Journal of Teacher Education} 66 (1): 68--85.
+\url{https://doi.org/10.1177/0022487114549810}.
+
+\bibitem[\citeproctext]{ref-wolff2021classroom}
+Wolff, C. E., H. Jarodzka, and H. P. A. Boshuizen. 2021. {``Classroom
+Management Scripts: A Theoretical Model Contrasting Expert and Novice
+Teachers' Knowledge and Awareness of Classroom Events.''}
+\emph{Educational Psychology Review} 33 (1): 131--48.
+\url{https://doi.org/10.1007/s10648-020-09542-0}.
+
+\end{CSLReferences}
 

### 2024-11-07 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd

@@
 round(d_number_stud, 2)
+
+```
+
+#### 2.2.2 Number of fixations per minute (AOI others)
+```{r nof_others, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### NUMBER OF FIXATIONS (AOI others) ########################
+
+# filter group & total duration & number fixation (AOI others)
+df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select (
+    Group,
+    Duration_of_interval,
+    Participant,
+    "Total_duration_of_fixations.Board_Screen",
+    "Total_duration_of_fixations.Classroom_Others",
+    "Total_duration_of_fixations.Material_Students",
+    "Total_duration_of_fixations.Material_Teacher",
+    "Total_duration_of_fixations.Nametag_Anna",
+    "Total_duration_of_fixations.Nametag_Bianca",
+    "Total_duration_of_fixations.Nametag_Carl(a)",
+    "Number_of_fixations.Board_Screen",
+    "Number_of_fixations.Classroom_Others",
+    "Number_of_fixations.Material_Students",
+    "Number_of_fixations.Material_Teacher",
+    "Number_of_fixations.Nametag_Anna",
+    "Number_of_fixations.Nametag_Bianca",
+    "Number_of_fixations.Nametag_Carl(a)"
+  ) %>%
+  rowwise() %>%
+  transmute(
+    Group = as_factor(Group),
+    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
+    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
+    Participant = Participant,
+    Others_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Others_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Others_number_fixation_min = round(Others_number_fixation / Duration_of_interval_min, digits = 2),
+    Average_duration_others = round(Others_duration_fixation / Others_number_fixation, digits = 0)
+    ) -> df_aoi_others
+
+# N, M, SD, min & max number of fixations per minute (AOI students)
+nof.min.others.table <-
+  df_aoi_others %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(Others_number_fixation_min), digits = 2),
+    "SD" = round(sd(Others_number_fixation_min), digits = 2),
+    "Min" = round(min(Others_number_fixation_min), digits = 2),
+    "Max" = round(max(Others_number_fixation_min), digits = 2)
+  )
+
+knitr::kable(nof.min.others.table,
+             caption = "N, M, SD, min & max number of fixations per minute (AOI others)")
+
+# plotting number of fixations per minute on AOI Students
+df_aoi_stud %>%
+  ggplot(mapping = aes(x = Group, y = Stud_number_fixation_min)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.005
+    )
+  ) +
+  ylim(0, 50) +
+  labs(x = "", y = "Number of fixations per minute") +
+  scale_fill_brewer(palette  = "RdBu") +
+  ggtitle("Number of fixations per minute\n(AOI students)") +
+  theme_cowplot() +
+  theme(legend.position = "none") -> plot_number_min_stud
+
+plot_number_min_stud
+
+```
+
+#### t-test & effect size "Number of fixation" (AOI others)
+```{r nof_others_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# NUMBER OF FIXATIONS on AOI others 
+# t-test for expertise differences
+t.test(
+  x = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Expert"],
+  y = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Novice"],
+  var.equal = TRUE
+)
+
+# NUMBER OF FIXATIONS on AOI students
+# effect size for expertise differences
+d_number_others <- CohenD(
+  x = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Expert"],
+  y = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Novice"],
+  na.rm = TRUE
+)
+
+round(d_number_others, 2)
 

### 2024-11-11 02_paper/02_study/02_expertise_paper/expertise_2024_09_24_outlierdetection_MK.Rmd
x - adding all Aois

--- 2024-09-30 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_24_outlierdetection_MK.Rmd
@@
 round(d_number_stud, 2)
+
+```
+
+#### 2.2.3 Number of fixations (AOI others)
+```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### NUMBER OF FIXATION ON AOI DISRUPTIVE PERSON ########################
+
+##################### NUMBER OF FIXATIONS (AOI others) ########################
+
+# filter group & total duration & number fixation (AOI others)
+df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select (
+    Group,
+    Duration_of_interval,
+    Participant,
+    "Total_duration_of_fixations.Board_Screen",
+    "Total_duration_of_fixations.Classroom_Others",
+    "Total_duration_of_fixations.Material_Students",
+    "Total_duration_of_fixations.Material_Teacher",
+    "Total_duration_of_fixations.Nametag_Anna",
+    "Total_duration_of_fixations.Nametag_Bianca",
+    "Total_duration_of_fixations.Nametag_Carl(a)",
+    "Number_of_fixations.Board_Screen",
+    "Number_of_fixations.Classroom_Others",
+    "Number_of_fixations.Material_Students",
+    "Number_of_fixations.Material_Teacher",
+    "Number_of_fixations.Nametag_Anna",
+    "Number_of_fixations.Nametag_Bianca",
+    "Number_of_fixations.Nametag_Carl(a)"
+  ) %>%
+  rowwise() %>%
+  transmute(
+    Group = as_factor(Group),
+    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
+    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
+    Participant = Participant,
+    Others_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Others_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Others_number_fixation_min = round(Others_number_fixation / Duration_of_interval_min, digits = 2),
+    Average_duration_others = round(Others_duration_fixation / Others_number_fixation, digits = 0)
+    ) -> df_aoi_others
+
+# filter only for experts
+df_aoi_others_expert <- df_aoi_others %>% 
+  filter(Group == "Expert")
+
+# filter only for novices
+df_aoi_others_novice <- df_aoi_others %>% 
+  filter(Group == "Novice")
+
+######## Statistical Methods for Outlier Detection
+
+### EXPERTS ###
+
+# Boxplot showing outliers for experts
+ggplot(df_aoi_others_expert, aes(x = "", y = Others_number_fixation_min)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "EXPERTS: Boxplot of number of fixations per minute (AOI others)",
+       y = "Number of fixations per minute") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_others_expert$Others_number_fixation_min, 0.25)
+Q3 <- quantile(df_aoi_others_expert$Others_number_fixation_min, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_others_exp <- df_aoi_others_expert %>%
+  filter(Others_number_fixation_min >= LowerBound & Others_number_fixation_min <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_others_expert)  # Original data
+nrow(df_no_outliers_others_exp)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_others_exp <- df_aoi_others_expert %>%
+  filter(Others_number_fixation_min < LowerBound | Others_number_fixation_min > UpperBound)
+
+# View the removed outliers
+df_outliers_others_exp
+
+### NOVICES ###
+
+# Boxplot showing outliers for novices
+ggplot(df_aoi_others_novice, aes(x = "", y = Others_number_fixation_min)) + 
+  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
+  labs(title = "NOVICES: Boxplot of number of fixations per minute (AOI others)",
+       y = "Number of fixations per minute") +
+  theme_minimal()
+
+# Calculate the IQR and bounds
+Q1 <- quantile(df_aoi_others_novice$Others_number_fixation_min, 0.25)
+Q3 <- quantile(df_aoi_others_novice$Others_number_fixation_min, 0.75)
+IQR <- Q3 - Q1
+
+LowerBound <- Q1 - 1.5 * IQR
+UpperBound <- Q3 + 1.5 * IQR
+
+# Filter to remove outliers
+df_no_outliers_others_nov <- df_aoi_others_novice %>%
+  filter(Others_number_fixation_min >= LowerBound & Others_number_fixation_min <= UpperBound)
+
+# Check the number of rows before and after filtering
+nrow(df_aoi_others_novice)  # Original data
+nrow(df_no_outliers_others_nov)  # After removing outliers
+
+# Create a dataframe with only the outliers
+df_outliers_others_nov <- df_aoi_others_novice %>%
+  filter(Others_number_fixation_min < LowerBound | Others_number_fixation_min > UpperBound)
+
+# View the removed outliers
+df_outliers_others_nov
 

### 2024-11-11 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x - adding all Aois

@@
 ---
-title: "Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study"
+title: "Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study"
 output: 
-  pdf_document:
+  html_document:
     toc: true           # Add a table of contents
     number_sections: true
-    latex_engine: xelatex  # Specify LaTeX engine if needed
-    keep_tex: true      # Keep .tex file for debugging or customization
 ---
@@
 
-## 1. Participants
+## Participants
 ```{r demographicstable, include = TRUE, echo=FALSE}
@@
 
-## 2. Measures
-
-### 2.1 Eye-Tracking Data
+## Measures
+
+### Eye-Tracking Data
 ```{r eyetracking_read_in_data, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
@@
 
-#### 2.2.2 Letter search
+#### Letter search
 ```{r letter_search, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.1 Number of fixations per minute (micro-teaching unit)
+### Fixations per minute across all AOIs
+```{r nof_all_aois, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# Filter data and select relevant columns, excluding "Disruptive_Person" only for the total fixations
+df_aoi_filtered <- df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  select(
+    Group,
+    Participant,
+    Duration_of_interval,
+    starts_with("Number_of_fixations")
+  )
+
+# Add a new AOI 'Students' by summing fixations for Anna, Bianca, and Carl(a)
+df_aoi_filtered <- df_aoi_filtered %>%
+  mutate(
+    Number_of_fixations.Students = 
+      `Number_of_fixations.Anna` +
+      `Number_of_fixations.Bianca` +
+      `Number_of_fixations.Carl(a)`,
+
+    # Calculate Total Fixations for all AOIs, excluding "Disruptive_Person"
+    Total_fixations_all = sum(c_across(starts_with("Number_of_fixations"))[!names(c_across(starts_with("Number_of_fixations"))) == "Number_of_fixations.Disruptive_Person"], na.rm = TRUE)
+  )
+
+# Convert duration to minutes and calculate fixations per minute
+df_aoi_filtered <- df_aoi_filtered %>%
+  mutate(Duration_of_interval_min = Duration_of_interval / 60000)
+
+df_aoi_long <- df_aoi_filtered %>%
+  rowwise() %>%
+  mutate(
+    across(starts_with("Number_of_fixations"), ~ .x / Duration_of_interval_min, .names = "fixation_per_min_{.col}")
+  ) %>%
+  ungroup() %>%
+  pivot_longer(
+    cols = starts_with("fixation_per_min_Number_of_fixations"),
+    names_to = "AOI",
+    values_to = "Fixations_per_minute"
+  ) %>%
+  mutate(AOI = str_remove(AOI, "fixation_per_min_Number_of_fixations.")) %>%
+  mutate(AOI = factor(AOI, levels = c("All", "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
+                                      "Board_Screen", "Material_Teacher", "Material_Students", 
+                                      "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"))) %>%
+  arrange(AOI)
+
+# Summarize descriptives
+aois_descriptives_fixations <- df_aoi_long %>%
+  group_by(Group, AOI) %>%
+  summarise(
+    N = n(),
+    M = round(mean(Fixations_per_minute, na.rm = TRUE), 2),
+    SD = round(sd(Fixations_per_minute, na.rm = TRUE), 2),
+    Min = round(min(Fixations_per_minute, na.rm = TRUE), 2),
+    Max = round(max(Fixations_per_minute, na.rm = TRUE), 2)
+  )
+
+knitr::kable(nof.table,
+             caption = "N, M, SD, min & max number of fixation per minute (across all AOIs)")
+
+# Visualization: Boxplot for fixations per minute across AOIs
+ggplot(df_aoi_long, aes(x = AOI, y = Fixations_per_minute, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(
+    position = position_jitterdodge(jitter.width = 0.15),
+    size = 1.5,
+    alpha = 0.7
+  ) +
+  scale_fill_brewer(palette = "RdBu") +
+  labs(x = "AOI", y = "Number of fixations per minute") +
+  ggtitle("Fixations per minute across all AOIs") +
+  theme_minimal() +
+  theme(legend.position = "top", axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
+
+#### Number of fixations per minute (micro-teaching unit)
 ```{r nof_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.2 Number of fixations per minute (AOI students)
+#### Number of fixations per minute (AOI students)
 ```{r nof_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.2 Number of fixations per minute (AOI others)
+#### Number of fixations per minute (AOI others)
 ```{r nof_others, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 # plotting number of fixations per minute on AOI Students
-df_aoi_stud %>%
-  ggplot(mapping = aes(x = Group, y = Stud_number_fixation_min)) +
+df_aoi_others %>%
+  ggplot(mapping = aes(x = Group, y = Others_number_fixation_min)) +
   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
@@
   ) +
-  ylim(0, 50) +
+  ylim(0, 100) +
   labs(x = "", y = "Number of fixations per minute") +
   scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Number of fixations per minute\n(AOI students)") +
+  ggtitle("Number of fixations per minute\n(AOI others)") +
   theme_cowplot() +
-  theme(legend.position = "none") -> plot_number_min_stud
-
-plot_number_min_stud
+  theme(legend.position = "none") -> plot_number_min_others
+
+plot_number_min_others
 
@@
 
-#### 2.2.3 Number of fixations (AOI disruptive person)
+#### Number of fixations (AOI disruptive person)
 ```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.4 Average duration of fixations in milliseconds (micro-teaching unit)
+### Duration of Fixations across all AOIs
+```{r average_dur_all_aoi, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# Filtere und wähle die relevanten Spalten aus
+df_aoi_filtered <- df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  select(
+    Group,
+    Participant,
+    Duration_of_interval,
+    starts_with("Total_duration_of_fixations"),
+    starts_with("Number_of_fixations")
+  )
+
+# Erstelle die AOI "Students" durch Summieren der Werte für Anna, Bianca und Carl(a)
+df_aoi_filtered <- df_aoi_filtered %>%
+  mutate(
+    Total_duration_of_fixations.Students = 
+      `Total_duration_of_fixations.Anna` +
+      `Total_duration_of_fixations.Bianca` +
+      `Total_duration_of_fixations.Carl(a)`,
+    Number_of_fixations.Students = 
+      `Number_of_fixations.Anna` +
+      `Number_of_fixations.Bianca` +
+      `Number_of_fixations.Carl(a)`
+  )
+
+# Berechne die durchschnittliche Fixationsdauer für jede AOI individuell (einschließlich "Disruptive_Person")
+df_aoi_avg_long <- df_aoi_filtered %>%
+  pivot_longer(
+    cols = starts_with("Total_duration_of_fixations") | starts_with("Number_of_fixations"),
+    names_to = "Measure_AOI",
+    values_to = "Values"
+  ) %>%
+  separate(Measure_AOI, into = c("Measure", "AOI"), sep = "\\.", extra = "merge") %>%
+  pivot_wider(
+    names_from = Measure,
+    values_from = Values
+  ) %>%
+  mutate(
+    Average_duration = round(Total_duration_of_fixations / Number_of_fixations, digits = 2)
+  )
+
+# Berechne `Average_duration_mtu` und `Number_fixation_mtu` durch Aufsummieren der Fixationsdauer und -anzahl, ohne "Disruptive_Person"
+df_mtu_summary <- df_aoi_filtered %>%
+  rowwise() %>%  # Zeilenweise Berechnung
+  mutate(
+    Total_duration_excl_disruptive = sum(c_across(starts_with("Total_duration_of_fixations")), na.rm = TRUE) - `Total_duration_of_fixations.Disruptive_Person`,
+    Total_fixations_excl_disruptive = sum(c_across(starts_with("Number_of_fixations")), na.rm = TRUE) - `Number_of_fixations.Disruptive_Person`
+  ) %>%
+  ungroup() %>%
+  summarise(
+    Group = unique(Group),
+    Average_duration_mtu = round(mean(Total_duration_excl_disruptive / Total_fixations_excl_disruptive, na.rm = TRUE), 2),
+    Number_fixation_mtu = sum(Total_fixations_excl_disruptive, na.rm = TRUE)
+  ) %>%
+  mutate(AOI = "MTU")
+
+# Füge `Average_duration_mtu` und `Number_fixation_mtu` zur Langformat-Datenstruktur hinzu
+df_aoi_avg_long <- bind_rows(df_aoi_avg_long, df_mtu_summary)
+
+# Setze die AOIs in der gewünschten Reihenfolge, einschließlich "MTU"
+df_aoi_avg_long <- df_aoi_avg_long %>%
+  mutate(AOI = factor(AOI, levels = c(
+    "MTU", "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
+    "Board_Screen", "Material_Teacher", "Material_Students", 
+    "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"
+  ))) %>%
+  arrange(AOI)
+
+# Berechne deskriptive Statistiken, einschließlich "MTU"
+aois_descriptives_durations <- df_aoi_avg_long %>%
+  group_by(Group, AOI) %>%
+  summarise(
+    N = n(),
+    M = round(mean(Average_duration, na.rm = TRUE), 2),
+    SD = round(sd(Average_duration, na.rm = TRUE), 2),
+    Min = round(min(Average_duration, na.rm = TRUE), 2),
+    Max = round(max(Average_duration, na.rm = TRUE), 2)
+  )
+
+# Visualisierung: Boxplot der durchschnittlichen Fixationsdauer für alle AOIs
+ggplot(df_aoi_avg_long, aes(x = AOI, y = Average_duration, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(
+    position = position_jitterdodge(jitter.width = 0.15),
+    size = 1.5,
+    alpha = 0.7
+  ) +
+  scale_fill_brewer(palette = "RdBu") +
+  labs(x = "AOI", y = "Average Duration of Fixations (ms)") +
+  ggtitle("Average Duration of Fixations across all AOIs") +
+  theme_minimal() +
+  theme(legend.position = "top", axis.text.x = element_text(angle = 45, hjust = 1))
+
+# Ausgabe der deskriptiven Tabelle, einschließlich "MTU"
+knitr::kable(aois_descriptives_durations,
+             caption = "N, M, SD, min & max duration of fixations in milliseconds (across all AOIs)")
+
+```
+
+#### Average duration of fixations in milliseconds (micro-teaching unit)
 ```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.5 Average duration of fixations (AOI students)
+#### Average duration of fixations (AOI students)
 ```{r dur_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.6 Average duration of fixations (AOI disruptive person)
+#### Average duration of fixations (AOI disruptive person)
 ```{r dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.7 Gaze Relational Index (GRI; micro-teaching unit)
+#### Gaze Relational Index (GRI; micro-teaching unit)
 ```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-#### 2.2.10 Time to first fixation in seconds (AOI disruptive person)
+#### Time to first fixation in seconds (AOI disruptive person)
 ```{r ttff_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-### 2.2 Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
+### Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
 ```{r rating_scales, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-# ```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-# 
-# ############## Prevalence Rating #########################
-# 
-# sri.preva.table <-
-#   sri %>%
-#   group_by(ID) %>%
-#   summarise(
-#     N = n(),
-#     "M" = round(mean(prevalence_rating), digits = 2),
-#     "SD" = round(sd(prevalence_rating), digits = 2),
-#     "Min" = min(prevalence_rating),
-#     "Max" = max(prevalence_rating)
-#   )
-# 
-# # insert a table into HTML
-# knitr::kable(sri.preva.table,
-#              caption = "Prevalence rating")
-# 
-# #### with event 
-# sri.preva.event.table <-
-#   sri %>%
-#   group_by(ID, event) %>%
-#   summarise(
-#     N = n(),
-#     "M" = round(mean(prevalence_rating), digits = 2),
-#     "SD" = round(sd(prevalence_rating), digits = 2),
-#     "Min" = min(prevalence_rating),
-#     "Max" = max(prevalence_rating)
-#   )
-# 
-# # insert a table into HTML
-# knitr::kable(sri.preva.event.table,
-#              caption = "Prevalence rating with events")
-# 
-# # create a new data frame with rating
-# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
-# 
-# # plotting prevalence rating for groups
-# preva_group_plot <- 
-#   sri_preva %>% 
-#   mutate(ID = factor(ID,
-#                      levels = c("Novice",
-#                                 "Expert"
-#                                 )
-#                      )
-#          ) %>% 
-#   ggplot(mapping = aes(x = ID,
-#                        y = prevalence_rating)) +
-#   geom_boxplot(mapping = aes(fill = ID),
-#                outlier.shape = NA) +
-#   geom_point(size = 1,
-#              alpha = 0.4,
-#              position = position_jitter(seed = 1,
-#                                         width = 0.1,
-#                                         height = 0.1)) +
-#   scale_x_discrete(limits = c("Novice", "Expert")) +
-#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
-#   labs(x = "",
-#        y = "Prevalence Rating") + 
-#   scale_fill_brewer(palette  = "RdBu") +  
-#   ggtitle("How widespread is this event in the classroom?") +
-#   theme_cowplot()
-# 
-# preva_group_plot
-# 
-# ```
-
-#### t-Test & effect size "Prevalence rating"
-# ```{r sri_pr_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-# 
-# #################### T-TEST & EFFECT SIZE ############
-# 
-# # Prevalence Rating 
-# # t-test for expertise differences
-# t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
-#        y = sri$prevalence_rating[sri$ID == "Novice"],
-#        var.equal = TRUE)
-# 
-# # Prevalence Rating 
-# # effect size for expertise differences
-# d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
-#                       y = sri$prevalence_rating[sri$ID == "Novice"],
-#                       na.rm = TRUE)
-# 
-# round(d_sri_preva, 2)
-# 
-# ```
+### Prevalence Rating as manipulation check
+```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+############## Prevalence Rating #########################
+
+sri.preva.table <-
+  sri %>%
+  group_by(ID) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(prevalence_rating), digits = 2),
+    "SD" = round(sd(prevalence_rating), digits = 2),
+    "Min" = min(prevalence_rating),
+    "Max" = max(prevalence_rating)
+  )
+
+knitr::kable(sri.preva.table,
+             caption = "Prevalence rating")
+
+sri.preva.event.table <-
+  sri %>%
+  group_by(ID, event) %>%
+  summarise(
+    N = n(),
+    "M" = round(mean(prevalence_rating), digits = 2),
+    "SD" = round(sd(prevalence_rating), digits = 2),
+    "Min" = min(prevalence_rating),
+    "Max" = max(prevalence_rating)
+  )
+
+knitr::kable(sri.preva.event.table,
+             caption = "Prevalence rating with events")
+
+sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
+
+preva_group_plot <- 
+  sri_preva %>% 
+  mutate(ID = factor(ID,
+                     levels = c("Novice",
+                                "Expert"
+                                )
+                     )
+         ) %>% 
+  ggplot(mapping = aes(x = ID,
+                       y = prevalence_rating)) +
+  geom_boxplot(mapping = aes(fill = ID),
+               outlier.shape = NA) +
+  geom_point(size = 1,
+             alpha = 0.4,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  scale_x_discrete(limits = c("Novice", "Expert")) +
+  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
+  labs(x = "",
+       y = "Prevalence Rating") + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  ggtitle("How widespread is this event in the classroom?") +
+  theme_cowplot()
+
+preva_group_plot
+
+#################### T-TEST & EFFECT SIZE ############
+
+t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
+       y = sri$prevalence_rating[sri$ID == "Novice"],
+       var.equal = TRUE)
+
+d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
+                      y = sri$prevalence_rating[sri$ID == "Novice"],
+                      na.rm = TRUE)
+
+round(d_sri_preva, 2)
+```
 
@@
 
-### Prevalence Rating as manipulation check
-```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-# 
-# ############## Prevalence Rating as manipulation check #########################
-# 
-# sri.preva.table <-
-#   sri %>%
-#   group_by(ID) %>%
-#   summarise(
-#     N = n(),
-#     "M" = round(mean(prevalence_rating), digits = 2),
-#     "SD" = round(sd(prevalence_rating), digits = 2),
-#     "Min" = min(prevalence_rating),
-#     "Max" = max(prevalence_rating)
-#   )
-# 
-# # insert a table into HTML
-# knitr::kable(sri.preva.table,
-#              caption = "Prevalence rating")
-# 
-# #### with event 
-# sri.preva.event.table <-
-#   sri %>%
-#   group_by(ID, event) %>%
-#   summarise(
-#     N = n(),
-#     "M" = round(mean(prevalence_rating), digits = 2),
-#     "SD" = round(sd(prevalence_rating), digits = 2),
-#     "Min" = min(prevalence_rating),
-#     "Max" = max(prevalence_rating)
-#   )
-# 
-# # insert a table into HTML
-# knitr::kable(sri.preva.event.table,
-#              caption = "Prevalence rating with events")
-# 
-# # create a new data frame with rating
-# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
-# 
-# # plotting prevalence rating for groups
-# preva_group_plot <- 
-#   sri_preva %>% 
-#   mutate(ID = factor(ID,
-#                      levels = c("Novice",
-#                                 "Expert"
-#                                 )
-#                      )
-#          ) %>% 
-#   ggplot(mapping = aes(x = ID,
-#                        y = prevalence_rating)) +
-#   geom_boxplot(mapping = aes(fill = ID),
-#                outlier.shape = NA) +
-#   geom_point(size = 1,
-#              alpha = 0.4,
-#              position = position_jitter(seed = 1,
-#                                         width = 0.1,
-#                                         height = 0.1)) +
-#   scale_x_discrete(limits = c("Novice", "Expert")) +
-#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
-#   labs(x = "",
-#        y = "Prevalence Rating") + 
-#   scale_fill_brewer(palette  = "RdBu") +  
-#   ggtitle("How widespread is this event in the classroom?") +
-#   theme_cowplot()
-# 
-# preva_group_plot
-
-```
-
-### 2.3 Situational Jugdement Test
+### Situational Jugdement Test
 ```{r sjt, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-### 2.4 Classroom Questionnaire
+### Classroom Questionnaire
 ```{r classroom questionnaire, echo=FALSE, results='asis'}
@@
 
-## 3. Correlations
+## Correlations
 ```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}

### 2024-11-12 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x paper

@@
 
+### Check variables
+
 #### Letter search
@@
   mutate(AOI = str_remove(AOI, "fixation_per_min_Number_of_fixations.")) %>%
-  mutate(AOI = factor(AOI, levels = c("All", "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
+  mutate(AOI = factor(AOI, levels = c("Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
                                       "Board_Screen", "Material_Teacher", "Material_Students", 
@@
 
-knitr::kable(nof.table,
+knitr::kable(aois_descriptives_fixations,
              caption = "N, M, SD, min & max number of fixation per minute (across all AOIs)")
@@
 
-# Filtere und wähle die relevanten Spalten aus
+# Filter and select necessary columns
 df_aoi_filtered <- df_aoi %>%
@@
 
-# Erstelle die AOI "Students" durch Summieren der Werte für Anna, Bianca und Carl(a)
+# Create a new AOI 'Students' by summing durations and counts for Anna, Bianca, and Carl(a)
 df_aoi_filtered <- df_aoi_filtered %>%
@@
       `Number_of_fixations.Bianca` +
-      `Number_of_fixations.Carl(a)`
-  )
-
-# Berechne die durchschnittliche Fixationsdauer für jede AOI individuell (einschließlich "Disruptive_Person")
+      `Number_of_fixations.Carl(a)`,
+
+    # Calculate Average Duration for all AOIs, excluding "Disruptive_Person"
+    Total_duration_excl_disruptive = sum(c_across(starts_with("Total_duration_of_fixations"))[!names(c_across(starts_with("Total_duration_of_fixations"))) == "Total_duration_of_fixations.Disruptive_Person"], na.rm = TRUE),
+    Total_fixations_excl_disruptive = sum(c_across(starts_with("Number_of_fixations"))[!names(c_across(starts_with("Number_of_fixations"))) == "Number_of_fixations.Disruptive_Person"], na.rm = TRUE),
+    Average_duration_all = round(Total_duration_excl_disruptive / Total_fixations_excl_disruptive, digits = 2)  # Overall average duration
+  )
+
+# Calculate average fixation duration for each AOI individually, excluding disruptive person
 df_aoi_avg_long <- df_aoi_filtered %>%
@@
   ) %>%
+  filter(AOI != "Disruptive_Person") %>%
   mutate(
@@
 
-# Berechne `Average_duration_mtu` und `Number_fixation_mtu` durch Aufsummieren der Fixationsdauer und -anzahl, ohne "Disruptive_Person"
-df_mtu_summary <- df_aoi_filtered %>%
-  rowwise() %>%  # Zeilenweise Berechnung
-  mutate(
-    Total_duration_excl_disruptive = sum(c_across(starts_with("Total_duration_of_fixations")), na.rm = TRUE) - `Total_duration_of_fixations.Disruptive_Person`,
-    Total_fixations_excl_disruptive = sum(c_across(starts_with("Number_of_fixations")), na.rm = TRUE) - `Number_of_fixations.Disruptive_Person`
-  ) %>%
-  ungroup() %>%
-  summarise(
-    Group = unique(Group),
-    Average_duration_mtu = round(mean(Total_duration_excl_disruptive / Total_fixations_excl_disruptive, na.rm = TRUE), 2),
-    Number_fixation_mtu = sum(Total_fixations_excl_disruptive, na.rm = TRUE)
-  ) %>%
-  mutate(AOI = "MTU")
-
-# Füge `Average_duration_mtu` und `Number_fixation_mtu` zur Langformat-Datenstruktur hinzu
-df_aoi_avg_long <- bind_rows(df_aoi_avg_long, df_mtu_summary)
-
-# Setze die AOIs in der gewünschten Reihenfolge, einschließlich "MTU"
+# Set the order of AOIs based on the specified sequence
 df_aoi_avg_long <- df_aoi_avg_long %>%
   mutate(AOI = factor(AOI, levels = c(
-    "MTU", "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
+    "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_person", 
     "Board_Screen", "Material_Teacher", "Material_Students", 
@@
 
-# Berechne deskriptive Statistiken, einschließlich "MTU"
+# Summarize descriptives for average duration of fixations
 aois_descriptives_durations <- df_aoi_avg_long %>%
@@
 
-# Visualisierung: Boxplot der durchschnittlichen Fixationsdauer für alle AOIs
+knitr::kable(aois_descriptives_durations,
+             caption = "N, M, SD, min & max duration of fixation per minute (across all AOIs)")
+
+# Visualization: Boxplot for average duration of fixations across AOIs
 ggplot(df_aoi_avg_long, aes(x = AOI, y = Average_duration, fill = Group)) +
@@
   ) +
+  ylim(0, 1500) +
   scale_fill_brewer(palette = "RdBu") +
@@
   theme(legend.position = "top", axis.text.x = element_text(angle = 45, hjust = 1))
-
-# Ausgabe der deskriptiven Tabelle, einschließlich "MTU"
-knitr::kable(aois_descriptives_durations,
-             caption = "N, M, SD, min & max duration of fixations in milliseconds (across all AOIs)")
 

### 2024-11-12 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.Rmd
literaturverzeichnis
literatur Sachen
Literatur

@@
 header-includes:
-  - \setcitestyle{sort&compress}
+  - \usepackage{hyperref}
+  - \hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}
+  - \setcitestyle{numbers, sort&compress}
   - \usepackage{tabularx}
@@
 Classroom disruptions are a major stressor in teachers’ daily work [@boyle1995structural; @aloe2014multivariate], and learning how to deal with them is an important aspect of professional expertise [@wolff2015keeping].
-According to @lazarus1990theory transactional model of stress and coping, the experience of stress in response to stressors such as classroom disruptions depends on the teacher´s subjective appraisal, which, in turn, depends on their coping resources, such as their professional knowledge.
+According to @lazarus1990theory transactional model of stress and coping, the experience of stress in response to stressors such as classroom disruptions depends on the teacher's subjective appraisal, which, in turn, depends on their coping resources, such as their professional knowledge.
 The resulting stress response has a psychological, physiological, or behavioral dimension [@kyriacou1978].

### 2024-11-12 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.tex
literatur Sachen
Literatur

--- 2024-10-29 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.tex
@@
 \usepackage[]{natbib}
-\bibliographystyle{plainnat}
+\bibliographystyle{apa}
 
@@
 
-\setcitestyle{sort&compress}
+\usepackage{hyperref}
+\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}
+\setcitestyle{numbers, sort&compress}
 \usepackage{tabularx}
@@
 response to stressors such as classroom disruptions depends on the
-teacher´s subjective appraisal, which, in turn, depends on their coping
+teacher's subjective appraisal, which, in turn, depends on their coping
 resources, such as their professional knowledge. The resulting stress

### 2024-11-13 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x paper

@@
   group_by(Group) %>%
-  summarise(N=n(),
-            "Women in percent" = round(sum(Gender/Sum_participants) * 100, 
-                                               digits = 2),
-            "M Age in years" = round(mean(Age), 
-                                     digits = 2),
-            "SD Age in years" = round(sd(Age), 
-                                      digits = 2),
+  summarise(
+    N = n(),
+    "Women in percent" = round(sum(Gender / Sum_participants) * 100, digits = 2),
+    "M Age in years" = round(mean(Age), digits = 2),
+    "SD Age in years" = round(sd(Age), digits = 2),
     "Min Age in years" = min(Age),
@@
     "SD Exp." = round(sd(`Teaching Experience`), 2),
+    "Median Exp." = median(`Teaching Experience`),
     "Min Exp." = min(`Teaching Experience`),
@@
   group_by(Group) %>%
-  summarise(N=n(),
+  summarise(
+    N = n(),
     "M Exp." = round(mean(`Teaching Experience`), 2),
     "SD Exp." = round(sd(`Teaching Experience`), 2),
+    "Median Exp." = median(`Teaching Experience`),
     "Min Exp." = min(`Teaching Experience`),
@@
     "Max Internship" = max(Internship),
-            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
-            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
-           )
+    "Extracurricular Teaching Experience" = round(
+      sum(`Extracurricular Teaching Experience` / Sum_participants) * 100,
+      digits = 2
+    ),
+    "Secondary Teaching Activities" = round(sum(
+      `Secondary Teaching Activities` / Sum_participants
+    ) * 100)
+  )
+
+knitr::kable(exp.table,
+             caption = "Demographic information & teaching experience")
 
@@
          ) -> df_letter
-# missing IDs: 101, 111, 205
+# excluded IDs: 111 (due to viewing problems), 205 (missing letter search)
 
@@
 
-# filter group & total duration & number fixation on AOI "disruptive person"
-df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select(Group, 
-                Participant, 
+# Define the list of disruptions and categories
+disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
+                 "Drumming_with_hands", "Head_on_table", "Heckling", 
+                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
+
+# Define categories for each type of disruption
+verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
+physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
+lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")
+
+# Filter data to include only the specified disruptions
+df_aoi_disrup <- df_aoi %>%
+  filter(TOI %in% disruptions) %>%
+  dplyr::select(Group, Participant, TOI, Duration_of_interval, 
                 "Number_of_fixations.Disruptive_Person") %>%
-  mutate(Group = as_factor(Group)) -> df_aoi_disrup
-
-# N, M, SD, min & max number of fixation on AOI "disruptive person"
-nof.disrup.table <-
-  df_aoi_disrup %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(Number_of_fixations.Disruptive_Person), digits = 2),
-    "SD" = round(sd(Number_of_fixations.Disruptive_Person), digits = 2),
-    "Min" = round(min(Number_of_fixations.Disruptive_Person), digits = 2),
-    "Max" = round(max(Number_of_fixations.Disruptive_Person), digits = 2)
-  )
-
-knitr::kable(nof.disrup.table,
-             caption = "N, M, SD, min & max number of fixation (AOI disruptive person)")
-
-# plotting average duration on AOI Disruptive person
-df_aoi_disrup %>%
-  ggplot(mapping = aes(x = Group, y = Number_of_fixations.Disruptive_Person)) +
+  mutate(Group = as_factor(Group))
+
+# Add a column for Disruption_Category based on TOI values
+df_aoi_disrup <- df_aoi_disrup %>%
+  mutate(
+    Disruption_Category = case_when(
+      TOI %in% verbal_disruptions ~ "Verbal disruptions",
+      TOI %in% physical_disruptions ~ "Physical disruptions",
+      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
+      TRUE ~ NA_character_
+    )
+  ) %>%
+  filter(!is.na(Disruption_Category)) # Keep only rows with valid category
+
+# Convert duration from milliseconds to seconds
+df_aoi_disrup <- df_aoi_disrup %>%
+  mutate(Duration_of_interval_sec = Duration_of_interval / 1000)
+
+# Summarize total duration in seconds and fixation counts for "Disruptive_Person" by group, participant, and category
+disruption_summary <- df_aoi_disrup %>%
+  group_by(Group, Participant, Disruption_Category) %>%
+  summarize(
+    total_duration_sec = sum(Duration_of_interval_sec, na.rm = TRUE),
+    fixation_count = sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE),
+    .groups = "drop"
+  ) %>%
+  mutate(fixations_per_second = fixation_count / total_duration_sec)
+
+# Step 1: Aggregate disruptions on an individual level (one value per participant)
+# Calculate the mean fixation rate per participant
+individual_summary <- disruption_summary %>%
+  group_by(Group, Participant) %>%
+  summarize(
+    mean_fixations_per_second = mean(fixations_per_second, na.rm = TRUE),
+    .groups = "drop"
+  )
+
+# First Plot: Overall fixation rate by Group (using aggregated individual data)
+plot_overall <- individual_summary %>%
+  ggplot(mapping = aes(x = Group, y = mean_fixations_per_second)) +
   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
@@
   ) +
-  ylim(0, 150) +
-  labs(x = "", y = "Number of fixations") +
+  ylim (0, 1) + 
+  labs(x = "", y = "Mean Fixations per Second per Participant") +
+  ggtitle("Overall Fixation Rate per Participant\n(AOI disruptive person)") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Number of fixations\n(AOI disruptive person)") +
   theme_cowplot() +
-  theme(legend.position = "none") -> plot_number_disrup
-
-plot_number_disrup
+  theme(legend.position = "none")
+
+# Second Plot: Fixation rate by Group and Disruption_Category (no aggregation, shows all data points)
+plot_category <- disruption_summary %>%
+  ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) + # Wrap long facet labels
+  labs(x = "", y = "Fixations per Second") +
+  ggtitle("Fixation Rate by Disruption Category\n(AOI disruptive person)") +
+  scale_fill_brewer(palette = "RdBu") +
+  theme_cowplot() +
+  theme(
+    legend.position = "none",
+    strip.text = element_text(size = 10) # Adjust facet text size if necessary
+  )
+
+# Display both plots
+plot_overall
+plot_category
+
 ```
@@
 
-# NUMBER OF FIXATIONS on AOI disruptive person 
-# t-test for expertise differences
-t.test(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
-       y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"],
-       var.equal = TRUE)
-
-# NUMBER OF FIXATIONS 
-# effect size for expertise differences
-d_number_disrup <- CohenD(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
-                        y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"],
-                        na.rm = TRUE)
-
-round(d_number_disrup, 2)
+# Function to format t-test and Cohen's d results into a tidy data frame, with checks for non-numeric values
+format_results <- function(t_test, cohen_d) {
+  data.frame(
+    "t-value" = if (is.numeric(t_test$statistic)) round(t_test$statistic, 2) else NA,
+    "df" = if (is.numeric(t_test$parameter)) round(t_test$parameter, 2) else NA,
+    "p-value" = if (!is.null(t_test$p.value)) format.pval(t_test$p.value, digits = 3, eps = .001) else "NA",
+    "Mean Difference" = if (is.numeric(t_test$estimate[1] - t_test$estimate[2])) round(t_test$estimate[1] - t_test$estimate[2], 2) else NA,
+    "Cohen's d" = if (is.numeric(cohen_d$estimate)) round(cohen_d$estimate, 2) else NA,
+    "95% CI (d)" = if (!is.null(cohen_d$conf.int)) 
+                    paste0("[", round(cohen_d$conf.int[1], 2), ", ", round(cohen_d$conf.int[2], 2), "]") 
+                   else "NA"
+  )
+}
+
+# 1. t-Test and Cohen's d for fixations per second between Experts and Novices
+t_fixations_group <- t.test(fixations_per_second ~ Group, data = disruption_summary)
+d_fixations_group <- cohen.d(fixations_per_second ~ Group, data = disruption_summary)
+fixations_group_result <- format_results(t_fixations_group, d_fixations_group)  # Formatting results
+
+# 2. t-Test and Cohen's d for fixations per second by category
+# Iterate over each category and calculate t-test and Cohen's d
+categories <- unique(disruption_summary$Disruption_Category)
+fixations_category_results <- list()
+
+for (cat in categories) {
+  cat_data <- disruption_summary %>% filter(Disruption_Category == cat)
+  t_test_cat <- t.test(fixations_per_second ~ Group, data = cat_data)
+  d_cat <- cohen.d(fixations_per_second ~ Group, data = cat_data)
+  fixations_category_results[[cat]] <- format_results(t_test_cat, d_cat)  # Format results for each category
+}
+
+# Convert the list of results into a single data frame
+fixations_category_df <- do.call(rbind, fixations_category_results)
+fixations_category_df <- data.frame(Category = categories, fixations_category_df, row.names = NULL)  # Ensure Category column aligns
+
+# Render tables in HTML format with kableExtra for APA style
+knitr::kable(fixations_group_result, caption = "T-test and Effect Size for Fixations per Second (Experts vs. Novices)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+knitr::kable(fixations_category_df, caption = "T-test and Effect Size for Fixations per Second by Category") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+```
+
+### Duration of disruption
+```{r disrup_dur, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# Define the list of disruptions and categories
+disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
+                 "Drumming_with_hands", "Head_on_table", "Heckling", 
+                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
+
+# Define categories for each type of disruption
+verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
+physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
+lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")
+
+# Filter data to include only the specified disruptions
+df_aoi_disrup <- df_aoi %>%
+  filter(TOI %in% disruptions) %>%
+  dplyr::select(Group, Participant, TOI, Duration_of_interval) %>%
+  mutate(Group = as_factor(Group))
+
+# Add a column for Disruption_Category based on TOI values
+df_aoi_disrup <- df_aoi_disrup %>%
+  mutate(
+    Disruption_Category = case_when(
+      TOI %in% verbal_disruptions ~ "Verbal disruptions",
+      TOI %in% physical_disruptions ~ "Physical disruptions",
+      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
+      TRUE ~ NA_character_
+    )
+  ) %>%
+  filter(!is.na(Disruption_Category)) # Keep only rows with valid category
+
+# Convert duration from milliseconds to seconds and round to 2 decimal places
+df_aoi_disrup <- df_aoi_disrup %>%
+  mutate(Duration_of_interval_sec = round(Duration_of_interval / 1000, 2))
+
+# First Table: Total duration of disruptions by group (Novice and Expert)
+duration_summary_group <- df_aoi_disrup %>%
+  group_by(Group) %>%
+  summarize(
+    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2),
+    mean_duration_sec = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
+    sd_duration_sec = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
+    min_duration_sec = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
+    max_duration_sec = round(max(Duration_of_interval_sec, na.rm = TRUE), 2)
+  )
+
+# Second Table: Total duration of disruptions by group and category
+duration_summary_category <- df_aoi_disrup %>%
+  group_by(Group, Disruption_Category) %>%
+  summarize(
+    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2),
+    mean_duration_sec = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
+    sd_duration_sec = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
+    min_duration_sec = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
+    max_duration_sec = round(max(Duration_of_interval_sec, na.rm = TRUE), 2)
+  )
+
+# Display tables
+print("Duration Summary by Group:")
+print(duration_summary_group)
+
+print("Duration Summary by Group and Category:")
+print(duration_summary_category)
+
+# First Plot: Boxplot of disruption duration by group
+plot_duration_group <- df_aoi_disrup %>%
+  ggplot(mapping = aes(x = Group, y = Duration_of_interval_sec)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  labs(x = "", y = "Disruption Duration (seconds)") +
+  ggtitle("Disruption Duration by Group") +
+  scale_fill_brewer(palette = "RdBu") +
+  theme_cowplot() +
+  theme(legend.position = "none")
+
+# Second Plot: Boxplot of disruption duration by group and category
+plot_duration_category <- df_aoi_disrup %>%
+  ggplot(mapping = aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) +
+  labs(x = "", y = "Disruption Duration (seconds)") +
+  ggtitle("Disruption Duration by Group and Category") +
+  scale_fill_brewer(palette = "RdBu") +
+  theme_cowplot() +
+  theme(legend.position = "none")
+
+# Display the plots
+plot_duration_group
+plot_duration_category
+
+```
+
+#### t-test & effect size "Duration of disruptions"
+```{r disrup_dur_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# Function to format t-test and Cohen's d results into a tidy data frame
+# Function to format t-test and Cohen's d results into a tidy data frame, with checks for non-numeric values
+format_results <- function(t_test, cohen_d) {
+  data.frame(
+    "t-value" = if (is.numeric(t_test$statistic)) round(t_test$statistic, 2) else NA,
+    "df" = if (is.numeric(t_test$parameter)) round(t_test$parameter, 2) else NA,
+    "p-value" = if (!is.null(t_test$p.value)) format.pval(t_test$p.value, digits = 3, eps = .001) else "NA",
+    "Mean Difference" = if (is.numeric(t_test$estimate[1] - t_test$estimate[2])) round(t_test$estimate[1] - t_test$estimate[2], 2) else NA,
+    "Cohen's d" = if (is.numeric(cohen_d$estimate)) round(cohen_d$estimate, 2) else NA,
+    "95% CI (d)" = if (!is.null(cohen_d$conf.int)) 
+                    paste0("[", round(cohen_d$conf.int[1], 2), ", ", round(cohen_d$conf.int[2], 2), "]") 
+                   else "NA"
+  )
+}
+
+# 3. Overall t-test and Cohen's d for Duration by Group
+t_duration_group <- t.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup)
+d_duration_group <- cohen.d(Duration_of_interval_sec ~ Group, data = df_aoi_disrup)
+duration_group_result <- format_results(t_duration_group, d_duration_group)
+
+# 4. t-test and Cohen's d for Duration by Category
+duration_category_results <- lapply(categories, function(cat) {
+  cat_data <- df_aoi_disrup %>% filter(Disruption_Category == cat)
+  t_test_cat <- t.test(Duration_of_interval_sec ~ Group, data = cat_data)
+  d_cat <- cohen.d(Duration_of_interval_sec ~ Group, data = cat_data)
+  format_results(t_test_cat, d_cat)
+})
+
+# Convert the list of results into a single data frame
+duration_category_df <- do.call(rbind, duration_category_results)
+duration_category_df <- data.frame(Category = categories, duration_category_df, row.names = NULL)  # Ensure row names are reset
+
+# Render tables in HTML format with kableExtra for APA style
+knitr::kable(duration_group_result, caption = "T-test and Effect Size for Duration (Experts vs. Novices)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+knitr::kable(duration_category_df, caption = "T-test and Effect Size for Duration by Category") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
   summarise(
+    N = n(),
     Mean = round(mean(N, na.rm = TRUE), digits = 2),
@@
 
+### Internal consistency (Omega) for Classroom Questionnaire
+```{r cm_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# read in data
+df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  dplyr::select(LM01_01:LM01_08, # classroom management 
+                LP01_01:LP01_08) # non- & paraverbal communication
+
+# calculate omega with omega() function  
+df_quest <- omega(df_quest)
+
+# display the results 
+print(df_quest)
+
+### CLASSROOM MANAGEMENT
+# read in data
+df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  dplyr::select(LM01_01:LM01_08, # classroom management 
+                LP01_01:LP01_08) # non- & paraverbal communication
+
+# select relevant columns
+df_quest_cm <- df_quest %>%
+    dplyr::select(LM01_01:LM01_08)
+
+# remove NAs
+df_quest_cm <- na.omit(df_quest_cm)
+
+# calculate omega with omega() function  
+omega_quest_cm <- omega(df_quest_cm)
+
+# display the results 
+print(omega_quest_cm)
+
+### NON- & PARAVERBAL COMMUNICATION
+# read in data
+df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  dplyr::select(LM01_01:LM01_08, # classroom management 
+                LP01_01:LP01_08) # non- & paraverbal communication
+
+# select relevant columns
+df_quest_npvc <- df_quest %>%
+    dplyr::select(LP01_01:LP01_08)
+
+# remove NAs
+df_quest_npvc <- na.omit(df_quest_npvc)
+
+# calculate omega with omega() function  
+omega_quest_npvc <- omega(df_quest_npvc)
+
+# display the results 
+print(omega_quest_npvc)
+
+```
+
 ## Correlations
@@
 
+# p-value for GRI x STJ_All
+cor.test(df_merge$GRI_mtu, df_merge$SJT_All)
+
+# p-value for GRI x Quest_All
+cor.test(df_merge$GRI_mtu, df_merge$Quest_All)
+
+# p-value for GRI x Disruption Rating
+cor.test(df_merge$GRI_mtu, df_merge$Mean_disruption_appraisal)
+
+# p-value for GRI x Confidence Rating
+cor.test(df_merge$GRI_mtu, df_merge$Mean_confidence_appraisal)
+
 ### Teaching experience with only experts
@@
 
-# p-value for GRI x STJ_All
-cor.test(df_merge$GRI_mtu, df_merge$SJT_All)
-
-# p-value for GRI x Quest_All
-cor.test(df_merge$GRI_mtu, df_merge$Quest_All)
-
-# p-value for GRI x Disruption Rating
-cor.test(df_merge$GRI_mtu, df_merge$Mean_disruption_appraisal)
-
-# p-value for GRI x Confidence Rating
-cor.test(df_merge$GRI_mtu, df_merge$Mean_confidence_appraisal)
-
 # p-value for GRI x Teaching Experience
@@
 
-```
+# ### Only novices
+# # merge all data frames in list
+# df_merge_novices <-
+#   df_list %>% reduce(full_join, by='Participant') %>%
+#   filter(`Teaching Experience` == 0) %>% 
+#   dplyr::select(`Teaching Experience`,
+#                 Stud_number_fixation_min,
+#                 Average_duration_stud,
+#                 Number_of_fixations.Disruptive_Person,
+#                 Average_duration_disrup,
+#                 Disrup_time_fixation_sec,
+#                 GRI_mtu,
+#                 SJT_All,
+#                 SJT_Monitoring,
+#                 Quest_All
+#                 )
+# 
+# # create a correlation matrix
+# cor_tab_novices <- 
+#   df_merge_novices %>% 
+#   cor(method = "pearson") %>% 
+#   round(., digits = 2)
+# 
+# # p-value for GRI x Teaching Experience
+# cor.test(cor_tab_novices$GRI_mtu, cor_tab_novices$`Teaching Experience`)
+
+```

### 2024-11-14 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x paper update

@@
       apaTables,
-      rstatix)
+      rstatix,
+      effsize,
+      knitr
+      )
 
@@
 
-# read in data and select and rename relevant columns with transmute 
-demo.data <- 
-  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
-  filter(!LI06_05 == 201,
-         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
-  transmute(Group = LI06_05,
-            Gender = LI02_01_1,
+# Read and process the data
+demo_data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  filter(!LI06_05 %in% c(201, 223)) %>%
+  transmute(
+    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),
+    Gender = as.numeric(ifelse(LI02_01_1 == 2, "1", "0")),
     Age = LI03_01,
     `Teaching Experience` = LI04_01,
-            School_type = LI18,
-            Grade = LI16_05,
-            Subject = LI10_05,
-            Semester = LI11_01,
+    School_type = factor(
+      replace(LI18, LI18 == 2, 1),
+      levels = c(1, 3, 4, 5, -1),
+      labels = c("Primary School", "Secondary School", "Special Education", "Vocational School", "Other School Type")
+    ),
+    Semester = as.numeric(LI11_01),
     Internship = LI13_01,
-            `Extracurricular Teaching Experience` = LI14,
-            `Secondary Teaching Activities` = LI17
-            )
-
-# define expert and novice with ifelse function
-demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")
-
-# changing gender to count female gender (male = 2 --> 0)
-demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")
-
-# changing character Gender into numeric
-demo.data$Gender <- as.numeric(demo.data$Gender)
-
-# creating new column with total participants to calculate percent of gender
-demo.data <- demo.data %>%
-  group_by(Group) %>%
-  mutate(Sum_participants = n())
-
-# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
-demo.data$School_type[demo.data$School_type == 2] <- "1"
-
-# creating new column to calculate percent of school type
-demo.data <- 
-  demo.data %>%
-  group_by(School_type, Group) %>%
-  mutate(Count_Schooltype = sum(n())) %>% 
-  mutate(Percent_schooltype = round((Count_Schooltype/Sum_participants) * 100, 
-         digits = 2))
-
-# changing character Percent_schooltype into numeric
-demo.data$Percent_schooltype <- as.numeric(demo.data$Percent_schooltype)
-
-# changing character Semester into numeric
-demo.data$Semester <- as.numeric(demo.data$Semester)
-
-# changing Type of School into character
-# LI18:
-# 1: Grundschule
-# 2: Oberschule
-# 3: Gymnasium
-# 4: Förderschule/Sondershausen
-# 5: Berufsbildende Schule
-# -1: andere Schulform
-demo.data$School_type <- factor(x = demo.data$School_type,
-                   levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
-                   labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen
-
-# changing `Extracurricular Teaching Experience` to count experience (no experience = 2 --> 0)
-demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 1, "1","0")
-
-# changing character Extra. Exp. into numeric
-demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)
-
-# changing `Secondary Teaching Activities` to count experience (no experience = 2 --> 0)
-demo.data$`Secondary Teaching Activities` = ifelse(demo.data$`Secondary Teaching Activities` == 1, "1","0")
-
-# changing character Extra. Exp. into numeric
-demo.data$`Secondary Teaching Activities` <- as.numeric(demo.data$`Secondary Teaching Activities`)
-
-# create new columns that give proportion of Gender
-# percent = female gender divided by all female Gender
-# demo.data <- demo.data  %>% 
-#   group_by(Group) %>% 
-#   mutate(Gender_percent = Gender/Sum_participants) %>% 
-#   mutate(Gender_percent = round(sum(Gender_percent)*100, digits=0))
-
-# create a basic table (tibble) using tidyverse functions
-demo.table <- demo.data %>%
+    `Extracurricular Teaching Experience` = as.numeric(ifelse(LI14 == 1, "1", "0")),
+    `Secondary Teaching Activities` = as.numeric(ifelse(LI17 == 1, "1", "0"))
+  )
+
+# Calculate summaries used across both tables, handling cases where all values are NA
+summary_data <- demo_data %>%
   group_by(Group) %>%
@@
     N = n(),
-    "Women in percent" = round(sum(Gender / Sum_participants) * 100, digits = 2),
-    "M Age in years" = round(mean(Age), digits = 2),
-    "SD Age in years" = round(sd(Age), digits = 2),
-    "Min Age in years" = min(Age),
-    "Max Age in years" = max(Age),
-    "M Exp." = round(mean(`Teaching Experience`), 2),
-    "SD Exp." = round(sd(`Teaching Experience`), 2),
-    "Median Exp." = median(`Teaching Experience`),
-    "Min Exp." = min(`Teaching Experience`),
-    "Max Exp." = max(`Teaching Experience`)
-  )
-
-knitr::kable(demo.table,
-             caption = "Demographic information & teaching experience")
-
-# create a basic table (tibble) using tidyverse functions
-exp.table <- demo.data %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    "M Exp." = round(mean(`Teaching Experience`), 2),
-    "SD Exp." = round(sd(`Teaching Experience`), 2),
-    "Median Exp." = median(`Teaching Experience`),
-    "Min Exp." = min(`Teaching Experience`),
-    "Max Exp." = max(`Teaching Experience`),
-    "M Semester" = round(mean(Semester), 2),
-    "SD Semester" = round(sd(Semester), 2),
-    "Min Semester" = min(Semester),
-    "Max Semester" = max(Semester),
-    "M Internship" = round(mean(Internship), 2),
-    "SD Internship" = round(sd(Internship), 2),
-    "Min Internship" = min(Internship),
-    "Max Internship" = max(Internship),
-    "Extracurricular Teaching Experience" = round(
-      sum(`Extracurricular Teaching Experience` / Sum_participants) * 100,
-      digits = 2
-    ),
-    "Secondary Teaching Activities" = round(sum(
-      `Secondary Teaching Activities` / Sum_participants
-    ) * 100)
-  )
-
-knitr::kable(exp.table,
-             caption = "Demographic information & teaching experience")
+    `Women in %` = ifelse(all(is.na(Gender)), NA, round(mean(Gender, na.rm = TRUE) * 100, 2)),
+    `M Age` = ifelse(all(is.na(Age)), NA, round(mean(Age, na.rm = TRUE), 2)),
+    `SD Age` = ifelse(all(is.na(Age)), NA, round(sd(Age, na.rm = TRUE), 2)),
+    `Min Age` = ifelse(all(is.na(Age)), NA, min(Age, na.rm = TRUE)),
+    `Max Age` = ifelse(all(is.na(Age)), NA, max(Age, na.rm = TRUE)),
+    `M Teaching Exp.` = ifelse(all(is.na(`Teaching Experience`)), NA, round(mean(`Teaching Experience`, na.rm = TRUE), 2)),
+    `SD Teaching Exp.` = ifelse(all(is.na(`Teaching Experience`)), NA, round(sd(`Teaching Experience`, na.rm = TRUE), 2)),
+    `Median Teaching Exp.` = ifelse(all(is.na(`Teaching Experience`)), NA, median(`Teaching Experience`, na.rm = TRUE)),
+    `Min Teaching Exp.` = ifelse(all(is.na(`Teaching Experience`)), NA, min(`Teaching Experience`, na.rm = TRUE)),
+    `Max Teaching Exp.` = ifelse(all(is.na(`Teaching Experience`)), NA, max(`Teaching Experience`, na.rm = TRUE)),
+    `M Semester` = ifelse(all(is.na(Semester)), NA, round(mean(Semester, na.rm = TRUE), 2)),
+    `SD Semester` = ifelse(all(is.na(Semester)), NA, round(sd(Semester, na.rm = TRUE), 2)),
+    `Min Semester` = ifelse(all(is.na(Semester)), NA, min(Semester, na.rm = TRUE)),
+    `Max Semester` = ifelse(all(is.na(Semester)), NA, max(Semester, na.rm = TRUE)),
+    `M Internship` = ifelse(all(is.na(Internship)), NA, round(mean(Internship, na.rm = TRUE), 2)),
+    `SD Internship` = ifelse(all(is.na(Internship)), NA, round(sd(Internship, na.rm = TRUE), 2)),
+    `Min Internship` = ifelse(all(is.na(Internship)), NA, min(Internship, na.rm = TRUE)),
+    `Max Internship` = ifelse(all(is.na(Internship)), NA, max(Internship, na.rm = TRUE)),
+    `Extracurricular Teaching Experience %` = ifelse(all(is.na(`Extracurricular Teaching Experience`)), NA, round(mean(`Extracurricular Teaching Experience`, na.rm = TRUE) * 100, 2)),
+    `Secondary Teaching Activities %` = ifelse(all(is.na(`Secondary Teaching Activities`)), NA, round(mean(`Secondary Teaching Activities`, na.rm = TRUE) * 100, 2))
+  )
+
+# Separate the tables from the summarized data
+demo_table <- summary_data %>%
+  select(Group, N, `Women in %`, `M Age`, `SD Age`, `Min Age`, `Max Age`, 
+         `M Teaching Exp.`, `SD Teaching Exp.`, `Median Teaching Exp.`, 
+         `Min Teaching Exp.`, `Max Teaching Exp.`)
+
+exp_table <- summary_data %>%
+  select(Group, N, `M Teaching Exp.`, `SD Teaching Exp.`, `Median Teaching Exp.`, 
+         `Min Teaching Exp.`, `Max Teaching Exp.`, `M Semester`, `SD Semester`, 
+         `Min Semester`, `Max Semester`, `M Internship`, `SD Internship`, 
+         `Min Internship`, `Max Internship`, `Extracurricular Teaching Experience %`, 
+         `Secondary Teaching Activities %`)
+
+# Display APA-style HTML tables
+demo_table %>%
+  kbl(caption = "Demographic Information & Teaching Experience", format = "html") %>%
+  kable_styling(full_width = FALSE, position = "center")
+
+exp_table %>%
+  kbl(caption = "Experience Details by Group", format = "html") %>%
+  kable_styling(full_width = FALSE, position = "center") %>% 
+  scroll_box(width = "100%", height = "400px") # Enables scrolling if needed
 
@@
 
-# return a character vector with names of .tsv data in data folder
- file_names <- list.files(path = "data",
-                          pattern = "interval_complete.tsv")
-
-# read every object names in file_names and save it as a tibble
- for (i in file_names) {
-
-   work_data <-
-     read_tsv(file = paste0("data/", i),
-              locale = locale(decimal_mark = ",")) %>%
-     dplyr::select(Group,
+# Step 1: List all .tsv files in the "data" folder that contain "interval_complete"
+file_names <- list.files(path = "data", pattern = "interval_complete.tsv", full.names = TRUE)
+
+# Step 2: Read and bind all .tsv files into a single tibble
+df_aoi <- file_names %>%
+  map_dfr(~ read_tsv(.x, locale = locale(decimal_mark = ",")) %>%
+            select(
+              Group,
               Participant,
@@
               starts_with("Time_to_first_fixation")
-     )
-
-   assign(value = work_data,
-          x = str_remove(paste0("tib_", i),
-                         pattern = ".tsv"))
-
- }
-
-# bind every tibble that contains "interval_complete" to a new tible
- df_aoi <-
-   mget(ls(pattern = "interval_complete")) %>%
-   bind_rows()
-
-# extract only participants ID number
- df_aoi$Participant <- as.numeric(
-   str_extract(df_aoi$Participant,
-               "\\d{3}")
-   )
-
-# exclude invalid participants
+            ))
+
+# Step 3: Extract only the participant's ID number (3 digits)
 df_aoi <- df_aoi %>%
-  filter(!Participant == 223)
-
-# remove temporary data for a cleaner workspace
- rm(list = ls(pattern = "^tib_ProVisio"))
- rm(work_data)
- rm(file_names)
- rm(i)
-
-```
-
+  mutate(Participant = as.numeric(str_extract(Participant, "\\d{3}")))
+
+# Step 4: Exclude invalid participant ID 223
+df_aoi <- df_aoi %>%
+  filter(Participant != 223)
+
+```
 ### Check variables
@@
 
-##################### LETTER SEARCH ########################
-
-# filter
-df_aoi %>%
-  filter(TOI == "Letter_search") %>% 
-  dplyr::select (
-    TOI,
-    Group,
-    Participant,
-    Duration_of_interval) %>% 
-  mutate(Duration_of_interval_sec = 
-           round(Duration_of_interval/1000, digits = 2)
-         ) -> df_letter
-# excluded IDs: 111 (due to viewing problems), 205 (missing letter search)
-
-# N, M, SD, min & max 
-letter.table <-
-  df_letter %>%
+##################### LETTER SEARCH #####################
+# 1. Filter and Prepare Data for "Letter Search"
+df_letter <- df_aoi %>%
+  filter(TOI == "Letter_search", !Participant %in% c(111, 205)) %>%  # Exclude participants with IDs 111 and 205
+  select(TOI, Group, Participant, Duration_of_interval) %>%
+  mutate(Duration_of_interval_sec = round(Duration_of_interval / 1000, 2))
+
+# 2. Descriptive Statistics: N, Mean (M), SD, Min, Max for "Letter Search" Duration
+letter_table <- df_letter %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M" = round(mean(Duration_of_interval_sec), digits = 2),
-    "SD" = round(sd(Duration_of_interval_sec), digits = 2),
-    "Min" = round(min(Duration_of_interval_sec), digits = 2),
-    "Max" = round(max(Duration_of_interval_sec), digits = 2)
-  )
-
-knitr::kable(letter.table,
-             caption = "N, M, SD, min & max letter search in seconds")
-
-```
-
-#### t-test & effect size "Letter search"
-```{r letter_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# LETTER SEARCH 
-# t-test for expertise differences
-t.test(
-  x = df_letter$Duration_of_interval_sec[df_letter$Group == "Expert"],
-  y = df_letter$Duration_of_interval_sec[df_letter$Group == "Novice"],
+    M = round(mean(Duration_of_interval_sec), 2),
+    SD = round(sd(Duration_of_interval_sec), 2),
+    Min = round(min(Duration_of_interval_sec), 2),
+    Max = round(max(Duration_of_interval_sec), 2)
+  )
+
+# Display Descriptive Statistics Table in APA Style
+knitr::kable(letter_table, caption = "N, M, SD, Min & Max Letter Search Duration (in seconds)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# 3. Conduct t-Test and Calculate Cohen's d for "Letter Search" Duration
+t_test_letter <- t.test(
+  Duration_of_interval_sec ~ Group,
+  data = df_letter,
   var.equal = TRUE
@@
 
-# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit)
-# effect size for expertise differences
-d_letter <- CohenD(
-  x = df_letter$Duration_of_interval_sec[df_letter$Group == "Expert"],
-  y = df_letter$Duration_of_interval_sec[df_letter$Group == "Novice"],
-  na.rm = TRUE
-)
-
-round(d_letter, 2)
-
-```
-
-### Fixations per minute across all AOIs
-```{r nof_all_aois, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# Filter data and select relevant columns, excluding "Disruptive_Person" only for the total fixations
-df_aoi_filtered <- df_aoi %>%
+# Calculate Cohen's d for the Effect Size
+d_letter <- cohen.d(
+  Duration_of_interval_sec ~ Group,
+  data = df_letter
+)
+
+# 4. Format t-Test and Cohen's d Results for APA Table
+t_test_result <- data.frame(
+  "Group Comparison" = "Experts vs. Novices",
+  "t-value" = round(t_test_letter$statistic, 2),
+  "df" = t_test_letter$parameter,
+  "p-value" = format.pval(t_test_letter$p.value, digits = 3, eps = .001),
+  "Mean Difference" = round(t_test_letter$estimate[1] - t_test_letter$estimate[2], 2),
+  "Cohen's d" = round(d_letter$estimate, 2),
+  "95% CI (d)" = paste0("[", round(d_letter$conf.int[1], 2), ", ", round(d_letter$conf.int[2], 2), "]")
+)
+
+# Display t-Test and Effect Size Results in APA Style
+knitr::kable(t_test_result, caption = "t-Test and Effect Size for Letter Search Duration (Experts vs. Novices)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+```
+
+#### Percentage of fixations on each AOI, relative to the total number of fixations during the entire "Lesson" 
+```{r nof_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# Step 1: Define AOI categories
+aoi_columns <- list(
+  "AOI_Students" = c(
+    "Number_of_fixations.Anna",
+    "Number_of_fixations.Bianca",
+    "Number_of_fixations.Carl(a)"
+  ),
+  "AOI_Disruptive_Person" = c("Number_of_fixations.Disruptive_Person"),
+  "AOI_Teacher_Material" = c(
+    "Number_of_fixations.Board_Screen",
+    "Number_of_fixations.Material_Teacher"
+  ),
+  "AOI_Student_Desk" = c(
+    "Number_of_fixations.Nametag_Anna",
+    "Number_of_fixations.Nametag_Bianca",
+    "Number_of_fixations.Nametag_Carl(a)",
+    "Number_of_fixations.Material_Students"
+  ),
+  "AOI_Classroom_Others" = c("Number_of_fixations.Classroom_Others")
+)
+
+# Step 2: Filter data for "Lesson" and select relevant columns
+df_fixations <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  select(
-    Group,
-    Participant,
-    Duration_of_interval,
-    starts_with("Number_of_fixations")
-  )
-
-# Add a new AOI 'Students' by summing fixations for Anna, Bianca, and Carl(a)
-df_aoi_filtered <- df_aoi_filtered %>%
-  mutate(
-    Number_of_fixations.Students = 
-      `Number_of_fixations.Anna` +
-      `Number_of_fixations.Bianca` +
-      `Number_of_fixations.Carl(a)`,
-
-    # Calculate Total Fixations for all AOIs, excluding "Disruptive_Person"
-    Total_fixations_all = sum(c_across(starts_with("Number_of_fixations"))[!names(c_across(starts_with("Number_of_fixations"))) == "Number_of_fixations.Disruptive_Person"], na.rm = TRUE)
-  )
-
-# Convert duration to minutes and calculate fixations per minute
-df_aoi_filtered <- df_aoi_filtered %>%
-  mutate(Duration_of_interval_min = Duration_of_interval / 60000)
-
-df_aoi_long <- df_aoi_filtered %>%
+  dplyr::select(Participant, Group, starts_with("Number_of_fixations"))
+
+# Step 3: Calculate total fixations per participant, excluding "Disruptive Person"
+# Extract relevant column names excluding "Disruptive Person"
+relevant_columns <- unlist(aoi_columns[c("AOI_Students", "AOI_Teacher_Material", "AOI_Student_Desk", "AOI_Classroom_Others")])
+
+# Calculate row sums for the relevant columns and add as a new column
+df_fixations <- df_fixations %>%
+  mutate(Total_fixations_excluding_disruptive = rowSums(across(all_of(relevant_columns)), na.rm = TRUE))
+
+# Step 4: Calculate fixation percentages for each AOI based on the adjusted total
+aoi_percentages <- df_fixations %>%
   rowwise() %>%
   mutate(
-    across(starts_with("Number_of_fixations"), ~ .x / Duration_of_interval_min, .names = "fixation_per_min_{.col}")
-  ) %>%
-  ungroup() %>%
-  pivot_longer(
-    cols = starts_with("fixation_per_min_Number_of_fixations"),
-    names_to = "AOI",
-    values_to = "Fixations_per_minute"
-  ) %>%
-  mutate(AOI = str_remove(AOI, "fixation_per_min_Number_of_fixations.")) %>%
-  mutate(AOI = factor(AOI, levels = c("Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
-                                      "Board_Screen", "Material_Teacher", "Material_Students", 
-                                      "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"))) %>%
-  arrange(AOI)
-
-# Summarize descriptives
-aois_descriptives_fixations <- df_aoi_long %>%
-  group_by(Group, AOI) %>%
+    AOI_Students_pct = sum(c_across(any_of(
+      aoi_columns$AOI_Students
+    )), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100,
+    AOI_Disruptive_Person_pct = sum(c_across(
+      any_of(aoi_columns$AOI_Disruptive_Person)
+    ), na.rm = TRUE) / (
+      Total_fixations_excluding_disruptive + sum(c_across(
+        any_of(aoi_columns$AOI_Disruptive_Person)
+      ), na.rm = TRUE)
+    ) * 100,
+    AOI_Teacher_Material_pct = sum(c_across(
+      any_of(aoi_columns$AOI_Teacher_Material)
+    ), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100,
+    AOI_Student_Desk_pct = sum(c_across(any_of(
+      aoi_columns$AOI_Student_Desk
+    )), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100,
+    AOI_Classroom_Others_pct = sum(c_across(
+      any_of(aoi_columns$AOI_Classroom_Others)
+    ), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100
+  ) %>%
+  ungroup()
+
+# Step 5: Summarize fixation percentages by Group and arrange in descending order
+grouped_aoi_percentages <- aoi_percentages %>%
+  group_by(Group) %>%
   summarise(
-    N = n(),
-    M = round(mean(Fixations_per_minute, na.rm = TRUE), 2),
-    SD = round(sd(Fixations_per_minute, na.rm = TRUE), 2),
-    Min = round(min(Fixations_per_minute, na.rm = TRUE), 2),
-    Max = round(max(Fixations_per_minute, na.rm = TRUE), 2)
-  )
-
-knitr::kable(aois_descriptives_fixations,
-             caption = "N, M, SD, min & max number of fixation per minute (across all AOIs)")
-
-# Visualization: Boxplot for fixations per minute across AOIs
-ggplot(df_aoi_long, aes(x = AOI, y = Fixations_per_minute, fill = Group)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_jitter(
-    position = position_jitterdodge(jitter.width = 0.15),
-    size = 1.5,
-    alpha = 0.7
+    Mean_AOI_Students_pct = round(mean(AOI_Students_pct, na.rm = TRUE), 2),
+    Mean_AOI_Disruptive_Person_pct = round(mean(AOI_Disruptive_Person_pct, na.rm = TRUE), 2),
+    Mean_AOI_Teacher_Material_pct = round(mean(AOI_Teacher_Material_pct, na.rm = TRUE), 2),
+    Mean_AOI_Student_Desk_pct = round(mean(AOI_Student_Desk_pct, na.rm = TRUE), 2),
+    Mean_AOI_Classroom_Others_pct = round(mean(AOI_Classroom_Others_pct, na.rm = TRUE), 2)
+  ) %>%
+  pivot_longer(cols = starts_with("Mean_AOI"), names_to = "AOI", values_to = "Fixation_Percentage") %>%
+  mutate(AOI = recode(AOI,
+                      "Mean_AOI_Students_pct" = "Students",
+                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Person",
+                      "Mean_AOI_Teacher_Material_pct" = "Teacher Material",
+                      "Mean_AOI_Student_Desk_pct" = "Student Desk",
+                      "Mean_AOI_Classroom_Others_pct" = "Classroom/Others")) %>%
+  arrange(Group, desc(Fixation_Percentage))
+
+# Step 6: Display the table with APA style
+kable(grouped_aoi_percentages, 
+      col.names = c("AOI", "Expert (%)", "Novice (%)"),
+      caption = "Average Fixation Percentage per AOI by Group (Novice vs. Expert) - Descending Order") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
+  add_header_above(c(" " = 1, "Fixation Percentage" = 2)) %>%
+  row_spec(0, bold = TRUE) %>%
+  column_spec(2:3, width = "3em", border_left = TRUE)
+
+# Step 7: Plot with descending AOI order, y-axis limit set to 100%, and percentage labels inside the bars
+ggplot(grouped_aoi_percentages, aes(x = reorder(AOI, -Fixation_Percentage), y = Fixation_Percentage, fill = Group)) +
+  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
+  geom_text(aes(label = paste0(Fixation_Percentage, "%")), 
+            position = position_dodge(width = 0.8), 
+            vjust = -0.3, size = 3) +
+  labs(
+    title = "Average Fixation Percentage by AOI and Group (Descending Order)",
+    x = "AOI",
+    y = "Fixation Percentage (%)"
   ) +
   scale_fill_brewer(palette = "RdBu") +
-  labs(x = "AOI", y = "Number of fixations per minute") +
-  ggtitle("Fixations per minute across all AOIs") +
   theme_minimal() +
-  theme(legend.position = "top", axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(
+    plot.title = element_text(hjust = 0.5, face = "bold"),
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  guides(fill = guide_legend(title = "Group")) +
+  ylim(0, 100)  # Set y-axis limit to 100%
+
+# Step 8: Perform a t-test between Experts and Novices on the percentage values and calculate Cohen's d
+# Define the AOIs you want to analyze with names matching those generated in Step 4
+aoi_list <- c("AOI_Students_pct", "AOI_Disruptive_Person_pct", "AOI_Teacher_Material_pct", "AOI_Student_Desk_pct", "AOI_Classroom_Others_pct")
+
+# Initialize an empty data frame to store the results
+results <- data.frame()
+
+# Loop over each AOI and calculate t-test and Cohen's d
+for (column_name in aoi_list) {
+
+  # Ensure that the column exists in the data
+  if (column_name %in% names(aoi_percentages)) {
+
+    # Filter the data for the current AOI and rename the column to Fixation_Percentage for consistency
+    aoi_data <- aoi_percentages %>%
+      select(Group, !!sym(column_name)) %>%
+      rename(Fixation_Percentage = !!sym(column_name))
+
+    # Separate data for each group
+    expert_data <- aoi_data$Fixation_Percentage[aoi_data$Group == "Expert"]
+    novice_data <- aoi_data$Fixation_Percentage[aoi_data$Group == "Novice"]
+
+    # Check if both groups have at least one observation
+    if (length(expert_data) > 0 && length(novice_data) > 0) {
+
+      # Perform a t-test between Experts and Novices on the current AOI's fixation percentage
+      t_test_result <- t.test(expert_data, novice_data, var.equal = TRUE)
+
+      # Calculate Cohen's d for the current AOI
+      cohen_d_value <- cohen.d(expert_data, novice_data, pooled = TRUE)$estimate
+
+      # Format the results for the current AOI and add to the results data frame
+      results <- rbind(
+        results,
+        data.frame(
+          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
+          "Group Comparison" = "Experts vs. Novices",
+          "t-value" = round(t_test_result$statistic, 2),
+          "df" = t_test_result$parameter,
+          "p-value" = format.pval(t_test_result$p.value, digits = 3, eps = .001),
+          "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
+          "Cohen's d" = round(cohen_d_value, 2),
+          "95% CI (d)" = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
+        )
+      )
+
+    } else {
+      # If one group has no data, append N/A values for this AOI
+      results <- rbind(
+        results,
+        data.frame(
+          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
+          "Group Comparison" = "Experts vs. Novices",
+          "t-value" = NA,
+          "df" = NA,
+          "p-value" = NA,
+          "Mean Difference" = NA,
+          "Cohen's d" = NA,
+          "95% CI (d)" = NA
+        )
+      )
+    }
+  }
+}
+
+# Clean up AOI names for readability in the final table
+aoi_name_mapping <- c(
+  "AOI_Students" = "Students",
+  "AOI_Disruptive_Person" = "Disruptive Person",
+  "AOI_Teacher_Material" = "Teacher Material",
+  "AOI_Student_Desk" = "Student Desk",
+  "AOI_Classroom_Others" = "Classroom/Others"
+)
+results$AOI <- aoi_name_mapping[results$AOI]
+
+# Display the combined results table in APA style without row names
+knitr::kable(results, caption = "t-Test and Effect Size for Fixation Percentage across AOIs (Experts vs. Novices)", row.names = FALSE) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 
-# filter group, participants, total duration & number fixation (micro-teaching unit)
-df_aoi %>%
+# 1. Data Preparation: Filter and Calculate Fixations per Minute in Micro-Teaching Unit
+df_aoi_sum <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  dplyr::select (
+  dplyr::select(
     Group,
@@
     starts_with("Average_duration"),
-    !"Total_duration_of_fixations.Disruptive_Person",
-    !"Number_of_fixations.Disruptive_Person",
-    !"Average_duration_of_fixations.Disruptive_Person"
+    -contains("Disruptive_Person")
   ) %>%
@@
     Participant = Participant,
-    Duration_of_interval = Duration_of_interval, 
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
-    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
+    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
+    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
     Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
-    Number_fixation_msec_mtu = round(Sum_number_fixation / Duration_of_interval, digits = 6),
-    Number_fixation_sec_mtu = round(Sum_number_fixation / Duration_of_interval_sec, digits = 2),
-    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
+    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, 0),
     Group = as_factor(Group)
   ) %>%
-  drop_na() -> df_aoi_sum
-
-# N, M, SD, min & max number of fixation per minute (micro-teaching unit)
-nof.table <-
-  df_aoi_sum %>%
+  drop_na()
+
+# 2. Descriptive Statistics Table
+nof_table <- df_aoi_sum %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M" = round(mean(Number_fixation_min_mtu), digits = 2),
-    "SD" = round(sd(Number_fixation_min_mtu), digits = 2),
-    "Min" = round(min(Number_fixation_min_mtu), digits = 2),
-    "Max" = round(max(Number_fixation_min_mtu), digits = 2)
-  )
-
-knitr::kable(nof.table,
-             caption = "N, M, SD, min & max number of fixation per minute (micro-teaching unit)")
-
-# plotting number of fixations (micro-teaching unit)
-df_aoi_sum %>%
+    M = round(mean(Number_fixation_min_mtu), 2),
+    SD = round(sd(Number_fixation_min_mtu), 2),
+    Min = round(min(Number_fixation_min_mtu), 2),
+    Max = round(max(Number_fixation_min_mtu), 2)
+  )
+
+# Display the descriptive table in APA style
+knitr::kable(nof_table, caption = "N, M, SD, min & max number of fixation per minute (micro-teaching unit)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# 3. Calculate means and standard deviations for Novice and Expert
+mean_novice_mtu <- mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE)
+sd_novice_mtu <- sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE)
+mean_expert_mtu <- mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE)
+sd_expert_mtu <- sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE)
+
+# 4. Perform t-test to get the p-value
+t_test_mtu <- t.test(
+  Number_fixation_min_mtu ~ Group,
+  data = df_aoi_sum,
+  var.equal = TRUE
+)
+p_value_mtu <- round(t_test_mtu$p.value, 3)
+
+# 5. Calculate Cohen's d for effect size using formula syntax
+library(effsize)
+cohen_d_mtu <- round(cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)$estimate, 2)
+
+# 6. Plotting the Number of Fixations per Minute (Micro-Teaching Unit)
+# Set y-limit based on data to provide space for annotations
+y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5
+
+plot_number_group <- df_aoi_sum %>%
   ggplot(mapping = aes(x = Group, y = Number_fixation_min_mtu)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
+  geom_jitter(
+    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
   ) +
-  ylim(0, 150) +
+  ylim(0, y_max_mtu) +
   labs(x = "", y = "Number of fixations per minute") +
@@
   theme_cowplot() +
-  theme(legend.position = "none") -> plot_number_group
+  theme(legend.position = "none") +
+  # Add annotations for mean (M) and SD using atop() to place SD below M
+  annotate("text", x = 1, y = y_max_mtu * 0.85,
+           label = paste0("atop(italic(M) == ", mean_novice_mtu, ", italic(SD) == ", sd_novice_mtu, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  annotate("text", x = 2, y = y_max_mtu * 0.85,
+           label = paste0("atop(italic(M) == ", mean_expert_mtu, ", italic(SD) == ", sd_expert_mtu, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  # Add p-value and Cohen's d annotations above the boxplots
+  annotate("text", x = 1.5, y = y_max_mtu * 0.95,
+           label = paste0("p = ", p_value_mtu, "\nd = ", cohen_d_mtu),
+           hjust = 0.5, size = 4, fontface = "italic")
 
@@
 
-```
-
-#### t-test & effect size "Number of fixation (micro-teaching unit)"
-```{r nof_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit) 
-# t-test for expertise differences
-t.test(
-  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
-  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
-  var.equal = TRUE
-)
-
-# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit)
-# effect size for expertise differences
-d_number_all <- CohenD(
-  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
-  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
-  na.rm = TRUE
-)
-
-round(d_number_all, 2)
+# 7. Format the t-Test and Cohen's d results for APA Table
+t_test_result <- data.frame(
+  "Group Comparison" = "Experts vs. Novices",
+  "t-value" = round(t_test_mtu$statistic, 2),
+  "df" = t_test_mtu$parameter,
+  "p-value" = format.pval(t_test_mtu$p.value, digits = 3, eps = .001),
+  "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
+  "Cohen's d" = cohen_d_mtu,
+  "95% CI (d)" = paste0("[", round(t_test_mtu$conf.int[1], 2), ", ", round(t_test_mtu$conf.int[2], 2), "]")
+)
+
+# Display t-Test and Effect Size results in APA style
+knitr::kable(t_test_result, caption = "t-Test and Effect Size for Number of Fixations per Minute (Micro-Teaching Unit)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 
-# filter group & total duration & number fixation (AOI students)
-df_aoi %>%
+# 1. Data Preparation: Filter and Calculate Fixations per Minute on AOI Students
+df_aoi_stud <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  dplyr::select (
+  select(
     Group,
@@
     Participant,
-    "Total_duration_of_fixations.Anna",
-    "Total_duration_of_fixations.Bianca",
-    "Total_duration_of_fixations.Carl(a)",
-    "Number_of_fixations.Anna",
-    "Number_of_fixations.Bianca",
-    "Number_of_fixations.Carl(a)"
+    starts_with("Total_duration_of_fixations"),
+    starts_with("Number_of_fixations")
   ) %>%
@@
     Group = as_factor(Group),
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
-    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
+    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
+    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
     Participant = Participant,
@@
     Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, digits = 2),
-    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, digits = 2),
-    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0)
-    ) -> df_aoi_stud
-
-# N, M, SD, min & max number of fixations per minute (AOI students)
-nof.min.stud.table <-
-  df_aoi_stud %>%
+    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
+    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, 2),
+    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
+  ) %>%
+  drop_na()
+
+# 2. Descriptive Statistics: N, Mean (M), SD, Min, Max for Fixations per Minute (AOI Students)
+nof_min_stud_table <- df_aoi_stud %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M" = round(mean(Stud_number_fixation_min), digits = 2),
-    "SD" = round(sd(Stud_number_fixation_min), digits = 2),
-    "Min" = round(min(Stud_number_fixation_min), digits = 2),
-    "Max" = round(max(Stud_number_fixation_min), digits = 2)
-  )
-
-knitr::kable(nof.min.stud.table,
-             caption = "N, M, SD, min & max number of fixations per minute (AOI students)")
-
-# plotting number of fixations per minute on AOI Students
-df_aoi_stud %>%
+    M = round(mean(Stud_number_fixation_min), 2),
+    SD = round(sd(Stud_number_fixation_min), 2),
+    Min = round(min(Stud_number_fixation_min), 2),
+    Max = round(max(Stud_number_fixation_min), 2)
+  )
+
+# Display Descriptive Statistics Table in APA Style
+knitr::kable(nof_min_stud_table, caption = "N, M, SD, Min & Max Number of Fixations per Minute (AOI Students)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# 3. Plotting the Number of Fixations per Minute on AOI Students
+# Calculate descriptive statistics
+summary_stats <- df_aoi_stud %>%
+  group_by(Group) %>%
+  summarise(
+    M = round(mean(Stud_number_fixation_min), 2),
+    SD = round(sd(Stud_number_fixation_min), 2)
+  )
+
+# Conduct t-test and calculate effect size
+t_test_stud <- t.test(
+  Stud_number_fixation_min ~ Group,
+  data = df_aoi_stud,
+  var.equal = TRUE
+)
+
+# Cohen's d for effect size
+d_number_stud <- cohen.d(
+  Stud_number_fixation_min ~ Group,
+  data = df_aoi_stud
+)
+
+# Extract statistical values
+mean_expert <- summary_stats %>% filter(Group == "Expert") %>% pull(M)
+sd_expert <- summary_stats %>% filter(Group == "Expert") %>% pull(SD)
+mean_novice <- summary_stats %>% filter(Group == "Novice") %>% pull(M)
+sd_novice <- summary_stats %>% filter(Group == "Novice") %>% pull(SD)
+p_value <- format.pval(t_test_stud$p.value, digits = 3, eps = .001)
+cohen_d <- round(d_number_stud$estimate, 2)
+
+# Determine max value for ylim to ensure all text is visible
+y_max <- max(df_aoi_stud$Stud_number_fixation_min) * 1.5  # Increase this multiplier if needed
+
+# Plot with adjusted ylim and annotations for readability
+plot_number_min_stud <- df_aoi_stud %>%
   ggplot(mapping = aes(x = Group, y = Stud_number_fixation_min)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.005
-    )
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
+  geom_jitter(
+    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
   ) +
-  ylim(0, 50) +
   labs(x = "", y = "Number of fixations per minute") +
@@
   theme_cowplot() +
-  theme(legend.position = "none") -> plot_number_min_stud
+  theme(legend.position = "none") +
+  ylim(0, y_max) +  # Set y-axis limit to ensure space for annotations
+  # Adjusted annotations for mean (M) and SD using atop() to place SD below M
+  annotate("text", x = 1, y = y_max * 0.85,
+           label = paste0("atop(italic(M) == ", mean_novice, ", italic(SD) == ", sd_novice, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  annotate("text", x = 2, y = y_max * 0.85,
+           label = paste0("atop(italic(M) == ", mean_expert, ", italic(SD) == ", sd_expert, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  # Place p-value and d above the boxplots
+  annotate("text", x = 1.5, y = y_max * 0.95,
+           label = paste0("p = ", p_value, "\nd = ", cohen_d),
+           hjust = 0.5, size = 4, fontface = "italic")
 
@@
 
-```
-
-#### t-test & effect size "Number of fixation" (AOI students)
-```{r nof_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# NUMBER OF FIXATIONS on AOI students 
-# t-test for expertise differences
-t.test(
-  x = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Expert"],
-  y = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Novice"],
+# 4. t-Test and Effect Size Calculation for Number of Fixations per Minute on AOI Students
+t_test_stud <- t.test(
+  Stud_number_fixation_min ~ Group,
+  data = df_aoi_stud,
   var.equal = TRUE
@@
 
-# NUMBER OF FIXATIONS on AOI students
-# effect size for expertise differences
-d_number_stud <- CohenD(
-  x = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Expert"],
-  y = df_aoi_stud$Stud_number_fixation_min[df_aoi_stud$Group == "Novice"],
-  na.rm = TRUE
-)
-
-round(d_number_stud, 2)
-
-```
-
-#### Number of fixations per minute (AOI others)
-```{r nof_others, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### NUMBER OF FIXATIONS (AOI others) ########################
-
-# filter group & total duration & number fixation (AOI others)
-df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select (
-    Group,
-    Duration_of_interval,
-    Participant,
-    "Total_duration_of_fixations.Board_Screen",
-    "Total_duration_of_fixations.Classroom_Others",
-    "Total_duration_of_fixations.Material_Students",
-    "Total_duration_of_fixations.Material_Teacher",
-    "Total_duration_of_fixations.Nametag_Anna",
-    "Total_duration_of_fixations.Nametag_Bianca",
-    "Total_duration_of_fixations.Nametag_Carl(a)",
-    "Number_of_fixations.Board_Screen",
-    "Number_of_fixations.Classroom_Others",
-    "Number_of_fixations.Material_Students",
-    "Number_of_fixations.Material_Teacher",
-    "Number_of_fixations.Nametag_Anna",
-    "Number_of_fixations.Nametag_Bianca",
-    "Number_of_fixations.Nametag_Carl(a)"
-  ) %>%
-  rowwise() %>%
-  transmute(
-    Group = as_factor(Group),
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
-    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
-    Participant = Participant,
-    Others_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Others_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Others_number_fixation_min = round(Others_number_fixation / Duration_of_interval_min, digits = 2),
-    Average_duration_others = round(Others_duration_fixation / Others_number_fixation, digits = 0)
-    ) -> df_aoi_others
-
-# N, M, SD, min & max number of fixations per minute (AOI students)
-nof.min.others.table <-
-  df_aoi_others %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(Others_number_fixation_min), digits = 2),
-    "SD" = round(sd(Others_number_fixation_min), digits = 2),
-    "Min" = round(min(Others_number_fixation_min), digits = 2),
-    "Max" = round(max(Others_number_fixation_min), digits = 2)
-  )
-
-knitr::kable(nof.min.others.table,
-             caption = "N, M, SD, min & max number of fixations per minute (AOI others)")
-
-# plotting number of fixations per minute on AOI Students
-df_aoi_others %>%
-  ggplot(mapping = aes(x = Group, y = Others_number_fixation_min)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.005
-    )
-  ) +
-  ylim(0, 100) +
-  labs(x = "", y = "Number of fixations per minute") +
-  scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Number of fixations per minute\n(AOI others)") +
-  theme_cowplot() +
-  theme(legend.position = "none") -> plot_number_min_others
-
-plot_number_min_others
-
-```
-
-#### t-test & effect size "Number of fixation" (AOI others)
-```{r nof_others_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# NUMBER OF FIXATIONS on AOI others 
-# t-test for expertise differences
-t.test(
-  x = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Expert"],
-  y = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Novice"],
-  var.equal = TRUE
-)
-
-# NUMBER OF FIXATIONS on AOI students
-# effect size for expertise differences
-d_number_others <- CohenD(
-  x = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Expert"],
-  y = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Novice"],
-  na.rm = TRUE
-)
-
-round(d_number_others, 2)
-
-```
-
-#### Number of fixations (AOI disruptive person)
+# Calculate Cohen's d for the Effect Size
+d_number_stud <- cohen.d(
+  Stud_number_fixation_min ~ Group,
+  data = df_aoi_stud
+)
+
+# 5. Format t-Test and Cohen's d Results for APA Table
+t_test_result_stud <- data.frame(
+  "Group Comparison" = "Experts vs. Novices",
+  "t-value" = round(t_test_stud$statistic, 2),
+  "df" = t_test_stud$parameter,
+  "p-value" = format.pval(t_test_stud$p.value, digits = 3, eps = .001),
+  "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2),
+  "Cohen's d" = round(d_number_stud$estimate, 2),
+  "95% CI (d)" = paste0("[", round(d_number_stud$conf.int[1], 2), ", ", round(d_number_stud$conf.int[2], 2), "]")
+)
+
+# Display t-Test and Effect Size Results in APA Style
+knitr::kable(t_test_result_stud, caption = "t-Test and Effect Size for Number of Fixations per Minute (AOI Students)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+```
+
+#### Number of fixations per seconds (AOI disruptive person)
 ```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-```
-
-#### t-test & effect size "Number of fixations" (AOI disruptive person)
-```{r nof_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
 # Function to format t-test and Cohen's d results into a tidy data frame, with checks for non-numeric values
@@
 
-```
-
-#### t-test & effect size "Duration of disruptions"
-```{r disrup_dur_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# Function to format t-test and Cohen's d results into a tidy data frame
-# Function to format t-test and Cohen's d results into a tidy data frame, with checks for non-numeric values
+# Define categories if not already defined
+categories <- unique(df_aoi_disrup$Disruption_Category)
+
+# Function to format t-test and Cohen's d results into a tidy data frame with additional debugging
 format_results <- function(t_test, cohen_d) {
+  if (is.list(cohen_d) && !is.null(cohen_d$estimate) && !is.null(cohen_d$conf.int)) {
     data.frame(
-    "t-value" = if (is.numeric(t_test$statistic)) round(t_test$statistic, 2) else NA,
-    "df" = if (is.numeric(t_test$parameter)) round(t_test$parameter, 2) else NA,
-    "p-value" = if (!is.null(t_test$p.value)) format.pval(t_test$p.value, digits = 3, eps = .001) else "NA",
-    "Mean Difference" = if (is.numeric(t_test$estimate[1] - t_test$estimate[2])) round(t_test$estimate[1] - t_test$estimate[2], 2) else NA,
-    "Cohen's d" = if (is.numeric(cohen_d$estimate)) round(cohen_d$estimate, 2) else NA,
-    "95% CI (d)" = if (!is.null(cohen_d$conf.int)) 
-                    paste0("[", round(cohen_d$conf.int[1], 2), ", ", round(cohen_d$conf.int[2], 2), "]") 
-                   else "NA"
+      "t-value" = round(t_test$statistic, 2),
+      "df" = round(t_test$parameter, 2),
+      "p-value" = format.pval(t_test$p.value, digits = 3, eps = .001),
+      "Mean Difference" = round(t_test$estimate[1] - t_test$estimate[2], 2),
+      "Cohen's d" = round(cohen_d$estimate, 2),
+      "95% CI (d)" = paste0("[", round(cohen_d$conf.int[1], 2), ", ", round(cohen_d$conf.int[2], 2), "]")
+    )
+  } else {
+    print("Cohen's d returned an unexpected structure or NA values. Setting values to NA.")
+    print(cohen_d)  # Print the structure of cohen_d for debugging
+    data.frame(
+      "t-value" = round(t_test$statistic, 2),
+      "df" = round(t_test$parameter, 2),
+      "p-value" = format.pval(t_test$p.value, digits = 3, eps = .001),
+      "Mean Difference" = round(t_test$estimate[1] - t_test$estimate[2], 2),
+      "Cohen's d" = NA,
+      "95% CI (d)" = NA
     )
   }
-
-# 3. Overall t-test and Cohen's d for Duration by Group
+}
+
+# 1. Overall t-test and Cohen's d for Duration by Group
 t_duration_group <- t.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup)
-d_duration_group <- cohen.d(Duration_of_interval_sec ~ Group, data = df_aoi_disrup)
+d_duration_group <- tryCatch(cohen.d(Duration_of_interval_sec ~ Group, data = df_aoi_disrup), 
+                             error = function(e) NA)
 duration_group_result <- format_results(t_duration_group, d_duration_group)
 
-# 4. t-test and Cohen's d for Duration by Category
+# 2. t-test and Cohen's d for Duration by Category with debugging output
 duration_category_results <- lapply(categories, function(cat) {
   cat_data <- df_aoi_disrup %>% filter(Disruption_Category == cat)
+
+  # Perform t-test
   t_test_cat <- t.test(Duration_of_interval_sec ~ Group, data = cat_data)
-  d_cat <- cohen.d(Duration_of_interval_sec ~ Group, data = cat_data)
+
+  # Calculate Cohen's d with error handling
+  d_cat <- tryCatch(cohen.d(Duration_of_interval_sec ~ Group, data = cat_data), 
+                    error = function(e) NA)
+
+  # Debugging: Check structure of d_cat for each category
+  print(paste("Category:", cat))
+  print("Structure of Cohen's d result:")
+  str(d_cat)  # Display the structure of d_cat to debug
+
+  # Format results with error handling
   format_results(t_test_cat, d_cat)
@@
 duration_category_df <- do.call(rbind, duration_category_results)
-duration_category_df <- data.frame(Category = categories, duration_category_df, row.names = NULL)  # Ensure row names are reset
+duration_category_df <- data.frame(Category = categories, duration_category_df, row.names = NULL)
 
@@
 
-### Duration of Fixations across all AOIs
-```{r average_dur_all_aoi, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# Filter and select necessary columns
-df_aoi_filtered <- df_aoi %>%
+#### Percentage of fixation durations on each AOI, relative to the total duration of fixations during the entire "Lesson" 
+```{r dur_fix_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# Step 1: Define AOI categories with correct column names for fixation duration
+aoi_columns <- list(
+  "AOI_Students" = c(
+    "Total_duration_of_fixations.Anna",
+    "Total_duration_of_fixations.Bianca",
+    "Total_duration_of_fixations.Carl(a)"
+  ),
+  "AOI_Disruptive_Person" = c("Total_duration_of_fixations.Disruptive_Person"),
+  "AOI_Teacher_Material" = c(
+    "Total_duration_of_fixations.Board_Screen",
+    "Total_duration_of_fixations.Material_Teacher"
+  ),
+  "AOI_Student_Desk" = c(
+    "Total_duration_of_fixations.Nametag_Anna",
+    "Total_duration_of_fixations.Nametag_Bianca",
+    "Total_duration_of_fixations.Nametag_Carl(a)",
+    "Total_duration_of_fixations.Material_Students"
+  ),
+  "AOI_Classroom_Others" = c("Total_duration_of_fixations.Classroom_Others")
+)
+
+# Step 2: Filter data for "Lesson" and select relevant columns for fixation duration
+df_durations <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  select(
+  dplyr::select(Participant, Group, starts_with("Total_duration_of_fixations"))
+
+# Step 3: Calculate total fixation duration per participant, excluding "Disruptive Person"
+relevant_columns <- unlist(aoi_columns[c("AOI_Students", "AOI_Teacher_Material", "AOI_Student_Desk", "AOI_Classroom_Others")])
+
+df_durations <- df_durations %>%
+  mutate(Total_duration_excluding_disruptive = rowSums(across(all_of(relevant_columns)), na.rm = TRUE))
+
+# Step 4: Calculate fixation duration percentages for each AOI based on the adjusted total duration
+aoi_durations_percentages <- df_durations %>%
+  rowwise() %>%
+  mutate(
+    AOI_Students_pct = sum(c_across(any_of(aoi_columns$AOI_Students)), na.rm = TRUE) / Total_duration_excluding_disruptive * 100,
+    AOI_Disruptive_Person_pct = sum(c_across(any_of(aoi_columns$AOI_Disruptive_Person)), na.rm = TRUE) / (
+      Total_duration_excluding_disruptive + sum(c_across(any_of(aoi_columns$AOI_Disruptive_Person)), na.rm = TRUE)
+    ) * 100,
+    AOI_Teacher_Material_pct = sum(c_across(any_of(aoi_columns$AOI_Teacher_Material)), na.rm = TRUE) / Total_duration_excluding_disruptive * 100,
+    AOI_Student_Desk_pct = sum(c_across(any_of(aoi_columns$AOI_Student_Desk)), na.rm = TRUE) / Total_duration_excluding_disruptive * 100,
+    AOI_Classroom_Others_pct = sum(c_across(any_of(aoi_columns$AOI_Classroom_Others)), na.rm = TRUE) / Total_duration_excluding_disruptive * 100
+  ) %>%
+  ungroup()
+
+# Step 5: Summarize fixation duration percentages by Group and arrange in descending order
+grouped_aoi_durations_percentages <- aoi_durations_percentages %>%
+  group_by(Group) %>%
+  summarise(
+    Mean_AOI_Students_pct = round(mean(AOI_Students_pct, na.rm = TRUE), 2),
+    Mean_AOI_Disruptive_Person_pct = round(mean(AOI_Disruptive_Person_pct, na.rm = TRUE), 2),
+    Mean_AOI_Teacher_Material_pct = round(mean(AOI_Teacher_Material_pct, na.rm = TRUE), 2),
+    Mean_AOI_Student_Desk_pct = round(mean(AOI_Student_Desk_pct, na.rm = TRUE), 2),
+    Mean_AOI_Classroom_Others_pct = round(mean(AOI_Classroom_Others_pct, na.rm = TRUE), 2)
+  ) %>%
+  pivot_longer(cols = starts_with("Mean_AOI"), names_to = "AOI", values_to = "Duration_Percentage") %>%
+  mutate(AOI = recode(AOI,
+                      "Mean_AOI_Students_pct" = "Students",
+                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Person",
+                      "Mean_AOI_Teacher_Material_pct" = "Teacher Material",
+                      "Mean_AOI_Student_Desk_pct" = "Student Desk",
+                      "Mean_AOI_Classroom_Others_pct" = "Classroom/Others")) %>%
+  arrange(Group, desc(Duration_Percentage))
+
+# Step 6: Plot the fixation duration percentages by AOI and Group
+ggplot(grouped_aoi_durations_percentages, aes(x = reorder(AOI, -Duration_Percentage), y = Duration_Percentage, fill = Group)) +
+  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
+  geom_text(aes(label = paste0(Duration_Percentage, "%")), 
+            position = position_dodge(width = 0.8), 
+            vjust = -0.3, size = 3) +
+  labs(
+    title = "Average Fixation Duration Percentage by AOI and Group (Descending Order)",
+    x = "AOI",
+    y = "Fixation Duration Percentage (%)"
+  ) +
+  scale_fill_brewer(palette = "RdBu") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5, face = "bold"),
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  guides(fill = guide_legend(title = "Group")) +
+  ylim(0, 100)  # Set y-axis limit to 100%
+
+# Step 7: Perform a t-test between Experts and Novices on the duration percentages and calculate Cohen's d
+aoi_list <- c("AOI_Students_pct", "AOI_Disruptive_Person_pct", "AOI_Teacher_Material_pct", "AOI_Student_Desk_pct", "AOI_Classroom_Others_pct")
+results <- data.frame()
+
+for (column_name in aoi_list) {
+  if (column_name %in% names(aoi_durations_percentages)) {
+    aoi_data <- aoi_durations_percentages %>%
+      select(Group, !!sym(column_name)) %>%
+      rename(Duration_Percentage = !!sym(column_name))
+
+    expert_data <- aoi_data$Duration_Percentage[aoi_data$Group == "Expert"]
+    novice_data <- aoi_data$Duration_Percentage[aoi_data$Group == "Novice"]
+
+    if (length(expert_data) > 0 && length(novice_data) > 0) {
+      t_test_result <- t.test(expert_data, novice_data, var.equal = TRUE)
+      cohen_d_value <- cohen.d(expert_data, novice_data, pooled = TRUE)$estimate
+
+      results <- rbind(
+        results,
+        data.frame(
+          "AOI" = gsub("_pct", "", column_name),
+          "Group Comparison" = "Experts vs. Novices",
+          "t-value" = round(t_test_result$statistic, 2),
+          "df" = t_test_result$parameter,
+          "p-value" = format.pval(t_test_result$p.value, digits = 3, eps = .001),
+          "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
+          "Cohen's d" = round(cohen_d_value, 2),
+          "95% CI (d)" = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
+        )
+      )
+    } else {
+      results <- rbind(
+        results,
+        data.frame(
+          "AOI" = gsub("_pct", "", column_name),
+          "Group Comparison" = "Experts vs. Novices",
+          "t-value" = NA,
+          "df" = NA,
+          "p-value" = NA,
+          "Mean Difference" = NA,
+          "Cohen's d" = NA,
+          "95% CI (d)" = NA
+        )
+      )
+    }
+  }
+}
+
+# Map AOI names to clean versions for readability in the final results table
+results$AOI <- recode(results$AOI,
+                      "AOI_Students" = "Students",
+                      "AOI_Disruptive_Person" = "Disruptive Person",
+                      "AOI_Teacher_Material" = "Teacher Material",
+                      "AOI_Student_Desk" = "Student Desk",
+                      "AOI_Classroom_Others" = "Classroom/Others")
+
+# Display the t-Test and Effect Size table in APA style
+knitr::kable(results, 
+             caption = "t-Test and Effect Size for Fixation Duration Percentage across AOIs (Experts vs. Novices)", 
+             row.names = FALSE) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+```
+
+#### Average duration of fixations in milliseconds (micro-teaching unit)
+```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### AVERAGE FIXATION DURATION ANALYSIS ########################
+
+# 1. Data Preparation: Filter and Calculate Average Fixation Duration in the Micro-Teaching Unit
+df_aoi_sum <- df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select(
     Group,
@@
     starts_with("Total_duration_of_fixations"),
-    starts_with("Number_of_fixations")
-  )
-
-# Create a new AOI 'Students' by summing durations and counts for Anna, Bianca, and Carl(a)
-df_aoi_filtered <- df_aoi_filtered %>%
-  mutate(
-    Total_duration_of_fixations.Students = 
-      `Total_duration_of_fixations.Anna` +
-      `Total_duration_of_fixations.Bianca` +
-      `Total_duration_of_fixations.Carl(a)`,
-    Number_of_fixations.Students = 
-      `Number_of_fixations.Anna` +
-      `Number_of_fixations.Bianca` +
-      `Number_of_fixations.Carl(a)`,
-
-    # Calculate Average Duration for all AOIs, excluding "Disruptive_Person"
-    Total_duration_excl_disruptive = sum(c_across(starts_with("Total_duration_of_fixations"))[!names(c_across(starts_with("Total_duration_of_fixations"))) == "Total_duration_of_fixations.Disruptive_Person"], na.rm = TRUE),
-    Total_fixations_excl_disruptive = sum(c_across(starts_with("Number_of_fixations"))[!names(c_across(starts_with("Number_of_fixations"))) == "Number_of_fixations.Disruptive_Person"], na.rm = TRUE),
-    Average_duration_all = round(Total_duration_excl_disruptive / Total_fixations_excl_disruptive, digits = 2)  # Overall average duration
-  )
-
-# Calculate average fixation duration for each AOI individually, excluding disruptive person
-df_aoi_avg_long <- df_aoi_filtered %>%
-  pivot_longer(
-    cols = starts_with("Total_duration_of_fixations") | starts_with("Number_of_fixations"),
-    names_to = "Measure_AOI",
-    values_to = "Values"
-  ) %>%
-  separate(Measure_AOI, into = c("Measure", "AOI"), sep = "\\.", extra = "merge") %>%
-  pivot_wider(
-    names_from = Measure,
-    values_from = Values
-  ) %>%
-  filter(AOI != "Disruptive_Person") %>%
-  mutate(
-    Average_duration = round(Total_duration_of_fixations / Number_of_fixations, digits = 2)
-  )
-
-# Set the order of AOIs based on the specified sequence
-df_aoi_avg_long <- df_aoi_avg_long %>%
-  mutate(AOI = factor(AOI, levels = c(
-    "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_person", 
-    "Board_Screen", "Material_Teacher", "Material_Students", 
-    "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"
-  ))) %>%
-  arrange(AOI)
-
-# Summarize descriptives for average duration of fixations
-aois_descriptives_durations <- df_aoi_avg_long %>%
-  group_by(Group, AOI) %>%
-  summarise(
-    N = n(),
-    M = round(mean(Average_duration, na.rm = TRUE), 2),
-    SD = round(sd(Average_duration, na.rm = TRUE), 2),
-    Min = round(min(Average_duration, na.rm = TRUE), 2),
-    Max = round(max(Average_duration, na.rm = TRUE), 2)
-  )
-
-knitr::kable(aois_descriptives_durations,
-             caption = "N, M, SD, min & max duration of fixation per minute (across all AOIs)")
-
-# Visualization: Boxplot for average duration of fixations across AOIs
-ggplot(df_aoi_avg_long, aes(x = AOI, y = Average_duration, fill = Group)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_jitter(
-    position = position_jitterdodge(jitter.width = 0.15),
-    size = 1.5,
-    alpha = 0.7
-  ) +
-  ylim(0, 1500) +
-  scale_fill_brewer(palette = "RdBu") +
-  labs(x = "AOI", y = "Average Duration of Fixations (ms)") +
-  ggtitle("Average Duration of Fixations across all AOIs") +
-  theme_minimal() +
-  theme(legend.position = "top", axis.text.x = element_text(angle = 45, hjust = 1))
-
-```
-
-#### Average duration of fixations in milliseconds (micro-teaching unit)
-```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### AVERAGE DURATION OF FIXATIONS (MICRO-TEACHING UNIT) ########################
-
-# N, M, SD, min & max average duration of fixations (micro-teaching unit)
-dur.table <- 
-  df_aoi_sum %>%  
+    starts_with("Number_of_fixations"),
+    starts_with("Average_duration"),
+    !"Total_duration_of_fixations.Disruptive_Person",
+    !"Number_of_fixations.Disruptive_Person",
+    !"Average_duration_of_fixations.Disruptive_Person"
+  ) %>%
+  rowwise() %>%
+  transmute(
+    Group = as_factor(Group),
+    Participant = Participant,
+    Duration_of_interval = Duration_of_interval,
+    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
+    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
+    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Average_duration_fixation = round(Sum_duration_fixation / Sum_number_fixation, 2)
+  ) %>%
+  drop_na()
+
+# 2. Descriptive Statistics Table
+fixation_duration_table <- df_aoi_sum %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M in ms" = round(mean(Average_duration_mtu), digits = 2),
-    "SD in ms" = round(sd(Average_duration_mtu), digits = 2),
-    "Min in ms" = round(min(Average_duration_mtu), digits = 2),
-    "Max in ms" = round(max(Average_duration_mtu), digits = 2)
-    )
-
-knitr::kable(dur.table,
-             caption = "N, M, SD, min & max duration of fixations in milliseconds (micro-teaching unit)")
-
-# plotting average duration (micro-teaching unit)
-df_aoi_sum %>% 
-  ggplot(mapping = aes(x = Group,
-                       y = Average_duration_mtu)) +
-  geom_boxplot(mapping = aes(fill = Group),
-               outlier.shape = NA) +
-  geom_point(size = 2,
-             alpha = 0.7,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  ylim(0, 1000) +
-
-  labs(x ="",
-       y = "Milliseconds") + 
+    M = round(mean(Average_duration_fixation, na.rm = TRUE), 2),
+    SD = round(sd(Average_duration_fixation, na.rm = TRUE), 2),
+    Min = round(min(Average_duration_fixation, na.rm = TRUE), 2),
+    Max = round(max(Average_duration_fixation, na.rm = TRUE), 2)
+  )
+
+# Display the descriptive table in APA style
+knitr::kable(fixation_duration_table, caption = "N, M, SD, min & max Average Fixation Duration (micro-teaching unit)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# 3. Calculate means and standard deviations for Novice and Expert groups
+mean_novice_fixation <- round(mean(df_aoi_sum$Average_duration_fixation[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
+sd_novice_fixation <- round(sd(df_aoi_sum$Average_duration_fixation[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
+mean_expert_fixation <- round(mean(df_aoi_sum$Average_duration_fixation[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)
+sd_expert_fixation <- round(sd(df_aoi_sum$Average_duration_fixation[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)
+
+# 4. Perform t-test to get the p-value
+t_test_fixation <- t.test(
+  Average_duration_fixation ~ Group,
+  data = df_aoi_sum,
+  var.equal = TRUE
+)
+p_value_fixation <- round(t_test_fixation$p.value, 3)
+
+# 5. Calculate Cohen's d for effect size using formula syntax
+library(effsize)
+cohen_d_fixation <- round(cohen.d(Average_duration_fixation ~ Group, data = df_aoi_sum)$estimate, 2)
+
+# 6. Plotting the Average Fixation Duration
+y_max_fixation <- max(df_aoi_sum$Average_duration_fixation) * 1.5
+
+plot_avg_fixation_group <- df_aoi_sum %>%
+  ggplot(mapping = aes(x = Group, y = Average_duration_fixation)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
+  geom_jitter(
+    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
+  ) +
+  ylim(0, y_max_fixation) +
+  labs(x = "", y = "Average Fixation Duration (ms)") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Average duration of fixations\n(micro-teaching unit)") +
+  ggtitle("Average Fixation Duration\n(micro-teaching unit)") +
   theme_cowplot() +
-  theme(legend.position="none") -> plot_average_duration_group
-
-plot_average_duration_group
-
-```
-
-#### t-test & effect size "Average duration of fixations" (micro-teaching unit)
-```{r dur_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# AVERAGE DURATION OF FIXATIONS on all AOIs 
-# t-test for expertise differences
-t.test(x = df_aoi_sum$Average_duration_mtu[df_aoi_sum$Group == "Expert"],
-       y = df_aoi_sum$Average_duration_mtu[df_aoi_sum$Group == "Novice"],
-       var.equal = TRUE)
-
-# AVERAGE DURATION OF FIXATIONS on all AOIs
-# effect size for expertise differences
-d_aver_all <- CohenD(x = df_aoi_sum$Average_duration_mtu[df_aoi_sum$Group == "Expert"],
-                     y = df_aoi_sum$Average_duration_mtu[df_aoi_sum$Group == "Novice"],
-                    na.rm = TRUE)
-round(d_aver_all, 2)
+  theme(legend.position = "none") +
+  # Add annotations for mean (M) and SD
+  annotate("text", x = 1, y = y_max_fixation * 0.85,
+           label = paste0("atop(italic(M) == ", mean_novice_fixation, ", italic(SD) == ", sd_novice_fixation, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  annotate("text", x = 2, y = y_max_fixation * 0.85,
+           label = paste0("atop(italic(M) == ", mean_expert_fixation, ", italic(SD) == ", sd_expert_fixation, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  # Add p-value and Cohen's d annotations
+  annotate("text", x = 1.5, y = y_max_fixation * 0.95,
+           label = paste0("p = ", p_value_fixation, "\nd = ", cohen_d_fixation),
+           hjust = 0.5, size = 4, fontface = "italic")
+
+plot_avg_fixation_group
+
+# 7. Format the t-Test and Cohen's d results for APA Table without the first column
+t_test_result <- data.frame(
+  "Group Comparison" = "Experts vs. Novices",
+  "t-value" = round(t_test_fixation$statistic, 2),
+  "df" = t_test_fixation$parameter,
+  "p-value" = round(t_test_fixation$p.value, 3),
+  "Mean Difference" = round(t_test_fixation$estimate[1] - t_test_fixation$estimate[2], 2),
+  "Cohen's d" = cohen_d_fixation,
+  "95% CI (d)" = paste0("[", round(t_test_fixation$conf.int[1], 2), ", ", round(t_test_fixation$conf.int[2], 2), "]")
+)
+
+# Display t-Test and Effect Size results in APA style without row names
+knitr::kable(t_test_result, caption = "t-Test and Effect Size for Average Fixation Duration (Micro-Teaching Unit)", row.names = FALSE) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 
-# filter group & total duration & number fixation on AOI Students
-df_aoi %>%
+# 1. Data Preparation: Filter and Calculate Average Duration of Fixations on AOI Students
+df_aoi_stud <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  dplyr::select (
+  dplyr::select(
     Group,
-    "Total_duration_of_fixations.Anna",
-    "Total_duration_of_fixations.Bianca",
-    "Total_duration_of_fixations.Carl(a)",
-    "Number_of_fixations.Anna",
-    "Number_of_fixations.Bianca",
-    "Number_of_fixations.Carl(a)"
+    starts_with("Total_duration_of_fixations"),
+    starts_with("Number_of_fixations")
   ) %>%
@@
   transmute(
-    Group = Group,
+    Group = as_factor(Group),
     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
-  ) %>%
-  mutate(
-    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
-    Group = as_factor(Group)
-  ) -> df_aoi_stud
-
-# N, M, SD, min & max average duration of fixations on AOI students
-dur.stud.table <-
-  df_aoi_stud %>%
+    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 2) # Retained in milliseconds
+  ) %>%
+  drop_na()
+
+# 2. Descriptive Statistics Table
+dur_stud_table <- df_aoi_stud %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M in ms" = round(mean(Average_duration_stud), digits = 2),
-    "SD in ms" = round(sd(Average_duration_stud), digits = 2),
-    "Min in ms" = round(min(Average_duration_stud), digits = 2),
-    "Max in ms" = round(max(Average_duration_stud), digits = 2)
-  )
-
-knitr::kable(dur.stud.table,
-             caption = "N, M, SD, min & max average duration of fixations in milliseconds (AOI students)")
-
-# plotting average duration on AOI Students
-df_aoi_stud %>%
+    "M in ms" = round(mean(Average_duration_stud, na.rm = TRUE), 2),
+    "SD in ms" = round(sd(Average_duration_stud, na.rm = TRUE), 2),
+    "Min in ms" = round(min(Average_duration_stud, na.rm = TRUE), 2),
+    "Max in ms" = round(max(Average_duration_stud, na.rm = TRUE), 2)
+  )
+
+# Display the descriptive table in APA style
+knitr::kable(dur_stud_table,
+             caption = "N, M, SD, min & max average duration of fixations in milliseconds (AOI students)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# 3. Plotting Average Duration on AOI Students
+y_max_stud <- max(df_aoi_stud$Average_duration_stud) * 1.2  # Adjust y-axis limit based on data
+
+plot_average_duration_stud <- df_aoi_stud %>%
   ggplot(mapping = aes(x = Group, y = Average_duration_stud)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
+  geom_jitter(
+    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
   ) +
-  ylim(0, 1200) + 
-  labs(x ="",
-       y = "Milliseconds") + 
+  ylim(0, y_max_stud) + 
+  labs(x = "", y = "Milliseconds") + 
   scale_fill_brewer(palette = "RdBu") + 
@@
   theme_cowplot() +
-  theme(legend.position="none") -> plot_average_duration_stud
+  theme(legend.position = "none")
 
@@
 
-```
-
-#### t-test & effect size "Average duration of fixations" (AOI students)
-```{r dur_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# AVERAGE DURATION OF FIXATIONS on AOI Students 
-# t-test for expertise differences
-t.test(
-  x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
-  y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
+# 4. t-Test and Effect Size Calculation for Average Duration of Fixations on AOI Students
+# Conduct t-test
+t_test_stud <- t.test(
+  Average_duration_stud ~ Group,
+  data = df_aoi_stud,
   var.equal = TRUE
 )
-
-# AVERAGE DURATION OF FIXATIONS on AOI Students
-# effect size for expertise differences
-d_aver_stud <- CohenD(
-  x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
-  y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
-  na.rm = TRUE
-)
-
-round(d_aver_stud, 2)
+t_test_stud_result <- data.frame(
+  "Group Comparison" = "Experts vs. Novices",
+  "t-value" = round(t_test_stud$statistic, 2),
+  "df" = t_test_stud$parameter,
+  "p-value" = round(t_test_stud$p.value, 3),
+  "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2)
+)
+
+# Calculate Cohen's d effect size
+library(effsize)
+d_aver_stud <- cohen.d(Average_duration_stud ~ Group, data = df_aoi_stud)
+t_test_stud_result$`Cohen's d` <- round(d_aver_stud$estimate, 2)
+t_test_stud_result$`95% CI (d)` <- paste0("[", round(d_aver_stud$conf.int[1], 2), ", ", round(d_aver_stud$conf.int[2], 2), "]")
+
+# Display t-Test and Effect Size results in APA style
+knitr::kable(t_test_stud_result,
+             caption = "t-Test and Effect Size for Average Fixation Duration on AOI Students (milliseconds)",
+             row.names = FALSE) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 
-##################### AVERAGE DURATIONS ON AOI DISRUPTIVE PERSON ########################
-
-# filter group & total duration & number fixation on AOI Disruptive person
-df_aoi %>%
+##################### AVERAGE DURATION ON AOI DISRUPTIVE PERSON ########################
+
+# 1. Data Preparation: Filter and Calculate Average Duration of Fixations on AOI Disruptive Person
+df_aoi_disrup <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  dplyr::select (
+  dplyr::select(
     Group,
@@
   mutate(
-    Average_duration_disrup = round(
-      Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person,
-      digits = 0
-    ),
-    Group = as_factor(Group)
-  ) -> df_aoi_disrup
-
-# N, M, SD, min & max average duration of fixations in milliseconds (AOI disruptive person)"
-dur.disrup.table <-
-  df_aoi_disrup %>%
+    Group = as_factor(Group),
+    Average_duration_disrup = round(Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person, 2) # In milliseconds
+  ) %>%
+  drop_na()
+
+# 2. Descriptive Statistics Table
+dur_disrup_table <- df_aoi_disrup %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M in ms" = round(mean(Average_duration_disrup), digits = 2),
-    "SD in ms" = round(sd(Average_duration_disrup), digits = 2),
-    "Min in ms" = round(min(Average_duration_disrup), digits = 2),
-    "Max in ms" = round(max(Average_duration_disrup), digits = 2)
-  )
-
-knitr::kable(dur.disrup.table,
-             caption = "N, M, SD, min & max average duration of fixations in milliseconds (AOI disruptive person)")
-
-# plotting average duration on AOI Disruptive person
-df_aoi_disrup %>% 
-  ggplot(mapping = aes(x = Group,
-                       y = Average_duration_disrup)) +
-  geom_boxplot(mapping = aes(fill = Group),
-               outlier.shape = NA) +
-  geom_point(size = 2,
-             alpha = 0.7,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  ylim(0, 1500) +
-  labs(x ="",
-       y = "Milliseconds") + 
+    "M in ms" = round(mean(Average_duration_disrup, na.rm = TRUE), 2),
+    "SD in ms" = round(sd(Average_duration_disrup, na.rm = TRUE), 2),
+    "Min in ms" = round(min(Average_duration_disrup, na.rm = TRUE), 2),
+    "Max in ms" = round(max(Average_duration_disrup, na.rm = TRUE), 2)
+  )
+
+# Display the descriptive table in APA style
+knitr::kable(dur_disrup_table,
+             caption = "N, M, SD, min & max average duration of fixations in milliseconds (AOI disruptive person)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# 3. Plotting Average Duration on AOI Disruptive Person
+y_max_disrup <- max(df_aoi_disrup$Average_duration_disrup, na.rm = TRUE) * 1.2  # Adjust y-axis limit based on data
+
+plot_average_duration_disrup <- df_aoi_disrup %>%
+  ggplot(mapping = aes(x = Group, y = Average_duration_disrup)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
+  geom_jitter(
+    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
+  ) +
+  ylim(0, y_max_disrup) + 
+  labs(x = "", y = "Milliseconds") + 
   scale_fill_brewer(palette = "RdBu") + 
@@
   theme_cowplot() +
-  theme(legend.position="none") -> plot_average_duration_disrup
+  theme(legend.position = "none")
 
 plot_average_duration_disrup
+
+# 4. t-Test and Effect Size Calculation for Average Duration of Fixations on AOI Disruptive Person
+# Conduct t-test
+t_test_disrup <- t.test(
+  Average_duration_disrup ~ Group,
+  data = df_aoi_disrup,
+  var.equal = TRUE
+)
+t_test_disrup_result <- data.frame(
+  "Group Comparison" = "Experts vs. Novices",
+  "t-value" = round(t_test_disrup$statistic, 2),
+  "df" = t_test_disrup$parameter,
+  "p-value" = round(t_test_disrup$p.value, 3),
+  "Mean Difference" = round(t_test_disrup$estimate[1] - t_test_disrup$estimate[2], 2)
+)
+
+# Calculate Cohen's d effect size
+library(effsize)
+d_dur_disrup <- cohen.d(Average_duration_disrup ~ Group, data = df_aoi_disrup)
+t_test_disrup_result$`Cohen's d` <- round(d_dur_disrup$estimate, 2)
+t_test_disrup_result$`95% CI (d)` <- paste0("[", round(d_dur_disrup$conf.int[1], 2), ", ", round(d_dur_disrup$conf.int[2], 2), "]")
+
+# Display t-Test and Effect Size results in APA style
+knitr::kable(t_test_disrup_result,
+             caption = "t-Test and Effect Size for Average Fixation Duration on AOI Disruptive Person (milliseconds)",
+             row.names = FALSE) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 

### 2024-11-18 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper

--- 2024-11-14 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
@@
       effsize,
-      knitr
+      knitr,
+      papaja
       )
@@
 
-# Step 6: Display the table with APA style
-kable(grouped_aoi_percentages, 
-      col.names = c("AOI", "Expert (%)", "Novice (%)"),
-      caption = "Average Fixation Percentage per AOI by Group (Novice vs. Expert) - Descending Order") %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
-  add_header_above(c(" " = 1, "Fixation Percentage" = 2)) %>%
-  row_spec(0, bold = TRUE) %>%
-  column_spec(2:3, width = "3em", border_left = TRUE)
+# # Step 6: Display the table with APA style
+# kable(grouped_aoi_percentages, 
+#       col.names = c("AOI", "Expert (%)", "Novice (%)"),
+#       caption = "Average Fixation Percentage per AOI by Group (Novice vs. Expert) - Descending Order") %>%
+#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
+#   add_header_above(c(" " = 1, "Fixation Percentage" = 2)) %>%
+#   row_spec(0, bold = TRUE) %>%
+#   column_spec(2:3, width = "3em", border_left = TRUE)
 
@@
 
-##################### NUMBER OF FIXATION IN MICRO-TEACHING UNIT ########################
+##################### NUMBER OF FIXATIONS PER MINUTE IN MICRO-TEACHING UNIT ########################
 
@@
     Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, 0),
+    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, 2),
     Group = as_factor(Group)
@@
 
-# 2. Descriptive Statistics Table
+# 2. Descriptive Statistics Table for Number of Fixations per Minute
 nof_table <- df_aoi_sum %>%
@@
 # Display the descriptive table in APA style
-knitr::kable(nof_table, caption = "N, M, SD, min & max number of fixation per minute (micro-teaching unit)") %>%
+knitr::kable(nof_table, caption = "N, M, SD, Min & Max Number of Fixations per Minute (Micro-Teaching Unit)") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
@@
 # 3. Calculate means and standard deviations for Novice and Expert
-mean_novice_mtu <- mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE)
-sd_novice_mtu <- sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE)
-mean_expert_mtu <- mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE)
-sd_expert_mtu <- sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE)
+mean_novice_mtu <- round(mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
+sd_novice_mtu <- round(sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
+mean_expert_mtu <- round(mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)
+sd_expert_mtu <- round(sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)
 
@@
 # 6. Plotting the Number of Fixations per Minute (Micro-Teaching Unit)
-# Set y-limit based on data to provide space for annotations
 y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5
@@
   ylim(0, y_max_mtu) +
-  labs(x = "", y = "Number of fixations per minute") +
+  labs(x = "", y = "Number of Fixations per Minute") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Number of fixations per minute\n(micro-teaching unit)") +
+  ggtitle("Number of Fixations per Minute\n(Micro-Teaching Unit)") +
   theme_cowplot() +
   theme(legend.position = "none") +
-  # Add annotations for mean (M) and SD using atop() to place SD below M
+  # Annotations for mean (M) and SD using atop() to place SD below M
   annotate("text", x = 1, y = y_max_mtu * 0.85,
@@
 
-##################### NUMBER OF FIXATION ON AOI DISRUPTIVE PERSON ########################
-
-# Define the list of disruptions and categories
+##################### NUMBER OF FIXATIONS ON AOI DISRUPTIVE PERSON ########################
+
+# Define the different types of disruptions and categories
 disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
@@
                  "Looking_at_phone", "Snipping_with_fingers", "Whispering")
-
-# Define categories for each type of disruption
 verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
@@
 
-# Filter data to include only the specified disruptions
+# Step 1: Filter and prepare the data
 df_aoi_disrup <- df_aoi %>%
-  filter(TOI %in% disruptions) %>%
-  dplyr::select(Group, Participant, TOI, Duration_of_interval, 
-                "Number_of_fixations.Disruptive_Person") %>%
-  mutate(Group = as_factor(Group))
-
-# Add a column for Disruption_Category based on TOI values
-df_aoi_disrup <- df_aoi_disrup %>%
+  filter(TOI %in% disruptions) %>% # Filter rows based on the disruption list
+  select(Group, Participant, TOI, Duration_of_interval, "Number_of_fixations.Disruptive_Person") %>%
   mutate(
-    Disruption_Category = case_when(
+    Group = as_factor(Group), # Convert Group column to a factor
+    Disruption_Category = case_when( # Assign categories based on disruption type
       TOI %in% verbal_disruptions ~ "Verbal disruptions",
@@
       TRUE ~ NA_character_
-    )
-  ) %>%
-  filter(!is.na(Disruption_Category)) # Keep only rows with valid category
-
-# Convert duration from milliseconds to seconds
-df_aoi_disrup <- df_aoi_disrup %>%
-  mutate(Duration_of_interval_sec = Duration_of_interval / 1000)
-
-# Summarize total duration in seconds and fixation counts for "Disruptive_Person" by group, participant, and category
+    ),
+    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2) # Convert duration to seconds
+  ) %>%
+  filter(!is.na(Disruption_Category)) # Keep only rows with valid categories
+
+# Step 2: Summarize data by disruption category
 disruption_summary <- df_aoi_disrup %>%
   group_by(Group, Participant, Disruption_Category) %>%
-  summarize(
-    total_duration_sec = sum(Duration_of_interval_sec, na.rm = TRUE),
-    fixation_count = sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE),
+  summarise(
+    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2), # Total time in seconds
+    fixation_count = round(sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE), 2), # Total fixations
+    fixations_per_second = round(fixation_count / total_duration_sec, 2), # Fixation rate per second
     .groups = "drop"
-  ) %>%
-  mutate(fixations_per_second = fixation_count / total_duration_sec)
-
-# Step 1: Aggregate disruptions on an individual level (one value per participant)
-# Calculate the mean fixation rate per participant
+  )
+
+# Step 3: Summarize by participant
 individual_summary <- disruption_summary %>%
   group_by(Group, Participant) %>%
-  summarize(
-    mean_fixations_per_second = mean(fixations_per_second, na.rm = TRUE),
+  summarise(
+    mean_fixations_per_second = round(mean(fixations_per_second, na.rm = TRUE), 2), # Mean fixation rate
     .groups = "drop"
@@
 
-# First Plot: Overall fixation rate by Group (using aggregated individual data)
-plot_overall <- individual_summary %>%
-  ggplot(mapping = aes(x = Group, y = mean_fixations_per_second)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
-  ) +
-  ylim (0, 1) + 
+##################### DESCRIPTIVE STATISTICS ########################
+
+# Descriptive statistics for overall fixation rate
+overall_stats <- individual_summary %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(), # Number of participants
+    Mean = round(mean(mean_fixations_per_second, na.rm = TRUE), 2), # Mean fixation rate
+    SD = round(sd(mean_fixations_per_second, na.rm = TRUE), 2), # Standard deviation
+    Min = round(min(mean_fixations_per_second, na.rm = TRUE), 2), # Minimum value
+    Max = round(max(mean_fixations_per_second, na.rm = TRUE), 2), # Maximum value
+    .groups = "drop"
+  )
+
+# Display the overall descriptive statistics table
+kable(
+  overall_stats,
+  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Overall Fixation Rate by Group",
+  col.names = c("Group", "N", "M", "SD", "Min", "Max"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Descriptive statistics by disruption category
+category_stats <- disruption_summary %>%
+  group_by(Group, Disruption_Category) %>%
+  summarise(
+    N = n(), # Number of data points
+    Mean = round(mean(fixations_per_second, na.rm = TRUE), 2), # Mean fixation rate
+    SD = round(sd(fixations_per_second, na.rm = TRUE), 2), # Standard deviation
+    Min = round(min(fixations_per_second, na.rm = TRUE), 2), # Minimum value
+    Max = round(max(fixations_per_second, na.rm = TRUE), 2), # Maximum value
+    .groups = "drop"
+  )
+
+# Display the descriptive statistics table by category
+kable(
+  category_stats,
+  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Fixation Rate by Group and Category",
+  col.names = c("Group", "Category", "N", "M", "SD", "Min", "Max"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### PLOTS ########################
+##################### FIRST PLOT: FIXATION RATE OVERALL ########################
+
+# Calculate values for annotations
+mean_novice <- round(mean(individual_summary$mean_fixations_per_second[individual_summary$Group == "Novice"], na.rm = TRUE), 2)
+sd_novice <- round(sd(individual_summary$mean_fixations_per_second[individual_summary$Group == "Novice"], na.rm = TRUE), 2)
+mean_expert <- round(mean(individual_summary$mean_fixations_per_second[individual_summary$Group == "Expert"], na.rm = TRUE), 2)
+sd_expert <- round(sd(individual_summary$mean_fixations_per_second[individual_summary$Group == "Expert"], na.rm = TRUE), 2)
+
+# t-Test and effect size
+t_test <- t.test(mean_fixations_per_second ~ Group, data = individual_summary, var.equal = TRUE)
+p_value <- round(t_test$p.value, 3)
+cohen_d <- round(cohen.d(mean_fixations_per_second ~ Group, data = individual_summary)$estimate, 2)
+
+# Overall fixation rate plot with annotations
+y_max_overall <- max(individual_summary$mean_fixations_per_second, na.rm = TRUE) * 1.5
+plot_overall <- ggplot(individual_summary, aes(x = Group, y = mean_fixations_per_second, fill = Group)) +
+  geom_boxplot(outlier.shape = NA, width = 0.5) +
+  geom_jitter(width = 0.1, alpha = 0.7, color = "black", size = 1.5) +
   labs(x = "", y = "Mean Fixations per Second per Participant") +
-  ggtitle("Overall Fixation Rate per Participant\n(AOI disruptive person)") +
+  ggtitle("Overall Fixation Rate per Participant\n(AOI Disruptive Person)") +
   scale_fill_brewer(palette = "RdBu") +
   theme_cowplot() +
-  theme(legend.position = "none")
-
-# Second Plot: Fixation rate by Group and Disruption_Category (no aggregation, shows all data points)
-plot_category <- disruption_summary %>%
+  ylim(0, y_max_overall) +
+  theme(legend.position = "none") +
+  annotate("text", x = 1, y = y_max_overall * 0.85,
+           label = paste0("M = ", mean_novice, "\nSD = ", sd_novice),
+           hjust = 0.5, size = 4, fontface = "italic") +
+  annotate("text", x = 2, y = y_max_overall * 0.85,
+           label = paste0("M = ", mean_expert, "\nSD = ", sd_expert),
+           hjust = 0.5, size = 4, fontface = "italic") +
+  annotate("text", x = 1.5, y = y_max_overall * 0.95,
+           label = paste0("p = ", p_value, "\nd = ", cohen_d),
+           hjust = 0.5, size = 4, fontface = "italic")
+
+##################### SECOND PLOT: FIXATION RATE BY CATEGORY ########################
+
+# Calculate metrics (mean, SD, p, d) by Disruption_Category and Group
+category_stats_with_tests <- disruption_summary %>%
+  group_by(Disruption_Category) %>%
+  summarise(
+    M_Novice = round(mean(fixations_per_second[Group == "Novice"], na.rm = TRUE), 2),
+    SD_Novice = round(sd(fixations_per_second[Group == "Novice"], na.rm = TRUE), 2),
+    M_Expert = round(mean(fixations_per_second[Group == "Expert"], na.rm = TRUE), 2),
+    SD_Expert = round(sd(fixations_per_second[Group == "Expert"], na.rm = TRUE), 2),
+    t_test = list(t.test(fixations_per_second ~ Group, var.equal = TRUE)), # Perform t-test
+    p_value = round(t.test(fixations_per_second ~ Group, var.equal = TRUE)$p.value, 3),
+    cohen_d = round(cohen.d(fixations_per_second ~ Group)$estimate, 2),
+    .groups = "drop"
+  ) %>%
+  mutate(
+    label = paste0(
+      "M (N) = ", M_Novice, ", SD (N) = ", SD_Novice, "\n",
+      "M (E) = ", M_Expert, ", SD (E) = ", SD_Expert, "\n",
+      "p = ", p_value, ", d = ", cohen_d
+    )
+  )
+
+# Join annotation labels with the main dataset
+disruption_summary_annotated <- disruption_summary %>%
+  left_join(category_stats_with_tests %>% select(Disruption_Category, label), by = "Disruption_Category")
+
+# Determine y-axis max value for each category for better placement of annotations
+y_max_by_category <- disruption_summary %>%
+  group_by(Disruption_Category) %>%
+  summarise(y_max = max(fixations_per_second, na.rm = TRUE) * 1.1, .groups = "drop")
+
+# Merge y_max values into the dataset for consistent annotation placement
+disruption_summary_annotated <- disruption_summary_annotated %>%
+  left_join(y_max_by_category, by = "Disruption_Category")
+
+# Plot with facets and annotations
+plot_category <- disruption_summary_annotated %>%
   ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
@@
     strip.text = element_text(size = 10) # Adjust facet text size if necessary
-  )
-
-# Display both plots
+  ) +
+  geom_text(
+    data = disruption_summary_annotated %>%
+      distinct(Disruption_Category, label, y_max), # Ensure unique labels per facet
+    aes(x = 1.5, y = y_max, label = label),
+    inherit.aes = FALSE,
+    size = 3.5, hjust = 0.5, vjust = 0
+  )
+
+# Display the both plots
 plot_overall
@@
 
-# Function to format t-test and Cohen's d results into a tidy data frame, with checks for non-numeric values
-format_results <- function(t_test, cohen_d) {
-  data.frame(
-    "t-value" = if (is.numeric(t_test$statistic)) round(t_test$statistic, 2) else NA,
-    "df" = if (is.numeric(t_test$parameter)) round(t_test$parameter, 2) else NA,
-    "p-value" = if (!is.null(t_test$p.value)) format.pval(t_test$p.value, digits = 3, eps = .001) else "NA",
-    "Mean Difference" = if (is.numeric(t_test$estimate[1] - t_test$estimate[2])) round(t_test$estimate[1] - t_test$estimate[2], 2) else NA,
-    "Cohen's d" = if (is.numeric(cohen_d$estimate)) round(cohen_d$estimate, 2) else NA,
-    "95% CI (d)" = if (!is.null(cohen_d$conf.int)) 
-                    paste0("[", round(cohen_d$conf.int[1], 2), ", ", round(cohen_d$conf.int[2], 2), "]") 
-                   else "NA"
-  )
-}
-
-# 1. t-Test and Cohen's d for fixations per second between Experts and Novices
-t_fixations_group <- t.test(fixations_per_second ~ Group, data = disruption_summary)
-d_fixations_group <- cohen.d(fixations_per_second ~ Group, data = disruption_summary)
-fixations_group_result <- format_results(t_fixations_group, d_fixations_group)  # Formatting results
-
-# 2. t-Test and Cohen's d for fixations per second by category
-# Iterate over each category and calculate t-test and Cohen's d
-categories <- unique(disruption_summary$Disruption_Category)
-fixations_category_results <- list()
-
-for (cat in categories) {
-  cat_data <- disruption_summary %>% filter(Disruption_Category == cat)
-  t_test_cat <- t.test(fixations_per_second ~ Group, data = cat_data)
-  d_cat <- cohen.d(fixations_per_second ~ Group, data = cat_data)
-  fixations_category_results[[cat]] <- format_results(t_test_cat, d_cat)  # Format results for each category
-}
-
-# Convert the list of results into a single data frame
-fixations_category_df <- do.call(rbind, fixations_category_results)
-fixations_category_df <- data.frame(Category = categories, fixations_category_df, row.names = NULL)  # Ensure Category column aligns
-
-# Render tables in HTML format with kableExtra for APA style
-knitr::kable(fixations_group_result, caption = "T-test and Effect Size for Fixations per Second (Experts vs. Novices)") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-knitr::kable(fixations_category_df, caption = "T-test and Effect Size for Fixations per Second by Category") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+##################### STATISTICAL TESTS ########################
+
+# Table summarizing overall t-test and Cohen's d
+overall_effect <- data.frame(
+  Group = c("Overall"),
+  `t-value` = round(t_test$statistic, 2),
+  `p-value` = p_value,
+  `Cohen's d` = cohen_d
+)
+
+# Display t-test and effect size table
+kable(
+  overall_effect,
+  caption = "Overall t-Test and Effect Size for Fixation Rate",
+  col.names = c("Group", "t-value", "p-value", "Cohen's d"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 ### Duration of disruption
-```{r disrup_dur, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# Define the list of disruptions and categories
-disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
-                 "Drumming_with_hands", "Head_on_table", "Heckling", 
-                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
-
-# Define categories for each type of disruption
-verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
-physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
-lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")
-
-# Filter data to include only the specified disruptions
+```{r dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### DURATION OF DISRUPTIONS ########################
+
+# 1. Data Preparation: Filter and Calculate Disruption Duration
 df_aoi_disrup <- df_aoi %>%
-  filter(TOI %in% disruptions) %>%
-  dplyr::select(Group, Participant, TOI, Duration_of_interval) %>%
-  mutate(Group = as_factor(Group))
-
-# Add a column for Disruption_Category based on TOI values
-df_aoi_disrup <- df_aoi_disrup %>%
+  filter(TOI %in% disruptions, Duration_of_interval <= 30000) %>%
+  select(Group, Participant, TOI, Duration_of_interval) %>%
   mutate(
+    Group = as_factor(Group),
     Disruption_Category = case_when(
@@
       TRUE ~ NA_character_
-    )
-  ) %>%
-  filter(!is.na(Disruption_Category)) # Keep only rows with valid category
-
-# Convert duration from milliseconds to seconds and round to 2 decimal places
-df_aoi_disrup <- df_aoi_disrup %>%
-  mutate(Duration_of_interval_sec = round(Duration_of_interval / 1000, 2))
-
-# First Table: Total duration of disruptions by group (Novice and Expert)
-duration_summary_group <- df_aoi_disrup %>%
+    ),
+    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2)
+  ) %>%
+  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
+  drop_na()
+
+##################### DESCRIPTIVE STATISTICS ########################
+
+# 2. Descriptive Statistics by Group (Overall)
+summary_stats <- df_aoi_disrup %>%
   group_by(Group) %>%
-  summarize(
-    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2),
-    mean_duration_sec = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
-    sd_duration_sec = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
-    min_duration_sec = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
-    max_duration_sec = round(max(Duration_of_interval_sec, na.rm = TRUE), 2)
-  )
-
-# Second Table: Total duration of disruptions by group and category
-duration_summary_category <- df_aoi_disrup %>%
+  summarise(
+    Mean = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
+    SD = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
+    .groups = "drop"
+  )
+
+# 3. Descriptive Statistics by Group and Category
+disruption_stats_table <- df_aoi_disrup %>%
   group_by(Group, Disruption_Category) %>%
-  summarize(
-    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2),
-    mean_duration_sec = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
-    sd_duration_sec = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
-    min_duration_sec = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
-    max_duration_sec = round(max(Duration_of_interval_sec, na.rm = TRUE), 2)
-  )
-
-# Display tables
-print("Duration Summary by Group:")
-print(duration_summary_group)
-
-print("Duration Summary by Group and Category:")
-print(duration_summary_category)
-
-# First Plot: Boxplot of disruption duration by group
-plot_duration_group <- df_aoi_disrup %>%
-  ggplot(mapping = aes(x = Group, y = Duration_of_interval_sec)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
-  ) +
-  labs(x = "", y = "Disruption Duration (seconds)") +
+  summarise(
+    N = n(),
+    Mean = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
+    SD = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
+    Min = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
+    Max = round(max(Duration_of_interval_sec, na.rm = TRUE), 2),
+    .groups = "drop"
+  )
+
+# Overall t-Test and Cohen's d for Plot Annotations
+t_test_overall <- t.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, var.equal = TRUE)
+d_overall <- cohen.d(Duration_of_interval_sec ~ Group, data = df_aoi_disrup)
+
+# By Category t-Test and Cohen's d for Plot Annotations
+category_stats <- df_aoi_disrup %>%
+  group_by(Disruption_Category) %>%
+  summarise(
+    t_value = t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$statistic,
+    df = t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$parameter,
+    p_value = round(t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$p.value, 3),
+    cohen_d = round(cohen.d(Duration_of_interval_sec ~ Group)$estimate, 2),
+    .groups = "drop"
+  )
+
+##################### PLOTS ########################
+
+# Plot 1: Disruption Duration by Group (Overall)
+y_max <- max(df_aoi_disrup$Duration_of_interval_sec) * 1.5
+
+plot_duration_group <- ggplot(df_aoi_disrup, aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
+  geom_boxplot(outlier.shape = NA, width = 0.5) +
+  geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
+  labs(x = "Group", y = "Disruption Duration (seconds)") +
+  theme_cowplot() +
+  scale_fill_brewer(palette = "RdBu") +
   ggtitle("Disruption Duration by Group") +
+  theme(legend.position = "none") +
+  ylim(0, y_max) +
+  annotate("text", x = 1, y = y_max * 0.85,
+           label = paste0("M = ", summary_stats$Mean[summary_stats$Group == "Novice"],
+                          "\nSD = ", summary_stats$SD[summary_stats$Group == "Novice"]),
+           hjust = 0.5, size = 4, fontface = "italic") +
+  annotate("text", x = 2, y = y_max * 0.85,
+           label = paste0("M = ", summary_stats$Mean[summary_stats$Group == "Expert"],
+                          "\nSD = ", summary_stats$SD[summary_stats$Group == "Expert"]),
+           hjust = 0.5, size = 4, fontface = "italic") +
+  annotate("text", x = 1.5, y = y_max * 0.95,
+           label = paste0("p = ", format.pval(t_test_overall$p.value, digits = 3, eps = .001),
+                          "\nd = ", round(d_overall$estimate, 2)),
+           hjust = 0.5, size = 4, fontface = "italic")
+
+plot_duration_group
+
+# Plot 2: Disruption Duration by Group and Category
+plot_duration_category <- ggplot(df_aoi_disrup, aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
+  geom_boxplot(outlier.shape = NA, width = 0.5) +
+  geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
+  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) +
+  labs(x = "Group", y = "Disruption Duration (seconds)") +
+  theme_cowplot() +
   scale_fill_brewer(palette = "RdBu") +
-  theme_cowplot() +
-  theme(legend.position = "none")
-
-# Second Plot: Boxplot of disruption duration by group and category
-plot_duration_category <- df_aoi_disrup %>%
-  ggplot(mapping = aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
-  ) +
-  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) +
-  labs(x = "", y = "Disruption Duration (seconds)") +
   ggtitle("Disruption Duration by Group and Category") +
-  scale_fill_brewer(palette = "RdBu") +
-  theme_cowplot() +
-  theme(legend.position = "none")
-
-# Display the plots
-plot_duration_group
+  theme(legend.position = "none") +
+  ylim(0, y_max) +
+  geom_text(data = category_stats, aes(
+    x = 1.5, y = y_max * 0.85,
+    label = paste0("p = ", p_value, "\nd = ", cohen_d)
+  ), inherit.aes = FALSE, size = 4, fontface = "italic")
+
 plot_duration_category
 
-# Define categories if not already defined
-categories <- unique(df_aoi_disrup$Disruption_Category)
-
-# Function to format t-test and Cohen's d results into a tidy data frame with additional debugging
-format_results <- function(t_test, cohen_d) {
-  if (is.list(cohen_d) && !is.null(cohen_d$estimate) && !is.null(cohen_d$conf.int)) {
-    data.frame(
-      "t-value" = round(t_test$statistic, 2),
-      "df" = round(t_test$parameter, 2),
-      "p-value" = format.pval(t_test$p.value, digits = 3, eps = .001),
-      "Mean Difference" = round(t_test$estimate[1] - t_test$estimate[2], 2),
-      "Cohen's d" = round(cohen_d$estimate, 2),
-      "95% CI (d)" = paste0("[", round(cohen_d$conf.int[1], 2), ", ", round(cohen_d$conf.int[2], 2), "]")
-    )
-  } else {
-    print("Cohen's d returned an unexpected structure or NA values. Setting values to NA.")
-    print(cohen_d)  # Print the structure of cohen_d for debugging
-    data.frame(
-      "t-value" = round(t_test$statistic, 2),
-      "df" = round(t_test$parameter, 2),
-      "p-value" = format.pval(t_test$p.value, digits = 3, eps = .001),
-      "Mean Difference" = round(t_test$estimate[1] - t_test$estimate[2], 2),
-      "Cohen's d" = NA,
-      "95% CI (d)" = NA
-    )
-  }
-}
-
-# 1. Overall t-test and Cohen's d for Duration by Group
-t_duration_group <- t.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup)
-d_duration_group <- tryCatch(cohen.d(Duration_of_interval_sec ~ Group, data = df_aoi_disrup), 
-                             error = function(e) NA)
-duration_group_result <- format_results(t_duration_group, d_duration_group)
-
-# 2. t-test and Cohen's d for Duration by Category with debugging output
-duration_category_results <- lapply(categories, function(cat) {
-  cat_data <- df_aoi_disrup %>% filter(Disruption_Category == cat)
-
-  # Perform t-test
-  t_test_cat <- t.test(Duration_of_interval_sec ~ Group, data = cat_data)
-
-  # Calculate Cohen's d with error handling
-  d_cat <- tryCatch(cohen.d(Duration_of_interval_sec ~ Group, data = cat_data), 
-                    error = function(e) NA)
-
-  # Debugging: Check structure of d_cat for each category
-  print(paste("Category:", cat))
-  print("Structure of Cohen's d result:")
-  str(d_cat)  # Display the structure of d_cat to debug
-
-  # Format results with error handling
-  format_results(t_test_cat, d_cat)
-})
-
-# Convert the list of results into a single data frame
-duration_category_df <- do.call(rbind, duration_category_results)
-duration_category_df <- data.frame(Category = categories, duration_category_df, row.names = NULL)
-
-# Render tables in HTML format with kableExtra for APA style
-knitr::kable(duration_group_result, caption = "T-test and Effect Size for Duration (Experts vs. Novices)") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-knitr::kable(duration_category_df, caption = "T-test and Effect Size for Duration by Category") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+##################### t-TEST AND EFFECT SIZE RESULTS ########################
+
+# 1. Overall t-Test and Cohen's d
+t_test_overall <- t.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, var.equal = TRUE)
+d_overall <- cohen.d(Duration_of_interval_sec ~ Group, data = df_aoi_disrup)
+
+# 2. t-Test and Cohen's d Results by Category
+category_stats <- df_aoi_disrup %>%
+  group_by(Disruption_Category) %>%
+  summarise(
+    t_value = round(t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$statistic, 2),
+    df = round(t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$parameter, 0),
+    p_value = round(t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$p.value, 3),
+    cohen_d = round(cohen.d(Duration_of_interval_sec ~ Group)$estimate, 2),
+    "95% CI (d)" = paste0(
+      "[", round(cohen.d(Duration_of_interval_sec ~ Group)$conf.int[1], 2),
+      ", ", round(cohen.d(Duration_of_interval_sec ~ Group)$conf.int[2], 2), "]"
+    ),
+    .groups = "drop"
+  )
+
+# 3. Format Overall t-Test Results for APA Table
+t_test_result_overall <- data.frame(
+  "t-value" = round(t_test_overall$statistic, 2),
+  "df" = round(t_test_overall$parameter, 0),
+  "p-value" = round(t_test_overall$p.value, 3),
+  "Mean Difference" = round(diff(t_test_overall$estimate), 2),
+  "Cohen's d" = round(d_overall$estimate, 2),
+  "95% CI (d)" = paste0("[", round(d_overall$conf.int[1], 2), ", ", round(d_overall$conf.int[2], 2), "]")
+)
+
+# Display Overall t-Test Results in APA Style
+kable(
+  t_test_result_overall,
+  caption = "t-Test and Effect Size for Disruption Duration (Overall)",
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# 4. Display Category-Specific t-Test Results in APA Style
+kable(
+  category_stats,
+  caption = "t-Test and Effect Size for Disruption Duration by Category",
+  col.names = c("Category", "t-value", "df", "p-value", "Cohen's d", "95% CI (d)"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
     Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, 2),
     Average_duration_fixation = round(Sum_duration_fixation / Sum_number_fixation, 2)
@@
 knitr::kable(dur_stud_table,
-             caption = "N, M, SD, min & max average duration of fixations in milliseconds (AOI students)") %>%
+             caption = "N, M, SD, Min & Max Average Duration of Fixations in Milliseconds (AOI Students)") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
@@
 # 3. Plotting Average Duration on AOI Students
-y_max_stud <- max(df_aoi_stud$Average_duration_stud) * 1.2  # Adjust y-axis limit based on data
-
+# Calculate values for annotation
+mean_novice_stud <- round(mean(df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"], na.rm = TRUE), 2)
+sd_novice_stud <- round(sd(df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"], na.rm = TRUE), 2)
+mean_expert_stud <- round(mean(df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"], na.rm = TRUE), 2)
+sd_expert_stud <- round(sd(df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"], na.rm = TRUE), 2)
+
+# Maximum y-axis value for plot
+y_max_stud <- max(df_aoi_stud$Average_duration_stud) * 1.2
+
+# Conduct t-test
+t_test_stud <- t.test(
+  Average_duration_stud ~ Group,
+  data = df_aoi_stud,
+  var.equal = TRUE
+)
+
+# Extract p-value
+p_value_stud <- round(t_test_stud$p.value, 3)
+
+# Calculate Cohen's d (full result object)
+d_aver_stud_full <- cohen.d(Average_duration_stud ~ Group, data = df_aoi_stud, pooled = TRUE)
+
+# Extract Cohen's d and confidence interval
+d_aver_stud <- round(d_aver_stud_full$estimate, 2)
+d_conf_int <- paste0("[", round(d_aver_stud_full$conf.int[1], 2), ", ", round(d_aver_stud_full$conf.int[2], 2), "]")
+
+# Annotated Plot
 plot_average_duration_stud <- df_aoi_stud %>%
@@
   ylim(0, y_max_stud) + 
-  labs(x = "", y = "Milliseconds") + 
+  labs(x = "", y = "Average Fixation Duration (ms)") + 
   scale_fill_brewer(palette = "RdBu") + 
-  ggtitle("Average duration of fixations\n(AOI students)") +
+  ggtitle("Average Duration of Fixations\n(AOI Students)") +
   theme_cowplot() +
-  theme(legend.position = "none")
+  theme(legend.position = "none") +
+  # Annotate mean (M) and SD
+  annotate("text", x = 1, y = y_max_stud * 0.85,
+           label = paste0("atop(italic(M) == ", mean_novice_stud, ", italic(SD) == ", sd_novice_stud, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  annotate("text", x = 2, y = y_max_stud * 0.85,
+           label = paste0("atop(italic(M) == ", mean_expert_stud, ", italic(SD) == ", sd_expert_stud, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  # Annotate p-value and Cohen's d
+  annotate("text", x = 1.5, y = y_max_stud * 0.95,
+           label = paste0("p = ", p_value_stud, "\nd = ", d_aver_stud),
+           hjust = 0.5, size = 4, fontface = "italic")
 
@@
 
-# 4. t-Test and Effect Size Calculation for Average Duration of Fixations on AOI Students
-# Conduct t-test
-t_test_stud <- t.test(
-  Average_duration_stud ~ Group,
-  data = df_aoi_stud,
-  var.equal = TRUE
-)
+# 4. t-Test and Effect Size Results Table
 t_test_stud_result <- data.frame(
@@
   "p-value" = round(t_test_stud$p.value, 3),
-  "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2)
-)
-
-# Calculate Cohen's d effect size
-library(effsize)
-d_aver_stud <- cohen.d(Average_duration_stud ~ Group, data = df_aoi_stud)
-t_test_stud_result$`Cohen's d` <- round(d_aver_stud$estimate, 2)
-t_test_stud_result$`95% CI (d)` <- paste0("[", round(d_aver_stud$conf.int[1], 2), ", ", round(d_aver_stud$conf.int[2], 2), "]")
-
-# Display t-Test and Effect Size results in APA style
+  "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2),
+  "Cohen's d" = d_aver_stud,
+  "95% CI (d)" = d_conf_int
+)
+
+# Display the t-Test and Effect Size results table in APA style
 knitr::kable(t_test_stud_result,
@@
 #### Average duration of fixations (AOI disruptive person)
-```{r dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r average_dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 knitr::kable(dur_disrup_table,
-             caption = "N, M, SD, min & max average duration of fixations in milliseconds (AOI disruptive person)") %>%
+             caption = "N, M, SD, Min & Max Average Duration of Fixations in Milliseconds (AOI Disruptive Person)") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
@@
 # 3. Plotting Average Duration on AOI Disruptive Person
-y_max_disrup <- max(df_aoi_disrup$Average_duration_disrup, na.rm = TRUE) * 1.2  # Adjust y-axis limit based on data
-
+# Calculate values for annotation
+mean_novice_disrup <- round(mean(df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"], na.rm = TRUE), 2)
+sd_novice_disrup <- round(sd(df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"], na.rm = TRUE), 2)
+mean_expert_disrup <- round(mean(df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"], na.rm = TRUE), 2)
+sd_expert_disrup <- round(sd(df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"], na.rm = TRUE), 2)
+
+# Maximum y-axis value for plot
+y_max_disrup <- max(df_aoi_disrup$Average_duration_disrup, na.rm = TRUE) * 1.2
+
+# Conduct t-test
+t_test_disrup <- t.test(
+  Average_duration_disrup ~ Group,
+  data = df_aoi_disrup,
+  var.equal = TRUE
+)
+
+# Extract p-value
+p_value_disrup <- round(t_test_disrup$p.value, 3)
+
+# Calculate Cohen's d (full result object)
+d_dur_disrup_full <- cohen.d(Average_duration_disrup ~ Group, data = df_aoi_disrup, pooled = TRUE)
+
+# Extract Cohen's d and confidence interval
+d_dur_disrup <- round(d_dur_disrup_full$estimate, 2)
+d_conf_int_disrup <- paste0("[", round(d_dur_disrup_full$conf.int[1], 2), ", ", round(d_dur_disrup_full$conf.int[2], 2), "]")
+
+# Annotated Plot
 plot_average_duration_disrup <- df_aoi_disrup %>%
@@
   scale_fill_brewer(palette = "RdBu") + 
-  ggtitle("Average duration of fixations\n(AOI disruptive person)") +
+  ggtitle("Average Duration of Fixations\n(AOI Disruptive Person)") +
   theme_cowplot() +
-  theme(legend.position = "none")
+  theme(legend.position = "none") +
+  # Annotate mean (M) and SD
+  annotate("text", x = 1, y = y_max_disrup * 0.85,
+           label = paste0("atop(italic(M) == ", mean_novice_disrup, ", italic(SD) == ", sd_novice_disrup, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  annotate("text", x = 2, y = y_max_disrup * 0.85,
+           label = paste0("atop(italic(M) == ", mean_expert_disrup, ", italic(SD) == ", sd_expert_disrup, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  # Annotate p-value and Cohen's d
+  annotate("text", x = 1.5, y = y_max_disrup * 0.95,
+           label = paste0("p = ", p_value_disrup, "\nd = ", d_dur_disrup),
+           hjust = 0.5, size = 4, fontface = "italic")
 
@@
 
-# 4. t-Test and Effect Size Calculation for Average Duration of Fixations on AOI Disruptive Person
-# Conduct t-test
-t_test_disrup <- t.test(
-  Average_duration_disrup ~ Group,
-  data = df_aoi_disrup,
-  var.equal = TRUE
-)
+# 4. t-Test and Effect Size Results Table
 t_test_disrup_result <- data.frame(
@@
   "p-value" = round(t_test_disrup$p.value, 3),
-  "Mean Difference" = round(t_test_disrup$estimate[1] - t_test_disrup$estimate[2], 2)
-)
-
-# Calculate Cohen's d effect size
-library(effsize)
-d_dur_disrup <- cohen.d(Average_duration_disrup ~ Group, data = df_aoi_disrup)
-t_test_disrup_result$`Cohen's d` <- round(d_dur_disrup$estimate, 2)
-t_test_disrup_result$`95% CI (d)` <- paste0("[", round(d_dur_disrup$conf.int[1], 2), ", ", round(d_dur_disrup$conf.int[2], 2), "]")
-
-# Display t-Test and Effect Size results in APA style
+  "Mean Difference" = round(t_test_disrup$estimate[1] - t_test_disrup$estimate[2], 2),
+  "Cohen's d" = d_dur_disrup,
+  "95% CI (d)" = d_conf_int_disrup
+)
+
+# Display the t-Test and Effect Size results table in APA style
 knitr::kable(t_test_disrup_result,
@@
 
-#### t-test & effect size "Average duration of fixations" (AOI disruptive person)
-```{r _disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# AVERAGDE DURATION OF FIXATIONS on AOI disruptive person 
-# t-test for expertise differences
-t.test(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
-       y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"],
-       var.equal = TRUE)
-
-# NUMBER OF FIXATIONS 
-# effect size for expertise differences
-d_dur_disrup <- CohenD(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
-                        y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"],
-                        na.rm = TRUE)
-
-round(d_dur_disrup, 2)
-
-```
-
 #### Gaze Relational Index (GRI; micro-teaching unit)
@@
 
-##################### GRI IN MICRO-TEACHING UNIT ########################
-
-# filter group, participants, total duration & number fixation in entire micro-teaching unit
-df_aoi_sum %>%
+##################### GRI in MICRO-TEACHING UNIT ########################
+
+# Step 1: Calculate GRI (Gaze Ratio Index) for each participant
+df_gri <- df_aoi_sum %>%
+  mutate(GRI = round(Average_duration_fixation / Number_fixation_min_mtu, 2))
+
+# Step 2: Summarize GRI statistics (N, Mean, SD, Min, Max) by Group
+gri_table <- df_gri %>%
   group_by(Group) %>%
-  mutate(
-    GRI = round(Average_duration_mtu / Number_fixation_min_mtu, digits = 2),
-    )-> df_gri
-
-# N, M, SD, min & max number of fixation (micro-teaching unit)
-gri.table <-
-  df_gri %>%
-  group_by(Group) %>%
   summarise(
     N = n(),
-    "M" = round(mean(GRI), digits = 2),
-    "SD" = round(sd(GRI), digits = 2),
-    "Min" = round(min(GRI), digits = 2),
-    "Max" = round(max(GRI), digits = 2)
-  )
-
-knitr::kable(gri.table,
-             caption = "N, M, SD, min & max GRI (micro-teaching unit)")
-
-# plotting number of fixations on ALL AOIS
-df_gri %>%
-  ggplot(mapping = aes(x = Group, y = GRI)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
+    "M" = round(mean(GRI, na.rm = TRUE), 2),
+    "SD" = round(sd(GRI, na.rm = TRUE), 2),
+    "Min" = round(min(GRI, na.rm = TRUE), 2),
+    "Max" = round(max(GRI, na.rm = TRUE), 2)
+  )
+
+# Display the GRI summary table in APA format
+knitr::kable(gri_table,
+             caption = "N, M, SD, Min, and Max GRI (Micro-Teaching Unit)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Step 3: Plot GRI by Group with boxplot and jittered points
+# Calculate annotation values
+mean_novice_gri <- round(mean(df_gri$GRI[df_gri$Group == "Novice"], na.rm = TRUE), 2)
+sd_novice_gri <- round(sd(df_gri$GRI[df_gri$Group == "Novice"], na.rm = TRUE), 2)
+mean_expert_gri <- round(mean(df_gri$GRI[df_gri$Group == "Expert"], na.rm = TRUE), 2)
+sd_expert_gri <- round(sd(df_gri$GRI[df_gri$Group == "Expert"], na.rm = TRUE), 2)
+
+# Maximum y-axis value for plot
+y_max_gri <- max(df_gri$GRI, na.rm = TRUE) * 1.2
+
+# Conduct t-test
+t_test_gri <- t.test(
+  GRI ~ Group,
+  data = df_gri,
+  var.equal = TRUE
+)
+
+# Extract p-value
+p_value_gri <- round(t_test_gri$p.value, 3)
+
+# Calculate Cohen's d (full result object)
+d_gri_full <- cohen.d(GRI ~ Group, data = df_gri, pooled = TRUE)
+
+# Extract Cohen's d and confidence interval
+d_gri <- round(d_gri_full$estimate, 2)
+d_conf_int_gri <- paste0("[", round(d_gri_full$conf.int[1], 2), ", ", round(d_gri_full$conf.int[2], 2), "]")
+
+# Annotated Plot
+plot_gri_group <- df_gri %>%
+  ggplot(aes(x = Group, y = GRI, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 2, alpha = 0.7, width = 0.1, height = 0.1, seed = 1) +
+  ylim(0, y_max_gri) +
+  labs(x = "", y = "Average Duration of Fixations /\nNumber of Fixations per Minute") +
+  scale_fill_brewer(palette = "RdBu") +
+  ggtitle("GRI\n(Micro-Teaching Unit)") +
+  theme_minimal() +
+  theme(
+    legend.position = "none",
+    plot.title = element_text(hjust = 0.5, face = "bold")
   ) +
-  ylim(0, 12) +
-  labs(x = "", y = "average duration of fixations/\nnumber of fixations per minute") +
-  scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("GRI\n(micro-teaching unit)") +
-  theme_cowplot() +
-  theme(legend.position = "none") -> plot_gri_group
+  # Annotate mean (M) and SD
+  annotate("text", x = 1, y = y_max_gri * 0.85,
+           label = paste0("atop(italic(M) == ", mean_novice_gri, ", italic(SD) == ", sd_novice_gri, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  annotate("text", x = 2, y = y_max_gri * 0.85,
+           label = paste0("atop(italic(M) == ", mean_expert_gri, ", italic(SD) == ", sd_expert_gri, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  # Annotate p-value and Cohen's d
+  annotate("text", x = 1.5, y = y_max_gri * 0.95,
+           label = paste0("p = ", p_value_gri, "\nd = ", d_gri),
+           hjust = 0.5, size = 4, fontface = "italic")
 
@@
 
-```
-
-#### t-test & effect size "GRI" (micro-teaching unit)
-```{r gri_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# GRI (mirco-teaching unit)
-# t-test for expertise differences
-t.test(x = df_gri$GRI[df_gri$Group == "Expert"],
-       y = df_gri$GRI[df_gri$Group == "Novice"],
-       var.equal = TRUE)
-
-# GRI (mirco-teaching unit) 
-# effect size for expertise differences
-d_gri_all <- CohenD(x = df_gri$GRI[df_gri$Group == "Expert"],
-                        y = df_gri$GRI[df_gri$Group == "Novice"],
-                        na.rm = TRUE)
-
-round(d_gri_all, 2)
-
-```
-
-```{r gri_stud, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# ##################### GRI on AOI students ########################
-# 
-# # filter group, participants, total duration & number fixation on AOI students
-# df_aoi_stud %>%
-#   group_by(Group) %>% 
-#   mutate(
-#     GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2),
-#     )-> df_gri_stud
-# 
-# 
-# # N, M, SD, min & max GRI (AOI students)
-# gri.stud.table <-
-#   df_gri_stud %>%
-#   group_by(Group) %>%
-#   summarise(
-#     N = n(),
-#     "M" = round(mean(GRI_stud), digits = 2),
-#     "SD" = round(sd(GRI_stud), digits = 2),
-#     "Min" = round(min(GRI_stud), digits = 2),
-#     "Max" = round(max(GRI_stud), digits = 2)
-#   )
-# 
-# knitr::kable(gri.stud.table,
-#              caption = "N, M, SD, min & max GRI (AOI students)")
-# 
-# 
-# # plotting GRI on AOI students
-# df_gri_stud %>%
-#   ggplot(mapping = aes(x = Group, y = GRI_stud)) +
-#   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-#   geom_point(
-#     size = 2,
-#     alpha = 0.7,
-#     position = position_jitter(
-#       seed = 1,
-#       width = 0.1,
-#       height = 0.1
-#     )
-#   ) +
-#   ylim(0, 2.5) +
-#   labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
-#   scale_fill_brewer(palette  = "RdBu") +
-#   ggtitle("GRI\n(AOI students)") +
-#   theme_cowplot() +
-#   theme(legend.position = "none") -> plot_gri_stud
-# 
-# plot_gri_stud
-
-```
-
-```{r gri_stud_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# # GRI (AOI students)
-# # t-test for expertise differences
-# t.test(x = df_gri_stud$GRI_stud[df_gri_stud$Group == "Expert"],
-#        y = df_gri_stud$GRI_stud[df_gri_stud$Group == "Novice"],
-#        var.equal = TRUE)
-# 
-# # GRI (AOI students) 
-# # effect size for expertise differences
-# d_gri_stud <- CohenD(x = df_gri_stud$GRI_stud[df_gri_stud$Group == "Expert"],
-#                      y = df_gri_stud$GRI_stud[df_gri_stud$Group == "Novice"],
-#                      na.rm = TRUE)
-# 
-# round(d_gri_stud, 2)
-
-```
-
-```{r gri_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# ##################### GRI on AOI students ########################
-# 
-# # filter
-# df_aoi_disrup %>%
-#   group_by(Group) %>% 
-#   mutate(
-#     GRI_disrup = round(Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2),
-#     )-> df_gri_disrup
-# 
-# 
-# # N, M, SD, min & max GRI (AOI disruptive person)
-# gri.disrup.table <-
-#   df_gri_disrup %>%
-#   group_by(Group) %>%
-#   summarise(
-#     N = n(),
-#     "M" = round(mean(GRI_disrup), digits = 2),
-#     "SD" = round(sd(GRI_disrup), digits = 2),
-#     "Min" = round(min(GRI_disrup), digits = 2),
-#     "Max" = round(max(GRI_disrup), digits = 2)
-#   )
-# 
-# knitr::kable(gri.disrup.table,
-#              caption = "N, M, SD, min & max GRI (AOI disruptive person)")
-# 
-# 
-# # plotting GRI on AOI disruptive person
-# df_gri_disrup %>%
-#   ggplot(mapping = aes(x = Group, y = GRI_disrup)) +
-#   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-#   geom_point(
-#     size = 2,
-#     alpha = 0.7,
-#     position = position_jitter(
-#       seed = 1,
-#       width = 0.1,
-#       height = 0.1
-#     )
-#   ) +
-#   ylim(0, 25) +
-#   labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
-#   scale_fill_brewer(palette  = "RdBu") +
-#   ggtitle("GRI\n(AOI disruptive person)") +
-#   theme_cowplot() +
-#   theme(legend.position = "none") -> plot_gri_disrup
-# 
-# plot_gri_disrup
-
-```
-
-```{r gri_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# # GRI (AOI disruptive person)
-# # t-test for expertise differences
-# t.test(x = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Expert"],
-#        y = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Novice"],
-#        var.equal = TRUE)
-# 
-# # GRI (AOI disruptive person)
-# # effect size for expertise differences
-# d_gri_disrup <- CohenD(x = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Expert"],
-#                        y = df_gri_disrup$GRI_disrup[df_gri_disrup$Group == "Novice"],
-#                        na.rm = TRUE)
-# 
-# round(d_gri_disrup, 2)
+##################### t-Test & Effect Size for GRI ########################
+
+# Step 6: Create a table for the t-test and Cohen's d results
+gri_t_test_table <- data.frame(
+  "Group Comparison" = "Experts vs. Novices",
+  "t-value" = round(t_test_gri$statistic, 2),
+  "df" = t_test_gri$parameter,
+  "p-value" = round(t_test_gri$p.value, 3),
+  "Mean Difference" = round(t_test_gri$estimate[1] - t_test_gri$estimate[2], 2),
+  "Cohen's d" = d_gri,
+  "95% CI (d)" = d_conf_int_gri
+)
+
+# Display the t-Test and Effect Size table for GRI in APA format
+knitr::kable(gri_t_test_table, 
+             caption = "t-Test and Effect Size for GRI (Micro-Teaching Unit)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 
-############### TIME TO FIRST FIXATION ####################
-
-df_aoi %>% 
-  filter(TOI %in% c("Chatting_with_neighbour",
-                    "Clicking_pen",
-                    "Drawing",
-                    "Drumming_with_hands",
-                    "Head_on_table",
-                    "Heckling",
-                    "Looking_at_phone",
-                    "Snipping_with_fingers",
-                    "Whispering"
-                    )
-         ) %>% 
-  dplyr::select(Participant,
+##################### TIME TO FIRST FIXATION ########################
+
+# Define disruptions and categories
+verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
+physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
+lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")
+
+# Step 1: Data Preparation
+df_ttff_disrup <- df_aoi %>%
+  filter(TOI %in% c(verbal_disruptions, physical_disruptions, lack_of_eagerness)) %>%
+  dplyr::select(
+    Participant,
     TOI,
-                Time_to_first_fixation.Disruptive_Person,
-                ) %>% 
-  rowwise() %>% 
+    Time_to_first_fixation.Disruptive_Person
+  ) %>%
+  mutate(
+    Group = ifelse(Participant < 200, "Novice", "Expert"),
+    Disruption_Category = case_when(
+      TOI %in% verbal_disruptions ~ "Verbal disruptions",
+      TOI %in% physical_disruptions ~ "Physical disruptions",
+      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
+      TRUE ~ NA_character_
+    )
+  ) %>%
+  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
   drop_na() %>%
-  group_by(Participant) %>% 
-  filter(!Time_to_first_fixation.Disruptive_Person == 0, # exclude all participants with 0 msec
-         !Time_to_first_fixation.Disruptive_Person > 30000) %>% # cut-off 30sec
-  summarise(N = n(),
-            Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person/N)
-            ) %>% 
-  mutate(Group = ifelse(Participant < 200, "Novice", "Expert"),
-         Sum_disruptions = sum(N),
-         Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000, 
-                                          digits = 2)) -> df_ttff_disrup # changing milliseconds into seconds
-
-############### M, SD, min, max time to first fixation "Disruptive Person"
-ttff.disrup.table <-
-  df_ttff_disrup %>%
-  filter(!Participant %in% c("216", "113", "123")) %>% 
+  filter(
+    Time_to_first_fixation.Disruptive_Person > 0, # Exclude zero fixation times
+    Time_to_first_fixation.Disruptive_Person <= 30000 # Cut-off at 30 seconds
+  ) %>%
+  mutate(
+    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2)
+  )
+
+# Step 2: Descriptive Statistics
+ttff_disrup_table <- df_ttff_disrup %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M in sec" = round(mean(Disrup_time_fixation_sec), digits = 2),
-    "SD in sec" = round(sd(Disrup_time_fixation_sec), digits = 2),
-    "Min in sec" = round(min(Disrup_time_fixation_sec), digits = 2),
-    "Max in sec" = round(max(Disrup_time_fixation_sec), digits = 2)
-  )
-
-knitr::kable(ttff.disrup.table,
-             caption = "N, M, SD, min & max time to first fixation in seconds (AOI disruptive person)")
-
-############### M, SD, min, max of the perceived "Disruptive Person" ############### 
-number.perceived.disrup.table <-
- df_ttff_disrup %>%
-  filter(!Participant %in% c("216", "113", "123")) %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    Mean = round(mean(N, na.rm = TRUE), digits = 2),
-    SD = round(sd(N, na.rm = TRUE), digits = 2), 
-    Min = min(N, na.rm = TRUE),
-    Max = max(N, na.rm = TRUE)
-  )
-
-knitr::kable(number.perceived.disrup.table,
-             caption = "N, M, SD, min & max of the perceived ´disruptive person´")
-
-############### PLOTTING ###############
-
-##################### plotting "perceived disruptive person" for groups ##################### 
-plot_n_disrup <- 
-  df_ttff_disrup %>%
-  filter(!Participant %in% c("216", "113", "123")) %>%
-  ggplot(mapping = aes(x = Group,
-                       y = N)) +
- geom_boxplot(mapping = aes(fill = Group),
-               outlier.shape = NA) +
-  geom_point(size = 2,
-             alpha = 0.7,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  ylim(0,10) +
-  labs(x ="",
-       y = "Counts") + 
+    "M in sec" = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "SD in sec" = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Min in sec" = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Max in sec" = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2)
+  )
+
+knitr::kable(ttff_disrup_table,
+             caption = "N, M, SD, Min & Max Time to First Fixation in Seconds (AOI Disruptive Person)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Step 3: Split Data by Disruption Categories
+disruption_summary <- df_ttff_disrup %>%
+  group_by(Group, Disruption_Category) %>%
+  summarise(
+    Mean_Time_to_Fixation = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    SD_Time_to_Fixation = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    .groups = "drop"
+  )
+
+# Step 4: Plotting Time to First Fixation by Group and Overall
+# a) By Group
+y_max <- max(df_ttff_disrup$Disrup_time_fixation_sec, na.rm = TRUE) * 1.2
+
+# Calculate mean and SD for Experts and Novices
+mean_expert_ttff <- mean(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE)
+sd_expert_ttff <- sd(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE)
+mean_novice_ttff <- mean(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE)
+sd_novice_ttff <- sd(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE)
+
+# Conduct t-test and calculate Cohen's d for the overall data
+t_test_overall <- t.test(Disrup_time_fixation_sec ~ Group, data = df_ttff_disrup, var.equal = TRUE)
+p_value_ttff <- round(t_test_overall$p.value, 3)
+d_overall <- cohen.d(Disrup_time_fixation_sec ~ Group, data = df_ttff_disrup)
+cohen_d_ttff <- round(d_overall$estimate, 2)
+
+# Annotated Plot
+plot_time_disrup <- df_ttff_disrup %>%
+  ggplot(mapping = aes(x = Group, y = Disrup_time_fixation_sec, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 2, alpha = 0.7, width = 0.1, height = 0.1) +
+  ylim(0, y_max) +
+  labs(x = "", y = "Time to First Fixation (sec)") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Counts of the perceived ´disruptive person´\n") +
-  theme_cowplot() +
-  theme(legend.position="none")
-
-plot_n_disrup
-
-##################### plotting time to first fixation for groups ##################### 
-plot_time_disrup <- 
-  df_ttff_disrup %>%
-  filter(!Participant %in% c("216", "113", "123")) %>%
-  ggplot(mapping = aes(x = Group,
-                       y = Disrup_time_fixation_sec)) +
- geom_boxplot(mapping = aes(fill = Group),
-               outlier.shape = NA) +
-  geom_point(size = 2,
-             alpha = 0.7,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  ylim(0,10) +
-  labs(x ="",
-       y = "Seconds") + 
-  scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Time to first fixation\n(AOI disruptive person)") +
-  theme_cowplot() +
-  theme(legend.position="none")
-
+  ggtitle("Time to First Fixation\n(AOI Disruptive Person)") +
+  theme_apa() +
+  theme(legend.position = "none") +
+  # Annotate means and SDs for Experts and Novices
+  annotate("text", x = 1, y = y_max * 0.85,
+           label = paste0("M = ", round(mean_expert_ttff, 2), "\nSD = ", round(sd_expert_ttff, 2)),
+           hjust = 0.5, size = 4.5, fontface = "italic") +
+  annotate("text", x = 2, y = y_max * 0.85,
+           label = paste0("M = ", round(mean_novice_ttff, 2), "\nSD = ", round(sd_novice_ttff, 2)),
+           hjust = 0.5, size = 4.5, fontface = "italic") +
+  # Annotate p-value and Cohen's d between the groups
+  annotate("text", x = 1.5, y = y_max * 0.95,
+           label = paste0("p = ", p_value_ttff, "\nd = ", cohen_d_ttff),
+           hjust = 0.5, size = 4.5, fontface = "italic")
+
+# Display the final plot with improved readability
 plot_time_disrup
 
-```
-
-#### t-test & effect size "Time to first fixation" (AOI disruptive person)
-```{r ttff_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# TIME TO FIRST FIXATIONS on disruptive person 
-# t-test for expertise differences
-t.test(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
-       y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
-       var.equal = TRUE)
-
-# TIME TO FIRST FIXATIONS on disruptive person 
-# effect size for expertise differences
-d_time_disrup <- CohenD(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
-                    y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
-                    na.rm = TRUE)
-
-round(d_time_disrup, 2)
+# Step 5: Statistical Tests by Category
+category_results <- list()
+
+for (category in unique(df_ttff_disrup$Disruption_Category)) {
+  cat_data <- df_ttff_disrup %>% filter(Disruption_Category == category)
+  t_cat <- t.test(Disrup_time_fixation_sec ~ Group, data = cat_data, var.equal = TRUE)
+  d_cat <- cohen.d(Disrup_time_fixation_sec ~ Group, data = cat_data)
+  category_results[[category]] <- data.frame(
+    "Group Comparison" = "Experts vs. Novices",
+    "Disruption Category" = category,
+    "t-value" = round(t_cat$statistic, 2),
+    "df" = t_cat$parameter,
+    "p-value" = round(t_cat$p.value, 3),
+    "Mean Difference" = round(t_cat$estimate[1] - t_cat$estimate[2], 2),
+    "Cohen's d" = round(d_cat$estimate, 2),
+    "95% CI (d)" = paste0("[", round(d_cat$conf.int[1], 2), ", ", round(d_cat$conf.int[2], 2), "]")
+  )
+}
+
+# Combine results into a single table
+category_stats <- do.call(rbind, category_results)
+
+knitr::kable(category_stats, 
+             caption = "t-Test and Effect Size for Time to First Fixation by Disruption Category") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 
-### Classroom Questionnaire
-```{r classroom questionnaire, echo=FALSE, results='asis'}
+### Self-evaluation 
+```{r self-eval, echo=FALSE, results='asis'}
 
@@
 df_quest_long <- df_quest_plot %>% 
-  pivot_longer(!Group, names_to = "Scales Classroom Questionnaire", values_to = "Mean")
+  pivot_longer(!Group, names_to = "Scales Self-evaluation", values_to = "Mean")
 
@@
   scale_fill_brewer(palette  = "RdBu") +  
-  facet_wrap(vars(`Scales Classroom Questionnaire`), 
+  facet_wrap(vars(`Scales Self-evaluation`), 
              nrow = 1, strip.position = "bottom") +
   theme_cowplot() +
-  ggtitle("Classroom Questionnaire") +
+  ggtitle("Self-evaluation") +
     theme(
@@
 
-### Internal consistency (Omega) for Classroom Questionnaire
+### Internal consistency (Omega) for Self-evaluation
 ```{r cm_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

### 2024-11-19 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
updated R script

@@
   ggtitle("GRI\n(Micro-Teaching Unit)") +
-  theme_minimal() +
+  theme_cowplot() +
   theme(
@@
 
-# read in data and combine multiple excel sheets into a single table 
-sri <-
-  excel_sheets("data/Coding_SRI.xlsx") %>%
+# Data Import and Preprocessing ------------------------------------------
+sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
   map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
   filter(
-    !ID %in% c(201),
-    !disruption_appraisal == -100,
-    !confidence_appraisal == -100,
-    !disruption_appraisal == -99,
-    !confidence_appraisal == -99,
-    !disruption_appraisal == -88,
-    !confidence_appraisal == -88,
-    !prevalence_rating == -100,
-    !prevalence_rating == -99,
-    !prevalence_rating == -88
+    !ID %in% c(201, 223),
+    !disruption_appraisal %in% c(-100, -99, -88),
+    !confidence_appraisal %in% c(-100, -99, -88),
+    !prevalence_rating %in% c(-100, -99, -88)
   ) %>%
@@
 
-############## Disruption appraisal #########################
-
-sri.disrup.table <-
-  sri %>%
+# Descriptive Statistics -------------------------------------------------
+## Disruption Appraisal
+sri_disrup_table <- sri %>%
   group_by(ID) %>%
@@
     N = n(),
-    "M" = round(mean(disruption_appraisal), digits = 2),
-    "SD" = round(sd(disruption_appraisal), digits = 2),
-    "Min" = min(disruption_appraisal),
-    "Max" = max(disruption_appraisal)
-    )
-
-knitr::kable(sri.disrup.table,
-             caption = "Disruption Appraisal")
-
-### with event
-sri.disrup.event.table <-
-  sri %>%
-  group_by(ID, event) %>%
+    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
+    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
+    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
+    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
+  )
+
+## Confidence Appraisal
+sri_confi_table <- sri %>%
+  group_by(ID) %>%
   summarise(
     N = n(),
-    "M" = round(mean(disruption_appraisal), digits = 2),
-    "SD" = round(sd(disruption_appraisal), digits = 2),
-    "Min" = min(disruption_appraisal),
-    "Max" = max(disruption_appraisal)
-  )
-
-# insert a table into HTML
-knitr::kable(sri.disrup.event.table,
-             caption = "Disruption appraisal with event")
-
-# create a new data frame with appraisal
-sri_disrup <- subset.data.frame(sri, select = c(ID, event, disruption_appraisal))
-
-# plotting disruption appraisal for groups
-dist_group_plot <- 
-  sri_disrup %>% 
-  mutate(ID = factor(ID,
-                     levels = c("Novice",
-                                "Expert"
-                                )
-                     )
-         ) %>% 
-  ggplot(mapping = aes(x = ID,
-                       y = disruption_appraisal)) +
-  geom_boxplot(mapping = aes(fill = ID),
-               outlier.shape = NA) +
-  geom_point(size = 1,
-             alpha = 0.4,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  scale_x_discrete(limits = c("Novice", "Expert")) +
-  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
-  labs(x = "",
-       y = "Disruption Appraisal") + 
+    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
+    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
+    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
+    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
+  )
+
+## Prevalence Rating
+sri_preva_table <- sri %>%
+  group_by(ID) %>%
+  summarise(
+    N = n(),
+    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
+    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
+    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
+    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
+  )
+
+# APA-Conform Tables -----------------------------------------------------
+kable(sri_disrup_table, caption = "Descriptive Statistics for Disruption Appraisal", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+kable(sri_confi_table, caption = "Descriptive Statistics for Confidence Appraisal", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+kable(sri_preva_table, caption = "Descriptive Statistics for Prevalence Rating", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+# t-Tests and Effect Sizes -----------------------------------------------
+## Disruption Appraisal
+disrup_ttest <- t.test(
+  disruption_appraisal ~ ID, data = sri, var.equal = TRUE
+)
+disrup_d <- cohen.d(disruption_appraisal ~ ID, data = sri)
+
+## Confidence Appraisal
+confi_ttest <- t.test(
+  confidence_appraisal ~ ID, data = sri, var.equal = TRUE
+)
+confi_d <- cohen.d(confidence_appraisal ~ ID, data = sri)
+
+## Prevalence Rating
+preva_ttest <- t.test(
+  prevalence_rating ~ ID, data = sri, var.equal = TRUE
+)
+preva_d <- cohen.d(prevalence_rating ~ ID, data = sri)
+
+# APA-Conform Tables for t-Tests and Effect Sizes ------------------------
+disrup_stats <- tibble(
+  Statistic = c("t-value", "df", "p-value", "Cohen's d"),
+  Value = c(
+    round(disrup_ttest$statistic, 2),
+    round(disrup_ttest$parameter, 2),
+    round(disrup_ttest$p.value, 3),
+    round(disrup_d$estimate, 2)
+  )
+)
+
+confi_stats <- tibble(
+  Statistic = c("t-value", "df", "p-value", "Cohen's d"),
+  Value = c(
+    round(confi_ttest$statistic, 2),
+    round(confi_ttest$parameter, 2),
+    round(confi_ttest$p.value, 3),
+    round(confi_d$estimate, 2)
+  )
+)
+
+preva_stats <- tibble(
+  Statistic = c("t-value", "df", "p-value", "Cohen's d"),
+  Value = c(
+    round(preva_ttest$statistic, 2),
+    round(preva_ttest$parameter, 2),
+    round(preva_ttest$p.value, 3),
+    round(preva_d$estimate, 2)
+  )
+)
+
+kable(disrup_stats, caption = "t-Test and Effect Size for Disruption Appraisal", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+kable(confi_stats, caption = "t-Test and Effect Size for Confidence Appraisal", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+kable(preva_stats, caption = "t-Test and Effect Size for Prevalence Rating", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+# Plotting ---------------------------------------------------------------
+## Disruption Appraisal
+disrup_plot <- sri %>%
+  ggplot(aes(x = ID, y = disruption_appraisal, fill = ID)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
+  labs(x = "", y = "Disruption Appraisal") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("How disruptive was the event for you?") +
-  theme_cowplot()
-
-dist_group_plot
-```
-
-#### t-Test & effect size "Disruption appraisal"
-```{r sri_da_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-#################### T-TEST & EFFECT SIZE ############
-
-# Disruption appraisal 
-# t-test for expertise differences
-t.test(x = sri$disruption_appraisal[sri$ID == "Expert"],
-       y = sri$disruption_appraisal[sri$ID == "Novice"],
-       var.equal = TRUE)
-
-# Disruption appraisal 
-# effect size for expertise differences
-d_sri_disrup <- CohenD(x = sri$disruption_appraisal[sri$ID == "Expert"],
-                       y = sri$disruption_appraisal[sri$ID == "Novice"],
-                       na.rm = TRUE)
-
-round(d_sri_disrup, 2)
-```
-
-```{r sri_ca, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-############## Confidence appraisal #########################
-
-sri.confi.table <-
-  sri %>%
-  group_by(ID) %>%
-  summarise(
-    "M" = round(mean(confidence_appraisal), digits = 2),
-    "SD" = round(sd(confidence_appraisal), digits = 2),
-    "Min" = min(confidence_appraisal),
-    "Max" = max(confidence_appraisal)
-  )
-
-# insert a table into HTML
-knitr::kable(sri.confi.table,
-             caption = "Confidence appraisal")
-
-### with event
-sri.confi.event.table <- 
-  sri %>%
-  group_by(ID, event) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(confidence_appraisal), digits = 2),
-    "SD" = round(sd(confidence_appraisal), digits = 2),
-    "Min" = min(confidence_appraisal),
-    "Max" = max(confidence_appraisal)
-  )
-
-knitr::kable(sri.confi.event.table,
-             caption = "Confidence appraisal with event")
-
-# create a new data frame with appraisal
-sri_confi <- subset.data.frame(sri, 
-                               select = c(ID, 
-                                          event, 
-                                          confidence_appraisal)
-                               )
-
-# plotting confidence appraisal for groups
-confi_group_plot <- 
-  sri_confi %>% 
-  mutate(ID = factor(ID,
-                     levels = c("Novice",
-                                "Expert"
-                                )
-                     )
-         ) %>% 
-  ggplot(mapping = aes(x = ID,
-                       y = confidence_appraisal)) +
-  geom_boxplot(mapping = aes(fill = ID),
-               outlier.shape = NA) +
-  geom_point(size = 1,
-             alpha = 0.4,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  scale_x_discrete(limits = c("Novice", "Expert")) +
-  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
-  labs(x = "",
-       y = "Confidence Appraisal") + 
+  ggtitle("Disruption Appraisal by Group") +
+  theme_cowplot() +
+  theme(legend.position = "none") +
+  annotate(
+    "text", x = 1.5, y = max(sri$disruption_appraisal, na.rm = TRUE) * 1.2,
+    label = paste0(
+      "p = ", round(disrup_ttest$p.value, 3), ", d = ",
+      round(disrup_d$estimate, 2)
+    ),
+    size = 4, hjust = 0.5, fontface = "italic"
+  )
+
+print(disrup_plot)
+
+## Confidence Appraisal
+confi_plot <- sri %>%
+  ggplot(aes(x = ID, y = confidence_appraisal, fill = ID)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
+  labs(x = "", y = "Confidence Appraisal") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("How confident did you feel dealing with this event?") +
-  theme_cowplot()
-
-confi_group_plot
-```
-
-#### t-Test & effect size "Confidence appraisal"
-```{r sri_ca_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-#################### T-TEST & EFFECT SIZE ############
-
-# Confidence Appraisal 
-# t-test for expertise differences
-t.test(x = sri$confidence_appraisal[sri$ID == "Expert"],
-       y = sri$confidence_appraisal[sri$ID == "Novice"],
-       var.equal = TRUE)
-
-# Disruption Factor 
-# effect size for expertise differences
-d_sri_confi <- CohenD(x = sri$confidence_appraisal[sri$ID == "Expert"],
-                      y = sri$confidence_appraisal[sri$ID == "Novice"],
-                      na.rm = TRUE)
-
-round(d_sri_confi, 2)
-```
-
-### Prevalence Rating as manipulation check
-```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-############## Prevalence Rating #########################
-
-sri.preva.table <-
-  sri %>%
-  group_by(ID) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(prevalence_rating), digits = 2),
-    "SD" = round(sd(prevalence_rating), digits = 2),
-    "Min" = min(prevalence_rating),
-    "Max" = max(prevalence_rating)
-  )
-
-knitr::kable(sri.preva.table,
-             caption = "Prevalence rating")
-
-sri.preva.event.table <-
-  sri %>%
-  group_by(ID, event) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(prevalence_rating), digits = 2),
-    "SD" = round(sd(prevalence_rating), digits = 2),
-    "Min" = min(prevalence_rating),
-    "Max" = max(prevalence_rating)
-  )
-
-knitr::kable(sri.preva.event.table,
-             caption = "Prevalence rating with events")
-
-sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
-
-preva_group_plot <- 
-  sri_preva %>% 
-  mutate(ID = factor(ID,
-                     levels = c("Novice",
-                                "Expert"
-                                )
-                     )
-         ) %>% 
-  ggplot(mapping = aes(x = ID,
-                       y = prevalence_rating)) +
-  geom_boxplot(mapping = aes(fill = ID),
-               outlier.shape = NA) +
-  geom_point(size = 1,
-             alpha = 0.4,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  scale_x_discrete(limits = c("Novice", "Expert")) +
-  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
-  labs(x = "",
-       y = "Prevalence Rating") + 
+  ggtitle("Confidence Appraisal by Group") +
+  theme_cowplot() +
+  theme(legend.position = "none") +
+  annotate(
+    "text", x = 1.5, y = max(sri$confidence_appraisal, na.rm = TRUE) * 1.2,
+    label = paste0(
+      "p = ", round(confi_ttest$p.value, 3), ", d = ",
+      round(confi_d$estimate, 2)
+    ),
+    size = 4, hjust = 0.5, fontface = "italic"
+  )
+
+print(confi_plot)
+
+## Prevalence Rating
+preva_plot <- sri %>%
+  ggplot(aes(x = ID, y = prevalence_rating, fill = ID)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
+  labs(x = "", y = "Prevalence Rating") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("How widespread is this event in the classroom?") +
-  theme_cowplot()
-
-preva_group_plot
-
-#################### T-TEST & EFFECT SIZE ############
-
-t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
-       y = sri$prevalence_rating[sri$ID == "Novice"],
-       var.equal = TRUE)
-
-d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
-                      y = sri$prevalence_rating[sri$ID == "Novice"],
-                      na.rm = TRUE)
-
-round(d_sri_preva, 2)
-```
-
-### Internal consistency (Omega) for disruption and confidence appraisal
-```{r sri_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# Select the relevant columns (e.g., Disruption Appraisal and Confidence Appraisal)
-sri <-
-  excel_sheets("data/Coding_SRI.xlsx") %>%
+  ggtitle("Prevalence Rating by Group") +
+  theme_cowplot() +
+  theme(legend.position = "none") +
+  annotate(
+    "text", x = 1.5, y = max(sri$prevalence_rating, na.rm = TRUE) * 1.2,
+    label = paste0(
+      "p = ", round(preva_ttest$p.value, 3), ", d = ",
+      round(preva_d$estimate, 2)
+    ),
+    size = 4, hjust = 0.5, fontface = "italic"
+  )
+
+print(preva_plot)
+
+# Omega Calculations -----------------------------------------------------
+# Data Import ------------------------------------------------------------
+sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
   map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
   filter(
-    !ID %in% c(201),
-    !disruption_appraisal == -100,
-    !confidence_appraisal == -100,
-    !disruption_appraisal == -99,
-    !confidence_appraisal == -99,
-    !disruption_appraisal == -88,
-    !confidence_appraisal == -88,
-    !prevalence_rating == -100,
-    !prevalence_rating == -99,
-    !prevalence_rating == -88
-    )
-
-# change long to wide format
+    !ID %in% c(201, 223), # Exclude specific IDs
+    !disruption_appraisal %in% c(-100, -99, -88),
+    !confidence_appraisal %in% c(-100, -99, -88),
+    !prevalence_rating %in% c(-100, -99, -88)
+  )
+
+# Change Long Format to Wide Format --------------------------------------
 sri_wide <- sri %>%
-  pivot_wider(names_from = event, 
-              values_from = c(disruption_appraisal, confidence_appraisal, prevalence_rating))
-
-### DISRUPTIONS APPRAISAL
-
-# create new data frame with only disruption items
+  pivot_wider(
+    names_from = event,
+    values_from = c(disruption_appraisal, confidence_appraisal, prevalence_rating)
+  )
+
+# Helper Function for Omega Calculation -----------------------------------
+calculate_omega_total <- function(data, scale_name) {
+  if (nrow(data) == 0 || ncol(data) == 0) {
+    warning(paste("No valid data for", scale_name))
+    return(NA)
+  }
+
+  # Try Omega Calculation
+  result <- tryCatch(
+    omega(data),
+    error = function(e) {
+      warning(paste("Omega calculation failed for", scale_name, ":", e$message))
+      return(NULL)
+    }
+  )
+
+  # Check if Result is Valid and Extract omega.tot
+  if (is.null(result) || !"omega.tot" %in% names(result)) {
+    warning(paste("Omega total not available for", scale_name))
+    return(NA)
+  }
+
+  return(round(result$omega.tot, 2))
+}
+
+# Disruption Appraisal ---------------------------------------------------
 sri_wide_disrup <- sri_wide %>%
   dplyr::select(starts_with("disruption_appraisal")) %>%
+  mutate(across(everything(), ~ as.numeric(.))) %>%
   drop_na()
 
-# calculate omega with omega() function  
-omega_disrup <- omega(sri_wide_disrup)
-
-# display the results 
-print(omega_disrup)
-
-### CONFIDENCE APPRAISAL
-
-# create new data frame with only confidence items
+omega_total_disrup <- calculate_omega_total(sri_wide_disrup, "Disruption Appraisal")
+
+# Confidence Appraisal ---------------------------------------------------
 sri_wide_confi <- sri_wide %>%
   dplyr::select(starts_with("confidence_appraisal")) %>%
+  mutate(across(everything(), ~ as.numeric(.))) %>%
   drop_na()
 
-# calculate omega with omega() function  
-omega_confi <- omega(sri_wide_confi)
-
-# display the results 
-print(omega_confi)
+omega_total_confi <- calculate_omega_total(sri_wide_confi, "Confidence Appraisal")
+
+# Prevalence Rating ------------------------------------------------------
+sri_wide_preva <- sri_wide %>%
+  dplyr::select(starts_with("prevalence_rating")) %>%
+  mutate(across(everything(), ~ as.numeric(.))) %>%
+  drop_na()
+
+omega_total_preva <- calculate_omega_total(sri_wide_preva, "Prevalence Rating")
+
+# APA-Conform Table ------------------------------------------------------
+omega_table <- tibble(
+  Measure = c("Disruption Appraisal", "Confidence Appraisal", "Prevalence Rating"),
+  Omega_Total = c(omega_total_disrup, omega_total_confi, omega_total_preva)
+)
+
+# Display APA-Conform Table ----------------------------------------------
+kable(omega_table, caption = "Internal Consistency (Omega Total) for Appraisal Measures", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
 
@@
 
-# read in data
-df_sjt <- 
-  read_excel("./data/SJT.xlsx")
-
-# select relevant columns --> only subject ID and mean 
-df_sjt <- df_sjt %>%
-  dplyr::select(UI06_05, # ID
+# Data Import and Preprocessing ------------------------------------------
+df_sjt <- read_excel("./data/SJT.xlsx") %>%
+  dplyr::select(
+    UI06_05,  # ID
     SJT_AL_gek, # Monitoring
@@
     SJT_R_gek,  # Rules and routines
-         SJT_KF_gek) %>% # All
-  filter(!UI06_05 == 201) # exclude ID with no eye tracking data
-
-# remove NAs
-df_sjt <- na.omit(df_sjt)
-
-# rename columns
-df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
-                           "Monitoring" = "SJT_AL_gek",
-                           "Managing momentum" = "SJT_ST_gek",
-                           "Rules and routines" = "SJT_R_gek",
-                           "All" = "SJT_KF_gek"))
-
-# changing from wide to long format
+    SJT_KF_gek  # All
+  ) %>%
+  filter(!UI06_05 == 201) %>% # Exclude specific ID
+  na.omit() %>% # Remove NAs
+  rename(
+    Group = UI06_05,
+    Monitoring = SJT_AL_gek,
+    `Managing momentum` = SJT_ST_gek,
+    `Rules and routines` = SJT_R_gek,
+    All = SJT_KF_gek
+  ) %>%
+  mutate(Group = ifelse(Group < 200, "Novice", "Expert")) # Define groups
+
+# Reshape Data to Long Format --------------------------------------------
 df_sjt_long <- df_sjt %>%
-  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")
-
-# define expert and novice with ifelse function
-df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")
-
-#################### N, MEAN & SD ############
-
-# mean & SD SJT ALL
-sjt_mean <- df_sjt_long %>%
-  filter(`Facets Classroom Management` == "All") %>%
+  pivot_longer(
+    !Group,
+    names_to = "Facets Classroom Management",
+    values_to = "Mean"
+  )
+
+# Descriptive Statistics Tables ------------------------------------------
+## Function to Calculate Descriptive Stats
+descriptive_stats <- function(data, facet) {
+  data %>%
+    filter(`Facets Classroom Management` == facet) %>%
     group_by(Group) %>%
-  summarise(N = n(),
-            "M" = round(mean(Mean), 2),
-            "SD" = round(sd(Mean), 2), 
-            "Min" = round(min(Mean), 2),
-            "Max" = round(max(Mean), 2), 
-            )
-
-# insert a table into HTML
-knitr::kable(sjt_mean,
-             caption = "N, M and SD for overall value")
-
-# mean SJT Managing Momentum
-sjt_mm <- df_sjt_long %>%
-  filter(`Facets Classroom Management` == "Managing momentum") %>%
-  group_by(Group) %>%
-  summarise(N = n(),
-            "M" = round(mean(Mean), 2),
-            "SD" = round(sd(Mean), 2), 
-            "Min" = round(min(Mean), 2),
-            "Max" = round(max(Mean), 2), 
-            )
-
-# insert a table into HTML
-knitr::kable(sjt_mm,
-             caption = "N, M and SD for managing momentum")
-
-# mean SJT Monitoring
-sjt_m <- df_sjt_long %>%
-  filter(`Facets Classroom Management` == "Monitoring") %>%
-  group_by(Group) %>%
-  summarise(N = n(),
-            "M" = round(mean(Mean), 2),
-            "SD" = round(sd(Mean), 2), 
-            "Min" = round(min(Mean), 2),
-            "Max" = round(max(Mean), 2), 
-            )
-
-# insert a table into HTML
-knitr::kable(sjt_m,
-             caption = "N, M and SD for monitoring")
-
-# mean SJT Rules and routins
-sjt_r <- df_sjt_long %>%
-  filter(`Facets Classroom Management` == "Rules and routines") %>%
-  group_by(Group) %>%
-  summarise(N = n(),
-            "M" = round(mean(Mean), 2),
-            "SD" = round(sd(Mean), 2), 
-            "Min" = round(min(Mean), 2),
-            "Max" = round(max(Mean), 2), 
-            )
-
-# insert a table into HTML
-knitr::kable(sjt_r,
-             caption = "N, M and SD for rules and routines")
-
-#################### Plots ############
-
-# plotting mean of all aspects 
-mean_plot <- 
-df_sjt_long %>% 
-  mutate(Group = factor(Group,
-                        levels = c("Novice", 
-                                   "Expert")
-                        )
-         ) %>% 
-  ggplot(mapping = aes(x = Group,
-                       y = Mean)) +
-  geom_boxplot(mapping = aes(fill = Group), 
-               outlier.shape = NA) +
-  geom_point(size = 1, 
+    summarise(
+      N = n(),
+      M = round(mean(Mean), 2),
+      SD = round(sd(Mean), 2),
+      Min = round(min(Mean), 2),
+      Max = round(max(Mean), 2),
+      .groups = "drop"
+    )
+}
+
+## Generate Tables
+sjt_all <- descriptive_stats(df_sjt_long, "All")
+sjt_mm <- descriptive_stats(df_sjt_long, "Managing momentum")
+sjt_m <- descriptive_stats(df_sjt_long, "Monitoring")
+sjt_r <- descriptive_stats(df_sjt_long, "Rules and routines")
+
+## Display APA-Conform Tables
+kable(sjt_all, caption = "Descriptive Statistics for Overall SJT Score") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+kable(sjt_mm, caption = "Descriptive Statistics for Managing Momentum") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+kable(sjt_m, caption = "Descriptive Statistics for Monitoring") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+kable(sjt_r, caption = "Descriptive Statistics for Rules and Routines") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+# Plotting SJT Facets ----------------------------------------------------
+mean_plot <- df_sjt_long %>%
+  mutate(Group = factor(Group, levels = c("Novice", "Expert"))) %>%
+  ggplot(aes(x = Group, y = Mean)) +
+  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 1,
     alpha = 0.4,
-             position = position_jitter(seed = 1, 
-                                        width = 0.1,
-                                        height = 0.1)) +
-  labs(x = "") +
-  ylim(0,1) + 
+    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
+  ) +
+  labs(x = "", y = "Mean SJT Score") +
   scale_fill_brewer(palette = "RdBu") +
-  facet_wrap(vars(`Facets Classroom Management`), 
-             nrow = 1, strip.position = "bottom") +
+  facet_wrap(~`Facets Classroom Management`, nrow = 1, strip.position = "bottom") +
   theme_cowplot() +
-  ggtitle("SJT") +
+  ggtitle("SJT Scores by Group") +
   theme(
-    plot.title = element_text(size = 25, 
-                              face = "bold"),
-    legend.title = element_text(size = 20),
-    legend.text = element_text(size = 15),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    strip.text.x = element_text(size = 8),
-    axis.title.y = element_text(size = 20),
-    axis.title.x = element_text(size = 22)
-        )
-
-mean_plot
-```
-
-#### t-test & effect size "STJ - All"
-```{r sjt_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#################### T-TEST & EFFECT SIZE ##################
-
-# define expert and novice with ifelse function in wide format
-df_sjt$Group = ifelse(df_sjt$Group < 200, "Novice","Expert")
-
-#### ALL #### 
-# t-test for expertise differences 
-t.test(x = df_sjt$All[df_sjt$Group == "Expert"],
-       y = df_sjt$All[df_sjt$Group == "Novice"],
-       var.equal = TRUE)
-
-# effect size for expertise differences
-d_sjt_all <- CohenD(x = df_sjt$All[df_sjt$Group == "Expert"],
-                    y = df_sjt$All[df_sjt$Group == "Novice"],
-                    na.rm = TRUE
-                    )
-
-round(d_sjt_all, 2)
-
-```
-
-#### t-test & effect size "SJT - Managing momentum"
-```{r sjt_mm, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-#### MANAGING MOMENTUM #### 
-# t-test for expertise differences 
-t.test(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
-       y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
+    plot.title = element_text(size = 20, face = "bold"),
+    legend.title = element_text(size = 14),
+    legend.text = element_text(size = 12),
+    axis.title.y = element_text(size = 14),
+    axis.text.x = element_text(size = 12)
+  )
+
+print(mean_plot)
+
+# Statistical Tests ------------------------------------------------------
+## Function to Perform t-Test and Effect Size
+t_test_stats <- function(data, group_col, value_col, facet_name) {
+  group_col <- ensym(group_col)  # Ensure proper quoting of group column
+  value_col <- ensym(value_col)  # Ensure proper quoting of value column
+
+  # Perform t-Test
+  t_test <- t.test(
+    formula = as.formula(paste0("`", quo_name(value_col), "` ~ ", quo_name(group_col))),
+    data = data,
     var.equal = TRUE
@@
 
-# effect size for expertise differences
-d_sjt_mm <- CohenD(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
-                   y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
-                   na.rm = TRUE
-                  )
-
-round(d_sjt_mm, 2)
-```
-
-#### t-test & effect size "SJT - Monitoring"
-```{r sjt_m, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-#### MONITORING ####
-# t-test for expertise differences 
-t.test(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
-       y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
-       var.equal = TRUE
-       )
-
-# effect size for expertise differences
-d_sjt_moni <- CohenD(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
-                     y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
-                     na.rm = TRUE
-                    )
-
-round(d_sjt_moni, 2)
-```
-
-#### t-test & effect size "SJT - Rules & routines"
-```{r sjt_rr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-#### RULES & ROUTINES #### 
-# t-test for expertise differences 
-t.test(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
-       y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"],
-       var.equal = TRUE
-      )
-
-# effect size for expertise differences
-d_sjt_rr <- CohenD(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
-                   y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"],
-                   na.rm = TRUE
-                  )
-
-round(d_sjt_rr, 2)
-
-```
-
-### Internal consistency (Omega) for SJT
-```{r sjt_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# read in data
-df_sjt <- 
-  read_excel("./data/SJT.xlsx")
-
-### MANAGING MOMENTUM
-
-# select relevant columns
-df_sjt_mm <- df_sjt %>%
-    dplyr::select(WT_S1_F1F2_AL:WT_S4_F4F6_AL)
-
-# remove NAs
-df_sjt_mm <- na.omit(df_sjt_mm)
-
-# calculate omega with omega() function  
-omega_sjt_mm <- omega(df_sjt_mm)
-
-# display the results 
-print(omega_sjt_mm)
-
-### MONITORING
-
-# select relevant columns
-df_sjt_m <- df_sjt %>%
-    dplyr::select(WT_S5_F1F2_ST:WT_S9_F4F5_ST)
-
-# remove NAs
-df_sjt_m <- na.omit(df_sjt_m)
-
-# calculate omega with omega() function  
-omega_sjt_m <- omega(df_sjt_m)
-
-# display the results 
-print(omega_sjt_m)
-
-### RULES & ROUTINES
-
-# select relevant columns
-df_sjt_r <- df_sjt %>%
-  dplyr::select(WT_S11_F1F5_R:WT_S14_F4F6_R)
-
-# remove NAs
-df_sjt_r <- na.omit(df_sjt_r)
-
-# calculate omega with omega() function  
-omega_sjt_r <- omega(df_sjt_r)
-
-# display the results 
-print(omega_sjt_r)
+  # Calculate Cohen's d
+  cohen_d <- CohenD(
+    x = data %>% filter(!!group_col == "Expert") %>% pull(!!value_col),
+    y = data %>% filter(!!group_col == "Novice") %>% pull(!!value_col)
+  )
+
+  tibble(
+    `Facet` = facet_name,
+    `t-value` = round(t_test$statistic, 2),
+    `p-value` = round(t_test$p.value, 3),
+    `Cohen's d` = round(cohen_d, 2)
+  )
+}
+
+## Generate t-Test Tables
+t_test_all <- t_test_stats(df_sjt, "Group", "All", "Overall")
+t_test_mm <- t_test_stats(df_sjt, "Group", "Managing momentum", "Managing Momentum")
+t_test_m <- t_test_stats(df_sjt, "Group", "Monitoring", "Monitoring")
+t_test_r <- t_test_stats(df_sjt, "Group", "Rules and routines", "Rules and Routines")
+
+## Combine Results into a Table
+t_test_results <- bind_rows(t_test_all, t_test_mm, t_test_m, t_test_r)
+
+## Display APA-Conform Table
+kable(t_test_results, caption = "t-Test and Effect Sizes for SJT Facets") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+# Internal Consistency (Omega) -------------------------------------------
+# Data Import
+df_sjt <- read_excel("./data/SJT.xlsx")
+
+# Subset Data for Each Scale ---------------------------------------------
+## Managing Momentum
+df_managing_momentum <- df_sjt %>%
+  select(matches("^WT_S1|^WT_S2|^WT_S3|^WT_S4")) %>%
+  na.omit()
+
+## Monitoring
+df_monitoring <- df_sjt %>%
+  select(matches("^WT_S5|^WT_S6|^WT_S7|^WT_S8|^WT_S9")) %>%
+  na.omit()
+
+## Rules and Routines
+df_rules_routines <- df_sjt %>%
+  select(matches("^WT_S11|^WT_S12|^WT_S13|^WT_S14")) %>%
+  na.omit()
+
+## Overall Mean (All Items Combined)
+df_overall <- df_sjt %>%
+  select(matches("^WT_S")) %>%  # Select all items starting with "WT_S"
+  na.omit()
+
+# Calculate Omega Total for Each Scale -----------------------------------
+## Helper Function for Omega Calculation
+calculate_omega <- function(data, scale_name) {
+  tryCatch({
+    result <- omega(data)
+    return(round(result$total$omega.tot, 2))  # Extract Omega Total
+  }, error = function(e) {
+    warning(paste("Omega calculation failed for", scale_name, ":", e$message))
+    return(NA)
+  })
+}
+
+## Calculate Omegas
+omega_managing_momentum <- calculate_omega(df_managing_momentum, "Managing Momentum")
+omega_monitoring <- calculate_omega(df_monitoring, "Monitoring")
+omega_rules_routines <- calculate_omega(df_rules_routines, "Rules and Routines")
+omega_overall <- calculate_omega(df_overall, "Overall Test")
+
+# Combine Results into a Table -------------------------------------------
+omega_results <- tibble(
+  Facet = c("Managing Momentum", "Monitoring", "Rules and Routines", "Overall Test"),
+  `Omega Total` = c(
+    omega_managing_momentum,
+    omega_monitoring,
+    omega_rules_routines,
+    omega_overall
+  )
+)
+
+# Display APA-Conform Table ----------------------------------------------
+kable(omega_results, caption = "Internal Consistency (Omega Total) for SJT Facets and Overall Test") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
 

### 2024-11-21 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper self-eval

@@
 # Omega Calculations -----------------------------------------------------
-# Data Import ------------------------------------------------------------
+# Data Import
 sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
@@
 
-# Change Long Format to Wide Format --------------------------------------
+# Change Long Format to Wide Format
 sri_wide <- sri %>%
@@
 
-# Helper Function for Omega Calculation -----------------------------------
+# Helper Function for Omega Calculation
 calculate_omega_total <- function(data, scale_name) {
@@
   ) %>%
-  filter(!UI06_05 == 201) %>% # Exclude specific ID
+  filter(!UI06_05 == 201,
+         !UI06_05 == 223) %>% # Exclude specific IDs
   na.omit() %>% # Remove NAs
@@
     axis.title.y = element_text(size = 14),
-    axis.text.x = element_text(size = 12)
+    axis.text.x = element_blank(), # Remove x-axis text
+    axis.ticks.x = element_blank(), # Remove x-axis ticks
+    strip.text = element_text(size = 10) # Increase facet label font size
   )
@@
 # Internal Consistency (Omega) -------------------------------------------
-# Data Import
-df_sjt <- read_excel("./data/SJT.xlsx")
-
-# Subset Data for Each Scale ---------------------------------------------
-## Managing Momentum
-df_managing_momentum <- df_sjt %>%
-  select(matches("^WT_S1|^WT_S2|^WT_S3|^WT_S4")) %>%
+# Read in Data
+df_sjt <- read_excel("./data/SJT.xlsx")  # Replace with the correct path
+
+# Helper Function for Omega Calculation
+calculate_omega_total <- function(data, scale_name) {
+  if (nrow(data) == 0 || ncol(data) == 0) {
+    warning(paste("No valid data for", scale_name))
+    return(NA)
+  }
+
+  # Try Omega Calculation
+  result <- tryCatch(
+    omega(data),
+    error = function(e) {
+      warning(paste("Omega calculation failed for", scale_name, ":", e$message))
+      return(NULL)
+    }
+  )
+
+  # Check if Result is Valid and Extract omega.tot
+  if (is.null(result) || !"omega.tot" %in% names(result)) {
+    warning(paste("Omega total not available for", scale_name))
+    return(NA)
+  }
+
+  return(round(result$omega.tot, 2))
+}
+
+### MANAGING MOMENTUM ----------------------------------------------------
+# Select relevant columns and remove NAs
+df_sjt_mm <- df_sjt %>%
+  dplyr::select(WT_S1_F1F2_AL:WT_S4_F4F6_AL) %>%
   na.omit()
 
-## Monitoring
-df_monitoring <- df_sjt %>%
-  select(matches("^WT_S5|^WT_S6|^WT_S7|^WT_S8|^WT_S9")) %>%
+# Calculate omega
+omega_mm <- calculate_omega_total(df_sjt_mm, "Managing Momentum")
+
+### MONITORING -----------------------------------------------------------
+# Select relevant columns and remove NAs
+df_sjt_m <- df_sjt %>%
+  dplyr::select(WT_S5_F1F2_ST:WT_S9_F4F5_ST) %>%
   na.omit()
 
-## Rules and Routines
-df_rules_routines <- df_sjt %>%
-  select(matches("^WT_S11|^WT_S12|^WT_S13|^WT_S14")) %>%
+# Calculate omega
+omega_m <- calculate_omega_total(df_sjt_m, "Monitoring")
+
+### RULES & ROUTINES -----------------------------------------------------
+# Select relevant columns and remove NAs
+df_sjt_r <- df_sjt %>%
+  dplyr::select(WT_S11_F1F5_R:WT_S14_F4F6_R) %>%
   na.omit()
 
-## Overall Mean (All Items Combined)
+# Calculate omega
+omega_r <- calculate_omega_total(df_sjt_r, "Rules and Routines")
+
+### OVERALL TEST -----------------------------------------------------
+# Select relevant columns and remove NAs
 df_overall <- df_sjt %>%
-  select(matches("^WT_S")) %>%  # Select all items starting with "WT_S"
-  na.omit()
-
-# Calculate Omega Total for Each Scale -----------------------------------
-## Helper Function for Omega Calculation
-calculate_omega <- function(data, scale_name) {
-  tryCatch({
-    result <- omega(data)
-    return(round(result$total$omega.tot, 2))  # Extract Omega Total
-  }, error = function(e) {
-    warning(paste("Omega calculation failed for", scale_name, ":", e$message))
-    return(NA)
-  })
-}
-
-## Calculate Omegas
-omega_managing_momentum <- calculate_omega(df_managing_momentum, "Managing Momentum")
-omega_monitoring <- calculate_omega(df_monitoring, "Monitoring")
-omega_rules_routines <- calculate_omega(df_rules_routines, "Rules and Routines")
-omega_overall <- calculate_omega(df_overall, "Overall Test")
-
-# Combine Results into a Table -------------------------------------------
+  select(matches("WT_S")) %>%
+  mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
+  drop_na()
+
+# Calculate omega
+omega_overall <- calculate_omega_total(df_overall, "Overall Test")
+
+### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
+# APA-Conform Table ------------------------------------------------------
 omega_results <- tibble(
-  Facet = c("Managing Momentum", "Monitoring", "Rules and Routines", "Overall Test"),
-  `Omega Total` = c(
-    omega_managing_momentum,
-    omega_monitoring,
-    omega_rules_routines,
-    omega_overall
-  )
+  Facet = c("Overall Test", "Managing Momentum", "Monitoring", "Rules and Routines"),
+  `Omega Total` = c(omega_overall, omega_mm, omega_m, omega_r)
 )
@@
 # Display APA-Conform Table ----------------------------------------------
-kable(omega_results, caption = "Internal Consistency (Omega Total) for SJT Facets and Overall Test") %>%
+kable(omega_results, caption = "Internal Consistency (Omega) for SJT Facets") %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
@@
 
-# load data files with modified scales
+# Data Import and Preparation --------------------------------------------
 df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LI06_05,
-                LM01_01:LM01_08, # classroom management 
-                LP01_01:LP01_08) %>% # non- & paraverbal communication 
-  filter(!LI06_05 == 201) %>% # exclude ID with no eye tracking data
-  mutate(LI06_05 = ifelse(LI06_05 < 200, "Novice", "Expert")) %>% 
-  rename(Group = LI06_05)
-
-# remove NAs
-df_quest <- na.omit(df_quest)
-
-# create table with means
-df_quest_table <-
-  df_quest %>%
+  dplyr::select(
+    LI06_05, 
+    LM01_01:LM01_08,  # Classroom Management
+    LP01_01:LP01_08   # Non-/Paraverbal Communication
+  ) %>%
+  filter(LI06_05 != 201,
+         LI06_05 != 223) %>%  # Exclude ID 201
+  mutate(Group = ifelse(LI06_05 < 200, "Novice", "Expert")) %>%  # Group Definition
+  select(-LI06_05) %>%  # Drop ID column
+  na.omit()  # Remove NAs
+
+# Summary Statistics Table -----------------------------------------------
+df_quest_table <- df_quest %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M cm" = round(mean(c_across(starts_with(
-      "LM"
-    )), na.rm = TRUE), 2),
-    "SD cm" = round(sd(c_across(starts_with(
-      "LM"
-    )), na.rm = TRUE), 2),
-    "Min cm" = round(min(c_across(starts_with(
-      "LM"
-    )), na.rm = TRUE), 2),
-    "Max cm" = round(max(c_across(starts_with(
-      "LM"
-    )), na.rm = TRUE), 2),
-    # "N cm" = length(c_across(starts_with("LP")), na.rm = TRUE),
-    "M n&pv com" = round(mean(c_across(starts_with(
-      "LP"
-    )), na.rm = TRUE), 2),
-    "SD n&pv com" = round(sd(c_across(starts_with(
-      "LP"
-    )), na.rm = TRUE), 2),
-    "Min n&pv com" = round(min(c_across(starts_with(
-      "LP"
-    )), na.rm = TRUE), 2),
-    "Max n&pv com" = round(max(c_across(starts_with(
-      "LP"
-    )), na.rm = TRUE), 2)
-  )
-
-knitr::kable(df_quest_table,
-             caption = "Mean, SD, min, max for classroom managament (cm) and non-/paraverbal communication (n&pv com)")
-
-#################### Plots ############
-
-# create table with means
-df_quest_plot <-
-  df_quest %>%
+    `M cm` = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
+    `SD cm` = round(sd(c_across(starts_with("LM")), na.rm = TRUE), 2),
+    `Min cm` = round(min(c_across(starts_with("LM")), na.rm = TRUE), 2),
+    `Max cm` = round(max(c_across(starts_with("LM")), na.rm = TRUE), 2),
+    `M n&pv com` = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2),
+    `SD n&pv com` = round(sd(c_across(starts_with("LP")), na.rm = TRUE), 2),
+    `Min n&pv com` = round(min(c_across(starts_with("LP")), na.rm = TRUE), 2),
+    `Max n&pv com` = round(max(c_across(starts_with("LP")), na.rm = TRUE), 2)
+  )
+
+# Display APA-Conform Table
+kable(df_quest_table, 
+      caption = "Summary Statistics for Classroom Management and Non-/Paraverbal Communication") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+# Create Dataset for Plotting --------------------------------------------
+df_quest_plot <- df_quest %>%
   rowwise() %>%
-  transmute(Group = Group,
-            "All" = round(mean(c_across(starts_with("L")), na.rm = TRUE), 2),
-            "Classroom management" = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
-            "Non-/paraverbal communication" = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2)
-            )
-
-# changing from wide to long format
-df_quest_long <- df_quest_plot %>% 
+  transmute(
+    Group = Group,
+    All = round(mean(c_across(starts_with("L")), na.rm = TRUE), 2),
+    `Classroom Management` = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
+    `Non-/Paraverbal Communication` = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2)
+  ) %>%
+  ungroup() %>%
   pivot_longer(!Group, names_to = "Scales Self-evaluation", values_to = "Mean")
 
-# plotting mean of all aspects 
-quest_plot <- 
-df_quest_long %>% 
-  mutate(Group = factor(Group,
-                        levels = c("Novice", 
-                                   "Expert")
-                        )
-         ) %>% 
-  ggplot(mapping = aes(x = Group,
-                       y = Mean)) +
-  geom_boxplot(mapping = aes(fill = Group), 
-               outlier.shape = NA) +
-  geom_point(size = 1, 
+# Plot Mean Scores by Group ----------------------------------------------
+quest_plot <- df_quest_plot %>%
+  mutate(Group = factor(Group, levels = c("Novice", "Expert"))) %>%
+  ggplot(aes(x = Group, y = Mean)) +
+  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 1,
     alpha = 0.4,
-             position = position_jitter(seed = 1, 
-                                        width = 0.1,
-                                        height = 0.1)) +
-  labs(x = "") +
-  ylim(0,4) + 
+    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
+  ) +
+  labs(x = "", y = "Mean Scores") +
   scale_fill_brewer(palette = "RdBu") +
-  facet_wrap(vars(`Scales Self-evaluation`), 
-             nrow = 1, strip.position = "bottom") +
+  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
   theme_cowplot() +
-  ggtitle("Self-evaluation") +
+  ggtitle("Self-Evaluation Scores") +
   theme(
-    plot.title = element_text(size = 25, 
-                              face = "bold"),
+    plot.title = element_text(size = 25, face = "bold"),
     legend.title = element_text(size = 20),
@@
     strip.text.x = element_text(size = 8),
-    axis.title.y = element_text(size = 20),
-    axis.title.x = element_text(size = 22)
-        )
-
-quest_plot
-```
-
-#### t-test & effect size "Classroom Questionnaire - All"
-```{r classroom questionnaire_all, echo=FALSE, results='asis'}
-
-#################### T-TEST & EFFECT SIZE ##################
-
-#### All #### 
-# t-test for expertise differences 
-t.test(x = df_quest_plot$All[df_quest_plot$Group == "Expert"],
-       y = df_quest_plot$All[df_quest_plot$Group == "Novice"],
+    axis.title.y = element_text(size = 20)
+  )
+
+print(quest_plot)
+
+# T-Test and Effect Sizes ------------------------------------------------
+# t-Test Function for Long Format ----------------------------------------
+t_test_stats_long <- function(data, group_col, scale_filter, scale_name) {
+  # Subset Data for the Specific Scale
+  filtered_data <- data %>%
+    filter(`Scales Self-evaluation` == scale_filter)
+
+  # Perform t-Test
+  t_test <- t.test(
+    Mean ~ get(group_col),
+    data = filtered_data,
     var.equal = TRUE
@@
 
-# effect size for expertise differences
-d_quest_all <- CohenD(x = df_quest_plot$All[df_quest_plot$Group == "Expert"],
-                      y = df_quest_plot$All[df_quest_plot$Group == "Novice"],
-                      na.rm = TRUE
-                      )
-
-round(d_quest_all, 2)
-
-```
-
-#### t-test & effect size "Classroom Questionnaire - Classroom Management"
-```{r classroom questionnaire_cm, echo=FALSE, results='asis'}
-
-#### Classroom Management #### 
-# t-test for expertise differences 
-t.test(x = df_quest_plot$`Classroom management`[df_quest_plot$Group == "Expert"],
-       y = df_quest_plot$`Classroom management`[df_quest_plot$Group == "Novice"],
-       var.equal = TRUE)
-
-# effect size for expertise differences
-d_quest_cm <- CohenD(x = df_quest_plot$`Classroom management`[df_quest_plot$Group == "Expert"],
-                      y = df_quest_plot$`Classroom management`[df_quest_plot$Group == "Novice"],
-                      na.rm = TRUE
-                      )
-
-round(d_quest_cm, 2)
-```
-
-#### t-test & effect size "Classroom Questionnaire - Non-/paraverbal communication"
-```{r classroom questionnaire_npvc, echo=FALSE, results='asis'}
-
-#### Non-/paraverbal communication #### 
-# t-test for expertise differences 
-t.test(x = df_quest_plot$`Non-/paraverbal communication`[df_quest_plot$Group == "Expert"],
-       y = df_quest_plot$`Non-/paraverbal communication`[df_quest_plot$Group == "Novice"],
-       var.equal = TRUE)
-
-# effect size for expertise differences
-d_quest_npvc <- CohenD(x = df_quest_plot$`Non-/paraverbal communication`[df_quest_plot$Group == "Expert"],
-                      y = df_quest_plot$`Non-/paraverbal communication`[df_quest_plot$Group == "Novice"],
-                      na.rm = TRUE
-                      )
-
-round(d_quest_npvc, 2)
-
-```
-
-### Internal consistency (Omega) for Self-evaluation
-```{r cm_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# read in data
-df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LM01_01:LM01_08, # classroom management 
-                LP01_01:LP01_08) # non- & paraverbal communication
-
-# calculate omega with omega() function  
-df_quest <- omega(df_quest)
-
-# display the results 
-print(df_quest)
-
-### CLASSROOM MANAGEMENT
-# read in data
-df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LM01_01:LM01_08, # classroom management 
-                LP01_01:LP01_08) # non- & paraverbal communication
-
-# select relevant columns
-df_quest_cm <- df_quest %>%
-    dplyr::select(LM01_01:LM01_08)
-
-# remove NAs
-df_quest_cm <- na.omit(df_quest_cm)
-
-# calculate omega with omega() function  
-omega_quest_cm <- omega(df_quest_cm)
-
-# display the results 
-print(omega_quest_cm)
-
-### NON- & PARAVERBAL COMMUNICATION
-# read in data
-df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LM01_01:LM01_08, # classroom management 
-                LP01_01:LP01_08) # non- & paraverbal communication
-
-# select relevant columns
-df_quest_npvc <- df_quest %>%
-    dplyr::select(LP01_01:LP01_08)
-
-# remove NAs
-df_quest_npvc <- na.omit(df_quest_npvc)
-
-# calculate omega with omega() function  
-omega_quest_npvc <- omega(df_quest_npvc)
-
-# display the results 
-print(omega_quest_npvc)
-
+  # Calculate Cohen's d
+  cohen_d <- CohenD(
+    x = filtered_data %>% filter(!!rlang::sym(group_col) == "Expert") %>% pull(Mean),
+    y = filtered_data %>% filter(!!rlang::sym(group_col) == "Novice") %>% pull(Mean)
+  )
+
+  # Return Results
+  tibble(
+    `Scale` = scale_name,
+    `t-value` = round(t_test$statistic, 2),
+    `p-value` = round(t_test$p.value, 3),
+    `Cohen's d` = round(cohen_d, 2)
+  )
+}
+
+# Perform t-Tests for Each Scale
+t_test_all <- t_test_stats_long(df_quest_long, "Group", "All", "Overall")
+t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
+t_test_npvc <- t_test_stats_long(df_quest_long, "Group", "Non-/Paraverbal Communication", "Non-/Paraverbal Communication")
+
+# Combine Results into a Single Table
+t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_npvc)
+
+# Display Results in APA-Conform Table
+kable(t_test_results, caption = "t-Test and Effect Sizes for Self-Evaluation Scales") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+# Internal Consistency (Omega) -------------------------------------------
+# Helper Function for Omega Calculation
+calculate_omega_total <- function(data, scale_name) {
+  if (nrow(data) == 0 || ncol(data) == 0) {
+    warning(paste("No valid data for", scale_name))
+    return(NA)
+  }
+
+  # Try Omega Calculation
+  result <- tryCatch(
+    omega(data),
+    error = function(e) {
+      warning(paste("Omega calculation failed for", scale_name, ":", e$message))
+      return(NULL)
+    }
+  )
+
+  # Check if Result is Valid and Extract omega.tot
+  if (is.null(result) || !"omega.tot" %in% names(result)) {
+    warning(paste("Omega total not available for", scale_name))
+    return(NA)
+  }
+
+  return(round(result$omega.tot, 2))
+}
+
+### CLASSROOM MANAGEMENT -------------------------------------------------
+# Select relevant columns and remove NAs
+df_cm <- df_quest %>% select(starts_with("LM"))
+
+# Calculate omega
+omega_cm <- calculate_omega_total(df_cm, "Classroom Management")
+
+### NON & PARAVERBAL COMMUNICATION --------------------------------------
+# Select relevant columns and remove NAs
+df_npvc <- df_quest %>% select(starts_with("LP"))
+
+# Calculate omega
+omega_npvc <- calculate_omega_total(df_npvc, "Non-/Paraverbal Communication")
+
+### OVERALL TEST -----------------------------------------------------
+# Select relevant columns and remove NAs
+df_self_all <- df_quest %>%
+  select(matches("L")) %>%
+  mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
+  drop_na()
+
+# Calculate omega
+omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation")
+
+### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
+# APA-Conform Table ------------------------------------------------------
+omega_results <- tibble(
+  Facet = c("Overall Evaluation", "Classroom Management", "Non-/Paraverbal Communication"),
+  `Omega Total` = c(omega_self_all, omega_cm, omega_npvc)
+)
+
+# Display APA-Conform Table ----------------------------------------------
+kable(omega_results, caption = "Internal Consistency (Omega) for Self-evaluation") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
 ```

### 2024-11-22 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper update

@@
   filter(TOI == "Lesson") %>%
-  select(
+  dplyr::select (
     Group,
@@
     Participant,
-    starts_with("Total_duration_of_fixations"),
-    starts_with("Number_of_fixations")
+    "Total_duration_of_fixations.Anna",
+    "Total_duration_of_fixations.Bianca",
+    "Total_duration_of_fixations.Carl(a)",
+    "Number_of_fixations.Anna",
+    "Number_of_fixations.Bianca",
+    "Number_of_fixations.Carl(a)"
   ) %>%
@@
 
-# Determine max value for ylim to ensure all text is visible
-y_max <- max(df_aoi_stud$Stud_number_fixation_min) * 1.5  # Increase this multiplier if needed
-
-# Plot with adjusted ylim and annotations for readability
+# Determine the maximum y-value for ylim to ensure all data points and annotations are visible
+y_max <- max(df_aoi_stud$Stud_number_fixation_min) * 1.5  # Increase the multiplier if needed
+
+# Create the boxplot with jittered data points for better readability
 plot_number_min_stud <- df_aoi_stud %>%
@@
   geom_jitter(
-    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
+    width = 0.15, height = 0, alpha = 0.6, color = "black", size = 1.2
   ) +
@@
   theme(legend.position = "none") +
-  ylim(0, y_max) +  # Set y-axis limit to ensure space for annotations
-  # Adjusted annotations for mean (M) and SD using atop() to place SD below M
+  ylim(0, y_max) +  # Adjust y-axis limit to include annotations
+  # Annotate the means (M) and standard deviations (SD) for each group
   annotate("text", x = 1, y = y_max * 0.85,
-           label = paste0("atop(italic(M) == ", mean_novice, ", italic(SD) == ", sd_novice, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+           label = paste0("italic(M) == ", mean_novice, "~italic(SD) == ", sd_novice),
+           hjust = 0.5, size = 4, vjust = -0.5, parse = TRUE) +
   annotate("text", x = 2, y = y_max * 0.85,
-           label = paste0("atop(italic(M) == ", mean_expert, ", italic(SD) == ", sd_expert, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  # Place p-value and d above the boxplots
+           label = paste0("italic(M) == ", mean_expert, "~italic(SD) == ", sd_expert),
+           hjust = 0.5, size = 4, vjust = -0.5, parse = TRUE) +
+  # Display p-value and effect size above the plot
   annotate("text", x = 1.5, y = y_max * 0.95,
-           label = paste0("p = ", p_value, "\nd = ", cohen_d),
+           label = paste0("p = ", p_value, ", d = ", cohen_d),
            hjust = 0.5, size = 4, fontface = "italic")
 
+# Display the plot
 plot_number_min_stud
@@
   labs(
-    title = "Average Fixation Duration Percentage by AOI and Group (Descending Order)",
+    title = "Total Fixation Duration Percentage by AOI and Group (Descending Order)",
     x = "AOI",
@@
 # 1. Data Preparation: Filter and Calculate Average Duration of Fixations on AOI Students
-df_aoi_stud <- df_aoi %>%
+df_aoi %>%
   filter(TOI == "Lesson") %>%
-  dplyr::select(
+  dplyr::select (
     Group,
-    starts_with("Total_duration_of_fixations"),
-    starts_with("Number_of_fixations")
+    Duration_of_interval,
+    Participant,
+    "Total_duration_of_fixations.Anna",
+    "Total_duration_of_fixations.Bianca",
+    "Total_duration_of_fixations.Carl(a)",
+    "Number_of_fixations.Anna",
+    "Number_of_fixations.Bianca",
+    "Number_of_fixations.Carl(a)"
   ) %>%
@@
     Group = as_factor(Group),
+    Participant = Participant,
+    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
+    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
     Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 2) # Retained in milliseconds
-  ) %>%
-  drop_na()
+    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, digits = 2),
+    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, digits = 2),
+    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0)
+    ) -> df_aoi_stud
 
@@
 
-##################### TIME TO FIRST FIXATION ########################
+##################### NUMBER OF FIXATION ON AOI DISRUPTIVE PERSON ########################
 
 # Define disruptions and categories
+disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
+                 "Drumming_with_hands", "Head_on_table", "Heckling", 
+                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
 verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
@@
 
-# Step 1: Data Preparation
-df_ttff_disrup <- df_aoi %>%
-  filter(TOI %in% c(verbal_disruptions, physical_disruptions, lack_of_eagerness)) %>%
-  dplyr::select(
-    Participant,
-    TOI,
-    Time_to_first_fixation.Disruptive_Person
-  ) %>%
+# Filter and prepare data
+df_aoi_disrup <- df_aoi %>%
+  filter(TOI %in% disruptions) %>%
+  dplyr::select(Group, Participant, TOI, Duration_of_interval, 
+                "Number_of_fixations.Disruptive_Person") %>%
   mutate(
-    Group = ifelse(Participant < 200, "Novice", "Expert"),
+    Group = as_factor(Group),
     Disruption_Category = case_when(
@@
       TRUE ~ NA_character_
-    )
-  ) %>%
-  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
-  drop_na() %>%
-  filter(
-    Time_to_first_fixation.Disruptive_Person > 0, # Exclude zero fixation times
-    Time_to_first_fixation.Disruptive_Person <= 30000 # Cut-off at 30 seconds
-  ) %>%
-  mutate(
-    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2)
-  )
-
-# Step 2: Descriptive Statistics
-ttff_disrup_table <- df_ttff_disrup %>%
+    ),
+    Duration_of_interval_sec = Duration_of_interval / 1000
+  ) %>%
+  filter(!is.na(Disruption_Category))
+
+# Summarize data
+disruption_summary <- df_aoi_disrup %>%
+  group_by(Group, Participant, Disruption_Category) %>%
+  summarize(
+    total_duration_sec = sum(Duration_of_interval_sec, na.rm = TRUE),
+    fixation_count = sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE),
+    .groups = "drop"
+  ) %>%
+  mutate(fixations_per_second = fixation_count / total_duration_sec)
+
+# Individual-level aggregation
+individual_summary <- disruption_summary %>%
+  group_by(Group, Participant) %>%
+  summarize(
+    mean_fixations_per_second = mean(fixations_per_second, na.rm = TRUE),
+    .groups = "drop"
+  )
+
+# 1. APA-Conform Table: Overall Fixation Rate
+overall_stats <- individual_summary %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M in sec" = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    "SD in sec" = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    "Min in sec" = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    "Max in sec" = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2)
-  )
-
-knitr::kable(ttff_disrup_table,
-             caption = "N, M, SD, Min & Max Time to First Fixation in Seconds (AOI Disruptive Person)") %>%
+    M = round(mean(mean_fixations_per_second, na.rm = TRUE), 2),
+    SD = round(sd(mean_fixations_per_second, na.rm = TRUE), 2),
+    Min = round(min(mean_fixations_per_second, na.rm = TRUE), 2),
+    Max = round(max(mean_fixations_per_second, na.rm = TRUE), 2)
+  )
+
+# Render table for overall fixation rate
+overall_table <- knitr::kable(
+  overall_stats,
+  caption = "Descriptive Statistics for Overall Fixation Rate (AOI Disruptive Person)",
+  col.names = c("Group", "N", "M", "SD", "Min", "Max")
+) %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
-# Step 3: Split Data by Disruption Categories
-disruption_summary <- df_ttff_disrup %>%
-  group_by(Group, Disruption_Category) %>%
-  summarise(
-    Mean_Time_to_Fixation = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    SD_Time_to_Fixation = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    .groups = "drop"
-  )
-
-# Step 4: Plotting Time to First Fixation by Group and Overall
-# a) By Group
-y_max <- max(df_ttff_disrup$Disrup_time_fixation_sec, na.rm = TRUE) * 1.2
-
-# Calculate mean and SD for Experts and Novices
-mean_expert_ttff <- mean(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE)
-sd_expert_ttff <- sd(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE)
-mean_novice_ttff <- mean(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE)
-sd_novice_ttff <- sd(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE)
-
-# Conduct t-test and calculate Cohen's d for the overall data
-t_test_overall <- t.test(Disrup_time_fixation_sec ~ Group, data = df_ttff_disrup, var.equal = TRUE)
-p_value_ttff <- round(t_test_overall$p.value, 3)
-d_overall <- cohen.d(Disrup_time_fixation_sec ~ Group, data = df_ttff_disrup)
-cohen_d_ttff <- round(d_overall$estimate, 2)
-
-# Annotated Plot
-plot_time_disrup <- df_ttff_disrup %>%
-  ggplot(mapping = aes(x = Group, y = Disrup_time_fixation_sec, fill = Group)) +
+# Display overall table
+overall_table
+
+# 2. APA-Conform Table: Fixation Rate by Category Clustered by Disruption Category
+category_stats <- disruption_summary %>%
+  group_by(Disruption_Category, Group) %>%  # Group by category first, then by group
+  summarise(
+    N = n(),
+    M = round(mean(fixations_per_second, na.rm = TRUE), 2),
+    SD = round(sd(fixations_per_second, na.rm = TRUE), 2),
+    Min = round(min(fixations_per_second, na.rm = TRUE), 2),
+    Max = round(max(fixations_per_second, na.rm = TRUE), 2),
+    .groups = "drop"  # Ungroup after summarization
+  )
+
+# Render the table clustered by Disruption Categories
+category_table <- knitr::kable(
+  category_stats,
+  caption = "Descriptive Statistics for Fixation Rate by Disruption Category (AOI Disruptive Person)",
+  col.names = c("Disruption Category", "Group", "N", "M", "SD", "Min", "Max")
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE) %>%
+  kableExtra::group_rows(
+    index = table(category_stats$Disruption_Category)  # Automatically cluster by category
+  )
+
+# Display the clustered category-specific table
+category_table
+
+# 3. Plot: Overall Fixation Rate
+plot_overall <- individual_summary %>%
+  ggplot(mapping = aes(x = Group, y = mean_fixations_per_second)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  ylim (0, 1) + 
+  labs(x = "", y = "Mean Fixations per Second per Participant") +
+  ggtitle("Overall Fixation Rate per Participant\n(AOI disruptive person)") +
+  scale_fill_brewer(palette = "RdBu") +
+  theme_cowplot() +
+  theme(legend.position = "none")
+
+# 4. Plot: Fixation Rate by Disruption Category
+plot_category <- disruption_summary %>%
+  ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
   geom_boxplot(outlier.shape = NA) +
-  geom_jitter(size = 2, alpha = 0.7, width = 0.1, height = 0.1) +
-  ylim(0, y_max) +
-  labs(x = "", y = "Time to First Fixation (sec)") +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) + # Wrap long facet labels
+  labs(x = "", y = "Fixations per Second") +
+  ggtitle("Fixation Rate by Disruption Category\n(AOI disruptive person)") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Time to First Fixation\n(AOI Disruptive Person)") +
-  theme_apa() +
-  theme(legend.position = "none") +
-  # Annotate means and SDs for Experts and Novices
-  annotate("text", x = 1, y = y_max * 0.85,
-           label = paste0("M = ", round(mean_expert_ttff, 2), "\nSD = ", round(sd_expert_ttff, 2)),
-           hjust = 0.5, size = 4.5, fontface = "italic") +
-  annotate("text", x = 2, y = y_max * 0.85,
-           label = paste0("M = ", round(mean_novice_ttff, 2), "\nSD = ", round(sd_novice_ttff, 2)),
-           hjust = 0.5, size = 4.5, fontface = "italic") +
-  # Annotate p-value and Cohen's d between the groups
-  annotate("text", x = 1.5, y = y_max * 0.95,
-           label = paste0("p = ", p_value_ttff, "\nd = ", cohen_d_ttff),
-           hjust = 0.5, size = 4.5, fontface = "italic")
-
-# Display the final plot with improved readability
-plot_time_disrup
+  theme_cowplot() +
+  theme(
+    legend.position = "none",
+    strip.text = element_text(size = 10) # Adjust facet text size if necessary
+  )
+
+# Display plots
+plot_overall
+plot_category
 
@@
 
-for (category in unique(df_ttff_disrup$Disruption_Category)) {
-  cat_data <- df_ttff_disrup %>% filter(Disruption_Category == category)
-  t_cat <- t.test(Disrup_time_fixation_sec ~ Group, data = cat_data, var.equal = TRUE)
-  d_cat <- cohen.d(Disrup_time_fixation_sec ~ Group, data = cat_data)
+for (category in unique(disruption_summary$Disruption_Category)) {
+  cat_data <- disruption_summary %>% filter(Disruption_Category == category)
+  t_cat <- t.test(fixations_per_second ~ Group, data = cat_data, var.equal = TRUE)
+  d_cat <- cohen.d(fixations_per_second ~ Group, data = cat_data)
   category_results[[category]] <- data.frame(
     "Group Comparison" = "Experts vs. Novices",
-    "Disruption Category" = category,
     "t-value" = round(t_cat$statistic, 2),
@@
 
-# Combine results into a single table
-category_stats <- do.call(rbind, category_results)
-
-knitr::kable(category_stats, 
-             caption = "t-Test and Effect Size for Time to First Fixation by Disruption Category") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# Combine results into a single data frame and include Disruption Category
+category_stats <- do.call(rbind, lapply(names(category_results), function(cat) {
+  result <- category_results[[cat]]
+  result$Disruption_Category <- cat  # Add Disruption Category as a column
+  return(result)
+}))
+
+# Remove redundant Disruption Category column from the table
+category_stats <- category_stats %>%
+  relocate(Disruption_Category) %>%
+  arrange(Disruption_Category) %>%  # Ensure proper order by category
+  select(-Disruption_Category)  # Drop the column after adding grouping below
+
+# Render the table with grouped rows
+knitr::kable(
+  category_stats,
+  caption = "t-Test and Effect Size for Fixation Rate by Disruption Category",
+  col.names = c("Group Comparison", "t-value", "df", "p-value", "Mean Difference", "Cohen's d", "95% CI (d)")
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE) %>%
+  kableExtra::group_rows(
+    group_label = "Lack of eagerness to learn",
+    start_row = 1,
+    end_row = 1
+  ) %>%
+  kableExtra::group_rows(
+    group_label = "Physical disruptions",
+    start_row = 2,
+    end_row = 2
+  ) %>%
+  kableExtra::group_rows(
+    group_label = "Verbal disruptions",
+    start_row = 3,
+    end_row = 3
+  )
 
@@
   ) %>%
-  filter(LI06_05 != 201,
-         LI06_05 != 223) %>%  # Exclude ID 201
+  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
   mutate(Group = ifelse(LI06_05 < 200, "Novice", "Expert")) %>%  # Group Definition
@@
 # Create Dataset for Plotting --------------------------------------------
-df_quest_plot <- df_quest %>%
+df_quest_long <- df_quest %>%
   rowwise() %>%
@@
 # Plot Mean Scores by Group ----------------------------------------------
-quest_plot <- df_quest_plot %>%
+quest_plot <- df_quest_long %>%
   mutate(Group = factor(Group, levels = c("Novice", "Expert"))) %>%
@@
 ```
-
 ## Correlations
-```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}
-
-# demo data 
-df_demo <- 
-  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
-  filter(!LI06_05 == 201,
-         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
-  transmute(Participant = LI06_05,
-            `Teaching Experience` = LI04_01,
-            )
-
-# average duration, number fixation, GRI (micro-teaching unit)
-df_aoi %>%
+
+```{r correlation, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# 1. Load and Prepare Data -----------------------------------------------
+
+# Demo Data
+df_demo <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  filter(!LI06_05 %in% c(201, 223)) %>%  # Exclude participants without eye-tracking data
+  transmute(
+    Participant = LI06_05,
+    `Teaching Experience` = LI04_01
+  ) %>%
+  arrange(Participant)
+
+# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Person
+df_aoi_numb_dur <- df_aoi %>%
   filter(TOI == "Lesson") %>%
   dplyr::select(
-    Duration_of_interval,
     Participant,
@@
     starts_with("Average_duration"),
-    !"Total_duration_of_fixations.Disruptive_Person",
-    !"Number_of_fixations.Disruptive_Person",
-    !"Average_duration_of_fixations.Disruptive_Person"
+    Duration_of_interval  # Ensure this variable is included
+  ) %>%
+  dplyr::select(
+    -contains("Disruptive_Person")  # Exclude Disruptive Person
   ) %>%
@@
   transmute(
-    Participant = Participant,
-    Duration_of_interval = Duration_of_interval, 
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
-    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
-    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
-    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
-    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, digits = 2)
-    ) %>%
-  drop_na() %>% 
-  dplyr::select(Participant,
-         Number_fixation_min_mtu, 
-         Average_duration_mtu,
-         GRI_mtu) -> df_aoi_numb_dur
-
-# average duration, number fixation, GRI (AOI student)
-df_aoi %>%
+    Participant,
+    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
+    Number_fixation_min_mtu = round(sum(c_across(starts_with("Number_of")), na.rm = TRUE) /
+                                      Duration_of_interval_min, 0),
+    Average_duration_mtu = round(sum(c_across(starts_with("Total_duration")), na.rm = TRUE) /
+                                    sum(c_across(starts_with("Number_of")), na.rm = TRUE), 0),
+    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, 2)
+  ) %>%
+  arrange(Participant)
+
+# ET-Measures (AOI Students) - Exclude Disruptive Person
+df_aoi_stud <- df_aoi %>%
   filter(TOI == "Lesson") %>%
   dplyr::select (
+    Group,
+    Duration_of_interval,
     Participant,
-    Duration_of_interval,
     "Total_duration_of_fixations.Anna",
@@
   transmute(
+    Group = as_factor(Group),
+    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
+    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
     Participant = Participant,
-    Duration_of_interval = Duration_of_interval,
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
     Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
     Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Stud_number_fixation_min = round(Duration_of_interval_min / Stud_number_fixation, digits = 2),
-    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
-    GRI_stud = round(Average_duration_stud / Stud_number_fixation, digits = 2)
-    ) %>%
-  dplyr::select(Participant,
-                Stud_number_fixation_min,
-                Average_duration_stud,
-                GRI_stud) -> df_aoi_stud
-
-# average duration, number fixation, GRI (AOI disruptive person)
-df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select(Participant,
-                "Total_duration_of_fixations.Disruptive_Person",
-                "Number_of_fixations.Disruptive_Person"
-                ) %>%
-  rowwise() %>%
-  mutate(
-    Average_duration_disrup = round(
-      Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person,
-      digits = 0),
-    GRI_disrup = round(
-      Average_duration_disrup / Number_of_fixations.Disruptive_Person, digits = 2)) %>%
-  dplyr::select(Participant,
-                Number_of_fixations.Disruptive_Person,
-                Average_duration_disrup,
-                GRI_disrup
-                ) -> df_aoi_disrup
-
-df_aoi %>% 
-  filter(TOI %in% c("Chatting_with_neighbour",
+    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
+    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, 2),
+    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
+  ) %>%
+  drop_na()
+
+# ET-Measures (AOI Disruptive Person)
+# Number of fixations per second
+# Define the different types of disruptions and categories
+disruptions <- c(
+  "Chatting_with_neighbour",
   "Clicking_pen",
@@
 )
-         ) %>% 
-  dplyr::select(Participant,
+verbal_disruptions <- c("Chatting_with_neighbour",
+                        "Heckling",
+                        "Whispering")
+physical_disruptions <- c("Clicking_pen",
+                          "Drumming_with_hands",
+                          "Snipping_with_fingers")
+lack_of_eagerness <- c("Looking_at_phone",
+                       "Head_on_table",
+                       "Drawing")
+
+# Step 1: Filter and prepare the data
+df_aoi_disrup <- df_aoi %>%
+  filter(TOI %in% disruptions) %>%  # Filter rows based on the disruption list
+  select(
+    Group,
+    Participant,
     TOI,
-                Time_to_first_fixation.Disruptive_Person,
-                ) %>% 
-  rowwise() %>% 
-  drop_na() %>% 
-  group_by(Participant) %>% 
-  filter(!Time_to_first_fixation.Disruptive_Person == 0, # exclude all participants with 0 msec
-         !Time_to_first_fixation.Disruptive_Person > 30000) %>% # cut-off 30sec
-  summarise(N = n(),
-            Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person/N)
-            ) %>% 
-  mutate(Group = ifelse(Participant < 200, "Novice", "Expert"),
-         Sum_disruptions = sum(N),
-         Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000, 
-                                          digits = 2)) -> df_ttff_disrup # changing milliseconds into seconds
-
-# rating scales
-df_sri <-
-  excel_sheets("data/Coding_SRI.xlsx") %>%
-  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
-  filter(
-    !ID %in% c(201,
-               223),
-    !disruption_appraisal == -100,
-    !confidence_appraisal == -100,
-    !disruption_appraisal == -99,
-    !confidence_appraisal == -99,
-    !disruption_appraisal == -88,
-    !confidence_appraisal == -88,
-    !prevalence_rating == -100,
-    !prevalence_rating == -99,
-    !prevalence_rating == -88
-    ) %>% 
+    Duration_of_interval,
+    "Number_of_fixations.Disruptive_Person"
+  ) %>%
+  mutate(
+    Group = as_factor(Group),  # Convert Group column to a factor
+    Disruption_Category = case_when(
+      # Assign categories based on disruption type
+      TOI %in% verbal_disruptions ~ "Verbal disruptions",
+      TOI %in% physical_disruptions ~ "Physical disruptions",
+      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
+      TRUE ~ NA_character_
+    ),
+    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2)  # Convert duration to seconds
+  ) %>%
+  filter(!is.na(Disruption_Category))  # Keep only rows with valid categories
+
+# Step 2: Aggregate data by Participant and Disruption Category
+df_aoi_numb_disrup <- df_aoi_disrup %>%
+  group_by(Participant, Disruption_Category) %>%
+  summarise(
+    Total_Number_of_Fixations = sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE),
+    Total_Duration_of_Interval_Sec = sum(Duration_of_interval_sec, na.rm = TRUE),
+    .groups = "drop"  # Avoid unnecessary grouping
+  )
+
+# Step 3: Pivot the data to create a single row for each Participant
+df_summary <- df_aggregated %>%
+  pivot_wider(
+    names_from = Disruption_Category,
+    values_from = c(Total_Number_of_Fixations, Total_Duration_of_Interval_Sec),
+    values_fill = 0  # Replace missing values with 0
+  )
+
+# SRI Rating Data
+df_sri <- read_xlsx("data/Coding_SRI.xlsx") %>%
+  filter(!ID %in% c(201, 223)) %>%
   rename(Participant = ID) %>%
@@
   summarise(
-    Mean_disruption_appraisal = round(mean(disruption_appraisal), 2),
-    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
-    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
-    )%>% 
-  dplyr::select(Participant,
-                Mean_disruption_appraisal,
-                Mean_confidence_appraisal)
-
-# sjt
-df_sjt <-
-  read_excel("./data/SJT.xlsx") %>%
-  dplyr::select(UI06_05, # Participant
-                SJT_AL_gek, # Monitoring
-                SJT_ST_gek, # Managing momentum
-                SJT_R_gek, # Rules and routines
-                SJT_KF_gek) %>% # All
-  filter(!UI06_05 %in% c(201, 223)) %>%  # exclude ID with no eye tracking data
+    Mean_disruption_appraisal = mean(disruption_appraisal, na.rm = TRUE),
+    Mean_confidence_appraisal = mean(confidence_appraisal, na.rm = TRUE),
+    Mean_prevalence_rating = mean(prevalence_rating, na.rm = TRUE)
+  )
+
+# Situational Judgment Test (SJT)
+df_sjt <- read_excel("./data/SJT.xlsx") %>%
+  filter(!UI06_05 %in% c(201, 223)) %>%
   transmute(
     Participant = UI06_05,
-    SJT_Monitoring = round(SJT_AL_gek, 2),
-    SJT_All = round(SJT_KF_gek, 2),
-  ) %>%
-  arrange(Participant)
-
-# classroom questionnaire
-df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(LI06_05, LM01_01:LM01_08, # classroom management
-                LP01_01:LP01_08) %>% # non- & paraverbal communication
-  filter(!LI06_05 %in% c(201, 223)) %>% # exclude ID with no eye tracking data
-  rename(Participant = LI06_05) %>%
-  group_by(Participant) %>%
+    SJT_All = SJT_KF_gek,
+    SJT_Monitoring = SJT_AL_gek
+  )
+
+# Self-Evaluation Data
+df_self_eval <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  filter(!LI06_05 %in% c(201, 223)) %>%
+  mutate(across(starts_with("L"), as.numeric)) %>%  # Convert all "L"-prefix columns to numeric
   transmute(
-    Participant = Participant,
-    "Quest_All" = round(mean(c_across(starts_with(
-      "L"
-    )), na.rm = TRUE), 2),
-    "Quest_classroom_management" = round(mean(c_across(starts_with(
-      "LM"
-    )), na.rm = TRUE), 2),
-    "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with(
-      "LP"
-    )), na.rm = TRUE), 2)
-  )
-
-# create a big data frame with all measures 
-# put all data frames into list
-df_list <- list(df_demo,
+    Participant = LI06_05,
+    Self_eval_classroom_management = rowMeans(select(., starts_with("LM")), na.rm = TRUE),
+    Self_eval_non_paraverbal_communication = rowMeans(select(., starts_with("LP")), na.rm = TRUE),
+    Self_eval_total = rowMeans(select(., starts_with("L")), na.rm = TRUE)
+  )
+
+# 2. Combine All Data ---------------------------------------------------
+
+# Combine all prepared datasets
+df_list <- list(
+  df_demo,
   df_aoi_numb_dur,
@@
   df_aoi_disrup,
-                df_ttff_disrup,
   df_sri,
   df_sjt,
-                df_quest)
-
-# merge all data frames in list
-df_merge <-
-  df_list %>% reduce(full_join, by='Participant') %>%
-  # filter(`Teaching Experience` > 0) %>% 
-  dplyr::select(GRI_mtu,
-                SJT_All,
-                Quest_All,
-                Mean_disruption_appraisal,
-                Mean_confidence_appraisal
-                )
-
-# create a correlation matrix
-cor_tab <- 
-  df_merge %>% 
-  cor(method = "pearson") %>% 
-  round(., digits = 2)
-
-# p-value for GRI x STJ_All
-cor.test(df_merge$GRI_mtu, df_merge$SJT_All)
-
-# p-value for GRI x Quest_All
-cor.test(df_merge$GRI_mtu, df_merge$Quest_All)
-
-# p-value for GRI x Disruption Rating
-cor.test(df_merge$GRI_mtu, df_merge$Mean_disruption_appraisal)
-
-# p-value for GRI x Confidence Rating
-cor.test(df_merge$GRI_mtu, df_merge$Mean_confidence_appraisal)
-
-### Teaching experience with only experts
-# merge all data frames in list
-df_merge_experts <-
-  df_list %>% reduce(full_join, by='Participant') %>%
-  filter(`Teaching Experience` > 0) %>% 
-  dplyr::select(`Teaching Experience`,
-                Stud_number_fixation_min,
-                Average_duration_stud,
-                Number_of_fixations.Disruptive_Person,
-                Average_duration_disrup,
-                Disrup_time_fixation_sec,
-                GRI_mtu,
-                SJT_All,
-                SJT_Monitoring,
-                Quest_All
-                )
-
-# create a correlation matrix
-cor_tab_experts <- 
-  df_merge_experts %>% 
-  cor(method = "pearson") %>% 
-  round(., digits = 2)
-
-# p-value for GRI x Teaching Experience
-cor.test(df_merge_experts$GRI_mtu, df_merge_experts$`Teaching Experience`)
-
-# ### Only novices
-# # merge all data frames in list
-# df_merge_novices <-
-#   df_list %>% reduce(full_join, by='Participant') %>%
-#   filter(`Teaching Experience` == 0) %>% 
-#   dplyr::select(`Teaching Experience`,
-#                 Stud_number_fixation_min,
-#                 Average_duration_stud,
-#                 Number_of_fixations.Disruptive_Person,
-#                 Average_duration_disrup,
-#                 Disrup_time_fixation_sec,
-#                 GRI_mtu,
-#                 SJT_All,
-#                 SJT_Monitoring,
-#                 Quest_All
-#                 )
-# 
-# # create a correlation matrix
-# cor_tab_novices <- 
-#   df_merge_novices %>% 
-#   cor(method = "pearson") %>% 
-#   round(., digits = 2)
-# 
-# # p-value for GRI x Teaching Experience
-# cor.test(cor_tab_novices$GRI_mtu, cor_tab_novices$`Teaching Experience`)
+  df_self_eval
+)
+
+df_merge <- reduce(df_list, full_join, by = "Participant") %>%
+  select(
+    GRI_mtu, SJT_All, Self_eval_total, Mean_disruption_appraisal, Mean_confidence_appraisal
+  )
+
+# 3. Correlation Analysis -----------------------------------------------
+
+# Compute Correlation Matrix
+cor_tab <- cor(df_merge, method = "pearson", use = "complete.obs") %>% round(2)
+
+# Create APA-Style Correlation Table
+apa.cor.table(
+  cor_tab,
+  filename = "correlation_table.docx"
+)
+
+# p-values for specific correlations
+pval_gri_sjt <- cor.test(df_merge$GRI_mtu, df_merge$SJT_All)$p.value
+pval_gri_self_eval <- cor.test(df_merge$GRI_mtu, df_merge$Self_eval_total)$p.value
+
+# Print Correlation Results
+print(cor_tab)
+cat("P-value (GRI x SJT):", pval_gri_sjt, "\n")
+cat("P-value (GRI x Self-evaluation):", pval_gri_self_eval, "\n")
 

### 2024-11-25 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
xxxxxx paperrrrr

@@
 library(needs)
-needs(tidyverse,
-      lubridate,
-      viridis,
-      grid,
-      gridExtra,
-      cowplot,
-      readxl,
-      ARTofR,
-      moments,
-      ltm,
-      sjPlot,
-      kableExtra,
-      xtable,
-      DescTools,
-      formattable,
-      psych,
-      apaTables,
-      rstatix,
-      effsize,
-      knitr,
-      papaja
+needs(
+  tidyverse,     # A collection of packages (e.g., ggplot2, dplyr, tidyr) for data manipulation, visualization, and general workflows.
+  lubridate,     # For working with dates and times (e.g., parsing, manipulation, arithmetic).
+  viridis,       # Provides colorblind-friendly color palettes for plots and visualizations.
+  grid,          # A base R package for low-level grid graphics, useful for customizing complex plots.
+  gridExtra,     # Extends grid by allowing multiple grid-based plots to be arranged into a single layout.
+  cowplot,       # Simplifies creating publication-quality multi-panel plots, often combined with ggplot2.
+  readxl,        # For reading Excel files (.xls, .xlsx) into R without requiring external dependencies.
+  ARTofR,        # For applying aligned rank transform (ART) to factorial data for nonparametric analysis.
+  moments,       # Provides functions to compute statistical moments (e.g., skewness, kurtosis).
+  ltm,           # Used for latent trait models, including item response theory (IRT) analysis.
+  sjPlot,        # A package to create publication-ready tables and visualizations for statistical models.
+  kableExtra,    # Enhances the `knitr::kable()` function for producing polished and customizable tables in R Markdown.
+  xtable,        # Converts R objects to LaTeX/HTML tables, especially useful for integration with Sweave/knitr.
+  DescTools,     # A toolbox of descriptive statistics, effect size calculations, and data manipulation utilities.
+  formattable,   # Allows creation of "formattable" data frames with customized formatting for reporting.
+  psych,         # Provides tools for psychological research, including reliability analysis and descriptive statistics.
+  apaTables,     # Simplifies the creation of APA-style tables for inclusion in papers or reports.
+  rstatix,       # User-friendly pipe-compatible functions for common statistical tests and effect sizes.
+  effsize,       # Computes effect sizes (e.g., Cohen's d) for t-tests and other statistical comparisons.
+  knitr,         # Enables dynamic reporting by weaving R code and outputs into documents (e.g., R Markdown).
+  papaja,        # Helps produce APA-style manuscripts directly from R Markdown.
+  afex,          # Performs ANOVAs, including mixed-designs and generalized linear models, with a focus on user-friendliness.
+  emmeans        # Computes estimated marginal means (or least-squares means) for post-hoc comparisons in models.
 )
@@
   ylim(0, y_max) +  # Adjust y-axis limit to include annotations
-  # Annotate the means (M) and standard deviations (SD) for each group
+  # Annotations for mean (M) and SD using atop() to place SD below M
   annotate("text", x = 1, y = y_max * 0.85,
-           label = paste0("italic(M) == ", mean_novice, "~italic(SD) == ", sd_novice),
-           hjust = 0.5, size = 4, vjust = -0.5, parse = TRUE) +
+           label = paste0("atop(italic(M) == ", mean_novice, ", italic(SD) == ", sd_novice, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
   annotate("text", x = 2, y = y_max * 0.85,
-           label = paste0("italic(M) == ", mean_expert, "~italic(SD) == ", sd_expert),
-           hjust = 0.5, size = 4, vjust = -0.5, parse = TRUE) +
-  # Display p-value and effect size above the plot
+           label = paste0("atop(italic(M) == ", mean_expert, ", italic(SD) == ", sd_expert, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  # Add p-value and Cohen's d annotations above the boxplots
   annotate("text", x = 1.5, y = y_max * 0.95,
-           label = paste0("p = ", p_value, ", d = ", cohen_d),
+           label = paste0("p = ", p_value, "\nd = ", cohen_d),
            hjust = 0.5, size = 4, fontface = "italic")
@@
 category_stats <- disruption_summary %>%
-  group_by(Group, Disruption_Category) %>%
+  group_by(Disruption_Category, Group) %>%
   summarise(
@@
 
-# Calculate metrics (mean, SD, p, d) by Disruption_Category and Group
-category_stats_with_tests <- disruption_summary %>%
-  group_by(Disruption_Category) %>%
-  summarise(
-    M_Novice = round(mean(fixations_per_second[Group == "Novice"], na.rm = TRUE), 2),
-    SD_Novice = round(sd(fixations_per_second[Group == "Novice"], na.rm = TRUE), 2),
-    M_Expert = round(mean(fixations_per_second[Group == "Expert"], na.rm = TRUE), 2),
-    SD_Expert = round(sd(fixations_per_second[Group == "Expert"], na.rm = TRUE), 2),
-    t_test = list(t.test(fixations_per_second ~ Group, var.equal = TRUE)), # Perform t-test
-    p_value = round(t.test(fixations_per_second ~ Group, var.equal = TRUE)$p.value, 3),
-    cohen_d = round(cohen.d(fixations_per_second ~ Group)$estimate, 2),
-    .groups = "drop"
-  ) %>%
-  mutate(
-    label = paste0(
-      "M (N) = ", M_Novice, ", SD (N) = ", SD_Novice, "\n",
-      "M (E) = ", M_Expert, ", SD (E) = ", SD_Expert, "\n",
-      "p = ", p_value, ", d = ", cohen_d
-    )
-  )
-
-# Join annotation labels with the main dataset
-disruption_summary_annotated <- disruption_summary %>%
-  left_join(category_stats_with_tests %>% select(Disruption_Category, label), by = "Disruption_Category")
-
-# Determine y-axis max value for each category for better placement of annotations
-y_max_by_category <- disruption_summary %>%
-  group_by(Disruption_Category) %>%
-  summarise(y_max = max(fixations_per_second, na.rm = TRUE) * 1.1, .groups = "drop")
-
-# Merge y_max values into the dataset for consistent annotation placement
-disruption_summary_annotated <- disruption_summary_annotated %>%
-  left_join(y_max_by_category, by = "Disruption_Category")
-
-# Plot with facets and annotations
+# # Prepare annotation data for labels
+# annotation_data <- category_stats_with_tests %>%
+#   left_join(y_max_by_category, by = "Disruption_Category") %>%
+#   mutate(
+#     novice_label = paste0("italic(M) == ", M_Novice, " ~ ", "italic(SD) == ", SD_Novice),
+#     expert_label = paste0("italic(M) == ", M_Expert, " ~ ", "italic(SD) == ", SD_Expert),
+#     overall_label = paste0("italic(p) == ", p_value, " ~ ", "italic(d) == ", cohen_d)
+#   )
+
+# Create the plot
 plot_category <- disruption_summary_annotated %>%
@@
   ) +
-  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) + # Wrap long facet labels
+  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) + # Fixed y-axis across facets
   labs(x = "", y = "Fixations per Second") +
@@
     strip.text = element_text(size = 10) # Adjust facet text size if necessary
-  ) +
-  geom_text(
-    data = disruption_summary_annotated %>%
-      distinct(Disruption_Category, label, y_max), # Ensure unique labels per facet
-    aes(x = 1.5, y = y_max, label = label),
-    inherit.aes = FALSE,
-    size = 3.5, hjust = 0.5, vjust = 0
-  )
+  ) 
+# +
+#   # Annotate novice statistics
+#   geom_text(
+#     data = annotation_data,
+#     aes(x = 1, y = y_max, label = novice_label),
+#     inherit.aes = FALSE,
+#     parse = TRUE, size = 3.5, hjust = 0.5, vjust = 0
+#   ) +
+#   # Annotate expert statistics
+#   geom_text(
+#     data = annotation_data,
+#     aes(x = 2, y = y_max, label = expert_label),
+#     inherit.aes = FALSE,
+#     parse = TRUE, size = 3.5, hjust = 0.5, vjust = 0
+#   ) +
+#   # Annotate p-value and Cohen's d
+#   geom_text(
+#     data = annotation_data,
+#     aes(x = 1.5, y = y_max * 1.05, label = overall_label),
+#     inherit.aes = FALSE,
+#     parse = TRUE, size = 4, fontface = "italic", hjust = 0.5, vjust = 0
+#   )
 
@@
   row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### REPEATED MEASURES ANOVA ########################
+
+# Perform the repeated-measures ANOVA
+anova_afex <- afex::aov_ez(
+  id = "Participant", # Random effect
+  dv = "fixations_per_second", # Dependent variable
+  between = "Group", # Between-subject factor
+  within = "Disruption_Category", # Within-subject factor
+  data = anova_data
+)
+
+# Extract the ANOVA table
+anova_results <- as.data.frame(anova_afex$anova_table)
+
+# Recalculate generalized eta squared (η²)
+eta_squared_results <- effectsize::eta_squared(anova_afex, partial = FALSE)
+
+# Combine recalculated eta squared with the ANOVA table
+anova_table_apa <- anova_results %>%
+  rownames_to_column(var = "Effect") %>% # Move row names to a column
+  left_join(
+    as.data.frame(eta_squared_results), 
+    by = c("Effect" = "Parameter") # Match the correct columns
+  ) %>%
+  mutate(
+    `F` = round(`F`, 2), # Round F-values
+    `η²` = round(Eta2, 3), # Round generalized eta squared
+    `p-value` = ifelse(
+      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 3) # Format p-values
+    )
+  ) %>%
+  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`) # Order columns, place η² last
+
+# Display the table
+kable(
+  anova_table_apa,
+  caption = "Repeated-Measures ANOVA Results (Including Effect Sizes)",
+  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
+  digits = 2
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Post-hoc comparisons for Disruption_Category
+  post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)
+
+  # Extract pairwise contrasts
+  post_hoc_results <- as.data.frame(post_hoc_disruption$contrasts)
+
+  # Clean up category names in the contrast column
+  post_hoc_results$contrast <- gsub("_", " ", post_hoc_results$contrast) # Replace underscores with spaces
+  post_hoc_results$contrast <- gsub("\\.", " ", post_hoc_results$contrast) # Replace dots with spaces
+
+  # Calculate Cohen's d for each pairwise comparison using pooled SD from emmeans
+  post_hoc_results <- post_hoc_results %>%
+    mutate(
+      pooled_sd = sqrt((SE^2 * 2)), # Approximation for pooled SD from SE
+      d = round(estimate / pooled_sd, 2), # Calculate Cohen's d
+      p.value = ifelse(
+        p.value < 0.05, "< .05", round(p.value, 3)
+      ),
+      t = round(t.ratio, 2),
+      df = round(df, 2),
+      Estimate = round(estimate, 2),
+      SE = round(SE, 2)
+    ) %>%
+    select(contrast, Estimate, SE, df, t, p.value, d) # Include Cohen's d
+
+  # Display APA-styled post-hoc table
+  kable(
+    post_hoc_results,
+    caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Including Effect Sizes)",
+    col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+    digits = 2
   ) %>%
@@
 
-# 1. Data Preparation: Filter and Calculate Average Duration of Fixations on AOI Disruptive Person
+##################### DATA PREPARATION ########################
+
+# Define the different types of disruptions and categories
+disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
+                 "Drumming_with_hands", "Head_on_table", "Heckling", 
+                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
+verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
+physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
+lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")
+
+# Step 1: Filter and prepare the data
 df_aoi_disrup <- df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select(
-    Group,
+  filter(TOI %in% disruptions) %>% # Filter rows based on the disruption list
+  select(Group, Participant, TOI, 
          "Total_duration_of_fixations.Disruptive_Person", 
-    "Number_of_fixations.Disruptive_Person"
-  ) %>%
-  rowwise() %>%
+         "Number_of_fixations.Disruptive_Person") %>%
   mutate(
-    Group = as_factor(Group),
-    Average_duration_disrup = round(Total_duration_of_fixations.Disruptive_Person / Number_of_fixations.Disruptive_Person, 2) # In milliseconds
-  ) %>%
-  drop_na()
-
-# 2. Descriptive Statistics Table
-dur_disrup_table <- df_aoi_disrup %>%
+    Group = as_factor(Group), # Convert Group column to a factor
+    Disruption_Category = case_when( # Assign categories based on disruption type
+      TOI %in% verbal_disruptions ~ "Verbal disruptions",
+      TOI %in% physical_disruptions ~ "Physical disruptions",
+      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
+      TRUE ~ NA_character_
+    ),
+    Average_duration_disrup = round(Total_duration_of_fixations.Disruptive_Person / 
+                                    Number_of_fixations.Disruptive_Person, 2) # Average duration in milliseconds
+  ) %>%
+  filter(!is.na(Disruption_Category) & !is.na(Average_duration_disrup)) # Remove NAs
+
+##################### DESCRIPTIVE STATISTICS ########################
+
+# Step 2: Summarize data by disruption category
+disruption_summary <- df_aoi_disrup %>%
+  group_by(Group, Participant, Disruption_Category) %>%
+  summarise(
+    mean_duration_ms = round(mean(Average_duration_disrup, na.rm = TRUE), 2),
+    .groups = "drop"
+  )
+
+# Step 3: Summarize by participant
+individual_summary <- disruption_summary %>%
+  group_by(Group, Participant) %>%
+  summarise(
+    mean_duration = round(mean(mean_duration_ms, na.rm = TRUE), 2), # Mean duration per participant
+    .groups = "drop"
+  )
+
+# Overall descriptive statistics
+overall_stats <- individual_summary %>%
   group_by(Group) %>%
   summarise(
-    N = n(),
-    "M in ms" = round(mean(Average_duration_disrup, na.rm = TRUE), 2),
-    "SD in ms" = round(sd(Average_duration_disrup, na.rm = TRUE), 2),
-    "Min in ms" = round(min(Average_duration_disrup, na.rm = TRUE), 2),
-    "Max in ms" = round(max(Average_duration_disrup, na.rm = TRUE), 2)
-  )
-
-# Display the descriptive table in APA style
-knitr::kable(dur_disrup_table,
-             caption = "N, M, SD, Min & Max Average Duration of Fixations in Milliseconds (AOI Disruptive Person)") %>%
+    N = n(), # Number of participants
+    Mean = round(mean(mean_duration, na.rm = TRUE), 2), # Mean duration
+    SD = round(sd(mean_duration, na.rm = TRUE), 2), # Standard deviation
+    Min = round(min(mean_duration, na.rm = TRUE), 2), # Minimum value
+    Max = round(max(mean_duration, na.rm = TRUE), 2), # Maximum value
+    .groups = "drop"
+  )
+
+# Display the overall descriptive statistics table
+knitr::kable(
+  overall_stats,
+  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Average Duration by Group",
+  col.names = c("Group", "N", "M", "SD", "Min", "Max"),
+  row.names = FALSE
+) %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
-# 3. Plotting Average Duration on AOI Disruptive Person
-# Calculate values for annotation
-mean_novice_disrup <- round(mean(df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"], na.rm = TRUE), 2)
-sd_novice_disrup <- round(sd(df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"], na.rm = TRUE), 2)
-mean_expert_disrup <- round(mean(df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"], na.rm = TRUE), 2)
-sd_expert_disrup <- round(sd(df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"], na.rm = TRUE), 2)
-
-# Maximum y-axis value for plot
-y_max_disrup <- max(df_aoi_disrup$Average_duration_disrup, na.rm = TRUE) * 1.2
-
-# Conduct t-test
-t_test_disrup <- t.test(
-  Average_duration_disrup ~ Group,
-  data = df_aoi_disrup,
-  var.equal = TRUE
-)
-
-# Extract p-value
-p_value_disrup <- round(t_test_disrup$p.value, 3)
-
-# Calculate Cohen's d (full result object)
-d_dur_disrup_full <- cohen.d(Average_duration_disrup ~ Group, data = df_aoi_disrup, pooled = TRUE)
-
-# Extract Cohen's d and confidence interval
-d_dur_disrup <- round(d_dur_disrup_full$estimate, 2)
-d_conf_int_disrup <- paste0("[", round(d_dur_disrup_full$conf.int[1], 2), ", ", round(d_dur_disrup_full$conf.int[2], 2), "]")
-
-# Annotated Plot
-plot_average_duration_disrup <- df_aoi_disrup %>%
-  ggplot(mapping = aes(x = Group, y = Average_duration_disrup)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
-  geom_jitter(
-    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
-  ) +
-  ylim(0, y_max_disrup) + 
-  labs(x = "", y = "Milliseconds") + 
+# Descriptive statistics by category
+category_stats <- disruption_summary %>%
+  group_by(Disruption_Category, Group) %>%
+  summarise(
+    N = n(), # Number of data points
+    Mean = round(mean(mean_duration_ms, na.rm = TRUE), 2), # Mean duration
+    SD = round(sd(mean_duration_ms, na.rm = TRUE), 2), # Standard deviation
+    Min = round(min(mean_duration_ms, na.rm = TRUE), 2), # Minimum value
+    Max = round(max(mean_duration_ms, na.rm = TRUE), 2), # Maximum value
+    .groups = "drop"
+  )
+
+# Display the descriptive statistics table by category
+knitr::kable(
+  category_stats,
+  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Average Duration by Group and Category",
+  col.names = c("Category", "Group", "N", "M", "SD", "Min", "Max"),
+  row.names = FALSE
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### PLOTTING ########################
+
+# Overall plot
+mean_novice <- round(mean(individual_summary$mean_duration[individual_summary$Group == "Novice"], na.rm = TRUE), 2)
+sd_novice <- round(sd(individual_summary$mean_duration[individual_summary$Group == "Novice"], na.rm = TRUE), 2)
+mean_expert <- round(mean(individual_summary$mean_duration[individual_summary$Group == "Expert"], na.rm = TRUE), 2)
+sd_expert <- round(sd(individual_summary$mean_duration[individual_summary$Group == "Expert"], na.rm = TRUE), 2)
+
+# t-Test and effect size
+t_test <- t.test(mean_duration ~ Group, data = individual_summary, var.equal = TRUE)
+p_value <- round(t_test$p.value, 3)
+cohen_d <- round(effsize::cohen.d(mean_duration ~ Group, data = individual_summary)$estimate, 2)
+
+# Overall plot
+y_max_overall <- max(individual_summary$mean_duration, na.rm = TRUE) * 1.5
+plot_overall <- ggplot(individual_summary, aes(x = Group, y = mean_duration, fill = Group)) +
+  geom_boxplot(outlier.shape = NA, width = 0.5) +
+  geom_jitter(width = 0.1, alpha = 0.7, color = "black", size = 1.5) +
+  labs(x = "", y = "Mean Duration (ms) per Participant") +
+  ggtitle("Overall Average Duration per Participant\n(AOI Disruptive Person)") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Average Duration of Fixations\n(AOI Disruptive Person)") +
   theme_cowplot() +
+  ylim(0, y_max_overall) +
   theme(legend.position = "none") +
-  # Annotate mean (M) and SD
-  annotate("text", x = 1, y = y_max_disrup * 0.85,
-           label = paste0("atop(italic(M) == ", mean_novice_disrup, ", italic(SD) == ", sd_novice_disrup, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  annotate("text", x = 2, y = y_max_disrup * 0.85,
-           label = paste0("atop(italic(M) == ", mean_expert_disrup, ", italic(SD) == ", sd_expert_disrup, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  # Annotate p-value and Cohen's d
-  annotate("text", x = 1.5, y = y_max_disrup * 0.95,
-           label = paste0("p = ", p_value_disrup, "\nd = ", d_dur_disrup),
+  annotate("text", x = 1, y = y_max_overall * 0.85,
+           label = paste0("M = ", mean_novice, "\nSD = ", sd_novice),
+           hjust = 0.5, size = 4, fontface = "italic") +
+  annotate("text", x = 2, y = y_max_overall * 0.85,
+           label = paste0("M = ", mean_expert, "\nSD = ", sd_expert),
+           hjust = 0.5, size = 4, fontface = "italic") +
+  annotate("text", x = 1.5, y = y_max_overall * 0.95,
+           label = paste0("p = ", p_value, "\nd = ", cohen_d),
            hjust = 0.5, size = 4, fontface = "italic")
 
-plot_average_duration_disrup
-
-# 4. t-Test and Effect Size Results Table
-t_test_disrup_result <- data.frame(
-  "Group Comparison" = "Experts vs. Novices",
-  "t-value" = round(t_test_disrup$statistic, 2),
-  "df" = t_test_disrup$parameter,
-  "p-value" = round(t_test_disrup$p.value, 3),
-  "Mean Difference" = round(t_test_disrup$estimate[1] - t_test_disrup$estimate[2], 2),
-  "Cohen's d" = d_dur_disrup,
-  "95% CI (d)" = d_conf_int_disrup
-)
-
-# Display the t-Test and Effect Size results table in APA style
-knitr::kable(t_test_disrup_result,
-             caption = "t-Test and Effect Size for Average Fixation Duration on AOI Disruptive Person (milliseconds)",
-             row.names = FALSE) %>%
+# Plot by category
+plot_category <- disruption_summary %>%
+  ggplot(aes(x = Group, y = mean_duration_ms, fill = Group)) +
+  geom_boxplot(outlier.shape = NA, width = 0.5) +
+  geom_jitter(width = 0.1, alpha = 0.7, size = 1.5, color = "black") +
+  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 20)) +
+  ylim(0, 2000) +
+  labs(x = "", y = "Mean Duration (ms)") +
+  ggtitle("Average Duration of Fixations by Disruption Category and Group") +
+  scale_fill_brewer(palette = "RdBu") +
+  theme_cowplot() +
+  theme(
+    legend.position = "none",
+    strip.text = element_text(size = 10)
+  )
+
+# Display plots
+plot_overall
+plot_category
+
+##################### ANOVA AND POST-HOC TESTS ########################
+
+# Perform the repeated-measures ANOVA
+anova_afex <- afex::aov_ez(
+  id = "Participant", # Random effect
+  dv = "mean_duration_ms", # Dependent variable
+  between = "Group", # Between-subject factor
+  within = "Disruption_Category", # Within-subject factor
+  data = disruption_summary
+)
+
+# Extract the ANOVA table
+anova_results <- as.data.frame(anova_afex$anova_table)
+
+# Recalculate generalized eta squared (η²)
+eta_squared_results <- effectsize::eta_squared(anova_afex, partial = FALSE)
+
+# Combine recalculated eta squared with the ANOVA table
+anova_table_apa <- anova_results %>%
+  rownames_to_column(var = "Effect") %>% # Move row names to a column
+  left_join(
+    as.data.frame(eta_squared_results), 
+    by = c("Effect" = "Parameter") # Match the correct columns
+  ) %>%
+  mutate(
+    `F` = round(`F`, 2), # Round F-values
+    `η²` = round(Eta2, 3), # Round generalized eta squared
+    `p-value` = ifelse(
+      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 3) # Format p-values
+    )
+  ) %>%
+  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`) # Order columns, place η² last
+
+# Display the ANOVA table
+kable(
+  anova_table_apa,
+  caption = "Repeated-Measures ANOVA Results for Average Duration (Including Effect Sizes)",
+  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
+  digits = 2
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### POST-HOC TESTS ########################
+
+# Perform post-hoc pairwise comparisons for Group
+post_hoc_group <- emmeans::emmeans(anova_afex, pairwise ~ Group)
+
+# Extract post-hoc pairwise contrasts for Group
+post_hoc_results_group <- as.data.frame(post_hoc_group$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast), # Replace underscores with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 3)),
+    Cohen_d = round(estimate / sqrt(SE^2 * 2), 2) # Approximate Cohen's d
+  ) %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d) # Keep relevant columns
+
+# Perform post-hoc pairwise comparisons for Disruption_Category
+post_hoc_disruption <- emmeans::emmeans(anova_afex, pairwise ~ Disruption_Category)
+
+# Extract post-hoc pairwise contrasts for Disruption_Category
+post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 3)),
+    Cohen_d = round(estimate / sqrt(SE^2 * 2), 2) # Approximate Cohen's d
+  ) %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d) # Keep relevant columns
+
+##################### TABLE FOR GROUP ########################
+
+# Display the post-hoc test results for Group
+knitr::kable(
+  post_hoc_results_group,
+  caption = "Post-Hoc Pairwise Comparisons for Group (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### TABLE FOR DISRUPTION CATEGORY ########################
+
+# Display the post-hoc test results for Disruption_Category
+knitr::kable(
+  post_hoc_results_disruption,
+  caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

### 2024-11-26 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper mwu test

@@
 
-##################### DURATION OF DISRUPTIONS ########################
-
-# 1. Data Preparation: Filter and Calculate Disruption Duration
+##################### DATA PREPARATION ########################
+
+# Prepare data for analysis: filter, calculate, and categorize disruptions
 df_aoi_disrup <- df_aoi %>%
@@
   ) %>%
-  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
+  filter(!is.na(Disruption_Category)) %>%
   drop_na()
@@
 
-# 2. Descriptive Statistics by Group (Overall)
-summary_stats <- df_aoi_disrup %>%
+# Descriptive Statistics by Group
+summary_stats_group <- df_aoi_disrup %>%
   group_by(Group) %>%
-  summarise(
-    Mean = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
-    SD = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
-    .groups = "drop"
-  )
-
-# 3. Descriptive Statistics by Group and Category
-disruption_stats_table <- df_aoi_disrup %>%
-  group_by(Group, Disruption_Category) %>%
   summarise(
@@
     SD = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
+    Median = round(median(Duration_of_interval_sec, na.rm = TRUE), 2),
+    IQR = round(IQR(Duration_of_interval_sec, na.rm = TRUE), 2),
     Min = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
@@
 
-# Overall t-Test and Cohen's d for Plot Annotations
-t_test_overall <- t.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, var.equal = TRUE)
-d_overall <- cohen.d(Duration_of_interval_sec ~ Group, data = df_aoi_disrup)
-
-# By Category t-Test and Cohen's d for Plot Annotations
-category_stats <- df_aoi_disrup %>%
-  group_by(Disruption_Category) %>%
-  summarise(
-    t_value = t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$statistic,
-    df = t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$parameter,
-    p_value = round(t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$p.value, 3),
-    cohen_d = round(cohen.d(Duration_of_interval_sec ~ Group)$estimate, 2),
+# Descriptive Statistics by Category and Group
+summary_stats_category_group <- df_aoi_disrup %>%
+  group_by(Disruption_Category, Group) %>%
+  summarise(
+    N = n(),
+    Mean = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
+    SD = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
+    Median = round(median(Duration_of_interval_sec, na.rm = TRUE), 2),
+    IQR = round(IQR(Duration_of_interval_sec, na.rm = TRUE), 2),
+    Min = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
+    Max = round(max(Duration_of_interval_sec, na.rm = TRUE), 2),
     .groups = "drop"
@@
 
+# Display Descriptive Tables
+kable(
+  summary_stats_group,
+  caption = "Descriptive Statistics for Disruption Duration by Group",
+  col.names = c("Group", "N", "Mean", "SD", "Median", "IQR", "Min", "Max"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+kable(
+  summary_stats_category_group,
+  caption = "Descriptive Statistics for Disruption Duration by Category and Group",
+  col.names = c("Category", "Group", "N", "Mean", "SD", "Median", "IQR", "Min", "Max"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
 ##################### PLOTS ########################
 
-# Plot 1: Disruption Duration by Group (Overall)
-y_max <- max(df_aoi_disrup$Duration_of_interval_sec) * 1.5
-
+# Plot 1: Disruption Duration by Group
 plot_duration_group <- ggplot(df_aoi_disrup, aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
@@
   theme(legend.position = "none") +
-  ylim(0, y_max) +
-  annotate("text", x = 1, y = y_max * 0.85,
-           label = paste0("M = ", summary_stats$Mean[summary_stats$Group == "Novice"],
-                          "\nSD = ", summary_stats$SD[summary_stats$Group == "Novice"]),
-           hjust = 0.5, size = 4, fontface = "italic") +
-  annotate("text", x = 2, y = y_max * 0.85,
-           label = paste0("M = ", summary_stats$Mean[summary_stats$Group == "Expert"],
-                          "\nSD = ", summary_stats$SD[summary_stats$Group == "Expert"]),
-           hjust = 0.5, size = 4, fontface = "italic") +
-  annotate("text", x = 1.5, y = y_max * 0.95,
-           label = paste0("p = ", format.pval(t_test_overall$p.value, digits = 3, eps = .001),
-                          "\nd = ", round(d_overall$estimate, 2)),
-           hjust = 0.5, size = 4, fontface = "italic")
+  annotate("text", x = 1, y = max(df_aoi_disrup$Duration_of_interval_sec) + 4,
+           label = paste0("Median = ", summary_stats_group$Median[summary_stats_group$Group == "Novice"],
+                          "\nIQR = ", summary_stats_group$IQR[summary_stats_group$Group == "Novice"]),
+           hjust = 0.5, size = 4) +
+  annotate("text", x = 2, y = max(df_aoi_disrup$Duration_of_interval_sec) + 4,
+           label = paste0("Median = ", summary_stats_group$Median[summary_stats_group$Group == "Expert"],
+                          "\nIQR = ", summary_stats_group$IQR[summary_stats_group$Group == "Expert"]),
+           hjust = 0.5, size = 4)
 
@@
   theme_cowplot() +
+  ylim(0, 30) + 
   scale_fill_brewer(palette = "RdBu") +
   ggtitle("Disruption Duration by Group and Category") +
-  theme(legend.position = "none") +
-  ylim(0, y_max) +
-  geom_text(data = category_stats, aes(
-    x = 1.5, y = y_max * 0.85,
-    label = paste0("p = ", p_value, "\nd = ", cohen_d)
-  ), inherit.aes = FALSE, size = 4, fontface = "italic")
+  theme(legend.position = "none")
 
@@
 
-##################### t-TEST AND EFFECT SIZE RESULTS ########################
-
-# 1. Overall t-Test and Cohen's d
-t_test_overall <- t.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, var.equal = TRUE)
-d_overall <- cohen.d(Duration_of_interval_sec ~ Group, data = df_aoi_disrup)
-
-# 2. t-Test and Cohen's d Results by Category
-category_stats <- df_aoi_disrup %>%
-  group_by(Disruption_Category) %>%
-  summarise(
-    t_value = round(t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$statistic, 2),
-    df = round(t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$parameter, 0),
-    p_value = round(t.test(Duration_of_interval_sec ~ Group, var.equal = TRUE)$p.value, 3),
-    cohen_d = round(cohen.d(Duration_of_interval_sec ~ Group)$estimate, 2),
-    "95% CI (d)" = paste0(
-      "[", round(cohen.d(Duration_of_interval_sec ~ Group)$conf.int[1], 2),
-      ", ", round(cohen.d(Duration_of_interval_sec ~ Group)$conf.int[2], 2), "]"
-    ),
+##################### STATISTICAL TESTS ########################
+
+# Normality Tests (Shapiro-Wilk)
+normality_tests <- df_aoi_disrup %>%
+  group_by(Group) %>%
+  summarise(
+    Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),
     .groups = "drop"
@@
 
-# 3. Format Overall t-Test Results for APA Table
-t_test_result_overall <- data.frame(
-  "t-value" = round(t_test_overall$statistic, 2),
-  "df" = round(t_test_overall$parameter, 0),
-  "p-value" = round(t_test_overall$p.value, 3),
-  "Mean Difference" = round(diff(t_test_overall$estimate), 2),
-  "Cohen's d" = round(d_overall$estimate, 2),
-  "95% CI (d)" = paste0("[", round(d_overall$conf.int[1], 2), ", ", round(d_overall$conf.int[2], 2), "]")
-)
-
-# Display Overall t-Test Results in APA Style
 kable(
-  t_test_result_overall,
-  caption = "t-Test and Effect Size for Disruption Duration (Overall)",
+  normality_tests,
+  caption = "Shapiro-Wilk Test for Normality by Group",
+  col.names = c("Group", "Shapiro-Wilk p-value"),
   row.names = FALSE
@@
 
-# 4. Display Category-Specific t-Test Results in APA Style
+# Mann-Whitney U-Test and Effect Size
+mann_whitney_test <- wilcox.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, exact = FALSE)
+
+# Effect Size Calculation for Mann-Whitney (r)
+n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))
+n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))
+r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
+
+mann_whitney_results <- data.frame(
+  "Test" = "Mann-Whitney U",
+  "W" = round(mann_whitney_test$statistic, 2),
+  "p-value" = round(mann_whitney_test$p.value, 3),
+  "Effect Size (r)" = round(r_effect, 3)
+)
+
 kable(
-  category_stats,
-  caption = "t-Test and Effect Size for Disruption Duration by Category",
-  col.names = c("Category", "t-value", "df", "p-value", "Cohen's d", "95% CI (d)"),
+  mann_whitney_results,
+  caption = "Mann-Whitney U-Test Results for Disruption Duration",
   row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Kruskal-Wallis Test and Pairwise Comparisons
+kruskal_test <- kruskal.test(Duration_of_interval_sec ~ Disruption_Category, data = df_aoi_disrup)
+
+kruskal_results <- data.frame(
+  "Test" = "Kruskal-Wallis",
+  "Chi-squared" = round(kruskal_test$statistic, 2),
+  "df" = kruskal_test$parameter,
+  "p-value" = round(kruskal_test$p.value, 3)
+)
+
+kable(
+  kruskal_results,
+  caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Pairwise Wilcoxon test with Bonferroni correction
+pairwise_wilcox <- pairwise.wilcox.test(
+  x = df_aoi_disrup$Duration_of_interval_sec,
+  g = df_aoi_disrup$Disruption_Category,
+  p.adjust.method = "bonferroni"
+)
+
+# Extract and round the p-values to 3 decimal places
+pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
+  mutate(across(everything(), ~ round(., 3)))
+
+# Display the results with rounded p-values
+kable(
+  pairwise_results,
+  caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",
+  row.names = TRUE
 ) %>%

### 2024-11-27 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper

@@
 df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  dplyr::select(
-    LI06_05, 
-    LM01_01:LM01_08,  # Classroom Management
-    LP01_01:LP01_08   # Non-/Paraverbal Communication
-  ) %>%
   filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
-  mutate(Group = ifelse(LI06_05 < 200, "Novice", "Expert")) %>%  # Group Definition
-  select(-LI06_05) %>%  # Drop ID column
+  mutate(
+    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
+    Participant = LI06_05  # Add new column "Participant"
+  ) %>%
+  arrange(Participant) %>% 
+  select(
+    Participant, 
+    Group, 
+    LM01_01:LM01_05,  # Classroom Management
+    LM01_06:LM01_08,  # Disruption Handling
+    LP01_01:LP01_08   # Presence
+  ) %>%
+  rename(
+    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
+    DH_01 = LM01_06, DH_02 = LM01_07, DH_03 = LM01_08,
+    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
+    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
+  ) %>%
   na.omit()  # Remove NAs
-
-# Summary Statistics Table -----------------------------------------------
-df_quest_table <- df_quest %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    `M cm` = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
-    `SD cm` = round(sd(c_across(starts_with("LM")), na.rm = TRUE), 2),
-    `Min cm` = round(min(c_across(starts_with("LM")), na.rm = TRUE), 2),
-    `Max cm` = round(max(c_across(starts_with("LM")), na.rm = TRUE), 2),
-    `M n&pv com` = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2),
-    `SD n&pv com` = round(sd(c_across(starts_with("LP")), na.rm = TRUE), 2),
-    `Min n&pv com` = round(min(c_across(starts_with("LP")), na.rm = TRUE), 2),
-    `Max n&pv com` = round(max(c_across(starts_with("LP")), na.rm = TRUE), 2)
-  )
-
-# Display APA-Conform Table
-kable(df_quest_table, 
-      caption = "Summary Statistics for Classroom Management and Non-/Paraverbal Communication") %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
 
@@
     Group = Group,
-    All = round(mean(c_across(starts_with("L")), na.rm = TRUE), 2),
-    `Classroom Management` = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
-    `Non-/Paraverbal Communication` = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2)
+    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),
+    `Disruption Handling` = round(mean(c_across(starts_with("DH")), na.rm = TRUE), 2),
+    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2)  # Excluding Participant column
   ) %>%
@@
   labs(x = "", y = "Mean Scores") +
+  ylim(0, 4) + 
   scale_fill_brewer(palette = "RdBu") +

### 2024-11-28 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper

@@
 
-### Self-evaluation 
-```{r self-eval, echo=FALSE, results='asis'}
+### Self-evaluation (5 classroom management items, 3 disruption handling items, 8 presence items)
+```{r self-eval_5-3-8, echo=FALSE, results='asis'}
 
@@
 
-# Create Dataset for Plotting --------------------------------------------
+# Create Dataset for Plotting with Overall Measure --------------------------------------------
 df_quest_long <- df_quest %>%
@@
     `Disruption Handling` = round(mean(c_across(starts_with("DH")), na.rm = TRUE), 2),
-    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2)  # Excluding Participant column
+    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2),  # Excluding Participant column
+    `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, DH_01, DH_02, DH_03, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value
   ) %>%
   ungroup() %>%
-  pivot_longer(!Group, names_to = "Scales Self-evaluation", values_to = "Mean")
+  pivot_longer(cols = c(`Classroom Management`, `Disruption Handling`, `Presence`, `Overall`),
+               names_to = "Scales Self-evaluation", values_to = "Mean")
 
@@
 quest_plot <- df_quest_long %>%
-  mutate(Group = factor(Group, levels = c("Novice", "Expert"))) %>%
+  mutate(
+    Group = factor(Group, levels = c("Novice", "Expert")),
+    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Disruption Handling", "Presence", "Overall"))  # Reorder scales
+  ) %>%
   ggplot(aes(x = Group, y = Mean)) +
@@
 
-# T-Test and Effect Sizes ------------------------------------------------
+# t-Test and Effect Sizes ------------------------------------------------
+
 # t-Test Function for Long Format ----------------------------------------
@@
     filter(`Scales Self-evaluation` == scale_filter)
+
+  # Check if there are exactly two levels in the group
+  if (length(unique(filtered_data[[group_col]])) != 2) {
+    warning(paste("Skipping t-test for", scale_name, ": Group must have exactly two levels"))
+    return(tibble(
+      `Scale` = scale_name,
+      `t-value` = NA,
+      `p-value` = NA,
+      `Cohen's d` = NA
+    ))
+  }
 
@@
 # Perform t-Tests for Each Scale
-t_test_all <- t_test_stats_long(df_quest_long, "Group", "All", "Overall")
+t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
 t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
-t_test_npvc <- t_test_stats_long(df_quest_long, "Group", "Non-/Paraverbal Communication", "Non-/Paraverbal Communication")
+t_test_npvc <- t_test_stats_long(df_quest_long, "Group", "Disruption Handling", "Disruption Handling")
+t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")
 
 # Combine Results into a Single Table
-t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_npvc)
+t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_npvc, t_test_presence)
 
@@
 # Select relevant columns and remove NAs
-df_cm <- df_quest %>% select(starts_with("LM"))
-
-# Calculate omega
+df_cm <- df_quest %>% select(starts_with("CM"))
+
+# Calculate omega for Classroom Management
 omega_cm <- calculate_omega_total(df_cm, "Classroom Management")
 
-### NON & PARAVERBAL COMMUNICATION --------------------------------------
+### DISRUPTION HANDLING --------------------------------------------------
 # Select relevant columns and remove NAs
-df_npvc <- df_quest %>% select(starts_with("LP"))
-
-# Calculate omega
-omega_npvc <- calculate_omega_total(df_npvc, "Non-/Paraverbal Communication")
+df_dh <- df_quest %>% select(starts_with("DH"))
+
+# Calculate omega for Disruption Handling
+omega_dh <- calculate_omega_total(df_dh, "Disruption Handling")
+
+### PRESENCE ------------------------------------------------------------
+# Select relevant columns and remove NAs
+df_presence <- df_quest %>% select(starts_with("P") & !starts_with("Participant"))
+
+# Calculate omega for Presence
+omega_presence <- calculate_omega_total(df_presence, "Presence")
 
 ### OVERALL TEST -----------------------------------------------------
-# Select relevant columns and remove NAs
+# Select relevant columns and remove NAs (for overall evaluation)
 df_self_all <- df_quest %>%
-  select(matches("L")) %>%
+  select(starts_with("CM"), starts_with("DH"), starts_with("P") & !starts_with("Participant")) %>%
   mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
@@
 
-# Calculate omega
+# Calculate omega for Overall Evaluation
 omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation")
@@
 omega_results <- tibble(
-  Facet = c("Overall Evaluation", "Classroom Management", "Non-/Paraverbal Communication"),
-  `Omega Total` = c(omega_self_all, omega_cm, omega_npvc)
+  Facet = c("Overall Evaluation", "Classroom Management", "Disruption Handling", "Presence"),
+  `Omega Total` = c(omega_self_all, omega_cm, omega_dh, omega_presence)
 )
@@
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
 ```
+
+### Self-evaluation (8 classroom management items, 8 presence items)
+```{r self-eval_8-8, echo=FALSE, results='asis'}
+
+# Data Import and Preparation --------------------------------------------
+df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
+  mutate(
+    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
+    Participant = LI06_05  # Add new column "Participant"
+  ) %>%
+  arrange(Participant) %>% 
+  select(
+    Participant, 
+    Group, 
+    LM01_01:LM01_08,  # Classroom Management and Disruption Handling combined
+    LP01_01:LP01_08   # Presence
+  ) %>%
+  rename(
+    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
+    CM_06 = LM01_06, CM_07 = LM01_07, CM_08 = LM01_08,  # Renaming combined columns
+    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
+    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
+  ) %>%
+  na.omit()  # Remove NAs
+
+# Create Dataset for Plotting with Combined Scales -------------------------
+df_quest_long <- df_quest %>%
+  rowwise() %>%
+  transmute(
+    Group = Group,
+    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),  # Combine Classroom Management and Disruption Handling
+    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2),  # Excluding Participant column
+    `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, CM_06, CM_07, CM_08, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value
+  ) %>%
+  ungroup() %>%
+  pivot_longer(cols = c(`Classroom Management`, `Presence`, `Overall`),
+               names_to = "Scales Self-evaluation", values_to = "Mean")
+
+# Plot Mean Scores by Group ----------------------------------------------
+quest_plot <- df_quest_long %>%
+  mutate(
+    Group = factor(Group, levels = c("Novice", "Expert")),
+    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Presence", "Overall"))  # Reorder scales
+  ) %>%
+  ggplot(aes(x = Group, y = Mean)) +
+  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 1,
+    alpha = 0.4,
+    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
+  ) +
+  labs(x = "", y = "Mean Scores") +
+  ylim(0, 4) + 
+  scale_fill_brewer(palette = "RdBu") +
+  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
+  theme_cowplot() +
+  ggtitle("Self-Evaluation Scores") +
+  theme(
+    plot.title = element_text(size = 25, face = "bold"),
+    legend.title = element_text(size = 20),
+    legend.text = element_text(size = 15),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    strip.text.x = element_text(size = 8),
+    axis.title.y = element_text(size = 20)
+  )
+
+print(quest_plot)
+
+# t-Test and Effect Sizes ------------------------------------------------
+# t-Test Function for Long Format ----------------------------------------
+t_test_stats_long <- function(data, group_col, scale_filter, scale_name) {
+  # Subset Data for the Specific Scale
+  filtered_data <- data %>%
+    filter(`Scales Self-evaluation` == scale_filter)
+
+  # Check if there are exactly two levels in the group
+  if (length(unique(filtered_data[[group_col]])) != 2) {
+    warning(paste("Skipping t-test for", scale_name, ": Group must have exactly two levels"))
+    return(tibble(
+      `Scale` = scale_name,
+      `t-value` = NA,
+      `p-value` = NA,
+      `Cohen's d` = NA
+    ))
+  }
+
+  # Perform t-Test
+  t_test <- t.test(
+    Mean ~ get(group_col),
+    data = filtered_data,
+    var.equal = TRUE
+  )
+
+  # Calculate Cohen's d
+  cohen_d <- CohenD(
+    x = filtered_data %>% filter(!!rlang::sym(group_col) == "Expert") %>% pull(Mean),
+    y = filtered_data %>% filter(!!rlang::sym(group_col) == "Novice") %>% pull(Mean)
+  )
+
+  # Return Results
+  tibble(
+    `Scale` = scale_name,
+    `t-value` = round(t_test$statistic, 2),
+    `p-value` = round(t_test$p.value, 3),
+    `Cohen's d` = round(cohen_d, 2)
+  )
+}
+
+# Perform t-Tests for Each Scale
+t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
+t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
+t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")
+
+# Combine Results into a Single Table
+t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_presence)
+
+# Display Results in APA-Conform Table
+kable(t_test_results, caption = "t-Test and Effect Sizes for Self-Evaluation Scales") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+# Internal Consistency (Omega) -------------------------------------------
+# Helper Function for Omega Calculation
+calculate_omega_total <- function(data, scale_name) {
+  if (nrow(data) == 0 || ncol(data) == 0) {
+    warning(paste("No valid data for", scale_name))
+    return(NA)
+  }
+
+  # Try Omega Calculation
+  result <- tryCatch(
+    omega(data),
+    error = function(e) {
+      warning(paste("Omega calculation failed for", scale_name, ":", e$message))
+      return(NULL)
+    }
+  )
+
+  # Check if Result is Valid and Extract omega.tot
+  if (is.null(result) || !"omega.tot" %in% names(result)) {
+    warning(paste("Omega total not available for", scale_name))
+    return(NA)
+  }
+
+  return(round(result$omega.tot, 2))
+}
+
+### CLASSROOM MANAGEMENT -------------------------------------------------
+# Select relevant columns and remove NAs
+df_cm <- df_quest %>% select(starts_with("CM"))
+
+# Calculate omega for Classroom Management
+omega_cm <- calculate_omega_total(df_cm, "Classroom Management")
+
+### PRESENCE ------------------------------------------------------------
+# Select relevant columns and remove NAs
+df_presence <- df_quest %>% select(starts_with("P") & !starts_with("Participant"))
+
+# Calculate omega for Presence
+omega_presence <- calculate_omega_total(df_presence, "Presence")
+
+### OVERALL TEST -----------------------------------------------------
+# Select relevant columns and remove NAs (for overall evaluation)
+df_self_all <- df_quest %>%
+  select(starts_with("CM"), starts_with("P") & !starts_with("Participant")) %>%
+  mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
+  drop_na()
+
+# Calculate omega for Overall Evaluation
+omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation")
+
+### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
+# APA-Conform Table ------------------------------------------------------
+omega_results <- tibble(
+  Facet = c("Overall Evaluation", "Classroom Management", "Presence"),
+  `Omega Total` = c(omega_self_all, omega_cm, omega_presence)
+)
+
+# Display APA-Conform Table ----------------------------------------------
+kable(omega_results, caption = "Internal Consistency (Omega) for Self-evaluation") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+```
+
 ## Correlations
@@
   ) %>%
+  select(Participant,
+        Number_fixation_min_mtu,
+        Average_duration_mtu,
+        GRI_mtu) %>% 
   arrange(Participant)
@@
     Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
-    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, 2),
     Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
   ) %>%
+  select(Participant,
+         Stud_number_fixation_min,
+         Average_duration_stud
+         ) %>% 
+  arrange(Participant) %>% 
   drop_na()
@@
 # Step 3: Pivot the data to create a single row for each Participant
-df_summary <- df_aggregated %>%
+df_summary <- df_aoi_numb_disrup %>%
   pivot_wider(

### 2024-11-28 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
Update expertise_2024_11_18_MK.Rmd

@@
 
-# Step 3: Extract only the participant's ID number (3 digits)
+# Step 3: Extract only the participant's ID number (3 digits) and assign group based on Participant ID
 df_aoi <- df_aoi %>%
-  mutate(Participant = as.numeric(str_extract(Participant, "\\d{3}")))
+  mutate(
+    Participant = as.numeric(str_extract(Participant, "\\d{3}")),
+    Group = case_when(  # Assign group based on Participant ID
+      Participant > 200 ~ "Expert",
+      Participant < 200 ~ "Novice",
+      TRUE ~ NA_character_  # In case there's any other value or missing
+    )
+  )
 
@@
 ```
+
 ### Check variables
@@
 ##################### AVERAGE DURATION ON AOI DISRUPTIVE PERSON ########################
-
 ##################### DATA PREPARATION ########################
@@
 
-##################### NUMBER OF FIXATION ON AOI DISRUPTIVE PERSON ########################
+##################### TIME TO FIRST FIXATION ########################
 
 # Define disruptions and categories
-disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
-                 "Drumming_with_hands", "Head_on_table", "Heckling", 
-                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
 verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
@@
 
-# Filter and prepare data
-df_aoi_disrup <- df_aoi %>%
-  filter(TOI %in% disruptions) %>%
-  dplyr::select(Group, Participant, TOI, Duration_of_interval, 
-                "Number_of_fixations.Disruptive_Person") %>%
+# Step 1: Data Preparation
+df_ttff_disrup <- df_aoi %>%
+  filter(TOI %in% c(verbal_disruptions, physical_disruptions, lack_of_eagerness)) %>%
+  dplyr::select(
+    Participant,
+    TOI,
+    Time_to_first_fixation.Disruptive_Person
+  ) %>%
   mutate(
-    Group = as_factor(Group),
+    Group = ifelse(Participant < 200, "Novice", "Expert"),  # Assigning Group based on Participant
     Disruption_Category = case_when(
@@
       TRUE ~ NA_character_
-    ),
-    Duration_of_interval_sec = Duration_of_interval / 1000
-  ) %>%
-  filter(!is.na(Disruption_Category))
-
-# Summarize data
-disruption_summary <- df_aoi_disrup %>%
-  group_by(Group, Participant, Disruption_Category) %>%
-  summarize(
-    total_duration_sec = sum(Duration_of_interval_sec, na.rm = TRUE),
-    fixation_count = sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE),
-    .groups = "drop"
-  ) %>%
-  mutate(fixations_per_second = fixation_count / total_duration_sec)
-
-# Individual-level aggregation
-individual_summary <- disruption_summary %>%
-  group_by(Group, Participant) %>%
-  summarize(
-    mean_fixations_per_second = mean(fixations_per_second, na.rm = TRUE),
-    .groups = "drop"
-  )
-
-# 1. APA-Conform Table: Overall Fixation Rate
-overall_stats <- individual_summary %>%
+    )
+  ) %>%
+  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
+  drop_na() %>%
+  filter(
+    Time_to_first_fixation.Disruptive_Person > 0, # Exclude zero fixation times
+    Time_to_first_fixation.Disruptive_Person <= 30000 # Cut-off at 30 seconds
+  ) %>%
+  mutate(
+    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2)
+  )
+
+##################### DESCRIPTIVE STATISTICS ########################
+
+# Step 2: Descriptive Statistics by Group
+ttff_disrup_table <- df_ttff_disrup %>%
   group_by(Group) %>%
@@
     N = n(),
-    M = round(mean(mean_fixations_per_second, na.rm = TRUE), 2),
-    SD = round(sd(mean_fixations_per_second, na.rm = TRUE), 2),
-    Min = round(min(mean_fixations_per_second, na.rm = TRUE), 2),
-    Max = round(max(mean_fixations_per_second, na.rm = TRUE), 2)
-  )
-
-# Render table for overall fixation rate
-overall_table <- knitr::kable(
-  overall_stats,
-  caption = "Descriptive Statistics for Overall Fixation Rate (AOI Disruptive Person)",
-  col.names = c("Group", "N", "M", "SD", "Min", "Max")
-) %>%
+    "M in sec" = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "SD in sec" = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Min in sec" = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Max in sec" = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2)
+  )
+
+knitr::kable(ttff_disrup_table,
+             caption = "N, M, SD, Min & Max Time to First Fixation in Seconds (AOI Disruptive Person)") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
-# Display overall table
-overall_table
-
-# 2. APA-Conform Table: Fixation Rate by Category Clustered by Disruption Category
-category_stats <- disruption_summary %>%
-  group_by(Disruption_Category, Group) %>%  # Group by category first, then by group
+##################### STATISTICS BY DISRUPTION CATEGORY ########################
+
+# Step 3: Descriptive Statistics by Category and Group
+summary_stats_category_group <- df_ttff_disrup %>%
+  group_by(Disruption_Category, Group) %>%
   summarise(
     N = n(),
-    M = round(mean(fixations_per_second, na.rm = TRUE), 2),
-    SD = round(sd(fixations_per_second, na.rm = TRUE), 2),
-    Min = round(min(fixations_per_second, na.rm = TRUE), 2),
-    Max = round(max(fixations_per_second, na.rm = TRUE), 2),
-    .groups = "drop"  # Ungroup after summarization
-  )
-
-# Render the table clustered by Disruption Categories
-category_table <- knitr::kable(
-  category_stats,
-  caption = "Descriptive Statistics for Fixation Rate by Disruption Category (AOI Disruptive Person)",
-  col.names = c("Disruption Category", "Group", "N", "M", "SD", "Min", "Max")
-) %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE) %>%
-  kableExtra::group_rows(
-    index = table(category_stats$Disruption_Category)  # Automatically cluster by category
-  )
-
-# Display the clustered category-specific table
-category_table
-
-# 3. Plot: Overall Fixation Rate
-plot_overall <- individual_summary %>%
-  ggplot(mapping = aes(x = Group, y = mean_fixations_per_second)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
-  ) +
-  ylim (0, 1) + 
-  labs(x = "", y = "Mean Fixations per Second per Participant") +
-  ggtitle("Overall Fixation Rate per Participant\n(AOI disruptive person)") +
+    Mean = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    SD = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    Median = round(median(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    IQR = round(IQR(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    Min = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    Max = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    .groups = "drop"
+  )
+
+knitr::kable(
+  summary_stats_category_group,
+  caption = "Descriptive Statistics for Time to First Fixation by Category and Group",
+  col.names = c("Category", "Group", "N", "Mean", "SD", "Median", "IQR", "Min", "Max"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### PLOTS ########################
+
+# Plot 1: Time to First Fixation by Group
+plot_ttff_group <- ggplot(df_ttff_disrup, aes(x = Group, y = Disrup_time_fixation_sec, fill = Group)) +
+  geom_boxplot(outlier.shape = NA, width = 0.5) +
+  geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
+  labs(x = "Group", y = "Time to First Fixation (seconds)") +
+  theme_cowplot() +
   scale_fill_brewer(palette = "RdBu") +
+  ggtitle("Time to First Fixation by Group") +
+  theme(legend.position = "none") +
+  annotate("text", x = 1, y = max(df_ttff_disrup$Disrup_time_fixation_sec, na.rm = TRUE) * 1.1,
+           label = paste0("Median = ", round(median(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE), 2),
+                          "\nIQR = ", round(IQR(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE), 2)),
+           hjust = 0.5, size = 4) +
+  annotate("text", x = 2, y = max(df_ttff_disrup$Disrup_time_fixation_sec, na.rm = TRUE) * 1.1,
+           label = paste0("Median = ", round(median(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE), 2),
+                          "\nIQR = ", round(IQR(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE), 2)),
+           hjust = 0.5, size = 4)
+
+# Display the first plot
+plot_ttff_group
+
+# Plot 2: Time to First Fixation by Group and Disruption Category
+plot_ttff_category <- ggplot(df_ttff_disrup, aes(x = Group, y = Disrup_time_fixation_sec, fill = Group)) +
+  geom_boxplot(outlier.shape = NA, width = 0.5) +
+  geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
+  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) +
+  labs(x = "Group", y = "Time to First Fixation (seconds)") +
   theme_cowplot() +
+  scale_fill_brewer(palette = "RdBu") +
+  ggtitle("Time to First Fixation by Group and Disruption Category") +
   theme(legend.position = "none")
 
-# 4. Plot: Fixation Rate by Disruption Category
-plot_category <- disruption_summary %>%
-  ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
-  ) +
-  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) + # Wrap long facet labels
-  labs(x = "", y = "Fixations per Second") +
-  ggtitle("Fixation Rate by Disruption Category\n(AOI disruptive person)") +
-  scale_fill_brewer(palette = "RdBu") +
-  theme_cowplot() +
-  theme(
-    legend.position = "none",
-    strip.text = element_text(size = 10) # Adjust facet text size if necessary
-  )
-
-# Display plots
-plot_overall
-plot_category
-
-# Step 5: Statistical Tests by Category
-category_results <- list()
-
-for (category in unique(disruption_summary$Disruption_Category)) {
-  cat_data <- disruption_summary %>% filter(Disruption_Category == category)
-  t_cat <- t.test(fixations_per_second ~ Group, data = cat_data, var.equal = TRUE)
-  d_cat <- cohen.d(fixations_per_second ~ Group, data = cat_data)
-  category_results[[category]] <- data.frame(
-    "Group Comparison" = "Experts vs. Novices",
-    "t-value" = round(t_cat$statistic, 2),
-    "df" = t_cat$parameter,
-    "p-value" = round(t_cat$p.value, 3),
-    "Mean Difference" = round(t_cat$estimate[1] - t_cat$estimate[2], 2),
-    "Cohen's d" = round(d_cat$estimate, 2),
-    "95% CI (d)" = paste0("[", round(d_cat$conf.int[1], 2), ", ", round(d_cat$conf.int[2], 2), "]")
-  )
-}
-
-# Combine results into a single data frame and include Disruption Category
-category_stats <- do.call(rbind, lapply(names(category_results), function(cat) {
-  result <- category_results[[cat]]
-  result$Disruption_Category <- cat  # Add Disruption Category as a column
-  return(result)
-}))
-
-# Remove redundant Disruption Category column from the table
-category_stats <- category_stats %>%
-  relocate(Disruption_Category) %>%
-  arrange(Disruption_Category) %>%  # Ensure proper order by category
-  select(-Disruption_Category)  # Drop the column after adding grouping below
-
-# Render the table with grouped rows
-knitr::kable(
-  category_stats,
-  caption = "t-Test and Effect Size for Fixation Rate by Disruption Category",
-  col.names = c("Group Comparison", "t-value", "df", "p-value", "Mean Difference", "Cohen's d", "95% CI (d)")
-) %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE) %>%
-  kableExtra::group_rows(
-    group_label = "Lack of eagerness to learn",
-    start_row = 1,
-    end_row = 1
-  ) %>%
-  kableExtra::group_rows(
-    group_label = "Physical disruptions",
-    start_row = 2,
-    end_row = 2
-  ) %>%
-  kableExtra::group_rows(
-    group_label = "Verbal disruptions",
-    start_row = 3,
-    end_row = 3
-  )
+# Display the second plot
+plot_ttff_category
+
+##################### STATISTICAL TESTS ########################
+
+# Normality Tests (Shapiro-Wilk)
+normality_tests <- df_ttff_disrup %>%
+  group_by(Group) %>%
+  summarise(
+    Shapiro_Wilk_p = round(shapiro.test(Disrup_time_fixation_sec)$p.value, 3),
+    .groups = "drop"
+  )
+
+kable(
+  normality_tests,
+  caption = "Shapiro-Wilk Test for Normality by Group",
+  col.names = c("Group", "Shapiro-Wilk p-value"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Mann-Whitney U-Test and Effect Size
+mann_whitney_test <- wilcox.test(Disrup_time_fixation_sec ~ Group, data = df_ttff_disrup, exact = FALSE)
+
+# Effect Size Calculation for Mann-Whitney (r)
+n1 <- nrow(df_ttff_disrup %>% filter(Group == "Novice"))
+n2 <- nrow(df_ttff_disrup %>% filter(Group == "Expert"))
+r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
+
+mann_whitney_results <- data.frame(
+  "Test" = "Mann-Whitney U",
+  "W" = round(mann_whitney_test$statistic, 2),
+  "p-value" = round(mann_whitney_test$p.value, 3),
+  "Effect Size (r)" = round(r_effect, 3)
+)
+
+kable(
+  mann_whitney_results,
+  caption = "Mann-Whitney U-Test Results for Time to First Fixation",
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Kruskal-Wallis Test and Pairwise Comparisons
+kruskal_test <- kruskal.test(Disrup_time_fixation_sec ~ Disruption_Category, data = df_ttff_disrup)
+
+kruskal_results <- data.frame(
+  "Test" = "Kruskal-Wallis",
+  "Chi-squared" = round(kruskal_test$statistic, 2),
+  "df" = kruskal_test$parameter,
+  "p-value" = round(kruskal_test$p.value, 3)
+)
+
+kable(
+  kruskal_results,
+  caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Pairwise Wilcoxon test with Bonferroni correction
+pairwise_wilcox <- pairwise.wilcox.test(
+  x = df_ttff_disrup$Disrup_time_fixation_sec,
+  g = df_ttff_disrup$Disruption_Category,
+  p.adjust.method = "bonferroni"
+)
+
+# Extract and round the p-values to 3 decimal places
+pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
+  mutate(across(everything(), ~ round(., 3)))
+
+# Display the results with rounded p-values
+kable(
+  pairwise_results,
+  caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",
+  row.names = TRUE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 # ET-Measures (AOI Disruptive Person)
-# Number of fixations per second
+# Number of fixations per second and Average duration of fixations
 # Define the different types of disruptions and categories
-disruptions <- c(
-  "Chatting_with_neighbour",
-  "Clicking_pen",
-  "Drawing",
-  "Drumming_with_hands",
-  "Head_on_table",
-  "Heckling",
-  "Looking_at_phone",
-  "Snipping_with_fingers",
-  "Whispering"
-)
-verbal_disruptions <- c("Chatting_with_neighbour",
-                        "Heckling",
-                        "Whispering")
-physical_disruptions <- c("Clicking_pen",
-                          "Drumming_with_hands",
-                          "Snipping_with_fingers")
-lack_of_eagerness <- c("Looking_at_phone",
-                       "Head_on_table",
-                       "Drawing")
-
-# Step 1: Filter and prepare the data
+disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
+                 "Drumming_with_hands", "Head_on_table", "Heckling", 
+                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
+verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
+physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
+lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")
+
+# Step 1: Filter and prepare the data for both fixation counts and average durations
 df_aoi_disrup <- df_aoi %>%
   filter(TOI %in% disruptions) %>%  # Filter rows based on the disruption list
-  select(
-    Group,
-    Participant,
-    TOI,
+  select(Group, Participant, TOI, 
          Duration_of_interval, 
-    "Number_of_fixations.Disruptive_Person"
-  ) %>%
+         "Number_of_fixations.Disruptive_Person", 
+         "Total_duration_of_fixations.Disruptive_Person") %>%
   mutate(
     Group = as_factor(Group),  # Convert Group column to a factor
-    Disruption_Category = case_when(
-      # Assign categories based on disruption type
+    Disruption_Category = case_when(  # Assign categories based on disruption type
       TOI %in% verbal_disruptions ~ "Verbal disruptions",
@@
     ),
-    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2)  # Convert duration to seconds
-  ) %>%
-  filter(!is.na(Disruption_Category))  # Keep only rows with valid categories
-
-# Step 2: Aggregate data by Participant and Disruption Category
-df_aoi_numb_disrup <- df_aoi_disrup %>%
-  group_by(Participant, Disruption_Category) %>%
+    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),  # Convert duration to seconds
+    Disrup_average_fixations = round(Total_duration_of_fixations.Disruptive_Person / 
+                                     `Number_of_fixations.Disruptive_Person`, 2)  # Average duration in seconds
+  ) %>%
+  filter(!is.na(Disruption_Category))  # Remove rows with NA in disruption category
+
+# Step 2: Summarize data by disruption category
+disruption_summary <- df_aoi_disrup %>%
+  group_by(Group, Participant, Disruption_Category) %>%
   summarise(
-    Total_Number_of_Fixations = sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE),
-    Total_Duration_of_Interval_Sec = sum(Duration_of_interval_sec, na.rm = TRUE),
-    .groups = "drop"  # Avoid unnecessary grouping
-  )
-
-# Step 3: Pivot the data to create a single row for each Participant
-df_summary <- df_aoi_numb_disrup %>%
-  pivot_wider(
-    names_from = Disruption_Category,
-    values_from = c(Total_Number_of_Fixations, Total_Duration_of_Interval_Sec),
-    values_fill = 0  # Replace missing values with 0
-  )
+    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2),  # Total time in seconds
+    fixation_count = round(sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE), 2),  # Total fixations
+    Disrup_fixations_per_second = round(fixation_count / total_duration_sec, 2),  # Fixation rate per second
+    Disrup_average_fixations = round(mean(Disrup_average_fixations, na.rm = TRUE), 2),  # Average disruption fixations duration
+    .groups = "drop"
+  )
+
+# Step 3: Summarize by participant
+df_aoi_disrup <- disruption_summary %>%
+  group_by(Group, Participant) %>%
+  summarise(
+    Disrup_fixations_per_second = round(mean(Disrup_fixations_per_second, na.rm = TRUE), 2),  # Mean fixation rate per participant
+    Disrup_average_fixations = round(mean(Disrup_average_fixations, na.rm = TRUE), 2),  # Mean disruption fixation duration per participant
+    .groups = "drop"
+  ) %>% 
+  select(Participant, Disrup_fixations_per_second, Disrup_average_fixations) %>%  # Select only relevant columns
+  arrange(Participant)
 
@@
   summarise(
-    Mean_disruption_appraisal = mean(disruption_appraisal, na.rm = TRUE),
-    Mean_confidence_appraisal = mean(confidence_appraisal, na.rm = TRUE),
-    Mean_prevalence_rating = mean(prevalence_rating, na.rm = TRUE)
-  )
+    Disruption_appraisal = round(mean(disruption_appraisal, na.rm = TRUE), 2),
+    Confidence_appraisal = round(mean(confidence_appraisal, na.rm = TRUE), 2),
+    Prevalence_rating = round(mean(prevalence_rating, na.rm = TRUE), 2)
+  ) %>% 
+  arrange(Participant)
 

### 2024-11-29 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper

@@
   afex,          # Performs ANOVAs, including mixed-designs and generalized linear models, with a focus on user-friendliness.
-  emmeans        # Computes estimated marginal means (or least-squares means) for post-hoc comparisons in models.
+  emmeans,       # Computes estimated marginal means (or least-squares means) for post-hoc comparisons in models.
+  corrplot       # Visualize correlation matrices in a visually appealing way.
 )
@@
   summarise(
-    N = n(), # Number of data points
+    N = n_distinct(Participant), # Count unique participants
     Mean = round(mean(fixations_per_second, na.rm = TRUE), 2), # Mean fixation rate
@@
 
-##################### PLOTS ########################
 ##################### FIRST PLOT: FIXATION RATE OVERALL ########################
@@
 
-# # Prepare annotation data for labels
-# annotation_data <- category_stats_with_tests %>%
-#   left_join(y_max_by_category, by = "Disruption_Category") %>%
-#   mutate(
-#     novice_label = paste0("italic(M) == ", M_Novice, " ~ ", "italic(SD) == ", SD_Novice),
-#     expert_label = paste0("italic(M) == ", M_Expert, " ~ ", "italic(SD) == ", SD_Expert),
-#     overall_label = paste0("italic(p) == ", p_value, " ~ ", "italic(d) == ", cohen_d)
-#   )
-
 # Create the plot
-plot_category <- disruption_summary_annotated %>%
+plot_category <- disruption_summary %>%
   ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
@@
   labs(x = "", y = "Fixations per Second") +
-  ggtitle("Fixation Rate by Disruption Category\n(AOI disruptive person)") +
+  ggtitle("Fixation Rate by Disruption Category\n(AOI Disruptive Person)") +
   scale_fill_brewer(palette = "RdBu") +
@@
   )
-# +
-#   # Annotate novice statistics
-#   geom_text(
-#     data = annotation_data,
-#     aes(x = 1, y = y_max, label = novice_label),
-#     inherit.aes = FALSE,
-#     parse = TRUE, size = 3.5, hjust = 0.5, vjust = 0
-#   ) +
-#   # Annotate expert statistics
-#   geom_text(
-#     data = annotation_data,
-#     aes(x = 2, y = y_max, label = expert_label),
-#     inherit.aes = FALSE,
-#     parse = TRUE, size = 3.5, hjust = 0.5, vjust = 0
-#   ) +
-#   # Annotate p-value and Cohen's d
-#   geom_text(
-#     data = annotation_data,
-#     aes(x = 1.5, y = y_max * 1.05, label = overall_label),
-#     inherit.aes = FALSE,
-#     parse = TRUE, size = 4, fontface = "italic", hjust = 0.5, vjust = 0
-#   )
-
-# Display the both plots
+
+# Display the plots
 plot_overall
@@
   within = "Disruption_Category", # Within-subject factor
-  data = anova_data
+  data = disruption_summary
 )
@@
 # Clean up category names in the contrast column
-  post_hoc_results$contrast <- gsub("_", " ", post_hoc_results$contrast) # Replace underscores with spaces
-  post_hoc_results$contrast <- gsub("\\.", " ", post_hoc_results$contrast) # Replace dots with spaces
+post_hoc_results$contrast <- gsub("_", " ", post_hoc_results$contrast)
+post_hoc_results$contrast <- gsub("\\.", " ", post_hoc_results$contrast)
 
@@
 
-# Normality Tests (Shapiro-Wilk)
+# 1. Normality Tests (Shapiro-Wilk)
+# The Shapiro-Wilk test is used to assess whether the data for each group (Novice and Expert) follows a normal distribution.
 normality_tests <- df_aoi_disrup %>%
-  group_by(Group) %>%
+  group_by(Group) %>%  # Group data by "Group" (Novice and Expert)
   summarise(
-    Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),
-    .groups = "drop"
-  )
-
+    Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),  # Perform Shapiro-Wilk test for normality and round the p-value
+    .groups = "drop"  # Drop the grouping after summarizing
+  )
+
+# The p-value here is extremely small (0), which indicates that both the "Novice" and "Expert" groups deviate significantly from a normal distribution.
+This suggests that the data in both groups are not normally distributed, and therefore, non-parametric tests like the Mann-Whitney U test are more appropriate for analyzing differences between these groups.
+
+# Display the Shapiro-Wilk test results in a nicely formatted table
 kable(
-  normality_tests,
-  caption = "Shapiro-Wilk Test for Normality by Group",
-  col.names = c("Group", "Shapiro-Wilk p-value"),
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Mann-Whitney U-Test and Effect Size
+  normality_tests,  # Table with Shapiro-Wilk p-values for each group
+  caption = "Shapiro-Wilk Test for Normality by Group",  # Caption for the table
+  col.names = c("Group", "Shapiro-Wilk p-value"),  # Column names
+  row.names = FALSE  # Don't show row names
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Style the table with a striped pattern
+
+# 2. Mann-Whitney U-Test and Effect Size
+# The Mann-Whitney U test is used to compare the duration of disruption between the Novice and Expert groups
+# This is a non-parametric test used when the data is not normally distributed (based on the Shapiro-Wilk test results).
 mann_whitney_test <- wilcox.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, exact = FALSE)
 
-# Effect Size Calculation for Mann-Whitney (r)
-n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))
-n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))
+# Calculate Effect Size (r) for the Mann-Whitney U test
+# Formula for r: r = |W - (n1 * n2 / 2)| / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
+n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))  # Number of Novice participants
+n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))  # Number of Expert participants
 r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
 
+# Create a data frame with the Mann-Whitney U test results, including the test statistic, p-value, and effect size
 mann_whitney_results <- data.frame(
-  "Test" = "Mann-Whitney U",
-  "W" = round(mann_whitney_test$statistic, 2),
-  "p-value" = round(mann_whitney_test$p.value, 3),
-  "Effect Size (r)" = round(r_effect, 3)
-)
-
+  "Test" = "Mann-Whitney U",  # Test name
+  "W" = round(mann_whitney_test$statistic, 2),  # Test statistic (W)
+  "p-value" = round(mann_whitney_test$p.value, 3),  # p-value from the test
+  "Effect Size (r)" = round(r_effect, 3)  # Effect size (r) rounded to 3 decimals
+)
+
+# Display the Mann-Whitney U test results in a formatted table
 kable(
   mann_whitney_results,
-  caption = "Mann-Whitney U-Test Results for Disruption Duration",
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Kruskal-Wallis Test and Pairwise Comparisons
+  caption = "Mann-Whitney U-Test Results for Disruption Duration",  # Table caption
+  row.names = FALSE  # Don't show row names
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
+
+# 3. Kruskal-Wallis Test and Pairwise Comparisons
+# The Kruskal-Wallis test is a non-parametric test to compare multiple groups (Disruption Categories) at once.
+# It tests whether the distributions of disruption duration across categories are equal.
 kruskal_test <- kruskal.test(Duration_of_interval_sec ~ Disruption_Category, data = df_aoi_disrup)
 
+# Create a data frame with the Kruskal-Wallis test results, including Chi-squared statistic, degrees of freedom, and p-value
 kruskal_results <- data.frame(
-  "Test" = "Kruskal-Wallis",
-  "Chi-squared" = round(kruskal_test$statistic, 2),
-  "df" = kruskal_test$parameter,
-  "p-value" = round(kruskal_test$p.value, 3)
-)
-
+  "Test" = "Kruskal-Wallis",  # Test name
+  "Chi-squared" = round(kruskal_test$statistic, 2),  # Chi-squared statistic from the test
+  "df" = kruskal_test$parameter,  # Degrees of freedom (df)
+  "p-value" = round(kruskal_test$p.value, 3)  # p-value from the test
+)
+
+# Display the Kruskal-Wallis test results in a formatted table
 kable(
   kruskal_results,
-  caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Pairwise Wilcoxon test with Bonferroni correction
+  caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",  # Table caption
+  row.names = FALSE  # Don't show row names
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
+
+# 4. Pairwise Wilcoxon test with Bonferroni correction
+# The pairwise Wilcoxon test is a non-parametric test used for multiple comparisons between pairs of disruption categories.
+# The p-values are adjusted for multiple comparisons using the Bonferroni correction to control for type I error.
 pairwise_wilcox <- pairwise.wilcox.test(
-  x = df_aoi_disrup$Duration_of_interval_sec,
-  g = df_aoi_disrup$Disruption_Category,
-  p.adjust.method = "bonferroni"
-)
-
-# Extract and round the p-values to 3 decimal places
+  x = df_aoi_disrup$Duration_of_interval_sec,  # The dependent variable (Duration of Interval)
+  g = df_aoi_disrup$Disruption_Category,  # The grouping factor (Disruption Category)
+  p.adjust.method = "bonferroni"  # Adjust p-values using the Bonferroni method
+)
+
+# Extract the p-values from the pairwise Wilcoxon test results and round to 3 decimal places
 pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
-  mutate(across(everything(), ~ round(., 3)))
-
-# Display the results with rounded p-values
+  mutate(across(everything(), ~ round(., 3)))  # Round p-values to 3 decimals
+
+# Display the pairwise Wilcoxon test results (with Bonferroni correction) in a formatted table
 kable(
   pairwise_results,
-  caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",
-  row.names = TRUE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+  caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",  # Table caption
+  row.names = TRUE  # Display row names
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
 
@@
 
+# Summarize the Disrup_time_fixation_sec by Participant
+df_ttff_disrup_participant_summary <- df_ttff_disrup %>%
+  group_by(Participant, Group) %>%
+  summarise(
+    Disrup_time_fixation_sec = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average time to first fixation per participant
+    .groups = "drop"
+  )
+
 ##################### DESCRIPTIVE STATISTICS ########################
@@
 # Step 2: Descriptive Statistics by Group
-ttff_disrup_table <- df_ttff_disrup %>%
+ttff_disrup_table <- df_ttff_disrup_participant_summary %>%
   group_by(Group) %>%
@@
   summarise(
-    N = n(),
+    N = n_distinct(Participant),  # Count unique participants
     Mean = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
@@
 
+# Display the table
 knitr::kable(
@@
   caption = "Descriptive Statistics for Time to First Fixation by Category and Group",
-  col.names = c("Category", "Group", "N", "Mean", "SD", "Median", "IQR", "Min", "Max"),
+  col.names = c("Category", "Group", "N (Participants)", "Mean", "SD", "Median", "IQR", "Min", "Max"), # Ensure the column names match
   row.names = FALSE
@@
 
-# Demo Data
+# Demo Data --------------------------------------------
 df_demo <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
@@
 
-# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Person
+# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Person --------------------------------------------
 df_aoi_numb_dur <- df_aoi %>%
@@
 
-# ET-Measures (AOI Students) - Exclude Disruptive Person
+# ET-Measures (AOI Students) - Exclude Disruptive Person --------------------------------------------
 df_aoi_stud <- df_aoi %>%
@@
 
-# ET-Measures (AOI Disruptive Person)
-# Number of fixations per second and Average duration of fixations
+# ET-Measures (AOI Disruptive Person) --------------------------------------------
+
+# Number of fixations per second and Average duration of fixations --------------------------------------------
 # Define the different types of disruptions and categories
@@
 
-# SRI Rating Data
+# Time to first fixation on AOI Disruptive Person --------------------------------------------
+# Step 1: Data Preparation
+df_ttff_disrup <- df_aoi %>%
+  filter(TOI %in% c(verbal_disruptions, physical_disruptions, lack_of_eagerness)) %>%
+  dplyr::select(
+    Participant,
+    TOI,
+    Time_to_first_fixation.Disruptive_Person
+  ) %>%
+  mutate(
+    Group = ifelse(Participant < 200, "Novice", "Expert"),  # Assigning Group based on Participant
+    Disruption_Category = case_when(
+      TOI %in% verbal_disruptions ~ "Verbal disruptions",
+      TOI %in% physical_disruptions ~ "Physical disruptions",
+      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
+      TRUE ~ NA_character_
+    )
+  ) %>%
+  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
+  drop_na() %>%
+  filter(
+    Time_to_first_fixation.Disruptive_Person > 0, # Exclude zero fixation times
+    Time_to_first_fixation.Disruptive_Person <= 30000 # Cut-off at 30 seconds
+  ) %>%
+  mutate(
+    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2)
+  )
+
+# Summarize the Disrup_time_fixation_sec by Participant
+df_ttff_disrup_participant_summary <- df_ttff_disrup %>%
+  group_by(Participant) %>%
+  summarise(
+    Disrup_time_fixation_sec = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average time to first fixation per participant
+    .groups = "drop"
+  ) %>% 
+  arrange(Participant)
+
+# SRI Rating Data --------------------------------------------
+# Data Import and Preprocessing ------------------------------------------
 df_sri <- read_xlsx("data/Coding_SRI.xlsx") %>%
-  filter(!ID %in% c(201, 223)) %>%
-  rename(Participant = ID) %>%
+filter(
+    !ID %in% c(201, 223),
+    !disruption_appraisal %in% c(-100, -99, -88),
+    !confidence_appraisal %in% c(-100, -99, -88),
+    !prevalence_rating %in% c(-100, -99, -88)
+  ) %>%  rename(Participant = ID) %>%
   group_by(Participant) %>%
@@
 
-# Situational Judgment Test (SJT)
+# Situational Judgment Test (SJT) --------------------------------------------
 df_sjt <- read_excel("./data/SJT.xlsx") %>%
@@
     Participant = UI06_05,
-    SJT_All = SJT_KF_gek,
-    SJT_Monitoring = SJT_AL_gek
-  )
-
-# Self-Evaluation Data
-df_self_eval <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  filter(!LI06_05 %in% c(201, 223)) %>%
-  mutate(across(starts_with("L"), as.numeric)) %>%  # Convert all "L"-prefix columns to numeric
-  transmute(
-    Participant = LI06_05,
-    Self_eval_classroom_management = rowMeans(select(., starts_with("LM")), na.rm = TRUE),
-    Self_eval_non_paraverbal_communication = rowMeans(select(., starts_with("LP")), na.rm = TRUE),
-    Self_eval_total = rowMeans(select(., starts_with("L")), na.rm = TRUE)
-  )
+    SJT_All = round(SJT_KF_gek, 2),
+    SJT_Monitoring = round(SJT_AL_gek, 2)
+  ) %>%
+  arrange(Participant)
+
+# Self-Evaluation Data --------------------------------------------
+# Data Import and Preparation
+df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
+  mutate(
+    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
+    Participant = LI06_05  # Add new column "Participant"
+  ) %>%
+  arrange(Participant) %>% 
+  select(
+    Participant, 
+    Group, 
+    LM01_01:LM01_08,  # Classroom Management and Disruption Handling combined
+    LP01_01:LP01_08   # Presence
+  ) %>%
+  rename(
+    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
+    CM_06 = LM01_06, CM_07 = LM01_07, CM_08 = LM01_08,  # Renaming combined columns
+    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
+    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
+  ) %>%
+  na.omit()  # Remove NAs
+
+# Summarize the scales to a mean per participant, rounded to 2 decimals
+df_quest_summary <- df_quest %>%
+  mutate(
+    # Calculate mean for Classroom Management (CM)
+    Self_Eval_CM = round(rowMeans(select(., starts_with("CM")), na.rm = TRUE), 2),
+    # Calculate mean for Presence (P), excluding the Participant column
+    Self_Eval_Presence = round(rowMeans(select(., starts_with("P"))[, -1], na.rm = TRUE), 2) # Exclude Participant column
+  ) %>%
+  select(Participant, Self_Eval_CM, Self_Eval_Presence) %>% # Keep Participant and means for each scale
+  arrange(Participant)
 
@@
 
-# Combine all prepared datasets
 df_list <- list(
@@
   df_aoi_disrup,
+  df_ttff_disrup_participant_summary,
   df_sri,
   df_sjt,
-  df_self_eval
-)
-
-df_merge <- reduce(df_list, full_join, by = "Participant") %>%
+  df_quest_summary
+)
+
+df_merge <- reduce(df_list, full_join, by = "Participant")
+
+# 3. Correlation Analysis ---------------------------------------------
+
+# Select relevant variables for correlation analysis
+df_correlation <- df_merge %>%
   select(
-    GRI_mtu, SJT_All, Self_eval_total, Mean_disruption_appraisal, Mean_confidence_appraisal
-  )
-
-# 3. Correlation Analysis -----------------------------------------------
-
-# Compute Correlation Matrix
-cor_tab <- cor(df_merge, method = "pearson", use = "complete.obs") %>% round(2)
-
-# Create APA-Style Correlation Table
-apa.cor.table(
-  cor_tab,
-  filename = "correlation_table.docx"
-)
-
-# p-values for specific correlations
-pval_gri_sjt <- cor.test(df_merge$GRI_mtu, df_merge$SJT_All)$p.value
-pval_gri_self_eval <- cor.test(df_merge$GRI_mtu, df_merge$Self_eval_total)$p.value
-
-# Print Correlation Results
-print(cor_tab)
-cat("P-value (GRI x SJT):", pval_gri_sjt, "\n")
-cat("P-value (GRI x Self-evaluation):", pval_gri_self_eval, "\n")
-
+    `Teaching Experience`, 
+    Number_fixation_min_mtu, 
+    Average_duration_mtu, 
+    GRI_mtu, 
+    Stud_number_fixation_min, 
+    Average_duration_stud, 
+    Disrup_fixations_per_second, 
+    Disrup_average_fixations, 
+    Disrup_time_fixation_sec, 
+    Disruption_appraisal, 
+    Confidence_appraisal, 
+    SJT_All, 
+    SJT_Monitoring, 
+    Self_Eval_CM, 
+    Self_Eval_Presence
+  )
+
+# Compute the correlation matrix
+cor_matrix <- cor(df_correlation, use = "complete.obs")
+
+# Visualize the correlation matrix
+corrplot(cor_matrix, method = "circle", type = "lower", order = "hclust", tl.col = "black", tl.srt = 45)
+
+# 4. Correlation Analysis with Experts ---------------------------------------------
+
+# Filter data for Experts (Participants with ID > 200)
+df_experts <- df_merge %>%
+  filter(Participant > 200)  # Only include Experts (ID > 200)
+
+# Select relevant variables for correlation analysis with Teaching Experience
+df_correlation_experts <- df_experts %>%
+  select(
+    `Teaching Experience`, 
+    Number_fixation_min_mtu, 
+    Average_duration_mtu, 
+    GRI_mtu, 
+    Stud_number_fixation_min, 
+    Average_duration_stud, 
+    Disrup_fixations_per_second, 
+    Disrup_average_fixations, 
+    Disrup_time_fixation_sec, 
+    Disruption_appraisal, 
+    Confidence_appraisal, 
+    SJT_All, 
+    SJT_Monitoring, 
+    Self_Eval_CM, 
+    Self_Eval_Presence
+  )
+
+# Check the column types to make sure they are numeric
+sapply(df_correlation_experts, class)
+
+# Compute the correlation matrix
+cor_matrix_experts <- cor(df_correlation_experts, use = "complete.obs")
+
+# Visualize the correlation matrix
+corrplot(cor_matrix_experts, method = "circle", type = "lower", order = "hclust", tl.col = "black", tl.srt = 45)
+
+# 5. Correlation Analysis with Novices ---------------------------------------------
+
+# Filter data for Novices (Participants with ID < 200)
+df_novices <- df_merge %>%
+  filter(Participant < 200)  # Only include Novices (ID < 200)
+
+# Select relevant variables for correlation analysis without Teaching Experience
+df_correlation_novices <- df_novices %>%
+  select(
+    Number_fixation_min_mtu, 
+    Average_duration_mtu, 
+    GRI_mtu, 
+    Stud_number_fixation_min, 
+    Average_duration_stud, 
+    Disrup_fixations_per_second, 
+    Disrup_average_fixations, 
+    Disrup_time_fixation_sec, 
+    Disruption_appraisal, 
+    Confidence_appraisal, 
+    SJT_All, 
+    SJT_Monitoring, 
+    Self_Eval_CM, 
+    Self_Eval_Presence
+  )
+
+# Ensure all selected columns are numeric and handle non-numeric entries
+df_correlation_novices_clean <- df_correlation_novices %>%
+  mutate(across(everything(), as.numeric))  # Convert all columns to numeric
+
+# Remove rows with any NA or problematic values
+df_correlation_novices_clean <- df_correlation_novices_clean %>%
+  drop_na()  # Remove rows with NA values
+
+# Check if all columns are numeric after conversion
+sapply(df_correlation_novices_clean, class)
+
+# Compute the correlation matrix for Novices
+cor_matrix_novices <- cor(df_correlation_novices_clean, use = "complete.obs")
+
+# Visualize the correlation matrix for Novices
+corrplot(cor_matrix_novices, method = "circle", type = "lower", order = "hclust", tl.col = "black", tl.srt = 45)
 ```

### 2024-12-04 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
xxxxx papperrrr

@@
   "df" = t_test_letter$parameter,
-  "p-value" = format.pval(t_test_letter$p.value, digits = 3, eps = .001),
+  "p-value" = format.pval(t_test_letter$p.value, digits = 2, eps = .05),
   "Mean Difference" = round(t_test_letter$estimate[1] - t_test_letter$estimate[2], 2),
@@
           "df" = t_test_result$parameter,
-          "p-value" = format.pval(t_test_result$p.value, digits = 3, eps = .001),
+          "p-value" = format.pval(t_test_result$p.value, digits = 2, eps = .05),
           "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
@@
 )
-p_value_mtu <- round(t_test_mtu$p.value, 3)
+p_value_mtu <- round(t_test_mtu$p.value, 2)
 
@@
   "df" = t_test_mtu$parameter,
-  "p-value" = format.pval(t_test_mtu$p.value, digits = 3, eps = .001),
+  "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
   "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
@@
 sd_novice <- summary_stats %>% filter(Group == "Novice") %>% pull(SD)
-p_value <- format.pval(t_test_stud$p.value, digits = 3, eps = .001)
+p_value <- format.pval(t_test_stud$p.value, digits = 2, eps = .05)
 cohen_d <- round(d_number_stud$estimate, 2)
@@
   "df" = t_test_stud$parameter,
-  "p-value" = format.pval(t_test_stud$p.value, digits = 3, eps = .001),
+  "p-value" = format.pval(t_test_stud$p.value, digits = 2, eps = .05),
   "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2),
@@
 t_test <- t.test(mean_fixations_per_second ~ Group, data = individual_summary, var.equal = TRUE)
-p_value <- round(t_test$p.value, 3)
+p_value <- round(t_test$p.value, 2)
 cohen_d <- round(cohen.d(mean_fixations_per_second ~ Group, data = individual_summary)$estimate, 2)
@@
 
-# Post-hoc comparisons for Disruption_Category
+##################### POST-HOC TESTS ########################
+
+# Perform post-hoc pairwise comparisons for Disruption_Category (within-subject factor)
 post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)
 
-# Extract pairwise contrasts
-post_hoc_results <- as.data.frame(post_hoc_disruption$contrasts)
-
-# Clean up category names in the contrast column
-post_hoc_results$contrast <- gsub("_", " ", post_hoc_results$contrast)
-post_hoc_results$contrast <- gsub("\\.", " ", post_hoc_results$contrast)
-
-# Calculate Cohen's d for each pairwise comparison using pooled SD from emmeans
-post_hoc_results <- post_hoc_results %>%
+# Extract post-hoc pairwise contrasts for Disruption_Category
+post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
   mutate(
-    pooled_sd = sqrt((SE^2 * 2)), # Approximation for pooled SD from SE
-    d = round(estimate / pooled_sd, 2), # Calculate Cohen's d
-    p.value = ifelse(
-      p.value < 0.05, "< .05", round(p.value, 3)
-    ),
+    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
     t = round(t.ratio, 2),
-    df = round(df, 2),
-    Estimate = round(estimate, 2),
-    SE = round(SE, 2)
-  ) %>%
-  select(contrast, Estimate, SE, df, t, p.value, d) # Include Cohen's d
-
-# Display APA-styled post-hoc table
-kable(
-  post_hoc_results,
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))
+  )
+
+##################### COHEN'S D CALCULATION ########################
+
+# Define the disruption categories
+categories <- c("Lack of eagerness to learn", "Physical disruptions", "Verbal disruptions")
+
+# Initialize an empty list to store the Cohen's d values
+cohen_d_values <- vector("list", length = nrow(post_hoc_results_disruption))
+
+# Loop over the post-hoc results to calculate Cohen's d for each comparison
+for (i in 1:nrow(post_hoc_results_disruption)) {
+  # Extract the two categories being compared
+  group1 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][1]
+  group2 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][2]
+
+  # Get the data for the two groups being compared using fixations_per_second
+  group1_data <- disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == group1]
+  group2_data <- disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == group2]
+
+  # Calculate the means and standard deviations for each group
+  mean1 <- mean(group1_data, na.rm = TRUE)
+  mean2 <- mean(group2_data, na.rm = TRUE)
+
+  sd1 <- sd(group1_data, na.rm = TRUE)
+  sd2 <- sd(group2_data, na.rm = TRUE)
+
+  # Calculate the pooled standard deviation
+  pooled_sd <- sqrt(((length(group1_data) - 1) * sd1^2 + (length(group2_data) - 1) * sd2^2) / (length(group1_data) + length(group2_data) - 2))
+
+  # Calculate Cohen's d using the formula (mean difference / pooled SD)
+  d_value <- (mean1 - mean2) / pooled_sd
+
+  # Store the absolute value of Cohen's d
+  cohen_d_values[[i]] <- abs(round(d_value, 2))  # Take the absolute value of Cohen's d
+}
+
+# Add the Cohen's d values to the post-hoc results
+post_hoc_results_disruption$Cohen_d <- unlist(cohen_d_values)
+
+##################### TABLE FOR DISRUPTION CATEGORY ########################
+
+# Ensure the number of column names matches the number of columns in the data frame
+post_hoc_results_disruption <- post_hoc_results_disruption %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+
+# Displaying the table
+knitr::kable(
+  post_hoc_results_disruption,
   caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Including Effect Sizes)",
@@
 ) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# # effect size for category differences
+# d_fix_disrup <- CohenD(
+#   x = disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == "Lack of eagerness to learn"],
+#   y = disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# round(d_fix_disrup, 2)
 
@@
   geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
-  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) +
+  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) +  # Use fixed scale for all facets
   labs(x = "Group", y = "Disruption Duration (seconds)") +
   theme_cowplot() +
-  ylim(0, 30) + 
   scale_fill_brewer(palette = "RdBu") +
@@
 
+# Display the plot
 plot_duration_category
@@
 
-# 1. Normality Tests (Shapiro-Wilk)
-# The Shapiro-Wilk test is used to assess whether the data for each group (Novice and Expert) follows a normal distribution.
-normality_tests <- df_aoi_disrup %>%
-  group_by(Group) %>%  # Group data by "Group" (Novice and Expert)
-  summarise(
-    Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),  # Perform Shapiro-Wilk test for normality and round the p-value
-    .groups = "drop"  # Drop the grouping after summarizing
-  )
-
-# The p-value here is extremely small (0), which indicates that both the "Novice" and "Expert" groups deviate significantly from a normal distribution.
+##################### REPEATED MEASURES ANOVA ########################
+
+# Perform the repeated-measures ANOVA with `Duration_of_interval_sec` as the dependent variable
+anova_afex_duration <- afex::aov_ez(
+  id = "Participant",  # Random effect
+  dv = "Duration_of_interval_sec",  # Dependent variable: disruption duration in seconds
+  between = "Group",  # Between-subject factor: Group (Novice vs Expert)
+  within = "Disruption_Category",  # Within-subject factor: Disruption Categories
+  data = df_aoi_disrup
+)
+
+# Extract the ANOVA table
+anova_results_duration <- as.data.frame(anova_afex_duration$anova_table)
+
+# Recalculate generalized eta squared (η²) for effect size
+eta_squared_results_duration <- effectsize::eta_squared(anova_afex_duration, partial = FALSE)
+
+# Combine recalculated eta squared with the ANOVA table
+anova_table_apa_duration <- anova_results_duration %>%
+  rownames_to_column(var = "Effect") %>%  # Move row names to a column
+  left_join(
+    as.data.frame(eta_squared_results_duration), 
+    by = c("Effect" = "Parameter")  # Match the correct columns
+  ) %>%
+  mutate(
+    `F` = round(`F`, 2),  # Round F-values
+    `η²` = round(Eta2, 3),  # Round generalized eta squared
+    `p-value` = ifelse(
+      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 3)  # Format p-values
+    )
+  ) %>%
+  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`)  # Order columns, place η² last
+
+# Display the ANOVA table
+kable(
+  anova_table_apa_duration,
+  caption = "Repeated-Measures ANOVA Results for Disruption Duration (Including Effect Sizes)",
+  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
+  digits = 2
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### POST-HOC TESTS Disruption_Category (main effect) ########################
+
+# Perform post-hoc pairwise comparisons for Disruption_Category (main effect)
+post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)
+
+# Extract post-hoc pairwise contrasts for Disruption_Category (main effect)
+post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))
+  )
+
+##################### COHEN'S D CALCULATION ########################
+
+# Initialize empty lists to store Cohen's d values for both post-hoc tests
+cohen_d_values_disruption <- vector("list", length = nrow(post_hoc_results_disruption))
+
+# Loop over the post-hoc results for Disruption_Category to calculate Cohen's d for each comparison (main effect)
+for (i in 1:nrow(post_hoc_results_disruption)) {
+  # Extract the two categories being compared
+  group1 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][1]
+  group2 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][2]
+
+  # Get the data for the two groups being compared using Duration_of_interval_sec
+  group1_data <- df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Disruption_Category == group1]
+  group2_data <- df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Disruption_Category == group2]
+
+  # Calculate the means and standard deviations for each group
+  mean1 <- mean(group1_data, na.rm = TRUE)
+  mean2 <- mean(group2_data, na.rm = TRUE)
+
+  sd1 <- sd(group1_data, na.rm = TRUE)
+  sd2 <- sd(group2_data, na.rm = TRUE)
+
+  # Calculate the pooled standard deviation
+  pooled_sd <- sqrt(((length(group1_data) - 1) * sd1^2 + (length(group2_data) - 1) * sd2^2) / (length(group1_data) + length(group2_data) - 2))
+
+  # Calculate Cohen's d using the formula (mean difference / pooled SD)
+  d_value <- (mean1 - mean2) / pooled_sd
+
+  # Store the absolute value of Cohen's d
+  cohen_d_values_disruption[[i]] <- abs(round(d_value, 2))  # Take the absolute value of Cohen's d
+}
+
+# Add the Cohen's d values to the post-hoc results
+post_hoc_results_disruption$Cohen_d <- unlist(cohen_d_values_disruption)
+
+##################### TABLE FOR DISRUPTION CATEGORY ########################
+
+# Ensure the number of column names matches the number of columns in the data frame
+post_hoc_results_disruption <- post_hoc_results_disruption %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+
+# Displaying the post-hoc results for Disruption Category (main effect)
+knitr::kable(
+  post_hoc_results_disruption,
+  caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Main Effect)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
+kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+#################### POST-HOC TESTS interaction effect (Group:Disruption_Category) ########################
+
+# Calculate post-hoc pairwise comparisons for the interaction effect (Group:Disruption_Category)
+post_hoc_interaction <- emmeans(anova_afex, pairwise ~ Group * Disruption_Category)
+
+# Extract the post-hoc contrasts for the interaction
+post_hoc_results_interaction <- as.data.frame(post_hoc_interaction$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))  # Round p-values to 2 decimals
+  )
+
+##################### COHEN'S D CALCULATION ########################
+
+# 1. Novice Lack of eagerness to learn vs Expert Lack of eagerness to learn
+d_LackOfEagerness_Novice_vs_Expert <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  na.rm = TRUE
+)
+
+# 2. Novice Lack of eagerness to learn vs Novice Physical disruptions
+d_LackOfEagerness_vs_Physical_Novice <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+# 3. Novice Lack of eagerness to learn vs Expert Physical disruptions
+d_LackOfEagerness_vs_Physical_Expert <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+# 4. Novice Lack of eagerness to learn vs Novice Verbal disruptions
+d_LackOfEagerness_vs_Verbal_Novice <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+# 5. Novice Lack of eagerness to learn vs Expert Verbal disruptions
+d_LackOfEagerness_vs_Verbal_Expert <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+# 6. Expert Lack of eagerness to learn vs Novice Physical disruptions
+d_Expert_LackOfEagerness_vs_Physical_Novice <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+# 7. Expert Lack of eagerness to learn vs Expert Physical disruptions
+d_Expert_LackOfEagerness_vs_Physical_Expert <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+# 8. Expert Lack of eagerness to learn vs Novice Verbal disruptions
+d_Expert_LackOfEagerness_vs_Verbal_Novice <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+# 9. Expert Lack of eagerness to learn vs Expert Verbal disruptions
+d_Expert_LackOfEagerness_vs_Verbal_Expert <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+# 10. Novice Physical disruptions vs Expert Physical disruptions
+d_Physical_Novice_vs_Expert <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+# 11. Novice Physical disruptions vs Novice Verbal disruptions
+d_Physical_Novice_vs_Verbal_Novice <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+# 12. Novice Physical disruptions vs Expert Verbal disruptions
+d_Physical_Novice_vs_Verbal_Expert <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+# 13. Expert Physical disruptions vs Novice Verbal disruptions
+d_Physical_Expert_vs_Verbal_Novice <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+# 14. Expert Physical disruptions vs Expert Verbal disruptions
+d_Physical_Expert_vs_Verbal_Expert <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+# 15. Novice Verbal disruptions vs Expert Verbal disruptions
+d_Verbal_Novice_vs_Expert <- CohenD(
+  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+##################### CREATE A NAMED VECTOR FOR COHEN'S D ########################
+
+# Create a named vector with the correct Cohen's d values
+cohen_d_values_interaction <- c(
+  "Novice Lack of eagerness to learn - Expert Lack of eagerness to learn" = round(d_LackOfEagerness_Novice_vs_Expert, 2),
+  "Novice Lack of eagerness to learn - Novice Physical disruptions" = round(d_LackOfEagerness_vs_Physical_Novice, 2),
+  "Novice Lack of eagerness to learn - Expert Physical disruptions" = round(d_LackOfEagerness_vs_Physical_Expert, 2),
+  "Novice Lack of eagerness to learn - Novice Verbal disruptions" = round(d_LackOfEagerness_vs_Verbal_Novice, 2),
+  "Novice Lack of eagerness to learn - Expert Verbal disruptions" = round(d_LackOfEagerness_vs_Verbal_Expert, 2),
+  "Expert Lack of eagerness to learn - Novice Physical disruptions" = round(d_Expert_LackOfEagerness_vs_Physical_Novice, 2),
+  "Expert Lack of eagerness to learn - Expert Physical disruptions" = round(d_Expert_LackOfEagerness_vs_Physical_Expert, 2),
+  "Expert Lack of eagerness to learn - Novice Verbal disruptions" = round(d_Expert_LackOfEagerness_vs_Verbal_Novice, 2),
+  "Expert Lack of eagerness to learn - Expert Verbal disruptions" = round(d_Expert_LackOfEagerness_vs_Verbal_Expert, 2),
+  "Novice Physical disruptions - Expert Physical disruptions" = round(d_Physical_Novice_vs_Expert, 2),
+  "Novice Physical disruptions - Novice Verbal disruptions" = round(d_Physical_Novice_vs_Verbal_Novice, 2),
+  "Novice Physical disruptions - Expert Verbal disruptions" = round(d_Physical_Novice_vs_Verbal_Expert, 2),
+  "Expert Physical disruptions - Novice Verbal disruptions" = round(d_Physical_Expert_vs_Verbal_Novice, 2),
+  "Expert Physical disruptions - Expert Verbal disruptions" = round(d_Physical_Expert_vs_Verbal_Expert, 2),
+  "Novice Verbal disruptions - Expert Verbal disruptions" = round(d_Verbal_Novice_vs_Expert, 2)
+)
+
+##################### ADD COHEN'S D VALUES TO THE POST-HOC RESULTS ########################
+
+# Add Cohen's d values to the post-hoc results for each comparison
+post_hoc_results_interaction$Cohen_d <- cohen_d_values_interaction[post_hoc_results_interaction$Comparison]
+
+##################### TABLE FOR INTERACTION EFFECT ########################
+
+# Ensure the number of column names matches the number of columns in the data frame
+post_hoc_results_interaction <- post_hoc_results_interaction %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+
+# Display the post-hoc results for Group x Disruption_Category interaction with Cohen's d
+knitr::kable(
+  post_hoc_results_interaction,
+  caption = "Post-Hoc Pairwise Comparisons for Group x Disruption Category Interaction (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# 
+# # 1. Normality Tests (Shapiro-Wilk)
+# # The Shapiro-Wilk test is used to assess whether the data for each group (Novice and Expert) follows a normal distribution.
+# normality_tests <- df_aoi_disrup %>%
+#   group_by(Group) %>%  # Group data by "Group" (Novice and Expert)
+#   summarise(
+#     Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),  # Perform Shapiro-Wilk test for normality and round the p-value
+#     .groups = "drop"  # Drop the grouping after summarizing
+#   )
+# 
+# # The p-value here is extremely small (0), which indicates that both the "Novice" and "Expert" groups deviate significantly from a normal distribution.
 This suggests that the data in both groups are not normally distributed, and therefore, non-parametric tests like the Mann-Whitney U test are more appropriate for analyzing differences between these groups.
-
-# Display the Shapiro-Wilk test results in a nicely formatted table
-kable(
-  normality_tests,  # Table with Shapiro-Wilk p-values for each group
-  caption = "Shapiro-Wilk Test for Normality by Group",  # Caption for the table
-  col.names = c("Group", "Shapiro-Wilk p-value"),  # Column names
-  row.names = FALSE  # Don't show row names
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Style the table with a striped pattern
-
-# 2. Mann-Whitney U-Test and Effect Size
-# The Mann-Whitney U test is used to compare the duration of disruption between the Novice and Expert groups
-# This is a non-parametric test used when the data is not normally distributed (based on the Shapiro-Wilk test results).
-mann_whitney_test <- wilcox.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, exact = FALSE)
-
-# Calculate Effect Size (r) for the Mann-Whitney U test
-# Formula for r: r = |W - (n1 * n2 / 2)| / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
-n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))  # Number of Novice participants
-n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))  # Number of Expert participants
-r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
-
-# Create a data frame with the Mann-Whitney U test results, including the test statistic, p-value, and effect size
-mann_whitney_results <- data.frame(
-  "Test" = "Mann-Whitney U",  # Test name
-  "W" = round(mann_whitney_test$statistic, 2),  # Test statistic (W)
-  "p-value" = round(mann_whitney_test$p.value, 3),  # p-value from the test
-  "Effect Size (r)" = round(r_effect, 3)  # Effect size (r) rounded to 3 decimals
-)
-
-# Display the Mann-Whitney U test results in a formatted table
-kable(
-  mann_whitney_results,
-  caption = "Mann-Whitney U-Test Results for Disruption Duration",  # Table caption
-  row.names = FALSE  # Don't show row names
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
-
-# 3. Kruskal-Wallis Test and Pairwise Comparisons
-# The Kruskal-Wallis test is a non-parametric test to compare multiple groups (Disruption Categories) at once.
-# It tests whether the distributions of disruption duration across categories are equal.
-kruskal_test <- kruskal.test(Duration_of_interval_sec ~ Disruption_Category, data = df_aoi_disrup)
-
-# Create a data frame with the Kruskal-Wallis test results, including Chi-squared statistic, degrees of freedom, and p-value
-kruskal_results <- data.frame(
-  "Test" = "Kruskal-Wallis",  # Test name
-  "Chi-squared" = round(kruskal_test$statistic, 2),  # Chi-squared statistic from the test
-  "df" = kruskal_test$parameter,  # Degrees of freedom (df)
-  "p-value" = round(kruskal_test$p.value, 3)  # p-value from the test
-)
-
-# Display the Kruskal-Wallis test results in a formatted table
-kable(
-  kruskal_results,
-  caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",  # Table caption
-  row.names = FALSE  # Don't show row names
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
-
-# 4. Pairwise Wilcoxon test with Bonferroni correction
-# The pairwise Wilcoxon test is a non-parametric test used for multiple comparisons between pairs of disruption categories.
-# The p-values are adjusted for multiple comparisons using the Bonferroni correction to control for type I error.
-pairwise_wilcox <- pairwise.wilcox.test(
-  x = df_aoi_disrup$Duration_of_interval_sec,  # The dependent variable (Duration of Interval)
-  g = df_aoi_disrup$Disruption_Category,  # The grouping factor (Disruption Category)
-  p.adjust.method = "bonferroni"  # Adjust p-values using the Bonferroni method
-)
-
-# Extract the p-values from the pairwise Wilcoxon test results and round to 3 decimal places
-pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
-  mutate(across(everything(), ~ round(., 3)))  # Round p-values to 3 decimals
-
-# Display the pairwise Wilcoxon test results (with Bonferroni correction) in a formatted table
-kable(
-  pairwise_results,
-  caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",  # Table caption
-  row.names = TRUE  # Display row names
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
+# 
+# # Display the Shapiro-Wilk test results in a nicely formatted table
+# kable(
+#   normality_tests,  # Table with Shapiro-Wilk p-values for each group
+#   caption = "Shapiro-Wilk Test for Normality by Group",  # Caption for the table
+#   col.names = c("Group", "Shapiro-Wilk p-value"),  # Column names
+#   row.names = FALSE  # Don't show row names
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Style the table with a striped pattern
+# 
+# # 2. Mann-Whitney U-Test and Effect Size
+# # The Mann-Whitney U test is used to compare the duration of disruption between the Novice and Expert groups
+# # This is a non-parametric test used when the data is not normally distributed (based on the Shapiro-Wilk test results).
+# mann_whitney_test <- wilcox.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, exact = FALSE)
+# 
+# # Calculate Effect Size (r) for the Mann-Whitney U test
+# # Formula for r: r = |W - (n1 * n2 / 2)| / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
+# n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))  # Number of Novice participants
+# n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))  # Number of Expert participants
+# r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
+# 
+# # Create a data frame with the Mann-Whitney U test results, including the test statistic, p-value, and effect size
+# mann_whitney_results <- data.frame(
+#   "Test" = "Mann-Whitney U",  # Test name
+#   "W" = round(mann_whitney_test$statistic, 2),  # Test statistic (W)
+#   "p-value" = round(mann_whitney_test$p.value, 3),  # p-value from the test
+#   "Effect Size (r)" = round(r_effect, 3)  # Effect size (r) rounded to 3 decimals
+# )
+# 
+# # Explanation: The Mann-Whitney U test is a non-parametric test used to compare differences between two independent groups (in this case, Novices and Experts).
+It is used because the data is not normally distributed, as indicated by the Shapiro-Wilk test.
+# # p-value: A p-value of 0.879 is much larger than the common significance threshold of 0.05.
+This means there is no significant difference between the Novice and Expert groups in terms of the disruption duration.
+# # Effect size (r): The effect size value of 0.152 suggests a small effect.
+This confirms that even though the test was not significant, there was still a small effect observed, but it's not large enough to be practically meaningful.
+# 
+# 
+# # Display the Mann-Whitney U test results in a formatted table
+# kable(
+#   mann_whitney_results,
+#   caption = "Mann-Whitney U-Test Results for Disruption Duration",  # Table caption
+#   row.names = FALSE  # Don't show row names
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
+# 
+# # 3. Kruskal-Wallis Test and Pairwise Comparisons
+# # The Kruskal-Wallis test is a non-parametric test to compare multiple groups (Disruption Categories) at once.
+# # It tests whether the distributions of disruption duration across categories are equal.
+# kruskal_test <- kruskal.test(Duration_of_interval_sec ~ Disruption_Category, data = df_aoi_disrup)
+# 
+# # Create a data frame with the Kruskal-Wallis test results, including Chi-squared statistic, degrees of freedom, and p-value
+# kruskal_results <- data.frame(
+#   "Test" = "Kruskal-Wallis",  # Test name
+#   "Chi-squared" = round(kruskal_test$statistic, 2),  # Chi-squared statistic from the test
+#   "df" = kruskal_test$parameter,  # Degrees of freedom (df)
+#   "p-value" = round(kruskal_test$p.value, 3)  # p-value from the test
+# )
+# 
+# # Explanation: The Kruskal-Wallis test is a non-parametric test used to compare more than two independent groups (in this case, different types of disruptions).
+It is used when the assumption of normality is not met (as in the Shapiro-Wilk test).
+# # p-value: A p-value of 0 indicates a highly significant difference between the disruption categories (i.e., "Verbal disruptions", "Physical disruptions", and "Lack of eagerness to learn").
+This suggests that there is a significant difference in disruption duration among these categories.
+# # Chi-squared: The large value of 145.07 supports this conclusion, indicating a strong effect in terms of the differences between disruption categories.
+# 
+# # Display the Kruskal-Wallis test results in a formatted table
+# kable(
+#   kruskal_results,
+#   caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",  # Table caption
+#   row.names = FALSE  # Don't show row names
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
+# 
+# # 4. Pairwise Wilcoxon test with Bonferroni correction
+# # The pairwise Wilcoxon test is a non-parametric test used for multiple comparisons between pairs of disruption categories.
+# # The p-values are adjusted for multiple comparisons using the Bonferroni correction to control for type I error.
+# pairwise_wilcox <- pairwise.wilcox.test(
+#   x = df_aoi_disrup$Duration_of_interval_sec,  # The dependent variable (Duration of Interval)
+#   g = df_aoi_disrup$Disruption_Category,  # The grouping factor (Disruption Category)
+#   p.adjust.method = "bonferroni"  # Adjust p-values using the Bonferroni method
+# )
+# 
+# # Extract the p-values from the pairwise Wilcoxon test results and round to 3 decimal places
+# pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
+#   mutate(across(everything(), ~ round(., 3)))  # Round p-values to 3 decimals
+# 
+# # Display the pairwise Wilcoxon test results (with Bonferroni correction) in a formatted table
+# kable(
+#   pairwise_results,
+#   caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",  # Table caption
+#   row.names = TRUE  # Display row names
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
 
@@
 )
-p_value_fixation <- round(t_test_fixation$p.value, 3)
+p_value_fixation <- round(t_test_fixation$p.value, 2)
 
 # 5. Calculate Cohen's d for effect size using formula syntax
-library(effsize)
 cohen_d_fixation <- round(cohen.d(Average_duration_fixation ~ Group, data = df_aoi_sum)$estimate, 2)
@@
   "df" = t_test_fixation$parameter,
-  "p-value" = round(t_test_fixation$p.value, 3),
+  "p-value" = round(t_test_fixation$p.value, 2),
   "Mean Difference" = round(t_test_fixation$estimate[1] - t_test_fixation$estimate[2], 2),
@@
 # Extract p-value
-p_value_stud <- round(t_test_stud$p.value, 3)
+p_value_stud <- round(t_test_stud$p.value, 2)
 
@@
   "df" = t_test_stud$parameter,
-  "p-value" = round(t_test_stud$p.value, 3),
+  "p-value" = round(t_test_stud$p.value, 2),
   "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2),
@@
 t_test <- t.test(mean_duration ~ Group, data = individual_summary, var.equal = TRUE)
-p_value <- round(t_test$p.value, 3)
+p_value <- round(t_test$p.value, 2)
 cohen_d <- round(effsize::cohen.d(mean_duration ~ Group, data = individual_summary)$estimate, 2)
@@
   labs(x = "", y = "Mean Duration (ms) per Participant") +
-  ggtitle("Overall Average Duration per Participant\n(AOI Disruptive Person)") +
+  ggtitle("Average Duration per Participant\n(AOI Disruptive Person)") +
   scale_fill_brewer(palette = "RdBu") +
@@
 plot_category <- disruption_summary %>%
-  ggplot(aes(x = Group, y = mean_duration_ms, fill = Group)) +
+  ggplot(aes(x = Group, y = mean_duration_ms, fill = Group)) +  # Ensure using correct column name here
   geom_boxplot(outlier.shape = NA, width = 0.5) +
@@
 
-##################### ANOVA AND POST-HOC TESTS ########################
-
-# Perform the repeated-measures ANOVA
+##################### REPEATED MEASURES ANOVA ########################
+
+# Perform the repeated-measures ANOVA with `mean_duration_ms` as the dependent variable
 anova_afex <- afex::aov_ez(
@@
 
-##################### POST-HOC TESTS ########################
-
-# Perform post-hoc pairwise comparisons for Group
-post_hoc_group <- emmeans::emmeans(anova_afex, pairwise ~ Group)
-
-# Extract post-hoc pairwise contrasts for Group
+##################### POST-HOC TESTS Group (between-subject factor) ########################
+
+# Perform post-hoc pairwise comparisons for Group (between-subject factor)
+post_hoc_group <- emmeans(anova_afex, pairwise ~ Group)
+
+# Calculate Cohen's d manually
+# Extract group means, standard deviations, and sample sizes from the data
+group_stats <- individual_summary %>%
+  group_by(Group) %>%
+  summarise(
+    Mean = mean(mean_duration, na.rm = TRUE),
+    SD = sd(mean_duration, na.rm = TRUE),
+    N = n(),
+    .groups = "drop"
+  )
+
+# Calculate pooled standard deviation for Cohen's d
+pooled_sd <- sqrt(
+  ((group_stats$N[1] - 1) * group_stats$SD[1]^2 + (group_stats$N[2] - 1) * group_stats$SD[2]^2) /
+    (sum(group_stats$N) - 2)
+)
+
+# Calculate Cohen's d
+cohen_d <- round((group_stats$Mean[1] - group_stats$Mean[2]) / pooled_sd, 2)
+
+# Add Cohen's d to the post-hoc results table
 post_hoc_results_group <- as.data.frame(post_hoc_group$contrasts) %>%
@@
     t = round(t.ratio, 2),
-    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 3)),
-    Cohen_d = round(estimate / sqrt(SE^2 * 2), 2) # Approximate Cohen's d
-  ) %>%
-  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d) # Keep relevant columns
-
-# Perform post-hoc pairwise comparisons for Disruption_Category
-post_hoc_disruption <- emmeans::emmeans(anova_afex, pairwise ~ Disruption_Category)
+    df = round(df, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2)),
+    `Cohen's d` = cohen_d
+  ) %>%
+  select(Comparison, Estimate, SE, df, t, p.value, `Cohen's d`)
+
+##################### TABLE FOR GROUP ########################
+
+# Display the post-hoc test results for Group
+knitr::kable(
+  post_hoc_results_group,
+  caption = "Post-Hoc Pairwise Comparisons for Group (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### POST-HOC TESTS Disruption_Category (within-subject factor) ########################
+
+# Perform post-hoc pairwise comparisons for Disruption_Category (within-subject factor)
+post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)
 
@@
     t = round(t.ratio, 2),
-    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 3)),
-    Cohen_d = round(estimate / sqrt(SE^2 * 2), 2) # Approximate Cohen's d
-  ) %>%
-  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d) # Keep relevant columns
-
-##################### TABLE FOR GROUP ########################
-
-# Display the post-hoc test results for Group
-knitr::kable(
-  post_hoc_results_group,
-  caption = "Post-Hoc Pairwise Comparisons for Group (Including Effect Sizes)",
-  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
-  digits = 2
-) %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))
+  )
+
+##################### COHEN'S D CALCULATION ########################
+
+# Define the disruption categories
+categories <- c("Lack of eagerness to learn", "Physical disruptions", "Verbal disruptions")
+
+# Initialize an empty list to store the Cohen's d values
+cohen_d_values <- vector("list", length = nrow(post_hoc_results_disruption))
+
+# Loop over the post-hoc results to calculate Cohen's d for each comparison
+for (i in 1:nrow(post_hoc_results_disruption)) {
+  # Extract the two categories being compared
+  group1 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][1]
+  group2 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][2]
+
+  # Calculate Cohen's d for the pair of categories
+  d_value <- CohenD(
+    x = disruption_summary$mean_duration_ms[disruption_summary$Disruption_Category == group1],
+    y = disruption_summary$mean_duration_ms[disruption_summary$Disruption_Category == group2],
+    na.rm = TRUE
+  )
+
+  # Store the absolute value of Cohen's d
+  cohen_d_values[[i]] <- abs(round(d_value, 2))  # Take the absolute value of Cohen's d
+}
+
+# Add the Cohen's d values to the post-hoc results
+post_hoc_results_disruption$Cohen_d <- unlist(cohen_d_values)
 
@@
 
-# Display the post-hoc test results for Disruption_Category
+# Ensure the number of column names matches the number of columns in the dataframe
+post_hoc_results_disruption <- post_hoc_results_disruption %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+
+# Displaying the table
 knitr::kable(
@@
 # Extract p-value
-p_value_gri <- round(t_test_gri$p.value, 3)
+p_value_gri <- round(t_test_gri$p.value, 2)
 
@@
   "df" = t_test_gri$parameter,
-  "p-value" = round(t_test_gri$p.value, 3),
+  "p-value" = round(t_test_gri$p.value, 2),
   "Mean Difference" = round(t_test_gri$estimate[1] - t_test_gri$estimate[2], 2),
@@
   geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
-  facet_wrap(~Disruption_Category, scales = "free", labeller = label_wrap_gen(width = 15)) +
+  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) +  # Use fixed scale for all facets  
+  ylim(0, 30) + 
   labs(x = "Group", y = "Time to First Fixation (seconds)") +
@@
 
-# Normality Tests (Shapiro-Wilk)
-normality_tests <- df_ttff_disrup %>%
-  group_by(Group) %>%
-  summarise(
-    Shapiro_Wilk_p = round(shapiro.test(Disrup_time_fixation_sec)$p.value, 3),
-    .groups = "drop"
-  )
-
-kable(
-  normality_tests,
-  caption = "Shapiro-Wilk Test for Normality by Group",
-  col.names = c("Group", "Shapiro-Wilk p-value"),
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Mann-Whitney U-Test and Effect Size
-mann_whitney_test <- wilcox.test(Disrup_time_fixation_sec ~ Group, data = df_ttff_disrup, exact = FALSE)
-
-# Effect Size Calculation for Mann-Whitney (r)
-n1 <- nrow(df_ttff_disrup %>% filter(Group == "Novice"))
-n2 <- nrow(df_ttff_disrup %>% filter(Group == "Expert"))
-r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
-
-mann_whitney_results <- data.frame(
-  "Test" = "Mann-Whitney U",
-  "W" = round(mann_whitney_test$statistic, 2),
-  "p-value" = round(mann_whitney_test$p.value, 3),
-  "Effect Size (r)" = round(r_effect, 3)
-)
-
-kable(
-  mann_whitney_results,
-  caption = "Mann-Whitney U-Test Results for Time to First Fixation",
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Kruskal-Wallis Test and Pairwise Comparisons
-kruskal_test <- kruskal.test(Disrup_time_fixation_sec ~ Disruption_Category, data = df_ttff_disrup)
-
-kruskal_results <- data.frame(
-  "Test" = "Kruskal-Wallis",
-  "Chi-squared" = round(kruskal_test$statistic, 2),
-  "df" = kruskal_test$parameter,
-  "p-value" = round(kruskal_test$p.value, 3)
-)
-
-kable(
-  kruskal_results,
-  caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Pairwise Wilcoxon test with Bonferroni correction
-pairwise_wilcox <- pairwise.wilcox.test(
-  x = df_ttff_disrup$Disrup_time_fixation_sec,
-  g = df_ttff_disrup$Disruption_Category,
-  p.adjust.method = "bonferroni"
-)
-
-# Extract and round the p-values to 3 decimal places
-pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
-  mutate(across(everything(), ~ round(., 3)))
-
-# Display the results with rounded p-values
-kable(
-  pairwise_results,
-  caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",
-  row.names = TRUE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+##################### REPEATED MEASURES ANOVA ########################
+
+# Perform the repeated-measures ANOVA with `Disrup_time_fixation_sec` as the dependent variable
+anova_afex_ttff <- afex::aov_ez(
+  id = "Participant",  # Random effect (each participant is measured multiple times)
+  dv = "Disrup_time_fixation_sec",  # Dependent variable: Time to First Fixation (seconds)
+  between = "Group",  # Between-subject factor: Group (Novice vs Expert)
+  within = "Disruption_Category",  # Within-subject factor: Disruption Categories (Verbal, Physical, Lack of eagerness)
+  data = df_ttff_disrup  # The data frame that contains the TTFF data
+)
+
+# Extract the ANOVA table
+anova_results_ttff <- as.data.frame(anova_afex_ttff$anova_table)
+
+# Recalculate generalized eta squared (η²) for effect size
+eta_squared_results_ttff <- effectsize::eta_squared(anova_afex_ttff, partial = FALSE)
+
+# Combine recalculated eta squared with the ANOVA table
+anova_table_apa_ttff <- anova_results_ttff %>%
+  rownames_to_column(var = "Effect") %>%  # Move row names to a column
+  left_join(
+    as.data.frame(eta_squared_results_ttff), 
+    by = c("Effect" = "Parameter")  # Match the correct columns
+  ) %>%
+  mutate(
+    `F` = round(`F`, 2),  # Round F-values
+    `η²` = round(Eta2, 3),  # Round generalized eta squared
+    `p-value` = ifelse(
+      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 2)  # Format p-values
+    )
+  ) %>%
+  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`)  # Order columns, place η² last
+
+# Display the ANOVA table for Time to First Fixation
+knitr::kable(
+  anova_table_apa_ttff,
+  caption = "Repeated-Measures ANOVA Results for Time to First Fixation (Including Effect Sizes)",
+  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### POST-HOC TESTS Disruption_Category (within-subject factor) ########################
+
+# Perform post-hoc pairwise comparisons for Disruption_Category (within-subject factor)
+post_hoc_disruption <- emmeans(anova_afex_ttff, pairwise ~ Disruption_Category)
+
+# Extract post-hoc pairwise contrasts for Disruption_Category
+post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast),
+    # Replace underscores with spaces
+    Comparison = gsub("\\.", " ", Comparison),
+    # Replace periods with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))  # Round p-values to 2 decimals
+  )
+
+##################### COHEN'S D CALCULATION ########################
+
+# Calculate Cohen's d for each pairwise comparison
+d_LackOfEagerness_vs_Physical <- CohenD(
+  x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+d_LackOfEagerness_vs_Verbal <- CohenD(
+  x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+d_Physical_vs_Verbal <- CohenD(
+  x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+##################### ADD COHEN'S D VALUES TO THE POST-HOC RESULTS ########################
+
+# Create a named vector with the correct Cohen's d values
+cohen_d_values <- c(
+  "Physical disruptions - Lack of eagerness to learn" = round(d_LackOfEagerness_vs_Physical, 2),
+  "Physical disruptions - Verbal disruptions" = round(d_Physical_vs_Verbal, 2),
+  "Lack of eagerness to learn - Verbal disruptions" = round(d_LackOfEagerness_vs_Verbal, 2)
+)
+
+# Add Cohen's d values to the post-hoc results
+post_hoc_results_disruption$Cohen_d <- cohen_d_values[post_hoc_results_disruption$Comparison]
+
+##################### TABLE FOR DISRUPTION CATEGORY ########################
+
+# Ensure the number of column names matches the number of columns in the dataframe
+post_hoc_results_disruption <- post_hoc_results_disruption %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+
+# Displaying the post-hoc results for Disruption Category (main effect) with Cohen's d
+knitr::kable(
+  post_hoc_results_disruption,
+  caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# # Normality Tests (Shapiro-Wilk)
+# normality_tests <- df_ttff_disrup %>%
+#   group_by(Group) %>%
+#   summarise(
+#     Shapiro_Wilk_p = round(shapiro.test(Disrup_time_fixation_sec)$p.value, 2),
+#     .groups = "drop"
+#   )
+# 
+# kable(
+#   normality_tests,
+#   caption = "Shapiro-Wilk Test for Normality by Group",
+#   col.names = c("Group", "Shapiro-Wilk p-value"),
+#   row.names = FALSE
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# # Mann-Whitney U-Test and Effect Size
+# mann_whitney_test <- wilcox.test(Disrup_time_fixation_sec ~ Group, data = df_ttff_disrup, exact = FALSE)
+# 
+# # Effect Size Calculation for Mann-Whitney (r)
+# n1 <- nrow(df_ttff_disrup %>% filter(Group == "Novice"))
+# n2 <- nrow(df_ttff_disrup %>% filter(Group == "Expert"))
+# r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
+# 
+# mann_whitney_results <- data.frame(
+#   "Test" = "Mann-Whitney U",
+#   "W" = round(mann_whitney_test$statistic, 2),
+#   "p-value" = round(mann_whitney_test$p.value, 2),
+#   "Effect Size (r)" = round(r_effect, 3)
+# )
+# 
+# kable(
+#   mann_whitney_results,
+#   caption = "Mann-Whitney U-Test Results for Time to First Fixation",
+#   row.names = FALSE
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# # Kruskal-Wallis Test and Pairwise Comparisons
+# kruskal_test <- kruskal.test(Disrup_time_fixation_sec ~ Disruption_Category, data = df_ttff_disrup)
+# 
+# kruskal_results <- data.frame(
+#   "Test" = "Kruskal-Wallis",
+#   "Chi-squared" = round(kruskal_test$statistic, 2),
+#   "df" = kruskal_test$parameter,
+#   "p-value" = round(kruskal_test$p.value, 2)
+# )
+# 
+# kable(
+#   kruskal_results,
+#   caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",
+#   row.names = FALSE
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# # Pairwise Wilcoxon test with Bonferroni correction
+# pairwise_wilcox <- pairwise.wilcox.test(
+#   x = df_ttff_disrup$Disrup_time_fixation_sec,
+#   g = df_ttff_disrup$Disruption_Category,
+#   p.adjust.method = "bonferroni"
+# )
+# 
+# # Extract and round the p-values to 3 decimal places
+# pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
+#   mutate(across(everything(), ~ round(., 2)))
+# 
+# # Display the results with rounded p-values
+# kable(
+#   pairwise_results,
+#   caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",
+#   row.names = TRUE
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
   filter(
-    !ID %in% c(201, 223),
-    !disruption_appraisal %in% c(-100, -99, -88),
-    !confidence_appraisal %in% c(-100, -99, -88),
-    !prevalence_rating %in% c(-100, -99, -88)
-  ) %>%
-  mutate(ID = ifelse(ID < 200, "Novice", "Expert"))
+    !ID %in% c(201, 223),  # Removing invalid IDs
+    !disruption_appraisal %in% c(-100, -99, -88),  # Removing invalid disruption appraisals
+    !confidence_appraisal %in% c(-100, -99, -88),  # Removing invalid confidence appraisals
+    !prevalence_rating %in% c(-100, -99, -88)  # Removing invalid prevalence ratings
+  ) %>%
+  mutate(
+    Group = ifelse(ID < 200, "Novice", "Expert"),  # Create a Group column based on ID
+    ID = as.factor(ID)  # Ensure that ID is treated as a factor (if needed)
+  )
+
+# Ensure no NAs and that all relevant columns exist
+sri <- sri %>%
+  drop_na(disruption_appraisal, confidence_appraisal, prevalence_rating, event, ID)
+
+# Define disruptions and categories based on the exact event names
+verbal_disruptions <- c("chatting", "heckling", "whispering")
+physical_disruptions <- c("clicking pen", "drumming", "snipping")
+lack_of_eagerness <- c("looking at phone", "head on table", "drawing")
+
+# Step 1: Data Preparation for Disruption Categories
+df_sri_disrup <- sri %>%
+  mutate(
+    Disruption_Category = case_when(
+      event %in% verbal_disruptions ~ "Verbal disruptions",
+      event %in% physical_disruptions ~ "Physical disruptions",
+      event %in% lack_of_eagerness ~ "Lack of eagerness to learn",
+      TRUE ~ NA_character_
+    )
+  ) %>%
+  filter(!is.na(Disruption_Category)) %>%
+  drop_na()
 
 # Descriptive Statistics -------------------------------------------------
-## Disruption Appraisal
+## Disruption Appraisal by Group
 sri_disrup_table <- sri %>%
-  group_by(ID) %>%
+  group_by(Group) %>%
   summarise(
@@
 
-## Confidence Appraisal
+## Disruption Appraisal by Disruption Category (Split by Novice and Expert)
+sri_disrup_category_table <- df_sri_disrup %>%
+  group_by(Group, Disruption_Category) %>%
+  summarise(
+    N = n(),
+    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
+    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
+    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
+    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
+  )
+
+## Disruption Appraisal for each disruption event
+sri_disrup_single_table <- df_sri_disrup %>%
+  group_by(Group, event) %>%
+  summarise(
+    N = n(),
+    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
+    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
+    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
+    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
+  )
+
+## Confidence Appraisal by Group
 sri_confi_table <- sri %>%
-  group_by(ID) %>%
+  group_by(Group) %>%
   summarise(
@@
 
-## Prevalence Rating
+## Confidence Appraisal by Disruption Category (Split by Novice and Expert)
+sri_confi_category_table <- df_sri_disrup %>%
+  group_by(Group, Disruption_Category) %>%
+  summarise(
+    N = n(),
+    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
+    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
+    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
+    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
+  )
+
+## Confidence Appraisal for each disruption event
+sri_confi_single_table <- df_sri_disrup %>%
+  group_by(Group, event) %>%
+  summarise(
+    N = n(),
+    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
+    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
+    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
+    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
+  )
+
+## Prevalence Rating by Group
 sri_preva_table <- sri %>%
-  group_by(ID) %>%
+  group_by(Group) %>%
   summarise(
@@
 
-# APA-Conform Tables -----------------------------------------------------
+## Prevalence Rating by Disruption Category (Split by Novice and Expert)
+sri_preva_category_table <- df_sri_disrup %>%
+  group_by(Group, Disruption_Category) %>%
+  summarise(
+    N = n(),
+    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
+    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
+    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
+    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
+  )
+
+## Prevalence Rating for each disruption event
+sri_preva_single_table <- sri %>%
+  group_by(Group, event) %>%
+  summarise(
+    N = n(),
+    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
+    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
+    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
+    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
+  )
+
+# Step 4: Arrange Values in Descending Order by Mean for Each Event ----------------------------------------
+
+## Disruption Appraisal for each disruption event, sorted by Mean
+sri_disrup_single_table_sorted <- sri_disrup_single_table %>%
+  arrange(Group, desc(M))  # Sorting by mean (M) in descending order within each ID group
+
+## Confidence Appraisal for each disruption event, sorted by Mean
+sri_confi_single_table_sorted <- sri_confi_single_table %>%
+  arrange(Group, desc(M))  # Sorting by mean (M) in descending order within each ID group
+
+## Prevalence Rating for each disruption event, sorted by Mean
+sri_preva_single_table_sorted <- sri_preva_single_table %>%
+  arrange(Group, desc(M))  # Sorting by mean (M) in descending order within each ID group
+
+# APA-Conform Tables with Sorted Values --------------------------------------------
+
+## Disruption Appraisal by Group
 kable(sri_disrup_table, caption = "Descriptive Statistics for Disruption Appraisal", digits = 2) %>%
@@
 
+## Disruption Appraisal by Disruption Category (Split by Novice and Expert)
+kable(sri_disrup_category_table, caption = "Descriptive Statistics for Disruption Appraisal by Disruption Category", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+## Disruption Appraisal for each disruption event (Sorted by Mean)
+kable(sri_disrup_single_table_sorted, caption = "Descriptive Statistics for Disruption Appraisal by Disruption Event (Sorted by Mean)", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+## Confidence Appraisal by Group
 kable(sri_confi_table, caption = "Descriptive Statistics for Confidence Appraisal", digits = 2) %>%
@@
 
+## Confidence Appraisal by Disruption Category (Split by Novice and Expert)
+kable(sri_confi_category_table, caption = "Descriptive Statistics for Confidence Appraisal by Disruption Category", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+## Confidence Appraisal for each disruption event (Sorted by Mean)
+kable(sri_confi_single_table_sorted, caption = "Descriptive Statistics for Confidence Appraisal by Disruption Event (Sorted by Mean)", digits = 2) %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+## Prevalence Rating by Group
 kable(sri_preva_table, caption = "Descriptive Statistics for Prevalence Rating", digits = 2) %>%
@@
 
-# t-Tests and Effect Sizes -----------------------------------------------
-## Disruption Appraisal
-disrup_ttest <- t.test(
-  disruption_appraisal ~ ID, data = sri, var.equal = TRUE
-)
-disrup_d <- cohen.d(disruption_appraisal ~ ID, data = sri)
-
-## Confidence Appraisal
-confi_ttest <- t.test(
-  confidence_appraisal ~ ID, data = sri, var.equal = TRUE
-)
-confi_d <- cohen.d(confidence_appraisal ~ ID, data = sri)
-
-## Prevalence Rating
-preva_ttest <- t.test(
-  prevalence_rating ~ ID, data = sri, var.equal = TRUE
-)
-preva_d <- cohen.d(prevalence_rating ~ ID, data = sri)
-
-# APA-Conform Tables for t-Tests and Effect Sizes ------------------------
-disrup_stats <- tibble(
-  Statistic = c("t-value", "df", "p-value", "Cohen's d"),
-  Value = c(
-    round(disrup_ttest$statistic, 2),
-    round(disrup_ttest$parameter, 2),
-    round(disrup_ttest$p.value, 3),
-    round(disrup_d$estimate, 2)
-  )
-)
-
-confi_stats <- tibble(
-  Statistic = c("t-value", "df", "p-value", "Cohen's d"),
-  Value = c(
-    round(confi_ttest$statistic, 2),
-    round(confi_ttest$parameter, 2),
-    round(confi_ttest$p.value, 3),
-    round(confi_d$estimate, 2)
-  )
-)
-
-preva_stats <- tibble(
-  Statistic = c("t-value", "df", "p-value", "Cohen's d"),
-  Value = c(
-    round(preva_ttest$statistic, 2),
-    round(preva_ttest$parameter, 2),
-    round(preva_ttest$p.value, 3),
-    round(preva_d$estimate, 2)
-  )
-)
-
-kable(disrup_stats, caption = "t-Test and Effect Size for Disruption Appraisal", digits = 2) %>%
+## Prevalence Rating by Disruption Category (Split by Novice and Expert)
+kable(sri_preva_category_table, caption = "Descriptive Statistics for Prevalence Rating by Disruption Category", digits = 2) %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
 
-kable(confi_stats, caption = "t-Test and Effect Size for Confidence Appraisal", digits = 2) %>%
+## Prevalence Rating for each disruption event (Sorted by Mean)
+kable(sri_preva_single_table_sorted, caption = "Descriptive Statistics for Prevalence Rating by Disruption Event (Sorted by Mean)", digits = 2) %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
 
-kable(preva_stats, caption = "t-Test and Effect Size for Prevalence Rating", digits = 2) %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
 # Plotting ---------------------------------------------------------------
+
 ## Disruption Appraisal
 disrup_plot <- sri %>%
-  ggplot(aes(x = ID, y = disruption_appraisal, fill = ID)) +
+  ggplot(aes(x = Group, y = disruption_appraisal, fill = Group)) +
   geom_boxplot(outlier.shape = NA) +
@@
   labs(x = "", y = "Disruption Appraisal") +
-  scale_fill_brewer(palette = "RdBu") +
+  scale_fill_brewer(palette = "RdBu") +  # Using the RdBu color palette for Novice and Expert
   ggtitle("Disruption Appraisal by Group") +
   theme_cowplot() +
-  theme(legend.position = "none") +
-  annotate(
-    "text", x = 1.5, y = max(sri$disruption_appraisal, na.rm = TRUE) * 1.2,
-    label = paste0(
-      "p = ", round(disrup_ttest$p.value, 3), ", d = ",
-      round(disrup_d$estimate, 2)
-    ),
-    size = 4, hjust = 0.5, fontface = "italic"
-  )
+  theme(legend.position = "none")  # No legend for the main plot
 
 print(disrup_plot)
+
+## Disruption Appraisal by Disruption Category, Split by ID (Novice vs Expert)
+disrup_cat_plot <- df_sri_disrup %>%
+  ggplot(aes(x = Disruption_Category, y = disruption_appraisal, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
+  labs(x = "", y = "Disruption Appraisal") +
+  scale_fill_brewer(palette = "RdBu") +  # Use the same RdBu color palette as in disrup_plot
+  ggtitle("Disruption Appraisal by Disruption Category") +
+  theme_cowplot() +
+  theme(legend.position = "top") +  # Place the legend at the top
+  scale_fill_discrete(name = "Group")  # Add a title to the legend
+
+print(disrup_cat_plot)
 
@@
 confi_plot <- sri %>%
-  ggplot(aes(x = ID, y = confidence_appraisal, fill = ID)) +
+  ggplot(aes(x = Group, y = confidence_appraisal, fill = Group)) +
   geom_boxplot(outlier.shape = NA) +
@@
   labs(x = "", y = "Confidence Appraisal") +
-  scale_fill_brewer(palette = "RdBu") +
+  scale_fill_brewer(palette = "RdBu") +  # Using the RdBu color palette for Novice and Expert
   ggtitle("Confidence Appraisal by Group") +
   theme_cowplot() +
-  theme(legend.position = "none") +
-  annotate(
-    "text", x = 1.5, y = max(sri$confidence_appraisal, na.rm = TRUE) * 1.2,
-    label = paste0(
-      "p = ", round(confi_ttest$p.value, 3), ", d = ",
-      round(confi_d$estimate, 2)
-    ),
-    size = 4, hjust = 0.5, fontface = "italic"
-  )
+  theme(legend.position = "none")  # No legend for the main plot
 
 print(confi_plot)
+
+## Confidence Appraisal by Disruption Category, Split by ID (Novice vs Expert)
+confi_cat_plot <- df_sri_disrup %>%
+  ggplot(aes(x = Disruption_Category, y = confidence_appraisal, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
+  labs(x = "", y = "Confidence Appraisal") +
+  scale_fill_brewer(palette = "RdBu") +  # Use the same RdBu color palette as in confi_plot
+  ggtitle("Confidence Appraisal by Disruption Category") +
+  theme_cowplot() +
+  theme(legend.position = "top") +  # Place the legend at the top
+  scale_fill_discrete(name = "Group")  # Add a title to the legend
+
+print(confi_cat_plot)
 
@@
 preva_plot <- sri %>%
-  ggplot(aes(x = ID, y = prevalence_rating, fill = ID)) +
+  ggplot(aes(x = Group, y = prevalence_rating, fill = Group)) +
   geom_boxplot(outlier.shape = NA) +
@@
   labs(x = "", y = "Prevalence Rating") +
-  scale_fill_brewer(palette = "RdBu") +
+  scale_fill_brewer(palette = "RdBu") +  # Using the RdBu color palette for Novice and Expert
   ggtitle("Prevalence Rating by Group") +
   theme_cowplot() +
-  theme(legend.position = "none") +
-  annotate(
-    "text", x = 1.5, y = max(sri$prevalence_rating, na.rm = TRUE) * 1.2,
-    label = paste0(
-      "p = ", round(preva_ttest$p.value, 3), ", d = ",
-      round(preva_d$estimate, 2)
-    ),
-    size = 4, hjust = 0.5, fontface = "italic"
-  )
+  theme(legend.position = "none")  # No legend for the main plot
 
 print(preva_plot)
+
+## Prevalence Rating by Disruption Category, Split by ID (Novice vs Expert)
+preva_cat_plot <- df_sri_disrup %>%
+  ggplot(aes(x = Disruption_Category, y = prevalence_rating, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
+  labs(x = "", y = "Prevalence Rating") +
+  scale_fill_brewer(palette = "RdBu") +  # Use the same RdBu color palette as in preva_plot
+  ggtitle("Prevalence Rating by Disruption Category") +
+  theme_cowplot() +
+  theme(legend.position = "top") +  # Place the legend at the top
+  scale_fill_discrete(name = "Group")  # Add a title to the legend
+
+print(preva_cat_plot)
+
+# REPEATED MEASURES ANOVA ---------------------------------------------------------------
+
+# Perform the repeated-measures ANOVA for Disruption Appraisal with the main effects of ID and Disruption_Category
+# and the interaction between them
+anova_disrup_appraisal <- afex::aov_ez(
+  id = "ID",  # Random effect (each participant is measured multiple times)
+  dv = "disruption_appraisal",  # Dependent variable: Disruption Appraisal
+  within = "Disruption_Category",  # Within-subject factor: Disruption Categories (Verbal, Physical, Lack of eagerness)
+  between = "Group",  # Between-subject factor: Group (Novice vs Expert)
+  data = df_sri_disrup,  # The data frame that contains the disruption appraisal data
+  factorize = TRUE,  # Ensure factors are treated as factors
+  detailed = TRUE  # Include detailed output to check interaction effects
+)
+
+# Perform the repeated-measures ANOVA for Confidence Appraisal with the main effects of ID and Disruption_Category
+# and the interaction between them
+anova_confi_appraisal <- afex::aov_ez(
+  id = "ID",  # Random effect (each participant is measured multiple times)
+  dv = "confidence_appraisal",  # Dependent variable: Confidence Appraisal
+  within = "Disruption_Category",  # Within-subject factor: Disruption Categories (Verbal, Physical, Lack of eagerness)
+  between = "Group",  # Between-subject factor: Group (Novice vs Expert)
+  data = df_sri_disrup,  # The data frame that contains the confidence appraisal data
+  factorize = TRUE,  # Ensure factors are treated as factors
+  detailed = TRUE  # Include detailed output to check interaction effects
+)
+
+# Extract the ANOVA tables for both dependent variables
+anova_results_disrup_appraisal <- as.data.frame(anova_disrup_appraisal$anova_table)
+anova_results_confi_appraisal <- as.data.frame(anova_confi_appraisal$anova_table)
+
+# Recalculate generalized eta squared (η²) for effect size for both ANOVAs
+eta_squared_disrup_appraisal <- effectsize::eta_squared(anova_disrup_appraisal, partial = FALSE)
+eta_squared_confi_appraisal <- effectsize::eta_squared(anova_confi_appraisal, partial = FALSE)
+
+# Combine recalculated eta squared with the ANOVA tables
+anova_table_apa_disrup_appraisal <- anova_results_disrup_appraisal %>%
+  rownames_to_column(var = "Effect") %>%
+  left_join(
+    as.data.frame(eta_squared_disrup_appraisal),
+    by = c("Effect" = "Parameter")  # Match the correct columns
+  ) %>%
+  mutate(
+    `F` = round(`F`, 2),  # Round F-values
+    `η²` = round(Eta2, 3),  # Round generalized eta squared
+    `p-value` = ifelse(
+      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 2)  # Format p-values
+    )
+  ) %>%
+  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`)  # Order columns, place η² last
+
+anova_table_apa_confi_appraisal <- anova_results_confi_appraisal %>%
+  rownames_to_column(var = "Effect") %>%
+  left_join(
+    as.data.frame(eta_squared_confi_appraisal),
+    by = c("Effect" = "Parameter")  # Match the correct columns
+  ) %>%
+  mutate(
+    `F` = round(`F`, 2),  # Round F-values
+    `η²` = round(Eta2, 3),  # Round generalized eta squared
+    `p-value` = ifelse(
+      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 2)  # Format p-values
+    )
+  ) %>%
+  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`)  # Order columns, place η² last
+
+# Display the ANOVA tables for Disruption Appraisal and Confidence Appraisal
+knitr::kable(
+  anova_table_apa_disrup_appraisal,
+  caption = "Repeated-Measures ANOVA Results for Disruption Appraisal (Including Effect Sizes)",
+  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+knitr::kable(
+  anova_table_apa_confi_appraisal,
+  caption = "Repeated-Measures ANOVA Results for Confidence Appraisal (Including Effect Sizes)",
+  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### POST-HOC TESTS for Disruption Appraisal (Group and Disruption_Category) ########################
+
+# Perform post-hoc pairwise comparisons for Group (between-subject factor) for disruption_appraisal
+post_hoc_group_disrup <- emmeans(anova_disrup_appraisal, pairwise ~ Group)
+
+# Extract post-hoc pairwise contrasts for Group (Disruption Appraisal)
+post_hoc_results_group_disrup <- as.data.frame(post_hoc_group_disrup$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2)),
+
+    # Calculate Cohen's d for Group comparison using pooled SD formula
+    group1 = "Novice",  # Define group1 for Cohen's d
+    group2 = "Expert",  # Define group2 for Cohen's d
+
+    # Get the means for both groups
+    mean1 = sri %>% 
+      filter(Group == group1) %>%
+      summarise(mean1 = mean(disruption_appraisal, na.rm = TRUE)) %>% 
+      pull(mean1),
+
+    mean2 = sri %>% 
+      filter(Group == group2) %>%
+      summarise(mean2 = mean(disruption_appraisal, na.rm = TRUE)) %>% 
+      pull(mean2),
+
+    # Get the standard deviations for both groups
+    sd1 = sri %>% 
+      filter(Group == group1) %>%
+      summarise(sd1 = sd(disruption_appraisal, na.rm = TRUE)) %>% 
+      pull(sd1),
+
+    sd2 = sri %>% 
+      filter(Group == group2) %>%
+      summarise(sd2 = sd(disruption_appraisal, na.rm = TRUE)) %>% 
+      pull(sd2),
+
+    # Get the sample sizes for both groups
+    n1 = nrow(sri %>% filter(Group == group1)),
+    n2 = nrow(sri %>% filter(Group == group2)),
+
+    # Calculate pooled standard deviation
+    pooled_sd = sqrt(((n1 - 1) * sd1^2 + (n2 - 1) * sd2^2) / (n1 + n2 - 2)),
+
+    # Calculate Cohen's d using the correct formula (mean difference / pooled SD)
+    Cohen_d = ifelse(pooled_sd > 0, round(abs(mean1 - mean2) / pooled_sd, 2), NA)  # Avoid division by zero
+  ) %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)  # Keep relevant columns
+
+##################### POST-HOC TESTS for Confidence Appraisal (Group and Disruption_Category) ########################
+
+# Perform post-hoc pairwise comparisons for Group (between-subject factor) for confidence_appraisal
+post_hoc_group_confi <- emmeans(anova_confi_appraisal, pairwise ~ Group)
+
+# Extract post-hoc pairwise contrasts for Group (Confidence Appraisal)
+post_hoc_results_group_confi <- as.data.frame(post_hoc_group_confi$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2)),
+
+    # Calculate Cohen's d for Group comparison using pooled SD formula
+    group1 = "Novice",  # Define group1 for Cohen's d
+    group2 = "Expert",  # Define group2 for Cohen's d
+
+    # Get the means for both groups
+    mean1 = sri %>% 
+      filter(Group == group1) %>%
+      summarise(mean1 = mean(confidence_appraisal, na.rm = TRUE)) %>% 
+      pull(mean1),
+
+    mean2 = sri %>% 
+      filter(Group == group2) %>%
+      summarise(mean2 = mean(confidence_appraisal, na.rm = TRUE)) %>% 
+      pull(mean2),
+
+    # Get the standard deviations for both groups
+    sd1 = sri %>% 
+      filter(Group == group1) %>%
+      summarise(sd1 = sd(confidence_appraisal, na.rm = TRUE)) %>% 
+      pull(sd1),
+
+    sd2 = sri %>% 
+      filter(Group == group2) %>%
+      summarise(sd2 = sd(confidence_appraisal, na.rm = TRUE)) %>% 
+      pull(sd2),
+
+    # Get the sample sizes for both groups
+    n1 = nrow(sri %>% filter(Group == group1)),
+    n2 = nrow(sri %>% filter(Group == group2)),
+
+    # Calculate pooled standard deviation
+    pooled_sd = sqrt(((n1 - 1) * sd1^2 + (n2 - 1) * sd2^2) / (n1 + n2 - 2)),
+
+    # Calculate Cohen's d using the correct formula (mean difference / pooled SD)
+    Cohen_d = ifelse(pooled_sd > 0, round(abs(mean1 - mean2) / pooled_sd, 2), NA)  # Avoid division by zero
+  ) %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)  # Keep relevant columns
+
+##################### POST-HOC TESTS for Disruption_Category (within-subject factor) ########################
+
+# Perform post-hoc pairwise comparisons for Disruption_Category (within-subject factor) for disruption_appraisal
+post_hoc_disruption_disrup <- emmeans(anova_disrup_appraisal, pairwise ~ Disruption_Category)
+
+# Extract post-hoc pairwise contrasts for Disruption_Category (Disruption Appraisal)
+post_hoc_results_disruption_disrup <- as.data.frame(post_hoc_disruption_disrup$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))  # Round p-values to 2 decimals
+  )
+
+# Perform post-hoc pairwise comparisons for Disruption_Category (within-subject factor) for confidence_appraisal
+post_hoc_disruption_confi <- emmeans(anova_confi_appraisal, pairwise ~ Disruption_Category)
+
+# Extract post-hoc pairwise contrasts for Disruption_Category (Confidence Appraisal)
+post_hoc_results_disruption_confi <- as.data.frame(post_hoc_disruption_confi$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))  # Round p-values to 2 decimals
+  )
+
+##################### COHEN'S D CALCULATION ########################
+
+# Calculate Cohen's d for each pairwise comparison for disruption_appraisal
+d_LackOfEagerness_vs_Physical_disrup <- CohenD(
+  x = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+d_LackOfEagerness_vs_Verbal_disrup <- CohenD(
+  x = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+d_Physical_vs_Verbal_disrup <- CohenD(
+  x = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+# Calculate Cohen's d for each pairwise comparison for confidence_appraisal
+d_LackOfEagerness_vs_Physical_confi <- CohenD(
+  x = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+d_LackOfEagerness_vs_Verbal_confi <- CohenD(
+  x = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+d_Physical_vs_Verbal_confi <- CohenD(
+  x = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+##################### COHEN'S D CALCULATION DISRUPTION APPRAISAL ########################
+
+# Calculate Cohen's d for each pairwise comparison for disruption_appraisal
+d_LackOfEagerness_vs_Verbal_disrup <- CohenD(
+  x = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+d_LackOfEagerness_vs_Physical_disrup <- CohenD(
+  x = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+d_Physical_vs_Verbal_disrup <- CohenD(
+  x = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_sri_disrup$disruption_appraisal[df_sri_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+###################### ADD MISSING COHEN'S D VALUES ########################
+
+# Add the missing Cohen's d values to the cohen_d_values_disrup vector
+cohen_d_values_disrup <- c(
+  "Verbal disruptions - Lack of eagerness to learn" = round(d_LackOfEagerness_vs_Verbal_disrup, 2),
+  "Physical disruptions - Lack of eagerness to learn" = round(d_LackOfEagerness_vs_Physical_disrup, 2),
+  "Physical disruptions - Verbal disruptions" = round(d_Physical_vs_Verbal_disrup, 2),
+  "Verbal disruptions - Physical disruptions" = round(d_Physical_vs_Verbal_disrup, 2),  # Add missing comparison
+  "Lack of eagerness to learn - Physical disruptions" = round(d_LackOfEagerness_vs_Physical_disrup, 2)  # Add missing comparison
+)
+
+# Add Cohen's d values to the post-hoc results for disruption_appraisal
+post_hoc_results_disruption_disrup$Cohen_d <- cohen_d_values_disrup[post_hoc_results_disruption_disrup$Comparison]
+
+# Ensure the number of column names matches the number of columns in the data frame
+post_hoc_results_disruption_disrup <- post_hoc_results_disruption_disrup %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+
+##################### COHEN'S D CALCULATION FOR CONFIDENCE APPRAISAL ########################
+
+# Calculate Cohen's d for each pairwise comparison for confidence_appraisal
+d_LackOfEagerness_vs_Physical_confi <- CohenD(
+  x = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Physical disruptions"],
+  na.rm = TRUE
+)
+
+d_LackOfEagerness_vs_Verbal_confi <- CohenD(
+  x = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+d_Physical_vs_Verbal_confi <- CohenD(
+  x = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_sri_disrup$confidence_appraisal[df_sri_disrup$Disruption_Category == "Verbal disruptions"],
+  na.rm = TRUE
+)
+
+##################### ADD MISSING COHEN'S D VALUES FOR CONFIDENCE APPRAISAL ########################
+
+# Create a named vector with the correct Cohen's d values for confidence_appraisal
+cohen_d_values_confi <- c(
+  "Verbal disruptions - Lack of eagerness to learn" = round(d_LackOfEagerness_vs_Verbal_confi, 2),
+  "Physical disruptions - Lack of eagerness to learn" = round(d_LackOfEagerness_vs_Physical_confi, 2),
+  "Physical disruptions - Verbal disruptions" = round(d_Physical_vs_Verbal_confi, 2),
+  "Verbal disruptions - Physical disruptions" = round(d_Physical_vs_Verbal_confi, 2),  # Add missing comparison
+  "Lack of eagerness to learn - Physical disruptions" = round(d_LackOfEagerness_vs_Physical_confi, 2)  # Add missing comparison
+)
+
+# Add Cohen's d values to the post-hoc results for confidence_appraisal
+post_hoc_results_disruption_confi$Cohen_d <- cohen_d_values_confi[post_hoc_results_disruption_confi$Comparison]
+
+# Ensure the number of column names matches the number of columns in the data frame
+post_hoc_results_disruption_confi <- post_hoc_results_disruption_confi %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+
+##################### TABLE FOR GROUP AND DISRUPTION CATEGORY ########################
+
+# Display the post-hoc test results for Group (Disruption Appraisal)
+knitr::kable(
+  post_hoc_results_group_disrup,
+  caption = "Post-Hoc Pairwise Comparisons for Disruption Appraisal by Group (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+)%>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Display the post-hoc test results for Disruption Category (Disruption Appraisal) with Cohen's d
+knitr::kable(
+  post_hoc_results_disruption_disrup,
+  caption = "Post-Hoc Pairwise Comparisons for Disruption Appraisal by Disruption Category (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Display the post-hoc test results for Group (Confidence Appraisal)
+knitr::kable(
+  post_hoc_results_group_confi,
+  caption = "Post-Hoc Pairwise Comparisons for Confidence Appraisal by Group (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Displaying the post-hoc results for Disruption Category (Confidence Appraisal) with Cohen's d
+knitr::kable(
+  post_hoc_results_disruption_confi,
+  caption = "Post-Hoc Pairwise Comparisons for Confidence Appraisal by Disruption Category (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# # t-Tests and Effect Sizes -----------------------------------------------
+# ## Disruption Appraisal
+# disrup_ttest <- t.test(
+#   disruption_appraisal ~ ID, data = sri, var.equal = TRUE
+# )
+# disrup_d <- cohen.d(disruption_appraisal ~ ID, data = sri)
+# 
+# ## Confidence Appraisal
+# confi_ttest <- t.test(
+#   confidence_appraisal ~ ID, data = sri, var.equal = TRUE
+# )
+# confi_d <- cohen.d(confidence_appraisal ~ ID, data = sri)
+# 
+# ## Prevalence Rating
+# preva_ttest <- t.test(
+#   prevalence_rating ~ ID, data = sri, var.equal = TRUE
+# )
+# preva_d <- cohen.d(prevalence_rating ~ ID, data = sri)
+# 
+# # APA-Conform Tables for t-Tests and Effect Sizes ------------------------
+# disrup_stats <- tibble(
+#   Statistic = c("t-value", "df", "p-value", "Cohen's d"),
+#   Value = c(
+#     round(disrup_ttest$statistic, 2),
+#     round(disrup_ttest$parameter, 2),
+#     round(disrup_ttest$p.value, 2),
+#     round(disrup_d$estimate, 2)
+#   )
+# )
+# 
+# confi_stats <- tibble(
+#   Statistic = c("t-value", "df", "p-value", "Cohen's d"),
+#   Value = c(
+#     round(confi_ttest$statistic, 2),
+#     round(confi_ttest$parameter, 2),
+#     round(confi_ttest$p.value, 2),
+#     round(confi_d$estimate, 2)
+#   )
+# )
+# 
+# preva_stats <- tibble(
+#   Statistic = c("t-value", "df", "p-value", "Cohen's d"),
+#   Value = c(
+#     round(preva_ttest$statistic, 2),
+#     round(preva_ttest$parameter, 2),
+#     round(preva_ttest$p.value, 2),
+#     round(preva_d$estimate, 2)
+#   )
+# )
+# 
+# kable(disrup_stats, caption = "t-Test and Effect Size for Disruption Appraisal", digits = 2) %>%
+#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+# 
+# kable(confi_stats, caption = "t-Test and Effect Size for Confidence Appraisal", digits = 2) %>%
+#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+# 
+# kable(preva_stats, caption = "t-Test and Effect Size for Prevalence Rating", digits = 2) %>%
+#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
 
@@
     `t-value` = round(t_test$statistic, 2),
-    `p-value` = round(t_test$p.value, 3),
+    `p-value` = round(t_test$p.value, 2),
     `Cohen's d` = round(cohen_d, 2)
@@
 
-### Self-evaluation (5 classroom management items, 3 disruption handling items, 8 presence items)
-```{r self-eval_5-3-8, echo=FALSE, results='asis'}
+<!-- ### Self-evaluation (5 classroom management items, 3 disruption handling items, 8 presence items) -->
+<!-- ```{r self-eval_5-3-8, echo=FALSE, results='asis'} -->
+
+<!-- # Data Import and Preparation -------------------------------------------- -->
+<!-- df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% -->
+<!--   filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs -->
+<!--   mutate( -->
+<!--     Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition -->
+<!--     Participant = LI06_05  # Add new column "Participant" -->
+<!--   ) %>% -->
+<!--   arrange(Participant) %>%  -->
+<!--   select( -->
+<!--     Participant,  -->
+<!--     Group,  -->
+<!--     LM01_01:LM01_05,  # Classroom Management -->
+<!--     LM01_06:LM01_08,  # Disruption Handling -->
+<!--     LP01_01:LP01_08   # Presence -->
+<!--   ) %>% -->
+<!--   rename( -->
+<!--     CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05, -->
+<!--     DH_01 = LM01_06, DH_02 = LM01_07, DH_03 = LM01_08, -->
+<!--     P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05, -->
+<!--     P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08 -->
+<!--   ) %>% -->
+<!--   na.omit()  # Remove NAs -->
+
+<!-- # Create Dataset for Plotting with Overall Measure -------------------------------------------- -->
+<!-- df_quest_long <- df_quest %>% -->
+<!--   rowwise() %>% -->
+<!--   transmute( -->
+<!--     Group = Group, -->
+<!--     `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2), -->
+<!--     `Disruption Handling` = round(mean(c_across(starts_with("DH")), na.rm = TRUE), 2), -->
+<!--     `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2),  # Excluding Participant column -->
+<!--     `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, DH_01, DH_02, DH_03, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value -->
+<!--   ) %>% -->
+<!--   ungroup() %>% -->
+<!--   pivot_longer(cols = c(`Classroom Management`, `Disruption Handling`, `Presence`, `Overall`), -->
+<!--                names_to = "Scales Self-evaluation", values_to = "Mean") -->
+
+<!-- # Plot Mean Scores by Group ---------------------------------------------- -->
+<!-- quest_plot <- df_quest_long %>% -->
+<!--   mutate( -->
+<!--     Group = factor(Group, levels = c("Novice", "Expert")), -->
+<!--     `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Disruption Handling", "Presence", "Overall"))  # Reorder scales -->
+<!--   ) %>% -->
+<!--   ggplot(aes(x = Group, y = Mean)) + -->
+<!--   geom_boxplot(aes(fill = Group), outlier.shape = NA) + -->
+<!--   geom_point( -->
+<!--     size = 1, -->
+<!--     alpha = 0.4, -->
+<!--     position = position_jitter(seed = 1, width = 0.1, height = 0.1) -->
+<!--   ) + -->
+<!--   labs(x = "", y = "Mean Scores") + -->
+<!--   ylim(0, 4) +  -->
+<!--   scale_fill_brewer(palette = "RdBu") + -->
+<!--   facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") + -->
+<!--   theme_cowplot() + -->
+<!--   ggtitle("Self-Evaluation Scores") + -->
+<!--   theme( -->
+<!--     plot.title = element_text(size = 25, face = "bold"), -->
+<!--     legend.title = element_text(size = 20), -->
+<!--     legend.text = element_text(size = 15), -->
+<!--     axis.text.x = element_blank(), -->
+<!--     axis.ticks.x = element_blank(), -->
+<!--     strip.text.x = element_text(size = 8), -->
+<!--     axis.title.y = element_text(size = 20) -->
+<!--   ) -->
+
+<!-- print(quest_plot) -->
+
+<!-- # t-Test and Effect Sizes ------------------------------------------------ -->
+
+<!-- # t-Test Function for Long Format ---------------------------------------- -->
+<!-- t_test_stats_long <- function(data, group_col, scale_filter, scale_name) { -->
+<!--   # Subset Data for the Specific Scale -->
+<!--   filtered_data <- data %>% -->
+<!--     filter(`Scales Self-evaluation` == scale_filter) -->
+
+<!--   # Check if there are exactly two levels in the group -->
+<!--   if (length(unique(filtered_data[[group_col]])) != 2) { -->
+<!--     warning(paste("Skipping t-test for", scale_name, ": Group must have exactly two levels")) -->
+<!--     return(tibble( -->
+<!--       `Scale` = scale_name, -->
+<!--       `t-value` = NA, -->
+<!--       `p-value` = NA, -->
+<!--       `Cohen's d` = NA -->
+<!--     )) -->
+<!--   } -->
+
+<!--   # Perform t-Test -->
+<!--   t_test <- t.test( -->
+<!--     Mean ~ get(group_col), -->
+<!--     data = filtered_data, -->
+<!--     var.equal = TRUE -->
+<!--   ) -->
+
+<!--   # Calculate Cohen's d -->
+<!--   cohen_d <- CohenD( -->
+<!--     x = filtered_data %>% filter(!!rlang::sym(group_col) == "Expert") %>% pull(Mean), -->
+<!--     y = filtered_data %>% filter(!!rlang::sym(group_col) == "Novice") %>% pull(Mean) -->
+<!--   ) -->
+
+<!--   # Return Results -->
+<!--   tibble( -->
+<!--     `Scale` = scale_name, -->
+<!--     `t-value` = round(t_test$statistic, 2), -->
+<!--     `p-value` = round(t_test$p.value, 2), -->
+<!--     `Cohen's d` = round(cohen_d, 2) -->
+<!--   ) -->
+<!-- } -->
+
+<!-- # Perform t-Tests for Each Scale -->
+<!-- t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation") -->
+<!-- t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management") -->
+<!-- t_test_npvc <- t_test_stats_long(df_quest_long, "Group", "Disruption Handling", "Disruption Handling") -->
+<!-- t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence") -->
+
+<!-- # Combine Results into a Single Table -->
+<!-- t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_npvc, t_test_presence) -->
+
+<!-- # Display Results in APA-Conform Table -->
+<!-- kable(t_test_results, caption = "t-Test and Effect Sizes for Self-Evaluation Scales") %>% -->
+<!--   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) -->
+
+<!-- # Internal Consistency (Omega) ------------------------------------------- -->
+<!-- # Helper Function for Omega Calculation -->
+<!-- calculate_omega_total <- function(data, scale_name) { -->
+<!--   if (nrow(data) == 0 || ncol(data) == 0) { -->
+<!--     warning(paste("No valid data for", scale_name)) -->
+<!--     return(NA) -->
+<!--   } -->
+
+<!--   # Try Omega Calculation -->
+<!--   result <- tryCatch( -->
+<!--     omega(data), -->
+<!--     error = function(e) { -->
+<!--       warning(paste("Omega calculation failed for", scale_name, ":", e$message)) -->
+<!--       return(NULL) -->
+<!--     } -->
+<!--   ) -->
+
+<!--   # Check if Result is Valid and Extract omega.tot -->
+<!--   if (is.null(result) || !"omega.tot" %in% names(result)) { -->
+<!--     warning(paste("Omega total not available for", scale_name)) -->
+<!--     return(NA) -->
+<!--   } -->
+
+<!--   return(round(result$omega.tot, 2)) -->
+<!-- } -->
+
+<!-- ### CLASSROOM MANAGEMENT ------------------------------------------------- -->
+<!-- # Select relevant columns and remove NAs -->
+<!-- df_cm <- df_quest %>% select(starts_with("CM")) -->
+
+<!-- # Calculate omega for Classroom Management -->
+<!-- omega_cm <- calculate_omega_total(df_cm, "Classroom Management") -->
+
+<!-- ### DISRUPTION HANDLING -------------------------------------------------- -->
+<!-- # Select relevant columns and remove NAs -->
+<!-- df_dh <- df_quest %>% select(starts_with("DH")) -->
+
+<!-- # Calculate omega for Disruption Handling -->
+<!-- omega_dh <- calculate_omega_total(df_dh, "Disruption Handling") -->
+
+<!-- ### PRESENCE ------------------------------------------------------------ -->
+<!-- # Select relevant columns and remove NAs -->
+<!-- df_presence <- df_quest %>% select(starts_with("P") & !starts_with("Participant")) -->
+
+<!-- # Calculate omega for Presence -->
+<!-- omega_presence <- calculate_omega_total(df_presence, "Presence") -->
+
+<!-- ### OVERALL TEST ----------------------------------------------------- -->
+<!-- # Select relevant columns and remove NAs (for overall evaluation) -->
+<!-- df_self_all <- df_quest %>% -->
+<!--   select(starts_with("CM"), starts_with("DH"), starts_with("P") & !starts_with("Participant")) %>% -->
+<!--   mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data -->
+<!--   drop_na() -->
+
+<!-- # Calculate omega for Overall Evaluation -->
+<!-- omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation") -->
+
+<!-- ### COMBINE RESULTS INTO AN APA-CONFORM TABLE ---------------------------- -->
+<!-- # APA-Conform Table ------------------------------------------------------ -->
+<!-- omega_results <- tibble( -->
+<!--   Facet = c("Overall Evaluation", "Classroom Management", "Disruption Handling", "Presence"), -->
+<!--   `Omega Total` = c(omega_self_all, omega_cm, omega_dh, omega_presence) -->
+<!-- ) -->
+
+<!-- # Display APA-Conform Table ---------------------------------------------- -->
+<!-- kable(omega_results, caption = "Internal Consistency (Omega) for Self-evaluation") %>% -->
+<!--   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) -->
+
+<!-- ``` -->
+
+### Self-evaluation (8 classroom management items, 8 presence items)
+```{r self-eval_8-8, echo=FALSE, results='asis'}
 
@@
     Group, 
-    LM01_01:LM01_05,  # Classroom Management
-    LM01_06:LM01_08,  # Disruption Handling
+    LM01_01:LM01_08,  # Classroom Management and Disruption Handling combined
     LP01_01:LP01_08   # Presence
@@
     CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
-    DH_01 = LM01_06, DH_02 = LM01_07, DH_03 = LM01_08,
+    CM_06 = LM01_06, CM_07 = LM01_07, CM_08 = LM01_08,  # Renaming combined columns
     P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
@@
 
-# Create Dataset for Plotting with Overall Measure --------------------------------------------
+# Create Dataset for Plotting with Combined Scales -------------------------
 df_quest_long <- df_quest %>%
@@
     Group = Group,
-    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),
-    `Disruption Handling` = round(mean(c_across(starts_with("DH")), na.rm = TRUE), 2),
+    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),  # Combine Classroom Management and Disruption Handling
     `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2),  # Excluding Participant column
-    `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, DH_01, DH_02, DH_03, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value
+    `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, CM_06, CM_07, CM_08, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value
   ) %>%
   ungroup() %>%
-  pivot_longer(cols = c(`Classroom Management`, `Disruption Handling`, `Presence`, `Overall`),
+  pivot_longer(cols = c(`Classroom Management`, `Presence`, `Overall`),
                names_to = "Scales Self-evaluation", values_to = "Mean")
@@
     Group = factor(Group, levels = c("Novice", "Expert")),
-    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Disruption Handling", "Presence", "Overall"))  # Reorder scales
+    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Presence", "Overall"))  # Reorder scales
   ) %>%
@@
 # t-Test and Effect Sizes ------------------------------------------------
-
 # t-Test Function for Long Format ----------------------------------------
@@
     `t-value` = round(t_test$statistic, 2),
-    `p-value` = round(t_test$p.value, 3),
-    `Cohen's d` = round(cohen_d, 2)
-  )
-}
-
-# Perform t-Tests for Each Scale
-t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
-t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
-t_test_npvc <- t_test_stats_long(df_quest_long, "Group", "Disruption Handling", "Disruption Handling")
-t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")
-
-# Combine Results into a Single Table
-t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_npvc, t_test_presence)
-
-# Display Results in APA-Conform Table
-kable(t_test_results, caption = "t-Test and Effect Sizes for Self-Evaluation Scales") %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
-# Internal Consistency (Omega) -------------------------------------------
-# Helper Function for Omega Calculation
-calculate_omega_total <- function(data, scale_name) {
-  if (nrow(data) == 0 || ncol(data) == 0) {
-    warning(paste("No valid data for", scale_name))
-    return(NA)
-  }
-
-  # Try Omega Calculation
-  result <- tryCatch(
-    omega(data),
-    error = function(e) {
-      warning(paste("Omega calculation failed for", scale_name, ":", e$message))
-      return(NULL)
-    }
-  )
-
-  # Check if Result is Valid and Extract omega.tot
-  if (is.null(result) || !"omega.tot" %in% names(result)) {
-    warning(paste("Omega total not available for", scale_name))
-    return(NA)
-  }
-
-  return(round(result$omega.tot, 2))
-}
-
-### CLASSROOM MANAGEMENT -------------------------------------------------
-# Select relevant columns and remove NAs
-df_cm <- df_quest %>% select(starts_with("CM"))
-
-# Calculate omega for Classroom Management
-omega_cm <- calculate_omega_total(df_cm, "Classroom Management")
-
-### DISRUPTION HANDLING --------------------------------------------------
-# Select relevant columns and remove NAs
-df_dh <- df_quest %>% select(starts_with("DH"))
-
-# Calculate omega for Disruption Handling
-omega_dh <- calculate_omega_total(df_dh, "Disruption Handling")
-
-### PRESENCE ------------------------------------------------------------
-# Select relevant columns and remove NAs
-df_presence <- df_quest %>% select(starts_with("P") & !starts_with("Participant"))
-
-# Calculate omega for Presence
-omega_presence <- calculate_omega_total(df_presence, "Presence")
-
-### OVERALL TEST -----------------------------------------------------
-# Select relevant columns and remove NAs (for overall evaluation)
-df_self_all <- df_quest %>%
-  select(starts_with("CM"), starts_with("DH"), starts_with("P") & !starts_with("Participant")) %>%
-  mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
-  drop_na()
-
-# Calculate omega for Overall Evaluation
-omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation")
-
-### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
-# APA-Conform Table ------------------------------------------------------
-omega_results <- tibble(
-  Facet = c("Overall Evaluation", "Classroom Management", "Disruption Handling", "Presence"),
-  `Omega Total` = c(omega_self_all, omega_cm, omega_dh, omega_presence)
-)
-
-# Display APA-Conform Table ----------------------------------------------
-kable(omega_results, caption = "Internal Consistency (Omega) for Self-evaluation") %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
-```
-
-### Self-evaluation (8 classroom management items, 8 presence items)
-```{r self-eval_8-8, echo=FALSE, results='asis'}
-
-# Data Import and Preparation --------------------------------------------
-df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
-  mutate(
-    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
-    Participant = LI06_05  # Add new column "Participant"
-  ) %>%
-  arrange(Participant) %>% 
-  select(
-    Participant, 
-    Group, 
-    LM01_01:LM01_08,  # Classroom Management and Disruption Handling combined
-    LP01_01:LP01_08   # Presence
-  ) %>%
-  rename(
-    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
-    CM_06 = LM01_06, CM_07 = LM01_07, CM_08 = LM01_08,  # Renaming combined columns
-    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
-    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
-  ) %>%
-  na.omit()  # Remove NAs
-
-# Create Dataset for Plotting with Combined Scales -------------------------
-df_quest_long <- df_quest %>%
-  rowwise() %>%
-  transmute(
-    Group = Group,
-    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),  # Combine Classroom Management and Disruption Handling
-    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2),  # Excluding Participant column
-    `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, CM_06, CM_07, CM_08, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value
-  ) %>%
-  ungroup() %>%
-  pivot_longer(cols = c(`Classroom Management`, `Presence`, `Overall`),
-               names_to = "Scales Self-evaluation", values_to = "Mean")
-
-# Plot Mean Scores by Group ----------------------------------------------
-quest_plot <- df_quest_long %>%
-  mutate(
-    Group = factor(Group, levels = c("Novice", "Expert")),
-    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Presence", "Overall"))  # Reorder scales
-  ) %>%
-  ggplot(aes(x = Group, y = Mean)) +
-  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 1,
-    alpha = 0.4,
-    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
-  ) +
-  labs(x = "", y = "Mean Scores") +
-  ylim(0, 4) + 
-  scale_fill_brewer(palette = "RdBu") +
-  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
-  theme_cowplot() +
-  ggtitle("Self-Evaluation Scores") +
-  theme(
-    plot.title = element_text(size = 25, face = "bold"),
-    legend.title = element_text(size = 20),
-    legend.text = element_text(size = 15),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    strip.text.x = element_text(size = 8),
-    axis.title.y = element_text(size = 20)
-  )
-
-print(quest_plot)
-
-# t-Test and Effect Sizes ------------------------------------------------
-# t-Test Function for Long Format ----------------------------------------
-t_test_stats_long <- function(data, group_col, scale_filter, scale_name) {
-  # Subset Data for the Specific Scale
-  filtered_data <- data %>%
-    filter(`Scales Self-evaluation` == scale_filter)
-
-  # Check if there are exactly two levels in the group
-  if (length(unique(filtered_data[[group_col]])) != 2) {
-    warning(paste("Skipping t-test for", scale_name, ": Group must have exactly two levels"))
-    return(tibble(
-      `Scale` = scale_name,
-      `t-value` = NA,
-      `p-value` = NA,
-      `Cohen's d` = NA
-    ))
-  }
-
-  # Perform t-Test
-  t_test <- t.test(
-    Mean ~ get(group_col),
-    data = filtered_data,
-    var.equal = TRUE
-  )
-
-  # Calculate Cohen's d
-  cohen_d <- CohenD(
-    x = filtered_data %>% filter(!!rlang::sym(group_col) == "Expert") %>% pull(Mean),
-    y = filtered_data %>% filter(!!rlang::sym(group_col) == "Novice") %>% pull(Mean)
-  )
-
-  # Return Results
-  tibble(
-    `Scale` = scale_name,
-    `t-value` = round(t_test$statistic, 2),
-    `p-value` = round(t_test$p.value, 3),
+    `p-value` = round(t_test$p.value, 2),
     `Cohen's d` = round(cohen_d, 2)
@@
 # Data Import and Preprocessing ------------------------------------------
-df_sri <- read_xlsx("data/Coding_SRI.xlsx") %>%
+df_sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
+  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
   filter(
-    !ID %in% c(201, 223),
-    !disruption_appraisal %in% c(-100, -99, -88),
-    !confidence_appraisal %in% c(-100, -99, -88),
-    !prevalence_rating %in% c(-100, -99, -88)
-  ) %>%  rename(Participant = ID) %>%
+    !ID %in% c(201, 223),  # Removing invalid IDs
+    !disruption_appraisal %in% c(-100, -99, -88),  # Removing invalid disruption appraisals
+    !confidence_appraisal %in% c(-100, -99, -88),  # Removing invalid confidence appraisals
+    !prevalence_rating %in% c(-100, -99, -88)  # Removing invalid prevalence ratings
+  ) %>%
+  mutate(
+    Group = ifelse(ID < 200, "Novice", "Expert"),  # Create a Group column based on ID
+    Participant = ID,  # Keep ID as is for Participant column
+    Disruption_Appraisal = as.numeric(disruption_appraisal),
+    Confidence_Appraisal = as.numeric(confidence_appraisal),
+    Prevalence_Rating = as.numeric(prevalence_rating)
+  ) %>%
+  select(-ID) %>% # Remove the original ID column after renaming
+  arrange(Participant)
+
+# Summarize the SRI Data for Disruptions and Overall Columns
+
+# Step 1: Filter for specific disruptions
+verbal_disruptions <- c("whispering", "chatting")
+lack_of_eagerness <- c("drawing", "looking at phone")
+
+# Step 2: Summarize appraisals for each disruption
+df_sri_disrup_summary <- df_sri %>%
+  filter(event %in% c(verbal_disruptions, lack_of_eagerness)) %>%
+  group_by(Participant, event) %>%
+  summarise(
+    Disruption_Appraisal_Mean = mean(disruption_appraisal, na.rm = TRUE),
+    Confidence_Appraisal_Mean = mean(confidence_appraisal, na.rm = TRUE),
+    .groups = "drop"
+  ) %>%
+  pivot_wider(
+    names_from = event,
+    values_from = c(Disruption_Appraisal_Mean, Confidence_Appraisal_Mean),
+    names_sep = "_"
+  ) %>%
+  mutate(across(everything(), ~ replace_na(., 0))) %>%   # Replace missing values with 0
+  arrange(Participant)
+
+# Step 3: Summarize overall appraisals by Participant
+df_sri_clean <- df_sri %>%
   group_by(Participant) %>%
   summarise(
-    Disruption_appraisal = round(mean(disruption_appraisal, na.rm = TRUE), 2),
-    Confidence_appraisal = round(mean(confidence_appraisal, na.rm = TRUE), 2),
-    Prevalence_rating = round(mean(prevalence_rating, na.rm = TRUE), 2)
+    Disruption_Appraisal = round(mean(Disruption_Appraisal, na.rm = TRUE), 2),
+    Confidence_Appraisal = round(mean(Confidence_Appraisal, na.rm = TRUE), 2),
+    Prevalence_Rating = round(mean(Prevalence_Rating, na.rm = TRUE), 2),
+    .groups = "drop"
   ) %>%
   arrange(Participant)
+
+# Combine both summaries (disruption-specific and overall)
+df_sri_combined <- full_join(df_sri_clean, df_sri_disrup_summary, by = "Participant")
 
@@
 
+# Ensure Participant is consistent across all dataframes
+df_demo <- df_demo %>% mutate(Participant = as.numeric(Participant))
+df_aoi_numb_dur <- df_aoi_numb_dur %>% mutate(Participant = as.numeric(Participant))
+df_aoi_stud <- df_aoi_stud %>% mutate(Participant = as.numeric(Participant))
+df_aoi_disrup <- df_aoi_disrup %>% mutate(Participant = as.numeric(Participant))
+df_ttff_disrup_participant_summary <- df_ttff_disrup_participant_summary %>% mutate(Participant = as.numeric(Participant))
+df_sri_combined <- df_sri_combined %>% mutate(Participant = as.numeric(Participant))
+df_sjt <- df_sjt %>% mutate(Participant = as.numeric(Participant))
+df_quest_summary <- df_quest_summary %>% mutate(Participant = as.numeric(Participant))
+
+# Merge the dataframes
 df_list <- list(
@@
   df_ttff_disrup_participant_summary,
-  df_sri,
+  df_sri_combined,
   df_sjt,
@@
 
+# Combine all dataframes by Participant
 df_merge <- reduce(df_list, full_join, by = "Participant")
 
-# 3. Correlation Analysis ---------------------------------------------
+# Load required libraries
+library(tidyverse)
+library(Hmisc)
+library(knitr)
+library(kableExtra)
+
+# 3. Correlation Analysis: Overall ---------------------------------------------
 
 # Select relevant variables for correlation analysis
+
 df_correlation <- df_merge %>%
   select(
+    Participant,
     `Teaching Experience`, 
@@
     Disrup_time_fixation_sec, 
-    Disruption_appraisal, 
-    Confidence_appraisal, 
+    Disruption_Appraisal, 
+    Confidence_Appraisal, 
+    Prevalence_Rating,
+    Disruption_Appraisal_Mean_chatting,
+    Disruption_Appraisal_Mean_drawing,
+    Disruption_Appraisal_Mean_whispering,
+    Confidence_Appraisal_Mean_chatting,
+    Confidence_Appraisal_Mean_drawing,
+    Confidence_Appraisal_Mean_whispering,
     SJT_All, 
@@
 
-# Compute the correlation matrix
-cor_matrix <- cor(df_correlation, use = "complete.obs")
-
-# Visualize the correlation matrix
-corrplot(cor_matrix, method = "circle", type = "lower", order = "hclust", tl.col = "black", tl.srt = 45)
-
-# 4. Correlation Analysis with Experts ---------------------------------------------
+# Compute correlation coefficients and p-values for the full dataset
+cor_results <- rcorr(as.matrix(df_correlation))
+cor_matrix <- as.data.frame(cor_results$r)  # Extract correlation coefficients
+p_matrix <- as.data.frame(cor_results$P)   # Extract p-values
+
+# Reshape correlation coefficients and p-values into a tidy format
+correlation_pvalues <- cor_matrix %>%
+  rownames_to_column(var = "Variable1") %>%
+  pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
+  left_join(
+    p_matrix %>%
+      rownames_to_column(var = "Variable1") %>%
+      pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
+    by = c("Variable1", "Variable2")
+  ) %>%
+  mutate(
+    Correlation = round(Correlation, 2),  # Round correlation coefficients
+    P_value = round(P_value, 2),          # Round p-values
+    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))  # Format APA style
+  )
+
+# Create an APA-style table
+correlation_table <- correlation_pvalues %>%
+  select(Variable1, Variable2, APA_Format) %>%
+  pivot_wider(
+    names_from = Variable2,
+    values_from = APA_Format
+  )
+
+# Display the table
+kable(correlation_table, format = "html", caption = "Correlation Table: Overall") %>%
+  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
+
+# 4. Correlation Analysis: Experts ---------------------------------------------
 
@@
 df_experts <- df_merge %>%
-  filter(Participant > 200)  # Only include Experts (ID > 200)
-
-# Select relevant variables for correlation analysis with Teaching Experience
-df_correlation_experts <- df_experts %>%
-  select(
-    `Teaching Experience`, 
-    Number_fixation_min_mtu, 
-    Average_duration_mtu, 
-    GRI_mtu, 
-    Stud_number_fixation_min, 
-    Average_duration_stud, 
-    Disrup_fixations_per_second, 
-    Disrup_average_fixations, 
-    Disrup_time_fixation_sec, 
-    Disruption_appraisal, 
-    Confidence_appraisal, 
-    SJT_All, 
-    SJT_Monitoring, 
-    Self_Eval_CM, 
-    Self_Eval_Presence
-  )
-
-# Check the column types to make sure they are numeric
-sapply(df_correlation_experts, class)
-
-# Compute the correlation matrix
-cor_matrix_experts <- cor(df_correlation_experts, use = "complete.obs")
-
-# Visualize the correlation matrix
-corrplot(cor_matrix_experts, method = "circle", type = "lower", order = "hclust", tl.col = "black", tl.srt = 45)
-
-# 5. Correlation Analysis with Novices ---------------------------------------------
+  filter(Participant > 200) %>% 
+  select(-Participant)
+
+# Compute correlation coefficients and p-values for Experts
+cor_results_experts <- rcorr(as.matrix(df_experts))
+cor_matrix_experts <- as.data.frame(cor_results_experts$r)  # Extract correlation coefficients
+p_matrix_experts <- as.data.frame(cor_results_experts$P)   # Extract p-values
+
+# Reshape data into tidy format for Experts
+correlation_pvalues_experts <- cor_matrix_experts %>%
+  rownames_to_column(var = "Variable1") %>%
+  pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
+  left_join(
+    p_matrix_experts %>%
+      rownames_to_column(var = "Variable1") %>%
+      pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
+    by = c("Variable1", "Variable2")
+  ) %>%
+  mutate(
+    Correlation = round(Correlation, 2),
+    P_value = round(P_value, 2),
+    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
+  )
+
+# Create an APA-style table for Experts
+correlation_table_experts <- correlation_pvalues_experts %>%
+  select(Variable1, Variable2, APA_Format) %>%
+  pivot_wider(
+    names_from = Variable2,
+    values_from = APA_Format
+  )
+
+# Display the Experts table
+kable(correlation_table_experts, format = "html", caption = "Correlation Table: Experts") %>%
+  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
+
+# 5. Correlation Analysis: Novices ---------------------------------------------
 
@@
 df_novices <- df_merge %>%
-  filter(Participant < 200)  # Only include Novices (ID < 200)
-
-# Select relevant variables for correlation analysis without Teaching Experience
-df_correlation_novices <- df_novices %>%
-  select(
-    Number_fixation_min_mtu, 
-    Average_duration_mtu, 
-    GRI_mtu, 
-    Stud_number_fixation_min, 
-    Average_duration_stud, 
-    Disrup_fixations_per_second, 
-    Disrup_average_fixations, 
-    Disrup_time_fixation_sec, 
-    Disruption_appraisal, 
-    Confidence_appraisal, 
-    SJT_All, 
-    SJT_Monitoring, 
-    Self_Eval_CM, 
-    Self_Eval_Presence
-  )
-
-# Ensure all selected columns are numeric and handle non-numeric entries
-df_correlation_novices_clean <- df_correlation_novices %>%
-  mutate(across(everything(), as.numeric))  # Convert all columns to numeric
-
-# Remove rows with any NA or problematic values
-df_correlation_novices_clean <- df_correlation_novices_clean %>%
-  drop_na()  # Remove rows with NA values
-
-# Check if all columns are numeric after conversion
-sapply(df_correlation_novices_clean, class)
-
-# Compute the correlation matrix for Novices
-cor_matrix_novices <- cor(df_correlation_novices_clean, use = "complete.obs")
-
-# Visualize the correlation matrix for Novices
-corrplot(cor_matrix_novices, method = "circle", type = "lower", order = "hclust", tl.col = "black", tl.srt = 45)
+  filter(Participant < 200) %>% 
+  select(-`Teaching Experience`,
+         -Participant)
+
+# Compute correlation coefficients and p-values for Novices
+cor_results_novices <- rcorr(as.matrix(df_novices))
+cor_matrix_novices <- as.data.frame(cor_results_novices$r)  # Extract correlation coefficients
+p_matrix_novices <- as.data.frame(cor_results_novices$P)   # Extract p-values
+
+# Reshape data into tidy format for Novices
+correlation_pvalues_novices <- cor_matrix_novices %>%
+  rownames_to_column(var = "Variable1") %>%
+  pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
+  left_join(
+    p_matrix_novices %>%
+      rownames_to_column(var = "Variable1") %>%
+      pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
+    by = c("Variable1", "Variable2")
+  ) %>%
+  mutate(
+    Correlation = round(Correlation, 2),
+    P_value = round(P_value, 2),
+    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
+  )
+
+# Create an APA-style table for Novices
+correlation_table_novices <- correlation_pvalues_novices %>%
+  select(Variable1, Variable2, APA_Format) %>%
+  pivot_wider(
+    names_from = Variable2,
+    values_from = APA_Format
+  )
+
+# Display the Novices table
+kable(correlation_table_novices, format = "html", caption = "Correlation Table: Novices") %>%
+  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
+
 ```

### 2024-12-11 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper

@@
 # Step 7: Plot with descending AOI order, y-axis limit set to 100%, and percentage labels inside the bars
-ggplot(grouped_aoi_percentages, aes(x = reorder(AOI, -Fixation_Percentage), y = Fixation_Percentage, fill = Group)) +
-  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
-  geom_text(aes(label = paste0(Fixation_Percentage, "%")), 
+percentage_number_fixation <-
+  ggplot(grouped_aoi_percentages,
+         aes(
+           x = reorder(AOI, -Fixation_Percentage),
+           y = Fixation_Percentage,
+           fill = Group
+         )) +
+  geom_bar(stat = "identity",
            position = position_dodge(width = 0.8),
-            vjust = -0.3, size = 3) +
-  labs(
-    title = "Average Fixation Percentage by AOI and Group (Descending Order)",
-    x = "AOI",
-    y = "Fixation Percentage (%)"
+           width = 0.7) +
+  geom_text(
+    aes(label = paste0(Fixation_Percentage, "%")),
+    position = position_dodge(width = 0.8),
+    vjust = -0.3,
+    size = 3
   ) +
+  labs(title = "Average Fixation Percentage by AOI and Group (Descending Order)", x = "AOI", y = "Fixation Percentage (%)") +
   scale_fill_brewer(palette = "RdBu") +
-  theme_minimal() +
+  theme_cowplot() +
   theme(
@@
   ylim(0, 100)  # Set y-axis limit to 100%
+
+ggsave(filename = "plots/percentage_number_fixation.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
 
@@
 plot_number_group
+
+ggsave(filename = "plots/plot_number_group.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
 
@@
 
+ggsave(filename = "plots/plot_number_min_stud.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
+
 # 4. t-Test and Effect Size Calculation for Number of Fixations per Minute on AOI Students
@@
 y_max_overall <- max(individual_summary$mean_fixations_per_second, na.rm = TRUE) * 1.5
-plot_overall <- ggplot(individual_summary, aes(x = Group, y = mean_fixations_per_second, fill = Group)) +
+plot_overall_fix_disrup <- ggplot(individual_summary,
+          aes(x = Group, y = mean_fixations_per_second, fill = Group)) +
   geom_boxplot(outlier.shape = NA, width = 0.5) +
-  geom_jitter(width = 0.1, alpha = 0.7, color = "black", size = 1.5) +
+  geom_jitter(
+    width = 0.1,
+    alpha = 0.7,
+    color = "black",
+    size = 1.5
+  ) +
   labs(x = "", y = "Mean Fixations per Second per Participant") +
@@
   theme(legend.position = "none") +
-  annotate("text", x = 1, y = y_max_overall * 0.85,
+  annotate(
+    "text",
+    x = 1,
+    y = y_max_overall * 0.85,
     label = paste0("M = ", mean_novice, "\nSD = ", sd_novice),
-           hjust = 0.5, size = 4, fontface = "italic") +
-  annotate("text", x = 2, y = y_max_overall * 0.85,
+    hjust = 0.5,
+    size = 4,
+    fontface = "italic"
+  ) +
+  annotate(
+    "text",
+    x = 2,
+    y = y_max_overall * 0.85,
     label = paste0("M = ", mean_expert, "\nSD = ", sd_expert),
-           hjust = 0.5, size = 4, fontface = "italic") +
-  annotate("text", x = 1.5, y = y_max_overall * 0.95,
+    hjust = 0.5,
+    size = 4,
+    fontface = "italic"
+  ) +
+  annotate(
+    "text",
+    x = 1.5,
+    y = y_max_overall * 0.95,
     label = paste0("p = ", p_value, "\nd = ", cohen_d),
-           hjust = 0.5, size = 4, fontface = "italic")
+    hjust = 0.5,
+    size = 4,
+    fontface = "italic"
+  )
+
+ggsave(filename = "plots/plot_overall_fix_disrup.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
 
@@
 # Create the plot
-plot_category <- disruption_summary %>%
+plot_category_fix_disrup <- disruption_summary %>%
   ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
@@
 
+ggsave(filename = "plots/plot_category_fix_disrup.svg",
+       width = 24,
+       height = 12,
+       units = "cm")
+
 # Display the plots
-plot_overall
+plot_overall_fix_disrup
 plot_category
@@
 
+ggsave(filename = "plots/plot_duration_group.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
+
 # Plot 2: Disruption Duration by Group and Category
@@
 plot_duration_category
+
+ggsave(filename = "plots/plot_duration_category.svg",
+       width = 24,
+       height = 12,
+       units = "cm")
 
@@
 # Step 6: Plot the fixation duration percentages by AOI and Group
-ggplot(grouped_aoi_durations_percentages, aes(x = reorder(AOI, -Duration_Percentage), y = Duration_Percentage, fill = Group)) +
-  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
-  geom_text(aes(label = paste0(Duration_Percentage, "%")), 
+percentage_duration_fixation <- ggplot(
+  grouped_aoi_durations_percentages,
+  aes(
+    x = reorder(AOI, -Duration_Percentage),
+    y = Duration_Percentage,
+    fill = Group
+  )
+) +
+  geom_bar(stat = "identity",
            position = position_dodge(width = 0.8),
-            vjust = -0.3, size = 3) +
-  labs(
-    title = "Total Fixation Duration Percentage by AOI and Group (Descending Order)",
-    x = "AOI",
-    y = "Fixation Duration Percentage (%)"
+           width = 0.7) +
+  geom_text(
+    aes(label = paste0(Duration_Percentage, "%")),
+    position = position_dodge(width = 0.8),
+    vjust = -0.3,
+    size = 3
   ) +
+  labs(title = "Total Fixation Duration Percentage by AOI and Group (Descending Order)", x = "AOI", y = "Fixation Duration Percentage (%)") +
   scale_fill_brewer(palette = "RdBu") +
-  theme_minimal() +
+  theme_cowplot() +
   theme(
@@
   ylim(0, 100)  # Set y-axis limit to 100%
+
+ggsave(
+  filename = "plots/percentage_duration_fixation.svg",
+  width = 24,
+  height = 12,
+  units = "cm"
+)
 
@@
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Average Fixation Duration\n(micro-teaching unit)") +
+  ggtitle("Average Fixation Duration\n(Micro-Teaching Unit)") +
   theme_cowplot() +
@@
 plot_avg_fixation_group
+
+ggsave(
+  filename = "plots/plot_avg_fixation_group.svg",
+  width = 20,
+  height = 12,
+  units = "cm"
+)
 
@@
 
+ggsave(
+  filename = "plots/plot_average_duration_stud.svg",
+  width = 20,
+  height = 12,
+  units = "cm"
+)
+
 # 4. t-Test and Effect Size Results Table
@@
 y_max_overall <- max(individual_summary$mean_duration, na.rm = TRUE) * 1.5
-plot_overall <- ggplot(individual_summary, aes(x = Group, y = mean_duration, fill = Group)) +
+plot_overall_dur_disrup <- ggplot(individual_summary, aes(x = Group, y = mean_duration, fill = Group)) +
   geom_boxplot(outlier.shape = NA, width = 0.5) +
@@
 
+ggsave(
+  filename = "plots/plot_overall_dur_disrup.svg",
+  width = 20,
+  height = 12,
+  units = "cm"
+)
+
 # Plot by category
-plot_category <- disruption_summary %>%
+plot_category_dur_disrup <- disruption_summary %>%
   ggplot(aes(x = Group, y = mean_duration_ms, fill = Group)) +  # Ensure using correct column name here
@@
     strip.text = element_text(size = 10)
+  )
+
+ggsave(
+  filename = "plots/plot_category_dur_disrup.svg",
+  width = 24,
+  height = 12,
+  units = "cm"
 )

### 2024-12-19 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.Rmd
literatur_vz
plots plots plots

@@
   - \hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}
-  - \setcitestyle{numbers, sort&compress}
+  - \setcitestyle{numbers}
   - \usepackage{tabularx}
@@
                              b = 5),
-        text = element_text(family = "Times",
+        text = element_text(family = "Sans-Serif",
                             size = 14)
@@
                                                  size = 14,       
-                                                 family = "Times")
+                                                 family = "Sans-Serif")
                               )
@@
 ggsave(loess_comp,
-       filename = "plots_publication/loess_plot_std_unstd_new.pdf",
+       filename = "plots_publication/loess_plot_std_unstd_new.svg",
        width = 25,
@@
 box_plot <-
-  main_single_hr |> 
-  filter(time_span != "overall") |>  
+  main_single_hr %>% 
+  filter(time_span != "overall") %>%
   dplyr::select("ID",
          "time_span",
-         "heart_rate_std") |> 
+         "heart_rate_std") %>% 
   mutate(time_span = fct_recode(time_span,
@@
                             )
-         ) |> 
-  distinct() |> 
-  group_by(ID, time_span) |> 
+         ) %>%
+  distinct() %>% 
+  group_by(ID, time_span) %>%
   summarise(mean_hr_std = 
@@
                    na.rm = TRUE)
-            ) |> 
+            ) %>% 
   ggplot(mapping = aes(x = time_span,
@@
          ) +
-  geom_boxplot()+
+  geom_boxplot() +
+  stat_summary(
+    fun = mean, geom = "point", 
+    shape = 4, size = 3, color = "red" # Mean as red "x"
+  ) +
+  stat_summary(
+    fun.data = mean_sdl, 
+    fun.args = list(mult = 1), 
+    geom = "errorbar", 
+    width = 0.2, color = "blue" # SD as blue error bars
+  ) +
 scale_y_continuous(breaks=seq(-2, 2, 1), 
@@
                      ) +
-  # geom_jitter(width = 0.2) +
   theme_apa() + 
-  theme(text = element_text(family = "Times"),
-        axis.text.x = element_text(
+  theme(axis.text.x = 
+          element_text(family = 'Sans-Serif',
             color="black",
-            size = 14,
-            family = "Times"),
+            size = 12),
         plot.caption = element_text(hjust = 0)
@@
   labs(x = "",
-       y = "Mean Standardized Heart Rate",
-       caption = expression(
-         paste(italic("Note: N"), 
-               "= 81 participants per interval. Fig. shows median (bold line), interquartile range (box) and outliers (dots)."
-         )
-       ))
-
-ggsave(filename = "plots_publication/box_plot.pdf",
+       y = "Mean Standardized Heart Rate Level"
+         )
+
+ggsave(filename = "plots_publication/box_plot.svg",
        plot = box_plot,
@@
         ylab('Heart Rate (Standardized)') +  # Y-axis label (similar to 'Nettoeinkommen')
+        ylim(-4, 4) +
         scale_x_continuous(breaks = c(0, 5, 10)) +  # Customize x-axis breaks as needed
@@
         theme_bw() + # Use a clean theme
-        theme(text = element_text(family = "Times",
-                                  size = 14)
+        theme(text = element_text(size = 14,
+                                  family = 'Sans-Serif')
               )
@@
 ggsave(preparation_plot,
-       filename = "plots_publication/plot_preparation_appendix.pdf",
+       filename = "plots_publication/plot_preparation_appendix.svg",
        width = 25,
@@
 ggsave(teaching_plot,
-       filename = "plots_publication/plot_teaching_appendix.pdf",
+       filename = "plots_publication/plot_teaching_appendix.svg",
        width = 25,
@@
 ggsave(post_teaching_plot,
-       filename = "plots_publication/plot_post_teaching_appendix.pdf",
+       filename = "plots_publication/plot_post_teaching_appendix.svg",
        width = 25,
@@
 ggsave(interview_plot,
-       filename = "plots_publication/plot_interview_appendix.pdf",
+       filename = "plots_publication/plot_interview_appendix.svg",
        width = 25,
@@
 ggsave(end_plot,
-       filename = "plots_publication/plot_end_appendix.pdf",
+       filename = "plots_publication/plot_end_appendix.svg",
        width = 25,

### 2024-12-19 02_paper/02_study/01_fitbit_paper/analysis_270423.Rmd
blabla

--- 2024-09-17 02_paper/02_study/01_fitbit paper/analysis_270423.Rmd
@@
 
-## Box Plot (over 81 participants) 
 box_plot <-
@@
          ) +
-  geom_boxplot()+
+  geom_boxplot() +
+  stat_summary(
+    fun = mean, geom = "point", 
+    shape = 4, size = 3, color = "red" # Mean as red "x"
+  ) +
+  stat_summary(
+    fun.data = mean_sdl, 
+    fun.args = list(mult = 1), 
+    geom = "errorbar", 
+    width = 0.2, color = "blue" # SD as blue error bars
+  ) +
   scale_y_continuous(breaks=seq(-2, 2, 1), 
@@
                      ) +   
-  # geom_jitter(width = 0.2) +
   theme_apa() + 
@@
   labs(x = "",
-       y = "Mean Standardized Heart Rate",
-       caption = expression(
-         paste(italic("Note: N"), 
-               "= 81 participants per interval. Fig. shows median (bold line), interquartile range (box) and outliers (dots)."
-         )
-       ))
+       y = "Mean Standardized Heart Rate Level")
+)
 
@@
 
-ggsave(filename = "plots_publication/box_plot.png",
+ggsave(filename = "plots_publication/box_plot.svg",
        plot = box_plot,

### 2025-01-15 02_paper/02_study/02_expertise_paper/old R scripts/expertise_2024_09_26_no_outlierdetection_MK.Rmd
update

--- 2024-11-14 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
@@
 
-##################### GRI IN MICRO-TEACHING UNIT ########################
-
-# filter group, participants, total duration & number fixation in entire micro-teaching unit
-df_aoi_sum %>%
-  group_by(Group) %>% 
-  mutate(
-    GRI = round(Average_duration_mtu / Number_fixation_min_mtu, digits = 2),
-    )-> df_gri
-
-# N, M, SD, min & max number of fixation (micro-teaching unit)
-gri.table <-
-  df_gri %>%
+##################### GRI in MICRO-TEACHING UNIT ########################
+
+# Step 1: Calculate GRI (Gaze Ratio Index) for each participant
+df_gri <- df_aoi_sum %>%
+  mutate(GRI = round(Average_duration_fixation / Number_fixation_min_mtu, 2))
+
+# Step 2: Summarize GRI statistics (N, Mean, SD, Min, Max) by Group
+gri_table <- df_gri %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M" = round(mean(GRI), digits = 2),
-    "SD" = round(sd(GRI), digits = 2),
-    "Min" = round(min(GRI), digits = 2),
-    "Max" = round(max(GRI), digits = 2)
-  )
-
-knitr::kable(gri.table,
-             caption = "N, M, SD, min & max GRI (micro-teaching unit)")
-
-# plotting number of fixations on ALL AOIS
-df_gri %>%
-  ggplot(mapping = aes(x = Group, y = GRI)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
+    "M" = round(mean(GRI, na.rm = TRUE), 2),
+    "SD" = round(sd(GRI, na.rm = TRUE), 2),
+    "Min" = round(min(GRI, na.rm = TRUE), 2),
+    "Max" = round(max(GRI, na.rm = TRUE), 2)
+  )
+
+# Display the GRI summary table in APA format
+knitr::kable(gri_table,
+             caption = "N, M, SD, Min, and Max GRI (Micro-Teaching Unit)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Step 3: Plot GRI by Group with boxplot and jittered points
+# Calculate annotation values
+mean_novice_gri <- round(mean(df_gri$GRI[df_gri$Group == "Novice"], na.rm = TRUE), 2)
+sd_novice_gri <- round(sd(df_gri$GRI[df_gri$Group == "Novice"], na.rm = TRUE), 2)
+mean_expert_gri <- round(mean(df_gri$GRI[df_gri$Group == "Expert"], na.rm = TRUE), 2)
+sd_expert_gri <- round(sd(df_gri$GRI[df_gri$Group == "Expert"], na.rm = TRUE), 2)
+
+# Maximum y-axis value for plot
+y_max_gri <- max(df_gri$GRI, na.rm = TRUE) * 1.2
+
+# Conduct t-test
+t_test_gri <- t.test(
+  GRI ~ Group,
+  data = df_gri,
+  var.equal = TRUE
+)
+
+# Extract p-value
+p_value_gri <- round(t_test_gri$p.value, 3)
+
+# Calculate Cohen's d (full result object)
+d_gri_full <- cohen.d(GRI ~ Group, data = df_gri, pooled = TRUE)
+
+# Extract Cohen's d and confidence interval
+d_gri <- round(d_gri_full$estimate, 2)
+d_conf_int_gri <- paste0("[", round(d_gri_full$conf.int[1], 2), ", ", round(d_gri_full$conf.int[2], 2), "]")
+
+# Annotated Plot
+plot_gri_group <- df_gri %>%
+  ggplot(aes(x = Group, y = GRI, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 2, alpha = 0.7, width = 0.1, height = 0.1, seed = 1) +
+  ylim(0, y_max_gri) +
+  labs(x = "", y = "Average Duration of Fixations /\nNumber of Fixations per Minute") +
+  scale_fill_brewer(palette = "RdBu") +
+  ggtitle("GRI\n(Micro-Teaching Unit)") +
+  theme_minimal() +
+  theme(
+    legend.position = "none",
+    plot.title = element_text(hjust = 0.5, face = "bold")
   ) +
-  ylim(0, 12) +
-  labs(x = "", y = "average duration of fixations/\nnumber of fixations per minute") +
-  scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("GRI\n(micro-teaching unit)") +
-  theme_cowplot() +
-  theme(legend.position = "none") -> plot_gri_group
+  # Annotate mean (M) and SD
+  annotate("text", x = 1, y = y_max_gri * 0.85,
+           label = paste0("atop(italic(M) == ", mean_novice_gri, ", italic(SD) == ", sd_novice_gri, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  annotate("text", x = 2, y = y_max_gri * 0.85,
+           label = paste0("atop(italic(M) == ", mean_expert_gri, ", italic(SD) == ", sd_expert_gri, ")"),
+           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
+  # Annotate p-value and Cohen's d
+  annotate("text", x = 1.5, y = y_max_gri * 0.95,
+           label = paste0("p = ", p_value_gri, "\nd = ", d_gri),
+           hjust = 0.5, size = 4, fontface = "italic")
 
@@
     N = n(),
-    "M in sec" = round(mean(Disrup_time_fixation_sec), digits = 2),
-    "SD in sec" = round(sd(Disrup_time_fixation_sec), digits = 2),
-    "Min in sec" = round(min(Disrup_time_fixation_sec), digits = 2),
-    "Max in sec" = round(max(Disrup_time_fixation_sec), digits = 2)
-  )
-
-knitr::kable(ttff.disrup.table,
-             caption = "N, M, SD, min & max time to first fixation in seconds (AOI disruptive person)")
-
-############### M, SD, min, max of the perceived "Disruptive Person" ############### 
-number.perceived.disrup.table <-
- df_ttff_disrup %>%
-  filter(!Participant %in% c("216", "113", "123")) %>%
-  group_by(Group) %>%
+    "M in sec" = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "SD in sec" = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Min in sec" = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Max in sec" = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2)
+  )
+
+knitr::kable(ttff_disrup_table,
+             caption = "N, M, SD, Min & Max Time to First Fixation in Seconds (AOI Disruptive Person)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Step 3: Split Data by Disruption Categories
+disruption_summary <- df_ttff_disrup %>%
+  group_by(Group, Disruption_Category) %>%
   summarise(
-    N = n(),
-    Mean = round(mean(N, na.rm = TRUE), digits = 2),
-    SD = round(sd(N, na.rm = TRUE), digits = 2), 
-    Min = min(N, na.rm = TRUE),
-    Max = max(N, na.rm = TRUE)
-  )
-
-knitr::kable(number.perceived.disrup.table,
-             caption = "N, M, SD, min & max of the perceived ´disruptive person´")
-
-############### PLOTTING ###############
-
-##################### plotting "perceived disruptive person" for groups ##################### 
-plot_n_disrup <- 
-  df_ttff_disrup %>%
-  filter(!Participant %in% c("216", "113", "123")) %>%
-  ggplot(mapping = aes(x = Group,
-                       y = N)) +
- geom_boxplot(mapping = aes(fill = Group),
-               outlier.shape = NA) +
-  geom_point(size = 2,
-             alpha = 0.7,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  ylim(0,10) +
-  labs(x ="",
-       y = "Counts") + 
+    Mean_Time_to_Fixation = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    SD_Time_to_Fixation = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    .groups = "drop"
+  )
+
+# Step 4: Plotting Time to First Fixation by Group and Overall
+# a) By Group
+y_max <- max(df_ttff_disrup$Disrup_time_fixation_sec, na.rm = TRUE) * 1.2
+
+# Calculate mean and SD for Experts and Novices
+mean_expert_ttff <- mean(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE)
+sd_expert_ttff <- sd(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE)
+mean_novice_ttff <- mean(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE)
+sd_novice_ttff <- sd(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE)
+
+# Conduct t-test and calculate Cohen's d for the overall data
+t_test_overall <- t.test(Disrup_time_fixation_sec ~ Group, data = df_ttff_disrup, var.equal = TRUE)
+p_value_ttff <- round(t_test_overall$p.value, 3)
+d_overall <- cohen.d(Disrup_time_fixation_sec ~ Group, data = df_ttff_disrup)
+cohen_d_ttff <- round(d_overall$estimate, 2)
+
+# Annotated Plot
+plot_time_disrup <- df_ttff_disrup %>%
+  ggplot(mapping = aes(x = Group, y = Disrup_time_fixation_sec, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(size = 2, alpha = 0.7, width = 0.1, height = 0.1) +
+  ylim(0, y_max) +
+  labs(x = "", y = "Time to First Fixation (sec)") +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Counts of the perceived ´disruptive person´\n") +
-  theme_cowplot() +
-  theme(legend.position="none")
-
-plot_n_disrup
-
-##################### plotting time to first fixation for groups ##################### 
-plot_time_disrup <- 
-  df_ttff_disrup %>%
-  filter(!Participant %in% c("216", "113", "123")) %>%
-  ggplot(mapping = aes(x = Group,
-                       y = Disrup_time_fixation_sec)) +
- geom_boxplot(mapping = aes(fill = Group),
-               outlier.shape = NA) +
-  geom_point(size = 2,
-             alpha = 0.7,
-             position = position_jitter(seed = 1,
-                                        width = 0.1,
-                                        height = 0.1)) +
-  ylim(0,10) +
-  labs(x ="",
-       y = "Seconds") + 
-  scale_fill_brewer(palette  = "RdBu") +
-  ggtitle("Time to first fixation\n(AOI disruptive person)") +
-  theme_cowplot() +
-  theme(legend.position="none")
-
+  ggtitle("Time to First Fixation\n(AOI Disruptive Person)") +
+  theme_apa() +
+  theme(legend.position = "none") +
+  # Annotate means and SDs for Experts and Novices
+  annotate("text", x = 1, y = y_max * 0.85,
+           label = paste0("M = ", round(mean_expert_ttff, 2), "\nSD = ", round(sd_expert_ttff, 2)),
+           hjust = 0.5, size = 4.5, fontface = "italic") +
+  annotate("text", x = 2, y = y_max * 0.85,
+           label = paste0("M = ", round(mean_novice_ttff, 2), "\nSD = ", round(sd_novice_ttff, 2)),
+           hjust = 0.5, size = 4.5, fontface = "italic") +
+  # Annotate p-value and Cohen's d between the groups
+  annotate("text", x = 1.5, y = y_max * 0.95,
+           label = paste0("p = ", p_value_ttff, "\nd = ", cohen_d_ttff),
+           hjust = 0.5, size = 4.5, fontface = "italic")
+
+# Display the final plot with improved readability
 plot_time_disrup
 
-```
-
-#### t-test & effect size "Time to first fixation" (AOI disruptive person)
-```{r ttff_disrup_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-# TIME TO FIRST FIXATIONS on disruptive person 
-# t-test for expertise differences
-t.test(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
-       y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
-       var.equal = TRUE)
-
-# TIME TO FIRST FIXATIONS on disruptive person 
-# effect size for expertise differences
-d_time_disrup <- CohenD(x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"],
-                    y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"],
-                    na.rm = TRUE)
-
-round(d_time_disrup, 2)
+# Step 5: Statistical Tests by Category
+category_results <- list()
+
+for (category in unique(df_ttff_disrup$Disruption_Category)) {
+  cat_data <- df_ttff_disrup %>% filter(Disruption_Category == category)
+  t_cat <- t.test(Disrup_time_fixation_sec ~ Group, data = cat_data, var.equal = TRUE)
+  d_cat <- cohen.d(Disrup_time_fixation_sec ~ Group, data = cat_data)
+  category_results[[category]] <- data.frame(
+    "Group Comparison" = "Experts vs. Novices",
+    "Disruption Category" = category,
+    "t-value" = round(t_cat$statistic, 2),
+    "df" = t_cat$parameter,
+    "p-value" = round(t_cat$p.value, 3),
+    "Mean Difference" = round(t_cat$estimate[1] - t_cat$estimate[2], 2),
+    "Cohen's d" = round(d_cat$estimate, 2),
+    "95% CI (d)" = paste0("[", round(d_cat$conf.int[1], 2), ", ", round(d_cat$conf.int[2], 2), "]")
+  )
+}
+
+# Combine results into a single table
+category_stats <- do.call(rbind, category_results)
+
+knitr::kable(category_stats, 
+             caption = "t-Test and Effect Size for Time to First Fixation by Disruption Category") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 

### 2025-01-15 02_paper/02_study/02_expertise_paper/old R scripts/expertise_2024_09_26_no_outlierdetection_MK.tex
update

--- 2024-11-06 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.tex
@@
 }
-\subsection{1. Participants}\label{participants}
+\subsection{Participants}\label{participants}
 
@@
 
-\subsection{2. Measures}\label{measures}
-
-\subsubsection{2.1 Eye-Tracking Data}\label{eye-tracking-data}
-
-\paragraph{2.2.2 Letter search}\label{letter-search}
+\subsection{Measures}\label{measures}
+
+\subsubsection{Eye-Tracking Data}\label{eye-tracking-data}
+
+\paragraph{Letter search}\label{letter-search}
 
@@
 
-\paragraph{2.2.1 Number of fixations per minute (micro-teaching
+\paragraph{Number of fixations per minute (micro-teaching
 unit)}\label{number-of-fixations-per-minute-micro-teaching-unit}
@@
 
-\paragraph{2.2.2 Number of fixations per minute (AOI
+\paragraph{Number of fixations per minute (AOI
 students)}\label{number-of-fixations-per-minute-aoi-students}
@@
 
-\paragraph{2.2.2 Number of fixations per minute (AOI
+\paragraph{Number of fixations per minute (AOI
 others)}\label{number-of-fixations-per-minute-aoi-others}
@@
 
-\paragraph{2.2.3 Number of fixations (AOI disruptive
+\subsubsection{ALL AOIs}\label{all-aois}
+
+\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/nof_all_aois-1.pdf}
+
+\paragraph{Number of fixations (AOI disruptive
 person)}\label{number-of-fixations-aoi-disruptive-person}
@@
 
-\paragraph{2.2.4 Average duration of fixations in milliseconds
-(micro-teaching
+\paragraph{Average duration of fixations in milliseconds (micro-teaching
 unit)}\label{average-duration-of-fixations-in-milliseconds-micro-teaching-unit}
@@
 
-\paragraph{2.2.5 Average duration of fixations (AOI
+\paragraph{Average duration of fixations (AOI
 students)}\label{average-duration-of-fixations-aoi-students}
@@
 
-\paragraph{2.2.6 Average duration of fixations (AOI disruptive
+\paragraph{Average duration of fixations (AOI disruptive
 person)}\label{average-duration-of-fixations-aoi-disruptive-person}
@@
 
-\paragraph{2.2.7 Gaze Relational Index (GRI; micro-teaching
+\paragraph{Gaze Relational Index (GRI; micro-teaching
 unit)}\label{gaze-relational-index-gri-micro-teaching-unit}
@@
 
-\paragraph{2.2.10 Time to first fixation in seconds (AOI disruptive
+\paragraph{Time to first fixation in seconds (AOI disruptive
 person)}\label{time-to-first-fixation-in-seconds-aoi-disruptive-person}
@@
 
-\subsubsection{2.2 Rating Scales (Disruption Appraisal, Confidence
+\subsubsection{Rating Scales (Disruption Appraisal, Confidence
 Appraisal, Prevalence
@@
 
-\section{\texorpdfstring{\texttt{\{r\ sri\_pr,\ echo=FALSE,\ message=FALSE,\ warning=FALSE,\ results=\textquotesingle{}asis\textquotesingle{}\}\ \#\ \ \#\ \#\#\#\#\#\#\#\#\#\#\#\#\#\#\ Prevalence\ Rating\ \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\ \#\ \ \#\ sri.preva.table\ \textless{}-\ \#\ \ \ sri\ \%\textgreater{}\%\ \#\ \ \ group\_by(ID)\ \%\textgreater{}\%\ \#\ \ \ summarise(\ \#\ \ \ \ \ N\ =\ n(),\ \#\ \ \ \ \ "M"\ =\ round(mean(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "SD"\ =\ round(sd(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "Min"\ =\ min(prevalence\_rating),\ \#\ \ \ \ \ "Max"\ =\ max(prevalence\_rating)\ \#\ \ \ )\ \#\ \ \#\ \#\ insert\ a\ table\ into\ HTML\ \#\ knitr::kable(sri.preva.table,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ caption\ =\ "Prevalence\ rating")\ \#\ \ \#\ \#\#\#\#\ with\ event\ \ \#\ sri.preva.event.table\ \textless{}-\ \#\ \ \ sri\ \%\textgreater{}\%\ \#\ \ \ group\_by(ID,\ event)\ \%\textgreater{}\%\ \#\ \ \ summarise(\ \#\ \ \ \ \ N\ =\ n(),\ \#\ \ \ \ \ "M"\ =\ round(mean(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "SD"\ =\ round(sd(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "Min"\ =\ min(prevalence\_rating),\ \#\ \ \ \ \ "Max"\ =\ max(prevalence\_rating)\ \#\ \ \ )\ \#\ \ \#\ \#\ insert\ a\ table\ into\ HTML\ \#\ knitr::kable(sri.preva.event.table,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ caption\ =\ "Prevalence\ rating\ with\ events")\ \#\ \ \#\ \#\ create\ a\ new\ data\ frame\ with\ rating\ \#\ sri\_preva\ \textless{}-\ subset.data.frame(sri,\ select\ =\ c(ID,\ event,\ prevalence\_rating))\ \#\ \ \#\ \#\ plotting\ prevalence\ rating\ for\ groups\ \#\ preva\_group\_plot\ \textless{}-\ \ \#\ \ \ sri\_preva\ \%\textgreater{}\%\ \ \#\ \ \ mutate(ID\ =\ factor(ID,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ levels\ =\ c("Novice",\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ "Expert"\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ )\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ )\ \#\ \ \ \ \ \ \ \ \ \ )\ \%\textgreater{}\%\ \ \#\ \ \ ggplot(mapping\ =\ aes(x\ =\ ID,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ =\ prevalence\_rating))\ +\ \#\ \ \ geom\_boxplot(mapping\ =\ aes(fill\ =\ ID),\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ outlier.shape\ =\ NA)\ +\ \#\ \ \ geom\_point(size\ =\ 1,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ alpha\ =\ 0.4,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ position\ =\ position\_jitter(seed\ =\ 1,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ width\ =\ 0.1,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ height\ =\ 0.1))\ +\ \#\ \ \ scale\_x\_discrete(limits\ =\ c("Novice",\ "Expert"))\ +\ \#\ \ \ scale\_y\_continuous(breaks\ =\ seq(from\ =\ 0,\ to\ =\ 10,\ by\ =\ 1))\ +\ \ \#\ \ \ labs(x\ =\ "",\ \#\ \ \ \ \ \ \ \ y\ =\ "Prevalence\ Rating")\ +\ \ \#\ \ \ scale\_fill\_brewer(palette\ \ =\ "RdBu")\ +\ \ \ \#\ \ \ ggtitle("How\ widespread\ is\ this\ event\ in\ the\ classroom?")\ +\ \#\ \ \ theme\_cowplot()\ \#\ \ \#\ preva\_group\_plot\ \#\ \ \#}}{\{r sri\_pr, echo=FALSE, message=FALSE, warning=FALSE, results=\textquotesingle asis\textquotesingle\} \#  \# \#\#\#\#\#\#\#\#\#\#\#\#\#\# Prevalence Rating \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\# \#  \# sri.preva.table \textless- \#   sri \%\textgreater\% \#   group\_by(ID) \%\textgreater\% \#   summarise( \#     N = n(), \#     "M" = round(mean(prevalence\_rating), digits = 2), \#     "SD" = round(sd(prevalence\_rating), digits = 2), \#     "Min" = min(prevalence\_rating), \#     "Max" = max(prevalence\_rating) \#   ) \#  \# \# insert a table into HTML \# knitr::kable(sri.preva.table, \#              caption = "Prevalence rating") \#  \# \#\#\#\# with event  \# sri.preva.event.table \textless- \#   sri \%\textgreater\% \#   group\_by(ID, event) \%\textgreater\% \#   summarise( \#     N = n(), \#     "M" = round(mean(prevalence\_rating), digits = 2), \#     "SD" = round(sd(prevalence\_rating), digits = 2), \#     "Min" = min(prevalence\_rating), \#     "Max" = max(prevalence\_rating) \#   ) \#  \# \# insert a table into HTML \# knitr::kable(sri.preva.event.table, \#              caption = "Prevalence rating with events") \#  \# \# create a new data frame with rating \# sri\_preva \textless- subset.data.frame(sri, select = c(ID, event, prevalence\_rating)) \#  \# \# plotting prevalence rating for groups \# preva\_group\_plot \textless-  \#   sri\_preva \%\textgreater\%  \#   mutate(ID = factor(ID, \#                      levels = c("Novice", \#                                 "Expert" \#                                 ) \#                      ) \#          ) \%\textgreater\%  \#   ggplot(mapping = aes(x = ID, \#                        y = prevalence\_rating)) + \#   geom\_boxplot(mapping = aes(fill = ID), \#                outlier.shape = NA) + \#   geom\_point(size = 1, \#              alpha = 0.4, \#              position = position\_jitter(seed = 1, \#                                         width = 0.1, \#                                         height = 0.1)) + \#   scale\_x\_discrete(limits = c("Novice", "Expert")) + \#   scale\_y\_continuous(breaks = seq(from = 0, to = 10, by = 1)) +  \#   labs(x = "", \#        y = "Prevalence Rating") +  \#   scale\_fill\_brewer(palette  = "RdBu") +   \#   ggtitle("How widespread is this event in the classroom?") + \#   theme\_cowplot() \#  \# preva\_group\_plot \#  \#}}\label{r-sri_pr-echofalse-messagefalse-warningfalse-resultsasis-prevalence-rating-sri.preva.table---sri-group_byid-summarise-n-n-m-roundmeanprevalence_rating-digits-2-sd-roundsdprevalence_rating-digits-2-min-minprevalence_rating-max-maxprevalence_rating-insert-a-table-into-html-knitrkablesri.preva.table-caption-prevalence-rating-with-event-sri.preva.event.table---sri-group_byid-event-summarise-n-n-m-roundmeanprevalence_rating-digits-2-sd-roundsdprevalence_rating-digits-2-min-minprevalence_rating-max-maxprevalence_rating-insert-a-table-into-html-knitrkablesri.preva.event.table-caption-prevalence-rating-with-events-create-a-new-data-frame-with-rating-sri_preva---subset.data.framesri-select-cid-event-prevalence_rating-plotting-prevalence-rating-for-groups-preva_group_plot---sri_preva-mutateid-factorid-levels-cnovice-expert-ggplotmapping-aesx-id-y-prevalence_rating-geom_boxplotmapping-aesfill-id-outlier.shape-na-geom_pointsize-1-alpha-0.4-position-position_jitterseed-1-width-0.1-height-0.1-scale_x_discretelimits-cnovice-expert-scale_y_continuousbreaks-seqfrom-0-to-10-by-1-labsx-y-prevalence-rating-scale_fill_brewerpalette-rdbu-ggtitlehow-widespread-is-this-event-in-the-classroom-theme_cowplot-preva_group_plot}
-
-\paragraph{t-Test \& effect size ``Prevalence
-rating''}\label{t-test-effect-size-prevalence-rating}
-
-\section{\texorpdfstring{\texttt{\{r\ sri\_pr\_ttest,\ echo=FALSE,\ message=FALSE,\ warning=FALSE,\ results=\textquotesingle{}asis\textquotesingle{}\}\ \#\ \ \#\ \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\ T-TEST\ \&\ EFFECT\ SIZE\ \#\#\#\#\#\#\#\#\#\#\#\#\ \#\ \ \#\ \#\ Prevalence\ Rating\ \ \#\ \#\ t-test\ for\ expertise\ differences\ \#\ t.test(x\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Expert"{]},\ \#\ \ \ \ \ \ \ \ y\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Novice"{]},\ \#\ \ \ \ \ \ \ \ var.equal\ =\ TRUE)\ \#\ \ \#\ \#\ Prevalence\ Rating\ \ \#\ \#\ effect\ size\ for\ expertise\ differences\ \#\ d\_sri\_preva\ \textless{}-\ CohenD(x\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Expert"{]},\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Novice"{]},\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ na.rm\ =\ TRUE)\ \#\ \ \#\ round(d\_sri\_preva,\ 2)\ \#\ \ \#}}{\{r sri\_pr\_ttest, echo=FALSE, message=FALSE, warning=FALSE, results=\textquotesingle asis\textquotesingle\} \#  \# \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\# T-TEST \& EFFECT SIZE \#\#\#\#\#\#\#\#\#\#\#\# \#  \# \# Prevalence Rating  \# \# t-test for expertise differences \# t.test(x = sri\$prevalence\_rating{[}sri\$ID == "Expert"{]}, \#        y = sri\$prevalence\_rating{[}sri\$ID == "Novice"{]}, \#        var.equal = TRUE) \#  \# \# Prevalence Rating  \# \# effect size for expertise differences \# d\_sri\_preva \textless- CohenD(x = sri\$prevalence\_rating{[}sri\$ID == "Expert"{]}, \#                       y = sri\$prevalence\_rating{[}sri\$ID == "Novice"{]}, \#                       na.rm = TRUE) \#  \# round(d\_sri\_preva, 2) \#  \#}}\label{r-sri_pr_ttest-echofalse-messagefalse-warningfalse-resultsasis-t-test-effect-size-prevalence-rating-t-test-for-expertise-differences-t.testx-sriprevalence_ratingsriid-expert-y-sriprevalence_ratingsriid-novice-var.equal-true-prevalence-rating-effect-size-for-expertise-differences-d_sri_preva---cohendx-sriprevalence_ratingsriid-expert-y-sriprevalence_ratingsriid-novice-na.rm-true-roundd_sri_preva-2}
+\subsubsection{Prevalence Rating as manipulation
+check}\label{prevalence-rating-as-manipulation-check}
+
+\begin{longtable}[]{@{}lrrrrr@{}}
+\caption{Prevalence rating}\tabularnewline
+\toprule\noalign{}
+ID & N & M & SD & Min & Max \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+ID & N & M & SD & Min & Max \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Expert & 352 & 6.53 & 2.72 & 1 & 10 \\
+Novice & 357 & 7.02 & 2.20 & 1 & 10 \\
+\end{longtable}
+
+\begin{longtable}[]{@{}llrrrrr@{}}
+\caption{Prevalence rating with events}\tabularnewline
+\toprule\noalign{}
+ID & event & N & M & SD & Min & Max \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+ID & event & N & M & SD & Min & Max \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Expert & chatting & 41 & 6.41 & 2.61 & 2 & 10 \\
+Expert & clicking pen & 38 & 5.76 & 2.54 & 1 & 10 \\
+Expert & drawing & 35 & 8.43 & 1.77 & 3 & 10 \\
+Expert & drumming & 39 & 6.00 & 2.56 & 1 & 10 \\
+Expert & head on table & 40 & 6.05 & 2.59 & 1 & 10 \\
+Expert & heckling & 41 & 5.15 & 2.70 & 1 & 10 \\
+Expert & looking at phone & 36 & 7.03 & 2.52 & 1 & 10 \\
+Expert & snipping & 41 & 5.27 & 2.77 & 1 & 10 \\
+Expert & whispering & 41 & 8.95 & 1.40 & 5 & 10 \\
+Novice & chatting & 42 & 6.86 & 2.18 & 1 & 10 \\
+Novice & clicking pen & 40 & 6.85 & 2.02 & 3 & 10 \\
+Novice & drawing & 35 & 8.40 & 1.48 & 4 & 10 \\
+Novice & drumming & 40 & 5.47 & 2.14 & 1 & 10 \\
+Novice & head on table & 40 & 6.62 & 1.85 & 3 & 10 \\
+Novice & heckling & 41 & 5.76 & 2.32 & 2 & 10 \\
+Novice & looking at phone & 35 & 7.26 & 2.05 & 3 & 10 \\
+Novice & snipping & 42 & 7.05 & 1.96 & 3 & 10 \\
+Novice & whispering & 42 & 9.05 & 1.23 & 4 & 10 \\
+\end{longtable}
+
+\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/sri_pr-1.pdf}
+Two Sample t-test
+
+data: sri\(prevalence_rating[sri\)ID == ``Expert''{]} and
+sri\(prevalence_rating[sri\)ID == ``Novice''{]} t = -2.6154, df = 707,
+p-value = 0.009103 alternative hypothesis: true difference in means is
+not equal to 0 95 percent confidence interval: -0.8499891 -0.1210448
+sample estimates: mean of x mean of y 6.534091 7.019608
+
+{[}1{]} -0.2 attr(,``magnitude'') {[}1{]} ``negligible''
 
@@
 
-\subsubsection{Prevalence Rating as manipulation
-check}\label{prevalence-rating-as-manipulation-check}
-
-\subsubsection{2.3 Situational Jugdement
+\subsubsection{Situational Jugdement
 Test}\label{situational-jugdement-test}
@@
 
-\subsubsection{2.4 Classroom
-Questionnaire}\label{classroom-questionnaire}
+\subsubsection{Classroom Questionnaire}\label{classroom-questionnaire}
 
@@
 
-\subsection{3. Correlations}\label{correlations}
+\subsection{Correlations}\label{correlations}
 

### 2025-01-23 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
x paper

--- 2024-12-04 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
@@
   emmeans,       # Computes estimated marginal means (or least-squares means) for post-hoc comparisons in models.
-  corrplot       # Visualize correlation matrices in a visually appealing way.
+  corrplot,      # Visualize correlation matrices in a visually appealing way.
+  flextable,     # Allows for creating customizable and professional tables
+  officer        # Enables integration of tables and content into Microsoft Office documents like Word and PowerPoint
 )
@@
 
+# Gaze Allocation Across Areas of Interest 
+```{r nof__dur_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 #### Percentage of fixations on each AOI, relative to the total number of fixations during the entire "Lesson" 
-```{r nof_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
 # Step 1: Define AOI categories
@@
 
-# # Step 6: Display the table with APA style
-# kable(grouped_aoi_percentages, 
-#       col.names = c("AOI", "Expert (%)", "Novice (%)"),
-#       caption = "Average Fixation Percentage per AOI by Group (Novice vs. Expert) - Descending Order") %>%
-#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
-#   add_header_above(c(" " = 1, "Fixation Percentage" = 2)) %>%
-#   row_spec(0, bold = TRUE) %>%
-#   column_spec(2:3, width = "3em", border_left = TRUE)
-
-# Step 7: Plot with descending AOI order, y-axis limit set to 100%, and percentage labels inside the bars
-ggplot(grouped_aoi_percentages, aes(x = reorder(AOI, -Fixation_Percentage), y = Fixation_Percentage, fill = Group)) +
+# Step 6: Restructure data for grouping and calculate 95% CI
+grouped_aoi_percentages_ci <- aoi_percentages %>%
+  pivot_longer(
+    cols = starts_with("AOI"),
+    names_to = "AOI",
+    values_to = "Percentage"
+  ) %>%
+  mutate(AOI = recode(
+    AOI,
+    "AOI_Students_pct" = "Students",
+    "AOI_Disruptive_Person_pct" = "Disruptive Person",
+    "AOI_Teacher_Material_pct" = "Teacher Material",
+    "AOI_Student_Desk_pct" = "Student Desk",
+    "AOI_Classroom_Others_pct" = "Classroom/Others"
+  )) %>%
+  group_by(Group, AOI) %>%
+  summarise(
+    Mean_Percentage = mean(Percentage, na.rm = TRUE),
+    CI_Lower = Mean_Percentage - qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
+    CI_Upper = Mean_Percentage + qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
+    .groups = "drop"
+  )
+
+# Step 7: Plot with 95% confidence intervals
+percentage_number_fixation <- ggplot(
+  grouped_aoi_percentages_ci %>% 
+    mutate(Group = recode(Group, 
+                          "Expert" = "Experienced", 
+                          "Novice" = "Inexperienced")),  # Rename groups
+  aes(
+    x = reorder(AOI, -Mean_Percentage),
+    y = Mean_Percentage,
+    fill = Group
+  )
+) +
   geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
-  geom_text(aes(label = paste0(Fixation_Percentage, "%")), 
+  geom_errorbar(
+    aes(ymin = CI_Lower, ymax = CI_Upper),
     position = position_dodge(width = 0.8),
-            vjust = -0.3, size = 3) +
-  labs(
-    title = "Average Fixation Percentage by AOI and Group (Descending Order)",
+    width = 0.2
+  ) +
+  geom_text(
+    aes(label = paste0(round(Mean_Percentage, 2), "%")),
+    position = position_dodge(width = 0.8),
+    vjust = -2.5,  # Adjusted to place the labels above the bars
+    size = 3
+  ) +
+  labs(title = "Average Fixation Number Percentage by AOI and Group", 
        x = "AOI", 
-    y = "Fixation Percentage (%)"
-  ) +
+       y = "Fixation Percentage (%)") +
   scale_fill_brewer(palette = "RdBu") +
-  theme_minimal() +
+  theme_cowplot() +
   theme(
@@
   ) +
-  guides(fill = guide_legend(title = "Group")) +
-  ylim(0, 100)  # Set y-axis limit to 100%
+  guides(fill = guide_legend(title = "Group"))
+
+percentage_number_fixation
+
+# Save the updated plot
+ggsave(filename = "plots/percentage_number_fixation_with_ci.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
 
@@
 # Initialize an empty data frame to store the results
-results <- data.frame()
+results_number <- data.frame()
 
@@
 
-      # Format the results for the current AOI and add to the results data frame
-      results <- rbind(
-        results,
+      # Format the results_number for the current AOI and add to the results_number data frame
+      results_number <- rbind(
+        results_number,
         data.frame(
@@
       # If one group has no data, append N/A values for this AOI
-      results <- rbind(
-        results,
+      results_number <- rbind(
+        results_number,
         data.frame(
           "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
-          "Group Comparison" = "Experts vs. Novices",
+          "Group Comparison" = "Experienced vs. Inexperienced",
           "t-value" = NA,
@@
 )
-results$AOI <- aoi_name_mapping[results$AOI]
-
-# Display the combined results table in APA style without row names
-knitr::kable(results, caption = "t-Test and Effect Size for Fixation Percentage across AOIs (Experts vs. Novices)", row.names = FALSE) %>%
+results_number$AOI <- aoi_name_mapping[results_number$AOI]
+
+# Display the combined results_number table in APA style without row names
+knitr::kable(results_number, caption = "t-Test and Effect Size for Fixation Percentage across AOIs (Experts vs. Novices)", row.names = FALSE) %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
-```
-
-#### Number of fixations per minute (micro-teaching unit)
-```{r nof_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### NUMBER OF FIXATIONS PER MINUTE IN MICRO-TEACHING UNIT ########################
-
-# 1. Data Preparation: Filter and Calculate Fixations per Minute in Micro-Teaching Unit
-df_aoi_sum <- df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select(
-    Group,
-    Participant,
-    Duration_of_interval,
-    starts_with("Total_duration_of_fixations"),
-    starts_with("Number_of_fixations"),
-    starts_with("Average_duration"),
-    -contains("Disruptive_Person")
-  ) %>%
-  rowwise() %>%
-  transmute(
-    Group = Group,
-    Participant = Participant,
-    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
-    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
-    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, 2),
-    Group = as_factor(Group)
-  ) %>%
-  drop_na()
-
-# 2. Descriptive Statistics Table for Number of Fixations per Minute
-nof_table <- df_aoi_sum %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    M = round(mean(Number_fixation_min_mtu), 2),
-    SD = round(sd(Number_fixation_min_mtu), 2),
-    Min = round(min(Number_fixation_min_mtu), 2),
-    Max = round(max(Number_fixation_min_mtu), 2)
-  )
-
-# Display the descriptive table in APA style
-knitr::kable(nof_table, caption = "N, M, SD, Min & Max Number of Fixations per Minute (Micro-Teaching Unit)") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# 3. Calculate means and standard deviations for Novice and Expert
-mean_novice_mtu <- round(mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
-sd_novice_mtu <- round(sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
-mean_expert_mtu <- round(mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)
-sd_expert_mtu <- round(sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)
-
-# 4. Perform t-test to get the p-value
-t_test_mtu <- t.test(
-  Number_fixation_min_mtu ~ Group,
-  data = df_aoi_sum,
-  var.equal = TRUE
-)
-p_value_mtu <- round(t_test_mtu$p.value, 2)
-
-# 5. Calculate Cohen's d for effect size using formula syntax
-library(effsize)
-cohen_d_mtu <- round(cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)$estimate, 2)
-
-# 6. Plotting the Number of Fixations per Minute (Micro-Teaching Unit)
-y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5
-
-plot_number_group <- df_aoi_sum %>%
-  ggplot(mapping = aes(x = Group, y = Number_fixation_min_mtu)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
-  geom_jitter(
-    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
-  ) +
-  ylim(0, y_max_mtu) +
-  labs(x = "", y = "Number of Fixations per Minute") +
-  scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Number of Fixations per Minute\n(Micro-Teaching Unit)") +
-  theme_cowplot() +
-  theme(legend.position = "none") +
-  # Annotations for mean (M) and SD using atop() to place SD below M
-  annotate("text", x = 1, y = y_max_mtu * 0.85,
-           label = paste0("atop(italic(M) == ", mean_novice_mtu, ", italic(SD) == ", sd_novice_mtu, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  annotate("text", x = 2, y = y_max_mtu * 0.85,
-           label = paste0("atop(italic(M) == ", mean_expert_mtu, ", italic(SD) == ", sd_expert_mtu, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  # Add p-value and Cohen's d annotations above the boxplots
-  annotate("text", x = 1.5, y = y_max_mtu * 0.95,
-           label = paste0("p = ", p_value_mtu, "\nd = ", cohen_d_mtu),
-           hjust = 0.5, size = 4, fontface = "italic")
-
-plot_number_group
-
-# 7. Format the t-Test and Cohen's d results for APA Table
-t_test_result <- data.frame(
-  "Group Comparison" = "Experts vs. Novices",
-  "t-value" = round(t_test_mtu$statistic, 2),
-  "df" = t_test_mtu$parameter,
-  "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
-  "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
-  "Cohen's d" = cohen_d_mtu,
-  "95% CI (d)" = paste0("[", round(t_test_mtu$conf.int[1], 2), ", ", round(t_test_mtu$conf.int[2], 2), "]")
-)
-
-# Display t-Test and Effect Size results in APA style
-knitr::kable(t_test_result, caption = "t-Test and Effect Size for Number of Fixations per Minute (Micro-Teaching Unit)") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-```
-
-#### Number of fixations per minute (AOI students)
-```{r nof_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### NUMBER OF FIXATIONS (AOI STUDENTS) ########################
-
-# 1. Data Preparation: Filter and Calculate Fixations per Minute on AOI Students
-df_aoi_stud <- df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select (
-    Group,
-    Duration_of_interval,
-    Participant,
-    "Total_duration_of_fixations.Anna",
-    "Total_duration_of_fixations.Bianca",
-    "Total_duration_of_fixations.Carl(a)",
-    "Number_of_fixations.Anna",
-    "Number_of_fixations.Bianca",
-    "Number_of_fixations.Carl(a)"
-  ) %>%
-  rowwise() %>%
-  transmute(
-    Group = as_factor(Group),
-    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
-    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
-    Participant = Participant,
-    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
-    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, 2),
-    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
-  ) %>%
-  drop_na()
-
-# 2. Descriptive Statistics: N, Mean (M), SD, Min, Max for Fixations per Minute (AOI Students)
-nof_min_stud_table <- df_aoi_stud %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    M = round(mean(Stud_number_fixation_min), 2),
-    SD = round(sd(Stud_number_fixation_min), 2),
-    Min = round(min(Stud_number_fixation_min), 2),
-    Max = round(max(Stud_number_fixation_min), 2)
-  )
-
-# Display Descriptive Statistics Table in APA Style
-knitr::kable(nof_min_stud_table, caption = "N, M, SD, Min & Max Number of Fixations per Minute (AOI Students)") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# 3. Plotting the Number of Fixations per Minute on AOI Students
-# Calculate descriptive statistics
-summary_stats <- df_aoi_stud %>%
-  group_by(Group) %>%
-  summarise(
-    M = round(mean(Stud_number_fixation_min), 2),
-    SD = round(sd(Stud_number_fixation_min), 2)
-  )
-
-# Conduct t-test and calculate effect size
-t_test_stud <- t.test(
-  Stud_number_fixation_min ~ Group,
-  data = df_aoi_stud,
-  var.equal = TRUE
-)
-
-# Cohen's d for effect size
-d_number_stud <- cohen.d(
-  Stud_number_fixation_min ~ Group,
-  data = df_aoi_stud
-)
-
-# Extract statistical values
-mean_expert <- summary_stats %>% filter(Group == "Expert") %>% pull(M)
-sd_expert <- summary_stats %>% filter(Group == "Expert") %>% pull(SD)
-mean_novice <- summary_stats %>% filter(Group == "Novice") %>% pull(M)
-sd_novice <- summary_stats %>% filter(Group == "Novice") %>% pull(SD)
-p_value <- format.pval(t_test_stud$p.value, digits = 2, eps = .05)
-cohen_d <- round(d_number_stud$estimate, 2)
-
-# Determine the maximum y-value for ylim to ensure all data points and annotations are visible
-y_max <- max(df_aoi_stud$Stud_number_fixation_min) * 1.5  # Increase the multiplier if needed
-
-# Create the boxplot with jittered data points for better readability
-plot_number_min_stud <- df_aoi_stud %>%
-  ggplot(mapping = aes(x = Group, y = Stud_number_fixation_min)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
-  geom_jitter(
-    width = 0.15, height = 0, alpha = 0.6, color = "black", size = 1.2
-  ) +
-  labs(x = "", y = "Number of fixations per minute") +
-  scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Number of fixations per minute\n(AOI students)") +
-  theme_cowplot() +
-  theme(legend.position = "none") +
-  ylim(0, y_max) +  # Adjust y-axis limit to include annotations
-  # Annotations for mean (M) and SD using atop() to place SD below M
-  annotate("text", x = 1, y = y_max * 0.85,
-           label = paste0("atop(italic(M) == ", mean_novice, ", italic(SD) == ", sd_novice, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  annotate("text", x = 2, y = y_max * 0.85,
-           label = paste0("atop(italic(M) == ", mean_expert, ", italic(SD) == ", sd_expert, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  # Add p-value and Cohen's d annotations above the boxplots
-  annotate("text", x = 1.5, y = y_max * 0.95,
-           label = paste0("p = ", p_value, "\nd = ", cohen_d),
-           hjust = 0.5, size = 4, fontface = "italic")
-
-# Display the plot
-plot_number_min_stud
-
-# 4. t-Test and Effect Size Calculation for Number of Fixations per Minute on AOI Students
-t_test_stud <- t.test(
-  Stud_number_fixation_min ~ Group,
-  data = df_aoi_stud,
-  var.equal = TRUE
-)
-
-# Calculate Cohen's d for the Effect Size
-d_number_stud <- cohen.d(
-  Stud_number_fixation_min ~ Group,
-  data = df_aoi_stud
-)
-
-# 5. Format t-Test and Cohen's d Results for APA Table
-t_test_result_stud <- data.frame(
-  "Group Comparison" = "Experts vs. Novices",
-  "t-value" = round(t_test_stud$statistic, 2),
-  "df" = t_test_stud$parameter,
-  "p-value" = format.pval(t_test_stud$p.value, digits = 2, eps = .05),
-  "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2),
-  "Cohen's d" = round(d_number_stud$estimate, 2),
-  "95% CI (d)" = paste0("[", round(d_number_stud$conf.int[1], 2), ", ", round(d_number_stud$conf.int[2], 2), "]")
-)
-
-# Display t-Test and Effect Size Results in APA Style
-knitr::kable(t_test_result_stud, caption = "t-Test and Effect Size for Number of Fixations per Minute (AOI Students)") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-```
-
-#### Number of fixations per seconds (AOI disruptive person)
-```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### NUMBER OF FIXATIONS ON AOI DISRUPTIVE PERSON ########################
-
-# Define the different types of disruptions and categories
-disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
-                 "Drumming_with_hands", "Head_on_table", "Heckling", 
-                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
-verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
-physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
-lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")
-
-# Step 1: Filter and prepare the data
-df_aoi_disrup <- df_aoi %>%
-  filter(TOI %in% disruptions) %>% # Filter rows based on the disruption list
-  select(Group, Participant, TOI, Duration_of_interval, "Number_of_fixations.Disruptive_Person") %>%
-  mutate(
-    Group = as_factor(Group), # Convert Group column to a factor
-    Disruption_Category = case_when( # Assign categories based on disruption type
-      TOI %in% verbal_disruptions ~ "Verbal disruptions",
-      TOI %in% physical_disruptions ~ "Physical disruptions",
-      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
-      TRUE ~ NA_character_
-    ),
-    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2) # Convert duration to seconds
-  ) %>%
-  filter(!is.na(Disruption_Category)) # Keep only rows with valid categories
-
-# Step 2: Summarize data by disruption category
-disruption_summary <- df_aoi_disrup %>%
-  group_by(Group, Participant, Disruption_Category) %>%
-  summarise(
-    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2), # Total time in seconds
-    fixation_count = round(sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE), 2), # Total fixations
-    fixations_per_second = round(fixation_count / total_duration_sec, 2), # Fixation rate per second
-    .groups = "drop"
-  )
-
-# Step 3: Summarize by participant
-individual_summary <- disruption_summary %>%
-  group_by(Group, Participant) %>%
-  summarise(
-    mean_fixations_per_second = round(mean(fixations_per_second, na.rm = TRUE), 2), # Mean fixation rate
-    .groups = "drop"
-  )
-
-##################### DESCRIPTIVE STATISTICS ########################
-
-# Descriptive statistics for overall fixation rate
-overall_stats <- individual_summary %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(), # Number of participants
-    Mean = round(mean(mean_fixations_per_second, na.rm = TRUE), 2), # Mean fixation rate
-    SD = round(sd(mean_fixations_per_second, na.rm = TRUE), 2), # Standard deviation
-    Min = round(min(mean_fixations_per_second, na.rm = TRUE), 2), # Minimum value
-    Max = round(max(mean_fixations_per_second, na.rm = TRUE), 2), # Maximum value
-    .groups = "drop"
-  )
-
-# Display the overall descriptive statistics table
-kable(
-  overall_stats,
-  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Overall Fixation Rate by Group",
-  col.names = c("Group", "N", "M", "SD", "Min", "Max"),
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Descriptive statistics by disruption category
-category_stats <- disruption_summary %>%
-  group_by(Disruption_Category, Group) %>%
-  summarise(
-    N = n_distinct(Participant), # Count unique participants
-    Mean = round(mean(fixations_per_second, na.rm = TRUE), 2), # Mean fixation rate
-    SD = round(sd(fixations_per_second, na.rm = TRUE), 2), # Standard deviation
-    Min = round(min(fixations_per_second, na.rm = TRUE), 2), # Minimum value
-    Max = round(max(fixations_per_second, na.rm = TRUE), 2), # Maximum value
-    .groups = "drop"
-  )
-
-# Display the descriptive statistics table by category
-kable(
-  category_stats,
-  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Fixation Rate by Group and Category",
-  col.names = c("Group", "Category", "N", "M", "SD", "Min", "Max"),
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-##################### FIRST PLOT: FIXATION RATE OVERALL ########################
-
-# Calculate values for annotations
-mean_novice <- round(mean(individual_summary$mean_fixations_per_second[individual_summary$Group == "Novice"], na.rm = TRUE), 2)
-sd_novice <- round(sd(individual_summary$mean_fixations_per_second[individual_summary$Group == "Novice"], na.rm = TRUE), 2)
-mean_expert <- round(mean(individual_summary$mean_fixations_per_second[individual_summary$Group == "Expert"], na.rm = TRUE), 2)
-sd_expert <- round(sd(individual_summary$mean_fixations_per_second[individual_summary$Group == "Expert"], na.rm = TRUE), 2)
-
-# t-Test and effect size
-t_test <- t.test(mean_fixations_per_second ~ Group, data = individual_summary, var.equal = TRUE)
-p_value <- round(t_test$p.value, 2)
-cohen_d <- round(cohen.d(mean_fixations_per_second ~ Group, data = individual_summary)$estimate, 2)
-
-# Overall fixation rate plot with annotations
-y_max_overall <- max(individual_summary$mean_fixations_per_second, na.rm = TRUE) * 1.5
-plot_overall <- ggplot(individual_summary, aes(x = Group, y = mean_fixations_per_second, fill = Group)) +
-  geom_boxplot(outlier.shape = NA, width = 0.5) +
-  geom_jitter(width = 0.1, alpha = 0.7, color = "black", size = 1.5) +
-  labs(x = "", y = "Mean Fixations per Second per Participant") +
-  ggtitle("Overall Fixation Rate per Participant\n(AOI Disruptive Person)") +
-  scale_fill_brewer(palette = "RdBu") +
-  theme_cowplot() +
-  ylim(0, y_max_overall) +
-  theme(legend.position = "none") +
-  annotate("text", x = 1, y = y_max_overall * 0.85,
-           label = paste0("M = ", mean_novice, "\nSD = ", sd_novice),
-           hjust = 0.5, size = 4, fontface = "italic") +
-  annotate("text", x = 2, y = y_max_overall * 0.85,
-           label = paste0("M = ", mean_expert, "\nSD = ", sd_expert),
-           hjust = 0.5, size = 4, fontface = "italic") +
-  annotate("text", x = 1.5, y = y_max_overall * 0.95,
-           label = paste0("p = ", p_value, "\nd = ", cohen_d),
-           hjust = 0.5, size = 4, fontface = "italic")
-
-##################### SECOND PLOT: FIXATION RATE BY CATEGORY ########################
-
-# Create the plot
-plot_category <- disruption_summary %>%
-  ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_point(
-    size = 2,
-    alpha = 0.7,
-    position = position_jitter(
-      seed = 1,
-      width = 0.1,
-      height = 0.1
-    )
-  ) +
-  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) + # Fixed y-axis across facets
-  labs(x = "", y = "Fixations per Second") +
-  ggtitle("Fixation Rate by Disruption Category\n(AOI Disruptive Person)") +
-  scale_fill_brewer(palette = "RdBu") +
-  theme_cowplot() +
-  theme(
-    legend.position = "none",
-    strip.text = element_text(size = 10) # Adjust facet text size if necessary
-  )
-
-# Display the plots
-plot_overall
-plot_category
-
-##################### STATISTICAL TESTS ########################
-
-# Table summarizing overall t-test and Cohen's d
-overall_effect <- data.frame(
-  Group = c("Overall"),
-  `t-value` = round(t_test$statistic, 2),
-  `p-value` = p_value,
-  `Cohen's d` = cohen_d
-)
-
-# Display t-test and effect size table
-kable(
-  overall_effect,
-  caption = "Overall t-Test and Effect Size for Fixation Rate",
-  col.names = c("Group", "t-value", "p-value", "Cohen's d"),
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-##################### REPEATED MEASURES ANOVA ########################
-
-# Perform the repeated-measures ANOVA
-anova_afex <- afex::aov_ez(
-  id = "Participant", # Random effect
-  dv = "fixations_per_second", # Dependent variable
-  between = "Group", # Between-subject factor
-  within = "Disruption_Category", # Within-subject factor
-  data = disruption_summary
-)
-
-# Extract the ANOVA table
-anova_results <- as.data.frame(anova_afex$anova_table)
-
-# Recalculate generalized eta squared (η²)
-eta_squared_results <- effectsize::eta_squared(anova_afex, partial = FALSE)
-
-# Combine recalculated eta squared with the ANOVA table
-anova_table_apa <- anova_results %>%
-  rownames_to_column(var = "Effect") %>% # Move row names to a column
-  left_join(
-    as.data.frame(eta_squared_results), 
-    by = c("Effect" = "Parameter") # Match the correct columns
-  ) %>%
-  mutate(
-    `F` = round(`F`, 2), # Round F-values
-    `η²` = round(Eta2, 3), # Round generalized eta squared
-    `p-value` = ifelse(
-      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 3) # Format p-values
-    )
-  ) %>%
-  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`) # Order columns, place η² last
-
-# Display the table
-kable(
-  anova_table_apa,
-  caption = "Repeated-Measures ANOVA Results (Including Effect Sizes)",
-  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
-  digits = 2
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-##################### POST-HOC TESTS ########################
-
-# Perform post-hoc pairwise comparisons for Disruption_Category (within-subject factor)
-post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)
-
-# Extract post-hoc pairwise contrasts for Disruption_Category
-post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
-  mutate(
-    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
-    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
-    Estimate = round(estimate, 2),
-    SE = round(SE, 2),
-    t = round(t.ratio, 2),
-    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))
-  )
-
-##################### COHEN'S D CALCULATION ########################
-
-# Define the disruption categories
-categories <- c("Lack of eagerness to learn", "Physical disruptions", "Verbal disruptions")
-
-# Initialize an empty list to store the Cohen's d values
-cohen_d_values <- vector("list", length = nrow(post_hoc_results_disruption))
-
-# Loop over the post-hoc results to calculate Cohen's d for each comparison
-for (i in 1:nrow(post_hoc_results_disruption)) {
-  # Extract the two categories being compared
-  group1 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][1]
-  group2 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][2]
-
-  # Get the data for the two groups being compared using fixations_per_second
-  group1_data <- disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == group1]
-  group2_data <- disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == group2]
-
-  # Calculate the means and standard deviations for each group
-  mean1 <- mean(group1_data, na.rm = TRUE)
-  mean2 <- mean(group2_data, na.rm = TRUE)
-
-  sd1 <- sd(group1_data, na.rm = TRUE)
-  sd2 <- sd(group2_data, na.rm = TRUE)
-
-  # Calculate the pooled standard deviation
-  pooled_sd <- sqrt(((length(group1_data) - 1) * sd1^2 + (length(group2_data) - 1) * sd2^2) / (length(group1_data) + length(group2_data) - 2))
-
-  # Calculate Cohen's d using the formula (mean difference / pooled SD)
-  d_value <- (mean1 - mean2) / pooled_sd
-
-  # Store the absolute value of Cohen's d
-  cohen_d_values[[i]] <- abs(round(d_value, 2))  # Take the absolute value of Cohen's d
-}
-
-# Add the Cohen's d values to the post-hoc results
-post_hoc_results_disruption$Cohen_d <- unlist(cohen_d_values)
-
-##################### TABLE FOR DISRUPTION CATEGORY ########################
-
-# Ensure the number of column names matches the number of columns in the data frame
-post_hoc_results_disruption <- post_hoc_results_disruption %>%
-  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
-
-# Displaying the table
-knitr::kable(
-  post_hoc_results_disruption,
-  caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Including Effect Sizes)",
-  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
-  digits = 2
-) %>%
-kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# # effect size for category differences
-# d_fix_disrup <- CohenD(
-#   x = disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == "Lack of eagerness to learn"],
-#   y = disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == "Verbal disruptions"],
-#   na.rm = TRUE
-# )
-# 
-# round(d_fix_disrup, 2)
-
-```
-
-### Duration of disruption
-```{r dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### DATA PREPARATION ########################
-
-# Prepare data for analysis: filter, calculate, and categorize disruptions
-df_aoi_disrup <- df_aoi %>%
-  filter(TOI %in% disruptions, Duration_of_interval <= 30000) %>%
-  select(Group, Participant, TOI, Duration_of_interval) %>%
-  mutate(
-    Group = as_factor(Group),
-    Disruption_Category = case_when(
-      TOI %in% verbal_disruptions ~ "Verbal disruptions",
-      TOI %in% physical_disruptions ~ "Physical disruptions",
-      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
-      TRUE ~ NA_character_
-    ),
-    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2)
-  ) %>%
-  filter(!is.na(Disruption_Category)) %>%
-  drop_na()
-
-##################### DESCRIPTIVE STATISTICS ########################
-
-# Descriptive Statistics by Group
-summary_stats_group <- df_aoi_disrup %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    Mean = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
-    SD = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
-    Median = round(median(Duration_of_interval_sec, na.rm = TRUE), 2),
-    IQR = round(IQR(Duration_of_interval_sec, na.rm = TRUE), 2),
-    Min = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
-    Max = round(max(Duration_of_interval_sec, na.rm = TRUE), 2),
-    .groups = "drop"
-  )
-
-# Descriptive Statistics by Category and Group
-summary_stats_category_group <- df_aoi_disrup %>%
-  group_by(Disruption_Category, Group) %>%
-  summarise(
-    N = n(),
-    Mean = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
-    SD = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
-    Median = round(median(Duration_of_interval_sec, na.rm = TRUE), 2),
-    IQR = round(IQR(Duration_of_interval_sec, na.rm = TRUE), 2),
-    Min = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
-    Max = round(max(Duration_of_interval_sec, na.rm = TRUE), 2),
-    .groups = "drop"
-  )
-
-# Display Descriptive Tables
-kable(
-  summary_stats_group,
-  caption = "Descriptive Statistics for Disruption Duration by Group",
-  col.names = c("Group", "N", "Mean", "SD", "Median", "IQR", "Min", "Max"),
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-kable(
-  summary_stats_category_group,
-  caption = "Descriptive Statistics for Disruption Duration by Category and Group",
-  col.names = c("Category", "Group", "N", "Mean", "SD", "Median", "IQR", "Min", "Max"),
-  row.names = FALSE
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-##################### PLOTS ########################
-
-# Plot 1: Disruption Duration by Group
-plot_duration_group <- ggplot(df_aoi_disrup, aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
-  geom_boxplot(outlier.shape = NA, width = 0.5) +
-  geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
-  labs(x = "Group", y = "Disruption Duration (seconds)") +
-  theme_cowplot() +
-  scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Disruption Duration by Group") +
-  theme(legend.position = "none") +
-  annotate("text", x = 1, y = max(df_aoi_disrup$Duration_of_interval_sec) + 4,
-           label = paste0("Median = ", summary_stats_group$Median[summary_stats_group$Group == "Novice"],
-                          "\nIQR = ", summary_stats_group$IQR[summary_stats_group$Group == "Novice"]),
-           hjust = 0.5, size = 4) +
-  annotate("text", x = 2, y = max(df_aoi_disrup$Duration_of_interval_sec) + 4,
-           label = paste0("Median = ", summary_stats_group$Median[summary_stats_group$Group == "Expert"],
-                          "\nIQR = ", summary_stats_group$IQR[summary_stats_group$Group == "Expert"]),
-           hjust = 0.5, size = 4)
-
-plot_duration_group
-
-# Plot 2: Disruption Duration by Group and Category
-plot_duration_category <- ggplot(df_aoi_disrup, aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
-  geom_boxplot(outlier.shape = NA, width = 0.5) +
-  geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
-  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) +  # Use fixed scale for all facets
-  labs(x = "Group", y = "Disruption Duration (seconds)") +
-  theme_cowplot() +
-  scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Disruption Duration by Group and Category") +
-  theme(legend.position = "none")
-
-# Display the plot
-plot_duration_category
-
-##################### STATISTICAL TESTS ########################
-
-##################### REPEATED MEASURES ANOVA ########################
-
-# Perform the repeated-measures ANOVA with `Duration_of_interval_sec` as the dependent variable
-anova_afex_duration <- afex::aov_ez(
-  id = "Participant",  # Random effect
-  dv = "Duration_of_interval_sec",  # Dependent variable: disruption duration in seconds
-  between = "Group",  # Between-subject factor: Group (Novice vs Expert)
-  within = "Disruption_Category",  # Within-subject factor: Disruption Categories
-  data = df_aoi_disrup
-)
-
-# Extract the ANOVA table
-anova_results_duration <- as.data.frame(anova_afex_duration$anova_table)
-
-# Recalculate generalized eta squared (η²) for effect size
-eta_squared_results_duration <- effectsize::eta_squared(anova_afex_duration, partial = FALSE)
-
-# Combine recalculated eta squared with the ANOVA table
-anova_table_apa_duration <- anova_results_duration %>%
-  rownames_to_column(var = "Effect") %>%  # Move row names to a column
-  left_join(
-    as.data.frame(eta_squared_results_duration), 
-    by = c("Effect" = "Parameter")  # Match the correct columns
-  ) %>%
-  mutate(
-    `F` = round(`F`, 2),  # Round F-values
-    `η²` = round(Eta2, 3),  # Round generalized eta squared
-    `p-value` = ifelse(
-      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 3)  # Format p-values
-    )
-  ) %>%
-  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`)  # Order columns, place η² last
-
-# Display the ANOVA table
-kable(
-  anova_table_apa_duration,
-  caption = "Repeated-Measures ANOVA Results for Disruption Duration (Including Effect Sizes)",
-  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
-  digits = 2
-) %>%
-  kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-##################### POST-HOC TESTS Disruption_Category (main effect) ########################
-
-# Perform post-hoc pairwise comparisons for Disruption_Category (main effect)
-post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)
-
-# Extract post-hoc pairwise contrasts for Disruption_Category (main effect)
-post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
-  mutate(
-    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
-    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
-    Estimate = round(estimate, 2),
-    SE = round(SE, 2),
-    t = round(t.ratio, 2),
-    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))
-  )
-
-##################### COHEN'S D CALCULATION ########################
-
-# Initialize empty lists to store Cohen's d values for both post-hoc tests
-cohen_d_values_disruption <- vector("list", length = nrow(post_hoc_results_disruption))
-
-# Loop over the post-hoc results for Disruption_Category to calculate Cohen's d for each comparison (main effect)
-for (i in 1:nrow(post_hoc_results_disruption)) {
-  # Extract the two categories being compared
-  group1 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][1]
-  group2 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][2]
-
-  # Get the data for the two groups being compared using Duration_of_interval_sec
-  group1_data <- df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Disruption_Category == group1]
-  group2_data <- df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Disruption_Category == group2]
-
-  # Calculate the means and standard deviations for each group
-  mean1 <- mean(group1_data, na.rm = TRUE)
-  mean2 <- mean(group2_data, na.rm = TRUE)
-
-  sd1 <- sd(group1_data, na.rm = TRUE)
-  sd2 <- sd(group2_data, na.rm = TRUE)
-
-  # Calculate the pooled standard deviation
-  pooled_sd <- sqrt(((length(group1_data) - 1) * sd1^2 + (length(group2_data) - 1) * sd2^2) / (length(group1_data) + length(group2_data) - 2))
-
-  # Calculate Cohen's d using the formula (mean difference / pooled SD)
-  d_value <- (mean1 - mean2) / pooled_sd
-
-  # Store the absolute value of Cohen's d
-  cohen_d_values_disruption[[i]] <- abs(round(d_value, 2))  # Take the absolute value of Cohen's d
-}
-
-# Add the Cohen's d values to the post-hoc results
-post_hoc_results_disruption$Cohen_d <- unlist(cohen_d_values_disruption)
-
-##################### TABLE FOR DISRUPTION CATEGORY ########################
-
-# Ensure the number of column names matches the number of columns in the data frame
-post_hoc_results_disruption <- post_hoc_results_disruption %>%
-  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
-
-# Displaying the post-hoc results for Disruption Category (main effect)
-knitr::kable(
-  post_hoc_results_disruption,
-  caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Main Effect)",
-  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
-  digits = 2
-) %>%
-kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-#################### POST-HOC TESTS interaction effect (Group:Disruption_Category) ########################
-
-# Calculate post-hoc pairwise comparisons for the interaction effect (Group:Disruption_Category)
-post_hoc_interaction <- emmeans(anova_afex, pairwise ~ Group * Disruption_Category)
-
-# Extract the post-hoc contrasts for the interaction
-post_hoc_results_interaction <- as.data.frame(post_hoc_interaction$contrasts) %>%
-  mutate(
-    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
-    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
-    Estimate = round(estimate, 2),
-    SE = round(SE, 2),
-    t = round(t.ratio, 2),
-    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))  # Round p-values to 2 decimals
-  )
-
-##################### COHEN'S D CALCULATION ########################
-
-# 1. Novice Lack of eagerness to learn vs Expert Lack of eagerness to learn
-d_LackOfEagerness_Novice_vs_Expert <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  na.rm = TRUE
-)
-
-# 2. Novice Lack of eagerness to learn vs Novice Physical disruptions
-d_LackOfEagerness_vs_Physical_Novice <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  na.rm = TRUE
-)
-
-# 3. Novice Lack of eagerness to learn vs Expert Physical disruptions
-d_LackOfEagerness_vs_Physical_Expert <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  na.rm = TRUE
-)
-
-# 4. Novice Lack of eagerness to learn vs Novice Verbal disruptions
-d_LackOfEagerness_vs_Verbal_Novice <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  na.rm = TRUE
-)
-
-# 5. Novice Lack of eagerness to learn vs Expert Verbal disruptions
-d_LackOfEagerness_vs_Verbal_Expert <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  na.rm = TRUE
-)
-
-# 6. Expert Lack of eagerness to learn vs Novice Physical disruptions
-d_Expert_LackOfEagerness_vs_Physical_Novice <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  na.rm = TRUE
-)
-
-# 7. Expert Lack of eagerness to learn vs Expert Physical disruptions
-d_Expert_LackOfEagerness_vs_Physical_Expert <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  na.rm = TRUE
-)
-
-# 8. Expert Lack of eagerness to learn vs Novice Verbal disruptions
-d_Expert_LackOfEagerness_vs_Verbal_Novice <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  na.rm = TRUE
-)
-
-# 9. Expert Lack of eagerness to learn vs Expert Verbal disruptions
-d_Expert_LackOfEagerness_vs_Verbal_Expert <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  na.rm = TRUE
-)
-
-# 10. Novice Physical disruptions vs Expert Physical disruptions
-d_Physical_Novice_vs_Expert <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  na.rm = TRUE
-)
-
-# 11. Novice Physical disruptions vs Novice Verbal disruptions
-d_Physical_Novice_vs_Verbal_Novice <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  na.rm = TRUE
-)
-
-# 12. Novice Physical disruptions vs Expert Verbal disruptions
-d_Physical_Novice_vs_Verbal_Expert <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  na.rm = TRUE
-)
-
-# 13. Expert Physical disruptions vs Novice Verbal disruptions
-d_Physical_Expert_vs_Verbal_Novice <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  na.rm = TRUE
-)
-
-# 14. Expert Physical disruptions vs Expert Verbal disruptions
-d_Physical_Expert_vs_Verbal_Expert <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  na.rm = TRUE
-)
-
-# 15. Novice Verbal disruptions vs Expert Verbal disruptions
-d_Verbal_Novice_vs_Expert <- CohenD(
-  x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
-  na.rm = TRUE
-)
-
-##################### CREATE A NAMED VECTOR FOR COHEN'S D ########################
-
-# Create a named vector with the correct Cohen's d values
-cohen_d_values_interaction <- c(
-  "Novice Lack of eagerness to learn - Expert Lack of eagerness to learn" = round(d_LackOfEagerness_Novice_vs_Expert, 2),
-  "Novice Lack of eagerness to learn - Novice Physical disruptions" = round(d_LackOfEagerness_vs_Physical_Novice, 2),
-  "Novice Lack of eagerness to learn - Expert Physical disruptions" = round(d_LackOfEagerness_vs_Physical_Expert, 2),
-  "Novice Lack of eagerness to learn - Novice Verbal disruptions" = round(d_LackOfEagerness_vs_Verbal_Novice, 2),
-  "Novice Lack of eagerness to learn - Expert Verbal disruptions" = round(d_LackOfEagerness_vs_Verbal_Expert, 2),
-  "Expert Lack of eagerness to learn - Novice Physical disruptions" = round(d_Expert_LackOfEagerness_vs_Physical_Novice, 2),
-  "Expert Lack of eagerness to learn - Expert Physical disruptions" = round(d_Expert_LackOfEagerness_vs_Physical_Expert, 2),
-  "Expert Lack of eagerness to learn - Novice Verbal disruptions" = round(d_Expert_LackOfEagerness_vs_Verbal_Novice, 2),
-  "Expert Lack of eagerness to learn - Expert Verbal disruptions" = round(d_Expert_LackOfEagerness_vs_Verbal_Expert, 2),
-  "Novice Physical disruptions - Expert Physical disruptions" = round(d_Physical_Novice_vs_Expert, 2),
-  "Novice Physical disruptions - Novice Verbal disruptions" = round(d_Physical_Novice_vs_Verbal_Novice, 2),
-  "Novice Physical disruptions - Expert Verbal disruptions" = round(d_Physical_Novice_vs_Verbal_Expert, 2),
-  "Expert Physical disruptions - Novice Verbal disruptions" = round(d_Physical_Expert_vs_Verbal_Novice, 2),
-  "Expert Physical disruptions - Expert Verbal disruptions" = round(d_Physical_Expert_vs_Verbal_Expert, 2),
-  "Novice Verbal disruptions - Expert Verbal disruptions" = round(d_Verbal_Novice_vs_Expert, 2)
-)
-
-##################### ADD COHEN'S D VALUES TO THE POST-HOC RESULTS ########################
-
-# Add Cohen's d values to the post-hoc results for each comparison
-post_hoc_results_interaction$Cohen_d <- cohen_d_values_interaction[post_hoc_results_interaction$Comparison]
-
-##################### TABLE FOR INTERACTION EFFECT ########################
-
-# Ensure the number of column names matches the number of columns in the data frame
-post_hoc_results_interaction <- post_hoc_results_interaction %>%
-  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
-
-# Display the post-hoc results for Group x Disruption_Category interaction with Cohen's d
-knitr::kable(
-  post_hoc_results_interaction,
-  caption = "Post-Hoc Pairwise Comparisons for Group x Disruption Category Interaction (Including Effect Sizes)",
-  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
-  digits = 2
-) %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# 
-# # 1. Normality Tests (Shapiro-Wilk)
-# # The Shapiro-Wilk test is used to assess whether the data for each group (Novice and Expert) follows a normal distribution.
-# normality_tests <- df_aoi_disrup %>%
-#   group_by(Group) %>%  # Group data by "Group" (Novice and Expert)
-#   summarise(
-#     Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),  # Perform Shapiro-Wilk test for normality and round the p-value
-#     .groups = "drop"  # Drop the grouping after summarizing
-#   )
-# 
-# # The p-value here is extremely small (0), which indicates that both the "Novice" and "Expert" groups deviate significantly from a normal distribution.
-This suggests that the data in both groups are not normally distributed, and therefore, non-parametric tests like the Mann-Whitney U test are more appropriate for analyzing differences between these groups.
-# 
-# # Display the Shapiro-Wilk test results in a nicely formatted table
-# kable(
-#   normality_tests,  # Table with Shapiro-Wilk p-values for each group
-#   caption = "Shapiro-Wilk Test for Normality by Group",  # Caption for the table
-#   col.names = c("Group", "Shapiro-Wilk p-value"),  # Column names
-#   row.names = FALSE  # Don't show row names
-# ) %>%
-#   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Style the table with a striped pattern
-# 
-# # 2. Mann-Whitney U-Test and Effect Size
-# # The Mann-Whitney U test is used to compare the duration of disruption between the Novice and Expert groups
-# # This is a non-parametric test used when the data is not normally distributed (based on the Shapiro-Wilk test results).
-# mann_whitney_test <- wilcox.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, exact = FALSE)
-# 
-# # Calculate Effect Size (r) for the Mann-Whitney U test
-# # Formula for r: r = |W - (n1 * n2 / 2)| / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
-# n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))  # Number of Novice participants
-# n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))  # Number of Expert participants
-# r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
-# 
-# # Create a data frame with the Mann-Whitney U test results, including the test statistic, p-value, and effect size
-# mann_whitney_results <- data.frame(
-#   "Test" = "Mann-Whitney U",  # Test name
-#   "W" = round(mann_whitney_test$statistic, 2),  # Test statistic (W)
-#   "p-value" = round(mann_whitney_test$p.value, 3),  # p-value from the test
-#   "Effect Size (r)" = round(r_effect, 3)  # Effect size (r) rounded to 3 decimals
-# )
-# 
-# # Explanation: The Mann-Whitney U test is a non-parametric test used to compare differences between two independent groups (in this case, Novices and Experts).
-It is used because the data is not normally distributed, as indicated by the Shapiro-Wilk test.
-# # p-value: A p-value of 0.879 is much larger than the common significance threshold of 0.05.
-This means there is no significant difference between the Novice and Expert groups in terms of the disruption duration.
-# # Effect size (r): The effect size value of 0.152 suggests a small effect.
-This confirms that even though the test was not significant, there was still a small effect observed, but it's not large enough to be practically meaningful.
-# 
-# 
-# # Display the Mann-Whitney U test results in a formatted table
-# kable(
-#   mann_whitney_results,
-#   caption = "Mann-Whitney U-Test Results for Disruption Duration",  # Table caption
-#   row.names = FALSE  # Don't show row names
-# ) %>%
-#   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
-# 
-# # 3. Kruskal-Wallis Test and Pairwise Comparisons
-# # The Kruskal-Wallis test is a non-parametric test to compare multiple groups (Disruption Categories) at once.
-# # It tests whether the distributions of disruption duration across categories are equal.
-# kruskal_test <- kruskal.test(Duration_of_interval_sec ~ Disruption_Category, data = df_aoi_disrup)
-# 
-# # Create a data frame with the Kruskal-Wallis test results, including Chi-squared statistic, degrees of freedom, and p-value
-# kruskal_results <- data.frame(
-#   "Test" = "Kruskal-Wallis",  # Test name
-#   "Chi-squared" = round(kruskal_test$statistic, 2),  # Chi-squared statistic from the test
-#   "df" = kruskal_test$parameter,  # Degrees of freedom (df)
-#   "p-value" = round(kruskal_test$p.value, 3)  # p-value from the test
-# )
-# 
-# # Explanation: The Kruskal-Wallis test is a non-parametric test used to compare more than two independent groups (in this case, different types of disruptions).
-It is used when the assumption of normality is not met (as in the Shapiro-Wilk test).
-# # p-value: A p-value of 0 indicates a highly significant difference between the disruption categories (i.e., "Verbal disruptions", "Physical disruptions", and "Lack of eagerness to learn").
-This suggests that there is a significant difference in disruption duration among these categories.
-# # Chi-squared: The large value of 145.07 supports this conclusion, indicating a strong effect in terms of the differences between disruption categories.
-# 
-# # Display the Kruskal-Wallis test results in a formatted table
-# kable(
-#   kruskal_results,
-#   caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",  # Table caption
-#   row.names = FALSE  # Don't show row names
-# ) %>%
-#   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
-# 
-# # 4. Pairwise Wilcoxon test with Bonferroni correction
-# # The pairwise Wilcoxon test is a non-parametric test used for multiple comparisons between pairs of disruption categories.
-# # The p-values are adjusted for multiple comparisons using the Bonferroni correction to control for type I error.
-# pairwise_wilcox <- pairwise.wilcox.test(
-#   x = df_aoi_disrup$Duration_of_interval_sec,  # The dependent variable (Duration of Interval)
-#   g = df_aoi_disrup$Disruption_Category,  # The grouping factor (Disruption Category)
-#   p.adjust.method = "bonferroni"  # Adjust p-values using the Bonferroni method
-# )
-# 
-# # Extract the p-values from the pairwise Wilcoxon test results and round to 3 decimal places
-# pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
-#   mutate(across(everything(), ~ round(., 3)))  # Round p-values to 3 decimals
-# 
-# # Display the pairwise Wilcoxon test results (with Bonferroni correction) in a formatted table
-# kable(
-#   pairwise_results,
-#   caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",  # Table caption
-#   row.names = TRUE  # Display row names
-# ) %>%
-#   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
-
-```
-
 #### Percentage of fixation durations on each AOI, relative to the total duration of fixations during the entire "Lesson" 
-```{r dur_fix_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
 # Step 1: Define AOI categories with correct column names for fixation duration
@@
 
-# Step 6: Plot the fixation duration percentages by AOI and Group
-ggplot(grouped_aoi_durations_percentages, aes(x = reorder(AOI, -Duration_Percentage), y = Duration_Percentage, fill = Group)) +
+# Step 6: Restructure data for grouping and calculate 95% CI for fixation durations
+grouped_aoi_durations_ci <- aoi_durations_percentages %>%
+  pivot_longer(
+    cols = starts_with("AOI"),
+    names_to = "AOI",
+    values_to = "Duration_Percentage"
+  ) %>%
+  mutate(AOI = recode(
+    AOI,
+    "AOI_Students_pct" = "Students",
+    "AOI_Disruptive_Person_pct" = "Disruptive Person",
+    "AOI_Teacher_Material_pct" = "Teacher Material",
+    "AOI_Student_Desk_pct" = "Student Desk",
+    "AOI_Classroom_Others_pct" = "Classroom/Others"
+  )) %>%
+  group_by(Group, AOI) %>%
+  summarise(
+    Mean_Duration_Percentage = mean(Duration_Percentage, na.rm = TRUE),
+    CI_Lower = Mean_Duration_Percentage - qt(0.975, df = n() - 1) * sd(Duration_Percentage, na.rm = TRUE) / sqrt(n()),
+    CI_Upper = Mean_Duration_Percentage + qt(0.975, df = n() - 1) * sd(Duration_Percentage, na.rm = TRUE) / sqrt(n()),
+    .groups = "drop"
+  )
+
+# Step 7: Plot with 95% confidence intervals
+percentage_duration_fixation <- ggplot(
+  grouped_aoi_durations_ci %>%
+    mutate(Group = recode(Group, "Expert" = "Experienced", "Novice" = "Inexperienced")), # Rename groups
+  aes(
+    x = reorder(AOI, -Mean_Duration_Percentage),
+    y = Mean_Duration_Percentage,
+    fill = Group
+  )
+) +
   geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
-  geom_text(aes(label = paste0(Duration_Percentage, "%")), 
+  geom_errorbar(
+    aes(ymin = CI_Lower, ymax = CI_Upper),
     position = position_dodge(width = 0.8),
-            vjust = -0.3, size = 3) +
+    width = 0.2
+  ) +
+  geom_text(
+    aes(label = paste0(round(Mean_Duration_Percentage, 2), "%")),
+    position = position_dodge(width = 0.8),
+    vjust = -2.5,  # Adjusted to place the labels above the bars
+    size = 3
+  ) +
+  ylim(0, 60) + 
   labs(
-    title = "Total Fixation Duration Percentage by AOI and Group (Descending Order)",
+    title = "Average Fixation Duration Percentage by AOI and Group",
     x = "AOI",
@@
   scale_fill_brewer(palette = "RdBu") +
-  theme_minimal() +
+  theme_cowplot() +
   theme(
@@
   ) +
-  guides(fill = guide_legend(title = "Group")) +
-  ylim(0, 100)  # Set y-axis limit to 100%
+  guides(fill = guide_legend(title = "Group"))
+percentage_duration_fixation
+
+ggsave(
+  filename = "plots/percentage_duration_fixation_with_ci.svg",
+  width = 20,
+  height = 12,
+  units = "cm"
+)
 
@@
 aoi_list <- c("AOI_Students_pct", "AOI_Disruptive_Person_pct", "AOI_Teacher_Material_pct", "AOI_Student_Desk_pct", "AOI_Classroom_Others_pct")
-results <- data.frame()
+results_duration <- data.frame()
 
@@
 
-      results <- rbind(
-        results,
+      results_duration <- rbind(
+        results_duration,
         data.frame(
@@
     } else {
-      results <- rbind(
-        results,
+      results_duration <- rbind(
+        results_duration,
         data.frame(
           "AOI" = gsub("_pct", "", column_name),
-          "Group Comparison" = "Experts vs. Novices",
+          "Group Comparison" = "Experienced vs. Inexperienced",
           "t-value" = NA,
@@
 
-# Map AOI names to clean versions for readability in the final results table
-results$AOI <- recode(results$AOI,
+# Map AOI names to clean versions for readability in the final results_duration table
+results_duration$AOI <- recode(results_duration$AOI,
                       "AOI_Students" = "Students",
@@
 # Display the t-Test and Effect Size table in APA style
-knitr::kable(results, 
+knitr::kable(results_duration, 
              caption = "t-Test and Effect Size for Fixation Duration Percentage across AOIs (Experts vs. Novices)", 
@@
 
-#### Average duration of fixations in milliseconds (micro-teaching unit)
-```{r dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### AVERAGE FIXATION DURATION ANALYSIS ########################
-
-# 1. Data Preparation: Filter and Calculate Average Fixation Duration in the Micro-Teaching Unit
+#### Number of fixations per minute and fixation duration in ms (micro-teaching unit)
+```{r nof_dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+##################### NUMBER OF FIXATIONS PER MINUTE ########################
+
+##################### Data Preparation ########################
 df_aoi_sum <- df_aoi %>%
@@
   transmute(
-    Group = as_factor(Group),
-    Participant = Participant,
-    Duration_of_interval = Duration_of_interval,
-    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
-    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
+    Group = factor(Group, levels = c("Expert", "Novice"), labels = c("Experienced", "Inexperienced")),
+    Participant,
+    Duration_of_interval_min = Duration_of_interval / 60000,
     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
     Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, 2),
-    Average_duration_fixation = round(Sum_duration_fixation / Sum_number_fixation, 2)
+    Number_fixation_min_mtu = Sum_number_fixation / Duration_of_interval_min,
+    Avg_fixation_duration = Sum_duration_fixation / Sum_number_fixation
   ) %>%
@@
 
-# 2. Descriptive Statistics Table
-fixation_duration_table <- df_aoi_sum %>%
+##################### Number of Fixations per Minute ########################
+
+# Descriptive Statistics for Number of Fixations per Minute
+nof_stats <- df_aoi_sum %>%
   group_by(Group) %>%
@@
     N = n(),
-    M = round(mean(Average_duration_fixation, na.rm = TRUE), 2),
-    SD = round(sd(Average_duration_fixation, na.rm = TRUE), 2),
-    Min = round(min(Average_duration_fixation, na.rm = TRUE), 2),
-    Max = round(max(Average_duration_fixation, na.rm = TRUE), 2)
-  )
-
-# Display the descriptive table in APA style
-knitr::kable(fixation_duration_table, caption = "N, M, SD, min & max Average Fixation Duration (micro-teaching unit)") %>%
+    M = round(mean(Number_fixation_min_mtu, na.rm = TRUE), 2),
+    SD = round(sd(Number_fixation_min_mtu, na.rm = TRUE), 2),
+    Min = round(min(Number_fixation_min_mtu, na.rm = TRUE), 2),
+    Max = round(max(Number_fixation_min_mtu, na.rm = TRUE), 2)
+  )
+
+# Display Table
+knitr::kable(nof_stats, caption = "N, M, SD, Min & Max for Number of Fixations per Minute") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
-# 3. Calculate means and standard deviations for Novice and Expert groups
-mean_novice_fixation <- round(mean(df_aoi_sum$Average_duration_fixation[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
-sd_novice_fixation <- round(sd(df_aoi_sum$Average_duration_fixation[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
-mean_expert_fixation <- round(mean(df_aoi_sum$Average_duration_fixation[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)
-sd_expert_fixation <- round(sd(df_aoi_sum$Average_duration_fixation[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)
-
-# 4. Perform t-test to get the p-value
-t_test_fixation <- t.test(
-  Average_duration_fixation ~ Group,
-  data = df_aoi_sum,
-  var.equal = TRUE
-)
-p_value_fixation <- round(t_test_fixation$p.value, 2)
-
-# 5. Calculate Cohen's d for effect size using formula syntax
-cohen_d_fixation <- round(cohen.d(Average_duration_fixation ~ Group, data = df_aoi_sum)$estimate, 2)
-
-# 6. Plotting the Average Fixation Duration
-y_max_fixation <- max(df_aoi_sum$Average_duration_fixation) * 1.5
-
-plot_avg_fixation_group <- df_aoi_sum %>%
-  ggplot(mapping = aes(x = Group, y = Average_duration_fixation)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
-  geom_jitter(
-    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
-  ) +
-  ylim(0, y_max_fixation) +
-  labs(x = "", y = "Average Fixation Duration (ms)") +
+# t-Test and Cohen's d
+t_test_mtu <- t.test(Number_fixation_min_mtu ~ Group, data = df_aoi_sum, var.equal = TRUE)
+cohen_d_mtu <- cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)
+
+# APA Table
+t_test_result_mtu <- data.frame(
+  "Group Comparison" = "Experienced vs. Inexperienced",
+  "t-value" = round(t_test_mtu$statistic, 2),
+  "df" = t_test_mtu$parameter,
+  "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
+  "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
+  "Cohen's d" = round(cohen_d_mtu$estimate, 2),
+  "95% CI (d)" = paste0("[", round(cohen_d_mtu$conf.int[1], 2), ", ", round(cohen_d_mtu$conf.int[2], 2), "]")
+)
+
+knitr::kable(t_test_result_mtu, caption = "t-Test and Effect Size for Number of Fixations per Minute") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Ensure cohen_d_mtu is numeric
+cohen_d_mtu <- round(as.numeric(cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)$estimate), 2)
+
+# Plot: Number of Fixations per Minute
+y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5
+
+plot_number_fixation_group <- df_aoi_sum %>%
+  ggplot(aes(x = Group, y = Number_fixation_min_mtu, fill = Group)) +
+  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
+  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
+  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Average Fixation Duration\n(micro-teaching unit)") +
+  ylim(0, y_max_mtu) +
+  labs(title = "Number of Fixations per Minute\n(Micro-Teaching Unit)", x = "", y = "Fixations per Minute") +
   theme_cowplot() +
   theme(legend.position = "none") +
-  # Add annotations for mean (M) and SD
-  annotate("text", x = 1, y = y_max_fixation * 0.85,
-           label = paste0("atop(italic(M) == ", mean_novice_fixation, ", italic(SD) == ", sd_novice_fixation, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  annotate("text", x = 2, y = y_max_fixation * 0.85,
-           label = paste0("atop(italic(M) == ", mean_expert_fixation, ", italic(SD) == ", sd_expert_fixation, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  # Add p-value and Cohen's d annotations
-  annotate("text", x = 1.5, y = y_max_fixation * 0.95,
-           label = paste0("p = ", p_value_fixation, "\nd = ", cohen_d_fixation),
-           hjust = 0.5, size = 4, fontface = "italic")
-
-plot_avg_fixation_group
-
-# 7. Format the t-Test and Cohen's d results for APA Table without the first column
-t_test_result <- data.frame(
-  "Group Comparison" = "Experts vs. Novices",
-  "t-value" = round(t_test_fixation$statistic, 2),
-  "df" = t_test_fixation$parameter,
-  "p-value" = round(t_test_fixation$p.value, 2),
-  "Mean Difference" = round(t_test_fixation$estimate[1] - t_test_fixation$estimate[2], 2),
-  "Cohen's d" = cohen_d_fixation,
-  "95% CI (d)" = paste0("[", round(t_test_fixation$conf.int[1], 2), ", ", round(t_test_fixation$conf.int[2], 2), "]")
-)
-
-# Display t-Test and Effect Size results in APA style without row names
-knitr::kable(t_test_result, caption = "t-Test and Effect Size for Average Fixation Duration (Micro-Teaching Unit)", row.names = FALSE) %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-```
-
-#### Average duration of fixations (AOI students)
-```{r dur_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### AVERAGE DURATION ON AOI STUDENTS ########################
-
-# 1. Data Preparation: Filter and Calculate Average Duration of Fixations on AOI Students
-df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select (
-    Group,
-    Duration_of_interval,
-    Participant,
-    "Total_duration_of_fixations.Anna",
-    "Total_duration_of_fixations.Bianca",
-    "Total_duration_of_fixations.Carl(a)",
-    "Number_of_fixations.Anna",
-    "Number_of_fixations.Bianca",
-    "Number_of_fixations.Carl(a)"
-  ) %>%
-  rowwise() %>%
-  transmute(
-    Group = as_factor(Group),
-    Participant = Participant,
-    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
-    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
-    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, digits = 2),
-    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, digits = 2),
-    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0)
-    ) -> df_aoi_stud
-
-# 2. Descriptive Statistics Table
-dur_stud_table <- df_aoi_stud %>%
+  annotate("text", x = 1, y = 3,
+           label = paste0("italic(M) == ", round(nof_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[1], 2)),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  annotate("text", x = 2, y = 3,
+           label = paste0("italic(M) == ", round(nof_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[2], 2)),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  annotate("text", x = 1.5, y = y_max_mtu * 0.95,
+           label = paste0("italic(p) == ", round(t_test_mtu$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_mtu),
+           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
+
+plot_number_fixation_group
+
+ggsave(filename = "plots/plot_number_fixation_group.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+##################### Average Fixation Duration ########################
+
+# Descriptive Statistics for Average Fixation Duration
+fixation_stats <- df_aoi_sum %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M in ms" = round(mean(Average_duration_stud, na.rm = TRUE), 2),
-    "SD in ms" = round(sd(Average_duration_stud, na.rm = TRUE), 2),
-    "Min in ms" = round(min(Average_duration_stud, na.rm = TRUE), 2),
-    "Max in ms" = round(max(Average_duration_stud, na.rm = TRUE), 2)
-  )
-
-# Display the descriptive table in APA style
-knitr::kable(dur_stud_table,
-             caption = "N, M, SD, Min & Max Average Duration of Fixations in Milliseconds (AOI Students)") %>%
+    M = round(mean(Avg_fixation_duration, na.rm = TRUE), 2),
+    SD = round(sd(Avg_fixation_duration, na.rm = TRUE), 2),
+    Min = round(min(Avg_fixation_duration, na.rm = TRUE), 2),
+    Max = round(max(Avg_fixation_duration, na.rm = TRUE), 2)
+  )
+
+# Display Table
+knitr::kable(fixation_stats, caption = "N, M, SD, Min & Max for Average Fixation Duration") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
-# 3. Plotting Average Duration on AOI Students
-# Calculate values for annotation
-mean_novice_stud <- round(mean(df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"], na.rm = TRUE), 2)
-sd_novice_stud <- round(sd(df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"], na.rm = TRUE), 2)
-mean_expert_stud <- round(mean(df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"], na.rm = TRUE), 2)
-sd_expert_stud <- round(sd(df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"], na.rm = TRUE), 2)
-
-# Maximum y-axis value for plot
-y_max_stud <- max(df_aoi_stud$Average_duration_stud) * 1.2
-
-# Conduct t-test
-t_test_stud <- t.test(
-  Average_duration_stud ~ Group,
-  data = df_aoi_stud,
-  var.equal = TRUE
-)
-
-# Extract p-value
-p_value_stud <- round(t_test_stud$p.value, 2)
-
-# Calculate Cohen's d (full result object)
-d_aver_stud_full <- cohen.d(Average_duration_stud ~ Group, data = df_aoi_stud, pooled = TRUE)
-
-# Extract Cohen's d and confidence interval
-d_aver_stud <- round(d_aver_stud_full$estimate, 2)
-d_conf_int <- paste0("[", round(d_aver_stud_full$conf.int[1], 2), ", ", round(d_aver_stud_full$conf.int[2], 2), "]")
-
-# Annotated Plot
-plot_average_duration_stud <- df_aoi_stud %>%
-  ggplot(mapping = aes(x = Group, y = Average_duration_stud)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
-  geom_jitter(
-    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
-  ) +
-  ylim(0, y_max_stud) + 
-  labs(x = "", y = "Average Fixation Duration (ms)") + 
+# t-Test and Cohen's d
+t_test_fixation <- t.test(Avg_fixation_duration ~ Group, data = df_aoi_sum, var.equal = TRUE)
+cohen_d_fixation <- cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)
+
+# APA Table
+t_test_result_fixation <- data.frame(
+  "Group Comparison" = "Experienced vs. Inexperienced",
+  "t-value" = round(t_test_fixation$statistic, 2),
+  "df" = t_test_fixation$parameter,
+  "p-value" = format.pval(t_test_fixation$p.value, digits = 2, eps = .05),
+  "Mean Difference" = round(t_test_fixation$estimate[1] - t_test_fixation$estimate[2], 2),
+  "Cohen's d" = round(cohen_d_fixation$estimate, 2),
+  "95% CI (d)" = paste0("[", round(cohen_d_fixation$conf.int[1], 2), ", ", round(cohen_d_fixation$conf.int[2], 2), "]")
+)
+
+knitr::kable(t_test_result_fixation, caption = "t-Test and Effect Size for Average Fixation Duration") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Ensure cohen_d_fixation is numeric
+cohen_d_fixation <- round(cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)$estimate, 2)
+
+# Plot: Average Fixation Duration
+plot_avg_fixation_group <- df_aoi_sum %>%
+  ggplot(aes(x = Group, y = Avg_fixation_duration, fill = Group)) +
+  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
+  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
+  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Average Duration of Fixations\n(AOI Students)") +
+  labs(title = "Average Fixation Duration\n(Micro-Teaching Unit)", x = "", y = "Fixation Duration (ms)") +
   theme_cowplot() +
   theme(legend.position = "none") +
-  # Annotate mean (M) and SD
-  annotate("text", x = 1, y = y_max_stud * 0.85,
-           label = paste0("atop(italic(M) == ", mean_novice_stud, ", italic(SD) == ", sd_novice_stud, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  annotate("text", x = 2, y = y_max_stud * 0.85,
-           label = paste0("atop(italic(M) == ", mean_expert_stud, ", italic(SD) == ", sd_expert_stud, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  # Annotate p-value and Cohen's d
-  annotate("text", x = 1.5, y = y_max_stud * 0.95,
-           label = paste0("p = ", p_value_stud, "\nd = ", d_aver_stud),
-           hjust = 0.5, size = 4, fontface = "italic")
-
-plot_average_duration_stud
-
-# 4. t-Test and Effect Size Results Table
-t_test_stud_result <- data.frame(
-  "Group Comparison" = "Experts vs. Novices",
-  "t-value" = round(t_test_stud$statistic, 2),
-  "df" = t_test_stud$parameter,
-  "p-value" = round(t_test_stud$p.value, 2),
-  "Mean Difference" = round(t_test_stud$estimate[1] - t_test_stud$estimate[2], 2),
-  "Cohen's d" = d_aver_stud,
-  "95% CI (d)" = d_conf_int
-)
-
-# Display the t-Test and Effect Size results table in APA style
-knitr::kable(t_test_stud_result,
-             caption = "t-Test and Effect Size for Average Fixation Duration on AOI Students (milliseconds)",
-             row.names = FALSE) %>%
+  # Add M and SD values below the x-axis for each group
+  annotate("text", x = 1, y = -50,  # Adjust y-coordinate to place below the x-axis
+           label = paste0("italic(M) == ", round(fixation_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[1], 2)),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  annotate("text", x = 2, y = -50,  # Adjust y-coordinate to place below the x-axis
+           label = paste0("italic(M) == ", round(fixation_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[2], 2)),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  # Add p-value and d-value above the plot
+  annotate("text", x = 1.5, y = max(df_aoi_sum$Avg_fixation_duration) * 1.1,
+           label = paste0("italic(p) == ", round(t_test_fixation$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_fixation),
+           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
+
+plot_avg_fixation_group
+
+ggsave(filename = "plots/plot_avg_fixation_group.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+# Load the patchwork library
+install.packages("patchwork")
+library(patchwork)
+
+# Combine the two plots side by side
+combined_plot <- plot_number_fixation_group + plot_avg_fixation_group +
+  plot_layout(ncol = 2, guides = "collect") &
+  theme(legend.position = "none")
+
+# Display the combined plot
+combined_plot
+
+# Save the combined plot
+ggsave(
+  filename = "plots/combined_results_plot.svg",
+  plot = combined_plot,
+  width = 25,
+  height = 12,
+  units = "cm"
+)
+
+```
+
+#### Gaze Relational Index (GRI; micro-teaching unit)
+```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+##################### GRI in MICRO-TEACHING UNIT ########################
+
+##################### Data Preparation ########################
+# Step 1: Calculate GRI (Gaze Relational Index) for each participant
+df_gri <- df_aoi_sum %>%
+  mutate(GRI = Avg_fixation_duration / Number_fixation_min_mtu)
+
+##################### Descriptive Statistics ########################
+# Step 2: Summarize GRI statistics (N, M, SD, Min, Max) by Group
+gri_stats <- df_gri %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    M = round(mean(GRI, na.rm = TRUE), 2),
+    SD = round(sd(GRI, na.rm = TRUE), 2),
+    Min = round(min(GRI, na.rm = TRUE), 2),
+    Max = round(max(GRI, na.rm = TRUE), 2)
+  )
+
+# Display the GRI summary table in APA format
+knitr::kable(gri_stats,
+             caption = "N, M, SD, Min, and Max for Gaze Relational Index (GRI)") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
+##################### t-Test and Effect Size ########################
+# Step 3: Conduct t-Test and Cohen's d
+t_test_gri <- t.test(GRI ~ Group, data = df_gri, var.equal = TRUE)
+cohen_d_gri <- cohen.d(GRI ~ Group, data = df_gri)
+
+# Step 4: Create a t-Test and Effect Size APA Table
+t_test_result_gri <- data.frame(
+  "Group Comparison" = "Experienced vs. Inexperienced",
+  "t-value" = round(t_test_gri$statistic, 2),
+  "df" = t_test_gri$parameter,
+  "p-value" = format.pval(t_test_gri$p.value, digits = 2, eps = .05),
+  "Mean Difference" = round(t_test_gri$estimate[1] - t_test_gri$estimate[2], 2),
+  "Cohen's d" = round(cohen_d_gri$estimate, 2),
+  "95% CI (d)" = paste0("[", round(cohen_d_gri$conf.int[1], 2), ", ", round(cohen_d_gri$conf.int[2], 2), "]")
+)
+
+# Display t-Test and Effect Size results in APA format
+knitr::kable(t_test_result_gri, 
+             caption = "t-Test and Effect Size for Gaze Relational Index (GRI)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### Plot: GRI by Group ########################
+# Calculate annotation values for the plot
+mean_expert_gri <- round(mean(df_gri$GRI[df_gri$Group == "Experienced"], na.rm = TRUE), 2)
+sd_expert_gri <- round(sd(df_gri$GRI[df_gri$Group == "Experienced"], na.rm = TRUE), 2)
+mean_novice_gri <- round(mean(df_gri$GRI[df_gri$Group == "Inexperienced"], na.rm = TRUE), 2)
+sd_novice_gri <- round(sd(df_gri$GRI[df_gri$Group == "Inexperienced"], na.rm = TRUE), 2)
+y_max_gri <- max(df_gri$GRI, na.rm = TRUE) * 1.5
+
+# Step 5: Plot GRI by Group
+plot_gri_group <- df_gri %>%
+  ggplot(aes(x = Group, y = GRI, fill = Group)) +
+  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
+  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
+  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.5) +
+  scale_fill_brewer(palette = "RdBu") +
+  ylim(0, y_max_gri) +
+  labs(title = "Gaze Relational Index\n(Micro-Teaching Unit)", x = "", y = "GRI") +
+  theme_cowplot() +
+  theme(legend.position = "none") +
+  # Annotate mean (M) and SD above the x-axis
+  annotate("text", x = 1, y = 0.5,  # Adjust y-coordinate to place above the x-axis
+           label = paste0("italic(M) == ", mean_expert_gri, " * ',' ~ italic(SD) == ", sd_expert_gri),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  annotate("text", x = 2, y = 0.5,  # Adjust y-coordinate to place above the x-axis
+           label = paste0("italic(M) == ", mean_novice_gri, " * ',' ~ italic(SD) == ", sd_novice_gri),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  # Annotate p-value and Cohen's d above the plot
+  annotate("text", x = 1.5, y = y_max_gri * 0.95,
+           label = paste0("italic(p) == ", round(t_test_gri$p.value, 2), " * ',' ~ italic(d) == ", round(cohen_d_gri$estimate, 2)),
+           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
+
+plot_gri_group
+
+# Save the plot
+ggsave(filename = "plots/plot_gri_group.svg", 
+       width = 20, 
+       height = 12, 
+       units = "cm")
 ```
 
-#### Average duration of fixations (AOI disruptive person)
-```{r average_dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+#### Number of fixations per minute and average fixation duration (AOI students)
+```{r nof_dur_students, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+#### Number of Fixations per Minute and Average Fixation Duration (AOI Students)
+
+##################### Data Preparation ########################
+df_aoi_stud <- df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select(
+    Group,
+    Participant,
+    Duration_of_interval,
+    starts_with("Total_duration_of_fixations"),
+    starts_with("Number_of_fixations")
+  ) %>%
+  rowwise() %>%
+  transmute(
+    Group = factor(Group, levels = c("Expert", "Novice"), labels = c("Experienced", "Inexperienced")),
+    Participant,
+    Duration_of_interval_min = Duration_of_interval / 60000,
+    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Stud_number_fixation_min = Stud_number_fixation / Duration_of_interval_min,
+    Avg_fixation_duration_stud = Stud_duration_fixation / Stud_number_fixation
+  ) %>%
+  drop_na()
+
+##################### Number of Fixations per Minute ########################
+
+# Descriptive Statistics for Number of Fixations per Minute
+nof_stats_stud <- df_aoi_stud %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    M = round(mean(Stud_number_fixation_min, na.rm = TRUE), 2),
+    SD = round(sd(Stud_number_fixation_min, na.rm = TRUE), 2),
+    Min = round(min(Stud_number_fixation_min, na.rm = TRUE), 2),
+    Max = round(max(Stud_number_fixation_min, na.rm = TRUE), 2)
+  )
+
+# Display Table
+knitr::kable(nof_stats_stud, caption = "N, M, SD, Min & Max for Number of Fixations per Minute (AOI Students)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# t-Test and Cohen's d
+t_test_nof_stud <- t.test(Stud_number_fixation_min ~ Group, data = df_aoi_stud, var.equal = TRUE)
+cohen_d_nof_stud <- cohen.d(Stud_number_fixation_min ~ Group, data = df_aoi_stud)
+
+# APA Table
+t_test_result_nof_stud <- data.frame(
+  "Group Comparison" = "Experienced vs. Inexperienced",
+  "t-value" = round(t_test_nof_stud$statistic, 2),
+  "df" = t_test_nof_stud$parameter,
+  "p-value" = format.pval(t_test_nof_stud$p.value, digits = 2, eps = .05),
+  "Mean Difference" = round(t_test_nof_stud$estimate[1] - t_test_nof_stud$estimate[2], 2),
+  "Cohen's d" = round(cohen_d_nof_stud$estimate, 2),
+  "95% CI (d)" = paste0("[", round(cohen_d_nof_stud$conf.int[1], 2), ", ", round(cohen_d_nof_stud$conf.int[2], 2), "]")
+)
+
+knitr::kable(t_test_result_nof_stud, caption = "t-Test and Effect Size for Number of Fixations per Minute (AOI Students)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Plot: Number of Fixations per Minute
+y_max_nof_stud <- max(df_aoi_stud$Stud_number_fixation_min) * 1.5
+
+plot_nof_stud <- df_aoi_stud %>%
+  ggplot(aes(x = Group, y = Stud_number_fixation_min, fill = Group)) +
+  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
+  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
+  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
+  scale_fill_brewer(palette = "RdBu") +
+  ylim(0, y_max_nof_stud) +
+  labs(title = "Number of Fixations per Minute\n(AOI Students)", x = "", y = "Fixations per Minute") +
+  theme_cowplot() +
+  theme(legend.position = "none") +
+  annotate("text", x = 1, y = 3,
+           label = paste0("italic(M) == ", round(nof_stats_stud$M[1], 2), " * ',' ~ italic(SD) == ", round(nof_stats_stud$SD[1], 2)),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  annotate("text", x = 2, y = 3,
+           label = paste0("italic(M) == ", round(nof_stats_stud$M[2], 2), " * ',' ~ italic(SD) == ", round(nof_stats_stud$SD[2], 2)),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  annotate("text", x = 1.5, y = y_max_nof_stud * 0.95,
+           label = paste0("italic(p) == ", round(t_test_nof_stud$p.value, 2), " * ',' ~ italic(d) == ", round(cohen_d_nof_stud$estimate, 2)),
+           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
+
+plot_nof_stud
+
+ggsave(filename = "plots/plot_nof_stud.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+##################### Average Fixation Duration ########################
+
+# Descriptive Statistics for Average Fixation Duration
+fixation_stats_stud <- df_aoi_stud %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    M = round(mean(Avg_fixation_duration_stud, na.rm = TRUE), 2),
+    SD = round(sd(Avg_fixation_duration_stud, na.rm = TRUE), 2),
+    Min = round(min(Avg_fixation_duration_stud, na.rm = TRUE), 2),
+    Max = round(max(Avg_fixation_duration_stud, na.rm = TRUE), 2)
+  )
+
+# Display Table
+knitr::kable(fixation_stats_stud, caption = "N, M, SD, Min & Max for Average Fixation Duration (AOI Students)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# t-Test and Cohen's d
+t_test_fixation_stud <- t.test(Avg_fixation_duration_stud ~ Group, data = df_aoi_stud, var.equal = TRUE)
+cohen_d_fixation_stud <- cohen.d(Avg_fixation_duration_stud ~ Group, data = df_aoi_stud)
+
+# APA Table
+t_test_result_fixation_stud <- data.frame(
+  "Group Comparison" = "Experienced vs. Inexperienced",
+  "t-value" = round(t_test_fixation_stud$statistic, 2),
+  "df" = t_test_fixation_stud$parameter,
+  "p-value" = format.pval(t_test_fixation_stud$p.value, digits = 2, eps = .05),
+  "Mean Difference" = round(t_test_fixation_stud$estimate[1] - t_test_fixation_stud$estimate[2], 2),
+  "Cohen's d" = round(cohen_d_fixation_stud$estimate, 2),
+  "95% CI (d)" = paste0("[", round(cohen_d_fixation_stud$conf.int[1], 2), ", ", round(cohen_d_fixation_stud$conf.int[2], 2), "]")
+)
+
+knitr::kable(t_test_result_fixation_stud, caption = "t-Test and Effect Size for Average Fixation Duration (AOI Students)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Plot: Average Fixation Duration
+y_max_fixation_stud <- max(df_aoi_stud$Avg_fixation_duration_stud) * 1.5
+
+plot_fixation_duration_stud <- df_aoi_stud %>%
+  ggplot(aes(x = Group, y = Avg_fixation_duration_stud, fill = Group)) +
+  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
+  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
+  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
+  scale_fill_brewer(palette = "RdBu") +
+  ylim(0, y_max_fixation_stud) +
+  labs(title = "Average Fixation Duration\n(AOI Students)", x = "", y = "Fixation Duration (ms)") +
+  theme_cowplot() +
+  theme(legend.position = "none") +
+  annotate("text", x = 1, y = 10,  # Adjust y-coordinate to place above the x-axis
+           label = paste0("italic(M) == ", round(fixation_stats_stud$M[1], 2), " * ',' ~ italic(SD) == ", round(fixation_stats_stud$SD[1], 2)),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  annotate("text", x = 2, y = 10,  # Adjust y-coordinate to place above the x-axis
+           label = paste0("italic(M) == ", round(fixation_stats_stud$M[2], 2), " * ',' ~ italic(SD) == ", round(fixation_stats_stud$SD[2], 2)),
+           hjust = 0.5, size = 4, parse = TRUE) +
+  annotate("text", x = 1.5, y = y_max_fixation_stud * 0.95,
+           label = paste0("italic(p) == ", round(t_test_fixation_stud$p.value, 2), " * ',' ~ italic(d) == ", round(cohen_d_fixation_stud$estimate, 2)),
+           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
+
+plot_fixation_duration_stud
+
+ggsave(filename = "plots/plot_fixation_duration_stud.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+```
+
+#### Number of fixations per seconds (AOI disruptive person)
+```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+##################### NUMBER OF FIXATIONS ON AOI DISRUPTIVE PERSON ########################
+
+# Define the different types of disruptions and categories
+disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
+                 "Drumming_with_hands", "Head_on_table", "Heckling", 
+                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
+verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
+physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
+lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")
+
+# Step 1: Filter and prepare the data
+df_aoi_disrup <- df_aoi %>%
+  filter(TOI %in% disruptions) %>% # Filter rows based on the disruption list
+  select(Group, Participant, TOI, Duration_of_interval, "Number_of_fixations.Disruptive_Person") %>%
+  mutate(
+    Group = as_factor(Group), # Convert Group column to a factor
+    Disruption_Category = case_when( # Assign categories based on disruption type
+      TOI %in% verbal_disruptions ~ "Verbal disruptions",
+      TOI %in% physical_disruptions ~ "Physical disruptions",
+      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
+      TRUE ~ NA_character_
+    ),
+    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2) # Convert duration to seconds
+  ) %>%
+  filter(!is.na(Disruption_Category)) # Keep only rows with valid categories
+
+# Step 2: Summarize data by disruption category
+disruption_summary <- df_aoi_disrup %>%
+  group_by(Group, Participant, Disruption_Category) %>%
+  summarise(
+    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2), # Total time in seconds
+    fixation_count = round(sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE), 2), # Total fixations
+    fixations_per_second = round(fixation_count / total_duration_sec, 2), # Number of fixations per second
+    .groups = "drop"
+  )
+
+# Step 3: Summarize by participant
+individual_summary <- disruption_summary %>%
+  group_by(Group, Participant) %>%
+  summarise(
+    mean_fixations_per_second = round(mean(fixations_per_second, na.rm = TRUE), 2), # Mean number of fixations
+    .groups = "drop"
+  )
+
+##################### DESCRIPTIVE STATISTICS ########################
+
+# Descriptive statistics for number of fixations
+overall_stats <- individual_summary %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(), # Number of participants
+    Mean = round(mean(mean_fixations_per_second, na.rm = TRUE), 2), # Mean number of fixations
+    SD = round(sd(mean_fixations_per_second, na.rm = TRUE), 2), # Standard deviation
+    Min = round(min(mean_fixations_per_second, na.rm = TRUE), 2), # Minimum value
+    Max = round(max(mean_fixations_per_second, na.rm = TRUE), 2), # Maximum value
+    .groups = "drop"
+  )
+
+# Display the overall descriptive statistics table
+kable(
+  overall_stats,
+  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Number of Fixations by Group (AOI Disruptive Person)",
+  col.names = c("Group", "N", "M", "SD", "Min", "Max"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+# Descriptive statistics by disruption category
+category_stats <- disruption_summary %>%
+  group_by(Disruption_Category, Group) %>%
+  summarise(
+    N = n_distinct(Participant), # Count unique participants
+    Mean = round(mean(fixations_per_second, na.rm = TRUE), 2), # Mean number of fixations
+    SD = round(sd(fixations_per_second, na.rm = TRUE), 2), # Standard deviation
+    Min = round(min(fixations_per_second, na.rm = TRUE), 2), # Minimum value
+    Max = round(max(fixations_per_second, na.rm = TRUE), 2), # Maximum value
+    .groups = "drop"
+  )
+
+# Display the descriptive statistics table by category
+kable(
+  category_stats,
+  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Number of Fixations by Group and Category (AOI Disruptive Person)",
+  col.names = c("Group", "Category", "N", "M", "SD", "Min", "Max"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### FIRST PLOT: Number of Fixations AOI Disruptive Person ########################
+
+# Calculate values for annotations
+mean_novice <- round(mean(individual_summary$mean_fixations_per_second[individual_summary$Group == "Novice"], na.rm = TRUE), 2)
+sd_novice <- round(sd(individual_summary$mean_fixations_per_second[individual_summary$Group == "Novice"], na.rm = TRUE), 2)
+mean_expert <- round(mean(individual_summary$mean_fixations_per_second[individual_summary$Group == "Expert"], na.rm = TRUE), 2)
+sd_expert <- round(sd(individual_summary$mean_fixations_per_second[individual_summary$Group == "Expert"], na.rm = TRUE), 2)
+
+# t-Test and effect size
+t_test <- t.test(mean_fixations_per_second ~ Group, data = individual_summary, var.equal = TRUE)
+p_value <- round(t_test$p.value, 2)
+cohen_d <- round(cohen.d(mean_fixations_per_second ~ Group, data = individual_summary)$estimate, 2)
+
+# Number of fixations plot with annotations
+y_max_overall <- max(individual_summary$mean_fixations_per_second, na.rm = TRUE) * 1.5
+
+plot_number_fix_disrup <- ggplot(individual_summary,
+          aes(x = Group, y = mean_fixations_per_second, fill = Group)) +
+  geom_boxplot(outlier.shape = NA, width = 0.5) +
+  geom_jitter(
+    width = 0.1,
+    alpha = 0.7,
+    color = "black",
+    size = 1.5
+  ) +
+  labs(x = "", y = "Number of Fixations per Second") +
+  ggtitle("Number of Fixations per Second \n(AOI Disruptive Person)") +
+  scale_fill_brewer(palette = "RdBu") +
+  theme_cowplot() +
+  ylim(0, y_max_overall) +
+  theme(legend.position = "none") +
+  annotate(
+    "text",
+    x = 1,
+    y = y_max_overall * 0.85,
+    label = paste0("M = ", mean_novice, "\nSD = ", sd_novice),
+    hjust = 0.5,
+    size = 4,
+    fontface = "italic"
+  ) +
+  annotate(
+    "text",
+    x = 2,
+    y = y_max_overall * 0.85,
+    label = paste0("M = ", mean_expert, "\nSD = ", sd_expert),
+    hjust = 0.5,
+    size = 4,
+    fontface = "italic"
+  ) +
+  annotate(
+    "text",
+    x = 1.5,
+    y = y_max_overall * 0.95,
+    label = paste0("p = ", p_value, "\nd = ", cohen_d),
+    hjust = 0.5,
+    size = 4,
+    fontface = "italic"
+  )
+
+ggsave(filename = "plots/plot_number_fix_disrup.svg",
+       width = 20,
+       height = 12,
+       units = "cm")
+
+##################### SECOND PLOT: NUMBER OF FIXATIONS BY CATEGORY (AOI DISRUPTIVE PERSON) ########################
+
+# Create the plot
+plot_category_fix_disrup <- disruption_summary %>%
+  ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_point(
+    size = 2,
+    alpha = 0.7,
+    position = position_jitter(
+      seed = 1,
+      width = 0.1,
+      height = 0.1
+    )
+  ) +
+  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) + # Fixed y-axis across facets
+  labs(x = "", y = "Number of Fixations per Second") +
+  ggtitle("Number of Fixations per Second Splitted by Disruption Category and Group\n(AOI Disruptive Person)") +
+  scale_fill_brewer(palette = "RdBu") +
+  theme_cowplot() +
+  theme(
+    legend.position = "none",
+    strip.text = element_text(size = 10) # Adjust facet text size if necessary
+  )
+
+ggsave(filename = "plots/plot_category_fix_disrup.svg",
+       width = 24,
+       height = 12,
+       units = "cm")
+
+# Display the plots
+plot_number_fix_disrup
+plot_category_fix_disrup
+
+##################### STATISTICAL TESTS ########################
+
+# Table summarizing overall t-test and Cohen's d
+overall_effect <- data.frame(
+  Group = c("Overall"),
+  `t-value` = round(t_test$statistic, 2),
+  `p-value` = p_value,
+  `Cohen's d` = cohen_d
+)
+
+# Display t-test and effect size table
+kable(
+  overall_effect,
+  caption = "t-Test and Effect Size for Number of Fixations (AOI DIsruptive Person)",
+  col.names = c("Group", "t-value", "p-value", "Cohen's d"),
+  row.names = FALSE
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### REPEATED MEASURES ANOVA ########################
+
+# Perform the repeated-measures ANOVA
+anova_afex <- afex::aov_ez(
+  id = "Participant", # Random effect
+  dv = "fixations_per_second", # Dependent variable
+  between = "Group", # Between-subject factor
+  within = "Disruption_Category", # Within-subject factor
+  data = disruption_summary
+)
+
+# Extract the ANOVA table
+anova_results <- as.data.frame(anova_afex$anova_table)
+
+# Recalculate generalized eta squared (η²)
+eta_squared_results <- effectsize::eta_squared(anova_afex, partial = FALSE)
+
+# Combine recalculated eta squared with the ANOVA table
+anova_table_apa <- anova_results %>%
+  rownames_to_column(var = "Effect") %>% # Move row names to a column
+  left_join(
+    as.data.frame(eta_squared_results), 
+    by = c("Effect" = "Parameter") # Match the correct columns
+  ) %>%
+  mutate(
+    `F` = round(`F`, 2), # Round F-values
+    `η²` = round(Eta2, 3), # Round generalized eta squared
+    `p-value` = ifelse(
+      `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 3) # Format p-values
+    )
+  ) %>%
+  select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`) # Order columns, place η² last
+
+# Display the table
+kable(
+  anova_table_apa,
+  caption = "Repeated-Measures ANOVA Results (Including Effect Sizes)",
+  col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
+  digits = 2
+) %>%
+  kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### POST-HOC TESTS ########################
+
+# Perform post-hoc pairwise comparisons for Disruption_Category (within-subject factor)
+post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)
+
+# Extract post-hoc pairwise contrasts for Disruption_Category
+post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
+  mutate(
+    Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+    Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
+    Estimate = round(estimate, 2),
+    SE = round(SE, 2),
+    t = round(t.ratio, 2),
+    p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))
+  )
+
+##################### COHEN'S D CALCULATION ########################
+
+# Define the disruption categories
+categories <- c("Lack of eagerness to learn", "Physical disruptions", "Verbal disruptions")
+
+# Initialize an empty list to store the Cohen's d values
+cohen_d_values <- vector("list", length = nrow(post_hoc_results_disruption))
+
+# Loop over the post-hoc results to calculate Cohen's d for each comparison
+for (i in 1:nrow(post_hoc_results_disruption)) {
+  # Extract the two categories being compared
+  group1 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][1]
+  group2 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][2]
+
+  # Get the data for the two groups being compared using fixations_per_second
+  group1_data <- disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == group1]
+  group2_data <- disruption_summary$fixations_per_second[disruption_summary$Disruption_Category == group2]
+
+  # Calculate the means and standard deviations for each group
+  mean1 <- mean(group1_data, na.rm = TRUE)
+  mean2 <- mean(group2_data, na.rm = TRUE)
+
+  sd1 <- sd(group1_data, na.rm = TRUE)
+  sd2 <- sd(group2_data, na.rm = TRUE)
+
+  # Calculate the pooled standard deviation
+  pooled_sd <- sqrt(((length(group1_data) - 1) * sd1^2 + (length(group2_data) - 1) * sd2^2) / (length(group1_data) + length(group2_data) - 2))
+
+  # Calculate Cohen's d using the formula (mean difference / pooled SD)
+  d_value <- (mean1 - mean2) / pooled_sd
+
+  # Store the absolute value of Cohen's d
+  cohen_d_values[[i]] <- abs(round(d_value, 2))  # Take the absolute value of Cohen's d
+}
+
+# Add the Cohen's d values to the post-hoc results
+post_hoc_results_disruption$Cohen_d <- unlist(cohen_d_values)
+
+##################### TABLE FOR DISRUPTION CATEGORY ########################
+
+# Ensure the number of column names matches the number of columns in the data frame
+post_hoc_results_disruption <- post_hoc_results_disruption %>%
+  select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+
+# Displaying the table
+knitr::kable(
+  post_hoc_results_disruption,
+  caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Including Effect Sizes)",
+  col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+  digits = 2
+) %>%
+kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 y_max_overall <- max(individual_summary$mean_duration, na.rm = TRUE) * 1.5
-plot_overall <- ggplot(individual_summary, aes(x = Group, y = mean_duration, fill = Group)) +
+
+plot_overall_dur_disrup <- ggplot(individual_summary, aes(x = Group, y = mean_duration, fill = Group)) +
   geom_boxplot(outlier.shape = NA, width = 0.5) +
   geom_jitter(width = 0.1, alpha = 0.7, color = "black", size = 1.5) +
-  labs(x = "", y = "Mean Duration (ms) per Participant") +
-  ggtitle("Average Duration per Participant\n(AOI Disruptive Person)") +
+  labs(x = "", y = "Average Fixation Duration (ms)") +
+  ggtitle("Average Fixation Duration\n(AOI Disruptive Person)") +
   scale_fill_brewer(palette = "RdBu") +
@@
   ylim(0, 2000) +
-  labs(x = "", y = "Mean Duration (ms)") +
-  ggtitle("Average Duration of Fixations by Disruption Category and Group") +
+  labs(x = "", y = "Average Fixation Duration (ms)") +
+  ggtitle("Average Duration of Fixations Splitted by Disruption Category and Group\n(AOI Disruptive Person)") +
   scale_fill_brewer(palette = "RdBu") +
@@
 
+ggsave(
+  filename = "plots/plot_category_dur_disrup.svg",
+  width = 24,
+  height = 12,
+  units = "cm"
+)
+
 # Display plots
-plot_overall
-plot_category
+plot_overall_dur_disrup
+plot_category_dur_disrup
 
@@
 ) %>%
-kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-```
-
-#### Gaze Relational Index (GRI; micro-teaching unit)
-```{r gri_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-##################### GRI in MICRO-TEACHING UNIT ########################
-
-# Step 1: Calculate GRI (Gaze Ratio Index) for each participant
-df_gri <- df_aoi_sum %>%
-  mutate(GRI = round(Average_duration_fixation / Number_fixation_min_mtu, 2))
-
-# Step 2: Summarize GRI statistics (N, Mean, SD, Min, Max) by Group
-gri_table <- df_gri %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    "M" = round(mean(GRI, na.rm = TRUE), 2),
-    "SD" = round(sd(GRI, na.rm = TRUE), 2),
-    "Min" = round(min(GRI, na.rm = TRUE), 2),
-    "Max" = round(max(GRI, na.rm = TRUE), 2)
-  )
-
-# Display the GRI summary table in APA format
-knitr::kable(gri_table,
-             caption = "N, M, SD, Min, and Max GRI (Micro-Teaching Unit)") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Step 3: Plot GRI by Group with boxplot and jittered points
-# Calculate annotation values
-mean_novice_gri <- round(mean(df_gri$GRI[df_gri$Group == "Novice"], na.rm = TRUE), 2)
-sd_novice_gri <- round(sd(df_gri$GRI[df_gri$Group == "Novice"], na.rm = TRUE), 2)
-mean_expert_gri <- round(mean(df_gri$GRI[df_gri$Group == "Expert"], na.rm = TRUE), 2)
-sd_expert_gri <- round(sd(df_gri$GRI[df_gri$Group == "Expert"], na.rm = TRUE), 2)
-
-# Maximum y-axis value for plot
-y_max_gri <- max(df_gri$GRI, na.rm = TRUE) * 1.2
-
-# Conduct t-test
-t_test_gri <- t.test(
-  GRI ~ Group,
-  data = df_gri,
-  var.equal = TRUE
-)
-
-# Extract p-value
-p_value_gri <- round(t_test_gri$p.value, 2)
-
-# Calculate Cohen's d (full result object)
-d_gri_full <- cohen.d(GRI ~ Group, data = df_gri, pooled = TRUE)
-
-# Extract Cohen's d and confidence interval
-d_gri <- round(d_gri_full$estimate, 2)
-d_conf_int_gri <- paste0("[", round(d_gri_full$conf.int[1], 2), ", ", round(d_gri_full$conf.int[2], 2), "]")
-
-# Annotated Plot
-plot_gri_group <- df_gri %>%
-  ggplot(aes(x = Group, y = GRI, fill = Group)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_jitter(size = 2, alpha = 0.7, width = 0.1, height = 0.1, seed = 1) +
-  ylim(0, y_max_gri) +
-  labs(x = "", y = "Average Duration of Fixations /\nNumber of Fixations per Minute") +
-  scale_fill_brewer(palette = "RdBu") +
-  ggtitle("GRI\n(Micro-Teaching Unit)") +
-  theme_cowplot() +
-  theme(
-    legend.position = "none",
-    plot.title = element_text(hjust = 0.5, face = "bold")
-  ) +
-  # Annotate mean (M) and SD
-  annotate("text", x = 1, y = y_max_gri * 0.85,
-           label = paste0("atop(italic(M) == ", mean_novice_gri, ", italic(SD) == ", sd_novice_gri, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  annotate("text", x = 2, y = y_max_gri * 0.85,
-           label = paste0("atop(italic(M) == ", mean_expert_gri, ", italic(SD) == ", sd_expert_gri, ")"),
-           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
-  # Annotate p-value and Cohen's d
-  annotate("text", x = 1.5, y = y_max_gri * 0.95,
-           label = paste0("p = ", p_value_gri, "\nd = ", d_gri),
-           hjust = 0.5, size = 4, fontface = "italic")
-
-plot_gri_group
-
-##################### t-Test & Effect Size for GRI ########################
-
-# Step 6: Create a table for the t-test and Cohen's d results
-gri_t_test_table <- data.frame(
-  "Group Comparison" = "Experts vs. Novices",
-  "t-value" = round(t_test_gri$statistic, 2),
-  "df" = t_test_gri$parameter,
-  "p-value" = round(t_test_gri$p.value, 2),
-  "Mean Difference" = round(t_test_gri$estimate[1] - t_test_gri$estimate[2], 2),
-  "Cohen's d" = d_gri,
-  "95% CI (d)" = d_conf_int_gri
-)
-
-# Display the t-Test and Effect Size table for GRI in APA format
-knitr::kable(gri_t_test_table, 
-             caption = "t-Test and Effect Size for GRI (Micro-Teaching Unit)") %>%
 kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
@@
 #   kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+```
+
+### Duration of disruption
+```{r dur_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+# 
+# ##################### DATA PREPARATION ########################
+# 
+# # Prepare data for analysis: filter, calculate, and categorize disruptions
+# df_aoi_disrup <- df_aoi %>%
+#   filter(TOI %in% disruptions, Duration_of_interval <= 30000) %>%
+#   select(Group, Participant, TOI, Duration_of_interval) %>%
+#   mutate(
+#     Group = as_factor(Group),
+#     Disruption_Category = case_when(
+#       TOI %in% verbal_disruptions ~ "Verbal disruptions",
+#       TOI %in% physical_disruptions ~ "Physical disruptions",
+#       TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
+#       TRUE ~ NA_character_
+#     ),
+#     Duration_of_interval_sec = round(Duration_of_interval / 1000, 2)
+#   ) %>%
+#   filter(!is.na(Disruption_Category)) %>%
+#   drop_na()
+# 
+# ##################### DESCRIPTIVE STATISTICS ########################
+# 
+# # Descriptive Statistics by Group
+# summary_stats_group <- df_aoi_disrup %>%
+#   group_by(Group) %>%
+#   summarise(
+#     N = n(),
+#     Mean = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     SD = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     Median = round(median(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     IQR = round(IQR(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     Min = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     Max = round(max(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     .groups = "drop"
+#   )
+# 
+# # Descriptive Statistics by Category and Group
+# summary_stats_category_group <- df_aoi_disrup %>%
+#   group_by(Disruption_Category, Group) %>%
+#   summarise(
+#     N = n(),
+#     Mean = round(mean(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     SD = round(sd(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     Median = round(median(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     IQR = round(IQR(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     Min = round(min(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     Max = round(max(Duration_of_interval_sec, na.rm = TRUE), 2),
+#     .groups = "drop"
+#   )
+# 
+# # Display Descriptive Tables
+# kable(
+#   summary_stats_group,
+#   caption = "Descriptive Statistics for Disruption Duration by Group",
+#   col.names = c("Group", "N", "Mean", "SD", "Median", "IQR", "Min", "Max"),
+#   row.names = FALSE
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# kable(
+#   summary_stats_category_group,
+#   caption = "Descriptive Statistics for Disruption Duration by Category and Group",
+#   col.names = c("Category", "Group", "N", "Mean", "SD", "Median", "IQR", "Min", "Max"),
+#   row.names = FALSE
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# ##################### PLOTS ########################
+# 
+# # Plot 1: Disruption Duration by Group
+# plot_duration_group <- ggplot(df_aoi_disrup, aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
+#   geom_boxplot(outlier.shape = NA, width = 0.5) +
+#   geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
+#   labs(x = "Group", y = "Disruption Duration (seconds)") +
+#   theme_cowplot() +
+#   scale_fill_brewer(palette = "RdBu") +
+#   ggtitle("Disruption Duration by Group") +
+#   theme(legend.position = "none") +
+#   annotate("text", x = 1, y = max(df_aoi_disrup$Duration_of_interval_sec) + 4,
+#            label = paste0("Median = ", summary_stats_group$Median[summary_stats_group$Group == "Novice"],
+#                           "\nIQR = ", summary_stats_group$IQR[summary_stats_group$Group == "Novice"]),
+#            hjust = 0.5, size = 4) +
+#   annotate("text", x = 2, y = max(df_aoi_disrup$Duration_of_interval_sec) + 4,
+#            label = paste0("Median = ", summary_stats_group$Median[summary_stats_group$Group == "Expert"],
+#                           "\nIQR = ", summary_stats_group$IQR[summary_stats_group$Group == "Expert"]),
+#            hjust = 0.5, size = 4)
+# 
+# plot_duration_group
+# 
+# ggsave(filename = "plots/plot_duration_group.svg",
+#        width = 20,
+#        height = 12,
+#        units = "cm")
+# 
+# 
+# # Plot 2: Disruption Duration by Group and Category
+# plot_duration_category <- ggplot(df_aoi_disrup, aes(x = Group, y = Duration_of_interval_sec, fill = Group)) +
+#   geom_boxplot(outlier.shape = NA, width = 0.5) +
+#   geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
+#   facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) +  # Use fixed scale for all facets
+#   labs(x = "Group", y = "Disruption Duration (seconds)") +
+#   theme_cowplot() +
+#   scale_fill_brewer(palette = "RdBu") +
+#   ggtitle("Disruption Duration by Group and Category") +
+#   theme(legend.position = "none")
+# 
+# # Display the plot
+# plot_duration_category
+# 
+# ggsave(filename = "plots/plot_duration_category.svg",
+#        width = 24,
+#        height = 12,
+#        units = "cm")
+# 
+# 
+# ##################### STATISTICAL TESTS ########################
+# 
+# ##################### REPEATED MEASURES ANOVA ########################
+# 
+# # Perform the repeated-measures ANOVA with `Duration_of_interval_sec` as the dependent variable
+# anova_afex_duration <- afex::aov_ez(
+#   id = "Participant",  # Random effect
+#   dv = "Duration_of_interval_sec",  # Dependent variable: disruption duration in seconds
+#   between = "Group",  # Between-subject factor: Group (Novice vs Expert)
+#   within = "Disruption_Category",  # Within-subject factor: Disruption Categories
+#   data = df_aoi_disrup
+# )
+# 
+# # Extract the ANOVA table
+# anova_results_duration <- as.data.frame(anova_afex_duration$anova_table)
+# 
+# # Recalculate generalized eta squared (η²) for effect size
+# eta_squared_results_duration <- effectsize::eta_squared(anova_afex_duration, partial = FALSE)
+# 
+# # Combine recalculated eta squared with the ANOVA table
+# anova_table_apa_duration <- anova_results_duration %>%
+#   rownames_to_column(var = "Effect") %>%  # Move row names to a column
+#   left_join(
+#     as.data.frame(eta_squared_results_duration), 
+#     by = c("Effect" = "Parameter")  # Match the correct columns
+#   ) %>%
+#   mutate(
+#     `F` = round(`F`, 2),  # Round F-values
+#     `η²` = round(Eta2, 3),  # Round generalized eta squared
+#     `p-value` = ifelse(
+#       `Pr(>F)` < 0.05, "< .05", round(`Pr(>F)`, 3)  # Format p-values
+#     )
+#   ) %>%
+#   select(Effect, `num Df`, `den Df`, `F`, `p-value`, `η²`)  # Order columns, place η² last
+# 
+# # Display the ANOVA table
+# kable(
+#   anova_table_apa_duration,
+#   caption = "Repeated-Measures ANOVA Results for Disruption Duration (Including Effect Sizes)",
+#   col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
+#   digits = 2
+# ) %>%
+#   kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# ##################### POST-HOC TESTS Disruption_Category (main effect) ########################
+# 
+# # Perform post-hoc pairwise comparisons for Disruption_Category (main effect)
+# post_hoc_disruption <- emmeans(anova_afex, pairwise ~ Disruption_Category)
+# 
+# # Extract post-hoc pairwise contrasts for Disruption_Category (main effect)
+# post_hoc_results_disruption <- as.data.frame(post_hoc_disruption$contrasts) %>%
+#   mutate(
+#     Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+#     Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
+#     Estimate = round(estimate, 2),
+#     SE = round(SE, 2),
+#     t = round(t.ratio, 2),
+#     p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))
+#   )
+# 
+# ##################### COHEN'S D CALCULATION ########################
+# 
+# # Initialize empty lists to store Cohen's d values for both post-hoc tests
+# cohen_d_values_disruption <- vector("list", length = nrow(post_hoc_results_disruption))
+# 
+# # Loop over the post-hoc results for Disruption_Category to calculate Cohen's d for each comparison (main effect)
+# for (i in 1:nrow(post_hoc_results_disruption)) {
+#   # Extract the two categories being compared
+#   group1 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][1]
+#   group2 <- strsplit(post_hoc_results_disruption$Comparison[i], " - ")[[1]][2]
+#   
+#   # Get the data for the two groups being compared using Duration_of_interval_sec
+#   group1_data <- df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Disruption_Category == group1]
+#   group2_data <- df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Disruption_Category == group2]
+#   
+#   # Calculate the means and standard deviations for each group
+#   mean1 <- mean(group1_data, na.rm = TRUE)
+#   mean2 <- mean(group2_data, na.rm = TRUE)
+#   
+#   sd1 <- sd(group1_data, na.rm = TRUE)
+#   sd2 <- sd(group2_data, na.rm = TRUE)
+#   
+#   # Calculate the pooled standard deviation
+#   pooled_sd <- sqrt(((length(group1_data) - 1) * sd1^2 + (length(group2_data) - 1) * sd2^2) / (length(group1_data) + length(group2_data) - 2))
+#   
+#   # Calculate Cohen's d using the formula (mean difference / pooled SD)
+#   d_value <- (mean1 - mean2) / pooled_sd
+#   
+#   # Store the absolute value of Cohen's d
+#   cohen_d_values_disruption[[i]] <- abs(round(d_value, 2))  # Take the absolute value of Cohen's d
+# }
+# 
+# 
+# # Add the Cohen's d values to the post-hoc results
+# post_hoc_results_disruption$Cohen_d <- unlist(cohen_d_values_disruption)
+# 
+# 
+# ##################### TABLE FOR DISRUPTION CATEGORY ########################
+# 
+# # Ensure the number of column names matches the number of columns in the data frame
+# post_hoc_results_disruption <- post_hoc_results_disruption %>%
+#   select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+# 
+# # Displaying the post-hoc results for Disruption Category (main effect)
+# knitr::kable(
+#   post_hoc_results_disruption,
+#   caption = "Post-Hoc Pairwise Comparisons for Disruption Categories (Main Effect)",
+#   col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+#   digits = 2
+# ) %>%
+# kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# 
+# #################### POST-HOC TESTS interaction effect (Group:Disruption_Category) ########################
+# 
+# # Calculate post-hoc pairwise comparisons for the interaction effect (Group:Disruption_Category)
+# post_hoc_interaction <- emmeans(anova_afex, pairwise ~ Group * Disruption_Category)
+# 
+# # Extract the post-hoc contrasts for the interaction
+# post_hoc_results_interaction <- as.data.frame(post_hoc_interaction$contrasts) %>%
+#   mutate(
+#     Comparison = gsub("_", " ", contrast),  # Replace underscores with spaces
+#     Comparison = gsub("\\.", " ", Comparison), # Replace periods with spaces
+#     Estimate = round(estimate, 2),
+#     SE = round(SE, 2),
+#     t = round(t.ratio, 2),
+#     p.value = ifelse(p.value < 0.05, "< .05", round(p.value, 2))  # Round p-values to 2 decimals
+#   )
+# 
+# ##################### COHEN'S D CALCULATION ########################
+# 
+# # 1. Novice Lack of eagerness to learn vs Expert Lack of eagerness to learn
+# d_LackOfEagerness_Novice_vs_Expert <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   na.rm = TRUE
+# )
+# 
+# # 2. Novice Lack of eagerness to learn vs Novice Physical disruptions
+# d_LackOfEagerness_vs_Physical_Novice <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 3. Novice Lack of eagerness to learn vs Expert Physical disruptions
+# d_LackOfEagerness_vs_Physical_Expert <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 4. Novice Lack of eagerness to learn vs Novice Verbal disruptions
+# d_LackOfEagerness_vs_Verbal_Novice <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 5. Novice Lack of eagerness to learn vs Expert Verbal disruptions
+# d_LackOfEagerness_vs_Verbal_Expert <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 6. Expert Lack of eagerness to learn vs Novice Physical disruptions
+# d_Expert_LackOfEagerness_vs_Physical_Novice <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 7. Expert Lack of eagerness to learn vs Expert Physical disruptions
+# d_Expert_LackOfEagerness_vs_Physical_Expert <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 8. Expert Lack of eagerness to learn vs Novice Verbal disruptions
+# d_Expert_LackOfEagerness_vs_Verbal_Novice <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 9. Expert Lack of eagerness to learn vs Expert Verbal disruptions
+# d_Expert_LackOfEagerness_vs_Verbal_Expert <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Lack of eagerness to learn"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 10. Novice Physical disruptions vs Expert Physical disruptions
+# d_Physical_Novice_vs_Expert <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 11. Novice Physical disruptions vs Novice Verbal disruptions
+# d_Physical_Novice_vs_Verbal_Novice <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 12. Novice Physical disruptions vs Expert Verbal disruptions
+# d_Physical_Novice_vs_Verbal_Expert <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 13. Expert Physical disruptions vs Novice Verbal disruptions
+# d_Physical_Expert_vs_Verbal_Novice <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 14. Expert Physical disruptions vs Expert Verbal disruptions
+# d_Physical_Expert_vs_Verbal_Expert <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Physical disruptions"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# # 15. Novice Verbal disruptions vs Expert Verbal disruptions
+# d_Verbal_Novice_vs_Expert <- CohenD(
+#   x = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Novice" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   y = df_aoi_disrup$Duration_of_interval_sec[df_aoi_disrup$Group == "Expert" & df_aoi_disrup$Disruption_Category == "Verbal disruptions"],
+#   na.rm = TRUE
+# )
+# 
+# ##################### CREATE A NAMED VECTOR FOR COHEN'S D ########################
+# 
+# # Create a named vector with the correct Cohen's d values
+# cohen_d_values_interaction <- c(
+#   "Novice Lack of eagerness to learn - Expert Lack of eagerness to learn" = round(d_LackOfEagerness_Novice_vs_Expert, 2),
+#   "Novice Lack of eagerness to learn - Novice Physical disruptions" = round(d_LackOfEagerness_vs_Physical_Novice, 2),
+#   "Novice Lack of eagerness to learn - Expert Physical disruptions" = round(d_LackOfEagerness_vs_Physical_Expert, 2),
+#   "Novice Lack of eagerness to learn - Novice Verbal disruptions" = round(d_LackOfEagerness_vs_Verbal_Novice, 2),
+#   "Novice Lack of eagerness to learn - Expert Verbal disruptions" = round(d_LackOfEagerness_vs_Verbal_Expert, 2),
+#   "Expert Lack of eagerness to learn - Novice Physical disruptions" = round(d_Expert_LackOfEagerness_vs_Physical_Novice, 2),
+#   "Expert Lack of eagerness to learn - Expert Physical disruptions" = round(d_Expert_LackOfEagerness_vs_Physical_Expert, 2),
+#   "Expert Lack of eagerness to learn - Novice Verbal disruptions" = round(d_Expert_LackOfEagerness_vs_Verbal_Novice, 2),
+#   "Expert Lack of eagerness to learn - Expert Verbal disruptions" = round(d_Expert_LackOfEagerness_vs_Verbal_Expert, 2),
+#   "Novice Physical disruptions - Expert Physical disruptions" = round(d_Physical_Novice_vs_Expert, 2),
+#   "Novice Physical disruptions - Novice Verbal disruptions" = round(d_Physical_Novice_vs_Verbal_Novice, 2),
+#   "Novice Physical disruptions - Expert Verbal disruptions" = round(d_Physical_Novice_vs_Verbal_Expert, 2),
+#   "Expert Physical disruptions - Novice Verbal disruptions" = round(d_Physical_Expert_vs_Verbal_Novice, 2),
+#   "Expert Physical disruptions - Expert Verbal disruptions" = round(d_Physical_Expert_vs_Verbal_Expert, 2),
+#   "Novice Verbal disruptions - Expert Verbal disruptions" = round(d_Verbal_Novice_vs_Expert, 2)
+# )
+# 
+# ##################### ADD COHEN'S D VALUES TO THE POST-HOC RESULTS ########################
+# 
+# # Add Cohen's d values to the post-hoc results for each comparison
+# post_hoc_results_interaction$Cohen_d <- cohen_d_values_interaction[post_hoc_results_interaction$Comparison]
+# 
+# ##################### TABLE FOR INTERACTION EFFECT ########################
+# 
+# # Ensure the number of column names matches the number of columns in the data frame
+# post_hoc_results_interaction <- post_hoc_results_interaction %>%
+#   select(Comparison, Estimate, SE, df, t, p.value, Cohen_d)
+# 
+# # Display the post-hoc results for Group x Disruption_Category interaction with Cohen's d
+# knitr::kable(
+#   post_hoc_results_interaction,
+#   caption = "Post-Hoc Pairwise Comparisons for Group x Disruption Category Interaction (Including Effect Sizes)",
+#   col.names = c("Comparison", "Estimate", "SE", "df", "t", "p", "Cohen's d"),
+#   digits = 2
+# ) %>%
+#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# 
+# # 
+# # # 1. Normality Tests (Shapiro-Wilk)
+# # # The Shapiro-Wilk test is used to assess whether the data for each group (Novice and Expert) follows a normal distribution.
+# # normality_tests <- df_aoi_disrup %>%
+# #   group_by(Group) %>%  # Group data by "Group" (Novice and Expert)
+# #   summarise(
+# #     Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),  # Perform Shapiro-Wilk test for normality and round the p-value
+# #     .groups = "drop"  # Drop the grouping after summarizing
+# #   )
+# # 
+# # # The p-value here is extremely small (0), which indicates that both the "Novice" and "Expert" groups deviate significantly from a normal distribution.
+This suggests that the data in both groups are not normally distributed, and therefore, non-parametric tests like the Mann-Whitney U test are more appropriate for analyzing differences between these groups.
+# # 
+# # # Display the Shapiro-Wilk test results in a nicely formatted table
+# # kable(
+# #   normality_tests,  # Table with Shapiro-Wilk p-values for each group
+# #   caption = "Shapiro-Wilk Test for Normality by Group",  # Caption for the table
+# #   col.names = c("Group", "Shapiro-Wilk p-value"),  # Column names
+# #   row.names = FALSE  # Don't show row names
+# # ) %>%
+# #   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Style the table with a striped pattern
+# # 
+# # # 2. Mann-Whitney U-Test and Effect Size
+# # # The Mann-Whitney U test is used to compare the duration of disruption between the Novice and Expert groups
+# # # This is a non-parametric test used when the data is not normally distributed (based on the Shapiro-Wilk test results).
+# # mann_whitney_test <- wilcox.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, exact = FALSE)
+# # 
+# # # Calculate Effect Size (r) for the Mann-Whitney U test
+# # # Formula for r: r = |W - (n1 * n2 / 2)| / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
+# # n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))  # Number of Novice participants
+# # n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))  # Number of Expert participants
+# # r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
+# # 
+# # # Create a data frame with the Mann-Whitney U test results, including the test statistic, p-value, and effect size
+# # mann_whitney_results <- data.frame(
+# #   "Test" = "Mann-Whitney U",  # Test name
+# #   "W" = round(mann_whitney_test$statistic, 2),  # Test statistic (W)
+# #   "p-value" = round(mann_whitney_test$p.value, 3),  # p-value from the test
+# #   "Effect Size (r)" = round(r_effect, 3)  # Effect size (r) rounded to 3 decimals
+# # )
+# # 
+# # # Explanation: The Mann-Whitney U test is a non-parametric test used to compare differences between two independent groups (in this case, Novices and Experts).
+It is used because the data is not normally distributed, as indicated by the Shapiro-Wilk test.
+# # # p-value: A p-value of 0.879 is much larger than the common significance threshold of 0.05.
+This means there is no significant difference between the Novice and Expert groups in terms of the disruption duration.
+# # # Effect size (r): The effect size value of 0.152 suggests a small effect.
+This confirms that even though the test was not significant, there was still a small effect observed, but it's not large enough to be practically meaningful.
+# # 
+# # 
+# # # Display the Mann-Whitney U test results in a formatted table
+# # kable(
+# #   mann_whitney_results,
+# #   caption = "Mann-Whitney U-Test Results for Disruption Duration",  # Table caption
+# #   row.names = FALSE  # Don't show row names
+# # ) %>%
+# #   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
+# # 
+# # # 3. Kruskal-Wallis Test and Pairwise Comparisons
+# # # The Kruskal-Wallis test is a non-parametric test to compare multiple groups (Disruption Categories) at once.
+# # # It tests whether the distributions of disruption duration across categories are equal.
+# # kruskal_test <- kruskal.test(Duration_of_interval_sec ~ Disruption_Category, data = df_aoi_disrup)
+# # 
+# # # Create a data frame with the Kruskal-Wallis test results, including Chi-squared statistic, degrees of freedom, and p-value
+# # kruskal_results <- data.frame(
+# #   "Test" = "Kruskal-Wallis",  # Test name
+# #   "Chi-squared" = round(kruskal_test$statistic, 2),  # Chi-squared statistic from the test
+# #   "df" = kruskal_test$parameter,  # Degrees of freedom (df)
+# #   "p-value" = round(kruskal_test$p.value, 3)  # p-value from the test
+# # )
+# # 
+# # # Explanation: The Kruskal-Wallis test is a non-parametric test used to compare more than two independent groups (in this case, different types of disruptions).
+It is used when the assumption of normality is not met (as in the Shapiro-Wilk test).
+# # # p-value: A p-value of 0 indicates a highly significant difference between the disruption categories (i.e., "Verbal disruptions", "Physical disruptions", and "Lack of eagerness to learn").
+This suggests that there is a significant difference in disruption duration among these categories.
+# # # Chi-squared: The large value of 145.07 supports this conclusion, indicating a strong effect in terms of the differences between disruption categories.
+# # 
+# # # Display the Kruskal-Wallis test results in a formatted table
+# # kable(
+# #   kruskal_results,
+# #   caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",  # Table caption
+# #   row.names = FALSE  # Don't show row names
+# # ) %>%
+# #   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
+# # 
+# # # 4. Pairwise Wilcoxon test with Bonferroni correction
+# # # The pairwise Wilcoxon test is a non-parametric test used for multiple comparisons between pairs of disruption categories.
+# # # The p-values are adjusted for multiple comparisons using the Bonferroni correction to control for type I error.
+# # pairwise_wilcox <- pairwise.wilcox.test(
+# #   x = df_aoi_disrup$Duration_of_interval_sec,  # The dependent variable (Duration of Interval)
+# #   g = df_aoi_disrup$Disruption_Category,  # The grouping factor (Disruption Category)
+# #   p.adjust.method = "bonferroni"  # Adjust p-values using the Bonferroni method
+# # )
+# # 
+# # # Extract the p-values from the pairwise Wilcoxon test results and round to 3 decimal places
+# # pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
+# #   mutate(across(everything(), ~ round(., 3)))  # Round p-values to 3 decimals
+# # 
+# # # Display the pairwise Wilcoxon test results (with Bonferroni correction) in a formatted table
+# # kable(
+# #   pairwise_results,
+# #   caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",  # Table caption
+# #   row.names = TRUE  # Display row names
+# # ) %>%
+# #   kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table
 
@@
     fixation_count = round(sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE), 2),  # Total fixations
-    Disrup_fixations_per_second = round(fixation_count / total_duration_sec, 2),  # Fixation rate per second
+    Disrup_fixations_per_second = round(fixation_count / total_duration_sec, 2),  # Number of Fixation per second
     Disrup_average_fixations = round(mean(Disrup_average_fixations, na.rm = TRUE), 2),  # Average disruption fixations duration
@@
   summarise(
-    Disrup_fixations_per_second = round(mean(Disrup_fixations_per_second, na.rm = TRUE), 2),  # Mean fixation rate per participant
+    Disrup_fixations_per_second = round(mean(Disrup_fixations_per_second, na.rm = TRUE), 2),  # Mean Number of Fixation per participant
     Disrup_average_fixations = round(mean(Disrup_average_fixations, na.rm = TRUE), 2),  # Mean disruption fixation duration per participant

### 2025-01-28 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
x paper

@@
 
-# Gaze Allocation Across Areas of Interest 
+# Gaze Behavior Across Areas of Interest 
 ```{r nof__dur_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#### Percentage of fixations on each AOI, relative to the total number of fixations during the entire "Lesson" 
-# Step 1: Define AOI categories
-aoi_columns <- list(
-  "AOI_Students" = c(
-    "Number_of_fixations.Anna",
-    "Number_of_fixations.Bianca",
-    "Number_of_fixations.Carl(a)"
-  ),
-  "AOI_Disruptive_Person" = c("Number_of_fixations.Disruptive_Person"),
-  "AOI_Teacher_Material" = c(
-    "Number_of_fixations.Board_Screen",
-    "Number_of_fixations.Material_Teacher"
-  ),
-  "AOI_Student_Desk" = c(
-    "Number_of_fixations.Nametag_Anna",
-    "Number_of_fixations.Nametag_Bianca",
-    "Number_of_fixations.Nametag_Carl(a)",
-    "Number_of_fixations.Material_Students"
-  ),
-  "AOI_Classroom_Others" = c("Number_of_fixations.Classroom_Others")
-)
-
-# Step 2: Filter data for "Lesson" and select relevant columns
-df_fixations <- df_aoi %>%
-  filter(TOI == "Lesson") %>%
-  dplyr::select(Participant, Group, starts_with("Number_of_fixations"))
-
-# Step 3: Calculate total fixations per participant, excluding "Disruptive Person"
-# Extract relevant column names excluding "Disruptive Person"
-relevant_columns <- unlist(aoi_columns[c("AOI_Students", "AOI_Teacher_Material", "AOI_Student_Desk", "AOI_Classroom_Others")])
-
-# Calculate row sums for the relevant columns and add as a new column
-df_fixations <- df_fixations %>%
-  mutate(Total_fixations_excluding_disruptive = rowSums(across(all_of(relevant_columns)), na.rm = TRUE))
-
-# Step 4: Calculate fixation percentages for each AOI based on the adjusted total
-aoi_percentages <- df_fixations %>%
-  rowwise() %>%
-  mutate(
-    AOI_Students_pct = sum(c_across(any_of(
-      aoi_columns$AOI_Students
-    )), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100,
-    AOI_Disruptive_Person_pct = sum(c_across(
-      any_of(aoi_columns$AOI_Disruptive_Person)
-    ), na.rm = TRUE) / (
-      Total_fixations_excluding_disruptive + sum(c_across(
-        any_of(aoi_columns$AOI_Disruptive_Person)
-      ), na.rm = TRUE)
-    ) * 100,
-    AOI_Teacher_Material_pct = sum(c_across(
-      any_of(aoi_columns$AOI_Teacher_Material)
-    ), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100,
-    AOI_Student_Desk_pct = sum(c_across(any_of(
-      aoi_columns$AOI_Student_Desk
-    )), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100,
-    AOI_Classroom_Others_pct = sum(c_across(
-      any_of(aoi_columns$AOI_Classroom_Others)
-    ), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100
-  ) %>%
-  ungroup()
-
-# Step 5: Summarize fixation percentages by Group and arrange in descending order
-grouped_aoi_percentages <- aoi_percentages %>%
-  group_by(Group) %>%
-  summarise(
-    Mean_AOI_Students_pct = round(mean(AOI_Students_pct, na.rm = TRUE), 2),
-    Mean_AOI_Disruptive_Person_pct = round(mean(AOI_Disruptive_Person_pct, na.rm = TRUE), 2),
-    Mean_AOI_Teacher_Material_pct = round(mean(AOI_Teacher_Material_pct, na.rm = TRUE), 2),
-    Mean_AOI_Student_Desk_pct = round(mean(AOI_Student_Desk_pct, na.rm = TRUE), 2),
-    Mean_AOI_Classroom_Others_pct = round(mean(AOI_Classroom_Others_pct, na.rm = TRUE), 2)
-  ) %>%
-  pivot_longer(cols = starts_with("Mean_AOI"), names_to = "AOI", values_to = "Fixation_Percentage") %>%
-  mutate(AOI = recode(AOI,
-                      "Mean_AOI_Students_pct" = "Students",
-                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Person",
-                      "Mean_AOI_Teacher_Material_pct" = "Teacher Material",
-                      "Mean_AOI_Student_Desk_pct" = "Student Desk",
-                      "Mean_AOI_Classroom_Others_pct" = "Classroom/Others")) %>%
-  arrange(Group, desc(Fixation_Percentage))
-
-# Step 6: Restructure data for grouping and calculate 95% CI
-grouped_aoi_percentages_ci <- aoi_percentages %>%
-  pivot_longer(
-    cols = starts_with("AOI"),
-    names_to = "AOI",
-    values_to = "Percentage"
-  ) %>%
-  mutate(AOI = recode(
-    AOI,
-    "AOI_Students_pct" = "Students",
-    "AOI_Disruptive_Person_pct" = "Disruptive Person",
-    "AOI_Teacher_Material_pct" = "Teacher Material",
-    "AOI_Student_Desk_pct" = "Student Desk",
-    "AOI_Classroom_Others_pct" = "Classroom/Others"
-  )) %>%
-  group_by(Group, AOI) %>%
-  summarise(
-    Mean_Percentage = mean(Percentage, na.rm = TRUE),
-    CI_Lower = Mean_Percentage - qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
-    CI_Upper = Mean_Percentage + qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
-    .groups = "drop"
-  )
-
-# Step 7: Plot with 95% confidence intervals
-percentage_number_fixation <- ggplot(
-  grouped_aoi_percentages_ci %>% 
-    mutate(Group = recode(Group, 
-                          "Expert" = "Experienced", 
-                          "Novice" = "Inexperienced")),  # Rename groups
-  aes(
-    x = reorder(AOI, -Mean_Percentage),
-    y = Mean_Percentage,
-    fill = Group
-  )
-) +
-  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
-  geom_errorbar(
-    aes(ymin = CI_Lower, ymax = CI_Upper),
-    position = position_dodge(width = 0.8),
-    width = 0.2
-  ) +
-  geom_text(
-    aes(label = paste0(round(Mean_Percentage, 2), "%")),
-    position = position_dodge(width = 0.8),
-    vjust = -2.5,  # Adjusted to place the labels above the bars
-    size = 3
-  ) +
-  labs(title = "Average Fixation Number Percentage by AOI and Group", 
-       x = "AOI", 
-       y = "Fixation Percentage (%)") +
-  scale_fill_brewer(palette = "RdBu") +
-  theme_cowplot() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  ) +
-  guides(fill = guide_legend(title = "Group"))
-
-percentage_number_fixation
-
-# Save the updated plot
-ggsave(filename = "plots/percentage_number_fixation_with_ci.svg",
-       width = 20,
-       height = 12,
-       units = "cm")
-
-# Step 8: Perform a t-test between Experts and Novices on the percentage values and calculate Cohen's d
-# Define the AOIs you want to analyze with names matching those generated in Step 4
-aoi_list <- c("AOI_Students_pct", "AOI_Disruptive_Person_pct", "AOI_Teacher_Material_pct", "AOI_Student_Desk_pct", "AOI_Classroom_Others_pct")
-
-# Initialize an empty data frame to store the results
-results_number <- data.frame()
-
-# Loop over each AOI and calculate t-test and Cohen's d
-for (column_name in aoi_list) {
-
-  # Ensure that the column exists in the data
-  if (column_name %in% names(aoi_percentages)) {
-
-    # Filter the data for the current AOI and rename the column to Fixation_Percentage for consistency
-    aoi_data <- aoi_percentages %>%
-      select(Group, !!sym(column_name)) %>%
-      rename(Fixation_Percentage = !!sym(column_name))
-
-    # Separate data for each group
-    expert_data <- aoi_data$Fixation_Percentage[aoi_data$Group == "Expert"]
-    novice_data <- aoi_data$Fixation_Percentage[aoi_data$Group == "Novice"]
-
-    # Check if both groups have at least one observation
-    if (length(expert_data) > 0 && length(novice_data) > 0) {
-
-      # Perform a t-test between Experts and Novices on the current AOI's fixation percentage
-      t_test_result <- t.test(expert_data, novice_data, var.equal = TRUE)
-
-      # Calculate Cohen's d for the current AOI
-      cohen_d_value <- cohen.d(expert_data, novice_data, pooled = TRUE)$estimate
-
-      # Format the results_number for the current AOI and add to the results_number data frame
-      results_number <- rbind(
-        results_number,
-        data.frame(
-          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
-          "Group Comparison" = "Experts vs. Novices",
-          "t-value" = round(t_test_result$statistic, 2),
-          "df" = t_test_result$parameter,
-          "p-value" = format.pval(t_test_result$p.value, digits = 2, eps = .05),
-          "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
-          "Cohen's d" = round(cohen_d_value, 2),
-          "95% CI (d)" = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
-        )
-      )
-
-    } else {
-      # If one group has no data, append N/A values for this AOI
-      results_number <- rbind(
-        results_number,
-        data.frame(
-          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
-          "Group Comparison" = "Experienced vs. Inexperienced",
-          "t-value" = NA,
-          "df" = NA,
-          "p-value" = NA,
-          "Mean Difference" = NA,
-          "Cohen's d" = NA,
-          "95% CI (d)" = NA
-        )
-      )
-    }
-  }
-}
-
-# Clean up AOI names for readability in the final table
-aoi_name_mapping <- c(
-  "AOI_Students" = "Students",
-  "AOI_Disruptive_Person" = "Disruptive Person",
-  "AOI_Teacher_Material" = "Teacher Material",
-  "AOI_Student_Desk" = "Student Desk",
-  "AOI_Classroom_Others" = "Classroom/Others"
-)
-results_number$AOI <- aoi_name_mapping[results_number$AOI]
-
-# Display the combined results_number table in APA style without row names
-knitr::kable(results_number, caption = "t-Test and Effect Size for Fixation Percentage across AOIs (Experts vs. Novices)", row.names = FALSE) %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
 #### Percentage of fixation durations on each AOI, relative to the total duration of fixations during the entire "Lesson" 
@@
 
-# Step 3: Calculate total fixation duration per participant, excluding "Disruptive Person"
+# Step 3: Calculate total fixation duration per participant, excluding "Disruptive Student"
 relevant_columns <- unlist(aoi_columns[c("AOI_Students", "AOI_Teacher_Material", "AOI_Student_Desk", "AOI_Classroom_Others")])
@@
                       "Mean_AOI_Students_pct" = "Students",
-                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Person",
+                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Student",
                       "Mean_AOI_Teacher_Material_pct" = "Teacher Material",
@@
     "AOI_Students_pct" = "Students",
-    "AOI_Disruptive_Person_pct" = "Disruptive Person",
+    "AOI_Disruptive_Person_pct" = "Disruptive Student",
     "AOI_Teacher_Material_pct" = "Teacher Material",
@@
                       "AOI_Students" = "Students",
-                      "AOI_Disruptive_Person" = "Disruptive Person",
+                      "AOI_Disruptive_Person" = "Disruptive Student",
                       "AOI_Teacher_Material" = "Teacher Material",
@@
 
-```
-
-#### Number of fixations per minute and fixation duration in ms (micro-teaching unit)
-```{r nof_dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-##################### NUMBER OF FIXATIONS PER MINUTE ########################
-
-##################### Data Preparation ########################
-df_aoi_sum <- df_aoi %>%
+#### Percentage of fixations on each AOI, relative to the total number of fixations during the entire "Lesson" 
+# Step 1: Define AOI categories
+aoi_columns <- list(
+  "AOI_Students" = c(
+    "Number_of_fixations.Anna",
+    "Number_of_fixations.Bianca",
+    "Number_of_fixations.Carl(a)"
+  ),
+  "AOI_Disruptive_Person" = c("Number_of_fixations.Disruptive_Person"),
+  "AOI_Teacher_Material" = c(
+    "Number_of_fixations.Board_Screen",
+    "Number_of_fixations.Material_Teacher"
+  ),
+  "AOI_Student_Desk" = c(
+    "Number_of_fixations.Nametag_Anna",
+    "Number_of_fixations.Nametag_Bianca",
+    "Number_of_fixations.Nametag_Carl(a)",
+    "Number_of_fixations.Material_Students"
+  ),
+  "AOI_Classroom_Others" = c("Number_of_fixations.Classroom_Others")
+)
+
+# Step 2: Filter data for "Lesson" and select relevant columns
+df_fixations <- df_aoi %>%
   filter(TOI == "Lesson") %>%
-  dplyr::select(
-    Group,
-    Participant,
-    Duration_of_interval,
-    starts_with("Total_duration_of_fixations"),
-    starts_with("Number_of_fixations"),
-    starts_with("Average_duration"),
-    -contains("Disruptive_Person")
-  ) %>%
+  dplyr::select(Participant, Group, starts_with("Number_of_fixations"))
+
+# Step 3: Calculate total fixations per participant, excluding "Disruptive Student"
+# Extract relevant column names excluding "Disruptive Student"
+relevant_columns <- unlist(aoi_columns[c("AOI_Students", "AOI_Teacher_Material", "AOI_Student_Desk", "AOI_Classroom_Others")])
+
+# Calculate row sums for the relevant columns and add as a new column
+df_fixations <- df_fixations %>%
+  mutate(Total_fixations_excluding_disruptive = rowSums(across(all_of(relevant_columns)), na.rm = TRUE))
+
+# Step 4: Calculate fixation percentages for each AOI based on the adjusted total
+aoi_percentages <- df_fixations %>%
   rowwise() %>%
-  transmute(
-    Group = factor(Group, levels = c("Expert", "Novice"), labels = c("Experienced", "Inexperienced")),
-    Participant,
-    Duration_of_interval_min = Duration_of_interval / 60000,
-    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
-    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
-    Number_fixation_min_mtu = Sum_number_fixation / Duration_of_interval_min,
-    Avg_fixation_duration = Sum_duration_fixation / Sum_number_fixation
-  ) %>%
-  drop_na()
-
-##################### Number of Fixations per Minute ########################
-
-# Descriptive Statistics for Number of Fixations per Minute
-nof_stats <- df_aoi_sum %>%
+  mutate(
+    AOI_Students_pct = sum(c_across(any_of(
+      aoi_columns$AOI_Students
+    )), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100,
+    AOI_Disruptive_Person_pct = sum(c_across(
+      any_of(aoi_columns$AOI_Disruptive_Person)
+    ), na.rm = TRUE) / (
+      Total_fixations_excluding_disruptive + sum(c_across(
+        any_of(aoi_columns$AOI_Disruptive_Person)
+      ), na.rm = TRUE)
+    ) * 100,
+    AOI_Teacher_Material_pct = sum(c_across(
+      any_of(aoi_columns$AOI_Teacher_Material)
+    ), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100,
+    AOI_Student_Desk_pct = sum(c_across(any_of(
+      aoi_columns$AOI_Student_Desk
+    )), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100,
+    AOI_Classroom_Others_pct = sum(c_across(
+      any_of(aoi_columns$AOI_Classroom_Others)
+    ), na.rm = TRUE) / Total_fixations_excluding_disruptive * 100
+  ) %>%
+  ungroup()
+
+# Step 5: Summarize fixation percentages by Group and arrange in descending order
+grouped_aoi_percentages <- aoi_percentages %>%
   group_by(Group) %>%
   summarise(
-    N = n(),
-    M = round(mean(Number_fixation_min_mtu, na.rm = TRUE), 2),
-    SD = round(sd(Number_fixation_min_mtu, na.rm = TRUE), 2),
-    Min = round(min(Number_fixation_min_mtu, na.rm = TRUE), 2),
-    Max = round(max(Number_fixation_min_mtu, na.rm = TRUE), 2)
-  )
-
-# Display Table
-knitr::kable(nof_stats, caption = "N, M, SD, Min & Max for Number of Fixations per Minute") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# t-Test and Cohen's d
-t_test_mtu <- t.test(Number_fixation_min_mtu ~ Group, data = df_aoi_sum, var.equal = TRUE)
-cohen_d_mtu <- cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)
-
-# APA Table
-t_test_result_mtu <- data.frame(
-  "Group Comparison" = "Experienced vs. Inexperienced",
-  "t-value" = round(t_test_mtu$statistic, 2),
-  "df" = t_test_mtu$parameter,
-  "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
-  "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
-  "Cohen's d" = round(cohen_d_mtu$estimate, 2),
-  "95% CI (d)" = paste0("[", round(cohen_d_mtu$conf.int[1], 2), ", ", round(cohen_d_mtu$conf.int[2], 2), "]")
-)
-
-knitr::kable(t_test_result_mtu, caption = "t-Test and Effect Size for Number of Fixations per Minute") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Ensure cohen_d_mtu is numeric
-cohen_d_mtu <- round(as.numeric(cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)$estimate), 2)
-
-# Plot: Number of Fixations per Minute
-y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5
-
-plot_number_fixation_group <- df_aoi_sum %>%
-  ggplot(aes(x = Group, y = Number_fixation_min_mtu, fill = Group)) +
-  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
-  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
-  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
+    Mean_AOI_Students_pct = round(mean(AOI_Students_pct, na.rm = TRUE), 2),
+    Mean_AOI_Disruptive_Person_pct = round(mean(AOI_Disruptive_Person_pct, na.rm = TRUE), 2),
+    Mean_AOI_Teacher_Material_pct = round(mean(AOI_Teacher_Material_pct, na.rm = TRUE), 2),
+    Mean_AOI_Student_Desk_pct = round(mean(AOI_Student_Desk_pct, na.rm = TRUE), 2),
+    Mean_AOI_Classroom_Others_pct = round(mean(AOI_Classroom_Others_pct, na.rm = TRUE), 2)
+  ) %>%
+  pivot_longer(cols = starts_with("Mean_AOI"), names_to = "AOI", values_to = "Fixation_Percentage") %>%
+  mutate(AOI = recode(AOI,
+                      "Mean_AOI_Students_pct" = "Students",
+                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Student",
+                      "Mean_AOI_Teacher_Material_pct" = "Teacher Material",
+                      "Mean_AOI_Student_Desk_pct" = "Student Desk",
+                      "Mean_AOI_Classroom_Others_pct" = "Classroom/Others")) %>%
+  arrange(Group, desc(Fixation_Percentage))
+
+# Step 6: Restructure data for grouping and calculate 95% CI
+grouped_aoi_percentages_ci <- aoi_percentages %>%
+  pivot_longer(
+    cols = starts_with("AOI"),
+    names_to = "AOI",
+    values_to = "Percentage"
+  ) %>%
+  mutate(AOI = recode(
+    AOI,
+    "AOI_Students_pct" = "Students",
+    "AOI_Disruptive_Person_pct" = "Disruptive Student",
+    "AOI_Teacher_Material_pct" = "Teacher Material",
+    "AOI_Student_Desk_pct" = "Student Desk",
+    "AOI_Classroom_Others_pct" = "Classroom/Others"
+  )) %>%
+  group_by(Group, AOI) %>%
+  summarise(
+    Mean_Percentage = mean(Percentage, na.rm = TRUE),
+    CI_Lower = Mean_Percentage - qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
+    CI_Upper = Mean_Percentage + qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
+    .groups = "drop"
+  )
+
+# Step 7: Plot with 95% confidence intervals
+percentage_number_fixation <- ggplot(
+  grouped_aoi_percentages_ci %>% 
+    mutate(Group = recode(Group, 
+                          "Expert" = "Experienced", 
+                          "Novice" = "Inexperienced")),  # Rename groups
+  aes(
+    x = reorder(AOI, -Mean_Percentage),
+    y = Mean_Percentage,
+    fill = Group
+  )
+) +
+  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
+  geom_errorbar(
+    aes(ymin = CI_Lower, ymax = CI_Upper),
+    position = position_dodge(width = 0.8),
+    width = 0.2
+  ) +
+  geom_text(
+    aes(label = paste0(round(Mean_Percentage, 2), "%")),
+    position = position_dodge(width = 0.8),
+    vjust = -2.5,  # Adjusted to place the labels above the bars
+    size = 3
+  ) +
+  labs(title = "Average Fixation Number Percentage by AOI and Group", 
+       x = "AOI", 
+       y = "Fixation Percentage (%)") +
   scale_fill_brewer(palette = "RdBu") +
-  ylim(0, y_max_mtu) +
-  labs(title = "Number of Fixations per Minute\n(Micro-Teaching Unit)", x = "", y = "Fixations per Minute") +
   theme_cowplot() +
-  theme(legend.position = "none") +
-  annotate("text", x = 1, y = 3,
-           label = paste0("italic(M) == ", round(nof_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[1], 2)),
-           hjust = 0.5, size = 4, parse = TRUE) +
-  annotate("text", x = 2, y = 3,
-           label = paste0("italic(M) == ", round(nof_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[2], 2)),
-           hjust = 0.5, size = 4, parse = TRUE) +
-  annotate("text", x = 1.5, y = y_max_mtu * 0.95,
-           label = paste0("italic(p) == ", round(t_test_mtu$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_mtu),
-           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
-
-plot_number_fixation_group
-
-ggsave(filename = "plots/plot_number_fixation_group.svg",
+  theme(
+    plot.title = element_text(hjust = 0.5, face = "bold"),
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  guides(fill = guide_legend(title = "Group"))
+
+percentage_number_fixation
+
+# Save the updated plot
+ggsave(filename = "plots/percentage_number_fixation_with_ci.svg",
        width = 20,
@@
 
-##################### Average Fixation Duration ########################
-
-# Descriptive Statistics for Average Fixation Duration
-fixation_stats <- df_aoi_sum %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    M = round(mean(Avg_fixation_duration, na.rm = TRUE), 2),
-    SD = round(sd(Avg_fixation_duration, na.rm = TRUE), 2),
-    Min = round(min(Avg_fixation_duration, na.rm = TRUE), 2),
-    Max = round(max(Avg_fixation_duration, na.rm = TRUE), 2)
-  )
-
-# Display Table
-knitr::kable(fixation_stats, caption = "N, M, SD, Min & Max for Average Fixation Duration") %>%
+# Step 8: Perform a t-test between Experts and Novices on the percentage values and calculate Cohen's d
+# Define the AOIs you want to analyze with names matching those generated in Step 4
+aoi_list <- c("AOI_Students_pct", "AOI_Disruptive_Person_pct", "AOI_Teacher_Material_pct", "AOI_Student_Desk_pct", "AOI_Classroom_Others_pct")
+
+# Initialize an empty data frame to store the results
+results_number <- data.frame()
+
+# Loop over each AOI and calculate t-test and Cohen's d
+for (column_name in aoi_list) {
+
+  # Ensure that the column exists in the data
+  if (column_name %in% names(aoi_percentages)) {
+
+    # Filter the data for the current AOI and rename the column to Fixation_Percentage for consistency
+    aoi_data <- aoi_percentages %>%
+      select(Group, !!sym(column_name)) %>%
+      rename(Fixation_Percentage = !!sym(column_name))
+
+    # Separate data for each group
+    expert_data <- aoi_data$Fixation_Percentage[aoi_data$Group == "Expert"]
+    novice_data <- aoi_data$Fixation_Percentage[aoi_data$Group == "Novice"]
+
+    # Check if both groups have at least one observation
+    if (length(expert_data) > 0 && length(novice_data) > 0) {
+
+      # Perform a t-test between Experts and Novices on the current AOI's fixation percentage
+      t_test_result <- t.test(expert_data, novice_data, var.equal = TRUE)
+
+      # Calculate Cohen's d for the current AOI
+      cohen_d_value <- cohen.d(expert_data, novice_data, pooled = TRUE)$estimate
+
+      # Format the results_number for the current AOI and add to the results_number data frame
+      results_number <- rbind(
+        results_number,
+        data.frame(
+          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
+          "Group Comparison" = "Experts vs. Novices",
+          "t-value" = round(t_test_result$statistic, 2),
+          "df" = t_test_result$parameter,
+          "p-value" = format.pval(t_test_result$p.value, digits = 2, eps = .05),
+          "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
+          "Cohen's d" = round(cohen_d_value, 2),
+          "95% CI (d)" = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
+        )
+      )
+
+    } else {
+      # If one group has no data, append N/A values for this AOI
+      results_number <- rbind(
+        results_number,
+        data.frame(
+          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
+          "Group Comparison" = "Experienced vs. Inexperienced",
+          "t-value" = NA,
+          "df" = NA,
+          "p-value" = NA,
+          "Mean Difference" = NA,
+          "Cohen's d" = NA,
+          "95% CI (d)" = NA
+        )
+      )
+    }
+  }
+}
+
+# Clean up AOI names for readability in the final table
+aoi_name_mapping <- c(
+  "AOI_Students" = "Students",
+  "AOI_Disruptive_Person" = "Disruptive Student",
+  "AOI_Teacher_Material" = "Teacher Material",
+  "AOI_Student_Desk" = "Student Desk",
+  "AOI_Classroom_Others" = "Classroom/Others"
+)
+results_number$AOI <- aoi_name_mapping[results_number$AOI]
+
+# Display the combined results_number table in APA style without row names
+knitr::kable(results_number, caption = "t-Test and Effect Size for Fixation Percentage across AOIs (Experts vs. Novices)", row.names = FALSE) %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
-# t-Test and Cohen's d
-t_test_fixation <- t.test(Avg_fixation_duration ~ Group, data = df_aoi_sum, var.equal = TRUE)
-cohen_d_fixation <- cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)
-
-# APA Table
-t_test_result_fixation <- data.frame(
-  "Group Comparison" = "Experienced vs. Inexperienced",
-  "t-value" = round(t_test_fixation$statistic, 2),
-  "df" = t_test_fixation$parameter,
-  "p-value" = format.pval(t_test_fixation$p.value, digits = 2, eps = .05),
-  "Mean Difference" = round(t_test_fixation$estimate[1] - t_test_fixation$estimate[2], 2),
-  "Cohen's d" = round(cohen_d_fixation$estimate, 2),
-  "95% CI (d)" = paste0("[", round(cohen_d_fixation$conf.int[1], 2), ", ", round(cohen_d_fixation$conf.int[2], 2), "]")
-)
-
-knitr::kable(t_test_result_fixation, caption = "t-Test and Effect Size for Average Fixation Duration") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Ensure cohen_d_fixation is numeric
-cohen_d_fixation <- round(cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)$estimate, 2)
-
-# Plot: Average Fixation Duration
-plot_avg_fixation_group <- df_aoi_sum %>%
-  ggplot(aes(x = Group, y = Avg_fixation_duration, fill = Group)) +
-  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
-  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
-  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
-  scale_fill_brewer(palette = "RdBu") +
-  labs(title = "Average Fixation Duration\n(Micro-Teaching Unit)", x = "", y = "Fixation Duration (ms)") +
-  theme_cowplot() +
-  theme(legend.position = "none") +
-  # Add M and SD values below the x-axis for each group
-  annotate("text", x = 1, y = -50,  # Adjust y-coordinate to place below the x-axis
-           label = paste0("italic(M) == ", round(fixation_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[1], 2)),
-           hjust = 0.5, size = 4, parse = TRUE) +
-  annotate("text", x = 2, y = -50,  # Adjust y-coordinate to place below the x-axis
-           label = paste0("italic(M) == ", round(fixation_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[2], 2)),
-           hjust = 0.5, size = 4, parse = TRUE) +
-  # Add p-value and d-value above the plot
-  annotate("text", x = 1.5, y = max(df_aoi_sum$Avg_fixation_duration) * 1.1,
-           label = paste0("italic(p) == ", round(t_test_fixation$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_fixation),
-           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
-
-plot_avg_fixation_group
-
-ggsave(filename = "plots/plot_avg_fixation_group.svg",
-       width = 20,
-       height = 12,
-       units = "cm")
-
-# Load the patchwork library
-install.packages("patchwork")
-library(patchwork)
-
-# Combine the two plots side by side
-combined_plot <- plot_number_fixation_group + plot_avg_fixation_group +
-  plot_layout(ncol = 2, guides = "collect") &
-  theme(legend.position = "none")
-
-# Display the combined plot
-combined_plot
-
-# Save the combined plot
-ggsave(
-  filename = "plots/combined_results_plot.svg",
-  plot = combined_plot,
-  width = 25,
-  height = 12,
-  units = "cm"
-)
+```
+
+#### Number of fixations per minute and fixation duration in ms (micro-teaching unit)
+```{r nof_dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+# ##################### NUMBER OF FIXATIONS PER MINUTE ########################
+# 
+# ##################### Data Preparation ########################
+# df_aoi_sum <- df_aoi %>%
+#   filter(TOI == "Lesson") %>%
+#   dplyr::select(
+#     Group,
+#     Participant,
+#     Duration_of_interval,
+#     starts_with("Total_duration_of_fixations"),
+#     starts_with("Number_of_fixations"),
+#     starts_with("Average_duration"),
+#     -contains("Disruptive_Person")
+#   ) %>%
+#   rowwise() %>%
+#   transmute(
+#     Group = factor(Group, levels = c("Expert", "Novice"), labels = c("Experienced", "Inexperienced")),
+#     Participant,
+#     Duration_of_interval_min = Duration_of_interval / 60000,
+#     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+#     Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+#     Number_fixation_min_mtu = Sum_number_fixation / Duration_of_interval_min,
+#     Avg_fixation_duration = Sum_duration_fixation / Sum_number_fixation
+#   ) %>%
+#   drop_na()
+# 
+# ##################### Number of Fixations per Minute ########################
+# 
+# # Descriptive Statistics for Number of Fixations per Minute
+# nof_stats <- df_aoi_sum %>%
+#   group_by(Group) %>%
+#   summarise(
+#     N = n(),
+#     M = round(mean(Number_fixation_min_mtu, na.rm = TRUE), 2),
+#     SD = round(sd(Number_fixation_min_mtu, na.rm = TRUE), 2),
+#     Min = round(min(Number_fixation_min_mtu, na.rm = TRUE), 2),
+#     Max = round(max(Number_fixation_min_mtu, na.rm = TRUE), 2)
+#   )
+# 
+# 
+# # Display Table
+# knitr::kable(nof_stats, caption = "N, M, SD, Min & Max for Number of Fixations per Minute") %>%
+#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# # t-Test and Cohen's d
+# t_test_mtu <- t.test(Number_fixation_min_mtu ~ Group, data = df_aoi_sum, var.equal = TRUE)
+# cohen_d_mtu <- cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)
+# 
+# # APA Table
+# t_test_result_mtu <- data.frame(
+#   "Group Comparison" = "Experienced vs. Inexperienced",
+#   "t-value" = round(t_test_mtu$statistic, 2),
+#   "df" = t_test_mtu$parameter,
+#   "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
+#   "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
+#   "Cohen's d" = round(cohen_d_mtu$estimate, 2),
+#   "95% CI (d)" = paste0("[", round(cohen_d_mtu$conf.int[1], 2), ", ", round(cohen_d_mtu$conf.int[2], 2), "]")
+# )
+# 
+# knitr::kable(t_test_result_mtu, caption = "t-Test and Effect Size for Number of Fixations per Minute") %>%
+#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# # Ensure cohen_d_mtu is numeric
+# cohen_d_mtu <- round(as.numeric(cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)$estimate), 2)
+# 
+# # Plot: Number of Fixations per Minute
+# y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5
+# 
+# plot_number_fixation_group <- df_aoi_sum %>%
+#   ggplot(aes(x = Group, y = Number_fixation_min_mtu, fill = Group)) +
+#   geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
+#   geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
+#   stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
+#   scale_fill_brewer(palette = "RdBu") +
+#   ylim(0, y_max_mtu) +
+#   labs(title = "Number of Fixations per Minute\n(Micro-Teaching Unit)", x = "", y = "Fixations per Minute") +
+#   theme_cowplot() +
+#   theme(legend.position = "none") +
+#   annotate("text", x = 1, y = 3,
+#            label = paste0("italic(M) == ", round(nof_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[1], 2)),
+#            hjust = 0.5, size = 4, parse = TRUE) +
+#   annotate("text", x = 2, y = 3,
+#            label = paste0("italic(M) == ", round(nof_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[2], 2)),
+#            hjust = 0.5, size = 4, parse = TRUE) +
+#   annotate("text", x = 1.5, y = y_max_mtu * 0.95,
+#            label = paste0("italic(p) == ", round(t_test_mtu$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_mtu),
+#            hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
+# 
+# plot_number_fixation_group
+# 
+# ggsave(filename = "plots/plot_number_fixation_group.svg",
+#        width = 20,
+#        height = 12,
+#        units = "cm")
+# 
+# ##################### Average Fixation Duration ########################
+# 
+# # Descriptive Statistics for Average Fixation Duration
+# fixation_stats <- df_aoi_sum %>%
+#   group_by(Group) %>%
+#   summarise(
+#     N = n(),
+#     M = round(mean(Avg_fixation_duration, na.rm = TRUE), 2),
+#     SD = round(sd(Avg_fixation_duration, na.rm = TRUE), 2),
+#     Min = round(min(Avg_fixation_duration, na.rm = TRUE), 2),
+#     Max = round(max(Avg_fixation_duration, na.rm = TRUE), 2)
+#   )
+# 
+# # Display Table
+# knitr::kable(fixation_stats, caption = "N, M, SD, Min & Max for Average Fixation Duration") %>%
+#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# # t-Test and Cohen's d
+# t_test_fixation <- t.test(Avg_fixation_duration ~ Group, data = df_aoi_sum, var.equal = TRUE)
+# cohen_d_fixation <- cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)
+# 
+# # APA Table
+# t_test_result_fixation <- data.frame(
+#   "Group Comparison" = "Experienced vs. Inexperienced",
+#   "t-value" = round(t_test_fixation$statistic, 2),
+#   "df" = t_test_fixation$parameter,
+#   "p-value" = format.pval(t_test_fixation$p.value, digits = 2, eps = .05),
+#   "Mean Difference" = round(t_test_fixation$estimate[1] - t_test_fixation$estimate[2], 2),
+#   "Cohen's d" = round(cohen_d_fixation$estimate, 2),
+#   "95% CI (d)" = paste0("[", round(cohen_d_fixation$conf.int[1], 2), ", ", round(cohen_d_fixation$conf.int[2], 2), "]")
+# )
+# 
+# knitr::kable(t_test_result_fixation, caption = "t-Test and Effect Size for Average Fixation Duration") %>%
+#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# # Ensure cohen_d_fixation is numeric
+# cohen_d_fixation <- round(cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)$estimate, 2)
+# 
+# # Plot: Average Fixation Duration
+# plot_avg_fixation_group <- df_aoi_sum %>%
+#   ggplot(aes(x = Group, y = Avg_fixation_duration, fill = Group)) +
+#   geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
+#   geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
+#   stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
+#   scale_fill_brewer(palette = "RdBu") +
+#   labs(title = "Average Fixation Duration\n(Micro-Teaching Unit)", x = "", y = "Fixation Duration (ms)") +
+#   theme_cowplot() +
+#   theme(legend.position = "none") +
+#   # Add M and SD values below the x-axis for each group
+#   annotate("text", x = 1, y = -50,  # Adjust y-coordinate to place below the x-axis
+#            label = paste0("italic(M) == ", round(fixation_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[1], 2)),
+#            hjust = 0.5, size = 4, parse = TRUE) +
+#   annotate("text", x = 2, y = -50,  # Adjust y-coordinate to place below the x-axis
+#            label = paste0("italic(M) == ", round(fixation_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[2], 2)),
+#            hjust = 0.5, size = 4, parse = TRUE) +
+#   # Add p-value and d-value above the plot
+#   annotate("text", x = 1.5, y = max(df_aoi_sum$Avg_fixation_duration) * 1.1,
+#            label = paste0("italic(p) == ", round(t_test_fixation$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_fixation),
+#            hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
+# 
+# plot_avg_fixation_group
+# 
+# ggsave(filename = "plots/plot_avg_fixation_group.svg",
+#        width = 20,
+#        height = 12,
+#        units = "cm")
+# 
+# # Load the patchwork library
+# install.packages("patchwork")
+# library(patchwork)
+# 
+# # Combine the two plots side by side
+# combined_plot <- plot_number_fixation_group + plot_avg_fixation_group +
+#   plot_layout(ncol = 2, guides = "collect") &
+#   theme(legend.position = "none")
+# 
+# # Display the combined plot
+# combined_plot
+# 
+# # Save the combined plot
+# ggsave(
+#   filename = "plots/combined_results_plot.svg",
+#   plot = combined_plot,
+#   width = 25,
+#   height = 12,
+#   units = "cm"
+# )
 
@@
 
-##################### Average Fixation Duration ########################
-
-# Descriptive Statistics for Average Fixation Duration
-fixation_stats_stud <- df_aoi_stud %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    M = round(mean(Avg_fixation_duration_stud, na.rm = TRUE), 2),
-    SD = round(sd(Avg_fixation_duration_stud, na.rm = TRUE), 2),
-    Min = round(min(Avg_fixation_duration_stud, na.rm = TRUE), 2),
-    Max = round(max(Avg_fixation_duration_stud, na.rm = TRUE), 2)
-  )
-
-# Display Table
-knitr::kable(fixation_stats_stud, caption = "N, M, SD, Min & Max for Average Fixation Duration (AOI Students)") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# t-Test and Cohen's d
-t_test_fixation_stud <- t.test(Avg_fixation_duration_stud ~ Group, data = df_aoi_stud, var.equal = TRUE)
-cohen_d_fixation_stud <- cohen.d(Avg_fixation_duration_stud ~ Group, data = df_aoi_stud)
-
-# APA Table
-t_test_result_fixation_stud <- data.frame(
-  "Group Comparison" = "Experienced vs. Inexperienced",
-  "t-value" = round(t_test_fixation_stud$statistic, 2),
-  "df" = t_test_fixation_stud$parameter,
-  "p-value" = format.pval(t_test_fixation_stud$p.value, digits = 2, eps = .05),
-  "Mean Difference" = round(t_test_fixation_stud$estimate[1] - t_test_fixation_stud$estimate[2], 2),
-  "Cohen's d" = round(cohen_d_fixation_stud$estimate, 2),
-  "95% CI (d)" = paste0("[", round(cohen_d_fixation_stud$conf.int[1], 2), ", ", round(cohen_d_fixation_stud$conf.int[2], 2), "]")
-)
-
-knitr::kable(t_test_result_fixation_stud, caption = "t-Test and Effect Size for Average Fixation Duration (AOI Students)") %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
-
-# Plot: Average Fixation Duration
-y_max_fixation_stud <- max(df_aoi_stud$Avg_fixation_duration_stud) * 1.5
-
-plot_fixation_duration_stud <- df_aoi_stud %>%
-  ggplot(aes(x = Group, y = Avg_fixation_duration_stud, fill = Group)) +
-  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
-  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
-  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
-  scale_fill_brewer(palette = "RdBu") +
-  ylim(0, y_max_fixation_stud) +
-  labs(title = "Average Fixation Duration\n(AOI Students)", x = "", y = "Fixation Duration (ms)") +
-  theme_cowplot() +
-  theme(legend.position = "none") +
-  annotate("text", x = 1, y = 10,  # Adjust y-coordinate to place above the x-axis
-           label = paste0("italic(M) == ", round(fixation_stats_stud$M[1], 2), " * ',' ~ italic(SD) == ", round(fixation_stats_stud$SD[1], 2)),
-           hjust = 0.5, size = 4, parse = TRUE) +
-  annotate("text", x = 2, y = 10,  # Adjust y-coordinate to place above the x-axis
-           label = paste0("italic(M) == ", round(fixation_stats_stud$M[2], 2), " * ',' ~ italic(SD) == ", round(fixation_stats_stud$SD[2], 2)),
-           hjust = 0.5, size = 4, parse = TRUE) +
-  annotate("text", x = 1.5, y = y_max_fixation_stud * 0.95,
-           label = paste0("italic(p) == ", round(t_test_fixation_stud$p.value, 2), " * ',' ~ italic(d) == ", round(cohen_d_fixation_stud$estimate, 2)),
-           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
-
-plot_fixation_duration_stud
-
-ggsave(filename = "plots/plot_fixation_duration_stud.svg",
-       width = 20,
-       height = 12,
-       units = "cm")
+# ##################### Average Fixation Duration ########################
+# # Descriptive Statistics for Average Fixation Duration
+# fixation_stats_stud <- df_aoi_stud %>%
+#   group_by(Group) %>%
+#   summarise(
+#     N = n(),
+#     M = round(mean(Avg_fixation_duration_stud, na.rm = TRUE), 2),
+#     SD = round(sd(Avg_fixation_duration_stud, na.rm = TRUE), 2),
+#     Min = round(min(Avg_fixation_duration_stud, na.rm = TRUE), 2),
+#     Max = round(max(Avg_fixation_duration_stud, na.rm = TRUE), 2)
+#   )
+# 
+# # Display Table
+# knitr::kable(fixation_stats_stud, caption = "N, M, SD, Min & Max for Average Fixation Duration (AOI Students)") %>%
+#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# # t-Test and Cohen's d
+# t_test_fixation_stud <- t.test(Avg_fixation_duration_stud ~ Group, data = df_aoi_stud, var.equal = TRUE)
+# cohen_d_fixation_stud <- cohen.d(Avg_fixation_duration_stud ~ Group, data = df_aoi_stud)
+# 
+# # APA Table
+# t_test_result_fixation_stud <- data.frame(
+#   "Group Comparison" = "Experienced vs. Inexperienced",
+#   "t-value" = round(t_test_fixation_stud$statistic, 2),
+#   "df" = t_test_fixation_stud$parameter,
+#   "p-value" = format.pval(t_test_fixation_stud$p.value, digits = 2, eps = .05),
+#   "Mean Difference" = round(t_test_fixation_stud$estimate[1] - t_test_fixation_stud$estimate[2], 2),
+#   "Cohen's d" = round(cohen_d_fixation_stud$estimate, 2),
+#   "95% CI (d)" = paste0("[", round(cohen_d_fixation_stud$conf.int[1], 2), ", ", round(cohen_d_fixation_stud$conf.int[2], 2), "]")
+# )
+# 
+# knitr::kable(t_test_result_fixation_stud, caption = "t-Test and Effect Size for Average Fixation Duration (AOI Students)") %>%
+#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+# 
+# # Plot: Average Fixation Duration
+# y_max_fixation_stud <- max(df_aoi_stud$Avg_fixation_duration_stud) * 1.5
+# 
+# plot_fixation_duration_stud <- df_aoi_stud %>%
+#   ggplot(aes(x = Group, y = Avg_fixation_duration_stud, fill = Group)) +
+#   geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
+#   geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
+#   stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
+#   scale_fill_brewer(palette = "RdBu") +
+#   ylim(0, y_max_fixation_stud) +
+#   labs(title = "Average Fixation Duration\n(AOI Students)", x = "", y = "Fixation Duration (ms)") +
+#   theme_cowplot() +
+#   theme(legend.position = "none") +
+#   annotate("text", x = 1, y = 10,  # Adjust y-coordinate to place above the x-axis
+#            label = paste0("italic(M) == ", round(fixation_stats_stud$M[1], 2), " * ',' ~ italic(SD) == ", round(fixation_stats_stud$SD[1], 2)),
+#            hjust = 0.5, size = 4, parse = TRUE) +
+#   annotate("text", x = 2, y = 10,  # Adjust y-coordinate to place above the x-axis
+#            label = paste0("italic(M) == ", round(fixation_stats_stud$M[2], 2), " * ',' ~ italic(SD) == ", round(fixation_stats_stud$SD[2], 2)),
+#            hjust = 0.5, size = 4, parse = TRUE) +
+#   annotate("text", x = 1.5, y = y_max_fixation_stud * 0.95,
+#            label = paste0("italic(p) == ", round(t_test_fixation_stud$p.value, 2), " * ',' ~ italic(d) == ", round(cohen_d_fixation_stud$estimate, 2)),
+#            hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
+# 
+# plot_fixation_duration_stud
+# 
+# ggsave(filename = "plots/plot_fixation_duration_stud.svg",
+#        width = 20,
+#        height = 12,
+#        units = "cm")
 
@@
 
-#### Number of fixations per seconds (AOI disruptive person)
+#### Number of fixations per seconds (AOI Disruptive Student)
 ```{r nof_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
-##################### NUMBER OF FIXATIONS ON AOI DISRUPTIVE PERSON ########################
+##################### NUMBER OF FIXATIONS ON AOI Disruptive Student ########################
 
@@
   overall_stats,
-  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Number of Fixations by Group (AOI Disruptive Person)",
+  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Number of Fixations by Group (AOI Disruptive Student)",
   col.names = c("Group", "N", "M", "SD", "Min", "Max"),
@@
   category_stats,
-  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Number of Fixations by Group and Category (AOI Disruptive Person)",
+  caption = "Descriptive Statistics (N, Mean, SD, Min, Max) for Number of Fixations by Group and Category (AOI Disruptive Student)",
   col.names = c("Group", "Category", "N", "M", "SD", "Min", "Max"),
@@
 
-##################### FIRST PLOT: Number of Fixations AOI Disruptive Person ########################
+##################### FIRST PLOT: Number of Fixations AOI Disruptive Student ########################
 
@@
   labs(x = "", y = "Number of Fixations per Second") +
-  ggtitle("Number of Fixations per Second \n(AOI Disruptive Person)") +
+  ggtitle("Number of Fixations per Second \n(AOI Disruptive Student)") +
   scale_fill_brewer(palette = "RdBu") +
@@
 
-##################### SECOND PLOT: NUMBER OF FIXATIONS BY CATEGORY (AOI DISRUPTIVE PERSON) ########################
+##################### SECOND PLOT: NUMBER OF FIXATIONS BY CATEGORY (AOI Disruptive Student) ########################
 
@@
   labs(x = "", y = "Number of Fixations per Second") +
-  ggtitle("Number of Fixations per Second Splitted by Disruption Category and Group\n(AOI Disruptive Person)") +
+  ggtitle("Number of Fixations per Second Splitted by Disruption Category and Group\n(AOI Disruptive Student)") +
   scale_fill_brewer(palette = "RdBu") +
@@
   overall_effect,
-  caption = "t-Test and Effect Size for Number of Fixations (AOI DIsruptive Person)",
+  caption = "t-Test and Effect Size for Number of Fixations (AOI Disruptive Student)",
   col.names = c("Group", "t-value", "p-value", "Cohen's d"),
@@
 
-##################### AVERAGE DURATION ON AOI DISRUPTIVE PERSON ########################
+##################### AVERAGE DURATION ON AOI Disruptive Student ########################
 ##################### DATA PREPARATION ########################
@@
   labs(x = "", y = "Average Fixation Duration (ms)") +
-  ggtitle("Average Fixation Duration\n(AOI Disruptive Person)") +
+  ggtitle("Average Fixation Duration\n(AOI Disruptive Student)") +
   scale_fill_brewer(palette = "RdBu") +
@@
   labs(x = "", y = "Average Fixation Duration (ms)") +
-  ggtitle("Average Duration of Fixations Splitted by Disruption Category and Group\n(AOI Disruptive Person)") +
+  ggtitle("Average Duration of Fixations Splitted by Disruption Category and Group\n(AOI Disruptive Student)") +
   scale_fill_brewer(palette = "RdBu") +
@@
 
-#### Time to first fixation in seconds (AOI disruptive person)
+#### Time to first fixation in seconds (AOI Disruptive Student)
 ```{r ttff_disrup, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 knitr::kable(ttff_disrup_table,
-             caption = "N, M, SD, Min & Max Time to First Fixation in Seconds (AOI Disruptive Person)") %>%
+             caption = "N, M, SD, Min & Max Time to First Fixation in Seconds (AOI Disruptive Student)") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
@@
 
-# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Person --------------------------------------------
+# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Student --------------------------------------------
 df_aoi_numb_dur <- df_aoi %>%
@@
   dplyr::select(
-    -contains("Disruptive_Person")  # Exclude Disruptive Person
+    -contains("Disruptive_Person")  # Exclude Disruptive Student
   ) %>%
@@
 
-# ET-Measures (AOI Students) - Exclude Disruptive Person --------------------------------------------
+# ET-Measures (AOI Students) - Exclude Disruptive Student --------------------------------------------
 df_aoi_stud <- df_aoi %>%
@@
 
-# ET-Measures (AOI Disruptive Person) --------------------------------------------
+# ET-Measures (AOI Disruptive Student) --------------------------------------------
 
@@
 
-# Time to first fixation on AOI Disruptive Person --------------------------------------------
+# Time to first fixation on AOI Disruptive Student --------------------------------------------
 # Step 1: Data Preparation

### 2025-01-29 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
x paper

@@
   mutate(
-    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2)
-  )
-
-# Summarize the Disrup_time_fixation_sec by Participant
+    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2),
+    log_Disrup_time_fixation_sec = round(log(Disrup_time_fixation_sec), 2) # Log-transformed variable
+  )
+
+# Summarize the log-transformed variable by Participant
 df_ttff_disrup_participant_summary <- df_ttff_disrup %>%
@@
   summarise(
-    Disrup_time_fixation_sec = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average time to first fixation per participant
+    log_Disrup_time_fixation_sec = round(mean(log_Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average log time to first fixation per participant
     .groups = "drop"
@@
 # Step 2: Descriptive Statistics by Group
-ttff_disrup_table <- df_ttff_disrup_participant_summary %>%
+log_ttff_disrup_table <- df_ttff_disrup_participant_summary %>%
   group_by(Group) %>%
@@
     N = n(),
-    "M in sec" = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    "SD in sec" = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    "Min in sec" = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    "Max in sec" = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2)
-  )
-
-knitr::kable(ttff_disrup_table,
-             caption = "N, M, SD, Min & Max Time to First Fixation in Seconds (AOI Disruptive Student)") %>%
+    "M (log-sec)" = round(mean(log_Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "SD (log-sec)" = round(sd(log_Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Min (log-sec)" = round(min(log_Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Max (log-sec)" = round(max(log_Disrup_time_fixation_sec, na.rm = TRUE), 2)
+  )
+
+knitr::kable(log_ttff_disrup_table,
+             caption = "N, M, SD, Min & Max Log-Transformed Time to First Fixation (AOI Disruptive Student)") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
@@
 # Step 3: Descriptive Statistics by Category and Group
-summary_stats_category_group <- df_ttff_disrup %>%
+summary_stats_log_category_group <- df_ttff_disrup %>%
   group_by(Disruption_Category, Group) %>%
@@
     N = n_distinct(Participant),  # Count unique participants
-    Mean = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    SD = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    Median = round(median(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    IQR = round(IQR(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    Min = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    Max = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2),
-    .groups = "drop"
+    "M (log-sec)" = round(mean(log_Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "SD (log-sec)" = round(sd(log_Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Min (log-sec)" = round(min(log_Disrup_time_fixation_sec, na.rm = TRUE), 2),
+    "Max (log-sec)" = round(max(log_Disrup_time_fixation_sec, na.rm = TRUE), 2)
   )
@@
 knitr::kable(
-  summary_stats_category_group,
-  caption = "Descriptive Statistics for Time to First Fixation by Category and Group",
-  col.names = c("Category", "Group", "N (Participants)", "Mean", "SD", "Median", "IQR", "Min", "Max"), # Ensure the column names match
+  summary_stats_log_category_group,
+  caption = "Descriptive Statistics for Log-Transformed Time to First Fixation by Category and Group",
+  col.names = c("Category", "Group", "N (Participants)", "Mean", "SD", "Min", "Max"), # Ensure the column names match
   row.names = FALSE
@@
 
-# Plot 1: Time to First Fixation by Group
-plot_ttff_group <- ggplot(df_ttff_disrup, aes(x = Group, y = Disrup_time_fixation_sec, fill = Group)) +
+# Plot 1: Log Time to First Fixation by Group
+plot_log_ttff_group <- ggplot(df_ttff_disrup_participant_summary, aes(x = Group, y = log_Disrup_time_fixation_sec, fill = Group)) +
   geom_boxplot(outlier.shape = NA, width = 0.5) +
   geom_jitter(width = 0.15, alpha = 0.5, color = "black", size = 1.5) +
-  labs(x = "Group", y = "Time to First Fixation (seconds)") +
+  labs(x = "Group", y = "Log Time to First Fixation (log-seconds)") +
   theme_cowplot() +
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Time to First Fixation by Group") +
-  theme(legend.position = "none") +
-  annotate("text", x = 1, y = max(df_ttff_disrup$Disrup_time_fixation_sec, na.rm = TRUE) * 1.1,
-           label = paste0("Median = ", round(median(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE), 2),
-                          "\nIQR = ", round(IQR(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Novice"], na.rm = TRUE), 2)),
-           hjust = 0.5, size = 4) +
-  annotate("text", x = 2, y = max(df_ttff_disrup$Disrup_time_fixation_sec, na.rm = TRUE) * 1.1,
-           label = paste0("Median = ", round(median(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE), 2),
-                          "\nIQR = ", round(IQR(df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Group == "Expert"], na.rm = TRUE), 2)),
-           hjust = 0.5, size = 4)
+  ggtitle("Log Time to First Fixation by Group") +
+  scale_y_continuous(limits = c(-3, 3), breaks = seq(-3, 3, 1)) + # Manuelle Achseneinteilung
+  theme(legend.position = "none")
 
 # Display the first plot
-plot_ttff_group
-
-# Plot 2: Time to First Fixation by Group and Disruption Category
-plot_ttff_category <- ggplot(df_ttff_disrup, aes(x = Group, y = Disrup_time_fixation_sec, fill = Group)) +
+plot_log_ttff_group
+
+# Plot 2: Log Time to First Fixation by Group and Disruption Category
+plot_log_ttff_category <- ggplot(df_ttff_disrup, aes(x = Group, y = log_Disrup_time_fixation_sec, fill = Group)) +
   geom_boxplot(outlier.shape = NA, width = 0.5) +
@@
   facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) +  # Use fixed scale for all facets  
-  ylim(0, 30) + 
-  labs(x = "Group", y = "Time to First Fixation (seconds)") +
+  labs(x = "Group", y = "Log Time to First Fixation (log-seconds)") +
   theme_cowplot() +
+  scale_y_continuous(limits = c(-5, 5), breaks = seq(-5, 5, 1)) + # Manuelle Achseneinteilung
   scale_fill_brewer(palette = "RdBu") +
-  ggtitle("Time to First Fixation by Group and Disruption Category") +
+  ggtitle("Log Time to First Fixation by Group and Disruption Category") +
   theme(legend.position = "none")
@@
 # Display the second plot
-plot_ttff_category
+plot_log_ttff_category
 
@@
 
-# Perform the repeated-measures ANOVA with `Disrup_time_fixation_sec` as the dependent variable
-anova_afex_ttff <- afex::aov_ez(
+# Perform the repeated-measures ANOVA with `log_Disrup_time_fixation_sec` as the dependent variable
+anova_afex_ttff_log <- afex::aov_ez(
   id = "Participant",  # Random effect (each participant is measured multiple times)
-  dv = "Disrup_time_fixation_sec",  # Dependent variable: Time to First Fixation (seconds)
+  dv = "log_Disrup_time_fixation_sec",  # Dependent variable: Log Time to First Fixation (log-seconds)
   between = "Group",  # Between-subject factor: Group (Novice vs Expert)
   within = "Disruption_Category",  # Within-subject factor: Disruption Categories (Verbal, Physical, Lack of eagerness)
-  data = df_ttff_disrup  # The data frame that contains the TTFF data
+  data = df_ttff_disrup  # The data frame that contains the log-transformed TTFF data
 )
@@
 # Extract the ANOVA table
-anova_results_ttff <- as.data.frame(anova_afex_ttff$anova_table)
+anova_results_ttff_log <- as.data.frame(anova_afex_ttff_log$anova_table)
 
 # Recalculate generalized eta squared (η²) for effect size
-eta_squared_results_ttff <- effectsize::eta_squared(anova_afex_ttff, partial = FALSE)
+eta_squared_results_ttff_log <- effectsize::eta_squared(anova_afex_ttff_log, partial = FALSE)
 
 # Combine recalculated eta squared with the ANOVA table
-anova_table_apa_ttff <- anova_results_ttff %>%
+anova_table_apa_ttff_log <- anova_results_ttff_log %>%
   rownames_to_column(var = "Effect") %>%  # Move row names to a column
   left_join(
-    as.data.frame(eta_squared_results_ttff), 
+    as.data.frame(eta_squared_results_ttff_log), 
     by = c("Effect" = "Parameter")  # Match the correct columns
@@
 
-# Display the ANOVA table for Time to First Fixation
+# Display the ANOVA table for Log Time to First Fixation
 knitr::kable(
-  anova_table_apa_ttff,
-  caption = "Repeated-Measures ANOVA Results for Time to First Fixation (Including Effect Sizes)",
+  anova_table_apa_ttff_log,
+  caption = "Repeated-Measures ANOVA Results for Log-Transformed Time to First Fixation (Including Effect Sizes)",
   col.names = c("Effect", "Df1", "Df2", "F", "p", "η²"),
@@
 # Perform post-hoc pairwise comparisons for Disruption_Category (within-subject factor)
-post_hoc_disruption <- emmeans(anova_afex_ttff, pairwise ~ Disruption_Category)
+post_hoc_disruption <- emmeans(anova_afex_ttff_log, pairwise ~ Disruption_Category)
 
@@
 d_LackOfEagerness_vs_Physical <- CohenD(
-  x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Physical disruptions"],
+  x = df_ttff_disrup$log_Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_ttff_disrup$log_Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Physical disruptions"],
   na.rm = TRUE
@@
 d_LackOfEagerness_vs_Verbal <- CohenD(
-  x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Lack of eagerness to learn"],
-  y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Verbal disruptions"],
+  x = df_ttff_disrup$log_Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Lack of eagerness to learn"],
+  y = df_ttff_disrup$log_Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Verbal disruptions"],
   na.rm = TRUE
@@
 d_Physical_vs_Verbal <- CohenD(
-  x = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Physical disruptions"],
-  y = df_ttff_disrup$Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Verbal disruptions"],
+  x = df_ttff_disrup$log_Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Physical disruptions"],
+  y = df_ttff_disrup$log_Disrup_time_fixation_sec[df_ttff_disrup$Disruption_Category == "Verbal disruptions"],
   na.rm = TRUE
@@
 
+## Classroom Management Measures
+
 ### Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
@@
 
-### Self-evaluation (8 classroom management items, 8 presence items)
+### self-evaluations of disruption prevention and management competencies (5 classroom management items + 3 self-developed, 8 presence items)
 ```{r self-eval_8-8, echo=FALSE, results='asis'}

### 2025-01-30 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
xxxxx

@@
 ##################### GRI in MICRO-TEACHING UNIT ########################
+
+#################### Data Preparation ########################
+df_aoi_sum <- df_aoi %>%
+  filter(TOI == "Lesson") %>%
+  dplyr::select(
+    Group,
+    Participant,
+    Duration_of_interval,
+    starts_with("Total_duration_of_fixations"),
+    starts_with("Number_of_fixations"),
+    starts_with("Average_duration"),
+    -contains("Disruptive_Person")
+  ) %>%
+  rowwise() %>%
+  transmute(
+    Group = factor(Group, levels = c("Expert", "Novice"), labels = c("Experienced", "Inexperienced")),
+    Participant,
+    Duration_of_interval_min = Duration_of_interval / 60000,
+    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
+    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
+    Number_fixation_min_mtu = Sum_number_fixation / Duration_of_interval_min,
+    Avg_fixation_duration = Sum_duration_fixation / Sum_number_fixation
+  ) %>%
+  drop_na()
 
@@
 
+### Self-evaluations of disruption prevention and management competencies (5 classroom management items + 3 self-developed, 8 presence items)
+```{r self-eval_8-8, echo=FALSE, results='asis'}
+
+# Data Import and Preparation --------------------------------------------
+df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
+  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
+  mutate(
+    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
+    Participant = LI06_05  # Add new column "Participant"
+  ) %>%
+  arrange(Participant) %>% 
+  select(
+    Participant, 
+    Group, 
+    LM01_01:LM01_08,  # Classroom Management and Disruption Handling combined
+    LP01_01:LP01_08   # Presence
+  ) %>%
+  rename(
+    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
+    CM_06 = LM01_06, CM_07 = LM01_07, CM_08 = LM01_08,  # Renaming combined columns
+    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
+    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
+  ) %>%
+  na.omit()  # Remove NAs
+
+# Create Dataset for Plotting with Combined Scales -------------------------
+df_quest_long <- df_quest %>%
+  rowwise() %>%
+  transmute(
+    Group = Group,
+    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),  # Combine Classroom Management and Disruption Handling
+    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2),  # Excluding Participant column
+    `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, CM_06, CM_07, CM_08, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value
+  ) %>%
+  ungroup() %>%
+  pivot_longer(cols = c(`Classroom Management`, `Presence`, `Overall`),
+               names_to = "Scales Self-evaluation", values_to = "Mean")
+
+# Plot Mean Scores by Group ----------------------------------------------
+quest_plot <- df_quest_long %>%
+  mutate(
+    Group = factor(Group, levels = c("Novice", "Expert")),
+    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management + 3 Items", "Presence", "Overall"))  # Reorder scales
+  ) %>%
+  ggplot(aes(x = Group, y = Mean)) +
+  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
+  geom_point(
+    size = 1,
+    alpha = 0.4,
+    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
+  ) +
+  labs(x = "", y = "Mean Scores") +
+  ylim(0, 4) + 
+  scale_fill_brewer(palette = "RdBu") +
+  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
+  theme_cowplot() +
+  ggtitle("Self-Evaluation Scores") +
+  theme(
+    plot.title = element_text(size = 25, face = "bold"),
+    legend.title = element_text(size = 20),
+    legend.text = element_text(size = 15),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    strip.text.x = element_text(size = 8),
+    axis.title.y = element_text(size = 20)
+  )
+
+print(quest_plot)
+
+# # Create Dataset for Plotting with Overall Score Only -------------------------
+# df_quest_long <- df_quest %>%
+#   rowwise() %>%
+#   transmute(
+#     Group = Group,
+#     `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, CM_06, CM_07, CM_08, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Overall score only
+#   ) %>%
+#   ungroup()
+# 
+# # Plot Overall Mean Scores by Group ----------------------------------------------
+# quest_plot <- df_quest_long %>%
+#   mutate(
+#     Group = factor(Group, levels = c("Novice", "Expert"))
+#   ) %>%
+#   ggplot(aes(x = Group, y = Overall, fill = Group)) +
+#   geom_boxplot(outlier.shape = NA) +
+#   geom_point(
+#     size = 1,
+#     alpha = 0.4,
+#     position = position_jitter(seed = 1, width = 0.1, height = 0.1)
+#   ) +
+#   labs(x = "", y = "Overall Mean Score") +
+#   ylim(0, 4) + 
+#   scale_fill_brewer(palette = "RdBu") +
+#   theme_cowplot() +
+#   ggtitle("Overall Self-Evaluation Scores") +
+#   theme(
+#     plot.title = element_text(size = 25, face = "bold"),
+#     legend.title = element_text(size = 20),
+#     legend.text = element_text(size = 15),
+#     axis.text.x = element_blank(),
+#     axis.ticks.x = element_blank(),
+#     axis.title.y = element_text(size = 20)
+#   )
+# 
+# print(quest_plot)
+
+# t-Test and Effect Sizes ------------------------------------------------
+# t-Test Function for Long Format ----------------------------------------
+t_test_stats_long <- function(data, group_col, scale_filter, scale_name) {
+  # Subset Data for the Specific Scale
+  filtered_data <- data %>%
+    filter(`Scales Self-evaluation` == scale_filter)
+
+  # Check if there are exactly two levels in the group
+  if (length(unique(filtered_data[[group_col]])) != 2) {
+    warning(paste("Skipping t-test for", scale_name, ": Group must have exactly two levels"))
+    return(tibble(
+      `Scale` = scale_name,
+      `t-value` = NA,
+      `p-value` = NA,
+      `Cohen's d` = NA
+    ))
+  }
+
+  # Perform t-Test
+  t_test <- t.test(
+    Mean ~ get(group_col),
+    data = filtered_data,
+    var.equal = TRUE
+  )
+
+  # Calculate Cohen's d
+  cohen_d <- CohenD(
+    x = filtered_data %>% filter(!!rlang::sym(group_col) == "Expert") %>% pull(Mean),
+    y = filtered_data %>% filter(!!rlang::sym(group_col) == "Novice") %>% pull(Mean)
+  )
+
+  # Return Results
+  tibble(
+    `Scale` = scale_name,
+    `t-value` = round(t_test$statistic, 2),
+    `p-value` = round(t_test$p.value, 2),
+    `Cohen's d` = round(cohen_d, 2)
+  )
+}
+
+# Perform t-Tests for Each Scale
+t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
+t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management + 3 Items", "Classroom Management + 3 Items")
+t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")
+
+# Combine Results into a Single Table
+t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_presence)
+
+# Display Results in APA-Conform Table
+kable(t_test_results, caption = "t-Test and Effect Sizes for Self-Evaluation Scales") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+# Internal Consistency (Omega) -------------------------------------------
+# Helper Function for Omega Calculation
+calculate_omega_total <- function(data, scale_name) {
+  if (nrow(data) == 0 || ncol(data) == 0) {
+    warning(paste("No valid data for", scale_name))
+    return(NA)
+  }
+
+  # Try Omega Calculation
+  result <- tryCatch(
+    omega(data),
+    error = function(e) {
+      warning(paste("Omega calculation failed for", scale_name, ":", e$message))
+      return(NULL)
+    }
+  )
+
+  # Check if Result is Valid and Extract omega.tot
+  if (is.null(result) || !"omega.tot" %in% names(result)) {
+    warning(paste("Omega total not available for", scale_name))
+    return(NA)
+  }
+
+  return(round(result$omega.tot, 2))
+}
+
+### CLASSROOM MANAGEMENT -------------------------------------------------
+# Select relevant columns and remove NAs
+df_cm <- df_quest %>% select(starts_with("CM"))
+
+# Calculate omega for Classroom Management
+omega_cm <- calculate_omega_total(df_cm, "Classroom Management + 3 Items")
+
+### PRESENCE ------------------------------------------------------------
+# Select relevant columns and remove NAs
+df_presence <- df_quest %>% select(starts_with("P") & !starts_with("Participant"))
+
+# Calculate omega for Presence
+omega_presence <- calculate_omega_total(df_presence, "Presence")
+
+### OVERALL TEST -----------------------------------------------------
+# Select relevant columns and remove NAs (for overall evaluation)
+df_self_all <- df_quest %>%
+  select(starts_with("CM"), starts_with("P") & !starts_with("Participant")) %>%
+  mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
+  drop_na()
+
+# Calculate omega for Overall Evaluation
+omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation")
+
+### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
+# APA-Conform Table ------------------------------------------------------
+omega_results <- tibble(
+  Facet = c("Overall Evaluation", "Classroom Management + 3 Items", "Presence"),
+  `Omega Total` = c(omega_self_all, omega_cm, omega_presence)
+)
+
+# Display APA-Conform Table ----------------------------------------------
+kable(omega_results, caption = "Internal Consistency (Omega) for Self-evaluation") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+```
+
 ### Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
@@
 
-### self-evaluations of disruption prevention and management competencies (5 classroom management items + 3 self-developed, 8 presence items)
-```{r self-eval_8-8, echo=FALSE, results='asis'}
-
-# Data Import and Preparation --------------------------------------------
-df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
-  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
-  mutate(
-    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
-    Participant = LI06_05  # Add new column "Participant"
-  ) %>%
-  arrange(Participant) %>% 
-  select(
-    Participant, 
-    Group, 
-    LM01_01:LM01_08,  # Classroom Management and Disruption Handling combined
-    LP01_01:LP01_08   # Presence
-  ) %>%
-  rename(
-    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
-    CM_06 = LM01_06, CM_07 = LM01_07, CM_08 = LM01_08,  # Renaming combined columns
-    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
-    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
-  ) %>%
-  na.omit()  # Remove NAs
-
-# Create Dataset for Plotting with Combined Scales -------------------------
-df_quest_long <- df_quest %>%
-  rowwise() %>%
-  transmute(
-    Group = Group,
-    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),  # Combine Classroom Management and Disruption Handling
-    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2),  # Excluding Participant column
-    `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, CM_06, CM_07, CM_08, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Correct Overall value
-  ) %>%
-  ungroup() %>%
-  pivot_longer(cols = c(`Classroom Management`, `Presence`, `Overall`),
-               names_to = "Scales Self-evaluation", values_to = "Mean")
-
-# Plot Mean Scores by Group ----------------------------------------------
-quest_plot <- df_quest_long %>%
-  mutate(
-    Group = factor(Group, levels = c("Novice", "Expert")),
-    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Presence", "Overall"))  # Reorder scales
-  ) %>%
-  ggplot(aes(x = Group, y = Mean)) +
-  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
-  geom_point(
-    size = 1,
-    alpha = 0.4,
-    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
-  ) +
-  labs(x = "", y = "Mean Scores") +
-  ylim(0, 4) + 
-  scale_fill_brewer(palette = "RdBu") +
-  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
-  theme_cowplot() +
-  ggtitle("Self-Evaluation Scores") +
-  theme(
-    plot.title = element_text(size = 25, face = "bold"),
-    legend.title = element_text(size = 20),
-    legend.text = element_text(size = 15),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    strip.text.x = element_text(size = 8),
-    axis.title.y = element_text(size = 20)
-  )
-
-print(quest_plot)
-
-# t-Test and Effect Sizes ------------------------------------------------
-# t-Test Function for Long Format ----------------------------------------
-t_test_stats_long <- function(data, group_col, scale_filter, scale_name) {
-  # Subset Data for the Specific Scale
-  filtered_data <- data %>%
-    filter(`Scales Self-evaluation` == scale_filter)
-
-  # Check if there are exactly two levels in the group
-  if (length(unique(filtered_data[[group_col]])) != 2) {
-    warning(paste("Skipping t-test for", scale_name, ": Group must have exactly two levels"))
-    return(tibble(
-      `Scale` = scale_name,
-      `t-value` = NA,
-      `p-value` = NA,
-      `Cohen's d` = NA
-    ))
-  }
-
-  # Perform t-Test
-  t_test <- t.test(
-    Mean ~ get(group_col),
-    data = filtered_data,
-    var.equal = TRUE
-  )
-
-  # Calculate Cohen's d
-  cohen_d <- CohenD(
-    x = filtered_data %>% filter(!!rlang::sym(group_col) == "Expert") %>% pull(Mean),
-    y = filtered_data %>% filter(!!rlang::sym(group_col) == "Novice") %>% pull(Mean)
-  )
-
-  # Return Results
-  tibble(
-    `Scale` = scale_name,
-    `t-value` = round(t_test$statistic, 2),
-    `p-value` = round(t_test$p.value, 2),
-    `Cohen's d` = round(cohen_d, 2)
-  )
-}
-
-# Perform t-Tests for Each Scale
-t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
-t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
-t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")
-
-# Combine Results into a Single Table
-t_test_results <- bind_rows(t_test_all, t_test_cm, t_test_presence)
-
-# Display Results in APA-Conform Table
-kable(t_test_results, caption = "t-Test and Effect Sizes for Self-Evaluation Scales") %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
-# Internal Consistency (Omega) -------------------------------------------
-# Helper Function for Omega Calculation
-calculate_omega_total <- function(data, scale_name) {
-  if (nrow(data) == 0 || ncol(data) == 0) {
-    warning(paste("No valid data for", scale_name))
-    return(NA)
-  }
-
-  # Try Omega Calculation
-  result <- tryCatch(
-    omega(data),
-    error = function(e) {
-      warning(paste("Omega calculation failed for", scale_name, ":", e$message))
-      return(NULL)
-    }
-  )
-
-  # Check if Result is Valid and Extract omega.tot
-  if (is.null(result) || !"omega.tot" %in% names(result)) {
-    warning(paste("Omega total not available for", scale_name))
-    return(NA)
-  }
-
-  return(round(result$omega.tot, 2))
-}
-
-### CLASSROOM MANAGEMENT -------------------------------------------------
-# Select relevant columns and remove NAs
-df_cm <- df_quest %>% select(starts_with("CM"))
-
-# Calculate omega for Classroom Management
-omega_cm <- calculate_omega_total(df_cm, "Classroom Management")
-
-### PRESENCE ------------------------------------------------------------
-# Select relevant columns and remove NAs
-df_presence <- df_quest %>% select(starts_with("P") & !starts_with("Participant"))
-
-# Calculate omega for Presence
-omega_presence <- calculate_omega_total(df_presence, "Presence")
-
-### OVERALL TEST -----------------------------------------------------
-# Select relevant columns and remove NAs (for overall evaluation)
-df_self_all <- df_quest %>%
-  select(starts_with("CM"), starts_with("P") & !starts_with("Participant")) %>%
-  mutate(across(everything(), as.numeric)) %>%  # Ensure numeric data
-  drop_na()
-
-# Calculate omega for Overall Evaluation
-omega_self_all <- calculate_omega_total(df_self_all, "Overall Evaluation")
-
-### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
-# APA-Conform Table ------------------------------------------------------
-omega_results <- tibble(
-  Facet = c("Overall Evaluation", "Classroom Management", "Presence"),
-  `Omega Total` = c(omega_self_all, omega_cm, omega_presence)
-)
-
-# Display APA-Conform Table ----------------------------------------------
-kable(omega_results, caption = "Internal Consistency (Omega) for Self-evaluation") %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
-```
-
 ## Correlations

### 2025-02-04 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
x paper

@@
   filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
-  drop_na() %>%
+  drop_na()
+
+# Count total observations before filtering
+total_count <- nrow(df_ttff_disrup)
+
+# Count dropouts due to filtering conditions
+dropout_count <- df_ttff_disrup %>%
+  filter(Time_to_first_fixation.Disruptive_Person <= 0 | 
+         Time_to_first_fixation.Disruptive_Person > 30000) %>%
+  nrow()
+
+dropout_percentage <- round((dropout_count / total_count) * 100, 2)
+
+# Print the number and percentage of dropouts
+cat("Number of dropouts due to filtering conditions:", dropout_count, "(", dropout_percentage, "%)\n")
+
+# Apply final filtering
+df_ttff_disrup <- df_ttff_disrup %>%
   filter(
@@
              caption = "N, M, SD, Min & Max Log-Transformed Time to First Fixation (AOI Disruptive Student)") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
+
+##################### t-Test and Cohen's d ########################
+
+# Perform independent t-test
+log_t_test_ttff <- t.test(log_Disrup_time_fixation_sec ~ Group, 
+                          data = df_ttff_disrup_participant_summary, 
+                          var.equal = TRUE)
+
+# Compute Cohen's d
+log_cohen_d_ttff <- cohen.d(log_Disrup_time_fixation_sec ~ Group, 
+                            data = df_ttff_disrup_participant_summary)
+
+# Create APA-style table
+log_t_test_result_ttff <- data.frame(
+  "Group Comparison" = "Novice vs. Expert",
+  "t-value" = round(log_t_test_ttff$statistic, 2),
+  "df" = log_t_test_ttff$parameter,
+  "p-value" = format.pval(log_t_test_ttff$p.value, digits = 2, eps = .05),
+  "Mean Difference" = round(log_t_test_ttff$estimate[1] - log_t_test_ttff$estimate[2], 2),
+  "Cohen's d" = round(log_cohen_d_ttff$estimate, 2),
+  "95% CI (d)" = paste0("[", round(log_cohen_d_ttff$conf.int[1], 2), ", ", 
+                         round(log_cohen_d_ttff$conf.int[2], 2), "]")
+)
+
+# Display APA table
+knitr::kable(log_t_test_result_ttff, 
+             caption = "t-Test and Effect Size for Log-Transformed Time to First Fixation (AOI Disruptive Student)") %>%
   kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

### 2025-02-04 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
xxxx

@@
 
+# Create APA-Conform Table for Overall Evaluation
+overall_summary <- df_quest_long %>%
+  filter(`Scales Self-evaluation` == "Overall") %>%
+  group_by(Group) %>%
+  summarise(
+    N = n(),
+    M = round(mean(Mean, na.rm = TRUE), 2),
+    SD = round(sd(Mean, na.rm = TRUE), 2),
+    Min = round(min(Mean, na.rm = TRUE), 2),
+    Max = round(max(Mean, na.rm = TRUE), 2)
+  )
+
+# Display the table in APA format
+kable(overall_summary, caption = "Descriptive Statistics for Overall Evaluation") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
 # Create Dataset for Plotting with Combined Scales -------------------------
@@
     Group = factor(Group, levels = c("Novice", "Expert")),
-    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management + 3 Items", "Presence", "Overall"))  # Reorder scales
+    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Presence", "Overall"))  # Reorder scales
   ) %>%
@@
 t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
-t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management + 3 Items", "Classroom Management + 3 Items")
+t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
 t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")
@@
 # Calculate omega for Classroom Management
-omega_cm <- calculate_omega_total(df_cm, "Classroom Management + 3 Items")
+omega_cm <- calculate_omega_total(df_cm, "Classroom Management")
 
@@
 omega_results <- tibble(
-  Facet = c("Overall Evaluation", "Classroom Management + 3 Items", "Presence"),
+  Facet = c("Overall Evaluation", "Classroom Management", "Presence"),
   `Omega Total` = c(omega_self_all, omega_cm, omega_presence)
@@
 
-# Data Import and Preprocessing ------------------------------------------
-sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
-  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+# Read the dataset
+sri <- read_excel("data/Coding_SRI.xlsx") %>%
   filter(
@@
     Group = ifelse(ID < 200, "Novice", "Expert"),  # Create a Group column based on ID
-    ID = as.factor(ID)  # Ensure that ID is treated as a factor (if needed)
+    ID = as.factor(ID)  # Convert ID to factor if needed
   )
@@
   summarise(
-    N = n(),
+    n_distinct(ID),
     M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
@@
   summarise(
-    N = n(),
+    n_distinct(ID),
     M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
@@
 
-## Prevalence Rating by Group
-sri_preva_table <- sri %>%
-  group_by(Group) %>%
-  summarise(
-    N = n(),
-    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
-    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
-    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
-    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
-  )
-
-## Prevalence Rating by Disruption Category (Split by Novice and Expert)
-sri_preva_category_table <- df_sri_disrup %>%
-  group_by(Group, Disruption_Category) %>%
-  summarise(
-    N = n(),
-    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
-    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
-    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
-    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
-  )
-
-## Prevalence Rating for each disruption event
-sri_preva_single_table <- sri %>%
-  group_by(Group, event) %>%
-  summarise(
-    N = n(),
-    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
-    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
-    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
-    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
-  )
+# ## Prevalence Rating by Group
+# sri_preva_table <- sri %>%
+#   group_by(Group) %>%
+#   summarise(
+#     n_distinct(ID),
+#     M = round(mean(prevalence_rating, na.rm = TRUE), 2),
+#     SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
+#     Min = round(min(prevalence_rating, na.rm = TRUE), 2),
+#     Max = round(max(prevalence_rating, na.rm = TRUE), 2)
+#   )
+# 
+# ## Prevalence Rating by Disruption Category (Split by Novice and Expert)
+# sri_preva_category_table <- df_sri_disrup %>%
+#   group_by(Group, Disruption_Category) %>%
+#   summarise(
+#     n_distinct(ID),
+#     M = round(mean(prevalence_rating, na.rm = TRUE), 2),
+#     SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
+#     Min = round(min(prevalence_rating, na.rm = TRUE), 2),
+#     Max = round(max(prevalence_rating, na.rm = TRUE), 2)
+#   )
+# 
+# ## Prevalence Rating for each disruption event
+# sri_preva_single_table <- sri %>%
+#   group_by(Group, event) %>%
+#   summarise(
+#     N = n(),
+#     M = round(mean(prevalence_rating, na.rm = TRUE), 2),
+#     SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
+#     Min = round(min(prevalence_rating, na.rm = TRUE), 2),
+#     Max = round(max(prevalence_rating, na.rm = TRUE), 2)
+#   )
 
@@
 
-## Prevalence Rating by Group
-kable(sri_preva_table, caption = "Descriptive Statistics for Prevalence Rating", digits = 2) %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
-## Prevalence Rating by Disruption Category (Split by Novice and Expert)
-kable(sri_preva_category_table, caption = "Descriptive Statistics for Prevalence Rating by Disruption Category", digits = 2) %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
-## Prevalence Rating for each disruption event (Sorted by Mean)
-kable(sri_preva_single_table_sorted, caption = "Descriptive Statistics for Prevalence Rating by Disruption Event (Sorted by Mean)", digits = 2) %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+# ## Prevalence Rating by Group
+# kable(sri_preva_table, caption = "Descriptive Statistics for Prevalence Rating", digits = 2) %>%
+#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+# 
+# ## Prevalence Rating by Disruption Category (Split by Novice and Expert)
+# kable(sri_preva_category_table, caption = "Descriptive Statistics for Prevalence Rating by Disruption Category", digits = 2) %>%
+#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+# 
+# ## Prevalence Rating for each disruption event (Sorted by Mean)
+# kable(sri_preva_single_table_sorted, caption = "Descriptive Statistics for Prevalence Rating by Disruption Event (Sorted by Mean)", digits = 2) %>%
+#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
 
@@
 
-## Prevalence Rating
-preva_plot <- sri %>%
-  ggplot(aes(x = Group, y = prevalence_rating, fill = Group)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
-  labs(x = "", y = "Prevalence Rating") +
-  scale_fill_brewer(palette = "RdBu") +  # Using the RdBu color palette for Novice and Expert
-  ggtitle("Prevalence Rating by Group") +
-  theme_cowplot() +
-  theme(legend.position = "none")  # No legend for the main plot
-
-print(preva_plot)
-
-## Prevalence Rating by Disruption Category, Split by ID (Novice vs Expert)
-preva_cat_plot <- df_sri_disrup %>%
-  ggplot(aes(x = Disruption_Category, y = prevalence_rating, fill = Group)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
-  labs(x = "", y = "Prevalence Rating") +
-  scale_fill_brewer(palette = "RdBu") +  # Use the same RdBu color palette as in preva_plot
-  ggtitle("Prevalence Rating by Disruption Category") +
-  theme_cowplot() +
-  theme(legend.position = "top") +  # Place the legend at the top
-  scale_fill_discrete(name = "Group")  # Add a title to the legend
-
-print(preva_cat_plot)
+# ## Prevalence Rating
+# preva_plot <- sri %>%
+#   ggplot(aes(x = Group, y = prevalence_rating, fill = Group)) +
+#   geom_boxplot(outlier.shape = NA) +
+#   geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
+#   labs(x = "", y = "Prevalence Rating") +
+#   scale_fill_brewer(palette = "RdBu") +  # Using the RdBu color palette for Novice and Expert
+#   ggtitle("Prevalence Rating by Group") +
+#   theme_cowplot() +
+#   theme(legend.position = "none")  # No legend for the main plot
+# 
+# print(preva_plot)
+# 
+# ## Prevalence Rating by Disruption Category, Split by ID (Novice vs Expert)
+# preva_cat_plot <- df_sri_disrup %>%
+#   ggplot(aes(x = Disruption_Category, y = prevalence_rating, fill = Group)) +
+#   geom_boxplot(outlier.shape = NA) +
+#   geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
+#   labs(x = "", y = "Prevalence Rating") +
+#   scale_fill_brewer(palette = "RdBu") +  # Use the same RdBu color palette as in preva_plot
+#   ggtitle("Prevalence Rating by Disruption Category") +
+#   theme_cowplot() +
+#   theme(legend.position = "top") +  # Place the legend at the top
+#   scale_fill_discrete(name = "Group")  # Add a title to the legend
+# 
+# print(preva_cat_plot)
+
+# Ensure no duplicates (keeping one row per participant)
+sri_clean <- sri %>%
+  group_by(ID) %>%
+  summarise(
+    Group = first(Group),
+    disruption_appraisal = mean(disruption_appraisal, na.rm = TRUE),
+    confidence_appraisal = mean(confidence_appraisal, na.rm = TRUE)
+  ) %>%
+  ungroup()
+
+# Check the number of unique participants
+print(nrow(sri_clean))  # Should be 82
+
+# t-Test for Disruption Appraisal
+t_test_disrup <- t.test(disruption_appraisal ~ Group, data = sri_clean, var.equal = TRUE)
+cohen_d_disrup <- cohen.d(disruption_appraisal ~ Group, data = sri_clean)
+
+# t-Test for Confidence Appraisal
+t_test_confi <- t.test(confidence_appraisal ~ Group, data = sri_clean, var.equal = TRUE)
+cohen_d_confi <- cohen.d(confidence_appraisal ~ Group, data = sri_clean)
+
+# Create APA-Formatted Table
+t_test_results <- data.frame(
+  "Group Comparison" = c("Experienced vs. Inexperienced", "Experienced vs. Inexperienced"),
+  "Variable" = c("Disruption Appraisal", "Confidence Appraisal"),
+  "t-value" = round(c(t_test_disrup$statistic, t_test_confi$statistic), 2),
+  "df" = c(t_test_disrup$parameter, t_test_confi$parameter),
+  "p-value" = format.pval(c(t_test_disrup$p.value, t_test_confi$p.value), digits = 3, eps = .001),
+  "Mean Difference" = round(c(
+    diff(t_test_disrup$estimate), 
+    diff(t_test_confi$estimate)
+  ), 2),
+  "Cohen's d" = round(c(cohen_d_disrup$estimate, cohen_d_confi$estimate), 2),
+  "95% CI (d)" = c(
+    paste0("[", round(cohen_d_disrup$conf.int[1], 2), ", ", round(cohen_d_disrup$conf.int[2], 2), "]"),
+    paste0("[", round(cohen_d_confi$conf.int[1], 2), ", ", round(cohen_d_confi$conf.int[2], 2), "]")
+  )
+)
+
+# Print APA-formatted Table
+knitr::kable(t_test_results, caption = "t-Test and Effect Sizes for Disruption and Confidence Ratings") %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
 
@@
 # Data Import
-sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
-  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+sri <- read_excel("data/Coding_SRI.xlsx") %>%
   filter(
@@
                                     sum(c_across(starts_with("Number_of")), na.rm = TRUE), 0),
-    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, 2)
+    GRI = round(Average_duration_mtu / Number_fixation_min_mtu, 2)
   ) %>%
@@
         Average_duration_mtu,
-        GRI_mtu) %>% 
+        GRI) %>% 
   arrange(Participant)
@@
          Stud_number_fixation_min,
-         Average_duration_stud
          ) %>% 
@@
 
-# Number of fixations per second and Average duration of fixations --------------------------------------------
-# Define the different types of disruptions and categories
-disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
-                 "Drumming_with_hands", "Head_on_table", "Heckling", 
-                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
+# Time to first fixation on AOI Disruptive Student --------------------------------------------
+
+# Define disruptions and categories
 verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
@@
 
-# Step 1: Filter and prepare the data for both fixation counts and average durations
-df_aoi_disrup <- df_aoi %>%
-  filter(TOI %in% disruptions) %>%  # Filter rows based on the disruption list
-  select(Group, Participant, TOI, 
-         Duration_of_interval, 
-         "Number_of_fixations.Disruptive_Person", 
-         "Total_duration_of_fixations.Disruptive_Person") %>%
-  mutate(
-    Group = as_factor(Group),  # Convert Group column to a factor
-    Disruption_Category = case_when(  # Assign categories based on disruption type
-      TOI %in% verbal_disruptions ~ "Verbal disruptions",
-      TOI %in% physical_disruptions ~ "Physical disruptions",
-      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
-      TRUE ~ NA_character_
-    ),
-    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),  # Convert duration to seconds
-    Disrup_average_fixations = round(Total_duration_of_fixations.Disruptive_Person / 
-                                     `Number_of_fixations.Disruptive_Person`, 2)  # Average duration in seconds
-  ) %>%
-  filter(!is.na(Disruption_Category))  # Remove rows with NA in disruption category
-
-# Step 2: Summarize data by disruption category
-disruption_summary <- df_aoi_disrup %>%
-  group_by(Group, Participant, Disruption_Category) %>%
-  summarise(
-    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2),  # Total time in seconds
-    fixation_count = round(sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE), 2),  # Total fixations
-    Disrup_fixations_per_second = round(fixation_count / total_duration_sec, 2),  # Number of Fixation per second
-    Disrup_average_fixations = round(mean(Disrup_average_fixations, na.rm = TRUE), 2),  # Average disruption fixations duration
-    .groups = "drop"
-  )
-
-# Step 3: Summarize by participant
-df_aoi_disrup <- disruption_summary %>%
-  group_by(Group, Participant) %>%
-  summarise(
-    Disrup_fixations_per_second = round(mean(Disrup_fixations_per_second, na.rm = TRUE), 2),  # Mean Number of Fixation per participant
-    Disrup_average_fixations = round(mean(Disrup_average_fixations, na.rm = TRUE), 2),  # Mean disruption fixation duration per participant
-    .groups = "drop"
-  ) %>% 
-  select(Participant, Disrup_fixations_per_second, Disrup_average_fixations) %>%  # Select only relevant columns
-  arrange(Participant)
-
-# Time to first fixation on AOI Disruptive Student --------------------------------------------
 # Step 1: Data Preparation
@@
   filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
-  drop_na() %>%
+  drop_na()
+
+# Apply final filtering
+df_ttff_disrup <- df_ttff_disrup %>%
   filter(
@@
   summarise(
-    Disrup_time_fixation_sec = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average time to first fixation per participant
+    log_Disrup_time_fixation_sec = round(mean(log_Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average log time to first fixation per participant
     .groups = "drop"
-  ) %>% 
-  arrange(Participant)
+  )
 
@@
 # Data Import and Preprocessing ------------------------------------------
-df_sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
-  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
+df_sri <- read_excel("data/Coding_SRI.xlsx") %>%
   filter(
@@
     Participant = ID,  # Keep ID as is for Participant column
-    Disruption_Appraisal = as.numeric(disruption_appraisal),
-    Confidence_Appraisal = as.numeric(confidence_appraisal),
+    Disruption_Rating = as.numeric(disruption_appraisal),
+    Confidence_Rating = as.numeric(confidence_appraisal),
     Prevalence_Rating = as.numeric(prevalence_rating)
@@
 
-# Step 1: Filter for specific disruptions
-verbal_disruptions <- c("whispering", "chatting")
-lack_of_eagerness <- c("drawing", "looking at phone")
-
-# Step 2: Summarize appraisals for each disruption
+# Step 1: Summarize appraisals for each disruption
 df_sri_disrup_summary <- df_sri %>%
@@
 
-# Step 3: Summarize overall appraisals by Participant
+# Step 2: Summarize overall appraisals by Participant
 df_sri_clean <- df_sri %>%
@@
   summarise(
-    Disruption_Appraisal = round(mean(Disruption_Appraisal, na.rm = TRUE), 2),
-    Confidence_Appraisal = round(mean(Confidence_Appraisal, na.rm = TRUE), 2),
-    Prevalence_Rating = round(mean(Prevalence_Rating, na.rm = TRUE), 2),
+    Disruption_Rating = round(mean(Disruption_Rating, na.rm = TRUE), 2),
+    Confidence_Rating = round(mean(Disruption_Rating, na.rm = TRUE), 2),
     .groups = "drop"
@@
   mutate(
-    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
-    Participant = LI06_05  # Add new column "Participant"
+    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Define groups
+    Participant = LI06_05  # Create a new Participant column
   ) %>%
@@
     Group, 
-    LM01_01:LM01_08,  # Classroom Management and Disruption Handling combined
-    LP01_01:LP01_08   # Presence
-  ) %>%
-  rename(
-    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
-    CM_06 = LM01_06, CM_07 = LM01_07, CM_08 = LM01_08,  # Renaming combined columns
-    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
-    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
-  ) %>%
-  na.omit()  # Remove NAs
-
-# Summarize the scales to a mean per participant, rounded to 2 decimals
+    starts_with("LM01"),  # Classroom Management and Disruption Handling
+    starts_with("LP01")   # Presence
+  ) %>%
+  na.omit()  # Remove rows with missing values
+
+# Summarize the scales to an overall mean per participant
 df_quest_summary <- df_quest %>%
   mutate(
-    # Calculate mean for Classroom Management (CM)
-    Self_Eval_CM = round(rowMeans(select(., starts_with("CM")), na.rm = TRUE), 2),
-    # Calculate mean for Presence (P), excluding the Participant column
-    Self_Eval_Presence = round(rowMeans(select(., starts_with("P"))[, -1], na.rm = TRUE), 2) # Exclude Participant column
-  ) %>%
-  select(Participant, Self_Eval_CM, Self_Eval_Presence) %>% # Keep Participant and means for each scale
+    # Calculate the overall self-evaluation mean across all classroom management and presence subscales
+    Self_Eval_Overall = round(rowMeans(select(., starts_with("LM01"), starts_with("LP01")), na.rm = TRUE), 2)
+  ) %>%
+  select(Participant, Self_Eval_Overall) %>%  # Keep only the overall self-evaluation score
   arrange(Participant)
@@
 df_aoi_stud <- df_aoi_stud %>% mutate(Participant = as.numeric(Participant))
-df_aoi_disrup <- df_aoi_disrup %>% mutate(Participant = as.numeric(Participant))
 df_ttff_disrup_participant_summary <- df_ttff_disrup_participant_summary %>% mutate(Participant = as.numeric(Participant))
@@
   df_aoi_stud,
-  df_aoi_disrup,
   df_ttff_disrup_participant_summary,
@@
 # 3. Correlation Analysis: Overall ---------------------------------------------
-
-# Select relevant variables for correlation analysis
-
+# 1. Select relevant variables for correlation analysis --------------------
 df_correlation <- df_merge %>%
   select(
-    Participant,
-    `Teaching Experience`, 
     Number_fixation_min_mtu, 
@@
     Stud_number_fixation_min,
-    Average_duration_stud, 
-    Disrup_fixations_per_second, 
-    Disrup_average_fixations, 
-    Disrup_time_fixation_sec, 
-    Disruption_Appraisal, 
-    Confidence_Appraisal, 
-    Prevalence_Rating,
-    Disruption_Appraisal_Mean_chatting,
-    Disruption_Appraisal_Mean_drawing,
-    Disruption_Appraisal_Mean_whispering,
-    Confidence_Appraisal_Mean_chatting,
-    Confidence_Appraisal_Mean_drawing,
-    Confidence_Appraisal_Mean_whispering,
+    log_Disrup_time_fixation_sec,
+    Disruption_Rating, 
+    Confidence_Rating, 
     SJT_All, 
-    SJT_Monitoring, 
-    Self_Eval_CM, 
-    Self_Eval_Presence
-  )
-
-# Compute correlation coefficients and p-values for the full dataset
+    Self_Eval_Overall
+  ) %>%
+  drop_na()  # Remove rows with missing values for accurate correlation
+
+# 2. Compute correlation coefficients and p-values ------------------------
 cor_results <- rcorr(as.matrix(df_correlation))
-cor_matrix <- as.data.frame(cor_results$r)  # Extract correlation coefficients
-p_matrix <- as.data.frame(cor_results$P)   # Extract p-values
-
-# Reshape correlation coefficients and p-values into a tidy format
-correlation_pvalues <- cor_matrix %>%
-  rownames_to_column(var = "Variable1") %>%
-  pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
+cor_matrix <- cor_results$r  # Extract correlation coefficients
+p_matrix <- cor_results$P    # Extract p-values
+
+# 3. Reshape correlation coefficients and p-values into a tidy format -----
+correlation_pvalues <- as.data.frame(as.table(cor_matrix)) %>%
+  rename(Variable1 = Var1, Variable2 = Var2, Correlation = Freq) %>%
   left_join(
-    p_matrix %>%
-      rownames_to_column(var = "Variable1") %>%
-      pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
+    as.data.frame(as.table(p_matrix)) %>%
+      rename(Variable1 = Var1, Variable2 = Var2, P_value = Freq),
     by = c("Variable1", "Variable2")
   ) %>%
+  filter(Variable1 != Variable2) %>%  # Remove redundant self-correlations
   mutate(
     Correlation = round(Correlation, 2),  # Round correlation coefficients
-    P_value = round(P_value, 2),          # Round p-values
-    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))  # Format APA style
-  )
-
-# Create an APA-style table
+    P_value = round(P_value, 3),          # Round p-values
+    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))  # APA formatting
+  )
+
+# 4. Create an APA-style correlation table --------------------------------------------
 correlation_table <- correlation_pvalues %>%
@@
 
-# Display the table
-kable(correlation_table, format = "html", caption = "Correlation Table: Overall") %>%
-  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
-
-# 4. Correlation Analysis: Experts ---------------------------------------------
-
-# Filter data for Experts (Participants with ID > 200)
-df_experts <- df_merge %>%
-  filter(Participant > 200) %>% 
-  select(-Participant)
-
-# Compute correlation coefficients and p-values for Experts
-cor_results_experts <- rcorr(as.matrix(df_experts))
-cor_matrix_experts <- as.data.frame(cor_results_experts$r)  # Extract correlation coefficients
-p_matrix_experts <- as.data.frame(cor_results_experts$P)   # Extract p-values
-
-# Reshape data into tidy format for Experts
-correlation_pvalues_experts <- cor_matrix_experts %>%
-  rownames_to_column(var = "Variable1") %>%
-  pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
-  left_join(
-    p_matrix_experts %>%
-      rownames_to_column(var = "Variable1") %>%
-      pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
-    by = c("Variable1", "Variable2")
-  ) %>%
-  mutate(
-    Correlation = round(Correlation, 2),
-    P_value = round(P_value, 2),
-    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
-  )
-
-# Create an APA-style table for Experts
-correlation_table_experts <- correlation_pvalues_experts %>%
-  select(Variable1, Variable2, APA_Format) %>%
-  pivot_wider(
-    names_from = Variable2,
-    values_from = APA_Format
-  )
-
-# Display the Experts table
-kable(correlation_table_experts, format = "html", caption = "Correlation Table: Experts") %>%
-  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
-
-# 5. Correlation Analysis: Novices ---------------------------------------------
-
-# Filter data for Novices (Participants with ID < 200)
-df_novices <- df_merge %>%
-  filter(Participant < 200) %>% 
-  select(-`Teaching Experience`,
-         -Participant)
-
-# Compute correlation coefficients and p-values for Novices
-cor_results_novices <- rcorr(as.matrix(df_novices))
-cor_matrix_novices <- as.data.frame(cor_results_novices$r)  # Extract correlation coefficients
-p_matrix_novices <- as.data.frame(cor_results_novices$P)   # Extract p-values
-
-# Reshape data into tidy format for Novices
-correlation_pvalues_novices <- cor_matrix_novices %>%
-  rownames_to_column(var = "Variable1") %>%
-  pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
-  left_join(
-    p_matrix_novices %>%
-      rownames_to_column(var = "Variable1") %>%
-      pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
-    by = c("Variable1", "Variable2")
-  ) %>%
-  mutate(
-    Correlation = round(Correlation, 2),
-    P_value = round(P_value, 2),
-    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
-  )
-
-# Create an APA-style table for Novices
-correlation_table_novices <- correlation_pvalues_novices %>%
-  select(Variable1, Variable2, APA_Format) %>%
-  pivot_wider(
-    names_from = Variable2,
-    values_from = APA_Format
-  )
-
-# Display the Novices table
-kable(correlation_table_novices, format = "html", caption = "Correlation Table: Novices") %>%
-  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
+# Ensure Variable1 is a factor to maintain order
+correlation_table$Variable1 <- factor(correlation_table$Variable1, levels = unique(correlation_table$Variable1))
+
+# Convert to flextable for APA formatting
+cor_flextable <- correlation_table %>%
+  flextable() %>%
+  theme_booktabs() %>%
+  autofit() %>%
+  set_caption("Table 1: Correlation Table (APA Format)")
+
+# Load required libraries
+library(officer)
+library(flextable)
+
+# Ensure flextable is properly formatted
+cor_flextable <- cor_flextable %>%
+  fontsize(size = 11, part = "all") %>%  # Set font size
+  bold(part = "header") %>%  # Make headers bold
+  align(align = "center", part = "all") %>%  # Center align the text
+  width(width = 1.5)  # Adjust column width
+
+# Print table to check before saving (Debugging Step)
+print(cor_flextable)
+
+# 5. Save the table as a Word document --------------------------------------
+doc <- read_docx() %>% 
+  body_add_par("Table 1: Correlation Table (APA Format)", style = "heading 1") %>%
+  body_add_par("", style = "Normal") %>%  # Add a blank space before the table
+  body_add_flextable(cor_flextable) %>%
+  body_add_par("", style = "Normal")  # Add blank space after the table
+
+# Save the document
+docx_path <- "Correlation_Table_APA.docx"
+save_as_docx(doc, path = docx_path)
+
+# Define the full file path explicitly
+docx_path <- file.path(getwd(), "Correlation_Table_APA.docx")
+
+# Save the document
+save_as_docx(doc, path = docx_path)
+
+# # 4. Correlation Analysis: Experts ---------------------------------------------
+# 
+# # Filter data for Experts (Participants with ID > 200)
+# df_experts <- df_merge %>%
+#   filter(Participant > 200) %>% 
+#   select(-Participant)
+# 
+# # Compute correlation coefficients and p-values for Experts
+# cor_results_experts <- rcorr(as.matrix(df_experts))
+# cor_matrix_experts <- as.data.frame(cor_results_experts$r)  # Extract correlation coefficients
+# p_matrix_experts <- as.data.frame(cor_results_experts$P)   # Extract p-values
+# 
+# # Reshape data into tidy format for Experts
+# correlation_pvalues_experts <- cor_matrix_experts %>%
+#   rownames_to_column(var = "Variable1") %>%
+#   pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
+#   left_join(
+#     p_matrix_experts %>%
+#       rownames_to_column(var = "Variable1") %>%
+#       pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
+#     by = c("Variable1", "Variable2")
+#   ) %>%
+#   mutate(
+#     Correlation = round(Correlation, 2),
+#     P_value = round(P_value, 2),
+#     APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
+#   )
+# 
+# # Create an APA-style table for Experts
+# correlation_table_experts <- correlation_pvalues_experts %>%
+#   select(Variable1, Variable2, APA_Format) %>%
+#   pivot_wider(
+#     names_from = Variable2,
+#     values_from = APA_Format
+#   )
+# 
+# # Display the Experts table
+# kable(correlation_table_experts, format = "html", caption = "Correlation Table: Experts") %>%
+#   kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
+# 
+# 
+# # 5. Correlation Analysis: Novices ---------------------------------------------
+# 
+# # Filter data for Novices (Participants with ID < 200)
+# df_novices <- df_merge %>%
+#   filter(Participant < 200) %>% 
+#   select(-`Teaching Experience`,
+#          -Participant)
+# 
+# # Compute correlation coefficients and p-values for Novices
+# cor_results_novices <- rcorr(as.matrix(df_novices))
+# cor_matrix_novices <- as.data.frame(cor_results_novices$r)  # Extract correlation coefficients
+# p_matrix_novices <- as.data.frame(cor_results_novices$P)   # Extract p-values
+# 
+# # Reshape data into tidy format for Novices
+# correlation_pvalues_novices <- cor_matrix_novices %>%
+#   rownames_to_column(var = "Variable1") %>%
+#   pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
+#   left_join(
+#     p_matrix_novices %>%
+#       rownames_to_column(var = "Variable1") %>%
+#       pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
+#     by = c("Variable1", "Variable2")
+#   ) %>%
+#   mutate(
+#     Correlation = round(Correlation, 2),
+#     P_value = round(P_value, 2),
+#     APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
+#   )
+# 
+# # Create an APA-style table for Novices
+# correlation_table_novices <- correlation_pvalues_novices %>%
+#   select(Variable1, Variable2, APA_Format) %>%
+#   pivot_wider(
+#     names_from = Variable2,
+#     values_from = APA_Format
+#   )
+# 
+# # Display the Novices table
+# kable(correlation_table_novices, format = "html", caption = "Correlation Table: Novices") %>%
+#   kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
 

### 2025-02-10 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
x paper

@@
     Participant = LI06_05,
-    `Teaching Experience` = LI04_01
+    # `Teaching Experience` = LI04_01
   ) %>%
@@
   mutate(
-    Group = ifelse(ID < 200, "Novice", "Expert"),  # Create a Group column based on ID
     Participant = ID,  # Keep ID as is for Participant column
     Disruption_Rating = as.numeric(disruption_appraisal),
-    Confidence_Rating = as.numeric(confidence_appraisal),
-    Prevalence_Rating = as.numeric(prevalence_rating)
-  ) %>%
-  select(-ID) %>% # Remove the original ID column after renaming
-  arrange(Participant)
-
-# Summarize the SRI Data for Disruptions and Overall Columns
-
-# Step 1: Summarize appraisals for each disruption
-df_sri_disrup_summary <- df_sri %>%
-  filter(event %in% c(verbal_disruptions, lack_of_eagerness)) %>%
-  group_by(Participant, event) %>%
-  summarise(
-    Disruption_Appraisal_Mean = mean(disruption_appraisal, na.rm = TRUE),
-    Confidence_Appraisal_Mean = mean(confidence_appraisal, na.rm = TRUE),
-    .groups = "drop"
-  ) %>%
-  pivot_wider(
-    names_from = event,
-    values_from = c(Disruption_Appraisal_Mean, Confidence_Appraisal_Mean),
-    names_sep = "_"
-  ) %>%
-  mutate(across(everything(), ~ replace_na(., 0))) %>%   # Replace missing values with 0
-  arrange(Participant)
-
-# Step 2: Summarize overall appraisals by Participant
-df_sri_clean <- df_sri %>%
+    Confidence_Rating = as.numeric(confidence_appraisal)
+    )%>%
+  select(Participant, 
+         Disruption_Rating,
+         Confidence_Rating) %>% # Remove the original ID column after renaming
+  arrange(Participant) %>%
   group_by(Participant) %>%
@@
     Disruption_Rating = round(mean(Disruption_Rating, na.rm = TRUE), 2),
-    Confidence_Rating = round(mean(Disruption_Rating, na.rm = TRUE), 2),
-    .groups = "drop"
-  ) %>%
-  arrange(Participant)
-
-# Combine both summaries (disruption-specific and overall)
-df_sri_combined <- full_join(df_sri_clean, df_sri_disrup_summary, by = "Participant")
+    Confidence_Rating = round(mean(Confidence_Rating, na.rm = TRUE), 2)
+  )
 
@@
 df_ttff_disrup_participant_summary <- df_ttff_disrup_participant_summary %>% mutate(Participant = as.numeric(Participant))
-df_sri_combined <- df_sri_combined %>% mutate(Participant = as.numeric(Participant))
+df_sri <- df_sri %>% mutate(Participant = as.numeric(Participant))
 df_sjt <- df_sjt %>% mutate(Participant = as.numeric(Participant))
@@
   df_ttff_disrup_participant_summary,
-  df_sri_combined,
+  df_sri,
   df_sjt,
@@
 
-# 3. Correlation Analysis: Overall ---------------------------------------------
-# 1. Select relevant variables for correlation analysis --------------------
-df_correlation <- df_merge %>%
+# Separate Data by Experience Level
+# Experienced teachers (ID > 200)
+df_correlation_experienced <- df_merge %>%
+  filter(Participant > 200) %>%
   select(
@@
     Average_duration_mtu, 
-    GRI_mtu, 
+    GRI, 
     Stud_number_fixation_min,
@@
   ) %>%
-  drop_na()  # Remove rows with missing values for accurate correlation
-
-# 2. Compute correlation coefficients and p-values ------------------------
-cor_results <- rcorr(as.matrix(df_correlation))
-cor_matrix <- cor_results$r  # Extract correlation coefficients
-p_matrix <- cor_results$P    # Extract p-values
-
-# 3. Reshape correlation coefficients and p-values into a tidy format -----
-correlation_pvalues <- as.data.frame(as.table(cor_matrix)) %>%
+  drop_na()
+
+# Inexperienced teachers (ID < 200)
+df_correlation_inexperienced <- df_merge %>%
+  filter(Participant < 200) %>%
+  select(
+    Average_duration_mtu,
+    Number_fixation_min_mtu, 
+    GRI, 
+    Stud_number_fixation_min,
+    log_Disrup_time_fixation_sec,
+    Disruption_Rating, 
+    Confidence_Rating, 
+    Self_Eval_Overall,
+    SJT_All
+  ) %>%
+  drop_na()
+
+# Compute Correlations for Experienced Teachers
+cor_results_experienced <- rcorr(as.matrix(df_correlation_experienced))
+cor_matrix_experienced <- cor_results_experienced$r
+p_matrix_experienced <- cor_results_experienced$P
+
+# Compute Correlations for Inexperienced Teachers
+cor_results_inexperienced <- rcorr(as.matrix(df_correlation_inexperienced))
+cor_matrix_inexperienced <- cor_results_inexperienced$r
+p_matrix_inexperienced <- cor_results_inexperienced$P
+
+# Reshape correlation coefficients and p-values into a tidy format for experienced teachers
+correlation_pvalues_experienced <- as.data.frame(as.table(cor_matrix_experienced)) %>%
   rename(Variable1 = Var1, Variable2 = Var2, Correlation = Freq) %>%
   left_join(
-    as.data.frame(as.table(p_matrix)) %>%
+    as.data.frame(as.table(p_matrix_experienced)) %>%
       rename(Variable1 = Var1, Variable2 = Var2, P_value = Freq),
@@
   ) %>%
-  filter(Variable1 != Variable2) %>%  # Remove redundant self-correlations
+  filter(Variable1 != Variable2) %>%
   mutate(
-    Correlation = round(Correlation, 2),  # Round correlation coefficients
-    P_value = round(P_value, 3),          # Round p-values
-    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))  # APA formatting
-  )
-
-# 4. Create an APA-style correlation table --------------------------------------------
-correlation_table <- correlation_pvalues %>%
+    Correlation = round(Correlation, 2),
+    P_value = round(P_value, 3),
+    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
+  )
+
+# Reshape correlation coefficients and p-values into a tidy format for inexperienced teachers
+correlation_pvalues_inexperienced <- as.data.frame(as.table(cor_matrix_inexperienced)) %>%
+  rename(Variable1 = Var1, Variable2 = Var2, Correlation = Freq) %>%
+  left_join(
+    as.data.frame(as.table(p_matrix_inexperienced)) %>%
+      rename(Variable1 = Var1, Variable2 = Var2, P_value = Freq),
+    by = c("Variable1", "Variable2")
+  ) %>%
+  filter(Variable1 != Variable2) %>%
+  mutate(
+    Correlation = round(Correlation, 2),
+    P_value = round(P_value, 3),
+    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
+  )
+
+# Create correlation tables for both groups
+correlation_table_experienced <- correlation_pvalues_experienced %>%
   select(Variable1, Variable2, APA_Format) %>%
-  pivot_wider(
-    names_from = Variable2,
-    values_from = APA_Format
-  )
+  pivot_wider(names_from = Variable2, values_from = APA_Format)
+
+correlation_table_inexperienced <- correlation_pvalues_inexperienced %>%
+  select(Variable1, Variable2, APA_Format) %>%
+  pivot_wider(names_from = Variable2, values_from = APA_Format)
 
 # Ensure Variable1 is a factor to maintain order
-correlation_table$Variable1 <- factor(correlation_table$Variable1, levels = unique(correlation_table$Variable1))
+correlation_table_experienced$Variable1 <- factor(correlation_table_experienced$Variable1, levels = unique(correlation_table_experienced$Variable1))
+correlation_table_inexperienced$Variable1 <- factor(correlation_table_inexperienced$Variable1, levels = unique(correlation_table_inexperienced$Variable1))
 
 # Convert to flextable for APA formatting
-cor_flextable <- correlation_table %>%
+cor_flextable_experienced <- correlation_table_experienced %>%
   flextable() %>%
@@
   autofit() %>%
-  set_caption("Table 1: Correlation Table (APA Format)")
-
-# Load required libraries
-library(officer)
-library(flextable)
-
-# Ensure flextable is properly formatted
-cor_flextable <- cor_flextable %>%
-  fontsize(size = 11, part = "all") %>%  # Set font size
-  bold(part = "header") %>%  # Make headers bold
-  align(align = "center", part = "all") %>%  # Center align the text
-  width(width = 1.5)  # Adjust column width
-
-# Print table to check before saving (Debugging Step)
-print(cor_flextable)
-
-# 5. Save the table as a Word document --------------------------------------
-doc <- read_docx() %>% 
-  body_add_par("Table 1: Correlation Table (APA Format)", style = "heading 1") %>%
-  body_add_par("", style = "Normal") %>%  # Add a blank space before the table
-  body_add_flextable(cor_flextable) %>%
-  body_add_par("", style = "Normal")  # Add blank space after the table
-
-# Save the document
-docx_path <- "Correlation_Table_APA.docx"
-save_as_docx(doc, path = docx_path)
-
-# Define the full file path explicitly
-docx_path <- file.path(getwd(), "Correlation_Table_APA.docx")
-
-# Save the document
-save_as_docx(doc, path = docx_path)
-
-# # 4. Correlation Analysis: Experts ---------------------------------------------
-# 
-# # Filter data for Experts (Participants with ID > 200)
-# df_experts <- df_merge %>%
-#   filter(Participant > 200) %>% 
-#   select(-Participant)
-# 
-# # Compute correlation coefficients and p-values for Experts
-# cor_results_experts <- rcorr(as.matrix(df_experts))
-# cor_matrix_experts <- as.data.frame(cor_results_experts$r)  # Extract correlation coefficients
-# p_matrix_experts <- as.data.frame(cor_results_experts$P)   # Extract p-values
-# 
-# # Reshape data into tidy format for Experts
-# correlation_pvalues_experts <- cor_matrix_experts %>%
-#   rownames_to_column(var = "Variable1") %>%
-#   pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
-#   left_join(
-#     p_matrix_experts %>%
-#       rownames_to_column(var = "Variable1") %>%
-#       pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
-#     by = c("Variable1", "Variable2")
-#   ) %>%
-#   mutate(
-#     Correlation = round(Correlation, 2),
-#     P_value = round(P_value, 2),
-#     APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
-#   )
-# 
-# # Create an APA-style table for Experts
-# correlation_table_experts <- correlation_pvalues_experts %>%
-#   select(Variable1, Variable2, APA_Format) %>%
-#   pivot_wider(
-#     names_from = Variable2,
-#     values_from = APA_Format
-#   )
-# 
-# # Display the Experts table
-# kable(correlation_table_experts, format = "html", caption = "Correlation Table: Experts") %>%
-#   kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
-# 
-# 
-# # 5. Correlation Analysis: Novices ---------------------------------------------
-# 
-# # Filter data for Novices (Participants with ID < 200)
-# df_novices <- df_merge %>%
-#   filter(Participant < 200) %>% 
-#   select(-`Teaching Experience`,
-#          -Participant)
-# 
-# # Compute correlation coefficients and p-values for Novices
-# cor_results_novices <- rcorr(as.matrix(df_novices))
-# cor_matrix_novices <- as.data.frame(cor_results_novices$r)  # Extract correlation coefficients
-# p_matrix_novices <- as.data.frame(cor_results_novices$P)   # Extract p-values
-# 
-# # Reshape data into tidy format for Novices
-# correlation_pvalues_novices <- cor_matrix_novices %>%
-#   rownames_to_column(var = "Variable1") %>%
-#   pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
-#   left_join(
-#     p_matrix_novices %>%
-#       rownames_to_column(var = "Variable1") %>%
-#       pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
-#     by = c("Variable1", "Variable2")
-#   ) %>%
-#   mutate(
-#     Correlation = round(Correlation, 2),
-#     P_value = round(P_value, 2),
-#     APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
-#   )
-# 
-# # Create an APA-style table for Novices
-# correlation_table_novices <- correlation_pvalues_novices %>%
-#   select(Variable1, Variable2, APA_Format) %>%
-#   pivot_wider(
-#     names_from = Variable2,
-#     values_from = APA_Format
-#   )
-# 
-# # Display the Novices table
-# kable(correlation_table_novices, format = "html", caption = "Correlation Table: Novices") %>%
-#   kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
+  set_caption("Table 1: Correlation Table for Experienced Teachers")
+
+cor_flextable_inexperienced <- correlation_table_inexperienced %>%
+  flextable() %>%
+  theme_booktabs() %>%
+  autofit() %>%
+  set_caption("Table 2: Correlation Table for Inexperienced Teachers")
 

### 2025-02-18 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
xxxx

@@
 
+### Correlation table for all participants
+
+# Define relevant columns for correlation analysis
+correlation_columns <- c(
+  "GRI", 
+  "Stud_number_fixation_min",
+  "log_Disrup_time_fixation_sec",
+  "Disruption_Rating", 
+  "Confidence_Rating", 
+  "SJT_All", 
+  "Self_Eval_Overall"
+)
+
+# Drop rows with missing values
+df_correlation_all <- df_merge %>%
+  select(all_of(correlation_columns)) %>%
+  drop_na()
+
+# Compute Pearson correlation matrix
+cor_results_all <- rcorr(as.matrix(df_correlation_all))
+
+# Extract correlation coefficients and p-values
+cor_matrix_all <- cor_results_all$r
+p_matrix_all <- cor_results_all$P
+
+# Convert correlation and p-value matrices into a tidy format
+correlation_pvalues_all <- as.data.frame(as.table(cor_matrix_all)) %>%
+  rename(Variable1 = Var1, Variable2 = Var2, Correlation = Freq) %>%
+  left_join(
+    as.data.frame(as.table(p_matrix_all)) %>%
+      rename(Variable1 = Var1, Variable2 = Var2, P_value = Freq),
+    by = c("Variable1", "Variable2")
+  ) %>%
+  filter(Variable1 != Variable2) %>%
+  mutate(
+    Correlation = round(Correlation, 2),
+    P_value = round(P_value, 3),
+    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
+  )
+
+# Reshape into a correlation table format
+correlation_table_all <- correlation_pvalues_all %>%
+  select(Variable1, Variable2, APA_Format) %>%
+  pivot_wider(names_from = Variable2, values_from = APA_Format)
+
+# Ensure Variable1 is a factor to maintain order
+correlation_table_all$Variable1 <- factor(correlation_table_all$Variable1, levels = unique(correlation_table_all$Variable1))
+
+# Create APA-styled table
+cor_flextable_all <- correlation_table_all %>%
+  flextable() %>%
+  theme_booktabs() %>%
+  autofit() %>%
+  set_caption("Table: Correlation Table for All Participants")
+
+# Print the table
+cor_flextable_all
+
 ```
